\entryitemWithDescription{\hskip 0pt{}Semi-automatic rifle ban passes Washington state Legislature}{https://apnews.com/article/adbbc5bc0d3b92da0122a91d42bcd4f6}{Customers look at AR-15-style rifles on a mostly empty display wall at Rainier Arms Friday, April 14, 2023, in Auburn, Wash. as stock dwindles before potential legislation that would ban future sale of the weapons in the state. House Bill...}

\entryitemWithDescription{\hskip 0pt{}Rare solar eclipse to cross remote Australia, Indonesia}{https://apnews.com/article/76c01e7b0dcd3154ba1250d8f0c73b59}{FILE - The progression of a hybrid solar eclipse is seen from Nairobi, Kenya, on Sunday, Nov. 3, 2013. A rare solar eclipse will cross over remote parts of Australia, Indonesia and East Timor on Thursday, April 20, 2023. The lucky few in...}

\entryitemWithDescription{\hskip 0pt{}Mystery solved: Scientists ID Caribbean sea urchin killer}{https://apnews.com/article/e328a797c9eedd725384dacc81a5e460}{In this photo provided by researchers, Cornell University graduate student Brayan Vilanova Cuevas collects a swab sample from the surface of corals in St. Thomas, U.S. Virgin Islands in September 2022. A tiny single-celled organism is to...}

\entryitemWithDescription{\hskip 0pt{}Antiquities, plucked from storeroom, on Roman Forum display}{https://apnews.com/article/61fc43bf42e8f96ed460193c0d785cbd}{An archaic antefix, the upright termination of roof drain lines, shaped as the head of a silenus, the mythological companion and tutor to the Greek wine god Dionysus, is on display in the Roman Forum in Rome, Wednesday, April 19, 2023...}

\entryitemWithDescription{\hskip 0pt{}US judge sends Hugo Chavez's ex nurse to prison for 15 years}{https://apnews.com/article/3ecd77594ae560707ea74de265c56c5b}{FILE - Claudia Patricia Diaz Guillen, the former nurse of former Venezuelan President Hugo Chavez, leaves the national court in Madrid, Spain, Sept. 24, 2018. A federal judge in South Florida will announce Guillen\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Foo Fighters plan summer album, first since drummer's death}{https://apnews.com/article/eee77f6cbee4d1be4283bae30f9a77e0}{FILE - In this Sept. 29, 2019, file photo, Dave Grohl of the band Foo Fighters performs at the Rock in Rio music festival in Rio de Janeiro, Brazil. Foo Fighters have announced a new album is in the works, the first since the death of the...}

\entryitemWithDescription{\hskip 0pt{}France's Macron heckled by crowd angry over pensions}{https://apnews.com/article/cda2cdee1f4095965c50bc3066175597}{French President Emmanuel Macron argues with a person opposed to the pension reform, in Selestat, eastern France, Wednesday, April 19, 2023. French President Emmanuel Macron said Monday April 17, 2023 that he heard people\textquotesingle...}

\entryitemWithDescription{\hskip 0pt{}Study: Milder autism far outpacing 'profound' diagnoses}{https://apnews.com/article/bc21057fabe11774843d4ac2197956a4}{FILE - An autistic boy holds the hand of his adoptive father as they prepare to leave for a family outing from their home in Springfield, Mass., on Saturday, Dec. 12, 2015. Traditionally, autism was diagnosed only in kids with severe...}

\entryitemWithDescription{\hskip 0pt{}Tesla cuts U.S. prices again ahead of 1Q earnings release}{https://apnews.com/article/a75540dc2ad3ef45d3c4e437b97b17b6}{FILE - A Tesla electric vehicle emblem is affixed to a passenger vehicle Sunday, Feb. 21, 2021, in Boston. Tesla is dropping prices for the third time since late last year in an apparent effort to attract new buyers. The cuts range from \$...}

\entryitemWithDescription{\hskip 0pt{}Cloud seeding catching on amid Rocky Mountain drought}{https://apnews.com/article/1857c4d1ccd79e79ee1955fafca837e0}{Carver Cammans installs cloud seeding equipment Saturday, Dec. 3, 2022, in Lyons, Colo. The technique to get clouds to produce more snow is being used more as the Rocky Mountain region struggles with a two-decade drought. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}Corporate volunteerism: 'Not charity. It's good business.'}{https://apnews.com/article/2ba8ff9604b2c65846445429e7f91a0f}{In this photo provided by The Marcy Lab School, co-founder Reuben Ogbonna, left, talks with co-founder Maya Bhattacharjee, second from right, and fellows from the New York-based school on its Brooklyn campus in November 2022. The fellows...}

\entryitemWithDescription{\hskip 0pt{}Chinese panda on long-term loan to Thailand dies suddenly}{https://apnews.com/article/bba0b7f8ade77d64ab1be73efd3724c8}{FILE - Lin Hui, a female Panda on a 10-year loan from China is seen eating bamboo at the Chiang Mai Zoo in Chiang Mai province, northern Thailand, on Sept. 23, 2005. Lin Hui, the giant panda, died Wednesday, April 19, 2023, six months...}

\entryitemWithDescription{\hskip 0pt{}Fatal Hawaii shooting shows dangers of popular cockfights}{https://apnews.com/article/7cfeda7617dabf9e1e1907d3b76cf132}{FILE - Cockfighting takes place in Toa Baja, Puerto Rico, on Dec. 18, 2019. Honolulu police have yet to make any arrests in a fatal shooting Saturday, April 15, 2023, that\textquotesingle s highlighting the dangers that come with...}