\entryitemWithDescription{\hskip 0pt{}NBA champion, `Survivor' contestant Scot Pollard receives heart transplant}{https://apnews.com/article/1de85b7ca3321de6f3a813d41846502b}{NBA champion and ``Survivor'' contestant Scot Pollard has had a heart transplant, his wife said on social media on Friday night. ``Scot has a new heart!'' Dawn Pollard posted on X, formerly known as Twitter. ``Surgery went well and I've...}

\entryitemWithDescription{\hskip 0pt{}Pennsylvania magistrate judge is charged with shooting her ex-boyfriend as he slept}{https://apnews.com/article/4eeb11249dd828c5919b4f324f8c4ff0}{HARRISBURG, Pa. (AP) --- A suspended magistrate judge in Pennsylvania shot her estranged boyfriend in the head as he slept last weekend, police said Thursday in filing attempted murder and aggravated assault charges against her. Tests...}

\entryitemWithDescription{\hskip 0pt{}Got back! Paul McCartney's stolen bass is found and returned to the Beatle after more than 50 years}{https://apnews.com/article/e192765ddab258ac228be06268be9137}{LONDON (AP) --- Paul McCartney no longer gently weeps for his original bass guitar. A five-year search by the manufacturer of the instrument that was aided by a husband-and-wife team of journalists helped reunite The Beatles star with the...}

\entryitemWithDescription{\hskip 0pt{}NASA's final tally shows spacecraft returned double the amount of asteroid rubble}{https://apnews.com/article/2ea5ff565570c4db8ad492ed67dc2037}{CAPE CANAVERAL, Fla. (AP) --- NASA finally has counted up all the asteroid samples returned by a spacecraft last fall --- and it's double the rubble return goal. Officials reported Thursday that the Osiris-Rex spacecraft collected 121.6...}

\entryitemWithDescription{\hskip 0pt{}Cambodia to install hundreds of wildlife cameras in an effort to restore its tiger population}{https://apnews.com/article/52a5a1f9d06a16383aad4143f29aee97}{PHNOM PENH, Cambodia (AP) --- Cambodia will begin installing hundreds of monitoring cameras and import four tigers from India as part of a plan to restore its tiger population, officials said Friday. Tigers were declared ``functionally...}

\entryitemWithDescription{\hskip 0pt{}National Archives working to clean up red powder dumped on Constitution display by protesters}{https://apnews.com/article/2a6dcfadbf35a3263887ac2fce1e813e}{WASHINGTON (AP) --- Conservationists at the National Archives are still working to clean up the building's rotunda area after a pair of apparent environmental protesters on Wednesday dumped reddish powder on the display case housing the...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry races head-first down a skeleton sled track and says `everybody should do this'}{https://apnews.com/article/1296c5af6e25c66f3f0292dd543a9340}{WHISTLER, British Columbia (AP) --- Prince Harry raced head-first on a tiny skeleton sled going 99 kph (61.5 mph) down a track at next year's Invictus Games site Thursday, saying with a smile afterward that everyone should do it. Harry...}

\entryitemWithDescription{\hskip 0pt{}Tiger Woods hits a shank in his return to golf and opens with 72 at Riviera}{https://apnews.com/article/3c18812eb57fc228dc347cdae94db121}{LOS ANGELES (AP) --- Any chance of Tiger Woods breaking par in his first official PGA Tour event in 10 months ended with one swing Thursday and a five-letter word he wasn't afraid to say. Shank. Woods said his back began to spasm over the...}

\entryitemWithDescription{\hskip 0pt{}OpenAI reveals Sora, a tool to make instant videos from written prompts}{https://apnews.com/article/9f5392735b01f40ac2797e638946904b}{SAN FRANCISCO (AP) --- The maker of ChatGPT on Thursday unveiled its next leap into generative artificial intelligence with a tool that instantly makes short videos in response to written commands. San Francisco-based OpenAI's new text-to...}

\entryitemWithDescription{\hskip 0pt{}A fin whale decomposing on an Oregon beach creates a sad but `super educational' spectacle}{https://apnews.com/article/df76257b9f1863e12e165192fb55e053}{It's not yet known what killed an endangered fin whale, but people can marvel at the large marine mammal as it decomposes on an Oregon beach. ``While it's sad, it's also super educational,'' Tiffany Boothe, assistant manager of the...}

\entryitemWithDescription{\hskip 0pt{}Alaska woman gets 99 years for orchestrating catfished murder-for-hire plot in friend's death}{https://apnews.com/article/38b54382bf9928fd47d20f88e92bf219}{ANCHORAGE, Alaska (AP) --- An Anchorage woman has been sentenced to 99 years in prison for orchestrating the death of a developmentally disabled woman in a murder-for-hire plot, hoping to cash in on a \$9 million offer from a Midwestern...}

\entryitemWithDescription{\hskip 0pt{}Godzilla, Oscar newbie, stomps into the Academy Awards}{https://apnews.com/article/75fac58852704fe1b71e1a84e701c27d}{NEW YORK (AP) --- Godzilla has been to Tokyo, Hong Kong, Paris, San Francisco, Boston, Moscow, London and Hawaii. But before now, he's never been to the Oscars. When the Academy Awards roll around on March 10, Godzilla will stretch its...}

\entryitemWithDescription{\hskip 0pt{}US eases restrictions on Wells Fargo after years of strict oversight following scandal}{https://apnews.com/article/d3f41b3dbab4de74462fd3fe2585d50e}{NEW YORK (AP) --- The Biden Administration eased some of the restrictions on banking giant Wells Fargo, saying the bank has sufficiently fixed its toxic culture after years of scandals. The news sent Wells Fargo's stock up sharply...}