\entryitemWithDescription{\hskip 0pt{}US confirms China has had a spy base in Cuba since at least 2019}{https://apnews.com/article/0f655b577ae4141bdbeabc35d628b18f}{FILE - The American and Chinese flags wave at Genting Snow Park ahead of the 2022 Winter Olympics, Feb. 2, 2022, in Zhangjiakou, China. China has been operating a spy base in Cuba since at least 2019, as part of a global effort by Beijing...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: June spreads LGBTQ+ Pride and rainbows around the world}{https://apnews.com/article/d08a40da8bfad1cdf5c77951899cc409}{A couple hold hands at they leave the Pride Parade, Saturday, June 10, 2023, in Indianapolis. (AP Photo/Darron Cummings) June is Pride Month, a season intended to celebrate the lives and experiences of LGBTQ+ people and to protest threats...}

\entryitemWithDescription{\hskip 0pt{}Brittney Griner, Mercury teammates confronted at airport by 'provocateur,' WNBA says}{https://apnews.com/article/3dff38ebc2f17f8382f18be155b8606f}{Phoenix Mercury\textquotesingle s Brittney Griner prepares for the team\textquotesingle s WNBA basketball game against the Dallas Wings, Wednesday, June 7, 2023, in Arlington, Texas. (AP Photo/Tony Gutierrez) DALLAS (AP) --- Brittney...}

\entryitemWithDescription{\hskip 0pt{}North Carolina GOP censures Sen. Tillis for supporting LGBTQ+ rights, immigration policies}{https://apnews.com/article/15f25266d24c0b15cb4d2a1c61037678}{FILE - U.S. Sen. Thom Tillis, R-N.C., speaks during a Senate Judiciary Committee business meeting on Feb. 16, 2023, on Capitol Hill in Washington. On Saturday, June 10, 2023, Republican delegates in North Carolina voted at their annual...}

\entryitemWithDescription{\hskip 0pt{}Biden marks LGBTQ+ Pride Month with celebration on White House South Lawn}{https://apnews.com/article/108f336660b46cb807dc8d1eea8ac2dc}{People walk on the South Lawn of the White House during a Pride Month celebration Saturday, June 10, 2023, in Washington. (AP Photo/Manuel Balce Ceneta) WASHINGTON (AP) --- President Joe Biden welcomed hundreds to the White House on...}

\entryitemWithDescription{\hskip 0pt{}James Cameron feels he 'walked into an ambush' in Argentine lithium dispute}{https://apnews.com/article/87b601e8ac89a06768dcbc3fa537c4f1}{Director James Cameron walks in Purmamarca, Jujuy province, Argentina, Thursday, June 8, 2023. The filmmaker arrived to Argentina to participate in a Sustainable Development Forum. (AP Photo/Javier Corbalan) BUENOS AIRES, Argentina...}

\entryitemWithDescription{\hskip 0pt{}Randy Cox, paralyzed in police van, reaches \$45 million settlement with New Haven, Connecticut}{https://apnews.com/article/852ed131cb9d7477c6a5c7d4bc1314ff}{FILE - In this image taken from police surveillance video provided by New Haven Police, Richard "Randy" Cox slides down the back of a police van while being transported after being detained by New Haven Police on June 19, 2022, in New...}

\entryitemWithDescription{\hskip 0pt{}Canadians fighting wildfires see hope in improving weather conditions}{https://apnews.com/article/37f2e9b980a88f7099ccc7a41b49ae1e}{The Capitol is seen at sunrise in Washington, Friday, June 9, 2023. While the air quality remains unhealthy, the record smoke pollution from wildfires in eastern Canada this week has diminished significantly over the nation...}

\entryitemWithDescription{\hskip 0pt{}Man City beats Inter Milan 1-0 to win first Champions League title and complete 3-trophy sweep}{https://apnews.com/article/e83c25f081ba6c28919615545f13eb2e}{Manchester City\textquotesingle s Ilkay Gundogan holds up the trophy after winning the Champions League final soccer match between Manchester City and Inter Milan at the Ataturk Olympic Stadium in Istanbul, Turkey, Sunday, June 11, 2023...}

\entryitemWithDescription{\hskip 0pt{}Troops feel the heat, and several faint, as Prince William reviews military parade}{https://apnews.com/article/f29bac9accf2e90759da66912ac7d0f7}{A trombone player of the military band is carried out on a stretcher after a faint during the Colonel\textquotesingle s Review, the final rehearsal of the Trooping the Colour, the King\textquotesingle s annual birthday parade, at Horse...}

\entryitemWithDescription{\hskip 0pt{}Boris Johnson's bombshell exit from Parliament leaves UK politics reeling}{https://apnews.com/article/5f325834b8fa8e93e66addc758ce115e}{FILE - Britain\textquotesingle s Prime Minister Boris Johnson returns to 10 Downing Street after meeting with Queen Elizabeth II at Buckingham Palace, London, on Friday, Dec. 13, 2019. Former U.K. Prime Minister Johnson says he's quitting...}

\entryitemWithDescription{\hskip 0pt{}Pope Francis takes doctors' advice to skip Sunday public blessing as he recovers from major surgery}{https://apnews.com/article/95ea88e41d0d8e50252fd08befdd30d3}{Candles with the image of Pope Francis are left at the entrance of the Agostino Gemelli University Polyclinic in Rome, Friday, June 9, 2023, where Francis is recovering after undergoing abdominal surgery on Wednesday. The Vatican says...}

\entryitemWithDescription{\hskip 0pt{}Indonesia's Anak Krakatau volcano spews ash, lava in new eruption}{https://apnews.com/article/e9b17c2b60ecd56047867a6ebb352b59}{In this image made from video released by Indonesia\textquotesingle s Center for Volcanology and Geological Disaster Mitigation Agency (PVMBG), Anak Krakatau volcano releases volcanic materials into the air as it erupts on Friday, June 9...}