\entryitemWithDescription{\hskip 0pt{}Colombia beats Germany for the first time to deepen Euro 2024 host team's sense of angst}{https://apnews.com/article/bc701563801ec85c654fa3fe9146c695}{Germany players walk off the field at the end of the international friendly soccer match between Germany and Colombia at Veltins-Arena, in Gelsenkirchen, Germany, Tuesday, June 20, 2023. Colombia won 2-0. (AP Photo/Martin Meissner...}

\entryitemWithDescription{\hskip 0pt{}Detroit-area officer charged with assault after video shows him punching man}{https://apnews.com/article/c9b91fa61caab6aa203cdf412bdf9de2}{WARREN, Mich. (AP) --- A suburban Detroit police officer was charged with assault after video showed him punching a young man in the face and slamming his head to the ground at the jail, authorities said Tuesday. ``This is not what we do...}

\entryitemWithDescription{\hskip 0pt{}41 women die in grisly riot in Honduran prison that president blames on 'mara' gangs}{https://apnews.com/article/211c6031a29338f7a3da7c1175adfa4e}{Relatives of inmates wait in distress outside the entrance to the women\textquotesingle s prison in Tamara, on the outskirts of Tegucigalpa, Honduras, Tuesday, June 20, 2023. A riot at the women\textquotesingle s prison has left at least...}

\entryitemWithDescription{\hskip 0pt{}Blood-red crickets invade Nevada town, residents fight back with brooms, leaf blowers, snow plows}{https://apnews.com/article/3563fbe67c7ff25960e8c66a90ad3885}{Jeremiah Moore has a cricket climb onto his arm during the migration of Mormon crickets, Saturday, June 17, 2023, in Spring Creek, Nev. Outbreaks of Mormon crickets, which are native to the Great Basin and Intermountain West, have been...}

\entryitemWithDescription{\hskip 0pt{}Twins Amen and Ausar Thompson set to be taken in top-10 of NBA draft}{https://apnews.com/article/a34e7912942e90a202005ea35fcd0944}{In this handout provided by Overtime Elite, Ausar Thompson, left, and Amen Thompson of the City Reapers celebrate after an Overtime Elite Finals basketball game on Saturday, March 4, 2023, at OTE Arena in Atlanta. The 6-foot-7 guards out...}

\entryitemWithDescription{\hskip 0pt{}Lionel Messi is expected to make his Inter Miami debut July 21}{https://apnews.com/article/8ca6c1952d2192f3f2121a586d8b81e9}{Argentina\textquotesingle s Lionel Messi takes a corner kick during the friendly soccer match against Australia at the Workers\textquotesingle{} Stadium in Beijing, China, Thursday, June 15, 2023. (AP Photo/Andy Wong) MIAMI (AP...}

\entryitemWithDescription{\hskip 0pt{}Women pushed into ravine at German castle were recent Illinois college graduates}{https://apnews.com/article/2a39731a65a3b3e5debdef84dd6f45cb}{FILE - People stay on the Marien-Bridge at Castle Neuschwanstein, a 19th century creation by Bavaria\textquotesingle s fairy tale king Ludwig II and world renowned tourist attraction, is pictured in Hohenschwangau near Fuessen, southern...}

\entryitemWithDescription{\hskip 0pt{}Rapper Quando Rondo jailed on drug, gang charges in Georgia}{https://apnews.com/article/b89c811e80dd81ed4f5e42905cc0e1f3}{This jail booking photo released by the Chatham County Sheriff\textquotesingle s Office in Savannah, Ga., shows Tyquian Terrel Bowman, a rapper also known as Quando Rondo. Bowman was jailed on gang and drug charges on Friday, June 16...}

\entryitemWithDescription{\hskip 0pt{}How a Mexican spiritual leader preserves the sacred knowledge of the volcano known as El Popo}{https://apnews.com/article/84a4c7fcdae74dcf185053ad723e3296}{Moises Vega gives an interview at the Volcano Museum in Amecameca, Mexico, near the Popocatépetl volcano, Sunday, June 11, 2023. The 64-year-old Mexican says he can speak the sacred language of volcanoes to ask for good weather and a good...}

\entryitemWithDescription{\hskip 0pt{}Inside the deepening rivalry between Florida Gov. Ron DeSantis and California Gov. Gavin Newsom}{https://apnews.com/article/09475e131ebc2983a8d72e13f55a9955}{FILE - This combination of photos shows California Gov. Gavin Newsom speaking in Sacramento, Calif., on June 24, 2022, left, and Florida Gov. Ron DeSantis speaking in Sioux Center, Iowa, May 13, 2023, right. (AP Photo, File) SACRAMENTO...}

\entryitemWithDescription{\hskip 0pt{}Himalayan glaciers could lose 80\% of their volume if global warming isn't controlled, study finds}{https://apnews.com/article/85cf414573ed8a9fbde4cb56ecf4fdd7}{FILE - The Sutlej River flows in the valley below the tall snowy peaks in the Kinnaur district of the Himalayan state of Himachal Pradesh, India, March 13, 2023. A new report Tuesday, June 20, from a Nepal-based research organization...}

\entryitemWithDescription{\hskip 0pt{}LGBTQ+ pride flags vandalized at Stonewall National Monument 3 times during Pride month}{https://apnews.com/article/35e95fce9d0ae6c2d9e6c5f39bc8b2e6}{FILE - Pride flags, a symbol celebrating the LGBTQ+ community, decorate the fence at the Stonewall National Monument with U.S. Park police present, Tuesday, June 13, 2023, in New York. Dozens of LGBTQ+ Pride flags were damaged and ripped...}

\entryitemWithDescription{\hskip 0pt{}4 people wounded by man wielding axe who attacked diners at Chinese restaurants in New Zealand}{https://apnews.com/article/068eebe81b9d04cd098e7085c9d3d400}{Police tape cordons off a restaurant in Auckland, New Zealand, Tuesday, June 20, 2023, after an axe attack late Monday. Multiple people were hospitalized after a man armed with an axe began attacking diners at random at three neighboring...}