\entryitemWithDescription{\hskip 0pt{}Quaker Oats recalls granola products over concerns of salmonella contamination}{https://apnews.com/article/b4b821bf6c038e2815c788a092279aff}{CHICAGO (AP) --- Quaker Oats on Friday recalled several of its granola products, including granola bars and cereals, saying the foods could be contaminated with salmonella. Salmonella infections can cause fever, diarrhea, nausea, vomiting...}

\entryitemWithDescription{\hskip 0pt{}Browns star Myles Garrett fined \$25,000 by NFL for criticizing officials after game, AP source says}{https://apnews.com/article/d2bf34a507ae4f1c393b0a6b8e7449f1}{CLEVELAND (AP) --- Cleveland Browns star defensive end Myles Garrett was fined \$25,000 by the NFL for ``public criticism of officiating'' after he made pointed remarks following last week's game against Jacksonville, a person familiar...}

\entryitemWithDescription{\hskip 0pt{}US and Britain say their navies shot down 15 attack drones over the Red Sea}{https://apnews.com/article/38940c6d0f653f7a6a53920c47b19097}{LONDON (AP) --- A U.S. warship shot down 14 suspected attack drones over the Red Sea on Saturday, and a Royal Navy destroyer downed another drone that was targeting commercial ships, the British and American militaries said. Houthi rebels...}

\entryitemWithDescription{\hskip 0pt{}Mayim Bialik is out as a host of `Jeopardy!'}{https://apnews.com/article/545613a84a54c23d07da4a9f665172dd}{LOS ANGELES (AP) --- Mayim Bialik won't be giving answers as a host of ``Jeopardy!'' anymore. ``The Big Bang Theory'' actor posted news of her departure on Instagram on Friday. ``Sony has informed me that I will no longer be hosting the...}

\entryitemWithDescription{\hskip 0pt{}A Tesla driver to pay \$23K in restitution for a 2019 Los Angeles crash that killed 2 people}{https://apnews.com/article/d65c48236d4c9d4a420b6f8307669832}{LOS ANGELES (AP) --- A Tesla driver will pay more than \$23,000 in restitution for the deaths of two people during a 2019 car crash in a Los Angeles suburb, a decision announced the same day that the automaker recalled nearly all vehicles...}

\entryitemWithDescription{\hskip 0pt{}Minnesota edges close to picking new state flag to replace design offensive to Native Americans}{https://apnews.com/article/d0d8b430cd9006f1cbafd26d5a6298ba}{MINNEAPOLIS (AP) --- A state commission selected a basic design concept Friday for a new state flag for Minnesota to replace a current banner that is considered offensive to Native Americans, but will need more time to add the finishing...}

\entryitemWithDescription{\hskip 0pt{}Argentine President Javier Milei raffles off his last salary as lawmaker}{https://apnews.com/article/f5746c51234972ba2b3ebb080b1e90c0}{BUENOS AIRES, Argentina (AP) --- President Javier Milei on Friday raffled off the last salary he received as an Argentine lawmaker before being sworn in earlier this month as leader of the economically troubled nation. During a live video...}

\entryitemWithDescription{\hskip 0pt{}Matthew Perry died from the effects of ketamine, autopsy report says}{https://apnews.com/article/054e67f7495845804f801c57a1ae2522}{LOS ANGELES (AP) --- Matthew Perry died from the acute effects of the anesthetic ketamine, according to the results of an autopsy on the 54-year-old ``Friends'' actor released Friday. The Los Angeles County Department of Medical Examiner...}

\entryitemWithDescription{\hskip 0pt{}Shohei Ohtani's contract with the Dodgers could come with bonus of mostly avoiding California taxes}{https://apnews.com/article/7c9b5752d7734908853db407f7441a1f}{SACRAMENTO, Calif. (AP) --- If \$700 million wasn't enough, Shohei Ohtani's record-setting contract with the Los Angeles Dodgers could also include a bonus: skipping most of California's famously high income taxes. Not even the mighty...}

\entryitemWithDescription{\hskip 0pt{}Former Mississippi House candidate charged after Satanic Temple display is destroyed at Iowa Capitol}{https://apnews.com/article/199fb41983a3f3a390b7be370214bb64}{DES MOINES, Iowa (AP) --- A Satanic Temple display inside the Iowa Capitol in Des Moines was destroyed, and a former U.S. Navy fighter pilot who was recently defeated in a statehouse election in Mississippi is accused of causing the...}

\entryitemWithDescription{\hskip 0pt{}Biggest solar flare in years temporarily disrupts radio signals on Earth}{https://apnews.com/article/eb3389b4e41955c3292b9c917a5667dc}{CAPE CANAVERAL, Fla. (AP) --- A NASA telescope has captured the biggest solar flare in years, which temporarily knocked out radio communication on Earth. The sun spit out the huge flare along with a massive radio burst on Thursday...}

\entryitemWithDescription{\hskip 0pt{}A plane hit powerlines over I-26 in North Carolina and burst into flames. Nobody was seriously hurt}{https://apnews.com/article/151346565c085dcec2e0f59d75134230}{ASHEVILLE, N.C. (AP) --- A small plane crashed on a western North Carolina highway and caught fire Thursday night, but the two people on board escaped life-threatening injuries, authorities said. A single-engine Diamond DA-40 crashed on...}

\entryitemWithDescription{\hskip 0pt{}No regrets for Ja Morant over suspension with actions, not words, proving lesson learned}{https://apnews.com/article/9677c0b2bbb08a6b4eef496a890475e7}{MEMPHIS, Tenn. (AP) --- Being suspended for the first 25 games of the NBA season was tough on two-time All-Star Ja Morant, who said Friday he had ``some horrible days'' as he worked to focus on himself away from basketball. The Memphis...}