\entryitemWithDescription{\hskip 0pt{}Dancing with the bears lives on as a unique custom in Romania}{https://apnews.com/article/bd5e7f26d5a10d8dca8b7d27c27290c6}{COMANESTI, Romania (AP) --- A small industrial town in northeast Romania may seem like an unlikely tourist destination, but Comanesti is where huge numbers of visitors from as far away as Japan choose to spend part of the winter holiday...}

\entryitemWithDescription{\hskip 0pt{}Colorado mother suspected of killing her 2 children and wounding a third arrested in United Kingdom}{https://apnews.com/article/ce2ea1e183352bdc63bf5a20b98745bd}{A Colorado mother suspected of killing two of her young children and injuring a third was arrested Saturday in the United Kingdom, according to the Colorado Springs Police Department. Kimberlee Singler's 9-year-old daughter and 7-year-old...}

\entryitemWithDescription{\hskip 0pt{}Influential former Texas US Rep. Eddie Bernice Johnson dies at 88}{https://apnews.com/article/b72ea50b8f6bba4dd24768616f7ade4f}{DALLAS, Texas (AP) --- Trailblazing longtime U.S. Rep. Eddie Bernice Johnson, a nurse from Texas who helped bring hundreds of millions of federal dollars to the Dallas area as the region's most powerful Democrat, died Sunday. She was 88...}

\entryitemWithDescription{\hskip 0pt{}Surfer dies after shark ``encounter'' in Hawaii}{https://apnews.com/article/5fd98ad87b5e07a46b2d80be5289afe2}{PAIA, Hawaii (AP) --- A surfer in Hawaii has died after being injured in a shark encounter off Maui's northern shore, according to the Maui Police Department. Authorities stopped short of calling the event an attack and didn't describe...}

\entryitemWithDescription{\hskip 0pt{}`Wonka' ends the year No. 1 at the box office, 2023 sales reach \$9 billion in post-pandemic best}{https://apnews.com/article/92fef0f3e8ce0b900b64bfdb8c7ffea8}{NEW YORK (AP) --- Hollywood closed out an up and down 2023 with ``Wonka'' regaining No. 1 at the box office, strong sales for ``The Color Purple'' and an overall \$9 billion in ticket sales that improved on 2022's grosses but fell about \$...}

\entryitemWithDescription{\hskip 0pt{}Shecky Greene, legendary standup comic, improv master and lord of Las Vegas, dies at 97}{https://apnews.com/article/6f0455de97a4ae5faefa508ca55b6cd0}{LOS ANGELES (AP) --- Shecky Greene, the gifted comic and master improviser who became the consummate Las Vegas lounge headliner and was revered by his peers and live audiences as one of the greatest standup acts of his generation, has...}

\entryitemWithDescription{\hskip 0pt{}College Football Playoff semifinals could set betting records}{https://apnews.com/article/b7cec787e5424d46c146f6abe0f7e9e1}{LAS VEGAS (AP) --- Sportsbook director Jay Kornegay is anticipating massive crowds at Westgate's Las Vegas location this weekend and Monday to bet on the two College Football Playoff semifinal games. Part of it is timing. Last season's...}

\entryitemWithDescription{\hskip 0pt{}Denmark's Queen Margrethe II to step down from throne on Jan. 14}{https://apnews.com/article/92afd336166b4e643caf57289eaf8fbe}{STOCKHOLM, Sweden (AP) --- Denmark's Queen Margrethe II announced Sunday that she plans to abdicate after 52 years and hand over the throne to her son, Crown Prince Frederik. The queen, who is Europe's longest-reigning living monarch...}

\entryitemWithDescription{\hskip 0pt{}Sen. Fetterman says he thought news about his depression treatment would end his political career}{https://apnews.com/article/0f424652b43f77b40e7dac9e186b14bb}{WASHINGTON (AP) --- Sen. John Fetterman acknowledges having ``dark conversations'' about harming himself before he hit ``the emergency brake'' and sought treatment for depression. He remembers thinking about his three school-age kids. ``I...}

\entryitemWithDescription{\hskip 0pt{}South Korea's capital records heaviest single-day snowfall in December for 40 years}{https://apnews.com/article/f644c0a935cb0e2c674691ea9d5bf373}{SEOUL, South Korea (AP) --- The South Korean capital, Seoul, received the biggest single-day snowfall recorded in December for more than 40 years on Saturday but there have been no reports of any weather-related deaths or injuries. The...}

\entryitemWithDescription{\hskip 0pt{}At the stroke of midnight, the New Year gives a clean slate for long-elusive resolutions}{https://apnews.com/article/a022bcea9e37851b32b0a1a05107b9eb}{NEW YORK (AP) --- It's an annual end-of-year exercise in futility for many. But a clean slate awaits at the stroke of midnight for the next round of resolutions. From the first spray of fireworks to the closing chorus of ``Auld Lang...}

\entryitemWithDescription{\hskip 0pt{}High surf advisories remain in some parts of California, as ocean conditions begin to calm}{https://apnews.com/article/b2b834040a570dfce1f4f02f68d0bd59}{VENTURA, Calif. (AP) --- Southern California's Ventura County issued a temporary evacuation warning Saturday for some coastal residents due to high surf that pounded the West Coast this week but has begun to calm down. County officials...}

\entryitemWithDescription{\hskip 0pt{}Paula Abdul accuses `American Idol' producer Nigel Lythgoe of sexual assault in lawsuit}{https://apnews.com/article/ce22542ef62e4ac5a1081932c9a631ab}{LOS ANGELES (AP) --- Paula Abdul has accused former ``American Idol'' producer Nigel Lythgoe of sexually assaulting her in the early 2000s when she was a judge on the reality competition show, according to a new lawsuit. The lawsuit filed...}