\entryitemWithDescription{\hskip 0pt{}Actor Ian McKellen, 85, is hospitalized after toppling off stage in London}{https://apnews.com/article/7e319665f8186b2785b258920ed06fdd}{LONDON (AP) --- Actor Ian McKellen was hospitalized Monday after toppling off a London stage during a fight scene in a play. The 85-year-old known for playing Gandalf in the ``Lord of the Rings'' films and many stage roles over a six...}

\entryitemWithDescription{\hskip 0pt{}Tony Awards: That moment when Jay-Z joined Alicia Keys? It wasn't live}{https://apnews.com/article/be469a7819bcd013266addda699e747a}{NEW YORK (AP) --- Jay-Z's electrifying reunion with Alicia Keys on what appeared to be a live duet of ``Empire State of Mind'' at the Tony Awards was actually pre-taped, a show official who wasn't authorized to speak publicly told The...}

\entryitemWithDescription{\hskip 0pt{}Euro 2024: Mbappé suffers injury in France's 1-0 win against Austria}{https://apnews.com/article/cd666d2b964581f7cc034359502efcf4}{DUSSELDORF, Germany (AP) --- Kylian Mbappé suffered a facial injury and was replaced as France beat Austria 1-0 in its opening game of the European Championship on Monday. The striker, involved in the first-half goal, clashed heads with...}

\entryitemWithDescription{\hskip 0pt{}No lie: Perfectly preserved centuries-old cherries unearthed at George Washington's Mount Vernon}{https://apnews.com/article/3f4eddfc27e771ff01fc346e2b91075c}{MOUNT VERNON, Va. (AP) --- George Washington never did cut down the cherry tree, despite the famous story to the contrary, but he did pack away quite a few bottles of the fruit at his Mount Vernon home. Dozens of bottles of cherries and...}

\entryitemWithDescription{\hskip 0pt{}Historic ship SS United States is ordered out of its berth in Philadelphia}{https://apnews.com/article/3f2bd92e9a0e563f1bdf8935450a217e}{PHILADELPHIA (AP) --- The SS United States, a historic ship that still holds the transatlantic speed record it set more than 70 years ago, must leave its berth on the Delaware River in Philadelphia by Sept. 12, a federal judge says. The...}

\entryitemWithDescription{\hskip 0pt{}German investigators seize cocaine worth 2.6 billion euros, calling it their biggest find ever}{https://apnews.com/article/25dbc718f12ccdd52a5eb5c5b9e2408b}{BERLIN (AP) --- German investigators announced Monday that they seized cocaine worth 2.6 billion euros (\$2.78 billion) from several container ships and arrested seven people in what they called the biggest ever cocaine find in the...}

\entryitemWithDescription{\hskip 0pt{}Key moments at the Tonys: Jay-Z and Hillary Clinton in the house, strides for women and a late upset}{https://apnews.com/article/35d089910f965ddc93326510931bf516}{NEW YORK (AP) --- ``People, stop texting me!'' pleaded Kecia Lewis, with comic exasperation. The veteran Broadway performer had just won her first Tony award in a 40-year career, for the Alicia Keys musical ``Hell's Kitchen,'' and was...}

\entryitemWithDescription{\hskip 0pt{}Bryson DeChambeau wins another U.S. Open with a clutch finish to deny Rory McIlroy}{https://apnews.com/article/5f8a3ec8c68a1d341f0e119e364e28df}{PINEHURST, N.C. (AP) --- Bryson DeChambeau won the U.S. Open on Sunday for the second time with the best shot of his life for another memorable finish on the 18th hole at Pinehurst No. 2 --- and another heavy dose of heartache for Rory...}

\entryitemWithDescription{\hskip 0pt{}Longtime Southern Baptist leader Paul Pressler, who was accused of sexual abuse, dies at 94}{https://apnews.com/article/ac42aa8817b287fb6963edf3b0110273}{HOUSTON (AP) --- Paul Pressler, a leading figure of the Southern Baptist Convention who was accused of sexually abusing boys and young men and later settled a lawsuit over the allegations, has died. He was 94. Pressler's death, which...}

\entryitemWithDescription{\hskip 0pt{}Milan Fashion Week: Prada projects youthful optimism, not escapism, in a turbulent world}{https://apnews.com/article/984eeb35107212cab76461011f543afe}{MILAN (AP) --- Without making overt statements, Milan designers expressed their concern over the global turbulence through their collections. Miuccia Prada said she wanted to project optimism. ``Because even if the times are bad, I feel...}

\entryitemWithDescription{\hskip 0pt{}An emotional win for theaters, Hollywood: `Inside Out 2' scores massive \$155 million opening}{https://apnews.com/article/ea1994cf48357c6c2e833ff470051bbc}{Hollywood's summer movie anxieties gave way to joy this weekend with the massive debut of Disney and Pixar's `` Inside Out 2.'' The animated sequel earned \$155 million in ticket sales from 4,440 theaters in the U.S. and Canada, according...}

\entryitemWithDescription{\hskip 0pt{}Derek Jeter's New York castle might finally have a buyer}{https://apnews.com/article/c5dd773c420a5ae05d2dc35d608e5542}{GREENWOOD LAKE, N.Y. (AP) --- Former New York Yankees superstar Derek Jeter has found a potential buyer for his New York castle after the sprawling lakefront property had its price tag slashed by more than half. The property, known as...}

\entryitemWithDescription{\hskip 0pt{}Divers find remains of Finnish WWII plane that was shot down by Moscow with a US diplomat aboard}{https://apnews.com/article/8376e3aa3237ec2e551749afc74ccbbe}{HELSINKI (AP) --- The World War II mystery of what happened to a Finnish passenger plane after it was shot down over the Baltic Sea by Soviet bombers appears to finally be solved more than eight decades later. The plane was carrying...}