\entryitemWithDescription{\hskip 0pt{}US stands by decision that 50 million air bag inflators are dangerous, steps closer to huge recall}{https://apnews.com/article/70f0d5341e7999bfece4b80ee515f5fa}{DETROIT (AP) --- U.S. auto safety regulators say they stand by a conclusion that more than 50 million air bag inflators are dangerous and should not be in use, taking another step toward a massive recall. The decision Wednesday by the...}

\entryitemWithDescription{\hskip 0pt{}German city renamed `Swiftkirchen' for Taylor Swift concerts gets 1,400 bids for the signs}{https://apnews.com/article/01a68a8c505bf649a0d3f0f149be158e}{BERLIN (AP) --- The German city of Gelsenkirchen, which temporarily renamed itself ``Swiftkirchen'' before the American superstar played three concerts there in mid-July, said Wednesday it received about 1,400 bids from Germany and abroad...}

\entryitemWithDescription{\hskip 0pt{}Former ballerina in Florida is convicted of manslaughter in her estranged husband's 2020 shooting}{https://apnews.com/article/ac5bacf9bf958d6bfab322fdbff2effd}{BRADENTON, Fla. (AP) --- A former ballerina has been convicted of manslaughter in the 2020 shooting death of her estranged husband in Florida. A Manatee County jury returned the guilty verdict late Tuesday against Ashley Benefield, court...}

\entryitemWithDescription{\hskip 0pt{}A centuries-old secret script called nüshu is empowering young Chinese women}{https://apnews.com/article/b6a206b87c9682f743bf73d9a51a5d85}{BEIJING (AP) --- Chen Yulu never thought her home province of Hunan had any culture that she would be proud of, much less become an ambassador of. But these days, the 23-year-old is a self-proclaimed ambassador of nüshu, a script once...}

\entryitemWithDescription{\hskip 0pt{}White House chef retires after nearly 30 years, 1st woman and 1st person of color to have the job}{https://apnews.com/article/4f30d444c822863edfcf6c0fdf8ba234}{WASHINGTON (AP) --- The White House's executive chef has retired after nearly three decades of making meals and cooking up state dinners for five different presidents and their families. Cris Comerford is the first woman to hold the job...}

\entryitemWithDescription{\hskip 0pt{}Olympics bet against climate change with swimming in Seine and may lose. Scientists say told you so}{https://apnews.com/article/22a067bfdc50ba0e6478c008c93311c6}{With plans for athletes to swim the Seine River through the heart of Paris, Olympic organizers essentially bet against climate change's extreme weather. Now it's looking like they'll lose --- by ditching the swimming portion of triathlon...}

\entryitemWithDescription{\hskip 0pt{}Boar's Head expands recall to include 7 million more pounds of deli meats tied to listeria outbreak}{https://apnews.com/article/ebff78f4d6e5dad8483a6063623cd9a1}{The popular deli meat company Boar's Head is recalling an additional 7 million pounds of ready-to-eat products made at a Virginia plant as an investigation into a deadly outbreak of listeria food poisoning continues, U.S. Agriculture...}

\entryitemWithDescription{\hskip 0pt{}Florida school board suspends employee who allowed her transgender daughter to play girls volleyball}{https://apnews.com/article/625d687b3f234f0b5059b6346b1470d6}{PLANTATION, Fla. (AP) --- A Florida school employee who let her transgender daughter play on her high school's girls volleyball team is being suspended for 10 days after the district's board found on Tuesday that she violated state law...}

\entryitemWithDescription{\hskip 0pt{}Terrell Davis says United banned him after flight incident. Airline says it was already rescinded}{https://apnews.com/article/52cdb8305263de039e0740395a27efb3}{DENVER (AP) --- Pro Football Hall of Famer Terrell Davis posted an email from United Airlines Tuesday saying he was banned from flying the airline until a review of an incident earlier this month was complete. But United officials said...}

\entryitemWithDescription{\hskip 0pt{}Simone Biles and Team USA take aim at gold in the women's gymnastics team final}{https://apnews.com/article/f6863232f86ee3a7f8e0bf2ec1e47519}{PARIS (AP) --- American gymnastics star Simone Biles is inside Bercy Arena for the women's team final. Biles is competing after tweaking her left calf during qualifying on Sunday. The five-woman U.S. squad of Biles, Sunisa Lee, Jordan...}

\entryitemWithDescription{\hskip 0pt{}What is that? Olympic Phryge confounds some, but is very French}{https://apnews.com/article/fc8cb4d6fc1bd9c61b13a5c57f079ddf}{PARIS (AP) --- ``Is it the Eiffel Tower?'' asks a puzzled American tourist queued in front of the Paris 2024 Megastore. To international visitors, the triangular Olympic Phryge mascot might resemble the iconic monument, a ``poop...}

\entryitemWithDescription{\hskip 0pt{}1 dead and dozens sickened after eating roasted eel from a Japanese department store}{https://apnews.com/article/7393f8c55beed0dae91e01ebf0f8b731}{TOKYO (AP) --- One person died and nearly 150 others were sickened after eating grilled eel prepared by a restaurant chain and sold at a department store near Tokyo, officials said. Among those sickened, two required hospitalization...}

\entryitemWithDescription{\hskip 0pt{}Tesla recalling more than 1.8M vehicles due to hood issue}{https://apnews.com/article/7075c6591065ea890c7034fb31eeced1}{Tesla is recalling more than 1.8 million vehicles because of a hood issue that could increase the risk of a crash. Billionaire Elon Musk's Tesla is recalling some 2021-2024 Model 3, Model S, Model X, and 2020-2024 Model Y vehicles because...}