


\ipart{Developers}
\ichapter{Hacker News}
\entryitemTwoLinks{The Bitcoin whitepaper is hidden in every copy of macOS}{https://news.ycombinator.com/item?id=35461011}{https://waxy.org/2023/04/the-bitcoin-whitepaper-is-hidden-in-every-modern-copy-of-macos/}

\entryitemTwoLinks{Dang is going to have 65,535 karma points soon}{https://news.ycombinator.com/item?id=35460732}{https://news.ycombinator.com/user?id=dang}

\entryitemTwoLinks{Programmer interrupted: The cost of interruption and context switching (2022)}{https://news.ycombinator.com/item?id=35459333}{https://contextkeeper.io/blog/the-real-cost-of-an-interruption-and-context-switching/}

\entryitemTwoLinks{Neural Networks: Zero to Hero}{https://news.ycombinator.com/item?id=35459031}{https://karpathy.ai/zero-to-hero.html}

\entryitemTwoLinks{Firefox engineers discover a Windows Defender bug that causes high CPU usage}{https://news.ycombinator.com/item?id=35458746}{https://bugzilla.mozilla.org/show\_bug.cgi?id=1441918\#c82}

\entryitemTwoLinks{Remembering Bob Lee}{https://news.ycombinator.com/item?id=35457341}{https://news.ycombinator.com/item?id=35457341}

\entryitemTwoLinks{Run LLaMA and Alpaca on your computer}{https://news.ycombinator.com/item?id=35457225}{https://github.com/cocktailpeanut/dalai}

\entryitemTwoLinks{China plans to ban exports of rare earth magnet tech}{https://news.ycombinator.com/item?id=35456721}{https://japannews.yomiuri.co.jp/world/asia-pacific/20230405-101753/}

\entryitemTwoLinks{Show HN: Quadratic – Open-Source Spreadsheet with Python, AI (WASM and WebGL)}{https://news.ycombinator.com/item?id=35456509}{https://www.quadratichq.com/}

\entryitemTwoLinks{Read ``Gravity's Rainbow'' fifty years later}{https://news.ycombinator.com/item?id=35456192}{https://aurelien2022.substack.com/p/in-praise-of-the-preterite}

\entryitemTwoLinks{A SvelteKit template for building CMS-free editable websites}{https://news.ycombinator.com/item?id=35456083}{https://editable.website}

\entryitemTwoLinks{A trick to reaching flow: Leave your work broken}{https://news.ycombinator.com/item?id=35456059}{https://census.dev/blog/an-on-ramp-to-flow}

\entryitemTwoLinks{Using mmap to make LLaMA load faster}{https://news.ycombinator.com/item?id=35455930}{https://justine.lol/mmap/}

\entryitemTwoLinks{Perspective: Open Source WebAssembly-Powered BI}{https://news.ycombinator.com/item?id=35455850}{https://perspective.finos.org/}

\entryitemTwoLinks{DPReview's Founder Blasts Amazon's CEO: `What a Waste'}{https://news.ycombinator.com/item?id=35455797}{https://petapixel.com/2023/04/04/dpreviews-founder-blasts-amazons-ceo-what-a-waste/}

\entryitemTwoLinks{Grid World}{https://news.ycombinator.com/item?id=35455770}{https://alex.miller.garden/grid-world/}

\entryitemTwoLinks{Segment Anything Model (SAM) can "cut out" any object in an image}{https://news.ycombinator.com/item?id=35455566}{https://segment-anything.com/}

\entryitemTwoLinks{``Inside-out Wankel'' rotary engine delivers 5X the power of a diesel}{https://news.ycombinator.com/item?id=35455286}{https://newatlas.com/automotive/inside-out-wankel/}

\entryitemTwoLinks{Johnson and Johnson reaches deal for \$8.9B talc settlement}{https://news.ycombinator.com/item?id=35453857}{https://www.nytimes.com/2023/04/04/business/media/johnson-johnson-talc-settlement.html}

\entryitemTwoLinks{OpenAI Tokenizer}{https://news.ycombinator.com/item?id=35453400}{https://platform.openai.com/tokenizer}\ichapter{Phoronix}
\entryitemGeneric{\hskip 0pt{}Intel Vulkan Driver Squeezes In A Few More Performance Optimizations For Mesa 23.1}{https://www.phoronix.com/news/Mesa-23.1-Intel-ANV-More-Perf}

\entryitemGeneric{\hskip 0pt{}HP WMI Driver To Expose More Sensors Under Linux For Business-Class Systems}{https://www.phoronix.com/news/Linux-HP-WMI-Sensors-Patches}

\entryitemGeneric{\hskip 0pt{}AMD Ryzen 7 7800X3D Linux Performance}{https://www.phoronix.com/review/amd-ryzen-7-7800x3d-linux}

\entryitemGeneric{\hskip 0pt{}GTK 4.11.1 Released With Better Textures, Wayland Fractional Scaling}{https://www.phoronix.com/news/GTK-4.11.1}

\entryitemGeneric{\hskip 0pt{}Ubuntu Talks Up Rust Kernel Programming Potential With Ubuntu 23.04}{https://www.phoronix.com/news/Ubuntu-23.04-Rust-Linux-Kernel}

\entryitemGeneric{\hskip 0pt{}Zstd 1.5.5 Released With Corruption Fix, Improved Performance In Some Scenarios}{https://www.phoronix.com/news/Zstd-1.5.5}

\entryitemGeneric{\hskip 0pt{}LLVM 16.0.1 Released With Many Compiler Fixes, Backports AMD Zen 4 Scheduler Model}{https://www.phoronix.com/news/LLVM-16.0.1-Released}

\entryitemGeneric{\hskip 0pt{}MidnightBSD 3.0.1 Released With Security Fixes, rc.d Scripts Cleanup}{https://www.phoronix.com/news/MidnightBSD-3.0.1}

\entryitemGeneric{\hskip 0pt{}Chrome 112 Released With WASM Garbage Collection Trial, CSS Nesting}{https://www.phoronix.com/news/Google-Chrome-112}\ichapter{GitHub}
\entryitemWithDescription{\hskip 0pt{}terrastruct/d2}{https://github.com/terrastruct/d2}{D2 is a modern diagram scripting language that turns text to diagrams.\\
Language: Go\\
Stars: 12465\\
Forks: 250}

\entryitemWithDescription{\hskip 0pt{}iDvel/rime-ice}{https://github.com/iDvel/rime-ice}{Rime 配置：雾凇拼音 \textbar{} 长期维护的简体词库\\
Language: Go\\
Stars: 1638\\
Forks: 130}

\entryitemWithDescription{\hskip 0pt{}donnemartin/system-design-primer}{https://github.com/donnemartin/system-design-primer}{Learn how to design large-scale systems. Prep for the system design
interview. Includes Anki flashcards.\\
Language: Python\\
Stars: 216726\\
Forks: 38546}

\entryitemWithDescription{\hskip 0pt{}hwchase17/langchain}{https://github.com/hwchase17/langchain}{⚡ Building applications with LLMs through composability ⚡\\
Language: Python\\
Stars: 21194\\
Forks: 1937}\ichapter{Dribbble}
\entryitemGeneric{\hskip 0pt{}Custo® - How it works}{https://dribbble.com/shots/21063935}

\entryitemGeneric{\hskip 0pt{}[P] 1 → N}{https://dribbble.com/shots/21021513}

\entryitemGeneric{\hskip 0pt{}Flatfile Branding}{https://dribbble.com/shots/20919358}

\entryitemGeneric{\hskip 0pt{}Brainwave AI UI Kit - Add New List Modal}{https://dribbble.com/shots/21091477}

\entryitemGeneric{\hskip 0pt{}Onboarding mobile app for BOXXY}{https://dribbble.com/shots/21060070}

\entryitemGeneric{\hskip 0pt{}EV charger website design}{https://dribbble.com/shots/21072112}

\entryitemGeneric{\hskip 0pt{}Zelt graphic assets}{https://dribbble.com/shots/21107854}

\entryitemGeneric{\hskip 0pt{}Eco food packaging website ui}{https://dribbble.com/shots/21064870}

\entryitemGeneric{\hskip 0pt{}Letter.co Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20918567}

\entryitemGeneric{\hskip 0pt{}Sapforce - AI SaaS website design}{https://dribbble.com/shots/21107524}

\entryitemGeneric{\hskip 0pt{}3D Modeling for UX/UI Design}{https://dribbble.com/shots/21059700}

\entryitemGeneric{\hskip 0pt{}Nike Pickleball - April Fools' Day}{https://dribbble.com/shots/21089582}

\entryitemGeneric{\hskip 0pt{}Transcend Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20866281}

\entryitemGeneric{\hskip 0pt{}Logo, Branding, Mark, Symbol, Modern, lettermark, Logos}{https://dribbble.com/shots/21063110}

\entryitemGeneric{\hskip 0pt{}Finolio Brand Guidelines}{https://dribbble.com/shots/21042784}

\entryitemGeneric{\hskip 0pt{}Zelt Website Development}{https://dribbble.com/shots/21118990}

\entryitemGeneric{\hskip 0pt{}Guide - AI based 3d software website}{https://dribbble.com/shots/21086080}

\entryitemGeneric{\hskip 0pt{}Banking App}{https://dribbble.com/shots/21113553}

\entryitemGeneric{\hskip 0pt{}Visual identity. Branding, corporate brand design}{https://dribbble.com/shots/21091073}

\entryitemGeneric{\hskip 0pt{}AVAX Wallet - Page Transitions}{https://dribbble.com/shots/21094836}

\entryitemGeneric{\hskip 0pt{}Study(East Asian Muses)}{https://dribbble.com/shots/21058450}

\entryitemGeneric{\hskip 0pt{}Almanac Brand Refresh}{https://dribbble.com/shots/21099112}

\entryitemGeneric{\hskip 0pt{}Proemion Website Dashboard}{https://dribbble.com/shots/20918772}

\entryitemGeneric{\hskip 0pt{}3D Composition}{https://dribbble.com/shots/21091224}


\ipart{Developers~~~~(zh-Hans)}
\ichapter{Solidot}
\entryitemGeneric{\hskip 0pt{}Chrome 112 发布，支持 WASM 垃圾收集}{https://www.solidot.org/story?sid=74585}

\entryitemGeneric{\hskip 0pt{}美国青少年对虚拟现实缺乏兴趣}{https://www.solidot.org/story?sid=74584}

\entryitemGeneric{\hskip 0pt{}AI 进入企业控制的时代}{https://www.solidot.org/story?sid=74583}

\entryitemGeneric{\hskip 0pt{}Google 将削减提供给员工的各种福利}{https://www.solidot.org/story?sid=74582}

\entryitemGeneric{\hskip 0pt{}西部数据遭黑客入侵数据被盗}{https://www.solidot.org/story?sid=74581}

\entryitemGeneric{\hskip 0pt{}Google 将近距离文件共享带到 Windows}{https://www.solidot.org/story?sid=74580}

\entryitemGeneric{\hskip 0pt{}科学家完成基于时间的双缝实验}{https://www.solidot.org/story?sid=74579}

\entryitemGeneric{\hskip 0pt{}报告称全球六分之一人口受到不孕不育症影响}{https://www.solidot.org/story?sid=74578}

\entryitemGeneric{\hskip 0pt{}华硕宣布 Windows 掌机 ROG Ally}{https://www.solidot.org/story?sid=74577}

\entryitemGeneric{\hskip 0pt{}使用 3CX 的加密货币公司被植入了后门}{https://www.solidot.org/story?sid=74576}

\entryitemGeneric{\hskip 0pt{}Google Drive 撤销 500 万文件数量限制}{https://www.solidot.org/story?sid=74575}

\entryitemGeneric{\hskip 0pt{}Twitter 将网站 Logo 改为柴犬}{https://www.solidot.org/story?sid=74574}

\entryitemGeneric{\hskip 0pt{}NASA 公布重返月球的宇航员名单}{https://www.solidot.org/story?sid=74573}

\entryitemGeneric{\hskip 0pt{}Tor 项目推出捆绑 VPN 的隐私浏览器}{https://www.solidot.org/story?sid=74572}

\entryitemGeneric{\hskip 0pt{}3CX 公司最初以为供应链攻击是误报}{https://www.solidot.org/story?sid=74571}

\entryitemGeneric{\hskip 0pt{}数学家证明高维度黑洞形状可以是无限的}{https://www.solidot.org/story?sid=74570}

\entryitemGeneric{\hskip 0pt{}维基百科创始人谈用 AI 写文章}{https://www.solidot.org/story?sid=74569}

\entryitemGeneric{\hskip 0pt{}华为净利润大幅下滑}{https://www.solidot.org/story?sid=74568}

\entryitemGeneric{\hskip 0pt{}韦伯发现宇宙已知最古老黑洞}{https://www.solidot.org/story?sid=74567}

\entryitemGeneric{\hskip 0pt{}巴黎禁止共享电动滑板车}{https://www.solidot.org/story?sid=74566}\ichapter{V2EX}
\entryitemGeneric{\hskip 0pt{}[酷工作] [求职][全栈工程师][ PHP /Vue.js/ Swift /小程序] 远程/线下均可~}{https://www.v2ex.com/t/930119}

\entryitemGeneric{\hskip 0pt{}[随想] 中国女拳的解决思路}{https://www.v2ex.com/t/930118}

\entryitemGeneric{\hskip 0pt{}[分享创造] 我做了 ChatGPT 和 Copilot 的 UI Kit, 这套 UI Kit 应该能满足大部分 AI 产品的需求.}{https://www.v2ex.com/t/930117}

\entryitemGeneric{\hskip 0pt{}[问与答] MSDN I tell you 上面有些老链接失效了，还有什么替代下载途径吗？}{https://www.v2ex.com/t/930116}

\entryitemGeneric{\hskip 0pt{}[职场话题] 美国这一轮码农裁员大潮过后，找工作感到了深深的寒意}{https://www.v2ex.com/t/930115}

\entryitemGeneric{\hskip 0pt{}[问与答] 有什么办法可以检测/接受电脑版微信/钉钉等软件的消息，然后推送到手机上？}{https://www.v2ex.com/t/930114}

\entryitemGeneric{\hskip 0pt{}[分享创造] 寻找有时间的开发一起做根据图片生成关键词的网站, 即使没有兴趣开发产品, 也请帮忙看看产品的可行性.}{https://www.v2ex.com/t/930113}

\entryitemGeneric{\hskip 0pt{}[问与答] 是中病毒了吗？在任何地方复制钱包地址都不对}{https://www.v2ex.com/t/930112}

\entryitemGeneric{\hskip 0pt{}[问与答] 安装 stable-diffusion-webui 卡住怎么回事}{https://www.v2ex.com/t/930111}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 落格智聊的 GPT-4 一次回答 5 毛到 1 块，真用不起}{https://www.v2ex.com/t/930109}

\entryitemGeneric{\hskip 0pt{}[问与答] 继续考研还是国企上班}{https://www.v2ex.com/t/930108}

\entryitemGeneric{\hskip 0pt{}[问与答] 求推荐 lcd 手机，原生或类原生。}{https://www.v2ex.com/t/930107}

\entryitemGeneric{\hskip 0pt{}[Microsoft Office] Office365 家庭版五年}{https://www.v2ex.com/t/930106}

\entryitemGeneric{\hskip 0pt{}[VPS] 求推荐一个 VPS，预算每年 2000 预算吧，要求稳定 ping 低主要看奈飞}{https://www.v2ex.com/t/930105}

\entryitemGeneric{\hskip 0pt{}[强迫症] 我这种算强迫症吗，可以讨论下}{https://www.v2ex.com/t/930104}

\entryitemGeneric{\hskip 0pt{}[问与答] AHK 脚本在桌面界面多次按 ESC 后失效}{https://www.v2ex.com/t/930101}

\entryitemGeneric{\hskip 0pt{}[问与答] 有没有老哥玩过 22G 的 2080TI，体验如何？}{https://www.v2ex.com/t/930100}

\entryitemGeneric{\hskip 0pt{}[求职] 3 年 Java 想养老，深圳国企外企求推荐}{https://www.v2ex.com/t/930099}

\entryitemGeneric{\hskip 0pt{}[程序员] 你们在用 chatGPT 会不会出现结果输出不完整的问题？}{https://www.v2ex.com/t/930098}

\entryitemGeneric{\hskip 0pt{}[深圳] 龙华区租房求助}{https://www.v2ex.com/t/930096}

\entryitemGeneric{\hskip 0pt{}[Surge] iOS 科学工具｜有 QX 了还有必要入 surge 或者 loon 么？}{https://www.v2ex.com/t/930095}

\entryitemGeneric{\hskip 0pt{}[MacBook Pro] Macbook 使用过程突然卡住几秒钟，鼠标键盘触控板什么都操作不了是怎么回事？}{https://www.v2ex.com/t/930094}

\entryitemGeneric{\hskip 0pt{}[问与答] 最近硬件貌似降价了，准备 diy 主机，大家看看这样配置合适不}{https://www.v2ex.com/t/930093}

\entryitemGeneric{\hskip 0pt{}[分享发现] 金百达太牛逼了，把 32G*2 内存套条干到 800 以下.....太 tm 香了}{https://www.v2ex.com/t/930091}

\entryitemGeneric{\hskip 0pt{}[Linux] 为什么统信系统无法更新？}{https://www.v2ex.com/t/930090}

\entryitemGeneric{\hskip 0pt{}[问与答] 被墙的 vps 有没有好的办法 ssh 和传输文件？}{https://www.v2ex.com/t/930087}

\entryitemGeneric{\hskip 0pt{}[问与答] 有没有这类信息的学习渠道}{https://www.v2ex.com/t/930086}

\entryitemGeneric{\hskip 0pt{}[问与答] 有人在用谷歌拼音输入法吗？}{https://www.v2ex.com/t/930085}

\entryitemGeneric{\hskip 0pt{}[DNS] 群晖 myds.me DDNS 突然无法解析}{https://www.v2ex.com/t/930084}

\entryitemGeneric{\hskip 0pt{}[酷工作] 有 1 年半的离职在考研，每个公司都在知道辞职 Gap 后已读不回}{https://www.v2ex.com/t/930082}

\entryitemGeneric{\hskip 0pt{}[问与答] 房屋估价小问题}{https://www.v2ex.com/t/930081}

\entryitemGeneric{\hskip 0pt{}[Surge] Surge 5 macOS 寻 2 位车友}{https://www.v2ex.com/t/930079}

\entryitemGeneric{\hskip 0pt{}[问与答] 求助：在 iOS 设备上浏览器中使用语音输入时遇到的不一致的输入事件}{https://www.v2ex.com/t/930078}

\entryitemGeneric{\hskip 0pt{}[程序员] 问一个会计类的问题，如何计算退款时的折扣和利润率？}{https://www.v2ex.com/t/930075}

\entryitemGeneric{\hskip 0pt{}[程序员] ChatGPT 暂时关闭 Plus 付费，想用 Plus 还有什么办法？}{https://www.v2ex.com/t/930074}

\entryitemGeneric{\hskip 0pt{}[前端开发] F12 使用`复制值'复制 cookie 无法使用}{https://www.v2ex.com/t/930072}

\entryitemGeneric{\hskip 0pt{}[问与答] ChatGTP 美国 IP 也被限制？ error 1020 。怎么解呢？}{https://www.v2ex.com/t/930071}

\entryitemGeneric{\hskip 0pt{}[问与答] 有什么好玩的游戏顺带可以积累英语生词的}{https://www.v2ex.com/t/930070}

\entryitemGeneric{\hskip 0pt{}[分享发现] 似乎小米早就支持 eSIM？}{https://www.v2ex.com/t/930069}

\entryitemGeneric{\hskip 0pt{}[全球工单系统] 腾讯云叒出大问题了}{https://www.v2ex.com/t/930068}

\entryitemGeneric{\hskip 0pt{}[问与答] 有啥 app 能记录饮食的热量/蛋白/脂肪/维生素/矿物质么？}{https://www.v2ex.com/t/930067}

\entryitemGeneric{\hskip 0pt{}[问与答] 请教，国外的人如何寻找软件开发团队？}{https://www.v2ex.com/t/930065}

\entryitemGeneric{\hskip 0pt{}[分享发现] 真的是为我好嘛？休想把我关进高墙之中！}{https://www.v2ex.com/t/930064}

\entryitemGeneric{\hskip 0pt{}[Google] Google Voice 保号互助}{https://www.v2ex.com/t/930063}

\entryitemGeneric{\hskip 0pt{}[DevOps] 如何设置 azure devops 上 创建的 pull request 在满足某些条件时, 自动能够完成合并到目标分支}{https://www.v2ex.com/t/930062}

\entryitemGeneric{\hskip 0pt{}[问与答] 最近穷，谁能帮下载一份 CSDN 的 VIP 文章}{https://www.v2ex.com/t/930061}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 现在还有什么使用 GPT-4 的方法， Plus 的钱又被退回来了}{https://www.v2ex.com/t/930060}

\entryitemGeneric{\hskip 0pt{}[macOS] 分享 Parallels Desktop 能用的 Windows 10 arm64}{https://www.v2ex.com/t/930059}

\entryitemGeneric{\hskip 0pt{}[程序员] 设计并实现一款软件的 UI 界面真的挺难的。}{https://www.v2ex.com/t/930058}

\entryitemGeneric{\hskip 0pt{}[问与答] 你所使用的手机你最离不开的优点是？最反感的缺点是？}{https://www.v2ex.com/t/930057}


\ipart{Generic News}
\ichapter{AP News}
\entryitemWithDescription{\hskip 0pt{}Publisher drops children's illustrator for anti-trans notes}{https://apnews.com/article/9306e7e85c9f432e7bd2c79c13498c15}{The children\textquotesingle s book "You Are Home With Me," illustrated by Mitchell Thomas Watley, is shown at a bookstore in Portland, Ore. in this April 5, 2023 photo. Publisher Sasquatch books, owned by Penguin Random House, said...}

\entryitemWithDescription{\hskip 0pt{}LSU's Reese on White House flap: 'We'll go to the Obamas'}{https://apnews.com/article/53d311f3df8e3716e89499bc56019a2c}{First Lady Jill Biden and other listen to the national anthem before the NCAA Women\textquotesingle s Final Four championship basketball game =between LSU and Iowa Sunday, April 2, 2023, in Dallas. (AP Photo/Tony Gutierrez) First lady...}

\entryitemWithDescription{\hskip 0pt{}Novel treatment shows promise against rare cancer in kids}{https://apnews.com/article/9c957b7b0737067cb37a61d4449f38dc}{This December 1993 microscope photo provided by the National Cancer Institute shows a typical neuroblastoma with rosette formation. In a study published Wednesday, April 5, 2023, in the New England Journal of Medicine, a novel treatment...}

\entryitemWithDescription{\hskip 0pt{}NPR protests as Twitter calls it 'state-affiliated media'}{https://apnews.com/article/dea3e04905e423f7a8df9ba077d421f3}{FILE - The headquarters for National Public Radio (NPR) stands on North Capitol Street on April 15, 2013, in Washington. Twitter has labeled National Public Radio (NPR) as ``state-affiliated media'' on the social media site Wednesday...}

\entryitemWithDescription{\hskip 0pt{}Pence won't appeal order compelling grand jury testimony}{https://apnews.com/article/a09e5a4244c271587fac53ef9afcafb1}{FILE - Former Vice President Mike Pence speaks at the National Review Ideas Summit, March 31, 2023, in Washington. Pence won\textquotesingle t appeal order to testify in Justice Department\textquotesingle s Jan. 6 probe, according to his...}

\entryitemWithDescription{\hskip 0pt{}Whitmer strikes 1931 abortion ban from Michigan law}{https://apnews.com/article/2abb0525618a6ac5ee5a45b02ef4de3b}{Michigan Gov. Gretchen Whitmer addresses supporters before signing legislation to repeal the 1931 abortion ban statute, which criminalized abortion in nearly all cases during a bill signing ceremony, Wednesday, April 5, 2023, in...}

\entryitemWithDescription{\hskip 0pt{}Trump's bravado tested as legal woes overlap with campaign}{https://apnews.com/article/0bfe597c1d19e0f9d6e8c8bccb430176}{Former President Donald Trump speaks at his Mar-a-Lago estate Tuesday, April 4, 2023, in Palm Beach, Fla., after being arraigned earlier in the day in New York City. (AP Photo/Evan Vucci) NEW YORK (AP) --- When Donald Trump stepped into a...}

\entryitemWithDescription{\hskip 0pt{}Indiana, Idaho governors sign bans on gender-affirming care}{https://apnews.com/article/09bdabec268dbd8d79397a43f21694ed}{FILE - Indiana Gov. Eric Holcomb speaks with reporters at the Indiana Statehouse on Tuesday, April 4, 2023, in Indianapolis. On Wednesday, April 5, Holcomb signed a bill that bans all gender-affirming care for minors in the state despite...}

\entryitemWithDescription{\hskip 0pt{}Kansas bans transgender athletes from women's, girls' sports}{https://apnews.com/article/08604c663518fb2538565f3e1ac3d4ba}{Cat Poland, of Buhler, Kansas, poses with her 13-year-old trans son, Alex, after a day of lobbying by LGBTQ youth and their advocates at the Statehouse, Tuesday, March 28, 2023, in Topeka, Kan. Alex runs cross country and hopes to play...}

\entryitemWithDescription{\hskip 0pt{}Report details 'staggering' church sex abuse in Maryland}{https://apnews.com/article/7d5d3af098da59a1c9313a246566638c}{FILE - A Roman Catholic church in Lisbon is pictured on Feb. 10, 2023. On Wednesday, April 5, 2023, the Maryland Attorney General's Office publicly released a redacted version of an investigative report detailing sex abuse allegations...}

\entryitemWithDescription{\hskip 0pt{}US House leader and Taiwan president meet as China protests}{https://apnews.com/article/7f33d0bb7c307bb26da39b39df688b71}{House Speaker Kevin McCarthy, R-Calif., right, and Taiwanese President Tsai Ing-wen deliver statements to the press after a Bipartisan Leadership Meeting at the Ronald Reagan Presidential Library in Simi Valley, Calif., Wednesday, April...}

\entryitemWithDescription{\hskip 0pt{}Bob Lee, Cash App founder and MobileCoin exec, slain at 43}{https://apnews.com/article/6dce2ac028ae67720e24ea801b22e896}{A woman walks past flowers left outside an apartment building where a technology executive was fatally stabbed in San Francisco, Wednesday, April 5, 2023. Bob Lee, a technology executive who created Cash App and was currently chief...}

\entryitemWithDescription{\hskip 0pt{}Q\&A: Lewis Capaldi feels 'naked' releasing new documentary}{https://apnews.com/article/ffe4bc3fc71943fe6f69a376efbeaabe}{This image released by Netflix shows Lewis Capaldi in a scene from the documentary "Lewis Capaldi: How I\textquotesingle m Feeling Now." (Netflix via AP) Lewis Capaldi's first album went multiplatinum and led to chart-topping hits, sold...}\ichapter{Reuters}
\entryitemWithDescription{\hskip 0pt{}Violence erupts again at Jerusalem's Al-Aqsa Mosque}{https://www.reuters.com/world/middle-east/cross-border-fire-gaza-after-israeli-police-raid-al-aqsa-mosque-2023-04-05/}{Summary: Fears violence at Jerusalem holy site could spark wider conflict US urges Israelis, Palestinians to ease tensions Israeli security forces work at the Al-Aqsa compound, also known to Jews as the Temple Mount, while tension arises...}

\entryitemWithDescription{\hskip 0pt{}Man with axe kills four at crèche in southern Brazil}{https://www.reuters.com/world/americas/four-children-killed-pre-school-attack-southern-brazil-2023-04-05/}{People stand outside a pre-school after a 25-year-old man attacked children, killing several and injuring others, according to local police and hospital, in Blumenau, in the southern Brazilian state of Santa Catarina, Brazil April 5...}

\entryitemWithDescription{\hskip 0pt{}Mexican president criticizes Trump felony charges}{https://www.reuters.com/world/americas/mexican-president-criticizes-trump-felony-charges-2023-04-05/}{Mexico\textquotesingle s President Andres Manuel Lopez Obrador speaks during a news conference at the Secretariat of Security and Civilian Protection in Mexico City, Mexico March 9, 2023. REUTERS/Henry Romero/File Photo Mexican President...}

\entryitemWithDescription{\hskip 0pt{}Coronation roles for Prince George, Camilla's grandchildren, says Buckingham Palace}{https://www.reuters.com/world/uk/coronation-roles-prince-george-camillas-grandchildren-says-buckingham-palace-2023-04-04/}{The invitation for the Coronation of Britain\textquotesingle s King Charles III is seen in this undated handout image obtained by Reuters April 4, 2023. Buckingham Palace/Handout via REUTERS. Britain\textquotesingle s King Charles and...}

\entryitemWithDescription{\hskip 0pt{}'Operation Cookie Monster': International police action seizes dark web market}{https://www.reuters.com/world/uk/operation-cookie-monster-international-police-action-seizes-dark-web-market-2023-04-05/}{A projection of cyber code on a hooded man is pictured in this illustration picture taken on May 13, 2017. REUTERS/Kacper Pempel/Illustration A computer keyboard lit by a displayed cyber code is seen in this illustration picture taken on...}

\entryitemWithDescription{\hskip 0pt{}Taiwan leader, US Speaker McCarthy meet in California despite Chinese warnings}{https://www.reuters.com/world/taiwan-president-set-historic-meeting-with-us-house-speaker-california-2023-04-05/}{Taiwan\textquotesingle s President Tsai Ing-wen meets the U.S. Speaker of the House Kevin McCarthy at the Ronald Reagan Presidential Library in Simi Valley, California, U.S. April 5, 2023. REUTERS/David Swanson Taiwan\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}US, Britain walk out at UN on Russian wanted for war crimes}{https://www.reuters.com/world/europe/us-britain-walk-out-un-russian-wanted-war-crimes-2023-04-05/}{Russian Presidential Commissioner for Children\textquotesingle s Rights Maria Lvova-Belova speaks during a news conference in Moscow, Russia, April 4, 2023. A headline on a screen reads: "Aid to children from DPR (Donetsk People...}

\entryitemWithDescription{\hskip 0pt{}Putin berates US and EU envoys, top official says US aid fuelling Ukraine war's 'hot phase'}{https://www.reuters.com/world/europe/putin-berates-us-eu-ambassadors-kremlin-ceremony-2023-04-05/}{Russian President Vladimir Putin delivers a speech during a ceremony to receive diplomatic credentials from newly appointed foreign ambassadors at the Kremlin in Moscow, Russia, April 5, 2023. Sputnik/Vladimir Astapkovich/Pool via REUTERS...}

\entryitemWithDescription{\hskip 0pt{}Ireland to consult public on military neutrality in wake of Ukraine war}{https://www.reuters.com/world/europe/ireland-consult-public-military-neutrality-wake-ukraine-war-2023-04-05/}{Summary: Ireland neutrality remains widely popular Minister says must \textquotesingle respond to new reality\textquotesingle{} Cites Russia\textquotesingle s brutal disregard for international law Ireland\textquotesingle s Foreign...}

\entryitemWithDescription{\hskip 0pt{}Trump, facing criminal charges, calls for defunding the FBI}{https://www.reuters.com/world/us/trump-facing-criminal-charges-calls-defunding-fbi-2023-04-05/}{Former U.S. President Donald Trump delivers remarks on the day of his court appearance in New York after being indicted by a Manhattan grand jury following a probe into hush money paid to porn star Stormy Daniels, in Palm Beach, Florida...}

\entryitemWithDescription{\hskip 0pt{}Ukraine trains 40,000 storm brigade troops for counter-offensive}{https://www.reuters.com/world/europe/ukraine-trains-40000-storm-brigade-troops-counter-offensive-2023-04-05/}{Summary: Eight new units total 40,000 Ukrainian soldiers \textquotesingle I want revenge\textquotesingle{} on Russia, says volunteer recruit Kyiv hopes brigades will help drive back invasion Recruits of the Steel Border storm brigade...}

\entryitemWithDescription{\hskip 0pt{}China sends carrier group off Taiwan coast ahead of US meeting}{https://www.reuters.com/world/asia-pacific/china-sends-carrier-group-off-taiwan-coast-ahead-us-meeting-2023-04-05/}{Chinese and Taiwanese flags are seen in this illustration, August 6, 2022. REUTERS/Dado Ruvic/Illustration/File Photo Taiwan\textquotesingle s defence ministry said on Wednesday a Chinese aircraft carrier group was in the waters off the...}

\entryitemWithDescription{\hskip 0pt{}Why are Turkey and Hungary against Sweden joining NATO?}{https://www.reuters.com/world/europe/after-finland-joins-nato-why-is-turkey-making-sweden-wait-2023-04-04/}{The Finnish and Ukrainian flags flutter outside the city hall, as Finland becomes a member of NATO, in Helsinki, Finland, April 4, 2023. REUTERS/Tom Little Sweden\textquotesingle s path to NATO membership remains blocked by Turkey and...}\ichapter{联合早报}
\entryitemWithDescription{蔡麦会前大陆航母台海巡航}{https://www.zaobao.com/news/china/story20230405-1379880}{台湾总统蔡英文与美国众议院议长麦卡锡将在美西时间4月5日早上10时（新加坡时间4月6日凌晨1时）会面。消息传出同日，中国大陆海军``山东号''航母编队经台湾东南海域，首次展开西太平洋航训；福建海事局也在台海中北部，启动联合巡航巡查专项行动……}

\entryitemWithDescription{麦卡锡确认将与蔡英文会谈 蔡麦会前夕大陆军机飞越海峡中线}{https://www.zaobao.com/news/china/story20230405-1379585}{美国众议院议长麦卡锡（右）确认美国时间4月5日在洛杉矶与台湾总统蔡英文（左）会谈。（路透社） 将在加州进行的蔡麦会，是台美1979年断交后，在美国本土举行的最高级别会谈。大陆官方对此措辞强硬，这次的军事反应强度会不会超越佩洛西访台，没人说得准。 美国众议院议长麦卡锡确认美国时间4月5日（台湾时间4月6日清晨）在洛杉矶与台湾总统蔡英文会谈后，陆美台官方各持立场坚决回应……}

\entryitemWithDescription{银监会原官员姜丽明涉严重违纪违法 经调查被开除党籍}{https://www.zaobao.com/news/china/story20230405-1379586}{官方通报指姜丽明为逃避纪法惩处``处心积虑谋划离职''，离职后继续利用原职务影响谋取私利。（互联网） 中国金融反腐动作不断，一年前落马的中国银监会原农村中小金融机构监管部主任、恒大集团原副总裁姜丽明，星期二（4月4日）被开除党籍。官方通报特别指出，姜丽明是``逃逸式辞职''和政商``旋转门''的典型……}

\entryitemWithDescription{赴重庆抗日名将陵园献花 马英九含泪鞠躬}{https://www.zaobao.com/news/china/story20230405-1379587}{台湾前总统马英九星期二（4月4日）上午到重庆的张自忠将军烈士陵园参观。（马英九办公室） （台北／重庆综合讯）正在中国大陆访问的台湾前总统马英九星期二（4月4日）到重庆的抗日名将张自忠将军烈士陵园致哀，数度眼眶泛红，并亲自喊口号向墓碑三鞠躬。 综合《联合报》、东森新闻台和中新社等报道，马英九当天上午在张自忠孙子张庆成陪同下参观张自忠将军烈士陵园……}

\entryitemWithDescription{港前艳星彭丹自称 促成中洪建交有功}{https://www.zaobao.com/news/china/story20230405-1379588}{（香港讯）洪都拉斯宣布同台湾断交并与中国大陆建交，曾为香港艳星的彭丹，据报在当中发挥了``民间外交家''的推动作用……}

\entryitemWithDescription{沈斌任天主教上海教区主教}{https://www.zaobao.com/news/china/story20230405-1379589}{据港媒报道，中国天主教主教团主席、全国政协常委沈斌出任上海教区主教。 《星岛日报》报道，天主教上海教区光启社星期二（4月4日）说，天主教上海教区举行沈斌就职仪式。仪式由上海市天主教教务委员会主任、上海市天主教爱国会副主任吴建林神父主持，约有200人参加。 沈斌表示，将继续弘扬上海天主教爱国爱教的优良传统，坚持独立自主自办原则，坚持中国天主教中国化方向……}

\entryitemWithDescription{杨丹旭：马克龙访华谈什么？}{https://www.zaobao.com/news/china/story20230405-1379590}{马克龙此次访华的另一个任务，是在俄乌问题上寻求与北京沟通，这也是他此行最大看点……}

\entryitemWithDescription{港应对人手荒整体策略最迟年中公布}{https://www.zaobao.com/news/china/story20230405-1379591}{香港不同行业均有人手短缺问题，特别是建筑业及运输业，图为香港中环工地。（中新社） 近年香港出现移民潮，数以10万计的港人移居海外。李家超表示，整体人力不足会对市民活动、所接受的服务造成影响，也影响香港整体竞争力，当局会认真处理劳工短缺的情况。 香港多个行业在社会复常后皆闹人手荒，近来先后要求特区政府输入外劳，在社会上引起极大争议……}

\entryitemWithDescription{冠病疫苗需求锐减 康希诺生产线停产半年}{https://www.zaobao.com/news/china/story20230405-1379592}{中国疫苗生产企业康希诺生物制药有限公司位于上海的冠病疫苗生产线，自星期二（4月4日）开始停产半年，主要是由于冠病疫苗需求量锐减。 综合《每日经济新闻》与红星资本局报道，网传一份关于上药康希诺的通知显示，因外部市场环境变化，上药康希诺暂停生产，期限为180天。 康希诺生物相关人士确认了这一通知，并指这是基于冠病疫苗需求情况，公司做出的优化运营的决策……}

\entryitemWithDescription{重庆现3D人行道}{https://www.zaobao.com/news/china/story20230405-1379593}{（中新社） 中国重庆南滨路现``立体''人行道，吸引市民打卡。这个人行道通过不同颜色地砖交叉铺设的方式，形成3D立体效果，当人们俯视时能看到``立体''的人行道，而行人走在上面却和平路一样。``立体''人行道让道路看起来像是坡道或者立起来的装置，提醒司机减速慢行……}

\entryitemWithDescription{中国著名学者王缉思：症结在各自国内政治问题 中美再多对话也难改善关系}{https://www.zaobao.com/news/china/story20230404-1379240}{北京大学国际战略研究院创始院长王缉思4月3日在新加坡南洋理工大学拉惹勒南国际研究院演讲。（陈斌勤摄） 王缉思表示，美国民主党和共和党之间的共识是，用攻击中国来团结美国，美国国会和行政部门对华立场也一致。同样的，中国也因为美国这个外在威胁而团结起来。 中国著名学者王缉思说，中美关系恶化的症结在于各自的国内政治问题，再多的对话都难推动两国关系改善，中国也已不对改善中美关系抱任何期望……}

\entryitemWithDescription{国民党候选人悬而未决 为化解两岸逆境 马英九或再选总统？}{https://www.zaobao.com/news/china/story20230404-1379241}{台湾前总统马英九访问中国大陆的声量开低走高，在两岸民间掀起和平暖流。在国民党总统候选人悬而未决下，若为了化解两岸逆境，马英九能否再选总统？这个问题最近在民间引起了讨论。 受访学者评估，马英九不宜卷入选战恶斗，若他能周游陆美台并奠定和平论述，再由国民党征召出最能凝聚中间选民、非绿力量的候选人来执行，蓝军就有逆转胜的机会……}

\entryitemWithDescription{林青霞获颁 港大名誉博士学位}{https://www.zaobao.com/news/china/story20230404-1379242}{图为林青霞获颁港大名誉博士学位。~（中新社） 香港大学4月3日下午举行第209届学位颁授典礼，向七名杰出人士颁授名誉博士学位……}

\entryitemWithDescription{台陆委会：中国大陆必将介入台湾选举}{https://www.zaobao.com/news/china/story20230404-1379243}{台湾大陆委员会主委邱太三相信，中国大陆必将介入2024年台湾总统选举，希望一个立场与其相近的候选人当选。 台湾2024年将举行总统选举。据《自由时报》报道，邱太三直言，如果说中国大陆不想要影响台湾的选举，``这个就太小看它了''。他指出，无论是使用资金或其他方式，历届台湾总统选举都可以看到中国大陆介入的案例；一些在台特定团体会扮演角色，让代理人参与立委选举……}

\entryitemWithDescription{戴庆成：港府限制市民游行惹争议}{https://www.zaobao.com/news/china/story20230404-1379245}{眼下香港社会问题丛生，游行示威活动在人为因素的限制下大减，显然不利当局找出社会问题所在……}

\entryitemWithDescription{港天星小轮两航线加价}{https://www.zaobao.com/news/china/story20230404-1379248}{香港天星小轮两条航线4月3日起加价，``中环至尖沙咀''以及``湾仔至尖沙咀''航线，平日成人上层票价由3.2港元加至5港元（0.54新元至0.85新元）。周末、周日及公共假期，上层票价由4.2港元加至6.5港元。月票就由160港元加至190港元。长者免费乘船优惠取消，但合资格长者可以享用2港元乘车优惠……}

\entryitemWithDescription{港美国商会：逾七成会员 对港目前法治有信心}{https://www.zaobao.com/news/china/story20230404-1379249}{香港美国商会最新调查显示，逾七成会员对香港目前的法治有信心。不过，超过五成会员对香港过去一年的法治情况信心转差。 香港美国商会今年1月16日至2月26日进行调查，上星期四（3月30日）在商会网站公布调查报告。在接受调查的会员中，73\%对香港目前的法治有信心，非常有信心和有信心占29\%，一般有信心44\%，没信心和完全没信心占27\%……}

\entryitemWithDescription{钟南山建议中国民众 4月以后可不戴口罩}{https://www.zaobao.com/news/china/story20230403-1378917}{钟南山建议中国民众4月后在条件允许的情况下，可以不戴口罩。图为3月27日北京一处火车站等候登车的旅客，多数戴着口罩。（法新社） （广州讯） 按照中国目前的冠病疫情形势，中国工程院院士钟南山认为，佩戴口罩可成为非强制性的措施，建议今年4月以后在条件允许情况下让民众不戴口罩。 据《南方都市报》报道，钟南山星期五（3月31日）在广州一场有关冠病药物的研讨会上指出，过去三年，戴口罩是预防病毒的有效措施……}

\entryitemWithDescription{在湖南大学解说一中 马英九：两岸``都是中华民国''同属中国}{https://www.zaobao.com/news/china/story20230403-1378918}{马英九（中左）星期天带领台湾青年学生，与湖南大学校长段献忠（中右）等师生交流座谈，现场气氛友好热烈。（新华社） 马英九重申两岸同文同种，双方都坚持一个中国的立场，尽管目前分属两边，有各自的制度和政策，但希望双方真诚交流、减少不必要隔阂，并呼吁两岸青年生力军继续交流。 台湾前总统马英九星期天（4月2日）在与湖南大学师生座谈时说，``台湾和中国大陆都是中华民国''，但同属一个中国……}