\entryitemWithDescription{\hskip 0pt{}Publisher drops children's illustrator for anti-trans notes}{https://apnews.com/article/9306e7e85c9f432e7bd2c79c13498c15}{The children\textquotesingle s book "You Are Home With Me," illustrated by Mitchell Thomas Watley, is shown at a bookstore in Portland, Ore. in this April 5, 2023 photo. Publisher Sasquatch books, owned by Penguin Random House, said...}

\entryitemWithDescription{\hskip 0pt{}LSU's Reese on White House flap: 'We'll go to the Obamas'}{https://apnews.com/article/53d311f3df8e3716e89499bc56019a2c}{First Lady Jill Biden and other listen to the national anthem before the NCAA Women\textquotesingle s Final Four championship basketball game =between LSU and Iowa Sunday, April 2, 2023, in Dallas. (AP Photo/Tony Gutierrez) First lady...}

\entryitemWithDescription{\hskip 0pt{}Novel treatment shows promise against rare cancer in kids}{https://apnews.com/article/9c957b7b0737067cb37a61d4449f38dc}{This December 1993 microscope photo provided by the National Cancer Institute shows a typical neuroblastoma with rosette formation. In a study published Wednesday, April 5, 2023, in the New England Journal of Medicine, a novel treatment...}

\entryitemWithDescription{\hskip 0pt{}NPR protests as Twitter calls it 'state-affiliated media'}{https://apnews.com/article/dea3e04905e423f7a8df9ba077d421f3}{FILE - The headquarters for National Public Radio (NPR) stands on North Capitol Street on April 15, 2013, in Washington. Twitter has labeled National Public Radio (NPR) as ``state-affiliated media'' on the social media site Wednesday...}

\entryitemWithDescription{\hskip 0pt{}Pence won't appeal order compelling grand jury testimony}{https://apnews.com/article/a09e5a4244c271587fac53ef9afcafb1}{FILE - Former Vice President Mike Pence speaks at the National Review Ideas Summit, March 31, 2023, in Washington. Pence won\textquotesingle t appeal order to testify in Justice Department\textquotesingle s Jan. 6 probe, according to his...}

\entryitemWithDescription{\hskip 0pt{}Whitmer strikes 1931 abortion ban from Michigan law}{https://apnews.com/article/2abb0525618a6ac5ee5a45b02ef4de3b}{Michigan Gov. Gretchen Whitmer addresses supporters before signing legislation to repeal the 1931 abortion ban statute, which criminalized abortion in nearly all cases during a bill signing ceremony, Wednesday, April 5, 2023, in...}

\entryitemWithDescription{\hskip 0pt{}Trump's bravado tested as legal woes overlap with campaign}{https://apnews.com/article/0bfe597c1d19e0f9d6e8c8bccb430176}{Former President Donald Trump speaks at his Mar-a-Lago estate Tuesday, April 4, 2023, in Palm Beach, Fla., after being arraigned earlier in the day in New York City. (AP Photo/Evan Vucci) NEW YORK (AP) --- When Donald Trump stepped into a...}

\entryitemWithDescription{\hskip 0pt{}Indiana, Idaho governors sign bans on gender-affirming care}{https://apnews.com/article/09bdabec268dbd8d79397a43f21694ed}{FILE - Indiana Gov. Eric Holcomb speaks with reporters at the Indiana Statehouse on Tuesday, April 4, 2023, in Indianapolis. On Wednesday, April 5, Holcomb signed a bill that bans all gender-affirming care for minors in the state despite...}

\entryitemWithDescription{\hskip 0pt{}Kansas bans transgender athletes from women's, girls' sports}{https://apnews.com/article/08604c663518fb2538565f3e1ac3d4ba}{Cat Poland, of Buhler, Kansas, poses with her 13-year-old trans son, Alex, after a day of lobbying by LGBTQ youth and their advocates at the Statehouse, Tuesday, March 28, 2023, in Topeka, Kan. Alex runs cross country and hopes to play...}

\entryitemWithDescription{\hskip 0pt{}Report details 'staggering' church sex abuse in Maryland}{https://apnews.com/article/7d5d3af098da59a1c9313a246566638c}{FILE - A Roman Catholic church in Lisbon is pictured on Feb. 10, 2023. On Wednesday, April 5, 2023, the Maryland Attorney General's Office publicly released a redacted version of an investigative report detailing sex abuse allegations...}

\entryitemWithDescription{\hskip 0pt{}US House leader and Taiwan president meet as China protests}{https://apnews.com/article/7f33d0bb7c307bb26da39b39df688b71}{House Speaker Kevin McCarthy, R-Calif., right, and Taiwanese President Tsai Ing-wen deliver statements to the press after a Bipartisan Leadership Meeting at the Ronald Reagan Presidential Library in Simi Valley, Calif., Wednesday, April...}

\entryitemWithDescription{\hskip 0pt{}Bob Lee, Cash App founder and MobileCoin exec, slain at 43}{https://apnews.com/article/6dce2ac028ae67720e24ea801b22e896}{A woman walks past flowers left outside an apartment building where a technology executive was fatally stabbed in San Francisco, Wednesday, April 5, 2023. Bob Lee, a technology executive who created Cash App and was currently chief...}

\entryitemWithDescription{\hskip 0pt{}Q\&A: Lewis Capaldi feels 'naked' releasing new documentary}{https://apnews.com/article/ffe4bc3fc71943fe6f69a376efbeaabe}{This image released by Netflix shows Lewis Capaldi in a scene from the documentary "Lewis Capaldi: How I\textquotesingle m Feeling Now." (Netflix via AP) Lewis Capaldi's first album went multiplatinum and led to chart-topping hits, sold...}