\entryitemWithDescription{\hskip 0pt{}Prosecutors won't charge ex-UFC champ Conor McGregor with sexual assault after NBA Finals incident}{https://apnews.com/article/4b376708ed1521ce4da0ab33ead4a595}{MIAMI (AP) --- Former UFC champion Conor McGregor will not face sexual assault charges following an investigation of allegations that surfaced during the NBA Finals last June in Miami, his lawyer, police and prosecutors said Wednesday...}

\entryitemWithDescription{\hskip 0pt{}Fugees rapper says lawyer's use of AI helped tank his case, pushes for new trial}{https://apnews.com/article/d2c93aa5404eba63c3347a05fe8ba091}{WASHINGTON (AP) --- A multimillion-dollar conspiracy trial that stretched across the worlds of politics and entertainment is now touching on the tech world with arguments that a defense attorney for a Fugees rapper bungled closing...}

\entryitemWithDescription{\hskip 0pt{}Elephant dies at St. Louis Zoo shortly after her herd became agitated from a dog running loose}{https://apnews.com/article/5ad9cdc5b483c86b25b1adc21f013cc5}{ST. LOUIS (AP) --- A female Asian elephant at the St. Louis Zoo died shortly after her herd became agitated from a small dog running loose, zoo officials said. Rani (pronounced Rahn-ee) died Friday at age 27. The zoo announced her death...}

\entryitemWithDescription{\hskip 0pt{}NFL Commissioner Roger Goodell gets a contract extension through March 2027}{https://apnews.com/article/92cb22c666aae3ebdde208fd28d683eb}{NEW YORK (AP) --- NFL Commissioner Roger Goodell received his long-expected contract extension on Wednesday. ``The Compensation Committee updated the full ownership today that an agreement has been reached to extend Commissioner Roger...}

\entryitemWithDescription{\hskip 0pt{}United Airlines rolling out plan that lets passengers in economy class with window seats board first}{https://apnews.com/article/c912cef578c0b19be65dbc1b458aa359}{United Airlines will start boarding passengers in economy class with window seats first starting next week, a move designed to reduce the time planes spend sitting on the ground. The airline said in an internal memo that it will implement...}

\entryitemWithDescription{\hskip 0pt{}Amazon will start testing drones that will drop prescriptions on your doorstep, literally}{https://apnews.com/article/e258b418f2806098de1fba17069b9fe4}{Amazon will soon make prescription drugs fall from the sky when the e-commerce giant becomes the latest company to test drone deliveries for medications. The company said Wednesday that customers in College Station, Texas, can now get...}

\entryitemWithDescription{\hskip 0pt{}Serena Williams has a 2-book deal, starting with an `intimate' and `open-hearted' memoir}{https://apnews.com/article/b5f1380ad2ca051957bbc1aff50c7bf8}{NEW YORK (AP) --- Now that she's stepped back from the sport she dominated like few others, Serena Williams is ready to reflect. The tennis great has a two-book deal with the Random House Publishing Group, starting with an ``intimate''...}

\entryitemWithDescription{\hskip 0pt{}Musk's X tests \$1 fee for new users in the Philippines and New Zealand in bid to target spam}{https://apnews.com/article/0cb87465f38676282bbc5dd3a9672ca6}{LONDON (AP) --- Elon Musk's social media platform X has begun charging a \$1 fee to new users in the Philippines and New Zealand, in a test designed to cut down on the spam and fake accounts flourishing on the site formerly known as...}

\entryitemWithDescription{\hskip 0pt{}Report: Young driver fatality rates have fallen sharply in the US, helped by education, technology}{https://apnews.com/article/f3ce1bab8d8f525ffc2cbe4a77f94ca0}{NEW YORK (AP) --- Crash and fatality rates among drivers under 21 have fallen dramatically in the U.S. during the past 20 years, a new report says, while noting young drivers are still the riskiest group behind the wheel. Using data from...}

\entryitemWithDescription{\hskip 0pt{}Suspect in Holloway disappearance to appear in federal court for extortion case; plea deal possible}{https://apnews.com/article/30438803fa005835f3fa5ef0888ad8fc}{BIRMINGHAM, Ala. (AP) --- An attorney for the mother of Alabama teen Natalee Holloway, who disappeared in Aruba, said a possible plea deal with a suspect in an extortion case is contingent upon his disclosing details about her death...}

\entryitemWithDescription{\hskip 0pt{}Maren Morris files for divorce from Ryan Hurd, citing music couple's `irreconcilable differences'}{https://apnews.com/article/7aa7acf7686683159e35a4529fcd33c7}{NASHVILLE, Tenn. (AP) --- Maren Morris has filed for divorce from her husband Ryan Hurd, citing the prominent country music couple's ``irreconcilable differences'' after five years of marriage. Morris filed the divorce complaint in...}

\entryitemWithDescription{\hskip 0pt{}Britney Spears writes of abortion while dating Justin Timberlake in excerpts from upcoming memoir}{https://apnews.com/article/b67f8514d72acb0b2ecc7c0c9b6984cc}{Britney Spears wrote that she had an abortion while dating Justin Timberlake more than 20 years ago, according to a peek inside her hotly anticipated memoir. ``If it had been left up to me alone, I never would have done it,'' she writes...}

\entryitemWithDescription{\hskip 0pt{}Jada Pinkett Smith says revealing separation from Will Smith is a `weight off my shoulders'}{https://apnews.com/article/bfdc1490d17d6919cf126036d2231db8}{NEW YORK (AP) --- Jada Pinkett Smith is feeling free these days. She's no longer hiding that she's been separated from megastar husband Will Smith for seven years. ``It's a weight off my shoulders, honestly,'' said Pinkett Smith whose new...}