\entryitemWithDescription{\hskip 0pt{}How to watch Michigan vs. Washington in national championship: Channel, time, streaming}{https://apnews.com/article/238551023ead9a3474e75a007cbb9c5c}{Washington plays Michigan in the College Football Playoff championship game on Monday, with the Huskies looking for their first national title since 1991 and the Wolverines going for their first since 1997. Both teams are in their first...}

\entryitemWithDescription{\hskip 0pt{}Nadal withdraws from the Australian Open with an injury just one tournament into his comeback}{https://apnews.com/article/bc5b48b6c047e49eb09657aab3abbb66}{MELBOURNE, Australia (AP) --- Rafael Nadal's comeback from hip surgery is on hold after he withdrew from the Australian Open with an injury a week before the start of the season's first Grand Slam tournament. The 22-time major champion...}

\entryitemWithDescription{\hskip 0pt{}Coal miners in North Dakota unearth a mammoth tusk buried for thousands of years}{https://apnews.com/article/3fc986cc553553cade8c12628a93cdb6}{BISMARCK, N.D. (AP) --- The first person to spot it was a shovel operator working the overnight shift, eyeing a glint of white as he scooped up a giant mound of dirt and dropped it into a dump truck. Later, after the truck driver dumped...}

\entryitemWithDescription{\hskip 0pt{}Resurrected Golden Globes will restart the party with `Barbie,' `Oppenheimer' and Swift}{https://apnews.com/article/b684b6e3d6b0ddf07b74a0370413fb7a}{The Golden Globes are back from the dead, and ready to party. The long-running award show will again have the champagne flowing Sunday night when the 81st Globes begin at 8 p.m. EST. Much will look the same as always when well-attired...}

\entryitemWithDescription{\hskip 0pt{}Steelers top Lamar-less Ravens 17-10, will make the playoffs if Buffalo or Jacksonville loses}{https://apnews.com/article/e1454409a193af03deef3fcb4ea38a30}{BALTIMORE (AP) --- Cameron Heyward figures the Pittsburgh Steelers can make some noise in the playoffs. They still need a little help to get in, but they've certainly done their part down the stretch. ``Let us be dangerous,'' said...}

\entryitemWithDescription{\hskip 0pt{}Orthodox mark Christmas, but the celebration is overshadowed for many by conflict}{https://apnews.com/article/764b80abfea30a750801e7dfea056f73}{Orthodox Christians packed churches Saturday night for Christmas Eve services, a holiday overshadowed for many believers by conflict. Traditions vary, but typically the main worship service for Orthodox Christians takes place the night...}

\entryitemWithDescription{\hskip 0pt{}Florida's Greek community celebrates the Epiphany with annual dive into water to retrieve cross}{https://apnews.com/article/65ccabf6ff238bce44d8f60f22d73cde}{TARPON SPRINGS, Fla. (AP) --- After thunderstorms moved past, Florida's largest Greek Orthodox community celebrated the Epiphany on Saturday as a 16-year-old boy dove into chilly water to retrieve a cross in an annual rite that draws...}

\entryitemWithDescription{\hskip 0pt{}11-year-old killed in Iowa school shooting was a joyful boy known as `Smiley,' his mother says}{https://apnews.com/article/fd64d5afce815e0d91e004380b00664a}{DES MOINES, Iowa (AP) --- Ahmir Jolliff dashed out of his home in Perry Thursday morning, eager to see his friends on the first day back to school after winter break. It was vintage Ahmir --- known as ``Smiley'' around his house --- an 11...}

\entryitemWithDescription{\hskip 0pt{}A minibus explodes in Kabul, killing at least 2 civilians and wounding 14 others}{https://apnews.com/article/0e7594f1f21b01e5a512b8e6b94d7416}{ISLAMABAD (AP) --- A minibus exploded in a mostly Shiite Muslim neighborhood in Afghanistan's capital of Kabul killing at least two civilians and wounding 14 others, a Taliban official said Saturday. It was the first attack in the country...}

\entryitemWithDescription{\hskip 0pt{}Police probe UK Post Office for accusing over 700 employees of theft. The culprit was an IT glitch}{https://apnews.com/article/797199a37c4dbb91e0a4f1f9567fe96f}{LONDON (AP) --- U.K. police have opened a fraud investigation into Britain's Post Office over a miscarriage of justice that saw hundreds of postmasters wrongfully accused of stealing money when a faulty computer system was to blame. The...}

\entryitemWithDescription{\hskip 0pt{}Michigan Republicans vote to remove election denier, chair Karamo, who promises not to accept result}{https://apnews.com/article/0f4c85738f2f675f36ebe1df839c5239}{COMMERCE TOWNSHIP, Mich. (AP) --- Michigan Republicans have voted to remove election denier and state GOP Chairwoman Kristina Karamo during a meeting Saturday after many of the party's leaders called for her resignation following a year...}

\entryitemWithDescription{\hskip 0pt{}Judith Light and `Last of Us' actors are first-time winners at Creative Arts Emmy Awards}{https://apnews.com/article/0453719974b32c12ec84ee7bd0d52f96}{LOS ANGELES (AP) --- Judith Light from ``Poker Face'' and Nick Offerman and Storm Reid from ``The Last of Us'' were winners at Saturday night's Creative Arts Emmy Awards on a night when the theme was first-time Emmys for actors of all...}

\entryitemWithDescription{\hskip 0pt{}The US northeast is preparing for a weekend storm that threatens to dump snow, rain, and ice}{https://apnews.com/article/9d65fb1213a5a37b0231cde4b6623058}{Millions of people across the eastern U.S. are preparing for a wintry mix of precipitation as a potent storm system looks to bring snow, freezing rain and ice to the region. The system is expected to reach North Carolina by Saturday...}