\entryitemWithDescription{\hskip 0pt{}Mother of 6-year-old who shot teacher faces federal charges over marijuana use, gun possession}{https://apnews.com/article/6919841d0216e132326d2e0df3f92412}{FILE - Police look on as students return to Richneck Elementary following a school shooting in which a 6-year-old boy shot his teacher, Jan. 30, 2023, in Newport News, Va. The mother of the 6-year-old boy who shot his teacher in Virginia...}

\entryitemWithDescription{\hskip 0pt{}Jacob deGrom, oft-injured Rangers ace, to have season-ending Tommy John surgery}{https://apnews.com/article/c03d0e232655bfc10c6f01ca88f9c484}{FILE -Texas Rangers starting pitcher Jacob deGrom pitches during the third inning of a baseball game against the New York Yankees, Friday, April 28, 2023, in Arlington, Texas. Texas ace Jacob deGrom will have season-ending Tommy John...}

\entryitemWithDescription{\hskip 0pt{}Detroit clerk who locked door before customers were shot will face trial}{https://apnews.com/article/1f7fd704055272fb311088da5fe23fbc}{Al-Hassan Aiyash, center, leaves a court with his attorney Ben Gonek on Tuesday, June 6, 2023, in Detroit, Michigan. A judge ordered Aiyash to trial on an involuntary manslaughter charge. (AP Photo/Ed White) DETROIT (AP) --- A judge on...}

\entryitemWithDescription{\hskip 0pt{}With 'Across the Spider-Verse,' Phil Lord and Chris Miller 'blow the doors open'}{https://apnews.com/article/ac8a1c24bd001ee61000b1dd866413c7}{FILE - Phil Lord, left, and Christopher Miller arrive at the world premiere of "Spider-Man: Across The Spider-verse" on Tuesday, May 30, 2023, at the Regency Village Theatre in Los Angeles. (Photo by Richard Shotwell/Invision/AP, File...}

\entryitemWithDescription{\hskip 0pt{}Man pleads guilty to strangling and dumping body of Missouri woman 3 decades ago}{https://apnews.com/article/3f92853990defde434a6f553a9dd1e8b}{FILE - This Dec. 23, 2019 arrest photo provided by the Franklin County, Mo., Sheriff\textquotesingle s Department shows Kirby King. King has pleaded guilty Friday, June 2, 2023, to strangling a woman in Missouri and leaving her bound body...}

\entryitemWithDescription{\hskip 0pt{}Mexico lowers alert level for Popocatepetl volcano}{https://apnews.com/article/056e61050bb0f4f239743b8617099e07}{FILE - Jose Marcos de Olarte walks his mule to plant corn on his land near the Popocatepetl volcano, in Santiago Xalitzintla, Mexico, May 25, 2023. Mexico lowered the alert level on the Popocatepetl volcano Tuesday, June 6, 2023, after...}

\entryitemWithDescription{\hskip 0pt{}US weighs in on Roger Waters antisemitism debate, says artist has long history of denigrating Jews}{https://apnews.com/article/3aa8d1dadf8d633f2c3274a6a8f9ef6f}{Roger Waters performs at Barclays Arena in Hamburg, Germany, on Sunday, May 7, 2023, to kick off his "This Is Not A Drill" tour of Germany. (Daniel Bockwoldt/dpa via AP) WASHINGTON (AP) --- The Biden administration is weighing in on the...}

\entryitemWithDescription{\hskip 0pt{}Browns defensive players robbed of jewelry, vehicle by masked men in downtown stickup}{https://apnews.com/article/ac7ff013778c0ce2b6b642efcc86b717}{Cleveland Browns cornerback Greg Newsome II watches during a drill at the NFL football team\textquotesingle s practice facility Tuesday, June 6, 2023, in Berea, Ohio. (AP Photo/Ron Schwane) BEREA, Ohio (AP) --- Cleveland Browns coach...}

\entryitemWithDescription{\hskip 0pt{}EU member Slovenia overwhelmingly defeats Moscow ally Belarus for a seat on the UN Security Council}{https://apnews.com/article/d8ffe47a0353386b4fa9403f5207f8a3}{The UN Security Council meets to discuss the war in Ukraine, Monday, May 15, 2023, at United Nations headquarters. (AP Photo/John Minchillo) UNITED NATIONS (AP) --- In an election that reflected strong global opposition to Russia's war...}

\entryitemWithDescription{\hskip 0pt{}Papa Jake survived D-Day on Omaha Beach, now he's a TikTok star}{https://apnews.com/article/d049a9d5fab52932d341ca5a34fb49c5}{U.S. veteran SSgt. Jake M. Larson talks to a girl who wears an American flag around her neck during a gathering in preparation of the 79th D-Day anniversary in La Fiere, Normandy, France, Sunday, June 4, 2023. The landings on the coast of...}

\entryitemWithDescription{\hskip 0pt{}5 things to know from Prince Harry's day in court}{https://apnews.com/article/318b9c1443a0cab3d89151cdae49b774}{Prince Harry arrives at the High Court in London, Tuesday, June 6, 2023. Prince Harry is due at a London court to testify against a tabloid publisher he accuses of phone hacking and other unlawful snooping. Harry alleges that journalists...}

\entryitemWithDescription{\hskip 0pt{}Merck sues federal government, calling plan to negotiate Medicare drug prices extortion}{https://apnews.com/article/179cca2e1b9319782683909ccca5d24a}{FILE - A Merck scientist conducts research on Feb. 28, 2013, in West Point, Pa. Merck is suing the federal government Tuesday, June 6, 2023, over a plan to negotiate Medicare drug prices, calling the program a sham equivalent to...}

\entryitemWithDescription{\hskip 0pt{}Banks' growing reliance on chatbots to handle customer service tasks worries consumer watchdog}{https://apnews.com/article/0385eefec5b0054ce01cc6c4a56b9bd1}{FILE - Consumer Financial Protection Bureau Director Rohit Chopra, speaks from the South Court Auditorium on the White House complex in Washington, April 11, 2022. The Consumer Financial Protection Bureau released a report Tuesday where...}