\entryitemWithDescription{\hskip 0pt{}Some video game actors are letting AI clone their voices. They just don't want it to replace them}{https://apnews.com/article/517cc248f60a2f5e35f9b239b70f20a7}{If you are battling a video game goblin who speaks with a Cockney accent, or asking a gruff Scottish blacksmith to forge a virtual sword, you might be hearing the voice of actor Andy Magee. Except it's not quite Magee's voice. It's a...}

\entryitemWithDescription{\hskip 0pt{}Strike at the Eiffel Tower closes one of the world's most popular monuments to visitors}{https://apnews.com/article/2cb788d0648f282ca57a0933bd792c52}{PARIS (AP) --- Visitors to the Eiffel Tower were turned away on Monday because of a strike over poor financial management at one of the world's most-visited sites. A sign was posted at the entrance in English, saying, ``Due to strike, the...}

\entryitemWithDescription{\hskip 0pt{}Points records fall at the All-Star Game, with the East beating the West 211-186}{https://apnews.com/article/a1360d4bd306468522ee22dc9bf59da2}{INDIANAPOLIS (AP) --- The NBA wanted more competition. It got more points instead --- more than ever before. And once again, the All-Star Game was all offense. All-Star MVP Damian Lillard of the Milwaukee Bucks scored 39 points and the...}

\entryitemWithDescription{\hskip 0pt{}Jaromir Jagr's return to Pittsburgh ends with his No. 68 being retired — and catharsis}{https://apnews.com/article/7f5887d92045350753f3ccf8d001f9bc}{PITTSBURGH (AP) --- There were jokes. And laughter. And catharsis. Just no tears. At least none from Jaromir Jagr. Maybe because they were unnecessary when the Pittsburgh Penguins retired his iconic No. 68 on Sunday. The look on Jagr's...}

\entryitemWithDescription{\hskip 0pt{}LeBron James still committed to Paris Olympics, but health remains the big key}{https://apnews.com/article/05d1e4113d25a7593a2e11460da06fe4}{INDIANAPOLIS (AP) --- LeBron James still wants to participate in the Paris Olympics this summer, sure sounds like extending his NBA career for at least a couple more seasons is an option and said he would like to see his playing days end...}

\entryitemWithDescription{\hskip 0pt{}The Rock, Pitbull, DJ Khaled bring South Florida flavor to Daytona 500}{https://apnews.com/article/20df5d43adbaa18b9b06c7ddea8e0192}{DAYTONA BEACH, Fla. (AP) --- The 3-0-5 took over the Daytona 5-0-0. Dwayne ``The Rock'' Johnson, Pitbull and DJ Khaled represented South Florida at the Daytona 500, as the trio of Sunshine State celebrities brought a dose of star power to...}

\entryitemWithDescription{\hskip 0pt{}`Oppenheimer' aims for a record haul as stars shine at the British Academy Film Awards}{https://apnews.com/article/220af1ec73e47e6222abe2b0934cddc8}{LONDON (AP) --- Atom-bomb epic ``Oppenheimer'' could smash a 53-year-old record at the British Academy Film Awards on Sunday if it makes good on its field-leading 13 nominations. Christopher Nolan 's biopic of physicist J. Robert...}

\entryitemWithDescription{\hskip 0pt{}Stephen Curry tops Sabrina Ionescu in 3-point shootout at All-Star weekend}{https://apnews.com/article/b2e42e474bd3877bf2c36a5b2cf31213}{INDIANAPOLIS (AP) --- Stephen Curry was on a roll --- and it was barely enough to beat Sabrina Ionescu. And fittingly, he won by three. The Golden State star and NBA's all-time 3-point king beat Ionescu 29-26 in the Steph vs. Sabrina...}

\entryitemWithDescription{\hskip 0pt{}George Santos sues late-night host Jimmy Kimmel for tricking him into making videos to ridicule him}{https://apnews.com/article/41e1c2951945e11c069a41f9ea62281d}{NEW YORK (AP) --- Former U.S. Rep. George Santos alleged in a lawsuit filed Saturday in New York that late-night host Jimmy Kimmel deceived him into making videos on the Cameo app that were used to ridicule the disgraced lawmaker on the...}

\entryitemWithDescription{\hskip 0pt{}Trump hawks \$399 branded shoes at `Sneaker Con,' a day after a \$355 million ruling against him}{https://apnews.com/article/4de093eda6f8d1c68baf8fe8095f777b}{PHILADELPHIA (AP) --- As he closes in on the Republican presidential nomination, former President Donald Trump made a highly unusual stop Saturday, hawking new Trump-branded sneakers at ``Sneaker Con,'' a gathering that bills itself as...}

\entryitemWithDescription{\hskip 0pt{}ECU baseball player appears in game with prosthetic leg after boating accident}{https://apnews.com/article/5a7ee744c34595af89763efa5cabc8ef}{GREENVILLE, N.C. (AP) --- East Carolina sophomore Parker Byrd appeared in Friday's season-opening win against Rider with a prosthetic leg after having part of his right leg amputated following a 2022 boating accident. The school said he...}

\entryitemWithDescription{\hskip 0pt{}WWII Monuments Men weren't all men. The female members finally move into the spotlight}{https://apnews.com/article/42cb40c2a6c0704d424758706d758b38}{DALLAS (AP) --- After World War II, the U.S. Army's art experts set out to find and return millions of works stolen by the Nazis. Known as the Monuments Men, they included Mary Regan Quessenberry, who from her base in Berlin traveled to...}

\entryitemWithDescription{\hskip 0pt{}Pennsylvania magistrate judge is charged with shooting her ex-boyfriend as he slept}{https://apnews.com/article/4eeb11249dd828c5919b4f324f8c4ff0}{HARRISBURG, Pa. (AP) --- A suspended magistrate judge in Pennsylvania shot her estranged boyfriend in the head as he slept last weekend, police said Thursday in filing attempted murder and aggravated assault charges against her. Tests...}