\entryitemWithDescription{\hskip 0pt{}San Diego State muscles past Creighton, makes 1st Final Four}{https://apnews.com/article/9ca0eee57ad130c3f5e55793918d4f6f}{San Diego State forward Aguek Arop (33) celebrates victory against Creighton in the second half of a Elite 8 college basketball game in the South Regional of the NCAA Tournament, Sunday, March 26, 2023, in Louisville, Ky. San Diego State...}

\entryitemWithDescription{\hskip 0pt{}Army pulls recruiting ads after Jonathan Majors' arrest}{https://apnews.com/article/18c820b6ddf5e14fb68b731f2d37ab5c}{FILE - Jonathan Majors arrives at the premiere of "Creed III" on Feb. 27, 2023, at TCL Chinese Theatre in Los Angeles. The arrest of actor Majors on Saturday, March 25, 2023, has upended the Army's newly launched advertising campaign that...}

\entryitemWithDescription{\hskip 0pt{}UConn's return to prominence has been a family affair}{https://apnews.com/article/991ed964ad4e104fc14180b8026645e5}{UConn head coach Dan Hurley celebrates after cutting down the netting from the 82-54 win against Gonzaga of an Elite 8 college basketball game in the West Region final of the NCAA Tournament, Saturday, March 25, 2023, in Las Vegas. (AP...}

\entryitemWithDescription{\hskip 0pt{}Union Pacific 2nd railroad to drop push for one-person crews}{https://apnews.com/article/8bc04b745bf49337ad94cec87d2df92b}{FILE - A Union Pacific train engine sits in a rail yard on Wednesday, Sept. 14, 2022, in Commerce, Calif. Union Pacific said Saturday, March 25, 2023, that the company has backed away from the industry\textquotesingle s longstanding push...}

\entryitemWithDescription{\hskip 0pt{}Is the David porn? See for yourself, Italy ask Fla. parents}{https://apnews.com/article/56d2977c3fceefd02f475f9d4d0be3d9}{FILE - German Chancellor Angela Merkel, left, and Italian Prime Minister Matteo Renzi speak during a press conference in front of Michelangelo\textquotesingle s "David statue" after their bilateral summit in Florence, Italy, on Jan. 23...}

\entryitemWithDescription{\hskip 0pt{}Pray for rain: Spanish farmers hold unique Mass amid drought}{https://apnews.com/article/d4b07bb5f39a1009da23bf9557774e5b}{Local residents take part in a procession carrying a replica of the Our Lady of the Torrents, a virgin historically associated with drought, in l\textquotesingle Espunyola, north of Barcelona, Spain, Sunday, March 26, 2023. Farmers and...}

\entryitemWithDescription{\hskip 0pt{}4th person found dead in chocolate factory blast; 3 missing}{https://apnews.com/article/e4b3197a3cfa6d3a93a7519d83a7aa26}{Emergency responders and heavy equipment are seen at the site of a deadly explosion at a chocolate factory in West Reading, Pennsylvania, Saturday, March 25. (AP Photo/Michael Rubinkam) WEST READING, Pa. (AP) --- A fourth person was...}

\entryitemWithDescription{\hskip 0pt{}Biden's Justice Dept. keeps hard line in death row cases}{https://apnews.com/article/987c9f078d527220d75e728fa68d26a1}{This photo provided by Taylor Legal Team shows Rejon Taylor. Taylor hoped the election of Joe Biden, the first U.S. president to campaign on a pledge to end the death penalty, would mean a more sympathetic look at his claims that racial...}

\entryitemWithDescription{\hskip 0pt{}In Ghana, Kamala Harris 'excited about the future of Africa'}{https://apnews.com/article/a1ecb70d87bfecf3b983d15afc498379}{U.S. Vice President Kamala Harris greets school children during her arrival ceremony at Kotoka International Airport in Accra, Ghana Sunday, March 26, 2023. Harris is on a seven-day African visit that will also take her to Tanzania and...}

\entryitemWithDescription{\hskip 0pt{}States' divisions on abortion widen after Roe overturned}{https://apnews.com/article/fd2e6fffffec2fdcf328d7bca1e6fd78}{FILE - People line up, March 20, 2023, outside a hearing room in the Oregon state Capital in Salem, Ore., where a public hearing was being held on a bill seeking to expand access to abortion and gender-affirming care. In legislative...}

\entryitemWithDescription{\hskip 0pt{}Gap grows between TikTok users, lawmakers on potential ban}{https://apnews.com/article/a92f048762d6657f291affb7a0ce6386}{Supporters of TikTok hold signs during a rally to defend the app, Wednesday, March 22, 2023, at the Capitol in Washington. The House holds a hearing Thursday, with TikTok CEO Shou Zi Chew about the platform\textquotesingle s consumer...}

\entryitemWithDescription{\hskip 0pt{}Planets on parade: 5 will be lined up in night sky this week}{https://apnews.com/article/d0170eea9fee67680cf2f1bca68a4fcf}{FILE - A girl looks at the moon through a telescope in Caracas, Venezuela, on Sunday, May 15, 2022. The best day to spot five planets, Mercury, Jupiter, Venus, Uranus and Mars, lined up in the night sky is Tuesday, March 28, 2023, right...}

\entryitemWithDescription{\hskip 0pt{}Ukraine demands emergency UN meeting over Putin nuclear plan}{https://apnews.com/article/3aed32661ae3c218c59117d1ce593777}{Ukrainian servicemen fold the national flag over the coffin of their comrade Andrii Neshodovskiy during the funeral ceremony in Kyiv, Ukraine, Saturday, March 25, 2023. (AP Photo/Evgeniy Maloletka) KYIV, Ukraine (AP) --- Ukraine...}