\entryitemWithDescription{\hskip 0pt{}Three Americans killed, `many' wounded in drone attack by Iran-backed militia in Jordan, Biden says}{https://apnews.com/article/5cb774fd835a558d840ae91263037489}{COLUMBIA, S.C. (AP) --- Three American service members were killed and ``many'' were wounded in a drone strike in northeast Jordan near the Syrian border, President Joe Biden said in a statement Sunday. He attributed the attack to Iran...}

\entryitemWithDescription{\hskip 0pt{}James outduels Curry with a triple-double as Lakers take double-OT thriller vs. Warriors 145-144}{https://apnews.com/article/d1e76dfc2d5893ed83214b77209ec1b7}{SAN FRANCISCO (AP) --- LeBron James made a pair of free throws with 1.2 seconds left in the second overtime to cap his triple-double of 36 points, 20 rebounds and 12 assists, outdueling Stephen Curry as the Los Angeles Lakers held off the...}

\entryitemWithDescription{\hskip 0pt{}Spurs mascot The Coyote captures bat with net -- to the delight of Wembanyama}{https://apnews.com/article/245eb5921082659f186cd310702e1bb3}{SAN ANTONIO (AP) --- A bat descended on the court and delayed play after Victor Wembanyama made a 3-pointer two minutes into the San Antonio Spurs' 113-112 victory over the Minnesota Timberwolves on Saturday night. The Spurs' mascot, The...}

\entryitemWithDescription{\hskip 0pt{}Oregon weekly newspaper to relaunch print edition after theft forced it to lay off its entire staff}{https://apnews.com/article/c6d2b677a370afffa26dfc2b5cac5549}{PORTLAND, Ore. (AP) --- An Oregon weekly newspaper that had to lay off its entire staff after its funds were embezzled by a former employee will relaunch its print edition next month, its editor said, a move made possible in large part by...}

\entryitemWithDescription{\hskip 0pt{}Bullfight advocates working with young people to attract new followers in Mexico}{https://apnews.com/article/1e2ba4342b531b468e35493018b2d6a3}{ACULCO, Mexico (AP) --- The corral gate swings open and an energetic calf charges in, only to be wrestled stuggling to the ground and immobilized by having its legs tied. The men go to work vaccinating the calf and marking its number with...}

\entryitemWithDescription{\hskip 0pt{}A snowboarder spent 15 hours trapped in a ski gondola. She rubbed her hands and feet to keep warm}{https://apnews.com/article/0cdeaac5df9ce655f8b253c804fcd2a8}{SOUTH LAKE TAHOE, Calif. (AP) --- A snowboarder spent 15 hours trapped overnight inside a ski lift gondola amid freezing temperatures at a Lake Tahoe resort, according to officials and media reports. Monica Laso boarded the gondola around...}

\entryitemWithDescription{\hskip 0pt{}`Saltburn' actor Barry Keoghan named Hasty Pudding's Man of the Year}{https://apnews.com/article/b1334bb493311e77f4ea275b7198bff1}{CAMBRIDGE, Mass. (AP) --- Harvard University's Hasty Pudding Theatricals has named Barry Keoghan, best known for his roles in ``Dunkirk,'' ``The Killing of a Sacred Deer,'' ``Eternals,'' and ``The Banshees of Inisherin,'' as the recipient...}

\entryitemWithDescription{\hskip 0pt{}Zebras, camels and flames, oh my! Circus animals rescued after truck catches fire on Indiana highway}{https://apnews.com/article/6e05d02f6382ffc0c2858487b66b4848}{MARION, Ind. (AP) --- A truck hauling zebras and camels for a series of weekend circus performances caught fire early Saturday on a northeastern Indiana highway, prompting a police rescue of the animals, which roamed along the freeway...}

\entryitemWithDescription{\hskip 0pt{}Charges against country singer Chris Young in Nashville bar arrest have been dropped}{https://apnews.com/article/ead6a027aafa8c985cccbec3a34ba750}{NASHVILLE, Tenn. (AP) --- A district attorney in Tennessee has dropped charges against country singer Chris Young stemming from an encounter with Alcoholic Beverage Commission agents who were doing compliance checks. In a statement...}

\entryitemWithDescription{\hskip 0pt{}Crash involving multiple vehicles and injuries snarls traffic on Chesapeake Bay bridge in Maryland}{https://apnews.com/article/17df78c1204638e7f403b82eccb87f91}{BALTIMORE (AP) --- A crash involving multiple vehicles and injuries closed all lanes on the heavily-traveled U.S. 50 Bay Bridge in Maryland on Saturday and motorists were advised to expect major delays, authorities said. The Maryland...}

\entryitemWithDescription{\hskip 0pt{}The world's largest cruise ship begins its maiden voyage from the Port of Miami}{https://apnews.com/article/e841449d2796b1fd76d022bbfbb4dada}{MIAMI (AP) --- The world's largest cruise ship is set to begin its maiden voyage Saturday as it gets underway from the Port of Miami. Royal Caribbean's Icon of the Seas, which runs nearly 1,200 feet (365 meters) from bow to stern, is...}

\entryitemWithDescription{\hskip 0pt{}Wrestling icon Vince McMahon resigns from WWE after former employee files sex abuse lawsuit}{https://apnews.com/article/4b7e1cd46a6646538637307bb0c8202b}{STAMFORD, Conn. (AP) --- Wrestling icon Vince McMahon resigned Friday from WWE's parent company the day after a former employee filed a federal lawsuit accusing him and another former executive of serious sexual misconduct, including...}

\entryitemWithDescription{\hskip 0pt{}Other passengers support man who opened emergency exit and walked on plane's wing in Mexico airport}{https://apnews.com/article/91e3411716e22bfd8778905860a7850f}{MEXICO CITY (AP) --- At first it sounds like a typical case of bad behavior aboard airplanes. The Mexico City International Airport acknowledged in a statement Friday that a man had opened an emergency exit and walked out on a wing of a...}