\entryitemWithDescription{\hskip 0pt{}A bridge where firefighters rescued the driver of a semi dangling over the Ohio River remains closed}{https://apnews.com/article/1f352e8c40145dc5cd6c92a903e03f24}{LOUISVILLE, Ky. (AP) --- A bridge connecting Kentucky and Indiana remained closed Saturday following a harrowing crash and rescue of a tractor-trailer driver left hanging over the bridge's edge. Dramatic photos and video captured the...}

\entryitemWithDescription{\hskip 0pt{}A train derailment in eastern Pennsylvania scattered cars on a riverbank and one in the water}{https://apnews.com/article/3491b1e1c9496414bc88262b54c3d250}{BETHLEHEM, Pa. (AP) --- Authorities say a train derailment in eastern Pennsylvania has left some railroad cars along a riverbank Saturday morning and at least one partially in the river itself. Dispatchers in Northampton County said the...}

\entryitemWithDescription{\hskip 0pt{}Third baseman Matt Chapman and Giants reach a \$54 million, 3-year deal, AP source says}{https://apnews.com/article/d8ed8ad88cd3e16fd528d4622196d681}{NEW YORK (AP) --- Third baseman Matt Chapman and the San Francisco Giants have agreed to a \$54 million, three-year contract, a person familiar with the negotiations told The Associated Press. Chapman will get \$20 million this year and...}

\entryitemWithDescription{\hskip 0pt{}An arrest has been made in the slaying of a pregnant Amish woman in Pennsylvania}{https://apnews.com/article/ba56817e10a88be554966ef740d5b3c4}{SPARTANSBURG, Pa. (AP) --- A Pennsylvania man was arrested Saturday and charged with the slaying of a pregnant Amish woman whose body was found last week. Shawn C. Cranston, 52, of Corry, has been charged with criminal homicide, criminal...}

\entryitemWithDescription{\hskip 0pt{}A party like no other? Asia's richest man celebrates son's prenuptials with a star-studded bash}{https://apnews.com/article/d36e73d8b83229b7684e6253d84e23d5}{NEW DELHI (AP) --- What happens when the son of Asia's richest man is about to get married? His father throws a three-day prenuptial bash four months before the actual ceremony. Tycoons from around the world, heads of state, as well as...}

\entryitemWithDescription{\hskip 0pt{}A New Jersey city that limited street parking hasn't had a traffic death in 7 years}{https://apnews.com/article/007dec67706c1c09129da1436a3d9762}{Street parking was already scarce in Hoboken, New Jersey, when the death of an elderly pedestrian spurred city leaders to remove even more spaces in a bid to end traffic fatalities. For seven years now, the city of nearly 60,000 people...}

\entryitemWithDescription{\hskip 0pt{}The Missouri governor shortens the DWI prison sentence of former Chiefs assistant coach Britt Reid}{https://apnews.com/article/17630ef04030c056270b7993814e6aed}{JEFFERSON CITY, Mo. (AP) --- Missouri Gov. Mike Parson on Friday shortened the prison sentence of former Kansas City Chiefs assistant coach Britt Reid for a drunken driving crash that seriously injured a 5-year-old girl. Parson's...}

\entryitemWithDescription{\hskip 0pt{}Yogurts can make limited claim that the food reduces risk of type 2 diabetes, FDA says}{https://apnews.com/article/06f67fbea87fcb7b35176520f50acbc8}{Yogurt sold in the U.S. can make claims that the food may reduce the risk of type 2 diabetes, based on limited evidence, the U.S. Food and Drug Administration said Friday. The agency agreed that there is some evidence, but not significant...}

\entryitemWithDescription{\hskip 0pt{}Woman convicted of murder conspiracy, coverup, in 2019 disappearance of Connecticut mother}{https://apnews.com/article/5d81c9985561723e714ac788dfbaefa2}{A woman was convicted Friday of conspiring to murder Jennifer Dulos, a mother of five who vanished from a wealthy Connecticut enclave in 2019 and was never found. Michelle Troconis, 49, was found guilty by the Stamford jury following a...}

\entryitemWithDescription{\hskip 0pt{}With trash bins now required in NYC, only the rats are sorry to see the garbage piles go}{https://apnews.com/article/93ccb6f097d8351ffae648ba74221853}{NEW YORK (AP) --- New York City's tradition of piling garbage bags on the sidewalk for pickup is going the way of the dinosaur. As of Friday, all 200,000 businesses in the Big Apple are required to put out their bags of trash in garbage...}

\entryitemWithDescription{\hskip 0pt{}Lobster catch dips to lowest level since 2009 as fishers grapple with climate change, whale rules}{https://apnews.com/article/1ab254ee2e8e2dbc205ce24afce5eb8d}{PORTLAND, Maine (AP) --- America's lobster fishing business dipped in catch while grappling with challenges including a changing ocean environment and new rules designed to protect rare whales. The lobster industry, based mostly in Maine...}

\entryitemWithDescription{\hskip 0pt{}Private plane carrying Grammy winner Karol G makes emergency landing in Los Angeles}{https://apnews.com/article/003035756ea4c089eeed2cfda211fe28}{LOS ANGELES (AP) --- A private airplane carrying singer Karol G made an emergency landing at a Los Angeles airport Thursday evening, a news report said. The aircraft carrying the Grammy winner and others landed at Van Nuys Airport around...}

\entryitemWithDescription{\hskip 0pt{}TikToks of young people popping Zyn nicotine pouches are going viral, worrying some health experts}{https://apnews.com/article/026cc2789b48c10581a56242f4b23a4a}{WASHINGTON (AP) --- There's nothing complicated about the latest tobacco product trending online: Zyn is a tiny pouch filled with nicotine and flavoring. But it has stoked a debate among politicians, parents and pundits that reflects an...}