\entryitemWithDescription{\hskip 0pt{}Hulk Hogan visits Detroit Lions camp, says coach Dan Campbell missed his calling as a wrestler}{https://apnews.com/article/c0ae32309c25323e4a74b8def0390700}{ALLEN PARK, Mich. (AP) --- Hulk Hogan, visiting Detroit Lions practice, said coach Dan Campbell would have been good in the squared circle. The pro wrestling great even came up with a nickname for Campbell: ``Dirty Dan.'' ``He probably...}

\entryitemWithDescription{\hskip 0pt{}Thousands watch Chincoteague wild ponies complete 99th annual swim in Virginia}{https://apnews.com/article/07ea7f390422e56900245b44a1c3ad16}{CHINCOTEAGUE, Va. (AP) --- Thousands of people gathered in Virginia to watch the Chincoteague wild ponies make their annual swim across the Assateague Channel, the 99th year of the popular tradition. The ponies made the short swim across...}

\entryitemWithDescription{\hskip 0pt{}OpenAI tests ChatGPT-powered search engine that could compete with Google}{https://apnews.com/article/cc8c0bff15d69c845f5de0df1e0a89a2}{SAN FRANCISCO (AP) --- OpenAI is testing a ChatGPT-powered search engine that could put the artificial intelligence company in direct competition with search giant Google and affect the flow of internet traffic seeking news and other...}

\entryitemWithDescription{\hskip 0pt{}Dylan Cease throws second no-hitter in San Diego Padres history, 3-0 win over Washington Nationals}{https://apnews.com/article/187e43aee4ce49f84dc4a492d7f6f03e}{WASHINGTON (AP) --- Dylan Cease pitched the second no-hitter in San Diego Padres history, a 3-0 win over the Washington Nationals on Thursday that completed a three-game sweep. After falling one out short of a no-hitter two years ago when...}

\entryitemWithDescription{\hskip 0pt{}Jill Biden meets with US Olympic athletes in Paris — and even helps with a relay drill}{https://apnews.com/article/99efa3f779312ebf1c5f5bee57718a86}{PARIS (AP) --- U.S. first lady Jill Biden visited some American athletes at an Olympic training center in Paris on Thursday, wishing rugby and track and field competitors good luck and even taking part in a stationary relay drill with...}

\entryitemWithDescription{\hskip 0pt{}Flavor Flav is soaking up his 1st Olympic experience cheering on the US water polo teams}{https://apnews.com/article/34694545c54c229b9c81168ead939bb5}{PARIS (AP) --- Flavor Flav stopped for hugs, handshakes and high-fives as he made his way around the Team USA House at the Paris Games on Thursday. He never stopped smiling. ``This is quite an experience for me right now, you know...}

\entryitemWithDescription{\hskip 0pt{}Kamala Harris is using Beyoncé's `Freedom' as her campaign song: What to know about the anthem}{https://apnews.com/article/d575644248b9b609aafcd348f39146ef}{NEW YORK (AP) --- In Vice President Kamala Harris' first 2024 presidential campaign video, a familiar rhythm rings out. The clip, which touches on issues of gun violence, health care and abortion, is soundtracked by Beyoncé...}

\entryitemWithDescription{\hskip 0pt{}Booties. Indoor dog parks. And following the vet's orders. How to keep pets cool this summer}{https://apnews.com/article/5cd56811cc4538cfd3d0ff0bac73a774}{PHOENIX (AP) --- As much of the world swelters, it's not just people who need help with the dog days of summer. Pet owners have to consider how to both shield and cool down furry family members as intense --- at times deadly --- heat...}

\entryitemWithDescription{\hskip 0pt{}Southwest breaks with 50-year tradition and will assign seats; profit falls at Southwest, American}{https://apnews.com/article/6869dbe31934c87e049c9e428eae7761}{Southwest Airlines plans to drop its tradition of more than 50 years and start assigning seats and selling premium seating for customers who want more legroom. The airline said Thursday that it has been studying seating options and is...}

\entryitemWithDescription{\hskip 0pt{}Andy Murray withdraws from Olympic tennis singles and will only play doubles at the Paris Games}{https://apnews.com/article/d6809fb353f8a6e19599355b487a8f70}{PARIS (AP) --- Two-time Olympic tennis gold medalist Andy Murray pulled out of singles at the Paris Games on Thursday and only will compete in doubles with Dan Evans. Murray, a 37-year-old from Britain, has said these Olympics will be the...}

\entryitemWithDescription{\hskip 0pt{}How to watch the 2024 Olympics opening ceremony}{https://apnews.com/article/e2836f814931a0cdfe9745edfce860f3}{The opening ceremony for the Paris Olympics is set for Friday. Instead of a traditional march into a stadium, about 10,500 athletes will parade on more than 90 boats on the Seine River for 6 kilometers (3.7 miles). This will start the...}

\entryitemWithDescription{\hskip 0pt{}Judge orders release of Missouri man whose murder conviction was reversed over AG's objections}{https://apnews.com/article/e59ec2dc43b36b2c2ac2e9acf05ff2d4}{ST. LOUIS (AP) --- A Missouri judge on Wednesday ordered the release of Christopher Dunn, who has spent more than 30 years in prison for a killing he has long contended he didn't commit. St. Louis Circuit Judge Jason Sengheiser's decision...}

\entryitemWithDescription{\hskip 0pt{}Andrew Tate's defamation lawsuit against human trafficking accuser can go to trial, judge says}{https://apnews.com/article/93e37749d52ea0f1867347a3f13cea14}{FORT LAUDERDALE, Fla. (AP) --- A judge says controversial social media personality Andrew Tate `s defamation lawsuit against a Florida woman who accused him of imprisoning her in Romania can go to trial, but he threw out Tate's...}