\entryitemWithDescription{\hskip 0pt{}Spurs' Victor Wembanyama named NBA Rookie of the Year after a record-setting season}{https://apnews.com/article/7300f8e7c5173520b78c88a9e393164b}{Victor Wembanyama had a year like no rookie in NBA history. Others scored more points, others grabbed more rebounds, others had more blocks, others made more steals. But never had there been a player who, in Year 1 of his career, posted...}

\entryitemWithDescription{\hskip 0pt{}After AP investigation, family of missing students enrolls in school}{https://apnews.com/article/255757b5541bf425c4cfde48961af79e}{ATLANTA (AP) --- Four months after The Associated Press wrote about an Atlanta family struggling to enroll in school, all of the children --- in a complete turnaround --- returned to class last month. The project on Monday was named a...}

\entryitemWithDescription{\hskip 0pt{}After Barstool Sports sponsorship fizzles, Snoop Dogg brand is attached to Arizona Bowl, fo shizzle}{https://apnews.com/article/6815517c1949e3bf3867cbd13a003bfa}{TUCSON, Ariz. (AP) --- Snoop Dogg is putting his name on the Arizona Bowl for what will be the first partnership between an alcohol brand and a college bowl game, the rapper and media personality announced Monday. The ``Snoop Dogg Arizona...}

\entryitemWithDescription{\hskip 0pt{}Janet Jackson to play 2024 Essence Fest instead of the Smoothie King Center this summer}{https://apnews.com/article/6c5adc9eb8aac8d4262b1b54b590fd37}{NEW ORLEANS (AP) --- Janet Jackson will make her fourth appearance at the 2024 Essence Festival of Culture this summer in New Orleans. Jackson was originally scheduled to headline the Smoothie King Center on July 23 as part of her...}

\entryitemWithDescription{\hskip 0pt{}Brittney Griner still adjusting after Russian prison ordeal. WNBA star details experience in book}{https://apnews.com/article/3ad3b4052744fd426415329129ffebf5}{Brittney Griner continues her efforts to settle into a normal routine following her release from a Russian prison 17 months ago. Life isn't what it once was for the perennial WNBA All-Star. It may never be. The 6-foot-8 center looks...}

\entryitemWithDescription{\hskip 0pt{}Civil rights leader Daisy Bates and singer Johnny Cash to replace Arkansas statues at the US Capitol}{https://apnews.com/article/b8b76e7e10586ffff02e37d0c4a22c9d}{LITTLE ROCK, Ark. (AP) --- When Arkansas lawmakers decided five years ago to replace the statues representing the state at the U.S. Capitol, there was little objection to getting rid of the existing sculptures. The statues that had stood...}

\entryitemWithDescription{\hskip 0pt{}Tom Brady's Netflix roast features lots of humor, reunion between Robert Kraft and Bill Belichick}{https://apnews.com/article/7b1ec4699f14273beff599102159dd7d}{INGLEWOOD, Calif. (AP) --- Three months before Tom Brady gets roasted by critics as Fox Sports' top NFL analyst, he took his share of barbs from comedians, former teammates and his longtime coach Sunday night during a made-for-streaming...}

\entryitemWithDescription{\hskip 0pt{}How to stream and watch the Met Gala}{https://apnews.com/article/c157cb3c547e4784ee802d8f828548e7}{NEW YORK (AP) --- Attention all you fashionistas: It's Met Gala time. Yes, the first Monday in May is upon us. Looking to follow along? Here's a quick primer on what you need to know about the palooza of A-list celebrities from film...}

\entryitemWithDescription{\hskip 0pt{}Kim Godwin out as ABC News president after 3 years as first Black woman as network news chief}{https://apnews.com/article/ea586f896a075b8de35df530945eb979}{NEW YORK (AP) --- Kim Godwin is out after three tumultuous years as ABC News president, a move presaged earlier this year when network parent Walt Disney Co. installed one of its executives, Debra O'Connell, to oversee the news division...}

\entryitemWithDescription{\hskip 0pt{}Radek Faksa scores in return, Stars beat defending Stanley Cup champ Golden Knights 2-1 in Game 7}{https://apnews.com/article/7138fb07bd7b995a86b641d6fb66dc8e}{DALLAS (AP) --- Radek Faksa broke a tie in his return to the Dallas lineup, 20-year-old Wyatt Johnston scored in another Game 7 and the Stars beat the defending Stanley Cup champion Vegas Golden Knights 2-1 on Sunday night to wrap up the...}

\entryitemWithDescription{\hskip 0pt{}César Luis Menotti, coach who led Argentina to its first World Cup title in 1978, dies at 85}{https://apnews.com/article/6022169ae8acc097f10db95853ea32cb}{BUENOS AIRES, Argentina (AP) --- César Luis Menotti, the charismatic coach who led Argentina to its first World Cup title in 1978, has died, the Argentine Football Association said Sunday. He was 85. ``Goodbye, dear Flaco!'' the...}

\entryitemWithDescription{\hskip 0pt{}Sierra Nevada records snowiest day of the season from brief but potent California storm}{https://apnews.com/article/2ecf2790aa24e24d8eb3cd5b27b99373}{TRUCKEE, Calif. (AP) --- A weekend spring storm that drenched the San Francisco Bay area and closed Northern California mountain highways also set a single-day snowfall record for the season on Sunday in the Sierra Nevada. The wet weather...}

\entryitemWithDescription{\hskip 0pt{}Actor Bernard Hill, of `Titanic' and `Lord of the Rings,' has died at 79}{https://apnews.com/article/e361747aabebbd998edc0431199cb96e}{LONDON (AP) --- Actor Bernard Hill, who delivered a rousing cry before leading his people into battle in ``The Lord of the Rings: The Return of the King'' and went down with the ship as the captain in ``Titanic,'' has died. Hill, 79...}