\entryitemWithDescription{\hskip 0pt{}Flag football gives female players sense of community, scholarship options and soon shot at Olympics}{https://apnews.com/article/ef810674ccfc9807ac8aac8ca02198e9}{DENVER (AP) --- There were times when Jo Overstreet felt all alone as a standout flag football player on boys teams growing up in Texas. Sure, she was accepted. Considered just one of the boys. She longed for something more --- a sense of...}

\entryitemWithDescription{\hskip 0pt{}Herb Kohl, former US senator and owner of the Milwaukee Bucks, dies at 88}{https://apnews.com/article/f2f0a85ca0b84af794f73c22b7d8d420}{Herb Kohl, a former Democratic U.S. senator from Wisconsin and former owner of the NBA's Milwaukee Bucks, has died. He was 88. His death Wednesday was announced by Herb Kohl Philanthropies, which did not give a cause but said he died...}

\entryitemWithDescription{\hskip 0pt{}Danny Masterson sent to state prison to serve sentence for rape convictions, mug shot released}{https://apnews.com/article/fd8f700ccadd136757e6ccdf2a45f905}{DELANO, Calif. (AP) --- ``That `70s Show'' actor Danny Masterson has been sent to a California state prison to serve his sentence for two rape convictions. Authorities said Wednesday that the 47-year-old Masterson has been admitted to...}

\entryitemWithDescription{\hskip 0pt{}Family of Iowa teen killed by police files a lawsuit saying officers should have been better trained}{https://apnews.com/article/ba33b56ae733e8e8ba26b701d7a0ebb4}{DES MOINES, Iowa (AP) --- The family of a 16-year-old who was killed by Des Moines police in December 2022 has filed a lawsuit arguing that the teen never pointed a gun at officers and police should have had better training in de...}

\entryitemWithDescription{\hskip 0pt{}Russell Hamler, thought to be the last of WWII Merrill's Marauders jungle-fighting unit, dies at 99}{https://apnews.com/article/5d36ffad5b0d40d6367cd33ae758b16f}{HARRISBURG, Pa. (AP) --- The reputed last member of the famed American jungle fighting unit in World War II nicknamed the Merrill's Marauders has died. Russell Hamler, 99, died on Tuesday, his son Jeffrey said. He did not give a cause of...}

\entryitemWithDescription{\hskip 0pt{}2 models of Apple Watch can go on sale again, for now, after court lifts halt over a patent dispute}{https://apnews.com/article/42aa0bf3d22a8788a1df40b5bd96cc4f}{Two higher-end models of the Apple Watch can go on sale again after a federal court temporarily lifted a sales halt ordered by the International Trade Commission over a patent dispute. The ITC, a federal agency, ordered the halt in...}

\entryitemWithDescription{\hskip 0pt{}Jacksonville mayor has Confederate monument removed after years of controversy}{https://apnews.com/article/eb85c70216603e180db5df851f0f852c}{JACKSONVILLE, Fla. (AP) --- Crews removed a Confederate monument from a Jacksonville, Florida, park Wednesday morning following years of public controversy. Mayor Donna Deegan ordered the removal of the ``Tribute to the Women of the...}

\entryitemWithDescription{\hskip 0pt{}Gaston Glock, the Austrian developer of the Glock handgun, dies at 94}{https://apnews.com/article/730da2f1cbaaf082fbabeb328e9d51ae}{Gaston Glock, the Austrian developer of the handgun that bears his name, died on Wednesday. He was 94. The Glock company announced his death, the Austria Press Agency reported. Glock, a reclusive engineer, founded the company in 1963 in...}

\entryitemWithDescription{\hskip 0pt{}A woman who burned Wyoming's only full-service abortion clinic is ordered to pay \$298,000}{https://apnews.com/article/62779a51bdbcf5cd2d0612586227a514}{CHEYENNE, Wyo. (AP) --- A judge has ordered a woman who set fire to Wyoming's only full-service abortion clinic to pay nearly \$300,000 in restitution, the full amount sought by prosecutors. Lorna Green is serving five years in prison for...}

\entryitemWithDescription{\hskip 0pt{}Comedian Tom Smothers, one-half of the Smothers Brothers, dies at 86}{https://apnews.com/article/3e1727faf1b6469da7b2cfc7b2874c56}{Tom Smothers, half of the Smothers Brothers and the co-host of one of the most socially conscious and groundbreaking television shows in the history of the medium, has died at 86. The National Comedy Center, on behalf of his family, said...}

\entryitemWithDescription{\hskip 0pt{}US online retailer Zulily says it will go into liquidation, surprising customers}{https://apnews.com/article/2afdbb77665226ea1c9060c806502db4}{SEATTLE (AP) --- The U.S. online retailer Zulily is closing down, surprising customers and laying off hundreds of workers after efforts to salvage the business failed. The Seattle-based company said in a notice on its website that it had...}

\entryitemWithDescription{\hskip 0pt{}Wolfgang Schaeuble, German elder statesman and finance minister during euro debt crisis, dies at 81}{https://apnews.com/article/00bd6ad77afe14a6e0379b87837e7606}{BERLIN (AP) --- Wolfgang Schaeuble, who helped negotiate German reunification in 1990 and as finance minister was a central figure in the austerity-heavy effort to drag Europe out of its debt crisis two decades later, has died. He was 81...}

\entryitemWithDescription{\hskip 0pt{}Photographer Cecil Williams' vision gives South Carolina its only civil rights museum}{https://apnews.com/article/ee2807845bbab508f4a07c3dd26218d0}{ORANGEBURG, S.C. (AP) --- Much of how South Carolina has seen its civil rights history has been through the lens of photographer Cecil Williams. From sit-ins to prayer protests to portraits of African Americans integrating universities...}