\entryitemWithDescription{\hskip 0pt{}Shohei Ohtani agrees to record \$700 million, 10-year contract with Dodgers}{https://apnews.com/article/0462c7dcd08a5afedd92912ba69f8e8a}{NEW YORK (AP) --- Shohei Ohtani agreed Saturday to a record \$700 million, 10-year contract with the Los Angeles Dodgers. The deal was announced after days of speculation over where the two-way star would continue his career after six...}

\entryitemWithDescription{\hskip 0pt{}Thousands of revelers descend on NYC for annual Santa-themed bar crawl SantaCon}{https://apnews.com/article/616ee17f07906fde81d7378f6ba206d5}{NEW YORK (AP) --- Here come Santa Clauses. Again. Throngs of people dressed as jolly Old St. Nick descended on New York City for the annual SantaCon charity pub crawl on Saturday. The booze-fueled stroll, which included no shortage of...}

\entryitemWithDescription{\hskip 0pt{}Eagles security guard DiSandro banned from sideline for Sunday Night Football vs. Cowboys}{https://apnews.com/article/595e6c14141fb055b2a08e36d25902c5}{PHILADELPHIA (AP) --- Eagles security chief Dom DiSandro has been barred by the NFL from being on the sideline Sunday night against the Cowboys after he was ejected in last week's game for a scuffle with 49ers linebacker Dre Greenlaw, the...}

\entryitemWithDescription{\hskip 0pt{}A hospital fire near Rome kills at least 3 and causes an emergency evacuation of all patients}{https://apnews.com/article/512b53b92f03b4c45035be503adcac20}{ROME (AP) --- A fire broke out in a hospital on Rome's outskirts, killing at least three people and forcing the overnight evacuation of the smoke-filled facility and its nearly 200 patients, officials said Saturday. The blaze began in the...}

\entryitemWithDescription{\hskip 0pt{}Ryan O'Neal, star of `Love Story,' `Paper Moon,' `Peyton Place' and `Barry Lyndon,' dies at 82}{https://apnews.com/article/bbb21318db9742d0b1e5e4a51c2fa26d}{LOS ANGELES (AP) --- Ryan O'Neal, the heartthrob actor who went from a TV soap opera to an Oscar-nominated role in ``Love Story'' and delivered a wry performance opposite his charismatic 9-year-old daughter Tatum in ``Paper Moon,'' died...}

\entryitemWithDescription{\hskip 0pt{}With no supermarket for residents of Atlantic City, New Jersey and hospitals create mobile groceries}{https://apnews.com/article/c49c6eaf9be2ad959a6fea61e73c2aa0}{ATLANTIC CITY, N.J. (AP) --- In this seaside resort, where \$5 billion worth of in-person and online gambling gets done each year, there still is not a supermarket. People who live in Atlantic City must either drive off the island to a...}

\entryitemWithDescription{\hskip 0pt{}Jonathan Majors begged accuser to avoid hospital, warning of possible `investigation,' messages show}{https://apnews.com/article/87fb75a5ca50c7d7de4ce99cff3abe15}{NEW YORK (AP) --- The actor Jonathan Majors begged his former girlfriend not to seek medical attention after an incident that left her with a head injury last year, warning she had ``no perspective of what could happen'' if the truth got...}

\entryitemWithDescription{\hskip 0pt{}French actor Gerard Depardieu is under scrutiny over sexual remarks and gestures in new documentary}{https://apnews.com/article/731ae81b16fb66cde83055f6868f7eee}{PARIS (AP) --- French actor Gerard Depardieu's behavior toward women came under renewed scrutiny in France after a documentary showed him repeatedly making obscene remarks and gestures during a 2018 trip to North Korea. The footage...}

\entryitemWithDescription{\hskip 0pt{}Spotify's CFO is one of thousands to leave the company — after he moves to sell \$9 million in shares}{https://apnews.com/article/e3cd38dc2952df4b2a7fff9cbafe4950}{NEW YORK (AP) --- Spotify's chief financial officer will step down next year, according to the music streaming service, just days after it announced its third round of layoffs for 2023. In a statement announcing CFO Paul Vogel's...}

\entryitemWithDescription{\hskip 0pt{}Thousands of tons of dead sardines wash ashore in northern Japan}{https://apnews.com/article/88003e085359a88cb1135a818c722c05}{TOKYO (AP) --- Thousands of tons of dead sardines have washed up on a beach in northern Japan for unknown reasons, officials said Friday. The sardines and some mackerel washed ashore in Hakodate on Japan's northernmost main island of...}

\entryitemWithDescription{\hskip 0pt{}Woman charged with attempted arson of Martin Luther King Jr. birthplace in Atlanta}{https://apnews.com/article/a642a0d24866e272d3f7418873ef2702}{ATLANTA (AP) --- Atlanta police have arrested a woman who's accused of trying to burn down the birthplace of the Rev. Martin Luther King Jr. in Atlanta. Officers arrested the 26-year-old woman around 5:45 p.m. Thursday after responding to...}

\entryitemWithDescription{\hskip 0pt{}Johnny Depp among stars paying tribute at funeral of The Pogues singer Shane MacGowan}{https://apnews.com/article/c9db39a8b26073d6f149f5c969d93615}{LONDON (AP) --- Thousands of people lined the streets of Dublin on Friday to say goodbye to The Pogues frontman Shane MacGowan as his coffin wound through the Irish capital before a small-town funeral attended by family, neighbors and...}

\entryitemWithDescription{\hskip 0pt{}Nintendo cancels its Live 2024 Tokyo event after persistent threats to workers and customers}{https://apnews.com/article/e2782eb5ac3f0e1315f1df0d03a97610}{TOKYO (AP) --- Nintendo canceled its upcoming video game showcase and postponed several other events because of persistent threats to the company, its workers and players. ``We decided we could not amply ensure the safety of our...}