\entryitemWithDescription{\hskip 0pt{}What the submersible saga and the Greek migrant shipwreck say about our reactions to tragedy}{https://apnews.com/article/7db0c63b4439de820877af272527cb83}{Saleh: Mohammed Saleh, the father of 18-year-old Yahia Saleh, holds a phone with a photo of his son at home in Ibrash, Egypt, Sunday, June 18, 2023. Yahia is one of dozens from the village feared to have drowned after a packed fishing...}

\entryitemWithDescription{\hskip 0pt{}Orcas disrupt boat race near Spain in latest display of dangerous, puzzling behavior}{https://apnews.com/article/c13e7e67f1c8f536e5be9258455eed70}{A pod of killer whales bumped one of the boats in an endurance sailing race as it approached the Strait of Gibraltar, the latest encounter in what researchers say is a growing trend of sometimes-aggressive interactions with Iberian orcas...}

\entryitemWithDescription{\hskip 0pt{}New York doctors get legal protection to prescribe abortion pills across state lines}{https://apnews.com/article/161fc73174a04f68e93c4312b3b21ea0}{FILE - New York Gov. Kathy Hochul presents her executive state budget in the Red Room at the state Capitol Wednesday, Feb. 1, 2023, in Albany, N.Y. A law to protect doctors in New York who prescribe abortion pills to patients in states...}

\entryitemWithDescription{\hskip 0pt{}United States picked to host 2025 Club World Cup, an expanded soccer tournament with 32 teams}{https://apnews.com/article/cbc0fa69ecff46972e775c1afc477a07}{FILE - Real Madrid players celebrate with the trophy after winning the FIFA Club World Cup final match against Al Hilal at Prince Moulay Abdellah stadium in Rabat, Morocco, Saturday, Feb. 11, 2023. The United States will host the Club...}

\entryitemWithDescription{\hskip 0pt{}Union official says safety of railroads has been compromised by job cuts and time constraints}{https://apnews.com/article/29a4a6fab0eb21fcb69223a28ff41ea5}{East Palestine, Ohio resident Eric Cozza attends the National Transportation Safety Board investigative hearing at the East Palestine High School in East Palestine, Ohio, Thursday, June 22, 2023. The hearing is being held to investigate...}

\entryitemWithDescription{\hskip 0pt{}7.5 million Baby Shark bath toys are recalled after they cut or stabbed children}{https://apnews.com/article/2bace294be48edfb1bfc2bf17d57c097}{This image provided by Consumer Product Safety Commission shows Zuru's full-sized Robo Alive Junior Baby Shark Sing \& Swim Bath Toys. About 7.5 million ``Baby Shark'' bath toys are being recalled, Friday, June 23, 2023, after multiple...}

\entryitemWithDescription{\hskip 0pt{}Starbucks union calls strike over Pride displays, but the company calls it a misinformation campaign}{https://apnews.com/article/bf35812637c3b5cebb6737e69359f145}{A Starbucks sign sits above a store in the Financial District of Lower Manhattan, Tuesday, June 13, 2023, in New York. Starbucks is denying union organizers\textquotesingle{} claims that it banned LGBTQ+ Pride displays in its U.S. stores...}

\entryitemWithDescription{\hskip 0pt{}Tony-winning lyricist Sheldon Harnick 'Fiddler on the Roof' creator, dies at 99}{https://apnews.com/article/e6a9c8a883e245c3a25eb722abbb16ea}{FILE - Sheldon Harnick accepts the special Tony Award for lifetime achievement in the Theatre at the Tony Awards at the Beacon Theatre on Sunday, June 12, 2016, in New York. Harnick, who with composer Jerry Bock made up the premier...}

\entryitemWithDescription{\hskip 0pt{}Honda recalls nearly 1.2M vehicles because rear camera image may not appear on dashboard screen}{https://apnews.com/article/8d5d2992d0899b9580e4805c69b9f9c7}{FILE - A long row of unsold 2020 Odyssey minivans sits at a Honda dealership in Highlands Ranch, Colo on April 5, 2020. Honda is recalling nearly 1.2 million vehicles in the U.S. because the rear view camera image may not appear on the...}

\entryitemWithDescription{\hskip 0pt{}Tropical Storm Cindy forms behind Bret in an early and aggressive start to Atlantic hurricane season}{https://apnews.com/article/e2902edac76fd904cb2d3d780dc077b2}{This GeoColor satellite image taken Tuesday, June 20, 2023 and provided by NOAA, shows Tropical Storm Bret as it chugged toward the eastern Caribbean. (NOAA via AP) SAN JUAN, Puerto Rico (AP) --- Tropical Storm Cindy has formed behind...}

\entryitemWithDescription{\hskip 0pt{}Exploding fire extinguisher kills a student and injures 5 during a high school fire drill in Bangkok}{https://apnews.com/article/1143332d5c859d78d93ab357cc5c6606}{Firefighters investigate an explosion site at a school in Bangkok, Thailand, Friday, June 23, 2023. A fire extinguisher exploded during a high school\textquotesingle s annual fire drill Friday in Thailand\textquotesingle s capital. (AP...}

\entryitemWithDescription{\hskip 0pt{}Bulls expect Lonzo Ball to miss another season because of left knee injury}{https://apnews.com/article/4169d9711a07bf5769e4d30db0f4207c}{CHICAGO (AP) --- The Chicago Bulls expect point guard Lonzo Ball to miss another season because of his left knee injury. ``Everything is going well,'' executive vice president of basketball operations Arturas Karnisovas said Thursday. ``...}

\entryitemWithDescription{\hskip 0pt{}Is Twitter ready for Europe's new Big Tech rules? EU official says it has work to do}{https://apnews.com/article/824e107cf9b28595a7264d4565304bf9}{FILE - Twitter, now X. Corp, and Tesla CEO Elon Musk poses before his talks with French President Emmanuel Macron on Monday, May 15, 2023, at the Elysee Palace in Paris. A top European Union official is visiting Silicon Valley to...}