\entryitemWithDescription{\hskip 0pt{}Jonas Brothers release new album, plan to prioritize mental health on upcoming tour}{https://apnews.com/article/9d3bd17747eb4983b293badd4b3210de}{Nick Jonas, from left, Joe Jonas and Kevin Jonas of the Jonas Brothers perform on NBC\textquotesingle s Today show at Rockefeller Plaza on Friday, May 12, 2023, in New York. (Photo by Andy Kropa/Invision/AP) After two decades in the...}

\entryitemWithDescription{\hskip 0pt{}US Postal Service honors civil rights leader, Ponca tribe Chief Standing Bear, with stamp}{https://apnews.com/article/dc8db19c212f014805e10db4de85af81}{This image provided by the U.S. Postal Service shows the new stamp honoring Native American civil rights leader Chief Standing Bear, issued on Friday, May 12, 2023. Standing Bear won a landmark court ruling in 1879 recognizing that Native...}

\entryitemWithDescription{\hskip 0pt{}Former Trump prosecutor mostly mum before Congress on details of hush-money investigation}{https://apnews.com/article/50ffeb205c50dab473153d8de1db3e7f}{FILE - Attorney Mark Pomerantz arrives at Federal Court in New York, Aug. 12, 2002. An ex-prosecutor who once oversaw Manhattan\textquotesingle s yearslong investigation into former President Donald Trump repeatedly declined to...}

\entryitemWithDescription{\hskip 0pt{}See what baby names were the most popular last year}{https://apnews.com/article/97c955a0eca43e372142ec93572ec8e7}{FILE - The toes of a baby are seen DHR Health, July 29, 2020, in McAllen, Texas. Dutton and Wrenlee are on the rise but they're no match for champs Liam and Olivia as the top baby names in the U.S. last year. (AP Photo/Eric Gay, File...}

\entryitemWithDescription{\hskip 0pt{}Stragglers pack up as Swiss village is evacuated under rockslide threat}{https://apnews.com/article/4c8d3fbf90e4df2b898597e2a435c027}{View of the village and the "Brienzer Rutsch", taken in Brienz-Brinzauls, Switzerland, Friday, May 12, 2023. Authorities in eastern Switzerland have ordered residents of the tiny village of Brienz to evacuate by Friday evening because...}

\entryitemWithDescription{\hskip 0pt{}McDonald's found liable for hot Chicken McNugget that burned girl}{https://apnews.com/article/115737cffc47c539e3aed92daad264a4}{Philana Holmes and her daughter Olivia Caraballo, 7 listen to the final witness in their case at the Broward County Courthouse in Fort Lauderdale on Wednesday May 10, 2023. McDonald's and a franchise holder are at fault after a hot...}

\entryitemWithDescription{\hskip 0pt{}Toyota: Data on more than 2 million vehicles in Japan were at risk in decade-long breach}{https://apnews.com/article/7f686c990daf3cd85b57d7ffaa27c81a}{FILE - Shown is a Toyota logo at the Philadelphia Auto Show on Jan. 27, 2023, in Philadelphia. A decade-long data breach in Toyota's much-touted online service put some information on more than 2 million vehicles at risk, the Japanese...}

\entryitemWithDescription{\hskip 0pt{}Memphis 'snake factory' transplants slither into their new home in Louisiana}{https://apnews.com/article/ad5add13103d324f6c1c6373c6f86337}{A Louisiana pine snake bluffs in a posture to defend itself against predators, during the release of several of about 100 Louisiana pine snakes, which are a threatened species, in Kisatchie National Forest, La., Friday, May 5, 2023. (AP...}

\entryitemWithDescription{\hskip 0pt{}For Buffalo shooting victims' kin, Mother's Day is a reminder of loss, a lesson in navigating grief}{https://apnews.com/article/a4ec9fb05665e0ca445fb588e1c642a3}{Tirzah Patterson and her son Jaques "Jake" Patterson pose for a picture at their home, Tuesday, May. 9, 2023, in Buffalo, N.Y. Jake, 13, is the youngest child of beloved church deacon Heyward Patterson, who was gunned down at a...}

\entryitemWithDescription{\hskip 0pt{}California condors confront bird flu in flight from extinction}{https://apnews.com/article/875b1ed89ce668b757af5bcc5bd4feaf}{Condor chick LA1123 waits for it\textquotesingle s feeding in a temperature controlled enclosure at the Los Angeles Zoo on Tuesday, May 2, 2023. The chick hatched Sunday April 30, 2023. The latest breeding efforts to boost the population...}

\entryitemWithDescription{\hskip 0pt{}Youth climate lawsuit will go to trial despite Montana effort to derail case}{https://apnews.com/article/fa457bf1e8d0c39e8a0e6df611e7750e}{Judge Kathy Seeley listens to arguments during a status hearing for Held vs. Montana in the Lewis and Clark County Courthouse in Helena, Mont., on Friday, May 12, 2023. Seeley said a climate change lawsuit from young people challenging...}

\entryitemWithDescription{\hskip 0pt{}Tiny bats provide 'glimmer of hope' against a fungus that threatened entire species}{https://apnews.com/article/5f27793e29d104a283dc98390308b5b1}{Alyssa Bennett, small mammals biologist for the Vermont Department of Fish and Wildlife, holds a dead bat in a cave in Dorset, Vt., on May 2, 2023. Scientists studying bat species hit hard by the fungus that causes white nose syndrome...}

\entryitemWithDescription{\hskip 0pt{}Air Force One doubles as a campaign jet for Biden's reelection run. Who pays what?}{https://apnews.com/article/664a7d5265d98469ce20869050924242}{FILE - President Joe Biden waves as he boards Air Force One at Andrews Air Force Base, Md., Thursday, Feb. 9, 2023, en route to Florida. When Joe Biden was running for president three years ago, he flew on a white private jet with his...}