\entryitemWithDescription{\hskip 0pt{}What are the next steps for women's college basketball after title game drew 18.9 million?}{https://apnews.com/article/b592435cc286c75a7ac9278c97326ad8}{South Carolina's 87-75 victory over Caitlin Clark and Iowa in the women's NCAA championship game averaged 18.9 million viewers on ABC and ESPN, making it the second most-watched non-Olympic women's sporting event on U.S. television. The...}

\entryitemWithDescription{\hskip 0pt{}2-time All-Star Ja Morant defended himself during pickup game fight, judge says}{https://apnews.com/article/99de3acb474025165399af166dc10799}{MEMPHIS, Tenn. (AP) --- Ja Morant acted in self-defense when a teenager accused the two-time NBA All-Star of punching him during a pickup game at the home of the Memphis Grizzlies guard's parents in 2022, a judge has ruled. Shelby County...}

\entryitemWithDescription{\hskip 0pt{}Oklahoma judge orders Kansas City Chiefs superfan `ChiefsAholic' to pay \$10.8M to bank teller}{https://apnews.com/article/9302680414c3574b6fbe12a27c047ae2}{TULSA, Okla. (AP) --- An Oklahoma judge ordered a Kansas City Chiefs superfan known as ``ChiefsAholic'' who admitted to a series of bank robberies to pay \$10.8 million to a bank teller he threatened and assaulted with a gun. A judge in...}

\entryitemWithDescription{\hskip 0pt{}Florida woman is sentenced to a month in jail for selling Biden's daughter's diary}{https://apnews.com/article/fa1081c11b34a18f7d216f9cac8bf4e6}{NEW YORK (AP) --- A Florida mother was sentenced Tuesday to a month in prison and three months of home confinement for stealing and selling President Joe Biden's daughter's diary four years ago to the conservative group Project Veritas...}

\entryitemWithDescription{\hskip 0pt{}Rare copy of comic featuring Superman's first appearance sells for \$6 million at auction}{https://apnews.com/article/0bd4b08494eeb271e32557362815f5ff}{NEW YORK (AP) --- A 1938 copy of the comic that first ``introduced Superman to the world'' has sold for a record-setting \$6 million, the auctioneer that handled the purchase said last week. According to Heritage Auctions, the rare copy...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé becomes first Black woman to hit No. 1 on Billboard country albums chart}{https://apnews.com/article/9e542a074e5a8d6113d80caff6a3cda7}{NEW YORK (AP) --- Beyoncé has made history once again. Her latest album, the epic ``Act ll: Cowboy Carter'', hit No. 1 on the Billboard country albums chart, making her the first Black woman to top the chart since its 1964 inception. The...}

\entryitemWithDescription{\hskip 0pt{}UConn students celebrate into the early morning after second consecutive title}{https://apnews.com/article/79f0572414aeab9769a9fca5df67984e}{STORRS, Conn. (AP) --- Some windows were broken and street signs taken down, but celebrations following UConn's second consecutive men's basketball championship were mostly peaceful, the school said Tuesday. Thousands of students spilled...}

\entryitemWithDescription{\hskip 0pt{}Amanda Knox faces a new slander trial in Italy that could remove the last legal stain against her}{https://apnews.com/article/8da026157bd9c9391ebf23061195e6d2}{MILAN (AP) --- Amanda Knox faces another trial for slander this week in Italy in a case that could remove the last legal stain against her eight years after Italy's highest court threw out her conviction for the murder of her 21-year-old...}

\entryitemWithDescription{\hskip 0pt{}Many eclipse visitors to northern New England pulled an all-nighter trying to leave}{https://apnews.com/article/5fa6ac695a3a53a90b754b97c4719d31}{FRANCONIA, N.H. (AP) --- Thousands of visitors to northern New England communities in the path of the total solar eclipse were told to pack their patience for the trip. In some areas, they needed it for up to 12 hours after the event...}

\entryitemWithDescription{\hskip 0pt{}Explosive device thrown onto porch of Satanic Temple in Massachusetts, no injuries reported}{https://apnews.com/article/ac1214044f06ed2421b6eb3a8ef47d16}{SALEM, Mass. (AP) --- Someone threw an explosive device onto the porch of The Satanic Temple in Massachusetts at a time when no one was inside, and the device and damage it caused were not found until nearly 12 hours later, police said...}

\entryitemWithDescription{\hskip 0pt{}Istanbul airport provides anxious travelers with paw-sitive experience by hiring 5 therapy dogs}{https://apnews.com/article/59d4d9dde58d9e3457c84712798ac0e3}{ISTANBUL (AP) --- Five new hires are selflessly roaming the halls of one of the world's busiest transportation hubs, hoping to provide a paw-sitively stress-free travel experience for anxious passengers. Meet Istanbul Airport's therapy...}

\entryitemWithDescription{\hskip 0pt{}Tesla settles lawsuit over man's death in a crash involving its semi-autonomous driving software}{https://apnews.com/article/f4c19ce05e17669de212fc262265e351}{SANTA CLARA, Calif. (AP) --- Tesla has settled a lawsuit brought by the family of a Silicon Valley engineer who died in a crash while relying on the company's semi-autonomous driving software. The amount Tesla paid to settle the case was...}

\entryitemWithDescription{\hskip 0pt{}Morgan Wallen has been arrested after police say he threw a chair off of the roof of a 6-story bar}{https://apnews.com/article/016f6ed540dae5d4aa794025e3cf3e1e}{NASHVILLE, Tenn. (AP) --- Country music singer Morgan Wallen has been arrested after police say he threw a chair off the rooftop of a newly opened six-story bar in downtown Nashville. Wallen, 30, was booked into jail early Monday on three...}