\entryitemWithDescription{\hskip 0pt{}Pandemic youth mental health toll unprecedented, data show}{https://apnews.com/article/cd01cd672539d6a3dbada46bfa47203a}{FILE - Stanford women\textquotesingle s soccer team players wear warmup jerseys with "Mental Health Matters" on their backs as well as a butterfly patch on their sleeves to remember late goalie Katie Meyer, who died by suicide earlier in...}

\entryitemWithDescription{\hskip 0pt{}Rihanna's pregnancy reveal raises bar in all kinds of ways}{https://apnews.com/article/5a789ce2153e077e4c64c8609fb9aa31}{Pregnant Rihanna soars in Super Bowl halftime performance; U2 returning to stage in Las Vegas, minus one of quartet; "Magic Mike\textquotesingle s Last Dance" wins Super Bowl weekend box office in the U.S.. (Feb. 13) Rihanna performs...}

\entryitemWithDescription{\hskip 0pt{}Twitter's plan to charge for crucial tool prompts outcry}{https://apnews.com/article/eca5709035a08d2ebed8fac673809ea8}{FILE - Members of a search and rescue team work on a collapsed structure after the earthquake in Antakya, southeastern Turkey, Sunday, Feb. 12, 2023. Starting Monday, a crucial Twitter tool known as Application Developer Interface, used...}

\entryitemWithDescription{\hskip 0pt{}Newborn saved from rubble in quake-hit Syria in good health}{https://apnews.com/article/995037d2b1ce6c7ddac538c9ce260eaf}{A baby girl who was born under the rubble caused by an earthquake that hit Syria and Turkey receives treatment inside an incubator at a children\textquotesingle s hospital in the town of Afrin, Aleppo province, Syria, Tuesday, Feb. 7...}

\entryitemWithDescription{\hskip 0pt{}Roslyn Pope, author of 'Appeal for Human Rights,' dies at 84}{https://apnews.com/article/2a7df9e0cd9166455619eed54079ec81}{FILE - In this March 4, 2020 photo, Roslyn Pope poses with a framed copy of "An Appeal for Human Rights" in her home in Atlanta. Roslyn Pope, a college professor and musician who wrote ``An Appeal for Human Rights,'' laying out the...}

\entryitemWithDescription{\hskip 0pt{}Alabama hoops No. 1 in AP Top 25 for first time in 20 years}{https://apnews.com/article/3f9a5d5309a8bc2cbbffba9a4ef3bd49}{Alabama forward Nick Pringle (23) reacts after they beat Auburn in an NCAA college basketball game, Saturday, Feb. 11, 2023, in Auburn, Ala. (AP Photo/Butch Dill) Alabama is the new No. 1, rising to the top spot in The Associated Press...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl top moments happened on, off and above the field}{https://apnews.com/article/7be35ad8901fcd0d12923dc252032304}{Kansas City Chiefs defensive end Carlos Dunlap celebrates with the Vince Lombardi Trophy after the NFL Super Bowl 57 football game, Sunday, Feb. 12, 2023, in Glendale, Ariz. The Kansas City Chiefs defeated the Philadelphia Eagles 38-35...}

\entryitemWithDescription{\hskip 0pt{}U-Haul driver's NYC 'rampage' leaves 8 hurt, police say}{https://apnews.com/article/c77199ad232ee8ee259ba7156ef6841e}{Police vehicles surround a truck that was stopped and the driver arrested, Monday, Feb. 13, 2023, in New York. Police stopped the U-Haul truck and detained the driver after reports that the vehicle struck multiple pedestrians in New York...}

\entryitemWithDescription{\hskip 0pt{}Judge to release parts of Georgia special grand jury report}{https://apnews.com/article/fb2b882c3f404c196b73bc637e7cb32d}{Former President Donald Trump speaks at a campaign event at the South Carolina Statehouse, Saturday, Jan. 28, 2023, in Columbia, S.C. (AP Photo/Alex Brandon) ATLANTA (AP) --- A Georgia judge on Monday ordered the partial release later...}

\entryitemWithDescription{\hskip 0pt{}AP Interview: Moltzan catching up to US teammate Shiffrin}{https://apnews.com/article/20786ffc779a375640bdbe04075cb181}{FILE - United States\textquotesingle{} Paula Moltzan, right, smiles to winner United States\textquotesingle{} Mikaela Shiffrin after taking second place during an alpine ski, World Cup women\textquotesingle s slalom in Semmering, Austria...}

\entryitemWithDescription{\hskip 0pt{}After their genitals were cut, some women search for healing}{https://apnews.com/article/3557cd557f5061c0e416aa3b68d4fb44}{A 34-year-old Egyptian woman, who asked to be identified as N.S., visits a garden in Cairo, Egypt, Sept. 29, 2022. She remembers it all: How female relatives held her down when she was 11, legs spread and genitals exposed. The fear that...}

\entryitemWithDescription{\hskip 0pt{}Train derailment prompts water utility to take precautions}{https://apnews.com/article/b7943bd49fd11e62d45b28b77393e261}{FILE - A black plume rises over East Palestine, Ohio, as a result of a controlled detonation of a portion of the derailed Norfolk Southern trains, Feb. 6, 2023. West Virginia\textquotesingle s water utility says it\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}War for control of Haiti's capital targets women's bodies}{https://apnews.com/article/89757f336975cb28283025e65446affb}{A woman who did not want to give her name for fear of retaliation poses for a photo during an interview at a clinic near Port-au-Prince, Haiti, Friday, Jan. 20, 2023. The 36-year-old sent her two children to live with family in another...}