\entryitemWithDescription{\hskip 0pt{}Serena Williams is being honored as `fashion icon' at fashion's big awards night}{https://apnews.com/article/517a35780c1f17d05c2969a098d77943}{NEW YORK (AP) --- Serena Williams will be honored at Monday's Council of Fashion Designers of America awards for her career and contributions to American fashion. Williams, who retired from tennis last year, is the first athlete to win...}

\entryitemWithDescription{\hskip 0pt{}Rashida Tlaib defends pro-Palestinian video as rift among Michigan Democrats widens over war}{https://apnews.com/article/b6c2b4ca091c54d580b97fd01056ecf6}{LANSING, Mich. (AP) --- U.S. Rep. Rashida Tlaib of Michigan has received widespread criticism for a video she posted over the weekend that was deemed offensive to the Jewish community by some, but she said her critics should focus less on...}

\entryitemWithDescription{\hskip 0pt{}Nevada high court postpones NFL appeal in Jon Gruden emails lawsuit until January}{https://apnews.com/article/b01af1c56df2e64007ff18df54ec8075}{LAS VEGAS (AP) --- The Nevada Supreme Court has pushed back to Jan. 10 the date for oral arguments in a contract interference and conspiracy lawsuit filed against the NFL by former Las Vegas Raiders coach Jon Gruden. Postponement of the...}

\entryitemWithDescription{\hskip 0pt{}`Doc' Antle of Netflix's `Tiger King' pleads guilty to wildlife trafficking and money laundering}{https://apnews.com/article/3722f525fd760b096f03bd3bb41a81ba}{An exotic wildlife preserve owner who gained notoriety on the popular Netflix series ``Tiger King'' plead guilty Monday to animal trafficking and money laundering, the U.S. Justice Department announced. Bhagavan ``Doc'' Antle oversaw the...}

\entryitemWithDescription{\hskip 0pt{}This holiday season, the mean ol' Grinch gets a comedy podcast series hosted by James Austin Johnson}{https://apnews.com/article/12795fb5321e05ef915fdc832c4486fe}{NEW YORK (AP) --- What would the mean ol' Grinch be doing in 2023? Would that Christmas sad sack be hosting a cooking show on TikTok? Writing long essays for Substack? No, you know what he'd be doing --- a podcast. ``The Grinch Holiday...}

\entryitemWithDescription{\hskip 0pt{}New Zealand's ex-Premier Jacinda Ardern will join conservation group to rally for environment action}{https://apnews.com/article/9c13c56f61697b9385964716364faa3e}{WELLINGTON, New Zealand (AP) --- Former New Zealand Prime Minister Jacinda Ardern will work alongside leaders from Conservation International to advocate for climate action and better treatment of the environment, the group said Monday...}

\entryitemWithDescription{\hskip 0pt{}Prince William says deeper global cooperation can win the fight against illegal wildlife trafficking}{https://apnews.com/article/05f74345a08bef3cdc1cdfc6bd21a18a}{SINGAPORE (AP) --- Britain's Prince William said Monday that seven countries --- Australia, Canada, New Zealand, South Africa, Singapore, Britain and the United States --- have committed at a wildlife summit to deepen their intelligence...}

\entryitemWithDescription{\hskip 0pt{}Attorneys for former player suing Blackhawks say he was inspired to come forward by Kyle Beach}{https://apnews.com/article/220621b6d7a3cb973b4f1e7a777e1291}{CHICAGO (AP) --- Attorneys for a former player suing the Chicago Blackhawks for allegedly ignoring his complaints that a team employee sexually abused him during the 2009-10 Stanley Cup championship season said Monday that their client...}

\entryitemWithDescription{\hskip 0pt{}Ryan Blaney earns 1st career NASCAR championship and gives Roger Penske back-to-back Cup titles}{https://apnews.com/article/fa8afdb105925ac8be6f99e5ac649a62}{AVONDALE, Ariz. (AP) --- Ryan Blaney only had to beat Kyle Larson and William Byron to win his first NASCAR championship. He needlessly added Ross Chastain to his list, too, racing him pointlessly hard in an attempt to win the race Sunday...}

\entryitemWithDescription{\hskip 0pt{}Weekend box office results are muted without `Dune: Part Two'}{https://apnews.com/article/16b62d517187add73758413b07f2980b}{The North American box office had one of its slowest weekends of the year, due in large part to ``Dune: Part Two's'' absence from the lineup. Moviegoers had many other options to choose from. The video game adaptation ``Five Nights at...}

\entryitemWithDescription{\hskip 0pt{}Washington Post names veteran media executive Will Lewis as its new publisher and CEO}{https://apnews.com/article/2050bc460fcc8f40f5a61b62da7e147e}{NEW YORK (AP) --- The Washington Post has named veteran media executive Will Lewis to serve as its new CEO and publisher, hoping to turn around a recent slump that has seen job cuts and a declining audience. Lewis is the former top...}

\entryitemWithDescription{\hskip 0pt{}Prince William arrives in Singapore for the Earthshot Prize award, the first to be held in Asia}{https://apnews.com/article/74561b07776e69d121d27729bf432f8d}{SINGAPORE (AP) --- Prince William arrived Sunday in Singapore for the Earthshot Prize awards, the first to be held in Asia, to support environmental innovators with solutions to battle climate change and save the planet. Dozens of people...}

\entryitemWithDescription{\hskip 0pt{}Big Weekend: Rich Eisen reflects on NFL Network turning 20 and calling Chiefs-Dolphins on Sunday}{https://apnews.com/article/849e8bb4a385c820441f293ec04ba171}{Rich Eisen has had many memorable moments during his long tenure at NFL Network. This weekend though might end up being tough to beat. Saturday marks 20 years since NFL Network went on the air with Eisen anchoring ``Total Access.'' On...}