\entryitemWithDescription{\hskip 0pt{}First Bob Ross TV painting, completed in a half an hour, goes on sale for nearly \$10 million}{https://apnews.com/article/f79ecfd4437ca21c813a9b73646b54a7}{MINNEAPOLIS (AP) --- What would Bob Ross think? The artist who brought painting to the people, with works completed for PBS viewers in less than a half-hour with little more than a large bristle brush, putty knife and plenty of...}

\entryitemWithDescription{\hskip 0pt{}Ray Epps, Trump supporter targeted by Jan. 6 conspiracy theory, pleads guilty to Capitol riot charge}{https://apnews.com/article/157ce51c7ded7f30f21cfab834dcce74}{WASHINGTON (AP) --- Ray Epps, a onetime Donald Trump supporter who was the target of a right-wing conspiracy theory about the Jan. 6, 2021, attack that forced him into hiding, pleaded guilty on Wednesday to a misdemeanor charge for his...}

\entryitemWithDescription{\hskip 0pt{}Kevin Costner and wife Christine Baumgartner reach divorce settlement and avoid trial}{https://apnews.com/article/dd027459ce8cb3f9bcb26f081c97e4df}{SANTA BARBARA, Calif. (AP) --- Kevin Costner and his wife of nearly 19 years, Christine Baumgartner, have reached a settlement in their divorce. ``Kevin and Christine Costner have come to an amicable and mutually agreed upon resolution of...}

\entryitemWithDescription{\hskip 0pt{}A 96-year-old federal judge is barred from hearing cases in a bitter fight over her mental fitness}{https://apnews.com/article/afaa58f65bfd6612300ae5a925c7cc55}{A 96-year-old U.S. federal appeals court judge was barred Wednesday from hearing cases for a year after a panel said she refused to undergo medical testing amid concerns that she is no longer mentally fit to serve on the bench. It's the...}

\entryitemWithDescription{\hskip 0pt{}Maryland apologizes to man wrongly convicted of murder, agrees to \$340K payment for years in prison}{https://apnews.com/article/430db0112b6d33099f3248025a022857}{ANNAPOLIS, Md. (AP) --- A man wrongly convicted of two separate violent crimes will be compensated by the state of Maryland after spending years behind bars, including over a year after he had been proven innocent. A Maryland board...}

\entryitemWithDescription{\hskip 0pt{}Judge dismisses two suits filed by man whose work as informant inspired the movie `White Boy Rick'}{https://apnews.com/article/d0d0775264129d88548bd812c269ab27}{DETROIT (AP) --- Two lawsuits filed by a Detroit-area man whose decades in prison for drug dealing and work as an informant inspired the movie ``White Boy Rick'' have been dismissed by a federal judge who found he waited too long to file...}

\entryitemWithDescription{\hskip 0pt{}Connecticut agrees to a \$25 million settlement in the Henry Lee evidence fabrication case}{https://apnews.com/article/f87fb7a6fdcc256849a7daa72296b9bd}{HARTFORD, Conn. (AP) --- Connecticut's attorney general has agreed to a \$25.2 million settlement with two men who spent decades in prison for murder, based partly on evidence presented by famed forensic scientist Henry Lee that a judge...}

\entryitemWithDescription{\hskip 0pt{}Vanna White extends her time at the puzzle board on `Wheel of Fortune' for two additional seasons}{https://apnews.com/article/5603a165f731ae1ce426ba197b64873c}{Vanna White is not giving up her puzzle board when Ryan Seacrest takes over for Pat Sajak as host of ``Wheel of Fortune.'' In fact, she will be there for his first two seasons. Sony Pictures Television announced Tuesday that White has...}

\entryitemWithDescription{\hskip 0pt{}At 91, Georgia's longest serving sheriff says he won't seek another term in 2024}{https://apnews.com/article/2d28fbb1127308bb3430f6e0f5ad817c}{PERRY, Ga. (AP) --- A 91-year-old Georgia sheriff has said he will hand in his badge after more than 50 years as the county's chief lawman. Houston County Sheriff Cullen Talton tells WMAZ-TV that he won't seek reelection in 2024 and will...}

\entryitemWithDescription{\hskip 0pt{}Did missing ex-NFL player Sergio Brown post videos about mother's death? Police are investigating}{https://apnews.com/article/b72180f87abb49bb9eb6bcca1ea0f5ac}{MAYWOOD, Ill. (AP) --- Police in suburban Chicago are checking on the authenticity of Instagram videos that appear to show missing former NFL player Sergio Brown discussing the recent death of his mother, who died following an assault...}

\entryitemWithDescription{\hskip 0pt{}Tornadoes kill 10 people and seriously injure 4 others in eastern China}{https://apnews.com/article/b6208287d10c6ca5f87a9fff728ae5be}{BEIJING (AP) --- Two tornadoes within hours killed 10 people and seriously injured four others in eastern China, state media said Wednesday. The first tornado hit parts of Suqian city in Jiangsu province on Tuesday afternoon, state...}

\entryitemWithDescription{\hskip 0pt{}Kraft Heinz is recalling some American cheese slices because the wrappers could pose choking hazard}{https://apnews.com/article/0ff08e209613d280426493b4c77799e0}{Kraft Heinz said Tuesday it's recalling more than 83,000 cases of individually-wrapped Kraft Singles American processed cheese slices because part of the wrapper could stick to the slice and become a choking hazard. The company, which is...}

\entryitemWithDescription{\hskip 0pt{}Ohtani has elbow surgery. His doctor expects hitting return by opening day '24 and pitching by '25}{https://apnews.com/article/f05408238a4e8389ec500b52bec38154}{ST. PETERSBURG, Fla. (AP) --- Los Angeles Angels star Shohei Ohtani had elbow surgery Tuesday, and his doctor said he expects the two-way star will be available as a hitter on opening day next season and will return to the mound as a...}