\entryitemWithDescription{\hskip 0pt{}Former 'Family Feud' contestant charged in wife's slaying}{https://apnews.com/article/1be5e505ebd16bea04477304c9d34d89}{This booking image provided by Adams County, Illl., administration, shows Timothy Bliefnick of Quincy, Ill., who has been charged charged with first-degree murder in the death of his estranged wife, Rebecca Bliefnick. Bliefnick, 39, who...}

\entryitemWithDescription{\hskip 0pt{}Principal resigns after complaints on 'David' statue nudity}{https://apnews.com/article/84bba40d47339eff7770ec58fcb23dd1}{FILE - German Chancellor Angela Merkel, left, and Italian Prime Minister Matteo Renzi speak during a press conference in front of Michelangelo\textquotesingle s "David statue" after their bilateral summit in Florence, Italy, Jan. 23...}

\entryitemWithDescription{\hskip 0pt{}Russians, American delayed in space to return in September}{https://apnews.com/article/d8249e94068552aca6f79cf4387f6540}{MOSCOW (AP) --- Two cosmonauts and an astronaut who were supposed to leave the International Space Station this month will be brought back to Earth in late September, doubling their time aboard the orbiting laboratory to more than a year...}

\entryitemWithDescription{\hskip 0pt{}Darcelle, world's oldest working drag queen, dies at 92}{https://apnews.com/article/e187006c33c51d69e42e491024806964}{In this Sept. 2019 photo, Darcelle XV, performs in Portland, Ore. Walter C. Cole, better known as the iconic drag queen who performed for decades as Darcelle, has died of natural causes in Portland, Ore, on Thursday, March 24, 2023. (Beth...}

\entryitemWithDescription{\hskip 0pt{}US, Canada end loophole that let asylum-seekers cross border}{https://apnews.com/article/275d932944f831dc5c53d2d582f9ac45}{Haitian migrant Gerson Solay, 28, carries his daughter, Bianca, as he and his family cross into Canada at the non-official Roxham Road border crossing north of Champlain, N.Y., on Friday, March 24, 2023. A new US-Canadian migration...}

\entryitemWithDescription{\hskip 0pt{}4 ex-cops charged in Tyre Nichols' death barred from police}{https://apnews.com/article/facb607496ba0f8abf9d7cdf21c97446}{FILE - The screen at the Smoothie King Center in New Orleans honors Tyre Nichols before an NBA basketball game between the New Orleans Pelicans and the Washington Wizards, Jan. 28, 2023. Four of five former Memphis police officers charged...}

\entryitemWithDescription{\hskip 0pt{}Brazil's Bolsonaro turns in undeclared jewels to authorities}{https://apnews.com/article/a57b2ff22cef6149be0b80b8d5c54428}{This photo provided by Brazil's Federal Revenue Department shows jewelry seized by customs authorities at Guarulhos International Airport in Sao Paulo, Brazil, the week of March 24, 2023. The jewelry is part of an investigation into gifts...}

\entryitemWithDescription{\hskip 0pt{}Trump lawyer in court after being forced before grand jury}{https://apnews.com/article/623428540a6cff1b5dcdf697cdf45b5d}{M. Evan Corcoran, an attorney for former President Donald Trump, arrives at federal court in Washington, Friday, March 24, 2023. (AP Photo/Jose Luis Magana) WASHINGTON (AP) --- A lawyer for Donald Trump was back in court Friday after...}

\entryitemWithDescription{\hskip 0pt{}Debt, expenses stress lower income households: AP-NORC poll}{https://apnews.com/article/3225413a5d6aed5dfcf57c7cb03c7776}{The likeness of George Washington is seen on a U.S. one dollar bill, Monday, March 13, 2023, in Marple Township, Pa. (AP Photo/Matt Slocum) NEW YORK (AP) --- Personal finances are a major source of stress for about half of the lower...}

\entryitemWithDescription{\hskip 0pt{}Rwanda frees Paul Rusesabagina of 'Hotel Rwanda' fame}{https://apnews.com/article/5b1d0f01344e454b2ae7474af1da83e4}{FILE - Paul Rusesabagina, who inspired the film "Hotel Rwanda" and is credited with saving more than 1,000 people by sheltering them at the hotel he managed during the genocide, attends a court hearing in Kigali, Rwanda, Friday Feb. 26...}

\entryitemWithDescription{\hskip 0pt{}2 dead in Missouri flash flood; tornado threat in the South}{https://apnews.com/article/65e553e6358b56b2630ff5c588850505}{DECATUR, Texas (AP) --- Two people died early Friday in Missouri when a car was swept away during torrential rains that were part of a severe weather system roaring across parts of the Midwest and South. The accident happened just after...}

\entryitemWithDescription{\hskip 0pt{}Deutsche Bank shares drop amid global jitters over banks}{https://apnews.com/article/8a9a9b107638cf4c8872ea8772a70ed5}{Bubbles made by a soap bubble artist, fly in front of the headquarters of Deutsche Bank in Frankfurt, Germany, Friday, March 24, 2023. (AP Photo/Michael Probst) FRANKFURT, Germany (AP) --- Shares in Deutsche Bank fell sharply Friday...}

\entryitemWithDescription{\hskip 0pt{}Classic cocktails, with variations, for summer entertaining}{https://apnews.com/article/ce9e21e691644957ed899ab2e11eebfe}{This combination of photos show, from left, Daiquiri cocktail, a Manhattan, an Old Fashioned, a Poker cocktail and a Rum Old Fashioned cocktail. (Callum Duffy via AP) The arrival of spring means summer entertaining season isn't far...}