\entryitemWithDescription{\hskip 0pt{}Commander Biden bites another Secret Service employee at the White House}{https://apnews.com/article/ba9a59d8629f16f414ac028e3a868d84}{WASHINGTON (AP) --- President Joe Biden 's dog Commander has bitten another U.S. Secret Service employee. A uniformed division officer was bitten by the dog around 8 p.m. Monday at the White House, and was treated on-site by medical...}

\entryitemWithDescription{\hskip 0pt{}Mandela's granddaughter Zoleka dies at 43. Her life was full of tragedy but she embraced his legacy}{https://apnews.com/article/373d75f4fb63f58997364367774824cd}{CAPE TOWN, South Africa (AP) --- Zoleka Mandela, a granddaughter of Nelson Mandela whose life was tangled up in addiction, a suicide attempt, a battle with cancer and the tragedy of losing two young children before she came back from the...}

\entryitemWithDescription{\hskip 0pt{}Sophia Loren after leg-fracture surgery: `Thanks for all the affection, I'm better,' just need rest}{https://apnews.com/article/b290136ea53528ea7742e951a93cdb52}{ROME (AP) --- Sophia Loren is expressing gratitude for all the affection she received following surgery needed after the film star fractured a hip and thigh bone in a bathroom fall, her agent said Tuesday. Andrea Giusti quoted the...}

\entryitemWithDescription{\hskip 0pt{}Police are investigating if unprescribed drugs factored into death of ex-NFL player Mike Williams}{https://apnews.com/article/3a9c1ca31161e8c550b10b8943ef86da}{TAMPA, Fla. (AP) --- Police are investigating the death of former NFL player Mike Williams in Tampa after getting information that he may have received unprescribed drugs from someone while hospitalized after a construction site accident...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift is a fan of Travis Kelce and suddenly, so is everyone else}{https://apnews.com/article/d6fc6756069e0c2dc12c0af747941414}{NEW YORK (AP) --- Taylor Swift's trip to watch the Kansas City Chiefs' Travis Kelce play football on Sunday didn't just have the internet talking nonstop. Following the 12-time Grammy Award winner's appearance at Arrowhead Stadium, jersey...}

\entryitemWithDescription{\hskip 0pt{}London's Gatwick Airport limits flights this week due to staff illness, including COVID-19}{https://apnews.com/article/c27a62e268b29c07c616a14b19afb5d8}{LONDON (AP) --- Gatwick Airport, London's second-busiest, is limiting flights this week, partly because of an outbreak of COVID-19 within air traffic control. In a statement late Monday, the airport said a daily 800-flight limit...}

\entryitemWithDescription{\hskip 0pt{}Spain charges pop singer Shakira with tax evasion for a second time and demands more than \$7 million}{https://apnews.com/article/5d3698158bc565ac1dc6134c7d3baaa7}{BARCELONA, Spain (AP) --- Spanish prosecutors have charged pop star Shakira with failing to pay 6.7 million euros (\$7.1 million) in tax on her 2018 income, authorities said Tuesday, in Spain's latest fiscal allegations against the...}

\entryitemWithDescription{\hskip 0pt{}In Sweden, 2 explosions rip through dwellings and at least 1 is reportedly connected to a gang feud}{https://apnews.com/article/c7b7f1f907d0bbd662c7e2b33c4cadb6}{STOCKHOLM (AP) --- Two powerful explosions ripped through dwellings in central Sweden overnight, injuring at least three people and damaging buildings, with bricks and window sections left spread outside. Late on Monday, an explosion...}

\entryitemWithDescription{\hskip 0pt{}Leaf-peeping social media users are clogging a Vermont back road. The town is closing it}{https://apnews.com/article/a4d035847e0d0590ec3825bfc72ac716}{POMFRET, Vt. (AP) --- Social media users take note: You won't be able to snap that fall foliage selfie at a popular Vermont spot. The town has temporarily closed the road to nonresidents due to overcrowding and ``poorly behaved...}

\entryitemWithDescription{\hskip 0pt{}David McCallum, star of hit TV series `The Man From U.N.C.L.E.' and `NCIS,' dies at 90}{https://apnews.com/article/ffd87131857c4206b645d3be3254e991}{LOS ANGELES (AP) --- Actor David McCallum, who became a teen heartthrob in the hit series ``The Man From U.N.C.L.E.'' in the 1960s and was the eccentric medical examiner in the popular ``NCIS'' 40 years later, has died. He was 90...}

\entryitemWithDescription{\hskip 0pt{}DeSantis and Newsom to go head-to-head in November Fox News debate moderated by Sean Hannity}{https://apnews.com/article/4a7081f6778872eb088660209552480c}{NEW YORK (AP) --- Florida Gov. Ron DeSantis will take time out from debating fellow Republicans in two months to take on a Democrat, California Gov. Gavin Newsom. Fox News said Monday that the two politicians will appear in a 90-minute...}

\entryitemWithDescription{\hskip 0pt{}Diversity and inclusion celebrated in Milan with refrain: Make more space for color, curves}{https://apnews.com/article/992da174c7299495a7f673f304464d09}{MILAN (AP) --- More curvy models than ever showed up on Milan runways this season, due mostly to a single show by Brazilian designer Karoline Vitto, while designers of color showcased their work at collateral events meant to promote their...}

\entryitemWithDescription{\hskip 0pt{}Powerball jackpot climbs to \$835 million after no one overcomes awful odds to win top prize}{https://apnews.com/article/55e424dbafde3524dfb636e5f6768bfc}{DES MOINES, Iowa (AP) --- The Powerball jackpot climbed to an estimated \$835 million after no one beat the immense odds Monday night and won the top prize. The winning numbers were: 10, 12, 22, 36, 50 and 4. With the latest bit of...}