\entryitemWithDescription{\hskip 0pt{}Judge: Dominion defamation case against Fox will go to trial}{https://apnews.com/article/42cae434c4cfadbbafe73d1f2bca8e4d}{FILE - A headline about President Donald Trump is displayed outside Fox News studios in New York on Nov. 28, 2018. Dominion Voting Systems\textquotesingle{} defamation case against Fox News over its airing of false allegations about the...}

\entryitemWithDescription{\hskip 0pt{}Florida teen debuts trans visibility film as bans spread}{https://apnews.com/article/1b34bb200928b8165410d84b22e3e408}{Topher Malone, a 17-year-old trans high school student in Round Rock, Texas, talks about her experience for the documentary, ``You're Loved,'' which premieres at Green Light Cinema in St. Petersburg, Fla. on March 31, 2023. Carys Mullins...}

\entryitemWithDescription{\hskip 0pt{}Brooke Shields takes charge of her story in 'Pretty Baby'}{https://apnews.com/article/d6913f23eb7ebce34d4b4abb8cfe3094}{FILE - Brooke Shields poses for a portrait to promote the film "Pretty Baby: Brooke Shields" at the Latinx House during the Sundance Film Festival on Jan. 21, 2023, in Park City, Utah. The docuseries premieres Monday on Hulu. (Photo by...}

\entryitemWithDescription{\hskip 0pt{}US Marine's adoption of Afghan war orphan voided}{https://apnews.com/article/295673fb358cf30abd243995cd846c99}{Marine Maj. Joshua Mast and his wife, Stephanie, arrive at Circuit Court, Thursday, March 30, 2023 in Charlottesville, Va. In a highly unusual ruling, a state court judge on Thursday voided a U.S. Marine's adoption of an Afghan war...}

\entryitemWithDescription{\hskip 0pt{}Romania: Andrew Tate's detention replaced with house arrest}{https://apnews.com/article/21d9c3f050b76f28615b541217ea83be}{Andrew Tate, center, and his brother Tristan stand outside a detention facility in Bucharest, Romania, after his release from prison on Friday March 31, 2023. An official on Friday said Tate, the divisive internet personality who has...}

\entryitemWithDescription{\hskip 0pt{}Worries grow that Trump indictment will eclipse other probes}{https://apnews.com/article/395413afdf8861171ca184afefab2c97}{FILE - President Donald Trump arrives to speak at a rally in Washington, on Jan. 6, 2021. The indictment against former President Donald Trump involving a payoff to suppress claims of an extramarital affair is raising concerns that it...}

\entryitemWithDescription{\hskip 0pt{}Journalist's arrest threatens reporting from Russia}{https://apnews.com/article/2172a2edc07d652ebaf000eb1c3e3618}{Wall Street Journal reporter Evan Gershkovich is escorted by officers from the Lefortovsky court to a bus, in Moscow, Russia, Thursday, March 30, 2023. Russia\textquotesingle s top security agency says an American reporter for the Wall...}

\entryitemWithDescription{\hskip 0pt{}Factory explosion survivor, on fire, fell into chocolate vat}{https://apnews.com/article/c1c8e8cb8ee585db9cc9277fbb0b88e3}{This photo provided by Aaron Paz shows Patricia Borges at Reading Hospital in West Reading, Pa., on March 25, 2023. Borges was pulled alive from the rubble of the R.M. Palmer Co. factory, a chocolate factory in West Reading, Pa., after an...}

\entryitemWithDescription{\hskip 0pt{}EPA approves California rules phasing out diesel trucks}{https://apnews.com/article/02e279026cf9d9b5c088f9ebdfad3fd9}{FILE - Trucks line up to enter a Port of Oakland shipping terminal on Nov. 10, 2021, in Oakland, Calif. President Joe Biden\textquotesingle s administration cleared the way for California\textquotesingle s plan to phase out a wide range...}

\entryitemWithDescription{\hskip 0pt{}Minneapolis and state agree to revamp policing post-Floyd}{https://apnews.com/article/40342c35c09a300186e31c6b599f9d7c}{Minneapolis Mayor Jacob Frey, right, pats the shoulder of Minneapolis Police Chief Brian O\textquotesingle Hara after O\textquotesingle{} Hara spoke during a press conference announcing approval of a sweeping plan to reform policing that...}

\entryitemWithDescription{\hskip 0pt{}Final Four: At Florida Atlantic, it's not 'F-A-Who?' anymore}{https://apnews.com/article/fdda483a522a52c9450303957e05bb02}{Florida Atlantic head coach Dusty May holds up the championship trophy after Florida Atlantic defeated Kansas State 79-86 in an Elite 8 college basketball game in the NCAA Tournament\textquotesingle s East Region final, Saturday, March...}

\entryitemWithDescription{\hskip 0pt{}Gwyneth Paltrow scores court win that means more than \$1}{https://apnews.com/article/c9b0814973cb9040a96776fbb5d2c411}{Gwyneth Paltrow speaks with retired optometrist Terry Sanderson, left, as she walks out of the courtroom following the reading of the verdict in their lawsuit trial, Thursday, March 30, 2023, in Park City, Utah. Paltrow won her court...}

\entryitemWithDescription{\hskip 0pt{}Justice Department sues Norfolk Southern over derailment}{https://apnews.com/article/b5162c3a5d3eec681eaadfa4266ef5a6}{FILE - This photo taken with a drone shows portions of a Norfolk and Southern freight train that derailed Friday night in East Palestine, Ohio are still on fire at mid-day Saturday, Feb. 4, 2023. The federal government filed a lawsuit...}