\entryitemWithDescription{\hskip 0pt{}`Tiger King' star 'Doc' Antle convicted of wildlife trafficking in Virginia}{https://apnews.com/article/689456335b6be5cc51f87f48f7463539}{FILE - This image provided by the Horry County Sheriff\textquotesingle s Office in Conway, S.C., shows Bhagavan "Doc" Antle, wild animal trainer featured in the popular Netflix series ``Tiger King'', who has been convicted of wildlife...}

\entryitemWithDescription{\hskip 0pt{}Colombian military searches for heroic dog who helped find children in the Amazon jungle}{https://apnews.com/article/0c33da91820ad221d4dafd6b86c64844}{A dog walks through an opening at a Colombian Army training facility for military working dogs to serve alongside troops in various capacities, in Bogota, Colombia, Wednesday, June 21, 2023. (AP Photo/Ivan Valencia) BOGOTA, Colombia...}

\entryitemWithDescription{\hskip 0pt{}Drugmaker lobbying group sues over plan to negotiate Medicare drug prices}{https://apnews.com/article/712b8c06c3ca24313263ba3213b1f997}{FILE - Pharmaceuticals are seen in North Andover, Mass., on June 15, 2018. The Pharmaceutical Research and Manufacturers of America, or PhRMA, is suing over plans laid out in the Inflation Reduction Act to give the federal coverage...}

\entryitemWithDescription{\hskip 0pt{}IOC warns Afghanistan about Paris Olympics status over denying sports to women and girls}{https://apnews.com/article/5be25373ad420151da6258cfb19cf35a}{FILE - An Afghan women\textquotesingle s soccer team poses for a photo in Kabul, Afghanistan, Thursday, Sept. 22, 2022. Afghanistan\textquotesingle s status for the 2024 Paris Olympics was put in question Wednesday, June 21, 2023, by the...}

\entryitemWithDescription{\hskip 0pt{}Who will have the 2023 song of the summer? We offer some predictions}{https://apnews.com/article/411d7738986212bb7ffb06e8f3893408}{FILE - People cool off on Puerto de Sagunto beach in Spain, Tuesday, Aug. 16, 2022. (AP Photo/Alberto Saiz, File) LOS ANGELES (AP) --- The sun is shining, the beach is calling, and school is out: It's time to prepare the song of the...}

\entryitemWithDescription{\hskip 0pt{}Paris police look at gas leak as possible cause of explosion and fire that injured 24}{https://apnews.com/article/e46a56221f571532564ba80d3aec3c3f}{Firemen use a water canon as they fight a blaze Wednesday, June 21, 2023 in Paris. Firefighters fought a blaze on Paris\textquotesingle{} Left Bank that is sent smoke soaring over the domed Pantheon monument and prompted evacuation of...}

\entryitemWithDescription{\hskip 0pt{}Morgan and Rapinoe selected for the US Women's World Cup roster}{https://apnews.com/article/fca671883fae17401f20ce81a4ed2a12}{FILE - In this July 7, 2019 file photo, United States\textquotesingle{} Megan Rapinoe celebrates after scoring the opening goal from the penalty spot during the Women\textquotesingle s World Cup final soccer match against The Netherlands...}

\entryitemWithDescription{\hskip 0pt{}Pharrell fuses entertainment and fashion for confident Louis Vuitton menswear debut}{https://apnews.com/article/9adfe293e9c841a3d7448a7fb3962c94}{Designer Pharrell Williams accepts applause at the conclusion of the Louis Vuitton Menswear Spring/Summer 2024 fashion collection presented in Paris, Tuesday, June 20, 2023. (AP Photo/Christophe Ena) PARIS (AP) --- Unveiling a new chapter...}

\entryitemWithDescription{\hskip 0pt{}Andrew Tate appears in Romanian court to face rape and human trafficking charges}{https://apnews.com/article/bf98ebb2a03e158843622e8a753c588a}{Andrew Tate walks between bodyguards as he arrives at the Bucharest Tribunal, in Bucharest, Romania, Wednesday, June 21, 2023. Romanian prosecutors charged on Tuesday, June 20, 2023, the Tate brothers and two other suspects with human...}

\entryitemWithDescription{\hskip 0pt{}Aaron Rodgers is set to speak at a psychedelics conference}{https://apnews.com/article/bae8c5ae3f221770fb84b123a92cf2d2}{FILE - New York Jets\textquotesingle{} quarterback Aaron Rodgers smiles during an NFL football news conference at the Jets\textquotesingle{} training facility in Florham Park, N.J., Wednesday, April 26, 2023. Months after Colorado's...}

\entryitemWithDescription{\hskip 0pt{}Trump-Russia special counsel Durham at center of political clash as he appears before Congress}{https://apnews.com/article/b24ef8c4b781083227009d09d55bc5e7}{Special Counsel John Durham testifies before the House Judiciary Committee, Wednesday, June 21, 2023, on Capitol Hill in Washington. Durham recently completed his report on the FBI's investigation of Trump's 2016 campaign. (AP Photo/Jose...}

\entryitemWithDescription{\hskip 0pt{}Modi flexes India's cultural reach on Yoga Day with backbends and corpse poses on the UN lawn}{https://apnews.com/article/cbf22dc2e75e71b575a25f7806faa496}{India Prime Minister Narendra Modi, center, practices yoga during the International Yoga day event at United Nations headquarters in New York on Wednesday, June 21, 2023. Modi has joined diplomats and dignitaries at the United Nations for...}

\entryitemWithDescription{\hskip 0pt{}Once starved by war, millions of Ethiopians go hungry again as US, UN pause aid after massive theft}{https://apnews.com/article/c129b6942663cbfc44c6605fed97928b}{FILE - An Ethiopian woman argues with others over the allocation of yellow split peas after it was distributed by the Relief Society of Tigray in the town of Agula, in the Tigray region of northern Ethiopia, on May 8, 2021. In 2023...}