\entryitemWithDescription{\hskip 0pt{}Fond remembrances for Jimmy Carter after entering hospice}{https://apnews.com/article/52a467967c7758d36fec37b891343046}{FILE - Former President Jimmy Carter teaches Sunday school at Maranatha Baptist Church, in Plains, Ga., Nov. 3, 2019. Well-wishes and fond remembrances for the former president continued to roll in Sunday, Feb. 19, 2023, a day after he...}

\entryitemWithDescription{\hskip 0pt{}Mexican musician finds refuge in saxophone after acid attack}{https://apnews.com/article/76981182d530044e5a622104b1edb1b9}{Maria Elena Ríos holds her saxophone at the end of a rehearsal at the National Autonomous University of Mexico music department, in Mexico City, Tuesday, Feb. 14, 2023. Ríos, 29, thought her career as a musician and her devotion to...}

\entryitemWithDescription{\hskip 0pt{}'All Quiet' wins 7 BAFTAs, including best film, at UK awards}{https://apnews.com/article/f06c963b285c8a3c126e8c4815c98492}{Edward Berger poses for photographers with the Director Award for the film \textquotesingle All Quiet on the Western Front\textquotesingle{} at the 76th British Academy Film Awards, BAFTA\textquotesingle s, in London, Sunday, Feb. 19...}

\entryitemWithDescription{\hskip 0pt{}Drama of McCarthy's election may open House to more cameras}{https://apnews.com/article/f548d7f20e08e6d948087137b0e11c71}{FILE - Rep. Matt Gaetz, R-Fla., left, talks to Rep. Kevin McCarthy, R-Calif., right, in the House chamber as the House meets for the fourth day to elect a speaker and convene the 118th Congress in Washington on Jan. 6, 2023. Some members...}

\entryitemWithDescription{\hskip 0pt{}Michigan State set to resume classes after fatal shootings}{https://apnews.com/article/7641418dfd9ffd789ff9db268ece424e}{Michigan State University professor Marco Díaz-Muñoz talks during an interview at his home in Lansing, Mich., Thursday, Feb. 16, 2023. Díaz-Muñoz is still haunted by what he witnessed last Monday night, when a gunman entered his classroom...}

\entryitemWithDescription{\hskip 0pt{}Biden's test: Sustaining unity as Ukraine war enters Year 2}{https://apnews.com/article/15095c5e2fb8a9f9c0a235ffe0a161d0}{President Joe Biden is set to travel to Poland, meeting with allies to reassure them of the U.S. commitment as the one year anniversary of the invasion of Russia into Ukraine. (Feb. 19) FILE - President Joe Biden speaks with Ukrainian...}

\entryitemWithDescription{\hskip 0pt{}Ukrainian grain shipments drop as ship backups grow}{https://apnews.com/article/02978d1ab61d70939ff1581b1129d18a}{FILE - A boat with Russian, Ukrainian, Turkish and U.N. officials heads to inspect cargo ships coming from Ukraine loaded with grain, in the Marmara Sea in Istanbul, Turkey, Saturday, Oct. 1, 2022. The amount of grain leaving Ukraine has...}

\entryitemWithDescription{\hskip 0pt{}Russia's year of war: Purge of critics, surge of nationalism}{https://apnews.com/article/0fb016f9eb055b189b2b46e282867168}{Cars in Moscow, Russia, on Wednesday, March 30, 2022, drive past a building decorated with a huge letter ``Z,'' which has become a symbol of the Russian military operation in Ukraine, along with a hashtag reading, "We don\textquotesingle...}

\entryitemWithDescription{\hskip 0pt{}Health care vaccine mandate remains as some push for an end}{https://apnews.com/article/f24c4b1e65ab4e74f30511ab2b6ed64d}{Tim Corbin, left, the administrator of Truman Lake Manor, passes through the hallway of the nursing home on Feb. 14, 2023, in Lowry, Mo. The facility was cited in December for a violation of the federal vaccination requirement for health...}

\entryitemWithDescription{\hskip 0pt{}'I just want my legs back': Myanmar landmine casualties soar}{https://apnews.com/article/0451f807790016c8e46114bb01441fe4}{In this photo provided by the family, a young landmine victim learns to use his new prosthetic limbs at Hpa-An Orthopedic Rehabilitation Center in Hpa-An township, Karen State, Myanmar, on Dec. 7, 2022. The boy lost his legs in a landmine...}

\entryitemWithDescription{\hskip 0pt{}N. Korea makes fresh threats, US bombers fly after ICBM test}{https://apnews.com/article/d6781836ad90388ca62381368712017b}{In this photo provided by South Korea Defense Ministry, a U.S. Air Force B-1B bomber, top, flies in formation with U.S. Air Force F-16 fighter jets over the South Korea Peninsula during a joint air drill in South Korea, Sunday, Feb. 19...}

\entryitemWithDescription{\hskip 0pt{}Ukraine in mind, US frantic to avert Mideast showdown at UN}{https://apnews.com/article/f2e4430b235b683071f8cc4ce2e4531d}{United States Secretary of State Antony Blinken attends a panel discussion at the Munich Security Conference in Munich, Saturday, Feb. 18, 2023. The 59th Munich Security Conference (MSC) is taking place from Feb. 17 to Feb. 19, 2023 at...}

\entryitemWithDescription{\hskip 0pt{}Mac McClung soars to slam dunk title at All-Star Saturday}{https://apnews.com/article/6a2ea26147bafb0f80ea77620cacf2e9}{Mac McClung of the Philadelphia 76ers shoots during the slam dunk competition of the NBA basketball All-Star weekend Saturday, Feb. 18, 2023, in Salt Lake City. (AP Photo/Rob Gray) SALT LAKE CITY (AP) --- Mac McClung might have single...}