\entryitemWithDescription{\hskip 0pt{}Recently arrested Morgan Wallen says he's `not proud' of behavior}{https://apnews.com/article/12788b00384ed365ab75e12d5b166dee}{NASHVILLE, Tenn. (AP) --- Country music star Morgan Wallen, who faces charges stemming in part from accusations that he threw a chair off the rooftop of a six-story bar, says he's ``not proud'' of his behavior and accepts responsibility...}

\entryitemWithDescription{\hskip 0pt{}John Sterling honored by Yankees for 36 seasons and 5,631 games as radio voice}{https://apnews.com/article/556375b9e6c669cc032c3bed90939188}{NEW YORK (AP) --- John Sterling was honored during an on-field ceremony Saturday following his retirement as a New York Yankees broadcaster for 36 seasons. Sterling, who turns 86 on July 4, was presented a jersey with No. 5,631...}

\entryitemWithDescription{\hskip 0pt{}Third temporary channel opens for vessels to Baltimore port after bridge collapse}{https://apnews.com/article/aa60b8d9a813d60e7452055ad77d1395}{BALTIMORE (AP) --- A third temporary channel for boats to enter and depart the Port of Baltimore has opened, expanding further shipping access as collapsed sections of the Francis Scott Key Bridge are salvaged before the span can...}

\entryitemWithDescription{\hskip 0pt{}David Pryor, former Arkansas governor and senator, has died at age 89}{https://apnews.com/article/a4ce049c412b4d16b616a18e7c8f9422}{LITTLE ROCK, Ark. (AP) --- Former Arkansas governor and U.S. Sen. David Pryor, a Democrat who was one of the state's most beloved political figures and remained active in public service in the state long after he left office, has died. He...}

\entryitemWithDescription{\hskip 0pt{}AP Photos: The skies fill with color at a Chinese kite festival}{https://apnews.com/article/26c3e276665728fe246f74a603807115}{WEIFANG, China (AP) --- More than 1,000 kites filled the skies of Weifang, an eastern Chinese coastal city that touts itself as the ``kite capital of the world,'' on Saturday. Locals say there is nothing that can't sail the skies of...}

\entryitemWithDescription{\hskip 0pt{}Federal officials are investigating a Rockies coach's cockpit visit during a United flight}{https://apnews.com/article/25f5cb92f7178bc327f7feff04eb404c}{DENVER (AP) --- Federal transportation officials are investigating an unauthorized inflight cockpit visit by a coach for the Colorado Rockies baseball team during a United Airlines charter flight last week from Denver to Toronto. Video...}

\entryitemWithDescription{\hskip 0pt{}Mandisa, Grammy-winning singer and `American Idol' alum, dies at 47}{https://apnews.com/article/4b7ebbcb2b9499c429362de7f7329392}{NASHVILLE, Tenn. (AP) --- Mandisa, a contemporary Christian singer who appeared on ``American Idol'' and won a Grammy for her 2013 album `Overcomer', has died. She was 47. A representative for the singer told The Associated Press that the...}

\entryitemWithDescription{\hskip 0pt{}Catholic priest resigns from Michigan church following protests over his criticism of a gay author}{https://apnews.com/article/2033306cd8937b584a6f1f1c8e70d104}{BEAL CITY, Mich. (AP) --- A Catholic priest has resigned as pastor of a church in a small central Michigan community, the result of weeks of controversy following his publicly expressed regret that a gay author had read a book to...}

\entryitemWithDescription{\hskip 0pt{}Dick Van Dyke earns historic Daytime Emmy nomination at age 98}{https://apnews.com/article/ebba73bcb43c97a9e35b355fa21aa9f6}{LOS ANGELES (AP) --- Dick Van Dyke is vying for a historic Daytime Emmy at age 98. The actor was nominated Friday as guest performer in a daytime drama series for his part as amnesiac Timothy Robicheaux on Peacock's ``Days of Our Lives.''...}

\entryitemWithDescription{\hskip 0pt{}FAA investigating after it says a flight told to cross a runway where another was starting takeoff}{https://apnews.com/article/7eb1e99fdb209d79e3607b58d5e22f1c}{ARLINGTON, Va. (AP) --- The Federal Aviation Administration will investigate after a flight at Ronald Reagan Washington National Airport was instructed to cross a runway where another flight was starting its takeoff, the agency said. A...}

\entryitemWithDescription{\hskip 0pt{}Tesla recalling more than 3,000 of its 2024 Cybertrucks due to faulty pedal}{https://apnews.com/article/ff2018b672b1109543c52b0058698499}{Tesla is recalling more than 3,000 of its newly launched 2024 Cybertrucks because of the possibility that a pedal can get stuck and cause the vehicle to accelerate unintentionally, increasing the risk of a crash. Tesla said that the...}

\entryitemWithDescription{\hskip 0pt{}Firefighters to tackle scaffolding dangling outside ruins of fire-ravaged Danish landmark}{https://apnews.com/article/8772dbcf04a1a5aa33d9739076fb9478}{COPENHAGEN, Denmark (AP) --- Firefighters in Copenhagen plan to start taking down scaffolding that is left dangling dangerously Friday outside the ruins of the Danish capital's historic Old Stock Exchange building after a fire tore...}

\entryitemWithDescription{\hskip 0pt{}More people are evacuated after the dramatic eruption of an Indonesian volcano}{https://apnews.com/article/370e2e42120c4cf3d601dc00f3f21d6a}{MANADO, Indonesia (AP) --- More people living near an erupting volcano on Indonesia's Sulawesi Island were evacuated on Friday due to the dangers of spreading ash, falling rocks, hot volcanic clouds and the possibility of a tsunami. An...}