\entryitemWithDescription{\hskip 0pt{}Target removes some LGBTQ merchandise from stores ahead of June Pride month after threats to workers}{https://apnews.com/article/4bc9de6339f86748bcb8a453d7b9acf0}{FILE - A worker collects shopping carts in the parking lot of a Target store on June 9, 2021, in Highlands Ranch, Colo. Target is removing certain items from its stores and making other changes to its LGBTQ merchandise nationwide ahead of...}

\entryitemWithDescription{\hskip 0pt{}Woman charged in drunk driving killing of bride in South Carolina seeks bond}{https://apnews.com/article/ab1773ebf130cda41856e71435cfe7d3}{This photo provided by the Charleston County Sheriff\textquotesingle s Office, in South Carolina, shows Jamie Lee Komoroski, on April 29, 2023. Komoroski is charged with reckless vehicular homicide and three counts of driving under the...}

\entryitemWithDescription{\hskip 0pt{}4-year-old child is 'OK' after being dropped from high border wall in San Diego}{https://apnews.com/article/e5de40d8856c149adf381302a9905f53}{A man gestures as he waits with others to apply for asylum between two border walls Thursday, May 11, 2023, in San Diego. Many of the hundreds of migrants between the walls that separate Tijuana, Mexico, with San Diego have been waiting...}

\entryitemWithDescription{\hskip 0pt{}Peloton the rebrand: High end exercise bike maker says it's now a health company for all}{https://apnews.com/article/ead792b81c20a5396ef518355091482a}{FILE - A Peloton bike sits on Nov. 19, 2019, in San Francisco. Peloton is undergoing a significant rebranding, moving away from its image as a luxury exercise bike provider and towards a concept that is more inclusive, according to a...}

\entryitemWithDescription{\hskip 0pt{}Recent shark attacks are worrying beach-goers, yet experts say they're very rare}{https://apnews.com/article/98a80236f0eccefc2072b009b4932485}{CORRECTS BYLINE TO PHIL MARCELO INSTEAD OF CHARLES KRUPA - FILE - A white shark swims across a sand bar off the Massachusetts coast of Cape Cod, Aug. 13, 2021. Recent shark bites in Florida and Hawaii and a suspected case in New Jersey...}

\entryitemWithDescription{\hskip 0pt{}Bills safety Damar Hamlin eases back into practice 5 months since near-death experience}{https://apnews.com/article/a9eea54dceaee4e928928a070938b880}{Buffalo Bills defensive back Damar Hamlin (3) works out during NFL football practice in Orchard Park, N.Y., Tuesday May 23, 2023. (AP Photo/Jeffrey T. Barnes) ORCHARD PARK, N.Y. (AP) --- Wearing shorts and his familiar No. 3 blue practice...}

\entryitemWithDescription{\hskip 0pt{}Ford decides to keep AM radio on 2024 models, will restore AM on two electric vehicles from 2023}{https://apnews.com/article/aec6e6405d33ff95cff3dd31bef617db}{FILE - Jim Farley, Ford president and CEO, answers questions during a news conference, Sept. 28, 2021, in Memphis, Tenn. Owners of new Ford vehicles will be able to tune in to AM radio in their cars, trucks and SUVs after all. Farley...}

\entryitemWithDescription{\hskip 0pt{}Millionaire's elaborate jail escape plan foiled, Florida sheriff says}{https://apnews.com/article/43fa095dcf05531119320c167782139f}{This photo provided by Indian River County Sheriff\textquotesingle s Office shows John Manchec. Sheriff\textquotesingle s deputies in Florida say they foiled an elaborate escape plan by Manchec, a 78-year-old, dual citizenship businessman...}

\entryitemWithDescription{\hskip 0pt{}Double amputee Everest climber pledges to work for benefit of people with disabilities}{https://apnews.com/article/9c570a3bd3752047b913147b5f0ddc39}{Hari Budha Magar, former Gurkha veteran and double amputee climber who scaled Mount Everest, greets the crowd upon arrival at the airport in Kathmandu, Nepal, Tuesday, May 23, 2023. The former Gurkha veteran had lost both his legs in...}

\entryitemWithDescription{\hskip 0pt{}Some worshippers switching congregations amid United Methodist split over LGBTQ issues}{https://apnews.com/article/44fd14d471124d23e1fd5677a8f2b1d9}{The Rev. Bill Farmer preaches to his congregation at the Grace Methodist Church Sunday, May 14, 2023, in Homosassa Springs, Fla. Farmer came out of retirement to serve as the church\textquotesingle s pastor. The group\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Court rules against Prince Harry's offer to personally pay for police protection in UK}{https://apnews.com/article/565e4a2f542f2f64cd343656324f11b0}{FILE - Britain\textquotesingle s Prince Harry arrives at the Royal Courts Of Justice in London, Thursday, March 30, 2023. A lawyer has asked a London judge to allow Prince Harry to challenge the government\textquotesingle s denial of his...}

\entryitemWithDescription{\hskip 0pt{}Wish you could tweak that text? WhatsApp is letting users edit messages}{https://apnews.com/article/2cc4f708e043d8e2f299a9edae696496}{FILE - The WhatsApp communications app is seen on a smartphone, in New York, March 10, 2017. WhatsApp is allowing users to do just that, for the first 15 minutes after they send a message. The popular chat app announced in a blog post...}

\entryitemWithDescription{\hskip 0pt{}Family of Colorado man killed by police during mental health crisis gets \$19 million settlement}{https://apnews.com/article/4c0cdfc6d54a2dc488218d7e5e186925}{Simon Glass, left, and his wife, Sally Glass, talk about the \$19-million settlement from state and local law enforcement agencies for the killing of the couple\textquotesingle s 22-year-old son, Christian, in June 2022, while he suffered...}