\entryitemWithDescription{\hskip 0pt{}Illinois enacts mandatory paid leave 'for any reason'}{https://apnews.com/article/435fabf7f5ce88d9ca9f1df692dadc2d}{Illinois Gov. J.B. Pritzker signs into law the Paid Leave For All Workers Act on Monday, March 13, 2023, in Chicago. Illinois became one of three U.S. states to require employers to offer paid time off for any reason starting in January...}

\entryitemWithDescription{\hskip 0pt{}How this little see-through fish gets its rainbow shimmer}{https://apnews.com/article/7da1460beab335cf2110ac4dee610dee}{This image provided by Qibin Zhao shows ghost catfish showing iridescence. The ghost catfish has a see-through body that flickers with rainbow colors when the light hits it. Now, scientists have cracked the case of how the fish creates...}

\entryitemWithDescription{\hskip 0pt{}Divided jury means no death penalty for NYC bike path killer}{https://apnews.com/article/64cb1dd889e6eefbc3fc23add9b4f32b}{FILE - This booking photo provided by the St. Charles County Department of Corrections in St. Charles, Mo., shows Sayfullo Saipov. A jury said Monday, March 13, 2023 it could not reach a unanimous decision on whether to impose the death...}

\entryitemWithDescription{\hskip 0pt{}Biden administration lets Ukrainians who fled war stay in US}{https://apnews.com/article/1a57fb5f59d150380a6a1f3e7a5ef093}{FILE - Ukrainian refugees play with frisbees as they wait in front of a gymnasium April 5, 2022, in Tijuana, Mexico. The Biden administration is allowing thousands of Ukrainians who fled their homeland when Russia invaded a year ago to...}

\entryitemWithDescription{\hskip 0pt{}Flood problems grow as new storm heads toward California}{https://apnews.com/article/37859295c926b976de21a236783b6bf4}{A Northern California agricultural community famous for its strawberry crop has been forced to evacuate after the Pajaro River's levee was breached by flooding from a new atmospheric river that pummeled the state. (March 11) A CalTrans...}

\entryitemWithDescription{\hskip 0pt{}Patriots plan to re-sign cornerback Jonathan Jones}{https://apnews.com/article/882a3e2dc82dab146becb31c99a374e0}{FILE - New England Patriots cornerback Jonathan Jones (31) is shown prior to an NFL football game, Sunday, Jan. 1, 2023, in Foxborough, Mass. The Patriots have taken a step toward maintaining some stability in their secondary, agreeing to...}

\entryitemWithDescription{\hskip 0pt{}After two historic US bank failures, here's what comes next}{https://apnews.com/article/a04875a164165b50e971ff4576bf4e27}{FILE- The seal of the Board of Governors of the United States Federal Reserve System is displayed in the ground at the Marriner S. Eccles Federal Reserve Board Building in Washington, Feb. 5, 2018. Facing the prospect of a third financial...}

\entryitemWithDescription{\hskip 0pt{}School pulls test question equating politics to race, gender}{https://apnews.com/article/8b02bb533a12f613b15691e842fbc7f3}{FILE - This March 4, 2019 file photo shows Fairfax County Public Schools in Merrifield, Va. Virginia\textquotesingle s largest school system is removing a test question given to a college-level social studies class that equated liberals...}

\entryitemWithDescription{\hskip 0pt{}Imprisoned Navalny learns documentary about him wins Oscar}{https://apnews.com/article/b230e110e101808a48988cd9f2540a79}{Daniel Roher and the members of the crew from "Navalny" accept the award for best documentary feature film at the Oscars on Sunday, March 12, 2023, at the Dolby Theatre in Los Angeles. (AP Photo/Chris Pizzello) TALLINN, Estonia (AP...}

\entryitemWithDescription{\hskip 0pt{}South Carolina women cap wire-to-wire No. 1 run in AP Top 25}{https://apnews.com/article/af67a7b90a90aa49d3ba75b901bdc38e}{South Carolina\textquotesingle s Aliyah Boston holds up her piece of the the net after defeating Tennessee 74-58 to win the championship game of the Southeastern Conference women\textquotesingle s tournament in Greenville, S.C., Sunday...}

\entryitemWithDescription{\hskip 0pt{}New England, upstate New York, bracing for winter storm}{https://apnews.com/article/d3b2914f17a98328836de108163b9932}{Parts of the Northeast were bracing for a powerful winter storm that could dump heavy, wet snow and unleash strong winds, knocking out power to hundreds of thousands of people. The National Weather Service says the storm is expected to...}

\entryitemWithDescription{\hskip 0pt{}Gun laws, campus policies perplex college sports programs}{https://apnews.com/article/05a4962cd59264a997b9cdfb5256763f}{FILE - People work to remove flowers from the memorial at the Rock in honor of three students killed at Michigan State University on March 2, 2023, in East Lansing, Mich. At Michigan State, sports were suspended after gun violence on...}

\entryitemWithDescription{\hskip 0pt{}Alabama, Houston top final AP Top 25 ahead of March Madness}{https://apnews.com/article/42106cbd2916cdcd0513ed50a2ddd46d}{Alabama players celebrate on the court after an NCAA college basketball game against Texas A\&M in the finals of the Southeastern Conference Tournament, Sunday, March 12, 2023, in Nashville, Tenn. (AP Photo/John Amis) The overall No. 1...}