\entryitemWithDescription{\hskip 0pt{}Review: 'Cocaine Bear,' 100\% pure, uncut junk with no high}{https://apnews.com/article/a714bb5e5762d84d93996f0fc18d12dc}{This image released by Universal Pictures shows Keri Russell in a scene from "Cocaine Bear," directed by Elizabeth Banks. (Pat Redmond/Universal Pictures via AP) Yes, there\textquotesingle s a giant bear and, yes, it does a ton of coke...}

\entryitemWithDescription{\hskip 0pt{}Trans youth care ban headed to Tennessee governor's desk}{https://apnews.com/article/181952f6bd94a8e8c0a35be81afe00ad}{Advocates gather for a rally at the state Capitol complex in Nashville, Tenn., to oppose a series of bills that target the LGBTQ community, Tuesday, Feb. 14, 2023. Lawmakers are considering efforts to ban gender-affirming care for...}

\entryitemWithDescription{\hskip 0pt{}Rihanna will sing 'Lift Me Up' at the Oscars next month}{https://apnews.com/article/8f0080a8701ed56fd7f5995bb15995da}{Rihanna performs during the halftime show at the NFL Super Bowl 57 football game between the Kansas City Chiefs and the Philadelphia Eagles, Sunday, Feb. 12, 2023, in Glendale, Ariz. (AP Photo/Matt Slocum) LOS ANGELES (AP) --- Rihanna...}

\entryitemWithDescription{\hskip 0pt{}For donors, wartime Ukraine aid creates blurry ethical line}{https://apnews.com/article/a14805645c3135bdff261dba7a2ec8cc}{Volunteers with Razom for Ukraine, a New York-based nonprofit, load oxygen tanks into a container as they pack firefighting and medical donations for shipment to Ukraine, Wednesday, Feb. 8, 2023, in Woodbridge Township, N.J. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}Israel's rightward shift is straining its ties with US Jews}{https://apnews.com/article/c19f1de03e19428958181ebd2dcb1461}{FILE - An image of the U.S. flag is projected on the walls of Jerusalem\textquotesingle s Old City in honor of President Joe Biden\textquotesingle s visit to Jerusalem, Wednesday, July 13, 2022. Several U.S. Jewish leaders are sounding...}

\entryitemWithDescription{\hskip 0pt{}US ending extra help for groceries that started during COVID}{https://apnews.com/article/8a51237e17490ba1886a4e550c67f4a8}{Jaqueline Benitez pushes her cart down an aisle as she shops for groceries at a supermarket in Bellflower, Calif., on Monday, Feb. 13, 2023. Benitez, 21, who works as a preschool teacher, depends on California\textquotesingle s SNAP...}

\entryitemWithDescription{\hskip 0pt{}Workplace is the heart of thrilling series 'The Consultant'}{https://apnews.com/article/5a48cbd45431c8e475099e3183cd1ba0}{This image released by Amazon shows Christoph Waltz in a scene from "The Consultant." (Amazon via AP) NEW YORK (AP) --- Think your boss is bad? The one in the new TV series ``The Consultant'' phones his workers in the middle of the night...}

\entryitemWithDescription{\hskip 0pt{}On stand, Alex Murdaugh denies killings but admits lying}{https://apnews.com/article/7c491a9fbb295bd6b6766ec1b65f8905}{Alex Murdaugh swears to tell the truth before he takes the stand during his trial for murder at the Colleton County Courthouse on Thursday, Feb. 23, 2023 in Walterboro, S.C. (Joshua Boucher/The State via AP, Pool) Disgraced South Carolina...}

\entryitemWithDescription{\hskip 0pt{}Pregnant Russians flock to Argentina seeking new passports}{https://apnews.com/article/968af37c4ceabfc75602140117fbb1a4}{Russian nationals Alla Prigolovkina and her husband Andrei Ushakov, their Argentine-born son Lev Andres and their dogs Santa and Cometa, visit a park in Mendoza, Argentina, Tuesday, Feb. 14, 2023. In spite of the language barrier and the...}

\entryitemWithDescription{\hskip 0pt{}Dr. Seuss' 'How the Grinch stole Christmas!' gets a sequel}{https://apnews.com/article/5524eaf8396afaa8db26b7390c1b285e}{A recent undated image provided by Dr. Seuss Enterprises shows a page from the new book "How the Grinch Lost Christmas!" Seuss Enterprises, the company that owns the Dr. Seuss intellectual property, is releasing the sequel to the iconic...}

\entryitemWithDescription{\hskip 0pt{}US revises down last quarter's economic growth to 2.7\% rate}{https://apnews.com/article/cdc78b4b47af71113a2e97784fd60bdd}{FILE - Used car are on display on a lot in Wexford, Pa., Thursday, Sept. 29, 2022. The Commerce Department releases its revised estimate of how the U.S. economy fared in the fourth quarter on Thursday, Feb. 23, 2023. (AP Photo/Gene J...}

\entryitemWithDescription{\hskip 0pt{}Train crew had little warning before Ohio wreck, probe finds}{https://apnews.com/article/64908a6416662b5866809387f210aee5}{Transportation Secretary Pete Buttigieg, left, and Tristan Brown, deputy administrator of the Pipeline and Hazardous Materials Safety Administration, crouch down to look at part of a burned traincar, Thursday, Feb. 23, 2023, in East...}

\entryitemWithDescription{\hskip 0pt{}Trump investigation: Could grand juror's words tank charges?}{https://apnews.com/article/9938c36b008aaeb7a7b1502b09762bbd}{FILE - Former President Donald Trump speaks during the New Hampshire Republican State Committee 2023 annual meeting, Jan. 28, 2023, in Salem, N.H. Trump's lawyers in Georgia are criticizing the Fulton County investigation into potential...}