\entryitemWithDescription{\hskip 0pt{}Illegal tunnel under a synagogue in NYC is 60 feet long and destabilized nearby buildings, city says}{https://apnews.com/article/e133a0d771b61e1cc86b015157e5f78b}{NEW YORK (AP) --- The illegal tunnel discovered under a historic Brooklyn synagogue compromised the stability of several structures surrounding the religious complex, prompting an order to vacate as well as citations against its owners...}

\entryitemWithDescription{\hskip 0pt{}President Joe Biden's record age, 81, is an `asset,' first lady Jill Biden says}{https://apnews.com/article/d99f320b78dd63c60f2617979f776542}{WASHINGTON (AP) --- First lady Jill Biden says her husband's age is an ``asset,'' as President Joe Biden --- at 81 already the oldest American leader in history --- faces persistent questions from voters about his decision to seek another...}

\entryitemWithDescription{\hskip 0pt{}Lisa Marie Presley's posthumous memoir will be published in October}{https://apnews.com/article/31d9326fb4b113a4b00071f3de78558f}{NEW YORK (AP) --- A memoir that Lisa Marie Presley had been working on at the time of her death will be published this fall. The book, currently untitled, was completed with the help of actor Riley Keough, the eldest of Presley's four...}

\entryitemWithDescription{\hskip 0pt{}Vatican unveils plans for restoring Bernini's canopy in St. Peter's Basilica}{https://apnews.com/article/8b59dc9317bbff9214943c5438aa9f57}{VATICAN CITY (AP) --- The Vatican on Thursday unveiled plans for a yearlong restoration of the monumental baldacchino, or canopy, over the main altar of St. Peter's Basilica, pledging to complete the work on Bernini's masterpiece before...}

\entryitemWithDescription{\hskip 0pt{}Rapper G Herbo could be sentenced to more than a year in jail in fraud plot}{https://apnews.com/article/2d433f359b32efae901090a70e5fa9bf}{The rapper G Herbo could face just over a year in jail after pleading guilty to his role in a scheme that used stolen credit card information to pay for an opulent lifestyle including private jets and designer puppies. Under a deal with...}

\entryitemWithDescription{\hskip 0pt{}Alabama's Nick Saban retires after 7 national titles, most in major college football history}{https://apnews.com/article/ebb46230ca171dd6f310ff76e403fd23}{Nick Saban's coaching reign has come to an end. His dominance over college football, however, will forever linger in lore. Saban, who won seven national championships --- more than any major college football coach --- and turned Alabama...}

\entryitemWithDescription{\hskip 0pt{}Pat McAfee announces Aaron Rodgers' appearances are over for the rest of this NFL season}{https://apnews.com/article/299aad4008cff8434db5b8f3cf23fa3a}{Aaron Rodgers' Tuesday appearances on ``The Pat McAfee Show'' are over for the rest of this NFL season. Or possibly longer. McAfee announced at the beginning of his Wednesday show on ESPN that his fourth season of doing a weekly segment...}

\entryitemWithDescription{\hskip 0pt{}Kentucky Derby purse raised to \$5 million for 150th race in May}{https://apnews.com/article/376dc4a0285671994839e189db3b1b61}{LOUISVILLE, Ky. (AP) --- The Kentucky Derby purse has been raised to \$5 million for the 150th edition in May. The increase of \$2 million was announced Wednesday by Churchill Downs. The 1 1/4-mile race will be May 4. This year's winner...}

\entryitemWithDescription{\hskip 0pt{}Alaska Airlines cancels flights on certain Boeing planes through Saturday for mandatory inspections}{https://apnews.com/article/ebaccdbc28a38ccfea396840ae71ec38}{Alaska Airlines is canceling through Saturday all flights on Boeing 737 Max 9 planes like the one that suffered an in-flight blowout of a fuselage panel last week as it waits for new instructions from Boeing and federal officials on how...}

\entryitemWithDescription{\hskip 0pt{}Police investigation finds Colorado U.S. Rep. Lauren Boebert didn't punch ex-husband as he claimed}{https://apnews.com/article/ed3ba1a94e6dba08bf67f1d5d54ad9b3}{DENVER (AP) --- U.S. Rep. Lauren Boebert was cleared on Wednesday of domestic violence allegations after her ex-husband recanted his claim that she punched him during an altercation in a restaurant where they'd gone to try to get on...}

\entryitemWithDescription{\hskip 0pt{}SAG Awards 2024: See the complete list of nominees}{https://apnews.com/article/54ca44547de63fe460c7272a1d3e17c5}{LOS ANGELES (AP) --- Nominations for the 30th annual Screen Actors Guild Awards, which will be handed out on Feb. 24 in Los Angeles and shown live on Netflix: MOVIE ENSEMBLE ``American Fiction''; ``Barbie''; ``The Color Purple''; ``...}

\entryitemWithDescription{\hskip 0pt{}The largest great ape to ever live went extinct because of climate change, says new study}{https://apnews.com/article/8b801514b7e58d08c54c0bbcfbc2f27f}{WASHINGTON (AP) --- An ancient species of great ape was likely driven to extinction when climate change put their favorite fruits out of reach during dry seasons, scientists reported Wednesday. The species Gigantopithecus blacki, which...}

\entryitemWithDescription{\hskip 0pt{}ESPN's early season baseball schedule will be the Sho Show, featuring Shohei Ohtani and Dodgers}{https://apnews.com/article/35d2b806142d7390579d3e51d3e0c5b3}{BRISTOL, Conn. (AP) --- ESPN's early season baseball schedule will be the Sho Show. Shohei Ohtani and the Los Angeles Dodgers will be featured on two of ESPN's first three ``Sunday Night Baseball'' telecasts this season. The Dodgers'...}