\entryitemWithDescription{\hskip 0pt{}Joint Base Andrews on lockdown after armed person reported}{https://apnews.com/article/7a6f438c8ef35a886c7f7da5f3121b3d}{FILE - The sign for Joint Base Andrews is seen on March 26, 2021, at Andrews Air Force Base, Md. Joint Base Andrews has been locked down for reports of a man carrying an ``assault-style'' rifle on Thursday, March 30, 2023, authorities...}

\entryitemWithDescription{\hskip 0pt{}Cubs' Marcus Stroman commits MLB's 1st pitch-clock violation}{https://apnews.com/article/520024261f330e6af4c595f6cbf7cc2d}{Chicago Cubs starting pitcher Marcus Stroman throws during the first inning of a baseball game against the Milwaukee Brewers Thursday, March 30, 2023, in Chicago. (AP Photo/Erin Hooley) Major League Baseball will institute rule changes in...}

\entryitemWithDescription{\hskip 0pt{}FACT FOCUS: No 'incredible rise' in transgender shooters}{https://apnews.com/article/cd62492d066d41e820c138256570978c}{A young girl places an item at a growing memorial,Tuesday, March 28, 2023, in Nashville, at an entry to Covenant School for the victims of Monday\textquotesingle{} shooting. (AP Photo/John Amis) Moments after the assailant who killed six...}

\entryitemWithDescription{\hskip 0pt{}Has T. rex lost its bite? Menacing snarl may be wrong}{https://apnews.com/article/53d9cdf709d29bf3c687bbe4737be79f}{FILE - Stan, one of the largest and most complete Tyrannosaurus rex fossil discovered, is on display, Tuesday, Sept. 15, 2020, at Christie\textquotesingle s in New York. The teeth on T. rex and other big theropods were likely covered by...}

\entryitemWithDescription{\hskip 0pt{}Gun injuries in US surged during pandemic, CDC study shows}{https://apnews.com/article/308741db0a1130d79c601ec966ecf542}{FILE - The owner of a shooting range, prepares to load bullets in his 9mm semi-automatic handgun for a demonstration, Thursday, June 23, 2022, in New York. A government study released on Thursday, March 30, 2023, highlights just how...}

\entryitemWithDescription{\hskip 0pt{}US: Russia seeks arms-for-food deal with North Korea}{https://apnews.com/article/87af089d664ebbdad63ced526e3a6860}{National Security Council spokesman John Kirby speaks during a press briefing at the White House, Wednesday, March 29, 2023, in Washington. (AP Photo/Patrick Semansky) WASHINGTON (AP) --- The White House on Thursday said it has new...}

\entryitemWithDescription{\hskip 0pt{}Canada mass shooting inquiry identifies many police failings}{https://apnews.com/article/51cdd7e5a57849e9dd7fb96b7969f773}{FILE - A memorial pays tribute to Royal Canadian Mounted Police Constable Heidi Stevenson, a mother of two and a 23-year veteran of the force, along the highway in Shubenacadie, Nova Scotia, on Tuesday, April 21, 2020. A public inquiry...}

\entryitemWithDescription{\hskip 0pt{}Judge's ruling undercuts US health law's preventive care}{https://apnews.com/article/aa57fa6fd782e2170bc80210fd00065b}{FILE - The healthcare.gov website is seen on Dec. 14, 2021, in Fort Washington, Md. A federal judge in Texas who previously ruled to dismantle the Affordable Care Act struck down a narrower but key part of the nation\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Used car prices are surging. Here's why you should buy now}{https://apnews.com/article/522266dc94e089859f6eb393a4a786e1}{Carol Rice stands with her recently-purchased 2003 Ford Ranger Wednesday, March 15, 2023, in Shawnee, Kan. Rice\textquotesingle s timing to buy the truck was ideal, taking advantage of a recent dip in used car prices which now appear to...}

\entryitemWithDescription{\hskip 0pt{}CNN preaches patience as ratings tank during turnaround}{https://apnews.com/article/584ea2b45819d2cc416006d7bd8b77e8}{FILE - The CNN logo is displayed at the entrance to the CNN Center in Atlanta on Feb. 2, 2022. Cable news ratings are down across the board compared to 2022, when Russia\textquotesingle s invasion of Ukraine was in the news. CNN...}

\entryitemWithDescription{\hskip 0pt{}Evacuations end after fiery Minnesota ethanol derailment}{https://apnews.com/article/73cc3e80f616070806f8f8b35191a616}{A BNSF train carrying ethanol and corn syrup derailed and caught fire in Raymond, Minn., Thursday, March 30, 2023. BNSF officials said 22 cars derailed, including about 10 carrying ethanol, and the track remains blocked, but that no...}

\entryitemWithDescription{\hskip 0pt{}Bolsonaro returns to Brazil after 3-month stint in Florida}{https://apnews.com/article/a91b1253ac856c64bdc85bdfb4418dd8}{Brazil\textquotesingle s former President Jair Bolsonaro waves to supporters at the Liberal Party\textquotesingle s headquarters in Brasilia, Brazil, Thursday, March 30, 2023. Bolsonaro arrived back in Brazil on Thursday after a three...}

\entryitemWithDescription{\hskip 0pt{}Vatican rejects doctrine that fueled centuries of colonialism}{https://apnews.com/article/062e39ce5f7594a81bb80d0417b3f902}{FILE - Pope Francis arrives for a pilgrimage at the Lac Saint Anne, Canada, on July 26, 2022. The Vatican on Thursday, March 30, 2023, responded to Indigenous demands and formally repudiated the ``Doctrine of Discovery,'' the theories...}