\entryitemWithDescription{\hskip 0pt{}Google has the next move as Microsoft embraces OpenAI buzz}{https://apnews.com/article/a7f6f44fdd53730e45daa611555c8c23}{FILE - Zoubin Ghahramani, vice president of research at Google, speaks at the Google AI@ event on Wednesday, Nov. 2, 2022, in New York. Google has been cautious about who gets to play with its AI advancements despite growing pressure for...}

\entryitemWithDescription{\hskip 0pt{}Brady's unprecedented career filled with highlight moments}{https://apnews.com/article/64c660906bfdd828c9cf69e94cfefcb7}{FILE - In this Sept. 30, 2001 file photo, New England Patriots quarterback Tom Brady (12) passes during Brady\textquotesingle s first start of an NFL football game against the Indianapolis Colts in Foxborough, Mass. Brady, who won a...}

\entryitemWithDescription{\hskip 0pt{}How to make a mummy: Ancient Egyptian workshop has new clues}{https://apnews.com/article/68735c4de698a1662897910e8879e283}{This illustration provided by Nikola Nevenov in January 2023 depicts a priest during an embalming process in an underground chamber in Saqqara, Egypt. For thousands of years, ancient Egyptians mummified their dead to help them reach...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé announces much anticipated 'Renaissance' world tour}{https://apnews.com/article/86ec8ebe4422a2ae37b2feadf4bb5c1f}{FILE - Beyoncé appears at the 63rd annual Grammy Awards in Los Angeles on March 14, 2021. (AP Photo/Chris Pizzello, File) Beyoncé is taking her ``Renaissance'' global --- the superstar will start a world tour in Sweden in May with stops...}

\entryitemWithDescription{\hskip 0pt{}Pat Riley: Kareem never had potential, 'only greatness'}{https://apnews.com/article/e89167d4354de30b91a860bebcdef7d1}{FILE -Kareem Abdul-Jabbar reacts during the first half of Game 4 of basketball\textquotesingle s NBA Finals between the Milwaukee Bucks and the Phoenix Suns, Wednesday, July 14, 2021, in Milwaukee. Kareem Abdul-Jabbar\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Biden lawyer: FBI finds no classified docs at beach house}{https://apnews.com/article/383d3eababa179ad5d7b0c2805c1b192}{FILE - U.S. Secret Service agents are seen in front of Joe Biden\textquotesingle s Rehoboth Beach, Del., home on Jan. 12, 2021. The FBI is conducting a planned search of President Joe Biden's Rehoboth Beach, Delaware home as part of its...}

\entryitemWithDescription{\hskip 0pt{}'Dr. Phil' talk show to end daytime TV run after 21 years}{https://apnews.com/article/8ac4662100fafdb773cc6e7d4ade1dc4}{This Sept. 22, 2015 image released by CBS Media Ventures shows Oprah Winfrey, left, and Dr. Phil McGraw on the set of the "Dr. Phil." McGraw says he\textquotesingle ll stop making new episodes of his daytime TV show after 21 years this...}

\entryitemWithDescription{\hskip 0pt{}Black history class revised by College Board amid criticism}{https://apnews.com/article/722fb29dbaa13dd5c42d70c5129df48e}{Emmitt Glynn teaches AP African American studies to a group of Baton Rouge Magnet High School students on Monday, Jan. 30, 2023 in Baton Rouge, La. Baton Rouge Magnet High School in Louisiana is one of 60 schools around the country...}

\entryitemWithDescription{\hskip 0pt{}Tom Brady retires at 45, insisting this time it's 'for good'}{https://apnews.com/article/3ac2e55d0880672d330e8ff3d4318367}{FILE - New England Patriots\textquotesingle{} Tom Brady raises the Vince Lombardi Trophy after defeating the Atlanta Falcons in overtime at the NFL Super Bowl 51 football game Sunday, Feb. 5, 2017, in Houston. Brady, the seven-time Super...}

\entryitemWithDescription{\hskip 0pt{}Missy, Willie and George Michael among Rock Hall nominees}{https://apnews.com/article/3597e8fec2477f87f2f9cf719fdf4d35}{This combination of photos shows Missy Elliott, George Michael and Willie Nelson, who are among this year\textquotesingle s nominees for 2023 induction into the Rock \& Roll Hall of Fame. (AP Photo) NEW YORK (AP) --- Missy Elliott, Willie...}

\entryitemWithDescription{\hskip 0pt{}US winter storm causes 3rd day of dangerous, icy conditions}{https://apnews.com/article/9699c579e14b232af86401bf84f41192}{A pair of pedestrians cross a road as drivers make their way down slush and icy road conditions, Wednesday, Feb. 1, 2023, in Dallas. (AP Photo/Tony Gutierrez) OKLAHOMA CITY (AP) --- A deadly storm system lashed a large swath of the...}

\entryitemWithDescription{\hskip 0pt{}Russia said eyeing eastern Ukraine push; Kyiv targets graft}{https://apnews.com/article/4b87170d155cddb69849e3100049454e}{A man passes by an artwork by famous street artist TvBoy created on an older graffiti depicting a Ukrainian soldier firing an anti-tank missile. Writing on the missile reads: "The goal is one'', in Kyiv, Ukraine, Wednesday, Feb. 1, 2023...}

\entryitemWithDescription{\hskip 0pt{}Anti-Asian hate 'runs the gamut,' racist Yelp reviews show}{https://apnews.com/article/7918890755b00bd03c7996628597d764}{FILE- The Yelp app is seen on an iPad in Baltimore on March 19, 2018. There\textquotesingle s been a sharp increase in the number of hate-filled business reviews spotted by Yelp\textquotesingle s content moderators. (AP Photo/Patrick...}