\entryitemWithDescription{\hskip 0pt{}Cuomo could have run again for NY governor, but declined for family reasons, former top aide writes}{https://apnews.com/article/727425013c876ab97e4140fe922f5f99}{ALBANY, N.Y. (AP) --- Former New York Gov. Andrew Cuomo, who resigned after multiple women accused him of sexual harassment, discussed running to reclaim the office in 2022 but decided against it because he didn't want to subject his...}

\entryitemWithDescription{\hskip 0pt{}35 years later, Georgia authorities identify woman whose body was found in a dumpster}{https://apnews.com/article/e3dc410d90d63c4052e63998f6e135f2}{MILLEN, Ga. (AP) --- A body found wrapped in plastic inside a Georgia dumpster 35 years ago has been identified as that of a South Korean woman, officials announced Monday. The Georgia Bureau of Investigation said they used DNA analysis...}

\entryitemWithDescription{\hskip 0pt{}Theft of 2 million dimes from truckload of coins from US Mint leaves four facing federal charges}{https://apnews.com/article/c141bc2e0f974dc3c8c12ddaf809c12a}{PHILADELPHIA (AP) --- Federal authorities have released more details and unsealed charges in the theft of more than 2 million dimes earlier this year from a tractor-trailer that had picked up the coins from the U.S. Mint in Philadelphia...}

\entryitemWithDescription{\hskip 0pt{}Exhibits and collectors editions mark 400th anniversary of Shakespeare's First Folio}{https://apnews.com/article/fa2e28a06a15fd649c2d905cd148b8db}{NEW YORK (AP) --- On the 400th anniversary of Shakespeare's First Folio, rare originals are being displayed and publishers are offering collectors editions of Shakespeare's plays, including one that sells for \$1,500. Scholars believe...}

\entryitemWithDescription{\hskip 0pt{}University of Michigan slithers toward history with massive acquisition of jarred snake specimens}{https://apnews.com/article/9cdf0ce994042fe969ea6d5dc42c15c1}{ANN ARBOR, Mich. (AP) --- Greg Schneider scans rows upon rows of liquid-filled glass jars containing coiled snake specimens, just a portion of the University of Michigan Museum of Zoology's reptile and amphibian collection believed to be...}

\entryitemWithDescription{\hskip 0pt{}Eovaldi remains perfect, Rangers slug their way to 9-2 win over Astros to force Game 7 in ALCS}{https://apnews.com/article/0df6aba847e52ab62d8ba3572eb1e007}{HOUSTON (AP) --- One more Texas-sized matchup to finally settle this Lone Star State showdown. Nathan Eovaldi remained perfect this postseason, and Mitch Garver and Jonah Heim homered early before a ninth-inning grand slam by Adolis Garcí...}

\entryitemWithDescription{\hskip 0pt{}Michigan State suspends employee involved with allowing Hitler's image to be shown on videoboards}{https://apnews.com/article/23b8e62c44cf42c3caad30c908692632}{EAST LANSING, Mich. (AP) --- Michigan State athletic director Alan Haller said he has suspended an employee involved in allowing Adolf Hitler's image to be shown on videoboards before playing No. 2 Michigan. The employee, who was not...}

\entryitemWithDescription{\hskip 0pt{}Swift bests Scorsese at box office, but `Killers of the Flower Moon' opens strongly}{https://apnews.com/article/804edf3b87d51624a8c51f377553611e}{NEW YORK (AP) --- In a movie match-up almost as unlikely as ``Barbie'' and ``Oppenheimer,'' Martin Scorsese took on Taylor Swift in cinemas over the weekend. And while the box office belonged for a second time to ``Taylor Swift: The Eras...}

\entryitemWithDescription{\hskip 0pt{}New Netflix thriller tackling theme of justice in Nigeria is a global hit and a boon for Nollywood}{https://apnews.com/article/1350bd34e7529c7ab92670edaea904a1}{ABUJA, Nigeria (AP) --- A Nigerian action thriller that tells a gripping story of corruption and police brutality in Africa's most populous country has reached record viewership numbers on Netflix charts globally. It's a reminder of the...}

\entryitemWithDescription{\hskip 0pt{}Philadelphia Orchestra and musicians agree to 3-year labor deal with 15.8\% salary increase}{https://apnews.com/article/a3a960544a5e9ac8b58e9160cef8347b}{PHILADELPHIA (AP) --- Musicians of the Philadelphia Orchestra and the Philadelphia Orchestra Association have ratified a collective bargaining agreement calling for minimum salaries to increase by 15.8\% over three years. The deal...}

\entryitemWithDescription{\hskip 0pt{}What's in a game? `Dear England' probes the nation through the lens of its soccer team}{https://apnews.com/article/81b3181e9149661c3a17c98535d3b4fa}{LONDON (AP) --- Outside of families, few relationships are as intense as those between sports teams and their fans. In the case of England's bond with its national soccer team, it's not always been healthy. James Graham's play ``Dear...}

\entryitemWithDescription{\hskip 0pt{}Illinois government employee fired after posting antisemitic comments on social media}{https://apnews.com/article/42b9fb4dd66b20e903ca9b8c4515c327}{SPRINGFIELD, Ill. (AP) --- An employee with the Illinois comptroller's office has been fired after she posted vulgar antisemitic comments on social media during an exchange about the latest Israel-Hamas war. A spokesperson for Illinois...}

\entryitemWithDescription{\hskip 0pt{}Italian Premier Meloni announces separation from partner, father of daughter}{https://apnews.com/article/5eeaa4ae2596c5c9c36df20b16fa4614}{ROME (AP) --- Italian Premier Giorgia Meloni announced Friday that she is separating from her partner and the father of their young daughter after nearly a decade together. In a statement posted on social media, Meloni said her...}