\entryitemWithDescription{\hskip 0pt{}New York City owl Flaco was exposed to pigeon virus and rat poison before death, tests show}{https://apnews.com/article/470d3382d0d5b13ea8ba381261b5224e}{New York City's celebrity owl Flaco was suffering from a severe pigeon-borne illness and high levels of rat poison when he crashed into a building and died last month, officials at the Bronx Zoo said Monday. The Eurasian eagle-owl was...}

\entryitemWithDescription{\hskip 0pt{}Baby gorilla cuddled by mother at London Zoo remains nameless}{https://apnews.com/article/d62f97f14098502ec4474e08aaccfdfc}{LONDON (AP) --- The newest endangered baby gorilla at the London Zoo is more than six weeks old but doesn't yet have a name. Zookeepers aren't even sure if it's a male or female because they haven't been able to get close enough to...}

\entryitemWithDescription{\hskip 0pt{}MLB pitcher Dennis Eckersley's daughter reunited with her son after giving birth in woods in 2022}{https://apnews.com/article/26300151d48273a7f7cbce26206350bd}{CONCORD, N.H. (AP) --- The daughter of MLB Hall of Fame pitcher Dennis Eckersley has been reunited with her son as she awaits trial on reckless conduct and other charges after giving birth more than a year ago in a tent in subfreezing...}

\entryitemWithDescription{\hskip 0pt{}A London court will rule on Tuesday whether WikiLeaks' Assange can challenge extradition to the US}{https://apnews.com/article/ed71edbde7f2ecf1e01eb66b4b0d4f43}{LONDON (AP) --- A London court is due to rule whether WikiLeaks founder Julian Assange gets one final appeal in England to challenge extradition to the United States on espionage charges. Two judges are scheduled to issue a judgment...}

\entryitemWithDescription{\hskip 0pt{}The IRS has 940,000 unclaimed tax refunds from 2020 that are about to expire. Is one of them yours?}{https://apnews.com/article/7d448039c59df67f054806d00110ff18}{WASHINGTON (AP) --- The IRS is warning taxpayers that they may be leaving more than \$1 billion on the table. The federal tax collector said Monday that roughly 940,000 people in the U.S. have until May 17 to submit tax returns for...}

\entryitemWithDescription{\hskip 0pt{}Nearly \$2 billion is up for grabs as Mega Millions and Powerball jackpots soar}{https://apnews.com/article/5e77fc75273d31b6991bbd3c8614d3f6}{The stars have aligned in the lottery universe like never before, with two jackpots totaling nearly \$2 billion. With an estimated \$1.1 billion Mega Millions prize and an estimated \$800 million Powerball jackpot, it's the first time the...}

\entryitemWithDescription{\hskip 0pt{}Trump's social media company to start trading on the Nasdaq on Tuesday}{https://apnews.com/article/12187a6de91561798a68780ed48cf511}{Trump Media \& Technology Group, whose flagship product is social networking site Truth Social, will begin trading on the Nasdaq stock market on Tuesday. Shareholders of Digital World Acquisition Corp., a publicly traded shell company...}

\entryitemWithDescription{\hskip 0pt{}Bryan Cranston leading face of Major League Baseball's promotional campaign}{https://apnews.com/article/0ea78e4f48f450b9f481f9f6046aef4d}{NEW YORK (AP) --- Emmy, Tony and Olivier Award winner Bryan Cranston is a leading face of Major League Baseball's promotional campaign ahead of opening day for the second straight season, recording a video at Dodger Stadium highlighting...}

\entryitemWithDescription{\hskip 0pt{}Vinícius still a target for racial abuse ahead of Spain's `One Skin' game against Brazil}{https://apnews.com/article/4e7cb8d275e2fe840146dcbe0ddc03c2}{MADRID (AP) --- Vinícius Júnior clenched his right fist and raised it high above his head after scoring at Mestalla Stadium, posing for a moment to make sure everyone noticed. The symbolic gesture in early March came nearly a year after...}

\entryitemWithDescription{\hskip 0pt{}Maple syrup from New Jersey: You got a problem with that?}{https://apnews.com/article/6fe698eea78c598d9cc69c05383e82d6}{GALLOWAY TOWNSHIP, N.J. (AP) --- Welcome to New Jersey, known around the world for Tony Soprano, Turnpike tolls, chemical plants, and ... maple syrup? If a university in the southern part of the state has its way, the sticky sweet brown...}

\entryitemWithDescription{\hskip 0pt{}NBC's Chuck Todd lays into his network for hiring former RNC chief Ronna McDaniel as an analyst}{https://apnews.com/article/683aa560f0824725023dacde0f504ad6}{NEW YORK (AP) --- Former NBC News ``Meet the Press'' moderator Chuck Todd criticized his network Sunday for hiring former Republican National Committee head Ronna McDaniel as a paid contributor, saying on the air that many NBC journalists...}

\entryitemWithDescription{\hskip 0pt{}A man who survived a California mountain lion attack that killed his brother is expected to recover}{https://apnews.com/article/f253eeea5a1dc56228384a03cb18ba23}{GEORGETOWN, Calif. (AP) --- An 18-year-old Northern California man who survived a mountain lion attack that killed his older brother is expected to recover, authorities said Sunday. The 21-year-old's death on Saturday in a remote area...}

\entryitemWithDescription{\hskip 0pt{}`Ghostbusters: Frozen Empire'' is No. 1 with \$45.2M, Sydney Sweeney's `Immaculate' lands in fourth}{https://apnews.com/article/121f7363fa151454b86f91c612b9c671}{NEW YORK (AP) --- Ghost busting is still a good business. ``Ghostbusters: Frozen Empire'' collected \$45.2 million in ticket sales over the weekend, according to studio estimates Sunday, handing Sony Pictures the studio's first No. 1 film...}