\entryitemWithDescription{\hskip 0pt{}Globes analysis: Let the awards season of Barbenheimer begin}{https://apnews.com/article/2bb79c6f096930366663f56e25ea106d}{NEW YORK (AP) --- Early honors in Hollywood's unfurling awards season have gone to films like Celine Song's tender relationship drama ``Past Lives,'' Jonathan Glazer's piercing Holocaust film ``The Zone of Interest'' and Martin Scorsese's...}

\entryitemWithDescription{\hskip 0pt{}What did you Google in 2023? Here are the top internet searches of the year}{https://apnews.com/article/9f6b2bdf38a26bef731fb7f62131ccc4}{NEW YORK (AP) --- Your Google search history for 2023 has arrived. Well, actually, the world's. On Monday, the California-based tech giant released its ``Year in Search,'' a roundup of 2023's top global queries, ranging from unforgettable...}

\entryitemWithDescription{\hskip 0pt{}BTS members RM and V start compulsory military service in South Korea}{https://apnews.com/article/aac9d886a2fbae90712bd21c42cee299}{SEOUL, South Korea (AP) --- Singers RM and V of the K-pop band BTS began their mandatory military duties under South Korean law, their management agency announced Monday. This came a day before two of their bandmates, Jimin and Jung Kook...}

\entryitemWithDescription{\hskip 0pt{}Mariah Carey's 1994 hit `All I Want for Christmas is You' still dominates the holiday charts}{https://apnews.com/article/346d94b58c268edb5a7fcb3c912e982c}{NEW YORK (AP) --- If anything about Mariah Carey's ``All I Want for Christmas is You'' annoys you, best to avoid shopping malls now. Or the radio. Maybe music altogether, for that matter. Her 1994 carol dominates holiday music like...}

\entryitemWithDescription{\hskip 0pt{}`Barbie' leads Golden Globe nominations with 9, followed closely by `Oppenheimer'}{https://apnews.com/article/5c9e65ca2c6159b73d69d455b1d0c951}{Greta Gerwig's ``Barbie'' dominated the Golden Globe Awards nominations with nine nods for the blockbuster film, including best picture musical or comedy as well as acting nominations for Margot Robbie and Ryan Gosling and three of its...}

\entryitemWithDescription{\hskip 0pt{}Vikings beat Raiders 3-0 in lowest-scoring NFL game in 16 yearsMinnesota and Las Vegas played the lowest-scoring NFL game in 16 years, with Greg Josep...}{https://apnews.com/article/39365e49b2e51f938232040940e3cb78}{LAS VEGAS (AP) --- The brand of football Minnesota and Las Vegas played on Sunday set the NFL back 16 years. Only Greg Joseph's 36-yard field goal with 1:57 left that gave the Vikings a 3-0 victory over the Raiders prevented the teams...}

\entryitemWithDescription{\hskip 0pt{}Skiing Santas hit the slopes in MaineSanta's helpers are taking the day off to hit the slopes in Maine. With beards and stocking caps flapping, about...}{https://apnews.com/article/d8ee453f249771dd287377539875747c}{NEWRY, Maine (AP) --- Ho ho ho, away they go --- Santa's helpers took the day off on Sunday with a few hundred of the jolly ol' elves hitting the slopes. With beards and stocking caps flapping, some 300 red-suited Santas were lively and...}

\entryitemWithDescription{\hskip 0pt{}`Thankful' Bronny James makes college debut in loss for USC nearly 5 months after cardiac arrest}{https://apnews.com/article/3da6b8dafe1b0edc69932b8a257f6673}{LOS ANGELES (AP) --- Bronny James showed off his defensive skills in his college debut for Southern California nearly five months after he suffered cardiac arrest and expressed gratitude for the doctors and family who supported him. He...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk restores X account of conspiracy theorist Alex Jones}{https://apnews.com/article/90cfc990631dec5e8f337167fbe16372}{Elon Musk has restored the X account of conspiracy theorist Alex Jones, pointing to a poll on the social media platform formerly known as Twitter that came out in favor of the Infowars host who repeatedly called the 2012 Sandy Hook school...}

\entryitemWithDescription{\hskip 0pt{}Liz Magill, U. Penn's president, and board chair resign as antisemitism testimony draws backlash}{https://apnews.com/article/ae1294d644b3305cc51e8d9bb7252766}{HARRISBURG, Pa. (AP) --- The University of Pennsylvania's president has resigned amid pressure from donors and criticism over testimony at a congressional hearing where she was unable to say under repeated questioning that calls on campus...}

\entryitemWithDescription{\hskip 0pt{}Thousands descend on NYC for the annual Santa-themed bar crawl SantaConThousands of people dressed as jolly Old St. Nick have descended on New York Ci...}{https://apnews.com/article/616ee17f07906fde81d7378f6ba206d5}{NEW YORK (AP) --- Here come Santa Clauses. Again. Throngs of people dressed as jolly Old St. Nick descended on New York City for the annual SantaCon charity pub crawl on Saturday. The booze-fueled stroll, which included no shortage of...}

\entryitemWithDescription{\hskip 0pt{}With no supermarket for residents of Atlantic City, New Jersey and hospitals create mobile groceries}{https://apnews.com/article/c49c6eaf9be2ad959a6fea61e73c2aa0}{ATLANTIC CITY, N.J. (AP) --- In this seaside resort, where \$5 billion worth of in-person and online gambling gets done each year, there still is not a supermarket. People who live in Atlantic City must either drive off the island to a...}

\entryitemWithDescription{\hskip 0pt{}Spotify's CFO is one of thousands to leave the company — after he moves to sell \$9 million in shares}{https://apnews.com/article/e3cd38dc2952df4b2a7fff9cbafe4950}{NEW YORK (AP) --- Spotify's chief financial officer will step down next year, according to the music streaming service, just days after it announced its third round of layoffs for 2023. In a statement announcing CFO Paul Vogel's...}