\entryitemWithDescription{\hskip 0pt{}Tyson recalls 30,000 pounds of chicken nuggets after consumers report finding metal pieces}{https://apnews.com/article/703756f3a03de3289c70ec09782208c9}{Tyson Foods is recalling nearly 30,000 pounds (13,600 kilograms) of breaded chicken ""Fun Nuggets'\,' after consumers complained of finding metal pieces in the dinosaur-shaped patties. The nuggets, sold in 29-ounce bags, were produced on...}

\entryitemWithDescription{\hskip 0pt{}More fruit pouches for kids are being recalled because of illnesses that are linked to lead}{https://apnews.com/article/ff3ade3e5032357e922d6036cff81c8c}{Federal health officials are expanding an investigation into potentially lead-tainted pouches of apple cinnamon fruit puree marketed for children amid reports of more illnesses and additional product recalls. The U.S. Food and Drug...}

\entryitemWithDescription{\hskip 0pt{}Weekend box office results are muted without `Dune: Part Two'}{https://apnews.com/article/16b62d517187add73758413b07f2980b}{The North American box office had one of its slowest weekends of the year, due in large part to ``Dune: Part Two's'' absence from the lineup. Moviegoers had many other options to choose from. The video game adaptation ``Five Nights at...}

\entryitemWithDescription{\hskip 0pt{}Washington Post names veteran media executive Will Lewis as its new publisher and CEO}{https://apnews.com/article/2050bc460fcc8f40f5a61b62da7e147e}{NEW YORK (AP) --- The Washington Post has named veteran media executive Will Lewis to serve as its new CEO and publisher, hoping to turn around a recent slump that has seen job cuts and a declining audience. Lewis is the former top...}

\entryitemWithDescription{\hskip 0pt{}Big Weekend: Rich Eisen reflects on NFL Network turning 20 and calling Chiefs-Dolphins on Sunday}{https://apnews.com/article/849e8bb4a385c820441f293ec04ba171}{Rich Eisen has had many memorable moments during his long tenure at NFL Network. This weekend though might end up being tough to beat. Saturday marks 20 years since NFL Network went on the air with Eisen anchoring ``Total Access.'' On...}

\entryitemWithDescription{\hskip 0pt{}Mark Zuckerberg undergoes knee surgery after the Meta CEO got hurt during martial arts training}{https://apnews.com/article/ca637aabc564267b26bbdad78ee0fc26}{LOS ANGELES (AP) --- Mark Zuckerberg's latest martial arts sparring session sent him to the operating table. The Meta Platforms CEO and mixed martial arts enthusiast posted on social media Friday that he tore one of his anterior cruciate...}

\entryitemWithDescription{\hskip 0pt{}A Norway spruce from West Virginia is headed to the US Capitol to be this year's Christmas tree}{https://apnews.com/article/55a40819204cdaf7df093545bfe7cfbe}{CHARLESTON, W.Va. (AP) --- A 63-foot (19-meter) Norway spruce from the Allegheny Mountains of West Virginia is on its way to the West Lawn of the U.S. Capitol to be the Christmas tree for 2023. Snow fell on the crew members Wednesday in...}

\entryitemWithDescription{\hskip 0pt{}Tigers acquire veteran outfielder Mark Canha from Brewers in exchange for minor league pitcher}{https://apnews.com/article/ffc2a7cbdd52f6f0e074f8513f0eec57}{MILWAUKEE (AP) --- Veteran outfielder Mark Canha is on the move again, with the Milwaukee Brewers trading him to the Detroit Tigers on Saturday rather than picking up his option for the 2024 season. The Brewers acquired minor league...}

\entryitemWithDescription{\hskip 0pt{}Phoenix finishes clearing downtown homeless encampment after finding shelter for more than 500}{https://apnews.com/article/b0ccbe6bc03ee1592b4e6a087c839417}{PHOENIX (AP) --- The city of Phoenix has successfully cleared out a massive downtown homeless encampment by Saturday's court ordered deadline by helping more than 500 people find beds in shelters and motels. The hundreds of tents that...}

\entryitemWithDescription{\hskip 0pt{}Leroy Stover, Birmingham's first Black police officer, dies at 90}{https://apnews.com/article/cfbe9c34792833da197b8f7659e918a7}{BIRMINGHAM, Ala. (AP) --- The City of Birmingham's first Black police officer, Leroy Stover, has died. He was 90. Birmingham Police on Friday posted about Stover's death on X, formerly known as Twitter. ``Today, our hearts are heavy as we...}

\entryitemWithDescription{\hskip 0pt{}Arkansas man arrested after trying to crash through gates at South Carolina nuclear plant}{https://apnews.com/article/74193ea7e613b0528c84e590cfc9873b}{WALHALLA, S.C. (AP) --- An Arkansas man has been arrested for trying to crash through the exit gates of a South Carolina nuclear plant, authorities said. Doyle Wayne Whisenhunt, of Lockesburg, Arkansas, was taken into custody Friday night...}

\entryitemWithDescription{\hskip 0pt{}Right turn on red? With pedestrian deaths rising, US cities are considering bans}{https://apnews.com/article/7f5bdee9c7b3f4cbf005f1844f486123}{CHICAGO (AP) --- Sophee Langerman was on her way to a bicycle safety rally in Chicago's Lakeview neighborhood in June when a car turning right rolled through a red light and slammed into her bike, which she was walking off the curb and...}

\entryitemWithDescription{\hskip 0pt{}Illinois city tickets reporter for asking too many questions, in latest First Amendment dustup}{https://apnews.com/article/999a872f6fd45962547af94318e92950}{SPRINGFIELD, Ill. (AP) --- Officials in a suburban Chicago community have issued municipal citations to a local news reporter for what they say were persistent contacts with city officials seeking comment on treacherous fall flooding. The...}