\entryitemAp{\hskip 0pt{}EXPLAINER: How ominous is the debt limit problem?}{https://apnews.com/article/6fe9b54dcdfea58bead0f4c5f9f89a64}{FILE - Treasury Secretary Janet Yellen speaks with reporters during a visit to the Virginia Innovation Partnership Corporation incubator at the Center for Innovative Technology campus in Herndon, Va., Oct. 21, 2022. Yellen has notified...}

\entryitemAp{\hskip 0pt{}Renner says he's home from hospital after snow plow accident}{https://apnews.com/article/832fc60a878e8944e1ad7429e7862863}{FILE - Jeremy Renner arrives at the premiere of "Avengers: Endgame" at the Los Angeles Convention Center on Monday, April 22, 2019. Renner says he is out of the hospital after he was seriously injured in a snow plow accident. In response...}

\entryitemAp{\hskip 0pt{}After 2 virtual years, Sundance returns to the mountains}{https://apnews.com/article/eb6024d4d943043a50fb932ac4801e9f}{FILE - The marquee of the Egyptian Theatre appears during the Sundance Film Festival in Park City, Utah on Jan. 28, 2020. After two years of virtual editions, the Sundance Film Festival is returning to Park City, Utah armed with a robust...}

\entryitemAp{\hskip 0pt{}White House defends its delayed, limited document disclosure}{https://apnews.com/article/5840b75b342d9255d46b9f264789fa2e}{President Joe Biden meets with Dutch Prime Minister Mark Rutte in the Oval Office of the White House in Washington, Tuesday, Jan. 17, 2023. (AP Photo/Carolyn Kaster) WASHINGTON (AP) --- The White House brushed aside criticism Tuesday of...}

\entryitemAp{\hskip 0pt{}Davos organizers: Musk wasn't invited despite what he says}{https://apnews.com/article/7a82416400545f313ff46c0180e606d7}{FILE - Tesla and SpaceX Chief Executive Officer Elon Musk speaks at the SATELLITE Conference and Exhibition in Washington. A federal judge on Friday, Jan. 13 2023 rejected Tesla CEO Elon Musk's bid to move or delay a trial over a...}

\entryitemAp{\hskip 0pt{}Police arrest failed candidate in shootings at Democrats}{https://apnews.com/article/1410b516f5b66c18d62342a0d7a9b60f}{Solomon Pena, center, a Republican candidate for New Mexico House District 14, is taken into custody by Albuquerque Police officers, Monday, Jan. 16, 2023, in southwest Albuquerque, N.M. Pena was arrested in connection with a recent...}

\entryitemAp{\hskip 0pt{}Moving species emerges as last resort as climate warms}{https://apnews.com/article/1b4e2790b0f341bebd73fa431c1eefaa}{In this photo provided by the Pacific Rim Conservation, wildlife workers relocate Tristram's storm petrels on Hawaii's Tern Island, on March 29, 2022. Scientists are making a dramatic effort to save the birds in Hawaii by moving them to...}

\entryitemAp{\hskip 0pt{}Leslie Jones promises to be herself hosting 'The Daily Show'}{https://apnews.com/article/a183a4022298e7d4ef245f426c6a6080}{FILE - Leslie Jones appears at the 70th Primetime Emmy Awards in Los Angeles on Sept. 17, 2018. Jones will be taking a temporary whirl as host of ``The Daily Show'' on Comedy Central on Tuesday, Wednesday and Thursday. (Photo by Jordan...}

\entryitemAp{\hskip 0pt{}US, Ukraine top military chiefs meet in person for 1st time}{https://apnews.com/article/56bf9dc96a24f62c91903c8861ae7af7}{In this image provided by the U.S. Army, U.S. Chairman of the Joint Chiefs of Staff Gen. Mark Milley meets with U.S. Army leaders responsible for the collective training of Ukrainians at Grafenwoehr Training Area, Grafenwoehr, Germany, on...}

\entryitemAp{\hskip 0pt{}Fastest Corvette ever is all-wheel-drive gas-electric hybrid}{https://apnews.com/article/50e719fb41ba8716ee582224c1e26225}{The 2024 Corvette E Ray is displayed, Thursday, Jan. 12, 2023, in Milford Mich. The fastest corvette ever made comes out next year, and it\textquotesingle s not powered soley by the traditional howling V8. The E Ray is a gas electric...}

\entryitemAp{\hskip 0pt{}Should you worry about lichens, moss, algae on trees?}{https://apnews.com/article/c4af20f5891fa7c83348b78bac09094a}{This April 2, 2019, photo provided by the Forest Preserve District of Will County, IL, shows moss growing at the base of a tree at Raccoon Grove Nature Preserve in Monee, IL. (Forest Preserve District of Will County via AP) Now that...}

\entryitemAp{\hskip 0pt{}Greta Thunberg carried away by police at German mine protest}{https://apnews.com/article/a870ba0ba69c7816cc04f13b8be2cb94}{Police officers carry Swedish climate activist Greta Thunberg away from the edge of the Garzweiler II opencast lignite mine during a protest action by climate activists after the clearance of Luetzerath, Germany, Tuesday, Jan. 17, 2023...}

\entryitemAp{\hskip 0pt{}Passenger's video captures last moments before Nepal crash}{https://apnews.com/article/02c418467d273a3f43ef0d1b16df760f}{People observe a candlelight vigil in memory of victims of a plane crash in Kathmandu, Nepal, Monday, Jan. 16, 2023. The Yeti Airlines flight from Kathmandu that plummeted into a gorge Sunday killed at least 70 passengers out of the 72 on...}