\entryitemWithDescription{\hskip 0pt{}Surfer dies after shark ``encounter'' in Hawaii}{https://apnews.com/article/5fd98ad87b5e07a46b2d80be5289afe2}{PAIA, Hawaii (AP) --- A surfer in Hawaii has died after being injured in a shark encounter off Maui's northern shore, according to the Maui Police Department. Authorities stopped short of calling the event an attack and didn't describe...}

\entryitemWithDescription{\hskip 0pt{}Shecky Greene, legendary standup comic, improv master and lord of Las Vegas, dies at 97}{https://apnews.com/article/6f0455de97a4ae5faefa508ca55b6cd0}{LOS ANGELES (AP) --- Shecky Greene, the gifted comic and master improviser who became the consummate Las Vegas lounge headliner and was revered by his peers and live audiences as one of the greatest standup acts of his generation, has...}

\entryitemWithDescription{\hskip 0pt{}Denmark's Queen Margrethe II to step down from throne on Jan. 14}{https://apnews.com/article/92afd336166b4e643caf57289eaf8fbe}{STOCKHOLM, Sweden (AP) --- Denmark's Queen Margrethe II announced Sunday that she plans to abdicate after 52 years and hand over the throne to her son, Crown Prince Frederik. The queen, who is Europe's longest-reigning living monarch...}

\entryitemWithDescription{\hskip 0pt{}Sen. Fetterman says he thought news about his depression treatment would end his political career}{https://apnews.com/article/0f424652b43f77b40e7dac9e186b14bb}{WASHINGTON (AP) --- Sen. John Fetterman acknowledges having ``dark conversations'' about harming himself before he hit ``the emergency brake'' and sought treatment for depression. He remembers thinking about his three school-age kids. ``I...}

\entryitemWithDescription{\hskip 0pt{}South Korea's capital records heaviest single-day snowfall in December for 40 years}{https://apnews.com/article/f644c0a935cb0e2c674691ea9d5bf373}{SEOUL, South Korea (AP) --- The South Korean capital, Seoul, received the biggest single-day snowfall recorded in December for more than 40 years on Saturday but there have been no reports of any weather-related deaths or injuries. The...}

\entryitemWithDescription{\hskip 0pt{}At the stroke of midnight, the New Year gives a clean slate for long-elusive resolutions}{https://apnews.com/article/a022bcea9e37851b32b0a1a05107b9eb}{NEW YORK (AP) --- It's an annual end-of-year exercise in futility for many. But a clean slate awaits at the stroke of midnight for the next round of resolutions. From the first spray of fireworks to the closing chorus of ``Auld Lang...}

\entryitemWithDescription{\hskip 0pt{}New Year's Eve celebrations roll across Asia, but wars cast a shadow on the start of 2024}{https://apnews.com/article/17154156831f22b2354b82688d4272af}{Revelers across Asia celebrated the countdown to midnight on New Year's Eve with fireworks and brightly lit signs --- offering a hopeful start to 2024 for some, even as the globe's ongoing conflicts raised security concerns and let to...}

\entryitemWithDescription{\hskip 0pt{}High surf advisories remain in some parts of California, as ocean conditions begin to calm}{https://apnews.com/article/b2b834040a570dfce1f4f02f68d0bd59}{VENTURA, Calif. (AP) --- Southern California's Ventura County issued a temporary evacuation warning Saturday for some coastal residents due to high surf that pounded the West Coast this week but has begun to calm down. County officials...}

\entryitemWithDescription{\hskip 0pt{}Paula Abdul accuses `American Idol' producer Nigel Lythgoe of sexual assault in lawsuit}{https://apnews.com/article/ce22542ef62e4ac5a1081932c9a631ab}{LOS ANGELES (AP) --- Paula Abdul has accused former ``American Idol'' producer Nigel Lythgoe of sexually assaulting her in the early 2000s when she was a judge on the reality competition show, according to a new lawsuit. The lawsuit filed...}

\entryitemWithDescription{\hskip 0pt{}In a crisis-ridden world, Germany's chancellor uses his New Year's speech to convey confidence}{https://apnews.com/article/91794fc65fc12a08e677e01f03e4dcb4}{BERLIN (AP) --- Germany's chancellor used his New Year's speech to call on his country's citizens not to lose confidence in the future as they adapt to a world experiencing multiple crises and changing at an ever-faster pace. ``So much...}

\entryitemWithDescription{\hskip 0pt{}Family of 4 found dead in apparent murder-suicide by New York police sergeant}{https://apnews.com/article/b294adb78e1a9a2ac7a18fc522a63926}{NEW YORK (AP) --- A husband and wife and their two sons, ages 10 and 12, were found dead in a suburban New York home Saturday in what authorities described as a murder-suicide by a police sergeant. Police officials said Watson Morgan, a...}

\entryitemWithDescription{\hskip 0pt{}British actor Tom Wilkinson, known for `The Full Monty' and `Michael Clayton,' dies at 75}{https://apnews.com/article/9f69d232bf9e94ab59fe98c12b7f5856}{LONDON (AP) --- Tom Wilkinson, the Oscar-nominated British actor known for his roles in ``The Full Monty,'' ``Michael Clayton'' and ``The Best Exotic Marigold Hotel,'' has died, his family said. He was 75. A statement shared by his agent...}

\entryitemWithDescription{\hskip 0pt{}What does Watch Night mean for Black Americans today? It dates back to the Emancipation Proclamation}{https://apnews.com/article/9d169e7bc6be54a764a190d6b73cf760}{The tradition of Watch Night services in the United States dates back to Dec. 31, 1862, when many Black Americans gathered in churches and other venues, waiting for President Abraham Lincoln to sign the Emancipation Proclamation into law...}