\entryitemWithDescription{\hskip 0pt{}Michigan State didn't seek permission or pay for Hitler-related quiz content, YouTube creator says}{https://apnews.com/article/23b8e62c44cf42c3caad30c908692632}{EAST LANSING, Mich. (AP) --- The creator and producer of The Quiz Channel on YouTube, which includes Adolf Hitler's image as part of a quiz Michigan State used on its videoboards before a game against No. 2 Michigan, said the school didn'...}

\entryitemWithDescription{\hskip 0pt{}Swift bests Scorsese at box office, but `Killers of the Flower Moon'' opens strongly}{https://apnews.com/article/804edf3b87d51624a8c51f377553611e}{NEW YORK (AP) --- In a movie match-up almost as unlikely as ``Barbie'' and ``Oppenheimer,'' Martin Scorsese took on Taylor Swift in cinemas over the weekend. And while the box office belonged for a second time to ``Taylor Swift: The Eras...}

\entryitemWithDescription{\hskip 0pt{}New Netflix thriller tackling theme of justice in Nigeria is a global hit and a boon for Nollywood}{https://apnews.com/article/1350bd34e7529c7ab92670edaea904a1}{ABUJA, Nigeria (AP) --- A Nigerian action thriller that tells a gripping story of corruption and police brutality in Africa's most populous country has reached record viewership numbers on Netflix charts globally. It's a reminder of the...}

\entryitemWithDescription{\hskip 0pt{}Philadelphia Orchestra and musicians agree to 3-year labor deal with 15.8\% salary increase}{https://apnews.com/article/a3a960544a5e9ac8b58e9160cef8347b}{PHILADELPHIA (AP) --- Musicians of the Philadelphia Orchestra and the Philadelphia Orchestra Association have ratified a collective bargaining agreement calling for minimum salaries to increase by 15.8\% over three years. The deal...}

\entryitemWithDescription{\hskip 0pt{}What's in a game? `Dear England' probes the nation through the lens of its soccer team}{https://apnews.com/article/81b3181e9149661c3a17c98535d3b4fa}{LONDON (AP) --- Outside of families, few relationships are as intense as those between sports teams and their fans. In the case of England's bond with its national soccer team, it's not always been healthy. James Graham's play ``Dear...}

\entryitemWithDescription{\hskip 0pt{}Visitors tour New Mexico atomic site in likely record attendance fueled by `Oppenheimer' fanfare}{https://apnews.com/article/c5abb260f0fc50762929d83c579cbb08}{WHITE SANDS MISSILE RANGE, N.M. (AP) --- Visitors lined up Saturday to tour the southern New Mexico site where the world's first atomic bomb was detonated in what officials believe could be a record turnout amid ongoing fanfare...}

\entryitemWithDescription{\hskip 0pt{}Illinois government employee fired after posting antisemitic comments on social media}{https://apnews.com/article/42b9fb4dd66b20e903ca9b8c4515c327}{SPRINGFIELD, Ill. (AP) --- An employee with the Illinois comptroller's office has been fired after she posted vulgar antisemitic comments on social media during an exchange about the latest Israel-Hamas war. A spokesperson for Illinois...}

\entryitemWithDescription{\hskip 0pt{}UK stage and screen star Haydn Gwynne dies at 66 after cancer diagnosis}{https://apnews.com/article/5fb17dbc928656ee7e5678667cff0005}{LONDON (AP) --- Haydn Gwynne, a versatile and acclaimed performer on British stage and screen, has died. She was 66 and had recently been diagnosed with cancer. Gwynne's agent Alex Irwin said the actress died in a London hospital early...}

\entryitemWithDescription{\hskip 0pt{}Italian Premier Meloni announces separation from partner, father of daughter}{https://apnews.com/article/5eeaa4ae2596c5c9c36df20b16fa4614}{ROME (AP) --- Italian Premier Giorgia Meloni announced Friday that she is separating from her partner and the father of their young daughter after nearly a decade together. In a statement posted on social media, Meloni said her...}

\entryitemWithDescription{\hskip 0pt{}What's that bar band playing `Jumpin' Jack Flash'? Oh, it's the Rolling Stones!}{https://apnews.com/article/071ec5fd08fc3005657e4e4f98e81311}{NEW YORK (AP) --- Those miracles of modern science, the Rolling Stones, celebrated the release of their first album of original music in 18 years with a Manhattan club gig on Thursday. Before a celebrity-strewn audience of invited guests...}

\entryitemWithDescription{\hskip 0pt{}Baltimore firefighter dies and 4 others are injured battling rowhouse fire}{https://apnews.com/article/35eb6664afaccebfad9b71cadf19d28c}{BALTIMORE (AP) --- A rapidly intensifying blaze that engulfed multiple rowhouses in northwest Baltimore late Thursday afternoon left one firefighter dead and four others injured, city officials said. The injured firefighters sustained...}

\entryitemWithDescription{\hskip 0pt{}Britney Spears' book `The Woman In Me' makes private details public, and public events personal}{https://apnews.com/article/80d00a6d450d87ae68457bd826843be4}{LOS ANGELES (AP) --- Britney Spears' highly anticipated memoir ``The Woman in Me'' will be released Tuesday, revealing the pop superstar's personal take on events that have played out publicly in her decades as one of the most scrutinized...}

\entryitemWithDescription{\hskip 0pt{}Marlon Wayans says he is being unfairly prosecuted after being racially targeted by gate agent}{https://apnews.com/article/4ec0285ee770867d09d6a749b74e0927}{DENVER (AP) --- Actor and comedian Marlon Wayans says he is being unfairly prosecuted for disturbing the peace over a dispute with an airline employee who he alleges targeted him because of his race. Attorneys for Wayans, who is Black...}