\entryitemWithDescription{\hskip 0pt{}Herders in Kenya kill 10 lions, including Loonkiito, one of the country's oldest}{https://apnews.com/article/dfde18abce78e71e8ec3ddd44c8b4269}{This photo provided by Lion Guardians shows the male lion named "Loonkiito" in Amboseli National Park, in southern Kenya on Feb. 20, 2023. One of Kenya\textquotesingle s oldest wild lions, Loonkiito, 19, was killed by herders and the...}

\entryitemWithDescription{\hskip 0pt{}Border crossings are off from last week's highs as US pins hopes for order on mobile app}{https://apnews.com/article/410698368cdaa9b8adc820543d9b7bbc}{Venezuelan migrants rest inside their tents on the bank of the Rio Grande in Matamoros, Mexico, Sunday, May 14, 2023. As the U.S. ended its pandemic-era immigration restrictions, migrants are adapting to new asylum rules and legal...}

\entryitemWithDescription{\hskip 0pt{}He likes to be, under the sea: Florida man sets record for living underwater}{https://apnews.com/article/1b7657c223a738c7a7b6b129dc4a928b}{In this photo provided by the Florida Keys News Bureau, diving explorer and medical researcher Dr. Joseph Dituri peers out of a large porthole, Saturday, May 13, 2023, at Jules\textquotesingle{} Undersea Lodge positioned at the bottom of...}

\entryitemWithDescription{\hskip 0pt{}'Guardians Vol. 3' and 'Super Mario Bros.' top box office again}{https://apnews.com/article/061b10896ae701542a99c49b8fd8556d}{Left to right; actors Vin Diesel, Pom Klementieff, director James Gunn, Chris Pratt, Zoe Saldana, Karen Gillan pose for photographers upon arrival at the gala event for the film Guardians of the Galaxy Vol. 3 at Disneyland Paris Saturday...}

\entryitemWithDescription{\hskip 0pt{}Bolivian EV startup hopes tiny car will make it big in lithium-rich country}{https://apnews.com/article/bf89a1f936301d047f0c11d9eb813529}{Dr. Carlos Ortuno drives a Bolivian-made, Quantum electric car to a house call, in La Paz, Bolivia, Wednesday, May 3, 2023. Launched in 2019, Quantum Motors has only sold 350 electric cars in Bolivia. But their founders recently received...}

\entryitemWithDescription{\hskip 0pt{}Child social media stars have few protections. Illinois aims to fix that}{https://apnews.com/article/65a837e2ba7151c91c17f69b08862022}{Shreya Nallamothu looks at her phone in Bloomington, Ill., on Tuesday, May 9, 2023. Illinois lawmakers aim to make their state what they say will be the first in the country to create protections for child social media influencers...}

\entryitemWithDescription{\hskip 0pt{}AI presents political peril for 2024 with threat to mislead voters}{https://apnews.com/article/59fb51002661ac5290089060b3ae39a0}{FILE - A booth is ready for a voter, Feb. 24, 2020, at City Hall in Cambridge, Mass., on the first morning of early voting in the state. Thanks to recent advances in artificial intelligence, tools that can create lifelike photos, video...}

\entryitemWithDescription{\hskip 0pt{}Sweden celebrates Eurovision win; Ukrainian duo defiant after Russian strike on hometown}{https://apnews.com/article/c58643d6cca9f0cbc9e02636ef0e2f19}{Loreen of Sweden performs after winning the Grand Final of the Eurovision Song Contest in Liverpool, England, Saturday, May 13, 2023. (AP Photo/Martin Meissner) LIVERPOOL, England (AP) --- Liverpool cleaned up from the Eurovision Song...}

\entryitemWithDescription{\hskip 0pt{}Sherpa climbs Everest 26th time, matching record set by fellow Nepalese guide}{https://apnews.com/article/f8b77801e27b33ea4059f7ce52141e5f}{FILE - A bird flies with Mount Everest seen in the background from Namche Bajar, Solukhumbu district, Nepal, May 27, 2019. A Sherpa guide scaled Mount Everest on Sunday for the 26th time, matching the record set by a fellow Nepalese guide...}

\entryitemWithDescription{\hskip 0pt{}Minneapolis city council nomination brawlers could be expelled from Minnesota Democratic Party}{https://apnews.com/article/8c8fb4a25cf33753fd3aef81098535fb}{FILE - The Minnesota DFL logo appears on a podium at a DFL election-night party, Nov. 8, 2022, in St. Paul, Minn. On Saturday, May 14, 2023, a brawl broke out over nominations for Minneapolis City Council candidates Aisha Chughtai and...}

\entryitemWithDescription{\hskip 0pt{}Powerful Cyclone Mocha makes landfall in Myanmar, tearing off roofs and killing at least 3}{https://apnews.com/article/06512b0f496bf85c926f12925ab1ba7e}{Rescue workers remove the fallen tress after a storm in Teknaf, near Cox\textquotesingle s Bazar, Bangladesh, Sunday, May 14, 2023. Bangladesh and Myanmar braced Sunday as a severe cyclone started to hit coastal areas and authorities...}

\entryitemWithDescription{\hskip 0pt{}Biden to graduates of historically Black Howard University: US history hasn't been a 'fairy tale'}{https://apnews.com/article/435ef5385648d0d8e9d00dd5f0248288}{President Joe Biden speaks at Howard University\textquotesingle s commencement in Washington, Saturday, May 13, 2023. (AP Photo/Alex Brandon) WASHINGTON (AP) --- President Joe Biden on Saturday told graduates of a leading historically...}

\entryitemWithDescription{\hskip 0pt{}Kelly Clarkson responds to report accusing her daytime talk show of being a toxic workplace}{https://apnews.com/article/5892ed3967f759997ab9e56d82c7683a}{FILE - Kelly Clarkson performs during a tribute to Icon award winner Pink at the iHeartRadio Music Awards on Monday, March 27, 2023, at the Dolby Theatre in Los Angeles. Clarkson has responded, Saturday, May 13, to a Rolling Stone report...}