\entryitemWithDescription{\hskip 0pt{}Biden expected to tighten rules on US investment in China}{https://apnews.com/article/aad907e784784f65c7b579de3b8a5775}{FILE - The American and Chinese flags wave at Genting Snow Park ahead of the 2022 Winter Olympics, Feb. 2, 2022, in Zhangjiakou, China. The Biden administration is close to finalizing new regulations that would tighten rules on certain...}

\entryitemWithDescription{\hskip 0pt{}Marianne Williamson begins longshot 2024 challenge to Biden}{https://apnews.com/article/14e59754bed9e0c54dad4fdfbbc1fa6b}{Self-help author Marianne Williamson speaks to the crowd as she launches her 2024 presidential campaign in Washington, Saturday, March 4, 2023. The 70-year-old onetime spiritual adviser to Oprah Winfrey became the first Democrat to...}

\entryitemWithDescription{\hskip 0pt{}Heavy snow hits Northeast as storm cleanup begins in South}{https://apnews.com/article/ba29f2851946cf7c45a6189c75bdf865}{Rocio Franco, of Bellows Falls, shovels the snow from the open of her driveway on Saturday, March 4, 2023, in Bellow Falls, Windham County, Vt. (Kristopher Radder/The Brattleboro Reformer via AP) The winter-weary Northeast and upper...}

\entryitemWithDescription{\hskip 0pt{}Ja Morant says he'll get help after video shows apparent gun}{https://apnews.com/article/6aa0a20153dc4f2130a0a950b8379e15}{Memphis Grizzlies guard Ja Morant looks to the bench during the second half of the team\textquotesingle s NBA basketball game against the Denver Nuggets on Friday, March 3, 2023, in Denver. (AP Photo/David Zalubowski) Ja Morant will be...}

\entryitemWithDescription{\hskip 0pt{}Lawyers fight for man they say US wrongly deported to Haiti}{https://apnews.com/article/8a516a141f9d104e497c51598a075de3}{FILE - Haitians who were deported from the United States deplane at the Toussaint Louverture International Airport, in Port au Prince, Haiti, Sept. 19, 2021. More than 20,000 Haitians have been deported from the U.S. in 2022, as thousands...}

\entryitemWithDescription{\hskip 0pt{}Athlete dead in shipwreck left Pakistan to help disabled son}{https://apnews.com/article/29203e7b2f118ec8ed3363995be793ef}{In this handout photo provided by Pakistan Hockey Federation on Thursday, March 2, 2023, shows women\textquotesingle s field hockey player Shahida Raza, in Lahore, Pakistan. Raza was among other migrants who died in a shipwreck off Italy...}

\entryitemWithDescription{\hskip 0pt{}Can't take statins? New pill cuts cholesterol, heart attacks}{https://apnews.com/article/08aae402bf224bab4bbe4b15cd95200d}{FILE- This undated photo provided by Esperion Therapeutics Inc. shows the cholesterol-lowering drug Nexletol. In a major study released Saturday, March 4, 2023, Nexletol reduced the risk of heart attacks and other health problems in...}

\entryitemWithDescription{\hskip 0pt{}Pot vote has Oklahoma hungry to rake in green from Texas}{https://apnews.com/article/7f42b209187570a2640f92cf30a3ca3e}{Ethan McKee, vice president of Mango Cannabis, displays marijuana flowers at a dispensary, Tuesday, Feb. 28, 2023, in Oklahoma City. Voters in Oklahoma, which already has a robust medical marijuana program, will decide on Tuesday, March...}

\entryitemWithDescription{\hskip 0pt{}Civilians flee embattled town as Ukrainian pullout looms}{https://apnews.com/article/f893b10637da1b46939777379b5d9905}{A Ukrainian police van drives on the highway for evacuation civilians in Khromove near Bakhmut, Ukraine, Saturday, March 4, 2023. (AP Photo/Evgeniy Maloletka) KHROMOVE, Ukraine (AP) --- Pressure from Russian forces mounted Saturday on...}

\entryitemWithDescription{\hskip 0pt{}Election conspiracies fuel dispute over voter fraud system}{https://apnews.com/article/0c8654a687e259be58b2c8ef232ad21e}{FILE - A poll worker, center left, speaks through a plastic barrier while assisting a voter in a polling station at Marshfield High School, Nov. 3, 2020, in Marshfield, Mass. A bipartisan effort among states to combat voter fraud has...}

\entryitemWithDescription{\hskip 0pt{}In Britain, `warm hubs' emerge to beat soaring energy costs}{https://apnews.com/article/84dc6878fd3c5b91837f8d3558c1f672}{Wendy Freeman, an artist, writes poem at the Other Place theater, in Stratford-upon-Avon, Warwickshire, England, Tuesday, Feb. 28, 2023. The foyer of the Other Place theater in Shakespeare\textquotesingle s birthplace of Stratford-upon...}

\entryitemWithDescription{\hskip 0pt{}Olympic ticket sales for Paris Games get off to rocky start}{https://apnews.com/article/1f8f848ce6b764b1d4fb902d1a7ec79a}{FILE - The Olympic rings are seen on the Place du Trocadero that overlooks the Eiffel Tower, after the vote in Lima, Peru, awarding the 2024 Games to the French capital, in Paris, Sept. 13, 2017. Organizers of the Paris 2024 Olympics...}

\entryitemWithDescription{\hskip 0pt{}Global race to boost electric vehicle range in cold weather}{https://apnews.com/article/6d86b7aa19e233d5dcc4d2c9abb193ed}{A driver charges an electric car at a parking lot of a shopping mall in Tallinn, Estonia, Saturday, Feb. 11, 2023. Many electric vehicle batteries lose power when it\textquotesingle s very cold. (AP Photo/Sergei Grits) Many electric...}