\entryitemWithDescription{\hskip 0pt{}TikTok accuses federal agency of `political demagoguery' in legal challenge against potential US ban}{https://apnews.com/article/5fc3bb029141b314c1f9d54b2ea47e61}{TikTok disclosed a letter Thursday that accused the Biden administration of engaging in ``political demagoguery'' during high-stakes negotiations between the government and the company as it sought to relieve concerns about its presence...}

\entryitemWithDescription{\hskip 0pt{}New York moves to limit 'addictive' social media feeds for kids}{https://apnews.com/article/d30af590aff0e255a05f9f4955bdccf0}{New York Gov. Kathy Hochul on Thursday signed a bill that would allow parents to block their children from getting social media posts suggested by a platform's algorithm, a move to limit feeds critics argue are addictive. Under the...}

\entryitemWithDescription{\hskip 0pt{}Rapper Travis Scott arrested in Miami Beach for misdemeanor trespassing and public intoxication}{https://apnews.com/article/fc1485b36ee9f069e6ead5b4d8f3137b}{MIAMI BEACH, Fla. (AP) --- Rapper Travis Scott was arrested by Miami Beach police early Thursday on misdemeanor charges of trespassing and public intoxication. Miami Beach police confirmed the arrest, but did not immediately provide any...}

\entryitemWithDescription{\hskip 0pt{}Stonehenge not visibly damaged by protest paint. It's clean and ready to rock the solstice.}{https://apnews.com/article/f93506fdd75d9b5b8be1725f11ad8b33}{LONDON (AP) --- Stonehenge monuments that have stood for thousands of years appear unscathed after climate protesters were arrested for spraying orange paint on them, an official said Thursday. Workers cleaned the stones and the roughly...}

\entryitemWithDescription{\hskip 0pt{}Issey Miyake's wind-inspired show takes flight at Paris Fashion Week}{https://apnews.com/article/a19170ad46886266df4a6e90c4b49d60}{PARIS (AP) --- Diaphanous origami-like sculptures that floated like spring seeds caught in the wind captured the essence of the subtle, rich, and exquisite display from Issey Miyake at Paris Fashion Week --- one of the strongest in...}

\entryitemWithDescription{\hskip 0pt{}The Iberian lynx is back from the brink of extinction, thanks to conservation efforts}{https://apnews.com/article/b7e36b94510301bc5616511d84cdbe1c}{MADRID (AP) --- Things are looking up for the Iberian lynx. Just over two decades ago, the pointy-eared wild cat was on the brink of extinction, but as of Thursday the International Union for Conservation of Nature says it's no longer an...}

\entryitemWithDescription{\hskip 0pt{}After Drake battle, Kendrick Lamar turns victory lap concert into LA unity celebration}{https://apnews.com/article/977958e25837f56a73dd2379db43f916}{INGLEWOOD, Calif. (AP) --- Not content with merely taking a victory lap after winning his battle against fellow rap superstar Drake, Kendrick Lamar turned his Juneteenth ``Pop Out'' concert at the Forum into a cathartic livestreamed...}

\entryitemWithDescription{\hskip 0pt{}Movie Review: In `The Bikeriders,' the birth of a subculture on two wheels}{https://apnews.com/article/84a34f33f20c515714c23485b433b773}{Still images have been a source of wonder and mythology in the films of Jeff Nichols. ``Mud,'' Nichols' Twain-soaked Mississippi fable, seemed derived from the magical sight of a boat held aloft by a tree. ``Loving,'' about a `60s...}

\entryitemWithDescription{\hskip 0pt{}Snapchat Inc. to pay \$15 million to settle discrimination and harassment lawsuit in California}{https://apnews.com/article/7fd5bf7539e95578b47bf6e85ffc2f9c}{SAN FRANCISCO (AP) --- Snapchat Inc. will pay \$15 million to settle a lawsuit brought by California's civil rights agency that claimed the company discriminated against female employees, failed to prevent workplace sexual harassment and...}

\entryitemWithDescription{\hskip 0pt{}One of Rishi Sunak's bodyguards arrested over alleged bets on UK election date}{https://apnews.com/article/6bfe7059e2b0ef41cdcc166190960351}{LONDON (AP) --- One of Prime Minister Rishi Sunak's police bodyguards has been arrested over alleged bets on the date of Britain's national election made before it was announced, authorities said Wednesday. The Metropolitan Police force...}

\entryitemWithDescription{\hskip 0pt{}Climate protesters arrested after painting Stonehenge monument orange}{https://apnews.com/article/34d7591e858c904a1569ce415a8ad10b}{LONDON (AP) --- Two climate protesters were arrested Wednesday for spraying orange paint on the ancient Stonehenge monument in southern England, police said. The latest act by Just Stop Oil was quickly condemned by Prime Minister Rishi...}

\entryitemWithDescription{\hskip 0pt{}Pharrell at Louis Vuitton celebrates the diversity of human skin in Paris UNESCO show}{https://apnews.com/article/ac99d753ac8df9b73ef6d5b76e7de9b8}{PARIS (AP) --- In the run-up to the Paris Olympics, Louis Vuitton celebrated the beauty of humans and their skin in a star-studded menswear showcase at the headquarters of the U.N. cultural agency UNESCO in Paris. Models wearing garb in...}

\entryitemWithDescription{\hskip 0pt{}Baby moose trapped in a lake is saved by Alaska man and police as its worried mom watches}{https://apnews.com/article/f146ee2aedbf2d024b48832365cd315e}{ANCHORAGE, Alaska (AP) --- An Alaska man and two police officers rescued a baby moose from what police described as ``a sure demise'' after it fell into a lake and got stuck in a narrow space between a floatplane and a dock. Spencer...}