\entryitemWithDescription{\hskip 0pt{}Derek Jeter's New York castle might finally have a buyer}{https://apnews.com/article/c5dd773c420a5ae05d2dc35d608e5542}{GREENWOOD LAKE, N.Y. (AP) --- Former New York Yankees superstar Derek Jeter has found a potential buyer for his New York castle after the sprawling lakefront property had its price tag slashed by more than half. The property, known as...}

\entryitemWithDescription{\hskip 0pt{}Divers find remains of Finnish WWII plane that was shot down by Moscow with a US diplomat aboard}{https://apnews.com/article/8376e3aa3237ec2e551749afc74ccbbe}{HELSINKI (AP) --- The World War II mystery of what happened to a Finnish passenger plane after it was shot down over the Baltic Sea by Soviet bombers appears to finally be solved more than eight decades later. The plane was carrying...}

\entryitemWithDescription{\hskip 0pt{}Residents, communities preparing for heat wave that will envelop Midwest, Northeast next week}{https://apnews.com/article/fb30a71435ce078291b12f59c79bc17d}{Things are about to heat up in much of the U.S. with dangerously hot temperatures in the Midwest and Northeast next week, prompting health officials to urge people to make plans now to stay safe. The heat wave follows an earlier-than...}

\entryitemWithDescription{\hskip 0pt{}Lower your risk of falling as you get older with these simple steps}{https://apnews.com/article/ddd855dd47578167e9c6d48196fb220c}{One in four older adults in the U.S. will fall each year, putting them at risk of injury, broken bones and even death. Falls are a growing public health concern as the country's population sees record numbers of people turn 65 --- now and...}

\entryitemWithDescription{\hskip 0pt{}Charles Barkley says next season will be his last on TV, no matter what happens with NBA media deals}{https://apnews.com/article/00d6419edb31dc4b793d71f50cdd4c72}{Charles Barkley said Friday that next season will be his last on TV, no matter what happens with the NBA's media deals. The Hall of Fame player has spent the last 24 years working as a studio analyst for TNT, which could lose the rights...}

\entryitemWithDescription{\hskip 0pt{}Virginia city repeals ban on psychic readings as industry grows and gains more acceptance}{https://apnews.com/article/3d687dd365bdf799c4d9fd7ce0589fb9}{NORFOLK, Va. (AP) --- Ashley Branton has earned a living as a psychic medium for seven years, helping a growing number of people with heavy choices about toxic relationships, home purchases and cross-country moves. And while the tarot...}

\entryitemWithDescription{\hskip 0pt{}Move over grizzlies and wolves: Yellowstone visitors hope to catch a glimpse of rare white buffalo}{https://apnews.com/article/dd1d0613674df9879e81283d2a9f09a6}{YELLOWSTONE NATIONAL PARK, Wyo. (AP) --- Standing at the edge of a bluff overlooking the Lamar River in Yellowstone National Park, TJ Ammond stared through binoculars at hundreds of buffalo dotting the verdant valley below. Tan-colored...}

\entryitemWithDescription{\hskip 0pt{}Her dying husband worried she'd have money troubles. Then she won the lottery}{https://apnews.com/article/69183774077eee747454cd959aa66636}{FREEPORT, Pa. (AP) --- In the weeks before his death, Karen Coffman's husband worried she might have money troubles after he was gone. But two weeks before he died in April of complications from a brain tumor, the Pennsylvania woman...}

\entryitemWithDescription{\hskip 0pt{}Tejano singer and TV host Johnny Canales, who helped launch Selena's career, dies}{https://apnews.com/article/57f08320807cfb7977d624a28319f5e6}{Tejano singer and longtime television music show host Johnny Canales has died. He was 77. Canales' family confirmed his death in a statement posted Thursday on the Johnny and Nora Canales Show Facebook page. The post did not provide a...}

\entryitemWithDescription{\hskip 0pt{}NASA's Voyager 1, the most distant spacecraft from Earth, is doing science again after problem}{https://apnews.com/article/1b4a1f9f9adfa23d60b539301b3f035b}{DALLAS (AP) --- NASA's Voyager 1, the most distant spacecraft from Earth, is sending science data again. Voyager 1's four instruments are back in business after a computer problem in November, the Jet Propulsion Laboratory said this week...}

\entryitemWithDescription{\hskip 0pt{}Microsoft delays controversial AI Recall feature on new Windows computers}{https://apnews.com/article/6ba8df3f22e9fca599d20f2d5770cd95}{REDMOND, Wash. (AP) --- New laptops equipped with Microsoft Windows start shipping to customers next week without a flagship feature called Recall that drew concerns about privacy and cybersecurity. Microsoft CEO Satya Nadella touted the...}

\entryitemWithDescription{\hskip 0pt{}R.E.M. reunite at Songwriters Hall of Fame ceremony also honoring Timbaland and Steely Dan}{https://apnews.com/article/40a0909a1e8d403e3bcbe03a7bab738c}{NEW YORK (AP) --- A comet must have landed at the 2024 Songwriters Hall of Fame induction ceremony. The members of R.E.M. had joked only hours before it would take ``a comet'' to get the band to perform together one last time. Yet there...}

\entryitemWithDescription{\hskip 0pt{}Barkov, Bobrovsky and the Panthers beat the Oilers 4-3 to move within win of Stanley Cup title}{https://apnews.com/article/40cf3fc25c1935c1ca18f39ac096391a}{EDMONTON, Alberta (AP) --- Aleksander Barkov led the way offensively, Sergei Bobrovsky was in peak form in goal once again and the Florida Panthers are on the verge of lifting the Stanley Cup. Barkov set up a goal and scored another...}