\entryitemWithDescription{\hskip 0pt{}Children race to collect marshmallows dropped from a helicopter at a Detroit-area park}{https://apnews.com/article/ebc354cd8c8203ad835e4908158df63a}{SOUTHFIELD, Mich. (AP) --- It rained marshmallows at a suburban Detroit park on Friday as children raced to snatch up thousands of the gooey treats being dropped from a helicopter. The annual Great Marshmallow Drop took place at Catalpa...}

\entryitemWithDescription{\hskip 0pt{}California governor to deploy 500 surveillance cameras to Oakland to fight crime}{https://apnews.com/article/e4bd826bd13c2f406aa33d1bb723ac4e}{OAKLAND, Calif. (AP) --- Hundreds of high-tech surveillance cameras are being installed in the city of Oakland and surrounding freeways to battle crime, California Gov. Gavin Newsom announced Friday. Newsom, a Democrat, said in a news...}

\entryitemWithDescription{\hskip 0pt{}What stores are open on Easter Sunday 2024? See Walmart, Target, Costco hours}{https://apnews.com/article/e50a41a2ab375a72fbb4c3d72da3020f}{Easter-Stores-Open-Closed If the Easter bunny is still looking for basket stuffers, they better hop to it. Many stores will be closed in observance of the holiday. Easter is a Christian holiday, and also an occasion for dyed eggs and...}

\entryitemWithDescription{\hskip 0pt{}`Ozempig' remains Minnesota baseball team's mascot despite uproar that name is form of fat-shaming}{https://apnews.com/article/8fa84bf46d1a21802dad0d4ee9ba07a1}{For a Minnesota minor league baseball team known for a history of outlandish promotions, the idea of naming its longtime live pig mascot after the weight loss drug Ozempic made perfect sense. The St. Paul Saints quickly found out that not...}

\entryitemWithDescription{\hskip 0pt{}5 dead and over 100 hospitalized from recalled Japanese health supplements}{https://apnews.com/article/1ce6a27d6495e500e991e36581b2dbde}{TOKYO (AP) --- In the week since a line of Japanese health supplements began being recalled, five people have died and more than 100 people were hospitalized as of Friday. Osaka-based Kobayashi Pharmaceutical Co. came under fire for not...}

\entryitemWithDescription{\hskip 0pt{}Bus plunges off a bridge in South Africa, killing 45 people. An 8-year-old child is only survivor}{https://apnews.com/article/a5b31e9085a5f843f90d0582676ded37}{CAPE TOWN, South Africa (AP) --- A bus carrying worshippers headed to an Easter festival plunged off a bridge on a mountain pass and burst into flames in South Africa on Thursday, killing at least 45 people, authorities said. The only...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé's `Cowboy Carter' reinforces her dedication to Black reclamation — and country music}{https://apnews.com/article/9c865d00adf1f31f4bf22f126612e226}{LOS ANGELES (AP) --- First, Beyoncé arrived at the 2024 Grammy Awards in full cowboy regalia --- making a statement without saying a word. Then, during the Super Bowl, she dropped two hybrid country songs: ``Texas Hold `Em'' and ``16...}

\entryitemWithDescription{\hskip 0pt{}Michigan GOP lawmaker falsely claims that buses carrying March Madness teams are `illegal invaders'}{https://apnews.com/article/6217e5cda406954993a299329b98572b}{FARMINGTON HILLS, Mich. (AP) --- A Michigan state lawmaker involved in former President Donald Trump's election denials is being widely criticized after the Republican made false claims that buses carrying college athletes to Detroit for...}

\entryitemWithDescription{\hskip 0pt{}Flo Milli's new album proves the `Never Lose Me' rising artist's dreams of greatness are coming true}{https://apnews.com/article/3a81e06dc8d61fd7ddef09dc3aa11320}{NEW YORK (AP) --- Flo Milli always felt different from her peers growing up, believing she was destined for greatness. For her, the writing was always on the walls --- and in the stalls. ``In high school, I used to have a lot of girls...}

\entryitemWithDescription{\hskip 0pt{}NYC will try gun scanners in subway system in effort to deter violence underground}{https://apnews.com/article/fb22efbc2a5fd56b02fd6b2d95d75255}{NEW YORK (AP) --- New York City officials announced a pilot program on Thursday to deploy portable gun scanners in the subway system, part of an effort to deter violence underground and to make the system feel safer. The scanners will be...}

\entryitemWithDescription{\hskip 0pt{}The White House expects about 40,000 participants at its `egg-ucation'-themed annual Easter egg roll}{https://apnews.com/article/f1bbacddf2ae3b35812a5083ce12bc09}{Some 40,000 people are expected to participate in Monday's ``EGG-ucation''-themed White House Easter Egg Roll, about 10,000 more people than last year. A teacher for more than 30 years, Jill Biden is transforming an annual tradition first...}

\entryitemWithDescription{\hskip 0pt{}A fight to protect the dignity of Michelangelo's David raises questions about freedom of expression}{https://apnews.com/article/3fa1b7185fea36003e064fa6e2c309fd}{FLORENCE, Italy (AP) --- Michelangelo's David has been a towering figure in Italian culture since its completion in 1504. But in the current era of the quick buck, curators worry the marble statue's religious and political significance is...}

\entryitemWithDescription{\hskip 0pt{}Bob Uecker, 90, expected to broadcast Brewers' home opener, workload the rest of season uncertain}{https://apnews.com/article/240dcc23ee681d4631a633e0e903d3c9}{MILWAUKEE (AP) --- Bob Uecker will be back behind the microphone when the Milwaukee Brewers play their home opener Tuesday against the Minnesota Twins. How heavy a broadcasting workload the 90-year-old Uecker will have the rest of the...}