\entryitemWithDescription{\hskip 0pt{}`Star Wars' actor Mark Hamill drops by White House for a visit with `Joe-bi-Wan Kenobi'}{https://apnews.com/article/058ad8d8a17827d8e61ced61cd224a02}{WASHINGTON (AP) --- ``Star Wars'' actor Mark Hamill dropped by the White House on Friday for a visit with President Joe Biden and walked away with a pair of the president's aviator sunglasses and a greater respect for the office. ``I love...}

\entryitemWithDescription{\hskip 0pt{}Colorado school bus aide shown hitting autistic boy faces more charges}{https://apnews.com/article/dedeaf7f1f20ad85e12cdab82e683e93}{DENVER (AP) --- A school bus aide shown on surveillance video hitting a nonverbal autistic boy has been charged with 10 more counts of abuse involving two children, prosecutors said Friday. Kiarra Jones, 29, was arrested last month and...}

\entryitemWithDescription{\hskip 0pt{}South Dakota Gov. Noem erroneously describes meeting with North Korea's Kim Jong Un in new book}{https://apnews.com/article/90e61965e9ac486e52cec5b35da41f47}{WASHINGTON (AP) --- South Dakota Gov. Kristi Noem described in a new book having met with North Korean leader Kim Jong Un during her time in Congress. But her office said Friday that the story of the meeting was an error as further...}

\entryitemWithDescription{\hskip 0pt{}Distressed sawfish rescued in Florida Keys dies after aquarium treatment}{https://apnews.com/article/763706b297bfd08b130822183f0b0999}{SARASOTA, Fla. (AP) --- An endangered sawfish rescued last month in the Florida Keys after it was spotted acting erratically and swimming in circles has died as wildlife officials continue to search for what is causing fish to become...}

\entryitemWithDescription{\hskip 0pt{}The Eta Aquarid meteor shower, debris of Halley's comet, peaks this weekend. Here's how to see it}{https://apnews.com/article/ae413875e1c3178c3080e639dcc12eeb}{WASHINGTON (AP) --- The Eta Aquarid meteor shower, remnants of Halley's comet, peaks this weekend. And with just a waning crescent moon in the sky, it should be visible. The Eta Aquarids occur every year in early May. This year's peak...}

\entryitemWithDescription{\hskip 0pt{}Traffic snarled as workers begin removing bridge over I-95 following truck fire in Connecticut}{https://apnews.com/article/97b8a21a109e0e2f2186390c827e927a}{NORWALK, Conn. (AP) --- Workers on Friday began removing a bridge over a Connecticut highway that was damaged in a fiery crash involving a gasoline tanker truck --- a project expected to keep both sides of Interstate 95 closed through the...}

\entryitemWithDescription{\hskip 0pt{}Kenya president postpones reopening of schools as flood-related deaths pass 200}{https://apnews.com/article/70287228954b774fbe72ac9cabb1ee58}{NAIROBI, Kenya (AP) --- Kenyan President William Ruto has postponed next week's planned reopening of schools until further notice, as heavy rains and floods that have killed more than 200 people continue. The president in his state of the...}

\entryitemWithDescription{\hskip 0pt{}Former UK prime minister Boris Johnson turned away from polling station after forgetting photo ID}{https://apnews.com/article/038bf7bf72c7490137ec921a5242a2ef}{LONDON (AP) --- Former British Prime Minister Boris Johnson was turned away from a polling station after forgetting to bring ID to vote in the U.K.\textquotesingle s local elections. British media reported Friday that Johnson --- who...}

\entryitemWithDescription{\hskip 0pt{}China is sending a probe to get samples from the less-explored far side of the moon}{https://apnews.com/article/def5b9e054fbc3a681952d3c7ad002fe}{TAIPEI, Taiwan (AP) --- China is preparing to launch a lunar probe Friday that would land on the far side of the moon and return with samples that could provide insights into geological and other differences between the less-explored...}

\entryitemWithDescription{\hskip 0pt{}Fox News' Bill Hemmer heads north — way north — for look at U.S. military preparedness}{https://apnews.com/article/205978ac3e8cd2782aaa3e2a86760af0}{NEW YORK (AP) --- Fox News anchor Bill Hemmer needed a chain saw to complete one of his latest assignments. Hemmer traveled north for ``Battle for the Arctic,'' a documentary on the Fox Nation streaming service about the U.S. Navy's...}

\entryitemWithDescription{\hskip 0pt{}The first wrongful-death trial in Travis Scott concert deaths has been delayed}{https://apnews.com/article/a9164d7c7e6a06a14963a165833addd4}{HOUSTON (AP) --- The start of the first civil trial stemming from the 2021 Astroworld festival, at which 10 people were killed in a crowd surge, has been delayed. Jury selection had been set to begin next Tuesday in the wrongful-death...}

\entryitemWithDescription{\hskip 0pt{}Billie Jean King is getting the Breakfast of Champions treatment. She'll appear on a Wheaties box}{https://apnews.com/article/d46cafb8b9e890e1e3dbf0b184073f7d}{MINNEAPOLIS (AP) --- Billie Jean King is a 39-time Grand Slam champion and an equal rights champion --- and now she's getting the Breakfast of Champions treatment. The twice-inducted tennis Hall of Famer will appear on a limited-edition...}

\entryitemWithDescription{\hskip 0pt{}Britney Spears and Sam Asghari are officially divorced and single}{https://apnews.com/article/162471307c65330c233c51b3664e32da}{LOS ANGELES (AP) --- Britney Spears and Sam Asghari are officially divorced and single. The dissolution of the couple's marriage was finalized Friday by a Los Angeles County judge, nearly two years after the two were married. The judgment...}