\entryitemWithDescription{\hskip 0pt{}HBO estimates 2.9 million watched 'Succession' finale on Sunday night}{https://apnews.com/article/9bd47f9bfa7167bfbde00ad2f7ebb7c0}{This image released by HBO shows Matthew Macfadyen as Tom Wambsgans, left, and Nicholas Braun as Greg Hirsch in a scene from the series "Succession." (HBO via AP) NEW YORK (AP) --- HBO said 2.9 million people watched or streamed the...}

\entryitemWithDescription{\hskip 0pt{}Church associate arrested in death of pastor, councilwoman gunned down outside her New Jersey home}{https://apnews.com/article/37718f4023f270db246dc5dac53be802}{This undated photo provided by the Sayreville, N.J., Borough Council shows Sayreville Councilwoman Eunice Dwumfour. New Jersey prosecutors said Tuesday, May 30, 2023, that they arrested a Virginia man on murder and gun charges in the...}

\entryitemWithDescription{\hskip 0pt{}Delta Air Lines hit with lawsuit over claims of carbon neutrality}{https://apnews.com/article/469f2671010ba7f40c934cc23d62149a}{FILE - A Delta Air Lines plane takes off from Hartsfield-Jackson Atlanta International Airport in Atlanta, Nov. 22, 2022. A consumer class action lawsuit filed Tuesday, May 30, 2023, claims Delta Air Lines inaccurately billed itself as...}

\entryitemWithDescription{\hskip 0pt{}Ex-Trump White House official Peter Navarro to go on trial in September in Jan. 6 contempt case}{https://apnews.com/article/c0217332f2ed3282b0a15b94a63648d2}{FILE - Former White House trade adviser Peter Navarro listens as his legal team talk to members of the media outside the federal court in Washington, Aug. 31, 2022. Navarro is scheduled to stand trial in September on contempt of Congress...}

\entryitemWithDescription{\hskip 0pt{}Chipmaker Nvidia joins exclusive club of companies with a \$1 trillion market capitalization}{https://apnews.com/article/c2e5e41634dc4049209d4e1eba3836d8}{FILE - People gather in the Nvidia booth at the Mobile World Congress mobile phone trade show Thursday, Feb. 27, 2014 in Barcelona, Spain. Nvidia has joined the exclusive club of companies with a \$1 trillion market capitalization...}

\entryitemWithDescription{\hskip 0pt{}Ruling clears way for Purdue Pharma to settle opioid claims, protects Sacklers from lawsuits}{https://apnews.com/article/9d1f39c52d8d0f4f0c79960d930a5b84}{FILE - Jayde Newton helps to set up cardboard gravestones with the names of victims of opioid abuse outside the courthouse where the Purdue Pharma bankruptcy is taking place in White Plains, N.Y., on Aug. 9, 2021. A three-judge panel of...}

\entryitemWithDescription{\hskip 0pt{}Nuggets run to the NBA Finals stirs up memories of wonderful wackiness in the ABA}{https://apnews.com/article/9294860355b4db51adfb86ec3bce674e}{FILE - Denver Nuggets\textquotesingle{} Bobby Jones, second left, Nets\textquotesingle{} Julius Erving, fourth left, and New York Nets\textquotesingle{} Jim Eakins, right, battle for a rebound during the ABA championship playoff game at...}

\entryitemWithDescription{\hskip 0pt{}Biden attends memorial Mass to mark 8 years since son Beau's death from brain cancer}{https://apnews.com/article/e7458639de75afb28b159b5d733f8c56}{President Joe Biden, first lady Jill Biden and members of the Biden family walk to the grave of the president\textquotesingle s late son, Beau Biden, after attending a memorial mass at St. Joseph on the Brandywine Catholic Church in...}

\entryitemWithDescription{\hskip 0pt{}US ends probe into Tesla allowing video games while vehicles are moving, says feature was disabled}{https://apnews.com/article/9a72ae914d3920ff4f3ecb799ef5874e}{A worker stands next to a Tesla being charged in Beijing, Tuesday, May 30, 2023. China's foreign minister met Tesla Ltd. CEO Elon Musk on Tuesday and said strained U.S.-Chinese relations require ``mutual respect,'' while delivering a...}

\entryitemWithDescription{\hskip 0pt{}Norway says Beluga whale with apparent Russian-made harness swims south to Sweden}{https://apnews.com/article/4500803df50d82f30422886a614644ba}{In this photo taken in April 2019 a beluga whale found in Arctic Norway is feeded. Norwegian authorities say that a beluga whale first spotted in Arctic Norway in 2019 with an apparent Russian-made harness and alleged to have come from a...}

\entryitemWithDescription{\hskip 0pt{}No kidding: California overtime law threatens use of grazing goats to prevent wildfires}{https://apnews.com/article/3a547a83a0d94bd2db0a52cf2831daf5}{Goats graze on dry grass next to a housing complex in West Sacramento, Calif., on May 17, 2023. Goats are in high demand to clear vegetation as California prepares for the wildfire season, but a farmworker overtime law threatens the...}

\entryitemWithDescription{\hskip 0pt{}Offshore Typhoon Mawar lashes eastern Taiwan, northern Philippines as it heads for southern Japan}{https://apnews.com/article/23caae82aeb274003231541293b3ae2f}{Fishermen stay on a boat while taking shelter as Typhoon Mawar approaches to Taiwan in Yilan County, eastern coast of Taiwan, Tuesday, May 30, 2023. Typhoon Mawar lashed Taiwan\textquotesingle s eastern coast on Tuesday with wind, rains...}

\entryitemWithDescription{\hskip 0pt{}LGBTQ+ activists call for new strategies to promote equality after Target backlash}{https://apnews.com/article/a6872f755096647b0732cd5313b1b4b7}{A sign outside a Target store is seen Wednesday, May 24, 2023, in Nashville, Tenn. Target is removing certain items from its stores and making other changes to its LGBTQ+ merchandise nationwide ahead of Pride month after an intense...}