\entryitemWithDescription{\hskip 0pt{}Browns' plans for move to new dome stadium hits snag as county backs city's renovation proposal}{https://apnews.com/article/66055b5ad70ae6bf18e5057927dbba6d}{CLEVELAND (AP) --- The Browns' proposal to leave the lakefront and play in a new domed stadium in Cleveland's suburbs has hit a major snag. In a letter sent to team owners Dee and Jimmy Haslam, Cuyahoga County officials said Sunday they'...}

\entryitemWithDescription{\hskip 0pt{}Large desert tortoise rescued from Arizona highway after escaping from ostrich ranch 3 miles away}{https://apnews.com/article/0ad2ec215fed38a7b898b45430d28e3f}{PICACHO, Ariz. (AP) --- How long does it take a large desert tortoise to get to the other side of a southern Arizona highway? It's still a mystery, after a state Department of Public Safety trooper recently helped rescue an escaped...}

\entryitemWithDescription{\hskip 0pt{}Who won at the box office this weekend? The Reynolds-Lively household}{https://apnews.com/article/b5d25319d02489aa1c3b7bf2a786e5d7}{NEW YORK (AP) --- In the Ryan Reynolds-Blake Lively box-office showdown, both husband and wife came out winners. Reynolds' Marvel Studios smash ``Deadpool \& Wolverine'' remained the top movie in North American theaters for the third...}

\entryitemWithDescription{\hskip 0pt{}Billie Eilish, Snoop Dogg and Red Hot Chili Peppers to perform at Paris Olympics' closing ceremony}{https://apnews.com/article/dd3243e89611a50150087cf7ec36130c}{Follow along for the latest updates from today's Olympic action, including the gold medal men's basketball game between the U.S. and France. PARIS (AP) --- The closing ceremony for the Paris Olympics will bring out several stars: Billie...}

\entryitemWithDescription{\hskip 0pt{}American gymnast Jordan Chiles must return bronze medal after court mandates score change, IOC says}{https://apnews.com/article/d246c9d544faf9dfb44185ae3661e869}{Follow along for the latest updates from today's Olympic action, including the gold medal men's basketball game between the U.S. and France. PARIS (AP) --- American gymnast Jordan Chiles must return the bronze medal she won in the Paris...}

\entryitemWithDescription{\hskip 0pt{}World Boxing to announce major increase in membership after Paris in its bid to save Olympic boxing}{https://apnews.com/article/c65a0d40814f54e79d31af213a4bbf4c}{Follow along for the latest updates from today's Olympic action, including the gold medal men's basketball game between the U.S. and France. PARIS (AP) --- The nascent governing body fighting to keep boxing in the Olympics is about to get...}

\entryitemWithDescription{\hskip 0pt{}Harrison Ford, Miley Cyrus and more to be honored as Disney Legends at awards ceremony}{https://apnews.com/article/f989ab6ae9b024b39e842281380e2fd4}{ANAHEIM, Calif. (AP) --- Disney will bestow ``legends'' status to 14 artists, including Harrison Ford, Angela Bassett and Miley Cyrus, who have shaped the company. The honorees --- who the company says have had a ``significant impact'' on...}

\entryitemWithDescription{\hskip 0pt{}German open water athlete falls ill after swimming in the Seine River}{https://apnews.com/article/02d937f2d5f0fd20efafbf2250264aea}{Follow along for the latest updates from today's Olympic action. PARIS (AP) --- German swimmer Leonie Beck became ill after competing in the women's open water race at the Paris Olympics, despite assurances that the water in the Seine...}

\entryitemWithDescription{\hskip 0pt{}American b-boy Victor is among the quarterfinalists in first Olympic men's breaking event}{https://apnews.com/article/d228281403dd48342504e681cfbf83b8}{Follow along for the latest updates from today's Olympic action. PARIS (AP) --- B-boy Victor, an American two-time world champion, was among eight dancers to advance to the quarterfinals of the first Olympic men's breaking tournament on...}

\entryitemWithDescription{\hskip 0pt{}Mars and Jupiter get chummy in the night sky. The planets won't get this close again until 2033}{https://apnews.com/article/720b7f0cc67d4cb478f142eb846f3702}{CAPE CANAVERAL, Fla. (AP) --- Mars and Jupiter are cozying up in the night sky for their closest rendezvous this decade. They'll be so close Wednesday, at least from our perspective, that just a sliver of moon could fit between them. In...}

\entryitemWithDescription{\hskip 0pt{}Travis Scott remains in French police custody after altercation with security guard in Paris hotel}{https://apnews.com/article/91197786ba6c8074ec961b09ed48ce17}{PARIS (AP) --- Rapper Travis Scott remained in police custody after his arrest at a Paris hotel following an altercation with a security guard, French prosecutors said Saturday. A statement from the Paris prosecutor's office said the...}

\entryitemWithDescription{\hskip 0pt{}Large geological feature known as the `Double Arch' and the `Toilet Bowl' collapses in southern Utah}{https://apnews.com/article/7e13b23a72f825ba49f16b54ae86a815}{PAGE, Ariz. (AP) --- A large geological feature in southern Utah known as the ``Double Arch,'' the ``Hole in the Roof'' and sometimes the ``Toilet Bowl'' has collapsed, National Park Service officials said Friday. No injuries were...}

\entryitemWithDescription{\hskip 0pt{}Plane carrying Panthers players, coaches and staff gets stuck in the mud after landing in Charlotte}{https://apnews.com/article/07de6de2791823d3d3b57154f3f0e68a}{CHARLOTTE, N.C. (AP) --- Carolina Panthers players, coaches and staff members were unharmed after their Delta Airlines flight veered off the taxiway and got stuck in the mud while making its way to the gate at Charlotte Douglas...}