\entryitemWithDescription{\hskip 0pt{}Angels star Shohei Ohtani will have elbow surgery soon, out for the season because of oblique injury}{https://apnews.com/article/153797050423a70c15d45addc5224e7e}{ANAHEIM, Calif. (AP) --- Shohei Ohtani will have surgery soon on the ligament tear in his pitching elbow after the Los Angeles Angels' two-way star was ruled out for the rest of the season Saturday due to an oblique injury. Ohtani and the...}

\entryitemWithDescription{\hskip 0pt{}Comedian Russell Brand denies allegations of sexual assault published by three UK news organizations}{https://apnews.com/article/8e501489fc489fb66fe33f4e113d04e9}{LONDON (AP) --- Three British news organizations reported Saturday that comedian and social influencer Russell Brand has been accused of rape, sexual assault and abuse based on allegations from four women who knew him over a seven-year...}

\entryitemWithDescription{\hskip 0pt{}Italian air force aircraft crashes during an acrobatic exercise. A girl on the ground was killed}{https://apnews.com/article/fd7ec602db3186a12fea3f88e2b7263b}{MILAN (AP) --- An aircraft of the Italian acrobatic air team the Frecce Tricolori crashed on Saturday during a practice run outside the northern city of Turin, killing a child on the ground, Italian media reported. The plane or parts of...}

\entryitemWithDescription{\hskip 0pt{}Louisiana prisoner suit claims they're forced to endure dangerous conditions at Angola prison farm}{https://apnews.com/article/a091bf3375d091994d5814539dafb87f}{BATON ROUGE, La. (AP) --- Men incarcerated at Louisiana State Penitentiary filed a class-action lawsuit Saturday, contending they have been forced to work in the prison's fields for little or no pay, even when temperatures soar past 100...}

\entryitemWithDescription{\hskip 0pt{}Beer flows and crowds descend on Munich for the official start of Oktoberfest}{https://apnews.com/article/4e719c6ef30db862450674047bdc6498}{MUNICH (AP) --- The beer is flowing and millions of people descending on the Bavarian capital to celebrate the official opening of Oktoberfest. With the traditional cry of ``O'zapft is'' --- ``It's tapped'' --- Mayor Dieter Reiter...}

\entryitemWithDescription{\hskip 0pt{}Shohei Ohtani's locker has been packed up at Angel Stadium, and the Angels decline to say why}{https://apnews.com/article/d4daa9bed2115c35c5c7133d95c8d394}{ANAHEIM, Calif. (AP) --- Shohei Ohtani's locker has been mostly cleared out at Angel Stadium, and the Los Angeles Angels declined to say why Friday night. The two-way superstar missed his 11th consecutive game with an oblique muscle...}

\entryitemWithDescription{\hskip 0pt{}A preacher to death row inmates says he wants to end executions. Critics warn he's only seeking fame}{https://apnews.com/article/62ebfe9aa69ac8066d3562dcc96b9cbd}{OKLAHOMA CITY (AP) --- With just weeks left before his scheduled execution, Oklahoma death row inmate Anthony Sanchez took the unusual step of firing his attorneys and skipping a clemency hearing that many viewed as the last chance to...}

\entryitemWithDescription{\hskip 0pt{}Ashton Kutcher resigns as chair of anti-sex abuse organization after Danny Masterson letter}{https://apnews.com/article/b8ee3e125e7eb703eb0cae96d4564b1c}{LOS ANGELES (AP) --- Ashton Kutcher has resigned as chairman of the board of an anti-child sex abuse organization that he co-founded, after he and wife Mila Kunis wrote letters seeking leniency for their former ``That `70s Show'' co-star...}

\entryitemWithDescription{\hskip 0pt{}Hugh Jackman and Deborra-lee Jackman separate after 27 years of marriage}{https://apnews.com/article/f1fa97cf97b15a461fc479f4632cfa47}{NEW YORK (AP) --- Hugh Jackman and Deborra-lee Jackman have decided to end their marriage after 27 years and two children. ``We have been blessed to share almost 3 decades together as husband and wife in a wonderful, loving marriage. Our...}

\entryitemWithDescription{\hskip 0pt{}British neonatal nurse found guilty of murdering 7 babies launches bid to appeal her convictions}{https://apnews.com/article/6878518520a4d638c9ca3ef1000aca67}{LONDON (AP) --- A British neonatal nurse who was found guilty of murdering seven babies and the attempted murder of six others has launched a bid to appeal her convictions, officials said Friday. Lucy Letby, 33, was sentenced last month...}

\entryitemWithDescription{\hskip 0pt{}Alaska lawmaker's husband was flying meat from hunting camp when crash occurred, authorities say}{https://apnews.com/article/c28e0d1d496fc1465cb9c95a59e1d3f3}{ANCHORAGE, Alaska (AP) --- The plane flown by the husband of Alaska U.S. Rep. Mary Peltola was carrying a load of moose meat from a remote hunting camp when it crashed, killing him earlier this week, authorities said. Eugene Peltola Jr...}

\entryitemWithDescription{\hskip 0pt{}Tony Award-winner Michael McGrath, mourned as `adorable, mischievous, brilliant,' dies at 65}{https://apnews.com/article/f5fc39b08a95107c74fc6fb7250c33b4}{NEW YORK (AP) --- Michael McGrath, a Broadway character actor who shined in zany, feel-good musicals and won a Tony Award for ``Nice Work If You Can Get It,'' has died. He was 65. McGrath died Thursday at his home in Bloomfield, New...}

\entryitemWithDescription{\hskip 0pt{}Rep. Lauren Boebert apologizes after getting kicked out of show and falsely denying she vaped}{https://apnews.com/article/186d748f754d87a7441268744b0076cf}{DENVER (AP) --- Republican Rep. Lauren Boebert apologized Friday after getting kicked out of a musical play in Colorado last weekend for disruptive behavior and then falsely denying she had been vaping. The apology came a day after...}