\entryitemWithDescription{\hskip 0pt{}CANNES PHOTOS: Harrison Ford and Indiana Jones fever sweep Cannes on festival's 3rd day}{https://apnews.com/article/b8d2b7fdd0279beb4390f8a6286642f1}{Harrison Ford poses for photographers upon arrival at the premiere of the film \textquotesingle Indiana Jones and the Dial of Destiny\textquotesingle{} at the 76th international film festival, Cannes, southern France, Thursday, May 18...}

\entryitemWithDescription{\hskip 0pt{}Michigan boy who used slingshot to save sister says he 'was just lucky'}{https://apnews.com/article/e1617c360273d305d18025fb6e4b9383}{Andrew Burns, left, Owen Burns, center, and Margaret Burns pose with a slingshot Owen used to thwart an alleged kidnapping attempt of his sister, on Wednesday, May 17, 2023, in Alpena Township, Mich. The 13-year-old Michigan boy who used...}

\entryitemWithDescription{\hskip 0pt{}10K bridges similar to Pittsburgh one that collapsed should be checked for corrosion, report says}{https://apnews.com/article/c48540ffa35a062a0dfe246d1d240b6d}{FILE---This is a Pittsburgh Transit Authority bus that was on the Fern Hollow Bridge in Pittsburgh when it collapsed in this file photo from Jan. 28, 2022. Investigators looking into the collapse of the Pittsburgh bridge last year want...}

\entryitemWithDescription{\hskip 0pt{}At least 80 people were killed in an attack in northern Nigeria. Police arrested 7 suspects}{https://apnews.com/article/043596ecac029a7b5603cb3a0513732b}{ABUJA, Nigeria (AP) --- The death toll from an attack by dozens of gunmen in north central Nigeria\textquotesingle s Plateau state has reached 80, local authorities said Thursday, with survivors still searching for bodies days after the...}

\entryitemWithDescription{\hskip 0pt{}Will dashboard AM radio be saved? Bipartisan bill would require automakers to keep it in new cars}{https://apnews.com/article/ac3aa22e5db8d2acdc2448fe620c28f4}{FILE - A line of unsold 2018 Cooper Clubmen sit in a long row at a Mini dealership, March 30, 2018, in Highlands Ranch, Colo. Lawmakers on Capitol Hill are pushing to keep AM radio in the nation\textquotesingle s cars. A bipartisan group...}

\entryitemWithDescription{\hskip 0pt{}Mastodon bones unearthed by Michigan work crew go on display in museum}{https://apnews.com/article/294dd77ba8efe9eb10d6b9482d58933d}{Mastodon bones are displayed at the Grand Rapids Public Museum on Thursday, May 18, 2023, in Grand Rapids, Mich. The bones are part of an exhibit and were unearthed last year during a drainage dig in western Michigan and belonged to a...}

\entryitemWithDescription{\hskip 0pt{}Garth Brooks extends sold-out Las Vegas residency with 2024 dates}{https://apnews.com/article/d261db63f744d759f9611a70146f6b8b}{Host Garth Brooks speaks at the 58th annual Academy of Country Music Awards on Thursday, May 11, 2023, at the Ford Center in Frisco, Texas. (AP Photo/Chris Pizzello) LAS VEGAS (AP) --- Country music star Garth Brooks says his new Las...}

\entryitemWithDescription{\hskip 0pt{}Videos show purported ivory-billed woodpeckers as US moves toward extinction decision}{https://apnews.com/article/85c72ba92f27d06164c2a525890dbb4b}{FILE - An ivory-billed woodpecker specimen is on a display at the California Academy of Sciences in San Francisco, Friday, Sept. 24, 2021. New video and photographs purporting to show ivory-billed woodpeckers flying in a Louisiana forest...}

\entryitemWithDescription{\hskip 0pt{}Johnny Depp on his Cannes return and finding 'the basement to the bottom'}{https://apnews.com/article/da0d902bdfd902f9b21ef4ec4df60108}{Johnny Depp poses for portrait photographs for the film \textquotesingle Jeanne du Barry\textquotesingle, at the 76th international film festival, Cannes, southern France, Wednesday, May 17, 2023. (Photo by Joel C Ryan/Invision/AP...}

\entryitemWithDescription{\hskip 0pt{}Federal appeals court nominee withdraws in rare judicial defeat for Biden}{https://apnews.com/article/ceeca0f9ac4c0aa376c5fa7c8caf8290}{FILE - New Hampshire Attorney General Michael Delaney speaks about drug abuse issues in Concord, N.H., Feb. 22, 2013. The White House is expected to soon withdraw the nomination of Michael Delaney for the Boston-based 1st U.S. Circuit...}

\entryitemWithDescription{\hskip 0pt{}Remains of Georgia woman identified, confirmed as serial killer's 1977 victim}{https://apnews.com/article/5ebc64d8f92ddfafe9192beed6bcf2eb}{FILE - This Sept. 24, 2018, booking photo provided by the California Department of Corrections shows Samuel Little. The remains of a Georgia woman killed 46 years ago were identified and confirmed as a victim of Samuel Little, known as...}

\entryitemWithDescription{\hskip 0pt{}More than 30 million US drivers don't know if they're at risk from a rare but dangerous airbag blast}{https://apnews.com/article/8393a55574147c712d11d62f50ff249f}{File - Automobile traffic jams Route 93 South, Wednesday, July 14, 2021, in Boston. More than 33 million people in the United States are driving vehicles that contain a potentially deadly threat: Airbag inflators that in rare cases can...}

\entryitemWithDescription{\hskip 0pt{}Sam Zell, billionaire real estate investor, dies}{https://apnews.com/article/68dd59e71e5b4ad18308afa0b83c07f8}{FILE - Sam Zell, chairman of Equity Group Investments, and chairman of Equity International, smiles during an interview by Neil Cavuto, on the Fox Business Network, in New York, on Aug. 6, 2013. Zell, a Chicago real estate magnate who...}