\entryitemWithDescription{\hskip 0pt{}Minnesota officials say lodge that burned had 3 unresolved inspection violations}{https://apnews.com/article/ffb2fb37ff0e610ee345e6d76c434318}{ST. PAUL, Minn. (AP) --- Minnesota regulators said Wednesday that an historic lodge destroyed in a fire had three unresolved violations from a recent fire code inspection, but it wasn't clear if those violations played a role in the...}

\entryitemWithDescription{\hskip 0pt{}The Spurs held practice at a Miami Beach school. And kids there got a huge surprise}{https://apnews.com/article/801571b9af867e7b08583975d10bc44c}{MIAMI BEACH, Fla. (AP) --- Jacob Assaraf lost a bet, so he had to go through classes at Hebrew Academy on Wednesday wearing a suit instead of more casual attire. Turns out, that wasn't the most unusual part of his day. Members of the boys...}

\entryitemWithDescription{\hskip 0pt{}A sniper killed a Florida bank robber as he held a knife to a hostage's throat}{https://apnews.com/article/ce7595f0b3dda56a9c2e94cce09abf91}{FORT MYERS, Fla. (AP) --- A robber at a Florida bank took hostages after law enforcement arrived and was killed by a sheriff's sniper as he held a woman in a headlock with a knife to her throat, authorities said. Negotiators tried to...}

\entryitemWithDescription{\hskip 0pt{}Jury to decide on climate scientist Michael Mann's defamation suit over comparison to molester}{https://apnews.com/article/4246951093cd2a57e49cc9e0f38bf590}{WASHINGTON (AP) --- It's been 12 years since a pair of conservative writers compared a prominent climate scientist to a convicted child molester for his depiction of global warming. Now, a jury is about to decide whether the comments were...}

\entryitemWithDescription{\hskip 0pt{}Saturn's Death Star-looking moon may have vast underground ocean}{https://apnews.com/article/c506e45170f047096aaa5d093d05594c}{CAPE CANAVERAL, Fla. (AP) --- Astronomers have found the best evidence yet of a vast, young ocean beneath the icy exterior of Saturn's Death Star lookalike mini moon. The French-led team analyzed changes in Mimas' orbit and rotation and...}

\entryitemWithDescription{\hskip 0pt{}New York Community Bancorp tries to reassure investors, but its stock falls again}{https://apnews.com/article/adda7b9d0538ac8e1e29fc5cddadf9a9}{NEW YORK (AP) --- Shares of New York Community Bancorp fell another 10.5\% Wednesday after the bank's credit rating got downgraded to ``junk'' and investors worried the regional lender could suffer the same fate Silicon Valley Bank did...}

\entryitemWithDescription{\hskip 0pt{}Does Spain's popular Eurovision song `Zorra' insult women or defend them?}{https://apnews.com/article/07ac53321e07455651e5f550831e574c}{MADRID (AP) --- Spain's Eurovision song ``Zorra,'' whose title can be translated as an anti-female slur, is causing a storm among conservatives and feminists while Socialist Prime Minister Pedro Sánchez says he likes it. The song by the...}

\entryitemWithDescription{\hskip 0pt{}A pod of killer whales trapped in drift ice off northern Japan has apparently safely escaped}{https://apnews.com/article/5a2c6e1fa8b3f5a161ee608f4bb8f617}{TOKYO (AP) --- A pod of killer whales that was trapped in drift ice off Japan's northern main island of Hokkaido, prompting concern from environmental groups, has apparently safely escaped, officials said Wednesday. The killer whales...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift launches legal broadside at a college student who tracks private jets via public data}{https://apnews.com/article/c2a22089f84c9dcada4fca7ed138a399}{SAN FRANCISCO (AP) --- When it comes to dealing with a Florida college student who uses public data and social media to track the private jets of billionaires, politicians and other celebrities, Taylor Swift apparently can't just shake it...}

\entryitemWithDescription{\hskip 0pt{}Adult dancers in Washington state want a strippers' bill of rights. Here's how it could help them.}{https://apnews.com/article/c7b1ade1da1a0c42a19f73b6dbc731af}{SEATTLE (AP) --- For months, Andrea studied for her master's degree in library sciences between dancing naked at clubs in Seattle. But then she was sexually assaulted at work and slapped by a customer --- and nobody stepped in to help...}

\entryitemWithDescription{\hskip 0pt{}Coke hopes to excite younger drinkers with new raspberry-flavored Coca-Cola Spiced}{https://apnews.com/article/d9bd260ceac72cdb5ef1c1f3ad9bfb0a}{From Flamin' Hot Cheetos to Sweet Heat Starburst, America's snacks are getting spicier. Now, Coca-Cola wants in on the trend. On Wednesday, the Atlanta beverage giant introduced Coca-Cola Spiced, the first new permanent offering to its...}

\entryitemWithDescription{\hskip 0pt{}Former Ohio sheriff's deputy charged with murder testifies that the man he shot brandished gun}{https://apnews.com/article/2c46986d49612c5c75aacc17b9e9c4b9}{COLUMBUS, Ohio (AP) --- A former Ohio sheriff's deputy testified in a murder trial Tuesday that the man he killed lifted a gun to shoot him, despite prosecutors saying the man's gun was found on his kitchen floor with the safety mechanism...}

\entryitemWithDescription{\hskip 0pt{}Jam Master Jay's business partner says he grabbed a gun and sought whoever had killed the rap star}{https://apnews.com/article/d2d08ac74dc5d4fc5b7fb01fd7df2c1f}{Rap legend Jam Master Jay lay, mortally wounded, on his studio floor. One of his aides was in pain from a gunshot to the leg. Another was crying and screaming on the floor. Dashing in from an adjoining room, Randy Allen took in the bloody...}