\entryitemWithDescription{\hskip 0pt{}Dan Bongino, 'Unfiltered' Fox News host, leaving network}{https://apnews.com/article/e8dee7c39ae4307bd6e0b1120120f100}{FILE - Conservative commentator Dan Bongino speaks at the Conservative Political Action Committee annual conference in National Harbor, Md., on March 6, 2014. Fox News is parting ways with weekend host Bongino, after the former Secret...}

\entryitemWithDescription{\hskip 0pt{}Wyoming abortion clinic opens despite arson, legal obstacles}{https://apnews.com/article/f149c165fdaa0956fecdbff75488f7cb}{FILE - The fire-damaged Wellspring Health Access clinic is cordoned by tape on May 25, 2022, in in Casper, Wyo. Wyoming's first full-service abortion clinic in years defiantly opened Thursday, April, 20, 2023, nearly one year after an...}

\entryitemWithDescription{\hskip 0pt{}Gay pride parade canceled after anti-drag show law passes}{https://apnews.com/article/b0db01bf37576492637a5737f788f967}{PORT ST. LUCIE, Fla. (AP) --- Officials in a southeast Florida city have canceled a gay pride parade and restricted other pride events to people 21 years and older in anticipation of Republican Gov. Ron DeSantis signing a bill meant to...}

\entryitemWithDescription{\hskip 0pt{}Muslims end Ramadan, begin Eid holiday amid war, reconciliation}{https://apnews.com/article/edb6222035b545312cc464e626ea40a3}{Shiites observe the crescent moon to determine the start of the tenth Islamic month of Shawwal, which marks the end of a month-long fasting of Ramadan and the beginning of the Eid al-Fitr festival in Najaf, Iraq, Thursday, April 20...}

\entryitemWithDescription{\hskip 0pt{}Richard Riordan, former Los Angeles mayor, has died at 92}{https://apnews.com/article/5ffe9e5d48ad43ceb30b65864639e633}{FILE - Los Angeles Mayor Richard Riordan picks up a tip from a customer at his restaurant "The Pantry," Friday, June 29, 2001 in downtown Los Angeles. Riordan, the moderate Republican multimillionaire who won two terms as mayor in...}

\entryitemWithDescription{\hskip 0pt{}BuzzFeed to close news division, cut 15\% of all staff}{https://apnews.com/article/3105c3263998623d6acbee04ae5dfab1}{FILE - The entrance to BuzzFeed in New York is seen on Nov. 19, 2020. Pulitzer prize winning digital media company BuzzFeed is cutting about 15\% of its staff, according to multiple media reports. In a memo sent to staff, co-founder and...}

\entryitemWithDescription{\hskip 0pt{}US traffic deaths drop slightly in 2022 but still a 'crisis'}{https://apnews.com/article/6db6471e273b275920b6c4f9eb7e493b}{FILE - Traffic moves along the Interstate 76 highway on March 31, 2021, in Philadelphia. The number of people killed on U.S. roadways decreased slightly in 2022, but government officials said the 42,795 people who died is still a national...}

\entryitemWithDescription{\hskip 0pt{}Why is Karl Lagerfeld, the Met Gala theme, controversial?}{https://apnews.com/article/b0b79b075176852738713635080c6e2a}{FILE - German designer Karl Lagerfeld joins models, from left, American Cindy Crawford, Canadian Linda Evangelista and Claudia Schiffer of Germany after the presentation of his 1996 spring-summer ready-to-wear fashion collection for...}

\entryitemWithDescription{\hskip 0pt{}Tesla's price cuts drag share prices sharply lower}{https://apnews.com/article/4defe6cff38dd9c24639c30cd20944ae}{FILE - A sign bearing the Tesla company logo is displayed outside a Tesla store in Cherry Creek Mall in Denver, Colorado, Feb. 9, 2019. Tesla\textquotesingle s first-quarter vehicle sales in 2023 rose 36\% after the company cut prices...}

\entryitemWithDescription{\hskip 0pt{}Texan princess evicted from Rome villa, Caravaggio stays}{https://apnews.com/article/9abb47baaf8ca214755e3b8d59af9843}{Texas-born Princess Rita Boncompagni Ludovisi, born Rita Jenrette Carpenter and last wife of late Prince Nicolo Boncompagni Ludovisi, leaves her residence, The Casino dell\textquotesingle Aurora, also known as Villa Ludovisi, during the...}

\entryitemWithDescription{\hskip 0pt{}Michelin recalls tires that don't have enough snow traction}{https://apnews.com/article/09272ac5acdce9a1c723407b13869a58}{Snow coats the trees and cars in Edwards, Colo., Wednesday, March 22, 2023. The new snow was wet and heavy. (Chris Dillmann/Vail Daily via AP) DETROIT (AP) --- Michelin is recalling more than 542,000 light truck tires in the U.S. because...}

\entryitemWithDescription{\hskip 0pt{}AP image of Mariupol hospital attack wins World Press Photo}{https://apnews.com/article/699cb8362ac8cffefcec9496881fd9db}{FILE- Iryna Kalinina, 32, an injured pregnant woman, is carried from a maternity hospital that was damaged during a Russian airstrike in Mariupol, Ukraine, on 9 March 2022. Associated Press photographer Evgeniy Maloletka won the World...}

\entryitemWithDescription{\hskip 0pt{}\$252.6 million winning Powerball ticket sold in Ohio}{https://apnews.com/article/5506023262d64fb54556fb454a478615}{FILE - A Powerball lottery card rests on a table on Jan. 8, 2016, in Lyndhurst, Ohio. Someone in Ohio went to bed \$252.6 million richer, before taxes, after hitting the Powerball jackpot Wednesday night, April 19, 2023. (AP Photo/Tony...}