\entryitemWithDescription{\hskip 0pt{}COVID-19 pill Paxlovid moves closer to full FDA approval}{https://apnews.com/article/138d8c809c8519668e2c0bec6ab8ccba}{FILE - Doses of the anti-viral drug Paxlovid are displayed in New York, on Monday, Aug. 1, 2022. The COVID-19 medication won another vote of confidence from U.S. health advisors on Thursday, March 16, 2023, clearing the way for its full...}

\entryitemWithDescription{\hskip 0pt{}Microsoft adds AI tools to Office apps like Outlook, Word}{https://apnews.com/article/5a399068c29272b6841047535d9fd1c2}{FILE - In this July 3, 2014, file photo, the Microsoft Corp. logo is displayed outside the Microsoft Visitor Center in Redmond, Wash. Microsoft is infusing generative AI tools into its Office software, including Word, Excel and Outlook...}

\entryitemWithDescription{\hskip 0pt{}Why TikTok's security risks keep raising fears}{https://apnews.com/article/14ef5f93dc2114e4ade110b2e85433fd}{FILE - The icon for the video sharing TikTok app is seen on a smartphone, on Feb. 28, 2023. China accused the United States on Thursday, March 16, of spreading disinformation and suppressing TikTok following reports that the Biden...}

\entryitemWithDescription{\hskip 0pt{}Proposal to ban abortions at six weeks advances in Florida}{https://apnews.com/article/d104e6b69e27b9368265b6e450c1b028}{Florida Gov. Ron DeSantis answers questions from the media in the Florida Cabinet following his State of the State address during a joint session of the Senate and House of Representatives Tuesday, March 7, 2023, at the Capitol in...}

\entryitemWithDescription{\hskip 0pt{}Big banks create \$30B rescue package for First Republic}{https://apnews.com/article/9daaea0e7133007d5e7f8257030d1b1c}{A television screen displaying financial news is seen inside one of First Republic Bank\textquotesingle s branches in the Financial District of Manhattan, Thursday, March 16, 2023. The S\&P 500 was 0.8\% higher in midday trading after...}

\entryitemWithDescription{\hskip 0pt{}Pitino again a hot commodity at 70 and with checkered past}{https://apnews.com/article/b78aafde76213449c973139aa6e5bf70}{Iona head coach Rick Pitino calls out during the second half of an NCAA college basketball game against the Marist in the championship of the Metro Atlantic Athletic Conference Tournament, Saturday, March 11, 2023, in Atlantic City N.J...}

\entryitemWithDescription{\hskip 0pt{}Military moves to cut suicides, but defers action on guns}{https://apnews.com/article/950d57e49109aa9f0de76b2f6926ca75}{Secretary of Defense Lloyd Austin, speaks during a briefing with Chairman of the Joint Chiefs, Gen. Mark Milley at the Pentagon in Washington, Wednesday, March 15, 2023. (AP Photo/Andrew Harnik) WASHINGTON (AP) --- Defense Secretary Lloyd...}

\entryitemWithDescription{\hskip 0pt{}Floods fill some of California's summer strawberry fields}{https://apnews.com/article/7c9992cebb97f65c7a132aae3016680e}{This photo provided by the California Strawberry Commission shows a flooded Pajaro River area in Pajaro, Calif. on Tuesday, March 14, 2023. California\textquotesingle s strawberry farms have been hit hard by this year\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Kansas' Self, recovering from heart procedure, misses game}{https://apnews.com/article/482c51e6affea64f197c8dd9bbf13407}{Kansas head coach Bill Self applauds his team\textquotesingle s play against Texas Tech during the first half of an NCAA college basketball game in Lawrence, Kan., Tuesday, Feb. 28, 2023. (AP Photo/Reed Hoffmann) DES MOINES, Iowa (AP...}

\entryitemWithDescription{\hskip 0pt{}Nurses, paramedics reach pay deal to end England strikes}{https://apnews.com/article/9f3f526601253765677120aa10509abc}{FILE - Junior doctors hold placards on a picket line outside St Mary\textquotesingle s Hospital in London, Tuesday, March 14, 2023. Unions representing hundreds of thousands of nurses, ambulance crews and other health care workers in...}

\entryitemWithDescription{\hskip 0pt{}Senate takes first step in repealing Iraq War authorizations}{https://apnews.com/article/f5474c570fe133964d9d5dde57c765e2}{Sen. Tim Kaine, D-Va., center, and Sen. Todd Young, R-Ind., center left, are joined by representatives of the American Legion as they speak to reporters about ending the authorization for use of military force enacted after the Sept. 11...}

\entryitemWithDescription{\hskip 0pt{}Stephen Sondheim's last musical finds a New York City stage}{https://apnews.com/article/f042ae882dff593684b833eb10acb7fe}{Composer Stephen Sondheim appears at the premiere of "Sweeney Todd: The Demon Barber of Fleet Street" in New York on Dec. 3, 2007, left, and Joe Mantello appears the premiere of HBO Films\textquotesingle{} "The Normal Heart" in New York...}

\entryitemWithDescription{\hskip 0pt{}Family: Video of man's death shows 'absolute brutality'}{https://apnews.com/article/ed9d227abea1bfa6946aa7cade5ced8b}{Caroline Ouko, mother of Irvo Otieno, holds a portrait of her son with attorney Ben Crump, left, and her older son, Leon Ochieng at the Dinwiddie Courthouse in Dinwiddie, Va., on Thursday, March 16, 2023. Attorneys for the family of a...}