\entryitemWithDescription{\hskip 0pt{}Rioter who menaced officer with Confederate flag gets prison}{https://apnews.com/article/6057e74630701e1f77cf84aacbb3caaf}{Kevin Seefried, right, a Delaware man who stormed the Capitol with Confederate battle flag, departs Federal Court after sentencing, Thursday, Feb. 9, 2023, in Washington, with his public defender Eugene Ohm. Seefried, who threatened a...}

\entryitemWithDescription{\hskip 0pt{}Quebec parents recount moments after bus hit daycare center}{https://apnews.com/article/3173eaeef17bcc63abb88c9ba009dc63}{A woman stands next to a memorial at the site of a daycare centre in Laval, Quebec, Thursday, Feb. 9, 2023, where a bus crashed into the building killing two children. (Graham Hughes/The Canadian Press via AP) LAVAL, Quebec (AP...}

\entryitemWithDescription{\hskip 0pt{}Syria orphans from quake taken in by overwhelmed relatives}{https://apnews.com/article/9252308af8ceea28023782d506d73081}{Jana al-Abdo, 7 years-old, who was pulled from under the rubble after a 50-hour rescue operation caused by an earthquake that hit Syria and Turkey, receives treatment at a hospital run by the Syrian American Medical Society near the Bab...}

\entryitemWithDescription{\hskip 0pt{}Rihanna promises a 'jam-packed' Super Bowl halftime show}{https://apnews.com/article/1dee0e373be78ffa2c9785d5b05bfad1}{Rihanna poses for a photo after a halftime show news conference ahead of the Super Bowl 57 NFL football game, Thursday, Feb. 9, 2023, in Phoenix. (AP Photo/Mike Stewart) Rihanna is putting in the work ahead of her Super Bowl halftime...}

\entryitemWithDescription{\hskip 0pt{}Liquor before beer: Spirits beat brews in new market data}{https://apnews.com/article/464e8a74c984d1acd65d81ac6df17c52}{Gregory Megner, general manager and mixologist at Baltimore Spirits Company, pours two mixed drinks \_ a "Peanut Butter Jelly Thyme" on the left, and a "Best Cup of Coffee in a Manhattan" \_ containing whiskey distilled on premises...}

\entryitemWithDescription{\hskip 0pt{}Burt Bacharach, legendary composer of pop songs, dies at 94}{https://apnews.com/article/c1526b7c1b9b4389b17a3e657676b391}{FILE - Composer Burt Bacharach performs in Milan, Italy on July 16, 2011. The Grammy, Oscar and Tony-winning Bacharach died of natural causes Wednesday, Feb. 8, 2023, at home in Los Angeles, publicist Tina Brausam said Thursday. He was...}

\entryitemWithDescription{\hskip 0pt{}New "Toy Story," "Frozen" and "Zootopia" movies on tap}{https://apnews.com/article/509cb76c42ffe36f9d1020dcfff61826}{FILE - In this Aug. 8, 2017, file photo, The Walt Disney Co. logo appears on a screen above the floor of the New York Stock Exchange. Disney is working on sequels for its ``Toy Story,'' ``Frozen'' and ``Zootopia'' franchises as the...}

\entryitemWithDescription{\hskip 0pt{}Nicaragua frees 222 opponents of Ortega, sends them to US}{https://apnews.com/article/6e407b6d8c1c278a022d40328aa4a828}{FILE - Police stand guard at a holding center known as "El Chipote," officially called the Judicial Assistance Directorate, as they face demonstrators, on the other side of the fence, protesting the arrests of anti-government protesters...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl ads will tout Jesus 'gets us' to the masses}{https://apnews.com/article/424b36089913ff4a8639bbcf20c14ae3}{FILE - Dallas Cowboys quarterback Dak Prescott (4) points upward after scoring against Washington Commanders during the first half an NFL football game, Sunday, Jan. 8, 2023, in Landover, Md. While its Super Bowl commercial appearances...}

\entryitemWithDescription{\hskip 0pt{}Russian diplomat says ties with US in 'unprecedented crisis'}{https://apnews.com/article/cbc9e5e628564a6ac36caae94a082eb6}{FILE - Russian Deputy Foreign Minister Sergei Ryabkov attends a meeting in Moscow, Russia, Tuesday, March 15, 2022. A senior Russian diplomat says that Russia-U.S. relations are in a state of "unprecedented crisis" without any sign of...}

\entryitemWithDescription{\hskip 0pt{}Several universities to experiment with micro nuclear power}{https://apnews.com/article/86f6e0aadd29090b347ac2272c595d55}{Last Energy CEO Bret Kugelmass explains how power could be produced from a nuclear microreactor during a tour inside the company\textquotesingle s demonstration unit that contains a prototype reactor, Tuesday, Jan. 17, 2023, in...}

\entryitemWithDescription{\hskip 0pt{}FTX founder keeps talking, ignoring typical legal strategy}{https://apnews.com/article/e9c0be8d744dbccf289be82d6c29d79b}{Samuel Bankman-Fried departs Manhattan federal court in New York, Thursday, Feb. 9, 2023, in New York. (AP Photo/John Minchillo) NEW YORK (AP) --- For federal prosecutors, Sam Bankman-Fried could be the gift that keeps on giving. After...}

\entryitemWithDescription{\hskip 0pt{}US says China balloon could collect intelligence signals}{https://apnews.com/article/e45c759cb00294e83989fa35970935bc}{In this image provided by the FBI, FBI special agents assigned to the evidence response team process material recovered from the high altitude balloon recovered off the coast of South Carolina, Thursday, Feb. 9, 2023, at the FBI...}