\entryitemWithDescription{\hskip 0pt{}Samsung vies to make AI more mainstream by baking in more of the technology in its new Galaxy phones}{https://apnews.com/article/7e0a8d8d7aea1efc5b54c9301e53b684}{SAN JOSE, Calif. (AP) --- Smartphones could get much smarter this year as the next wave of artificial intelligence seeps into the devices that accompany people almost everywhere they go. Samsung, the biggest rival to Apple and its iPhone...}

\entryitemWithDescription{\hskip 0pt{}California Gov. Gavin Newsom says he won't sign a proposed ban on tackle football for kids under 12}{https://apnews.com/article/f3dfe0afb3e2ab809a1565d2c1a4d777}{SACRAMENTO, Calif. (AP) --- California Gov. Gavin Newsom said he will not sign a proposed ban on tackle football for children under 12, ending advocates' short-lived hopes of having the bill become law this year. ``I will not sign...}

\entryitemWithDescription{\hskip 0pt{}Helmet manufacturer: Mahomes' shattered lid in playoff game `did its job'}{https://apnews.com/article/213e5effa42271b79287dedf203dcba5}{KANSAS CITY, Mo. (AP) --- The manufacturer of the helmet that Chiefs quarterback Patrick Mahomes shattered during their AFC wild-card game with Miami says it ``did its job'' by protecting the league MVP ``during a head-to-head impact in...}

\entryitemWithDescription{\hskip 0pt{}Steely Dan, R.E.M., Timbaland, Hillary Lindsey and Dean Pitchford get into Songwriters Hall of Fame}{https://apnews.com/article/a1c7fbe1d470f45414c9fe87f78ad787}{NEW YORK (AP) --- Steely Dan, R.E.M., Timbaland, Hillary Lindsey and Dean Pitchford will be inducted into the Songwriters Hall of Fame, an incoming class of musicians who have scaled the heights of country, classic rock, pop, hip-hop and...}

\entryitemWithDescription{\hskip 0pt{}Coachella 2024: Lana Del Rey, Doja Cat and Tyler, the Creator to headline, No Doubt to reunite}{https://apnews.com/article/6c672b458c151dd142418193d319b9c8}{LOS ANGELES (AP) --- Music festival obsessives, the wait is over. The 2024 Coachella Valley Music and Arts Festival lineup is here. Lana Del Rey, Doja Cat and Tyler, the Creator will headline this year's festivities, joined by an...}

\entryitemWithDescription{\hskip 0pt{}Iowa Sen. Chuck Grassley, oldest member of Senate, hospitalized with infection}{https://apnews.com/article/ad1b263dff2d9d081f22fb34b479ee92}{WASHINGTON (AP) --- Iowa Sen. Chuck Grassley, the oldest member of the U.S. Senate, has been hospitalized in the Washington area with an infection and is receiving antibiotic infusions, his office said Tuesday. Grassley, 90, will return...}

\entryitemWithDescription{\hskip 0pt{}US fugitive accused of faking his death to avoid rape charges denies he is the suspect at hearing}{https://apnews.com/article/c58860e15ae8f4790c623bdfe8b058e8}{SALT LAKE CITY (AP) --- A man accused of faking his death and fleeing the U.S. to avoid rape charges in Utah denied at a court appearance Tuesday that he is the suspect and, in an apparent British accent, called allegations that he wasn't...}

\entryitemWithDescription{\hskip 0pt{}Wife of 49ers FB Kyle Juszczyk becomes designing star thanks to Taylor Swift}{https://apnews.com/article/475695716c93e5654390e6775dfc0ce7}{SANTA CLARA, Calif. (AP) --- For one night at least, San Francisco 49ers All-Pro fullback Kyle Juszczyk was not the biggest star in his family. All it took was pop superstar-turned-Chiefs fan Taylor Swift wearing a puffy winter coat...}

\entryitemWithDescription{\hskip 0pt{}Pharrell Williams' sophomore collection at Louis Vuitton showcases Americana, Native American spirit}{https://apnews.com/article/852b62a3ed4ecd39dc51c4e823327f43}{PARIS (AP) --- It was Wild West meets melting pot America at the Louis Vuitton Fall-Winter 2024 men's show Tuesday, where musician-turned-designer Pharrell Williams unveiled his highly-anticipated sophomore collection. The show, set...}

\entryitemWithDescription{\hskip 0pt{}Federal lawsuit accuses NY Knicks owner James Dolan, media mogul Harvey Weinstein of sexual assault}{https://apnews.com/article/beda85d53094dcec80123c4c7ce3a720}{LOS ANGELES (AP) --- A woman has alleged that New York Knicks owner James Dolan sexually assaulted her a decade ago and then set her up to be molested by now-imprisoned film producer Harvey Weinstein, according to a federal lawsuit filed...}

\entryitemWithDescription{\hskip 0pt{}CEO of Barstool Sports announces she's leaving, saying `the work I came here to do is done'}{https://apnews.com/article/2555e7b6e281ec1357f1931ce8fb7772}{NEW YORK (AP) --- Erika Ayers Badan will step down as CEO of Barstool Sports, the media brand that has grown explosively over the past decade, she said Tuesday. Badan said in a social media video that she feels ``like the work I came here...}

\entryitemWithDescription{\hskip 0pt{}Wrestler Hulk Hogan helps rescue teenage girl trapped after Florida car crash}{https://apnews.com/article/9717a7bee6d0d0f1276f43a18fc8d5c2}{TAMPA, Fla. (AP) --- Retired wrestler Hulk Hogan and a friend rescued a teenage girl who was trapped in an overturned vehicle after a crash in Florida, according to Hogan's social media posts. Hogan said on the social media platform X...}

\entryitemWithDescription{\hskip 0pt{}Sean `Diddy' Combs and Diageo settle, withdraw lawsuits in case that accused Diageo of racism}{https://apnews.com/article/3b554f9d03e007139484a6c7e0cf5bd4}{Rapper and entrepreneur Sean ``Diddy'' Combs has withdrawn his lawsuit against Diageo as part of a settlement with the London-based spirits giant. Combs and Diageo ``have now agreed to resolve all disputes between them,'' the two parties...}