\entryitemWithDescription{\hskip 0pt{}President Biden to end COVID-19 emergencies on May 11}{https://apnews.com/article/2a80b547f6d55706a6986debc343b9fe}{President Joe Biden talks with reporters on the South Lawn of the White House in Washington, Monday, Jan. 30, 2023, after returning from an event in Baltimore on infrastructure. (AP Photo/Susan Walsh) WASHINGTON (AP) --- President Joe...}

\entryitemWithDescription{\hskip 0pt{}Dems urge Biden to halt aid to Peru over protest crackdown}{https://apnews.com/article/518fac934a1ad6209d90434030889e55}{Anti-government protesters take refuge behind shields as police launch tear gas, in Lima, Peru, Saturday, Jan. 28, 2023. Protesters are seeking immediate elections, Boluarte\textquotesingle s resignation, the release of ousted President...}

\entryitemWithDescription{\hskip 0pt{}Treasury to increase borrowing amid debt ceiling standoff}{https://apnews.com/article/7ac35fbced6c3ed98228dc77c8e3e70d}{FILE - The Department of the Treasury\textquotesingle s seal outside the Treasury Department building in Washington on May 4, 2021. The national debt is at the core of a dispute about how to raise the government\textquotesingle s legal...}

\entryitemWithDescription{\hskip 0pt{}Dolphins, humans both benefit from fishing collaboration}{https://apnews.com/article/47621bd822b462a91ba81bcf0c6ed4ee}{In this 2008 photo, provided by Oregon State University, dolphin jump in front of fishermen at Praia da Tesoura, in Laguna, Brazil. In the seaside city of Laguna, scientists have, for the first time, used drones, underwater sound...}

\entryitemWithDescription{\hskip 0pt{}Defense faults crime scene collection in Alex Murdaugh trial}{https://apnews.com/article/24bed84d6a6c9564372148447dd9cd03}{Defendant Alex Murdaugh listens to testimony during his double murder trial at the Colleton County Courthouse in Walterboro, S.C., Friday, Jan. 27, 2023. The 54-year-old attorney is standing trial on two counts of murder in the shootings...}

\entryitemWithDescription{\hskip 0pt{}West Virginia advances school mandate on 'In God We Trust'}{https://apnews.com/article/e45fbd9f9c94c3536b849b5432ec84e5}{CHARLESTON, W.Va. (AP) --- Public schools in West Virginia may soon be required to display the phrase ``In God We Trust'' in every building if a bill passed by the state Senate on Monday becomes law. The bill was introduced by Republican...}

\entryitemWithDescription{\hskip 0pt{}Ex-Twitter execs to testify on block of Hunter Biden story}{https://apnews.com/article/adc0f668c76ac9a7099cd357679fb29d}{FILE - A sign at Twitter headquarters is shown in San Francisco, Dec. 8, 2022. The House Oversight Committee is set to hear testimony from former Twitter employees involved in the social media platform's handling of reporting on President...}

\entryitemWithDescription{\hskip 0pt{}Michael Jackson's nephew to star in King of Pop biopic}{https://apnews.com/article/7891fadc3607e778acda766c4fc1d754}{Jaafar Jackson appears during the "Living with The Jacksons" panel at the Reelz Channel 2014 Summer TCA in Beverly Hills, Calif., on July 12, 2014, left, and Michael Jackson appears at the American Cinema Award gala in Beverly Hills...}

\entryitemWithDescription{\hskip 0pt{}Purdue a unanimous No. 1 in AP Top 25; Vols up to No. 2}{https://apnews.com/article/4ff69267d009d9fe361b7d1eabfaac25}{Purdue center Zach Edey (15) moves to the basket between Michigan State center Mady Sissoko (22) and guard A.J. Hoggard (11)during the second half of an NCAA college basketball game in West Lafayette, Ind., Sunday, Jan. 29, 2023. Purdue...}

\entryitemWithDescription{\hskip 0pt{}Hall of Famer Bobby Hull, the Golden Jet, dies at 84}{https://apnews.com/article/78205480b86961baee2a5d517d7e6910}{FILE - Former Chicago Blackhawks player Bobby Hull is introduced to fans during the NHL hockey team\textquotesingle s convention in Chicago, July 26, 2019. Hull, a Hall of Fame forward who helped the Blackhawks win the 1961 Stanley Cup...}

\entryitemWithDescription{\hskip 0pt{}6th Memphis officer relieved of duty in Nichols arrest}{https://apnews.com/article/179a49b0e8b1c6494af2e6408581d47f}{A group of demonstrators protest outside a police precinct in response to the death of Tyre Nichols, who died after being beaten by Memphis police officers, in Memphis, Tenn., Sunday, Jan. 29, 2023. (AP Photo/Gerald Herbert) Church-goers...}

\entryitemWithDescription{\hskip 0pt{}Fed, set to impose smaller hike, may hint of fewer increases}{https://apnews.com/article/13723ffd05b1de3661248a8afc33abcd}{FILE - Federal Reserve chairman Jerome Powell appears on a monitor on the floor of the New York Stock Exchange in New York, Wednesday, Nov. 2, 2022. The Federal Reserve is poised this week to raise its benchmark interest rate for an...}

\entryitemWithDescription{\hskip 0pt{}Trevor Noah returns as Grammy host with comfort, nervousness}{https://apnews.com/article/a34c9d3b22f001321e1d17664b57f984}{FILE - Trevor Noah appears at the 63rd annual Grammy Awards in Los Angeles on March 14, 2021. Noah is hosting the Grammy Awards for a third-straight year. (Photo by Jordan Strauss/Invision/AP, File) LOS ANGELES (AP) --- Trevor Noah feels...}