\entryitemWithDescription{\hskip 0pt{}Gene Herrick, AP photographer who covered the Korean war and civil rights, dies at 97}{https://apnews.com/article/99c286e7b6802a626e23655605c7e2a0}{RICH CREEK, Va. (AP) --- Gene Herrick, a retired Associated Press photographer who covered the Korean War and is known for his iconic images of Martin Luther King Jr., Rosa Parks and the trial of the killers of Emmett Till in the early...}

\entryitemWithDescription{\hskip 0pt{}Divisive? Not for moviegoers. `Civil War' declares victory at box office.}{https://apnews.com/article/0933dabd6d399e3c10c2cd49378a102d}{Alex Garland's provocative `` Civil War '' didn't only ignite the discourse. The film also inspired audiences to go to the cinemas this weekend where it surpassed expectations and earned \$25.7 million in ticket sales in North America...}

\entryitemWithDescription{\hskip 0pt{}Pereira retains light heavyweight title with 1st-round KO of Hill at UFC 300}{https://apnews.com/article/b17cd3a05126abcb4af231ac7d6db00c}{LAS VEGAS (AP) --- Light heavyweight champion Alex Pereira knocked out top-ranked challenger Jamahal Hill at 3:14 of the first round in UFC 300 on Saturday night. Pereira dropped Hill to the canvas with a straight left hand and then...}

\entryitemWithDescription{\hskip 0pt{}The French connection: Paris flame to make first stop in Greece at heart of modern games' founder}{https://apnews.com/article/3d61ba905b606c87456c6cbeab355825}{ANCIENT OLYMPIA, Greece (AP) --- Just outside the site of the ancient Olympic Games, hooting owls break the nighttime silence at a white marble monument containing what's left of a singular Frenchman's heart. Baron Pierre de Coubertin was...}

\entryitemWithDescription{\hskip 0pt{}How the Masters gnomes became coveted collector's items}{https://apnews.com/article/9b7361d3ea99df6862189ce5caeb8648}{AUGUSTA, Ga. (AP) --- Gnomes, those quirky statues that people put in their gardens, are flying off the shelves at Augusta National. The Masters golf-centric gnomes been selling out within a couple of hours each morning after the...}

\entryitemWithDescription{\hskip 0pt{}Oldest living conjoined twins, Lori and George Schappell, die at 62}{https://apnews.com/article/72f6762bbe12642cd8c40a4051558494}{READING, Pa. (AP) --- Conjoined twins Lori and George Schappell, who pursued separate careers, interests and relationships during lives that defied medical expectations, died this month in Pennsylvania, according to funeral home...}

\entryitemWithDescription{\hskip 0pt{}`The ride of our lives': Wrexham gains promotion to English soccer's third division after 6-0 win}{https://apnews.com/article/26ffd83ae51bd40568f83c021f8257ab}{WREXHAM, Wales (AP) --- The sequel turned out to be just as good for Wrexham. The Welsh team co-owned by actor Ryan Reynolds clinched promotion to the third tier of English soccer thanks to a 6-0 home win over Forest Green on Saturday...}

\entryitemWithDescription{\hskip 0pt{}Executor of O.J. Simpson's estate plans to fight payout to the families of Brown and Goldman}{https://apnews.com/article/d34f28de478a07c3689547296f7228fd}{LAS VEGAS (AP) --- The executor of O.J. Simpson's estate says he will work to prevent a payout of a \$33.5 million judgment awarded by a California civil jury nearly three decades ago in a wrongful death lawsuit filed by the families of...}

\entryitemWithDescription{\hskip 0pt{}Right whale is found entangled off New England in a devastating year for the vanishing species}{https://apnews.com/article/cf694431333c9dec9cd1fd3e4f45d179}{PORTLAND, Maine (AP) --- A North Atlantic right whale has been spotted entangled in rope off New England, worsening an already devastating year for the vanishing animals, federal authorities said. The right whales number less than 360 and...}

\entryitemWithDescription{\hskip 0pt{}Argentina's populist president meets billionaire Elon Musk in Texas — and a bromance is born}{https://apnews.com/article/7af43102c5dcf5398a97d1010463f5a1}{BUENOS AIRES, Argentina (AP) --- One is an erratic billionaire entrepreneur and self-declared free-speech absolutist, prone to profanity-laden rants against ``wokeness'' and obsessed with making humanity a multi-planetary species. The...}

\entryitemWithDescription{\hskip 0pt{}Eleanor Coppola, matriarch of a filmmaking family, dies at 87}{https://apnews.com/article/d1174964d8fef8a1b63ced6a9387f62b}{Eleanor Coppola, who documented the making of some of her husband Francis Ford Coppola's iconic films, including the infamously tortured production of ``Apocalypse Now,'' and who raised a family of filmmakers, has died. She was 87...}

\entryitemWithDescription{\hskip 0pt{}Sheriff believes body in burned SUV to be South Florida woman who went missing after carjacking}{https://apnews.com/article/5a9ff783cb6a74b8dfde3aeb621c041f}{WINTER SPRINGS, Fla. (AP) --- Authorities in central Florida said they believe they've found the body of a South Florida woman who was taken in a carjacking. Katherine Altagracia Guerrero De Aguasvias, 31, of Homestead, was attacked and...}

\entryitemWithDescription{\hskip 0pt{}Italian fashion designer Roberto Cavalli has died at age 83, his company says}{https://apnews.com/article/0a0d4d0b3402f63c386cafc4519a7e2e}{ROME (AP) --- Italian fashion designer Roberto Cavalli, known for a flamboyant and glamorous style, has died at age 83, his company said Friday on Instagram. ``Dear Roberto, you may not be physically here with us anymore but I know I will...}