\entryitemWithDescription{\hskip 0pt{}Chef and TV personality Michael Chiarello dies at 61 after being treated for allergic reaction}{https://apnews.com/article/2492bed7e400b0d04c1d8244644ad627}{NEW YORK (AP) --- Michael Chiarello, a chef known for his Italian-inspired Californian restaurants who won an Emmy Award for best host for ``Easy Entertaining With Michael Chiarello'' and appeared on Bravo's ``Top Chef'' and ``Top Chef...}

\entryitemWithDescription{\hskip 0pt{}Louisiana public school principal apologizes after punishing student for dancing at a party}{https://apnews.com/article/82e706e9f63828fac685f65514362626}{WALKER, La. (AP) --- A Louisiana public school principal has apologized for punishing a student and questioning her religious beliefs after he saw a video of her dancing at an off-campus party. The 17-year-old student government president...}

\entryitemWithDescription{\hskip 0pt{}`Frasier' returns to TV but you don't need to be a superfan of the original to laugh at its jokes}{https://apnews.com/article/5c1a887d0b8ee3c5386523196ec86617}{You could say Joe Cristalli tweeted his role as co-executive producer and co-showrunner on the new ``Frasier'' sitcom into existence. About 10 years ago as a fledgling TV writer and ``Frasier'' super fan, Cristalli started a Twitter...}

\entryitemWithDescription{\hskip 0pt{}Chiefs star Travis Kelce shakes off an ankle injury with a key TD catch after his brief absence}{https://apnews.com/article/c8292645dc17ed7c15687a394311e977}{MINNEAPOLIS (AP) --- Travis Kelce was hurting at halftime, having limped off the field with an injury to his right ankle and Kansas City in a tied game at Minnesota. Patrick Mahomes knew better than to bother his close friend and favorite...}

\entryitemWithDescription{\hskip 0pt{}Unstoppable Simone Biles wraps up world championships comeback with 2 more gold medals}{https://apnews.com/article/3dcdfab536e0aa80fe224e2ae70b6e3e}{ANTWERP, Belgium (AP) --- Simone Biles was not too worried about the medal count, or the color of the medals, at the gymnastics world championships this week. That approach has sure paid off. The American superstar claimed a third, then a...}

\entryitemWithDescription{\hskip 0pt{}American mountaineer, local guide dead after avalanches hit Tibetan mountain. Two others are missing}{https://apnews.com/article/d9efbfeb74cc15f6bb1348d563543c44}{BEIJING (AP) --- American mountaineer Anna Gutu and a Nepalese guide Mingmar Sherpa were confirmed Sunday dead after avalanches struck the slopes of a Tibetan mountain, while two others remained missing, according to Chinese media...}

\entryitemWithDescription{\hskip 0pt{}An app shows how ancient Greek sites looked thousands of years ago. It's a glimpse of future tech}{https://apnews.com/article/273f4a1c64c6aa72a1c3c3d39e34d252}{ATHENS, Greece (AP) --- Tourists at the Acropolis this holiday season can witness the resolution of one of the world's most heated debates on cultural heritage. All they need is a smartphone. Visitors can now pinch and zoom their way...}

\entryitemWithDescription{\hskip 0pt{}Powerball jackpot up to \$1.55 billion as lottery losing streak continues}{https://apnews.com/article/0b897001206521758101be4d04c3ee6c}{DES MOINES, Iowa (AP) --- The Powerball jackpot climbed to an estimated \$1.55 billion after no one matched the game's six numbers Saturday and won the giant prize. The numbers drawn Saturday night were: 47, 54, 57, 60, 65 and red...}

\entryitemWithDescription{\hskip 0pt{}Albuquerque International Balloon Fiesta brings colorful displays to the New Mexico sky}{https://apnews.com/article/7350b1139ecaf2cfdab94c64b2dd6aec}{The Albuquerque International Balloon Fiesta has brought colorful displays to the New Mexico sky in an international event that attracts hundreds of thousands of spectators every year. The event started Saturday with a drone light show...}

\entryitemWithDescription{\hskip 0pt{}21 Savage cleared to legally travel abroad with plans of international performance in London}{https://apnews.com/article/e1df9a9a4d513ad388eb620192758453}{LOS ANGELES (AP) --- Rapper 21 Savage can now legally travel outside the United States and plans to make his international performance in his native London. Savage's lawyer, Charles Kuck, told The Associated Press in a statement Friday...}

\entryitemWithDescription{\hskip 0pt{}New witnesses share what they saw in the woods during a secretive FBI hunt for Civil War gold}{https://apnews.com/article/6b5feca00ebf3e04638a8bbce992809d}{PENFIELD, Pa. (AP) --- In the heart of Pennsylvania elk country, Eric McCarthy and his client, Don Reichel, got up before sunrise to scour the forest floor for so-called ``brown gold'' --- a rack of freshly shed antlers to add to Reichel'...}

\entryitemWithDescription{\hskip 0pt{}Man who attacked Capitol with tomahawk and now promotes Jan. 6 merchandise gets 7 years in prison}{https://apnews.com/article/d33fd96d4a8a747748d2a0a8adfb56d2}{WASHINGTON (AP) --- A Texas man who attacked the U.S. Capitol with a metal tomahawk --- and is now the face of a website selling merchandise portraying jailed rioters as ``political prisoners'' --- was sentenced Friday to seven years...}

\entryitemWithDescription{\hskip 0pt{}Broncos trade benched pass rusher Randy Gregory to 49ers in deal including swap of 2024 draft picks}{https://apnews.com/article/80bfda2b1b9d27275541223dd1be890b}{The Broncos on Friday traded benched pass rusher Randy Gregory to the San Francisco 49ers in a deal that also includes the exchange of 2024 draft picks, with Denver sending over a seventh-round selection for a sixth-round choice. Broncos...}