\entryitemWithDescription{\hskip 0pt{}Devastation followed by desperation in Acapulco after Hurricane Otis rips through}{https://apnews.com/article/7a09faf0d3c703b445f6a99d06b3e4cc}{ACAPULCO, Mexico (AP) --- First came the devastation, then people's desperation. Hurricane Otis blasted the Mexican tourist port of Acapulco like no other storm before in the Eastern Pacific. As a monstrous Category 5 meteor, with its 165...}

\entryitemWithDescription{\hskip 0pt{}A salty problem for people near the mouth of the Mississippi is a wakeup call for New Orleans}{https://apnews.com/article/1a55ad43ce83419247642929629377b2}{NEW ORLEANS (AP) --- The heating element removed from Monique Plaisance's water heater in September was disintegrating, streaked with rust and covered in a dry crust. She blamed the corrosion on the water piped in from the area's longtime...}

\entryitemWithDescription{\hskip 0pt{}The White House and Google launch a new virtual tour with audio captions, Spanish translation}{https://apnews.com/article/d422c4ede3424643fc131d6fb24e2636}{WASHINGTON (AP) --- Can't come to Washington? Couldn't get a ticket to tour the White House? Don't worry. The White House, Google Maps and Google Arts \& Culture launched a new virtual tour of the famous mansion on Friday, which is also...}

\entryitemWithDescription{\hskip 0pt{}DC pandas will be returning to China in mid-November, weeks earlier than expected}{https://apnews.com/article/96c106c85143621e29bcc579a24c068d}{WASHINGTON (AP) --- The National Zoo's three celebrity giant pandas will be heading home a little earlier than expected. Zoo officials told The Associated Press on Thursday that adult bears Mei Xiang and Tian Tian and their cub Xiao Qi Ji...}

\entryitemWithDescription{\hskip 0pt{}Arizona Diamondbacks take series of slights into surprise World Series against Texas Rangers}{https://apnews.com/article/fbd22417810138c1cfe396aa7c2bdfbd}{ARLINGTON, Texas (AP) --- Before opening the World Series, the Arizona Diamondbacks wanted to recount a series of slights. Overlooked by oddsmakers and angered by analysts, the Diamondbacks find themselves in a Surprise Series against the...}

\entryitemWithDescription{\hskip 0pt{}Radio host Larry Elder ends Republican presidential campaign and endorses Donald Trump}{https://apnews.com/article/a3d3665cd50d1e0d2071ab8800075482}{Conservative talk radio host Larry Elder announced Thursday that he was ending his 2024 Republican campaign for president and endorsing former President Donald Trump. Elder, who sought to replace California Gov. Gavin Newsom in a failed...}

\entryitemWithDescription{\hskip 0pt{}Ottawa's Shane Pinto suspended 41 games, becomes the 1st modern NHL player banned for gambling}{https://apnews.com/article/09cbedc1d9257fede6ec59251e76a914}{The NHL suspended Ottawa Senators forward Shane Pinto for 41 games on Thursday, making the 22-year-old American the first modern-day hockey player banned for sports gambling. The league said the half-season ban was for ``activities...}

\entryitemWithDescription{\hskip 0pt{}The last new Beatles song, `Now And Then,' will be released next week}{https://apnews.com/article/e7b3a349b0e1e58b8668e98ba2d9cd0b}{NEW YORK (AP) --- Sixty years after the onset of Beatlemania and with two of the quartet now dead, artificial intelligence has enabled the release next week of what is promised to be the last ``new'' Beatles song. The track, called ``Now...}

\entryitemWithDescription{\hskip 0pt{}China sends its youngest-ever crew to space as it seeks to put astronauts on moon before 2030}{https://apnews.com/article/0e538a1519b8fa7056078e2b968b52fa}{JIUQUAN SATELLITE LAUNCH CENTER, China (AP) --- China launched its youngest-ever crew for its orbiting space station on Thursday as it seeks to put astronauts on the moon before 2030. The Shenzhou 17 spacecraft lifted off from the Jiuquan...}

\entryitemWithDescription{\hskip 0pt{}No. 1 pick Wembanyama scores 15 points in NBA debut as Spurs fall to Mavericks in opener}{https://apnews.com/article/a0d4aa8851311110a55b59da9eb84023}{SAN ANTONIO (AP) --- The Victor Wembanyama era is underway in San Antonio. Wembanyama made his NBA debut with the Spurs against the Dallas Mavericks on Wednesday night and made an immediate splash. ``He's going to be amazing, he already...}

\entryitemWithDescription{\hskip 0pt{}Rep. Bowman of New York charged with misdemeanor, to pay fine after triggering House fire alarm}{https://apnews.com/article/1b9f8559a741a982116f7e8a4b6c6ac5}{WASHINGTON (AP) --- Democratic Rep. Jamaal Bowman was charged Wednesday with a misdemeanor for triggering a fire alarm as lawmakers scrambled to pass a funding bill before a government shutdown deadline in September. He is expected to...}

\entryitemWithDescription{\hskip 0pt{}Bud Light to return as the UFC's official beer next year as it recovers from a conservative backlash}{https://apnews.com/article/000522bcef9f691be9cb388616480392}{NEW YORK (AP) --- Bud Light is set to return as the official beer of the UFC in the U.S. next year as the brand tries to recover from a conservative backlash to a promotion with a transgender influencer. Under a new multiyear marketing...}

\entryitemWithDescription{\hskip 0pt{}First ever Florida Man games will feature beer belly wrestling and `evading arrest' obstacle course}{https://apnews.com/article/baba548edfa25a963b823ae0023fb227}{ST. AUGUSTINE, Fla. (AP) --- It ain't the Olympics, but a group of Floridians plan to host competitions themed according to the collective antics of the beer-loving, gator-possessing, rap-sheet heavy, mullet-wearing social media...}