\entryitemWithDescription{\hskip 0pt{}The Biden administration wants more money and technology to prevent close calls between planes}{https://apnews.com/article/49435f599a50c9cbc687c591e2a42939}{The Biden administration said Friday it will invest more money in aviation safety and consider requiring planes to be equipped with technology designed to prevent close calls around airports. The moves come after a string of close calls...}

\entryitemWithDescription{\hskip 0pt{}SpaceX can't launch its giant rocket again until fixes are made, FAA says}{https://apnews.com/article/a8d6cec63de579af4b6d5f040e51825d}{CAPE CANAVERAL, Fla. (AP) --- SpaceX must take a series of steps before it can launch its mega rocket again after its debut ended in an explosion, federal regulators said Friday. The Federal Aviation Administration said it closed its...}

\entryitemWithDescription{\hskip 0pt{}Country music star Zach Bryan says he was arrested and jailed briefly in northeastern Oklahoma}{https://apnews.com/article/d8f02726265687b86eda3cfad6b0e9f6}{OKLAHOMA CITY (AP) --- Country music star Zach Bryan was arrested by the Oklahoma Highway Patrol and jailed briefly Thursday in northeastern Oklahoma, according to a video posted on his account on the social media site X, formerly...}

\entryitemWithDescription{\hskip 0pt{}Miami Beach's iconic Clevelander Hotel and Bar to be replaced with affordable housing development}{https://apnews.com/article/55049da19da0f786908d64f360085775}{MIAMI BEACH, Fla. (AP) --- Plans are underway for an iconic Miami Beach hotel and bar to be replaced with a high-end restaurant and affordable housing units, the building's owner announced. The changes being submitted soon to the city of...}

\entryitemWithDescription{\hskip 0pt{}Queen Elizabeth II remembered a year after her death as gun salutes ring out for King Charles III}{https://apnews.com/article/96425ff28d72a04820ccf347cf4f8e7f}{LONDON (AP) --- With gun salutes and tolling bells, the United Kingdom on Friday marked the anniversary of the death of Queen Elizabeth II and the ascension of King Charles III, who remembered his mother as a symbol of stability during...}

\entryitemWithDescription{\hskip 0pt{}A person is shot and hurt at Lil Baby concert in Memphis. Police think it was premeditated, targeted}{https://apnews.com/article/a41dcdccb76584546d923b484b8f594a}{MEMPHIS, Tenn. (AP) --- One person was shot and wounded at a Memphis concert headlined by rapper Lil Baby in what was believed to be a premeditated, targeted shooting, police said. The Memphis Police Department posted on social media that...}

\entryitemWithDescription{\hskip 0pt{}From spaceships to `Batman' props, a Hollywood model maker's creations and collection up for auction}{https://apnews.com/article/eec2c2f546e801680163ea2f164576e8}{DALLAS (AP) --- From an early model of the iconic alien mothership from ``Close Encounters of the Third Kind'' to a complete Stormtrooper costume from ``Star Wars,'' bidding opens Friday on thousands of pieces Hollywood model maker Greg...}

\entryitemWithDescription{\hskip 0pt{}Parenting advice YouTuber Ruby Franke and business partner due in court on child abuse charges}{https://apnews.com/article/d659de95728e8945dd6886d336fd9c6d}{A Utah mother of six who gave parenting advice via a once-popular YouTube channel called ``8 Passengers'' is scheduled to make an initial court appearance Friday on charges that she and the owner of a relationship counseling business...}

\entryitemWithDescription{\hskip 0pt{}Trump hosts a \$100,000-per-person fundraiser to help Giuliani pay legal bills}{https://apnews.com/article/27724c04738a9d47114c3ea50b88b2ee}{NEW YORK (AP) --- Former President Donald Trump hosted a \$100,000-a-plate fundraiser for former New York Mayor Rudy Giuliani at his Bedminster, New Jersey, golf club as Giuliani struggles to pay his mounting legal bills. Giuliani, a...}

\entryitemWithDescription{\hskip 0pt{}Climate protester glues feet to floor at US Open, interrupts Coco Gauff's semifinal win over Muchova}{https://apnews.com/article/00a82f465076adea36b098aa6ca08a0d}{NEW YORK (AP) --- Coco Gauff's U.S. Open semifinal victory over Karolina Muchova was delayed by 50 minutes because of a disruption by four environmental activists in the Arthur Ashe Stadium stands Thursday night. One protester glued his...}

\entryitemWithDescription{\hskip 0pt{}South Dakota Gov. Kristi Noem expected to endorse Trump}{https://apnews.com/article/24c70d4f9e4e86aa845b062b87a9c98a}{WASHINGTON (AP) --- South Dakota Gov. Kristi Noem is expected to endorse Donald Trump's presidential campaign when he travels to her state for a Republican fundraiser on Friday. Trump will appear in Rapid City for an event hosted by the...}

\entryitemWithDescription{\hskip 0pt{}Bruce Springsteen has peptic ulcer disease. Doctors say it's easily treated}{https://apnews.com/article/4bf3deeebf89720a9968ce17340f1b85}{Bruce Springsteen announced Thursday that he's postponing a slate of concerts in September on the advice of doctors who treating him for peptic ulcer disease. Fans who aren't familiar with this common and potentially serious...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry to attend charity event in London -- but meeting up with the family isn't on the agenda}{https://apnews.com/article/f26773753a54247bd9628d8875faea6a}{LONDON (AP) --- Prince Harry is attending a charity event Thursday night in London, though he isn't expected to meet with King Charles III or Prince William as Britain prepares to mark the first anniversary of Queen Elizabeth II's death...}