\entryitemWithDescription{\hskip 0pt{}Farmworker tells TV station he killed 7 on California farms}{https://apnews.com/article/bcde624364934f396ff0e56953dec93c}{In this photo taken by a drone, a cluster of mobile homes is seen at the California Terra Garden, formerly Mountain Mushroom Farm in Half Moon Bay, Calif., Thursday, Jan. 26, 2023. A farmworker accused of killing seven people in shootings...}

\entryitemWithDescription{\hskip 0pt{}NYC bike path killer convicted, could face the death penalty}{https://apnews.com/article/ea3bad7f18d4481591113d0c5715448d}{In this courtroom sketch, in federal court in New York, Thursday, Jan. 26, 2023, Sayfullo Saipov, left, listens to the verdict in his trial. Saipov, an Islamic extremist who killed eight in a New York bike path attack was convicted of...}

\entryitemWithDescription{\hskip 0pt{}US military kills senior Islamic State official in Somalia}{https://apnews.com/article/d0a111658004a940ccd935cf49187bee}{Secretary of Defense Lloyd Austin speaks during a meeting with Albanian Defense Minister Niko Peleshi at the Pentagon, Thursday, Jan. 26, 2023, in Washington. (AP Photo/Alex Brandon) WASHINGTON (AP) --- U.S. special operations forces have...}

\entryitemWithDescription{\hskip 0pt{}Past US presidents, VPs asked to recheck for classified docs}{https://apnews.com/article/79e27674b7affd93da06b690351983f4}{FILE - The north face of the Archives of the United States is seen in this general view March 11, 2019, in Washington. The National Archives has asked former U.S. presidents and vice presidents to re-check their personal records for any...}

\entryitemWithDescription{\hskip 0pt{}NASA marks 20 years since space shuttle Columbia disaster}{https://apnews.com/article/863fd8d4742fb485a3888c31f8d11bf3}{A wreath is presented by, from left, Bob Cabana, Associate Administrator of NASA; Janet Petro, NASA KSC director, and Sheryl Chaffee, daughter of Apollo 1 astronaut Roger Chaffee, during NASA\textquotesingle s Day of Remembrance ceremony...}

\entryitemWithDescription{\hskip 0pt{}California storms boost water allocation for cities}{https://apnews.com/article/8b53096af50da30af02eb0ffbd091aa9}{FILE - Floodwaters cover a property along River Rd. in Monterey County, Calif., as the Salinas River overflows its banks on Jan. 13, 2023. California officials announced on Thursday, Jan. 26, 2023, that public water agencies will get 30\%...}

\entryitemWithDescription{\hskip 0pt{}Trump's return to Facebook could be major fundraising boost}{https://apnews.com/article/e4d02e3b3adba891549d09a43868ccdf}{FILE - In this Thursday, June 18, 2020 file photo, President Donald Trump looks at his phone during a roundtable with governors on the reopening of America\textquotesingle s small businesses, in the State Dining Room of the White House in...}

\entryitemWithDescription{\hskip 0pt{}Historically Black TSU hopes for Grammy with gospel album}{https://apnews.com/article/80c764f9ae5296d73ddec80e86ff84df}{Members of the Tennessee State University marching band, known as the Aristocrat of Bands, perform on Oct. 8, 2022, in Nashville, Tenn. TSU is hoping to make history after their marching band was nominated for a Grammy in the roots gospel...}

\entryitemWithDescription{\hskip 0pt{}Wrexham eyes Hollywood ending in impressive FA Cup run}{https://apnews.com/article/e3e876776205be4c79ddabaecda92261}{FILE - Britain\textquotesingle s King Charles III and Camilla, the Queen Consort meet Wrexham Soccer team co owners, US actors Ryan Reynolds and Rob McElhenney and players during their visit to Wrexham Association Football Club...}

\entryitemWithDescription{\hskip 0pt{}DA: 5 Memphis cops 'all responsible' for Tyre Nichols' death}{https://apnews.com/article/48d48f2137a2f34482274edb1bd1bab2}{This combo of booking images provided by the Shelby County Sheriff\textquotesingle s Office shows, from top row from left, Tadarrius Bean, Demetrius Haley, Emmitt Martin III, bottom row from left, Desmond Mills, Jr. and Justin Smith. The...}

\entryitemWithDescription{\hskip 0pt{}Church helps mining community evolve in dark, warming Arctic}{https://apnews.com/article/7ba037720afb81cf19e040e7620fc1eb}{The Rev. Siv Limstrand walks with her rifle to the church\textquotesingle s cabin in Bolterdalen, Norway, Monday, Jan. 9, 2023. For the lone pastor in this fragile, starkly beautiful environment, the challenge is to fulfill the church...}

\entryitemWithDescription{\hskip 0pt{}A fridge too far? Living sustainably in NYC by unplugging}{https://apnews.com/article/33163bb528cc60ed667aa808dcfb5731}{Josh Spodek shows the empty refrigerator in his Greenwich Village apartment he ditched to support his effort to live sustainably, Tuesday Jan. 24, 2023, in New York. Beyond the energy savings, Spodek says without a refrigerator he has...}

\entryitemWithDescription{\hskip 0pt{}Youth program founder hurt in shooting 'has biggest heart'}{https://apnews.com/article/1057159dd8f834c991438094c6fd65da}{In this image provided by the Des Moines Public Schools, community activist and rap artist Will Keeps works with students at Harding Middle School on Sept. 27, 2017, in Des Moines, Iowa. Students watched his latest music video...}