\entryitemWithDescription{\hskip 0pt{}Brazil and Jan. 6 in US: Parallel attacks, but not identical}{https://apnews.com/article/22a083f0d08bb9d1d93b67871a103b0c}{FILE - Protesters, supporters of Brazil\textquotesingle s former President Jair Bolsonaro, stand on the roof of the National Congress building after they stormed it, in Brasilia, Brazil, Sunday, Jan. 8, 2023. (AP Photo/Eraldo Peres, File...}

\entryitemWithDescription{\hskip 0pt{}DOJ reviewing potentially classified docs at Biden center}{https://apnews.com/article/812ef44a5333f6d93423a67a683fa024}{FILE - President Joe Biden waves before boarding Air Force One at El Paso International Airport in El Paso, Texas, Sunday, Jan. 8, 2023, to travel to Mexico City, Mexico. The Justice Department is reviewing a batch of potentially...}

\entryitemWithDescription{\hskip 0pt{}Having elected House speaker, Republicans try governing}{https://apnews.com/article/b9fcfd11427a695fe2eb49e36988f1a0}{Speaker of the House Kevin McCarthy, R-Calif., talks to reporters as he walks to the speaker\textquotesingle s ceremonial office at the Capitol in Washington, Monday, Jan. 9, 2023. (AP Photo/Jose Luis Magana) WASHINGTON (AP) --- Electing...}

\entryitemWithDescription{\hskip 0pt{}How Republicans are transforming the House in the majority}{https://apnews.com/article/60b4f098523b982b549823f4b3e8f9e4}{Newly-elected Speaker of the House Kevin McCarthy, R-Calif., walks to his office from the chamber after a contentious battle to lead the GOP majority in the 118th Congress, at the Capitol in Washington, Saturday, Jan. 7, 2023. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}\$1.1B Mega Millions prize also can be winner for retailers}{https://apnews.com/article/cf5a7fc41ee94466bbe5894e1ec48615}{FILE - Mega Millions lottery tickets and a wager slip are displayed, Friday, Jan. 6, 2023, in Derry, N.H. An estimated \$1.1 billion Mega Millions jackpot drawing Tuesday, Jan. 10, 2023, has people lined up at convenience stores...}

\entryitemWithDescription{\hskip 0pt{}Bills safety Hamlin back in Buffalo to continue recovery}{https://apnews.com/article/35005f5e4ac87eca56e7d99d49eaec65}{FILE - Buffalo Bills defensive back Damar Hamlin (3) leaves the field after an NFL football game against the New England Patriots, Thursday, Dec. 1, 2022, in Foxborough, Mass. Quick on-the-field emergency care from well-rehearsed medical...}

\entryitemWithDescription{\hskip 0pt{}As Brazil reels from riots, Bolsonaro finds home in Florida}{https://apnews.com/article/099db80c6511119b534ca17747f871fe}{Former Brazil President Jair Bolsonaro, center, meets with supporters outside a vacation home where he is staying near Orlando, Fla., on Wednesday, Jan. 4, 2023. (Skyler Swisher/Orlando Sentinel via AP) KISSIMMEE, Fla. (AP) --- As Brazil...}

\entryitemWithDescription{\hskip 0pt{}Israel's Netanyahu races ahead with hard-line agenda}{https://apnews.com/article/c3419b07e43f853e9a8d44d55fc4a886}{Israeli Prime Minister Benjamin Netanyahu convenes a weekly cabinet meeting at the Prime Minister\textquotesingle s office in Jerusalem, Sunday, Jan. 8, 2023. (Ronen Zvulun/Pool Photo via AP) Prime Minister Benjamin Netanyahu's new...}

\entryitemWithDescription{\hskip 0pt{}Chief: 6-year-old shot Virginia teacher during class lesson}{https://apnews.com/article/25cebfde17e46abc435c205210a7073d}{Messages of support for teacher Abby Zwerner, who was shot by a 6 year old student, grace the front door of Richneck Elementary School Newport News, Va. on Monday Jan. 9, 2023. The Virginia teacher who authorities say was shot by a 6-year...}

\entryitemWithDescription{\hskip 0pt{}Everyone in California's Montecito ordered out amid deluge}{https://apnews.com/article/7c151eeaf3f567a125d74245173327f1}{A man wades through a flooded street in the Rio Del Mar neighborhood of Aptos, Calif., Monday, Jan. 9, 2023. (AP Photo/Nic Coury) LOS ANGELES (AP) --- Rain-weary Californians grappled with flooding and mudslides Monday as the latest in a...}

\entryitemWithDescription{\hskip 0pt{}Famed Danish restaurant Noma to start new 'flavor search'}{https://apnews.com/article/4a772a42e11833976b49be943e50bf57}{FILE -- Danish restaurant Noma in Copenhagen, March 14, 2012. The innovative Danish restaurant Noma which has reclaimed the title of world's top restaurant several times, said Monday, Jan. 9, 2023, that it will shut down and become ``a...}

\entryitemWithDescription{\hskip 0pt{}Border pressures migrate north as Venezuelans head to Denver}{https://apnews.com/article/103c21b26482306a25e08416295f9e78}{A migrant looks through donated clothes at a makeshift shelter in Denver, Friday, Jan. 6, 2023. Over the past month, nearly 4,000 immigrants, almost all Venezuelans, have arrived unannounced in the frigid city, with nowhere to stay and...}

\entryitemWithDescription{\hskip 0pt{}Georgia grand jury ends probe of Trump, 2020 election}{https://apnews.com/article/fc08d39209ce3be768d933f96a434abf}{FILE - Former President Donald Trump speaks as he announces a third run for president, at Mar-a-Lago in Palm Beach, Fla., Nov. 15, 2022. The special grand jury investigating whether then-President Donald Trump and his allies committed any...}

\entryitemWithDescription{\hskip 0pt{}UN says ozone layer slowly healing, hole to mend by 2066}{https://apnews.com/article/83794d6e5ae6c4469b60effb185d1509}{FILE - In this NASA false-color image, the blue and purple shows the hole in Earth\textquotesingle s protective ozone layer over Antarctica on Oct. 5, 2022. Earth's protective ozone layer is slowly but noticeably healing at a pace that...}

\entryitemWithDescription{\hskip 0pt{}Shiffrin can break Vonn's record -- if she can stay awake}{https://apnews.com/article/eb3b1478862676e3a3e141de7c4e2de7}{United States\textquotesingle{} Mikaela Shiffrin smiles after winning an alpine ski, women\textquotesingle s World Cup giant slalom race, in Kranjska Gora, Slovenia, Sunday, Jan. 8, 2023. Shiffrin matched Lindsey Vonn\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Ukraine school rejects Russian claim of troops killed there}{https://apnews.com/article/79b6b7c903985358517088278d81cebe}{Municipal workers clear the rubble on the roof of College No. 47 which was damaged by a Russian rocket attack in Kramatorsk, Ukraine, Monday, Jan. 9, 2023. (AP Photo/Evgeniy Maloletka) KRAMATORSK, Ukraine (AP) --- Officials at a...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry accuses Camilla of 'dangerous' leaks to media}{https://apnews.com/article/4141be64bcd1521d1d5cf0f9b65e20b5}{A poster advertises the midnight opening of a store to sell the new book by Prince Harry called \textquotesingle Spare\textquotesingle{} in London, Monday, Jan. 9, 2023. Prince Harry has defended his memoir that lays bare rifts inside...}

\entryitemWithDescription{\hskip 0pt{}Analysis: Teammates gave Damar Hamlin the ultimate tribute}{https://apnews.com/article/2850fdfa5fd44dea388a09caa31430ba}{A video board at Levi\textquotesingle s Stadium shows a message for Damar Hamlin during an NFL football game between the San Francisco 49ers and the Arizona Cardinals in Santa Clara, Calif., Sunday, Jan. 8, 2023. (AP Photo/Jed Jacobsohn...}

\entryitemWithDescription{\hskip 0pt{}Mexico may accept more migrants expelled by US}{https://apnews.com/article/871328ff21fc6a87b698742f6e9ed3d4}{U.S. President Joe Biden is greeted at his arrival by Mexican President Andres Manuel Lopez Obrador, second left, Mexican Foreign Minister Marcelo Ebrard, second right, and U.S. Ambassador to Mexico Ken Salazar, right, at Biden...}

\entryitemWithDescription{\hskip 0pt{}CES 2023: Companies tout environmental tech innovations}{https://apnews.com/article/31d2663e9e47b6e18f99d87afc311338}{People look at a John Deere electric excavator at the John Deere booth during the CES tech show Friday, Jan. 6, 2023, in Las Vegas. (AP Photo/John Locher) LAS VEGAS (AP) --- The mottled bright green leaves of a pothos plant stood out...}

\entryitemWithDescription{\hskip 0pt{}Nurses go on strike at 2 big New York City hospitals}{https://apnews.com/article/d81f32cb7ac709404eb795a6d8822b34}{Nurses stage a strike in front of Mt. Sinai Hospital in the Manhattan borough of New York Monday, Jan. 9, 2023, after negotiations broke down hours earlier. (AP Photo/Craig Ruttle) Thousands of nurses are on strike at two major New York...}

\entryitemWithDescription{\hskip 0pt{}Cargo ship goes aground, is refloated in Egypt's Suez Canal}{https://apnews.com/article/fc27fee20b14d4017cfdc1bd7b2ffbc9}{In this photo released by Suez Canal Authority, tugboats pull the ship MV Glory in the Suez Canal between the cities of Port Said and Ismailiya, Egypt Monday, Jan. 9, 2023. A cargo ship carrying corn that went aground early on Monday in...}

\entryitemWithDescription{\hskip 0pt{}Stocks end up mixed on Wall Street after early gains fade}{https://apnews.com/article/adddcec61c0b2b377a9a38ccb10d0783}{FILE - Traders work on the floor at the New York Stock Exchange in New York, Tuesday, Oct. 4, 2022. (AP Photo/Seth Wenig, File) NEW YORK (AP) --- U.S. stocks were mixed Monday at the start of a week with a few events that could shake...}

\entryitemWithDescription{\hskip 0pt{}Kemp done being underestimated, aims to steer GOP past Trump}{https://apnews.com/article/65049bc27c3c2f5e197feaf15d1f031a}{FILE - Georgia Gov. Brian Kemp speaks at The Neighborhood Lot on July 29, 2022, in McDonough, Ga. Having vanquished both a Donald Trump-backed Republican challenger and Democratic star Stacey Abrams to win reelection, Kemp is looking to...}

\entryitemWithDescription{\hskip 0pt{}Authorities probe who was behind uprising in Brazil capital}{https://apnews.com/article/8766c0ad2fcc4ae7c8bf1aa7f9aaa0ec}{Police officers take position as supporters of Brazil\textquotesingle s former President Jair Bolsonaro leave a camp outside the Army headquarters in Brasilia, Brazil, Monday, Jan. 9, 2023. Since Bolsonaro lost re-election to Luiz Inácio...}

\entryitemWithDescription{\hskip 0pt{}New guidance: Use drugs, surgery early for obesity in kids}{https://apnews.com/article/c48d5896114beea7eda31d7b8b25461d}{This image provided by Novo Nordisk in January 2023, shows packaging for the company\textquotesingle s Wegovy drug. Children struggling with obesity should be evaluated and treated early and aggressively, with medications for kids as...}

\entryitemWithDescription{\hskip 0pt{}Hurts returns from injury, leads Eagles to No. 1 seed in NFC}{https://apnews.com/article/a80233e214f9e1b60db676bd2e5b6342}{Philadelphia Eagles quarterback Jalen Hurts throws a pass against the New York Giants during the first half of an NFL football game, Sunday, Jan. 8, 2023, in Philadelphia. (AP Photo/Matt Rourke) PHILADELPHIA (AP) --- Jalen Hurts walked...}

\entryitemWithDescription{\hskip 0pt{}Bills win for Hamlin and eliminate Patriots from playoffs}{https://apnews.com/article/25243cdf2ceb3780419859fc39537ef4}{Buffalo Bills wide receiver John Brown (16) celebrates his touchdown during the second half of an NFL football game against the New England Patriots, Sunday, Jan. 8, 2023, in Orchard Park. (AP Photo/Adrian Kraus) ORCHARD PARK, N.Y...}

\entryitemWithDescription{\hskip 0pt{}McCarthy's next big task: Win GOP support for House rules}{https://apnews.com/article/4922d22689eb79d5d05c1b49ca733123}{Dean of the House Rep. Hal Rogers, R-Ky., swears in Rep. Kevin McCarthy, R-Calif., as House Speaker on the House floor at the U.S. Capitol in Washington, early Saturday, Jan. 7, 2023. (AP Photo/Andrew Harnik) WASHINGTON (AP) --- After an...}

\entryitemWithDescription{\hskip 0pt{}Teacher shot by 6-year-old known as devoted to students}{https://apnews.com/article/2db4662a6d9f711c5bcd27b6142570a8}{Police respond to a shooting at Richneck Elementary School, Friday, Jan. 6, 2023 in Newport News, Va. A shooting at a Virginia elementary school sent a teacher to the hospital and ended with ``an individual'' in custody Friday, police and...}

\entryitemWithDescription{\hskip 0pt{}Adam Rich, former 'Eight Is Enough' child star, dies at 54}{https://apnews.com/article/7294e6bf8061f6c12604c2716d34b722}{FILE - One-time child actor Adam Rich, who starred in the 1970s TV show "Eight is Enough," walks out of a sheriff\textquotesingle s station after posting bail in City of Industry, Calif., Dec. 18, 2002. Rich, the child actor with a...}

\entryitemWithDescription{\hskip 0pt{}Pro-Bolsonaro rioters storm Brazil's top government offices}{https://apnews.com/article/0c03c098a5e2a09ac534412c30ae8355}{Protesters, supporters of Brazil\textquotesingle s former President Jair Bolsonaro, sit in front of police after inside Planalto Palace after storming it, in Brasilia, Brazil, Sunday, Jan. 8, 2023. Planalto is the official workplace of...}

\entryitemWithDescription{\hskip 0pt{}Hamlin in their hearts, the NFL pays tribute to No. 3}{https://apnews.com/article/47dc11b56ec33560542cd3847db4de45}{Buffalo Bills running back Taiwan Jones (25) kneels in prayer for safety Damar Hamlin before an NFL football game against the New England Patriots, Sunday, Jan. 8, 2023, in Orchard Park, N.Y. Hamlin remains hospitalized after suffering a...}

\entryitemWithDescription{\hskip 0pt{}Russell Banks, praised author of 'Cloudsplitter,' dies at 82}{https://apnews.com/article/bcec4ba2e2ea96f08341a95555241dcb}{FILE - Russell Banks, author of "Cloudsplitter," delivers a keynote address during the Hemingway \& Winship Awards ceremony at John F. Kennedy Library and Museum in Boston, April, 4, 2004. Banks, an award-winning fiction writer who rooted...}

\entryitemWithDescription{\hskip 0pt{}Spielberg, 'Top Gun' feted by National Board of Review}{https://apnews.com/article/41dffefdcdd2b918eb6a4c370c4ad6e5}{Best director honoree Steven Spielberg, left, and best actress honoree Michelle Yeoh attend the National Board of Review Awards Gala at Cipriani 42nd Street on Sunday, Jan. 8, 2023, in New York. (Photo by Evan Agostini/Invision/AP) NEW...}

\entryitemWithDescription{\hskip 0pt{}Alabama woman who joined IS hopes to return from Syria camp}{https://apnews.com/article/dfb3cde1330e15b69a4c18552c837664}{In this image taken from video Hoda Muthana talks during an interview in Roj detention camp in Syria where she is being held by U.S.-allied Kurdish forces, Wednesday, Nov. 9, 2022. Muthana, who ran away from home in Alabama at the age of...}

\entryitemWithDescription{\hskip 0pt{}CES 2023: Smelling, touching take center stage in metaverse}{https://apnews.com/article/c9de16360932e6a1fa7c4dcc8f86832c}{Attendees wear VR headsets while previewing the Caliverse Hyper-Realistic Metaverse experience at the Lotte booth during the CES tech show Friday, Jan. 6, 2023, in Las Vegas. (AP Photo/John Locher) LAS VEGAS (AP) --- Is the metaverse...}

\entryitemWithDescription{\hskip 0pt{}Russia claims deadly attack, but Kyiv denies anyone killed}{https://apnews.com/article/46a8599f1fa971b8c773af2745326540}{"Sirko", a Ukrainian serviceman of Karpatska Sich battalion tests his AK-74 rifle near the recently retaken town of Lyman, Ukraine, Sunday, Jan. 8, 2023. (AP Photo/Evgeniy Maloletka) KYIV, Ukraine (AP) --- The Russian military claimed...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry says explosive book is a bid to 'own my story'}{https://apnews.com/article/7082bf624e4b43826d0cc39ce69f961f}{A person at home in Edinburgh watches Prince Harry, the Duke of Sussex, being interviewed by ITV\textquotesingle s Tom Bradby during "Harry: The Interview," two days before his controversial autobiography "Spare" is published, Sunday...}

\entryitemWithDescription{\hskip 0pt{}40 people killed, dozens injured in bus crash in Senegal}{https://apnews.com/article/d04f6550211d40dbf7cbfb07ace108a8}{Two damaged buses are pictured after they collided on a road in Gniby, Senegal, Sunday Jan. 8, 2023. At least 40 people were killed and dozens injured in this bus crash in central Senegal, the country\textquotesingle s president Macky...}

\entryitemWithDescription{\hskip 0pt{}Biden inspects US-Mexico border in face of GOP criticism}{https://apnews.com/article/2e30ea26bbc55c7af509a6e60ad3d33c}{President Joe Biden walks with U.S. Border Patrol agents along a stretch of the U.S.-Mexico border in El Paso Texas, Sunday, Jan. 8, 2023. (AP Photo/Andrew Harnik) EL PASO, Texas (AP) --- President Joe Biden walked a muddy stretch of the...}

\entryitemWithDescription{\hskip 0pt{}California hit by more storms, braces for potential floods}{https://apnews.com/article/c09a7ab1620eac4049c9fa2b24f06426}{A tree collapsed and ripped up the sidewalk damaging a home in Sacramento, Calif., Sunday, Jan. 8, 2023. The National Weather Service warned of a ``relentless parade of atmospheric rivers" --- storms that are long plumes of moisture...}

\entryitemWithDescription{\hskip 0pt{}Israel revokes Palestinian FM's travel permit over UN move}{https://apnews.com/article/91ba538476380a16aad4e2cbdae2e235}{Israeli Prime Minister Benjamin Netanyahu convenes a weekly cabinet meeting at the Prime Minister\textquotesingle s office in Jerusalem, Sunday, Jan. 8, 2023. (Ronen Zvulun/Pool Photo via AP) JERUSALEM (AP) --- Israel on Sunday revoked...}

\entryitemWithDescription{\hskip 0pt{}Shiffrin shows her emotions after matching Vonn's record}{https://apnews.com/article/aa16eabb472c4d020dce712ba18530f3}{United States\textquotesingle{} Mikaela Shiffrin is overcome by emotion as she stands on the podium after winning an alpine ski, women\textquotesingle s World Cup giant slalom race, in Kranjska Gora, Slovenia, Sunday, Jan. 8, 2023...}

\entryitemWithDescription{\hskip 0pt{}Germany: Iranians held in suspected poison plot after US tip}{https://apnews.com/article/60f78b43bcb21e6aa8b4e43976ec4cb5}{Substances found during the search are examined on the premises of the fire department in Castrop-Rauxel, Sunday, Jan.8, 2023. In Castrop-Rauxel, there was a large-scale operation by the police and fire department on Saturday evening. A...}

\entryitemWithDescription{\hskip 0pt{}NFL playoffs: Brady's back to try for 8th Super Bowl win}{https://apnews.com/article/05b7768e4388d57e68983ceacaedf6ab}{Tampa Bay Buccaneers quarterback Tom Brady (12) sets back to pass during the first half of an NFL football game against the Atlanta Falcons, Sunday, Jan. 8, 2023, in Atlanta. (AP Photo/John Bazemore) Seven of the 14 teams in this year...}

\entryitemWithDescription{\hskip 0pt{}Golden Globes are back on TV, but are reform efforts enough?}{https://apnews.com/article/9ee1a25e378b0c707dcd1f5f205c405b}{FILE - Event signage appears above the red carpet at the 77th annual Golden Globe Awards on Jan. 5, 2020, in Beverly Hills, Calif. The 80th annual Golden Globe Awards will take place on Tuesday, Jan. 10. (Photo by Jordan Strauss/Invision/...}

\entryitemWithDescription{\hskip 0pt{}New this week: Margo Price and 'Gold, Lies \& Videotape'}{https://apnews.com/article/3920aaa29cc753fc5db2eeabfd6c8602}{This combination of images shows ``Good Thing We Stayed'' by Julia Wolf, left, and Margo Price's fourth studio full-length album, ``Strays." (BMG/Loma Vista Recordings via AP) Here's a collection curated by The Associated Press'...}

\entryitemWithDescription{\hskip 0pt{}Exiled Venezuela lawmakers chosen to lead anti-Maduro fight}{https://apnews.com/article/000642741a10bef98ba407b1a4c008c9}{FILE - Opposition leader Juan Guaido explains the income and expenses of his self-proclaimed, parallel government in Caracas, Venezuela, Sept. 16, 2022. Venezuela's opposition on Thursday, Jan. 5, 2023, has selected an all-female team of...}
