\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: MTV Video Music Awards celebrate music's global power with hip-hop, K-pop and Latin jams}{https://apnews.com/article/8cbb040e7eeac46f02187cf79b29e07f}{NEWARK, N.J. (AP) --- Taylor Swift took home the top prize at the 2023 MTV Video Music Awards for her ``Anti-Hero'' music video on a night full of surprises. But as much as Swift dominated, the VMAs centered on music's global power...}

\entryitemWithDescription{\hskip 0pt{}Israel's Netanyahu is to meet Elon Musk. Their sit-down comes as X faces antisemitism controversy}{https://apnews.com/article/8b9b625713ffe2e244945980c1caf8bc}{JERUSALEM (AP) --- Prime Minister Benjamin Netanyahu will meet billionaire businessman Elon Musk during a trip to the United States next week, the Israeli leader's office said Thursday. Netanyahu's office declined to discuss the agenda...}

\entryitemWithDescription{\hskip 0pt{}No. 2 House Republican Steve Scalise returns to the Capitol after his blood cancer diagnosis}{https://apnews.com/article/0fb80f9172086422834bb00a8075b789}{WASHINGTON (AP) --- Rep. Steve Scalise, the No. 2 House Republican, returned to the U.S. Capitol on Thursday for the first time since being diagnosed with a blood cancer known as multiple myeloma and told reporters his chemotherapy...}

\entryitemWithDescription{\hskip 0pt{}Johnson \& Johnson is getting rid of its script logo after more than 130 years}{https://apnews.com/article/7236463751d2ba89a7a8858c3accf162}{Johnson \& Johnson is signing off on a new logo. The health care giant said Thursday that it will replace the well-known signature script it has used since 1887 with a modern look that reflects its sharpened focus on pharmaceuticals and...}

\entryitemWithDescription{\hskip 0pt{}Botulism outbreak tied to sardines served in Bordeaux leaves 1 person dead and several hospitalized}{https://apnews.com/article/cfcd7549339a8f04dcd67968a80e198f}{PARIS (AP) --- Matt Jackson was riding an electric bike through Bordeaux wine country when he started feeling strange. Nine days later, he's on a breathing machine in a French intensive care unit, unable to open his eyes, communicating...}

\entryitemWithDescription{\hskip 0pt{}Shelter in place lifted after fire at Michigan paper mill produces plumes of heavy smoke}{https://apnews.com/article/21a5561e577d5abe95be102bd72adf7b}{CHEBOYGAN, Mich. (AP) --- People living near a northern Michigan paper mill that caught fire, filling the air with thick grey smoke, emerged from their homes Thursday after sheltering in place for more than a day, as environmental...}

\entryitemWithDescription{\hskip 0pt{}American explorer says he thought he would die during an 11-day ordeal in a Turkish cave}{https://apnews.com/article/75bf00bb15c3cfdcb19884399d775b11}{ISTANBUL (AP) --- An American researcher who spent 11 days stuck in a Turkish cave after falling ill said Thursday that he thought he would die there before a complex international rescue operation got him out. Mark Dickey, 40, appeared...}

\entryitemWithDescription{\hskip 0pt{}Largest US newspaper chain is hiring Taylor Swift and Beyoncé reporters, drawing interest and ire}{https://apnews.com/article/e345985bf3e863ca371258ad7d790198}{LOS ANGELES (AP) --- This week the United States' biggest newspaper chain posted to its site two unusual job listings: a Taylor Swift reporter and a Beyoncé reporter. Gannett, which owns more than 200 daily papers, will employ these new...}

\entryitemWithDescription{\hskip 0pt{}Man who threw flagpole at police during Jan. 6 riot gets more than 6 years in prison}{https://apnews.com/article/378d427e81bf5691b403579eac3bc0e0}{WASHINGTON (AP) --- A Tennessee man who wrote on social media about wanting to ``take over the Capitol building'' before the Jan. 6, 2021, riot, where he threw a flagpole at a police officer's head, was sentenced on Wednesday to more than...}

\entryitemWithDescription{\hskip 0pt{}After catching escaped murderer, officers took a photo with him. Experts say that was inappropriate}{https://apnews.com/article/1554042a24e1c43c35bf11b6f8d1203e}{PHILADELPHIA (AP) --- A group photo of about two dozen officers in tactical gear posing with escaped murderer Danelo Cavalcante minutes after his capture Wednesday in southeastern Pennsylvania drew criticism from policing reform advocates...}

\entryitemWithDescription{\hskip 0pt{}El Chapo's wife released from US custody after completing 3-year prison sentence}{https://apnews.com/article/b4ba4509ea9a762cfc12de39ac5ea59e}{The wife of Mexican drug kingpin Joaquin ``El Chapo'' Guzman was released from federal custody on Wednesday after completing a three-year sentence for helping him run his multibillion-dollar criminal empire, the federal Bureau of Prisons...}

\entryitemWithDescription{\hskip 0pt{}Environmental groups sue US over sluggish pace in listing the rare ghost orchid as endangered}{https://apnews.com/article/e01714a896b9b6bbc511262986b8b651}{ST. PETERSBURG, Fla. (AP) --- The rare ghost orchid found mainly in Florida and Cuba should be immediately protected by the U.S. as an endangered species, three environmental groups claimed Wednesday in a lawsuit arguing that federal...}

\entryitemWithDescription{\hskip 0pt{}Lauren Boebert kicked out of a `Beetlejuice' show in Denver}{https://apnews.com/article/01ba32a52aa332b087e881905041a318}{DENVER (AP) --- U.S. Rep. Lauren Boebert was kicked out of a ``Beetlejuice'' musical play in Denver on Sunday, according to security footage. The theater didn't name Boebert, but a spokesperson said Wednesday that the video --- which...}