\entryitemWithDescription{\hskip 0pt{}Firefighters battling large fire at the home of Miami Dolphins receiver Tyreek Hill}{https://apnews.com/article/3ecb10ffd9c727542eff19ea3ba332d4}{MIAMI GARDENS, Fla. (AP) --- Firefighters were battling a fire at the home of Miami Dolphins receiver Tyreek Hill on Wednesday afternoon. The house, which is located in Southwest Ranches in South Florida, was shown on local station WSVN 7...}

\entryitemWithDescription{\hskip 0pt{}Michigan detectives interview convicted murderer before his death, looking into unsolved slayings}{https://apnews.com/article/b4e2ddc669b3357647aef2edc5202111}{Authorities in western Michigan are looking into missing persons cases and unsolved homicides after interviewing a convicted murderer and long-haul truck driver with terminal cancer who died last week in a prison hospital. Kent County...}

\entryitemWithDescription{\hskip 0pt{}A hiker is rescued after falling down an Adirondack mountain peak on a wet, wintry night}{https://apnews.com/article/943580a551ca1d5e1ea7362227b92f15}{Forest rangers successfully rescued an upstate New York hiker who survived a frigid night on a rugged Adirondack mountain peak trapped above a cliff, after she slipped and fell hundreds of feet down from the summit. ``I thought I might...}

\entryitemWithDescription{\hskip 0pt{}12 years after she vanished, divers believe they have found body of woman in submerged vehicle}{https://apnews.com/article/db6f278040e45c5e0bee17cbc1b191ae}{KISSIMMEE, Fla. (AP) --- The body of a woman who went missing 12 years ago appears to have been found in a minivan submerged in a central Florida retention pond near Walt Disney World, according to family members and volunteer divers who...}

\entryitemWithDescription{\hskip 0pt{}Puerto Rico official says governor's office must stop using slogan that looks like electioneering}{https://apnews.com/article/c0449bfd238ac176d1839d7faf88c882}{SAN JUAN, Puerto Rico (AP) --- A widely used slogan by the office of Puerto Rico's governor that sparked heavy criticism across the U.S. territory has been struck down this election year, the electoral comptroller's office said Wednesday...}

\entryitemWithDescription{\hskip 0pt{}Bomb threats lead to brief lockdowns and the evacuation of multiple state capitols}{https://apnews.com/article/dfef5fbb98ec6572474807c260533b05}{A bomb threat emailed to officials in several states early Wednesday briefly disrupted government affairs and prompted some state capitol evacuations, but no explosives were found and federal officials quickly dismissed the threats as a...}

\entryitemWithDescription{\hskip 0pt{}Prosecutors seek to drop three felony charges against the brother of Patrick Mahomes}{https://apnews.com/article/e342afb174f0567499b9458504b79c2b}{Prosecutors in Kansas are asking a judge to drop three felony charges related to accusations that Jackson Mahomes --- the younger brother of Kansas City Chiefs quarterback Patrick Mahomes --- grabbed a woman by the neck and kissed her...}

\entryitemWithDescription{\hskip 0pt{}Blue Jays GM Ross Atkins expressed regret Shohei Ohtani turned down Toronto}{https://apnews.com/article/4d0b7105c1636768be21364e4b70a743}{TORONTO (AP) --- Blue Jays general manager Ross Atkins expressed regret Shoehei Ohtani turned down Toronto after meeting with the team and chose to sign a record \$700 million, 10-year contract with the Los Angeles Dodgers. Atkins for the...}

\entryitemWithDescription{\hskip 0pt{}Four children killed as a fire tears through a multifamily home in Connecticut}{https://apnews.com/article/352c42df046028c68df3aaf1847fba4e}{SOMERS, Conn. (AP) --- A fire that raced through a two-family home in northern Connecticut on Tuesday night killed four children and several animals as firefighters struggled with rescue efforts because of clutter, authorities said. The...}

\entryitemWithDescription{\hskip 0pt{}Sure, it might be cold and dark, but traveling to wintry places can be magical}{https://apnews.com/article/eada9f045fc81b90af05c1d29b0a66d9}{Planning a trip this winter? Yes, it's tempting to look for sunny spots where you can lie on a beach or play golf. But some of my favorite winter vacations have been to northerly destinations at their coldest, darkest times of year. I don'...}

\entryitemWithDescription{\hskip 0pt{}Gypsy Rose Blanchard is free and reflecting on prison term for conspiring to kill her abusive mother}{https://apnews.com/article/e312537bf2bd7858eeb35aeb4d6ce4aa}{Gypsy Rose Blanchard said she has found a way to forgive her mother --- and herself. But it has been a long journey from years of abuse and the darkest parts of her life splashed across tabloids to living in prison. Blanchard, now 32, was...}

\entryitemWithDescription{\hskip 0pt{}Body of missing Florida woman found in retention pond after nearly 12 years, volunteer divers say}{https://apnews.com/article/7fe85ff0e350e3acebb0ec07b87b445b}{KISSIMMEE, Fla. (AP) --- A group of volunteer divers believe they have found the remains of a woman in a vehicle submerged in a retention pond near Walt Disney World, apparently solving a 12-year-old mystery about what happened to her...}

\entryitemWithDescription{\hskip 0pt{}First Pooh, now Mickey. In public domain, early Mickey Mouse version will star in horror movies}{https://apnews.com/article/e5bd7d8c711554f42bdd277f0b7a29e7}{LOS ANGELES (AP) --- The earliest iteration of Mickey Mouse is on a rampage, barely two days in the public domain. Slashed free of Disney's copyright as of Monday, the iconic character from ``Steamboat Willie'' is already the focus of two...}