\entryitemWithDescription{\hskip 0pt{}Tory Lanez sentencing on Megan Thee Stallion shooting delayed to August}{https://apnews.com/article/4d454dd6329fe53eab5b549307d9eae6}{FILE - Rapper Tory Lanez performs at HOT 97 Summer Jam 2018 at MetLife Stadium in East Rutherford, N.J. Lanez's sentencing for shooting and wounding hip-hop star Megan Thee Stallion has been delayed until Aug. 7, 2023. Los Angeles...}

\entryitemWithDescription{\hskip 0pt{}Transgender activist no longer welcome at White House after going topless at Biden event}{https://apnews.com/article/811dc7f4473ad6b3dd43dbec7f8b5d37}{President Joe Biden, first lady Jill Biden and Betty Who, left in red, arrive for a Pride Month celebration on the South Lawn of the White House, Saturday, June 10, 2023, in Washington. (AP Photo/Manuel Balce Ceneta) WASHINGTON (AP...}

\entryitemWithDescription{\hskip 0pt{}South Carolina prisoner faces 2nd life sentence for using a cellphone to arrange killing}{https://apnews.com/article/bbcd18feb19cc39f8f2b7d1aae5e9eef}{This undated photo released by the South Carolina Department of Corrections shows Daniel Shannon. Shannon was sentenced to life in prison in federal court for orchestrating the killing of a man through a cellphone while Shannon serves a...}

\entryitemWithDescription{\hskip 0pt{}Death toll from Kenya cult tied to pastor surpasses 300, with more exhumations planned}{https://apnews.com/article/4029d3c201d7f4438969aebc22eff2a7}{FILE - Police and local residents load the exhumed bodies of victims of a religious cult into the back of a truck in the village of Shakahola, near the coastal city of Malindi, in southern Kenya on April 23, 2023. The number of people who...}

\entryitemWithDescription{\hskip 0pt{}'Avatar 3' pushed to 2025 and Disney sets two 'Star Wars' films for 2026}{https://apnews.com/article/e86969d1b3d3d69fb51e2fcc50a56181}{FILE - This image released by 20th Century Fox shows the characters Neytiri, right, and Jake in a scene from the 2009 movie "Avatar." The sequel, ``Avatar: The Way of Water'' may have finally arrived in theaters in 2022, but that long...}

\entryitemWithDescription{\hskip 0pt{}Mayor of Mexican border city of Tijuana living at army base after receiving threats}{https://apnews.com/article/388c60f85309de2695cb3d8156e3c3f5}{FILE - Mexican National Guards patrol among the lanes of cars entering the San Ysidro Port of Entry in Tijuana, Mexico, May 11, 2023. Montserrat Caballero, the mayor of the Mexican border city of Tijuana, said on June 12, 2023 she has...}

\entryitemWithDescription{\hskip 0pt{}Olympic sprinter Tori Bowie died from complications of childbirth, autopsy report concludes}{https://apnews.com/article/eecc4161f5326bbfb9a64b6ac9f6efb2}{FILE - United States\textquotesingle{} Tori Bowie gestures after receiving the gold medal she won in the women\textquotesingle s 100m final during the World Athletics Championships in London, Monday, Aug. 7, 2017. U.S. Olympic champion...}

\entryitemWithDescription{\hskip 0pt{}Passenger recounts fight to breathe after boat capsized in underground water tunnel in New York}{https://apnews.com/article/d7c6288dcdf6a79deb377c7ec429cf07}{Tour Guide Kyle Burkwit leads a group on the boat section during a tour of the Lockport Caves in Lockport, N.Y., on Aug. 21, 2014. A boat carrying hospitality workers capsized Monday, June 12, 2023, during a tour of the historic...}

\entryitemWithDescription{\hskip 0pt{}Buttigieg vows federal help to fix collapsed section of Interstate 95 in Philadelphia}{https://apnews.com/article/85b392e0cf19c51062712190f6487753}{Transportation Secretary Pete Buttigieg, left, meets with Philadelphia Mayor Jim Kenney at the scene of a collapsed elevated section of Interstate 95, in Philadelphia, Tuesday, June 13, 2023. (AP Photo/Matt Slocum) U.S. Transportation...}

\entryitemWithDescription{\hskip 0pt{}Stellantis recalling over 354,000 Jeeps worldwide; rear coil springs can detach while they're moving}{https://apnews.com/article/47c57c35f54d6c7090b682d704ab6d82}{FILE - This Jan. 14, 2019 photo shows a Jeep logo at the North American International Auto Show in Detroit. Stellantis is recalling more than 354,000 Jeeps worldwide, Tuesday, June 13, 2023, because the rear coil springs can fall off...}

\entryitemWithDescription{\hskip 0pt{}Microsoft's media literacy program aims to empower internet users and combat online misinformation}{https://apnews.com/article/1e086a5f9fc258ddb7391557b9f73401}{FILE - The Microsoft logo in the Mobile World Congress 2023 in Barcelona, Spain, on March 2, 2023. (AP Photo/Joan Mateu Parra, File) WASHINGTON (AP) --- People are hungry for accurate and reliable information online and may just need help...}

\entryitemWithDescription{\hskip 0pt{}Philippine villagers flee ashfall, sight of red-hot lava from erupting Mayon volcano}{https://apnews.com/article/69e9f29c9b76d3179ffce44dc8fcbd30}{Villagers ride a military truck as they evacuate their homes in Santo Domingo town, Albay province, northeastern Philippines, Tuesday, June 13, 2023. Truckloads of villagers on Tuesday fled from Philippine communities close to gently...}

\entryitemWithDescription{\hskip 0pt{}German curator on a mission to return silver heirlooms stolen from Jewish families by the Nazis}{https://apnews.com/article/e2fa10a027b5062b42638703e7ca7b9c}{Matthias Weniger, curator of the Bavarian National Museum, lifts one of the 111 silver objects stolen by the Nazis from the Jews during the Third Reich, in Munich, Germany, Saturday, June 10, 2023. Museum staff have made it their mission...}