\entryitemWithDescription{\hskip 0pt{}Court orders Trump lawyer to provide docs in Mar-a-Lago case}{https://apnews.com/article/1533b34b17c154be8576f581206a31b2}{FILE - Attorney M. Evan Corcoran arrives at federal court in Washington, July 22, 2022. (AP Photo/Jose Luis Magana, File) WASHINGTON (AP) --- A federal appeals court on Wednesday directed a lawyer for Donald Trump to turn over to...}

\entryitemWithDescription{\hskip 0pt{}What the Fed rate increase means for your credit card bill}{https://apnews.com/article/a1a5c342b60b63f45d1a700798b70b3a}{File - Credit cards as seen July 1, 2021, in Orlando, Fla. A low credit score can hurt your ability to take out a loan, secure a good interest rate, or increase a credit card spending limit. (AP Photo/John Raoux, File) NEW YORK (AP...}

\entryitemWithDescription{\hskip 0pt{}Rapper Tekashi 6ix9ine injured in assault at Florida gym}{https://apnews.com/article/9bbbf69b14e758ff7882df6fe067c9c0}{FILE - Rapper Daniel Hernandez, known as Tekashi 6ix9ine, performs during the Philipp Plein Women\textquotesingle s 2019 Spring-Summer Collection, unveiled during Fashion Week in Milan, Italy, Sept. 21, 2018. Palm Beach County, Fla...}

\entryitemWithDescription{\hskip 0pt{}DeSantis to expand 'Don't Say Gay' law to all grades}{https://apnews.com/article/d3a9c91f4b5383a5bf6df6f7d8ff65b6}{FILE - Florida Gov. Ron DeSantis answers questions from the media in the Florida Cabinet following his State of the State address during a joint session of the Senate and House of Representatives, Tuesday, March 7, 2023, at the state...}

\entryitemWithDescription{\hskip 0pt{}More deaths, injuries linked to recalled eyedrops}{https://apnews.com/article/2a0f0cc1273cc71b122702e6180492ca}{FILE - This scanning electron microscope image made available by the Centers for Disease Control and Prevention shows rod-shaped Pseudomonas aeruginosa bacteria. U.S. officials are reporting two more deaths and additional cases of vision...}

\entryitemWithDescription{\hskip 0pt{}Police: Boy shoots 2 administrators at Denver high school}{https://apnews.com/article/b7db159105dcaea44a816a8841ffd965}{Two women hug after a school shooting at East High School Wednesday, March 22, 2023, in Denver. Two school administrators were shot at the high school Wednesday morning after a handgun was found on a student subjected to daily searches...}

\entryitemWithDescription{\hskip 0pt{}Why TikTok's security risks keep raising fears}{https://apnews.com/article/cc36f36801d84fc0652112fa461ef140}{FILE - The icon for the video sharing TikTok app is seen on a smartphone, on Feb. 28, 2023. China appealed Friday, March 17, 2023, to other governments to treat its companies fairly after Britain and New Zealand joined the United States...}

\entryitemWithDescription{\hskip 0pt{}AP sources: Manhattan DA postpones Trump grand jury session}{https://apnews.com/article/7f3b3a8da083a8fcd98986c5c6a3bab1}{FILE - Manhattan District Attorney Alvin Bragg participates in a news conference in New York, Tuesday, Feb. 7, 2023. Bragg is standing firm against former President Donald Trump's increasingly hostile rhetoric, telling his staff that the...}

\entryitemWithDescription{\hskip 0pt{}Murdaugh trial gives unsolved death investigation a boost}{https://apnews.com/article/f74a87cd9ba18e925bed886a086a3fe1}{Members of the media and general public gathered outside the Colleton County Courthouse Thursday, March 2, 2023, in Walterboro, S.C. As the double murder trial of Alex Murdaugh wraps, the heaps of public attention poured on the case...}

\entryitemWithDescription{\hskip 0pt{}Republicans invoke Soros to steer narrative on Trump probe}{https://apnews.com/article/9dc8a81d35421388d82be25600db53f8}{FILE - George Soros, founder and chairman of the Open Society Foundations, attends the Joseph A. Schumpeter Award ceremony in Vienna, Austria, June 21, 2019. As former President Donald Trump braces for a potential indictment related to...}

\entryitemWithDescription{\hskip 0pt{}What made Beethoven sick? DNA from his hair offers clues}{https://apnews.com/article/d2d8c50fdd951eb5f5b9fdae00f795a3}{This photo provided by researchers in March 2023, shows the Stumpff Lock, from composer Ludwig van Beethoven, in a laboratory at the Max Planck Institute for the Science of Human History in Germany. Hundreds of years after Beethoven...}

\entryitemWithDescription{\hskip 0pt{}March Madness: Athletes balance privacy, online profile}{https://apnews.com/article/6df58222eafdb84b761e7d92a3b34640}{South Carolina forward Aliyah Boston (4) reaches over Norfolk State forward Kierra Wheeler (50) in the first half of a first-round college basketball game in the NCAA Tournament, Friday, March 17, 2023, in Columbia, S.C. (AP Photo/Sean...}

\entryitemWithDescription{\hskip 0pt{}Los Angeles strike highlights paltry US school worker pay}{https://apnews.com/article/62d5d8d6b68775a16a384205c891119f}{Cecily Myart-Cruz, United Teachers Los Angeles, UTLA President, with Max Arias, executive director of the Service Employees International SEIU Local 99 union, speak to thousands of Los Angeles Unified School District teachers and SEIU...}