\entryitemWithDescription{\hskip 0pt{}Princess Leia bikini costume from set of `Star Wars' movie sells at auction for \$175K}{https://apnews.com/article/d3217ee7325f66fb30cc794a64f683c0}{HOUSTON (AP) --- The gold bikini-style costume that Carrie Fisher wore as Princess Leia while making ``Return of the Jedi'' in the ``Star Wars'' franchise has sold for \$175,000, according to the auction house that handled the sale. The...}

\entryitemWithDescription{\hskip 0pt{}One Extraordinary Photo: Charlie Riedel captures Simone Biles in flight at the Paris Games}{https://apnews.com/article/3c9d9096c534aa88f4a7f14847ae6533}{PARIS (AP) --- Charlie Riedel has been an AP staff photographer in Kansas City, Missouri, for 24 years. This is his eighth Olympic games. Here is what Riedel had to say about making this extraordinary photo. Why this photo? Simone Biles...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift fans swarm a hill in Munich to watch her sold-out show for free}{https://apnews.com/article/476e861c34fad02a58ecaa7ac6f4028b}{MUNICH (AP) --- Thousands of Taylor Swift fans have gotten free seats to her concerts in Munich on a grassy hill near the concert venue. The Swifties packed the Olympic Hill, or Olympiaberg, one of the highest elevations in the southern...}

\entryitemWithDescription{\hskip 0pt{}`Deadpool \& Wolverine' smashes R-rated record with \$205 million debut, 8th biggest opening ever}{https://apnews.com/article/2ff49d29c7aa3cf037fb2326abbecd6f}{Marvel is back on top with `` Deadpool \& Wolverine.'' The comic-book movie made a staggering \$205 million in its first weekend in North American theaters, according to studio estimates Sunday. It shattered the opening record for R-rated...}

\entryitemWithDescription{\hskip 0pt{}`Tire whisperer' Russell holds off Hamilton for Mercedes 1-2 in Belgium but faces car weight inquiry}{https://apnews.com/article/0f26b9a6769838c5933389a100be4b05}{SPA-FRANCORCHAMPS, Belgium (AP) --- George Russell led a Mercedes one-two with Lewis Hamilton at the Belgian Grand Prix after pulling off an audacious one-stop strategy and keeping his teammate at bay to add to a thrilling Formula 1...}

\entryitemWithDescription{\hskip 0pt{}Paris Olympics organizers say they meant no disrespect with `Last Supper' tableau}{https://apnews.com/article/9dd5fc5f1849ce9b0720fa997f38ed27}{PARIS (AP) --- Paris Olympics organizers apologized Sunday to anyone who was offended by a tableau that evoked Leonardo da Vinci's ``The Last Supper'' during the glamorous opening ceremony. Da Vinci's painting depicts the moment when...}

\entryitemWithDescription{\hskip 0pt{}Two meteor showers will flash across the sky around the same time in late July}{https://apnews.com/article/134dc44b4f441ac94e70cb452cdc9d87}{Get ready for a meteor shower doubleheader. The Southern Delta Aquariid meteor shower peaks in late July. And this year, it will coincide with a second smaller meteor shower, the Alpha Capricornids. The Delta Aquariids occur every year in...}

\entryitemWithDescription{\hskip 0pt{}Surf's up! Paris Olympics surfing competition commences in Tahiti, with wave rides and wipe outs}{https://apnews.com/article/1e81e9747eb7cae6289f6aa6836c74b7}{TEAHUPO'O, Tahiti (AP) --- Surfers rode through and wiped out on barrel-shaped waves in their quest for gold during the first day of the Paris Olympics surfing competition in Tahiti on Saturday, with some of the biggest names in the sport...}

\entryitemWithDescription{\hskip 0pt{}The Paris Olympics are underway. Here's a look at Day 1}{https://apnews.com/article/58a47ca1dca8d5b5add8dca9dfa2a9ca}{Olympic athletes in Paris dried themselves off after Friday night's soggy-but-celebratory opening ceremony and got to business on Saturday. China won the first gold medal Games when Huang Yuting and Sheng Lihao beat South Korea's Keum...}

\entryitemWithDescription{\hskip 0pt{}Mets ace Kodai Senga expected to miss rest of regular season with calf strain}{https://apnews.com/article/c375ee7b57e83f34d4257679462b0b26}{NEW YORK (AP) --- Mets pitcher Kodai Senga is expected to miss the remainder of the regular season with a strained left calf. The team's projected No. 1 starter this year, Senga got hurt Friday night in the sixth inning of his season...}

\entryitemWithDescription{\hskip 0pt{}Marvel returns to Comic-Con with hotly anticipated panel about its post-'Deadpool \& Wolverine' plans}{https://apnews.com/article/c166d593d55e43825e3c8b397e5038ed}{SAN DIEGO (AP) --- Marvel Studios is returning to San Diego Comic-Con for its iconic Saturday night panel, which is expected to feature big announcements and surprise guests. After Marvel skipped the convention last year due to the...}

\entryitemWithDescription{\hskip 0pt{}Wreckage of schooner that sank in 1893 found in Lake Michigan}{https://apnews.com/article/a8ff26fb53bffc669ce6841fb1c45fa5}{ALGOMA, Wis. (AP) --- Marine archaeologists have discovered the wreckage of schooner that sank in Lake Michigan in the late 1800s. The Wisconsin Underwater Archaeology Association announced this month that its searchers found the Margaret...}

\entryitemWithDescription{\hskip 0pt{}A missing 12-year-old Georgia girl is found in Ohio after her community galvanized to locate her}{https://apnews.com/article/5dc5e84161d29a11a87910d0c8d363f9}{ATLANTA (AP) --- A 12-year-old girl whose disappearance galvanized a Georgia community has been found in Ohio. Hall County Sheriff Gerald Couch said Friday that Maria Gomez-Perez was found Thursday in Dover, about 70 miles (110...}