\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Easter Sunday around the world}{https://apnews.com/article/7a990b8e3f1241cb153bbf003b3d3af6}{Across the globe, people celebrated Easter Sunday --- commemorating the day when, according to Christian tradition, Jesus was resurrected in Jerusalem two millennia ago. In India, Christian families lit candles and placed flowers on the...}

\entryitemWithDescription{\hskip 0pt{}Kia recalls over 427,000 Telluride SUVs because they might roll away while parked}{https://apnews.com/article/8d0832de5e40e7124dfdae20ea0158af}{NEW YORK (AP) --- Kia is recalling more than 427,000 of its Telluride SUVs due to a defect that may cause the cars to roll away while they're parked. According to documents published by the National Highway Traffic Safety Administration...}

\entryitemWithDescription{\hskip 0pt{}`Godzilla x Kong: The New Empire'' roars to an \$80 million box office opening}{https://apnews.com/article/faad76c136390153dbfce09e0800c889}{LOS ANGELES (AP) --- The Godzilla-King Kong combo stomped on expectations as `` Godzilla x Kong: The New Empire '' roared to an \$80 million opening on 3,861 North American screens, according to Sunday studio estimates. The monster mash...}

\entryitemWithDescription{\hskip 0pt{}Numbers have been drawn for an estimated \$935 million Powerball jackpot}{https://apnews.com/article/cb08709b30ab08abbbb3c12e17686e00}{DES MOINES, Iowa (AP) --- The numbers were drawn Saturday night for an estimated \$935 million Powerball jackpot that has been growing since the last winner nearly three months ago. The numbers drawn were: 12, 13, 33, 50, 52 and the red...}

\entryitemWithDescription{\hskip 0pt{}Chance Perdomo, star of `Chilling Adventures of Sabrina' and `Gen V,' dies in motorcycle crash at 27}{https://apnews.com/article/d1806c43db485164ea7a4f9b40eb314c}{Actor Chance Perdomo, who rose to fame as a star of ``Chilling Adventures of Sabrina'' and ``Gen V,'' has died at age 27 following a motorcycle crash. ``On behalf of the family and his representatives, it is with heavy hearts that we...}

\entryitemWithDescription{\hskip 0pt{}An Associated Press photographer snaps a buzzy photo by focusing on the details during Holi}{https://apnews.com/article/5363565a6e5407499543ea977dcab0ef}{GUWAHATI, India (AP) --- Anupam Nath has been covering Holi, the Hindu festival of colors, in Guwahati in northeastern India for two decades. In that time, he's mastered navigating the large, vibrant celebrations, which allows him to...}

\entryitemWithDescription{\hskip 0pt{}Caitlin Clark leads Iowa to 89-68 win over Colorado and rematch with defending NCAA champion LSU}{https://apnews.com/article/516b776dd76a4e93a4aebef3d81fe153}{ALBANY, N.Y. (AP) --- Caitlin Clark had 29 points and 15 assists to lead top-seeded Iowa to an 89-68 win over fifth-seeded Colorado in the women's NCAA Tournament on Saturday, setting up a rematch of last year's national title game...}

\entryitemWithDescription{\hskip 0pt{}Harvard says it's removed human skin from binding of 19th century book}{https://apnews.com/article/c790d5a49be6a0ef389715f9a09a237a}{CAMBRIDGE, Mass. (AP) --- Harvard University said it has removed human skin from the binding of a 19th century book about the afterlife that has been in its collections since the 1930s. The decision came after a review found ethical...}

\entryitemWithDescription{\hskip 0pt{}Children race to collect marshmallows dropped from a helicopter at a Detroit-area park}{https://apnews.com/article/ebc354cd8c8203ad835e4908158df63a}{SOUTHFIELD, Mich. (AP) --- It rained marshmallows at a suburban Detroit park on Friday as children raced to snatch up thousands of the gooey treats being dropped from a helicopter. The annual Great Marshmallow Drop took place at Catalpa...}

\entryitemWithDescription{\hskip 0pt{}California governor to deploy 500 surveillance cameras to Oakland to fight crime}{https://apnews.com/article/e4bd826bd13c2f406aa33d1bb723ac4e}{OAKLAND, Calif. (AP) --- Hundreds of high-tech surveillance cameras are being installed in the city of Oakland and surrounding freeways to battle crime, California Gov. Gavin Newsom announced Friday. Newsom, a Democrat, said in a news...}

\entryitemWithDescription{\hskip 0pt{}What stores are open on Easter Sunday 2024? See Walmart, Target, Costco hours}{https://apnews.com/article/e50a41a2ab375a72fbb4c3d72da3020f}{Easter-Stores-Open-Closed If the Easter bunny is still looking for basket stuffers, they better hop to it. Many stores will be closed in observance of the holiday. Easter is a Christian holiday, and also an occasion for dyed eggs and...}

\entryitemWithDescription{\hskip 0pt{}`Ozempig' remains Minnesota baseball team's mascot despite uproar that name is form of fat-shaming}{https://apnews.com/article/8fa84bf46d1a21802dad0d4ee9ba07a1}{For a Minnesota minor league baseball team known for a history of outlandish promotions, the idea of naming its longtime live pig mascot after the weight loss drug Ozempic made perfect sense. The St. Paul Saints quickly found out that not...}

\entryitemWithDescription{\hskip 0pt{}Bus plunges off a bridge in South Africa, killing 45 people. An 8-year-old child is only survivor}{https://apnews.com/article/a5b31e9085a5f843f90d0582676ded37}{CAPE TOWN, South Africa (AP) --- A bus carrying worshippers headed to an Easter festival plunged off a bridge on a mountain pass and burst into flames in South Africa on Thursday, killing at least 45 people, authorities said. The only...}