\entryitemWithDescription{\hskip 0pt{}Elizabeth Holmes has 2nd child as she tries to avoid prison}{https://apnews.com/article/a0baf297ce677e262a92a82f92368054}{FILE - Theranos founder and CEO Elizabeth Holmes, center, walks into federal court in San Jose, Calif., Nov. 18, 2022. Holmes is citing her recently born child as another reason she should be allowed to delay the start of a more than 11...}

\entryitemWithDescription{\hskip 0pt{}Why do juries view crime scenes like the Murdaugh estate?}{https://apnews.com/article/be1992b44f8a1d9ea14d4c802f297505}{Evidence shown in Alex Murdaugh\textquotesingle s trial for murder shows the Colleton County property where the Murdaughs lived, at the Colleton County Courthouse in Walterboro, S.C. on Thursday, Feb. 2, 2023. The judge has agreed with a...}

\entryitemWithDescription{\hskip 0pt{}DOJ sues La. company over cancer risk to minority community}{https://apnews.com/article/1a57d0402a144bfa4da5d939b34ae6ea}{FILE - Angelo Bernard, who lives near the Denka Performance Elastomer Plant, poses with his grandchildren who are visiting him for the weekend, at his home in Reserve, La., on Sept. 23, 2022. From left are Korinne Bernard, 11, Karmen...}

\entryitemWithDescription{\hskip 0pt{}Endangered Mexican wolf population makes strides in US}{https://apnews.com/article/238c7c04ad5f75896dd5d8f5c8fd7874}{This Jan. 27, 2023 image provided by the Mexican Wolf Interagency Field Team shows Grace Dougan, a U.S. Fish and Wildlife Service volunteer, carrying a sedated wolf during the agency\textquotesingle s annual survey near Aragon, N.M. A...}

\entryitemWithDescription{\hskip 0pt{}Mexican president: Mexico has more democracy than US}{https://apnews.com/article/0103c02290e33c01c5af776acb9915a5}{Mexican President Andres Manuel Lopez Obrador gives his regularly scheduled morning press conference, decorated with an image of Francisco "Pancho" Villa, a general in the Mexican Revolution, at the National Palace in Mexico City...}

\entryitemWithDescription{\hskip 0pt{}The Oscar universe belongs to 'Everything Everywhere'}{https://apnews.com/article/c6db5dc1477c28e2b9e41270a036ac12}{The unlikely awards season juggernaut ``Everything Everywhere All at Once'' marched on at the Screen Actors Guild Awards, and even gathered stream with awards not just for best ensemble, Michelle Yeoh and Ke Huy Quan but also for Jamie...}

\entryitemWithDescription{\hskip 0pt{}JetBlue pilot landing in Boston averts potential collision}{https://apnews.com/article/e25f0cdb4b9c4c7a30628ac9acee95bf}{BOSTON (AP) --- A JetBlue pilot had to take ``evasive action" while landing at Boston's Logan International Airport when another aircraft crossed an intersecting runway, the Federal Aviation Administration said. The close call occurred at...}

\entryitemWithDescription{\hskip 0pt{}Biden to nominate Julie Su as next US labor secretary}{https://apnews.com/article/2bd9b13b9cffa0511cf667cbfdafb299}{FILE - Julie Su, of Calif., speaks during a hearing of the Senate Health, Education, Labor and Pensions Committee for her to be Deputy Secretary of Labor, on Capitol Hill, March 16, 2021, in Washington. President Joe Biden is nominating...}

\entryitemWithDescription{\hskip 0pt{}What time is it on moon? Europe pushing for lunar time zone}{https://apnews.com/article/2b0124415c14755e08a58e1b5ed5362a}{FILE - The moon rises beyond a sign in the outfield during the fifth inning of a baseball game between the Kansas City Royals and the Chicago White Sox Wednesday, Aug. 10, 2022, in Kansas City, Mo. With more lunar missions than ever on...}

\entryitemWithDescription{\hskip 0pt{}Tom Sizemore's family 'deciding end of life matters'}{https://apnews.com/article/c6a11283931c41efcb30c473aef26546}{FILE - In this Aug. 11, 2014 file photo, actor Tom Sizemore arrives at the premiere of "The Expendables 3" in Los Angeles. Sizemore is in critical condition after suffering a brain aneurism, a representative for the actor said Sunday...}

\entryitemWithDescription{\hskip 0pt{}US economy sending mixed signals: Here's what it all means}{https://apnews.com/article/f218111d29793783338e3ff6ec040da2}{An ironworker guides a beam during construction of a municipal building in Norristown, Pa., Wednesday, Feb. 15, 2023. The strength of the American job market has consistently defied expectations throughout the economic tumult of the COVID...}

\entryitemWithDescription{\hskip 0pt{}Hate your signature? Try plastic surgery for autographs}{https://apnews.com/article/517711adfa4b51b45ad3392f528c5568}{Priscilla Molina creates a custom signature in Los Angeles on Wednesday, Feb. 22, 2023. Molina designs a minimum of 300 custom signatures a month, offering packages that include up to three ways to sign, limitless drafts or a new set of...}

\entryitemWithDescription{\hskip 0pt{}How officials cracked case of eyedrops that blinded people}{https://apnews.com/article/2320289a358e9fe6fa7d38a1fc5f19f7}{FILE - This scanning electron microscope image made available by the Centers for Disease Control and Prevention shows rod-shaped Pseudomonas aeruginosa bacteria. Experts are marveling at how U.S. disease detectives figured out how...}