\entryitemWithDescription{\hskip 0pt{}Gaston Glock, the Austrian developer of the Glock handgun, dies at 94}{https://apnews.com/article/730da2f1cbaaf082fbabeb328e9d51ae}{Gaston Glock, the Austrian developer of the handgun that bears his name, died on Wednesday. He was 94. The Glock company announced his death, the Austria Press Agency reported. Glock, a reclusive engineer, founded the company in 1963 in...}

\entryitemWithDescription{\hskip 0pt{}A woman who burned Wyoming's only full-service abortion clinic is ordered to pay \$298,000}{https://apnews.com/article/62779a51bdbcf5cd2d0612586227a514}{CHEYENNE, Wyo. (AP) --- A judge has ordered a woman who set fire to Wyoming's only full-service abortion clinic to pay nearly \$300,000 in restitution, the full amount sought by prosecutors. Lorna Green is serving five years in prison for...}

\entryitemWithDescription{\hskip 0pt{}Man arrested in stabbing at New York's Grand Central Terminal charged with hate crimes}{https://apnews.com/article/d0442e1d4a5562450972c6f29364b808}{NEW YORK (AP) --- A New York City man has been charged with hate crimes following the Christmas Day stabbing of two teenage tourists from Paraguay at a restaurant inside Grand Central Terminal, authorities said. Esteban Esono-Asue, 36...}

\entryitemWithDescription{\hskip 0pt{}Argument over Christmas gifts turns deadly as 14-year-old kills his older sister, deputies say}{https://apnews.com/article/c6fd4bfde219ae10176fc7744e727c29}{LARGO, Fla. (AP) --- A Florida woman holding her 11-month-old son in a baby carrier was fatally shot by her 14-year-old brother while trying to defuse an argument over Christmas gifts he was having with a 15-year-old brother who also was...}

\entryitemWithDescription{\hskip 0pt{}Trapped in his crashed truck, an Indiana man is rescued after 6 days surviving on rainwater}{https://apnews.com/article/6de2925e48076671b9d9da49c7fe2ef9}{PORTAGE, Ind. (AP) --- A 27-year-old man survived for six days on only rainwater while pinned tightly inside his crashed pickup truck beneath a highway bridge in northwest Indiana, police said. His ordeal ended when two men scouting for...}

\entryitemWithDescription{\hskip 0pt{}The Eiffel Tower is closed while workers strike on the 100th anniversary of its founder's death}{https://apnews.com/article/7c8204f5b6d0c5df1c84969e11bfde08}{PARIS (AP) --- The Eiffel Tower was closed to visitors Wednesday because of a strike over contract negotiations timed to coincide with the 100th anniversary of the death of its creator, Gustave Eiffel. One of the world's most-visited...}

\entryitemWithDescription{\hskip 0pt{}Bill Granger, chef who brought Aussie-style breakfast to world capitals, dies at 54}{https://apnews.com/article/2e169be2a58c8eb3c594d0bcd5325bb3}{LONDON (AP) --- Bill Granger, the Australian chef, food writer and restaurant owner who brought Aussie-style food to international capitals from London to Seoul, has died. He was 54. Granger's family said on social media Tuesday that the...}

\entryitemWithDescription{\hskip 0pt{}US online retailer Zulily says it will go into liquidation, surprising customers}{https://apnews.com/article/2afdbb77665226ea1c9060c806502db4}{SEATTLE (AP) --- The U.S. online retailer Zulily is closing down, surprising customers and laying off hundreds of workers after efforts to salvage the business failed. The Seattle-based company said in a notice on its website that it had...}

\entryitemWithDescription{\hskip 0pt{}Photographer Cecil Williams' vision gives South Carolina its only civil rights museum}{https://apnews.com/article/ee2807845bbab508f4a07c3dd26218d0}{ORANGEBURG, S.C. (AP) --- Much of how South Carolina has seen its civil rights history has been through the lens of photographer Cecil Williams. From sit-ins to prayer protests to portraits of African Americans integrating universities...}

\entryitemWithDescription{\hskip 0pt{}US delegation is meeting with Mexico's government for talks on the surge of migrants at the border}{https://apnews.com/article/f39247c4848cb7cf1097fcbaa84edcbd}{MEXICO CITY (AP) --- A top U.S. delegation is meeting with Mexico's president Wednesday in what many see as an attempt to have Mexico do more to limit a surge of migrants reaching the U.S. southwestern border. Mexican President Andrés...}

\entryitemWithDescription{\hskip 0pt{}Prosecutors oppose Sen. Bob Menendez's effort to delay May bribery trial until July}{https://apnews.com/article/af5d97b5b9c1371cf48eebde10fb33c9}{NEW YORK (AP) --- Federal prosecutors on Tuesday urged a judge to reject U.S. Sen. Bob Menendez's request to delay his bribery trial scheduled for next spring by two months, until July. Prosecutors argued against the postponement a week...}

\entryitemWithDescription{\hskip 0pt{}1-2-3 and counting: Las Vegas weddings could hit record on New Year's Eve thanks to date's pattern}{https://apnews.com/article/6437521c2d6124a129fe9d8d0760fde2}{LAS VEGAS (AP) --- For better or for worse, a wave of couples saying ``I do'' in Las Vegas on New Year's Eve could set a record for the city's busiest wedding day ever. That's because 12/31/23 is known in the massive Las Vegas wedding...}

\entryitemWithDescription{\hskip 0pt{}Mariah Carey and Bryan Tanaka split after 7 years together, dancer confirms}{https://apnews.com/article/cf8ec4d3e8248f59ed31312d22b6da65}{Mariah Carey and Bryan Tanaka have split after 7 years together, the dancer confirmed Tuesday. In a statement shared with The Associated Press and published to Tanaka's Instagram, Carey's backup dancer-turned-creative director and partner...}