\entryitemWithDescription{\hskip 0pt{}Russian citizen mauled to death by tiger shark off Egypt's Red Sea coast in rare attack}{https://apnews.com/article/7c0d8f2b18532b79060b30ff172d2c26}{CAIRO (AP) --- A Russian man died after being mauled by a shark on Thursday off one of Egypt\textquotesingle s Red Sea resorts, Egyptian and Russian authorities said. Egypt\textquotesingle s Environment Ministry said the man was killed...}

\entryitemWithDescription{\hskip 0pt{}23 freight cars, new vehicles heavily damaged in train derailment in northern Arizona}{https://apnews.com/article/d75ac1da5d9d6f67f4d5d2ca298ff822}{This image provided by the Coconino County Emergency Management shows a vehicle damaged as a result of a freight train derailment, Wednesday, June 7, 2023 east of Williams, Ariz. (Coconino County Emergency Management via AP) WILLIAMS...}

\entryitemWithDescription{\hskip 0pt{}Ruff day in court: Supreme Court sides with Jack Daniel's in dispute with makers of dog toy}{https://apnews.com/article/be1ab568f1afcca458225b4125fc2f27}{FILE - A bottle of Jack Daniel\textquotesingle s Tennessee Whiskey is displayed next to a Bad Spaniels dog toy in Arlington, Va., Sunday, Nov. 20, 2022. The Supreme Court on Thursday, June 8, 2023, gave whiskey maker Jack Daniel...}

\entryitemWithDescription{\hskip 0pt{}Minnesota Vikings releasing star running back Dalvin Cook for salary cap reasons, AP source says}{https://apnews.com/article/429efea8f35dae0442d1f1be6cf53454}{FILE - Minnesota Vikings running back Dalvin Cook runs against the Chicago Bears during the first half of an NFL football game on Jan. 8, 2023, in Chicago. The Minnesota Vikings are parting ways with the star running back for salary cap...}

\entryitemWithDescription{\hskip 0pt{}NY governor warns Belmont Stakes could be affected if air quality doesn't improve}{https://apnews.com/article/7b056b200247faec759f97882ebc3808}{The sun is obscured by haze caused by northern wildfires as horses are bathed ahead of the Belmont Stakes horse race, Thursday, June 8, 2023, at Belmont Park in Elmont, N.Y. Training was cancelled for the day due to poor air quality. (AP...}

\entryitemWithDescription{\hskip 0pt{}Florida woman who fatally shot neighbor appears in court, sheriff releases details of racist threats}{https://apnews.com/article/05cb421ff23048a6b0dda0be02edf3bf}{A protester, holds a poster of Ajike Owens at the Marion County Courthouse, Tuesday, June 6, 2023, in Ocala, demanding the arrest of a woman who shot and killed Owens, a 35-year-old mother of four, last Friday night, June 2. Authorities...}

\entryitemWithDescription{\hskip 0pt{}Baltimore police commissioner departing after 4 years; led department through court-ordered reforms}{https://apnews.com/article/0a9f66c8b22da274612b8b1b7ac221c8}{FILE - Baltimore Police Commissioner Michael Harrison speaks during a news conference, July 23, 2019, in Baltimore. Commissioner Harrison is stepping down after four years in the role, a tenure that focused on leading the city. Harrison's...}

\entryitemWithDescription{\hskip 0pt{}Pat Robertson, broadcaster who helped make religion central to GOP politics, dies at 93}{https://apnews.com/article/91299d0953c014ca6860fe545cac793e}{FILE - Rev. Pat Robertson poses a question to a Republican presidential candidate during a forum at Regent University in Virginia Beach, Va., Oct. 23, 2015. Robertson, a religious broadcaster who turned a tiny Virginia station into the...}

\entryitemWithDescription{\hskip 0pt{}Authorities recover train from Austrian tunnel after fire forces evacuation}{https://apnews.com/article/d691e85c51775cddd90a2a2d9c028c11}{Firefighters help passengers near a train tunnel after a a fire broke out in a train forcing rescuers to evacuate the 151 people on board, in Fritzens near Innsbruck, Austria, Wednesday, June 7, 2023. (Georg Koechler/Zoom.Tirol via AP...}

\entryitemWithDescription{\hskip 0pt{}Malaysia, Singapore slam comedian for 'offensive' joke over MH370 plane disappearance}{https://apnews.com/article/dca9f7565fdf4fd5752b87576d874b72}{FILE - A man walks past a board reading "Pray for MH370" for passengers aboard a missing Malaysia Airlines plane, in Kuala Lumpur, Malaysia, on March 15, 2014. Malaysia\textquotesingle s government on Thursday, June 8, 2023, condemned a...}

\entryitemWithDescription{\hskip 0pt{}Biden, Sunak vow to stick together on Ukraine, deepen cooperation on clean energy transition, AI}{https://apnews.com/article/b88033bd61d4b934c5e32203330c6dd6}{President Joe Biden listens as British Prime Minister Rishi Sunak speaks during a news conference in the East Room of the White House in Washington, Thursday, June 8, 2023. (AP Photo/Susan Walsh) WASHINGTON (AP) --- President Joe Biden...}

\entryitemWithDescription{\hskip 0pt{}Main suspect in 2005 disappearance of Natalee Holloway arrives in US from Peru to face charges}{https://apnews.com/article/5e8259248ddf70bedf85ceb4604a8cc8}{Dutch citizen Joran van der Sloot is driven in a police vehicle from the Ancon I maximum-security prison, outskirts of Lima, Peru, Thursday, June 8, 2023. The main suspect in the unsolved 2005 disappearance of American student Natalee...}

\entryitemWithDescription{\hskip 0pt{}Replacement plane for Air India flight lands in San Francisco after being diverted to Russia}{https://apnews.com/article/cd1121ee112566e0199d5e4f5558e354}{FILE - Air India aircrafts stand at Indira Gandhi International Airport in New Delhi, India, April 29, 2011. An Air India plane flying from New Delhi to San Francisco landed in Russia after it developed an engine problem, officials said...}