\entryitemWithDescription{\hskip 0pt{}Justin Timberlake reaches plea deal to resolve drunken driving case, AP source says}{https://apnews.com/article/e274512147f2bea6eb44c6c1b713c175}{NEW YORK (AP) --- Justin Timberlake is scheduled to enter a new plea Friday in his drunken driving case in New York's Hamptons, prosecutors said. Details of the plea weren't disclosed, but a person with knowledge of the deal said...}

\entryitemWithDescription{\hskip 0pt{}Court could clear the way for Americans to legally bet on US elections}{https://apnews.com/article/4f45fdf2bd8b1d30d4e1f131e637418a}{ATLANTIC CITY, N.J. (AP) --- Amid the explosion of legal gambling in the United States, some things have remained off-limits, including betting on the outcome of U.S. elections. But that could be about to change. A federal judge in...}

\entryitemWithDescription{\hskip 0pt{}NFL averaged 21 million viewers per game for opening week, its highest on record}{https://apnews.com/article/01fce6b89c7d738c21badda85901e33c}{LOS ANGELES (AP) --- The NFL averaged 21.0 million viewers per game during the league's opening week, making it the most-watched Week 1 on record. The league and Nielsen said Wednesday morning that the per-game average on TV and digital...}

\entryitemWithDescription{\hskip 0pt{}Joe Jonas and Sophie Turner are declared divorced and single}{https://apnews.com/article/e2eed8595c89480e039c85306cd4fcb7}{A Florida judge has declared Joe Jonas and Sophie Turner divorced and single, signing off on a confidential agreement reached between the two. The Miami-Dade County judge approved the agreement on Friday, one year after the 35-year-old...}

\entryitemWithDescription{\hskip 0pt{}The MTV Video Music Awards are back. Will Taylor Swift make history?}{https://apnews.com/article/c8611104c22b980398b440ef9dd8ceed}{NEW YORK (AP) --- The MTV Video Music Awards return Wednesday night with a whole lot of Taylor Swift. Will she become the most-awarded musician in VMAs history? The pop star leads the nominations with 12 --- eight for her ``Fortnight''...}

\entryitemWithDescription{\hskip 0pt{}As Trump and Harris spar, ABC's moderators grapple with conducting a debate in a polarized country}{https://apnews.com/article/80459d35f25c8fd3207c558bdb7e2339}{The ABC News moderators were great. No, actually they were a ``disgraceful failure,'' They cut off Kamala Harris too much. No, actually they corrected Donald Trump unfairly. Such is the contentious tenor of the times in 2024's campaign...}

\entryitemWithDescription{\hskip 0pt{}James Earl Jones' Darth Vader voice lives on through AI. Voice actors see promise and peril in that}{https://apnews.com/article/10643d1a4b5b13575d4a7b457f0d858e}{LOS ANGELES (AP) --- Over the course of an acting career that spanned more than six decades, James Earl Jones' voice became an indelible piece of his work as a performer. On screen, Jones, who died Monday at 93, brought to life a...}

\entryitemWithDescription{\hskip 0pt{}`The Mentalist' star Simon Baker admits drinking and driving in Australia}{https://apnews.com/article/b504083a13aa3b2528e9c0fb414d0929}{MULLUMBIMBY, Australia (AP) --- Australian actor and director Simon Baker, best known for his role as Patrick Jane in the CBS drama series ``The Mentalist,'' avoided a conviction Wednesday after pleading guilty to a charge of driving...}

\entryitemWithDescription{\hskip 0pt{}Judge allows a man serving a 20-year prison sentence to remain on Alaska ballot}{https://apnews.com/article/183e138fd015cbf1d7c482edd94432e1}{JUNEAU, Alaska (AP) --- A man who is serving a 20-year prison sentence can remain on Alaska's ranked choice general election ballot in the race for the state's only U.S. House seat, a judge ruled Tuesday. State Superior Court Judge Ian...}

\entryitemWithDescription{\hskip 0pt{}Mauricio Pocchetino hired to succeed Gregg Berhalter as US men's national team coach}{https://apnews.com/article/3c41cf8619c8e365dc32c6a11ddbc8c0}{Former Tottenham and Chelsea manager Mauricio Pochettino was hired Tuesday to succeed Gregg Berhalter as U.S. men's national team coach, 21 months before the Americans host the 2026 World Cup. A 52-year-old Argentine, Pochettino became...}

\entryitemWithDescription{\hskip 0pt{}Dave Grohl says he's a father to a new daughter outside his 21-year marriage}{https://apnews.com/article/ebf5f567034af107a96132f50f39181a}{LOS ANGELES (AP) --- Dave Grohl says he recently fathered a daughter outside his 21-year marriage to Jordyn Blum, with whom he has three older daughters. ``I've recently become the father of a new baby daughter, born outside of my...}

\entryitemWithDescription{\hskip 0pt{}Pharrell as a Lego and Robbie Williams as a chimp? Music biopics get creative}{https://apnews.com/article/d1e968c738ee4b2197a486797eb75b98}{TORONTO (AP) --- Many of the expected conventions of music biopics are present in ``Piece by Piece,'' about the producer-turned-pop star Pharrell Williams, and ``Better Man,'' about the British singer Robbie Williams. There's the young...}

\entryitemWithDescription{\hskip 0pt{}Jon Stewart presses for a breakthrough to get the first 9/11 troops full care}{https://apnews.com/article/e8db4b191e18b1ef6486a0cc1a47847b}{WASHINGTON (AP) --- The first U.S. troops to deploy after the Sept. 11 attacks are suffering from radiation exposure that the government has yet to officially recognize 23 years later. They are a final group of 9/11 service members that...}