\entryitemWithDescription{\hskip 0pt{}Italian judge orders a journalist to pay 5,000 euros in damages for making fun of Meloni's height}{https://apnews.com/article/fabb0daa40941a86f17cb1bc1889c18c}{ROME (AP) --- A judge in Milan has ordered an Italian journalist to pay 5,000 euros (nearly \$5,500) in damages to Premier Giorgia Meloni for making fun of her height in social media posts. The judge ruled on Wednesday that two social...}

\entryitemWithDescription{\hskip 0pt{}EA Sports College Football 25, among most anticipated sports video games in history, hits the market}{https://apnews.com/article/4c864ba62e7622265ed1e4638191e629}{EA Sports College Football 25, among the most highly anticipated sports video games of all time, has flooded the market as gamers who waited more than a decade for the franchise's next installment rush to play. The game officially...}

\entryitemWithDescription{\hskip 0pt{}Harvey Weinstein due in NYC courtroom for hearing tied to upcoming retrial}{https://apnews.com/article/9f193bd6d55b829b6342ef948f31cc8e}{NEW YORK (AP) --- Harvey Weinstein is scheduled to appear in a New York court Friday ahead of a planned retrial on rape and sexual assault charges. The former Hollywood movie mogul's pretrial hearing in Manhattan criminal court will...}

\entryitemWithDescription{\hskip 0pt{}University of Florida president Ben Sasse is resigning after his wife was diagnosed with epilepsy}{https://apnews.com/article/d75ec128949376dafab5ff8a5160f186}{ORLANDO, Fla. (AP) --- University of Florida president Ben Sasse, a controversial pick almost two years ago when he was named to lead one of the top public universities in the U.S., plans to leave his position to focus on taking care of...}

\entryitemWithDescription{\hskip 0pt{}The winner in China's panda diplomacy: the pandas themselves}{https://apnews.com/article/e4f980ea601f5e64c87b1dfa584721a9}{WASHINGTON (AP) --- China's panda diplomacy may have one true winner: the pandas themselves. Decades after Beijing began working with zoos in the U.S. and Europe to protect the species, the number of giant pandas in the wild has risen to...}

\entryitemWithDescription{\hskip 0pt{}Lou Dobbs, conservative pundit and longtime cable TV host for Fox Business and CNN, dies at 78}{https://apnews.com/article/76c799df42c6b7d4912dece5d180b2de}{NEW YORK (AP) --- Lou Dobbs, the conservative political pundit and veteran cable TV host who was a founding anchor for CNN and later was a nightly presence on Fox Business Network for more than a decade, has died. He was 78. His death was...}

\entryitemWithDescription{\hskip 0pt{}Shannen Doherty finalizes divorce hours before death}{https://apnews.com/article/0d9fbb475ae64fed1ccdc0a03eb69cf6}{LOS ANGELES (AP) --- Shannen Doherty finalized her split with husband, Kurt Iswarienko, just hours before her death at age 53, and she was granted a rare posthumous divorce two days later. Doherty, the star of ``Beverly Hills, 90210''...}

\entryitemWithDescription{\hskip 0pt{}Netflix's subscriber and earnings growth gather more momentum as password-sharing crackdown pays off}{https://apnews.com/article/d77c9a1f7ce29d1647354a7acf70a7ea}{Netflix's subscriber and earnings growth accelerated in its latest quarter as the video streaming service benefits from a crackdown on freeloading viewers, an expansion into advertising and an acclaimed programming lineup. The results...}

\entryitemWithDescription{\hskip 0pt{}Comedian Bob Newhart, deadpan master of sitcoms and telephone monologues, dies at 94}{https://apnews.com/article/799460b72b3c47e7aaf4eeb246f00b8c}{LOS ANGELES (AP) --- Bob Newhart, the deadpan accountant-turned-comedian who became one of the most popular TV stars of his time after striking gold with a classic comedy album, has died at 94. Jerry Digney, Newhart's publicist, says the...}

\entryitemWithDescription{\hskip 0pt{}Paris Olympic competition nears total gender parity. Take a look at the athlete gender breakdown}{https://apnews.com/article/c194ca5934911efbce801363f28e8c04}{GENEVA (AP) --- The founder of the modern Olympics and former IOC president, Pierre de Coubertin, once said women competing in the Games would be ``impractical, uninteresting, unaesthetic and improper.'' Over a century later, the 2024...}

\entryitemWithDescription{\hskip 0pt{}McIlroy gets last chance to recover from another major letdown as British Open starts at Troon}{https://apnews.com/article/e25c3e8a727da82569918b1c6c824907}{TROON, Scotland (AP) --- The first step toward recovery for Rory McIlroy starts with the last major of the year. McIlroy was among early starters Thursday as the British Open began at Royal Troon on a cool, cloudy morning along the Irish...}

\entryitemWithDescription{\hskip 0pt{}Historic utility AND high fashion. 80-year-old LL Bean staple finds a new audience as a trendy bag}{https://apnews.com/article/47a258dd282cdf3aee27878257b0418a}{FREEPORT, Maine (AP) --- L.L. Bean created it 80 years ago to haul heavy blocks of ice. Now it's a must-have summer fashion accessory. The simple, sturdy canvas bag called the Boat and Tote is having an extended moment 80 years after its...}

\entryitemWithDescription{\hskip 0pt{}Too soon for comedy? After attempted assassination of Trump, US politics feel anything but funny}{https://apnews.com/article/4235bd43f3750c95e0460d158996a0e5}{Political jokes: too soon? The answer from many quarters at midweek was a resounding yes, days after an assassination attempt against Republican former president Donald Trump rattled the nation over political violence that has been...}