\entryitemWithDescription{\hskip 0pt{}Joe Jonas files for divorce from Sophie Turner after 4 years of marriage, 2 daughters}{https://apnews.com/article/054936d79f780e5704b130cd73f43311}{MIAMI (AP) --- Joe Jonas filed for divorce from Sophie Turner on Tuesday after four years of marriage and two children. The 34-year-old Jonas Brothers singer filed to end his marriage with the 27-year-old star of ``Game of Thrones'' and ``...}

\entryitemWithDescription{\hskip 0pt{}Alaska couple reunited with cat 26 days after home collapsed into river swollen by glacial outburst}{https://apnews.com/article/7d2acd81829fff7729f67ccee24a311b}{ANCHORAGE, ALaska (AP) --- A pair of Alaska teachers needed good news after they lost nearly all their possessions when their house collapsed into a river swollen by a glacial-outburst flood and their cat went missing. Elizabeth Wilkins...}

\entryitemWithDescription{\hskip 0pt{}Dodgers pitcher Julio Urías arrested on felony charge of corporal injury on a spouse}{https://apnews.com/article/f934f87ff3761967bd76379fa2fc3f92}{LOS ANGELES (AP) --- Los Angeles Dodgers pitcher Julio Urías was arrested on a felony charge of corporal injury on a spouse or cohabitant, a Los Angeles County Sheriff's Department spokeswoman said Tuesday. Urías did not travel with the...}

\entryitemWithDescription{\hskip 0pt{}Chiefs' All-Pro TE Travis Kelce hyperextends knee in practice for opener vs Detroit}{https://apnews.com/article/36ed6513beab37c312556a8de4d1a3be}{KANSAS CITY, Mo. (AP) --- Travis Kelce hyperextended his knee during the Chiefs' final practice before their opener against Detroit, leaving the status of the All-Pro tight end in question when Kansas City faces the Lions on Thursday...}

\entryitemWithDescription{\hskip 0pt{}United Airlines says the outage that held up departing flights was not a cybersecurity issue}{https://apnews.com/article/ce9623ae0fd1e657830dc6acb6cccbc4}{United Airlines said Tuesday that a software update triggered a glitch that forced it to halt departures nationwide, briefly crippling one of the nation's biggest carriers on a busy travel day. Federal officials said United crews had been...}

\entryitemWithDescription{\hskip 0pt{}US steps toward forcing recall of 52 million air bag inflators that can explode and hurl shrapnel}{https://apnews.com/article/503a2d52dce79bdc20825abe14598688}{DETROIT (AP) --- The U.S. government is taking a big step toward forcing a defiant Tennessee company to recall 52 million air bag inflators that could explode, hurl shrapnel and injure or kill people. The National Highway Traffic Safety...}

\entryitemWithDescription{\hskip 0pt{}With the Obamas and Biebers, Aaron Rodgers and Aaron Judge, the US Open stars aren't just on court}{https://apnews.com/article/7fb3b46b0d5b9cfbf6dd12111f3f4e9a}{NEW YORK (AP) --- Coco Gauff glanced up at one of the 35-foot-wide video boards high atop Arthur Ashe Stadium during a U.S. Open match last week and caught a glimpse of celebrity couple Justin and Hailey Bieber. ``I saw them immediately...}

\entryitemWithDescription{\hskip 0pt{}Authorities expand search area for killer who escaped Pennsylvania prison after latest sighting}{https://apnews.com/article/d051911a49fc0dc91410c46859f4cb1c}{KENNETT SQUARE, Pa. (AP) --- Authorities have moved and expanded the search area for a convicted murderer who escaped from a suburban Philadelphia prison last week, after he was spotted on a trail camera at one of the nation's premier...}

\entryitemWithDescription{\hskip 0pt{}NFL players follow musical passion to create songs featured on Madden 24 video game}{https://apnews.com/article/196380c831684fdb46e526a15dd4dada}{SANTA MONICA, Calif. (AP) --- When Miami Dolphins tackle Terron Armstead achieved his dream of being drafted into the NFL over a decade ago, he put his musical aspirations aside. Many other pro football players did the same thing. But...}

\entryitemWithDescription{\hskip 0pt{}Fan ejected from US Open match after German player said the man used language from Hitler's regime}{https://apnews.com/article/734cd0f9ba6c414a11906b98d5b4f640}{NEW YORK (AP) --- A fan was ejected from a U.S. Open tennis match early Tuesday morning after German player Alexander Zverev complained the man used language from Adolf Hitler's Nazi regime. Zverev, the No. 12 seed, was serving at 2-2 in...}