\entryitemWithDescription{\hskip 0pt{}Same storm, different names: How Invest 97L could graduate to Tropical Storm Debby}{https://apnews.com/article/5dd4956e4845f9e79f6662eaf71dead4}{It's an area of low atmospheric pressure, thunderstorms and wind sloshing out of the Caribbean Sea across Cuba, into the Gulf of Mexico and toward Florida. But by the time it dissipates, weather forecasters may have called it by five...}

\entryitemWithDescription{\hskip 0pt{}Third set of remains found with gunshot wound in search for 1921 Tulsa Race Massacre graves}{https://apnews.com/article/1d6d472e333cb155f22d6e33cd2dbbb4}{OKLAHOMA CITY (AP) --- A third set of remains with a gunshot wound has been found at Tulsa cemetery in the search for graves of victims of the 1921 Tulsa Race Massacre, according to a state official. The remains are one of three sets...}

\entryitemWithDescription{\hskip 0pt{}Florida deputy killed and 2 officers wounded in ambush shooting, police say}{https://apnews.com/article/a30d5a3c08d505fe12b379bc85d152dc}{A Florida sheriff's deputy was killed and two other deputies were wounded while attempting to reach the first officer in what police called an ambush shooting inside a home. The three deputies were shot at a house in Eustis, Florida, on...}

\entryitemWithDescription{\hskip 0pt{}22 injured during explosion in paddock area at Germany's Nuerburgring auto racing track}{https://apnews.com/article/c6a87ffa1cb73f3e101e979dee8faa53}{BERLIN (AP) --- Twenty-two people were injured by an explosion in the paddock area of Germany's famous Nuerbergring racetrack, police said Saturday. Police said the accident, which they believe was caused by the explosion of a compressed...}

\entryitemWithDescription{\hskip 0pt{}Aerosmith retires from touring, citing permanent damage to Steven Tyler's voice last year}{https://apnews.com/article/4ee917a6a1e203ccc086d72c992360b2}{LOS ANGELES (AP) --- Aerosmith says Steven Tyler's voice has been permanently damaged by a vocal cord injury last year and the band will no longer tour. The iconic band behind hits like ``Love in an Elevator'' and ``Livin' on the Edge''...}

\entryitemWithDescription{\hskip 0pt{}Justice Department sues TikTok, accusing the company of illegally collecting children's data}{https://apnews.com/article/eb0110e6f2281d8b9a7d2cad0af2e525}{The Justice Department sued TikTok on Friday, accusing the company of violating children's online privacy law and running afoul of a settlement it had reached with another federal agency. The complaint, filed together with the Federal...}

\entryitemWithDescription{\hskip 0pt{}Federal judge overturns \$4.7 billion jury verdict in `Sunday Ticket' lawsuit and rules for NFL}{https://apnews.com/article/f91c35820a1e59b3419d5bb1b88f9a08}{LOS ANGELES (AP) --- A federal judge has overturned a jury's \$4.7 billion verdict in the class-action lawsuit filed by ``Sunday Ticket'' subscribers against the NFL and has granted judgment to the NFL. U.S. District Judge Philip...}

\entryitemWithDescription{\hskip 0pt{}Sunisa Lee's long road back to the Olympics ended in a familiar spot: the medal stand}{https://apnews.com/article/d9b474fece0c1f1506373894c291759d}{PARIS (AP) --- Sunisa Lee called coach Jess Graba not long ago and told him it was over. The process of trying to navigate two kidney diseases that made the 2020 Olympic gymnastics champion's weight yo-yo had become too much. The...}

\entryitemWithDescription{\hskip 0pt{}Jimmy Carter's 100th birthday to be celebrated with musical gala at Atlanta's Fox Theatre}{https://apnews.com/article/ea362d89fb2e86da3b14120473f63827}{ATLANTA (AP) --- Former President Jimmy Carter will be honored next month, ahead of his 100th birthday, with a musical gala at the Fox Theatre in Atlanta, The Carter Center announced Thursday. The Sept. 17 event --- ``Jimmy Carter 100: A...}

\entryitemWithDescription{\hskip 0pt{}Bookmaker to plead guilty in gambling case tied to baseball star Shohei Ohtani's ex-interpreter}{https://apnews.com/article/65a16913c1dd5b428581d6863df777e8}{LOS ANGELES (AP) --- A Southern California bookmaker who took thousands of sports bets from the ex-interpreter for baseball star Shohei Ohtani has agreed to plead guilty to running an illegal gambling business, U.S. authorities announced...}

\entryitemWithDescription{\hskip 0pt{}Remember the ice bucket challenge? 10 years later, the viral campaign is again fundraising for ALS}{https://apnews.com/article/98578d550efff9923eb1db945099ebbc}{BOSTON (AP) --- Dozens of people, including the Massachusetts governor and several sports stars, dumped cold water on themselves at Fenway Park Thursday to mark the 10th anniversary of the ALS ice bucket challenge. The event is part of an...}

\entryitemWithDescription{\hskip 0pt{}Cardi B files for divorce from Offset, posts she's pregnant with their third child on Instagram}{https://apnews.com/article/b2b33367c6da8ca33e0ac53de3d1c006}{NEW YORK (AP) --- Cardi B has filed for divorce from her husband, Migos' rapper Offset. A representative for Cardi B confirmed the news to The Associated Press, writing, ``This is not based on any one particular incident, it has been a...}

\entryitemWithDescription{\hskip 0pt{}Who is Yusuf Dikec, the Turkish shooter who went viral at the 2024 Olympics?}{https://apnews.com/article/a7890124304080a48e7ee4294004d306}{CHATEAUROUX, France (AP) --- Turkish pistol shooter Yusuf Dikec has gone viral on social media for his seemingly casual attitude while shooting his way to a silver medal at the 2024 Olympics. The most-shared images show Dikec shooting in...}