\entryitemWithDescription{\hskip 0pt{}Report: drones attack convoy in east Syria coming from Iraq}{https://apnews.com/article/d1fec7d8c997214ed3ae291c041a2e18}{BEIRUT (AP) --- Drones attacked a convoy of trucks in eastern Syria Sunday night shortly after it crossed into the country from Iraq, Syrian opposition activists and a pro-government radio station said. There was no immediate word on...}

\entryitemWithDescription{\hskip 0pt{}Kansas City police find body in man's car after towing it}{https://apnews.com/article/014c538f85dda0db761f5d2238d11491}{KANSAS CITY, Mo. (AP) --- Family members and a forensic expert are questioning why Kansas City police didn\textquotesingle t find a man\textquotesingle s body in the cargo area of his own SUV until after they towed it to a Missouri police...}

\entryitemWithDescription{\hskip 0pt{}Baby girl found abandoned in Florida an hour after birth}{https://apnews.com/article/19a35bda66d4784884a9b1b03ea84d22}{MULBERRY, Fla. (AP) --- Florida authorities found a newborn girl wrapped in a blanket and still attached to a placenta on a hill outside a trailer park early Saturday morning. Polk County deputies responding to a call about a baby crying...}

\entryitemWithDescription{\hskip 0pt{}Ryan Reynolds goes through range of emotions in FA Cup match}{https://apnews.com/article/cf1bf531db622a8d2f088ba0bb02fa53}{Wrexham co-owner, actor Ryan Reynolds arrives prior to the English FA Cup 4th round Soccer match between Wrexham and Sheffield United at The Racecourse Ground, in Wrexham, England, Sunday, Jan. 29, 2023. (Peter Byrne/PA via AP) Ryan...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk's mysterious ways on display in Tesla tweet trial}{https://apnews.com/article/c65b26faff5af1a9016d44dcb677c2dd}{Elon Musk departs the Phillip Burton Federal Building and United States Court House in San Francisco, on Tuesday, Jan. 24, 2023. (AP Photo/ Benjamin Fanjoy) SAN FRANCISCO (AP) --- Elon Musk's enigmatic personality and unconventional...}

\entryitemWithDescription{\hskip 0pt{}Biden, McCarthy to discuss debt limit in talks on Wednesday}{https://apnews.com/article/e04740d1d172cf3900e6548180909752}{FILE - House Speaker Kevin McCarthy of Calif., pauses during a break in the taping of an interview for the Hannity show with Fox News Channel\textquotesingle s Sean Hannity, on Capitol Hill, Jan. 10, 2023, in Washington. (AP Photo/Alex...}

\entryitemWithDescription{\hskip 0pt{}'Avatar 2' tops box office for 7th weekend}{https://apnews.com/article/261bc81e996368b9789a01b8cc4bba3c}{This image released by 20th Century Studios shows Jake Sully, portrayed by Sam Worthington, in "Avatar: The Way of Water." (20th Century Studios via AP) ``Avatar: The Way of Water'' claimed the No. 1 spot on the domestic box office charts...}

\entryitemWithDescription{\hskip 0pt{}Trustees picked by DeSantis may change progressive college}{https://apnews.com/article/87ba3fc93a281188ac6b4acf254421b8}{New College second-year student Sam Sharf gestures during an interview Friday, Jan. 20, 2023, in Sarasota, Fla. Your education. Your way. Be original. Be you. That\textquotesingle s how New College of Florida describes its approach to...}

\entryitemWithDescription{\hskip 0pt{}Should federal grants favor highway repair over expansion?}{https://apnews.com/article/3737ff1cfc71c366c55f313cdd114fa1}{Traffic moves along the notoriously congested stretch of I-10 through tribal land called the Wild Horse Pass Corridor, Wednesday, Jan. 25, 2023 in Chandler, Ariz. With the Gila River Indian Community\textquotesingle s backing, Arizona...}

\entryitemWithDescription{\hskip 0pt{}Experts urge better opioid rescue drug access to save lives}{https://apnews.com/article/ec12f62eef12ebc67de77afdbb6f11b9}{Jessie Blanchard\textquotesingle s jeep bumper holds a sticker with the slogan "Yes We Narcan" on Monday, Jan. 23, 2023, in Albany, Ga. Naloxone, available as a nasal spray and in an injectable form, is a key tool in the battle against a...}

\entryitemWithDescription{\hskip 0pt{}AP Exclusive: Emails reveal tensions in Colorado River talks}{https://apnews.com/article/a93f42835b65171259c4ffd1de6faaf3}{A man stands on a hill overlooking a formerly sunken boat standing upright into the air with its stern buried in the mud along the shoreline of Lake Mead at the Lake Mead National Recreation Area, Friday, Jan. 27, 2023, near Boulder City...}

\entryitemWithDescription{\hskip 0pt{}'Don't be numb to this': Battling despair over gun deaths}{https://apnews.com/article/97475ef645314bf3762fdc82f64dae2c}{Zeneta Everhart stands outside a Tops supermarket in Buffalo, N.Y., on Jan. 27, 2023. Ten people were killed in the store in May 2022 after a gunman entered targeting Black people. Everhart\textquotesingle s then-19-year-old son survived...}

\entryitemWithDescription{\hskip 0pt{}Israeli-Palestinian cauldron tests US as Blinken visits}{https://apnews.com/article/00281032b69764afffc6f30c0db59741}{FILE - Secretary of State Antony Blinken speaks during The United States Conference of Mayors, Jan. 18, 2023, in Washington. Blinken will travel to Egypt, Israel and the West Bank this weekend in his first trip to the Middle East this...}