\entryitemWithDescription{\hskip 0pt{}`Oppenheimer' aims for a record haul as stars shine at the British Academy Film Awards}{https://apnews.com/article/220af1ec73e47e6222abe2b0934cddc8}{LONDON (AP) --- Atom-bomb epic ``Oppenheimer'' could smash a 53-year-old record at the British Academy Film Awards on Sunday if it makes good on its field-leading 13 nominations. Christopher Nolan 's biopic of physicist J. Robert...}

\entryitemWithDescription{\hskip 0pt{}Stephen Curry tops Sabrina Ionescu in 3-point shootout at All-Star weekend}{https://apnews.com/article/b2e42e474bd3877bf2c36a5b2cf31213}{INDIANAPOLIS (AP) --- Stephen Curry was on a roll --- and it was barely enough to beat Sabrina Ionescu. And fittingly, he won by three. The Golden State star and NBA's all-time 3-point king beat Ionescu 29-26 in the Steph vs. Sabrina...}

\entryitemWithDescription{\hskip 0pt{}George Santos sues late-night host Jimmy Kimmel for tricking him into making videos to ridicule him}{https://apnews.com/article/41e1c2951945e11c069a41f9ea62281d}{NEW YORK (AP) --- Former U.S. Rep. George Santos alleged in a lawsuit filed Saturday in New York that late-night host Jimmy Kimmel deceived him into making videos on the Cameo app that were used to ridicule the disgraced lawmaker on the...}

\entryitemWithDescription{\hskip 0pt{}ECU baseball player appears in game with prosthetic leg after boating accident}{https://apnews.com/article/5a7ee744c34595af89763efa5cabc8ef}{GREENVILLE, N.C. (AP) --- East Carolina sophomore Parker Byrd appeared in Friday's season-opening win against Rider with a prosthetic leg after having part of his right leg amputated following a 2022 boating accident. The school said he...}

\entryitemWithDescription{\hskip 0pt{}WWII Monuments Men weren't all men. The female members finally move into the spotlight}{https://apnews.com/article/42cb40c2a6c0704d424758706d758b38}{DALLAS (AP) --- After World War II, the U.S. Army's art experts set out to find and return millions of works stolen by the Nazis. Known as the Monuments Men, they included Mary Regan Quessenberry, who from her base in Berlin traveled to...}

\entryitemWithDescription{\hskip 0pt{}NBA champion, `Survivor' contestant Scot Pollard receives heart transplant}{https://apnews.com/article/1de85b7ca3321de6f3a813d41846502b}{NBA champion and ``Survivor'' contestant Scot Pollard has had a heart transplant, his wife said on social media on Friday night. ``Scot has a new heart!'' Dawn Pollard posted on X, formerly known as Twitter. ``Surgery went well and I've...}

\entryitemWithDescription{\hskip 0pt{}Pennsylvania magistrate judge is charged with shooting her ex-boyfriend as he slept}{https://apnews.com/article/4eeb11249dd828c5919b4f324f8c4ff0}{HARRISBURG, Pa. (AP) --- A suspended magistrate judge in Pennsylvania shot her estranged boyfriend in the head as he slept last weekend, police said Thursday in filing attempted murder and aggravated assault charges against her. Tests...}

\entryitemWithDescription{\hskip 0pt{}Got back! Paul McCartney's stolen bass is found and returned to the Beatle after more than 50 years}{https://apnews.com/article/e192765ddab258ac228be06268be9137}{LONDON (AP) --- Paul McCartney no longer gently weeps for his original bass guitar. A five-year search by the manufacturer of the instrument that was aided by a husband-and-wife team of journalists helped reunite The Beatles star with the...}

\entryitemWithDescription{\hskip 0pt{}NASA's final tally shows spacecraft returned double the amount of asteroid rubble}{https://apnews.com/article/2ea5ff565570c4db8ad492ed67dc2037}{CAPE CANAVERAL, Fla. (AP) --- NASA finally has counted up all the asteroid samples returned by a spacecraft last fall --- and it's double the rubble return goal. Officials reported Thursday that the Osiris-Rex spacecraft collected 121.6...}

\entryitemWithDescription{\hskip 0pt{}Cambodia to install hundreds of wildlife cameras in an effort to restore its tiger population}{https://apnews.com/article/52a5a1f9d06a16383aad4143f29aee97}{PHNOM PENH, Cambodia (AP) --- Cambodia will begin installing hundreds of monitoring cameras and import four tigers from India as part of a plan to restore its tiger population, officials said Friday. Tigers were declared ``functionally...}

\entryitemWithDescription{\hskip 0pt{}National Archives working to clean up red powder dumped on Constitution display by protesters}{https://apnews.com/article/2a6dcfadbf35a3263887ac2fce1e813e}{WASHINGTON (AP) --- Conservationists at the National Archives are still working to clean up the building's rotunda area after a pair of apparent environmental protesters on Wednesday dumped reddish powder on the display case housing the...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry races head-first down a skeleton sled track and says `everybody should do this'}{https://apnews.com/article/1296c5af6e25c66f3f0292dd543a9340}{WHISTLER, British Columbia (AP) --- Prince Harry raced head-first on a tiny skeleton sled going 99 kph (61.5 mph) down a track at next year's Invictus Games site Thursday, saying with a smile afterward that everyone should do it. Harry...}

\entryitemWithDescription{\hskip 0pt{}Tiger Woods hits a shank in his return to golf and opens with 72 at Riviera}{https://apnews.com/article/3c18812eb57fc228dc347cdae94db121}{LOS ANGELES (AP) --- Any chance of Tiger Woods breaking par in his first official PGA Tour event in 10 months ended with one swing Thursday and a five-letter word he wasn't afraid to say. Shank. Woods said his back began to spasm over the...}