


\ipart{Developers}
\ichapter{Hacker News}
\entryitemTwoLinks{Today is when the Amazon brain drain sent AWS down the spout}{https://news.ycombinator.com/item?id=45649178}{https://www.theregister.com/2025/10/20/aws\_outage\_amazon\_brain\_drain\_corey\_quinn/}

\entryitemTwoLinks{iOS 26.1 lets users control Liquid Glass transparency}{https://news.ycombinator.com/item?id=45648266}{https://www.macrumors.com/2025/10/20/ios-26-1-liquid-glass-toggle/}

\entryitemTwoLinks{J.P. Morgan's OpenAI loan is strange}{https://news.ycombinator.com/item?id=45648258}{https://marketunpack.com/j-p-morgans-openai-loan-is-strange/}

\entryitemTwoLinks{When a stadium adds AI to everything, it's worse experience for everyone}{https://news.ycombinator.com/item?id=45648249}{https://a.wholelottanothing.org/bmo-stadium-in-la-added-ai-to-everything-and-what-they-got-was-a-worse-experience-for-everyone/}

\entryitemTwoLinks{Claude Code on the web}{https://news.ycombinator.com/item?id=45647166}{https://www.anthropic.com/news/claude-code-on-the-web}

\entryitemTwoLinks{AWS outage shows internet users 'at mercy' of too few providers, experts say}{https://news.ycombinator.com/item?id=45646649}{https://www.theguardian.com/technology/2025/oct/20/amazon-web-services-aws-outage-hits-dozens-websites-apps}

\entryitemTwoLinks{Dutch spy services have restricted intelligence-sharing with the United States}{https://news.ycombinator.com/item?id=45646572}{https://intelnews.org/2025/10/20/01-3416/}

\entryitemTwoLinks{Chess grandmaster Daniel Naroditsky has died}{https://news.ycombinator.com/item?id=45646561}{https://old.reddit.com/r/chess/comments/1obnbmu/grandmaster\_daniel\_naroditsky\_has\_passed\_away/}

\entryitemTwoLinks{Production RAG: what I learned from processing 5M+ documents}{https://news.ycombinator.com/item?id=45645349}{https://blog.abdellatif.io/production-rag-processing-5m-documents}

\entryitemTwoLinks{Postman which I thought worked locally on my computer, is down}{https://news.ycombinator.com/item?id=45645172}{https://status.postman.com}

\entryitemTwoLinks{How much Anthropic and Cursor spend on Amazon Web Services}{https://news.ycombinator.com/item?id=45644777}{https://www.wheresyoured.at/costs/}

\entryitemTwoLinks{Commodore 64 Ultimate}{https://news.ycombinator.com/item?id=45644654}{https://www.commodore.net/product-page/commodore-64-ultimate-basic-beige-batch1}

\entryitemTwoLinks{BERT is just a single text diffusion step}{https://news.ycombinator.com/item?id=45644328}{https://nathan.rs/posts/roberta-diffusion/}

\entryitemTwoLinks{Servo v0.0.1}{https://news.ycombinator.com/item?id=45643357}{https://github.com/servo/servo}

\entryitemTwoLinks{Alibaba Cloud says it cut Nvidia AI GPU use by 82\% with new pooling system}{https://news.ycombinator.com/item?id=45643163}{https://www.tomshardware.com/tech-industry/semiconductors/alibaba-says-new-pooling-system-cut-nvidia-gpu-use-by-82-percent}

\entryitemTwoLinks{AI-generated 'poverty porn' fake images being used by aid agencies}{https://news.ycombinator.com/item?id=45643040}{https://www.theguardian.com/global-development/2025/oct/20/ai-generated-poverty-porn-fake-images-being-used-by-aid-agencies}

\entryitemTwoLinks{AWS Outage: A Single Cloud Region Shouldn't Take Down the World. But It Did}{https://news.ycombinator.com/item?id=45642951}{https://faun.dev/c/news/devopslinks/aws-outage-a-single-cloud-region-shouldnt-take-down-the-world-but-it-did/}

\entryitemTwoLinks{Matrix Conference 2025 Highlights}{https://news.ycombinator.com/item?id=45642923}{https://element.io/blog/the-matrix-conference-a-seminal-moment-for-matrix/}

\entryitemTwoLinks{Show HN: Playwright Skill for Claude Code – Less context than playwright-MCP}{https://news.ycombinator.com/item?id=45642911}{https://github.com/lackeyjb/playwright-skill}

\entryitemTwoLinks{Beaver-engineered dam in the Czech Republic}{https://news.ycombinator.com/item?id=45642562}{https://en.wikipedia.org/wiki/Beaver-engineered\_dam\_in\_the\_Czech\_Republic}\ichapter{Phoronix}
\entryitemGeneric{\hskip 0pt{}Patches Posted To Allow Hibernation Cancellation On Linux}{https://www.phoronix.com/news/Linux-Hibernation-Cancellation}

\entryitemGeneric{\hskip 0pt{}KosmicKrisp Vulkan To Apple Metal Driver Merged For Mesa 26.0}{https://www.phoronix.com/news/KosmicKrisp-Merged-Mesa-26.0}

\entryitemGeneric{\hskip 0pt{}AMD Announces "ROCm 7.9" As Technology Preview Paired With TheRock Build System}{https://www.phoronix.com/news/ROCm-Core-SDK-7.9}

\entryitemGeneric{\hskip 0pt{}AMD Ryzen 9 9950X vs. 9950X3D On Windows 11 \& Ubuntu Linux}{https://www.phoronix.com/review/windows-linux-amd-9950x-9950x3d}

\entryitemGeneric{\hskip 0pt{}Initial Tenstorrent Blackhole Support Aiming For Linux 6.19}{https://www.phoronix.com/news/Tenstorrent-Blackhole-Linux-619}

\entryitemGeneric{\hskip 0pt{}NTFSPLUS Announced: A New Linux Driver For NTFS With Better Performance, More Features}{https://www.phoronix.com/news/Linux-NTFSPLUS-NTFS-Driver}

\entryitemGeneric{\hskip 0pt{}Initial Intel Xe3P Graphics Support To Be Submitted For Linux 6.19}{https://www.phoronix.com/news/Intel-Xe3P-Starts-Linux-6.19}

\entryitemGeneric{\hskip 0pt{}Servo 0.0.1 Browser Engine Released}{https://www.phoronix.com/news/Servo-0.0.1-Released}

\entryitemGeneric{\hskip 0pt{}Linux 6.18-rc2 Released: "rc2 is on the bigger side"}{https://www.phoronix.com/news/Linux-6.18-rc2-Released}


\ipart{Developers~~~~(zh-Hans)}
\ichapter{Solidot}
\entryitemGeneric{\hskip 0pt{}AWS 宕机影响亚马逊和《堡垒之夜》等游戏}{https://www.solidot.org/story?sid=82588}

\entryitemGeneric{\hskip 0pt{}Xubuntu 官网被嵌入窃取加密货币的恶意程序}{https://www.solidot.org/story?sid=82587}

\entryitemGeneric{\hskip 0pt{}Windows 11 更新破坏了 Recovery Environment}{https://www.solidot.org/story?sid=82586}

\entryitemGeneric{\hskip 0pt{}日本电商巨头 ASKUL 遭勒索软件攻击}{https://www.solidot.org/story?sid=82585}

\entryitemGeneric{\hskip 0pt{}GIMP 正式提供 Snap 打包的版本}{https://www.solidot.org/story?sid=82584}

\entryitemGeneric{\hskip 0pt{}英伟达展示首块美制 Blackwell 芯片}{https://www.solidot.org/story?sid=82583}

\entryitemGeneric{\hskip 0pt{}7-Zip 远程代码执行漏洞 PoC 公开}{https://www.solidot.org/story?sid=82582}

\entryitemGeneric{\hskip 0pt{}GPT-5 并不能证明未解决的数学问题 }{https://www.solidot.org/story?sid=82581}

\entryitemGeneric{\hskip 0pt{}维基百科志愿者制服试图在大会上自杀的持枪男子}{https://www.solidot.org/story?sid=82580}

\entryitemGeneric{\hskip 0pt{}小鼠研究显示新疗法能在数小时内清除大脑中与痴呆症相关的斑块}{https://www.solidot.org/story?sid=82579}

\entryitemGeneric{\hskip 0pt{}物理学家杨振宁去世，享年 103 岁}{https://www.solidot.org/story?sid=82578}

\entryitemGeneric{\hskip 0pt{}维基百科称 AI 导致人类访问量下降}{https://www.solidot.org/story?sid=82577}\ichapter{V2EX}
\entryitemGeneric{\hskip 0pt{}[问与答] 想买台 miniLED 75 寸电视，有没好推荐的？}{https://www.v2ex.com/t/1167170}

\entryitemGeneric{\hskip 0pt{}[Amazon Web Services] AWS 重大故障！}{https://www.v2ex.com/t/1167169}

\entryitemGeneric{\hskip 0pt{}[iOS] iOS 26.1 Beta 4 增加「锁屏滑动打开相机」开关}{https://www.v2ex.com/t/1167168}

\entryitemGeneric{\hskip 0pt{}[问与答] 所谓看书，就是把要学的东西全部看完吗？}{https://www.v2ex.com/t/1167167}

\entryitemGeneric{\hskip 0pt{}[程序员] 好家伙， asana 崩了}{https://www.v2ex.com/t/1167166}

\entryitemGeneric{\hskip 0pt{}[分享发现] 一个不太一样的论坛，有兴趣可以玩玩儿～}{https://www.v2ex.com/t/1167165}

\entryitemGeneric{\hskip 0pt{}[Apple] 说个 macOS 26 的 Docker 液态玻璃的槽点}{https://www.v2ex.com/t/1167164}

\entryitemGeneric{\hskip 0pt{}[分享创造] 闲着无聊做了个 AI 改图工具-Nana banana}{https://www.v2ex.com/t/1167163}

\entryitemGeneric{\hskip 0pt{}[问与答] 前男友发疯，怎么断干净？？}{https://www.v2ex.com/t/1167161}

\entryitemGeneric{\hskip 0pt{}[问与答] 最近的电信宽带一到晚上就特别卡}{https://www.v2ex.com/t/1167160}

\entryitemGeneric{\hskip 0pt{}[分享创造] DeepSeek OCR 已经可以测试效果了，看着没吹牛}{https://www.v2ex.com/t/1167158}

\entryitemGeneric{\hskip 0pt{}[问与答] 怎么给老年人维护抖音推荐喜好？}{https://www.v2ex.com/t/1167156}

\entryitemGeneric{\hskip 0pt{}[职场话题] 制造业信息技术岗位怎么样？}{https://www.v2ex.com/t/1167154}

\entryitemGeneric{\hskip 0pt{}[天黑以后] 20251020 午夜俱乐部}{https://www.v2ex.com/t/1167153}

\entryitemGeneric{\hskip 0pt{}[问与答] 请教有没有发现什么好的 磁力聚合搜索 的工具？}{https://www.v2ex.com/t/1167152}

\entryitemGeneric{\hskip 0pt{}[全球工单系统] 腾讯云崩了吗？}{https://www.v2ex.com/t/1167151}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 大家家里网络怎么架构的啊}{https://www.v2ex.com/t/1167150}

\entryitemGeneric{\hskip 0pt{}[加密货币] OKB 现在市值低，值得入。投资就是投团队。}{https://www.v2ex.com/t/1167149}

\entryitemGeneric{\hskip 0pt{}[分享发现] 一个可以部署在 cf worker 上面的 matrix chatgpt 机器人}{https://www.v2ex.com/t/1167148}

\entryitemGeneric{\hskip 0pt{}[职场话题] 大家面试带纸质的简历过去嘛？}{https://www.v2ex.com/t/1167147}

\entryitemGeneric{\hskip 0pt{}[Claude] 刚开始，还只是有奇怪的口癖，现在厉害了。。。}{https://www.v2ex.com/t/1167146}

\entryitemGeneric{\hskip 0pt{}[随想] 对电子产品有处女情节,一旦摔过或类似的情况,就感觉手机有内伤或者哪里多少有毛病}{https://www.v2ex.com/t/1167145}

\entryitemGeneric{\hskip 0pt{}[问与答] 请问今年双十一适合买电脑吗？}{https://www.v2ex.com/t/1167144}

\entryitemGeneric{\hskip 0pt{}[English] ``long time no see''}{https://www.v2ex.com/t/1167143}

\entryitemGeneric{\hskip 0pt{}[奇思妙想] 用 Manus 和 KIMI 做了一个 PIX 主题魔改教程小网站～～}{https://www.v2ex.com/t/1167139}

\entryitemGeneric{\hskip 0pt{}[问与答] 为什么中文网页链接喜欢在新窗口打开}{https://www.v2ex.com/t/1167138}

\entryitemGeneric{\hskip 0pt{}[写周报] 一人公司周记 02：门前竹影疏，后圃树荫棉}{https://www.v2ex.com/t/1167137}

\entryitemGeneric{\hskip 0pt{}[加密货币] 新的空投来了，撸起来}{https://www.v2ex.com/t/1167136}

\entryitemGeneric{\hskip 0pt{}[Apple] ios 知乎真是个坏 b 软件,只要屏蔽了广告就给你无限请求，狂消耗电量}{https://www.v2ex.com/t/1167133}

\entryitemGeneric{\hskip 0pt{}[Excel] JSON Excel Tool | Convert Excel, JSON, CSV \& More}{https://www.v2ex.com/t/1167131}

\entryitemGeneric{\hskip 0pt{}[分享发现] 能否不要再将 LLM 翻译成法学硕士，真的每次看到都会笑}{https://www.v2ex.com/t/1167130}

\entryitemGeneric{\hskip 0pt{}[生活] 世间还有吓人的犯罪恐怖惊悚片吗？}{https://www.v2ex.com/t/1167129}

\entryitemGeneric{\hskip 0pt{}[Apple] 好恶心..JD 广告上岛了？}{https://www.v2ex.com/t/1167128}

\entryitemGeneric{\hskip 0pt{}[Faucet] 乞讨，求 sol gas}{https://www.v2ex.com/t/1167126}

\entryitemGeneric{\hskip 0pt{}[分享创造] 做了一个 How Attractive am I 网站，中文是颜值打分}{https://www.v2ex.com/t/1167125}

\entryitemGeneric{\hskip 0pt{}[iPhone] iPhone air 未来将在中国大陆推出 eSIM 快速转换功能}{https://www.v2ex.com/t/1167124}

\entryitemGeneric{\hskip 0pt{}[VPS] 有没有办法给 vps 限制每月的总流量?}{https://www.v2ex.com/t/1167123}

\entryitemGeneric{\hskip 0pt{}[硬件] 网上买了一个硬件，连了一个摄像头，写了一些程序，怎么做好看的产品外观}{https://www.v2ex.com/t/1167122}

\entryitemGeneric{\hskip 0pt{}[问与答] 双十一来了，求便携屏推荐}{https://www.v2ex.com/t/1167121}

\entryitemGeneric{\hskip 0pt{}[分享创造] 做了个 YouTube 字幕批量下载工具，支持登录账号"批量"下载会员视频字幕}{https://www.v2ex.com/t/1167120}

\entryitemGeneric{\hskip 0pt{}[程序员] 基于 Java 手搓模块化的 MCP 服务器}{https://www.v2ex.com/t/1167119}

\entryitemGeneric{\hskip 0pt{}[酷工作] 深圳 wlb 小而美不内卷-小鹅通内推！}{https://www.v2ex.com/t/1167117}

\entryitemGeneric{\hskip 0pt{}[问与答] 请教使用多种 ai 工具的场景下，如何有效轮询检查任务状态？}{https://www.v2ex.com/t/1167115}

\entryitemGeneric{\hskip 0pt{}[酷工作] [深圳][腾讯会议、腾讯元宝] Android 研发工程师急招}{https://www.v2ex.com/t/1167114}

\entryitemGeneric{\hskip 0pt{}[信息安全] 前两天 ASP.NET Core 爆出来的 9.9 分超大漏洞 CVE-2025-55315 影响 ASP.NET Core 5.0/6.0 吗？}{https://www.v2ex.com/t/1167113}

\entryitemGeneric{\hskip 0pt{}[Solana] 每天优化一点点, 距离真正可用又前进了一小步}{https://www.v2ex.com/t/1167112}

\entryitemGeneric{\hskip 0pt{}[Google] Google 账户验证问题，求点帮助}{https://www.v2ex.com/t/1167109}

\entryitemGeneric{\hskip 0pt{}[程序员] 2025 年了， express 还在被 "DDOS"}{https://www.v2ex.com/t/1167108}

\entryitemGeneric{\hskip 0pt{}[职场话题] 京东社招流程就是狗屎}{https://www.v2ex.com/t/1167107}

\entryitemGeneric{\hskip 0pt{}[问与答] CORS 会被废除吗？}{https://www.v2ex.com/t/1167106}


\ipart{Generic News}
