\entryitemWithDescription{\hskip 0pt{}Chiefs' Rashee Rice was driving Lamborghini in Dallas chain-reaction crash, his attorney says}{https://apnews.com/article/d36bee33712ebb41c4b78f7c3b54b833}{DALLAS (AP) --- Kansas City Chiefs' player Rashee Rice was the driver of one of two speeding sports cars who left after causing a chain-reaction crash on a Dallas highway over the weekend, the wide receiver's attorney said Thursday. Why...}

\entryitemWithDescription{\hskip 0pt{}Hits for sale: Notable artists who have had their music catalogs sell for big money}{https://apnews.com/article/57df80487ecd6cc6b2229560cd6c2469}{On Thursday, it was announced that American rock band Kiss had sold their catalog, brand name and IP to Swedish company Pophouse Entertainment Group in a deal estimated to be over \$300 million. They're the latest to participate in an...}

\entryitemWithDescription{\hskip 0pt{}Plea talks ongoing for 3rd man charged in killing of Run-DMC star Jam Master Jay}{https://apnews.com/article/f082950b68bc684e23cb447cf8515324}{Prosecutors and defense lawyers are exploring the possibility of a plea deal for the last of three men charged in the 2002 killing of Run-DMC star Jam Master Jay, both sides said Thursday, less than six weeks after two co-defendants were...}

\entryitemWithDescription{\hskip 0pt{}This Los Angeles heist sounds like it came from a thriller novel. Thieves stole \$30 million in cash}{https://apnews.com/article/21c37245b954d21d8714de668a986718}{LOS ANGELES (AP) --- Thieves got away with \$30 million in cash from a money storage facility in Los Angeles by breaking into the building on Easter Sunday and cracking the safe. Now detectives are seeking to unravel the brazen cash...}

\entryitemWithDescription{\hskip 0pt{}Powerball jackpot reaches \$1.23B as long odds mean lots of losing, just as designed}{https://apnews.com/article/b2471a4d796af84fc8628b2c3fa4f4e2}{Powerball will match a record for lottery drawings Saturday night with a stretch of more than three months without a jackpot winner. It's that string of futility that has enabled Powerball's top prize to reach \$1.23 billion, the 8th...}

\entryitemWithDescription{\hskip 0pt{}2 million Black \& Decker clothing steamers are under recall after dozens of burn injuries}{https://apnews.com/article/3e2140a7ec146671405a0d06b962e06d}{NEW YORK (AP) --- About 2 million Black \& Decker-branded clothing steamers are now under recall after consumers reported dozens of burn injuries that resulted from hot water spewing out of the devices. Empower Brands is significantly...}

\entryitemWithDescription{\hskip 0pt{}Where have you been? A California dog missing since the summer is found in Michigan}{https://apnews.com/article/d107aca6471dfaca5303a490d845e7c4}{HARPER WOODS, Mich. (AP) --- A dog missing in California since the summer turned up more than 2,000 miles away in Michigan. Police in Harper Woods, a Detroit suburb, responded to a call about a stray dog last week, picked up the terrier...}

\entryitemWithDescription{\hskip 0pt{}Technical error with Danish missile leads authorities to issue warning to ships. Air space closed}{https://apnews.com/article/5aba2e6076812b3bae5fc2de9829f728}{COPENHAGEN, Denmark (AP) --- A technical error on a navy missile Thursday spurred Danish authorities to issue a warning, saying there was a risk the missile could launch unintentionally --- but not explode --- resulting in fragments...}

\entryitemWithDescription{\hskip 0pt{}Free blue checks are back for some accounts on Elon Musk's X. Not everyone is happy about it}{https://apnews.com/article/518fb6c023a710ab96b19af7e317d0f2}{NEW YORK (AP) --- Elon Musk's X, the platform formerly known as Twitter, has begun restoring complimentary blue checks for some of its users, the latest unexpected shift to cause a lot of confusion on the platform. For years, Twitter's...}

\entryitemWithDescription{\hskip 0pt{}As more storms approach California, stretch of scenic Highway 1 that collapsed is closed again}{https://apnews.com/article/cb11966133915abb4774c83ba6ba0ea1}{BIG SUR, Calif. (AP) --- As more storms approach California, officials have closed a scenic stretch of iconic Highway 1 where a giant section collapsed into the ocean following heavy weekend rains. The Monterey County Sheriff's Office had...}

\entryitemWithDescription{\hskip 0pt{}California schools forced to compete with fast food industry for workers after minimum wage hike}{https://apnews.com/article/eecf616b677c3bac087b3a6940137817}{SACRAMENTO, Calif. (AP) --- Lost in the hubbub surrounding California's new \$20-per-hour minimum wage for fast food workers is how that raise could impact public schools, forcing districts to compete with the likes of McDonald's and...}

\entryitemWithDescription{\hskip 0pt{}All 10 skaters brawl off opening faceoff at start of Devils-Rangers game}{https://apnews.com/article/22e720cebcde0b7578d3458a2f29267a}{NEW YORK (AP) --- The New York Rangers and New Jersey Devils started Wednesday night's game with a brawl involving all 10 players on the ice off the opening faceoff. The main event was Rangers forward Matt Rempe taking on New Jersey's...}

\entryitemWithDescription{\hskip 0pt{}Transportation officials want NYC Marathon organizers to pay \$750K to cross the Verrazzano bridge}{https://apnews.com/article/d9632e185adebe104998552468d505c1}{NEW YORK (AP) --- The New York City Marathon organizers will soon have to pay a bridge toll, just like every other commuter, if New York transit officials have their way. The Metropolitan Transportation Authority is demanding the New York...}