\entryitemWithDescription{\hskip 0pt{}`Saltburn' actor Barry Keoghan named Hasty Pudding's Man of the Year}{https://apnews.com/article/b1334bb493311e77f4ea275b7198bff1}{CAMBRIDGE, Mass. (AP) --- Harvard University's Hasty Pudding Theatricals has named Barry Keoghan, best known for his roles in ``Dunkirk,'' ``The Killing of a Sacred Deer,'' ``Eternals,'' and ``The Banshees of Inisherin,'' as the recipient...}

\entryitemWithDescription{\hskip 0pt{}Zebras, camels and flames, oh my! Circus animals rescued after truck catches fire on Indiana highway}{https://apnews.com/article/6e05d02f6382ffc0c2858487b66b4848}{MARION, Ind. (AP) --- A truck hauling zebras and camels for a series of weekend circus performances caught fire early Saturday on a northeastern Indiana highway, prompting a police rescue of the animals, which roamed along the freeway...}

\entryitemWithDescription{\hskip 0pt{}Charges against country singer Chris Young in Nashville bar arrest have been dropped}{https://apnews.com/article/ead6a027aafa8c985cccbec3a34ba750}{NASHVILLE, Tenn. (AP) --- A district attorney in Tennessee has dropped charges against country singer Chris Young stemming from an encounter with Alcoholic Beverage Commission agents who were doing compliance checks. In a statement...}

\entryitemWithDescription{\hskip 0pt{}Crash involving multiple vehicles and injuries snarls traffic on Chesapeake Bay bridge in Maryland}{https://apnews.com/article/17df78c1204638e7f403b82eccb87f91}{BALTIMORE (AP) --- A crash involving multiple vehicles and injuries closed all lanes on the heavily-traveled U.S. 50 Bay Bridge in Maryland on Saturday and motorists were advised to expect major delays, authorities said. The Maryland...}

\entryitemWithDescription{\hskip 0pt{}Mexico confirms some Mayan ruin sites are unreachable because of gang violence and land conflicts}{https://apnews.com/article/189c99280e011ceae1f5f50d14660854}{MEXICO CITY (AP) --- Mexico's government has acknowledged that at least two well-known Mayan ruin sites are unreachable by visitors due to a toxic mix of cartel violence and land disputes. But two tourist guides in the southern state of...}

\entryitemWithDescription{\hskip 0pt{}Man convicted of manslaughter in the killing of former New Orleans Saints star Will Smith}{https://apnews.com/article/69a369ad5a819653053ee7b62a3610e2}{NEW ORLEANS (AP) --- A man who shot former New Orleans Saints star Will Smith following a traffic crash nearly eight years ago has been convicted of manslaughter. The jury deliberated for more than four hours and reached its verdict in...}

\entryitemWithDescription{\hskip 0pt{}The world's largest cruise ship begins its maiden voyage from the Port of Miami}{https://apnews.com/article/e841449d2796b1fd76d022bbfbb4dada}{MIAMI (AP) --- The world's largest cruise ship is set to begin its maiden voyage Saturday as it gets underway from the Port of Miami. Royal Caribbean's Icon of the Seas, which runs nearly 1,200 feet (365 meters) from bow to stern, is...}

\entryitemWithDescription{\hskip 0pt{}Wrestling icon Vince McMahon resigns from WWE after former employee files sex abuse lawsuit}{https://apnews.com/article/4b7e1cd46a6646538637307bb0c8202b}{STAMFORD, Conn. (AP) --- Wrestling icon Vince McMahon resigned Friday from WWE's parent company the day after a former employee filed a federal lawsuit accusing him and another former executive of serious sexual misconduct, including...}

\entryitemWithDescription{\hskip 0pt{}Other passengers support man who opened emergency exit and walked on plane's wing in Mexico airport}{https://apnews.com/article/91e3411716e22bfd8778905860a7850f}{MEXICO CITY (AP) --- At first it sounds like a typical case of bad behavior aboard airplanes. The Mexico City International Airport acknowledged in a statement Friday that a man had opened an emergency exit and walked out on a wing of a...}

\entryitemWithDescription{\hskip 0pt{}Jackie Robinson statue was stolen from Wichita park}{https://apnews.com/article/beea370b17079ad30092affe6aaea3c1}{WICHITA, Kan. (AP) --- A prized statue of Jackie Robinson was stolen from a public park in Kansas, spurring a police search Friday and outrage across the city of Wichita. The statue honors the first player to break Major League Baseball's...}

\entryitemWithDescription{\hskip 0pt{}Gun-waving St. Louis lawyer wants misdemeanor wiped off his record}{https://apnews.com/article/dcc5184b5b8bc3b099e86c52c8aa0d52}{ST. LOUIS (AP) --- A St. Louis man who gained notoriety for pointing a gun at social justice demonstrators as they marched past his home asked a local judge to wipe the misdemeanor from his record. Mark McCloskey pleaded guilty in 2021 to...}

\entryitemWithDescription{\hskip 0pt{}US regulators close investigation into Ford Escape door latches and will not seek a recall}{https://apnews.com/article/61eeff1e53bbd2b11383a9c26ae84f1e}{DETROIT (AP) --- U.S. auto safety regulators have closed an investigation into complaints that the doors on some Ford Escapes can open while the SUVs are being driven, without seeking a recall. The National Highway Traffic Safety...}

\entryitemWithDescription{\hskip 0pt{}Tesla recalling nearly 200,000 vehicles because software glitch can cause backup camera to go dark}{https://apnews.com/article/e8cc7acb4395a99789c2fee680bfeab3}{Tesla is recalling nearly 200,000 vehicles in the U.S. because the backup camera may not function while the car is in reverse. The recall covers certain Models Y, S and X from the 2023 model year. All are equipped with ``Full Self...}