\entryitemWithDescription{\hskip 0pt{}Bills' Hamlin attends 1st game since collapse, waves to fans}{https://apnews.com/article/ae41d5baace672bd347e6e146400f11d}{FILE - Buffalo Bills safety Damar Hamlin smiles prior to the start of the first half of a preseason NFL football game, Saturday, Aug. 28, 2021, in Orchard Park, N.Y. Hamlin was released from a Buffalo hospital on Wednesday, Jan. 11, 2023...}

\entryitemWithDescription{\hskip 0pt{}Swift firing of police is rare, but could become more common}{https://apnews.com/article/540299223bc8c7dd9db749a4dfac6135}{A portrait of Tyre Nichols is displayed at a memorial service for him on Tuesday, Jan. 17, 2023 in Memphis, Tenn. Nichols was killed during a traffic stop with Memphis Police on Jan. 7. (AP Photo/Adrian Sainz) BOSTON (AP) --- The speed...}

\entryitemWithDescription{\hskip 0pt{}Huge waves bring Hawaii surf contest The Eddie after hiatus}{https://apnews.com/article/db970b01da3e6b6ed25251fb5d86f308}{FILE - Kelly Slater surfs in the In Memory of Eddie Aikau big wave surf contest on the North Shore at Waimea Bay near Haleiwa, Hawaii, Dec. 8, 2009. One of the world\textquotesingle s most prestigious and storied surfing contests is...}

\entryitemWithDescription{\hskip 0pt{}AP sources: Biden to pick Zients as his next chief of staff}{https://apnews.com/article/6a8555dacf08877794a582a989888686}{FILE - White House COVID-19 Response Coordinator Jeff Zients removes a face mask as he prepares to speak at a press briefing at the White House, April 13, 2021, in Washington. (AP Photo/Patrick Semansky, File) WASHINGTON (AP...}

\entryitemWithDescription{\hskip 0pt{}Dems: Biden should be 'embarrassed' by classified docs case}{https://apnews.com/article/9c875e913618a68ac73d9e41505ab769}{FILE - President Joe Biden talks with reporters after speaking in the East Room of the White House in Washington, Jan 20, 2023. Senior Democratic lawmakers turned sharply more critical Sunday of President Joe Biden\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}'Here again': Abortion activists rally 50 years after Roe}{https://apnews.com/article/32f0773666b4e69b4626f4ba632cc37a}{Protesters are seen in the Wisconsin Capitol Rotunda during a march supporting overturning Wisconsin\textquotesingle s near total ban on abortion Sunday, Jan. 22, 2023, in Madison, Wis. (AP Photo/Morry Gash) MADISON, Wis. (AP) --- From...}

\entryitemWithDescription{\hskip 0pt{}Minister: Germany won't block Poland giving Ukraine tanks}{https://apnews.com/article/c9459e1bed9ad7358a59b541b3a5ae8c}{German Foreign Affairs Minister Annalena Baerbock, left, German Chancellor Olaf Scholz, second left, German Defense Minister Boris Pistorius, third left, French Defense Minister Sebastien Lecornu, second right, and French President...}

\entryitemWithDescription{\hskip 0pt{}Fans, celebs gather at Graceland to mourn Lisa Marie Presley}{https://apnews.com/article/b1b049e9ce7796830f48623fd173b9e2}{Axl Rose performs during a memorial service for Lisa Marie Presley Sunday, Jan. 22, 2023, in Memphis, Tenn. She died Jan. 12 after being hospitalized for a medical emergency and was buried on the property next to her son Benjamin Keough...}

\entryitemWithDescription{\hskip 0pt{}Brazil's new president works to reverse Amazon deforestation}{https://apnews.com/article/44ae576b9010a8f11795f8b1ad9e5b2d}{(AP Illustration/Peter Hamlin) RIO DE JANEIRO (AP) --- Shaking a traditional rattle, Brazil's incoming head of Indigenous affairs recently walked through every corner of the agency's headquarters --- even its coffee room --- as she...}

\entryitemWithDescription{\hskip 0pt{}Sanders' Latinx ban wades into community's generational rift}{https://apnews.com/article/4f23386e609acd8206d2396719c17cab}{FILE - Then-Arkansas Gov.-elect Sarah Huckabee Sanders answers a question while taking part in a panel discussion during a Republican Governors Association conference on Nov. 16, 2022, in Orlando, Fla. Arkansas Gov. Huckabee Sanders is...}

\entryitemWithDescription{\hskip 0pt{}Native Hawaiians flock to Las Vegas for affordable living}{https://apnews.com/article/64c59fdb620111723686b66f10110187}{Doreen Hall Vann walks with son Zaiden after tryouts for a club baseball team Saturday, Jan. 21, 2023, in Las Vegas. In 2019 Vann moved from Hawaii to Las Vegas to be closer to her daughter in Seattle. (AP Photo/John Locher) KAPOLEI...}

\entryitemWithDescription{\hskip 0pt{}Lawmakers seek to bar insurrectionists from holding office}{https://apnews.com/article/35feb56487697d2e228860ae5f646549}{FILE - Insurrectionists loyal to President Donald Trump try to break through a police barrier, Jan. 6, 2021, at the Capitol in Washington. (AP Photo/Julio Cortez, File) ALBANY, N.Y. (AP) --- Democratic lawmakers in a handful of states are...}

\entryitemWithDescription{\hskip 0pt{}Hockey brawls to debt limit: Emmer wrangles House GOP votes}{https://apnews.com/article/744b602f30285f3398da09d1489f37dd}{FILE - Rep. Tom Emmer, R-Minn., speaks at a news conference on Capitol Hill in Washington, Tuesday, Jan. 10, 2023. Standing behind Emmer are Rep. Anthony D\textquotesingle Esposito, R-N.Y., left, and House Majority Leader Steve Scalise of...}
