\entryitemWithDescription{\hskip 0pt{}8 Mexican army soldiers arrested in 2014 disappearances of 43 students}{https://apnews.com/article/e9a52df3ab24719c0e9170de766fb672}{FILE - Relatives and classmates of the missing 43 Ayotzinapa college students march in Mexico City, Sept. 26, 2022, on the anniversary of their disappearance in Iguala, Guerrero state. Eight soldiers linked to the disappearance of the...}

\entryitemWithDescription{\hskip 0pt{}Families detail stress, terror and sadness after Nashville school shooting in court documents}{https://apnews.com/article/948f138daa6dd47759ebd6cfd83d3add}{FILE - A child weeps while on the bus leaving The Covenant School following a mass shooting at the school in Nashville, Tenn., March 27, 2023. So far this year, the nation has witnessed the highest number on record of mass killings and...}

\entryitemWithDescription{\hskip 0pt{}Moms for Liberty chapter apologizes for quoting Hitler in its newsletter}{https://apnews.com/article/bcce698e901b9e782970030ccd710512}{An Indiana chapter of Moms for Liberty, a nonprofit that advocates for `` parental rights '' in education and was recently labeled as ``extremist'' by an anti-hate watchdog, is apologizing and condemning Adolf Hitler after using a quote...}

\entryitemWithDescription{\hskip 0pt{}Republicans vote to cut University of Wisconsin System's budget by \$32M in diversity programs spat}{https://apnews.com/article/c654d9cb21317c7d0a868602019c2dcf}{FILE - David Muir of ABC News gives the commencement address during graduation, May 12, 2018, at the University of Wisconsin in Madison, Wis. Republican lawmakers will cut the University of Wisconsin System\textquotesingle s budget by \$...}

\entryitemWithDescription{\hskip 0pt{}FDA warns stores to stop selling Elf Bar, the top disposable e-cigarette in the US}{https://apnews.com/article/4353becf747846b528ec2aea609ed2f9}{FILE - The U.S. Food and Drug Administration campus in Silver Spring, Md., is photographed on Oct. 14, 2015. The FDA on Thursday, June 22, 2023, said it has sent warning letters to dozens of retailers selling fruit- and candy-flavored...}

\entryitemWithDescription{\hskip 0pt{}Rep. George Santos' aunt and dad signed his bail bond to keep him out of jail while awaiting trial}{https://apnews.com/article/f1c7f2c18493400ba746a709cb02b846}{FILE - Rep. George Santos, R-N.Y., speaks to reporters outside the Capitol, in Washington, May 17, 2023. Santos, 34, has spent weeks fighting efforts by news outlets to unseal the names of the two people who co-signed the \$500,000 bond...}

\entryitemWithDescription{\hskip 0pt{}Tech billionaires' cage match? Musk throws down the gauntlet and Zuckerberg accepts challenge}{https://apnews.com/article/a4d6a698e233f5d0e848885e4f823e8d}{This combo of file images shows Facebook CEO Mark Zuckerberg, left, and Tesla and SpaceX CEO Elon Musk. Elon Musk and Mark Zuckerberg are ready to fight, offline. In a now-viral back-and-forth seen on Twitter and Instagram this week, the...}

\entryitemWithDescription{\hskip 0pt{}Ex-Texas congressman Will Hurd calls Trump a 'failed politician' as he launches GOP presidential run}{https://apnews.com/article/710f6f0d4bb6cc1f5046e20ed17ef602}{FILE - Former Texas Rep. Will Hurd speaks during the Iowa Faith and Freedom Coalition Spring Kick-Off Saturday, April 22, 2023, in Clive, Iowa. Hurd, a onetime CIA officer and fierce critic of Donald Trump, announced on Thursday that he...}

\entryitemWithDescription{\hskip 0pt{}Response to fiery Ohio derailment frustrated by poor communication and incomplete information}{https://apnews.com/article/bc2531012afcac4ee54e6b3999e31ed9}{FILE - In this photo taken with a drone, portions of a Norfolk Southern freight train that derailed the previous night in East Palestine, Ohio, remain on fire at mid-day, Feb. 4, 2023. The Pipelines and Hazardous Materials Safety...}

\entryitemWithDescription{\hskip 0pt{}Iconic Hong Kong dragon boat races are back in full force as thousands of spectators gather}{https://apnews.com/article/e34bf9443f2ee59f865ddc7fdcf15d4a}{Competitors take part in the annual dragon boat race to celebrate the Tuen Ng festival in Hong Kong, Thursday, June 22, 2023. (AP Photo/Louise Delmotte) HONG KONG (AP) --- Thousands gathered Thursday in southern Hong Kong to watch the...}

\entryitemWithDescription{\hskip 0pt{}Bridge sitting on key Russian supply route near Crimea struck by missiles}{https://apnews.com/article/8a011394589f6fe8fa62b23bd797448b}{A Ukrainian MSLR BM-21 "Grad" fires towards Russian positions, near Bakhmut at the frontline in Donetsk region, Ukraine, Wednesday, June 21, 2023. (Iryna Rybakova via AP) KYIV, Ukraine (AP) --- Russia-appointed officials in Crimea said...}

\entryitemWithDescription{\hskip 0pt{}Biden and Modi cheer booming economic ties in visit that also reckoned with India's record on rights}{https://apnews.com/article/5e4bc32e679ad6bae7225a28f7f6334d}{President Joe Biden speaks with India\textquotesingle s Prime Minister Narendra Modi during a State Arrival Ceremony on the South Lawn of the White House in Washington, Thursday, June 22, 2023. The Washington Monument is seen in the...}

\entryitemWithDescription{\hskip 0pt{}Moscow court rules US journalist Evan Gershkovich must stay in jail until late August}{https://apnews.com/article/0a859e4fd61b3265e7b35814dfb3f079}{Wall Street Journal reporter Evan Gershkovich stands in a glass cage in a courtroom at the Moscow City Court in Moscow, Russia, Thursday, June 22, 2023. Gershkovich, a Wall Street Journal reporter detained on espionage charges in Russia...}