\entryitemWithDescription{\hskip 0pt{}Bills hang on for 34-31 wild-card win over Dolphins}{https://apnews.com/article/e4e148766d48c402ed09589f7dfdc84a}{Buffalo Bills wide receiver Cole Beasley (11), left, is congratulated by quarterback Josh Allen after his touchdown catch during the second half of an NFL wild-card playoff football game against the Miami Dolphins, Sunday, Jan. 15, 2023...}

\entryitemWithDescription{\hskip 0pt{}House GOP demands visitor logs in Biden classified docs case}{https://apnews.com/article/915efbeb28a51ad9b5e9eac3fa81eb95}{FILE - Rep. James Comer, R-Ky., talks to reporters as he walks to the House chamber, on Capitol Hill in Washington, Thursday, Jan. 12, 2023. In a letter, Sunday, Jan. 15, to the White House, Comer, who chairs the House Oversight...}

\entryitemWithDescription{\hskip 0pt{}California gets more rain and snow, but dry days are ahead}{https://apnews.com/article/106951d1c71360f7482bfefa672f55d5}{Surfers brave the waves during a rain storm at Venice Beach in Los Angeles on Saturday, Jan. 14, 2023. (Keith Birmingham/The Orange County Register via AP) LOS ANGELES (AP) --- More rain and snow fell during the weekend in storm-battered...}

\entryitemWithDescription{\hskip 0pt{}Clearance of German hamlet for mine said to be near-complete}{https://apnews.com/article/20d1679b717f53cf6a57f9e151e21eee}{Police officers push a climate activist with a wheelbarrow off the site in the village Luetzerath in Erkelenz, Germany, Sunday, Jan. 15, 2023. The energy company RWE wants to excavate the coal lying under Luetzerath, for this purpose, the...}

\entryitemWithDescription{\hskip 0pt{}Hamlin cheers on Bills from home, says 'heart is with' team}{https://apnews.com/article/9629efc1667e2a755fff1988c6f6f73d}{A Buffalo Bills fan holds up a sign in support of Buffalo Bills safety Damar Hamlin (3) prior to an NFL wild-card playoff football game between the Buffalo Bills and the Miami Dolphins, Sunday, Jan. 15, 2023, in Orchard Park, N.Y. (AP...}

\entryitemWithDescription{\hskip 0pt{}UGa football player killed in wreck after title celebration}{https://apnews.com/article/ceb0e67ec4b6dbdf8a824392a4951cff}{Georgia head coach Kirby Smart speaks while standing between the 2022 and 2023 championship trophies during a ceremony celebrating the Bulldog\textquotesingle s second consecutive NCAA college football national championship, Saturday...}

\entryitemWithDescription{\hskip 0pt{}EXPLAINER: Tackling threat of mudslides in soaked California}{https://apnews.com/article/69b594ed7f68a6701543ae7b9560f7e6}{FILE - Rocks and vegetation cover Highway 70 following a landslide in the Dixie Fire zone on Oct. 24, 2021, in Plumas County, Calif. (AP Photo/Noah Berger, File) SAN DIEGO (AP) --- Relentless storms from a series of atmospheric rivers...}

\entryitemWithDescription{\hskip 0pt{}Wealth looms big as ever in post-scandal college admissions}{https://apnews.com/article/fd3767b552a14a1e64334d00596f7425}{FILE - In this March 12, 2019, file photo, William "Rick" Singer, founder of the Edge College \& Career Network, departs federal court in Boston after pleading guilty to charges in a nationwide college admissions bribery scandal. In the...}

\entryitemWithDescription{\hskip 0pt{}Congo's army says church bomb kills 10, extremists suspected}{https://apnews.com/article/3231311ca16dd73f79888bbdc0b17b35}{A suspected extremist attack at a church in eastern Congo killed at least 10 people and wounded more than three dozen, according to the country's army. GOMA, Congo (AP) --- A suspected extremist attack at a church in eastern Congo killed...}

\entryitemWithDescription{\hskip 0pt{}GOP action on mail ballot timelines angers military families}{https://apnews.com/article/ad6eaaca489d39aa4b6e63c2ce413bf8}{This March 16, 2022 photo shows Willis Gordon in Canton, Ohio. ``What kind of society do we call ourselves if we are disenfranchising people from the rights that they are over there protecting?'' said Gordon, a Navy veteran and veterans...}

\entryitemWithDescription{\hskip 0pt{}Ukraine building suffers deadliest civilian attack in months}{https://apnews.com/article/57dc26750d98b0451c6578df8f679953}{Emergency workers clear the rubble after a Russian rocket hit a multistory building leaving many people under debris in the southeastern city of Dnipro, Ukraine, Saturday, Jan. 14, 2023. (AP Photo/Evgeniy Maloletka) Rescue workers in...}

\entryitemWithDescription{\hskip 0pt{}Biden: Americans should 'pay attention' to MLK's legacy}{https://apnews.com/article/129b7e5180b99ab595c0129b39894517}{President Joe Biden speaks at Ebenezer Baptist Church in Atlanta, Sunday, Jan. 15, 2023, during a service honoring Martin Luther King Jr. (AP Photo/Carolyn Kaster) ATLANTA (AP) --- President Joe Biden made a historical pilgrimage Sunday...}

\entryitemWithDescription{\hskip 0pt{}As tornadoes hit, survivors hid in tubs, shipping container}{https://apnews.com/article/57edd68ae921958d581bbac2d2c306c4}{David Hollon stands inside his garage in Autauga County, Ala., on Saturday, Jan. 14, 2023. The Alabama engine mechanic took refuge in a shipping container near the back of his garage as a tornado from Thursday\textquotesingle s violent...}
