\entryitemWithDescription{\hskip 0pt{}Trader Joe's chicken soup dumplings recalled for possibly containing permanent marker plastic}{https://apnews.com/article/74d677e020d8f55bab6635508305e459}{NEW YORK (AP) --- More than 61,000 pounds of steamed chicken soup dumplings sold at Trader Joe's are being recalled for possibly containing hard plastic, U.S. regulators announced Saturday. The Agriculture Department's Food Safety and...}

\entryitemWithDescription{\hskip 0pt{}Fans gather to say goodbye to Flaco the owl in New York City memorial}{https://apnews.com/article/17e7f1aedc181d905880a73b37f8a5ae}{NEW YORK (AP) --- Mournful fans of Flaco the Eurasian eagle-owl were gathering in New York City on Sunday to say goodbye to the beloved celebrity creature who became an inspiration and joy to many as he flew around Manhattan after someone...}

\entryitemWithDescription{\hskip 0pt{}Surfers from Brazil and Australia win final Olympic qualifier in warm and windy Puerto Rico}{https://apnews.com/article/c1996c9ed0b024b277d80c3faae72973}{ARECIBO, Puerto Rico (AP) --- Top surfers Gabriel Medina of Brazil and Sally Fitzgibbons of Australia won the final qualifier for the upcoming Olympics on Sunday following nine days in which scores of competitors faced volatile weather...}

\entryitemWithDescription{\hskip 0pt{}`Dune: Part Two' brings spice power to the box office with \$81.5 million debut}{https://apnews.com/article/6d03d6b9aa6210ae4a517e124acf46de}{Movie theaters were looking for a savior and `` Dune: Part Two '' is delivering on the promise. Armed with sandworms, big screen spectacle and the star power of Timothée Chalamet, Denis Villeneuve 's science fiction epic stormed the North...}

\entryitemWithDescription{\hskip 0pt{}Vice President Kamala Harris to join in marking anniversary of Bloody Sunday on Alabama bridge}{https://apnews.com/article/dd03b6cc8e68e42ac89e1c9d641c12b9}{SELMA, Ala. (AP) --- Vice President Kamala Harris is expected to be among those marking the 59th anniversary of Bloody Sunday, the day Alabama law officers attacked Civil Rights demonstrators on the iconic Edmund Pettus Bridge in Selma...}

\entryitemWithDescription{\hskip 0pt{}AC Milan winger Pulisic threatened and abused following fiery Lazio win}{https://apnews.com/article/c7f27a5a786016036d01b8c2cca9ed47}{MILAN (AP) --- AC Milan winger Christian Pulisic has received a deluge of death threats and abuse on social media following their fiery 1-0 victory at Lazio in Serie A on Friday. Lazio finished the match with eight men and Pulisic was...}

\entryitemWithDescription{\hskip 0pt{}A bridge where firefighters rescued the driver of a semi dangling over the Ohio River remains closed}{https://apnews.com/article/1f352e8c40145dc5cd6c92a903e03f24}{LOUISVILLE, Ky. (AP) --- A bridge connecting Kentucky and Indiana remained closed Saturday following a harrowing crash and rescue of a tractor-trailer driver left hanging over the bridge's edge. Dramatic photos and video captured the...}

\entryitemWithDescription{\hskip 0pt{}A train derailment in eastern Pennsylvania scattered cars on a riverbank and one in the water}{https://apnews.com/article/3491b1e1c9496414bc88262b54c3d250}{BETHLEHEM, Pa. (AP) --- Authorities say a train derailment in eastern Pennsylvania has left some railroad cars along a riverbank Saturday morning and at least one partially in the river itself. Dispatchers in Northampton County said the...}

\entryitemWithDescription{\hskip 0pt{}Third baseman Matt Chapman and Giants reach a \$54 million, 3-year deal, AP source says}{https://apnews.com/article/d8ed8ad88cd3e16fd528d4622196d681}{NEW YORK (AP) --- Third baseman Matt Chapman and the San Francisco Giants have agreed to a \$54 million, three-year contract, a person familiar with the negotiations told The Associated Press. Chapman will get \$20 million this year and...}

\entryitemWithDescription{\hskip 0pt{}An arrest has been made in the slaying of a pregnant Amish woman in Pennsylvania}{https://apnews.com/article/ba56817e10a88be554966ef740d5b3c4}{SPARTANSBURG, Pa. (AP) --- A Pennsylvania man was arrested Saturday and charged with the slaying of a pregnant Amish woman whose body was found last week. Shawn C. Cranston, 52, of Corry, has been charged with criminal homicide, criminal...}

\entryitemWithDescription{\hskip 0pt{}A party like no other? Asia's richest man celebrates son's prenuptials with a star-studded bash}{https://apnews.com/article/d36e73d8b83229b7684e6253d84e23d5}{NEW DELHI (AP) --- What happens when the son of Asia's richest man is about to get married? His father throws a three-day prenuptial bash four months before the actual ceremony. Tycoons from around the world, heads of state, as well as...}

\entryitemWithDescription{\hskip 0pt{}Alaska's Iditarod dogs get neon visibility harnesses after 5 were fatally hit while training}{https://apnews.com/article/c6253e0122f487887993282d17c8a13a}{ANCHORAGE, Alaska (AP) --- The Iditarod, the annual sled dog race celebrating Alaska's official state sport, is set to get underway Saturday with a new focus on safety after five dogs died and eight were injured in collisions with...}

\entryitemWithDescription{\hskip 0pt{}A New Jersey city that limited street parking hasn't had a traffic death in 7 years}{https://apnews.com/article/007dec67706c1c09129da1436a3d9762}{Street parking was already scarce in Hoboken, New Jersey, when the death of an elderly pedestrian spurred city leaders to remove even more spaces in a bid to end traffic fatalities. For seven years now, the city of nearly 60,000 people...}