\entryitemWithDescription{\hskip 0pt{}Far-right parties make comeback in Greek election as conservatives sweep back to power}{https://apnews.com/article/3df35659fb5834777e3826650d97b19f}{A view of the Greek parliament, in Athens, Greece, Saturday, June 24, 2023. Greeks return to the polls Sunday for a second general election in five weeks, with the conservative front-runners eyeing a landslide win after toppling...}

\entryitemWithDescription{\hskip 0pt{}'Spider-Man: Across the Spider-Verse' slings back into box office top spot while 'The Flash' drops}{https://apnews.com/article/adfe842f6d1eb17bb2e968cdf151bba2}{This image released by Sony Pictures Animation shows Miles Morales as Spider-Man, voiced by Shameik Moore, in a scene from Columbia Pictures and Sony Pictures Animation\textquotesingle s "Spider-Man: Across the Spider-Verse." (Sony...}

\entryitemWithDescription{\hskip 0pt{}NYC gets \$25M for e-bike charging stations, seeking to prevent deadly battery fires}{https://apnews.com/article/b8ef142a1afc280cf0d9fe3054efb4b3}{FILE - A biker stops to look at a pile of e-bikes in the aftermath of a fire in Chinatown, which authorities say started at an e-bike shop and spread to upper-floor apartments, Tuesday June 20, 2023, in New York. New York City is...}

\entryitemWithDescription{\hskip 0pt{}Riders plunge from a derailed roller coaster in Sweden, killing one and injuring several others}{https://apnews.com/article/8a177435c6ce01c1aa6d20fcd5332290}{Police cordon off the Gröna Lund amusement park in Stockholm, Sunday, June 25, 2023. According to reports an accident occurred on a rollercoaster leaving one person dead. The amusement park was being evacuated and the police have set up...}

\entryitemWithDescription{\hskip 0pt{}Houston police say 1 killed and 3 wounded after groups exchange gunfire}{https://apnews.com/article/ef0f99eab1dcabd06e109babd876e5c2}{HOUSTON (AP) --- A shooting in southwest Houston early Sunday morning left one teenager dead and three other young people wounded, police said. Houston Assistant Police Chief Wyatt Martin said an altercation outside a business led to the...}

\entryitemWithDescription{\hskip 0pt{}Trump is returning to Michigan with hopes of repeating the battleground success he found in 2016}{https://apnews.com/article/f0eae34218b808e564012036ecb283ed}{FILE - Former President Donald Trump tosses caps to the crowd as he steps onstage during a rally at the Macomb Community College Sports \& Expo Center in Warren, Mich., Saturday, Oct. 1, 2022. Trump is set to appear in Michigan on Sunday...}

\entryitemWithDescription{\hskip 0pt{}Taliban leader claims women are provided with a 'comfortable and prosperous life' in Afghanistan}{https://apnews.com/article/7a28ac892b53cdc2ebff1faa0bc7664e}{FILE - Afghan women wait to receive food rations distributed by a humanitarian aid group, in Kabul, Afghanistan, on May 28, 2023. The supreme leader of the Taliban released a message Sunday, June 25, claiming that his government has taken...}

\entryitemWithDescription{\hskip 0pt{}EXPLAINER: What is the Hajj pilgrimage and what does it mean for Muslims?}{https://apnews.com/article/7e9773bfaa4f3f91b1947688d0983188}{Muslim pilgrims circumambulate around the Kaaba, the cubic structure at the Grand Mosque, during the annual hajj pilgrimage, in Mecca, Saudi Arabia, Saturday, June 24, 2023. Muslim pilgrims are converging on Saudi Arabia\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}A law that bans sex toys as obscene and morally harmful is being challenged by women in Zimbabwe}{https://apnews.com/article/f58681e4e19973500204706e6735e7f9}{A woman shows a selection of sex toys she sells to women in Zimbabwe, on Friday, June, 23, 2023. Zimbabwean woman Sitabile Dewa is challenging a sex toys ban in the country which she describes in court papers filed in March as "archaic"...}

\entryitemWithDescription{\hskip 0pt{}LGBTQ+ Pride Month reaches its grand crescendo on city streets from New York to San Francisco}{https://apnews.com/article/73226a9d1479d28e24e59415f73c228d}{A person holds a fan that reads "Equality" during the 31st annual San Francisco Dyke March on Saturday, June 24, 2023. (Santiago Mejia/San Francisco Chronicle via AP) NEW YORK (AP) --- Thousands of effusive marchers danced to club music...}

\entryitemWithDescription{\hskip 0pt{}Human remains found in California mountain area where actor Julian Sands disappeared 5 months ago}{https://apnews.com/article/1dd3af640f752394e5d8fe11a26006bd}{FILE - Actor Julian Sands attends the "Forbidden Fruit," readings from banned works of literature, Sunday, May 5, 2013, in Beverly Hills, Calif. Hikers have found human remains in a Southern California mountain area where Sands...}

\entryitemWithDescription{\hskip 0pt{}Reds' 12-game winning streak ends as Braves prevail 7-6 in 8-homer slugfest}{https://apnews.com/article/ffbb8a2a4eaec6b4954c8b857b659204}{Atlanta Braves relief pitcher Raisel Iglesias reacts after striking out Cincinnati Reds\textquotesingle{} Jonathan India to end a baseball game Saturday, June 24, 2023, in Cincinnati. (AP Photo/Jeff Dean) CINCINNATI (AP) --- Down three...}

\entryitemWithDescription{\hskip 0pt{}Hajj pilgrims perform final rituals in Mecca before heading to Mina}{https://apnews.com/article/cf09ee3c0504c4d4f5488728f2abba90}{Pilgrims walk beside pigeons outside the Grand Mosque, during the annual hajj pilgrimage, in Mecca, Saudi Arabia, Saturday, June 24, 2023. Muslim pilgrims are converging on Saudi Arabia\textquotesingle s holy city of Mecca for the largest...}