\entryitemWithDescription{\hskip 0pt{}Storms bring flash flooding to Dollywood amusement park in Tennessee}{https://apnews.com/article/33d1d54a0c8dc5d25bcaa68ab3519854}{PIGEON FORGE, Tenn. (AP) --- Strong thunderstorms brought flash flooding to Dolly Parton's Dollywood in east Tennessee. Park workers and the Pigeon Forge police and fire departments directed guests to safety on Sunday afternoon, and one...}

\entryitemWithDescription{\hskip 0pt{}`Deadpool \& Wolverine' now has the 6th biggest opening weekend of all time}{https://apnews.com/article/8d6c42b990703558360f45c1e5ae7da4}{``Deadpool \& Wolverine'' had a better Sunday than anticipated. The comic book film earned \$211 million in its first weekend in North American theaters, Disney said Monday. That's \$6 million more than was estimated on Sunday, putting ``...}

\entryitemWithDescription{\hskip 0pt{}Djokovic beats rival Nadal at the Paris Olympics in their 60th and likely last head-to-head matchup}{https://apnews.com/article/a228b2c97e4b2fa96d7a4bd9bf265778}{PARIS (AP) --- Novak Djokovic dominated rival Rafael Nadal at the start, then held off a comeback attempt to win 6-1, 6-4 at the Paris Olympics in the second round Monday, the 60th --- and likely last --- head-to-head matchup between the...}

\entryitemWithDescription{\hskip 0pt{}Triathlon cancels Olympic swim training for 2nd straight day due to poor water quality in Seine}{https://apnews.com/article/1248cb9afaae7d5185ca849123113eb9}{PARIS (AP) --- The water quality in the Seine River remained a concern Monday as officials called off the swimming portion of an Olympic triathlon training session for a second straight day. Event organizers overseeing the event at the...}

\entryitemWithDescription{\hskip 0pt{}US Rep. Sheila Jackson Lee of Texas to lie in state at Houston city hall}{https://apnews.com/article/0755f59092b8468d2e583372be5ea67a}{HOUSTON (AP) --- Several days of events honoring the life of longtime U.S. Rep. Sheila Jackson Lee of Texas were set to begin Monday with the lawmaker lying in state in Houston's city hall. President Joe Biden also was scheduled to come...}

\entryitemWithDescription{\hskip 0pt{}Princess Leia bikini costume from set of `Star Wars' movie sells at auction for \$175K}{https://apnews.com/article/d3217ee7325f66fb30cc794a64f683c0}{HOUSTON (AP) --- The gold bikini-style costume that Carrie Fisher wore as Princess Leia while making ``Return of the Jedi'' in the ``Star Wars'' franchise has sold for \$175,000, according to the auction house that handled the sale. The...}

\entryitemWithDescription{\hskip 0pt{}Beach volleyball at Eiffel Tower stadium draws the crowds looking for the perfect social media post}{https://apnews.com/article/f6f690af535cf96dc3d1d87e75ffaccc}{PARIS (AP) --- Lena Von Schōnlaub used Eiffel Tower Stadium as a backdrop for her own personal photo shoot. Von Schōnlaub shifted her head from side to side, smiling big while she held her phone in front of her face and clicked over and...}

\entryitemWithDescription{\hskip 0pt{}A manipulated video shared by Musk mimics Harris' voice, raising concerns about AI in politics}{https://apnews.com/article/3a5df582f911a808d34f68b766aa3b8e}{NEW YORK (AP) --- A manipulated video that mimics the voice of Vice President Kamala Harris saying things she did not say is raising concerns about the power of artificial intelligence to mislead with Election Day about three months away...}

\entryitemWithDescription{\hskip 0pt{}One Extraordinary (Olympic) Photo: Charlie Riedel captures Simone Biles in flight at the Paris Games}{https://apnews.com/article/3c9d9096c534aa88f4a7f14847ae6533}{PARIS (AP) --- Charlie Riedel has been an AP staff photographer in Kansas City, Missouri, for 24 years. This is his eighth Olympic games. Here is what Riedel had to say about making this extraordinary photo. Why this photo? Simone Biles...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift fans swarm a hill in Munich to watch her sold-out show for free}{https://apnews.com/article/476e861c34fad02a58ecaa7ac6f4028b}{MUNICH (AP) --- Thousands of Taylor Swift fans have gotten free seats to her concerts in Munich on a grassy hill near the concert venue. The Swifties packed the Olympic Hill, or Olympiaberg, one of the highest elevations in the southern...}

\entryitemWithDescription{\hskip 0pt{}Paris Olympics organizers say they meant no disrespect with `Last Supper' tableau}{https://apnews.com/article/9dd5fc5f1849ce9b0720fa997f38ed27}{PARIS (AP) --- Paris Olympics organizers apologized Sunday to anyone who was offended by a tableau that evoked Leonardo da Vinci's ``The Last Supper'' during the glamorous opening ceremony. Da Vinci's painting depicts the moment when...}

\entryitemWithDescription{\hskip 0pt{}Two meteor showers will flash across the sky around the same time in late July}{https://apnews.com/article/134dc44b4f441ac94e70cb452cdc9d87}{Get ready for a meteor shower doubleheader. The Southern Delta Aquariid meteor shower peaks in late July. And this year, it will coincide with a second smaller meteor shower, the Alpha Capricornids. The Delta Aquariids occur every year in...}

\entryitemWithDescription{\hskip 0pt{}The Paris Olympics are underway. Here's a look at Day 1}{https://apnews.com/article/58a47ca1dca8d5b5add8dca9dfa2a9ca}{Olympic athletes in Paris dried themselves off after Friday night's soggy-but-celebratory opening ceremony and got to business on Saturday. China won the first gold medal Games when Huang Yuting and Sheng Lihao beat South Korea's Keum...}