\entryitemWithDescription{\hskip 0pt{}Cruise line let passenger's body decompose, lawsuit says}{https://apnews.com/article/c940a669e70b685a3d86467888af5ca6}{FILE - The cruiser Celebrity Equinox built by the shipyard Meyer in Papenburg, Germany, goes down the river Ems near Gandersum on Saturday, June 20, 2009. A widow and her family are suing Celebrity Cruises for allegedly mishandling her...}

\entryitemWithDescription{\hskip 0pt{}Seeking a rebound, CNN turns to Charles Barkley, Gayle King}{https://apnews.com/article/4c4db6c0c849bee7ed90b837f2e963cc}{FILE- This photo file combo shows from left, Charles Barkley and Gayle King. TV hosts King and Barkley will headline a new primetime weekly CNN show. The network made the announcement Saturday, April 22, 2023. (AP Photo/File) NEW YORK...}

\entryitemWithDescription{\hskip 0pt{}DeSantis seeks federal aid for Fort Lauderdale flood victims}{https://apnews.com/article/6a838320ed04b8ee883a2c53b8b07fe2}{FILE - A man walks out of a flooded neighborhood Thursday, April 13, 2023, in Fort Lauderdale, Fla. Florida Gov. Ron DeSantis Saturday, April 22, 2023, is asking the Biden administration to declare Broward County a disaster area due to...}

\entryitemWithDescription{\hskip 0pt{}Shannen Doherty files for divorce after 11-year marriage}{https://apnews.com/article/54cbd739e4792972fbdea21db8fad442}{FILE - Shannen Doherty participates in Fox\textquotesingle s "BH90210" panel at the Television Critics Association Summer Press Tour on Aug. 7, 2019, in Beverly Hills, Calif. Doherty has filed for divorce from her husband, Kurt...}

\entryitemWithDescription{\hskip 0pt{}Heat wave in Thailand prompts warning to stay indoors}{https://apnews.com/article/68ae07fef2cc1131ed611af8b7497d8f}{A woman holds an umbrella to shelter from the sun in Bangkok, Thailand, Saturday, April 22, 2023. The authorities warned residents across Thailand to avoid outdoor activities due to extreme heat over the weekend. (AP Photo/Sakchai Lalit...}

\entryitemWithDescription{\hskip 0pt{}Oklahoma county worried about fallout from racist recording}{https://apnews.com/article/63bd5a40dd4367be91bce529ee73faa6}{Bartender June Davis pours drinks inside the Hochatown Distilling Co. bar in Broken Bow, Okla. on Thursday, April 20, 2023. The growing optimism of McCurtain County\textquotesingle s tourism boom over the last two decades took a gut punch...}

\entryitemWithDescription{\hskip 0pt{}Elephant dies at Pakistani zoo days after procedure}{https://apnews.com/article/ae0ef50c738affa81347cc29c90f0e45}{Misting fans are placed beside the body of an elephant named "Noor Jehan" at a zoo in Karachi, Pakistan, Saturday, April 22, 2023. The critically ill elephant that underwent a critical medical procedure by international veterinarians...}

\entryitemWithDescription{\hskip 0pt{}Explorers find WWII ship sunk with over 1,000 Allied POWs}{https://apnews.com/article/df030b8725be477b617b50bee144a767}{This photo provided by the Australian War Memorial shows the Montevideo Maru. A team of explorers announced it found the sunken Japanese ship that was transporting Allied prisoners of war when it was torpedoed off the coast of the...}

\entryitemWithDescription{\hskip 0pt{}Dame Edna creator Barry Humphries dies in Sydney at 89}{https://apnews.com/article/a9ee087f22a99facebb3c7b134dc0186}{FILE - Australian TV presenter Barry Humphries performs on stage as Dame Edna for the Farewell Tour, at the London Palladium theatre, in central London, on Nov. 13, 2013. Tony Award-winning comedian Barry Humphries, internationally...}

\entryitemWithDescription{\hskip 0pt{}Police: 8 people, including girl, wounded in 2 DC shootings}{https://apnews.com/article/af15fc46290343afadd645a4e731382f}{WASHINGTON (AP) --- Two shootings in Washington, D.C., on Friday night resulted in eight people, including a young girl, suffering injuries, the Metropolitan Police Department said. There were no fatalities in the two shootings, which...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Glimpses of a changing Earth, as seen from above}{https://apnews.com/article/bb825862661d27fdd93131400fd42826}{Water surrounds the coast of Cabo da Roca near Lisbon, Portugal, Friday, April 14, 2023. (AP Photo/Michael Probst) Charred, drained or swamped, built up, dug out or taken apart, blue or green or turned to dust: this is the Earth as seen...}

\entryitemWithDescription{\hskip 0pt{}Sculptures, artifacts returned to Peru in LA ceremony}{https://apnews.com/article/1bbf9ace619d4bdc264ca12ef6dd28de}{CLARIFIES THAT REPATRIATION OCCURRED FRIDAY AND NOT TUESDAY - Claudia Bastante, Peruvian Deputy-Counsel in Los Angeles and professional archaeologist, smiles as she looks at khipus, part of the recovered Peruvian cultural property in Los...}

\entryitemWithDescription{\hskip 0pt{}House Republicans, Manhattan DA end fight over Trump inquiry}{https://apnews.com/article/8ae9e9b2f2b076b3649b4fa25be73b0c}{FILE - Attorney Mark Pomerantz arrives at Federal Court in New York, Aug. 12, 2002. House Republicans on Thursday, April 6, subpoenaed Pomerantz, one of the former Manhattan prosecutors who had been leading a criminal investigation into...}