\entryitemWithDescription{\hskip 0pt{}Philadelphia votes to ban ski masks to decrease crime. Opponents worry it'll unfairly target some}{https://apnews.com/article/4f2213f3551f85dfb94ecb7e7228580c}{PHILADELPHIA (AP) --- Philadelphia City Council passed legislation to ban ski masks in some public spaces, a measure supporters say will increase public safety amid high violent crime, but opponents argue it will unfairly target people...}

\entryitemWithDescription{\hskip 0pt{}NOT REAL NEWS: A look at what didn't happen this week}{https://apnews.com/article/99ccb985d8e06b6cc7cd21fba1689a1c}{A roundup of some of the most popular but completely untrue stories and visuals of the week. None of these are legit, even though they were shared widely on social media. The Associated Press checked them out. Here are the facts: \_\_\_...}

\entryitemWithDescription{\hskip 0pt{}Young humpback whale leaps out of Seattle bay, dazzling onlookers}{https://apnews.com/article/8f0aa5af1b3a94052276f0bcbee7ab51}{SEATTLE (AP) --- A humpback whale visiting the waters off Seattle dazzled onlookers Thursday morning with several breaches in the bay just beyond the city's downtown area. The whale has been spotted for the last three days swimming around...}

\entryitemWithDescription{\hskip 0pt{}Sen. Rand Paul performed Heimlich maneuver on choking Sen. Joni Ernst during GOP lunch}{https://apnews.com/article/6cdde719bef9bb82d96903b5b390a16b}{WASHINGTON (AP) --- Sen. Joni Ernst, a Republican from Iowa, was choking on food during a luncheon Thursday when fellow Republican Sen. Rand Paul of Kentucky performed the Heimlich maneuver on her. The incident occurred during a closed...}

\entryitemWithDescription{\hskip 0pt{}Biden lights the National Christmas Tree, taking his turn to bring holiday spirit to Washington}{https://apnews.com/article/730fb9076756772a664162b3a87c6261}{WASHINGTON (AP) --- It was President Joe Biden `s turn to bring some holiday spirit to the U.S. capital. The president and his wife, Jill, participated Thursday in the annual tradition of lighting the National Christmas Tree on the...}

\entryitemWithDescription{\hskip 0pt{}`Killers of the Flower Moon' named best film of 2023 by New York film critics}{https://apnews.com/article/3620e2ea34519d9adf139adcbffc68fe}{NEW YORK (AP) --- Martin Scorsese's ``Killers of the Flower Moon'' has been named the best film of the year by the New York Film Critics Circle. It's the third time that Scorsese has been given the best film award from his hometown's...}

\entryitemWithDescription{\hskip 0pt{}Review: In concert film `Renaissance,' Beyoncé offers glimpse into personal life during world tour}{https://apnews.com/article/f615ffd3bd7c452d6aaa7e75df20c428}{LOS ANGELES (AP) --- In Beyoncé's concert film, she describes her recent Renaissance World Tour as being run like a machine: From lighting to set design, the superstar had a hand in everything production-related to ensure her stadium tour...}

\entryitemWithDescription{\hskip 0pt{}Will an earlier Oscars broadcast attract more viewers? ABC plans to try the 7 p.m. slot in 2024}{https://apnews.com/article/e9513b3a6132b3cd0462f47570297734}{Academy Awards enthusiasts won't have to stay up quite as late to hear the best picture winner in March. The 96th Oscars will begin one hour early, with the official show starting at 7 p.m. Eastern for the first time, ABC said Thursday...}

\entryitemWithDescription{\hskip 0pt{}Bills linebacker Von Miller turns himself in on felony domestic violence charge}{https://apnews.com/article/2d634ebf2d4824e71cf1f486ba96e612}{DALLAS (AP) --- Buffalo Bills linebacker Von Miller turned himself in to police in a Dallas suburb on Thursday after he was charged in a warrant with domestic violence against the mother of his children, who is pregnant, police said...}

\entryitemWithDescription{\hskip 0pt{}Cristiano Ronaldo faces a \$1 billion class-action lawsuit after promoting Binance NFTs}{https://apnews.com/article/09a034a90785390800cbc254ce0a2f68}{NEW YORK (AP) --- Portuguese soccer star Cristiano Ronaldo has been hit with class-action lawsuit seeking at least \$1 billion in damages for his role in promoting cryptocurrency-related ``non-fungible tokens,'' or NFTs, issued by the...}

\entryitemWithDescription{\hskip 0pt{}Musk uses expletive to tell audience he doesn't care about advertisers that fled X over hate speech}{https://apnews.com/article/f68bf51e756cce822a691b3badb2050a}{NEW YORK (AP) --- Billionaire Elon Musk said Wednesday that advertisers who have halted spending on his social media platform X in response to antisemitic and other hateful material are engaging in ``blackmail'' and, using a profanity...}

\entryitemWithDescription{\hskip 0pt{}Safety officials release details of their investigation into a close call between planes in Texas}{https://apnews.com/article/30544386553310b69dba7f490ed93d17}{DALLAS (AP) --- The air traffic controller on duty when FedEx and Southwest planes nearly collided earlier this year in Texas told investigators that he expected the airliner to take off more quickly --- before the incoming FedEx plane...}

\entryitemWithDescription{\hskip 0pt{}Iconic Christmas tree at Rockefeller Center illuminated in midst of pro-Palestinian protest}{https://apnews.com/article/745947a9f2d39c7d3649c35d539d95ba}{NEW YORK (AP) --- The iconic Christmas tree at Rockefeller Center was lit by more than 50,000 multicolored lights Wednesday night as crowds massed in New York City for the holiday tradition. The massive tree --- a 12 ton, 80-foot-tall...}