\entryitemWithDescription{\hskip 0pt{}Nun whose body shows little decay since 2019 death draws hundreds to rural Missouri}{https://apnews.com/article/50f099ca4346fd7192c78a8b5e22ae01}{People pray over the body of Sister Wilhelmina Lancaster at the Benedictines of Mary, Queen of Apostles abbey Sunday, May 28, 2023, near Gower, Mo. Hundreds of people visited the small town in Missouri this week to see the nun...}

\entryitemWithDescription{\hskip 0pt{}Uganda's president signs into law anti-gay legislation with death penalty in some cases}{https://apnews.com/article/e236013019a26a0348968e6593f04f14}{FILE - A gay Ugandan couple cover themselves with a pride flag as they pose for a photograph in Uganda on March 25, 2023. Uganda\textquotesingle s president Yoweri Museveni has signed into law tough new anti-gay legislation supported by...}

\entryitemWithDescription{\hskip 0pt{}Nepal honors Sherpa guides, climbers to mark 70th anniversary of Mount Everest conquest}{https://apnews.com/article/f3b5f647aadcb82c8ce3404adbec0c25}{Women hold placards and photos of various record-holding climbers as they mark the 70 anniversary of the first ascent of Mount Everest in Kathmandu, Nepal, Monday, May 29, 2023. The 8,849-meter (29,032-foot) mountain peak was first scaled...}

\entryitemWithDescription{\hskip 0pt{}China plans to land astronauts on moon before 2030, expand space station, bring on foreign partners}{https://apnews.com/article/368d45fa997307ae2c94bcd7e066e2b4}{Chinese astronauts for the upcoming Shenzhou-16 mission, from left, Gui Haichao, Jing Haipeng, and Zhu Yangzhu wave as they stand behind glass during a meeting with the press at the Jiuquan Satellite Launch Center in northwest China on...}

\entryitemWithDescription{\hskip 0pt{}Police: Fugitive's body found in Ohio River, days after recapture of fellow Ohio escapee}{https://apnews.com/article/f36a1106c074fa4ddf97703b7d529fa9}{Henderson Police Chief Sean McKinney holds a press conference after officials pulled what they believe to be the body of escaped Ohio prisoner Bradley Gillespie from the Ohio River in Henderson, Ky., Sunday afternoon, May 28, 2023. The...}

\entryitemWithDescription{\hskip 0pt{}Suspect arrested in 5 separate shootings in Phoenix metro area that left 4 dead}{https://apnews.com/article/8103c09c97006945127e5ae58802f2bc}{This booking photo provided by the Mesa, Ariz., Police Department shows Iren Byers. Byers has been arrested in connection with five separate shootings in the Phoenix metro area that left four people dead and a woman wounded, authorities...}

\entryitemWithDescription{\hskip 0pt{}Police: 3 killed in shootout involving outlaw biker gangs at New Mexico motorcycle rally}{https://apnews.com/article/eff64ef520fccb27ded36e3440419315}{Motorcycles line Main Street in Red River, N.M., Sunday, May 28, 2023. Three people were killed in a shootout Saturday during a Memorial Day motorcycle rally. (Chancey Bush/The Albuquerque Journal via AP) RED RIVER, N.M. (AP) --- Three...}

\entryitemWithDescription{\hskip 0pt{}'The Little Mermaid' makes box office splash with \$95.5 million opening}{https://apnews.com/article/c412720b88b421663b9e319692987595}{This image released by Disney shows Halle Bailey as Ariel in "The Little Mermaid." (Disney via AP) LOS ANGELES (AP) --- `` The Little Mermaid '' made moviegoers want to be under the sea on Memorial Day weekend. Disney\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}President attends 2nd grandchild's graduation as daughter of Biden's late son leaves high school}{https://apnews.com/article/2265e8f05a96d3d8bfd7003590481b88}{President Joe Biden steps off Marine One, Sunday, May 28, 2023, in Middletown, Del. Biden is attending his granddaughter Natalie Biden\textquotesingle s high school graduation. (AP Photo/Patrick Semansky) MIDDLETOWN, Del. (AP) --- It...}

\entryitemWithDescription{\hskip 0pt{}Jewish groups and city officials protest against Roger Waters concert in Frankfurt}{https://apnews.com/article/9cb70636d69019deab0b70e196b7f88b}{A woman holds a sign as she takes part in a demonstration against a concert later the day of former Pink Floyd musician Roger Waters in the Festhalle, background, in Frankfurt, Germany, Sunday, May 28, 2023. The Festhalle was the place...}

\entryitemWithDescription{\hskip 0pt{}Army Air Force pilot from Pennsylvania killed during WWII accounted for, authorities say}{https://apnews.com/article/c78c1420439fd4cc0c5e2176e0787944}{An Army Air Force pilot from Pennsylvania killed during World War II has been accounted for almost eight decades later, military authorities said. The Defense POW/MIA Accounting Agency said last week that 2nd Lt. James Litherland, 25, of...}

\entryitemWithDescription{\hskip 0pt{}Ukraine's Kostyuk booed at French Open after no handshake with Belarus' Sabalenka because of war}{https://apnews.com/article/246db658e900026603c160abd887dc32}{Aryna Sabalenka of Belarus, top, and Ukraine\textquotesingle s Marta Kostyuk, left, refused to shake hands at the end of their first round match of the French Open tennis tournament at the Roland Garros stadium in Paris, Sunday, May 28...}

\entryitemWithDescription{\hskip 0pt{}Josef Newgarden wins his first Indy 500, gives Roger Penske his 19th victory}{https://apnews.com/article/58a208b3c0aab7bc1d692b2cfd433179}{Josef Newgarden celebrates with his team and car owner Roger Penske, left, after winning the Indianapolis 500 auto race at Indianapolis Motor Speedway in Indianapolis, Sunday, May 28, 2023. (AP Photo/Michael Conroy) INDIANAPOLIS (AP...}