\entryitemWithDescription{\hskip 0pt{}Officials are preparing security in case of Trump indictment}{https://apnews.com/article/e35836ebb6179e1c0ea28877590cfc1c}{FILE - President Donald Trump speaks at his Mar-a-Lago estate on Jan. 3, 2019, in Palm Beach, Fla. Authorities are preparing for the possibility that former President Donald Trump could be indicted and arraigned as early as next week on...}

\entryitemWithDescription{\hskip 0pt{}Former Air Force officer gets prison term for Capitol attack}{https://apnews.com/article/4e25827679950d620ad0cc384a6e450f}{FILE - Retired Air Force officer Larry Rendall Brock Jr. walks out of Parker County Jail upon release on Jan. 14, 2021, in Weatherford, Texas. Brock, who stormed the U.S. Capitol dressed in combat gear and carried zip-tie handcuffs into...}

\entryitemWithDescription{\hskip 0pt{}Washington State's March Madness soundtrack? Shania Twain}{https://apnews.com/article/5cbbb40e4840bf7cf30c54334abff486}{Washington State celebrates by "punching their ticket" after the team defeated UCLA in an NCAA college basketball game in the finals of the Pac-12 women\textquotesingle s tournament, Sunday, March 5, 2023, in Las Vegas. (AP Photo/David...}

\entryitemWithDescription{\hskip 0pt{}Dems say some foreign gifts to Trump remain unaccounted for}{https://apnews.com/article/54ae698824250aeb5ff69e281967b515}{FILE - President Donald Trump speaks in the East Room of the White House in Washington on Feb. 20, 2018. Trump\textquotesingle s White House has failed to report more than 100 gifts from foreign nations worth more than a quarter-million...}

\entryitemWithDescription{\hskip 0pt{}Rural Missouri sheriff, 2 deputies arrested in plot to kidnap child}{https://apnews.com/article/56aee66d8280f68dd086e56b42a7b24e}{A rural Missouri sheriff and two deputies are jailed and facing charges accusing them of helping a man in a parental kidnapping plot. Officers with the Missouri State Highway Patrol on Thursday arrested Iron County Sheriff Jeff Burkett...}

\entryitemWithDescription{\hskip 0pt{}Biden calls for tougher penalties for execs of failed banks}{https://apnews.com/article/ed9881cd50894b513b34d38e3d4c3dee}{President Joe Biden speaks as he meets with Ireland\textquotesingle s Taoiseach Leo Varadkar in the Oval Office of the White House, Friday, March 17, 2023, in Washington. Biden on Friday called on Congress to allow regulators to impose...}

\entryitemWithDescription{\hskip 0pt{}International court issues war crimes warrant for Putin}{https://apnews.com/article/9857eb68d827340394960eccf0589253}{Russian President Vladimir Putin chairs a meeting on the social and economic development of Crimea and Sevastopol via a videoconference at the Moscow\textquotesingle s Kremlin in Moscow, Russia, Friday, March 17, 2023. (Sputnik, Kremlin...}

\entryitemWithDescription{\hskip 0pt{}Chauvin, who killed George Floyd, pleads guilty in tax case}{https://apnews.com/article/334b34e0e16875b22d49159e753d1f29}{Former Minneapolis police officer Derek Chauvin, serving time for the 2020 murder of George Floyd, appears via Zoom from a federal prison in Tucson, Ariz., on Friday, March 17, 2023. Chauvin pleaded guilty to aiding and abetting, failing...}

\entryitemWithDescription{\hskip 0pt{}Haaland criticized over `difficult' choice on Willow project}{https://apnews.com/article/2ed1969b5a6e79bdbbae33f1049c8d41}{FILE - Interior Secretary Deb Haaland announces that her agency will work to restore more large bison herds during a speech for World Wildlife Day at the National Geographic Society in Washington, March 3, 2023. (AP Photo/Andrew Harnik...}

\entryitemWithDescription{\hskip 0pt{}St. Patrick's Day rites: Parades, bagpipes, clinking pints}{https://apnews.com/article/f590dca8a1eac2fb351cf2111985dd15}{Oh, Danny boy, 'tis the time of year when Irish bagpipes are calling in the concrete glens of New York City. The annual parade --- which bills itself as the world's largest and oldest --- drew throngs to Fifth Avenue to await bagpipes and...}

\entryitemWithDescription{\hskip 0pt{}New COVID origins data point to raccoon dogs in China market}{https://apnews.com/article/4dafbb46a575e14eff9fedf2e705aee2}{FILE - Raccoon dogs are seen at a cage in Tokyo\textquotesingle s Ueno zoo Saturday, May 24, 2003. International scientists who examined previously unavailable genetic data from samples collected at a market close to where the first human...}

\entryitemWithDescription{\hskip 0pt{}Washington turns to Wall Street to help rescue dying bank}{https://apnews.com/article/2989c84b03a0f26ed4302d748fc5f39c}{A television screen displaying financial news is seen inside one of First Republic Bank\textquotesingle s branches in the Financial District of Manhattan, Thursday, March 16, 2023. The S\&P 500 was 0.8\% higher in midday trading after...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry sues tabloid for defamation over security story}{https://apnews.com/article/744b456fad30d2786f0727d6d228467c}{People walk past the Royal Court of Justice in London, Friday, March 17, 2023. The Duke of Sussex, Prince Harry is suing Associated Newspapers Limited (ANL) over an article about his separate judicial review proceedings against the Home...}