\entryitemWithDescription{\hskip 0pt{}Cohen meets Trump prosecutors amid renewed hush money probe}{https://apnews.com/article/8a1af5c032c56145830b7db8d19bb169}{FILE - Michael Cohen, former President Donald Trump\textquotesingle s longtime personal lawyer, arrives at Federal Court in New York, on Nov. 22, 2021. (AP Photo/Lawrence Neumeister, File) NEW YORK (AP) --- Donald Trump's former lawyer...}

\entryitemWithDescription{\hskip 0pt{}New Mexico shootings follow two years of election assaults}{https://apnews.com/article/fc96f8ea93cfc5107bf4e9bfaaa55482}{FILE - Solomon Pena, center, a Republican candidate for New Mexico House District 14, is taken into custody by Albuquerque Police officers, Jan. 16, 2023, in southwest Albuquerque, N.M. Two years since the attack on the U.S. Capitol, a...}

\entryitemWithDescription{\hskip 0pt{}Mother, 1-year-old son killed in Alaska polar bear attack}{https://apnews.com/article/96bc5f7f89f738547d4a074c29cb1822}{FILE - In this June 15, 2014, file photo released by the U.S. Geological Survey, a polar bear dries off after taking a swim in the Chukchi Sea in Alaska. A polar bear has attacked and killed two people in a remote village in western...}

\entryitemWithDescription{\hskip 0pt{}Biden-McConnell: Personally mismatched, professionally bound}{https://apnews.com/article/fd0cfdcae353e5b9644b6266c7cef27b}{FILE - President Joe Biden shakes hands with Senate Minority Leader Mitch McConnell of Ky., after speaking about his infrastructure agenda under the Clay Wade Bailey Bridge, Jan. 4, 2023, in Covington, Ky. By temperament and manner, Joe...}

\entryitemWithDescription{\hskip 0pt{}New ice core analysis shows sharp Greenland warming spike}{https://apnews.com/article/132636c35f162f94038d6be7c38f685c}{FILE - A boat navigates at night next to large icebergs near the town of Kulusuk, in eastern Greenland on Aug. 15, 2019. A sharp spike in Greenland temperatures since 1995 showed the giant northern island 2.7 degrees (1.5 degrees Celsius...}

\entryitemWithDescription{\hskip 0pt{}Anger grows in Virginia city where first-grader shot teacher}{https://apnews.com/article/c6b0f2360b8f083d3be15da85067bbd6}{Djifa lee, a second-grade teacher at Saunders Elementary, center, stands with her daughter as she speaks in front of the Newport News School Board at the Newport News Public Schools Administration building on Tuesday, Jan. 17, 2023, in...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk depicted as liar, visionary in Tesla tweet trial}{https://apnews.com/article/a9fa53e5485a36fd359dfead5cb51eae}{FILE - Tesla and SpaceX Chief Executive Officer Elon Musk speaks at the SATELLITE Conference and Exhibition in Washington. A federal judge on Friday, Jan. 13 2023 rejected Tesla CEO Elon Musk's bid to move or delay a trial over a...}

\entryitemWithDescription{\hskip 0pt{}Job cuts in tech sector spread, Microsoft lays off 10,000}{https://apnews.com/article/18fe0c9b8c9ff856e932e075161b1f43}{FILE - This July 3, 2014, file photo, shows the Microsoft Corp. logo outside the Microsoft Visitor Center in Redmond, Wash. Microsoft is cutting 10,000 workers, almost 5\% of its workforce, in response to ``macroeconomic conditions and...}

\entryitemWithDescription{\hskip 0pt{}Snoop Dogg, Gloria Estefan, Sade make it to Songwriters Hall}{https://apnews.com/article/c18fb65bf50c71c685bfcf6fff3bac64}{This combination of photos shows musicians Snoop Dogg, from left, Gloria Estefan, and Sade, who have been chosen to join the Songwriters Hall of Fame. (AP PHoto) NEW YORK (AP) --- Snoop Dogg, Gloria Estefan, Sade, Jeff Lynne, Glen...}

\entryitemWithDescription{\hskip 0pt{}US divided over Roe's repeal as abortion foes gird for march}{https://apnews.com/article/0a7e6ef93091d16307ca935e0ae1d2bd}{FILE - Anti-abortion activists march outside of the U.S. Supreme Court during the March for Life in Washington, Jan. 21, 2022. Anti-abortion activists will have multiple reasons to celebrate -- and some reasons for unease -\/- when they...}

\entryitemWithDescription{\hskip 0pt{}Shooting by 6-year-old raises complex cultural questions}{https://apnews.com/article/080df45fb792de5c825b151315ba8a8c}{Willow Crawford, left, and her older sister Ava, right, join friend Kaylynn Vestre, center, in expressing their support for Richneck Elementary School first-grade teacher Abby Zwerner during a candlelight vigil in her honor at the School...}

\entryitemWithDescription{\hskip 0pt{}Wholesale inflation in US slowed further in December to 6.2\%}{https://apnews.com/article/9e3cc464878b8e3cd84c93e27da6e705}{File - Auto parts are displayed on a shelf at a car repair shop, Wednesday, July 13, 2022, in Collingdale, Pa. On Wednesday, the Labor Department releases the Producer Price Index for December. (AP Photo/Matt Slocum, File) WASHINGTON...}

\entryitemWithDescription{\hskip 0pt{}Church of England refuses to back same-sex marriage}{https://apnews.com/article/5086b3376929156e5f41461193a67aa5}{FILE - The Archbishop of Canterbury Justin Welby walks in Westminster on Sept. 14, 2022. The Church of England said Wednesday, Jan. 18, 2023, it will allow blessings for same-sex, civil marriages for the first time --- but its position on...}
