\entryitemWithDescription{\hskip 0pt{}Carl Weathers, linebacker-turned-actor who starred in `Rocky' movies and `The Mandalorian,' dies}{https://apnews.com/article/3dd38b84ac0b6d18de9f9c25a28b1198}{NEW YORK (AP) --- Carl Weathers, a former NFL linebacker who became a Hollywood action movie and comedy star, playing nemesis-turned-ally Apollo Creed in the ``Rocky'' movies, facing off against Arnold Schwarzenegger in ``Predator'' and...}

\entryitemWithDescription{\hskip 0pt{}These are their stories: Sam Waterston to leave `Law \& Order' later this month after 400 episodes}{https://apnews.com/article/2587a07099acb7bb57bf74c3bca54f70}{NEW YORK (AP) --- Sam Waterston, who has played the spiky, no-nonsense district attorney on ``Law \& Order'' since the mid-1990s, is stepping down from his legal perch. The last episode for Waterston's Jack McCoy will be Feb. 22, NBC said...}

\entryitemWithDescription{\hskip 0pt{}As Mardi Gras nears, a beefed-up police presence and a rain-scrambled parade schedule in New Orleans}{https://apnews.com/article/1c281dfba3c6d8942c62ca3488a60963}{NEW ORLEANS (AP) --- New Orleans' annual Carnival celebration entered its high-intensity home stretch Friday with a beefed-up police presence and a weather forecast that threatened to disrupt the first of two weekends of elaborate...}

\entryitemWithDescription{\hskip 0pt{}Martin Lawrence shows off his strength in new Super Bowl commercial with Shannon Sharpe}{https://apnews.com/article/c9b7de2eac41e740ce1bc284a180413a}{LOS ANGELES (AP) --- Martin Lawrence has kept busy: The actor-comedian readies for his new ``Bad Boys'' film with Will Smith this summer, recently joined his `` Martin '' cast members during the Emmys and stars alongside Hall of Fame...}

\entryitemWithDescription{\hskip 0pt{}Too pretty? Easter poster depicting a handsome, fresh-faced Jesus prompts criticism in Spain}{https://apnews.com/article/e09de88385f8f50fea5f6260b0b35a5d}{MADRID (AP) --- A poster in the southern Spanish city of Seville that depicts a young, handsome Jesus wearing only a loincloth has unleashed a storm on social media, with some calling it an affront to the figure of Christ and others...}

\entryitemWithDescription{\hskip 0pt{}Fat Tuesday means big business for New Orleans bakers under exploding demand for King Cakes}{https://apnews.com/article/7dce247fda2662a1ba4b898373131f6f}{NEW ORLEANS (AP) --- It's Carnival season in New Orleans and that means lines are long outside local bakeries and the pace inside is brisk as workers strive to meet customer demand for king cakes --- those brightly colored seasonal...}

\entryitemWithDescription{\hskip 0pt{}The crane attacked potential mates. But then she fell for her keeper}{https://apnews.com/article/18762ba42e6471d286f47fa6f8254955}{WASHINGTON (AP) --- One of the great interspecies love stories of our time has come to an end. Walnut, a white-naped crane and internet celebrity, has passed away at age 42. She is survived by eight chicks, the loving staff at the...}

\entryitemWithDescription{\hskip 0pt{}Friends imprisoned for decades cleared of 1987 New Year's killing in Times Square}{https://apnews.com/article/1f9d807f9394776b0268a370016c4cc4}{NEW YORK (AP) --- In the early hours of New Year's Day in 1987, a French tourist was mugged while walking with his wife through Times Square. The man, 71-year-old Jean Casse, struck his head on the pavement. He was pronounced dead soon...}

\entryitemWithDescription{\hskip 0pt{}Educators played the same Powerball numbers for years, then hid a \$1M winning ticket in a math book}{https://apnews.com/article/bba33b1b54d8d82fb0e394671fe01830}{LOUISVILLE, Ky. (AP) --- A group of employees and teachers from a Kentucky middle school who bought a \$1 million Powerball winning ticket tucked it in a math textbook for safekeeping before claiming the prize this week. The group of 30...}

\entryitemWithDescription{\hskip 0pt{}Skyscraper-size asteroid will buzz by Earth on Friday, but no need to worry}{https://apnews.com/article/65e3f1c026922394b616435a2ac78763}{CAPE CANAVERAL, Fla. (AP) --- An asteroid as big as a skyscraper will pass within 1.7 million miles of Earth on Friday. Don't worry: There's no chance of it hitting us since it will pass seven times the distance from Earth to the moon...}

\entryitemWithDescription{\hskip 0pt{}Annette Bening named Harvard's Hasty Pudding Woman of the Year}{https://apnews.com/article/66faccbbff6e08e57d71fab801f216cb}{CAMBRIDGE, Mass. (AP) --- Annette Bening, a two-time Golden Globe winner who recently received her fifth Oscar nomination, was named Thursday as the 2024 Woman of the Year by Harvard University's Hasty Pudding Theatricals. The Pudding is...}

\entryitemWithDescription{\hskip 0pt{}Songs by Taylor Swift, Drake and more are starting to disappear from TikTok. Here's why}{https://apnews.com/article/9b708eceeac33d8c9c5670d855c64667}{NEW YORK (AP) --- TikTok may look (or sound) a little different when you scroll through the app going forward. Earlier this week, Universal Music Group --- which represents big-name artists like Taylor Swift, Bad Bunny and Drake --- said...}

\entryitemWithDescription{\hskip 0pt{}Street artist of `Super Pope' fame gets new stamp of Vatican approval}{https://apnews.com/article/13faba99b85304f34984d44f5059c5d2}{ROME (AP) --- Street artist Maupal, whose cartoon-like depictions of Pope Francis as a ``Super Pope'' have graced buildings around the Vatican for a decade, got an official stamp of approval on Thursday when he appeared at a Vatican news...}