\entryitemWithDescription{\hskip 0pt{}EXPLAINER: Why the US flipped on sending tanks to Ukraine}{https://apnews.com/article/7b8475342e6d5e0ad6e45715fe5a1fd9}{FILE - A Leopard 2 tank is pictured during a demonstration event held for the media by the German Bundeswehr in Munster near Hannover, Germany, Wednesday, Sept. 28, 2011. Chancellor Olaf Scholz is expected to announce Wednesday, Jan. 25...}

\entryitemWithDescription{\hskip 0pt{}Afghan soldier seeking US asylum freed from federal custody}{https://apnews.com/article/957bcc74c66f8aca60e8a5de353d8743}{Sami-ullah Safi holds photographs of his brother, Abdul Wasi Safi, as he talks about his brother\textquotesingle s journey to the U.S. during an interview Wednesday, Jan. 18, 2023, in Houston. Safi\textquotesingle s brother, who...}

\entryitemWithDescription{\hskip 0pt{}Spain: 1 dead in church machete attacks, terror link probed}{https://apnews.com/article/9fedf5fe435c743b4ef918d01debcb64}{Police work next to the body of a man killed in Algeciras, southern Spain, Wednesday, Jan. 25, 2023. Spain\textquotesingle s interior ministry says that one person has been killed and another serious injured in an attack carried out by a...}

\entryitemWithDescription{\hskip 0pt{}Tax season already? Some tips for avoiding stress and scams}{https://apnews.com/article/f626db81e3941974c8fa0fffa45e7295}{FILE - A man waits outside a H\&R Block tax preparation office on Monday, April 6, 2020, in the Brooklyn borough of New York. Tax season is here again. Whether you do your taxes by yourself, go to a tax clinic or hire a professional...}

\entryitemWithDescription{\hskip 0pt{}Suspect in Half Moon Bay farm killings faces 7 murder counts}{https://apnews.com/article/aad04bf67fb035dd36482de606611498}{Merced Martinez places a candle at a memorial for victims of the mass shooting the day before in Half Moon Bay, Calif., Tuesday, Jan. 24, 2023. (Carlos Avila Gonzalez/San Francisco Chronicle via AP) HALF MOON BAY, Calif. (AP) --- A...}

\entryitemWithDescription{\hskip 0pt{}New lawsuits target state restrictions on abortion pills}{https://apnews.com/article/57f4d6f79996e38788e0aa2f28deadb9}{FILE - Boxes of the drug mifepristone sit on a shelf at the West Alabama Women\textquotesingle s Center in Tuscaloosa, Ala., on March 16, 2022. Lawsuits have been filed in West Virginia and North Carolina challenging the states...}

\entryitemWithDescription{\hskip 0pt{}AmazonSmile's end is alarming, say nonprofits that benefited}{https://apnews.com/article/0c0cb5a4526adf87d7c16ce908325d46}{FILE - In this Feb. 14, 2019 file photo, people stand in the lobby for Amazon offices in New York. Amazon is ending a charity donation program it ran for a decade in its latest cost-cutting move. In a blog post on Wednesday, Jan. 18...}

\entryitemWithDescription{\hskip 0pt{}Despite concerns, US to send 31 Abrams tanks to Ukraine}{https://apnews.com/article/7b63726a3935da3f03424e98e52a85b2}{President Joe Biden speaks about Ukraine from the Roosevelt Room at the White House in Washington, Wednesday, Jan. 25, 2023, as Secretary of State Antony Blinken, left, and Defense Secretary Lloyd Austin listen. (AP Photo/Susan Walsh...}

\entryitemWithDescription{\hskip 0pt{}Lawyer: Admins were warned 3 times the day boy shot teacher}{https://apnews.com/article/a40dfad64388aadf1f90211177412522}{Lawyer Diane Toscano, who represents Abigail Zwerner, the Newport News teacher who was shot by a six-year-old student, reads a statement to media on Wednesday, Jan. 25, 2023, in Newport News, Va. (Mike Caudill/The Virginian-Pilot via AP...}

\entryitemWithDescription{\hskip 0pt{}EXPLAINER: Novak Djokovic's successful return to Australia}{https://apnews.com/article/3b1e5a3925f8519cfaad548fb9d3806e}{Novak Djokovic of Serbia signs autographs after defeating Andrey Rublev of Russia in their quarterfinal match at the Australian Open tennis championship in Melbourne, Australia, Wednesday, Jan. 25, 2023. (AP Photo/Dita Alangkara...}

\entryitemWithDescription{\hskip 0pt{}Hurts, Jefferson, Mahomes among AP NFL MVP finalists}{https://apnews.com/article/749e5bf5c9d3c7cd37872f34b49e0928}{Philadelphia Eagles quarterback Jalen Hurts runs for a touchdown against the New York Giants during the first half of an NFL divisional round playoff football game, Saturday, Jan. 21, 2023, in Philadelphia. (AP Photo/Matt Rourke) Jalen...}

\entryitemWithDescription{\hskip 0pt{}Central American gangs raising fears in southern Mexico}{https://apnews.com/article/bbebd03f8d7c28dc2d4e40faac5d1844}{Passengers sit in a passenger van with tinted windows, inside a station in Tapachula, Mexico, Thursday, Jan. 19, 2023. With threatening phone calls, burned minibuses and at least three suspected killings, street gangs more closely...}

\entryitemWithDescription{\hskip 0pt{}Leaders are meant to keep state secrets. Just not at home.}{https://apnews.com/article/8b55b7f48f6a999fd7608799655dbb93}{FILE - This image contained in a court filing by the Department of Justice on Aug. 30, 2022, and redacted by in part by the FBI, shows a photo of documents seized during the Aug. 8 search by the FBI of former President Donald Trump...}