\entryitemWithDescription{\hskip 0pt{}Scottie Scheffler's Louisville court date postponed after arrest during PGA Championship}{https://apnews.com/article/13fa44dcc4f27690acbe970913f1aea0}{LOUISVILLE, Ky. (AP) --- A Kentucky court has postponed pro golfer Scottie Scheffler's appearance on charges he injured a police officer and disobeyed commands outside the gates of Valhalla Golf Club as the venue hosted this year's PGA...}

\entryitemWithDescription{\hskip 0pt{}`The Apprentice,' about a young Donald Trump, premieres in Cannes}{https://apnews.com/article/e6bc0f699ad88c01211ac7956a443079}{CANNES, France (AP) --- While Donald Trump's hush money trial entered its sixth week in New York, an origin story for the Republican presidential candidate premiered at the Cannes Film Festival on Monday, unveiling a scathing portrait of...}

\entryitemWithDescription{\hskip 0pt{}Ricky Stenhouse could face suspension after throwing punch at Kyle Busch after All-Star Race}{https://apnews.com/article/baf98847b89b423aa82d1bdc017c72e6}{NORTH WILKESBORO, N.C. (AP) --- Ricky Stenhouse Jr. threw a right hook at Kyle Busch, and suddenly, an otherwise boring All-Star Race at North Wilkesboro Speedway had NASCAR fans buzzing heading into next weekend's marquee Coca-Cola 600...}

\entryitemWithDescription{\hskip 0pt{}In Saudi Arabia, an all-women psychedelic rock band jams outs as its conservative society loosens up}{https://apnews.com/article/1407595ad4f757cea8d74c5ff6f43b2d}{RIYADH, Saudi Arabia (AP) --- Leaning into the microphone in Saudi Arabia's capital, Nora let loose a primal scream. Guitars wailed and drums throbbed behind her as part of a set with her bandmates during a recent show. The performance by...}

\entryitemWithDescription{\hskip 0pt{}The Paralympics open in 100 days. Paris organizers are launching a campaign to boost ticket sales}{https://apnews.com/article/266d300a47ee4fc95daecd92b9fc8318}{PARIS (AP) --- With 100 days until the Paralympics begin, Paris organizers are delivering a message from the athletes in a bid to boost ticket sales: I am not missing anything, except you. The countdown campaign for the Aug 28-Sept. 8...}

\entryitemWithDescription{\hskip 0pt{}Sour Patch Kids Oreos? Peeps Pepsi? What's behind the weird flavors popping up on store shelves}{https://apnews.com/article/dec4521457e81fa5cc801baefb3b73f5}{Van Leeuwen Ice Cream usually draws customers with gourmet takes on classics like vanilla and pistachio. But occasionally, the artisanal ice cream maker headquartered in New York slips in what it calls a ``shock flavor,'' like Hidden...}

\entryitemWithDescription{\hskip 0pt{}Red Lobster seeks bankruptcy protection days after closing dozens of restaurants}{https://apnews.com/article/a30cf6293208eefd0aaaf2bcb2782291}{Red Lobster has filed for Chapter 11 bankruptcy protection days after shuttering dozens of restaurants. The seafood chain has struggled for has been struggling for some time with lease and labor costs piling up in recent years and also...}

\entryitemWithDescription{\hskip 0pt{}Edwards leads Wolves back from 20-point deficit for 98-90 win over defending NBA champion Nuggets}{https://apnews.com/article/377332a8eee6a516d9bb30cea2a371dd}{DENVER (AP) --- Anthony Edwards overcame a slow start and the Timberwolves roared back from a 20-point second-half deficit to eliminate the reigning NBA champion Denver Nuggets 98-90 in a Game 7 Minnesota masterpiece on Sunday night. The...}

\entryitemWithDescription{\hskip 0pt{}Schauffele wins first major at PGA Championship in a thriller at Valhalla}{https://apnews.com/article/5ceccfd6fbdc500dc53e914d74c99bb2}{LOUISVILLE, Ky. (AP) --- Xander Schauffele cashed in at just the right time Sunday by making a 6-foot birdie putt on the final hole to win the PGA Championship for his first major with the lowest score in major championship history. The...}

\entryitemWithDescription{\hskip 0pt{}Jim Otto, 'Mr. Raider' and Pro Football Hall of Famer, dies at 86}{https://apnews.com/article/b7b8f757afaf4f37b6986b7bbe11f0e4}{Jim Otto, the Hall of Fame center known as ``Mr. Raider'' for his durability through a litany of injuries, has died, the team confirmed Sunday night. He was 86. The cause of death was not immediately known. ``The Original Raider,'' the...}

\entryitemWithDescription{\hskip 0pt{}Man City fans party as Guardiola's dominant team wins a record fourth-straight Premier League title}{https://apnews.com/article/be4dbed05a28211cb7ec55cb04f0bcfa}{MANCHESTER, England (AP) --- Manchester City fans could hardly stand the wait for the final whistle. Not because they feared a last-minute twist and the unlikeliest of comebacks from West Ham. The tension during the dying moments of the...}

\entryitemWithDescription{\hskip 0pt{}John Krasinski's `IF' hits a box office nerve with \$35 million debut}{https://apnews.com/article/10c81c8666bc7d553c682acb8fcca77b}{John Krasinski's imaginary friends movie ``IF'' claimed the top spot at the box office this weekend according to studio estimates Sunday. Its \$35 million North American debut was also a bit lower than some projections. Is that a...}

\entryitemWithDescription{\hskip 0pt{}Man charged with punching actor Steve Buscemi is held on \$50,000 bond}{https://apnews.com/article/20a70f6b35e4e6ab20efdc25924dc02e}{NEW YORK (AP) --- The man charged with assaulting actor Steve Buscemi on a Midtown street has been held in jail on bond in New York, prosecutors said. Police have said the 66-year-old actor --- known for his roles in ``Boardwalk Empire,''...}