\entryitemWithDescription{\hskip 0pt{}Teen and Miss USA quit their crowns, citing mental health and personal values}{https://apnews.com/article/d188872c2d4948669e416aa7c6bd9870}{The reigning winners of Miss USA, Noelia Voigt, and Miss Teen USA, UmaSofia Srivastava, resigned from their titles within days of each other this week in a shock to the Miss Universe Organization. The resignations leave the longstanding...}

\entryitemWithDescription{\hskip 0pt{}Here's what to know about conservatorships and how Brian Wilson's case evolved}{https://apnews.com/article/283adf3e04aef5744ac818c36131cf9e}{LOS ANGELES (AP) --- A judge put Beach Boys founder Brian Wilson under a court conservatorship to oversee his personal and medical affairs after the legendary songwriter's doctor reported that he has a major neurocognitive disorder. The...}

\entryitemWithDescription{\hskip 0pt{}Djokovic needs medical attention after getting knocked on the head by a water bottle at Italian Open}{https://apnews.com/article/a72f39ee6658ce1bb592526320d5fdfc}{ROME (AP) --- Novak Djokovic needed medical attention after getting knocked on the head by a water bottle after a win at the Italian Open on Friday. A child was leaning over the railing to hand Djokovic a notebook for a signature and an...}

\entryitemWithDescription{\hskip 0pt{}Flavor Flav is the official hype man for the US women's water polo team in the Paris Olympics}{https://apnews.com/article/e9b87dfc32dcdeeabd3cd97121a83c89}{Maggie Steffens asked for more support for the U.S. women's water polo team, and the captain received one particularly surprising response. From a clock-wearing rap icon. Moved by Steffens' Instagram post, Flavor Flav has stepped forward...}

\entryitemWithDescription{\hskip 0pt{}Civil War General William T. Sherman's sword and other relics to be auctioned off in Ohio}{https://apnews.com/article/e6080cb1c6e52be71e57db85e9087a18}{COLUMBUS, Ohio (AP) --- Bidders will fight with their dollars next week at an Ohio auction house for the sword of the Civil War Union general who led a scored-earth campaign across Georgia and coined the phrase ``War is hell.'' General...}

\entryitemWithDescription{\hskip 0pt{}A train in central Buenos Aires strikes a boxcar on the track, injuring dozens}{https://apnews.com/article/a0ece469b27c7ed2a1059e90040501f6}{BUENOS AIRES, Argentina (AP) --- At least 90 people were injured in Argentina's capital when a passenger train struck an empty boxcar on the tracks and derailed Friday, authorities said, a rare collision that fueled questions about basic...}

\entryitemWithDescription{\hskip 0pt{}Liam and Olivia are still the most popular US baby names, and Mateo makes his debut on the list}{https://apnews.com/article/c4973e6d6520fa4ba94eb8d70ec41b6c}{WASHINGTON (AP) --- Liam and Olivia have for a fifth year together topped the list of baby names for brand new boys and girls born in the U.S. in 2023. And Mateo joins the top 10 baby names list for the first time. The Social Security...}

\entryitemWithDescription{\hskip 0pt{}Strong solar storm could disrupt communications and produce northern lights in US}{https://apnews.com/article/fc23251025efc2d20dc128dc0b6a7c68}{CAPE CANAVERAL, Fla. (AP) --- An unusually strong solar storm headed toward Earth could produce northern lights in the U.S. and potentially disrupt communications this weekend. The National Oceanic and Atmospheric Administration issued a...}

\entryitemWithDescription{\hskip 0pt{}Target to reduce number of stores carrying Pride-themed merchandise after last year's backlash}{https://apnews.com/article/667ab2f6545645f5f86ca76394e531d6}{NEW YORK (AP) --- Target confirmed that it won't be carrying its LGBTQ+ merchandise for Pride month in June in some stores after the discount retailer received backlash last year for its assortment that also cut into sales. Target, which...}

\entryitemWithDescription{\hskip 0pt{}For Israel's contestant, the Eurovision Song Contest comes with tight security, boos and cheers}{https://apnews.com/article/23304985ecffe31100968b020dfc23f3}{MALMO, Sweden (AP) --- Eden Golan is in Sweden for the Eurovision Song Contest, but she is not seeing much of the country. The 20-year-old Israeli singer is surrounded by security as she travels between hotel and the contest venue in the...}

\entryitemWithDescription{\hskip 0pt{}Japanese automaker Honda reports booming profit on sales growth, weak yen}{https://apnews.com/article/9dd30bc34774b6c93937768d1e99d92a}{TOKYO (AP) --- Honda's profit for the fiscal year through March jumped 70\% as vehicle sales grew and a weak yen buoyed overseas earnings, the Japanese automaker reported Friday. Annual profit at Tokyo-based Honda Motor Co. totaled 1.1...}

\entryitemWithDescription{\hskip 0pt{}California is testing new generative AI tools. Here's what to know}{https://apnews.com/article/0d6b3827138d744b1a40a4057dba8634}{SACRAMENTO, Calif. (AP) --- Generative artificial intelligence tools will soon be used by California's government. Democratic Gov. Gavin Newsom's administration announced Thursday the state will partner with five companies to develop and...}

\entryitemWithDescription{\hskip 0pt{}Scores of starving and sick pelicans are found along the California coast}{https://apnews.com/article/882091b247ece246a0c19afa5c15f110}{NEWPORT BEACH, Calif. (AP) --- Scores of sick and starving pelicans have been found in coastal California communities in recent weeks and many others have died. Lifeguards spotted a cluster of two dozen sick pelicans earlier this week on...}