\entryitemWithDescription{\hskip 0pt{}Navy releases first photos of Chinese balloon recovery}{https://apnews.com/article/55233ffb9eee393214b3962a9252e279}{This image provided by the U.S. Navy shows sailors assigned to Explosive Ordnance Disposal Group 2 recovering a high-altitude surveillance balloon off the coast of Myrtle Beach, S.C., Feb. 5, 2023. (U.S. Navy via AP) WASHINGTON (AP...}

\entryitemWithDescription{\hskip 0pt{}Microsoft bakes ChatGPT-like tech into search engine Bing}{https://apnews.com/article/dd445694f34a6b7a0444db9988330229}{Microsoft CEO Satya Nadella speaks during the introduction of the integration of Microsoft Bing search engine and Edge browser with OpenAI on Tuesday, Feb. 7, 2023, in Redmond, Wash. Microsoft is fusing ChatGPT-like technology into its...}

\entryitemWithDescription{\hskip 0pt{}Fed's Powell: Strong hiring could force further rate hikes}{https://apnews.com/article/d3468f5d9f6105dadffe69f30e411aa4}{Federal Reserve Chair Jerome Powell speaks at the Economic Club of Washington, Tuesday, Feb. 7, 2023, at the Renaissance Hotel in Washington. (AP Photo/Jess Rapfogel) WASHINGTON (AP) --- Federal Reserve Chair Jerome Powell said Tuesday...}

\entryitemWithDescription{\hskip 0pt{}NFL, DAZN sign agreement for Game Pass International package}{https://apnews.com/article/b932b0f4dd4b00e60c37c1260671656b}{Seniors from NCAA colleges run through drills to increase their status for the NFL Draft during practice for the Senior Bowl NCAA college football game Wednesday, Feb. 1, 2023, in Mobile, Ala.. (AP Photo/Butch Dill) NEW YORK (AP) --- The...}

\entryitemWithDescription{\hskip 0pt{}At last: Streisand memoir 'My Name is Barbra' coming Nov. 7}{https://apnews.com/article/d005154cb54587c2105c0dcead3c44c4}{This cover image released by Viking shows "My Name is Barbra" by Barbra Streisand. (Viking via AP) NEW YORK (AP) --- Barbra Streisand\textquotesingle s very long and very long-awaited memoir, a project she has talked about for years, is...}

\entryitemWithDescription{\hskip 0pt{}Gallup: Just 2 in 10 U.S. employees have work `best friend'}{https://apnews.com/article/faa0858e623e78c70e6f7eb02c55c7f1}{This image provided by Catalina María Gomez Caycedo shows Aleena Rupani, from left, Catalina María Gomez Caycedo, Henry Crabtree, and Michael Watkins in Crabtree\textquotesingle s London flat. The close friends met through their work at a...}

\entryitemWithDescription{\hskip 0pt{}Ticket demand, anticipation grows as LeBron nears Kareem}{https://apnews.com/article/8f24e21880de99d6d30d26c988954264}{Los Angeles Lakers forward LeBron James moves the ball up court in the second half of an NBA basketball game against the New Orleans Pelicans in New Orleans, Saturday, Feb. 4, 2023. The Pelicans won 121-136. (AP Photo/Gerald Herbert...}

\entryitemWithDescription{\hskip 0pt{}China says will 'safeguard interests' over balloon shootdown}{https://apnews.com/article/a75ba8d9fa157e5b87318483141b19ca}{FILE - Chinese Foreign Ministry spokesperson Mao Ning gestures during a press conference at the Ministry of Foreign Affairs in Beijing, Thursday, Oct 13, 2022. China said Tuesday, Feb. 7, 2023, it will ``resolutely safeguard its...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl gambling surging as states legalize it? You bet}{https://apnews.com/article/297114f58b89e5be88d9c875e74323fb}{Frank Caltagirone, a sports book employee at the Ocean Casino Resort in Atlantic City, N.J., counts money from his drawer Monday, Feb. 6, 2023. On Feb. 7, 2023, the gambling industry\textquotesingle s national trade group, the American...}

\entryitemWithDescription{\hskip 0pt{}Germany, Denmark, Netherlands pledge Ukraine Leopard 1 tanks}{https://apnews.com/article/a6e3f41e8a72e52466bff4d860bded38}{Anastasia, center, cries as soldiers carry the coffin of her brother Oleg Kunynets, a Ukrainian military servicemen who were killed in the east of the country, during his funeral in Lviv, Ukraine, Tuesday, Feb 7, 2023. (AP Photo/Emilio...}

\entryitemWithDescription{\hskip 0pt{}Amid soaring crime, Memphis cops lowered the bar for hiring}{https://apnews.com/article/93033874b99a4893c6c996fd56676795}{Memphis Police Director Cerelyn Davis speaks during an interview with The Associated Press in Memphis, Tenn., Friday, Jan. 27, 2023, in advance of the release of police body cam video showing Tyre Nichols being beaten by Memphis police...}

\entryitemWithDescription{\hskip 0pt{}Race to find survivors as quake aid pours into Turkey, Syria}{https://apnews.com/article/c727c62abe97d9f6171462351dc4584c}{In the northwestern Syrian town of Jinderis, a girl has been dug out from under a collapsed building. Rescue workers search for survivors on a collapsed building in Malatya, Turkey, Tuesday, Feb. 7, 2023. Search teams and aid are pouring...}

\entryitemWithDescription{\hskip 0pt{}Boeing plans to cut about 2,000 finance and HR jobs in 2023}{https://apnews.com/article/a6525dc7f58100c924ae2f7e2ce97e6d}{FILE - A Boeing 737 Max jet prepares to land at Boeing Field following a test flight in Seattle, Sept. 30, 2020. Boeing plans to make staffing cuts in the aerospace company\textquotesingle s finance and human resources support services...}