\entryitemWithDescription{\hskip 0pt{}Prince Harry challenges UK government's decision to strip him of security detail when he moved to US}{https://apnews.com/article/ff8146324be6c1674c26e05f433bb017}{LONDON (AP) --- A lawyer for Prince Harry on Tuesday challenged the British government's decision to strip him of his security detail after he gave up his status as a working member of the royal family and moved to the United States. The...}

\entryitemWithDescription{\hskip 0pt{}Alicia Keys' semi-autobiographical stage musical `Hell's Kitchen' moves to Broadway in spring}{https://apnews.com/article/dd968635e08cece242652747e2978045}{NEW YORK (AP) --- Broadway audiences will soon be hearing the hit songs of Alicia Keys --- not far from where the multiple-Grammy-winner grew up. ``Hell's Kitchen,'' the semi-autobiographical musical by the singer-songwriter, is making...}

\entryitemWithDescription{\hskip 0pt{}Photographs capture humpback whale's Seattle visit, breaching in waters in front of Space Needle}{https://apnews.com/article/e7b2b225231da34721e8028e6206f215}{Seattle (AP) --- Pictures released by a conservation group show a young humpback whale breaching in front of the Space Needle as it visited the waters off Seattle last week, capturing a rare display of wildlife next to a major city. The...}

\entryitemWithDescription{\hskip 0pt{}George Santos is offering personalized videos for \$200}{https://apnews.com/article/7aa0cf8ed6303a1e18da0b7a108e341c}{ALBANY, N.Y. (AP) --- George Santos already has a new gig. The former congressman, fresh off his historic expulsion last week, has created a Cameo account where the public can pay for a personalized video message. Screenshots of his...}

\entryitemWithDescription{\hskip 0pt{}US tourist from Boston killed in shark attack in Bahamas, police say}{https://apnews.com/article/13611abef5feb616d230345009f55eb5}{SAN JUAN, Puerto Rico (AP) --- A female tourist from Boston was killed Monday by a shark while paddleboarding in the Bahamas, police told reporters. The victim, who was not identified, was attacked less than a mile off the western end of...}

\entryitemWithDescription{\hskip 0pt{}Gloria Allred is representing the family of girl involved in Josh Giddey's case}{https://apnews.com/article/92e9175873c8486c2a69a1ac6caf4903}{OKLAHOMA CITY (AP) --- Gloria Allred is representing the family of the girl with whom Oklahoma City Thunder guard Josh Giddey is accused of having an improper relationship, the famed attorney confirmed Monday. Allred has been an advocate...}

\entryitemWithDescription{\hskip 0pt{}Whistleblower allegation: Harvard muzzled disinfo team after \$500 million Zuckerberg donation}{https://apnews.com/article/b4716aa988a721dcc1bc651462179f20}{A prominent disinformation scholar who left Harvard University in August has accused the school of muzzling her speech and stifling --- then dismantling --- her research team as it launched a deep dive in late 2021 into a trove of...}

\entryitemWithDescription{\hskip 0pt{}AP's top songs of 2023: `On My Mama,' `Flowers,' `Monaco' and more}{https://apnews.com/article/cab41d556a9bd9b220555719aaba9b56}{LOS ANGELES (AP) --- Ten of the best songs of the year, as determined by Associated Press Music Writer Maria Sherman, in no particular order. Dive in. ``On My Mama,'' Victoria Monét Buckle up for some positive affirmations! The 10-time...}

\entryitemWithDescription{\hskip 0pt{}Oxford University Press has named `rizz' as its word of the year}{https://apnews.com/article/2c01871c71fd3632b3c64c07a4d361f3}{LONDON (AP) --- Oxford University Press has named ``rizz″ as its word of the year, highlighting the popularity of a term used by Generation Z to describe someone's ability to attract or seduce another person. It topped ``Swiftie'' (an...}

\entryitemWithDescription{\hskip 0pt{}Indonesia's Marapi volcano erupts for the second day, halting search for 12 missing climbers}{https://apnews.com/article/16921eb03471c95069a28d34100dc7c2}{PADANG, Indonesia (AP) --- Indonesian authorities halted the search for 12 climbers after Mount Marapi volcano erupted again Monday, spewing a new burst of hot ash as high as 800 meters (2,620 feet) into the air, officials said. The...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift watches Travis Kelce at Lambeau Field as Packers beat Chiefs}{https://apnews.com/article/2a1a9e791afbf7a3cb86ec458b1aae67}{GREEN BAY, Wis. (AP) --- Taylor Swift was on hand at Lambeau Field to watch Travis Kelce and the Kansas City Chiefs in their Sunday night game against the Green Bay Packers. It was the fifth Chiefs game Swift has attended since the pop...}

\entryitemWithDescription{\hskip 0pt{}Mexican woman killed in shark attack on Pacific coast near the port of Manzanillo}{https://apnews.com/article/a58d3c40db536e0bc39888816cb42913}{MEXICO CITY (AP) --- A Mexican woman died after she was severely bitten in the leg by a shark in the Pacific Ocean off the beach town of Melaque, authorities said Sunday. Rafael Araiza, the head of the local civil defense office, said the...}

\entryitemWithDescription{\hskip 0pt{}Review: The long Kiss goodbye ends at New York's Madison Square Garden}{https://apnews.com/article/ee65cd326572ef07f4cd1ce5886b962c}{NEW YORK (AP) --- It's the end of the road for Kiss. But it's not the end of Kiss. The hard-rocking quartet from New York City played final live concerts Friday and Saturday at Madison Square Garden, culminating a half century of rocking...}