\entryitemWithDescription{\hskip 0pt{}Jacinda Ardern given a top New Zealand honor for her service during shooting, pandemic}{https://apnews.com/article/a193ffe05e6ab5651bde63133a432bdc}{FILE - New Zealand Prime Minister Jacinda Ardern speaks during a joint news conference with Australia\textquotesingle s Prime Minister Anthony Albanese in Sydney, July 8, 2022. On Monday, June 5, 2023, former Prime Minister Ardern...}

\entryitemWithDescription{\hskip 0pt{}'Spider-Man: Across the Spider-Verse' swings to massive \$120.5 million opening}{https://apnews.com/article/b618e5cbf841e33c829ea542f35383cb}{En esta imagen proporcionada por Sony Pictures Animation, Miles Morales como Spider-Man, con la voz de Shameik Moore, izquierda, y Spider-Gwen, con la voz de Hailee Steinfeld, en una escena de la película de Columbia Pictures y Sony...}

\entryitemWithDescription{\hskip 0pt{}Four dead in Missouri after car crosses center line, strikes motorcyclists}{https://apnews.com/article/a634e4a68a0cceaeff3686be33c901c7}{AURORA, Mo. (AP) --- Four people died and seven others were seriously injured when a car crossed the center line of a Missouri highway and struck five motorcycles. The accident happened Saturday afternoon on Missouri Route 39 near the...}

\entryitemWithDescription{\hskip 0pt{}Russia's most famous icon handed over from museum to church despite protests}{https://apnews.com/article/c78adcee0c929208013c9936f9969291}{In this photo released by Russian Orthodox Church Press Service, the Trinity icon by Andrei Rublev is displayed as Russian Orthodox Church Patriarch Kirill conducts an Orthodox service celebrating Trinity Sunday with Russia...}

\entryitemWithDescription{\hskip 0pt{}Apple is expected to unveil a sleek, pricey headset. Is it the device VR has been looking for?}{https://apnews.com/article/dc524172ada659536dbeed5f5efb11fa}{File - Apple CEO Tim Cook discusses the Apple Watch at the Apple event at the Bill Graham Civic Auditorium in San Francisco, Wednesday, Sept. 9, 2015. If Apple unveils a widely anticipated headset equipped with mixed reality technology on...}

\entryitemWithDescription{\hskip 0pt{}Hundreds of thousands march in Poland anti-government protests to show support for democracy}{https://apnews.com/article/4ab13141a16b88d63b060c1f977bb75e}{Participants join an anti-government march led by the centrist opposition party leader Donald Tusk, who along with other critics accuses the government of eroding democracy, in Warsaw, Poland, Sunday, June 4, 2023. Poland\textquotesingle...}

\entryitemWithDescription{\hskip 0pt{}Slow start to New York's legal pot market leaves farmers holding the bag}{https://apnews.com/article/6fccc18db3fa520ccd651bd6d9a162b0}{Last seasons plant stalks are seen at Seth Jacobs\textquotesingle{} marijuana planting field at his Slack Hollow farm in Argyle, N.Y., Friday, May 12, 2023. Farmers growing New York\textquotesingle s first legal adult marijuana crop are...}

\entryitemWithDescription{\hskip 0pt{}Florida woman charged with child neglect after her car catches fire as she was allegedly shoplifting}{https://apnews.com/article/1d568bf4998bae0fb4173a5df8cbe7da}{OVIEDO, Fla. (AP) --- A Florida woman faces charges of aggravated child neglect and arson after her car became engulfed in flames while she was allegedly shoplifting at a mall, according to an arrest report. Alicia Moore, 24, parked her...}

\entryitemWithDescription{\hskip 0pt{}What led Capitol Police to stop a youth performance of the `Star-Spangled Banner'}{https://apnews.com/article/750e6031a67fd2fca735799df96916fb}{In this image taken from a video, the Rushingbrook Children's Choir sings the ``Star-Spangled Banner'' in the U.S. Capitol's Statuary Hall on Friday, May 26, 2023, in Washington. Social media users are claiming the Greenville, South...}

\entryitemWithDescription{\hskip 0pt{}Texas bans gender-affirming care for minors after governor signs bill}{https://apnews.com/article/c3dd6c3147916e9ff4f2c91172afc1bc}{FILE - Texas Gov. Greg Abbott speaks at a news conference in Austin, Texas on June 8, 2021. Texas has become the most populous state to ban gender-affirming care for minors. Abbott signed legislation on Friday, June 2, 2023, instituting...}

\entryitemWithDescription{\hskip 0pt{}Wildfire in Canadian province contained, while another burns out of control}{https://apnews.com/article/fb4a05893fc375ecc1f0db9f37ce18dd}{In this aerial image, an aircraft, center, flies near a wildfire burning near Barrington Lake in Shelburne County, Nova Scotia, on Wednesday, May 31, 2023. (Communications Nova Scotia/The Canadian Press via AP) HALIFAX, Nova Scotia...}

\entryitemWithDescription{\hskip 0pt{}Cardinal performs rite to restore Vatican altar desecrated by man's naked protest}{https://apnews.com/article/98c8f3e617c922c2d4939fbf254283af}{CORRECTS CARDINAL NAME - Cardinal Mauro Gambetti, center, blesses the altar of the confession during a penitential rite inside St. Peter\textquotesingle s Basilica, Saturday, June 3, 2023. (AP Photo/Gregorio Borgia) VATICAN CITY (AP...}

\entryitemWithDescription{\hskip 0pt{}Trump-appointed judge rejects Tennessee's anti-drag law as too broad, too vague}{https://apnews.com/article/ff16eb4bdbd0d69863eef38bf93503cf}{FILE - Drag artist Vidalia Anne Gentry speaks during a news conference held by the Human Rights Campaign to draw attention to anti-drag bills in the Tennessee legislature, Tuesday, Feb. 14, 2023 in Nashville, Tenn. A federal judge says...}