\entryitemWithDescription{\hskip 0pt{}High jumper Yaroslava Mahuchikh wins Ukraine's 1st individual gold of the Paris Olympics}{https://apnews.com/article/d51aeacd172d5590c2f6e6dc17d4ea10}{SAINT-DENIS, France (AP) --- Ukrainian high jumper Yaroslava Mahuchikh, who was forced to flee her country due to the war with Russia, won gold at the Paris Olympics on Sunday. She had the perfect partner to celebrate with: teammate Iryna...}

\entryitemWithDescription{\hskip 0pt{}Noah Lyles wins Olympic 100-meter sprint by five-thousandths of a second}{https://apnews.com/article/ccf37184afc2f3318271d4c495d2a16b}{SAINT-DENIS, France (AP) --- Noah Lyles won the Olympic 100 meters by .005 seconds Sunday, waiting some 30 seconds after the finish of an excruciatingly close sprint to find out he'd beaten Kishane Thompson of Jamaica. The word ``Photo''...}

\entryitemWithDescription{\hskip 0pt{}Belgium withdraws from mixed relay triathlon after athlete who swam in Seine River falls ill}{https://apnews.com/article/0082feb9442a4fac02cf530508a7c969}{PARIS (AP) --- Belgium's Olympic committee announced Sunday that it would withdraw its team from the mixed relay triathlon at the Paris Olympics after one of its competitors who swam in the Seine River fell ill. Claire Michel, who...}

\entryitemWithDescription{\hskip 0pt{}With a \$97M second weekend, `Deadpool \& Wolverine' sets a new high mark for R-rated films}{https://apnews.com/article/f6d810c4de19c78c4875ccc8728b6960}{NEW YORK (AP) --- After 10 days in theaters, ``Deadpool \& Wolverine'' is already the highest-grossing R-rated movie ever, not accounting for inflation. In its second weekend, the Marvel Studios blockbuster starring Ryan Reynolds and Hugh...}

\entryitemWithDescription{\hskip 0pt{}Boxer Cindy Ngamba becomes first athlete competing as a refugee to clinch an Olympic medal}{https://apnews.com/article/ec1ef2dc1b288597c7a007f6b946db1e}{VILLEPINTE, France (AP) --- Boxer Cindy Ngamba made history on Sunday by becoming the first athlete competing as a refugee to clinch an Olympic medal. The 25-year-old originally from Cameroon offered hope for the Refugee Olympic Team that...}

\entryitemWithDescription{\hskip 0pt{}Mourad Merzouki brings hip-hop dance to the Olympic stage with `Dance of the Games'}{https://apnews.com/article/67480d521bd11107c08881b56b1e11e1}{CRETEIL, France (AP) --- In a sweltering enclosed stage, several dancers perform synchronized routines before scattering, as others practice twisting handstands and tumbles. Amid this, Mourad Merzouki directs them, ensuring their hip-hop...}

\entryitemWithDescription{\hskip 0pt{}Fans of the Olympics find a new star. And Laurie Hernandez is not even competing this time}{https://apnews.com/article/69f0b288be23ce2c765e9a0ae872cbb1}{PARIS (AP) --- Laurie Hernandez pauses briefly and taps her head. ``There's a lot going on in here,'' the two-time Olympic gymnastics medalist turned TV analyst said with a laugh. ``There's a lot of chatter.'' Yes, there is. And whatever...}

\entryitemWithDescription{\hskip 0pt{}Everything is tougher on a bike in the Olympics: eating, drinking and, yes, bathroom breaks}{https://apnews.com/article/f87aa77ce34d62a0ce6288ab9c55e15e}{PARIS (AP) --- German cyclist Nils Politt was feeling good early in the Olympic road race on Saturday, getting into a breakaway and giving the veteran of seven Tours de France the feeling that something magical could happen on the streets...}

\entryitemWithDescription{\hskip 0pt{}More US schools are taking breaks for meditation. Teachers say it helps students' mental health}{https://apnews.com/article/5f73bbd3324ad4e9e9723b5c49fa1616}{REX, Ga. (AP) --- The third-grade students at Roberta T. Smith Elementary School had only a few days until summer vacation, and an hour until lunch, but there was no struggle to focus as they filed into the classroom. They were ready for...}

\entryitemWithDescription{\hskip 0pt{}Paris Olympics water safety patrol `like guardian angels' during surfing competition in Tahiti}{https://apnews.com/article/3adb4b98e1330696f3e6d92139acde0c}{TEAHUPO'O, Tahiti (AP) --- Cracked helmets, sutured skin and checks for concussions have been all been part of the Paris Olympics surfing competition, as surfers go head-to-head on the treacherous waves of Teahupo'o, Tahiti on their quest...}

\entryitemWithDescription{\hskip 0pt{}Not even an Olympic gold medal can get Hungarian swimmer Kristóf Milák to break his silence}{https://apnews.com/article/a3fb607ae6157555855588701cfa5612}{NANTERRE. France (AP) --- Not even an Olympic gold medal could get Kristóf Milák to speak. Despite his victory Saturday night in the 100-meter butterfly at the Paris Olympics, his silence after the race was expected. Milák hasn't talked...}

\entryitemWithDescription{\hskip 0pt{}Same storm, different names: How Invest 97L could graduate to Tropical Storm Debby}{https://apnews.com/article/5dd4956e4845f9e79f6662eaf71dead4}{It's an area of low atmospheric pressure, thunderstorms and wind sloshing out of the Caribbean Sea across Cuba, into the Gulf of Mexico and toward Florida. But by the time it dissipates, weather forecasters may have called it by five...}

\entryitemWithDescription{\hskip 0pt{}Third set of remains found with gunshot wound in search for 1921 Tulsa Race Massacre graves}{https://apnews.com/article/1d6d472e333cb155f22d6e33cd2dbbb4}{OKLAHOMA CITY (AP) --- A third set of remains with a gunshot wound has been found at Tulsa cemetery in the search for graves of victims of the 1921 Tulsa Race Massacre, according to a state official. The remains are one of three sets...}