\entryitemWithDescription{\hskip 0pt{}Pat McAfee announces Aaron Rodgers' appearances are over for the rest of this NFL season}{https://apnews.com/article/299aad4008cff8434db5b8f3cf23fa3a}{Aaron Rodgers' Tuesday appearances on ``The Pat McAfee Show'' are over for the rest of this NFL season. Or possibly longer. McAfee announced at the beginning of his Wednesday show on ESPN that his fourth season of doing a weekly segment...}

\entryitemWithDescription{\hskip 0pt{}Kentucky Derby purse raised to \$5 million for 150th race in May}{https://apnews.com/article/376dc4a0285671994839e189db3b1b61}{LOUISVILLE, Ky. (AP) --- The Kentucky Derby purse has been raised to \$5 million for the 150th edition in May. The increase of \$2 million was announced Wednesday by Churchill Downs. The 1 1/4-mile race will be May 4. This year's winner...}

\entryitemWithDescription{\hskip 0pt{}Alaska Airlines cancels flights on certain Boeing planes through Saturday for mandatory inspections}{https://apnews.com/article/ebaccdbc28a38ccfea396840ae71ec38}{Alaska Airlines is canceling through Saturday all flights on Boeing 737 Max 9 planes like the one that suffered an in-flight blowout of a fuselage panel last week as it waits for new instructions from Boeing and federal officials on how...}

\entryitemWithDescription{\hskip 0pt{}Engine maker Cummins to repair, replace 600,000 Ram trucks in \$2 billion emissions cheating scandal}{https://apnews.com/article/5bf95ebbd255bcd9758edce5fad1205f}{The Department of Justice released new details of a settlement with engine manufacturer Cummins Inc. Wednesday that includes a mandatory recall of 600,000 Ram trucks, and that Cummins remedy environmental damage it caused when it...}

\entryitemWithDescription{\hskip 0pt{}Bills fan killed outside of Dolphins' stadium after last weekend's game, police say}{https://apnews.com/article/3cd533c19f36afcbd9e829db4d99a102}{MIAMI GARDENS, Fla. (AP) --- Police in South Florida say a man fatally shot a 30-year-old Buffalo Bills fan during an altercation outside Hard Rock Stadium after the Bills defeated the Miami Dolphins in the final regular season game. As...}

\entryitemWithDescription{\hskip 0pt{}Lauren Boebert's ex-husband arrested on charges stemming from restaurant incident}{https://apnews.com/article/ed3ba1a94e6dba08bf67f1d5d54ad9b3}{DENVER (AP) --- The ex-husband of U.S. Rep. Lauren Boebert was arrested on misdemeanor charges stemming from an apparent altercation with her at a Colorado restaurant, police said Wednesday. Authorities would not say whether Lauren...}

\entryitemWithDescription{\hskip 0pt{}Holiday gatherings and a new variant have driven up COVID cases globally, the UN health agency says}{https://apnews.com/article/f371e953b8034d16b1b0a1aba294d18c}{GENEVA (AP) --- The head of the U.N. health agency said Wednesday holiday gatherings and the spread of the most prominent variant globally led to increased transmission of COVID-19 last month. Tedros Adhanom Ghebreyesus said nearly 10,000...}

\entryitemWithDescription{\hskip 0pt{}Amazon's Twitch cuts more than 500 jobs attempting to turn expensive platform profitable}{https://apnews.com/article/a90a279c233fa379a946b0b2e42033e6}{Twitch, the video game streaming platform acquired by Amazon a decade ago for close to \$1 billion, is laying off more than 500 employees as the company tries to turn the tremendously expensive division profitable. Twitch CEO Dan Clancy...}

\entryitemWithDescription{\hskip 0pt{}At CES 2024, tech companies are transforming the kitchen with AI and robots that do the cooking}{https://apnews.com/article/c17becfd4b331db36346b8f64a2ab721}{LAS VEGAS (AP) --- Chef-like robots, AI-powered appliances and other high-tech kitchen gadgets are holding out the promise that humans don't need to cook --- or mix drinks --- for themselves anymore. There was plenty new in the food and...}

\entryitemWithDescription{\hskip 0pt{}ESPN's early season baseball schedule will be the Sho Show, featuring Shohei Ohtani and Dodgers}{https://apnews.com/article/35d2b806142d7390579d3e51d3e0c5b3}{BRISTOL, Conn. (AP) --- ESPN's early season baseball schedule will be the Sho Show. Shohei Ohtani and the Los Angeles Dodgers will be featured on two of ESPN's first three ``Sunday Night Baseball'' telecasts this season. The Dodgers'...}

\entryitemWithDescription{\hskip 0pt{}NFL regular-season games see 7\% increase in viewers. 17.9M average is second highest since 2015}{https://apnews.com/article/2fdce7e47184c3dacc46068929f3c83a}{NFL regular-season games averaged 17.9 million viewers, tied for the second highest since averages were first tracked in 1995. Buoyed by increases of at least 24\% in two of the five packages, the first year of the league's new television...}

\entryitemWithDescription{\hskip 0pt{}A spiritual leader in Nepal known as `Buddha Boy' arrested on charges of rape and kidnapping}{https://apnews.com/article/c22c81357f1ed0c555caf4d871f74145}{KATHMANDU, Nepal (AP) --- A controversial Nepalese spiritual leader known as ``Buddha Boy'' was arrested on charges of sexually assaulting a minor and involvement in the disappearance of at least four of his followers from his camps...}

\entryitemWithDescription{\hskip 0pt{}Amalija Knavs, mother of former first lady Melania Trump, dies}{https://apnews.com/article/28fc01c5098ad87813a36bfde7c49584}{WASHINGTON (AP) --- Amalija Knavs, the mother of former first lady Melania Trump, has died. Trump announced the death late Tuesday without disclosing the cause. ``It is with deep sadness that I announce the passing of my beloved mother...}