\entryitemWithDescription{\hskip 0pt{}World Baseball Classic players get artsy with custom cleats}{https://apnews.com/article/797bef7f88805f684ea2b6c13e297a4b}{Custom cleats are shown Wednesday, March 1, 2023, in New York. Many players in this year\textquotesingle s World Baseball Classic---where Alex Katz is a pitcher on Israel\textquotesingle s team, will be wearing custom-designed cleats...}

\entryitemWithDescription{\hskip 0pt{}Ex-Biden aide agrees to House interview on classified docs}{https://apnews.com/article/4320d7b4b389ddd76228b3d3bb9c03f6}{FILE - House Oversight and Accountability Committee Chairman James Comer, R-Ky., speaks during hearing on Capitol Hill, Feb. 8, 2023, in Washington. Kathy Chung. a former executive assistant to President Joe Biden has agreed to sit for an...}

\entryitemWithDescription{\hskip 0pt{}Rutgers pulls away in 2nd half vs. frigid-shooting Michigan}{https://apnews.com/article/c9e6114612af44640aaa8fa83483279b}{Rutgers\textquotesingle{} Cam Spencer (10) goes up for a basket during the first half of an NCAA college basketball game against Michigan at the Big Ten men\textquotesingle s tournament, Thursday, March 9, 2023, in Chicago. (AP Photo/Erin...}

\entryitemWithDescription{\hskip 0pt{}Ex-GOP Ohio speaker, lobbyist guilty in \$60M bribery scheme}{https://apnews.com/article/30763b21fc02e62464c20a77609a63ac}{FILE - Former Ohio House Speaker Larry Householder, center, walks into Potter Stewart U.S. Courthouse with his attorneys, Mark Marein, left, and Steven Bradley, right, before jury selection in his federal trial, Jan. 20, 2023, in...}

\entryitemWithDescription{\hskip 0pt{}Mexican president to US: Fentanyl is your problem}{https://apnews.com/article/26f735a54ee0ba075c394ce85aef03d0}{Mexican President Andres Manuel Lopez Obrador gives his regularly scheduled morning press conference at the National Palace in Mexico City, Tuesday, Feb. 28, 2023. (AP Photo/Marco Ugarte) MEXICO CITY (AP) --- Mexico's president said...}

\entryitemWithDescription{\hskip 0pt{}Ex-Goldman banker gets 10-year sentence in 1MDB looting plot}{https://apnews.com/article/5caee7298daf6fd088911ce5c6f4a58d}{Roger Ng, center, a former Goldman Sachs banker, leaves federal court with his lawyers Zach Intrater, left, and Teny Geragos, right, after being sentenced to 10 years in prison for his role in looting a Malaysian development fund...}

\entryitemWithDescription{\hskip 0pt{}Judge uses a slavery law to rule frozen embryos are property}{https://apnews.com/article/82e1f36ecbcf35ec4659e8e2c3443c4f}{A judge at the Fairfax County, Va., Courthouse, seen here on Tuesday, March 7, 2023, has ruled that frozen embryos can legally be considered property or "chattel," basing his opinion in part on how state law treated slaves before the...}

\entryitemWithDescription{\hskip 0pt{}Here's what Biden's budget would mean — if it had a chance}{https://apnews.com/article/3f0d64293eb6bf84d114d937627119b8}{President Joe Biden\textquotesingle s budget for fiscal year 2024 is photographed Thursday, March 9, 2023. As political gridlock puts the government at risk of defaulting, Biden is making an opening offer with a budget plan that would cut...}

\entryitemWithDescription{\hskip 0pt{}Former Trump lawyer censured for falsehoods about election}{https://apnews.com/article/fd6d72667a1f3bd01cd2249747bbbd85}{FILE - Jenna Ellis, a former member of then-President Donald Trump\textquotesingle s legal team, speaks during a news conference at the Republican National Committee headquarters, Nov. 19, 2020, in Washington. Ellis has been formally...}

\entryitemWithDescription{\hskip 0pt{}Mental health test ordered for man who disrupted flight}{https://apnews.com/article/f7d7c73677c3f7256d8999e97ec8c83c}{This still image from video provided by Lisa Olsen shows a man who federal authorities have identified as Francisco Severo Torres as he moves through the cabin on a weekend flight from Los Angeles to Boston, Sunday, March 5, 2023. Torres...}

\entryitemWithDescription{\hskip 0pt{}Yeti recalls 1.9 million coolers and cases for magnet hazard}{https://apnews.com/article/45e889593fa0b95e9dbbdd73edfc5d06}{This photo provided by the Consumer Product Safety Commission shows YETI Hopper M20 Soft Backpack Cooler. U.S. product regulators said Thursday, March 9, 2023, that Yeti has recalled 1.9 million coolers and gear cases because magnets can...}

\entryitemWithDescription{\hskip 0pt{}Apology letter found after US citizens killed in Mexico}{https://apnews.com/article/e35e8c6fcda926e5c2fb8f896aa91f4e}{A Mexican army soldier guards the Tamaulipas State Prosecutor\textquotesingle s headquarters in Matamoros, Mexico, Wednesday, March 8, 2023. A road trip to Mexico for cosmetic surgery veered violently off course when four Americans were...}

\entryitemWithDescription{\hskip 0pt{}New atmospheric river storm barrels toward California}{https://apnews.com/article/0f57c5dbe224813ead980d3fed8d566b}{After a blizzard swept through Southern California mountains, 79-year-old Alan Zagorsky found himself shut inside his home with snow blocking the door and stairways out. (March 8) A vehicle\textquotesingle s grill sticks out of a snow...}