\entryitemWithDescription{\hskip 0pt{}Taylor Swift's Rio tour marred by deaths, muggings and a dangerous heat wave}{https://apnews.com/article/713f3e0051d60c4f280f1f3b242b1569}{RIO DE JANEIRO (AP) --- The deaths of two people, muggings and a dangerous heat wave left legions of Taylor Swift's Brazilian fans angry and disappointed in the three-day Rio de Janeiro leg of the pop superstar's Eras Tour, which...}

\entryitemWithDescription{\hskip 0pt{}Boston Bruins forward Lucic to be arraigned on assault charge after wife called police to their home}{https://apnews.com/article/50b1a082368a38037f273ad1119f7dd7}{BOSTON (AP) --- Boston Bruins forward Milan Lucic is scheduled to be arraigned on an assault charge in connection with his arrest this weekend after his wife called police to their home and said he tried to choke her. A Boston Police...}

\entryitemWithDescription{\hskip 0pt{}Disneyland's \$60B expansion means parks in Hong Kong and Shanghai are only getting bigger}{https://apnews.com/article/dcf24e20ce3b8d4aa5ae40b029e7f940}{HONG KONG (AP) --- Hong Kong Disneyland opened its first Frozen-themed attraction on Monday, with thousands of eager visitors turning up to experience the new rides, some lining up for hours to get an early start. Based on Disney's wildly...}

\entryitemWithDescription{\hskip 0pt{}Pop star Shakira reaches a deal with Spanish prosecutors on the first day of tax fraud trial}{https://apnews.com/article/9c594f89ddce35c76ea08b02192b120b}{BARCELONA, Spain (AP) --- After having maintained her innocence for nearly five years, pop star Shakira struck a last-minute deal on the opening day of her tax fraud trial in Barcelona to avoid the risk of going to prison. Shakira told...}

\entryitemWithDescription{\hskip 0pt{}A\$AP Rocky appears in court where he will will soon learn if he's going to trial in shooting case}{https://apnews.com/article/e1aee44ace1a01124d1054f6fd0bdf39}{LOS ANGELES (AP) --- A Los Angeles judge found Monday that there is enough evidence for A\$AP Rocky to stand trial for allegations that he fired a gun at a former friend and collaborator outside a Hollywood hotel in 2021. Superior Court...}

\entryitemWithDescription{\hskip 0pt{}Here are some tips for Thanksgiving travelers}{https://apnews.com/article/e2d9d9eb61dd0b1591560ff89b3e3c5e}{CONCORD, N.H. (AP) --- Getting a big holiday meal on the table can be stressful for the cook (see ``The Bear,'' Season two, Episode six.) But for guests, just getting to the table also can be difficult, and there's no Butterball hotline...}

\entryitemWithDescription{\hskip 0pt{}Biden is spending his 81st birthday honoring White House tradition of pardoning Thanksgiving turkeys}{https://apnews.com/article/014375a236ba6a5995f6ed3d32c540c3}{WASHINGTON (AP) --- Liberty and Bell are ready for their presidential pardons. The two Thanksgiving turkeys were due at the White House on Monday to play their part in what has become an annual holiday tradition: a president sparing them...}

\entryitemWithDescription{\hskip 0pt{}Reactions to the death of Rosalynn Carter, former first lady and global humanitarian}{https://apnews.com/article/6d13e96cc89924a08895b200c10090c2}{ATLANTA (AP) --- Reactions to the death of Rosalynn Carter, former first lady and global humanitarian: \_\_\_ President Joe Biden said the Carters ``brought grace'' to the White House. ``He had this great integrity, still does. And she...}

\entryitemWithDescription{\hskip 0pt{}A hat worn by Napoleon sold for \$2.1 million at an auction of the French emperor's belongings}{https://apnews.com/article/17488b43e428aefee869c6b19bed2103}{PARIS (AP) --- A faded and cracked felt bicorne hat worn by Napoléon Bonaparte sold for \$2.1 million at an auction Sunday of the French emperor's belongings. Yes, \$2.1 million. The signature broad, black hat --- one of a handful still...}

\entryitemWithDescription{\hskip 0pt{}Hollywood's feast and famine before Thanksgiving, as `Hunger Games' prequel tops box office}{https://apnews.com/article/e7b3c01e186ad7d3765bde60b0355881}{``The Hunger Games: The Ballad of Songbirds \& Snakes'' topped the North American box office in its first weekend in theaters with \$44 million in ticket sales, according to studio estimates Sunday. It was a busy weekend at the multiplex...}

\entryitemWithDescription{\hskip 0pt{}Maine and Massachusetts are the last states to keep bans on Sunday hunting. That might soon change}{https://apnews.com/article/76bcbad45f23ff8e3ecf391fee0e905d}{PORTLAND, Maine (AP) --- Some states are steadily chipping away at longstanding bans on Sunday hunting, and there's a push to overturn the laws in Maine and Massachusetts, the final two states with full bans. Maine's highest court is...}

\entryitemWithDescription{\hskip 0pt{}Moldova's first dog nips Austrian president on the hand during official visit}{https://apnews.com/article/4105031b52b59fb6eb19326e473f03b8}{BERLIN (AP) --- Austrian President Alexander van der Bellen had an unusual encounter during an official visit to Moldova when the country's first dog, a rescue belonging to Moldovan President Maia Sandu, bit him on the hand. Video footage...}

\entryitemWithDescription{\hskip 0pt{}Sean `Diddy' Combs and singer Cassie settle lawsuit alleging abuse 1 day after it was filed}{https://apnews.com/article/2d2a4c8938eb82c34b62c01a30969554}{NEW YORK (AP) --- A lawsuit by singer Cassie containing allegations of beatings and abuse by music producer Sean ``Diddy'' Combs has been settled, the artists announced Friday, one day after the lawsuit was filed. The settlement was...}