\entryitemWithDescription{\hskip 0pt{}No cow needed: Oat and soy can be called milk, FDA proposes}{https://apnews.com/article/ed2acef14a014eef30a0fd24f98be07b}{FILE - Milk is displayed at a grocery store in Philadelphia, Tuesday, July 12, 2022. Food and Drug Administration officials issued guidance that says plant-based beverages don't pretend to be from dairy animals -- and that U.S. consumers...}

\entryitemWithDescription{\hskip 0pt{}Trump: East Palestine train derailment response a 'betrayal'}{https://apnews.com/article/a2d75b1403daa5b3b02a6f0ff1258f10}{Former President Donald Trump speaks at the East Palestine Fire Department as he visits the area in the aftermath of the Norfolk Southern train derailment Feb. 3 in East Palestine, Ohio, Wednesday, Feb. 22, 2023. (AP Photo/Matt Freed) The...}

\entryitemWithDescription{\hskip 0pt{}Alex Murdaugh law partner talks crime scene problems, thefts}{https://apnews.com/article/8d56f8296e59638a660f7eab98539b24}{Alex Murdaugh\textquotesingle s defense called his surviving son to the stand Tuesday to poke holes in evidence prosecutors have presented in the disgraced South Carolina attorney\textquotesingle s double murder trial. (Feb. 21) Alex...}

\entryitemWithDescription{\hskip 0pt{}MLB curtails infield shift, hopes for more singles, speed}{https://apnews.com/article/a66b8e9de1ef6b30a0b19fe4fb0dcb94}{Detroit Tigers infielders Javier Baez, left, and Jonathan Schoop, right, work on drills at second base during a spring training baseball workout Sunday, Feb. 19, 2023, in Lakeland, Fla. (AP Photo/David J. Phillip) PHOENIX (AP...}

\entryitemWithDescription{\hskip 0pt{}Space telescope uncovers massive galaxies near cosmic dawn}{https://apnews.com/article/e806176f01487742e9973e99adb24418}{This image provided by NASA and the European Space Agency shows images of six candidate massive galaxies, seen 500-800 million years after the Big Bang. One of the sources (bottom left) could contain as many stars as our present-day Milky...}

\entryitemWithDescription{\hskip 0pt{}Djokovic hopes to play in US despite being unvaccinated}{https://apnews.com/article/0bc35e230ffe3f52df9ebf504cf41aa1}{Serbian tennis player Novak Djokovic listens to a question during a press conference after his open practise session in Belgrade, Serbia, Wednesday, Feb. 22, 2023. Djokovic said Wednesday he still hopes US border authorities would allow...}

\entryitemWithDescription{\hskip 0pt{}Winner comes forward to claim \$1.35B Mega Millions jackpot}{https://apnews.com/article/4e71682820c68ec218a93311769fca2b}{FILE - A Mega Million sign displays the estimated jackpot of \$1.35 Billion at the Cranberry Super Mini Mart in Cranberry, Pa., Jan. 12, 2023. The winner of a \$1.35 billion Mega Millions jackpot has come forward to collect the prize. The...}

\entryitemWithDescription{\hskip 0pt{}How credit scores are evolving to improve access to credit}{https://apnews.com/article/680dba92330928cebf3ef572e62c5530}{File - Car shoppers consider a 2022 Cooper convertible on display in a Mini dealership in Highlands Ranch, Colo., on Friday, Feb. 18, 2022. A low credit score can hurt your ability to take out a loan, secure a good interest rate, or...}

\entryitemWithDescription{\hskip 0pt{}Russia's sports exile persists 1 year after invading Ukraine}{https://apnews.com/article/af3684913e1268cfaffa5bb08e38b731}{FILE - A Russian flag is held above the Olympic Rings at Adler Arena Skating Center during the Winter Olympics in Sochi, Russia on Feb. 18, 2014. Russia and its ally Belarus have been invited to compete at the Asian Games in the next step...}

\entryitemWithDescription{\hskip 0pt{}WWE leaning in to social media ahead of possible sale}{https://apnews.com/article/d7bacce55e68974266dbc4c3792afc3d}{File - Spectators watch fire works during the World Wrestling Entertainment "WWE" Crown Jewel matches at King Fahd International Stadium in Riyadh, Saudi Arabia, Thursday, Oct. 31, 2019. WWE, an organization that is already king of the...}

\entryitemWithDescription{\hskip 0pt{}Microsoft brings Bing chatbot to phones after curbing quirks}{https://apnews.com/article/522a2225391a968ee1d791e32d8b91eb}{FILE - The Microsoft Bing logo and the website\textquotesingle s page are shown in this photo taken in New York on Tuesday, Feb. 7, 2023. Microsoft is ready to take its new Bing chatbot mainstream --- less than a week after making major...}

\entryitemWithDescription{\hskip 0pt{}CNN's Don Lemon tweets another apology, returns to work}{https://apnews.com/article/52be979ee7c3b95dbcddedf23683e98c}{FILE - CNN anchors Kaitlan Collins, from left, Don Lemon and Poppy Harlow appear at the 16th annual CNN Heroes All-Star Tribute on Dec. 11, 2022, in New York. (Photo by Evan Agostini/Invision/AP, File) NEW YORK (AP) --- CNN anchor Don...}

\entryitemWithDescription{\hskip 0pt{}10 Palestinians killed, scores hurt in Israel West Bank raid}{https://apnews.com/article/b29ffacdfefb473aae06542b01e0fded}{Israeli troops entered a major Palestinian city in the occupied West Bank in a rare, daytime arrest operation, triggering fighting that killed at least 10 Palestinians and wounded scores of others. Smoke from fires fills the air as...}