\entryitemWithDescription{\hskip 0pt{}Netflix hypes `The Last Airbender,' `One Piece' at starry fan event}{https://apnews.com/article/5e53cd6f527fbd0db65ed45448a1bc62}{FILE - The Netflix logo is displayed on the company\textquotesingle s website, Feb. 2, 2023, in New York. Netflix gave audiences first looks at some planned and upcoming projects including ``Avatar: The Last Airbender,'' ``One Piece'' and...}

\entryitemWithDescription{\hskip 0pt{}Hovercraft suffers gash, beaches itself in New Hampshire}{https://apnews.com/article/c80f8ce0562a9f9bb9d266657698677a}{This photo provided by Hampton Police Chief Alex Reno shows a retired Canadian Coast Guard hovercraft that was deliberately run aground because of a tear in its skirt, on Hampton Beach, N.H., on Saturday, June 17, 2023. (Alex Reno/Hampton...}

\entryitemWithDescription{\hskip 0pt{}Bus driver arrested on DUI charge while driving Pirates from Chicago to Milwaukee}{https://apnews.com/article/04eb51a5cb7a05ff480915dc27137a3d}{MILWAUKEE (AP) --- A bus driver was arrested on a charge of driving under the influence while transporting the Pittsburgh Pirates from Chicago to Milwaukee for their weekend series with the Brewers. Illinois State Police said the driver...}

\entryitemWithDescription{\hskip 0pt{}Pope Francis, back to Vatican routine post-surgery, says thanks to shouts of 'Long live the pope!'}{https://apnews.com/article/32ba67cd9b8401572cb3587c0e50a60d}{Pope Francis delivers his blessing as he recites the Angelus noon prayer from the window of his studio overlooking St.Peter\textquotesingle s Square, at the Vatican, Sunday, June 18, 2023. (AP Photo/Andrew Medichini) VATICAN CITY (AP...}

\entryitemWithDescription{\hskip 0pt{}Parking lot party shooting leaves 1 dead and at least 22 people hurt in suburban Chicago}{https://apnews.com/article/a730bb6b0dbfbfd31b89f9784d469edc}{Investigators look over the scene of an overnight mass shooting at a strip mall in Willowbrook, Ill., Sunday, June 18, 2023. (AP Photo/Matt Marton) WILLOWBROOK, Ill. (AP) --- At least 23 people were shot, one fatally, early Sunday during...}

\entryitemWithDescription{\hskip 0pt{}Ugandan border town buries victims of rebel massacre that left 42 dead, mostly students}{https://apnews.com/article/fb944d3d288d505b43bcd57514201196}{The coffins of Florence Masika and her son Zakayo Masereka, who were both killed by suspected rebels as they retreated from Saturday\textquotesingle s attack on the Lhubiriha Secondary School, are carried to their burial in Nyabugando...}

\entryitemWithDescription{\hskip 0pt{}2 dead and 3 hurt -- including suspected shooter -- at Washington state music festival}{https://apnews.com/article/3026fae90bb769cc37930ec584b512e3}{GEORGE, Wash. (AP) --- Two people were killed and three others injured after police said a shooter began firing ``randomly" into a crowd at a Washington state campground that was hosting people attending a nearby music festival on...}

\entryitemWithDescription{\hskip 0pt{}Velociraptor statue heist ends with 3 arrests in South Dakota}{https://apnews.com/article/3ea3ece0092ab1f187bf66e920aff0e6}{SIOUX FALLS, S.D. (AP) --- Police have hunted down a velociraptor that was stolen from outside a South Dakota arts and science center. Sioux Falls police Sgt. Aaron Benson said Friday that a security officer spotted three people carrying...}

\entryitemWithDescription{\hskip 0pt{}A Utah city violated the First Amendment in denying a drag show permit, judge rules}{https://apnews.com/article/e3bac1d42a909f3028b1f86e8367568a}{FILE - Chris performs during the headlining drag show as part of the RaYnbow Collective\textquotesingle s Back to School Pride Night for BYU students at Kiwanis Park in Provo, Utah on Sept. 3, 2022. A federal judge has granted the request...}

\entryitemWithDescription{\hskip 0pt{}Pennsylvania trooper, suspect killed in shootout; 2nd trooper seriously wounded}{https://apnews.com/article/79255b93173ea44a6374a7b449743aee}{Authorities gather at the scene of a shootout between Pennsylvania State Troopers and a gunman near Mifflintown, Pa. The suspect\textquotesingle s pickup truck is seen in center, Saturday, June 17, 2023. (Sean Simmers/The Patriot-News via...}

\entryitemWithDescription{\hskip 0pt{}Mick Jagger, girlfriend have Florida house up for sale}{https://apnews.com/article/90ed7aa525081a1d63653f26ed091bb3}{FILE - Mick Jagger of The Rolling Stones performs onstage at the Groupama stadium, outside Lyon, central France, during a concert as part of their "Sixty" European tour, on July 19, 2022. Jagger and his dancer girlfriend Melanie Hamrick...}

\entryitemWithDescription{\hskip 0pt{}16 injured as Baltimore bus crashes into 2 cars, apartment building}{https://apnews.com/article/15c047e24ae93d63099c32378836becd}{First responders work the scene of a multi-vehicle crash in Baltimore on Saturday, June 17, 2023. Police say several people were injured when a mass transit bus crashed with two cars before hitting a building. (Kim Hairston/The Baltimore...}

\entryitemWithDescription{\hskip 0pt{}West Virginia basketball coach Bob Huggins resigns hours after drunken driving arrest}{https://apnews.com/article/fb441762888b47bade5efb1b4e247da0}{FILE - West Virginia head coach Bob Huggins watches from the bench during the first half of an NCAA college basketball game against Iowa State, Monday, Feb. 27, 2023, in Ames, Iowa. Huggins has been arrested on suspicion of drunken...}