\entryitemWithDescription{\hskip 0pt{}Taylor Swift and Travis Kelce attend the US Open men's final}{https://apnews.com/article/4f92f1af167f695f0a196bb61b7ddf52}{Taylor Swift is at the U.S. Open to watch another Taylor perform. Swift is at the men's final along with Travis Kelce on Sunday, four days after watching her boyfriend's Kansas City Chiefs open their NFL season with a victory. The singing...}

\entryitemWithDescription{\hskip 0pt{}AP Top 25: SEC grabs six of the first seven spots in rankings as Notre Dame tumbles to No. 18}{https://apnews.com/article/c6b37bc9a47827093f07e2c68c9d8b0c}{After the first shake-up of the college football season, the Southeastern Conference grabbed six of the top seven spots in the AP Top 25 --- a first in the 88-year history of the rankings --- and Notre Dame tumbled all the way to No. 18...}

\entryitemWithDescription{\hskip 0pt{}`Beetlejuice Beetlejuice' jolts box office with \$110 million opening weekend}{https://apnews.com/article/aa6796a00177befac22de6339d6c5a57}{After 36 years of waiting, the juice is finally loose again in ``Beetlejuice Beetlejuice,'' this time racking up a record-breaking \$110 million in its premiere weekend. The long-awaited Tim Burton sequel is the third-best opening weekend...}

\entryitemWithDescription{\hskip 0pt{}Dak Prescott and the Cowboys agree on a record contract that is the first at \$60 million per year}{https://apnews.com/article/318da54828e8bd96d7010f82c6dcfe22}{Dak Prescott has a new contract with the Dallas Cowboys hours before their season opener at Cleveland. The star quarterback and the Cowboys agreed on a \$240 million, four-year contract, the first in NFL history to average \$60 million...}

\entryitemWithDescription{\hskip 0pt{}Rap megastar Kendrick Lamar will headline the 2025 Super Bowl halftime show}{https://apnews.com/article/9631e4cb123a15567f29055c7de9e9d1}{LOS ANGELES (AP) --- Kendrick Lamar will pop out on the NFL's biggest stage next year: The Grammy winner will headline the Apple Music Super Bowl Halftime Show in New Orleans. The NFL, Apple Music and Roc Nation announced Sunday that...}

\entryitemWithDescription{\hskip 0pt{}Tyreek Hill is briefly detained for a traffic violation ahead of Dolphins' season opener}{https://apnews.com/article/b7818aea160bed284444594a689f453d}{MIAMI GARDENS, Fla. (AP) --- Miami Dolphins wide receiver Tyreek Hill was briefly detained for a traffic violation while entering Hard Rock Stadium on Sunday, hours before his team was set to open the season against the Jacksonville...}

\entryitemWithDescription{\hskip 0pt{}Morocco's El Idrissi smashes women's marathon world record on the last day of the Paralympic Games}{https://apnews.com/article/546d96ce9d5e03508510adfa2cdff0e5}{PARIS (AP) --- Morocco's Fatima Ezzahra El Idrissi has smashed the world record in the women's marathon for runners with visual impairments on the last day of the Paralympic Games. The 29-year-old El Idrissi finished in 2 hours, 48...}

\entryitemWithDescription{\hskip 0pt{}Cars talking to one another could help reduce fatal crashes on US roads}{https://apnews.com/article/4609b3f43768f6726bbb4e5442f40f21}{The secret to avoiding red lights during rush hour in Utah's largest city might be as simple as following a bus. Transportation officials have spent the past few years refining a system in which radio transmitters inside commuter buses...}

\entryitemWithDescription{\hskip 0pt{}Huge payout expected for a rare coin bought by Ohio farm family and hidden for decades}{https://apnews.com/article/574e1a50e1f80b310941ef373d3ca22d}{TOLEDO, Ohio (AP) --- Three sisters from Ohio who inherited a dime kept in a bank vault for more than 40 years knew it had some value. But they had no idea just how much until just a few years ago. The extraordinarily rare coin, struck by...}

\entryitemWithDescription{\hskip 0pt{}Mega Millions jackpot soars to an estimated \$800 million}{https://apnews.com/article/0e0ed863072cb7b837f75d4aa8c17b5c}{BOSTON (AP) --- The Mega Millions jackpot has risen to an estimated \$800 million with a cash option of \$401.8 million for Tuesday's drawing after no one matched all the winning numbers for Friday night's drawing. The jackpot was last...}

\entryitemWithDescription{\hskip 0pt{}Wisconsin health officials recall eggs after a multistate salmonella outbreak}{https://apnews.com/article/3844d37fd76ef04b84632075c48d45b0}{Wisconsin health officials initiated a recall of eggs following an outbreak of salmonella infections among 65 people in nine states that originated on a Wisconsin farm. The Wisconsin Department of Health Services said in a statement...}

\entryitemWithDescription{\hskip 0pt{}`The Bear' and `Shogun' could start claiming trophies early at Creative Arts Emmy Awards}{https://apnews.com/article/ad938745970aeed96b8d5e6ffef3eb16}{LOS ANGELES (AP) --- Top Emmy nominees ``Shogun'' and ``The Bear'' can start running up the score early at the two-night Creative Arts Emmy Awards, which honor artistic and technical achievement in television. The Saturday and Sunday...}

\entryitemWithDescription{\hskip 0pt{}A rare 1787 copy of the US Constitution is up for auction and it could be worth millions}{https://apnews.com/article/fcbb7605fe8990ad4a7c328b5488b3f1}{ASHEVILLE, N.C. (AP) --- Historical document appraiser and collector Seth Kaller spreads a broad sheet of paper across a desk. It's in good enough condition that he can handle it, carefully, with clean, bare hands. There are just a few...}