\entryitemWithDescription{\hskip 0pt{}Why Leonardo DiCaprio testified at trial of Fugees rapper}{https://apnews.com/article/b5ebfa4e3ab07ad4f15b94bed19ca656}{Prakazrel "Pras" Michel, a member of the 1990s hip-hop group the Fugees, accompanied by defense lawyer David Kenner, center left, arrives at federal court for his trial in an alleged campaign finance conspiracy, Monday, April 3, 2023, in...}

\entryitemWithDescription{\hskip 0pt{}Jill Biden wants champions LSU — and Iowa — at White House}{https://apnews.com/article/3095687ef97b6a323bd13e99ae063237}{First lady Jill Biden, front, makes a point as Colorado Speaker of the House Julie McCluskie looks on during a stop to attend a roundtable discussion on the federal workforce training program to help community college students earn...}

\entryitemWithDescription{\hskip 0pt{}What's happening with Twitter blue check marks?}{https://apnews.com/article/5b3d64e23ae21572ada42a0110e27c5e}{FILE - The Twitter application is seen on a digital device, April 25, 2022, in San Diego. Twitter has removed the verification check mark on the main account of The New York Times, one of CEO Elon Musk's most despised news organizations...}

\entryitemWithDescription{\hskip 0pt{}Ricochet, San Diego's surfing therapy dog, dies at 15}{https://apnews.com/article/8b84d4baa38127387a9dba7b9a5ed670}{FILE - Patrick Ivison, 15, and Ricochet, a golden retriever surfing partner, cruising toward shore during a surfing session at the Cardiff State Beach in San Diego. Ricochet, the beloved Golden Retriever who found her calling as a therapy...}

\entryitemWithDescription{\hskip 0pt{}A duo once more, Ben Affleck, Matt Damon come up for 'Air'}{https://apnews.com/article/29d9bfdde9a3f2421b74360e204e5883}{Ben Affleck, left, and Matt Damon pose for a portrait to promote the film "Air" on Monday, March 27, 2023, at the Four Seasons Hotel in Los Angeles. (AP Photo/Ashley Landis) NEW YORK (AP) --- While Ben Affleck and Matt Damon were...}

\entryitemWithDescription{\hskip 0pt{}Disney developing live-action 'Moana' with Dwayne Johnson}{https://apnews.com/article/cafe16834e9f63d9d80eb423e182cc11}{FILE - Actors Dwayne Johnson, left, and Auli\textquotesingle i Cravalho appear at the 2016 AFI Fest - "Moana" world premiere in Los Angeles on Nov. 14, 2016. Disney chief executive Bob Iger on Monday announced that a live-action ``Moana''...}

\entryitemWithDescription{\hskip 0pt{}More severe weather forecast for battered South, Midwest}{https://apnews.com/article/87a0babf97c6f399701551dcd5039564}{A man drags tree limbs to a pile at the Foxcroft Woods Condominiums, Sunday, April 2, 2023, in Little Rock, Ark. Residents across a wide swath of the U.S. raced to assess the destruction from fierce storms that spawned possibly dozens of...}

\entryitemWithDescription{\hskip 0pt{}Veto stands: Transgender pronouns OK in North Dakota schools}{https://apnews.com/article/c471f794bd0aa09befd2c43654d7fe97}{FILE - North Dakota Gov. Doug Burgum speaks at the state Capitol on April 10, 2020, in Bismarck, N.D. Teachers in North Dakota can still refer to transgender students by the personal pronouns they use, after lawmakers on Monday, April 3...}

\entryitemWithDescription{\hskip 0pt{}Nashville police: School shooter planned attack for months}{https://apnews.com/article/5233141e86bd91f1289a1989c3e54bfd}{Students march from Hume Fogg High School to the State Capitol for the March For Our Lives protest against gun violence in Nashville, Tenn., on Monday, April 3, 2023. (AP Photo/George Walker IV) NASHVILLE, Tenn. (AP) --- As students...}

\entryitemWithDescription{\hskip 0pt{}Autopsy finds cause of death for Irvo Otieno was asphyxia}{https://apnews.com/article/d7175e541e76b24cc5ff1eff759c4706}{The casket of Irvo Otieno is carried out of First Baptist Church of South Richmond after the celebration of life for Irvo Otieno in North Chesterfield, Va., on Wednesday, March 29, 2023. Irvo Otieno, a 28-year-old Black man, died after he...}

\entryitemWithDescription{\hskip 0pt{}DiCaprio testifies in money-laundering case of Fugees rapper}{https://apnews.com/article/59dc3ffb5ab1f5b2bea957482e9afdd7}{Prakazrel "Pras" Michel, a member of the 1990s hip-hop group the Fugees arrives at federal court for his trial in an alleged campaign finance conspiracy, Monday, April 3, 2023, in Washington. (AP Photo/Andrew Harnik) WASHINGTON (AP...}

\entryitemWithDescription{\hskip 0pt{}DeSantis signs bill to carry concealed guns without a permit}{https://apnews.com/article/ac7adbc200cc4c1bb429ea84357f73be}{Florida Gov. Ron DeSantis speaks to a crowd at Adventure Outdoors gun store, Thursday, March 30, 2023, in Smyrna, Ga. AP Photo/John Bazemore) TALLAHASSEE, Fla. (AP) --- Floridians will be able to carry concealed guns without a permit...}

\entryitemWithDescription{\hskip 0pt{}Distraction, speeding, alcohol drive up 2021 traffic deaths}{https://apnews.com/article/fb7ec8a9ddbb862c9b29f6ac87d508f9}{FILE - Emergency workers work the scene of a fatal accident on Aug. 24, 2021 in Tulsa, Okla. Nearly 43,000 people died in U.S. traffic crashes in 2021, with deaths due to speeding and impaired or distracted driving on the rise. The 2021...}