\entryitemWithDescription{\hskip 0pt{}Ex-Alabama player Miles indicted on capital murder charges}{https://apnews.com/article/887b6419c4b576da778b710a58b8acf7}{FILE - Alabama forward Darius Miles looks to pass in the second half an NCAA college basketball game against LSU in Baton Rouge, La., March 5, 2022. Former Alabama basketball player Darius Miles has been indicted by a grand jury on...}

\entryitemWithDescription{\hskip 0pt{}New this week: 'Ted Lasso,' U2 and 'The Boston Strangler'}{https://apnews.com/article/211eb0a5b4f8606f313c523c790f49d1}{This combination of images shows promotional art for "Ted Lasso," the Apple TV+ series premiering its season three on March 15, left, "Boston Strangler," a film premiering March 17 on Hulu, center, and "Agent Elvis," an animated series...}

\entryitemWithDescription{\hskip 0pt{}Why would Russia use hypersonic missile to strike Ukraine?}{https://apnews.com/article/e0dc1e20e9dd53528c5381ca5fdee66a}{FILE - Russian Tu-22M-3 long-range bombers fly during the Victory Day military parade marking 71 years after the victory in WWII in Red Square in Moscow, Russia, Monday, May 9, 2016. The latest Russian missile barrage against Ukraine's...}

\entryitemWithDescription{\hskip 0pt{}NOT REAL NEWS: A look at what didn't happen this week}{https://apnews.com/article/3c99392cf9be04e2338b1279d7c03f8d}{FILE - FILE - In this Jan. 6, 2021 file photo, supporters of President Donald Trump, including Jacob Chansley, right with fur hat, are confronted by U.S. Capitol Police officers outside the Senate Chamber inside the Capitol in Washington...}

\entryitemWithDescription{\hskip 0pt{}9th grader sues over Pledge of Allegiance confrontation}{https://apnews.com/article/77c0adcde3759b14d9b038c4ba20041a}{Marissa Barnwell, a River Bluff High School student, her parents and their lawyer, Tyler Bailey, hold a news conference in Columbia, S.C., on Thursday, March 9, 2023, regarding a lawsuit filed against Lexington School District One...}

\entryitemWithDescription{\hskip 0pt{}Standard time giving way to daylight saving in most of US}{https://apnews.com/article/24cd5e37b6cf9768edeee11f64587d37}{FILE - Dan LaMoore adjusts the hands on a Seth Thomas Post Clock at Electric Time Company, Oct. 23, 2020, in Medfield, Mass. Standard time comes to an end in most parts of the United States this weekend. You'll lose an hour of sleep for...}

\entryitemWithDescription{\hskip 0pt{}Atmospheric rivers flood California with more rain, snow}{https://apnews.com/article/a6ee9e41a31ba31a959c5aceb4d89111}{Crews assess storm damage, which washed out North Main Street in Soquel, Calif., Friday, March 10, 2023. (AP Photo/Nic Coury) SANTA CRUZ, Calif. (AP) --- More than 9,000 California residents were under evacuation orders Friday as a new...}

\entryitemWithDescription{\hskip 0pt{}Here's how the 4 Americans abducted in Mexico were found}{https://apnews.com/article/a3e563073079b5634a9146ae358694e4}{Today would have been Shaeed Woodard's 34th birthday, according to his father, James Woodard. (March 9) A Mexican police investigator inspects the minivan where four Americans where shot and taken from the previous week, at the Tamaulipas...}

\entryitemWithDescription{\hskip 0pt{}Florida abortion ban could have impact beyond the state}{https://apnews.com/article/b5ccc8e49d00ff3b17b44a2bd533d35b}{FILE - Florida Gov. Ron DeSantis answers questions from the media in the Florida Cabinet following his State of the State address during a joint session of the Senate and House of Representatives Tuesday, March 7, 2023, at the Capitol in...}

\entryitemWithDescription{\hskip 0pt{}House votes to declassify info about origins of COVID-19}{https://apnews.com/article/7018f8016c7346cfaa8193933ec10063}{FILE - This 2020 electron microscope image made available by the Centers for Disease Control and Prevention shows SARS-CoV-2 virus particles, which cause COVID-19. The House voted unanimously Friday, March 10, 2023, to declassify U.S...}

\entryitemWithDescription{\hskip 0pt{}Pandemic 3 years later: Has the COVID-19 virus won?}{https://apnews.com/article/59f39df14ddf65f786d3437cc9a52e54}{FILE - A person is taken on a stretcher into the United Memorial Medical Center after going through testing for COVID-19 Thursday, March 19, 2020, in Houston. On the third anniversary of the COVID-19 pandemic in 2023, the virus is still...}

\entryitemWithDescription{\hskip 0pt{}The view from above the Oscars: The slap, the snafu, Spike}{https://apnews.com/article/b7c595f40577da28a00dc352ced7164e}{FILE - "La La Land" producer Jordan Horowitz, left, presenter Warren Beatty, center, and host Jimmy Kimmel right, look at an envelope announcing "Moonlight" as best picture at the Oscars on Sunday, Feb. 26, 2017, in Los Angeles. It was...}

\entryitemWithDescription{\hskip 0pt{}In a first since 1961, the Oscars carpet will not be red}{https://apnews.com/article/fd4e6f4694056289aed979d1639fda78}{A crew member staples the white carpet to the ground in preparation for Sunday\textquotesingle s 95th Academy Awards, Wednesday, March 8, 2023, outside the Dolby Theatre in Los Angeles. (AP Photo/Chris Pizzello) Oscars host Jimmy Kimmel...}