\entryitemWithDescription{\hskip 0pt{}Rapper Lil Baby arrested in Las Vegas on suspicion of concealed weapon violation}{https://apnews.com/article/f694d747285e63c9ee1777af751fef37}{LAS VEGAS (AP) --- Rapper Lil Baby was arrested in Las Vegas after police accused him of carrying a concealed weapon without a permit. The Atlanta-born rapper, whose real name is Dominique Jones, was taken into custody on the Las Vegas...}

\entryitemWithDescription{\hskip 0pt{}Utah mother and children's book author Kouri Richins to stand trial in husband's death, judge rules}{https://apnews.com/article/390e6edca3be2906ae42894d79fdd406}{PARK CITY, Utah (AP) --- A Utah mother of three who published a children's book about grief after her husband's death and was later accused of fatally poisoning him will stand trial, a judge ruled Tuesday. Utah state Judge Richard Mrazik...}

\entryitemWithDescription{\hskip 0pt{}Ancient tombs with vibrant wall paintings open to public in southern Israel}{https://apnews.com/article/08598fe9d09d4a42859801be87913735}{ASHKELON, Israel (AP) --- Two nearly 2,000-year-old tombs with magnificent wall paintings will be open to the public for the first time in southern Israel after a painstaking conservation process, the Israel Antiquities Authority...}

\entryitemWithDescription{\hskip 0pt{}Karen Read now faces civil suit as well as murder charge in police officer boyfriend's death}{https://apnews.com/article/dc3a0a413df318a35903cb235ce4dabe}{PLYMOUTH, Mass. (AP) --- The family of the police officer boyfriend Karen Read is accused of killing by hitting him with her vehicle and leaving him to die in the snow has filed a wrongful death lawsuit against her and two bars where they...}

\entryitemWithDescription{\hskip 0pt{}Two workers killed and a third injured in an explosion at a Delta Air Lines facility in Atlanta}{https://apnews.com/article/978d4a77652375968b7000c8dee0ca7f}{ATLANTA (AP) --- Two workers were killed and another seriously injured in an explosion Tuesday at a Delta Air Lines maintenance facility near the Atlanta airport. Delta said it was working with local authorities to investigate what...}

\entryitemWithDescription{\hskip 0pt{}An injured and angry water buffalo is on the loose in Iowa}{https://apnews.com/article/18575ea9a9c78618a43f38e6eabf4099}{PLEASANT HILL, Iowa (AP) --- A water buffalo is on the loose in an Iowa town, and police are warning people that it is injured and aggressive. Police in the Des Moines suburb of Pleasant Hill responded Saturday to a call about an animal...}

\entryitemWithDescription{\hskip 0pt{}Does American tennis have a pickleball problem? Upstart's boom looms out of view at the US Open}{https://apnews.com/article/6a95ff52e3646f2dc4d5ddcca9168d94}{NEW YORK (AP) --- Does American tennis have a pickleball problem? Even as the U.S. Open opened this week with more than a million fans expected for the sport's biggest showcase, the game's leaders are being forced to confront a...}

\entryitemWithDescription{\hskip 0pt{}Mariah Carey's mother and sister died on the same day. The singer says her `heart is broken'}{https://apnews.com/article/cd6688c818f0f23064b2015577be5e2b}{LOS ANGELES (AP) --- Mariah Carey's mother Patricia and sister Alison both died on the same day, the singer said Monday. ``My heart is broken that I've lost my mother this past weekend. Sadly, in a tragic turn of events, my sister lost...}

\entryitemWithDescription{\hskip 0pt{}Diddy seeks to have producer's lawsuit tossed, says it's full of `blatant falsehoods'}{https://apnews.com/article/7ea05a3df7b1e70bc91174f6b3ecae42}{Sean ``Diddy'' Combs asked a federal judge Monday to throw out a lawsuit from a music producer who accused the music mogul of a broad pattern of sexual abuse and other misconduct. The lawsuit filed in February by Rodney ``Lil Rod''...}

\entryitemWithDescription{\hskip 0pt{}Apparent cyberattack leaves Seattle airport facing major internet outages}{https://apnews.com/article/627805ee04648592658150dfdfa18ca9}{SEATTLE (AP) --- An apparent cyberattack disrupted internet, phones, email and other systems at Seattle-Tacoma International Airport for a third day on Monday as Port of Seattle officials worked to investigate the outages and restore full...}

\entryitemWithDescription{\hskip 0pt{}Traveling over Labor Day weekend? Have a back-up plan for cancellations and delays, and be patient}{https://apnews.com/article/81c40a034787764631c4bb640861f7c3}{Many children have gone back to school in the U.S., and the days are getting shorter, but there is still one more excuse to use the swimsuits and beach towels before packing them up: Labor Day. Airports, highways, beaches and theme parks...}

\entryitemWithDescription{\hskip 0pt{}Ice cave collapse in Iceland kills 1 tourist, and 2 are still missing}{https://apnews.com/article/8d6a45480717589a4699f75f976e3df3}{BERLIN (AP) --- At least one person has died and two others are still missing after an ice cave partially collapsed as a group of tourists was visiting the Breidamerkurjokull glacier in southern Iceland. In a statement posted on social...}

\entryitemWithDescription{\hskip 0pt{}Venice Film Festival: From `Joker 2' to `Queer,' here are 10 movies to get excited about}{https://apnews.com/article/309c97d0d2a8cd103a8f79f3c5d36792}{VENICE, Italy (AP) --- Some of Hollywood's biggest stars are getting ready to descend on the Venice Film Festival this week, from George Clooney and Angelina Jolie to Lady Gaga and Brad Pitt. But while the allure of A-listers on those...}