\entryitemWithDescription{\hskip 0pt{}Women in Turkey brave ban on Istanbul march, get tear-gassed}{https://apnews.com/article/495c5b6e3080a95a2a30c46d1af5be05}{A protester argues with anti riot policemen at the end of the gathering to mark the International Women\textquotesingle s Day in Istanbul, Turkey, Wednesday, March 8, 2023. Women in Turkey and their allies converged on a central Istanbul...}

\entryitemWithDescription{\hskip 0pt{}Deadly Mexico kidnapping hits home in South Carolina}{https://apnews.com/article/f77a0d1d0cc60a1efa7adb37a73428a2}{A mural adorns a facade, Tuesday, March 7, 2023, in Lake City, S.C. The four Americans violently kidnapped last week in Mexico had ties to the small town in South Carolina. (AP Photo/James Pollard) LAKE CITY, S.C. (AP) --- Americans who...}

\entryitemWithDescription{\hskip 0pt{}A global mystery: What's known about Nord Stream explosions}{https://apnews.com/article/2561f98ba6462db700f7609352a28c24}{FILE - Pipes at the landfall facilities of the \textquotesingle Nord Stream 2\textquotesingle{} gas pipline are pictured in Lubmin, northern Germany, on Feb. 15, 2022. Russia clashed with the United States and other Western nations...}

\entryitemWithDescription{\hskip 0pt{}Veterans testify of 'catastrophic' impact of Afghan collapse}{https://apnews.com/article/2253b662b0e8636b105bbc599448c918}{Former Marine Sgt. Tyler Vargas-Andrews, who was gravely injured, losing an arm and a leg in a suicide attack at Hamid Karzai International Airport in Kabul, becomes emotional as he recounts his story during a House Committee on Foreign...}

\entryitemWithDescription{\hskip 0pt{}Americans found quickly, but Mexico's missing remain lost}{https://apnews.com/article/69153a59bbda81912714c54c974c3c01}{Mexican army soldiers prepare a search mission for four U.S. citizens kidnapped by gunmen in Matamoros, Mexico, Monday, March 6, 2023. Mexican President Andres Manuel Lopez Obrador said the four Americans were going to buy medicine and...}

\entryitemWithDescription{\hskip 0pt{}Tucker Carlson's scorn for Trump revealed in court papers}{https://apnews.com/article/96c305cf4046aaf373130876940fd06e}{Tucker Carlson, left, and former President Donald Trump, talk while watching golfers on the 16th tee during the final round of the LIV Golf Invitational at Trump National in Bedminster, N.J., July 31, 2022. A defamation lawsuit against...}

\entryitemWithDescription{\hskip 0pt{}DeSantis' new Disney World board hints at future controversy}{https://apnews.com/article/29d4ef59dc69538a545278fc427a365c}{FILE - People visit the Magic Kingdom Park at Walt Disney World Resort in Lake Buena Vista, Fla., April 18, 2022. The first meeting of the new board of Walt Disney World's government --- overhauled by sweeping legislation signed by...}

\entryitemWithDescription{\hskip 0pt{}3D-printed rocket's debut launch aborted at last minute}{https://apnews.com/article/03ebc69c0b1c041e1ab27ee478d06f3f}{A rocket made by the world\textquotesingle s largest metal 3D printer is set to lift off from Florida this week. Manufacturer Relativity Space hopes to pave the way for a new era of space exploration. (March 7) This image from video made...}

\entryitemWithDescription{\hskip 0pt{}What to know about prescription drugs promising weight loss}{https://apnews.com/article/92fa95115429c163eb7fa527ca6d94ce}{This image shows the logo of WeightWatchers on a mobile phone, and the company\textquotesingle s website, in New York, Tuesday, March 7, 2023. WeightWatchers shares soared Tuesday after the company said it was getting into the...}

\entryitemWithDescription{\hskip 0pt{}Harry \& Meghan's daughter christened, will use royal title}{https://apnews.com/article/1c66a39ae38521c05cb7e1f7c613b6dc}{FILE - Prince Harry and Meghan Markle, Duke and Duchess of Sussex leave after a service of thanksgiving for the reign of Queen Elizabeth II at St Paul\textquotesingle s Cathedral in London, Friday, June 3, 2022 on the second of four days...}

\entryitemWithDescription{\hskip 0pt{}Biden budget aims to cut deficits nearly \$3T over 10 years}{https://apnews.com/article/810ff80dcd8812f2138eef571f2444f3}{FILE - President Joe Biden delivers the State of the Union address to a joint session of Congress at the U.S. Capitol, Feb. 7, 2023, in Washington, as Vice President Kamala Harris and House Speaker Kevin McCarthy of Calif., listen. Biden...}

\entryitemWithDescription{\hskip 0pt{}After Taylor shooting, feds find police discrimination}{https://apnews.com/article/07017f9d2721e1b6f99494ea6b03f1f4}{FILE - A ground mural depicting a portrait of Breonna Taylor is seen at Chambers Park in Annapolis, Md., July 6, 2020. The U.S. Justice Department has found Louisville police have engaged in a pattern of violating constitutional rights...}

\entryitemWithDescription{\hskip 0pt{}Bruce Lee, Anna May Wong heirs talk legacy, roles for Asians}{https://apnews.com/article/b3a06c4e9181e3a85667d8093f1fb12d}{Anna Wong, niece of the late actress Anna May Wong, left, poses with Shannon Lee, daughter of the late martial arts actor Bruce Lee, at Douglas Park in Santa Monica, Calif., on Tuesday, March 7, 2023. They both discovered parallel...}