\entryitemWithDescription{\hskip 0pt{}Super Bowl 2023: Chiefs vs. Eagles live updates}{https://apnews.com/article/a1647c9d0c26198598708189bcc2ee6d}{Fans dance before the NFL Super Bowl 57 football game between the Kansas City Chiefs and the Philadelphia Eagles, Sunday, Feb. 12, 2023, in Glendale, Ariz. (AP Photo/Seth Wenig) Rihanna is putting in the work ahead of her Super Bowl...}

\entryitemWithDescription{\hskip 0pt{}Cardi B brings energy at pre-Super Bowl concert, joins crowd}{https://apnews.com/article/ba4a98c8c39f2fa0eda8ffbd8b82f532}{FILE - Musician Cardi B performs at the Chase Sapphire Lounge presented by SiriusXM during Art Week, Dec. 2, 2022, at the SLS South Beach in Miami Beach, Fla. Cardi B teamed with her husband Offset onstage, embraced Serena Williams and...}

\entryitemWithDescription{\hskip 0pt{}In Mexico, US complaints help union organizing efforts}{https://apnews.com/article/865577c8f3115f9e0bb243b79105e80b}{People work in a shoe maquiladora or factory in Leon, Mexico, Monday, Feb. 7, 2023. t has been nearly two years since the United States began pressing Mexico over labor rights violations, by using rapid dispute resolution methods (RRM...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl week was back to its normal wildness this year}{https://apnews.com/article/da9fec89d4bd5c630a9398b46d9edbf4}{The Pro football Hall of Fame class of 2023 poses during the NFL Honors award show ahead of the Super Bowl 57 football game,Thursday, Feb. 9, 2023, in Phoenix. (AP Photo/David J. Phillip) PHOENIX (AP) --- From Super Bowl opening night to...}

\entryitemWithDescription{\hskip 0pt{}'Unidentified object' downed over Lake Huron, 3rd this week}{https://apnews.com/article/acc1a333326c50ee9649760c569c300f}{FILE - The Pentagon is seen from Air Force One as it flies over Washington, March 2, 2022. U.S. officials say an ``unidentified object'' has been shot down Sunday for the third time in as many days, this time over Lake Huron, after...}

\entryitemWithDescription{\hskip 0pt{}GOP election tactics no surprise to Wisconsin's Black voters}{https://apnews.com/article/d0e0c0e90c307ed6a5074ad2771b1835}{A voter takes a sticker after casting an early ballot at a polling station Thursday, Feb. 9, 2023, in Milwaukee. Recent revelations about Republican election strategies targeting minority communities in Wisconsin's biggest city came as no...}

\entryitemWithDescription{\hskip 0pt{}Army sees safety, not 'wokeness,' as top recruiting obstacle}{https://apnews.com/article/6548adcb0fee590f3427771d1e1eeea7}{FILE - Military recruits are sworn in during halftime on Salute to Service military appreciation day at an NFL football game between the Jacksonville Jaguars and the Las Vegas Raiders, Nov. 6, 2022, in Jacksonville, Fla. The Army is...}

\entryitemWithDescription{\hskip 0pt{}Pope worried about Nicaraguan bishop sentenced to 26 years}{https://apnews.com/article/31939878a63a01f4259694f8265c5b69}{A Catholic woman attends Sunday\textquotesingle s mass at the Metropolitan Cathedral in Managua, Nicaragua, Sunday, Feb. 12, 2023. Pope Francis expressed sadness and worry at the news that Bishop Roland Alvarez, an outspoken critic of the...}

\entryitemWithDescription{\hskip 0pt{}Grief gives way to anger over Turkey's earthquake response}{https://apnews.com/article/0f7d4fb77ea45c94b7b5ecd637a930c7}{65 year-old Atari Kales mourns for her daughter in law and two grandchildren near the collapsed building that they were trapped in Antakya Saturday, Feb. 11, 2023. Rescue crews on Saturday pulled more survivors, including entire families...}

\entryitemWithDescription{\hskip 0pt{}IOC's Bach says Olympics on history's side in Russia issue}{https://apnews.com/article/393997c287f33cdf6bfd20cbce783839}{IOC (International Olympic Committee) president Thomas Bach walks in the finish area of the alpine ski, men\textquotesingle s World Championship downhill, in Courchevel, France, Sunday, Feb. 12, 2023. (AP Photo/Marco Trovati) COURCHEVEL...}

\entryitemWithDescription{\hskip 0pt{}Russia continues to shell Ukraine amid grinding push in east}{https://apnews.com/article/55af96dff4a79257502b8843b5f8a903}{Soldiers of the Ukrainian 3rd Army Assault Brigade of the Special Operations Forces (SSO) "Azov" rest in a blindage after night fight near Bakhmut, Donetsk region, Ukraine, Saturday, Feb. 11, 2023. (AP Photo/Libkos) KYIV, Ukraine (AP...}

\entryitemWithDescription{\hskip 0pt{}Turkey probes contractors as earthquake deaths pass 33,000}{https://apnews.com/article/658d897fe02316c474a8cc8078b690a3}{An excavator driver waits for a rescue team to recover the body of an earthquake victim from a collapsed building in Antakya, southeastern Turkey, Sunday, February 12, 2023. Six days after earthquakes killed tens of thousands in Syria and...}

\entryitemWithDescription{\hskip 0pt{}Neutral Austria under pressure to get tougher on Russia}{https://apnews.com/article/cd43bd689dfbd8c674c1b6d9d214d86f}{FILE - Flags wave in the wind in front of the entrance of the Permanent Council of the Organization for Security and Cooperation in Europe, OSCE, in Vienna, Austria, Feb. 15, 2022. Neutral Austria has come under heavy criticism for...}