\entryitemWithDescription{\hskip 0pt{}Jonathan Majors begged accuser to avoid hospital, warning of possible `investigation,' messages show}{https://apnews.com/article/87fb75a5ca50c7d7de4ce99cff3abe15}{NEW YORK (AP) --- The actor Jonathan Majors begged his former girlfriend not to seek medical attention after an incident that left her with a head injury last year, warning she had ``no perspective of what could happen'' if the truth got...}

\entryitemWithDescription{\hskip 0pt{}French actor Gerard Depardieu is under scrutiny over sexual remarks and gestures in new documentary}{https://apnews.com/article/731ae81b16fb66cde83055f6868f7eee}{PARIS (AP) --- French actor Gerard Depardieu's behavior toward women came under renewed scrutiny in France after a documentary showed him repeatedly making obscene remarks and gestures during a 2018 trip to North Korea. The footage...}

\entryitemWithDescription{\hskip 0pt{}Spotify's CFO is one of thousands to leave the company — after he moves to sell \$9 million in shares}{https://apnews.com/article/e3cd38dc2952df4b2a7fff9cbafe4950}{NEW YORK (AP) --- Spotify's chief financial officer will step down next year, according to the music streaming service, just days after it announced its third round of layoffs for 2023. In a statement announcing CFO Paul Vogel's...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift's Eras Tour is the first tour to gross over \$1 billion, Pollstar says}{https://apnews.com/article/52945111233438b1f2166aa19eee365f}{LOS ANGELES (AP) --- Taylor Swift's Eras Tour is the first tour to cross the billion-dollar mark, according to Pollstar's 2023 year-end charts. Not only was Swift's landmark Eras Tour the No. 1 tour both worldwide and in North America...}

\entryitemWithDescription{\hskip 0pt{}Thousands of tons of dead sardines wash ashore in northern Japan}{https://apnews.com/article/88003e085359a88cb1135a818c722c05}{TOKYO (AP) --- Thousands of tons of dead sardines have washed up on a beach in northern Japan for unknown reasons, officials said Friday. The sardines and some mackerel washed ashore in Hakodate on Japan's northernmost main island of...}

\entryitemWithDescription{\hskip 0pt{}Woman charged with attempted arson of Martin Luther King Jr. birthplace in Atlanta}{https://apnews.com/article/a642a0d24866e272d3f7418873ef2702}{ATLANTA (AP) --- Atlanta police have arrested a woman who's accused of trying to burn down the birthplace of the Rev. Martin Luther King Jr. in Atlanta. Officers arrested the 26-year-old woman around 5:45 p.m. Thursday after responding to...}

\entryitemWithDescription{\hskip 0pt{}Johnny Depp among stars paying tribute at funeral of The Pogues singer Shane MacGowan}{https://apnews.com/article/c9db39a8b26073d6f149f5c969d93615}{LONDON (AP) --- Thousands of people lined the streets of Dublin on Friday to say goodbye to The Pogues frontman Shane MacGowan as his coffin wound through the Irish capital before a small-town funeral attended by family, neighbors and...}

\entryitemWithDescription{\hskip 0pt{}Nintendo cancels its Live 2024 Tokyo event after persistent threats to workers and customers}{https://apnews.com/article/e2782eb5ac3f0e1315f1df0d03a97610}{TOKYO (AP) --- Nintendo canceled its upcoming video game showcase and postponed several other events because of persistent threats to the company, its workers and players. ``We decided we could not amply ensure the safety of our...}

\entryitemWithDescription{\hskip 0pt{}An asteroid will pass in front of bright star Betelgeuse to produce a rare eclipse visible to millions}{https://apnews.com/article/b9e3796c1ca915afdb84ed41509da9c8}{CAPE CANAVERAL, Fla. (AP) --- One of the biggest and brightest stars in the night sky will momentarily vanish as an asteroid passes in front of it to produce a one-of-a-kind eclipse. The rare and fleeting spectacle, late Monday into early...}

\entryitemWithDescription{\hskip 0pt{}Menu signed by Mao Zedong brings a quarter million dollars at auction}{https://apnews.com/article/a4634fce2bc71b3f9fc57a62834f4743}{BOSTON (AP) --- An official menu for a state banquet that bears the signature of former Chinese leader Mao Zedong has been auctioned for \$275,000. Boston-based RR Auction said the menu auctioned Wednesday was for a banquet held in...}

\entryitemWithDescription{\hskip 0pt{}Jonathan Majors' accuser breaks down on witness stand as footage shows actor shoving her}{https://apnews.com/article/4dac8b21f64b38b92d3b1ea5feb853b0}{NEW YORK (AP) --- The woman who accused Jonathan Majors of assaulting her in the backseat of a car broke down multiple times on the witness stand Thursday as the actor's attorney repeatedly played a surveillance video that showed Majors...}

\entryitemWithDescription{\hskip 0pt{}Rapper Kodak Black is arrested on cocaine charges in South Florida}{https://apnews.com/article/b2524d8a24479d6c7bc88a3ff22143ad}{FORT LAUDERDALE, Fla. (AP) --- Rapper Kodak Black has been arrested again in South Florida, this time on charges of possessing cocaine, jail records show. The Broward County jail listed Bill Kapri, Kodak Black's legal name, as being in...}

\entryitemWithDescription{\hskip 0pt{}Deputy U.S. Marshal charged with entering plane drunk after misconduct report on flight to London}{https://apnews.com/article/c85007f93d677eade7df5408d78186e4}{WASHINGTON (AP) --- A deputy U.S. Marshal was charged in the United Kingdom on Thursday with entering an aircraft while drunk, after being arrested on allegations of misconduct aboard a flight from New York, London police said. Michael...}