\entryitemWithDescription{\hskip 0pt{}Police responding to reported shooting at Dallas-area mall}{https://apnews.com/article/a5148bc28d78c69ba0c59967427a2f85}{ALLEN, Texas (AP) --- Law enforcement responded Saturday to reports of a shooting at an outlet mall in the Dallas area. The police department for Allen, Texas, said via Twitter about 4 p.m. that it was at the Allen Premium Outlets. Allen...}

\entryitemWithDescription{\hskip 0pt{}Eloy Jiménez of White Sox hospitalized with abdominal pain}{https://apnews.com/article/6fb5e41d22b90eaf62e68d5a5663cc9c}{Chicago White Sox\textquotesingle s Eloy Jimenez hits a single during the first inning of a baseball game against the Minnesota Twins in Chicago, Thursday, May 4, 2023. (AP Photo/Nam Y. Huh) CINCINNATI (AP) --- White Sox designated hitter...}

\entryitemWithDescription{\hskip 0pt{}Navy commissions USS Cooperstown; honors war veteran players}{https://apnews.com/article/ad63b48c0ab0ad9b269149715a291b84}{This photo provided by the U.S. Navy shows the Freedom-variant littoral combat ship USS Cooperstown (LCS 23) prior to the ship's commissioning ceremony, Saturday, May 6, 2023, in New York. On Saturday, the U.S. Navy commissioned the USS...}

\entryitemWithDescription{\hskip 0pt{}In London, Brazil's Lula calls for efforts to free Assange}{https://apnews.com/article/a994ffc406fc8df19e0f1a9ac1c0ed16}{Britain\textquotesingle s Prime Minister Rishi Sunak, right greets the President of Brazil, Lula da Silva during their meeting inside 10 Downing Street London, Friday, May 5, 2023. (AP Photo/Kin Cheung, POOL) RIO DE JANEIRO (AP) --- After...}

\entryitemWithDescription{\hskip 0pt{}Girl, 17, killed in California party shooting that wounds 5}{https://apnews.com/article/1c8f1cc0b1c97c0bd36777720dc90453}{Police investigate an incident on Columbus Avenue connected to another on West Seventh Street after midnight, Saturday, May 6, 2023, in Chico, California. Officials say officers responding around 3:30 a.m. Saturday to reports of gunfire...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Pageantry, rain herald King Charles' coronation}{https://apnews.com/article/7b5cddc23c69f3cf8d0f7198d027f5e3}{Britain\textquotesingle s King Charles III and Queen Camilla wave to the crowds from the balcony of Buckingham Palace after the coronation ceremony in London, Saturday, May 6, 2023. (AP Photo/Frank Augstein) LONDON (AP) --- A horse-drawn...}

\entryitemWithDescription{\hskip 0pt{}Chris Strachwitz, founded Arhoolie label, dies age 91}{https://apnews.com/article/e20882b0af2e4c34900c4163032fd95a}{FILE - Chris Strachwitz arrives at the 54th annual GRAMMY Awards on Feb. 12, 2012, in Los Angeles. Strachwitz, a producer, musicologist and one-man preservation society whose Arhoolie Records released thousands of songs by regional...}

\entryitemWithDescription{\hskip 0pt{}Tennis, or terriers? US Open's home hosts famed dog show}{https://apnews.com/article/f788548a9b117e03b2ecee6916064bab}{A handler and his dog compete in the agility preliminaries inside Arthur Ashe stadium during the 147th Westminster Kennel Club Dog show, Saturday, May 6, 2023, at the USTA Billie Jean King National Tennis Center in New York. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Kentucky Derby hat styles: Bigger is often better}{https://apnews.com/article/87134efb8d478f31518ad9397af55b67}{A race fan walks on the grounds of Churchill Downs before the 149th running of the Kentucky Derby horse race, Saturday, May 6, 2023, in Louisville, Ky. (AP Photo/Brynn Anderson) LOUISVILLE, Ky. (AP) --- The Kentucky Derby is arguably the...}

\entryitemWithDescription{\hskip 0pt{}Oprah tells class of 2023 to follow 'still, small voice'}{https://apnews.com/article/63f971b11cc8e249037c6712f5988eae}{Oprah Winfrey delivers the commencement address during the Tennessee State University graduation ceremony on Saturday, May 6, 2023, in Nashville, Tenn. (AP Photo/George Walker IV) NASHVILLE, Tenn. (AP) --- Oprah Winfrey delighted...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift returns to Nashville, reveals 'Speak Now' date}{https://apnews.com/article/f0000e9080f0e62724900c10c3fc3502}{Taylor Swift performs during "The Eras Tour" on Friday, May 5, 2023, at Nissan Stadium in Nashville, Tenn. (AP Photo/George Walker IV) NASHVILLE, Tenn. (AP) --- Taylor Swift is playing catch-up with her fans this year in a massive and...}

\entryitemWithDescription{\hskip 0pt{}Queen or queen consort? What to know about Camilla's title}{https://apnews.com/article/797b45b366926e77f238b895587a7288}{Queen Camilla is crowned with Queen Mary\textquotesingle s Crown by The Archbishop of Canterbury the Most Reverend Justin Welby, in Westminster Abbey, London, Saturday May 6, 2023. (Yui Mok, Pool via AP) LONDON (AP) --- Now that she has...}

\entryitemWithDescription{\hskip 0pt{}Hospitalized Berlusconi makes first public statements}{https://apnews.com/article/5f9aeadca1db2f45a4f6e138f89ddca1}{Silvio Berlusconi gestures as he talks in his video address during a Forza Italia party convention in Milan, Italy, Saturday, May 6, 2023. (AP Photo/Luca Bruno) MILAN (AP) --- Former Italian Premier Silvio Berlusconi has made his first...}