\entryitemWithDescription{\hskip 0pt{}CANNES PHOTOS: Helen Mirren's blue hair, Johnny Depp's return and more Day 1 scenes}{https://apnews.com/article/f0ec0d754d321b7b3c3544b024323b1b}{Helen Mirren poses for photographers upon arrival at the opening ceremony and the premiere of the film \textquotesingle Jeanne du Barry\textquotesingle{} at the 76th international film festival, Cannes, southern France, Tuesday, May 16...}

\entryitemWithDescription{\hskip 0pt{}AP Sources: Unknown man slipped undetected inside the home of White House official}{https://apnews.com/article/52fff78d75494a7656ed121670b543fa}{FILE - White House national security adviser Jake Sullivan speaks at a press briefing at the White House in Washington, April 24, 2023. Sullivan and senior Chinese foreign policy adviser Wang Yi held talks in Vienna this week, the latest...}

\entryitemWithDescription{\hskip 0pt{}Tesla lawyers want court to reconsider Musk tweet deemed 'threat' amid labor dispute}{https://apnews.com/article/357773388f8f1e3bc3e2ea5d15b2c3eb}{FILE - Elon Musk departs the Phillip Burton Federal Building and United States Court House in San Francisco, Jan. 24, 2023. Lawyers for Tesla are asking a federal appeals court to reconsider its ruling that Musk unlawfully threatened...}

\entryitemWithDescription{\hskip 0pt{}Saddleback Church appealing its ouster from the Southern Baptists on issue of women pastors}{https://apnews.com/article/64fac3a004fb90871f2127bf79c438c7}{FILE - Congregants arrive at Saddleback Church in Lake Forest, Calif., on Sunday, Oct. 16, 2022. Saddleback Church is appealing its ouster from the Southern Baptist Convention for having women pastors on staff, according to the...}

\entryitemWithDescription{\hskip 0pt{}Man and 12-year-old boy arrested after fatal shooting at Sonic restaurant in Texas}{https://apnews.com/article/167dbb9d0ec6e9f3a9632ed00872549c}{This photo released by the Keene Police Department on Sunday, May 14, 2023, shows Angel Gomez. Gomez and a 12-year-old boy have been arrested on murder warrants in the fatal shooting of a Sonic Drive-In employee in Keene, Texas. (Keene...}

\entryitemWithDescription{\hskip 0pt{}Recalled Gerber baby formula was sent to US retailers after recall began, wholesaler says}{https://apnews.com/article/7c31c0b8962ee31bd224f7358e351a6f}{This photo released by the U.S Food and Drug Administration on March 17, 2023, shows Gerber Good Start SootheProTM Powdered Infant Formula. In March, the Perrigo Company issued a voluntary recall of certain lots of the infant formula ``...}

\entryitemWithDescription{\hskip 0pt{}Man sentenced to 103 years for killing 4 SUV passengers, dumping bodies in cornfield}{https://apnews.com/article/951ee86d190029db0c5b7fef7a9b9a40}{FILE - This photo provided by Maricopa County, Ariz., Sheriff\textquotesingle s Office Antoine Suggs, convicted of killing four passengers in his Mercedes Benz SUV in Minnesota and dumping the bodies in a Wisconsin cornfield, who has been...}

\entryitemWithDescription{\hskip 0pt{}Lidia Bastianich honors immigrants and their food in PBS special 'Lidia Celebrates America'}{https://apnews.com/article/795129037451894fe9f8b2325067a4a9}{This image released by PBS shows celebrity chef Lidia Bastianich in Washington, DC on Nov. 7, 2022. The Emmy-award winning TV host, author and restaurateur explores the immigrant experience through food in the PBS special "Lidia...}

\entryitemWithDescription{\hskip 0pt{}Rain-swollen rivers flood some towns in north Italy; Venice prepares to raise mobile dike in lagoon}{https://apnews.com/article/0c14ed1883e785c452139a31ebd55a99}{This photo provided by the Italian Firefighters shows firefighters rescuing a person from a flooded house in Riccione, in the northern Italian region of Emilia Romagna, Tuesday, May 16, 2023. Unusually heavy rains have caused major...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry seeks to challenge denial of request to pay for own UK police protection}{https://apnews.com/article/2644bb64ef284dc715e8550c7fd3abed}{FILE - Britain\textquotesingle s Prince Harry arrives at the Royal Courts Of Justice in London, Thursday, March 30, 2023. A lawyer has asked a London judge to allow Prince Harry to challenge the government\textquotesingle s denial of his...}

\entryitemWithDescription{\hskip 0pt{}Former Missouri police officer accused of handcuffing man, allowing officer's brother to beat him}{https://apnews.com/article/50c5988e069d9400e73b53b56c0c4029}{This photo provided by The St. Louis County prosecutor\textquotesingle s office shows James Sims. St. Louis County prosecutors on Monday, May 15,2023, charged Sims with first-degree kidnapping, felony third-degree assault and misdemeanor...}

\entryitemWithDescription{\hskip 0pt{}Stellantis recalls nearly 220,000 Jeep Cherokee SUVs worldwide due to fire risk}{https://apnews.com/article/068e094ab43dc019f6bf4f685cf55d28}{FILE - This is the Jeep logo on the front end of a Jeep Cherokee on display at the Pittsburgh International Auto Show in Pittsburgh Thursday, Feb. 11, 2016. Stellantis is telling owners of nearly 220,000 Jeep Cherokee SUVs worldwide...}

\entryitemWithDescription{\hskip 0pt{}Skeletons found in Pompeii ruins reveal deaths by earthquake, not just Vesuvius' ancient eruption}{https://apnews.com/article/2e64ff244623ec088ac1e858fecfbc8e}{A picture made available Tuesday, May 16, 2023, by the Pompeii Archeological Park press office, showing two skeletons that archeologists believe were men who died when a wall collapsed on them during the powerful earthquakes that...}