\entryitemWithDescription{\hskip 0pt{}Countdown begins for April's total solar eclipse. What to know about watch parties and safe viewing}{https://apnews.com/article/83164668ee08b0a0c92e1d2ac41e91aa}{The sun is about to pull another disappearing act across North America, turning day into night during a total solar eclipse. The peak spectacle on April 8 will last up to 4 minutes, 28 seconds in the path of total darkness --- twice as...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Lunar New Year in the Philippines draws crowds to one of the world's oldest Chinatowns}{https://apnews.com/article/183d2476e1baab8efc6ac98e39aa1ebb}{MANILA, Philippines (AP) --- Crowds are flocking to Chinatown in the Philippine capital to usher in the Year of the Wood Dragon and experience lively traditional dances on lantern-lit streets with food, lucky charms and prayers for good...}

\entryitemWithDescription{\hskip 0pt{}Indonesian presidential hopefuls are trying social media, K-pop to win young voters. Will it work?}{https://apnews.com/article/73227fb99b0ed70f704c9f0f759622ce}{JAKARTA, Indonesia (AP) --- Seventeen-year-old Naima Khairiya Ismah started being bombarded by social media posts from candidates for Indonesia's presidential election on before she'd even given voting any thought. As three candidates vie...}

\entryitemWithDescription{\hskip 0pt{}CDC is investigating gastrointestinal sickness on luxury cruise ship Queen Victoria}{https://apnews.com/article/a4c08b114e3ee16534ff0c94a13c4fc7}{SAN FRANCISCO (AP) --- The Centers for Disease Control and Prevention is investigating an outbreak on a luxury cruise ship where more than 150 people have reported gastrointestinal illness, including diarrhea and vomiting. The Queen...}

\entryitemWithDescription{\hskip 0pt{}On live TV, Guardian Angels rough up a man in Times Square then misidentify him as a `migrant'}{https://apnews.com/article/dacb23b7cfe0679d12642bca116543d4}{NEW YORK (AP) --- Members of the Guardian Angels roughed up a man during a live interview on Fox News Tuesday night, then misidentified him as a ``migrant'' in a primetime segment meant to highlight disorder and crime caused by new...}

\entryitemWithDescription{\hskip 0pt{}Nick Saban joining ESPN's `College GameDay' road show}{https://apnews.com/article/cbbc9d91257d8368c14953d1083f5155}{Nick Saban is joining ESPN's ``College GameDay,'' the long-running Saturday pregame road show he appeared on as a guest so frequently during his 17 seasons as Alabama coach. The network announced Wednesday that Saban will be an on-set...}

\entryitemWithDescription{\hskip 0pt{}Idaho inmate nearing execution wants a new clemency hearing. The last one was a tie}{https://apnews.com/article/dba9cd7ed5ea43b5b5278b1060859d88}{BOISE, Idaho (AP) --- An Idaho man scheduled to be executed at the end of the month is asking a federal court to put his lethal injection on hold and order a new clemency hearing after the previous one resulted in a tie vote. Thomas...}

\entryitemWithDescription{\hskip 0pt{}Minnesota officials say lodge that burned had 3 unresolved inspection violations}{https://apnews.com/article/ffb2fb37ff0e610ee345e6d76c434318}{ST. PAUL, Minn. (AP) --- Minnesota regulators said Wednesday that an historic lodge destroyed in a fire had three unresolved violations from a recent fire code inspection, but it wasn't clear if those violations played a role in the...}

\entryitemWithDescription{\hskip 0pt{}Medical examiner rules death of baby decapitated during delivery was a homicide}{https://apnews.com/article/c2b1940871da17a41cff936390246d1d}{ATLANTA (AP) --- The death of a Georgia couple's baby that was decapitated during delivery has been classified by a medical examiner as a homicide, their attorneys announced Wednesday. Treveon Taylor Jr.\textquotesingle s parents have...}

\entryitemWithDescription{\hskip 0pt{}NFL's first Super Bowl in Las Vegas has plenty of storylines plus an interesting football matchup}{https://apnews.com/article/938a7c016988f4761d4f8a1f43b978bc}{LAS VEGAS (AP) --- The first Super Bowl in Las Vegas has everything the imaginary NFL scriptwriters could've wanted. There's Patrick Mahomes and the underdog Kansas City Chiefs (14-6) aiming to become the first repeat champions in 19...}

\entryitemWithDescription{\hskip 0pt{}Jury to decide on climate scientist Michael Mann's defamation suit over comparison to molester}{https://apnews.com/article/4246951093cd2a57e49cc9e0f38bf590}{WASHINGTON (AP) --- It's been 12 years since a pair of conservative writers compared a prominent climate scientist to a convicted child molester for his depiction of global warming. Now, a jury is about to decide whether the comments were...}

\entryitemWithDescription{\hskip 0pt{}Saturn's Death Star-looking moon may have vast underground ocean}{https://apnews.com/article/c506e45170f047096aaa5d093d05594c}{CAPE CANAVERAL, Fla. (AP) --- Astronomers have found the best evidence yet of a vast, young ocean beneath the icy exterior of Saturn's Death Star lookalike mini moon. The French-led team analyzed changes in Mimas' orbit and rotation and...}

\entryitemWithDescription{\hskip 0pt{}Does Spain's popular Eurovision song `Zorra' insult women or defend them?}{https://apnews.com/article/07ac53321e07455651e5f550831e574c}{MADRID (AP) --- Spain's Eurovision song ``Zorra,'' whose title can be translated as an anti-female slur, is causing a storm among conservatives and feminists while Socialist Prime Minister Pedro Sánchez says he likes it. The song by the...}