\entryitemWithDescription{\hskip 0pt{}Company that bred beagles for research pleads guilty to neglect, ordered to pay record \$35M fine}{https://apnews.com/article/49b77e5c3ac9a77dc06cde2498b1efc8}{A company that bred beagles for medical research agreed Monday to pay a record \$35 million as part of a criminal plea admitting it neglected thousands of dogs at its breeding facility in rural Virginia. Prosecutors said the penalties...}

\entryitemWithDescription{\hskip 0pt{}New Orleans valedictorian lived in a homeless shelter as he rose to the top of his class}{https://apnews.com/article/aed34ce1bb26a88391c15f137b28d92d}{NEW ORLEANS (AP) --- From a New Orleans homeless shelter to the top of his high school class, Elijah Hogan has already conquered much in life. Hogan recently graduated as one of two valedictorians at Walter L. Cohen charter high school...}

\entryitemWithDescription{\hskip 0pt{}Trial in the fatal daytime ambush of rapper Young Dolph reset to September}{https://apnews.com/article/cb3313d0c14ba1e909a06d8fd4c1fbeb}{MEMPHIS, Tenn. (AP) --- A judge on Monday reset the trial date for a man charged with killing rapper Young Dolph in a daytime shooting ambush at a cookie shop in his hometown of Memphis, Tennessee. Shelby County Judge Jennifer J. Mitchell...}

\entryitemWithDescription{\hskip 0pt{}Sandy Hook families ask bankruptcy judge to liquidate Alex Jones' media company}{https://apnews.com/article/e2aa4dde1277b5cd7c179e409e7bcf80}{Relatives of victims of the Sandy Hook Elementary School shooting are asking a bankruptcy judge to liquidate conspiracy theorist Alex Jones' media company, including Infowars, instead of allowing him to reorganize his business as they...}

\entryitemWithDescription{\hskip 0pt{}'SNL' lampooned men in artistic swimming. Bill May could be the sport's first male Olympian}{https://apnews.com/article/73b1a984c7f119658c7a733b15717b4f}{NEW YORK (AP) --- Bill May chuckles at the mere mention of the words ``Saturday Night Live,'' knowing that the conversation is about to turn to the TV show's 1984 skit starring Martin Short as one of two brothers attempting to make it to...}

\entryitemWithDescription{\hskip 0pt{}Toyota apologizes for cheating on vehicle testing and halts production of three models}{https://apnews.com/article/26585a96df2a32f7d67a4011a0a98772}{TOKYO (AP) --- Toyota Chairman Akio Toyoda apologized Monday for massive cheating on certification tests for seven vehicle models as the automaker suspended production of three of them. The wide-ranging faulty testing at Japan's top...}

\entryitemWithDescription{\hskip 0pt{}From decay to dazzling. Ford restores grandeur to former eyesore Detroit train station}{https://apnews.com/article/49c55d18ee0b377fa54c70f389168639}{DETROIT (AP) --- The once-blighted monolithic Michigan Central train station --- for decades a symbol of Detroit's decline --- has new life following a massive six-year, multimillion-dollar renovation to create a hub for mobility projects...}

\entryitemWithDescription{\hskip 0pt{}The matchup is set: Panthers, Oilers will meet in the Stanley Cup Final}{https://apnews.com/article/88e8b8c87432f2601ea942fd4011f495}{SUNRISE, Fla. (AP) --- Matthew Tkachuk is about to renew some acquaintances. Connor McDavid is going back to where his NHL career started. The Stanley Cup Final matchup is set: The Florida Panthers, back in the title round for the second...}

\entryitemWithDescription{\hskip 0pt{}Simone Biles continues Olympic prep by cruising to her 9th U.S. Championships title}{https://apnews.com/article/ee35d8671238d511467e794c97eaad47}{FORT WORTH, Texas (AP) --- Gymnastics superstar Simone Biles won her ninth U.S. Championship on Sunday, leaving little doubt that at 27 and a decade-plus into her run atop the sport, she is as good as ever. Biles posted a two-day all...}

\entryitemWithDescription{\hskip 0pt{}Yuka Saso wins another US Women's Open. This one was for Japan}{https://apnews.com/article/fbcd680141a45158ca45cbfb095cb926}{LANCASTER, Pa. (AP) --- Yuka Saso became a U.S. Women's Open champion for the second time Sunday and took her place in history with a rare footnote --- the first Filipino to win the Women's Open in 2021, and now the first from Japan. No...}

\entryitemWithDescription{\hskip 0pt{}Gay pride revelers in Sao Paulo reclaim Brazil's national symbols}{https://apnews.com/article/27c64e4b89da74b371e5b33fb401103f}{SAO PAULO, Brazil (AP) --- The iconic yellow and green of Brazil's flag mixed with a sea of rainbow-colored tutus, hand fans and drag queen hairdos at Sunday's LGBTQ+ pride parade in Sao Paulo, Brazil. The annual event along Sao Paulo's...}

\entryitemWithDescription{\hskip 0pt{}Rugby star and ALS campaigner Rob Burrow dies at age 41}{https://apnews.com/article/6810e415ec1b003c9b74ee4ba4220f54}{LEEDS, England (AP) --- Rob Burrow, a former rugby star who was widely praised for his fundraising campaigns after being diagnosed with Lou Gehrig's disease in 2019, has died. He was 41. Leeds Rhinos announced his death on Sunday. Burrow...}

\entryitemWithDescription{\hskip 0pt{}Ex-NJ officer sentenced to 27 years in shooting death of driver, wounding of passenger in 2019 chase}{https://apnews.com/article/e362ff23b64ed36e039c7d9acb32f0e3}{NEWARK, N.J. (AP) --- A former New Jersey police officer has been sentenced to a total of 27 years in prison in the shooting death of one man and the wounding of another during a high-speed car chase 5 1/2 years ago in the city of Newark...}