\entryitemWithDescription{\hskip 0pt{}Iditarod co-founder's grandson Ryan Redington wins dog race}{https://apnews.com/article/a9b7d7a789bf032e3d1538058901b249}{Ryan Redington poses with his lead dogs Sven, left, and Ghost, after he won the 2023 Iditarod Trail Sled Dog Race, Tuesday, March 14, 2023 in Nome, Alaska. Redington, 40, is the grandson of Joe Redington Sr., who helped co-found the...}

\entryitemWithDescription{\hskip 0pt{}NASA Webb telescope captures star on cusp of death}{https://apnews.com/article/2d703565f9521f71dcbf11441d920f67}{This image provided by NASA shows the star Wolf-Rayet 124, center, captured by the James Webb Space Telescope in June 2022. A surrounding nebula is made of material cast off from the aging star in random ejections, and from dust produced...}

\entryitemWithDescription{\hskip 0pt{}Nebraska lawmaker 3 weeks into filibuster over trans bill}{https://apnews.com/article/b9018fd1bf72112ca984ff58679eda6d}{State Sen. Machaela Cavanaugh prepares to speak before the Nebraska Legislature Monday, March 13, 2023, at the Nebraska State Capital in Lincoln, Neb. Cavanaugh is in her third week of an effort to filibuster every bill that comes before...}

\entryitemWithDescription{\hskip 0pt{}Ohio sues Norfolk Southern over toxic train derailment}{https://apnews.com/article/07a9727b4cdf8f6758a7d834431a38c1}{FILE - A black plume rises over East Palestine, Ohio, as a result of a controlled detonation of a portion of the derailed Norfolk Southern trains, Feb. 6, 2023. The Ohio attorney general said Tuesday, March 14, that the state filed a...}

\entryitemWithDescription{\hskip 0pt{}Lindsay Lohan announces pregnancy in Instagram post}{https://apnews.com/article/b15918294193bc9885bd13d737cc4ab1}{FILE - Lindsay Lohan appears the Christian Siriano Fall/Winter 2023 fashion show in New York on Feb. 9, 2023. Lohan is expecting her first child. The ``Mean Girls'' star announced her pregnancy on Instagram on Tuesday. (Photo by Charles...}

\entryitemWithDescription{\hskip 0pt{}Fed criticized for missing red flags before bank collapse}{https://apnews.com/article/609bde9b9248fbc590ff98775e0c8d49}{A pedestrian passes a Silicon Valley Bank branch in San Francisco, Monday, March 13, 2023. As the primary regulator of the bank, the Federal Reserve is coming under sharp criticism from financial watchdogs and banking experts. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}No Harvey Weinstein retrial on rape, sex assault charges}{https://apnews.com/article/1e349d8f9d4a1ef1f3ba75e13874fc2e}{FILE - Former film producer Harvey Weinstein appears in court at the Clara Shortridge Foltz Criminal Justice Center in Los Angeles, Calif., on Oct. 4 2022. Los Angeles prosecutors say they will not retry Harvey Weinstein on rape and...}

\entryitemWithDescription{\hskip 0pt{}Is my money safe? What you need to know about bank failures}{https://apnews.com/article/6aa3564a8acda9098929abe4741fcbfd}{A person leaves one of the Signature Bank branches in New York, Monday, March. 13, 2023. President Joe Biden is telling Americans that the nation's financial systems are sound. This comes after the swift and stunning collapse of two banks...}

\entryitemWithDescription{\hskip 0pt{}FIFA expands 2026 World Cup again to create 104-game program}{https://apnews.com/article/04ddfc15e9ef3042a631aece779c0145}{FILE - Argentina\textquotesingle s Lionel Messi kisses the trophy presented by FIFA President Gianni Infantino, left, as The Emir of Qatar Sheikh Tamim bin Hamad Al Thani looks on, after the World Cup final soccer match between Argentina...}

\entryitemWithDescription{\hskip 0pt{}Sanders signs Arkansas trans care malpractice bill into law}{https://apnews.com/article/41b7cd39b167b3bf2f3796d8be37ecf6}{LITTLE ROCK, Ark. (AP) --- Arkansas Gov. Sarah Huckabee Sanders has signed legislation making it easier to sue providers of gender-affirming care for children, a move that could effectively reinstate a blocked ban on such care. Sanders on...}

\entryitemWithDescription{\hskip 0pt{}Hundreds dead as Cyclone Freddy wrecks Malawi, Mozambique}{https://apnews.com/article/7a0949c6ea48dec4fa772f5d05c494d5}{An unrelenting Cyclone Freddy that is currently battering southern Africa has killed at least 68 people in Malawi and Mozambique since it struck the continent for a second time on Saturday night, authorities in both countries have...}

\entryitemWithDescription{\hskip 0pt{}New atmospheric river brings rain, wind to soggy California}{https://apnews.com/article/4ab2bb3ac82a7b79f720e60c7b29f9b7}{Some of the more than 8,500 residents evacuated from the flooded area say the levee should have been improved years ago after a similar breach back in 1995. (March 14) Pamela and Patrick Cerruti empty coins from Pajaro Coin Laundry as...}

\entryitemWithDescription{\hskip 0pt{}Biden says Jimmy Carter has asked him to deliver his eulogy}{https://apnews.com/article/7a854cb125b53283947ed7471e188f87}{Dr. Frank Richards serves as a senior advisor at the Carter Center. For nearly 20 years, he has worked to prevent and eradicate neglected tropical diseases. (Feb. 23) FILE - In this Feb. 20, 1978, file photo, President Jimmy Carter...}