\entryitemWithDescription{\hskip 0pt{}At least 189 bodies found decaying at a Colorado funeral home, up from 115, officials say}{https://apnews.com/article/d83e65897404bef632dbb7ad4a8e4bfe}{DENVER (AP) --- The remains of at least 189 bodies have been found decaying at a Colorado funeral home, up from about 115 reported when the bodies were discovered two weeks ago, officials said Tuesday. The remains were found by...}

\entryitemWithDescription{\hskip 0pt{}Britney Spears writes of abortion while dating Justin Timberlake in excerpts from upcoming memoir}{https://apnews.com/article/b67f8514d72acb0b2ecc7c0c9b6984cc}{Britney Spears wrote that she had an abortion while dating Justin Timberlake more than 20 years ago, according to a peek inside her hotly anticipated memoir. ``If it had been left up to me alone, I never would have done it,'' she writes...}

\entryitemWithDescription{\hskip 0pt{}Can New York's mayor speak Mandarin? No, but with AI he's making robocalls in different languages}{https://apnews.com/article/30517885466994e5f1f54745c08691e0}{ALBANY, N.Y. (AP) --- New York City Mayor Eric Adams has been using artificial intelligence to make robocalls that contort his own voice into several languages he doesn't actually speak, posing new ethical questions about the government's...}

\entryitemWithDescription{\hskip 0pt{}Rite Aid's bankruptcy plan stirs worries of new `pharmacy deserts'}{https://apnews.com/article/0739cda0df8d199d3a6c001612b0e8fc}{Rite Aid's plan to close more stores as part of its bankruptcy process could hurt access to medicine and care, particularly in some majority Black and Hispanic neighborhoods and in rural areas, experts say. The drugstore chain said late...}

\entryitemWithDescription{\hskip 0pt{}These five toys are regular finalists for Hall of Fame honors. Now fans can vote one in}{https://apnews.com/article/98b0f5b1a18b91b0835273610fcdfd22}{ROCHESTER, N.Y. (AP) --- They are playfully called the ``forgotten five'': A handful of toys --- the pogo stick, the Fisher-Price Corn Popper, My Little Pony, PEZ dispensers, and Transformers --- that regularly approach toybox royalty as...}

\entryitemWithDescription{\hskip 0pt{}Upcoming `Sesame Street' season stars Ariana DeBose, Brandi Carlile, ASL and an octopus chef}{https://apnews.com/article/758dd910c6489a3c8c1bed6875bc0996}{NEW YORK (AP) --- The upcoming season of ``Sesame Street'' features an octopus as a chef, an exploration of American Sign Language and Quinta Brunson giving Cookie Monster a little bit of attitude. The 54th season of the iconic children's...}

\entryitemWithDescription{\hskip 0pt{}Rolls-Royce is cutting up to 2,500 jobs in an overhaul of the UK jet engine maker}{https://apnews.com/article/375255aad3be447e9bd91a4ecffbb41e}{Jet engine maker Rolls-Royce said Tuesday it's cutting up to 2,500 jobs globally as part of a corporate overhaul that its new CEO is carrying out. The aerospace company was hit hard by the COVID-19 pandemic that decimated demand for air...}

\entryitemWithDescription{\hskip 0pt{}The internet is littered with fake reviews. Amazon, Glassdoor and others are trying to fight back}{https://apnews.com/article/43a478ac0b27d6bb773a3bbdba1858b1}{NEW YORK (AP) --- Some of the most used platforms for travel and online shopping said Tuesday they're going to team up to battle fake reviews. Amazon, reviews site Glassdoor and Trustpilot, as well as travel companies Expedia Group...}

\entryitemWithDescription{\hskip 0pt{}Biden campaign launches account on Trump's Truth Social, saying `converts welcome'}{https://apnews.com/article/f8b61b8d360318404be5905a0de6b5d2}{WASHINGTON (AP) --- President Joe Biden `s 2024 campaign launched an account on Donald Trump `s Truth Social on Monday, attempting to poke online fun at the Republican candidate he may well face again in next fall's election. Under the...}

\entryitemWithDescription{\hskip 0pt{}Reese's \$25,000 promotion may violate sweepstakes laws}{https://apnews.com/article/6baba25eced7f8ac528252c0588f3ed0}{Reese's may be in violation of state and federal laws with its new sweepstakes offer currently advertised on packs of peanut butter cups. The promotion on two-cup packages reads ``You could win \$25,000'' and, in smaller print, ``See...}

\entryitemWithDescription{\hskip 0pt{}Suzanne Somers, of `Three's Company,' dies at 76}{https://apnews.com/article/2b97c5362eab6709f594b30280dc79c3}{Suzanne Somers, the effervescent blonde actor known for playing Chrissy Snow on the television show ``Three's Company'' and who became an entrepreneur and New York Times best-selling author, has died. She was 76. Somers had breast cancer...}

\entryitemWithDescription{\hskip 0pt{}Stoneman Douglas High shooting site visited one last time by lawmakers and educators}{https://apnews.com/article/34e8e51d7ca69e3d995a8af3e295e80f}{PARKLAND, Fla. (AP) --- Florida lawmakers and education leaders from several states on Saturday took what is likely the final tour of a building at Marjory Stoneman Douglas High School in Parkland, where a former student shot 17 people to...}

\entryitemWithDescription{\hskip 0pt{}Ex-Connecticut police officer suspected of burglaries in 3 states}{https://apnews.com/article/7ab011b02612192e198f6e21cd571b0f}{GLASTONBURY, Conn. (AP) --- A former Connecticut police officer is suspected of being a serial burglar and committing 30 or more thefts in three states, including the community he had patrolled until recently. A newly unsealed warrant...}