\entryitemWithDescription{\hskip 0pt{}Nkamhoua, Tennessee bully Duke, advance to Sweet 16}{https://apnews.com/article/f4c355f3250bd333e4f2c9ff6788e018}{Tennessee forward Olivier Nkamhoua (13) celebrates after their win over Duke in a second-round college basketball game in the NCAA Tournament, Saturday, March 18, 2023, in Orlando, Fla. (AP Photo/Phelan M. Ebenhack) ORLANDO, Fla. (AP...}

\entryitemWithDescription{\hskip 0pt{}Prosecutor to release video of death of man in custody}{https://apnews.com/article/889ee3a6f97c2e45573e3780ca3013e4}{Caroline Ouko, mother of Irvo Otieno, holds a portrait of her son with attorney Ben Crump, left, her older son, Leon Ochieng and attorney Mark Krudys at the Dinwiddie Courthouse in Dinwiddie, Va., on Thursday, March 16, 2023. She said...}

\entryitemWithDescription{\hskip 0pt{}Some Trump rivals rally to his side as possible charges loom}{https://apnews.com/article/24fc4d906d09a85965f60ef0f68cdd93}{FILE - Former Vice President Mike Pence faces reporters after making remarks at a GOP fundraising dinner, March 16, 2023, in Keene, N.H. Top Republicans, including some of former President Donald Trump's potential rivals for the party's...}

\entryitemWithDescription{\hskip 0pt{}Pope promotes 'humanitarian corridors' for asylum-seekers}{https://apnews.com/article/a444d46927451d683960813b27079a8b}{Pope Francis meets with refugee families in the Paul VI hall at the Vatican, Saturday, March 18, 2023. (AP Photo/Gregorio Borgia) VATICAN CITY (AP) --- Pope Francis met Saturday with thousands of refugees and charity groups hosting them...}

\entryitemWithDescription{\hskip 0pt{}Ecuador earthquake kills at least 12, causes wide damage}{https://apnews.com/article/7517383684eb54226b6db5a3b81f01ea}{Rescue workers stand next to a car crushed by debris after an earthquake in Cuenca, Ecuador, Saturday, March 18, 2023.. The U.S. Geological Survey reported an earthquake with a magnitude of 6.7 about 50 miles south of Guayaquil. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}US Open 'very hopeful' unvaccinated Novak Djokovic can play}{https://apnews.com/article/ba8b4b42a363b1547bdaae313b6e7053}{FILE - Serbia\textquotesingle s Novak Djokovic looks up during the quarterfinals of the Dubai Duty Free Tennis Championships in Dubai, United Arab Emirates, Thursday, March 1, 2023. Djokovic has pulled out of the Miami Open because he can'...}

\entryitemWithDescription{\hskip 0pt{}Supervisor in Tyre Nichols' death retired before firing}{https://apnews.com/article/0c1d1ca671457c68a99ba4ed80f82fb3}{FILE - The screen at the Smoothie King Center in New Orleans honors Tyre Nichols before an NBA basketball game between the New Orleans Pelicans and the Washington Wizards, Jan. 28, 2023. Five former Memphis, Tenn., police officers were...}

\entryitemWithDescription{\hskip 0pt{}Russia, Ukraine extend grain deal to aid world's poor}{https://apnews.com/article/9b47d9d0b53e5ab0494c8eeea1197327}{FILE - The Eaubonne bulk carrier ship docks in the port of Mombasa, Kenya Saturday, Nov. 26, 2022. An unprecedented wartime deal that allows grain to flow from Ukraine to countries in Africa, the Middle East and Asia where hunger is a...}

\entryitemWithDescription{\hskip 0pt{}Vatican closes embassy in Nicaragua after Ortega's crackdown}{https://apnews.com/article/9b95ffffd3cfddf49b2286027356118f}{Catholics take part in a reenactment of the Stations of the Cross during the Lenten season at the Metropolitan Cathedral in Managua, Nicaragua, Friday, March 17, 2023. Amid tensions between the Vatican and the Daniel Ortega government...}

\entryitemWithDescription{\hskip 0pt{}Haley, Ramaswamy among those taking on 'woke ideology' in SC}{https://apnews.com/article/4692d1165483062c95be067b651f49cc}{Tech entrepreneur Vivek Ramaswamy speaks at the Vision \textquotesingle24 conference on Saturday, March 18, 2023, in North Charleston, S.C. Organizers are describing the gathering as ``casting the conservative vision" for the next White...}

\entryitemWithDescription{\hskip 0pt{}Trump says he expects to be arrested, calls for protest}{https://apnews.com/article/a48428984cf99d23f46b4157b34160ae}{Former Donald Trump attorney Michael Cohen has completed his second day of testimony before a grand jury investigating hush money paid to Stormy Daniels on Trump's behalf. (March 15) (AP video by Ted Shaffrey) FILE - Former President...}

\entryitemWithDescription{\hskip 0pt{}Pro-Moscow voices tried to steer Ohio train disaster debate}{https://apnews.com/article/49af27699727d6f4157a5d6d5f35819b}{FILE - This photo taken with a drone shows portions of a Norfolk and Southern freight train that derailed Friday night in East Palestine, Ohio are still on fire at mid-day Saturday, Feb. 4, 2023. Soon after the train derailed and spilled...}

\entryitemWithDescription{\hskip 0pt{}Bank failures: Anger in Congress, but division on what to do}{https://apnews.com/article/619c8075506a70eaada02223af39109e}{FILE - The Capitol is seen through a window in the Russell Senate Office Building as policymakers wrestle with fallout from the failure of Silicon Valley Bank, in Washington, March 15, 2023. While President Joe Biden called Monday on...}