


\ipart{Developers}
\ichapter{Hacker News}
\entryitemTwoLinks{Scammed by the top result for 'Bitcoin wallet' in Apple App Store}{https://news.ycombinator.com/item?id=39685272}{https://news.ycombinator.com/item?id=39685272}

\entryitemTwoLinks{On the new Dutch intelligence and security law}{https://news.ycombinator.com/item?id=39684472}{https://berthub.eu/articles/posts/dutch-intelligence-and-security-law/}

\entryitemTwoLinks{Fig is sunsetting}{https://news.ycombinator.com/item?id=39683889}{https://fig.io/blog/post/fig-is-sunsetting}

\entryitemTwoLinks{How Mandelbrot set images are affected by floating point precision}{https://news.ycombinator.com/item?id=39683455}{https://github.com/ProfJski/FloatCompMandelbrot}

\entryitemTwoLinks{Boeing whistleblower John Barnett found dead}{https://news.ycombinator.com/item?id=39682698}{https://www.npr.org/2024/03/12/1238033573/boeing-whistleblower-john-barnett-dead}

\entryitemTwoLinks{Astro DB}{https://news.ycombinator.com/item?id=39682366}{https://astro.build/db/}

\entryitemTwoLinks{Byte-Sized Swift: Building Tiny Games for the Playdate}{https://news.ycombinator.com/item?id=39682143}{https://www.swift.org/blog/byte-sized-swift-tiny-games-playdate/}

\entryitemTwoLinks{The NYPD sent a warrantless subpoena for a copwatcher's Twitter account}{https://news.ycombinator.com/item?id=39681920}{https://hellgatenyc.com/nypd-warrantless-subpoena-copwatcher-social-media}

\entryitemTwoLinks{Vulkan Foliage rendering using GPU Instancing}{https://news.ycombinator.com/item?id=39681812}{https://www.thegeeko.me/blog/foliage-rendering}

\entryitemTwoLinks{Pilot of Boeing flight says he lost control after instrument failure}{https://news.ycombinator.com/item?id=39681102}{https://www.cnn.com/2024/03/12/australia/latam-airlines-flight-injuries-new-zealand-tuesday-intl-hnk/index.html}

\entryitemTwoLinks{Building Meta's GenAI infrastructure}{https://news.ycombinator.com/item?id=39680997}{https://engineering.fb.com/2024/03/12/data-center-engineering/building-metas-genai-infrastructure/}

\entryitemTwoLinks{Deterministic simulation testing for our entire SaaS}{https://news.ycombinator.com/item?id=39680579}{https://www.warpstream.com/blog/deterministic-simulation-testing-for-our-entire-saas}

\entryitemTwoLinks{Devin: AI Software Engineer}{https://news.ycombinator.com/item?id=39679787}{https://www.cognition-labs.com/blog}

\entryitemTwoLinks{Show HN: Comma Separated Values (CSV) to Unicode Separated Values (USV)}{https://news.ycombinator.com/item?id=39679378}{https://crates.io/crates/csv-to-usv}

\entryitemTwoLinks{Weather forecasts have become more accurate}{https://news.ycombinator.com/item?id=39678783}{https://ourworldindata.org/weather-forecasts}

\entryitemTwoLinks{More options for apps distributed in the European Union}{https://news.ycombinator.com/item?id=39678555}{https://developer.apple.com/news/?id=8c1m8hqt}

\entryitemTwoLinks{Apple announces ability to download apps directly from websites in EU}{https://news.ycombinator.com/item?id=39678532}{https://www.macrumors.com/2024/03/12/apple-announces-app-downloads-from-websites/}

\entryitemTwoLinks{I no longer maintain my Emacs projects on Sourcehut}{https://news.ycombinator.com/item?id=39678491}{https://protesilaos.com/codelog/2024-01-27-sourcehut-no-more/}

\entryitemTwoLinks{The internet is slipping out of our reach}{https://news.ycombinator.com/item?id=39677677}{https://injuly.in/blog/darker-internet/index.html}

\entryitemTwoLinks{Google Announces Stealing Part of a Production Language Model}{https://news.ycombinator.com/item?id=39677611}{https://twitter.com/\_akhaliq/status/1767384751269150828}\ichapter{Phoronix}
\entryitemGeneric{\hskip 0pt{}OBS Studio 30.1 Released With AV1 Support For VA-API \& PipeWire Video Capture}{https://www.phoronix.com/news/OBS-Studio-30.1}

\entryitemGeneric{\hskip 0pt{}KDE Plasma 6.0.2 Delivers Another Week Worth Of Bug Fixes}{https://www.phoronix.com/news/KDE-Plasma-6.0.2}

\entryitemGeneric{\hskip 0pt{}GhostRace Detailed - Speculative Race Conditions Affecting All Major CPUs / ISAs}{https://www.phoronix.com/news/CPU-Speculative-GhostRace}

\entryitemGeneric{\hskip 0pt{}New Intel CPU Microcode \& "RFDS" Linux Kernel Patch For New Security Vulnerabilities}{https://www.phoronix.com/news/Intel-March-2024-Security}

\entryitemGeneric{\hskip 0pt{}Ubuntu 24.04 LTS To Help Further Boost AMD EPYC 9004 Series Performance}{https://www.phoronix.com/news/Ubuntu-24.04-AMD-EPYC-9004}

\entryitemGeneric{\hskip 0pt{}Linux 6.9 Lands Reworked Topology Code For Better Hybrid CPU Support}{https://www.phoronix.com/news/Linux-6.9-APIC-x86-CPU-Topology}

\entryitemGeneric{\hskip 0pt{}Many Networking Improvements \& New Wired/Wireless Devices For Linux 6.9}{https://www.phoronix.com/news/Linux-6.9-Networking}

\entryitemGeneric{\hskip 0pt{}AdaptiveCpp 24.02 Released: "One Of The Best SYCL Compilers" For Performance}{https://www.phoronix.com/news/AdaptiveCpp-24.02-Released}

\entryitemGeneric{\hskip 0pt{}Too Many Debug Messages Were Reportedly Slowing Down Some AMD Linux Systems}{https://www.phoronix.com/news/AMD-Linux-Too-Much-NMI}\ichapter{GitHub}
\entryitemWithDescription{\hskip 0pt{}gleam-lang/gleam}{https://github.com/gleam-lang/gleam}{⭐️ A friendly language for building type-safe, scalable systems!\\
Language: Rust\\
Stars: 11141\\
Forks: 440}

\entryitemWithDescription{\hskip 0pt{}krahets/hello-algo}{https://github.com/krahets/hello-algo}{《Hello 算法》：动画图解、一键运行的数据结构与算法教程，支持 Python,
C++, Java, C\#, Go, Swift, JS, TS, Dart, Rust, C, Zig 等语言。English
edition ongoing\\
Language: Java\\
Stars: 65664\\
Forks: 8067}

\entryitemWithDescription{\hskip 0pt{}microsoft/qlib}{https://github.com/microsoft/qlib}{Qlib is an AI-oriented quantitative investment platform that aims to
realize the potential, empower research, and create value using AI
technologies in quantitative investment, from exploring ideas to
implementing productions. Qlib supports diverse machine learning
modeling paradigms. including supervised learning, market dynamics
modeling, and RL.\\
Language: Python\\
Stars: 13708\\
Forks: 2382}

\entryitemWithDescription{\hskip 0pt{}electron/electron}{https://github.com/electron/electron}{:electron: Build cross-platform desktop apps with JavaScript, HTML, and
CSS\\
Language: C++\\
Stars: 111308\\
Forks: 14771}

\entryitemWithDescription{\hskip 0pt{}laurent22/joplin}{https://github.com/laurent22/joplin}{Joplin - the secure note taking and to-do app with synchronisation
capabilities for Windows, macOS, Linux, Android and iOS.\\
Language: TypeScript\\
Stars: 41893\\
Forks: 4508}\ichapter{Dribbble}



\ipart{Developers~~~~(zh-Hans)}
\ichapter{Solidot}
\entryitemGeneric{\hskip 0pt{}澳大利亚批准了能抵抗巴拿马病的转基因香蕉}{https://www.solidot.org/story?sid=77578}

\entryitemGeneric{\hskip 0pt{}收到 DMCA 通知后 GitHub 去年移除逾 2 万个项目}{https://www.solidot.org/story?sid=77577}

\entryitemGeneric{\hskip 0pt{}Windows 10 21H2 将于 6 月终止支持}{https://www.solidot.org/story?sid=77576}

\entryitemGeneric{\hskip 0pt{}OpenAI 开源 Transformer Debugger}{https://www.solidot.org/story?sid=77575}

\entryitemGeneric{\hskip 0pt{}在 Yuzu 废墟上诞生的 Suyu 项目试图避开诉讼}{https://www.solidot.org/story?sid=77574}

\entryitemGeneric{\hskip 0pt{}韦伯和哈勃确认哈勃常数是正确的}{https://www.solidot.org/story?sid=77573}

\entryitemGeneric{\hskip 0pt{}Airbnb 禁止室内监控探头}{https://www.solidot.org/story?sid=77572}

\entryitemGeneric{\hskip 0pt{}Midjourne 封掉了所有 Stability AI 公司雇员的账号}{https://www.solidot.org/story?sid=77571}

\entryitemGeneric{\hskip 0pt{}马斯克的慈善基金会}{https://www.solidot.org/story?sid=77570}

\entryitemGeneric{\hskip 0pt{}法国政府机构遭遇 DDoS 攻击}{https://www.solidot.org/story?sid=77569}

\entryitemGeneric{\hskip 0pt{}xAI 将开源其 AI 聊天机器人 Grok }{https://www.solidot.org/story?sid=77568}

\entryitemGeneric{\hskip 0pt{}前动视 CEO Bobby Kotick 考虑收购 TikTok}{https://www.solidot.org/story?sid=77567}

\entryitemGeneric{\hskip 0pt{}五角大楼否认向公众隐瞒外星科技或外星生物}{https://www.solidot.org/story?sid=77566}

\entryitemGeneric{\hskip 0pt{}阿拉巴马州紧急制定法律保护体外受精}{https://www.solidot.org/story?sid=77565}

\entryitemGeneric{\hskip 0pt{}Telegram 月活跃用户突破 9 亿，考虑 IPO}{https://www.solidot.org/story?sid=77564}

\entryitemGeneric{\hskip 0pt{}Linux Mint 构建新桌面聊天应用 Jargonaut}{https://www.solidot.org/story?sid=77563}

\entryitemGeneric{\hskip 0pt{}YouTube 对未登陆用户停止推荐视频}{https://www.solidot.org/story?sid=77562}

\entryitemGeneric{\hskip 0pt{}研究估计含铅汽油降低美国半数人口的 IQ 分数}{https://www.solidot.org/story?sid=77561}

\entryitemGeneric{\hskip 0pt{}俄罗斯使用 Starlink 引发 SpaceX 是否遵守美国制裁的调查}{https://www.solidot.org/story?sid=77560}

\entryitemGeneric{\hskip 0pt{}科学家解释说话和吸气不能同时进行的原因}{https://www.solidot.org/story?sid=77559}\ichapter{V2EX}
\entryitemGeneric{\hskip 0pt{}[macOS] macOS 上， Finder 无法重命名文件}{https://www.v2ex.com/t/1023066}

\entryitemGeneric{\hskip 0pt{}[iCloud] 如何将国内的 iCloud+里面的数据转移到外区？}{https://www.v2ex.com/t/1023065}

\entryitemGeneric{\hskip 0pt{}[Surge] 找拼车， surge for}{https://www.v2ex.com/t/1023064}

\entryitemGeneric{\hskip 0pt{}[问与答] 有没有用过转运中国的大佬}{https://www.v2ex.com/t/1023063}

\entryitemGeneric{\hskip 0pt{}[问与答] 人在美国 eBay 买个二手笔记本求推荐 2024}{https://www.v2ex.com/t/1023062}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 关于猫棒是否可以再拆分成单独系统+xpon 光电棒子}{https://www.v2ex.com/t/1023061}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 除了爱快，还有其他可选吗？}{https://www.v2ex.com/t/1023059}

\entryitemGeneric{\hskip 0pt{}[前端开发] 吐槽 tsc 的几大罪状}{https://www.v2ex.com/t/1023058}

\entryitemGeneric{\hskip 0pt{}[NAS] PVE 跟 PBS 在同一台机器上运行，但是 PBS 的备份数据放单独的备份盘，两块硬盘一起坏的概率高么？有什么推荐的异地备份方案？}{https://www.v2ex.com/t/1023057}

\entryitemGeneric{\hskip 0pt{}[程序员] 应届生的求职迷茫\&Offer 选择，渴望得到前辈们的一些指点}{https://www.v2ex.com/t/1023056}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 有什么做大型代码仓分析的 gpt 开源项目么}{https://www.v2ex.com/t/1023055}

\entryitemGeneric{\hskip 0pt{}[程序员] 我看谁还在说 PHP 开发没有前途，我就给他一个大闭斗}{https://www.v2ex.com/t/1023053}

\entryitemGeneric{\hskip 0pt{}[程序员] 打算配一台主机用于跑大模型玩，大佬们有推荐的配置吗}{https://www.v2ex.com/t/1023052}

\entryitemGeneric{\hskip 0pt{}[问与答] 这个诈骗网站如何取得 windows 点 net 的子域名的?}{https://www.v2ex.com/t/1023051}

\entryitemGeneric{\hskip 0pt{}[问与答] iPhone 如何像安卓那样管理、整理相册}{https://www.v2ex.com/t/1023050}

\entryitemGeneric{\hskip 0pt{}[分享发现] 不知道怎么开发网页？先把这套工具熟悉下。}{https://www.v2ex.com/t/1023048}

\entryitemGeneric{\hskip 0pt{}[汽车] 新 Taycan 发布了，来看看 18 年老 Taycan 发布时大家是怎么看待 800V 充电的}{https://www.v2ex.com/t/1023047}

\entryitemGeneric{\hskip 0pt{}[问与答] AlDente 为啥会自动把充电限制提高到 100\%？}{https://www.v2ex.com/t/1023046}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 建了一个直接用的 ChatGPT，速度快还不限次数，找合作}{https://www.v2ex.com/t/1023045}

\entryitemGeneric{\hskip 0pt{}[问与答] 和朋友会因为小事闹翻吗？}{https://www.v2ex.com/t/1023044}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 非广州、深圳、东莞、佛山四城的朋友，是否能够正常使用电信的 VoWiFi 业务？}{https://www.v2ex.com/t/1023043}

\entryitemGeneric{\hskip 0pt{}[Apple] Mac 上如何索引网络硬盘}{https://www.v2ex.com/t/1023042}

\entryitemGeneric{\hskip 0pt{}[程序员] 大厂开发面试如何准备？}{https://www.v2ex.com/t/1023040}

\entryitemGeneric{\hskip 0pt{}[Go 编程语言] [golang 跨端] 刚看完这篇文章感想， golang 在跨端领域目前如何了呢}{https://www.v2ex.com/t/1023038}

\entryitemGeneric{\hskip 0pt{}[奇思妙想] 基于 LLM 的资讯跟踪软件}{https://www.v2ex.com/t/1023037}

\entryitemGeneric{\hskip 0pt{}[程序员] 简书是不是快倒闭了，新文章好像 Google 都搜不到}{https://www.v2ex.com/t/1023036}

\entryitemGeneric{\hskip 0pt{}[奇思妙想] 基于蓝牙的多屏协同}{https://www.v2ex.com/t/1023035}

\entryitemGeneric{\hskip 0pt{}[Node.js] 请教 electron 调用 dll 报错的问题}{https://www.v2ex.com/t/1023034}

\entryitemGeneric{\hskip 0pt{}[分享创造] 为 jav 目录，用 rust tokio 写了个工具，可以清除一些 torrent 带的广告和规范视频名称}{https://www.v2ex.com/t/1023033}

\entryitemGeneric{\hskip 0pt{}[问与答] 推荐一款 esim 手机}{https://www.v2ex.com/t/1023032}

\entryitemGeneric{\hskip 0pt{}[Apple] macOS 被降频，从图中是不是基本可以判断出， mac 是被降频了。}{https://www.v2ex.com/t/1023031}

\entryitemGeneric{\hskip 0pt{}[职场话题] 双非一本计科大三败狗求大佬指点}{https://www.v2ex.com/t/1023030}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 能说说，大家用 api 调用 chatgpt 都用在什么地方？}{https://www.v2ex.com/t/1023029}

\entryitemGeneric{\hskip 0pt{}[Arc] Windows 版本 ARC 浏览器无法登录}{https://www.v2ex.com/t/1023028}

\entryitemGeneric{\hskip 0pt{}[问与答] USB-C 转千兆网口的适配器可以给手机充电吗？}{https://www.v2ex.com/t/1023027}

\entryitemGeneric{\hskip 0pt{}[程序员] 笔记本中南桥功效的板子坏了，某宝能买，但卖家说得换购，请教为什么要换购？}{https://www.v2ex.com/t/1023026}

\entryitemGeneric{\hskip 0pt{}[投资] 新人请教：试水美股， VOO 收益比不上国内券商 ETF 啊，问题在哪}{https://www.v2ex.com/t/1023025}

\entryitemGeneric{\hskip 0pt{}[Twitter] 老哥们现在推特还没有单个推文能设置成私密的选项吗？}{https://www.v2ex.com/t/1023023}

\entryitemGeneric{\hskip 0pt{}[程序员] 马来西亚能做个废物 IT 吗？}{https://www.v2ex.com/t/1023022}

\entryitemGeneric{\hskip 0pt{}[问与答] 高度近视广州配眼镜推荐网店还是实体店}{https://www.v2ex.com/t/1023021}

\entryitemGeneric{\hskip 0pt{}[分享发现] 分享一个 shiki magic move 的 playground}{https://www.v2ex.com/t/1023020}

\entryitemGeneric{\hskip 0pt{}[Surge] Surge iOS 新车， 3 车位等 2 位， 100 元/年}{https://www.v2ex.com/t/1023019}

\entryitemGeneric{\hskip 0pt{}[iCloud] 有没有好用的第三方软件访问 icloud}{https://www.v2ex.com/t/1023018}

\entryitemGeneric{\hskip 0pt{}[问与答] 为啥 emby 关闭服务器->转码->启用硬件加速,还是会自动转码?}{https://www.v2ex.com/t/1023017}

\entryitemGeneric{\hskip 0pt{}[macOS] Downie 怎么知道我用了 Little Snitch？}{https://www.v2ex.com/t/1023016}

\entryitemGeneric{\hskip 0pt{}[Apple] xdm 用 mac 的，有很多群晖 nas 里的视频文件不显示封面咋整， mp4 格式的}{https://www.v2ex.com/t/1023014}

\entryitemGeneric{\hskip 0pt{}[macOS] 越升级越离谱， Mbp 升级 14.4 出现问题了。}{https://www.v2ex.com/t/1023013}

\entryitemGeneric{\hskip 0pt{}[问与答] 分享一下曾经给我带来幸福感的东西}{https://www.v2ex.com/t/1023012}

\entryitemGeneric{\hskip 0pt{}[Apple] 请问一下， outlook 系邮箱大附件除了 onedrive 和网盘地址，还有什么方法发送？我看知乎上可以修改什么配置？}{https://www.v2ex.com/t/1023010}

\entryitemGeneric{\hskip 0pt{}[程序员] Java 自己写什么功能可以提升技术？}{https://www.v2ex.com/t/1023009}


\ipart{Generic News}
\ichapter{AP News}
\entryitemWithDescription{\hskip 0pt{}April's total solar eclipse is a month away. Here's why it's worth the watch and how to stay safe}{https://apnews.com/article/7bf41851855d2dd7dc7a63ac0e9b9c01}{The sun is about to pull another disappearing act across North America, turning day into night during a total solar eclipse. The peak spectacle on April 8 will last up to 4 minutes, 28 seconds in the path of total darkness --- twice as...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé's new album will be called `Act II: Cowboy Carter'}{https://apnews.com/article/d87c6a86bc5c5093ac233b18d1d373d6}{LOS ANGELES (AP) --- Beyoncé is full of surprises --- and on Tuesday, dropped yet another one. Her forthcoming album has a name: `Act II: Cowboy Carter.' The title was revealed on Bey's official website, along with details on a few...}

\entryitemWithDescription{\hskip 0pt{}Michigan man who was accidently shot in face with ghost gun sues manufacturer and former friend}{https://apnews.com/article/012cf03e79355419e3da9e5a181571e1}{A 19-year-old Michigan man who lost his right eye after being shot with a firearm made from a ghost gun kit filed a lawsuit Tuesday against his former best friend who accidently shot him and the Pennsylvania company that sold his friend...}

\entryitemWithDescription{\hskip 0pt{}Man, woman found dead after explosion destroys house in Pittsburgh area; cause under investigation}{https://apnews.com/article/f27af15aa896b436a333b7aaafb24bfb}{CRESCENT, Pa. (AP) --- Two people were found dead after an explosion that destroyed a house in the Pittsburgh area near the Ohio River, authorities said Tuesday. Allegheny County emergency dispatchers said the blast in Crescent Township...}

\entryitemWithDescription{\hskip 0pt{}Darryl Strawberry resting comfortably after heart attack, according to New York Mets}{https://apnews.com/article/002a53fd990e168734bfaa652260505a}{LAKE ST. LOUIS,. Mo. (AP) --- Former New York Mets and Yankees star Darryl Strawberry is recovering from a heart attack and is at SSM Health St. Joseph Hospital. Mets spokesman Jay Horwitz said Tuesday that Strawberry was stricken Monday...}

\entryitemWithDescription{\hskip 0pt{}Illinois police identify 5 people, including 3 children, killed when school bus, semitruck collide}{https://apnews.com/article/e7575f7b7c18f260da74fd8c064b28d9}{RUSHVILLE, Ill. (AP) --- Authorities have identified the five people killed in a fiery crash, including both drivers and three children, when a school bus and a semitruck collided along a highway in western Illinois. The eastbound bus...}

\entryitemWithDescription{\hskip 0pt{}A Russian military transport plane with 15 people on board has crashed on takeoff, officials say}{https://apnews.com/article/81b603d981618ba1fc8cb6cd012313a5}{MOSCOW (AP) --- A Russian military transport plane with 15 people on board crashed on Tuesday while taking off from an air base in western Russia, the Defense Ministry said. The ministry said the Il-76 aircraft with eight crew and seven...}

\entryitemWithDescription{\hskip 0pt{}Online influencer Andrew Tate detained in Romania, handed UK arrest warrant, his spokesperson says}{https://apnews.com/article/61697418a833bba10378bad7cbda5d76}{BUCHAREST, Romania (AP) --- Online influencer Andrew Tate was detained in Romania and handed an arrest warrant issued by British authorities, his spokesperson said Tuesday. Tate, 37, and his brother Tristan Tate were detained Monday...}

\entryitemWithDescription{\hskip 0pt{}Japanese animation studio founder Miyazaki isn't ready to retire just yet, after latest Oscar win}{https://apnews.com/article/f572248c232017f7e9e9801f9a0e2c0b}{TOKYO (AP) --- Ghibli, the Japanese studio that just won its second Oscar for feature animation for ``The Boy and The Heron,'' hasn't said yet what it plans next. But founder Hayao Miyazaki, who at 83 was the oldest director ever...}

\entryitemWithDescription{\hskip 0pt{}Libraries struggle to afford the demand for e-books, seek new state laws in fight with publishers}{https://apnews.com/article/5d494dbaee0961eea7eaac384b9f75d2}{HARTFORD, Conn. (AP) --- Whenever bestselling author Robin Cook releases a new medical thriller, the head of the public library in West Haven, Connecticut knows demand for digital copies will be high. So will the price. Like many...}

\entryitemWithDescription{\hskip 0pt{}Firefighters booed NY attorney general who prosecuted Trump. Officials are investigating}{https://apnews.com/article/6198bf96b01d5782cdcdc76b4a0be5ac}{NEW YORK (AP) --- A union representing New York City firefighters is raising concerns about possible disciplinary action against its members after state Attorney General Letitia James was booed and a pro-Donald Trump chant broke out...}

\entryitemWithDescription{\hskip 0pt{}Man bitten by a crocodile after falling off his boat at a Florida Everglades marina}{https://apnews.com/article/696c3b5c9791292b91f902638184ed27}{HOMESTEAD, Fla. (AP) --- A man visiting the Florida Everglades is recovering after being bitten by a crocodile after falling off a boat, officials said. The attack occurred Sunday afternoon at the Flamingo Marina in Everglades National...}

\entryitemWithDescription{\hskip 0pt{}3 children and 2 adults die after school bus collides with semi in Illinois, authorities say}{https://apnews.com/article/a79a75397e292ffe2def1eb49b546fa7}{RUSHVILLE, Ill. (AP) --- Five people, including three children, were killed Monday after a school bus and semitruck collided on a highway in western Illinois, authorities said. The bus was traveling eastbound on Illinois Route 24 when it...}\ichapter{Reuters}
\entryitemWithDescription{\hskip 0pt{}Japan's Space One counts down to inaugural Kairos rocket launch}{https://www.reuters.com/technology/space/japans-space-one-counts-down-inaugural-kairos-rocket-launch-2024-03-12/}{Japan\textquotesingle s Space One will launch its Kairos small rocket on its inaugural trip on Wednesday, in a bid to become the first private firm in the country to put a satellite in...}

\entryitemWithDescription{\hskip 0pt{}Biden-Netanyahu rift raises questions about US weapons to Israel}{https://www.reuters.com/world/biden-netanyahu-rift-raises-questions-about-us-weapons-israel-2024-03-12/}{A deepening rift between President Joe Biden and Israeli Prime Minister Benjamin Netanyahu over Gaza red lines has set up a potential showdown between the two leaders and raised questions about whether the U.S. might restrict military aid...}

\entryitemWithDescription{\hskip 0pt{}Exclusive: US, allies eye commercial maritime option for Gaza aid}{https://www.reuters.com/world/middle-east/us-allies-eye-commercial-maritime-option-gaza-aid-2024-03-12/}{The U.S. may urge partners and allies to fund a privately run operation to send aid by sea to Gaza that could begin before a much larger U.S. military effort, said three people familiar with the planning and a U.S...}

\entryitemWithDescription{\hskip 0pt{}View from a US military aid flight shows Gaza desolation}{https://www.reuters.com/world/middle-east/view-us-military-aid-flight-shows-gaza-desolation-2024-03-12/}{As a U.S C-130 aircraft flew over the Gaza Strip to drop food to people facing famine, there were few visible signs of life in the jumbled rubble of what was a bustling urban jungle before the Israel-Hamas...}

\entryitemWithDescription{\hskip 0pt{}Navalny aide Volkov attacked with hammer in Lithuania}{https://www.reuters.com/world/europe/navalnys-aide-volkov-was-attacked-with-hammer-navalnys-spokesperson-2024-03-12/}{Late Russian opposition leader Alexei Navalny\textquotesingle s long-time aide Leonid Volkov was assaulted with a hammer in the Lithuanian capitol Vilnius on Tuesday, former Navalny spokesperson Kira Yarmysh...}

\entryitemWithDescription{\hskip 0pt{}Man in Rio de Janeiro surrenders after holding 17 hostages on hijacked bus}{https://www.reuters.com/world/americas/man-hijacks-bus-rio-shoots-two-2024-03-12/}{Police in Brazil arrested a man on Tuesday after he hijacked a bus and shot two people at a bus station in Rio de Janeiro before holding 17 people hostage for about three...}

\entryitemWithDescription{\hskip 0pt{}UN uses new land route from Israel to reach northern Gaza}{https://www.reuters.com/world/middle-east/un-uses-new-land-route-israel-reach-northern-gaza-2024-03-12/}{The United Nations used a new land route on Tuesday to deliver food to northern Gaza for the first time in three weeks as global pressure grows on Israel to allow more access to the coastal enclave amid a looming...}

\entryitemWithDescription{\hskip 0pt{}Thousands protest in Slovakia against government's policy toward Russia}{https://www.reuters.com/world/europe/thousands-protest-slovakia-against-governments-policy-toward-russia-2024-03-12/}{Thousands of people took to the streets of Slovakia\textquotesingle s capital Bratislava on Tuesday to show support for Ukraine and protest against the Slovak government, which critics say has veered too close to...}

\entryitemWithDescription{\hskip 0pt{}EU clears path for 5 bln euro Ukraine military aid boost}{https://www.reuters.com/world/europe/eu-clears-path-5-bln-euro-ukraine-military-aid-boost-2024-03-12/}{European Union countries are close to a deal on a military aid fund for Ukraine that would pave the way for an injection of 5 billion euros (\$5.46 billion), diplomats said on...}

\entryitemWithDescription{\hskip 0pt{}Missile hits apartment buildings in Ukraine's Kryvyi Rih, 3 dead, 38 hurt}{https://www.reuters.com/world/europe/missile-hits-apartment-building-kryvyi-rih-two-dead-ukrainian-president-says-2024-03-12/}{A Russian missile slammed into two apartment buildings in the central Ukrainian city of Kryvyi Rih on Tuesday, killing three people and injuring at least 38, with rescue teams sifting through rubble late into the night in a search for...}

\entryitemWithDescription{\hskip 0pt{}Netanyahu says he will press forward with military campaign in Rafah}{https://www.reuters.com/world/middle-east/netanyahu-says-he-will-press-forward-with-military-campaign-rafah-2024-03-12/}{Israeli Prime Minister Benjamin Netanyahu said on Tuesday that Israel would press forward with its military campaign into Rafah in the southern Gaza Strip, amid rising international...}

\entryitemWithDescription{\hskip 0pt{}US, UN express concern about India's religion-based citizenship law}{https://www.reuters.com/world/us-un-express-concern-about-indias-religion-based-citizenship-law-2024-03-12/}{The U.S. government and the United Nations on Tuesday expressed concerns about a contentious religion-based citizenship law in India, with the UN calling the legislation "fundamentally discriminatory in...}

\entryitemWithDescription{\hskip 0pt{}US to send new weapons package worth \$300 million for Ukraine}{https://www.reuters.com/business/aerospace-defense/us-preparing-new-weapons-package-ukraine-officials-2024-03-12/}{The United States will send a new military aid package for Ukraine worth \$300 million, President Joe Biden\textquotesingle s administration said on Tuesday, the first such move in months as additional funds for Kyiv remain blocked by...}\ichapter{联合早报}
\entryitemWithDescription{杨丹旭：民营企业家的``爱国劫''}{https://www.zaobao.com/news/china/story20240313-3147370}{中国电动汽车巨头比亚迪的创始人王传福，近来成为又一位被推上舆论风口浪尖的中国企业家。 事缘松散汽车创始人张小雷近日在网上发布一条举报视频，爆料这名中国新能源汽车行业领军人物婚内出轨，不仅育有两个私生子女，而且还是美国籍……}

\entryitemWithDescription{农夫山泉舆论危机或冲击提振市场努力}{https://www.zaobao.com/news/china/story20240312-3147136}{有网民上周质疑农夫山泉旗下东方树叶的产品包装含有日本元素，批评其``不爱国''\,``媚日''，涉嫌辱华，要求下架。（互联网） 中国饮料巨头农夫山泉近期深陷舆论漩涡，创始人钟睒睒家族对中国的忠诚度受到不少网民质疑，引发一波抵制潮，拖累农夫山泉股价半个多月来重挫约6％……}

\entryitemWithDescription{学者：中国GDP一度突破美国的三分之二 不能怪美国担忧中国崛起}{https://www.zaobao.com/news/china/story20240312-3141999}{南洋理工大学经济学教授陈光炎3月8日在新加坡国立大学李光耀公共政策学院亚洲竞争力研究所2024年度研究会议上，分析中美博弈对本区域造成的冲击。（亚洲竞争力研究所提供） ``如果我是白宫首席战略师，我可能制定比拜登政府还更大规模的（对华）措施……}

\entryitemWithDescription{港立会前主席：不是所有境外势力都是魔鬼}{https://www.zaobao.com/news/china/story20240312-3146791}{（香港讯）香港立法会前主席曾钰成星期二指出，不是所有``境外势力''都是魔鬼，跟境外势力合作做正当合法的事，不会构成``境外干预罪''。 曾钰成星期二（3月12日）在《明报》撰文，评论香港特区政府上周五提交立法会审议的《维护国家安全条例草案》。 他指出，在条例草案下构成境外干预罪的元素，即``意图带来干预效果，而配合境外势力作出某项作为''，以及``作出该项作为时，使用不当手段''……}

\entryitemWithDescription{广州市区汽车与行人电动脚踏车碰撞11伤}{https://www.zaobao.com/news/china/story20240312-3146896}{（广州综合讯）中国广东省广州市星期二发生汽车与行人和电动脚踏车碰撞，造成11人受伤，涉事司机被警方控制。 广州市公安局交通警察支队星期二（3月12日）通报，一辆小汽车当天上午9时许，先后在广州市越秀区中山四路、广仁路与行人和电动自行车发生碰撞，造成11人受伤。 警方接报后，迅速派警员到场处置，并协助将伤者送医院救治。目前，49岁肇事男司机黄某已被警方控制，事故仍在进一步调查处置中……}

\entryitemWithDescription{中国空军副司令证实轰20即将面世 专家预计航程至少可飞8000公里}{https://www.zaobao.com/news/china/story20240312-3145269}{（香港综合讯）中国空军副司令员王伟近日证实，中国自主研发的新一代战略轰炸机``轰20''即将面世。军事专家分析，轰20的航程预计至少有8000公里，最高航程可达10000公里以上。 王伟星期天（3月10日）在北京出席全国两会（全国人大、政协年会）期间，被《香港商报》问及轰20何时能对外公布时说：``快了，你们等着吧。''报道称，这是中国官方首次证实轰20的真实存在……}

\entryitemWithDescription{在野立委联手成立``镜电视申设及后续弊案争议''调阅专案小组}{https://www.zaobao.com/news/china/story20240311-3142092}{台湾在野的国民党和民众党立法委员，星期一（3月11日）在立法院交通委员会以6比5的表决结果，决议成立``镜电视申设及后续弊案争议''调阅专案小组，并谴责国家通讯传播委员会（NCC）主任委员陈耀祥业务报告极尽敷衍，严重藐视立法院。 NCC于会后发布新闻稿强调，NCC组织法规定，该会委员应超出党派以外，独立行使职权……}

\entryitemWithDescription{中国官方首度称杨恒均可能不会处决}{https://www.zaobao.com/news/china/story20240311-3142031}{中国驻澳大使肖千星期一（3月11日）首度公开表态称杨恒均可能不会被处决。（杨恒均X平台（前称推特）账号） 澳大利亚籍华裔作家杨恒均今年2月被北京法院判处死缓，可能阻碍中澳进一步修复双边关系之际，中国驻澳大使肖千首度公开表态称杨恒均可能不会被处决。肖千也透露中国对澳洲葡萄酒关税的审查进展良好，暗示两国贸易纠纷有望完全落幕……}

\entryitemWithDescription{两会对台论述显示和统仍是首要目标}{https://www.zaobao.com/news/china/story20240311-3140807}{这次两会期间，不论是中国国务院总理李强（左）或全国政协主席王沪宁（右），对台相关论述都较以往简短。（路透社） 中国全国两会（人大、政协年会）星期一（3月11日）正式落幕。台湾学者受访时分析，这次两会的对台论述看不出新要求，可以确定``和平统一''仍是首要目标。不过随着北京``说少做多''趋势日渐明显，未来藉由两会观察对台政策的难度会上升……}

\entryitemWithDescription{港行会成员：在家存放《苹果日报》是否违法要看意图}{https://www.zaobao.com/news/china/story20240311-3141273}{（香港综合讯）香港特区行政会议成员称，《基本法》第23条立法后，港人在家存放《苹果日报》是否违法，将取决于此举的意图。 据网媒``香港01''星期一（3月11日）报道，作为行会成员的资深律师汤家骅，就市民在家中存放《苹果日报》是否会构成管有煽动刊物罪行做出回应时说，这种行为本身不是犯法，但要看是否有犯罪意图。 汤家骅举例称，如果市民把报纸放在床下留纪念，闲来自己阅读，并无犯罪意图……}

\entryitemWithDescription{美指中国起重机威胁港口安全 上海振华重工否认构成风险}{https://www.zaobao.com/news/china/story20240311-3140935}{美国指中国制造起重机对国家安全构成风险，对此，中国制造商上海振华重工回应否认其起重机构成网络安全风险。图为位于美国加利福尼亚州奥克兰港的上海振华重工供应起重机。（法新社） （上海／华盛顿综合讯）美国指中国制造的起重机对国家安全构成风险，将更换在美所有港口的中国造起重机。中国制造商上海振华重工回应称，其起重机不会对任何港口构成网络安全风险……}

\entryitemWithDescription{福建舰甲板涂装完成逾七成 中国首艘电磁弹射航母即将海试}{https://www.zaobao.com/news/china/story20240311-3140056}{最近网上传出的空照图片显示，仍在进行系泊试验的福建舰，飞行甲板涂装已完成超过七成，预计很快就会进行首次海试。（互联网） （香港讯）最近传出的空中俯拍照片显示，仍在进行系泊试验的中国首艘电磁弹射航空母舰``福建号''，其飞行甲板涂装已完成逾70\%，预计很快就会进行首次海试，中国海军距离``三航母时代''为期不远……}

\entryitemWithDescription{于泽远：TikTok又悬了？}{https://www.zaobao.com/news/china/story20240311-3136397}{就在中国忙于召开两会之际，美国又对TikTok出手了。这次出手来自美国国会，总统拜登3月9日也明确表态，如果国会通过制裁TikTok的法案，他将签署执行。 这项法案来得比较突然……}

\entryitemWithDescription{曹忠明出任中国驻新加坡大使 预计本月底履新}{https://www.zaobao.com/news/china/story20240310-3135781}{中国驻比利时原大使曹忠明将出任中国驻新加坡大使，预计将在本月底前履新。 （中国驻比利时大使馆官网） 中国驻比利时原大使曹忠明将出任中国驻新加坡大使，预计于本月底履新。 上一任中国驻新加坡大使孙海燕去年7月底卸任返回中国后，中国驻新加坡大使的职位一直悬空至今。据《联合早报》了解，曹忠明将接任，他的新职务近日已确定。 曹忠明此前是中国驻比利时大使……}

\entryitemWithDescription{仅访基辅半天 官方罕见未提李辉表态发言}{https://www.zaobao.com/news/china/story20240310-3137032}{中国政府欧亚事务特别代表李辉上星期四（3月7日）抵达基辅访问。中国外交部在李辉访乌后罕见未提供他在当地的任何表态发言。（路透社档案图） 中国政府欧亚事务特别代表李辉上周抵达基辅访问，仅短暂停留半天，比他10个月前访问乌克兰两天时间大幅缩短，此行也未获乌国总统泽连斯基会见。中国外交部在李辉访乌后以``坦诚友好''简短形容此访，但罕见未提供李辉在当地的任何表态发言……}

\entryitemWithDescription{贵州大数据中心创始人刘东昊因意外离世}{https://www.zaobao.com/news/china/story20240310-3136779}{贵州大数据安全工程研究中心创始人刘东昊3月5日因意外离世。（互联网） （贵州综合讯）贵州大数据安全工程研究中心创始人刘东昊因意外离世。 ``大数据安全工程研究中心''公众号星期六（3月9日）发布讣告，研究中心创始人、理事会秘书长刘东昊，因意外于3月5日离世。讣告未透露意外细节。 公开资料显示，刘东昊曾任贵州大数据安全工程研究中心常务副主任、大数据协同安全技术国家工程研究中心贵州分中心主任等职务……}

\entryitemWithDescription{``港车北上''突破50万辆次 港人北上消费成风尚}{https://www.zaobao.com/news/china/story20240310-3136729}{港珠澳大桥边检站星期天公（3月10日）布，截至3月9日，经该站查验的出入境香港单牌车数量已突破50万辆次。（中新社） （香港综合讯）今年2月``港车北上''数量首次超过单月10万辆次，累计已突破50万辆次。 自去年7月1日``港车北上''政策正式实施以来，驾驶单牌私家车北上中国大陆的香港居民数量持续上升……}

\entryitemWithDescription{中国两会期间加强网络管控 军方发短片普及翻墙违法}{https://www.zaobao.com/news/china/story20240310-3136587}{中国军方两会期间发布普及``翻墙''违法的宣传片，但因为内容过于详细被指像``翻墙教学片''。（视频截图） （北京综合讯）中国官方据报在今年两会（全国人大、政协年会）期间加大了网络管控力度。中国军方也在此期间发布普及``翻墙''违法的宣传片，但因为内容过于详细被指像``翻墙教学片''……}