\entryitemWithDescription{\hskip 0pt{}April's total solar eclipse is a month away. Here's why it's worth the watch and how to stay safe}{https://apnews.com/article/7bf41851855d2dd7dc7a63ac0e9b9c01}{The sun is about to pull another disappearing act across North America, turning day into night during a total solar eclipse. The peak spectacle on April 8 will last up to 4 minutes, 28 seconds in the path of total darkness --- twice as...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé's new album will be called `Act II: Cowboy Carter'}{https://apnews.com/article/d87c6a86bc5c5093ac233b18d1d373d6}{LOS ANGELES (AP) --- Beyoncé is full of surprises --- and on Tuesday, dropped yet another one. Her forthcoming album has a name: `Act II: Cowboy Carter.' The title was revealed on Bey's official website, along with details on a few...}

\entryitemWithDescription{\hskip 0pt{}Michigan man who was accidently shot in face with ghost gun sues manufacturer and former friend}{https://apnews.com/article/012cf03e79355419e3da9e5a181571e1}{A 19-year-old Michigan man who lost his right eye after being shot with a firearm made from a ghost gun kit filed a lawsuit Tuesday against his former best friend who accidently shot him and the Pennsylvania company that sold his friend...}

\entryitemWithDescription{\hskip 0pt{}Man, woman found dead after explosion destroys house in Pittsburgh area; cause under investigation}{https://apnews.com/article/f27af15aa896b436a333b7aaafb24bfb}{CRESCENT, Pa. (AP) --- Two people were found dead after an explosion that destroyed a house in the Pittsburgh area near the Ohio River, authorities said Tuesday. Allegheny County emergency dispatchers said the blast in Crescent Township...}

\entryitemWithDescription{\hskip 0pt{}Darryl Strawberry resting comfortably after heart attack, according to New York Mets}{https://apnews.com/article/002a53fd990e168734bfaa652260505a}{LAKE ST. LOUIS,. Mo. (AP) --- Former New York Mets and Yankees star Darryl Strawberry is recovering from a heart attack and is at SSM Health St. Joseph Hospital. Mets spokesman Jay Horwitz said Tuesday that Strawberry was stricken Monday...}

\entryitemWithDescription{\hskip 0pt{}Illinois police identify 5 people, including 3 children, killed when school bus, semitruck collide}{https://apnews.com/article/e7575f7b7c18f260da74fd8c064b28d9}{RUSHVILLE, Ill. (AP) --- Authorities have identified the five people killed in a fiery crash, including both drivers and three children, when a school bus and a semitruck collided along a highway in western Illinois. The eastbound bus...}

\entryitemWithDescription{\hskip 0pt{}A Russian military transport plane with 15 people on board has crashed on takeoff, officials say}{https://apnews.com/article/81b603d981618ba1fc8cb6cd012313a5}{MOSCOW (AP) --- A Russian military transport plane with 15 people on board crashed on Tuesday while taking off from an air base in western Russia, the Defense Ministry said. The ministry said the Il-76 aircraft with eight crew and seven...}

\entryitemWithDescription{\hskip 0pt{}Online influencer Andrew Tate detained in Romania, handed UK arrest warrant, his spokesperson says}{https://apnews.com/article/61697418a833bba10378bad7cbda5d76}{BUCHAREST, Romania (AP) --- Online influencer Andrew Tate was detained in Romania and handed an arrest warrant issued by British authorities, his spokesperson said Tuesday. Tate, 37, and his brother Tristan Tate were detained Monday...}

\entryitemWithDescription{\hskip 0pt{}Japanese animation studio founder Miyazaki isn't ready to retire just yet, after latest Oscar win}{https://apnews.com/article/f572248c232017f7e9e9801f9a0e2c0b}{TOKYO (AP) --- Ghibli, the Japanese studio that just won its second Oscar for feature animation for ``The Boy and The Heron,'' hasn't said yet what it plans next. But founder Hayao Miyazaki, who at 83 was the oldest director ever...}

\entryitemWithDescription{\hskip 0pt{}Libraries struggle to afford the demand for e-books, seek new state laws in fight with publishers}{https://apnews.com/article/5d494dbaee0961eea7eaac384b9f75d2}{HARTFORD, Conn. (AP) --- Whenever bestselling author Robin Cook releases a new medical thriller, the head of the public library in West Haven, Connecticut knows demand for digital copies will be high. So will the price. Like many...}

\entryitemWithDescription{\hskip 0pt{}Firefighters booed NY attorney general who prosecuted Trump. Officials are investigating}{https://apnews.com/article/6198bf96b01d5782cdcdc76b4a0be5ac}{NEW YORK (AP) --- A union representing New York City firefighters is raising concerns about possible disciplinary action against its members after state Attorney General Letitia James was booed and a pro-Donald Trump chant broke out...}

\entryitemWithDescription{\hskip 0pt{}Man bitten by a crocodile after falling off his boat at a Florida Everglades marina}{https://apnews.com/article/696c3b5c9791292b91f902638184ed27}{HOMESTEAD, Fla. (AP) --- A man visiting the Florida Everglades is recovering after being bitten by a crocodile after falling off a boat, officials said. The attack occurred Sunday afternoon at the Flamingo Marina in Everglades National...}

\entryitemWithDescription{\hskip 0pt{}3 children and 2 adults die after school bus collides with semi in Illinois, authorities say}{https://apnews.com/article/a79a75397e292ffe2def1eb49b546fa7}{RUSHVILLE, Ill. (AP) --- Five people, including three children, were killed Monday after a school bus and semitruck collided on a highway in western Illinois, authorities said. The bus was traveling eastbound on Illinois Route 24 when it...}