\entryitemWithDescription{\hskip 0pt{}Utah scraps untested lethal drug combination for man's August execution}{https://apnews.com/article/c742fd2dd99daa7611157fbc24155776}{Utah officials said Saturday that they are scrapping plans to use an untested lethal drug combination in next month's planned execution of a man in a 1998 murder case. They will instead seek out a drug that's been used previously in...}

\entryitemWithDescription{\hskip 0pt{}A fire severely damages the historic First Baptist Dallas church sanctuary}{https://apnews.com/article/f5559a87624a833944e4f3564f02de2f}{A fire all but destroyed the historic church sanctuary at First Baptist Dallas, sending smoke billowing over the city but causing no deaths or injuries, Dallas firefighters said. The fire in the Texas Historic Landmark, a Victorian-style...}

\entryitemWithDescription{\hskip 0pt{}Remnants of lives interrupted by war half a century ago captured in Cyprus' buffer zone}{https://apnews.com/article/84aaf7f59954edee3442a4b021d2d122}{NICOSIA, Cyprus (AP) --- A rickety piano leans crookedly against a peeling apartment wall, pots and pans filled with dust rest on a stove that has seen much better days and a book, its pages turning yellow with time, lies open next to a...}

\entryitemWithDescription{\hskip 0pt{}Disneyland workers authorize potential strike ahead of continued contract negotiations}{https://apnews.com/article/11b477abf4a84d1e0af6c1186810dfa5}{NEW YORK (AP) --- Thousands of workers at Disney's theme park and resort properties in California voted late Friday to authorize a potential strike, as contract negotiations drag on. The strike authorization was approved by an...}

\entryitemWithDescription{\hskip 0pt{}Longtime US Rep Sheila Jackson Lee of Texas, who had pancreatic cancer, has died}{https://apnews.com/article/b2de57de41d39053a7648b16438eb009}{Longtime U.S. Rep. Sheila Jackson Lee of Texas, who helped lead federal efforts to protect women from domestic violence and recognize Juneteenth as a national holiday, has died. She was 74. Lillie Conley, her chief of staff, confirmed...}

\entryitemWithDescription{\hskip 0pt{}NFL Hall of Famer Lawrence Taylor charged with failing to update address on sex offender registry}{https://apnews.com/article/152a808ded5b29e5ea71b6110bd5209d}{FORT LAUDERDALE, Fla. (AP) --- NFL Hall of Fame linebacker Lawrence Taylor was charged in Florida with failing to update his address on the state's sex offender registry, according to court records. The former New York Giants linebacker...}

\entryitemWithDescription{\hskip 0pt{}A man kills a grizzly bear in Montana after it attacks while he is picking berries}{https://apnews.com/article/1a999b1f05ebc996d92c2925b27baf22}{A man picking huckleberries in Montana shot and killed a grizzly bear after it attacked and injured him badly enough that he had to be hospitalized. The 72-year-old man was alone when the adult female charged him Thursday. He killed the...}

\entryitemWithDescription{\hskip 0pt{}Utah State says Blake Anderson fired for interviewing potential victim after Aggies player's arrest}{https://apnews.com/article/230f4b425f0e5d33dcaed51f36814878}{Utah State's Blake Anderson was fired for contacting a potential domestic violence victim and a witness to the incident after an Aggies football player was arrested, and failing to properly report the case, according to a termination...}

\entryitemWithDescription{\hskip 0pt{}Italian judge orders a journalist to pay 5,000 euros in damages for making fun of Meloni's height}{https://apnews.com/article/fabb0daa40941a86f17cb1bc1889c18c}{ROME (AP) --- A judge in Milan has ordered an Italian journalist to pay 5,000 euros (nearly \$5,500) in damages to Premier Giorgia Meloni for making fun of her height in social media posts. The judge ruled on Wednesday that two social...}

\entryitemWithDescription{\hskip 0pt{}Harvey Weinstein due in NYC courtroom for hearing tied to upcoming retrial}{https://apnews.com/article/9f193bd6d55b829b6342ef948f31cc8e}{NEW YORK (AP) --- Harvey Weinstein is scheduled to appear in a New York court Friday ahead of a planned retrial on rape and sexual assault charges. The former Hollywood movie mogul's pretrial hearing in Manhattan criminal court will...}

\entryitemWithDescription{\hskip 0pt{}University of Florida president Ben Sasse is resigning after his wife was diagnosed with epilepsy}{https://apnews.com/article/d75ec128949376dafab5ff8a5160f186}{ORLANDO, Fla. (AP) --- University of Florida president Ben Sasse, a controversial pick almost two years ago when he was named to lead one of the top public universities in the U.S., plans to leave his position to focus on taking care of...}

\entryitemWithDescription{\hskip 0pt{}Lou Dobbs, conservative pundit and longtime cable TV host for Fox Business and CNN, dies at 78}{https://apnews.com/article/76c799df42c6b7d4912dece5d180b2de}{NEW YORK (AP) --- Lou Dobbs, the conservative political pundit and veteran cable TV host who was a founding anchor for CNN and later was a nightly presence on Fox Business Network for more than a decade, has died. He was 78. His death was...}

\entryitemWithDescription{\hskip 0pt{}Shannen Doherty finalizes divorce hours before death}{https://apnews.com/article/0d9fbb475ae64fed1ccdc0a03eb69cf6}{LOS ANGELES (AP) --- Shannen Doherty finalized her split with husband, Kurt Iswarienko, just hours before her death at age 53, and she was granted a rare posthumous divorce two days later. Doherty, the star of ``Beverly Hills, 90210''...}