\entryitemWithDescription{\hskip 0pt{}NASA still deciding whether to keep 2 astronauts at space station until next year}{https://apnews.com/article/fc25e891987113206965b4e00681f525}{CAPE CANAVERAL, Fla. (AP) --- NASA said Wednesday it's still deciding whether to keep two astronauts at the International Space Station until early next year and send their troubled Boeing capsule back empty. Rather than flying Boeing's...}

\entryitemWithDescription{\hskip 0pt{}The paint is dry on Banksy's animal-themed street art that appeared across London over 9 days}{https://apnews.com/article/81bcf598437277c421544cd6d053a55c}{LONDON (AP) --- On the 10th day, after creating the mountain goat, elephants, pelicans, a rhinoceros and a gorilla, among other animals, Banksy rested. The elusive street artist's menagerie that appeared around London over nine...}

\entryitemWithDescription{\hskip 0pt{}Madonna to celebrate 66th birthday with a visit to the famed archaeological site at Pompeii}{https://apnews.com/article/4d8af2c873fb834817a4a96506c025ca}{ROME (AP) --- Madonna will celebrate her 66th birthday with a private evening tour of the famed Italian archaeological site at Pompeii, officials said. Naples Prefect Michele Di Bari denied Italian media speculation the singer was...}

\entryitemWithDescription{\hskip 0pt{}Victoria's Secret bringing in Hillary Super from Savage X Fenty as its new CEO}{https://apnews.com/article/1b34d28f8a51704592f3cca5d7bbdc17}{Victoria's Secret is making a change at the top, naming Hillary Super from Savage X Fenty as its new chief executive. Super will take over for Martin Waters, effective Sept. 9. Waters became CEO of Victoria's Secret in 2021. He will serve...}

\entryitemWithDescription{\hskip 0pt{}Rocked by cancellation of Vienna concerts, Swifties shake it off and flock to London}{https://apnews.com/article/7f4877fc2ba7b477a2ca601ad8f67a8a}{LONDON (AP) --- For Herve Tram, being a Taylor Swift fan isn't just about the music. The 28-year-old computer network engineer from Paris sees himself as part of a community, one of the Swifties as they are known. So when the pop...}

\entryitemWithDescription{\hskip 0pt{}Mars, maker of M\&M's and Snickers, to buy Cheez-It owner Kellanova for nearly \$30 billion}{https://apnews.com/article/b47c6906bea9c285c2a94711a543f6c7}{Mars, whose brands include M\&M's, Snickers and Skittles, is buying food company Kellanova in a deal worth nearly \$30 billion, giving it access to a huge portfolio of consumer brands from Cheez-It to Pop-Tarts. Kellanova was created when...}

\entryitemWithDescription{\hskip 0pt{}Japanese are worried and confused after first-ever megaquake advisory. What does it mean?}{https://apnews.com/article/c6c73431f51204089548ed660265d00c}{TOKYO (AP) --- Japan, one of the most earthquake-prone nations on earth, issued its first-ever ``megaquake advisory'' last week after a powerful quake struck off the southeastern coast of the southern main island of Kyushu. The magnitude...}

\entryitemWithDescription{\hskip 0pt{}Wyoming reporter caught using artificial intelligence to create fake quotes and stories}{https://apnews.com/article/ed076e2f276d9811f3b9ba051a03b7ae}{HELENA, Mont. (AP) --- A quote from Wyoming's governor and a local prosecutor were the first things that seemed slightly off to Powell Tribune reporter CJ Baker. Then, it was some of the phrases in the stories that struck him as nearly...}

\entryitemWithDescription{\hskip 0pt{}New Zealand food bank distributes candy made from a potentially lethal amount of methamphetamine}{https://apnews.com/article/4c31e29562cbf825ecfe82a48a0301ec}{WELLINGTON, New Zealand (AP) --- A charity working with homeless people in Auckland, New Zealand unknowingly distributed candies filled with a potentially lethal dose of methamphetamine in its food parcels after the sweets were donated by...}

\entryitemWithDescription{\hskip 0pt{}There's an apostrophe battle brewing among grammar nerds. Is it Harris' or Harris's?}{https://apnews.com/article/967c0bbefc09be6c804588daabed7ec9}{Whatever possessed Vice President Kamala Harris to pick Minnesota Gov. Tim Walz as her running mate, it probably wasn't a desire to inflame arguments about apostrophes. But it doesn't take much to get grammar nerds fired up. ``The lower...}

\entryitemWithDescription{\hskip 0pt{}Ford, Mazda warn owners to stop driving older vehicles with dangerous Takata air bag inflators}{https://apnews.com/article/3eb0b90b47c9d1417c15704db0b99f80}{DETROIT (AP) --- Ford and Mazda are warning the owners of more than 475,000 older vehicles in the U.S. not to drive them because they have dangerous Takata air bag inflators that have not been replaced. The warning issued Tuesday covers...}

\entryitemWithDescription{\hskip 0pt{}A burglary is reported at a Trump campaign office in Virginia}{https://apnews.com/article/073d9a821f1f2e58898126760ec5ff42}{ASHBURN, Va. (AP) --- A burglary was reported over the weekend at a Virginia campaign office for former President Donald Trump, and authorities are investigating whether anything was stolen. It happened Sunday at an office in Ashburn...}

\entryitemWithDescription{\hskip 0pt{}Arkansas officer fired after being caught on video beating inmate in back of patrol car}{https://apnews.com/article/94c962a1ba5f9b8b276ef00aee5c5424}{LITTLE ROCK, Ark. (AP) --- An Arkansas police officer has been fired after he was caught on video beating a handcuffed inmate in the back of his patrol car, and the police chief says he will refer the case to prosecutors. Jonesboro Police...}