\entryitemWithDescription{\hskip 0pt{}Judge says Alec Baldwin settlement in fatal shooting sealed}{https://apnews.com/article/eaca29be17620e099b27dde750f7cadf}{FILE - This aerial photo shows the movie set of "Rust" at Bonanza Creek Ranch in Santa Fe, N.M., on Saturday, Oct. 23, 2021. A judge is scheduled to resolve a weapons-related charge against a codefendant in the case against Alec Baldwin...}

\entryitemWithDescription{\hskip 0pt{}Odd spiral appears amid northern lights in Alaska night sky}{https://apnews.com/article/90e767058f328bb95bab62c3f5bed1cc}{In this photo provided by Christopher Hayden, a light baby blue spiral resembling a galaxy appears amid the aurora for a few minutes in the Alaska skies near Fairbanks, Saturday, April 15, 2023. The spiral was formed when excess fuel that...}

\entryitemWithDescription{\hskip 0pt{}Fugees rapper in political conspiracy trial launches defense}{https://apnews.com/article/6b473e98cd0531027e6773b6e3afb68b}{FILE - Prakazrel "Pras" Michel, left, a member of the 1990s hip-hop group the Fugees, accompanied by defense lawyer David Kenner, right, arrives at federal court for his trial in an alleged campaign finance conspiracy, Thursday, March 30...}

\entryitemWithDescription{\hskip 0pt{}CBC 'pausing' Twitter after 'government-funded media' label}{https://apnews.com/article/41bfb23aaea84c65c682f52fb5c3fd59}{FILE - A Twitter logo hangs outside the company\textquotesingle s offices in San Francisco, on Dec. 19, 2022. The Canadian Broadcasting Corporation paused its use of Twitter on Monday, April 17, 2023, after the social media platform owned...}

\entryitemWithDescription{\hskip 0pt{}Ben \& Jerry's workers announce plan to unionize in Vermont}{https://apnews.com/article/f42250e98d4f38c115c2041f7799988e}{The front of the Ben Jerry\textquotesingle s ice cream shop in Burlington, Vt., on Monday April 17, 2023. About 40 workers at the shop near where the company was founded announced Monday they were seeking to form a union. (AP Photo/Wilson...}

\entryitemWithDescription{\hskip 0pt{}Boy, 13, gets stuck climbing into claw machine for prize}{https://apnews.com/article/980d735bfad47a1df0945085d2692125}{CHARLOTTE, N.C. (AP) --- A 13-year-old boy had to be freed from a claw machine after he climbed inside hoping to score a prize, according to an official at a North Carolina amusement park. Carowinds officials were alerted just before 2 p...}

\entryitemWithDescription{\hskip 0pt{}Chauvin murder conviction upheld in George Floyd killing}{https://apnews.com/article/6941a6074dcc310c85e4f3eab2be97eb}{FILE In this image taken from video, former Minneapolis police Officer Derek Chauvin addresses the court at the Hennepin County Courthouse on June 25, 2021, in Minneapolis. The Minnesota Court of Appeals on Monday, April 17, 2023 upheld...}

\entryitemWithDescription{\hskip 0pt{}Hug, Scaroni take Boston Marathon wheelchair titles}{https://apnews.com/article/a2bedc95cc43597f3f6998b22aa74746}{Marcel Hug, of Switzerland, breaks the tape to win the men\textquotesingle s wheelchair division of the Boston Marathon, Monday, April 17, 2023, in Boston. (AP Photo/Charles Krupa) BOSTON (AP) --- A familiar name returned to the top of...}

\entryitemWithDescription{\hskip 0pt{}Minnesota is latest to settle with e-cigarette maker Juul}{https://apnews.com/article/7689e69ca87a2ee2354d155eb4a11165}{FILE - Minnesota Attorney General Keith Ellison speaks at a news conference at the State Capitol on Dec. 4, 2019, in St. Paul, Minn. Minnesota announced a settlement Monday, April 17, 2023 in its lawsuit against Juul Labs and tobacco...}

\entryitemWithDescription{\hskip 0pt{}David's Bridal files for bankruptcy, but your order is safe}{https://apnews.com/article/ace0eadbedadc97337b8c50213e73bca}{FILE - The David\textquotesingle s Bridal shop is shown Nov. 19, 2018, in Tampa, Fla. David's Bridal filed for bankruptcy protection Monday, April 17, 2023 the second time that the firm has sought such protection in the last five years...}

\entryitemWithDescription{\hskip 0pt{}SpaceX calls off 1st launch attempt of giant rocket in Texas}{https://apnews.com/article/c22f4b7dc476c6ca2d44522a2f9b68a5}{Children play in the waves with SpaceX\textquotesingle s Starship in the background in South Padre Island, Texas, Monday, April 17, 2023. SpaceX postponed the launch because of a problem with the first-stage booster. No people or...}

\entryitemWithDescription{\hskip 0pt{}Malala Yousafzai working on new book, her 'most personal'}{https://apnews.com/article/e9e140120b7aa1d3aa6c3e935bad0187}{FILE - Malala Yousafzai arrives at HISTORYTalks on Sept. 24, 2022, at DAR Constitution Hall in Washington. Yousafzai, a Nobel laureate, is working on a new memoir, the latest book by the young activist from Pakistan known for her advocacy...}

\entryitemWithDescription{\hskip 0pt{}While some students skip college, trade programs are booming}{https://apnews.com/article/075d7e7e2b0dc659920a9be6d054c8b2}{Tennessee College of Applied Technology Nashville student Abbey Carlson poses during welding class Wednesday, April 13, 2023, in Nashville, Tenn. While almost every sector of higher education is seeing fewer students registering for...}