\entryitemWithDescription{\hskip 0pt{}Young gymnast among 3 killed in shootings near Orlando}{https://apnews.com/article/bf21d5531c82f06be59d0fa1ed3cd5dc}{A person sits in front of the pop-up memorial for slain Spectrum News 13 journalist Dylan Lyons at the University of Central Florida Nicholson School of Communications in Orlando, Fla., Thursday, Feb. 23, 2023. Lyons, a graduate of UCF...}

\entryitemWithDescription{\hskip 0pt{}University to raze house where Idaho students were killed}{https://apnews.com/article/880b83391a0b356e4c97d9571feba4d9}{FILE - Bare spots are seen on Nov. 29, 2022, in the snowy parking lot in front of the home where four University of Idaho students were found dead on Nov. 13, in Moscow, Idaho, after vehicles belonging to the victims and others were towed...}

\entryitemWithDescription{\hskip 0pt{}E-bike batteries blamed for 22 NYC fires, 2 deaths this year}{https://apnews.com/article/73d9e56037996f137a4fb5475ff8c7f5}{FILE - A delivery worker rides his electric bicycle past the New York Stock Exchange, March 16, 2020, in New York.Lithium ion batteries used to power electric bicycles and scooters have already sparked 22 fires that caused 36 injuries and...}

\entryitemWithDescription{\hskip 0pt{}Did dioxins spread after the Ohio train derailment?}{https://apnews.com/article/ea75d5991f9529dc83a911297a07bb7a}{FILE - A plume rises over East Palestine, Ohio, as a result of the controlled detonation of a portion of the derailed Norfolk Southern trains, Feb. 6, 2023. After the catastrophic train car derailment in East Palestine, Ohio, some...}

\entryitemWithDescription{\hskip 0pt{}Navajo community wins fight to replace crumbling campus}{https://apnews.com/article/94f79d1103f17a60670b8706f70f7bac}{This Feb. 17, 2023 image shows a wall of sandbags protecting the school in the Navajo community of To\textquotesingle Hajiilee, New Mexico. To\textquotesingle Hajiilee Community School is just one of dozens funded by the U.S. Bureau of...}

\entryitemWithDescription{\hskip 0pt{}Court proceedings advance in deadly shooting on film set}{https://apnews.com/article/23d7a32e0c7c01878c51b55780ffefd8}{FILE - This aerial photo shows the movie set of "Rust" at Bonanza Creek Ranch in Santa Fe, N.M., on Oct. 23, 2021. Prosecutors have dropped the possibility of a sentence enhancement that could have carried a mandatory five-year sentence...}

\entryitemWithDescription{\hskip 0pt{}The AP Interview: Biden ready to run, US first lady says}{https://apnews.com/article/1659403d211d40212abbfef3b9847491}{First Lady of the United States Jill Biden speaks during an interview with Associated Press White House reporter Darlene Superville in Nairobi, Kenya, Friday, Feb. 24, 2023. Biden told The Associated Press in the exclusive interview that...}

\entryitemWithDescription{\hskip 0pt{}US Navy applies lessons from costly shipbuilding mistakes}{https://apnews.com/article/7798de1cdb622f7771dd6bfd23c02124}{FILE --- Welder Neal Larsen works on the hull of a Zumwalt-class destroyer Aug. 29, 2018, being built in the shipyard at Bath Iron Works in Bath, Maine. The U.S. Navy, following costly lessons after cramming too much new technology onto...}

\entryitemWithDescription{\hskip 0pt{}Q\&A: Austin Butler on what 'Elvis' taught him about fear}{https://apnews.com/article/bddde01cde0f50d1e39c963dd45d7a66}{Austin Butler poses for a portrait at the 95th Academy Awards Nominees Luncheon on Monday, Feb. 13, 2023, at the Beverly Hilton Hotel in Beverly Hills, Calif. (AP Photo/Chris Pizzello) Austin Butler, you may have heard, has taken a bit of...}

\entryitemWithDescription{\hskip 0pt{}Prosecutor: Alex Murdaugh 'fuzzy' about new details of case}{https://apnews.com/article/381d8e4ffe0b6848308f4c7335da218e}{Defendant Alex Murdaugh is cross examined by prosecutor Creighton Waters while testifying during his murder trial at the Colleton County Courthouse in Walterboro, S.C., Friday, Feb. 24, 2023. The 54-year-old attorney is standing trial on...}

\entryitemWithDescription{\hskip 0pt{}Key US inflation measure surges at fastest rate since June}{https://apnews.com/article/9b044c8ada5aa538d539237be1da9d14}{Customers walk around the Walmart Supercenter, Thursday, Feb. 9, 2023, in North Bergen, N.J. On Friday, the Commerce Department issues its January report on consumer spending. (AP Photo/Eduardo Munoz Alvarez) WASHINGTON (AP) --- The...}

\entryitemWithDescription{\hskip 0pt{}Penguin to publish 'classic' Roald Dahl books after backlash}{https://apnews.com/article/9770a7a3a2cb50cb1d53ca82d4b26070}{FILE - Books by Roald Dahl are displayed at the Barney\textquotesingle s store on East 60th Street in New York on Monday, Nov. 21, 2011. Critics are accusing the publisher of Roald Dahl's classic children's books of censorship after it...}

\entryitemWithDescription{\hskip 0pt{}US has a teacher shortage. HBCUs are helping to change that}{https://apnews.com/article/2372cb4f8186dbf05b57e30bf1567e80}{Student teacher Lana Scott, who plans to graduate from Bowie State University in the spring of 2023, teaches a small group of kindergartners at Whitehall Elementary School the alphabet, Tuesday, Jan. 24, 2023, in Bowie, Md. (AP Photo/...}