\entryitemWithDescription{\hskip 0pt{}US would bar full ban on trans athletes but allow exceptions}{https://apnews.com/article/2f6cf412d306e73e68efa2377fb5081a}{FILE - People attend a rally as part of a Transgender Day of Visibility, Friday, March 31, 2023, by the Capitol in Washington. Schools and colleges across the U.S. would be forbidden from enacting outright bans on transgender athletes...}

\entryitemWithDescription{\hskip 0pt{}Civil rights probe launched after fatal Park Police shooting}{https://apnews.com/article/946fc144342396684c0cbe54c3aed7b1}{This image taken from police body camera video released by the U.S. Park Police shows the scene after 17-year-old Dalaneo Martin was fatally shot by a U.S. Park Police officer on March 18, 2023, in Washington. The Justice Department has...}

\entryitemWithDescription{\hskip 0pt{}The Pink Ladies get their origin story in Paramount+ series}{https://apnews.com/article/4fe3b36dfc256aa9ca07c927f73ecf17}{This image released by Paramount+ shows Tricia Fukuhara, from left, Marisa Davila, Cheyenne Wells and Ari Notartomaso from the series "Grease: Rise of the Pink Ladies." (Eduardo Araquel/Paramount+ via AP) Four years before Frenchy, Rizzo...}

\entryitemWithDescription{\hskip 0pt{}IRS pledges more audits of wealthy, better customer service}{https://apnews.com/article/c845bfbfb32aaf24ae52f464b537e6cb}{FILE - Daniel Werfel testifies before the Senate Finance Committee during his confirmation hearing to be the Internal Revenue Service Commissioner, Feb. 15, 2023, in Washington. The IRS released details Thursday, April 6, on how it plans...}

\entryitemWithDescription{\hskip 0pt{}High court: Trans girl can run girls track in West Virginia}{https://apnews.com/article/64d2fd48678afb1a62e5eb84d7762c31}{The Supreme Court building is seen on Capitol Hill, Monday, March 27, 2023, in Washington. (AP Photo/Mariam Zuhaib) WASHINGTON (AP) --- The Supreme Court on Thursday allowed a 12-year-old transgender girl in West Virginia to continue...}

\entryitemWithDescription{\hskip 0pt{}Police: 4 dead in plane crash off Florida's Gulf Coast}{https://apnews.com/article/1035fc3d3c8b9bf05f623831a7408dce}{A U.S. Coast Guard helicopter flies over the Venice Fishing Pier Thursday morning, April 6, 2023, as emergency crews search a debris field in the Gulf of Mexico after a small airplane crash Wednesday night. Police say the bodies of two...}

\entryitemWithDescription{\hskip 0pt{}Biden review of chaotic Afghan withdrawal blames Trump}{https://apnews.com/article/5ff87c14ffd4f7daaa6675e52d3bba1c}{FILE - In this Aug. 22, 2021, file photo provided by the U.S. Air Force, Afghan passengers board a U.S. Air Force C-17 Globemaster III during the Afghanistan evacuation at Hamid Karzai International Airport in Kabul, Afghanistan. (MSgt...}

\entryitemWithDescription{\hskip 0pt{}Former NBA guard Ben Gordon arrested on weapons charge}{https://apnews.com/article/64e1d455a51a57d073be9b6efd31a998}{FILE - Orlando Magic\textquotesingle s Ben Gordon in action during an NBA basketball game against the Philadelphia 76ers, Nov. 5, 2014, in Philadelphia. Former NBA guard Ben Gordon was arrested Tuesday, April 4, 2023, on weapons and...}

\entryitemWithDescription{\hskip 0pt{}Justice Thomas reportedly took undisclosed luxury trips}{https://apnews.com/article/920da69fb952beaa69f84ad16562f60f}{FILE - Associate Justice Clarence Thomas joins other members of the Supreme Court as they pose for a new group portrait, at the Supreme Court building in Washington, Oct. 7, 2022. Thomas has for more than two decades accepted luxury trips...}

\entryitemWithDescription{\hskip 0pt{}Ex-head of Michigan marijuana board admits he took bribes}{https://apnews.com/article/c1af0c2163e7f214a7610c4e002e177c}{FILE - Rick Johnson chairs the committee as it meets before a capacity crowd in Lansing, Mich., June 26, 2017, at the first open meeting of the Michigan Medical Marijuana Board. Federal authorities said Thursday, April 6, 2023, that...}

\entryitemWithDescription{\hskip 0pt{}Tennessee House declines to expel 2nd Dem for gun protest}{https://apnews.com/article/d3f40559c56a051eec49e416a7b5dade}{Former Rep. Justin Jones, D-Nashville, raises his fist on the floor of the House chamber as he walks to his desk to collect his belongings after being expelled from the legislature on Thursday, April 6, 2023, in Nashville, Tenn. Tennessee...}

\entryitemWithDescription{\hskip 0pt{}Snake on a plane! South African pilot finds cobra under seat}{https://apnews.com/article/6facdc4b45ae59148f9f0f4c791a01da}{In this photo provided by Brian Emmenis, people look inside a plane at the Welkom Airport, in Welkom, South Africa, as they search for a venomous snake that the pilot found hiding under his seat midair, Monday April 3, 2023. Rudolf...}

\entryitemWithDescription{\hskip 0pt{}Dramatic photos show how storms filled California reservoirs}{https://apnews.com/article/da455706e614b95fb49d98a211f788d3}{A car crosses Enterprise Bridge over Lake Oroville\textquotesingle s dry banks on May 23, 2021, left, and the same location on March 26, 2023, in Butte County, Calif. (AP Photo/Noah Berger) FOLSOM, Calif. (AP) --- Water levels fell so low...}