\entryitemWithDescription{\hskip 0pt{}Rosalynn Carter, outspoken former first lady, dead at 96}{https://apnews.com/article/e4291133392444bc9ad9d1da461d95c1}{ATLANTA (AP) --- Former first lady Rosalynn Carter, the closest adviser to Jimmy Carter during his one term as U.S. president and their four decades thereafter as global humanitarians, has died at the age of 96. The Carter Center said she...}

\entryitemWithDescription{\hskip 0pt{}Maine and Massachusetts are the last states to keep bans on Sunday hunting. That might soon change}{https://apnews.com/article/76bcbad45f23ff8e3ecf391fee0e905d}{PORTLAND, Maine (AP) --- Some states are steadily chipping away at longstanding bans on Sunday hunting, and there's a push to overturn the laws in Maine and Massachusetts, the final two states with full bans. Maine's highest court is...}

\entryitemWithDescription{\hskip 0pt{}Tiger Woods to play in the Bahamas, his first competition since the Masters}{https://apnews.com/article/1dc0fc79cad338f1fd86b0d39ee21a65}{Tiger Woods showed he could walk four days while caddying for his son. Now he has decided he is fit enough to try to play. Woods announced on social media Saturday he will be playing in the Hero World Challenge, which starts Nov. 30 at...}

\entryitemWithDescription{\hskip 0pt{}Connecticut judge sets new primary date for mayor's race tainted by alleged ballot box stuffing}{https://apnews.com/article/b2786657fefa94953251571ba5aaa7ad}{BRIDGEPORT, Conn. (AP) --- A Connecticut judge has set Jan. 23 as the date for a new Democratic primary election in the Bridgeport mayor's race after having tossed out the September election results because of alleged ballot box stuffing...}

\entryitemWithDescription{\hskip 0pt{}A volcano may keep residents out of an evacuated Iceland town for months}{https://apnews.com/article/aaaf815bed6f5314057fba5f9ed4df57}{REYKJAVIK, Iceland (AP) --- People in southwest Iceland remained on edge Saturday, waiting to see whether a volcano rumbling under the Reykjanes Peninsula will erupt. Civil protection authorities said that even if it doesn't, it's likely...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift postpones Rio de Janeiro show, citing record heat a day after fan dies during concert}{https://apnews.com/article/b69ad355301a7ae6edebd3255c94a167}{RIO DE JANEIRO (AP) --- Taylor Swift postponed an Eras Tour concert in Rio de Janeiro Saturday after a 23-year-old fan died during her Friday night show, according to a message posted on the singer's Instagram. ``I'm writing this from my...}

\entryitemWithDescription{\hskip 0pt{}SpaceX launched its giant new rocket but explosions end the second test flight}{https://apnews.com/article/37c0893ddf605270b16a33ae64d69a85}{SpaceX launched its mega rocket Starship but lost both the booster and the spacecraft in a pair of explosions minutes into Saturday's test flight. The rocketship reached space following liftoff from South Texas before communication...}

\entryitemWithDescription{\hskip 0pt{}Moldova's first dog nips Austrian president on the hand during official visit}{https://apnews.com/article/4105031b52b59fb6eb19326e473f03b8}{BERLIN (AP) --- Austrian President Alexander van der Bellen had an unusual encounter during an official visit to Moldova when the country's first dog, a rescue belonging to Moldovan President Maia Sandu, bit him on the hand. Video footage...}

\entryitemWithDescription{\hskip 0pt{}Sean `Diddy' Combs and singer Cassie settle lawsuit alleging abuse 1 day after it was filed}{https://apnews.com/article/2d2a4c8938eb82c34b62c01a30969554}{NEW YORK (AP) --- A lawsuit by singer Cassie containing allegations of beatings and abuse by music producer Sean ``Diddy'' Combs has been settled, the artists announced Friday, one day after the lawsuit was filed. The settlement was...}

\entryitemWithDescription{\hskip 0pt{}Dogs are coming down with an unusual respiratory illness in several US states}{https://apnews.com/article/7495daf374ddb8179593b2276248da75}{Veterinary laboratories in several states are investigating an unusual respiratory illness in dogs, and encouraging people to take basic precautions to keep their pets healthy as veterinarians try to pin down what's making the animals...}

\entryitemWithDescription{\hskip 0pt{}Snoop Dogg says he's giving up `smoke.' It caught some of his fans off guard}{https://apnews.com/article/a7e2b4fc8d09f53e3d7a59b475a9196b}{NEW YORK (AP) --- Asking for privacy, hip-hop legend and longtime marijuana enthusiast Snoop Dogg says he's going to stop smoking --- though he didn't specify exactly what that might mean. ``After much consideration and conversation with...}

\entryitemWithDescription{\hskip 0pt{}One of Napoleon's signature bicorne hats on auction in France could fetch upwards of \$650,000}{https://apnews.com/article/f2e27d28718641e61f859481289dee8c}{FONTAINEBLEAU, France (AP) --- One of the signature broad, black bicorne hats that Napoleon Bonaparte wore when he ruled 19th-century France and waged war in Europe is expected to fetch upwards of 600,000 euros (\$650,000) at an auction...}

\entryitemWithDescription{\hskip 0pt{}Author A.S. Byatt, who wrote best-seller `Possession' and had a beetle named after her, dies at 87}{https://apnews.com/article/bb4f901f7131d3aa338738bbcc79f62b}{LONDON (AP) --- British author A.S. Byatt, who wove history, myth and a sharp eye for human foibles into books that included the Booker Prize-winning novel ``Possession,'' has died at the age of 87. Byatt's publisher, Chatto \& Windus...}