\entryitemWithDescription{\hskip 0pt{}Iga Swiatek and Jannik Sinner start French Open with straight-set victories}{https://apnews.com/article/dff0c7946d746eb4b050a9cb0383c7cd}{PARIS (AP) --- Ig Swiatek began her bid for a third consecutive French Open title with a straightforward 6-1, 6-2 victory over Leolia Jeanjean on Monday, stretching her winning streak to 13 matches. Swiatek, who has been ranked No. 1 for...}

\entryitemWithDescription{\hskip 0pt{}Chasing cheese wheels or lugging sacks of wool, UK competitors embrace quirky extreme races}{https://apnews.com/article/1a39dacba0218dc6762bf18d71aafbea}{LONDON (AP) --- Dairy-loving daredevils threw caution to the wind Monday for one of Britain's most extreme annual events: Cheese rolling. Cheered by several thousand spectators, scores of reckless racers chased 7-pound (3 kilogram) wheels...}

\entryitemWithDescription{\hskip 0pt{}Rafael Nadal's possible French Open farewell draws fans from all over the world}{https://apnews.com/article/6a1526f70efc07f6d2bb4e14885b78a5}{PARIS (AP) --- They traveled from all over --- from Europe and Oceania, from North America and South America --- to be at Roland Garros on Monday, intent on watching Rafael Nadal play what might be his last French Open match this year. Or...}

\entryitemWithDescription{\hskip 0pt{}`Furiosa' sneaks past `Garfield' to claim No. 1 spot over Memorial Day holiday weekend}{https://apnews.com/article/1eeefc4bf4fb9ea3d138a6802342a68b}{Furiosa won the holiday box office over Garfield by a hair. It was a close race, but the wasteland warrior of `` Furiosa: A Mad Max Saga '' came out slightly ahead of the plump orange cat with an estimated \$32 million in ticket sales...}

\entryitemWithDescription{\hskip 0pt{}The number of heat-related howler monkeys deaths in Mexico has risen to 157, with a few recovering}{https://apnews.com/article/371cfba7f293713544a0302320c53851}{MEXICO CITY (AP) --- The number of heat-related howler monkeys deaths in Mexico has risen to 157, the government said, with a tragically small number of the primates treated or recovering. A heat dome --- an area of strong high pressure...}

\entryitemWithDescription{\hskip 0pt{}Former `General Hospital' actor Johnny Wactor killed in downtown Los Angeles shooting}{https://apnews.com/article/949c92bd7a91cc3e88b68d277bf78d81}{LOS ANGELES (AP) --- Former ``General Hospital'' actor Johnny Wactor was shot and killed when he interrupted thieves stealing the catalytic converter from his car in Los Angeles, his family said Sunday. The shooting occurred around 3 a.m...}

\entryitemWithDescription{\hskip 0pt{}Paris' traffic-clogged Champs-Elysees turned into a mass picnic blanket for an unusual meal}{https://apnews.com/article/82b6afa486a40a50d777f762c427f995}{PARIS (AP) --- The French capital's most famous street, the Champs-Élysées, transformed into a massive picnic blanket Sunday as around 4,000 people sat in the sun enjoying an al fresco meal. The lucky picnickers were selected via a draw...}

\entryitemWithDescription{\hskip 0pt{}Grayson Murray's parents say the two-time PGA Tour winner died of suicide}{https://apnews.com/article/67dc0e05355e9011e4711b7b4cbe28d8}{Grayson Murray's parents said Sunday their 30-year-old son took his own life, just one day after he withdrew from a PGA Tour event. The family asked for privacy and that people honor Murray by being kind to one another. ``If that becomes...}

\entryitemWithDescription{\hskip 0pt{}`Furiosa,' `Garfield' lead slowest Memorial Day box office in decades}{https://apnews.com/article/1b2a9c0aefec99b5105a09bfaf15679b}{Movie theaters are looking more and more like a wasteland this summer. Neither `` Furiosa: A Mad Max Saga '' nor `` The Garfield Movie '' could save Memorial Day weekend, which is cruising towards a two-decade low. `` Furiosa,'' the Mad...}

\entryitemWithDescription{\hskip 0pt{}12 people injured after Qatar Airways plan hits turbulence on way to Dublin}{https://apnews.com/article/ad4d17adc46ac91fea8f214c7ef72541}{LONDON (AP) --- Twelve people were injured when a Qatar Airways plane flying from Doha to Dublin on Sunday hit turbulence, airport authorities said. Dublin Airport said in a statement that the plane landed safely as scheduled before 1 p...}

\entryitemWithDescription{\hskip 0pt{}The dreams of a 60-year-old beauty contestant come to an abrupt end in Argentina}{https://apnews.com/article/30aef40c681708b761e87c308b1d2303}{BUENOS AIRES, Argentina (AP) --- A 60-year-old woman saw her dreams of becoming the oldest Miss Universe contestant in history melt away in a haze of sequins and selfies Saturday at Argentina's annual beauty pageant. Alejandra Marisa Rodrí...}

\entryitemWithDescription{\hskip 0pt{}Indianapolis 500: A double bid, a whiff of scandal and the fear of rain as race day arrives}{https://apnews.com/article/af0fb6bd9f99433267893337e806209f}{INDIANAPOLIS (AP) --- The Indianapolis 500 is set for midday Sunday, though race day arrived with all eyes on the weather. The forecast called for a strong chance of rain, raising the prospect that the 108th running of IndyCar's showcase...}

\entryitemWithDescription{\hskip 0pt{}Rapper Nicki Minaj says Dutch police told her they found pot in bags}{https://apnews.com/article/f7c05e8ce6ddfc5482dbe37ba368038a}{AMSTERDAM (AP) --- Rapper Nicki Minaj said Saturday that police in the Netherlands discovered marijuana in her bags as she was preparing to leave the country for her next concert. Minaj tweeted that she was stopped at the Amsterdam...}