\entryitemWithDescription{\hskip 0pt{}3 teens arrested after Colorado driver killed by thrown rock}{https://apnews.com/article/e1ba95f0b114632c5dacfc2871daa8a8}{This photo provided by the Jefferson County Sheriff\textquotesingle s Office shows Nicholas "Mitch" Karol-Chik who is facing a first-degree murder charge. Authorities say Karol-Chik and two other teenagers are facing the first-degree...}

\entryitemWithDescription{\hskip 0pt{}Mississippi River flooding prompts evacuations, sandbagging}{https://apnews.com/article/99bcd6f626baf57f0dd8029cefa6dc7d}{The flooded Mississippi River surrounds the homes on Abel Island near Guttenberg, Iowa, on Tuesday, April 25, 2023. (Stephen Gassman/Telegraph Herald via AP) DES MOINES, Iowa (AP) --- Some residents along the swelling Upper Mississippi...}

\entryitemWithDescription{\hskip 0pt{}Elizabeth Holmes delays going to prison with another appeal}{https://apnews.com/article/e4159f46b8dafb49e8d0faac14d9619e}{FILE - Former Theranos CEO Elizabeth Holmes arrives at federal court in San Jose, Calif., March 17, 2023. The disgraced Theranos CEO has avoided starting her more than 11-year prison sentence on Thursday, April 27, by deploying the same...}

\entryitemWithDescription{\hskip 0pt{}Adnan Syed asks court to reconsider backing victim's family}{https://apnews.com/article/150bda59095bcd24f4a6fba6fb65e24d}{FILE - Adnan Syed gets emotional as he speaks to reporters outside the Robert C. Murphy Courts of Appeal building after a hearing, Feb. 2, 2023, in Annapolis, Md. Attorneys for Syed filed a motion, Wednesday, April 26, 2023, asking a...}

\entryitemWithDescription{\hskip 0pt{}US files charges in Michigan over diesel engine tampering}{https://apnews.com/article/e1baea098f965977d2ea098a2407b2dd}{FILE - Mark Totten, Democratic candidate for Michigan attorney general, gives his concession speech during an election night rally in Detroit, Nov. 4, 2014. Eleven people have been charged in Michigan in a scheme to evade air-pollution...}

\entryitemWithDescription{\hskip 0pt{}Review: Judy Blume goes Hollywood in `Are You There God?...'}{https://apnews.com/article/4e0797bf798e632d26096f3a71aa7add}{This image released by Lionsgate shows Rachel McAdams, left, and Abby Ryder Fortson in a scene from "Are You There God? It\textquotesingle s Me, Margaret." (Dana Hawley/Lionsgate via AP) There is not a cynical molecule in the big-screen...}

\entryitemWithDescription{\hskip 0pt{}First Republic shares sink again, down nearly 60\% in week}{https://apnews.com/article/f57c609d82d51158983ee24dc8041d31}{First Republic Bank signs and logos rest near a parking space, below, and on the exterior of a bank branch location, above, Wednesday, April 26, 2023, in Wellesley, Mass. First Republic Bank\textquotesingle s stock continued to slide...}

\entryitemWithDescription{\hskip 0pt{}Bavaria to make it easier to shoot wolves in Alpine region}{https://apnews.com/article/3c1c56af00de5f912b42273c30430ee0}{Bavaria\textquotesingle s governor Markus Soeder gestures as he attends a farmers meeting in Oberaudorf, Germany, Wednesday, April 26, 2023 because of the sheep ripping by a bear in the mountain region near the border. Officials in...}

\entryitemWithDescription{\hskip 0pt{}Freddie Mercury's eclectic collection of 'clutter' for sale}{https://apnews.com/article/444c3dce1364f173b08b1399c1e12b51}{A replica of St. Edward\textquotesingle s Crown, worn by Freddie Mercury in his final concert with Queen in 1986, is displayed at the Sotheby\textquotesingle s exhibition in London, Wednesday, April 26, 2023. The crown is said to be based...}

\entryitemWithDescription{\hskip 0pt{}Mississippi jail escapee believed dead after armed standoff}{https://apnews.com/article/3e84fdb1eb8c1e930e72084e687d8ec4}{This booking photo provided Jackson, Miss., Police Department Dylan Arrington, one of four Mississippi prisoners who escaped from the Raymon Detention Center over the weekend. He is now a suspect in the Monday night, April 24, 2023...}

\entryitemWithDescription{\hskip 0pt{}Prosecutors now doubt imprisoned mother killed her children}{https://apnews.com/article/baccb02deac65cc4a1ca47b5c676f667}{Kathleen Folbigg holds one of her diaries while appearing via video link screened at the New South Whales Coroners Court in Sydney, April 29, 2019. The Australian prosecutors office that proved 20 years ago mother Folbigg deliberately...}

\entryitemWithDescription{\hskip 0pt{}No one is driving this taxi. What possibly could go wrong?}{https://apnews.com/article/cc28730c6dc76882679ef19cbdb1c607}{The empty driver\textquotesingle s seat is shown in a driverless Chevy Bolt car named Peaches carrying Associated Press reporter Michael Liedtke during a ride in San Francisco on Tuesday, Sept.13, 2022. The experience provided a snapshot...}

\entryitemWithDescription{\hskip 0pt{}When told of Kishida attack, safety chief kept eating eel}{https://apnews.com/article/cc4fb660c0153ded9fd236a671960db3}{Chairperson of the National Public Safety Commission Koichi Tani speaks to reporters in Tokyo Wednesday, April 26, 2023. Tani has come under fire for his remark that he enjoyed eel rice so much that he kept eating even when his agency...}