\entryitemWithDescription{\hskip 0pt{}Taylor Swift turns out to see Travis Kelce, Kansas City Chiefs play Chicago Bears}{https://apnews.com/article/891e7df84295f5b35cfa97a5ec427721}{KANSAS CITY, Mo. (AP) --- Travis Kelce put the ball in Taylor Swift's court, and she wound up bringing it to Arrowhead Stadium after all. The 12-time Grammy Award winner took advantage of an invitation from the All-Pro tight end to see...}

\entryitemWithDescription{\hskip 0pt{}Dolphins rout Broncos 70-20, scoring the most points by an NFL team in a game since 1966}{https://apnews.com/article/7b63c4ac5c48e0f4156a8a4574de5c72}{MIAMI GARDENS, Fla. (AP) --- De'Von Achane could hear the crowd at Hard Rock Stadium chanting ``Three more points!'' on Miami's final drive. The Dolphins had the ball inside the Denver Broncos' 30 with less than a minute left, and they...}

\entryitemWithDescription{\hskip 0pt{}Usher to headline the 2024 Super Bowl halftime show in Las Vegas}{https://apnews.com/article/05a21fe7663feff1368bba8e8ba7c47b}{LOS ANGELES (AP) --- Usher has a new confession: The Grammy winner will headline the Apple Music Super Bowl Halftime Show in Las Vegas. The NFL, Apple Music and Roc Nation announced Sunday that Usher would lead the halftime festivities...}

\entryitemWithDescription{\hskip 0pt{}Science paints a new picture of the ancient past, when we mixed and mated with other kinds of humans}{https://apnews.com/article/e671a140b75fab3791fbd1c4b77cb6e7}{What does it mean to be human? For a long time, the answer seemed clear. Our species, Homo sapiens --- with our complex thoughts and deep emotions --- were the only true humans to ever walk the Earth. Earlier forms, like the Neanderthals...}

\entryitemWithDescription{\hskip 0pt{}Birthplace of the atomic bomb braces for its biggest mission since the top-secret Manhattan Project}{https://apnews.com/article/028c5acd03e4124485a042fab6601e68}{LOS ALAMOS, N.M. (AP) --- Los Alamos was the perfect spot for the U.S. government's top-secret Manhattan Project. Almost overnight, the ranching enclave on a remote plateau in northern New Mexico was transformed into a makeshift home for...}

\entryitemWithDescription{\hskip 0pt{}New York City further tightens time limit for migrants to move out of shelters}{https://apnews.com/article/a028edfe8b2cee99eaadf07f423a6f6a}{NEW YORK (AP) --- Beleaguered by a continuing influx of asylum seekers, New York City Mayor Eric Adams is further tightening shelter rules by limiting adult migrants to just 30 days in city-run facilities --- to help ease pressures on the...}

\entryitemWithDescription{\hskip 0pt{}A Black student was suspended for his hairstyle. Now his family is suing Texas officials}{https://apnews.com/article/e79ede512923b672a275abf054e2407b}{HOUSTON (AP) --- The family of a Black high school student in Texas who was suspended over his dreadlocks filed a federal civil rights lawsuit Saturday against the state's governor and attorney general, alleging they failed to enforce a...}

\entryitemWithDescription{\hskip 0pt{}A landslide in Sweden causes a huge sinkhole on a highway and 3 are injured when cars crash}{https://apnews.com/article/2e84cdd22780979324e304e8808a4aa7}{HELSINKI (AP) --- A landslide in western Sweden caused a huge sinkhole on a major highway to Norway early Saturday, and three people were injured when their cars and a bus skidded off the road, police said. Photos and video footage showed...}

\entryitemWithDescription{\hskip 0pt{}Historians race to find Great Lakes shipwrecks before quagga mussels destroy the sites}{https://apnews.com/article/841f6ae286d646d5818c94dbbeaf48de}{MADISON, Wis. (AP) --- The Great Lakes' frigid fresh water used to keep shipwrecks so well preserved that divers could see dishes in the cupboards. Downed planes that spent decades underwater were left so pristine they could practically...}

\entryitemWithDescription{\hskip 0pt{}Amazon Prime Video will soon come with ads, or a \$2.99 monthly charge to dodge them}{https://apnews.com/article/e3713ac21acc14b8ba8381fa7ab447e5}{Amazon Prime Video will include advertising during shows and movies starting early next year, joining other streaming services that have added different tiers of subscriptions. Members of Amazon Prime can pay \$2.99 per month in the U.S...}

\entryitemWithDescription{\hskip 0pt{}Three arrests made in boy's shooting death that sparked New Mexico governor's aggressive guns ban}{https://apnews.com/article/195a77de0d66c100b107d64c28fbba97}{ALBUQUERQUE, N.M. (AP) --- A third arrest was made Friday in connection with a shooting outside an Albuquerque baseball stadium that killed an 11-year-old boy and prompted the New Mexico governor to issue a controversial gun ban...}

\entryitemWithDescription{\hskip 0pt{}Hollywood actor and writer strikes have broad support among Americans, AP-NORC poll shows}{https://apnews.com/article/5727ed3078c4f69851c18c560670f480}{LOS ANGELES (AP) --- Public support for striking Hollywood actors and writers is broad, but not necessarily deep enough for most people to change their viewing habits, a new poll finds. A majority (55\%) of U.S. adults sympathize with the...}

\entryitemWithDescription{\hskip 0pt{}A toddler lost in the woods is found asleep using family dog as a pillow}{https://apnews.com/article/823829a26f1a4b387b46432a9a765309}{FAITHORN, Mich. (AP) --- A 2-year-old girl who walked away from her home in Michigan's Upper Peninsula alongside two family dogs was found in the woods hours later sleeping on the smaller dog like a furry pillow, state police said. ``She...}