\entryitemWithDescription{\hskip 0pt{}Intel agencies: No sign adversaries behind 'Havana syndrome'}{https://apnews.com/article/cf087b8255532056b5597232544bfb71}{FILE - Tourists ride classic convertible cars on the Malecon beside the United States Embassy in Havana, Cuba, Oct. 3, 2017. U.S. intelligence agencies cannot link a foreign adversary to any of the incidents associated with so-called ``...}

\entryitemWithDescription{\hskip 0pt{}Prosecution wraps its case at Alex Murdaugh murder trial}{https://apnews.com/article/5612574c166b6f8b4e71ff6395e38f9c}{Prosecutors have called their final witnesses in Alex Murdaugh's double murder trial. The jury will now head Wednesday about 40 minutes from the courthouse to see the family home where authorities say Murdaugh killed his wife and son in...}

\entryitemWithDescription{\hskip 0pt{}Georgia star Jalen Carter charged with racing in fatal wreck}{https://apnews.com/article/28df32b2e90b2c39432d5ae7166fbd10}{FILE - Georgia defensive lineman Jalen Carter speaks during media day ahead of the national championship NCAA College Football Playoff game between Georgia and TCU, Saturday, Jan. 7, 2023, in Los Angeles. Carter, projected as one of the...}

\entryitemWithDescription{\hskip 0pt{}Biden says Labor nominee Julie Su represents American dream}{https://apnews.com/article/2b7b06ee4673f26ceef4b9d2d78fca2a}{President Joe Biden talks about his nomination of Julie Su, left, to serve as the Secretary of Labor during an event in the East Room of the White House in Washington, Wednesday, March 1, 2023. (AP Photo/Susan Walsh) President Joe Biden...}

\entryitemWithDescription{\hskip 0pt{}NBC's Hoda Kotb off 'Today' show due to family health issue}{https://apnews.com/article/3f181b97ab4319d91eedbc77b1c50b61}{FILE - Co-anchors Savannah Guthrie, left, and Hoda Kotb pose on "Today" show set at NBC Studios on June 27, 2018, in New York. On Wednesday NBC addressed the mystery of Kotb\textquotesingle s absence on the program. Kotb, who has been...}

\entryitemWithDescription{\hskip 0pt{}Lilly plans to slash some insulin prices, expand cost cap}{https://apnews.com/article/419db92bfe554894bdc9c7463f2f3183}{This Wednesday, March 1, 2023 photo shows a vial of Eli Lilly\textquotesingle s Humalog insulin in New York. Eli Lilly will cut prices for some older insulins later this year and immediately give more patients access to a cap on costs...}

\entryitemWithDescription{\hskip 0pt{}TikTok sets new default time limits for minors}{https://apnews.com/article/f735bd496ea3513abfc6480e5637abd8}{FILE - The TikTok logo is seen on a cellphone on Oct. 14, 2022, in Boston. TikTok says every account held by a user under the age of 18 will automatically be set to a 60-minute daily screen time limit in the coming weeks amid growing...}

\entryitemWithDescription{\hskip 0pt{}Ukraine official: Forces may pull out of key city of Bakhmut}{https://apnews.com/article/c0e33e89b027c3604f585166a349c457}{Medics give the first aid to a wounded Ukrainian soldier near Bakhmut, the site of the heaviest battles with the Russian troops, Donetsk region, Ukraine, Monday, Feb. 27, 2023. (AP Photo/Yevhen Titov) KYIV, Ukraine (AP) --- The Ukrainian...}

\entryitemWithDescription{\hskip 0pt{}Long-lost ship found in Lake Huron, confirming tragic story}{https://apnews.com/article/91f6db8e3c42d37b2f8ade7b4df0a4bb}{In this image taken from video provided by the Thunder Bay National Marine Sanctuary, the bow of the Ironton is seen in Lake Huron off Michigan\textquotesingle s east coast in a June 2021 photo. Searchers have found the long-lost Great...}

\entryitemWithDescription{\hskip 0pt{}COVID-19 conspiracies soar after latest report on origins}{https://apnews.com/article/4a76f8196d7c504f288429d1018d2990}{FILE - Syringes with vaccines are prepared at the L.A. Care and Blue Shield of California Promise Health Plans\textquotesingle{} Community Resource Center where they were offering members and the public free flu and COVID-19 vaccines Oct...}

\entryitemWithDescription{\hskip 0pt{}China dismisses FBI statement on COVID-19 lab leak theory}{https://apnews.com/article/982ac59822e84499daa47cf87e4fb306}{People wearing face masks walk past rows of lanterns at a tourist shopping street in Beijing, Tuesday, Feb. 28, 2023. (AP Photo/Mark Schiefelbein) BEIJING (AP) --- For the second day in a row, China on Wednesday dismissed U.S. suggestions...}

\entryitemWithDescription{\hskip 0pt{}Ohio senators introduce rail safety bill after fiery crash}{https://apnews.com/article/82c55dc95aca9524d6ae8e6d01336dbe}{FILE - A view of the scene Friday, Feb. 24, 2023, as the cleanup continues at the site of a Norfolk Southern freight train derailment that happened on Feb. 3, in East Palestine, Ohio. On Tuesday, Feb. 28, in the wake of a fiery Ohio...}

\entryitemWithDescription{\hskip 0pt{}Slovakia basks under NATO umbrella, sends Ukraine old arms}{https://apnews.com/article/7374f6219ed9edff190437621ec84bc1}{FILE - Slovak Air Force MiG-29 goes through a water gate during an airshow in Malacky, Slovakia, Saturday, Aug. 27, 2022. Former Soviet satellite Slovakia has been a NATO member since 2004, but the reality of belonging to the world's...}