\entryitemWithDescription{\hskip 0pt{}NTSB says a JetBlue captain took off quickly to avoid an incoming plane in Colorado last yearFederal investigators are describing a close call between...}{https://apnews.com/article/effee382edc9fc2c3fe4f2e6b105dfc7}{Federal investigators say the tail of a JetBlue plane struck a Colorado runway during takeoff last year when the captain quickly pointed the jet's nose upward to avoid a head-on crash with a plane preparing to land on the same runway. The...}

\entryitemWithDescription{\hskip 0pt{}Judge questions whether legal cases cited by Michael Cohen's lawyer actually existA federal judge is questioning whether a lawyer for former Donald T...}{https://apnews.com/article/05a138cca16445aa63992134faa7cf14}{A lawyer for Michael Cohen, the fixer-turned-foe of former President Donald Trump, appears to have cited court rulings that do not exist in a legal filing seeking to have Cohen's post-prison supervision end early, according to a federal...}

\entryitemWithDescription{\hskip 0pt{}`Something catastrophic' broke support rod on Rhode Island bridge, transportation director saysRhode Island's Transportation Department director sa...}{https://apnews.com/article/6fce51be42ecd569fca91a190b9202af}{A review of state inspection reports of a critical Rhode Island bridge that was partially shut down over safety concerns, resulting in major traffic headaches, led authorities to believe that ``something catastrophic'' happened since July...}

\entryitemWithDescription{\hskip 0pt{}Anthony Anderson to host strike-delayed Emmys ceremony}{https://apnews.com/article/f4f03261caf9dbdfdad9238981b38f16}{LOS ANGELES (AP) --- Anthony Anderson has been nominated for multiple Emmy Awards, and now he'll be presiding over January's strike-delayed ceremony. The Fox network announced Anderson will host the Jan. 15 ceremony, which honors the best...}

\entryitemWithDescription{\hskip 0pt{}Rembrandt portraits that were privately held for nearly 200 years go on show in AmsterdamA pair of small portraits by 17th-century Dutch Master Rembra...}{https://apnews.com/article/33cba2b9ee92a852b829aea629b97d05}{THE HAGUE, Netherlands (AP) --- After nearly 200 years in a private collection, a pair of small portraits by 17th century Dutch Master Rembrandt van Rijn went on display Wednesday after a long-term loan to the Netherlands' national art...}

\entryitemWithDescription{\hskip 0pt{}Geminids meteor shower peaks this week under dark skies}{https://apnews.com/article/6171ffba7d79511cd9a59dd0f525d8d5}{CAPE CANAVERAL, Fla. (AP) --- The year's best meteor shower, the Geminids, peaks this week. Skygazers may see as many as one or even two a minute streaking across dark skies. The meteors will reach their frenzy Thursday. But Wednesday...}

\entryitemWithDescription{\hskip 0pt{}Body in Philadelphia warehouse IDed as inmate who escaped in 4th city breakout this yearPhiladelphia police say a body found inside a warehouse has be...}{https://apnews.com/article/a008a80c0b61a21cfec7d8f2e6ca4aff}{PHILADELPHIA (AP) --- A body found inside a Philadelphia warehouse has been identified as an inmate who walked away from a work detail almost two weeks ago in the fourth breakout from a city lockup this year, police announced late...}

\entryitemWithDescription{\hskip 0pt{}The world in other words: Here's a list of terms that reflected the popular mood in 2023Many sentiments are universal. Many words are not. As 2023 en...}{https://apnews.com/article/7d05a2c6d95828238c2aa01cd86a2430}{Many sentiments are universal. Many words are not. As 2023 ends, The Associated Press reached out to colleagues around the world for terms that emerged this year and seized or crystalized the popular mood. Some were newsy, some cultural...}

\entryitemWithDescription{\hskip 0pt{}Football player Matt Araiza dropped from woman's rape lawsuit and won't sue for defamationAttorneys say former Buffalo Bills punter Matt Araiza is b...}{https://apnews.com/article/ba34b821c0e5ff59268c6ae0c7b2842f}{SAN DIEGO (AP) --- Former Buffalo Bills punter Matt Araiza is being dropped from a lawsuit filed by a woman who alleged she was raped by San Diego State University football players in 2021, it was announced Tuesday. The woman agreed to...}

\entryitemWithDescription{\hskip 0pt{}Norfolk, Virginia, approves military-themed brewery despite some community pushbackA military-themed brewery will open in Virginia despite some commun...}{https://apnews.com/article/a6e286ed50c5adc7582fa21b211197df}{NORFOLK, Va. (AP) --- A military-themed brewery will open in Virginia despite some community opposition over alleged racist and homophobic remarks of a former U.S. Navy SEAL who has a small ownership stake in the business. Norfolk's City...}

\entryitemWithDescription{\hskip 0pt{}Emmy-winning actor Andre Braugher dies at 61 after a brief illness}{https://apnews.com/article/f2ee7dd990dbd40c8fd5258ac624bab7}{LOS ANGELES (AP) --- Andre Braugher, the Emmy-winning actor who would master gritty drama for seven seasons on ``Homicide: Life on The Street'' and modern comedy for eight on ``Brooklyn Nine-Nine,'' died Monday at 61. Braugher died after...}

\entryitemWithDescription{\hskip 0pt{}Russian man who flew on Los Angeles flight without passport or ticket charged with federal crimeA federal complaint filed by the FBI says a Russian ma...}{https://apnews.com/article/a9694914faf35ddb793066efdf5f633c}{LOS ANGELES (AP) --- A Russian man who flew on a plane from Denmark to Los Angeles in November without a passport or ticket told U.S. authorities he did not remember how he got through security in Europe, according to a federal complaint...}

\entryitemWithDescription{\hskip 0pt{}Nebraska priest, bleeding from multiple stab wounds, yelled `help me' when deputy arrived}{https://apnews.com/article/c48a12fd9ad044709e8ebbb8f53e4eab}{OMAHA, Neb. (AP) --- Moments after a Nebraska priest called 911 to report that a man was standing in his kitchen with a knife, a dispatcher on the line heard screaming and a struggle. A deputy arriving a few minutes later heard the priest...}