\entryitemWithDescription{\hskip 0pt{}Gay pride revelers in Sao Paulo reclaim Brazil's national symbols}{https://apnews.com/article/27c64e4b89da74b371e5b33fb401103f}{SAO PAULO, Brazil (AP) --- The iconic yellow and green of Brazil's flag mixed with a sea of rainbow-colored tutus, hand fans and drag queen hairdos at Sunday's LGBTQ+ pride parade in Sao Paulo, Brazil. The annual event along Sao Paulo's...}

\entryitemWithDescription{\hskip 0pt{}Rugby star and ALS campaigner Rob Burrow dies at age 41}{https://apnews.com/article/6810e415ec1b003c9b74ee4ba4220f54}{LEEDS, England (AP) --- Rob Burrow, a former rugby star who was widely praised for his fundraising campaigns after being diagnosed with Lou Gehrig's disease in 2019, has died. He was 41. Leeds Rhinos announced his death on Sunday. Burrow...}

\entryitemWithDescription{\hskip 0pt{}Michael Douglas pays solidarity visit to southern Israel}{https://apnews.com/article/6cd29180484d4bb8d5fa74010f2cbd87}{JERUSALEM (AP) --- Actor Michael Douglas on Sunday paid a solidarity visit to an Israeli kibbutz that was hit hard in the Oct. 7 Hamas attack that sparked Israel's war against the Islamic militant group. Douglas met with members of...}

\entryitemWithDescription{\hskip 0pt{}Rupert Murdoch ties the knot for the 5th time in ceremony at his California vineyard}{https://apnews.com/article/7523f6c2d2fafdca7356e35196983cda}{NEW YORK (AP) --- Media magnate Rupert Murdoch, 93, has married for the fifth time, newspapers owned by his corporation, News Corp, reported Sunday. Murdoch and Elena Zhukova, a 67-year-old Russian-born retired molecular biologist, wed...}

\entryitemWithDescription{\hskip 0pt{}Ex-NJ officer sentenced to 27 years in shooting death of driver, wounding of passenger in 2019 chase}{https://apnews.com/article/e362ff23b64ed36e039c7d9acb32f0e3}{NEWARK, N.J. (AP) --- A former New Jersey police officer has been sentenced to a total of 27 years in prison in the shooting death of one man and the wounding of another during a high-speed car chase 5 1/2 years ago in the city of Newark...}

\entryitemWithDescription{\hskip 0pt{}`Garfield,' `Furiosa' repeat atop box office charts as slow summer grinds on}{https://apnews.com/article/6d3467643a7abd5fe9027c758c9760bf}{It was a quiet weekend at North American movie theaters, dominated once again by Sony's ``The Garfield Movie'' and Warner Bros. `` Furiosa: A Mad Max Saga.'' Flipping the script from their Memorial weekend openings, the animated orange...}

\entryitemWithDescription{\hskip 0pt{}Monster truck clips aerial power line, toppling utility poles in spectator area}{https://apnews.com/article/f65875bdc83b3d4ac85408409ba07b5f}{TOPSHAM, Maine (AP) --- A lobster-themed monster truck performing for a crowd clipped an aerial power line, toppling several utility poles and sending two people to hospitals, police said. Others suffered minor injuries. The Topsham...}

\entryitemWithDescription{\hskip 0pt{}Makhachev beats Poirier by submission at UFC 302 to defend lightweight title}{https://apnews.com/article/20fe30cab61bd99134c00ec6802fd245}{NEWARK, N.J. (AP) --- Islam Makhachev defended his lightweight title and extended his winning streak to 14 fights, third-longest in UFC history, by getting a submission victory over Dustin Poirier in the fifth round on Saturday night at...}

\entryitemWithDescription{\hskip 0pt{}Oregon officials close entire coast to mussel harvesting due to shellfish poisoning}{https://apnews.com/article/06068473aeb8984efb8fdb3cdae20659}{SALEM, Ore. (AP) --- Oregon authorities have closed the state's entire coastline to mussel harvesting due to an ``unprecedented'' outbreak of shellfish poisoning that has sickened at least 20 people. They've also closed parts of the...}

\entryitemWithDescription{\hskip 0pt{}Live Nation reveals data breach at its Ticketmaster subsidiary}{https://apnews.com/article/a756d803c686e07f3b73444b3ca42c74}{Live Nation is investigating a data breach at its Ticketmaster subsidiary, which dominates ticketing for live events in the United States. Live Nation, based in Beverly Hills, California, said in a regulatory filing Friday that on May...}

\entryitemWithDescription{\hskip 0pt{}Downtown Atlanta water service disrupted, forcing business closings, water boil notice}{https://apnews.com/article/b288ea4f84da987649af33eb54dee20a}{ATLANTA (AP) --- Downtown Atlanta businesses and attractions were closed Saturday as the city tried to repair water main breaks that led to water outages and low pressure. Water gushed into the street where three large water mains...}

\entryitemWithDescription{\hskip 0pt{}Boeing counts down again to its first astronaut launch on a long-delayed test flight for NASA}{https://apnews.com/article/c4caeff8515da9e5effe7bad33cf0b81}{CAPE CANAVERAL, Fla. (AP) --- Boeing took another crack Saturday at launching astronauts for the first time aboard its new space capsule, after a delay for leak checks and rocket repairs. The company's Starliner capsule was due to rocket...}

\entryitemWithDescription{\hskip 0pt{}With his transgender identity public, skier Jay Riccomini finds success on and off the slopes}{https://apnews.com/article/f3f6f7e883580b57cdb3796ce0392ee0}{COPPER MOUNTAIN, Colo. (AP) --- One of freestyle skier Jay Riccomini's priceless life moments came this year in Switzerland, when he was recognized on the podium for a third-place finish in a major global competition. It was a...}