\entryitemWithDescription{\hskip 0pt{}Beyoncé's `Cowboy Carter' reinforces her dedication to Black reclamation — and country music}{https://apnews.com/article/9c865d00adf1f31f4bf22f126612e226}{LOS ANGELES (AP) --- First, Beyoncé arrived at the 2024 Grammy Awards in full cowboy regalia --- making a statement without saying a word. Then, during the Super Bowl, she dropped two hybrid country songs: ``Texas Hold `Em'' and ``16...}

\entryitemWithDescription{\hskip 0pt{}Michigan GOP lawmaker falsely claims that buses carrying March Madness teams are `illegal invaders'}{https://apnews.com/article/6217e5cda406954993a299329b98572b}{FARMINGTON HILLS, Mich. (AP) --- A Michigan state lawmaker involved in former President Donald Trump's election denials is being widely criticized after the Republican made false claims that buses carrying college athletes to Detroit for...}

\entryitemWithDescription{\hskip 0pt{}Flo Milli's new album proves the `Never Lose Me' rising artist's dreams of greatness are coming true}{https://apnews.com/article/3a81e06dc8d61fd7ddef09dc3aa11320}{NEW YORK (AP) --- Flo Milli always felt different from her peers growing up, believing she was destined for greatness. For her, the writing was always on the walls --- and in the stalls. ``In high school, I used to have a lot of girls...}

\entryitemWithDescription{\hskip 0pt{}Punxsutawney Phil, the spring-predicting groundhog, and wife Phyliss are parents of 2 babies}{https://apnews.com/article/839fa23e87006f75bc4eb716e55601e7}{Now we know what Punxsutawney Phil, the groundhog who predicts whether an early spring will arrive each Feb. 2, does on the other 364 days. The Pennsylvania group that handles Phil, and his groundhog wife, Phyliss, says the couple have...}

\entryitemWithDescription{\hskip 0pt{}Rays' Wander Franco placed on administrative leave through June 1 as sexual abuse probe continues}{https://apnews.com/article/195df3d118a9417cfe35ae17d35c85db}{ST. PETERSBURG, Fla. (AP) --- Tampa Bay All-Star shortstop Wander Franco was placed on administrative leave through June 1 under an agreement between Major League Baseball and the players' association while the investigation continues in...}

\entryitemWithDescription{\hskip 0pt{}Home Depot buying supplier to professional contractors in a deal valued at about \$18.25B}{https://apnews.com/article/d38b7a5863c084ca8880b2c1677fcbcd}{Home Depot will buy SRS Distribution, a materials provider for professionals, in a deal valued at approximately \$18.25 billion. It is Home Depot's largest acquisition in its history and with it, it steps more aggressively into the fast...}

\entryitemWithDescription{\hskip 0pt{}The White House expects about 40,000 participants at its `egg-ucation'-themed annual Easter egg roll}{https://apnews.com/article/f1bbacddf2ae3b35812a5083ce12bc09}{Some 40,000 people are expected to participate in Monday's ``EGG-ucation''-themed White House Easter Egg Roll, about 10,000 more people than last year. A teacher for more than 30 years, Jill Biden is transforming an annual tradition first...}

\entryitemWithDescription{\hskip 0pt{}A fight to protect the dignity of Michelangelo's David raises questions about freedom of expression}{https://apnews.com/article/3fa1b7185fea36003e064fa6e2c309fd}{FLORENCE, Italy (AP) --- Michelangelo's David has been a towering figure in Italian culture since its completion in 1504. But in the current era of the quick buck, curators worry the marble statue's religious and political significance is...}

\entryitemWithDescription{\hskip 0pt{}No police charges for Taylor Swift's dad over paparazzi incident in Sydney}{https://apnews.com/article/3d8722a67563051864da0970fd7e4381}{SYDNEY (AP) --- Taylor Swift's father will not be charged over a paparazzi photographer's claim that Scott Swift assaulted him on the Sydney waterfront hours after the pop star's Australian tour ended last month. Photographer Ben McDonald...}

\entryitemWithDescription{\hskip 0pt{}Bob Uecker, 90, expected to broadcast Brewers' home opener, workload the rest of season uncertain}{https://apnews.com/article/240dcc23ee681d4631a633e0e903d3c9}{MILWAUKEE (AP) --- Bob Uecker will be back behind the microphone when the Milwaukee Brewers play their home opener Tuesday against the Minnesota Twins. How heavy a broadcasting workload the 90-year-old Uecker will have the rest of the...}

\entryitemWithDescription{\hskip 0pt{}Lou Whittaker, among the most famous American mountaineers, has died at age 95}{https://apnews.com/article/b74435763e4b14cf5216995ed15f44fa}{SEATTLE (AP) --- Lou Whittaker, a legendary American mountaineer who helped lead ascents of Mount Everest, K2 and Denali, and who taught generations of climbers during his more than 250 trips up Mount Rainier, the tallest peak in...}

\entryitemWithDescription{\hskip 0pt{}Ukraine's soccer victory provides welcome distraction from tragedy of war}{https://apnews.com/article/791939f8f66d3dab6181f366b2d0a2c8}{KYIV, Ukraine (AP) --- Ukrainians have expressed pride and gratitude toward their men's national soccer team for qualifying for the European Championship, a rare bit of good news and a welcome distraction from the war with Russia. Though...}

\entryitemWithDescription{\hskip 0pt{}Talks on luring NHL's Washington Capitals and NBA's Washington Wizards to Virginia are over}{https://apnews.com/article/fedabae3b196b6e79a759f7e6aa44a86}{RICHMOND, Va. (AP) --- Negotiations on luring the NHL's Washington Capitals and the NBA's Washington Wizards to northern Virginia have ``ended'' and the proposal to create a development district with a new arena for the teams ``will not...}