\entryitemWithDescription{\hskip 0pt{}Man charged with firebombing Wisconsin anti-abortion office}{https://apnews.com/article/609510133018a8d9f259d65b3348a979}{FILE - Threatening graffiti is seen on the exterior of Wisconsin Family Action offices in Madison, Wis., May 8, 2022. Investigators on Tuesday, March 28, 2023, finally captured the man they believe firebombed the prominent Wisconsin anti...}

\entryitemWithDescription{\hskip 0pt{}Court backs victim's family in Adnan Syed's 'Serial' case}{https://apnews.com/article/0950d68b8b2807c4bbdf069824b5ad49}{FILE - Adnan Syed gets emotional as he speaks to reporters outside the Robert C. Murphy Courts of Appeal building after a hearing, Thursday, Feb. 2, 2023, in Annapolis, Md. A Maryland court did not give the family of the murder victim in...}

\entryitemWithDescription{\hskip 0pt{}Boy Scouts' \$2.4 billion bankruptcy plan upheld by judge}{https://apnews.com/article/f6359f826b98d471c290598573ebc5da}{FILE - A close up of a Boy Scout uniform is photographed on Feb. 4, 2013, in Irving, Texas. On Tuesday, March 28, 2023, a federal district court judge upheld the approval of a \$2.4 billion bankruptcy reorganization plan aimed at...}

\entryitemWithDescription{\hskip 0pt{}AP sources: Judge rules Pence must testify before grand jury}{https://apnews.com/article/07bdd3e97230dc28787f0becb98bcb4b}{FILE - Former Vice President Mike Pence speaks to reporters before the MockCon event at University Chapel at Washington and Lee University, March 21, 2023, in Lexington, Va. A federal judge has ruled that Pence will have to testify before...}

\entryitemWithDescription{\hskip 0pt{}Pirates board oil tanker with 16 crew in Gulf of Guinea}{https://apnews.com/article/7ec2963bd23bd61bbd2a2722915cec61}{DAKAR, Senegal (AP) --- Pirates have boarded a Liberian-flagged oil tanker with 16 crew members in West Africa\textquotesingle s Gulf of Guinea, the Danish vessel owner said Tuesday. The attack took place southwest of Port Pointe-Noire...}

\entryitemWithDescription{\hskip 0pt{}Minnesota youth vaping trial of e-cigarette maker Juul opens}{https://apnews.com/article/1c79b3154edd7791166679463cb4ac7b}{FILE - Minnesota Attorney General Keith Ellison speaks at a press conference at the State Capitol on Dec. 4, 2019, in St. Paul, Minn. Ellison is slated to lead off opening statements expected for Tuesday, March 28, 2023, in his state...}

\entryitemWithDescription{\hskip 0pt{}Their stories were lost to slavery. Now DNA is writing them}{https://apnews.com/article/c0aeabe3c0ab74ea34c074ba20479d99}{Crystal Kornickey holds up casts of her hands in a studio at the Gibbes Museum of Art in Charleston, S.C., on Thursday, Feb. 16, 2023. She is one of 36 people whose hands will be cast in bronze for a memorial to the likely enslaved people...}

\entryitemWithDescription{\hskip 0pt{}FTX founder Bankman-Fried charged with paying \$40M bribe}{https://apnews.com/article/0f9ed9ae6353c802416a98eb2ff94218}{FILE --- FTX founder Sam Bankman-Fried leaves Manhattan federal court in New York, Feb. 16, 2023. On Tuesday, Bankman-Fried is accused in new indictment of paying \$40 million bribe to unlock frozen crypto in China. (AP Photo/John...}

\entryitemWithDescription{\hskip 0pt{}MLB The Show breaks barrier with Negro League players}{https://apnews.com/article/4f85545eafefe219215c8df295a76785}{This image released by Sony Interactive Entertainment shows a digital rendering of Cuban baseball player Martín Dihigo from the game MLB The Show 23. The franchise has inserted some of the greatest Negro League players into the 2023...}

\entryitemWithDescription{\hskip 0pt{}Poll: Religious service attendance a bit down after pandemic}{https://apnews.com/article/20d2d7c26c77dcc7797c35ed479fd34a}{FILE - The Rev. Manuel Rodriguez sits in the pews of his church, Our Lady of Sorrows, on March 5, 2021, in the Queens borough of New York. A new survey by the Pew Research Center, Tuesday, March 28, 2023, says in-person attendance at...}

\entryitemWithDescription{\hskip 0pt{}Russia convicts father of teen who drew antiwar picture}{https://apnews.com/article/7ef43a8fb8f0110638b96a677a222b2b}{Alexei Moskalyov sits in a courtroom in Yefremov, Tula region, some 300 kilometers (186 miles) south of Moscow, Russia, Monday, March 27, 2023. A court in Russia on Tuesday convicted a single father over social media posts criticizing the...}

\entryitemWithDescription{\hskip 0pt{}US makes corporate transparency commitment with 20 nations}{https://apnews.com/article/9cbd998535d60a8f439243c5d3157d34}{Treasury Secretary Janet Yellen arrives to speak during an anti-corruption panel discussion as part of the 2023 Summit for Democracy at the Treasury Department, Tuesday, March 28, 2023, in Washington. (AP Photo/Andrew Harnik) WASHINGTON...}

\entryitemWithDescription{\hskip 0pt{}What we know about the Covenant school shooting in Nashville}{https://apnews.com/article/c46251973f815a3862312d6131cd552e}{Families leave a reunification site in Nashville, Tenn., Monday, March 27, 2023 after several children were killed in a shooting at Covenant School in Nashville. The suspect is dead after a confrontation with police. (AP Photo/John Amis...}