\entryitemWithDescription{\hskip 0pt{}Melinda Wilson, wife, manager and `savior' of musician Brian Wilson, is dead at 77}{https://apnews.com/article/b0ad07057942bbc56eab5ae4d683577a}{NEW YORK (AP) --- Melinda Ledbetter Wilson, the longtime wife and manager of Brian Wilson whom the Beach Boys co-founder often credited for stabilizing his famously troubled life, has died at age 77. Wilson died Tuesday at the couple's...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl-bound Chiefs tight end Travis Kelce to Taylor Swift: `Thanks for joining the team'}{https://apnews.com/article/9accf85733377ae70456d163495c0801}{KANSAS CITY, Mo. (AP) --- Travis Kelce is happy to have Taylor Swift on the Kansas City Chiefs bandwagon heading to the Super Bowl. As if that wasn't evident by their on-field smooch after the AFC title game. On the latest episode of...}

\entryitemWithDescription{\hskip 0pt{}Eyewitness to killing of Run-DMC's Jam Master Jay tells jury: ''Then I see Jay just fall'}{https://apnews.com/article/7a9c89f35f06e45f6c40937deaa02ca1}{For about 15 years, Uriel Rincon told authorities he didn't recognize the gunman who he saw kill Run-DMC's Jam Master Jay in the rap star's recording studio. But on Wednesday, Rincon --- who was himself wounded in the gunfire --- pointed...}

\entryitemWithDescription{\hskip 0pt{}Early money heavily on Kansas City Chiefs to repeat as Super Bowl champions}{https://apnews.com/article/0301831c7735b7cc78c093fc77d957c4}{LAS VEGAS (AP) --- Minutes after beating Baltimore 17-10 on Sunday to clinch a spot in the Super Bowl, Travis Kelce had a message to send. ``The Chiefs are still the Chiefs,'' Kelce said. Bettors agree. The early money is heavily on...}

\entryitemWithDescription{\hskip 0pt{}Music from Memphis' Stax Records, Detroit's Motown featured in online show}{https://apnews.com/article/a754d8188b96a0b15b7bf7cf872c15af}{MEMPHIS, Tenn. (AP) --- Fans of the soulful sounds of Detroit's Motown and Memphis' Stax Records will be able to enjoy music from both brands in the same place if they watch and listen to a free, online show streaming during Black History...}

\entryitemWithDescription{\hskip 0pt{}Man accused of destroying Satanic Temple display at Iowa Capitol is now charged with hate crime}{https://apnews.com/article/cb182f8b3235d25fd4949e0b2e4f43f7}{DES MOINES, Iowa (AP) --- A Mississippi man accused of destroying a statue of a pagan idol at Iowa's state Capitol is now being charged with a hate crime. The statue was brought to the Capitol by the Satanic Temple of Iowa under state...}

\entryitemWithDescription{\hskip 0pt{}A grainy sonar image reignites excitement and skepticism over Earhart's final flight}{https://apnews.com/article/e7d4f7fdfe9ff32c663bb396d33420a0}{COLUMBIA, S.C. (AP) --- A grainy sonar image recorded by a private pilot has reinvigorated interest in one of the past century's most alluring mysteries: What happened to Amelia Earhart when her plane vanished during her flight around the...}

\entryitemWithDescription{\hskip 0pt{}2024 Grammys Preview: Five big questions ahead of Sunday's award show}{https://apnews.com/article/94debb1a9bff1fdb73a17c64e81f0c47}{LOS ANGELES (AP) --- The 66th annual Grammy Awards are on Sunday, airing live from Los Angeles' Crypto.com Arena on CBS and Paramount+. So, what can viewers expect? Some new, some old. Executive producers Raj Kapoor, Ben Winston, and...}

\entryitemWithDescription{\hskip 0pt{}Hal Buell, who led AP's photo operations from darkroom era into the digital age, dies at 92}{https://apnews.com/article/78798eb6802044e087ddb9bf003edabb}{SUNNYVALE, Calif. (AP) --- Hal Buell, who led The Associated Press' photo operations from the darkroom era into the age of digital photography over a four-decade career with the news organization that included 12 Pulitzer Prizes and...}

\entryitemWithDescription{\hskip 0pt{}David Rubenstein has a deal to buy the Baltimore Orioles for \$1.725 billion, AP source says}{https://apnews.com/article/dffd7b500dc97d432ad1e739df656a67}{Carlyle Group Inc. co-founder David Rubenstein has reached an agreement to buy the Baltimore Orioles for \$1.725 billion, according to a person with knowledge of the deal. The person spoke to The Associated Press on condition of anonymity...}

\entryitemWithDescription{\hskip 0pt{}Spring a leak? Google will find it through a new partnership aimed at saving water in New Mexico}{https://apnews.com/article/604d14a4105524f598b6d0aab95aa6bf}{ALBUQUERQUE, N.M. (AP) --- New Mexico is teaming up with Google to hunt for leaky water pipes using satellite imagery as the drought-stricken state prepares for a future in which growing demand puts more pressure on already dwindling...}

\entryitemWithDescription{\hskip 0pt{}Western monarch butterflies overwintering in California dropped by 30\% last year, researchers say}{https://apnews.com/article/56955657a275ba26dc3197c6bb7482ac}{SAN FRANCISCO (AP) --- The number of western monarch butterflies overwintering in California dropped by 30\% last year, likely due to how wet it was, researchers said Tuesday. Volunteers who visited sites in California and Arizona around...}

\entryitemWithDescription{\hskip 0pt{}Burned remnants of prized Jackie Robinson statue found after theft from public park in Kansas}{https://apnews.com/article/45c08bbbd29322c05e6136a67f687459}{Fire crews found the burned remnants Tuesday of a prized bronze statue of Jackie Robinson that was stolen last week from a public park in Kansas, authorities said. The Wichita fire department received a call around 8:40 a.m. about a trash...}