\entryitemWithDescription{\hskip 0pt{}Scherzer tests pitch clock limits, gets quick-pitch balk}{https://apnews.com/article/7270c957ab32faf804839f501982a6bd}{New York Mets starting pitcher Max Scherzer throws during the third inning of a spring training baseball game against the Washington Nationals, Friday, March 3, 2023, in Port St. Lucie, Fla. (AP Photo/Lynne Sladky) Max Scherzer has...}

\entryitemWithDescription{\hskip 0pt{}Murdaugh's fast conviction sealed by his testimony: experts}{https://apnews.com/article/705e6ca540e81015775a1ac488375998}{FILE - Defendant Alex Murdaugh is cross examined by prosecutor Creighton Waters while testifying in his murder trial at the Colleton County Courthouse, Feb. 24, 2023, in Walterboro, S.C. Prosecutors in the case against Murdaugh had no...}

\entryitemWithDescription{\hskip 0pt{}Doctor: Lesion removed from Biden's chest was cancerous}{https://apnews.com/article/c8868eec1e99b28a9cf497ee39942359}{FILE - President Joe Biden arrives at Walter Reed National Military Medical Center in Bethesda, Thursday, Feb. 16, 2023. A skin lesion removed from Biden\textquotesingle s chest last month was a basal cell carcinoma --- a common form of...}

\entryitemWithDescription{\hskip 0pt{}The implications of Walgreens' decision on abortion pills}{https://apnews.com/article/fd2663ace286c3c48b9c66a74c652ef4}{FILE - The entrance to a Walgreens is seen on Oct. 14, 2022, in Boston. Walgreens said Thursday, March 2, 2023, that it will not start selling mifepristone, an abortion pill, in 20 states that had warned of legal consequences if it did...}

\entryitemWithDescription{\hskip 0pt{}Can the dogs of Chernobyl teach us new tricks on survival?}{https://apnews.com/article/f36bfae17b541bd6c3fba2b4abc0b0c6}{This photo taken by Timothy Mousseau shows dogs in the Chernobyl area of Ukraine on Oct. 3, 2022. More than 35 years after the world\textquotesingle s worst nuclear accident, the dogs of Chernobyl roam among decaying, abandoned buildings...}

\entryitemWithDescription{\hskip 0pt{}US sending bridge-launchers to Ukraine for spring fight}{https://apnews.com/article/0e52e87ade3d2300da8be14a3ebcc9ff}{Ukrainian servicemen attend combat training in Kyiv region, Ukraine, Friday, March. 3, 2023. (AP Photo/Efrem Lukatsky) WASHINGTON (AP) --- The U.S. announced a new \$400 million military aid package for Ukraine on Friday that for the...}

\entryitemWithDescription{\hskip 0pt{}Black Vietnam vet finally awarded Medal of Honor for bravery}{https://apnews.com/article/d119c97f491e5f59cca3bc2f0b549648}{An 83-year-old Vietnam veteran is finally getting his due. President Joe Biden awarded the Medal of Honor to Ret. Col. Paris Davis, one of the first Black officers to lead a Special Forces team in combat, nearly 60 years after he was...}

\entryitemWithDescription{\hskip 0pt{}Fire at Indonesian oil depot kills 17; thousands evacuated}{https://apnews.com/article/f548e3d8185c9a9f4bc02b8bb8490309}{Rescuers carry the body of a victim of a fire in Jakarta, Indonesia, Friday, March 3, 2023. A large fire broke out at a fuel storage depot in Indonesia's capital on Friday, killing several people, injuring dozens of others and forcing the...}

\entryitemWithDescription{\hskip 0pt{}Amazon pauses construction on 2nd headquarters in Virginia}{https://apnews.com/article/91395dd669f011b547196575db7d5c18}{This artist rendering provided by Amazon shows the next phase of the company\textquotesingle s headquarters redevelopment to be built in Arlington, Va. Amazon is pausing construction of its second headquarters in Virginia following the...}

\entryitemWithDescription{\hskip 0pt{}A decade under Maduro, migration marks Venezuelans' lives}{https://apnews.com/article/ea00ba8d5127bad7474da19ce33ec320}{A man peaks over the crowd waiting to cross the border into Colombia through the Simon Bolivar bridge in San Antonio del Tachira, Venezuela Sunday July 17, 2016. (AP Photo/Ariana Cubillos) Few Venezuelans have not had their lives touched...}

\entryitemWithDescription{\hskip 0pt{}NOT REAL NEWS: A look at what didn't happen this week}{https://apnews.com/article/5177158ebaa1306a6469a95313b94500}{FILE - In this June 11, 2009, file photo, the logo of the World Health Organization is seen at the WHO headquarters in Geneva, Switzerland. On Friday, March 3, 2023, The Associated Press reported on stories circulating online incorrectly...}

\entryitemWithDescription{\hskip 0pt{}US to focus bison restoration on expanding tribal herds}{https://apnews.com/article/6f5ad9227c70377a94a2a4efc809f3d8}{FILE - Bison awaiting transfer to Native American tribes walk in a herd inside a corral at Badlands National Park, on Oct. 13, 2022, near Wall, S.D. U.S. Interior Secretary Deb Haaland on Friday is expected to announce a secretarial order...}

\entryitemWithDescription{\hskip 0pt{}Abortion clinics crossing state borders not always welcome}{https://apnews.com/article/7dfed02251e668fdded6ac97ae7fd281}{Brass markers, marking the state line between Bristol, Tenn. and Bristol, Va., line State Street in Bristol, Va., on Thursday, Feb. 23, 2023. Residents in southwestern Virginia have battled for months over whether abortion clinics limited...}