\entryitemWithDescription{\hskip 0pt{}Netanyahu reverses firing of defense minister amid tension}{https://apnews.com/article/3fd670724b7c8f20ce8095e342695214}{Israeli Prime Minister Benjamin Netanyahu speaks to the media during a press conference, in Tel Aviv, Israel, Monday, April 10, 2023. (AP Photo/Ohad Zwigenberg) JERUSALEM (AP) --- Israeli Prime Minister Benjamin Netanyahu on Monday...}

\entryitemWithDescription{\hskip 0pt{}Commanders settle with Washington, D.C., on ticket deposits}{https://apnews.com/article/0f44ab7607f17c89413995f1890e3562}{FILE - Fans watch as the Washington Commanders face the Jacksonville Jaguars in an NFL football game, Sunday, Sept. 11, 2022, in Landover, Md. The Washington Commanders have settled a suit with the District of Columbia's attorney general'...}

\entryitemWithDescription{\hskip 0pt{}Blumenthal to leave hospital after surgery for parade injury}{https://apnews.com/article/f5cc3d61e64ee5457a1ad4adf585531e}{FILE - Sen. Richard Blumenthal, D-Conn., speaks during a news conference on Feb. 16, 2023, on Capitol Hill in Washington. Sen. Blumenthal is expected to be discharged from a hospital following surgery on a minor leg fracture he suffered...}

\entryitemWithDescription{\hskip 0pt{}California storms hit beekeepers, but honey outlook's sweet}{https://apnews.com/article/a643ed7ce3a32209e339d97b8361c1c5}{Beekeeper Gene Brandi tends to his hives at a cherry tree orchard in San Juan Bautista, Calif., Thursday, Aug. 6, 2023. (AP Photo/Terry Chea) During California\textquotesingle s prolonged, wet winter, beekeeper Gene Brandi said he had to...}

\entryitemWithDescription{\hskip 0pt{}WNBA adding charter flights for playoffs, back-to-back games}{https://apnews.com/article/13a1f959ad34f9ebca2b2e1465d9045e}{FILE - WNBA commissioner Cathy Engelbert waves to the crowd before Game 2 in the semifinals of the WNBA playoffs between the Las Vegas Aces and the Phoenix Mercury Thursday, Sept. 30, 2021, in Las Vegas. The WNBA is adding charter flights...}

\entryitemWithDescription{\hskip 0pt{}Rutgers faculty go on strike, picket outside classes}{https://apnews.com/article/a9f1ad0ef9e16ae79e9a1af1bf74861f}{Strikers march in front of Rutgers\textquotesingle{} buildings in New Brunswick, N.J., Monday, April 10, 2023. Thousands of professors, part-time lecturers and graduate student workers at New Jersey\textquotesingle s flagship university...}

\entryitemWithDescription{\hskip 0pt{}Dalai Lama apologizes after video shows him kissing boy}{https://apnews.com/article/6fd0635673f6830578b084f550dc69ca}{Tibetan spiritual leader the Dalai Lama in a ceremonial yellow hat arrives at the Tsuglakhang temple to give a sermon in Dharamshala, India, Tuesday, March 7, 2023. Tibetan spiritual leader Dalai Lama apologized Monday after a video...}

\entryitemWithDescription{\hskip 0pt{}78-year-old bank heist suspect: 'I didn't mean to scare you'}{https://apnews.com/article/fcaa66a6c78eefc0e7bdf1df4a88c8c2}{HARRISONVILLE, Mo. (AP) --- A 78-year-old woman with two past bank robbery convictions faces new charges after authorities allege she handed a teller a note that said ``I didn't mean to scare you'' during a recent Missouri heist. Bonnie...}

\entryitemWithDescription{\hskip 0pt{}Cubans seek solutions and solace in Santería amid crises}{https://apnews.com/article/e7bf183a2c2bdbe2e3ed4ff85a142b31}{A doll depicting the Yoruba deity Yemayá is propped up on a chair before the start of a Santería ceremony in the home of Mandy Arrazcaeta, in Havana, Cuba, Sunday, Nov. 13, 2022. A fusion of African religions and Catholicism, Santería was...}

\entryitemWithDescription{\hskip 0pt{}Blumenthal breaks leg at UConn parade, to undergo surgery}{https://apnews.com/article/57b735f4a2ee7c91390724f1fc994c6f}{FILE - Sen. Richard Blumenthal, D-Conn., speaks during a news conference on Feb. 16, 2023, on Capitol Hill in Washington. Sen. Blumenthal is expected to be discharged from a hospital following surgery on a minor leg fracture he suffered...}

\entryitemWithDescription{\hskip 0pt{}3 taken to hospital after Delaware mall shooting}{https://apnews.com/article/361706c3aa2306607adf7674efdb5f87}{CHRISTIANA, Del. (AP) --- A Delaware mall shooting left three people injured and forced shoppers to evacuate as police investigate. Delaware State Police said authorities do not have a suspect in custody in the shooting at the Christiana...}

\entryitemWithDescription{\hskip 0pt{}Browns' Watson scheduled to give deposition in civil lawsuit}{https://apnews.com/article/059e16686f7ab19ba4b33a1dec098362}{FILE - Cleveland Browns quarterback Deshaun Watson (4) look son during an NFL football game against the Cincinnati Bengals, Tuesday, Dec. 13, 2022, in Cincinnati. The Browns quarterback is scheduled to give a deposition on Monday, April...}

\entryitemWithDescription{\hskip 0pt{}Texas gov. seeks to pardon Army sergeant convicted of murder}{https://apnews.com/article/fa7feeadf552fe01bd6394d13de4178d}{FILE - This booking photo provided by the Austin, Texas, Police Department shows U.S. Army Sgt. Daniel Perry. Perry was convicted of murder for fatally shooting an armed protester in 2020 during nationwide protests against police violence...}