\entryitemWithDescription{\hskip 0pt{}Virginia city repeals ban on psychic readings as industry grows and gains more acceptance}{https://apnews.com/article/3d687dd365bdf799c4d9fd7ce0589fb9}{NORFOLK, Va. (AP) --- Ashley Branton has earned a living as a psychic medium for seven years, helping a growing number of people with heavy choices about toxic relationships, home purchases and cross-country moves. And while the tarot...}

\entryitemWithDescription{\hskip 0pt{}Move over grizzlies and wolves: Yellowstone visitors hope to catch a glimpse of rare white buffalo}{https://apnews.com/article/dd1d0613674df9879e81283d2a9f09a6}{YELLOWSTONE NATIONAL PARK, Wyo. (AP) --- Standing at the edge of a bluff overlooking the Lamar River in Yellowstone National Park, TJ Ammond stared through binoculars at hundreds of buffalo dotting the verdant valley below. Tan-colored...}

\entryitemWithDescription{\hskip 0pt{}Her dying husband worried she'd have money troubles. Then she won the lottery}{https://apnews.com/article/69183774077eee747454cd959aa66636}{FREEPORT, Pa. (AP) --- In the weeks before his death, Karen Coffman's husband worried she might have money troubles after he was gone. But two weeks before he died in April of complications from a brain tumor, the Pennsylvania woman...}

\entryitemWithDescription{\hskip 0pt{}Tejano singer and TV host Johnny Canales, who helped launch Selena's career, dies}{https://apnews.com/article/57f08320807cfb7977d624a28319f5e6}{Tejano singer and longtime television music show host Johnny Canales has died. He was 77. Canales' family confirmed his death in a statement posted Thursday on the Johnny and Nora Canales Show Facebook page. The post did not provide a...}

\entryitemWithDescription{\hskip 0pt{}NASA's Voyager 1, the most distant spacecraft from Earth, is doing science again after problem}{https://apnews.com/article/1b4a1f9f9adfa23d60b539301b3f035b}{DALLAS (AP) --- NASA's Voyager 1, the most distant spacecraft from Earth, is sending science data again. Voyager 1's four instruments are back in business after a computer problem in November, the Jet Propulsion Laboratory said this week...}

\entryitemWithDescription{\hskip 0pt{}Microsoft delays controversial AI Recall feature on new Windows computers}{https://apnews.com/article/6ba8df3f22e9fca599d20f2d5770cd95}{REDMOND, Wash. (AP) --- New laptops equipped with Microsoft Windows start shipping to customers next week without a flagship feature called Recall that drew concerns about privacy and cybersecurity. Microsoft CEO Satya Nadella touted the...}

\entryitemWithDescription{\hskip 0pt{}How do cicadas make their signature sound, so eerie and amazingly loud?}{https://apnews.com/article/14dafdf024b28967ae5d68b8dbc45801}{WHEATON, Ill. (AP) --- The most noticeable part of the cicada invasion blanketing the central United States is the sound --- an eerie, amazingly loud song that gets in a person's ears and won't let much else in. ``It's beautiful chaos,''...}

\entryitemWithDescription{\hskip 0pt{}R.E.M. reunite at Songwriters Hall of Fame ceremony also honoring Timbaland and Steely Dan}{https://apnews.com/article/40a0909a1e8d403e3bcbe03a7bab738c}{NEW YORK (AP) --- A comet must have landed at the 2024 Songwriters Hall of Fame induction ceremony. The members of R.E.M. had joked only hours before it would take ``a comet'' to get the band to perform together one last time. Yet there...}

\entryitemWithDescription{\hskip 0pt{}Chinese soccer fans are pouring money into a food stall run by Singapore's goalkeeper. Here's why}{https://apnews.com/article/1900d8995dd0fe3c2f4ffea9645989ee}{Chinese soccer fans have poured their love --- and money --- into a Singaporean goalkeeper's food stall after his performance in a game this week indirectly helped China advance to the third qualifying round for the World Cup in 2026...}

\entryitemWithDescription{\hskip 0pt{}Barkov, Bobrovsky and the Panthers beat the Oilers 4-3 to move within win of Stanley Cup title}{https://apnews.com/article/40cf3fc25c1935c1ca18f39ac096391a}{EDMONTON, Alberta (AP) --- Aleksander Barkov led the way offensively, Sergei Bobrovsky was in peak form in goal once again and the Florida Panthers are on the verge of lifting the Stanley Cup. Barkov set up a goal and scored another...}

\entryitemWithDescription{\hskip 0pt{}The FAA and NTSB are investigating an unusual rolling motion of a Southwest Airlines Boeing 737 Max}{https://apnews.com/article/0f9a5d59e54665902b2a49347164f1af}{WASHINGTON (AP) --- Federal officials said Thursday they are investigating an unusual rolling motion on a Southwest Airlines Boeing 737 Max that might have been caused by a damaged backup power-control unit. The Federal Aviation...}

\entryitemWithDescription{\hskip 0pt{}Utah Hockey Club will be the name of the NHL team in Salt Lake City for its inaugural season}{https://apnews.com/article/83d8a28225ac391c6ded4dea32049e4a}{Utah Hockey Club will be the name of the NHL team playing its games in Salt Lake City beginning this fall, with a long-term identity still to come. Smith Entertainment Group announced the move Thursday and unveiled the initial logos and...}

\entryitemWithDescription{\hskip 0pt{}Sen. John Fetterman was at fault in car accident and seen going `high rate of speed,' police say}{https://apnews.com/article/d714084a1b17a23f233f2733c5694b5a}{HARRISBURG, Pa. (AP) --- Pennsylvania Sen. John Fetterman was seen driving at a ``high rate of speed'' on Sunday morning just before he rear-ended another car on Interstate 70 in Maryland, according to a state police report. The police...}