\entryitemWithDescription{\hskip 0pt{}LSU cornerback Javien Toviano arrested on accusation of video voyeurism, authorities say}{https://apnews.com/article/e2ff0cff997879d9d855c27af60bd69f}{BATON ROUGE, La. (AP) --- LSU sophomore cornerback Javien Toviano surrendered to authorities Sunday on charges of video voyeurism, the East Baton Rouge Parish sheriff's office said. Toviano, 19, of Arlington, Texas, is accused of...}

\entryitemWithDescription{\hskip 0pt{}Beltré, Helton, Mauer and Leyland inducted into the Baseball Hall of Fame}{https://apnews.com/article/d65bdff9661e0c61af50801a22c778a3}{COOPERSTOWN, N.Y. (AP) --- Adrian Beltré, Joe Mauer and Todd Helton were pegged as athletic phenoms from a young age and all three lived up to expectations with their induction to the Baseball Hall of Fame on Sunday. The Los Angeles...}

\entryitemWithDescription{\hskip 0pt{}Hollywood reacts to Joe Biden exiting the presidential race}{https://apnews.com/article/0edc44c84e191a846ecf6a7067d424d7}{Hollywood was quick to react to the news that President Joe Biden was ending his bid for reelection and endorsing Vice President Kamala Harris. Barbra Streisand, a Democratic supporter, wrote Sunday on X that ``we should be grateful for...}

\entryitemWithDescription{\hskip 0pt{}`Twisters' whips up \$80.5 million at box office, while `Deadpool \& Wolverine' looms}{https://apnews.com/article/316b848fac02b7ea09ae60a1dadffbef}{Moviegoers ran toward the tornadoes this weekend, propelling `` Twisters '' to a blockbuster opening. The standalone sequel to the 1996 hit made \$80.5 million in ticket sales from 4,151 theaters in North America, according to studio...}

\entryitemWithDescription{\hskip 0pt{}Frozen treats, cold showers and lots of ice; Florida zoo works to protect animals from summer heat}{https://apnews.com/article/a2b6facf6b1993e69c20ff582adad107}{WEST PALM BEACH, Fla. (AP) --- Malayan tigers and Aldabra tortoises are native to hot and humid lands, but that doesn't mean they don't enjoy a frozen treat on a hot Florida summer day. Temperatures in South Florida this month have...}

\entryitemWithDescription{\hskip 0pt{}Ernest Hemingway fans celebrate the author's 125th birthday in his beloved Key West}{https://apnews.com/article/df34dc9b8642c7c5f923360aaa04e604}{KEY WEST, Fla. (AP) --- Ernest Hemingway spent the 1930s in Key West, Florida, and more than six decades after his death, fans, scholars and relatives continue to congregate on the island city to celebrate the author's award-winning...}

\entryitemWithDescription{\hskip 0pt{}Arike Ogunbowale and Caitlin Clark lead WNBA All-Stars to 117-109 win over U.S. Olympic team}{https://apnews.com/article/05d23aa56556dcf447edff0fea39643f}{PHOENIX (AP) --- Arike Ogunbowale was the dominant scorer on the floor. Caitlin Clark was the best passer. Angel Reese was her usual double-double machine. The U.S. may still have the best team at the Olympics, but at the All-Star Game...}

\entryitemWithDescription{\hskip 0pt{}89-year-old comedian recovering after she was randomly punched on New York street}{https://apnews.com/article/a78ef6ed281e106d6699f4a044394571}{NEW YORK (AP) --- An 89-year-old comedian is recovering after being randomly punched and knocked to the ground while waiting to cross a street in New York earlier this month. D'yan Forest said she had just stopped at a coffee shop and was...}

\entryitemWithDescription{\hskip 0pt{}Utah scraps untested lethal drug combination for man's August execution}{https://apnews.com/article/c742fd2dd99daa7611157fbc24155776}{Utah officials said Saturday that they are scrapping plans to use an untested lethal drug combination in next month's planned execution of a man in a 1998 murder case. They will instead seek out a drug that's been used previously in...}

\entryitemWithDescription{\hskip 0pt{}A fire severely damages the historic First Baptist Dallas church sanctuary}{https://apnews.com/article/f5559a87624a833944e4f3564f02de2f}{A fire all but destroyed the historic church sanctuary at First Baptist Dallas, sending smoke billowing over the city but causing no deaths or injuries, Dallas firefighters said. The fire in the Texas Historic Landmark, a Victorian-style...}

\entryitemWithDescription{\hskip 0pt{}Remnants of lives interrupted by war half a century ago captured in Cyprus' buffer zone}{https://apnews.com/article/84aaf7f59954edee3442a4b021d2d122}{NICOSIA, Cyprus (AP) --- A rickety piano leans crookedly against a peeling apartment wall, pots and pans filled with dust rest on a stove that has seen much better days and a book, its pages turning yellow with time, lies open next to a...}

\entryitemWithDescription{\hskip 0pt{}Disneyland workers authorize potential strike ahead of continued contract negotiations}{https://apnews.com/article/11b477abf4a84d1e0af6c1186810dfa5}{NEW YORK (AP) --- Thousands of workers at Disney's theme park and resort properties in California voted late Friday to authorize a potential strike, as contract negotiations drag on. The strike authorization was approved by an...}

\entryitemWithDescription{\hskip 0pt{}Do you really have to wait to go swimming after eating?}{https://apnews.com/article/49662b91c8201c252e24b5a47d415ad8}{Did your parents warn you against jumping in the pool right after eating? They were misguided. In most cases, there's no need to wait at least 30 minutes after eating to go for a swim, doctors say. That old warning stems from worry that...}