\entryitemWithDescription{\hskip 0pt{}Mother of man who killed Gabby Petito said in letter she would help son 'dispose of a body'}{https://apnews.com/article/f78819e0f7059373af700b59788945e9}{FILE - Gabby Petito\textquotesingle s mother Nichole Schmidt, wipes a tear from her face during a news conference on Nov. 3, 2022, in Salt Lake City. A letter written by Roberta Laundrie to her late son Brian Laundrie can be used by the...}

\entryitemWithDescription{\hskip 0pt{}Céline Dion cancels European concerts 'until I'm really ready to be back on stage'}{https://apnews.com/article/5e07d2642722eb4e2b14ddf5ed3181bd}{FILE - Singer Celine Dion performs during her first World Tour called Courage in Quebec City, Montreal, Canada on Sept. 18, 2019. Dion has canceled all her scheduled tour dates through April 2024 as she battles a rare neurological...}

\entryitemWithDescription{\hskip 0pt{}New British Cycling rules bar transgender women from competing in elite female events}{https://apnews.com/article/803bb9f13112519f1715dc125ef3b3ea}{FILE - Jon Dutton, the then Rugby League World Cup 2021 Chief Executive speaks at a media event to mark the forthcoming Rugby League World Cup in Manchester, England, Oct. 10, 2022. Riders who were born male will be prevented from racing...}

\entryitemWithDescription{\hskip 0pt{}Hugh Grant's lawsuit alleging illegal snooping by The Sun tabloid cleared for trial}{https://apnews.com/article/537b9aac9486020ce6317edbc2d06b7e}{FILE - Hugh Grant arrives at the 23rd annual Screen Actors Guild Awards at the Shrine Auditorium \& Expo Hall in Los Angeles, Sunday Jan. 29, 2023. A London court on Friday rejected an attempt by the publisher of The Sun tabloid to throw...}

\entryitemWithDescription{\hskip 0pt{}Unexploded WWII bomb forces evacuation of 2,500 residents in Poland}{https://apnews.com/article/3957fd8ddf7913bd77d09860ceeaaae4}{WARSAW, Poland (AP) --- A large unexploded bomb from World War II discovered in the Polish city of Wroclaw forced the evacuation of 2,500 residents on Friday. The bomb weighing 250 kilograms (550 pounds) was found near a railway overpass...}

\entryitemWithDescription{\hskip 0pt{}2 more Oath Keepers sentenced to prison terms for Jan. 6 Capitol attack}{https://apnews.com/article/73dcb93b0bcb6c33c88a812e6d7d811f}{FILE - This artist sketch depicts the trial of Oath Keepers leader Stewart Rhodes and four others charged with seditious conspiracy in the Jan. 6, 2021, Capitol attack, in Washington, Oct. 6, 2022. Shown above are, witness John Zimmerman...}

\entryitemWithDescription{\hskip 0pt{}California's epic melting snowpack means cold, deadly torrents ahead of Memorial Day weekend}{https://apnews.com/article/64451794a83035dd36411e0f6e198d58}{FILE - Fresno County Sheriff\textquotesingle s Office search and rescue team members return upriver to a boat launch near the Pine Flat Dam near Sanger, Calif., after reports that a boy\textquotesingle s body had been recovered on the...}

\entryitemWithDescription{\hskip 0pt{}Acclaimed Cleveland school dance teacher convicted of raping students, could face life in prison}{https://apnews.com/article/9313cd78a33307c741df9cf50bc3ffb3}{CLEVELAND (AP) --- A former school dance teacher in Cleveland faces up to life prison after being convicted Thursday of raping six teenage students and sexually abusing two others. Jurors in Cuyahoga County Common Pleas Court also found...}

\entryitemWithDescription{\hskip 0pt{}Minnesota governor signs paid family and medical leave act to give workers up to 20 weeks off}{https://apnews.com/article/2f1a16a28bcac2c78f13c86838eb84a9}{Democratic Minnesota Gov. Tim Walz jokes with kids as he shows off a bill he signed at the State Capitol in St. Paul, Minn., on Thursday, May 25, 2023, to establish a paid family and medical leave program in the state starting in 2026...}

\entryitemWithDescription{\hskip 0pt{}Tom Hanks urges Harvard grads to defend the truth and resist indifference}{https://apnews.com/article/3854c7084ffc98487e52bdcad67c800d}{Actor Tom Hanks delivers a commencement address during Harvard University commencement exercises on the school\textquotesingle s campus, Thursday, May 25, 2023, in Cambridge, Mass. (AP Photo/Steven Senne) CAMBRIDGE, Mass. (AP) --- Tom...}

\entryitemWithDescription{\hskip 0pt{}GOP field in Pennsylvania Senate race still wide open as hard-right state lawmaker says he won't run}{https://apnews.com/article/06a4a1ca16a0182ed25069d56e5e6c6d}{FILE - Pennsylvania Republican gubernatorial candidate Doug Mastriano speaks to supporters during an election night campaign event at the Penn Harris Hotel in Camp Hill, Pa., Nov. 8, 2022. Mastriano has said he will announce Thursday...}

\entryitemWithDescription{\hskip 0pt{}US study finds 1 in 10 get long COVID after omicron, starts identifying key symptoms}{https://apnews.com/article/cc9dcd473f0513e4e62aa7e24940577e}{FILE - This undated, colorized electron microscope image made available by the U.S. National Institutes of Health in February 2020 shows the Novel Coronavirus SARS-CoV-2, indicated in yellow, emerging from the surface of cells, indicated...}

\entryitemWithDescription{\hskip 0pt{}2 planes aborted landings in San Francisco when a Southwest jet taxied across their runways}{https://apnews.com/article/ec9df0e1a2ff8038992c4d152d8b2449}{FILE - Vehicles wait outside the international terminal at San Francisco International Airport in San Francisco on July 11, 2017. Two airliners aborted landings at San Francisco International Airport on May 19, 2023, after pilots spotted...}