\entryitemWithDescription{\hskip 0pt{}NBCUniversal CEO Shell departs over `inappropriate conduct'}{https://apnews.com/article/07bad3ee36d0eef660de9282cb88dcba}{FILE - Jeff Shell poses for a picture at the 2014 LA\textquotesingle s Promise Gala, Tuesday, Sept. 30, 2014, in Universal City, Calif. Shell, the chief executive of NBCUniversal, is departing the company after an investigation into...}

\entryitemWithDescription{\hskip 0pt{}Lizzo brings drag queens on stage, protesting Tennessee law}{https://apnews.com/article/c73bc8f777b28148dea90a3cca347701}{FILE - Lizzo arrives at the 65th annual Grammy Awards on Feb. 5, 2023, in Los Angeles. In a concert Friday, April 21, 2023 in Knoxville, Tenn., Lizzo filled the stage with drag queens in a glittery protest against the state...}

\entryitemWithDescription{\hskip 0pt{}Gunfire took their son at 20. Now it takes his daughter, 12}{https://apnews.com/article/74173049450d4915c71a25dc1b0c9f5c}{This image provided by Jeremy Stein shows Hartford Mayor Luke Bronin addressing a crowd gathering for a vigil on Saturday, April 22, 2023, on the same street where Se\textquotesingle Cret Pierce, 12, was shot in the head by a stray bullet...}

\entryitemWithDescription{\hskip 0pt{}Wahoo! `The Super Mario Bros. Movie' is No. 1 for third week}{https://apnews.com/article/5fff8c44f66627fa49fa4a630441fb26}{Jack Black arrives at the premiere of "The Super Mario Bros. Movie," Saturday, April 1, 2023, at Regal LA Live in Los Angeles. (Photo by Allison Dinner/Invision/AP) NEW YORK (AP) --- ``The Super Mario Bros. Movie'' continued to rack up...}

\entryitemWithDescription{\hskip 0pt{}Ex-Disney employee allegedly shot videos up women's skirts}{https://apnews.com/article/104cd805bbec63cc94adb27a7a0c5d65}{Cinderella Castle stands at the Magic Kingdom, at Walt Disney World, in Lake Buena Vista, Fla., Monday, April 3, 2023. (Joe Burbank/Orlando Sentinel via AP) ORLANDO, Fla. (AP) --- A former Walt Disney World employee is facing a charge...}

\entryitemWithDescription{\hskip 0pt{}Dying patients protest looming telehealth crackdown}{https://apnews.com/article/a6d5a0d3e923760f77cd246ea1927dd1}{Georgene White stands for a portrait with a photo of her mother, Teri Sheridan, in Belvidere, N.J., Thursday, April 20, 2023. At age 93, struggling with the effects of a stroke, heart failure and recurrent cancer, Sheridan was ready to...}

\entryitemWithDescription{\hskip 0pt{}39 bodies dug up in cult investigation of pastor in Kenya}{https://apnews.com/article/2a3dfeea30df8b841391bd5f1ef36783}{Police and local residents load the exhumed bodies of victims of a religious cult into the back of a truck in the village of Shakahola, near the coastal city of Malindi, in southeastern Kenya Sunday, April 23, 2023. Dozens of bodies have...}

\entryitemWithDescription{\hskip 0pt{}Struggling Bed Bath \& Beyond files for bankruptcy protection}{https://apnews.com/article/a597c1013b2f641b7b32e87ad81be6d8}{The entrance to a Bed Bath \& Beyond store is seen in Anchorage, Alaska, on Sunday, April 23, 2023. One of the original big box retailers, the company filed for bankruptcy protection on Sunday, following years of dismal sales and losses...}

\entryitemWithDescription{\hskip 0pt{}Dragon bursts into flames during popular Disneyland show}{https://apnews.com/article/d8bb15285b004f44134e55ddf4d99a58}{This photo courtesy of Shawna Bell shows a fire during the ``Fantasmic" show in the Tom Sawyer Island section of Disneyland resort in Anaheim, Calif., on Saturday, April 22, 2023. (Courtesy Shawna Bell via AP) ANAHEIM, Calif. (AP...}

\entryitemWithDescription{\hskip 0pt{}A deeply divided Israel limps toward its 75th birthday}{https://apnews.com/article/46fe485eb65b782e0558587641e03505}{FILE - Tens of thousands of Israelis protest against plans by Prime Minister Benjamin Netanyahu\textquotesingle s government to overhaul the judicial system in Tel Aviv, Israel, Saturday, April 15, 2023. As Israel turns 75, it has much to...}

\entryitemWithDescription{\hskip 0pt{}Coach Prime, Buffs stage quite the show in snowy spring game}{https://apnews.com/article/848ef6269e6c969bda35c333c7ed1c60}{Colorado head coach Deion Sanders looks on in the first half of the team\textquotesingle s spring practice NCAA college football game Saturday, April 22, 2023, in Boulder, Colo. (AP Photo/David Zalubowski) BOULDER, Colo. (AP) --- The cold...}

\entryitemWithDescription{\hskip 0pt{}Bud Light exec takes leave after boycott calls, reports say}{https://apnews.com/article/234ac7cf05d2124ed6ff7162e4771a43}{FILE - Cans of Bud Light beer are seen in Washington, Thursday Jan. 10, 2019. The marketing executive who oversaw a partnership between Bud Light and a transgender influencer is taking a leave of absence after it snowballed into cries for...}

\entryitemWithDescription{\hskip 0pt{}Cruise line let passenger's body decompose, lawsuit says}{https://apnews.com/article/c940a669e70b685a3d86467888af5ca6}{FILE - The cruiser Celebrity Equinox built by the shipyard Meyer in Papenburg, Germany, goes down the river Ems near Gandersum on Saturday, June 20, 2009. A widow and her family are suing Celebrity Cruises for allegedly mishandling her...}