\entryitemWithDescription{\hskip 0pt{}Radio host Larry Elder ends Republican presidential campaign and endorses Donald Trump}{https://apnews.com/article/a3d3665cd50d1e0d2071ab8800075482}{Conservative talk radio host Larry Elder announced Thursday that he was ending his 2024 Republican campaign for president and endorsing former President Donald Trump. Elder, who sought to replace California Gov. Gavin Newsom in a failed...}

\entryitemWithDescription{\hskip 0pt{}Ottawa's Shane Pinto suspended 41 games, becomes the 1st modern NHL player banned for gambling}{https://apnews.com/article/09cbedc1d9257fede6ec59251e76a914}{The NHL suspended Ottawa Senators forward Shane Pinto for 41 games on Thursday, making the 22-year-old American the first modern-day hockey player banned for sports gambling. The league said the half-season ban was for ``activities...}

\entryitemWithDescription{\hskip 0pt{}The last new Beatles song, `Now And Then,' will be released next week}{https://apnews.com/article/e7b3a349b0e1e58b8668e98ba2d9cd0b}{NEW YORK (AP) --- Sixty years after the onset of Beatlemania and with two of the quartet now dead, artificial intelligence has enabled the release next week of what is promised to be the last ``new'' Beatles song. The track, called ``Now...}

\entryitemWithDescription{\hskip 0pt{}China sends its youngest-ever crew to space as it seeks to put astronauts on moon before 2030}{https://apnews.com/article/0e538a1519b8fa7056078e2b968b52fa}{JIUQUAN SATELLITE LAUNCH CENTER, China (AP) --- China launched its youngest-ever crew for its orbiting space station on Thursday as it seeks to put astronauts on the moon before 2030. The Shenzhou 17 spacecraft lifted off from the Jiuquan...}

\entryitemWithDescription{\hskip 0pt{}No. 1 pick Wembanyama scores 15 points in NBA debut as Spurs fall to Mavericks in opener}{https://apnews.com/article/a0d4aa8851311110a55b59da9eb84023}{SAN ANTONIO (AP) --- The Victor Wembanyama era is underway in San Antonio. Wembanyama made his NBA debut with the Spurs against the Dallas Mavericks on Wednesday night and made an immediate splash. ``He's going to be amazing, he already...}

\entryitemWithDescription{\hskip 0pt{}Rep. Bowman of New York charged with misdemeanor, to pay fine after triggering House fire alarm}{https://apnews.com/article/1b9f8559a741a982116f7e8a4b6c6ac5}{WASHINGTON (AP) --- Democratic Rep. Jamaal Bowman was charged Wednesday with a misdemeanor for triggering a fire alarm as lawmakers scrambled to pass a funding bill before a government shutdown deadline in September. He is expected to...}

\entryitemWithDescription{\hskip 0pt{}Former NBA star Dwight Howard denies sexual assault lawsuit filed by Georgia man}{https://apnews.com/article/7bcfb45342393b48ddf07fd62e93fece}{ATLANTA (AP) --- Dwight Howard has denied accusations by a Georgia man who says he was sexually assaulted by the former NBA star and another person. Stephen Harper filed a state civil lawsuit against Howard in July, alleging assault and...}

\entryitemWithDescription{\hskip 0pt{}Bud Light to return as the UFC's official beer next year as it recovers from a conservative backlash}{https://apnews.com/article/000522bcef9f691be9cb388616480392}{NEW YORK (AP) --- Bud Light is set to return as the official beer of the UFC in the U.S. next year as the brand tries to recover from a conservative backlash to a promotion with a transgender influencer. Under a new multiyear marketing...}

\entryitemWithDescription{\hskip 0pt{}First ever Florida Man games will feature beer belly wrestling and `evading arrest' obstacle course}{https://apnews.com/article/baba548edfa25a963b823ae0023fb227}{ST. AUGUSTINE, Fla. (AP) --- It ain't the Olympics, but a group of Floridians plan to host competitions themed according to the collective antics of the beer-loving, gator-possessing, rap-sheet heavy, mullet-wearing social media...}

\entryitemWithDescription{\hskip 0pt{}Man trapped in jewelry vault overnight is freed when timer opens the chamber as scheduled}{https://apnews.com/article/9d7b68504d979e057105296b38df4325}{NEW YORK (AP) --- A man was trapped inside a steel-reinforced concrete jewelry vault in New York City overnight after firefighters had to abandon an attempt to rescue him for safety reasons. Fortunately, the vault was on a timer and...}

\entryitemWithDescription{\hskip 0pt{}`Shaft' star Richard Roundtree, considered the first Black action movie hero, has died at 81}{https://apnews.com/article/580aacdfa6ecac5cf79c553dd972f7e9}{LOS ANGELES (AP) --- Richard Roundtree, the trailblazing actor who starred as the ultra-smooth private detective in several ``Shaft'' films beginning in the early 1970s, has died. He was 81. Roundtree's longtime manager, Patrick McMinn...}

\entryitemWithDescription{\hskip 0pt{}Honolulu tells story of healers with dual male and female spirit through new plaque in Waikiki}{https://apnews.com/article/378357e19de52d73b893ef466b888814}{HONOLULU (AP) --- Honolulu officials on Tuesday introduced a new interpretive plaque for four large boulders in the center of Waikiki that honor Tahitian healers of dual male and female spirit who visited Oahu some 500 years ago. The...}

\entryitemWithDescription{\hskip 0pt{}Poison specialist and former medical resident at Mayo Clinic is charged with poisoning his wife}{https://apnews.com/article/9b8e8c259316dfbf0c7ea20f4624f0aa}{MINNEAPOLIS (AP) --- A poison specialist and former medical resident at Mayo Clinic in Minnesota is charged with fatally poisoning his wife, a 32-year-old pharmacist who died days after she went to a hospital in August with stomach...}