\entryitemWithDescription{\hskip 0pt{}Wendy Williams diagnosed with same form of dementia as Bruce Willis}{https://apnews.com/article/d3cebb8c20f750a623f9d180a50c03e8}{LOS ANGELES (AP) --- Former talk show host Wendy Williams has been diagnosed with the same form of dementia that actor Bruce Willis has, a statement released Thursday on behalf of her caretakers says. The statement said the 59-year-old's...}

\entryitemWithDescription{\hskip 0pt{}Herbstreit, Fowler to be voices in EA Sports college football game that will feature every FBS team}{https://apnews.com/article/4f78e19893ee1b361a131ebf536aa4ad}{Kirk Herbstreit and Chris Fowler are in the game. ESPN ``College GameDay'' analyst Herbstreit and network broadcaster Fowler announced Thursday on social media they will be voices in EA Sports' upcoming college football video game...}

\entryitemWithDescription{\hskip 0pt{}Space telescope spies neutron star in the debris of famous supernova}{https://apnews.com/article/26dce19f08868e4a1a5d59cbd03349d3}{Scientists have confirmed what became of a star that exploded in a stunning supernova visible to Earth more than three decades ago: It morphed into a neutron star, one of the oddest objects in the universe. In 1987, a star in a nearby...}

\entryitemWithDescription{\hskip 0pt{}Tiger Woods' son shoots 86 in pre-qualifier for PGA Tour event}{https://apnews.com/article/044dc8aa9bca5b220c7c1b10f315c66f}{HOBE SOUND, Fla. (AP) --- The PGA Tour will have to wait for the 15-year-old son of Tiger Woods. In a pre-qualifier Thursday, Charlie Woods took a 12 on one hole and shot 86. Woods didn't make a birdie at Lost Lake Golf Club, one of four...}

\entryitemWithDescription{\hskip 0pt{}HIV/AIDS activist Hydeia Broadbent, known for her inspirational talks as a young child, dies at 39}{https://apnews.com/article/f5adb5ce531f921b93249b1e0d0710f0}{LAS VEGAS (AP) --- Hydeia Broadbent, the HIV/AIDS activist who came to national prominence in the 1990s as a young child for her inspirational talks to reduce the stigma surrounding the virus she was born with, has died. She was 39...}

\entryitemWithDescription{\hskip 0pt{}A Missouri woman was killed in 1989. Three men are now charged in the crime}{https://apnews.com/article/16258e7429873d097048a638b25a9a78}{AVA, Mo. (AP) --- Authorities in Missouri say a 35-year cold case killing has been solved, thanks to someone who came forward with information about the crime. Douglas County authorities announced Wednesday that three men have been...}

\entryitemWithDescription{\hskip 0pt{}Volkswagen to recall 261,000 cars to fix pump problem that can let fuel leak and increase fire risk}{https://apnews.com/article/b6b5803488722307454e24f7062e6f9d}{DETROIT (AP) --- Volkswagen is recalling more than 261,000 cars in the U.S. to fix a potential fuel leak that can increase the risk of fires. The recall covers certain Audi A3s and VW Golfs and GTIs from the 2015 through 2020 model years...}

\entryitemWithDescription{\hskip 0pt{}Guinness World Records rescinds `oldest dog ever' title for a dead Portuguese canine after an investigation}{https://apnews.com/article/d002d5856ac34388a6401f6ae3d5afb3}{LISBON, Portugal (AP) --- Guinness World Records has ruled against a Portuguese dog that died last year keeping the title of oldest canine ever. Following a review, GWR said Thursday it ``no longer has the evidence it needs to support...}

\entryitemWithDescription{\hskip 0pt{}A Colorado man died after a Gila monster bite. Opinions and laws on keeping the lizard as a pet vary}{https://apnews.com/article/9892593eb16a2f1f2fad77e1c1610858}{A Colorado man who died after getting bitten by a Gila monster was hardly alone in having the gnarly looking lizard for a pet. They're legal to own in most states, easily found through breeders and at reptile shows, and widely regarded...}

\entryitemWithDescription{\hskip 0pt{}A Minnesota man was arrested for killing a woman who was found stuffed inside her refrigerator}{https://apnews.com/article/81339c5918f2dc40f1932ddfdda623d0}{LOS ANGELES (AP) --- A Minnesota man has been arrested on suspicion of killing a 31-year-old woman who was beaten, bound and stuffed inside the refrigerator at her Los Angeles apartment, authorities said Wednesday. The 41-year-old...}

\entryitemWithDescription{\hskip 0pt{}Federal judge affirms MyPillow's Mike Lindell must pay \$5M in election data dispute}{https://apnews.com/article/a9b27dd8d37eab1d0f22111566feba93}{ST. PAUL, Minn. (AP) --- A federal judge on Wednesday affirmed a \$5 million arbitration award against MyPillow chief executive Mike Lindell in favor of a software engineer who challenged data that Lindell said proves China interfered in...}

\entryitemWithDescription{\hskip 0pt{}Jimmy Carter becomes first living ex-president with official White House Christmas ornament}{https://apnews.com/article/65f99904dde73812e7e6db9c91726e67}{WASHINGTON (AP) --- Former President Jimmy Carter has another distinction to his name. The 99-year-old is the first of the U.S. presidents to be honored with an official White House Christmas ornament while still living. The ornament was...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé becomes first Black woman to claim top spot on Billboard's country music chart}{https://apnews.com/article/65daed689172543369b4d080580da3c6}{LOS ANGELES (AP) --- Beyoncé made history once again: The superstar singer has become the first Black woman to top Billboard's country music chart. The Grammy winner achieved the feat after her new single ``Texas Hold `Em'' reached No. 1...}