\entryitemWithDescription{\hskip 0pt{}Man recovering from shark bite on the Florida coast in state's third attack in a month}{https://apnews.com/article/a2e4835dbbd1eba9e68b14b83b1d86ec}{A man on Florida's northeast coast was bitten by a shark this weekend but is now recovering, authorities said Sunday, in the third shark attack in state waters over the past month. Officials from the Nassau County Sheriff's Office Marine...}

\entryitemWithDescription{\hskip 0pt{}More WestJet flight cancellations as Canadian airline strike hits tens of thousands of travelers}{https://apnews.com/article/2be751fc7a4623a2163c179e0e30391a}{TORONTO (AP) --- Canada's second largest airline, WestJet, said Sunday that it canceled more than 800 flights affecting tens of thousands of passengers as an unexpected strike by plane mechanics entered its third day. Around 680 workers...}

\entryitemWithDescription{\hskip 0pt{}Bellingham wonder goal sends England vs. Slovakia to extra time after 1-1 draw}{https://apnews.com/article/0e3f5e18fadf95899f4183b70e4a30da}{GELSENKIRCHEN, Germany (AP) --- Jude Bellingham scored in the fifth minute of stoppage time to send England's European Championship round of 16 game against Slovakia to extra time on Sunday. Bellingham's acrobatic overhead kick leveled...}

\entryitemWithDescription{\hskip 0pt{}`A Quiet Place' prequel box office speaks volumes as Costner's Western gets a bumpy start}{https://apnews.com/article/dadbeb6e8c9700ffcc723894fcab2e03}{`` A Quiet Place: Day One '' is making noise at the box office. The prequel earned an estimated \$53 million in its first weekend in North American theaters, according to studio estimates Sunday. It's both a franchise best and...}

\entryitemWithDescription{\hskip 0pt{}Animal rescuers try to keep dozens of dolphins away from Cape Cod shallows after mass stranding}{https://apnews.com/article/24fa9ebd22b62cc72b685ea0759b822e}{WELLFLEET, Mass. (AP) --- Animal rescuers were trying to keep dozens of dolphins away from shallow waters around Cape Cod on Saturday after 125 of the creatures stranded themselves a day earlier. Teams in Massachusetts found one group of...}

\entryitemWithDescription{\hskip 0pt{}Former Northeastern University lab manager convicted of staging hoax explosion at Boston campus}{https://apnews.com/article/344c872e2461207ac1a7c72845972406}{A former lab manager at Northeastern University has been convicted of staging a hoax explosion at the Boston campus and then lying about what happened to a federal agent. Jason Duhaime, 46, from San Antonio, Texas, was convicted on three...}

\entryitemWithDescription{\hskip 0pt{}Driver charged with DUI for New York nail salon crash that killed 4 and injured 9}{https://apnews.com/article/63277ae7c5b576d40ba7d0b7c25a139a}{DEER PARK, N.Y. (AP) --- Police on Long Island have arrested a man who is accused of driving while intoxicated after he crashed his SUV into a nail salon, killing four people and injuring nine others. Suffolk County Police said Saturday...}

\entryitemWithDescription{\hskip 0pt{}Canadian airline WestJet cancels at least 150 flights following a surprise strike by mechanics union}{https://apnews.com/article/a4801eb2f8eb2d09a449e91b58eb3ad8}{TORONTO (AP) --- Canada's second largest airline, WestJet, says it has cancelled at least 150 flights affecting 20,000 passengers beginning Saturday after the union of maintenance workers announced it has gone on strike. The Aircraft...}

\entryitemWithDescription{\hskip 0pt{}ESPN's Dick Vitale diagnosed with cancer for a 4th time with surgery scheduled for Tuesday}{https://apnews.com/article/eea649a5849be07e6c8dc151ace75707}{BRISTOL, Conn. (AP) --- Longtime ESPN college basketball analyst Dick Vitale said on social media he has been diagnosed with cancer for a fourth time. Vitale announced Friday that a biopsy of a lymph node in his network showed cancer. He...}

\entryitemWithDescription{\hskip 0pt{}Up to 125 Atlantic white-sided dolphins stranded in Cape Cod waters}{https://apnews.com/article/ecb818707c36f4f35aff22db1fde9ffe}{WELLFLEET, Mass. (AP) --- As many as 125 Atlantic white-sided dolphins became stranded Friday on Cape Cod and at least 10 died, prompting an intensive rescue effort, according to an animal rescue organization. The International Fund for...}

\entryitemWithDescription{\hskip 0pt{}Driver convicted in deaths of 8 people struck by SUV outside migrant shelter sentenced to 60 years}{https://apnews.com/article/2fad018df6f2e35d4be0b23e5f001e7e}{BROWNSVILLE, Texas (AP) --- A Texas jury on Friday found a driver guilty of intoxication manslaughter over the deaths of eight people who were struck by an SUV that plowed into a crowded bus stop outside a migrant shelter on the U.S...}

\entryitemWithDescription{\hskip 0pt{}Yellowstone officials: Rare white buffalo sacred to Native Americans not seen since June 4 birth}{https://apnews.com/article/86e95f80354a1ef6a5bced2b0a93bb49}{Yellowstone National Park officials said Friday a rare white buffalo sacred to Native Americans has not been seen since its birth on June 4. The birth of the white buffalo, which fulfilled a Lakota prophecy that portends better times, was...}

\entryitemWithDescription{\hskip 0pt{}Euro 2024: Penalty shootouts set to take center stage as psychology and new tactics come into play}{https://apnews.com/article/1105b350bc1c7ccb4c0deca1c9aada6e}{DORTMUND, Germany (AP) --- Here's a quiz question: What do the 2022 World Cup final, the 2021 African Cup of Nations final, the 2020 European Championship final and the 2016 Copa America final have in common? Answer: They were all settled...}