\entryitemWithDescription{\hskip 0pt{}Young bear spotted relaxing on a hammock in a Vermont yard}{https://apnews.com/article/e990b0047b1c5a1c2295422500b9fe98}{WAITSFIELD, Vt. (AP) --- Noah and Kristen Dweck have seen a number of black bears around their home in Vermont but this was a first: a bear relaxing on their hammock. Noah Dweck took iPhone video of two young bears in their yard in...}

\entryitemWithDescription{\hskip 0pt{}Florida's 2024 hurricane season arrives with a rainy deluge}{https://apnews.com/article/a37631902e119c0036d1fd51da2dba15}{The annual rainy season has arrived with a wallop in much of Florida, where a disorganized disturbance of tropical weather from the Gulf of Mexico has caused street flooding and triggered tornado watches but so far has not caused major...}

\entryitemWithDescription{\hskip 0pt{}Wreck of the last ship of famed Anglo-Irish explorer Shackleton found off the coast of Canada}{https://apnews.com/article/1b814ad4f88806980d687eeb7dce466b}{ST. JOHN'S, Newfoundland (AP) --- The wreck of the last ship belonging to Sir Ernest Shackleton, a famous Irish-born British explorer of Antarctica, has been found off the coast of Labrador in Canada, 62 years after it went missing. The...}

\entryitemWithDescription{\hskip 0pt{}Matty Healy's mom says The 1975 singer and model Gabbriette Bechtel are engaged}{https://apnews.com/article/bd658488094c931591a9eac884575849}{The 1975's Matty Healy and model Gabbriette Bechtel are engaged, accordingly to Healy's mother, the English actor Denise Welch. Welch, a regular panelist on the ITV talk show ``Loose Women,'' confirmed the news Wednesday on the U.K...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk drops lawsuit against ChatGPT-maker OpenAI without explanation}{https://apnews.com/article/e3932deb15957c915cd694d63583a043}{SAN FRANCISCO (AP) --- Elon Musk has dropped his lawsuit against OpenAI just ahead of a scheduled Wednesday hearing on the case. Musk in February sued the San Francisco artificial intelligence company and its CEO Sam Altman over what he...}

\entryitemWithDescription{\hskip 0pt{}Juan Soto joins Daddy Yankee and Kyle Tucker teams with Travis Scott on Topps Series 2 cards}{https://apnews.com/article/ab82f273a01dd4a10cef16f1b7e3e2f4}{Juan Soto has been on baseball cards with Ken Griffey Jr., Mike Trout, Fernando Tatis Jr., Manny Machado and Xander Bogaerts. But this one, well, this one was a little different for Soto. This one had the New York Yankees slugger and...}

\entryitemWithDescription{\hskip 0pt{}Heat wave in Greece halts visits to Acropolis as drones with thermal cameras monitor temperatures}{https://apnews.com/article/8384b3b1903da07f5915d2ead802fbd6}{ATHENS, Greece (AP) --- Authorities in Athens announced the closure of the Acropolis for five hours due to heat wave temperatures that also prompted many schools to close. The ancient site in the Greek capital --- which drew nearly 4...}

\entryitemWithDescription{\hskip 0pt{}At least 35 people have died in a building fire in Kuwait, state news agency says}{https://apnews.com/article/0c6b8c8abcbbe1e6b1162ad1592647ae}{DUBAI, United Arab Emirates (AP) --- At least 35 people died in a building fire early Wednesday in Kuwait, the state-run news agency reported. KUNA said another 15 people were injured in the fire, which broke out in the southern Mangaf...}

\entryitemWithDescription{\hskip 0pt{}Top investigator in Karen Read murder case questioned over inappropriate texts}{https://apnews.com/article/f3473c8ec93915b9a4deeb7061572a68}{The lead investigator in the case of a woman accused of leaving her Boston police officer boyfriend for dead in a snowbank has come under fire for a series of offensive and inappropriate texts he wrote about the defendant during the...}

\entryitemWithDescription{\hskip 0pt{}Americans celebrate their flag every year, and the holiday was born in Wisconsin}{https://apnews.com/article/6afcfece1f0e98ed7150a6c56b829ebf}{WAUBEKA, Wis. (AP) --- Each June, the people of Waubeka venerate perhaps the nation's most enduring symbol, celebrating Flag Day, a holiday that escapes the notice of many Americans. But this unincorporated Wisconsin town about 35 miles...}

\entryitemWithDescription{\hskip 0pt{}Rory McIlroy and wife end divorce proceedings to stay together as a family}{https://apnews.com/article/6ad269778c4d9cc7628ffddc91ae3480}{PINEHURST, N.C. (AP) --- Rory McIlroy and his wife Erica have scrapped plans to divorce and are putting their marriage back together. They filed for a voluntary dismissal of the case on Tuesday. It was another dramatic turn of events for...}

\entryitemWithDescription{\hskip 0pt{}Billy Ray Cyrus files for divorce from Firerose after 7 months of marriage}{https://apnews.com/article/9d1ece1ca2969c1bcc716cb80b04e3a5}{LOS ANGELES (AP) --- Billy Ray Cyrus has filed for divorce from singer Firerose after seven months of marriage. The 62-year-old country musician filed for divorce from the 36-year-old whose legal name is Johanna Rose Hodges in a Tennessee...}

\entryitemWithDescription{\hskip 0pt{}Bull that jumped the fence at Oregon rodeo forced to retire from competition, owner says}{https://apnews.com/article/e680e57cd3bc1a1a4bca636a9a883cc3}{PORTLAND, Ore. (AP) --- Party Bus, a 3-year-old bull bred for bucking, has performed in his first and last rodeo. Party Bus --- named after his father, Short Bus --- made national headlines last weekend at his first rodeo when he jumped...}