\entryitemWithDescription{\hskip 0pt{}Romanian authorities tow vehicles from Andrew Tate's home after new human trafficking allegations}{https://apnews.com/article/76457ce6c2e1e394114fed7c9a106221}{BUCHAREST, Romania (AP) --- Romanian authorities towed away a fleet of luxury vehicles Saturday from the home of the divisive social media personality Andrew Tate, days after he was placed under house arrest following new human...}

\entryitemWithDescription{\hskip 0pt{}Justin and Hailey Bieber welcome a baby boy, Jack Blues}{https://apnews.com/article/eecf522431d870ea1cee45ef38935b6f}{LOS ANGELES (AP) --- Justin Bieber, who rose to international stardom in 2010 with his hit ``Baby,'' has welcomed one of his own with his wife, Hailey Bieber (nee Baldwin). The singer, 30, posted a photo of a baby's foot Friday on...}

\entryitemWithDescription{\hskip 0pt{}Expert defends security guards in death of man at Detroit-area mall a decade ago}{https://apnews.com/article/74e37ef1eeae02a916782ce948818cc9}{DETROIT (AP) --- An expert in the use of force defended the tactics of security guards who restrained a man on the floor of a Detroit-area mall before he died, telling jurors Friday that their actions were reasonable. Charles Key...}

\entryitemWithDescription{\hskip 0pt{}Judge rules Breonna Taylor's boyfriend caused her death, dismisses some charges against ex-officers}{https://apnews.com/article/a7ff7c9b48307dd6423e9e999c667405}{LOUISVILLE, Ky. (AP) --- A federal judge has thrown out major felony charges against two former Louisville officers accused of falsifying a warrant that led police to Breonna Taylor's door before they fatally shot her. U.S. District Judge...}

\entryitemWithDescription{\hskip 0pt{}Late French film star Alain Delon wanted his dog buried with him. The dog gets to live}{https://apnews.com/article/7fddf62204b06a28466524b6c4dbcf2e}{PARIS (AP) --- Before he died this week, French film icon Alain Delon once suggested he wanted his beloved sheepdog Louba buried with him. To the relief of animal lovers around France, Loubo will be allowed to survive. Delon, an...}

\entryitemWithDescription{\hskip 0pt{}Last body from sunken superyacht has been recovered off Sicily}{https://apnews.com/article/55001fe25632c9adde0e51fc8100c8a0}{ROME (AP) --- Italian rescuers brought ashore the body of the final missing person who was on a superyacht that sunk off the coast of Sicily. The woman's body was detected on Friday, the Coast Guard said. She has not been officially...}

\entryitemWithDescription{\hskip 0pt{}The twins are here! A second set of giant panda cubs has arrived in Berlin}{https://apnews.com/article/a645ca9b993c59b9db2c835442e0c58e}{BERLIN (AP) --- Berlin Zoo announced Friday that longtime resident giant panda Meng Meng has given birth to twins --- for a second time. The cubs were born on Thursday and are doing well, the zoo said in a statement. They were born only...}

\entryitemWithDescription{\hskip 0pt{}Kamala Harris with Beyonce? Yes, but the star singer was only heard through loudspeakers}{https://apnews.com/article/6a6a0d8d1142b9410d1bb6e7d813dd66}{Kamala Harris introduced herself to the country she hopes to lead in the climactic moment of the Democratic national convention on Thursday --- and despite chatter about potential mystery guests, Beyonce's only appearance was over the...}

\entryitemWithDescription{\hskip 0pt{}Young humpback whale freed from fishing tackle that had entangled its tail in Sydney Harbor}{https://apnews.com/article/a0eb00783db26ff020d5077659d2bf51}{MELBOURNE, Australia (AP) --- A young humpback whale was freed from fishing tackle that had entangled its tail during an almost 24-hour rescue operation in Sydney Harbor. The juvenile whale immediately began swimming toward the Sydney...}

\entryitemWithDescription{\hskip 0pt{}See George Clooney's memorable moments at Venice Film Festival as actor prepares to return}{https://apnews.com/article/3365ea04d838e30d19b75d3df047aec4}{No Hollywood star seems as intrinsically tied to Venice as George Clooney. Twenty-six years ago he attended his first Venice Film Festival with the instant classic ``Out of Sight''; 19 years ago, it's where he debuted his sophomore...}

\entryitemWithDescription{\hskip 0pt{}What's for breakfast? At Chicago hotel hosting DNC event, there may have been mealworms}{https://apnews.com/article/f4c959f9235eb8c967b385174003f29b}{CHICAGO (AP) --- Mealworms may have sickened at least one person at a Chicago hotel event earlier this week during the Democratic National Convention, the city's police superintendent said Thursday. While the investigation by Chicago...}

\entryitemWithDescription{\hskip 0pt{}\$1M verdict for teen, already a victim when she was assaulted by an officer}{https://apnews.com/article/e772320d2c3f531cc7acbb0c94470bdd}{NEW ORLEANS (AP) --- The city of New Orleans owes \$1 million to a teenager who was already a victim of sexual assault when a city police offer with a history of misconduct complaints continued the abuse --- pretending to be a friend and...}

\entryitemWithDescription{\hskip 0pt{}Sword, bullhorn stolen from Hall of Fame basketball coach Rick Pitino's St. John's University office}{https://apnews.com/article/0f9217c25415cf16857f1323399e8332}{NEW YORK (AP) --- Two thieves swiped a ceremonial sword and a bullhorn from the office of St. John's University Coach Rick Pitino, a spokesperson for the Catholic institution in the New York City borough of Queens said Thursday. Brian...}