\entryitemWithDescription{\hskip 0pt{}Paralympics fans learn when to be silent and when to make noise at sports for the visually-impaired}{https://apnews.com/article/2ecaf2a27d840886cd6c5f822cc706c6}{PARIS (AP) --- A soft voice from the loudspeaker reminds the restless crowd: ``Shhh. Shhh.'' The whistle blows. Suddenly, spectators fall silent and even the slightest noise echoes through the Eiffel Tower Stadium. Fans pack the stadium...}

\entryitemWithDescription{\hskip 0pt{}Highlights from the first week of the Paralympic Games in Paris}{https://apnews.com/article/68bdad2e45ff47e9ffe22430a15e0c7e}{PARIS (AP) --- A gallery of highlights from the first week of the Paralympics captured by AP photographers at the Paris...}

\entryitemWithDescription{\hskip 0pt{}How do you get a grumpy 4-ton elephant to a new home 120 miles away? Call the elephant movers}{https://apnews.com/article/3ec60a8ebbba2179a52b5aa8a9e3d558}{CAPE TOWN, South Africa (AP) --- When it comes to the niche business of moving elephants, Dr. Amir Khalil and his team might be the best. The Egyptian veterinarian's résumé includes possibly the most famous elephant relocation on the...}

\entryitemWithDescription{\hskip 0pt{}Tilda Swinton, Julianne Moore attend Venice Film Festival with Almodóvar film}{https://apnews.com/article/df15aa8e16ef46e80576bad56b7b7d15}{VENICE, Italy (AP) --- Spanish filmmaker Pedro Almodóvar returns to the Venice Film Festival with stars Tilda Swinton and Julianne Moore, Monday. ``The Room Next Door'' will have its world premiere on the Lido in the evening. Though a new...}

\entryitemWithDescription{\hskip 0pt{}Thousands to parade through Brooklyn in one of world's largest Caribbean culture celebrations}{https://apnews.com/article/b2b87995006cfd8ab598862599905c52}{NEW YORK (AP) --- New York City's West Indian American Day Parade will kick off Monday with thousands of revelers dancing and marching through Brooklyn in one of the world's largest celebrations of Caribbean culture. The annual Labor Day...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Pope Francis' Asia trip marks 60 years of papal visits to the region}{https://apnews.com/article/41e3ccdbf0bc11b659e26e8ff33081fe}{BANGKOK, Thailand (AP) --- Pope Francis' visit to Southeast Asia, the longest trip in his papacy, is the latest in decades of regular papal visits to the Asia-Pacific region. Papal travel is a thing of the modern era, starting with Pope...}

\entryitemWithDescription{\hskip 0pt{}ESPN networks, ABC and Disney channels go dark on DirecTV on a busy night for sports}{https://apnews.com/article/94bb717f4b1a7f302e73102f23713308}{ESPN has gone off the air on a major carrier for the second straight year during the U.S. Open tennis tournament and in the midst of the first full weekend of college football. Disney Entertainment channels went dark on DirecTV Sunday...}

\entryitemWithDescription{\hskip 0pt{}Ukrainian badminton player chasing first Paralympic medal with an unexpected guest in the stands}{https://apnews.com/article/558939e4420de610248b97b323825fbc}{PARIS (AP) --- Oksana Kozyna's Paralympic debut was sure to have some unexpected moments, but the surprise she received might beat anything that could have happened on the court. The Ukrainian para badminton player was raised in an...}

\entryitemWithDescription{\hskip 0pt{}Scottie Scheffler caps off record season with FedEx Cup title and \$25 million bonus}{https://apnews.com/article/0818ddbff753b8d211c0211aa678dcf8}{ATLANTA (AP) --- Scottie Scheffler capped off the biggest year in golf in nearly two decades by winning the biggest prize in golf. Challenged briefly Sunday in the Tour Championship, Scheffler responded with three straight birdies to made...}

\entryitemWithDescription{\hskip 0pt{}Grigor Dimitrov returns to US Open quarterfinals by holding off Rublev with Serena watching}{https://apnews.com/article/0286357f22f9031f60c1c2b66e6c912c}{NEW YORK (AP) --- Grigor Dimitrov withstood Andrey Rublev's comeback attempt and returned to the U.S. Open quarterfinals Sunday with a 6-3, 7-6 (3), 1-6, 3-6, 6-3 victory Sunday. The No. 9 seed started fast in the first meeting of top-10...}

\entryitemWithDescription{\hskip 0pt{}Thousands of Turks protest controversial law to remove stray dogs}{https://apnews.com/article/66eff47e6a99f21041589c5786d89bcc}{ISTANBUL (AP) --- Thousands of demonstrators gathered in Istanbul on Sunday to protest recent legislation that critics say is leading to the killing of stray dogs across Turkey. Last month, legislators approved the new law aimed at...}

\entryitemWithDescription{\hskip 0pt{}Venice Film Festival welcomes Pitt and Clooney, and their new film `Wolfs'}{https://apnews.com/article/3af1903dc8e8b453e89173afd50a0bf0}{VENICE, Italy (AP) --- George Clooney and Brad Pitt are returning to the Venice Film Festival Sunday for the world premiere of ``Wolfs.'' In the crime-thriller directed by Jon Watts, the two Hollywood stars play lone wolf fixers...}

\entryitemWithDescription{\hskip 0pt{}49ers WR Ricky Pearsall shot in attempted robbery in San Francisco, condition `serious but stable'}{https://apnews.com/article/3afececadc18b6b10d2df411a27c7d43}{SAN FRANCISCO (AP) --- 49ers wide receiver Ricky Pearsall was shot in the chest Saturday during an attempted robbery in central San Francisco, officials said, and he was reported to be in serious but stable condition. Mayor London Breed...}