\entryitemWithDescription{\hskip 0pt{}Booth where Tony Soprano may have been whacked – or not – sells for a cool \$82K to mystery buyer}{https://apnews.com/article/3ab5d631b61b09c76ee03d3f4029a9e9}{BLOOMFIELD, N.J. (AP) --- The ice cream parlor booth where Tony Soprano may or may not have been whacked has sold for more than \$82,000. As Tony would say, Madone! An anonymous buyer bid \$82,600 Monday night in an online auction for the...}

\entryitemWithDescription{\hskip 0pt{}Homes near St. Louis County creek are being tested after radioactive contamination found in yards}{https://apnews.com/article/982fa4c3e2714f45dcd3794c0ab25489}{ST. LOUIS (AP) --- A federal agency is examining soil beneath homes in a small suburban St. Louis subdivision to determine if residents are living atop Cold War era nuclear contamination. But activists say the testing needs to be far more...}

\entryitemWithDescription{\hskip 0pt{}Caitlin Clark's record-setting game draws top women's basketball regular-season TV rating since 1999}{https://apnews.com/article/97ea3e573b26bd666fa99947dfd8bcdd}{Caitlin Clark's record-setting game for Iowa against Ohio State on Sunday attracted more than 4 million television viewers at its peak and was the most watched women's regular-season basketball game since 1999, Fox Sports announced...}

\entryitemWithDescription{\hskip 0pt{}V-J Day `Kiss' photo stays on display as VA head reverses department memo that would've banned it}{https://apnews.com/article/b24d5dba6930be867e9ac1be6dff16e5}{WASHINGTON (AP) --- The Veterans Affairs secretary has reversed a department memo that aimed to ban VA displays of the iconic ``V-J Day in Times Square'' photograph of a Navy sailor kissing a strange woman on the streets of New York at...}

\entryitemWithDescription{\hskip 0pt{}What is a whale native to the North Pacific doing off New England? Climate change could be the key}{https://apnews.com/article/28eb054f7dd05732f65d6c441fefdee8}{PORTLAND, Maine (AP) --- Scientists have confirmed the presence of a whale off New England that went extinct in the Atlantic Ocean two centuries ago --- an exciting discovery, but one they said that illustrates the impact of climate...}

\entryitemWithDescription{\hskip 0pt{}Facebook, Instagram, Messenger and Threads down in widespread outage}{https://apnews.com/article/974886228759761c2c3c28f2e984a2d6}{Users of Meta's Facebook, Instagram, Threads and Messenger platforms are experiencing login issues in what appears to be a widespread outage. Internet traffic observer Down Detector is reporting vast outages on several Meta platforms...}

\entryitemWithDescription{\hskip 0pt{}Dodge muscle cars live on with new versions of the Charger powered by electricity or gasoline}{https://apnews.com/article/591283bf2e0b50c7dac1612f3dea2b3a}{DETROIT (AP) --- America's muscle car culture will live on as the country transitions to electric vehicles, but the gas-powered performance car will last for at least a few more years. Dodge on Tuesday unveiled two battery-powered...}

\entryitemWithDescription{\hskip 0pt{}Production at a Tesla plant near Berlin is halted after a power outage. Officials suspect arson}{https://apnews.com/article/9d66c3efa104d03244bd2c4d920c35a0}{BERLIN (AP) --- Production at Tesla's electric vehicle plant near Berlin came to a standstill and workers were evacuated on Tuesday after a power outage that officials suspect was caused by arson. According to the Interior Ministry in the...}

\entryitemWithDescription{\hskip 0pt{}Like Banksy, France's mystery `Invader' marks cities with art. He could surprise the Paris Olympics}{https://apnews.com/article/f6c2821e22d33bfdd9f86f378dc82d8c}{PARIS (AP) --- For the Paris Olympics, it could almost be a new sport: Score points by hunting down mosaics that a mystery artist who calls himself ``Invader'' has cemented to walls across France's capital, the world and even had carried...}

\entryitemWithDescription{\hskip 0pt{}Singapore prime minister defends exclusive deal with Taylor Swift that riles some neighbors}{https://apnews.com/article/2652fc27f2efc9d4dca4db8d1468f261}{MELBOURNE, Australia (AP) --- Singapore's Prime Minister Lee Hsien Loong was called on during a key regional summit on Tuesday to defend an exclusive deal his city-state struck with Taylor Swift that prevents the pop star taking her...}

\entryitemWithDescription{\hskip 0pt{}Ammo supplier says he provided no live rounds in fatal shooting of cinematographer by Alec Baldwin}{https://apnews.com/article/511344673f08fb757024568d8c63c3e4}{SANTA FE, N.M. (AP) --- An ammunition supplier testified at trial Monday that he only provided inert dummy rounds to the Western film ``Rust'' where actor Alex Baldwin fatally shot a cinematographer in 2021, though he also was handling...}

\entryitemWithDescription{\hskip 0pt{}5-time Iditarod champion Dallas Seavey kills and guts a moose that got entangled with his dog team}{https://apnews.com/article/13c5e674d5062375bb0881d3ccb5e919}{ANCHORAGE, Alaska (AP) --- A veteran musher had to kill a moose after it injured his dog shortly after the start of this year's Iditarod, race officials said Monday. Dallas Seavey informed the officials with the Iditarod Trail Sled Dog...}

\entryitemWithDescription{\hskip 0pt{}Denver Broncos inform QB Russell Wilson they'll release him when new league year begins}{https://apnews.com/article/8dd648ea616e012c4e1d765b3bfa7c0a}{ENGLEWOOD, Colo. (AP) --- The Denver Broncos told Russell Wilson on Monday that they're going to release him next week, just 18 months after signing the Super Bowl-winning quarterback to a five-year, \$242 million contract extension. The...}