\entryitemWithDescription{\hskip 0pt{}The Grammys ended in controversy, again. Here's what to know}{https://apnews.com/article/68bfa38b02e797e3300b7c32f00d8b2c}{Harry Styles, left, embraces Kid Harpoon, center, while Tyler Johnson accepts the award for album of the year for "Harry\textquotesingle s House" at the 65th annual Grammy Awards on Sunday, Feb. 5, 2023, in Los Angeles. (AP Photo/Chris...}

\entryitemWithDescription{\hskip 0pt{}Balloon bursts hopes for end to spiraling US-China tensions}{https://apnews.com/article/0a0469109e8776f1676d7b813e46854f}{In this photo provided by Brian Branch, a large balloon drifts above the Kingstown, N.C. area, with an airplane and its contrail seen below it. The United States says it is a Chinese spy balloon moving east over America at an altitude of...}

\entryitemWithDescription{\hskip 0pt{}How Manchester City came to face Premier League charges}{https://apnews.com/article/cbe6cdd3f8cb4850ffc4fb7ab55d9102}{FILE - A exterior shot of the stadium before the English Premier League soccer match between Manchester City and Arsenal at the Etihad Stadium in Manchester, England, Wednesday, June 17, 2020. Manchester City has been accused of numerous...}

\entryitemWithDescription{\hskip 0pt{}Purdue stays No. 1 in AP Top 25; NC State in at No. 22}{https://apnews.com/article/939135c53ee56912d6b229ae00241ef8}{Purdue head coach Matt Painter argues a call during the second of an NCAA college basketball game against Indiana, Saturday, Feb. 4, 2023, in Bloomington, Ind. (AP Photo/Darron Cummings) Purdue\textquotesingle s unquestioned grip on No. 1...}

\entryitemWithDescription{\hskip 0pt{}Spiritual advisers offering final comfort in execution rooms}{https://apnews.com/article/dbc253bef85af688a63a42a836e00028}{The Rev. Darryl Gray, left, and the Rev. Lauren Bennett speak in Bennett\textquotesingle s office in St. Louis, Mo., on Jan. 10, 2023. Both served as spiritual advisers at recent executions in Missouri, sitting alongside the inmates and...}

\entryitemWithDescription{\hskip 0pt{}What to Watch: New political vibes this State of the Union}{https://apnews.com/article/d53d195a56d37c6d7c800779f07026ea}{FILE - The chamber of the House of Representatives is seen at the Capitol in Washington, Feb. 28, 2022. Expect lots of new faces and fresh political dynamics as President Joe Biden delivers this year's State of the Union address. That...}

\entryitemWithDescription{\hskip 0pt{}Release of toxic chemicals from derailed tanker cars begins}{https://apnews.com/article/bf5a60de2243cd6f7f730096aa33294c}{This photo taken with a drone shows portions of a Norfolk and Southern freight train that derailed Friday night in East Palestine, Ohio are still on fire at mid-day Saturday, Feb. 4, 2023. (AP Photo/Gene J. Puskar) EAST PALESTINE, Ohio...}

\entryitemWithDescription{\hskip 0pt{}Shiffrin's Beijing lesson helps after another big-race DNF}{https://apnews.com/article/81015e6deea3308ae35b7eef4fda22bb}{United States\textquotesingle{} Mikaela Shiffrin fails to complete the slalom portion of an alpine ski, women\textquotesingle s World Championship combined race, in Meribel, France, Monday, Feb. 6, 2023. (AP Photo/Alessandro Trovati...}

\entryitemWithDescription{\hskip 0pt{}National Enquirer, caught in 'catch-and-kill' scandal, sold}{https://apnews.com/article/ad911dcfadb4441fc3e7d9e0018c1dec}{FILE - In this July 12, 2017 file photo, an issue of the National Enquirer featuring President Donald Trump on its cover is displayed on a newsstand in a store in New York. VVIP Ventures is buying the U.S. and U.K editions of the National...}

\entryitemWithDescription{\hskip 0pt{}Russian forces keep up pressure as Ukraine anniversary nears}{https://apnews.com/article/b34d8a533e88f1b8c67b841a9b18e5d8}{Soldiers carry the coffin of Eduard Strauss, a Ukrainian serviceman who died in combat on Jan. 17 in Bakhmut, during a farewell ceremony in Kyiv, Ukraine, Monday, Feb. 6, 2023. (AP Photo/Daniel Cole) KYIV, Ukraine (AP) --- Russian forces...}

\entryitemWithDescription{\hskip 0pt{}Brignone wins worlds combined race after Shiffrin straddles}{https://apnews.com/article/6bd3067cdda995f5dee7fe189072767a}{Italy\textquotesingle s Federica Brignone, winner of an alpine ski, women\textquotesingle s World Championship combined race, is overcome by emotion on the podium during the national anthem, in Meribel, France, Monday, Feb. 6, 2023. (AP...}

\entryitemWithDescription{\hskip 0pt{}Retailers try to curb theft while not angering shoppers}{https://apnews.com/article/c5d9abbb9ca64c23419951c28380a534}{Pharmaceutical items are kept locked in a glass cabinet at a Gristedes supermarket, Tuesday Jan. 31, 2023, in New York. Increasingly, retailers are locking up more products or increasing the number of security guards at their stores to...}

\entryitemWithDescription{\hskip 0pt{}ChatGPT bot channels history to pen State of Union speech}{https://apnews.com/article/8b4dc4774acd0f4ba4ad2fb1ea768d47}{FILE - Text from the ChatGPT page of the OpenAI website is shown in this photo, in New York, Feb. 2, 2023. State of the Union speeches could be crafted on autopilot, so formulaic are they. To shake things up before President Joe Biden...}