\entryitemWithDescription{\hskip 0pt{}Larry Bird Museum officially opens in Terre Haute}{https://apnews.com/article/753c3ca2a5999b2a3dc7aa9aa1a49848}{TERRE HAUTE, Ind. (AP) --- By his own admission, Larry Bird has always been a shy introvert. So he wondered why he has to keep talking on stage in front of thousands of people. ``It's because of the love and respect I've had for my fans...}

\entryitemWithDescription{\hskip 0pt{}Officer who arrested Scottie Scheffler criticizes attorney but holds `no ill will' toward golfer}{https://apnews.com/article/efcff45da1114e16ee31e9e7ea406658}{LOUISVILLE, Ky. (AP) --- The Louisville police officer who arrested Scottie Scheffler said he has ``no ill will'' toward the pro golfer for injuries he said he suffered while directing traffic after a fatal accident during the PGA...}

\entryitemWithDescription{\hskip 0pt{}`Pure grit.' Jordan Chiles is making a run at a second Olympics, this time on her terms}{https://apnews.com/article/cb0a9ba90943d4fe61bff60d3a4f93db}{FORT WORTH, Texas (AP) --- Jordan Chiles doesn't have to put herself through this. She knows it. The proof is tattooed on her arm. It's sitting in her trophy room. It's sprinkled on her social media feeds, which happen to be dotted with...}

\entryitemWithDescription{\hskip 0pt{}Andrew Tate loses appeal to relax judicial restrictions as he awaits human trafficking, rape trial}{https://apnews.com/article/4418c0192bd511656dfd4084bb3e9a31}{BUCHAREST, Romania (AP) --- Andrew Tate, the divisive social media influencer awaiting trial in Romania on charges of human trafficking and rape, lost an appeal Thursday to have the court relax geographical restrictions preventing him...}

\entryitemWithDescription{\hskip 0pt{}Medline recalls 1.5 million adult bed rails following 2 reports of entrapment deaths}{https://apnews.com/article/58e177d548d0dc22321ba04031eb5c1d}{NEW YORK (AP) --- Medical supply company Medline Industries is recalling some 1.5 million portable adult bed rails across the U.S. and Canada, following two reports of entrapment deaths associated with the products. The recall impacts two...}

\entryitemWithDescription{\hskip 0pt{}Plaza dedicated at the site where Sojourner Truth gave her 1851 `Ain't I a Woman?' speech}{https://apnews.com/article/837714dbb2f88578ffb07290bdca63b9}{AKRON, Ohio (AP) --- Hundreds gathered in an Ohio city on Wednesday to unveil a plaza and statue dedicated to abolitionist Sojourner Truth at the very spot where the women's rights pioneer gave an iconic 1851 speech now known as ``Ain't I...}

\entryitemWithDescription{\hskip 0pt{}Clerk over Alex Murdaugh trial spent thousands on bonuses, meals and gifts, ethics complaint says}{https://apnews.com/article/1d9acf592ae759f851059fbd11e28deb}{COLUMBIA, S.C. (AP) --- South Carolina officials have filed 76 counts of ethics violations against the court clerk who handled the Alex Murdaugh murder trial. The 25 pages of allegations accuse former Colleton County Clerk of Court Becky...}

\entryitemWithDescription{\hskip 0pt{}Nelly Korda makes a 10 and faces uphill climb at Women's Open}{https://apnews.com/article/bb05b5893c368e0b1a58c3d35b46f7a7}{LANCASTER, Pa. (AP) --- Nelly Korda took a 10 on her third hole of the U.S. Women's Open on Thursday when she hit three short-game shots into the stream in front of the par-3 12th green. It was a devastating start for the No. 1 player in...}

\entryitemWithDescription{\hskip 0pt{}Usher, Victoria Monét will receive prestigious awards from music industry group ASCAP}{https://apnews.com/article/a0811d2265ae4f6b1ec794dd59526534}{LOS ANGELES (AP) --- Usher will add another prestigious award to his already loaded trophy case. The American Society of Composers, Authors and Publishers said Thursday that Usher will receive its Voice of the Culture Award. He'll be...}

\entryitemWithDescription{\hskip 0pt{}Mets to cut Jorge López after reliever throws glove into stands following ejection}{https://apnews.com/article/e7202e80b33309ff0080e4d8416154e4}{NEW YORK (AP) --- Jorge López will be cut by the struggling New York Mets after the reliever threw his cap on the ground and glove into the stands following his ejection Wednesday at Citi Field. Mets manager Carlos Mendoza called the...}

\entryitemWithDescription{\hskip 0pt{}McDonald's says \$18 Big Mac meal was an 'exception' and news reports overstated its price increases}{https://apnews.com/article/c9c4abef25369f6b87b2781f5658bc0e}{McDonald's is fighting back against viral tweets and media reports that it says have exaggerated its price increases. In a post on the company's website Wednesday, McDonald's U.S. President Joe Erlinger said reports suggesting the price...}

\entryitemWithDescription{\hskip 0pt{}The French Open introduces head-cams for chair umpires in bid to enhance TV viewing experience}{https://apnews.com/article/c5776fb154e4907e111e0c7276e66986}{PARIS (AP) --- From interactions with players to making the correct call at the French Open, TV viewers can now see exactly what the chair umpire is looking at. For the first time, chair umpires at the main Court Philippe Chatrier are...}

\entryitemWithDescription{\hskip 0pt{}A fifth grader's fundraiser cleared his school of meal debt. It named an award for him}{https://apnews.com/article/c6d8f4c82ef5a7651953c880c8513974}{As the school year drew to a close, Daken Kramer worried about children who owed money for meals at his school. So the enterprising fifth grader decided to do something about it. Daken, 11, posted a video last month challenging friends...}