\entryitemWithDescription{\hskip 0pt{}Arizona gov steps in; scheduled execution unlikely next week}{https://apnews.com/article/d522d5087030f73783881110d4b29056}{FILE - This undated file photo provided by the Arizona Department of Corrections, Rehabilitation and Reentry shows Aaron Brian Gunches, who was convicted of murder in the 2002 killing of Ted Price in Maricopa County, Ariz. The Arizona...}

\entryitemWithDescription{\hskip 0pt{}Why does Russia want tactical nuclear weapons in Belarus?}{https://apnews.com/article/583a92f8a9710c613449180abf49ab13}{FILE - Belarusian army Su-25 jet fighters fly during a parade marking Independence Day in Minsk, Belarus, Wednesday, July 3, 2019. Russian President Vladimir Putin has announced that he intends to deploy tactical nuclear weapons on the...}

\entryitemWithDescription{\hskip 0pt{}NJ takes over Paterson police after crisis worker's shooting}{https://apnews.com/article/331860a671700a0625f94c207837427c}{FILE - New Jersey Attorney General Matt Platkin speaks in Trenton, N.J., Feb. 3, 2020. On Monday, March 27, 2023, Platkin says his office has taken control of the police department in the state\textquotesingle s third-largest city...}

\entryitemWithDescription{\hskip 0pt{}What can Google's AI-powered Bard do? We tested it for you}{https://apnews.com/article/14ee02cb71b32f0e1fc87a4173c03796}{A portion of Google\textquotesingle s Bard website is shown in Glenside, Pa., Monday, March 27, 2023. The recently rolled-out bot dubbed Bard is the internet search giant\textquotesingle s answer to the ChatGPT tool that Microsoft has...}

\entryitemWithDescription{\hskip 0pt{}Chipotle agrees to pay after closing store that sought union}{https://apnews.com/article/af89f99249bd805fd714751bae040181}{FILE - The Chipotle Mexican Grill logo is seen on a storefront, Friday, Oct. 14, 2022, in Boston. On Monday, March 27, 2023, union officials said Chipotle Mexican Grill has agreed to pay \$240,000 to former employees as part of a...}

\entryitemWithDescription{\hskip 0pt{}Patriots owner Robert Kraft campaigns against antisemitism}{https://apnews.com/article/5da8844493522237f7e3426b93307d9a}{FILE - New England Patriots owner Robert Kraft walks the field during practice before an NFL football game against the Buffalo Bills, Sunday, Jan. 8, 2023, in Orchard Park, N.Y. On Monday, March 27, 2023, Kraft launched a \$25-million...}

\entryitemWithDescription{\hskip 0pt{}Twitter celebs balk at paying Elon Musk for blue check mark}{https://apnews.com/article/2a9fbe4ea805763f50d4de2c417ce4ff}{FILE - A Twitter logo hangs outside the company\textquotesingle s offices in San Francisco, on Dec. 19, 2022. William Shatner, Monica Lewinsky and other prolific Twitter commentators --- some household names, others little-known...}

\entryitemWithDescription{\hskip 0pt{}Taron Egerton slots Tetris story into place in new biopic}{https://apnews.com/article/a0d76e813f202017efeaa024aadbce36}{This image released by Apple TV+ shows Nikita Efremov, left, and Taron Egerton in a scene from "Tetris," premiering March 31, 2023. (Angus Pigott/Apple TV+ via AP) The origin story of the iconic computer game ``Tetris'' is more thrilling...}

\entryitemWithDescription{\hskip 0pt{}Nashville school shooter had drawn maps, done surveillance}{https://apnews.com/article/5da45b469ccb6c9533bbddf20c1bfe16}{Children and a woman depart the reunification center at the Woodmont Baptist church after a school shooting, Monday, March 27, 2023, in Nashville, Tenn. (AP Photo/John Bazemore) NASHVILLE, Tenn. (AP) --- The suspect in a Nashville school...}

\entryitemWithDescription{\hskip 0pt{}No atmosphere found at faraway Earth-sized world, study says}{https://apnews.com/article/c963f4a0647d88dea37f85fa4bdbb642}{This illustration provided by the European Space Agency depicts what the exoplanet TRAPPIST-1 b could look like. On Monday, March 27, 2023, scientists said the Webb Space Telescope has found no evidence of an atmosphere at this innermost...}

\entryitemWithDescription{\hskip 0pt{}Sabres' Russian player won't take part in Pride night warmup}{https://apnews.com/article/5ab30a581bfe0f372cf109bbdafa509a}{FILE - Buffalo Sabres\textquotesingle{} Ilya Lyubushkin plays during an NHL hockey game, Friday, March 17, 2023, in Philadelphia. Lyubushkin is citing an anti-gay Kremlin law and fears of facing retribution at home in Russia for electing...}

\entryitemWithDescription{\hskip 0pt{}In Trump probe, key witness as grand jury is back at work}{https://apnews.com/article/742461a52c86bb491667b085bc1aaa0b}{A vehicle leaves the garage at the state office building after David Pecker, former CEO of National Enquirer parent company, was believed to have met with a grand jury convening for the investigation of former President Donald Trump...}

\entryitemWithDescription{\hskip 0pt{}Whitney Houston's family wants to highlight her gospel roots}{https://apnews.com/article/8f6b27a4c8b4749352604ca64fc76d7e}{FILE - Singer Whitney Houston performs at the pre-Grammy gala \& salute to industry icons with Clive Davis honoring David Geffen in Beverly Hills, Calif., on Feb. 13, 2011. A new posthumous gospel album ``I Go to the Rock: The Gospel...}