\entryitemWithDescription{\hskip 0pt{}Severe solar storm creates dazzling auroras farther south}{https://apnews.com/article/9a3399d88ec0e14293f06e77d61099c4}{An aurora borealis, also known as the northern lights, is seen in the night sky in the early morning hours of Monday, April 24, 2023, near Washtucna, Wash. An intense solar storm has the aurora borealis gracing the skies farther south...}

\entryitemWithDescription{\hskip 0pt{}'Dancing With the Stars' judge Len Goodman dies at 78}{https://apnews.com/article/3202b3512776199678dbd821cf48f040}{FILE - From left, judges Craig Revel Horwood, Len Goodman and Bruno Tonioli gesture, during the final dress rehearsal for the opening of the \textquotesingle Strictly Come Dancing Live Tour\textquotesingle{} at the NIA, Birmingham...}

\entryitemWithDescription{\hskip 0pt{}Did Ed Sheeran hit pilfer Marvin Gaye classic? Trial to tell}{https://apnews.com/article/3f4f9f00ffcaa8dd8d9c6f51872e7285}{FILE - Ed Sheeran performs at Z100\textquotesingle s iHeartRadio Jingle Ball on Dec. 10, 2021, in New York. Jury selection and opening statements are expected to begin Monday, April 24, 2023, in a trial that mashes up Ed Sheeran...}

\entryitemWithDescription{\hskip 0pt{}Morgan Wallen cancels Ole Miss show after losing his voice}{https://apnews.com/article/6fc8f905d06b67ebd7ad120a157d8448}{FILE - Morgan Wallen performs on the first night of the 2022 iHeartRadio Music Festival, on Sept. 23, 2022, in Las Vegas. Thousands of country music fans were awaiting the singer when he suddenly canceled his performance Sunday night...}

\entryitemWithDescription{\hskip 0pt{}SeaWorld euthanizes sick sea lion found on San Diego freeway}{https://apnews.com/article/5e787fdfaad0187e681f91f32608bef3}{SAN DIEGO (AP) --- Freeway, the sea lion rescued after wandering inland from his ocean home and crossing busy San Diego thoroughfares, has been euthanized after falling ill. The sea lion earned his name in January 2022 after being found...}

\entryitemWithDescription{\hskip 0pt{}NBCUniversal CEO Shell departs over `inappropriate conduct'}{https://apnews.com/article/07bad3ee36d0eef660de9282cb88dcba}{FILE - Jeff Shell poses for a picture at the 2014 LA\textquotesingle s Promise Gala, Tuesday, Sept. 30, 2014, in Universal City, Calif. Shell, the chief executive of NBCUniversal, is departing the company after an investigation into...}

\entryitemWithDescription{\hskip 0pt{}Lizzo brings drag queens on stage, protesting Tennessee law}{https://apnews.com/article/c73bc8f777b28148dea90a3cca347701}{FILE - Lizzo arrives at the 65th annual Grammy Awards on Feb. 5, 2023, in Los Angeles. In a concert Friday, April 21, 2023 in Knoxville, Tenn., Lizzo filled the stage with drag queens in a glittery protest against the state...}

\entryitemWithDescription{\hskip 0pt{}Bird strike sparks plane engine fire shortly after takeoff}{https://apnews.com/article/83ad8ab9bb47edb321be9bbf75289f0c}{COLUMBUS, Ohio (AP) --- A bird strike sparked an engine fire on a plane shortly after it took off Sunday from an Ohio airport, and the airliner returned safely with no injuries reported, authorities said. American Airlines flight 1958 had...}

\entryitemWithDescription{\hskip 0pt{}Gunfire took their son at 20. Now it takes his daughter, 12}{https://apnews.com/article/74173049450d4915c71a25dc1b0c9f5c}{This image provided by Jeremy Stein shows Hartford Mayor Luke Bronin addressing a crowd gathering for a vigil on Saturday, April 22, 2023, on the same street where Se\textquotesingle Cret Pierce, 12, was shot in the head by a stray bullet...}

\entryitemWithDescription{\hskip 0pt{}Wahoo! `The Super Mario Bros. Movie' is No. 1 for third week}{https://apnews.com/article/5fff8c44f66627fa49fa4a630441fb26}{Jack Black arrives at the premiere of "The Super Mario Bros. Movie," Saturday, April 1, 2023, at Regal LA Live in Los Angeles. (Photo by Allison Dinner/Invision/AP) NEW YORK (AP) --- ``The Super Mario Bros. Movie'' continued to rack up...}

\entryitemWithDescription{\hskip 0pt{}Ex-Disney employee allegedly shot videos up women's skirts}{https://apnews.com/article/104cd805bbec63cc94adb27a7a0c5d65}{Cinderella Castle stands at the Magic Kingdom, at Walt Disney World, in Lake Buena Vista, Fla., Monday, April 3, 2023. (Joe Burbank/Orlando Sentinel via AP) ORLANDO, Fla. (AP) --- A former Walt Disney World employee is facing a charge...}

\entryitemWithDescription{\hskip 0pt{}Dying patients protest looming telehealth crackdown}{https://apnews.com/article/a6d5a0d3e923760f77cd246ea1927dd1}{Georgene White stands for a portrait with a photo of her mother, Teri Sheridan, in Belvidere, N.J., Thursday, April 20, 2023. At age 93, struggling with the effects of a stroke, heart failure and recurrent cancer, Sheridan was ready to...}

\entryitemWithDescription{\hskip 0pt{}39 bodies dug up in cult investigation of pastor in Kenya}{https://apnews.com/article/2a3dfeea30df8b841391bd5f1ef36783}{Police and local residents load the exhumed bodies of victims of a religious cult into the back of a truck in the village of Shakahola, near the coastal city of Malindi, in southeastern Kenya Sunday, April 23, 2023. Dozens of bodies have...}