\entryitemWithDescription{\hskip 0pt{}Fox Chair Murdoch says 2020 election was fair: court filings}{https://apnews.com/article/91d6c6e7d39083b7732787e013bb1fc4}{FILE - Rupert Murdoch introduces Secretary of State Mike Pompeo during the Herman Kahn Award Gala, in New York, Oct. 30, 2018. A voting technology company suing Fox News is arguing that Fox Corp. leaders Rupert and Lachlan Murdoch played...}

\entryitemWithDescription{\hskip 0pt{}When Hollywood needs a movie villain, the tech bro answers}{https://apnews.com/article/2eae1d6c3805d53339cdd7c1507f4687}{This image released by Netflix shows Edward Norton in a scene from "Glass Onion: A Knives Out Mystery." Norton portrays Miles Bron, an eccentric tech billionaire who brings his wealthy friends to a private island in Greece to take part in...}

\entryitemWithDescription{\hskip 0pt{}'Boy Meets World' star Ben Savage enters US House race in LA}{https://apnews.com/article/6b08ccc4a25f39c6cba562fb0b35da13}{FILE - Actor Ben Savage arrives at night one of the Creative Arts Emmy Awards in Los Angeles on Sept. 10, 2016. Savage has joined the race for a U.S. House seat in Southern California. The ``Boy Meets World'' star says on Instagram that ``...}

\entryitemWithDescription{\hskip 0pt{}Safety agency opens probe of Norfolk Southern rail accidents}{https://apnews.com/article/2c819f2c469102332d4b1abf4c6e8923}{A view of the scene Feb. 24, 2023, as the cleanup continues at the site of of a Norfolk Southern freight train derailment that happened on Feb. 3 in East Palestine, Ohio. Pennsylvania Gov. Josh Shapiro said Monday, March 6, 2023 that...}

\entryitemWithDescription{\hskip 0pt{}Women sue Texas over abortion ban, say it risked their lives}{https://apnews.com/article/632fad72e0f5b255a3a55274cd097fa9}{Amanda Zurawski, one of five plaintiffs in Zurawski v. State of Texas, speaks in front of the Texas State Capitol in Austin, Texas, Tuesday, March 7, 2023, as the Center for Reproductive Rights and the plaintiffs announced their lawsuit...}

\entryitemWithDescription{\hskip 0pt{}Prosecutor calls XXXTentacion's alleged killers 'predators'}{https://apnews.com/article/b5554a58f1f87043b8088e3d9b642425}{During her closing arguments in the XXXTentacion murder trial, Assistant State Attorney Pascale Achille holds up a camouflage hat with a red brim that was seen worn by shooting suspect Michael Boatwright in multiple surveillance videos...}

\entryitemWithDescription{\hskip 0pt{}US judge strikes down Missouri gun law as unconstitutional}{https://apnews.com/article/7a32436411f7b32c7f7870381c089b51}{FILE - Police investigate the scene where an officer was shot in the leg in a parking lot, April 29, 2021, in St Peters, Mo. A federal judge ruled Tuesday, March 7, 2023, that a Missouri law banning local police form enforcing federal gun...}

\entryitemWithDescription{\hskip 0pt{}Tucker Carlson amplifies Jan. 6 lies with GOP-provided video}{https://apnews.com/article/adc245e22f50b076925eb72948062808}{Some Republican Senators are disagreeing with a distorted display of the January 6 riot through videos broadcast by Tucker Carlson on his primetime Fox News show. (March 7) FILE - Rioters at the U.S. Capitol on Jan. 6, 2021, in...}

\entryitemWithDescription{\hskip 0pt{}Russian gallery shows art by 'Merchant of Death' freed by US}{https://apnews.com/article/1f3cef1eac6969bf288249c3b197f952}{Viktor Bout, a Russian arms dealer who was sentenced to 25 years in the United States, speaks to the media prior to an opening ceremony of the exhibition of his artworks at the Mosfilm studio in Moscow, Russia, Tuesday, March 7, 2023...}

\entryitemWithDescription{\hskip 0pt{}Battle for Bakhmut takes center stage in war in Ukraine}{https://apnews.com/article/9056fed0866bfb4c651283d85c895544}{FILE - video footage of Bakhmut shot from the air with a drone for The Associated Press on Monday, Feb. 13, 2023, shows how the longest battle of the year-long Russian invasion has turned the city of salt and gypsum mines in eastern...}

\entryitemWithDescription{\hskip 0pt{}In reversal, Biden weighs detaining migrant families}{https://apnews.com/article/0909546c3984ae439b376d02c40ac7ff}{President Joe Biden delivers remarks to the 2023 International Association of Fire Fighters Legislative Conference, Monday, March 6, 2023, in Washington. (AP Photo/Evan Vucci) WASHINGTON (AP) --- The Biden administration is considering...}

\entryitemWithDescription{\hskip 0pt{}How passengers teamed up to restrain man on chaotic flight}{https://apnews.com/article/537e7e75621d4a393852aac923ee694f}{This image provided by Simik Ghookasian shows passengers and crew members restraining a man who according to federal authorities tried to open an airliner's emergency door and tried to stab a flight attendant on a weekend flight from Los...}

\entryitemWithDescription{\hskip 0pt{}'Oh my daughter': Volunteer medic, 29, buried in Ukraine}{https://apnews.com/article/c7a12e4e769ac945025c8842f3fabd04}{Relatives gather next to the body of 29 year old Yana Rikhlitska, a Ukrainian army medic killed in the Bakhmut area, during the funeral in Vinnytsia, Ukraine, Tuesday, March 7, 2023. Just over a week ago, Yana Rikhlitska was filmed by The...}