\entryitemWithDescription{\hskip 0pt{}An engine cover on a Southwest Airlines plane rips off, forcing the flight to return to Denver}{https://apnews.com/article/7fd2b99e38f5552cfe48b513f72afbb3}{DENVER (AP) --- A Southwest Airlines jet returned to Denver Sunday morning after the engine cover fell off and struck the wing flap during takeoff, according to the Federal Aviation Administration. The Boeing 737 landed safely, and the...}

\entryitemWithDescription{\hskip 0pt{}`Godzilla x Kong' maintains box-office dominion in second weekend}{https://apnews.com/article/4ebc622a403a3eb21377927ffe77d8b7}{NEW YORK (AP) --- ``Godzilla x Kong: The New Empire'' easily swatted away a pair of challengers to hold on to the top spot at the box office for the second week in a row, according to studio estimates Sunday. After its above...}

\entryitemWithDescription{\hskip 0pt{}10,000 miles and 352 days later, a UK man reaches his goal of running the length of Africa}{https://apnews.com/article/dd53f51d3cb9a90fc431e007e58c2af0}{RAS ANGELA, Tunisia (AP) --- Sore and sandblasted but triumphant, runner Russ Cook reached the northernmost point of Africa on Sunday, almost a year after he set off from its southern tip on a quest to run the length of the continent...}

\entryitemWithDescription{\hskip 0pt{}CMT Awards return Sunday night with host Kelsea Ballerini and a tribute to the late Toby Keith}{https://apnews.com/article/ec7a3a43a049efc0ec1452811bcb9e39}{The CMT Music Awards, celebrating the best in country music videos, are set to return on Sunday night live from Austin, Texas. Hosted by Kelsea Ballerini, the fan-voted show begins at 8 p.m. Eastern and will be broadcast from the Moody...}

\entryitemWithDescription{\hskip 0pt{}Verstappen bounces back with dominant win at Japanese Grand Prix}{https://apnews.com/article/7d63bf4d38c914b52800f0fd323708ae}{SUZUKA, Japan (AP) --- Max Verstappen's record-breaking dominance in Formula 1 resumed Sunday with his victory in the Japanese Grand Prix, leading almost the entire race on a sunny day in central Japan. His abrupt breakdown two weeks ago...}

\entryitemWithDescription{\hskip 0pt{}Powerball draws numbers for estimated \$1.3B jackpot after delay of more than 3 hours}{https://apnews.com/article/bbc041bf14b984c38d9f66803394d398}{DES MOINES, Iowa (AP) --- Powerball drew the numbers early Sunday morning for an estimated \$1.3 billion jackpot after a delay of more than three hours. The numbers drawn were: 22, 27, 44, 52, 69 and the red Powerball 9. The latest...}

\entryitemWithDescription{\hskip 0pt{}19 cats roam Mexico's presidential palace. A new declaration gives them food and care fur-ever}{https://apnews.com/article/501eb21e6953850369261013c94a180a}{MEXICO CITY (AP) --- They prowl through palace gardens stalking pigeons and make cameos on televised press briefings. Some greet tourists at the doors, while others take a sneaky lick of ice cream from staff. Nineteen feral cats have free...}

\entryitemWithDescription{\hskip 0pt{}Iowa-UConn women's Final Four match was most-watched hoops game in ESPN history; 14.2M avg. viewers}{https://apnews.com/article/7ac76c353a0d1c2ed7f45c46a91b5ac5}{BRISTOL, Conn. (AP) --- Iowa's 71-69 victory over UConn at the women's Final Four on Friday night averaged 14.2 million viewers on ESPN, making it the most-viewed women's basketball game on record and the largest audience for an ESPN...}

\entryitemWithDescription{\hskip 0pt{}The world's oldest man says the secret to his longevity is luck, plus regular fish and chips}{https://apnews.com/article/cc1a154db05464106c1f05bdb09df73c}{LONDON (AP) --- The world's oldest man says the secret to his long life is luck, moderation --- and fish and chips every Friday. Englishman John Alfred Tinniswood, 111, has been confirmed as the new holder of the title by Guinness World...}

\entryitemWithDescription{\hskip 0pt{}A Virgin Atlantic plane clipped a BA jet at Heathrow but no injuries were reported}{https://apnews.com/article/fb60a9c42624b9fb61d312d346b34614}{LONDON (AP) --- A Virgin Atlantic jet collided with another plane while it was being towed at Heathrow Airport on Saturday, aviation authorities said. There were no reports of injuries. Virgin said its Boeing 787-9 had completed a flight...}

\entryitemWithDescription{\hskip 0pt{}Guardians ace Shane Bieber to have season-ending Tommy John surgery after solid start in 2024}{https://apnews.com/article/18cf94b906d91e02c2d83765f3f0e25d}{CLEVELAND (AP) --- Cleveland Guardians ace Shane Bieber will have season-ending Tommy John elbow surgery, a major blow to the team and the 2020 Cy Young winner. Bieber, who missed several months last season with elbow issues, experienced...}

\entryitemWithDescription{\hskip 0pt{}Powerball prize climbs to \$1.3B ahead of next drawing}{https://apnews.com/article/a46a6a91586a397dc7cb632cc4839c23}{DES MOINES, Iowa (AP) --- Lottery players will have another shot Saturday night at a Powerball jackpot that has grown to an estimated \$1.3 billion after more than three months without a winner. There have been 40 consecutive drawings...}

\entryitemWithDescription{\hskip 0pt{}Lawsuit naming Sean `Diddy' Combs as co-defendant alleges his son sexually assaulted woman on yacht}{https://apnews.com/article/9132c5408e81741489a23a2d982cf638}{LOS ANGELES (AP) --- A lawsuit that names Sean ``Diddy'' Combs as a co-defendant alleges that his son Christian ``King'' Combs sexually assaulted a woman working on a yacht chartered by his father. The suit filed Thursday in Los Angeles...}