\entryitemWithDescription{\hskip 0pt{}Documents detail EMTs' failure to aid Tyre Nichols}{https://apnews.com/article/d2a8c86ead813564d56d253a80c699f9}{FILE - In this image from video released and partially redacted by the city of Memphis, Tenn., Tyre Nichols lies on the ground during a brutal attack by Memphis Police officers, Jan. 7, 2023, in Memphis. Documents released Thursday, March...}

\entryitemWithDescription{\hskip 0pt{}Rep. George Santos under investigation by House Ethics panel}{https://apnews.com/article/898cc3e7e6af8659f9c6249f187362d4}{FILE - Rep. George Santos, R-N.Y., leaves a House GOP conference meeting on Capitol Hill, in Washington, Jan. 25, 2023. (AP Photo/Andrew Harnik, File) WASHINGTON (AP) --- The House Ethics Committee announced Thursday it is launching an...}

\entryitemWithDescription{\hskip 0pt{}George Santos now under investigation by House Ethics panel}{https://apnews.com/article/17e79bca35567b12e492664f0c3b5430}{FILE - Rep. George Santos, R-N.Y., leaves a House GOP conference meeting on Capitol Hill, in Washington, Jan. 25, 2023. (AP Photo/Andrew Harnik, File) WASHINGTON (AP) --- The House Ethics Committee on Thursday announced that it has...}

\entryitemWithDescription{\hskip 0pt{}New Easter Island statue found in volcanic crater's dry lake}{https://apnews.com/article/807e5de7b5cd006e73ce57402bfce302}{FILE - Moai statues stand on Ahu Tongariki near the Rano Raraku volcano, top, on Rapa Nui, or Easter Island, Chile, Nov. 27, 2022. According to Salvador Atan Hito, vice president of the Ma\textquotesingle u Henua Indigenous community...}

\entryitemWithDescription{\hskip 0pt{}Trump can be sued for Jan. 6 riot harm, Justice Dept. says}{https://apnews.com/article/d18d0c6369837c725578cf6e13c18883}{FILE - In this Jan. 6, 2021, file photo, President Donald Trump speaks during a rally protesting the electoral college certification of Joe Biden as President in Washington. Trump can be sued by injured Capitol Police officers and...}

\entryitemWithDescription{\hskip 0pt{}No bail for Pennsylvania man with explosives in suitcase}{https://apnews.com/article/0d2df43cc953f4883e44fb834bedb7b9}{This airport surveillance camera image released in an FBI affidavit shows alleged suspect Marc Muffley at Lehigh Valley International Airport in Allenstown, Pa., on Monday, Feb. 27, 2023. Muffley was arrested Monday after an explosive was...}

\entryitemWithDescription{\hskip 0pt{}Wayne Shorter, jazz saxophone pioneer, dies at 89}{https://apnews.com/article/1c0a39a5df81f2227db907f2d8ea87d0}{FILE - Jazz saxophonist Wayne Shorter performs at the 5 Continents Jazz Festival in Marseille, southern France on July 23, 2013. Shorter, whose lyrical jazz compositions and pioneering saxophone playing sounded through more than half a...}

\entryitemWithDescription{\hskip 0pt{}Bill limiting drag shows sparks chants of 'shame' from foes}{https://apnews.com/article/2a09ddd2ac572ba49c3eab5aeb3773c7}{Drag performer Poly Tics, right, attends a rally in Frankfort, Ky., on Thursday, March 2, 2023. She spoke earlier at a legislative committee hearing where she opposed a bill that would put limits on drag shows in Kentucky. (AP Photo/Bruce...}

\entryitemWithDescription{\hskip 0pt{}Why Sara Netanyahu's hair salon trip ended with riot police}{https://apnews.com/article/a2b2b7f9b85245aba53c9c4e7cd67cf7}{FILE - Former Israeli Prime Minister and the head of Likud party, Benjamin Netanyahu and his wife Sara gesture after first exit poll results for the Israeli Parliamentary election at his party\textquotesingle s headquarters in Jerusalem...}

\entryitemWithDescription{\hskip 0pt{}Gunmen threaten Messi, shoot up family-owned supermarket}{https://apnews.com/article/ce420f9d5d0daa06c3faccb8838b32d9}{FILE - A mural of soccer player Lionel Messi blankets the facade of an apartment building in Rosario, Argentina, Aug. 19, 2022. Gunmen threatened Messi in a written message left March 2, 2023 when they opened fire at a supermarket owned...}

\entryitemWithDescription{\hskip 0pt{}At New Mexico St, a meltdown that runs beyond basketball}{https://apnews.com/article/d2b20604aa91ddc11cc32a4f12e660f6}{New Mexico State coach Greg Heiar reacts during the team\textquotesingle s basketball game against UTEP on Nov. 30, 2022, in Las Cruces, N.M. At New Mexico State, the once-treasured men\textquotesingle s basketball program has been...}

\entryitemWithDescription{\hskip 0pt{}Defense says zeal to convict Murdaugh derailed investigation}{https://apnews.com/article/7db9faf0ad165899385c52bf990c54cd}{Alex Murdaugh listens to the jury charges during his double murder trial at the Colleton County Courthouse on Thursday, March 2, 2023, in Walterboro, S.C. The 54-year-old attorney is standing trial on two counts of murder in the shootings...}

\entryitemWithDescription{\hskip 0pt{}Half of California freed from drought thanks to rain, snow}{https://apnews.com/article/d28c947cc8633f741871844c41006b7e}{State Route 138 winds through snow-covered trees near Hesperia, Calif., Wednesday, March 1, 2023. Tremendous rains and snowfall since late last year have freed half of California from drought, but low groundwater levels remain a...}