\entryitemWithDescription{\hskip 0pt{}vlang/v}{https://github.com/vlang/v}{Simple, fast, safe, compiled language for developing maintainable
software. Compiles itself in \textless1s with zero library dependencies.
Supports automatic C =\textgreater{} V translation. https://vlang.io\\
Language: V\\
Stars: 32365\\
Forks: 1971}

\entryitemWithDescription{\hskip 0pt{}donnemartin/system-design-primer}{https://github.com/donnemartin/system-design-primer}{Learn how to design large-scale systems. Prep for the system design
interview. Includes Anki flashcards.\\
Language: Python\\
Stars: 212839\\
Forks: 38016}

\entryitemWithDescription{\hskip 0pt{}awesome-selfhosted/awesome-selfhosted}{https://github.com/awesome-selfhosted/awesome-selfhosted}{A list of Free Software network services and web applications which can
be hosted on your own servers\\
Language: Makefile\\
Stars: 122071\\
Forks: 7092}

\entryitemWithDescription{\hskip 0pt{}microsoft/unilm}{https://github.com/microsoft/unilm}{Large-scale Self-supervised Pre-training Across Tasks, Languages, and
Modalities\\
Language: Python\\
Stars: 9833\\
Forks: 1597}

\entryitemWithDescription{\hskip 0pt{}coollabsio/coolify}{https://github.com/coollabsio/coolify}{An open-source \& self-hostable Heroku / Netlify alternative.\\
Language: Svelte\\
Stars: 6813\\
Forks: 346}

\entryitemWithDescription{\hskip 0pt{}0x192/universal-android-debloater}{https://github.com/0x192/universal-android-debloater}{Cross-platform GUI written in Rust using ADB to debloat non-rooted
android devices. Improve your privacy, the security and battery life of
your device.\\
Language: Rust\\
Stars: 8363\\
Forks: 480}

\entryitemWithDescription{\hskip 0pt{}typeorm/typeorm}{https://github.com/typeorm/typeorm}{ORM for TypeScript and JavaScript. Supports MySQL, PostgreSQL, MariaDB,
SQLite, MS SQL Server, Oracle, SAP Hana, WebSQL databases. Works in
NodeJS, Browser, Ionic, Cordova and Electron platforms.\\
Language: TypeScript\\
Stars: 30571\\
Forks: 5677}

\entryitemWithDescription{\hskip 0pt{}lukasz-madon/awesome-remote-job}{https://github.com/lukasz-madon/awesome-remote-job}{A curated list of awesome remote jobs and resources. Inspired by
https://github.com/vinta/awesome-python\\
Language: Unknown\\
Stars: 24478\\
Forks: 2410}

\entryitemWithDescription{\hskip 0pt{}openai/openai-cookbook}{https://github.com/openai/openai-cookbook}{Examples and guides for using the OpenAI API\\
Language: Jupyter Notebook\\
Stars: 14523\\
Forks: 1923}

\entryitemWithDescription{\hskip 0pt{}willwulfken/MidJourney-Styles-and-Keywords-Reference}{https://github.com/willwulfken/MidJourney-Styles-and-Keywords-Reference}{A reference containing Styles and Keywords that you can use with
MidJourney AI. There are also pages showing resolution comparison, image
weights, and much more!\\
Language: Unknown\\
Stars: 3717\\
Forks: 616}

\entryitemWithDescription{\hskip 0pt{}f/awesome-chatgpt-prompts}{https://github.com/f/awesome-chatgpt-prompts}{This repo includes ChatGPT prompt curation to use ChatGPT better.\\
Language: HTML\\
Stars: 34991\\
Forks: 4005}