\entryitemWithDescription{\hskip 0pt{}First Pooh, now Mickey. In public domain, early Mickey Mouse version will star in horror movies}{https://apnews.com/article/e5bd7d8c711554f42bdd277f0b7a29e7}{LOS ANGELES (AP) --- The earliest iteration of Mickey Mouse is on a rampage, barely two days in the public domain. Slashed free of Disney's copyright as of Monday, the iconic character from ``Steamboat Willie'' is already the focus of two...}

\entryitemWithDescription{\hskip 0pt{}DeSantis and Haley will appear at next week's CNN debate at the same time as Trump's Fox town hall}{https://apnews.com/article/88cddd58efa6dad45ca87ce14469f32e}{NEW YORK (AP) --- Florida Gov. Ron DeSantis and former United Nations Ambassador Nikki Haley are set to appear at next week's Republican presidential debate on CNN, while former President Donald Trump participates in a Fox News town hall...}

\entryitemWithDescription{\hskip 0pt{}`Bachelorette' Rachel Lindsay's husband, Bryan Abasolo, files for divorce after 4 years of marriage}{https://apnews.com/article/8fa9ddcc1a1676326ba43757710b7231}{LOS ANGELES (AP) --- The bloom is off the final rose for ``Bachelorette'' star Rachel Lindsay and husband Bryan Abasolo, who found love on the reality dating show. Court records show that Abasolo filed to end their marriage Tuesday. He...}

\entryitemWithDescription{\hskip 0pt{}\$842 million Powerball ticket sold in Michigan, first time the game has been won on New Year's Day}{https://apnews.com/article/247f720c4248e9b0fa3bc73caaf9af9f}{JOHNSTON, Iowa (AP) --- Someone in Michigan won an \$842.4 million Powerball jackpot on the first day of 2024, the first time it has been won on New Year's Day since the game's start in 1992. The winning numbers drawn were: 12, 21, 42...}

\entryitemWithDescription{\hskip 0pt{}ESPN apologizes for showing video of woman flashing breast during Sugar Bowl broadcast}{https://apnews.com/article/8a210d87a4b0457cfb26f6bc6bba8e17}{NEW ORLEANS (AP) --- ESPN apologized Monday night for a video clip of a woman baring her breast that was shown during the broadcast of the Sugar Bowl in New Orleans. It was aired coming out of a commercial during the second half of...}

\entryitemWithDescription{\hskip 0pt{}Ex-gang leader makes his bid in Las Vegas court for house arrest before trial in Tupac Shakur case}{https://apnews.com/article/cb3817f66e204ec85ba678bd5bad4126}{LAS VEGAS (AP) --- A former Los Angeles-area gang leader charged with killing hip-hop music icon Tupac Shakur in 1996 in Las Vegas plans to ask a judge on Tuesday to release him to house arrest ahead of the trial in June. Court-appointed...}

\entryitemWithDescription{\hskip 0pt{}Les McCann, innovative jazz musician best known for `Compared to What,' dies at 88}{https://apnews.com/article/587892db9a20cc4331c8c51f636e115d}{Les McCann, a prolific and influential musician and recording artist who helped found the soul-jazz genre and became a favorite source for sampling by Dr. Dre, A Tribe Called Quest and hundreds of other hip-hop performers, has died. He...}

\entryitemWithDescription{\hskip 0pt{}Rays shortstop Wander Franco arrested amid allegations of relationship with minor, AP source says}{https://apnews.com/article/99e94b7d6da72435535ac2b4d9cecef2}{SANTO DOMINGO, Dominican Republic (AP) --- Tampa Bay Rays shortstop Wander Franco was arrested Monday in the Dominican Republic after being interviewed by prosecutors investigating him for an alleged relationship with a minor, according...}

\entryitemWithDescription{\hskip 0pt{}Ashes of Canadian `Star Trek' fan to be sent into space along with those of TV series' stars}{https://apnews.com/article/f3d795690919cafaa188080349bd4bda}{VANCOUVER, British Columbia (AP) --- The family of a mother of eight who was a huge ``Star Trek'' fan has ensured the final frontier will be her ultimate resting place. Gloria Knowlan was 86 at the time of her death 12 years ago. A small...}

\entryitemWithDescription{\hskip 0pt{}135th Rose Parade boasts floral floats and sunny skies as California tradition kicks off the new year}{https://apnews.com/article/ab1fbddeb87140ec465fa19ecf695949}{PASADENA, Calif. (AP) --- Floral floats, marching bands and equestrian units took to the streets under a sunny California sky as the 135th Rose Parade drew hundreds of thousands of spectators on New Year's Day. The Pasadena tradition on...}

\entryitemWithDescription{\hskip 0pt{}Former NBA G League player held in woman's killing due in Vegas court after transfer from Sacramento}{https://apnews.com/article/13c78b8a0d9da91931e15296ed185883}{LAS VEGAS (AP) --- A former NBA developmental league player accused with his ex-girlfriend of killing a woman whose body was found last month in southern Nevada is due to face a Las Vegas judge on Tuesday following his transfer in custody...}

\entryitemWithDescription{\hskip 0pt{}Elvis, fishmongers and a Kraken win in a nautical scene for the NHL Winter Classic}{https://apnews.com/article/428356869f7b273b5892ad9311869044}{SEATTLE (AP) --- The part-owner of the franchise who was once more known for his exploits on the football field led the way off the bus, followed by players clad in white T-shirts and orange overalls as a tribute to the fishmongers...}

\entryitemWithDescription{\hskip 0pt{}Influential former Texas US Rep. Eddie Bernice Johnson dies at 88}{https://apnews.com/article/b72ea50b8f6bba4dd24768616f7ade4f}{DALLAS, Texas (AP) --- Trailblazing longtime U.S. Rep. Eddie Bernice Johnson, a nurse from Texas who helped bring hundreds of millions of federal dollars to the Dallas area as the region's most powerful Democrat, died Sunday. She was 88...}