\entryitemAp{\hskip 0pt{}Jags return fumble for TD, beat Titans for AFC South title}{https://apnews.com/article/jacksonville-jaguars-los-angeles-chargers-sports-nfl-football-joshua-dobbs-245237965ff4389a7d33ce3e58732333}{Jacksonville Jaguars linebacker Josh Allen (41) returns a fumble for a touchdown as defensive end Arden Key (49) covers in the second half of an NFL football game against the Tennessee Titans, Saturday, Jan. 7, 2023, in }

\entryitemAp{\hskip 0pt{}Seattle schools sue tech giants over social media harm}{https://apnews.com/article/social-media-seattle-lawsuits-mental-health-965a8f373e3bfed8157571912cc3b542}{This combination of 2017-2022 photos shows the logos of Facebook, YouTube, TikTok and Snapchat on mobile devices. On Friday, Jan. 6, 2023, Seattle Public Schools filed a lawsuit in U.S. District Court, suing the tech...}

\entryitemAp{\hskip 0pt{}Travelers rush to take advantage of China reopening}{https://apnews.com/article/health-china-hong-kong-beijing-business-49e31dedb78fd24c1077b340ebdafa1f}{Workers wearing face masks walk by as travelers wait at the departure hall of the Lok Ma Chau station following the reopening of crossing border with mainland China, in Hong Kong, Sunday, Jan. 8, 2023. Travelers...}

\entryitemAp{\hskip 0pt{}Mahomes sets record, Chiefs beat Raiders for AFC's top seed}{https://apnews.com/article/kansas-city-chiefs-las-vegas-raiders-sports-nfl-football-damar-hamlin-5d08f366a1e2319104eb54ce22a570d2}{Kansas City Chiefs quarterback Patrick Mahomes runs with the ball against the Las Vegas Raiders during the first half of an NFL football game Saturday, Jan. 7, 2023, in Las Vegas. (AP Photo/John Locher) LAS VEGAS (AP) --}

\entryitemAp{\hskip 0pt{}On eve of Biden's border visit, migrants fear new rules}{https://apnews.com/article/biden-politics-el-paso-united-states-government-cuba-82701453fb018778c04255c1e2b10564}{A migrant, far left, reaches to bump fists with a local resident demonstrating in support of migrants in downtown El Paso, Texas, Saturday, Jan. 7, 2023. Several hundred marched through the streets of El Paso a day...}

\entryitemAp{\hskip 0pt{}Subway train collision in Mexico City kills 1, injures 57}{https://apnews.com/article/mexico-city-caribbean-accidents-5f604dfae19afaef940260065cd43e69}{A subway passenger, injured when two subway trains collided, is taken on a stretcher to a waiting ambulance, outside the Raza station in Mexico City, Saturday, Jan. 7, 2023. Authorities announced at least one person was }

\entryitemAp{\hskip 0pt{}Speaker McCarthy: A weakened leader or emboldened survivor?}{https://apnews.com/article/politics-united-states-house-of-representatives-kevin-mccarthy-government-e986c620149b72030bb418bd5fadb4a2}{House Speaker Kevin McCarthy of Calif., gestures towards the newly installed nameplate at his office after he was sworn in as speaker of the 118th Congress in Washington, early Saturday, Jan. 7, 2023. (AP Photo/ Matt...}

\entryitemAp{\hskip 0pt{}Golden Globes are back on TV, but are reform efforts enough?}{https://apnews.com/article/golden-globe-awards-hollywood-foreign-press-association-tv-television-9ee1a25e378b0c707dcd1f5f205c405b}{FILE - Event signage appears above the red carpet at the 77th annual Golden Globe Awards on Jan. 5, 2020, in Beverly Hills, Calif. The 80th annual Golden Globe Awards will take place on Tuesday, Jan. 10. (Photo by...}

\entryitemAp{\hskip 0pt{}Drugstores make slow headway on staffing problems}{https://apnews.com/article/health-business-medication-covid-pandemics-7aa39f8227449cc3b4e1bd2d3b130716}{Jessi Stout, owner of the Table Rock Pharmacy fills a prescription on Friday, Jan. 6, 2023, in Morganton, N.C. Drugstore chains are still trying to find enough employees to put a stop to temporary pharmacy closures. (AP }

\entryitemAp{\hskip 0pt{}Mayor: Teacher shot by 6-year-old 'red flag for the country'}{https://apnews.com/article/education-teaching-newport-news-virginia-38beb789647975e2f8f0d7c7447eb777}{Students and police gather outside of Richneck Elementary School after a shooting, Friday, Jan. 6, 2023 in Newport News, Va. A shooting at a Virginia elementary school sent a teacher to the hospital and ended with ``an...}

\entryitemAp{\hskip 0pt{}UK palace allies push back against Prince Harry's claims}{https://apnews.com/article/queen-elizabeth-ii-king-charles-iii-politics-united-kingdom-prince-harry-952c0cbaa0c39d18b8338ca651b49394}{This undated screengrab issued by ITV on Friday Jan. 6, 2023 shows Britain\textquotesingle s Prince Harry speaking during an interview with ITV\textquotesingle s Tom Bradby for the programme Harry: The Interview. (Harry:}

\entryitemAp{\hskip 0pt{}W.Va. journalist let go after reporting on abuse allegations}{https://apnews.com/article/west-virginia-state-government-jim-justice-af942f587d098b2d996cc6e01991d615}{This undated photo shows former West Virginia Public Broadcasting reporter Amelia Ferrell Knisely. Knisely was let go from her job at WVPB on Dec. 20, 2022, after she wrote about the alleged abuse of people with...}

\entryitemAp{\hskip 0pt{}A first for reclaimed Kyiv cathedral: Christmas in Ukrainian}{https://apnews.com/article/russia-ukraine-war-moscow-religion-orthodox-church-9bea8791e5eda36a0b01cb3b6da86bd5}{Metropolitan Epiphanius, center right, and priests deliver an Orthodox Christmas service inside the nearly 1,000-year-old Pechersk Lavra Cathedral of Kyiv, Ukraine, Saturday, Jan. 7, 2023. Hundreds of Ukrainians heard...}

\entryitemAp{\hskip 0pt{}Big week for US-Mexico ties going into North American summit}{https://apnews.com/article/biden-politics-mexico-government-us-national-security-council-united-states-599d640834d079503c5dd568c312c19f}{FILE - President Joe Biden speaks as he meets with Mexican President Andrés Manuel López Obrador in the Oval Office of the White House in Washington, July 12, 2022. Biden will become the first U.S. leader to visit...}

\entryitemAp{\hskip 0pt{}EXPLAINER: New drug slows Alzheimer's but comes with caveats}{https://apnews.com/article/health-medication-b42dc8b32d71f1b6892b07d85e0e7da0}{U.S. health officials have approved a new Alzheimer's drug that modestly slows the brain-robbing disease. (Jan. 6) This Dec. 21, 2022 image provided by Eisai in January 2023, shows vials and packaging for their...}

\entryitemAp{\hskip 0pt{}States target transgender health care in first bills of 2023}{https://apnews.com/article/politics-health-texas-state-government-tennessee-minnesota-878a9217fa434f3ecd83738a71e40572}{FILE - The Utah State Capitol is shown on Feb. 1, 2022, in Salt Lake City. After a midterm election and record flow of anti-transgender legislation in 2022, Republican state lawmakers this year are zeroing in on...}

\entryitemAp{\hskip 0pt{}Ukraine hails US military aid as cease-fire said to falter}{https://apnews.com/article/politics-united-states-government-ukraine-russia-war-moscow-9b3a132b330c90a10e8f031113be241b}{A cupola lies on the ground in front of the Orthodox Church which was destroyed by Russian forces in the recently retaken village of Bogorodychne, Ukraine, Saturday, Jan. 7, 2022. (AP Photo/Evgeniy Maloletka) KYIV...}

\entryitemAp{\hskip 0pt{}AP PHOTOS: Snow is a no-show as Europe feels the winter heat}{https://apnews.com/article/weather-climate-and-environment-droughts-europe-ac556a03360f361496aefb1c3a6569b6}{FILE - People ski on a cross country slope in Ramsau, Austria, Friday, Jan. 6, 2023. Sparse snowfall and unseasonably warm weather in much of Europe is allowing green grass to blanket many mountaintops across the region }

\entryitemAp{\hskip 0pt{}Chaos in the House: McCarthy's plea, and begging for votes}{https://apnews.com/article/politics-kevin-mccarthy-matt-gaetz-florida-f2a4a42b4845f2413cca5c1b4c6100dd}{Rep. Richard Hudson, R-N.C., left, pulls Rep. Mike Rogers, R-Ala., back as they talk with Rep. Matt Gaetz, R-Fla., and others during the 14th round of voting for speaker as the House meets for the fourth day to try and...}

\entryitemAp{\hskip 0pt{}Utah murder-suicide underscores frequency of family killings}{https://apnews.com/article/health-crime-utah-suicide-1e17fba2d7966f7436de96ddc974e530}{Jess, left, sits next to her sister, Cecily, during a press conference regarding the killing of a family in Enoch, Utah on Thursday, Jan. 5, 2023. A Utah man fatally shot his five children, his mother-in-law and his...}

\entryitemAp{\hskip 0pt{}Biden faces Israel quandary with new Netanyahu government}{https://apnews.com/article/biden-politics-israel-government-united-states-palestinian-territories-67a5be67c720bfa6c85d8d5a3050b65a}{FILE - Newly sworn-in Israeli Prime Minister Benjamin Netanyahu attends a cabinet meeting in Jerusalem, Dec. 29, 2022. Netanyahu\textquotesingle s new government is vexing the Biden administration as it embarks on...}

\entryitemAp{\hskip 0pt{}Mexican capo's arrest a gesture to US, not signal of change}{https://apnews.com/article/biden-mexico-andres-manuel-lopez-obrador-crime-medication-c4b7625503207540c2e821d8bf0e3ca6}{Army soldiers drive past a destroyed vehicle on the streets of Jesus Maria, Mexico, on Saturday, Jan. 7, 2023, the small town where Ovidio Guzman was detained earlier in the week. Thursday\textquotesingle s government...}

\entryitemAp{\hskip 0pt{}Heart screening may not have prevented Hamlin's collapse}{https://apnews.com/article/buffalo-bills-sports-health-heart-disease-youth-0c18b0c970a6af73fd9434a937517475}{FILE - Buffalo Bills\textquotesingle{} Damar Hamlin is examined during the first half of an NFL football game against the Cincinnati Bengals, Monday, Jan. 2, 2023, in Cincinnati. Quick on-the-field emergency care from...}

\entryitemAp{\hskip 0pt{}China suspends social media accounts of COVID policy critics}{https://apnews.com/article/health-china-government-covid-19-pandemic-beijing-3259cdf2fb41e8dd3d64f6c6d3b7cc80}{A man wearing a face mask shops for Chinese Lunar New Year decorations at a pavement store in Beijing, Saturday, Jan. 7, 2023. China has suspended or closed the social media accounts of more than 1,000 critics of the...}

\entryitemAp{\hskip 0pt{}Mega Millions jackpot rises to \$1.1 billion after no winner}{https://apnews.com/article/lotteries-business-91724709aa5fb0805e1bcf7157aad738}{Electrician Jose Valles, 59, from Rancho Cucamonga, Calif., buys a SuperLotto Plus ticket at the gas station that previously sold the \$2.04 billion-winning Powerball ticket award at Joe\textquotesingle s Service...}

\entryitemAp{\hskip 0pt{}Family of slain Utah family says husband took guns from home}{https://apnews.com/article/utah-divorce-suicide-b2742ac684ad5fb4b0b506efac85578b}{Jess, left, sits next to her sister, Cecily, during a press conference regarding the killing of a family in Enoch, Utah on Thursday, Jan. 5, 2023. A Utah man fatally shot his five children, his mother-in-law and his...}

\entryitemAp{\hskip 0pt{}CES 2023: Startups aim to reduce global food waste}{https://apnews.com/article/CES-2023-las-vegas-climate-technology-0d0e84044c3d5218b10dc032cd2ff3c4}{An exhibitor demonstrates the OneThird avocado ripeness checker during CES Unveiled before the start of the CES tech show, Tuesday, Jan. 3, 2023, in Las Vegas. More than a thousand startups are showcasing their products }

\entryitemAp{\hskip 0pt{}Old NASA satellite falling from sky this weekend, low threat}{https://apnews.com/article/science-oddities-aerospace-technology-national-aeronautics-and-space-administration-2b960095b8726632d53ebb103077007a}{In this photo made available by NASA, the space shuttle Challenger launches the Earth Radiation Budget Satellite in 1984. On Friday, Jan. 6, 2023, the U.S. space agency said the 38-year-old NASA satellite is about to...}

\entryitemAp{\hskip 0pt{}'RuPaul's Drag Race' cast push back against hate, threats}{https://apnews.com/article/rupaul-drag-race-threats-264b6f3ce1a161492226616ec6a9f201}{Drag performer Loosey LaDuca arrives at the season 15 premiere of "RuPaul's Drag Race" in New York on Thursday, Jan. 5, 2023. (AP Photo/John Carucci) Contestants from ``RuPaul's Drag Race'' talk new season at its...}

\entryitemAp{\hskip 0pt{}Bills uplifted by Hamlin's recovery, place focus on Patriots}{https://apnews.com/article/new-england-patriots-buffalo-bills-sports-nfl-football-damar-hamlin-10911df45ebe7be39dadb851f219dd67}{Crews clear snow from a parking lot near a sign showing support for Buffalo Bills safety Damar Hamlin outside Highmark Stadium on Wednesday, Jan. 4, 2023, in Orchard Park, N.Y. (AP Photo/Joshua Bessex) ORCHARD PARK, N.Y.}

\entryitemAp{\hskip 0pt{}EXPLAINER: How armored vehicles aid Ukraine at critical time}{https://apnews.com/article/politics-military-technology-ukraine-government-russia-war-2d59aae94a7ad8a5c22083e77d699417}{FILE - American soldiers drive a Bradley fighting vehicle during a joint exercise with Syrian Democratic Forces at the countryside of Deir Ezzor in northeastern Syria, Dec. 8, 2021. The U.S. and Germany are sending...}

\entryitemAp{\hskip 0pt{}NYC hospitals prep for nurse strike amid negotiations}{https://apnews.com/article/health-new-york-city-manhattan-business-covid-aa271a346234a352bba7abe67638b55b}{FILE - Zach Clapp, a nurse in the Pediatric Cardiac ICU at Mount Sinai Hospital signs a board demanding safe staffing during a rally by NYSNA nurses from NY Presbyterian and Mount Sinai, Tuesday, March 16, 2021, in New...}

\entryitemAp{\hskip 0pt{}Orthodox celebrate Christmas in shadow of conflict}{https://apnews.com/article/putin-ukraine-government-religion-e0d9f15655e18308c991997f7fc71cf7}{Russian Orthodox Patriarch Kirill delivers a Christmas service in the Christ the Saviour Cathedral in Moscow, Russia, Friday, Jan. 6, 2023. Orthodox Christians celebrate Christmas on Jan. 7, in accordance with the...}

\entryitemAp{\hskip 0pt{}Hawaii eruption not dangerous but offers spectacular sight}{https://apnews.com/article/volcanoes-kilauea-hawaii-climate-and-environment-0fd356cfa61a82c7977f88e428ae8200}{This photo provided by Janice Wei shows the eruption inside the summit crater of the Kilauea volcano on the Big Island of Hawaii, Thursday, Jan. 5, 2023. Hawaii\textquotesingle s Kilauea, one of the world\...}

\entryitemAp{\hskip 0pt{}Police: 6-year-old shoots teacher in Virginia classroom}{https://apnews.com/article/newport-news-virginia-88dfe91f65173cbbd198a8816a21b5be}{Police respond to a shooting at Richneck Elementary School, Friday, Jan. 6, 2023 in Newport News, Va. A shooting at a Virginia elementary school sent a teacher to the hospital and ended with ``an individual'' in custody }

\entryitemAp{\hskip 0pt{}Message from US asylum hopefuls: Financial sponsors needed}{https://apnews.com/article/biden-venezuela-mexico-spokane-violence-0eb316a474baed22f433359b0644320b}{Dr. Kyle Varner, second from the right, who sponsors and houses people through the Venezuelan humanitarian parole program, speaks at his house with program beneficiaries, from left, Maria Amare, Cesar Baez, Jenderson...}

\entryitemAp{\hskip 0pt{}EXPLAINER: What is ChatGPT and why are schools blocking it?}{https://apnews.com/article/what-is-chat-gpt-ac4967a4fb41fda31c4d27f015e32660}{A ChatGPT prompt is shown on a device near a public school in Brooklyn, New York, Thursday, Jan. 5, 2023. New York City school officials started blocking this week the impressive but controversial writing tool that can...}

\entryitemAp{\hskip 0pt{}US approves Alzheimer's drug that modestly slows disease}{https://apnews.com/article/health-medication-us-food-and-drug-administration-business-d2a155172735e00d2aa7baaeb8c24a9b}{This Dec. 21, 2022 image provided by Eisai in January 2023, shows vials and packaging for their medication Leqembi. On Friday, Jan. 6, 2023, U.S. health officials approved Leqembi, a new Alzheimer's drug that modestly...}

\entryitemAp{\hskip 0pt{}California gets brief lull after damaging 'bomb cyclone'}{https://apnews.com/article/weather-storms-california-climate-and-environment-b83bb05fa2d21796a85be9bfc690cf17}{Waves crash into a seawall in Pacifica, Calif., Friday, Jan. 6, 2023. California weather calmed Friday but the lull was expected to be brief as more Pacific storms lined up to blast into the state, where successive...}

\entryitemAp{\hskip 0pt{}WWE's Vince McMahon is back after misconduct investigation}{https://apnews.com/article/sports-vince-mcmahon-business-sexual-misconduct-d35dd1b3f197945181c0a3701f9939f5}{FILE - Vince McMahon stands at Republican state convention in Hartford, Conn., Friday, May 18, 2012. McMahon is rejoining the board of WWE several months after he stepped down as CEO and chairman of the sports...}

\entryitemAp{\hskip 0pt{}South Carolina US House district ruled racial gerrymander}{https://apnews.com/article/politics-south-carolina-state-government-hilton-head-island-charleston-9f48c6c7668b7b9404a7a9335d3a195a}{FILE - State Sen. Dick Harpootlian, D-Columbia, compares his proposed map of U.S. House districts drawn with 2020 U.S. Census data to a plan supported by Republicans on Thursday, Jan. 20, 2022, in Columbia, S.C. A panel }

\entryitemAp{\hskip 0pt{}Global food prices in 2022 hit record high amid drought, war}{https://apnews.com/article/russia-ukraine-inflation-health-business-climate-and-environment-00539505ec5db37de5877137b9febeb8}{FILE - Children stand near shelters at a camp for displaced people on the outskirts of Dollow, Somalia, Sept. 19, 2022. (AP Photo/Jerome Delay, File) ROME (AP) --- Global prices for food commodities like grain and...}

\entryitemAp{\hskip 0pt{}Bills' Hamlin breathing on his own, joins team via video}{https://apnews.com/article/bills-damar-hamlin-health-update-b1edba1849b580c3cd9ec2ea39a85d1e}{FILE - Buffalo Bills Damar Hamlin with his helmet off before playing the Los Angeles Rams during an NFL football game, Sept. 8, 2021, in Inglewood, Calif. The scenes of Hamlin\textquotesingle s on-field collapse after...}

\entryitemAp{\hskip 0pt{}Kremlin-ordered truce is uncertain amid mutual mistrust}{https://apnews.com/article/russia-ukraine-war-kremlin-ordered-truce-650d6c7930c80e61763a672d05757da8}{A local resident runs past a burning house hit by the Russian shelling in Kherson, Ukraine, on the Orthodox Christmas Eve Friday, Jan. 6, 2023. (AP Photo/LIBKOS) KYIV, Ukraine (AP) --- An uneasy quiet settled over Kyiv...}

\entryitemAp{\hskip 0pt{}Wall Street rallies on rate hopes, notches gain for the week}{https://apnews.com/article/inflation-business-united-states-government-federal-reserve-system-financial-markets-1192ebd20662f914bcc908c8b6d81c90}{The New York Stock Exchange is seen in New York, Thursday, Feb. 24, 2022. Markets are opening mostly higher on Wall Street Friday after a wild ride a day earlier. The S\&P 500 added 0.4\% in the early going, following...}

\entryitemAp{\hskip 0pt{}Best of CES 2023: Canine communication and a calming pillow}{https://apnews.com/article/ces2023-best-of-jan6-9d127822b54184e6c4d8313368667dc0}{Ducky demonstrates FluentPet dog communication buttons during the Pepcom Digital Experience before the start of the CES tech show, Wednesday, Jan. 4, 2023, in Las Vegas. (AP Photo/John Locher) LAS VEGAS (AP) --- Tech...}

\entryitemAp{\hskip 0pt{}Cooler hiring and milder pay gains could aid inflation fight}{https://apnews.com/article/us-jobs-report-jan6-2023-78943d9829087d93e9681426ca0c8ae2}{FILE - Construction workers work on a building in Philadelphia, Wednesday, Dec. 21, 2022. America's employers added a solid 223,000 jobs in December, evidence that the economy remains healthy yet also a sign that the...}

\entryitemAp{\hskip 0pt{}Mexico gives account of violence after 'Chapo' son nabbed}{https://apnews.com/article/politics-united-states-government-mexico-drug-crimes-city-d74ba460138c067ca538c862e3f0a5b0}{A police convoy patrols Culiacan, Sinaloa state, Mexico, Friday, Jan. 6, 2023. The government operation on Thursday to detain Ovidio Guzman, the son of imprisoned drug lord Joaquin ``El Chapo'' Guzman, unleashed...}

\entryitemAp{\hskip 0pt{}FTC proposes rule that would ban employee noncompete clauses}{https://apnews.com/article/biden-technology-politics-business-9fb699837e8bf8ecd9c70dcf27699dcf}{FILE - The Federal Trade Commission building in Washington is pictured on Jan. 28, 2015. The Federal Trade Commission is proposing a new rule that would prevent employers from imposing noncompete clauses on their...}

\entryitemAp{\hskip 0pt{}The Year of the Slap: Pop culture moments in 2022}{https://apnews.com/article/2022-major-pop-culture-moments-movies-music-fashion-6112da82e4b05559f3c67ce1970c15cf}{Taylor Swift was up. Elon Musk was in, out, in and maybe out again. Tom Cruise was back. BTS stepped aside, and so did Serena Williams, and Tom Brady too --- oops, scratch that. But the slap? The slap was everywhere...}