\entryitemWithDescription{\hskip 0pt{}Walmart recalls apple juice sold in 25 states due to elevated arsenic levels}{https://apnews.com/article/e4c185fd48af2438023ea94b3f6b2b74}{WASHINGTON (AP) --- Walmart has recalled nearly 10,000 cases of apple juice sold in stores across the U.S. that were found to contain potentially harmful levels of inorganic arsenic. The U.S. Food and Drug Administration gave the recall a...}

\entryitemWithDescription{\hskip 0pt{}`Deadpool' and `Alien' top charts again as `Blink Twice' sees quiet opening}{https://apnews.com/article/2f53c8cf7ab86a75226858df9d4981c4}{LOS ANGELES (AP) --- In a sleepy summer weekend at the box office, holdovers reigned supreme as newcomers landed without a splash. ``Deadpool \& Wolverine'' reclaimed first place at the North American box office in its fifth weekend...}

\entryitemWithDescription{\hskip 0pt{}Famed Coney Island Cyclone roller coaster is shut down after mid-ride malfunction}{https://apnews.com/article/32077ca8078705aba01927c0dbc2569b}{NEW YORK (AP) --- The famous Coney Island Cyclone roller coaster in New York City was shut down indefinitely after coming to a stop mid-ride this week. The 97-year-old wooden roller coaster at Luna Park was on its ascent on Thursday when...}

\entryitemWithDescription{\hskip 0pt{}Search continues for woman missing after Colorado River flash flood at Grand Canyon National Park}{https://apnews.com/article/ae0ae8e8aed57f6070cd40182e720db1}{SUPAI, Ariz. (AP) --- Search crews again Sunday were combing the Colorado River at Grand Canyon National Park for an Arizona woman missing after a flash flood days earlier. National Park Service officials said Chenoa Nickerson, 33, was...}

\entryitemWithDescription{\hskip 0pt{}Former five-time Lebanese prime minister Salim Hoss dies at 94}{https://apnews.com/article/2612d4cc9d551c9fd9c319a78ebb8dd9}{BEIRUT (AP) --- Five-time former Lebanese Prime Minister Salim Hoss, who served during some of the most tumultuous years of his country's modern history, died Sunday at age 94, the current premier said. Caretaker Prime Minister Najib...}

\entryitemWithDescription{\hskip 0pt{}American rapper Macklemore says he canceled Dubai show over UAE arming Sudan paramilitary forces}{https://apnews.com/article/f9c5592abf09a62187908979da4a7410}{DUBAI, United Arab Emirates (AP) --- American rapper Macklemore said he canceled an upcoming October concert in Dubai over the United Arab Emirates' role ``in the ongoing genocide and humanitarian crisis'' in Sudan through its reported...}

\entryitemWithDescription{\hskip 0pt{}Babe Ruth's `called shot' jersey sells at auction for over \$24 million}{https://apnews.com/article/7e859191d0e9a9d4104ae94c8a1438bd}{DALLAS (AP) --- The jersey Babe Ruth wore when he called his shot during the 1932 World Series, hitting a home run to center field, sold at auction early Sunday for over \$24 million. Heritage Auctions said the New York Yankee slugger's...}

\entryitemWithDescription{\hskip 0pt{}Paralympic social media accounts front traditional media with edgy take}{https://apnews.com/article/6ee2ed68a10114dcd7fb6e2f124e3a54}{PARIS (AP) --- The message is clear: Paralympians are not participating. They are competing. A number of athletes preparing for the Paris 2024 Paralympic Games have proclaimed that on their social feeds over the past few days, reminding...}

\entryitemWithDescription{\hskip 0pt{}This bird species was extinct in Europe. Now it's back, and humans must help it migrate for winter}{https://apnews.com/article/c0acde6dfd791d2ec1998b53699e9756}{PATERZELL, Germany (AP) --- How do you teach a bird how, and where, to fly? The distinctive Northern Bald Ibis, hunted essentially to extinction by the 17th century, was revived by breeding and rewilding efforts over the last two decades...}

\entryitemWithDescription{\hskip 0pt{}How do you deal with stress? In Nigeria, swinging a sledgehammer in a `rage room' helps}{https://apnews.com/article/0d32f9a5abd8e18bd87ff5932ad54ab8}{LAGOS, Nigeria (AP) --- How do you deal with stress? In Lagos, Nigeria's largest city, people are finding their reset button in a ``rage room'' where they pay to smash electronics and furniture with a sledgehammer as a break from the...}

\entryitemWithDescription{\hskip 0pt{}`We were expendable': Downwinders from world's 1st atomic test are on a mission to tell their story}{https://apnews.com/article/fac8d1f584f320be220196191ab8c46b}{LOS ALAMOS, N.M. (AP) --- It was the summer of 1945 when the United States dropped atomic bombs on Japan, killing thousands of people as waves of destructive energy obliterated two cites. It was a decisive move that helped bring about the...}

\entryitemWithDescription{\hskip 0pt{}A rare but deadly mosquito virus infection has Massachusetts towns urging vigilance}{https://apnews.com/article/4a99dcebab64a9f06fe23186a182a0e2}{A rare but deadly disease spread by mosquitoes has one town in Massachusetts closing its parks and fields each evening. Four other towns are urging people to avoid going outdoors at night. They're concerned about eastern equine...}

\entryitemWithDescription{\hskip 0pt{}Justin and Hailey Bieber welcome a baby boy, Jack Blues}{https://apnews.com/article/eecf522431d870ea1cee45ef38935b6f}{LOS ANGELES (AP) --- Justin Bieber, who rose to international stardom in 2010 with his hit ``Baby,'' has welcomed one of his own with his wife, Hailey Bieber (nee Baldwin). The singer, 30, posted a photo of a baby's foot Friday on...}