\entryitemWithDescription{\hskip 0pt{}Natalie Portman and Benjamin Millepied divorce after 11 years of marriage}{https://apnews.com/article/3d929091e9d905f1602221ad80244791}{NEW YORK (AP) --- Natalie Portman and Benjamin Millepied have divorced after 11 years of marriage and two children. The Oscar-winning actor and Millepied, a choreographer and director, finalized the divorce last month in France, where...}

\entryitemWithDescription{\hskip 0pt{}WWE, a social media powerhouse, tops 100 million subscribers on YouTube}{https://apnews.com/article/0ba7fec79d23a3da9382d47eb2c4b120}{As WWE gears up for its biggest annual premium live event next month, the company continues to harness the power of its social media presence to reach its fans. A key component of that strategy is YouTube, where WWE has hit an important...}

\entryitemWithDescription{\hskip 0pt{}Former US Rep. George Santos, expelled from Congress, says he is running again}{https://apnews.com/article/ebf8c0c87d939ed6def387ab1b56f884}{WASHINGTON (AP) --- Former U.S. Rep. George Santos, who was expelled from Congress in December and faces federal charges of defrauding donors to his 2022 campaign, has announced he is running for the House again. Santos, a Republican who...}

\entryitemWithDescription{\hskip 0pt{}Military's Ospreys are cleared to return to flight, 3 months after latest fatal crash in Japan}{https://apnews.com/article/549cb6173cede2f4ea04b994d67e8603}{WASHINGTON (AP) --- The Osprey, a workhorse aircraft vital to U.S. military missions, has been approved to return to flight after an ``unprecedented'' part failure led to the deaths of eight service members in a crash in Japan in...}

\entryitemWithDescription{\hskip 0pt{}`Dragon Ball' creator Akira Toriyama dies at 68}{https://apnews.com/article/0b2016bf985e1854d3cbcb2985d6e922}{TOKYO (AP) --- Akira Toriyama, the creator of the best-selling Dragon Ball and other popular anime who influenced Japanese comics, has died, his studio said Friday. He was 68. Toriyama's Dragon Ball manga series, which started in 1984, is...}

\entryitemWithDescription{\hskip 0pt{}Civil rights activist Naomi Barber King, a sister-in-law to the Rev. Martin Luther King, Jr., dies}{https://apnews.com/article/5fe722c29168e2a38a2e3cb8c9a65b0b}{ATLANTA (AP) --- Naomi Barber King, a civil rights activist who was married to the younger brother of the Rev. Martin Luther King, Jr., has died at age 92. She died in Atlanta on Thursday, according to family members who issued a...}

\entryitemWithDescription{\hskip 0pt{}Karol G becomes first Latina named woman of the year at Billboard ceremony honoring global musicians}{https://apnews.com/article/e01fbab01ea2031312dd99f5dbe4c6d0}{INGLEWOOD, Calif. (AP) --- Karol G made history at Wednesday night's Billboard Women in Music awards ceremony. ``This is the first time, ever, a Latina is named woman of the year,'' Karol G began her acceptance speech after a fiery...}

\entryitemWithDescription{\hskip 0pt{}United Airlines plane makes a safe emergency landing in LA after losing a tire during takeoff}{https://apnews.com/article/70115cf0d5dc9b9abd33c1cf7a58f545}{LOS ANGELES (AP) --- A United Airlines jetliner bound for Japan made a safe landing in Los Angeles on Thursday after losing a tire while taking off from San Francisco. Fire engines stood by at Los Angeles International Airport but weren't...}

\entryitemWithDescription{\hskip 0pt{}Steve Lawrence, singer, entertainer and half of popular stage duo Steve \& Eydie, dies at 88}{https://apnews.com/article/0d5716adcf8a4fd0a96f3f12854212d5}{NEW YORK (AP) --- Steve Lawrence, a singer and top stage act who as a solo performer and in tandem with his wife Eydie Gorme kept Tin Pan Alley alive during the rock era, died Thursday. He was 88. Lawrence, whose hits included ``Go Away...}

\entryitemWithDescription{\hskip 0pt{}Miami Seaquarium gets eviction notice several months after death of Lolita the orca}{https://apnews.com/article/a405d64ee4425794a7e97c1fe863e6ec}{MIAMI (AP) --- The Miami Seaquarium, an old-Florida style tourist attraction that was home to Lolita, the beloved Orca that died last year, is being evicted from the waterfront property it leases from Miami-Dade County. Miami-Dade County...}

\entryitemWithDescription{\hskip 0pt{}Cole Brauer becomes 1st American woman to race sailboat alone and nonstop around world}{https://apnews.com/article/c62f806bc011c29faf88f8a9b048953b}{A CORUNA, Spain (AP) --- Alone, Cole Brauer braved three oceans and the elements as she navigated her sailboat for months. When she and her 40-foot (12.2-meter) sailboat arrived Thursday in A Coruña, Spain, the 29-year-old became the...}

\entryitemWithDescription{\hskip 0pt{}Investigators say they confirmed pilots' account of a rudder-control failure on a Boeing Max jet}{https://apnews.com/article/fdc5a80e699d6bf215d9b1bc1681da82}{Federal investigators said Thursday they confirmed pilots' account of a brief failure of rudder controls on a Boeing 737 Max after it landed at Newark Liberty International Airport in New Jersey last month. United Airlines pilots said...}

\entryitemWithDescription{\hskip 0pt{}A girl went missing, seizing South Africa's attention. Now her mother is charged with selling her}{https://apnews.com/article/06072bd67ee5a7033c2780407db2466f}{CAPE TOWN, South Africa (AP) --- The mother of a 6-year-old girl who has been missing in South Africa for nearly three weeks was arrested and charged Thursday with kidnapping and selling or trafficking her daughter, a shocking twist in a...}