\entryitemWithDescription{\hskip 0pt{}Mother of young boy who shot teacher arrested in Virginia}{https://apnews.com/article/9f1a885a6a74bc92f48771b54e77d192}{FILE - Police look on as students return to Richneck Elementary on Jan. 30, 2023, in Newport News, Va. A grand jury in Virginia has indicted the mother of a 6-year-old boy who shot his teacher on charges of child neglect and failing to...}

\entryitemWithDescription{\hskip 0pt{}'Water was red': Hawaii surfer recalls costly shark attack}{https://apnews.com/article/596de17e7c47096275749a663896b99e}{Mike Morita poses for a photo from his hospital bed, Wednesday, April 10, 2023, in Honolulu. Morita credits a faith in God for surviving an Easter Sunday shark attack and for remaining at peace despite losing his right foot. (Kamu Morita...}

\entryitemWithDescription{\hskip 0pt{}Missouri to restrict transgender care for minors, adults}{https://apnews.com/article/4def2189dac9979a00d298efb3baf12a}{FILE - Missouri Attorney General Andrew Bailey speaks with reporters outside the Supreme Court on Capitol Hill in Washington, on Feb. 28, 2023. Minors in Missouri soon will be required to undergo 18 months of therapy before receiving...}

\entryitemWithDescription{\hskip 0pt{}Newly active Texas sinkhole unearths forgotten fears in some}{https://apnews.com/article/1e66ac058873d88bae702f5f5759c862}{CORRECTS NAME OF SOURCE TO ZEITVIEW, NOT DRONEBASE - This aerial image shows a massive sinkhole near Daisetta, Texas, Tuesday, April 11, 2023. Earlier this month, Daisetta officials announced the sinkhole, which had first emerged in 2008...}

\entryitemWithDescription{\hskip 0pt{}Philadelphia truck break-in ends in parking lot dime heist}{https://apnews.com/article/afd20e0c6201389d61665efc1086cc26}{PHILADELPHIA (AP) --- Thieves may not have been counting on finding a mountain of change when they broke into a truck filled with \$750,000 in dimes, but they still made off with a chunk of the cargo and left coins scattered around a...}

\entryitemWithDescription{\hskip 0pt{}Pitcher criticizes MLB teams for extending alcohol sales}{https://apnews.com/article/b9004637de6b735cbf38c1290962be3e}{A baseball fan looks at the offerings in a beer cooler at PNC Park before a baseball game between the Pittsburgh Pirates and the Houston Astros in Pittsburgh, Wednesday, April 12, 2023. (AP Photo/Gene J. Puskar) CINCINNATI (AP) --- A...}

\entryitemWithDescription{\hskip 0pt{}Montana close to becoming 1st state to completely ban TikTok}{https://apnews.com/article/a867974eb2171d498dac94171e7be830}{FILE - The icon for the video sharing TikTok app is seen on a smartphone, Feb. 28, 2023, in Marple Township, Pa. Montana lawmakers were expected to take a big step forward Thursday, April 13, 2023 on a bill to ban TikTok from operating in...}

\entryitemWithDescription{\hskip 0pt{}Navy veteran who stormed Capitol gets 3 years on gun charges}{https://apnews.com/article/67a7620610285e3b6d0394a017650834}{FILE - This booking photo provided by the Alexandria, Va., Sheriff\textquotesingle s Office shows Hatchet Speed. Speed, a former Navy reservist who stormed the U.S. Capitol on Jan. 6, 2021, and expressed admiration for Adolf Hitler, was...}

\entryitemWithDescription{\hskip 0pt{}Tech consultant charged in killing of Cash App founder Lee}{https://apnews.com/article/13dab701a332328c531b3c6c444983fd}{San Francisco Police chief William Scott provides an update on the homicide investigation of Robert Lee during a press conference where officials announced the arrest of a suspect, Thursday, April 13, 2023, in San Francisco. San Francisco...}

\entryitemWithDescription{\hskip 0pt{}Romance novel model gets prison for Jan. 6 attack on police}{https://apnews.com/article/bfdcac9eac64804bb6449a3ac6b99fbc}{In this image from the body-worn camera of a Washington Metropolitan Police Department officer, released and annotated by the Justice Department in the Government\textquotesingle s Sentencing Memorandum, Logan Barnhart, circled in yellow...}

\entryitemWithDescription{\hskip 0pt{}MLB ump Vanover still in hospital after hit in head by throw}{https://apnews.com/article/611ddcd5392eab9000988667d4ab8f2e}{FILE - Major League Baseball umpire Larry Vanover signals an out after a review during a baseball game between the Baltimore Orioles and the Cincinnati Reds in Cincinnati, Sunday, July 31, 2022. Vanover remained hospitalized Thursday...}

\entryitemWithDescription{\hskip 0pt{}Blackhawks say Toews will not return to team next season}{https://apnews.com/article/273a4b24488be6e15ae1fbfabd3d991c}{Chicago Blackhawks\textquotesingle{} Jonathan Toews waits for a faceoff during the third period of the team\textquotesingle s NHL hockey game against the Vancouver Canucks on Thursday, April 6, 2023, in Vancouver, British Columbia...}

\entryitemWithDescription{\hskip 0pt{}Irish rally driver Craig Breen killed in accident}{https://apnews.com/article/2cd10bba4710fb7a9edd7b9364bc1154}{FILE - Craig Breen is seen during a stopover on day 3 of Rally Sweden 2018 as part of the World Rally Championship (WRC) in Torsby, Sweden, on Feb. 17, 2018. Rally driver Craig Breen was killed in an accident Thursday, April 13, 2023...}