\entryitemWithDescription{\hskip 0pt{}Bruce Willis has frontotemporal dementia, condition worsens}{https://apnews.com/article/a61f251adf19a73ba0010f06a38d38a5}{FILE - Bruce Willis attends a movie premiere in New York on Friday, Oct. 11, 2019. Nearly a year after Bruce Willis' family announced that he would step away from acting after being diagnosed with aphasia, his family says his ``condition...}

\entryitemWithDescription{\hskip 0pt{}Sen. John Fetterman checks into hospital for depression}{https://apnews.com/article/a9051b43a6b31725a4969b9302740cac}{FILE - Sen. John Fetterman, D-Pa., leaves an intelligence briefing on the unknown aerial objects the U.S. military shot down this weekend at the Capitol in Washington, Feb. 14, 2023. Fetterman is in Walter Reed National Military Medical...}

\entryitemWithDescription{\hskip 0pt{}Tim McCarver, big league catcher and broadcaster, dies at 81}{https://apnews.com/article/58fed2018917409786f551df15a0102e}{FILE - Baseball announcer Tim McCarver poses in the press box before the start of Game 2 of the American League Division Series on Oct. 2, 2003 in New York. McCarver, the All-Star catcher and Hall of Fame broadcaster who during 60 years...}

\entryitemWithDescription{\hskip 0pt{}Biden wants 'sharper rules' on unknown aerial objects}{https://apnews.com/article/6457aaf3e7322dd24e2b7274c3ba4813}{President Joe Biden speaks about the Chinese surveillance balloon and other unidentified objects shot down by the U.S. military, Thursday, Feb. 16, 2023, in Washington. (AP Photo/Evan Vucci) WASHINGTON (AP) --- President Joe Biden said...}

\entryitemWithDescription{\hskip 0pt{}Tesla recalls 'Full Self-Driving' to fix unsafe actions}{https://apnews.com/article/875b54d4b71e97d43a17e968d7b856ae}{FILE - A sign bearing the company logo outside a Tesla store in Cherry Creek Mall in Denver is seen here on Feb. 9, 2019. Tesla is recalling nearly 363,000 vehicles with its ``Full Self-Driving'' system to fix problems with the way it...}

\entryitemWithDescription{\hskip 0pt{}YouTube CEO steps down, severing longtime ties to Google}{https://apnews.com/article/19e18ebcd986490e0ff9e66e429d66c2}{FILE - YouTube CEO Susan Wojcicki speaks during the introduction of YouTube TV at YouTube Space LA on Feb. 28, 2017, in Los Angeles. Wojcicki announced Thursday, Feb. 16, 2023, that she is stepping down as CEO at YouTube after spending...}

\entryitemWithDescription{\hskip 0pt{}Lonely tunes: Humpback whales wail less as population grows}{https://apnews.com/article/065e1b7c6a45b188ea1c918f4f2a75ee}{CORRECTS DAY TO THURSDAY - FILE - A humpback whale breaches off the coast of Port Stephens, Australia, on June 14, 2021. Lonely humpback whales are more likely to sing -- but as populations grow, whales wail less, a new study released on...}

\entryitemWithDescription{\hskip 0pt{}Michigan State University gunman's note had possible motive}{https://apnews.com/article/58d87c54210d30f9514f6b350e4f929d}{Mourners attend a vigil at The Rock on the grounds of Michigan State University in East Lansing, Mich., Wednesday, Feb. 15, 2023. Alexandria Verner, Brian Fraser and Arielle Anderson were killed and several other students remain in...}

\entryitemWithDescription{\hskip 0pt{}Ryan Seacrest to leave 'Live with Kelly and Ryan' in spring}{https://apnews.com/article/fe381d4752a8ad18272a4707151deef0}{This image released by ABC shows co-host Kelly Ripa, left, and Ryan Seacrest on the set of "Live! With Kelly and Ryan" on Feb. 8, 2023 in New York. Seacrest has revealed he's leaving the show this spring. Seacrest ends a six-year run...}

\entryitemWithDescription{\hskip 0pt{}Sturgeon's exit leaves Scottish independence path unclear}{https://apnews.com/article/bce30aa06447e1638c5d165b1e9ebe31}{Nicola Sturgeon speaks during a press conference at Bute House in Edinburgh, Wednesday, Feb. 15 2023. Sturgeon has resigned as first minister of Scotland following months of controversy over a law that makes it simpler for people to...}

\entryitemWithDescription{\hskip 0pt{}Wholesale price pressures emerge despite long-term slowdown}{https://apnews.com/article/375c18aa8f9d14912d53c080a5ca3d41}{File - A consist of John Deere tractors sit in Norfolk Southern\textquotesingle s Conway Yard in Conway, Pa., Monday, Dec. 5, 2022. On Thursday, the Labor Department releases the producer price index for January, an indicator of inflation...}

\entryitemWithDescription{\hskip 0pt{}Potential buyers of Manchester United crunching the numbers}{https://apnews.com/article/5a0cd2ca92c4568d195091c611f257af}{A corner flag showing the logo of Manchester United is seen ahead of the English FA Cup 4th round soccer match between Manchester United and Reading at Old Trafford in Manchester, England, Saturday, Jan. 28, 2023. (AP Photo/Rui Vieira...}

\entryitemWithDescription{\hskip 0pt{}Revelers celebrate street Carnival across German Rhineland}{https://apnews.com/article/bbda5c3c25af656989187b925af008e1}{Revellers celebrate at the traditional Alter Markt the start of the street carnival in Cologne, Germany, Thursday, Feb. 16, 2023. Hundreds of thousands will celebrate the carnival without any coronavirus restrictions in the streets of the...}