\entryitemWithDescription{\hskip 0pt{}The secret life of gift cards: Here's what happens to the billions that go unspent each year}{https://apnews.com/article/e9592f6b4067601a27d0f0199da898c8}{Gift cards make great stocking stuffers --- just as long as you don't stuff them in a drawer and forget about them after the holidays. Americans are expected to spend nearly \$30 billion on gift cards this holiday season, according to the...}

\entryitemWithDescription{\hskip 0pt{}Mike Nussbaum, prolific Chicago stage actor with film roles including `Field of Dreams,' dies at 99}{https://apnews.com/article/d96ca499c39ff20c18dcf965fd85f18b}{CHICAGO (AP) --- Mike Nussbaum, reputed as the oldest professional actor in America with a prolific stage career and roles in films including ``Field of Dreams'' and ``Men in Black,'' has died. He was 99. He died of old age at his Chicago...}

\entryitemWithDescription{\hskip 0pt{}The year of social media soul-searching: Twitter dies, X and Threads are born and AI gets personal}{https://apnews.com/article/98e4905027104347c7fd20fdff1641c8}{We lost Twitter and got X. We tried out Bluesky and Mastodon (well, some of us did). We fretted about AI bots and teen mental health. We cocooned in private chats and scrolled endlessly as we did in years past. For social media users...}

\entryitemWithDescription{\hskip 0pt{}Finding new dimensions, sisterhood, and healing in `The Color Purple'}{https://apnews.com/article/21c75312a55f8e001a5c1c5947c09bdd}{It's not a secret that Fantasia Barrino did not want to play Celie again. The ``American Idol'' winner hadn't had the best time doing ``The Color Purple'' on Broadway. The protagonist of Alice Walker's Pulitzer Prize-winning novel tells...}

\entryitemWithDescription{\hskip 0pt{}A man is killed and a woman injured in a `targeted' afternoon shooting at a Florida shopping mall}{https://apnews.com/article/990961110c48b7eddbbb76ea199c60df}{OCALA, Fla. (AP) --- A man died in a shooting at a shopping mall in central Florida two days before Christmas in which the victim was ``targeted'' for the attack, police said. Ocala Police Chief Mike Balken told reporters Saturday evening...}

\entryitemWithDescription{\hskip 0pt{}Suspect arrested in alleged theft of a Banksy stop sign decorated with military drones}{https://apnews.com/article/eba62d25eed6b60301289baa50f13e55}{LONDON (AP) --- A man suspected of stealing an artwork by Banksy of a stop sign adorned with three military drones, was arrested Saturday, London police said. A man in his 20s was in custody on suspicion of theft and criminal damage, the...}

\entryitemWithDescription{\hskip 0pt{}Inmates were locked in cells during April fire that injured 20 at NYC's Rikers Island, report finds}{https://apnews.com/article/e260f4399e44a7171179581273f87a31}{NEW YORK (AP) --- Inmates at New York City's Rikers Island were kept locked in their cells for nearly half an hour while a fire spread through one of the nation's largest and most notorious jail complexes this past April, injuring some 20...}

\entryitemWithDescription{\hskip 0pt{}Truck carrying gas hits railroad bridge and explodes as a train passes overhead}{https://apnews.com/article/57aa0e7c9572c56b2cccc5ed3c07e6be}{GLENVILLE, N.Y. (AP) --- A tractor-trailer loaded with what authorities believe were gas containers slammed into the bottom of an overhead railroad bridge in upstate New York and exploded Thursday night as a freight train was traveling on...}

\entryitemWithDescription{\hskip 0pt{}FDA says fake Ozempic shots are being sold through some legitimate sources}{https://apnews.com/article/86d152c78f180792e7764a435cb3334d}{The U.S. Food and Drug Administration said it has seized ``thousands of units'' of counterfeit Ozempic, the diabetes drug widely used for weight loss, that had been distributed through legitimate drug supply sources. The FDA and the drug'...}

\entryitemWithDescription{\hskip 0pt{}Ash from Indonesia's Marapi volcano forces airport to close and stops flights}{https://apnews.com/article/1367ed215ea7190c1a85e14161b7ed0a}{PADANG, Indonesia (AP) --- Volcanic ash spewing from Indonesia's Mount Marapi shut down airports and blanketed nearby communities on Sumatra island Friday. The nearly 2,900-meter (9,480-foot) volcano in the Agam district of West Sumatra...}

\entryitemWithDescription{\hskip 0pt{}Dreaming of a white Christmas? Alaska may be your best bet, as U.S. ski resorts see rain, not snow}{https://apnews.com/article/83af1982d88386348d3ab98b3212119c}{GILFORD, N.H. (AP) --- For most Americans dreaming of a white Christmas, this year's prospects aren't good. Although parts of the Rockies and Midwest already have snow or could get a fresh dusting by Monday, other parts of the country...}

\entryitemWithDescription{\hskip 0pt{}Track Santa here. A military command is keeping close watch on his sleigh}{https://apnews.com/article/2f9a2083102decafa3186a7d6f8f8e0f}{WASHINGTON (AP) --- As children around the world eagerly await Santa's arrival on Christmas, the military is closely tracking his every move. Armed with radar, sensors, aircraft and Christmas spirit, the North American Aerospace Defense...}

\entryitemWithDescription{\hskip 0pt{}Federal court revives lawsuit against Nirvana over 1991 `Nevermind' naked baby album cover}{https://apnews.com/article/e914b5f0b541295e44621680ac2d030f}{LOS ANGELES (AP) --- A federal appeals court on Thursday revived a child sexual exploitation lawsuit filed by the man who appeared naked as a 4-month-old on the cover of Nirvana's 1991 album ``Nevermind.'' Spencer Elden's lawsuit against...}