\entryitemWithDescription{\hskip 0pt{}Australia celebrates Australian-born queen of Denmark with cocktails, picnics and `Danish Fiesta'}{https://apnews.com/article/0f5786dd61d22462da549b555312fba4}{SYDNEY (AP) --- A day after an Australian became queen of Denmark. her native land on Monday celebrated the unlikely fairy tale with cocktails, picnics and a ``Danish Fiesta.'' Mary Donaldson's journey from Tasmania to the world's first...}

\entryitemWithDescription{\hskip 0pt{}Osaka's Grand Slam comeback ends in 1st-round loss to Garcia, Gauff advances at Australian Open}{https://apnews.com/article/496f2d4095e51e19477cdda36170a82f}{MELBOURNE, Australia (AP) --- Moments after her Grand Slam comeback ended in a first-round loss, Naomi Osaka walked back through the players' tunnel where her name has a prominent place among recent Australian Open champions. Three...}

\entryitemWithDescription{\hskip 0pt{}With snow still falling, Bills call on fans to help dig out stadium for playoff game vs. Steelers}{https://apnews.com/article/fe8f1e74e96f9c5fa762ecd31007b5f3}{BUFFALO, N.Y. (AP) --- Logan Eschrich came to Buffalo to witness the snowstorm, and he stayed for the shoveling on Sunday. Once the professional storm chaser saw the Buffalo Bills invite fans to help dig out a snow-filled Highmark Stadium...}

\entryitemWithDescription{\hskip 0pt{}Following review, Business Insider stands by reports on wife of ex-Harvard president's critic}{https://apnews.com/article/c8d7817314772b1b5443f656d0e2ae74}{NEW YORK (AP) --- Business Insider's top executive and parent company said Sunday they were satisfied with the fairness and accuracy of stories that made plagiarism accusations against a former MIT professor who is married to a prominent...}

\entryitemWithDescription{\hskip 0pt{}No joke: Feds are banning humorous electronic messages on highways}{https://apnews.com/article/3c7b0d11475d2b255f7edd197af771cc}{PHOENIX (AP) --- It's no joke. Humorous and quirky messages on electronic signs will soon disappear from highways and freeways across the country. The U.S. Federal Highway Administration has given states two years to implement all the...}

\entryitemWithDescription{\hskip 0pt{}This photo shows the moment Maine's record high tide washed away more than 100-year-old fishing shacks}{https://apnews.com/article/1a5d26f2d87e4af3fd8be9be57162af2}{MEREDITH, N.H. (AP) --- A record high tide in Maine washed away three historic fishing shacks that had stood since the 1800s and formed the backdrop of countless photographs. Michelle Erskine said she was visiting fisherman's point at...}

\entryitemWithDescription{\hskip 0pt{}`The Honeymooners' actress Joyce Randolph has died at 99; played Ed Norton's wife, Trixie}{https://apnews.com/article/2d6dff72f36e9672f0f8c49ba2e7e339}{NEW YORK (AP) --- Joyce Randolph, a veteran stage and television actress whose role as the savvy Trixie Norton on ``The Honeymooners'' provided the perfect foil to her dimwitted TV husband, has died. She was 99. Randolph died of natural...}

\entryitemWithDescription{\hskip 0pt{}`Mean Girls' takes 1st place at the box office. So fetch}{https://apnews.com/article/1bb56f71748fc52b3bcaa3fc77ea75f4}{Winter storms and cinema closures in North America didn't dampen the opening weekend for `` Mean Girls. '' The Paramount release, adapted from the Broadway musical and the 2004 Tina Fey movie, earned \$28 million in its first three days...}

\entryitemWithDescription{\hskip 0pt{}Volcano erupts in southwestern Iceland, sending lava flowing toward nearby settlement}{https://apnews.com/article/a7337b61f1df7184d52406416f0a67bf}{LONDON (AP) --- A volcano erupted in southwestern Iceland Sunday for the second time in less than a month, sending semi-molten rock toward a nearby settlement. The eruption just before 8 a.m. came after a swarm of earthquakes near the...}

\entryitemWithDescription{\hskip 0pt{}A Japanese domestic flight returns to airport with crack on a cockpit window. No injuries reported.}{https://apnews.com/article/370fab0f95fbca0e398763918c1b3819}{TOKYO (AP) --- An All Nippon Airways domestic flight turned back to Japan's northern airport of Sapporo after a crack was found on the cockpit window, according to the airline and media reports. ANA Flight 1182 was en route to Toyama...}

\entryitemWithDescription{\hskip 0pt{}Patrick Mahomes leads Chiefs to 26-7 playoff win over Miami in near-record low temps}{https://apnews.com/article/e3a23736da0c791ff4ec2067fc5a9ff2}{KANSAS CITY, Mo. (AP) --- Patrick Mahomes threw for 262 yards and a touchdown, had his helmet shattered when he took a hit in the second half, and proceeded to lead the Kansas City Chiefs to a 26-7 rout of the Miami Dolphins in the fourth...}

\entryitemWithDescription{\hskip 0pt{}Stroud becomes youngest QB to win a playoff game as Texans rout Browns 45-14}{https://apnews.com/article/e9e4e7262a26610bb2981c12acf8fad0}{HOUSTON (AP) --- As the games get bigger, C.J. Stroud just keeps getting better. The rookie became the youngest quarterback to win a playoff game after throwing for 274 yards and three touchdowns, and the Houston Texans returned two...}

\entryitemWithDescription{\hskip 0pt{}NTSB investigating 2 Brightline high speed train crashes that killed 3 people in Florida this week}{https://apnews.com/article/67020b2cd33b6cbcf9d85ed029d18310}{FORT LAUDERDALE Fla. (AP) --- The National Transportation Safety Board said Saturday it will investigate two crashes involving Florida's Brightline train that killed three people at the same railroad crossing on the high speed train's...}