\entryitemWithDescription{\hskip 0pt{}Hajj pilgrims perform final rituals in Mecca before heading to Mina}{https://apnews.com/article/cf09ee3c0504c4d4f5488728f2abba90}{Pilgrims walk beside pigeons outside the Grand Mosque, during the annual hajj pilgrimage, in Mecca, Saudi Arabia, Saturday, June 24, 2023. Muslim pilgrims are converging on Saudi Arabia\textquotesingle s holy city of Mecca for the largest...}

\entryitemWithDescription{\hskip 0pt{}Happ homers twice, Steele pitches Cubs over Cardinals 9-1 in MLB's return to London}{https://apnews.com/article/beb6fed85761846c7f91088e316f7a26}{Fans watch a baseball game between the St. Louis Cardinals and the Chicago Cubs Saturday, June 24, 2023, in London. (AP Photo/Kin Cheung) LONDON (AP) --- Pushing back the outfield fences in London couldn't keep Ian Happ in the ballpark...}

\entryitemWithDescription{\hskip 0pt{}Cardinals scratch Flaherty from start Sunday in London and Hicks is out with illness}{https://apnews.com/article/5fe8d1e843c0282b2962fd7f2e8e0a95}{St. Louis Cardinals starting pitcher Jack Flaherty sits in the dugout during the third inning of a baseball game against the Washington Nationals at Nationals Park, Monday, June 19, 2023, in Washington. (AP Photo/Alex Brandon) LONDON...}

\entryitemWithDescription{\hskip 0pt{}Assault charge dropped against Raiders' Davante Adams for shoving photographer}{https://apnews.com/article/04faa6220ca27453e54d14d0dedf43ec}{FILE - Las Vegas Raiders wide receiver Davante Adams speaks during a news conference at the NFL football team\textquotesingle s training facility Thursday, May 25, 2023, in Henderson, Nev. Prosecutors have dropped a misdemeanor assault...}

\entryitemWithDescription{\hskip 0pt{}Freight train carrying hot asphalt, molten sulfur plunges into Yellowstone River as bridge fails}{https://apnews.com/article/dbd905bac1b35a63107213db7983bafc}{Several train cars are immersed in the Yellowstone River after a bridge collapse near Columbus, Mont., on Saturday, June 24, 2023. The bridge collapsed overnight, causing a train that was traveling over it to plunge into the water below...}

\entryitemWithDescription{\hskip 0pt{}Montana Republicans report letters with mysterious powder after similar mailings in 2 other states}{https://apnews.com/article/e0e48401f2973232be975755ebbcc9e1}{Republican lawmakers in Montana are sharing that they received letters with white powder as federal agents investigate mysterious substances similarly mailed to GOP officials in two other states. In a Friday night tweet, Republican Gov...}

\entryitemWithDescription{\hskip 0pt{}Indian Prime Minister Modi arrives in Egypt on a two-day visit to strengthen ties}{https://apnews.com/article/1d5a1cae3fce891b80f35a9607fc5083}{India\textquotesingle s Prime Minister Narendra Modi speaks during a State Visit Luncheon at the State Department, Friday, June 23, 2023, in Washington. (AP Photo/Jacquelyn Martin) CAIRO (AP) --- Indian Prime Minister Narendra Modi kicked...}

\entryitemWithDescription{\hskip 0pt{}Three San Antonio police officers are charged with murder in the fatal shooting of a woman}{https://apnews.com/article/03e68bc18ba375b9910af0022f1258a9}{This photo combo shows from left, Sgt. Alfred Flores and Officers Eleazar Alejandro and Nathaniel Villalobos. The three San Antonio police officers have been charged, Friday, June 23, 2023, with murder in the fatal shooting of a woman who...}

\entryitemWithDescription{\hskip 0pt{}Fentanyl ruled as the cause of death for Adam Rich, former 'Eight is Enough' child star}{https://apnews.com/article/b47e798774cdfc3f5ca3aa6902d8b01e}{FILE - One-time child actor Adam Rich, who starred in the 1970s TV show "Eight is Enough," walks out of a sheriff\textquotesingle s station after posting bail in City of Industry, Calif., Dec. 18, 2002. The Los Angeles County Medical...}

\entryitemWithDescription{\hskip 0pt{}Beijing heat wave clouds long weekend and sets multi-day temperature record}{https://apnews.com/article/51441f6afb6b23a35d26936c544621d2}{People use a sun hat and an umbrella to protect themselves from the sun as they walk outside a shopping mall on an unseasonably hot day in Beijing, Saturday, June 24, 2023. Authorities continued a rare red alert for high temperatures in...}

\entryitemWithDescription{\hskip 0pt{}Tornado rips through massive Wyoming coal mining site, injures 8 people}{https://apnews.com/article/df483a7c93ff6bec2ece244845372cdf}{CAMPBELL COUNTY, Wyo. (AP) --- A tornado that ripped through the country\textquotesingle s largest coal mining site in northeast Wyoming left eight people injured and halted operations as first responders searched the massive open-pit...}

\entryitemWithDescription{\hskip 0pt{}In Iran, a restorer brings back to life famed Cadillac Sevilles once assembled in the country}{https://apnews.com/article/9e74bb9eb83aaa01a4931f273d622518}{A worker sands an under a restored Cadillac Seville at restorer Khosro Dahaghin\textquotesingle s workshop in Roudehen, some 30 miles (45 kilometers) east of downtown Tehran, Iran, Wednesday, June 7, 2023. Dahaghin's passion for restoring...}

\entryitemWithDescription{\hskip 0pt{}Judge agrees to narrow but not lift gag order in University of Idaho student slayings case}{https://apnews.com/article/13eb9c5a669323bb4a71eb27ee086554}{FILE - Bryan Kohberger, who is accused of killing four University of Idaho students in Nov. 2022, appears at a hearing in Latah County District Court, on Jan. 5, 2023, in Moscow, Idaho. An Idaho judge has denied a request from more than...}