\entryitemWithDescription{\hskip 0pt{}Late French film star Alain Delon wanted his dog buried with him. The dog gets to live}{https://apnews.com/article/7fddf62204b06a28466524b6c4dbcf2e}{PARIS (AP) --- Before he died this week, French film icon Alain Delon once suggested he wanted his beloved sheepdog Louba buried with him. To the relief of animal lovers around France, Loubo will be allowed to survive. Delon, an...}

\entryitemWithDescription{\hskip 0pt{}Last body from sunken superyacht has been recovered off Sicily}{https://apnews.com/article/55001fe25632c9adde0e51fc8100c8a0}{ROME (AP) --- Italian rescuers brought ashore the body of the final missing person who was on a superyacht that sunk off the coast of Sicily. The woman's body was detected on Friday, the Coast Guard said. She has not been officially...}

\entryitemWithDescription{\hskip 0pt{}The twins are here! A second set of giant panda cubs has arrived in Berlin}{https://apnews.com/article/a645ca9b993c59b9db2c835442e0c58e}{BERLIN (AP) --- Berlin Zoo announced Friday that longtime resident giant panda Meng Meng has given birth to twins --- for a second time. The cubs were born on Thursday and are doing well, the zoo said in a statement. They were born only...}

\entryitemWithDescription{\hskip 0pt{}Kamala Harris with Beyonce? Yes, but the star singer was only heard through loudspeakers}{https://apnews.com/article/6a6a0d8d1142b9410d1bb6e7d813dd66}{Kamala Harris introduced herself to the country she hopes to lead in the climactic moment of the Democratic national convention on Thursday --- and despite chatter about potential mystery guests, Beyonce's only appearance was over the...}

\entryitemWithDescription{\hskip 0pt{}Young humpback whale freed from fishing tackle that had entangled its tail in Sydney Harbor}{https://apnews.com/article/a0eb00783db26ff020d5077659d2bf51}{MELBOURNE, Australia (AP) --- A young humpback whale was freed from fishing tackle that had entangled its tail during an almost 24-hour rescue operation in Sydney Harbor. The juvenile whale immediately began swimming toward the Sydney...}

\entryitemWithDescription{\hskip 0pt{}See George Clooney's memorable moments at Venice Film Festival as actor prepares to return}{https://apnews.com/article/3365ea04d838e30d19b75d3df047aec4}{No Hollywood star seems as intrinsically tied to Venice as George Clooney. Twenty-six years ago he attended his first Venice Film Festival with the instant classic ``Out of Sight''; 19 years ago, it's where he debuted his sophomore...}

\entryitemWithDescription{\hskip 0pt{}How do you pronounce Kamala? Her grandnieces explain at the DNC}{https://apnews.com/article/64c009b56a951b7dc8dd7a1aa1544e3b}{WASHINGTON (AP) --- The final night of the Democratic National Convention included a tutorial on pronouncing Kamala Harris' name --- featuring none other than the candidate's great nieces. The actress Kerry Washington introduced the girls...}

\entryitemWithDescription{\hskip 0pt{}What's for breakfast? At Chicago hotel hosting DNC event, there may have been mealworms}{https://apnews.com/article/f4c959f9235eb8c967b385174003f29b}{CHICAGO (AP) --- Mealworms may have sickened at least one person at a Chicago hotel event earlier this week during the Democratic National Convention, the city's police superintendent said Thursday. While the investigation by Chicago...}

\entryitemWithDescription{\hskip 0pt{}\$1M verdict for teen, already a victim when she was assaulted by an officer}{https://apnews.com/article/e772320d2c3f531cc7acbb0c94470bdd}{NEW ORLEANS (AP) --- The city of New Orleans owes \$1 million to a teenager who was already a victim of sexual assault when a city police offer with a history of misconduct complaints continued the abuse --- pretending to be a friend and...}

\entryitemWithDescription{\hskip 0pt{}Sword, bullhorn stolen from Hall of Fame basketball coach Rick Pitino's St. John's University office}{https://apnews.com/article/0f9217c25415cf16857f1323399e8332}{NEW YORK (AP) --- Two thieves swiped a ceremonial sword and a bullhorn from the office of St. John's University Coach Rick Pitino, a spokesperson for the Catholic institution in the New York City borough of Queens said Thursday. Brian...}

\entryitemWithDescription{\hskip 0pt{}Andrew Tate placed under house arrest as new human trafficking allegations emerge involving minors}{https://apnews.com/article/197b1345b2ebdcb56c1ad58c48dd023c}{BUCHAREST, Romania (AP) --- A court in Romania's capital Thursday placed the divisive internet influencer Andrew Tate under house arrest for 30 days, as prosecutors investigate a sprawling new case that involves allegations of human...}

\entryitemWithDescription{\hskip 0pt{}Naming 2 baby giraffes is a tall order for a Berlin zoo}{https://apnews.com/article/0abd849576502d9cd54d7f239f64ea53}{BERLIN (AP) --- Naming two baby giraffes turned out to be a tall order this summer for a Berlin zoo. After the half-siblings were born on June 24 and Aug. 11 in the Tierpark, one of the city's two zoos, officials turned to a school class...}

\entryitemWithDescription{\hskip 0pt{}A German warship blasted the Darth Vader theme on the Thames. `No deeper message,' Navy says.}{https://apnews.com/article/85e889136c6a586bbe42c9a0eb358a35}{BERLIN (AP) --- Germany's Navy says there was ``no deeper message'' in the choice to blast the famed Imperial March --- Darth Vader's theme song in the ``Star Wars'' films --- from one of its warships as it cruised down the River Thames...}