\entryitemWithDescription{\hskip 0pt{}US to send Ukraine longer-range bombs in latest turnaround}{https://apnews.com/article/0f550a262fb6178a7d91b8be6e2c601b}{In this image provided by U.S. Transportation Command, a stevedore sits in a Bradley Fighting Vehicle before loading it onto the ARC Wallenius Wilhemsen Jan. 25, 2023, at the Transportation Core Dock in North Charleston, S.C. After months...}

\entryitemWithDescription{\hskip 0pt{}Biden's handwritten notes part of classified docs probe}{https://apnews.com/article/232f991e6f8697124a5771a979a46bbb}{FILE - President Joe Biden holds notes as he meets with Indian Prime Minister Narendra Modi in the Oval Office of the White House, Sept. 24, 2021, in Washington. Biden is a man who writes down his thoughts. And some of those handwritten...}

\entryitemWithDescription{\hskip 0pt{}At Nichols' funeral, Black America's grief on public display}{https://apnews.com/article/aa5645625c7827af256017045478eff9}{RowVaughn Wells cries as she and her husband Rodney Wells attend the funeral service for her son Tyre Nichols at Mississippi Boulevard Christian Church in Memphis, Tenn., on Wednesday, Feb. 1, 2023. Nichols died following a brutal beating...}

\entryitemWithDescription{\hskip 0pt{}Don't like Phil's forecast? Check out these rodents instead}{https://apnews.com/article/0fc9e31dccbddeab5a6cb5608f23d47a}{Groundhog Club handler A.J. Dereume holds Punxsutawney Phil, the weather prognosticating groundhog, during the 137th celebration of Groundhog Day on Gobbler\textquotesingle s Knob in Punxsutawney, Pa., Thursday, Feb. 2, 2023. Phil...}

\entryitemWithDescription{\hskip 0pt{}Eye drops linked to US drug-resistant bacteria outbreak}{https://apnews.com/article/4572be6da44f4fab4e0f691f5e37e3ed}{FILE - This scanning electron microscope image made available by the Centers for Disease Control and Prevention shows rod-shaped Pseudomonas aeruginosa bacteria. U.S. health officials are advising people to stop using the over-the-counter...}

\entryitemWithDescription{\hskip 0pt{}Iranian film director goes on hunger strike in prison}{https://apnews.com/article/c3d0364a79edb5ec90f29b8180ecf0a6}{FILE - Iranian filmmaker Jafar Panahi is shown at his home after he was freed from jail on bail after more than two months in custody, in Tehran, Iran, on May 25, 2010 . Panahi who was arrested last summer, weeks before his latest film...}

\entryitemWithDescription{\hskip 0pt{}Psychedelic churches in US pushing boundaries of religion}{https://apnews.com/article/5101fe47fe9a6e28de686272ed96ff46}{Colombian shaman Taita Pedro Davila, leads an ayahuasca ceremony with Hummingbird Church, in Hildale, Utah, on Sunday, Oct. 16, 2022. Following the traditions of his grandfather in Colombia, Davila prays, chants, and sings in Spanish and...}

\entryitemWithDescription{\hskip 0pt{}Share debacle a rare setback for Indian tycoon Adani}{https://apnews.com/article/a06d01ead7be3c6105b058998667f98d}{Gautam Adani speaks during the inauguration of Vibrant Gujarat Global Investor summit in Gandhinagar, India, Jan. 12, 2011. Embattled Indian billionaire Adani called off his flagship company\textquotesingle s \$2.5 billion share sale late...}

\entryitemWithDescription{\hskip 0pt{}Frustrated Texans endure winter storm with no power, heat}{https://apnews.com/article/43eac24afe75fa5b0420959b0408b43d}{Icicles hang from the Angelina Eberly statue in downtown Austin, Texas, during a winter storm on Wednesday, Feb. 1, 2023. (Jay Janner/Austin American-Statesman via AP) AUSTIN, Texas (AP) --- Thousands of frustrated Texans shivered in...}

\entryitemWithDescription{\hskip 0pt{}All-Star festivities showcase next generation of NHL stars}{https://apnews.com/article/3437c014d3b840e9af5dddee1b3b3635}{FILE - Dallas Stars\textquotesingle{} Jason Robertson celebrates after scoring a goal during the first period of an NHL hockey game against the New York Islanders on Jan. 10, 2023, in Elmont, N.Y. The NHL All Star festivities on Feb. 3...}

\entryitemWithDescription{\hskip 0pt{}Ghana water polo grows as sport looks for more diversity}{https://apnews.com/article/9885da4f374bd440521426109919983f}{Asante Prince, the founder of Ghana\textquotesingle s Awatu Winton Water Polo Club, oversees a training session in a swimming pool at the University of Ghana ahead of a competition in Accra, Ghana, Saturday, Jan. 14, 2023. Former water...}

\entryitemWithDescription{\hskip 0pt{}Florida city highlights conflicts over local gerrymandering}{https://apnews.com/article/0dea0c7bca4aa034d99c952201283687}{Marcella Washington, a plaintiff in a local gerrymandering case, speaks in Jacksonville, Fla., Jan. 18, 2023. A protracted legal fight over how city council districts were drawn in Jacksonville, Florida, reflects an aspect of...}

\entryitemWithDescription{\hskip 0pt{}Russia hits civilian targets anew, EU officials visit Kyiv}{https://apnews.com/article/30925e2a28638d1fb971b64d10acd6f8}{An aerial view of apartment buildings hit by Russian rockets in Kramatorsk, Ukraine, Thursday, Feb. 2, 2023. (AP Photo/Yevgen Honcharenko) KYIV, Ukraine (AP) --- Russian missiles hit residential areas in an eastern Ukrainian city Thursday...}