\entryitemWithDescription{\hskip 0pt{}Bronny James says he can handle `amplified' pressure of playing for Lakers with his famous father}{https://apnews.com/article/d9e08f11001b26d301633843e96ba82e}{EL SEGUNDO, Calif. (AP) --- Bronny James says the opportunity to play professionally alongside his famous father played no role in his decision to enter the NBA draft. Now that the 19-year-old son of LeBron James has been selected by the...}

\entryitemWithDescription{\hskip 0pt{}Ann Wilson announces cancer diagnosis, postpones Heart tour}{https://apnews.com/article/1542824b8a444552a8b3e4ef7091c979}{LOS ANGELES (AP) --- Ann Wilson, lead singer of rock band Heart, says she has cancer and the band is postponing the remaining shows on its Royal Flush Tour while she undergoes treatment. Wilson said in a statement Tuesday that she...}

\entryitemWithDescription{\hskip 0pt{}Rep. Lloyd Doggett is first Democrat to publicly call for Biden to step down as party's nominee}{https://apnews.com/article/98c3bd8c4138245e7ef8f79d621268e8}{WASHINGTON (AP) --- A House Democratic lawmaker has become the first in the party to publicly call for President Joe Biden to step down as the Democratic nominee for president, citing Biden's debate performance against Donald Trump...}

\entryitemWithDescription{\hskip 0pt{}Two plundered ancient Greek vases are repatriated from Switzerland}{https://apnews.com/article/cd0f8b3dce0aa6ad2aacde0a710977ca}{ATHENS, Greece (AP) --- Two plundered marble vases that marked ancient Athenians' graves more than 2,000 years ago, including one with an emotional family scene, have been returned to Greece from Switzerland. Greece's Culture Ministry...}

\entryitemWithDescription{\hskip 0pt{}Stripper sues Florida over new age restrictions for workers at adult entertainment businesses}{https://apnews.com/article/f1486e22649cd0b291b02aed4fd9952d}{TALLAHASSEE, Fla. (AP) --- A 19-year-old and the club where she worked as a stripper have sued Florida's attorney general and two local prosecutors to stop enforcement of a new state law prohibiting adult entertainment businesses from...}

\entryitemWithDescription{\hskip 0pt{}Indigenous activist Leonard Peltier denied parole for 1975 killings of 2 FBI agents serving warrants}{https://apnews.com/article/2d0df4e4997d988ec229b05de9dba648}{Indigenous activist Leonard Peltier, who has spent most of his life in prison since his conviction in the 1975 killings of two FBI agents in South Dakota, has been denied parole. The U.S. Parole Commission said in a statement Tuesday...}

\entryitemWithDescription{\hskip 0pt{}AI is learning from what you said on Reddit, Stack Overflow or Facebook. Are you OK with that?}{https://apnews.com/article/9d71b75ec16c78c0d2c51cc46121c1a4}{CAMBRIDGE, Mass. (AP) --- Post a comment on Reddit, answer coding questions on Stack Overflow, edit a Wikipedia entry or share a baby photo on your public Facebook or Instagram feed and you are also helping to train the next generation of...}

\entryitemWithDescription{\hskip 0pt{}Arthur Crudup: What to know about the bluesman who wrote Elvis's first hit and barely got paid}{https://apnews.com/article/97925d5c99bcd373584b382205f77aad}{FRANKTOWN, Va. (AP) --- Arthur ``Big Boy'' Crudup helped invent rock `n' roll. His 1946 song ``That's All Right'' would become the first single Elvis Presley ever released. Rod Stewart would sing it on a chart-topping album. Led Zeppelin...}

\entryitemWithDescription{\hskip 0pt{}Vandals behead a controversial sculpture of Mary giving birth to Jesus in an Austrian cathedral}{https://apnews.com/article/cc2276d626f38c1b726748205fc5a34b}{VATICAN CITY (AP) --- Vandals have beheaded a sculpture featuring the Virgin Mary giving birth to Jesus that had been exhibited in the cathedral in the Austrian city of Linz and drawn criticism from some traditionalist Catholics who said...}

\entryitemWithDescription{\hskip 0pt{}Final person to plead guilty in Denver fire that killed 5 people from Senegal could get 60 years}{https://apnews.com/article/ecc8e128fdb1fdaf66d00b277ab4cf41}{DENVER (AP) --- In between shifts at Amazon to earn money she could send home to her relatives in Senegal --- working opposite times as her sister-in-law so they could care for each other's children --- Hassan Diol would call to talk to...}

\entryitemWithDescription{\hskip 0pt{}Hunter Biden sues Fox News over explicit images featured in a streaming series}{https://apnews.com/article/f6cfb9a9d9a2d1e0d6203d14ee4fdf0b}{NEW YORK (AP) --- Hunter Biden accused Fox News in a lawsuit of unlawfully publishing explicit images of him as part of a streaming series. The president's son filed the lawsuit Sunday in state court in Manhattan over images in ``The...}

\entryitemWithDescription{\hskip 0pt{}Klay Thompson is leaving the Warriors and will join the Mavericks, AP sources say}{https://apnews.com/article/72906f3884470088fcee9ddd74d7b29a}{DALLAS (AP) --- Klay Thompson is moving on from the Golden State Warriors, with the four-time league champion agreeing to join the Western Conference champion Dallas Mavericks and change franchises for the first time in his 13-year NBA...}

\entryitemWithDescription{\hskip 0pt{}White Nebraska man shoots and wounds 7 Guatemalan immigrant neighbors}{https://apnews.com/article/7e4da2e4bc6d28eb36236e8712dcedb7}{CRETE, Neb. (AP) --- A white Nebraska man described as reclusive and confrontational shot and wounded seven neighbors who are Guatemalan immigrants, and investigators said they are not ruling out racist motives. About 15 people were at...}