\entryitemWithDescription{\hskip 0pt{}Barbara Rush, actor who co-starred with Frank Sinatra and Paul Newman among others, dies at 97}{https://apnews.com/article/841a0e7748da44de934294e4927ccd1f}{LOS ANGELES (AP) --- Barbara Rush, a popular leading actor in the 1950 and 1960s who co-starred with Frank Sinatra, Paul Newman and other top film performers and later had a thriving TV career, has died. She was 97. Rush's death was...}

\entryitemWithDescription{\hskip 0pt{}Lou Conter, last survivor of USS Arizona from Pearl Harbor attack, dies at 102}{https://apnews.com/article/e4fdc131104be724691c364177e55076}{HONOLULU (AP) --- The last living survivor of the USS Arizona battleship that exploded and sank during the Japanese bombing of Pearl Harbor has died. Lou Conter was 102. Conter passed away at his home Monday in Grass Valley, California...}

\entryitemWithDescription{\hskip 0pt{}Motorists creep along 1 lane after part of California's iconic Highway 1 collapses}{https://apnews.com/article/7776ec0459e9ca2f8e99500004c31b81}{BIG SUR, Calif. (AP) --- Motorists crept along one lane of a scenic stretch of California's iconic Highway 1 on Monday after a giant chunk of it collapsed into the ocean following heavy weekend rains, stranding as many as 1,600 people in...}

\entryitemWithDescription{\hskip 0pt{}White House Easter egg roll drawing a huge crowd after storm-delayed start}{https://apnews.com/article/985e4e994529bcbdb80898a62b9fe5fb}{WASHINGTON (AP) --- Thunder and lightning delayed the start of the Easter egg roll at the White House for 90 minutes on Monday, but the event eventually kicked off under gray skies with many youngsters wearing ponchos or colorful jackets...}

\entryitemWithDescription{\hskip 0pt{}Gillian Anderson and Rufus Sewell recreate a royal media disaster in Prince Andrew drama `Scoop'}{https://apnews.com/article/f5ca804aa03bb840926a23932e212eb8}{LONDON (AP) --- As the past few weeks have shown, British royalty and the media can be an explosive mix. The absence of the Princess of Wales after abdominal surgery in January sparked uncontrolled online speculation that was first...}

\entryitemWithDescription{\hskip 0pt{}Germany has legalized possession of small amounts of cannabis. But the buzz may not last.}{https://apnews.com/article/26e6a5ec254cfa69d063ec352036dfd8}{FRANKFURT, Germany (AP) --- Marijuana campaigners in Germany lit celebratory joints on Monday as the country liberalized rules on cannabis to allow possession of small amounts. The German Cannabis Association, which campaigned for the new...}

\entryitemWithDescription{\hskip 0pt{}Attempting to draw youth, Japan's royal family debuts Instagram. But so far, no candid photos shared}{https://apnews.com/article/f97a5424a92a52d3653450255f4058ca}{TOKYO (AP) --- Japan's imperial family made an Instagram debut with a barrage of posts on Monday, hoping to shake off their reclusive image and reach out to younger people on social media. The Imperial Household Agency, a government...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Easter Sunday around the world}{https://apnews.com/article/7a990b8e3f1241cb153bbf003b3d3af6}{Across the globe, people celebrated Easter Sunday --- commemorating the day when, according to Christian tradition, Jesus was resurrected in Jerusalem two millennia ago. In India, Christian families lit candles and placed flowers on the...}

\entryitemWithDescription{\hskip 0pt{}Kia recalls over 427,000 Telluride SUVs because they might roll away while parked}{https://apnews.com/article/8d0832de5e40e7124dfdae20ea0158af}{NEW YORK (AP) --- Kia is recalling more than 427,000 of its Telluride SUVs due to a defect that may cause the cars to roll away while they're parked. According to documents published by the National Highway Traffic Safety Administration...}

\entryitemWithDescription{\hskip 0pt{}`Godzilla x Kong: The New Empire'' roars to an \$80 million box office opening}{https://apnews.com/article/faad76c136390153dbfce09e0800c889}{LOS ANGELES (AP) --- The Godzilla-King Kong combo stomped on expectations as `` Godzilla x Kong: The New Empire '' roared to an \$80 million opening on 3,861 North American screens, according to Sunday studio estimates. The monster mash...}

\entryitemWithDescription{\hskip 0pt{}Pope overcomes health concerns, presides over blustery Easter Sunday Mass in St. Peter's Square}{https://apnews.com/article/a89541850baa416f69060ae8e699abac}{ROME (AP) --- Pope Francis overcame concerns about his health to preside over Easter Sunday Mass, leading tens of thousands of people in a flower-decked St. Peter's Square in one of the most important liturgies of the year. Just hours...}

\entryitemWithDescription{\hskip 0pt{}Numbers have been drawn for an estimated \$935 million Powerball jackpot}{https://apnews.com/article/cb08709b30ab08abbbb3c12e17686e00}{DES MOINES, Iowa (AP) --- The numbers were drawn Saturday night for an estimated \$935 million Powerball jackpot that has been growing since the last winner nearly three months ago. The numbers drawn were: 12, 13, 33, 50, 52 and the red...}

\entryitemWithDescription{\hskip 0pt{}Caitlin Clark leads Iowa to 89-68 win over Colorado and rematch with defending NCAA champion LSU}{https://apnews.com/article/516b776dd76a4e93a4aebef3d81fe153}{ALBANY, N.Y. (AP) --- Caitlin Clark had 29 points and 15 assists to lead top-seeded Iowa to an 89-68 win over fifth-seeded Colorado in the women's NCAA Tournament on Saturday, setting up a rematch of last year's national title game...}