\entryitemWithDescription{\hskip 0pt{}Jimmy Carter's 100th birthday to be celebrated with musical gala at Atlanta's Fox Theatre}{https://apnews.com/article/ea362d89fb2e86da3b14120473f63827}{ATLANTA (AP) --- Former President Jimmy Carter will be honored next month, ahead of his 100th birthday, with a musical gala at the Fox Theatre in Atlanta, The Carter Center announced Thursday. The Sept. 17 event --- ``Jimmy Carter 100: A...}

\entryitemWithDescription{\hskip 0pt{}Bookmaker to plead guilty in gambling case tied to baseball star Shohei Ohtani's ex-interpreter}{https://apnews.com/article/65a16913c1dd5b428581d6863df777e8}{LOS ANGELES (AP) --- A Southern California bookmaker who took thousands of sports bets from the ex-interpreter for baseball star Shohei Ohtani has agreed to plead guilty to running an illegal gambling business, U.S. authorities announced...}

\entryitemWithDescription{\hskip 0pt{}Remember the ice bucket challenge? 10 years later, the viral campaign is again fundraising for ALS}{https://apnews.com/article/98578d550efff9923eb1db945099ebbc}{BOSTON (AP) --- Dozens of people, including the Massachusetts governor and several sports stars, dumped cold water on themselves at Fenway Park Thursday to mark the 10th anniversary of the ALS ice bucket challenge. The event is part of an...}

\entryitemWithDescription{\hskip 0pt{}Cardi B files for divorce from Offset, posts she's pregnant with their third child on Instagram}{https://apnews.com/article/b2b33367c6da8ca33e0ac53de3d1c006}{NEW YORK (AP) --- Cardi B has filed for divorce from her husband, Migos' rapper Offset. A representative for Cardi B confirmed the news to The Associated Press, writing, ``This is not based on any one particular incident, it has been a...}

\entryitemWithDescription{\hskip 0pt{}Who is Yusuf Dikec, the Turkish shooter who went viral at the 2024 Olympics?}{https://apnews.com/article/a7890124304080a48e7ee4294004d306}{CHATEAUROUX, France (AP) --- Turkish pistol shooter Yusuf Dikec has gone viral on social media for his seemingly casual attitude while shooting his way to a silver medal at the 2024 Olympics. The most-shared images show Dikec shooting in...}

\entryitemWithDescription{\hskip 0pt{}Tahiti's youth surf culture gets a boost as island hosts the Paris Olympics}{https://apnews.com/article/0d6aa6aa6bea29f8df122037a0c14d33}{TEAHUPO'O, Tahiti (AP) --- As the heavy, barrel-shaped waves of Teahupo'o, Tahiti --- where the Paris Olympics surfing competition is being held --- crashed in the distance, another, smaller surf session was underway just off the shore. ``...}

\entryitemWithDescription{\hskip 0pt{}Don't panic! Taylor Swift warns fans to expect sirens for WWII anniversary in Warsaw before concert}{https://apnews.com/article/7a7fb64f2b37e74d9feb60f1ccf7bedf}{WARSAW, Poland (AP) --- Taylor Swift is telling fans traveling to her concert in Warsaw on Thursday to not panic, and expect to hear loud sirens in the afternoon honoring a key World War II anniversary. The Polish capital is holding...}

\entryitemWithDescription{\hskip 0pt{}Hollywood's video game performers head to the picket line over AI protections}{https://apnews.com/article/f3f18ad01c5b8f4d525a836aeb531447}{LOS ANGELES (AP) --- Hollywood's video game performers are heading to the Warner Bros. Studios lot Thursday to picket against what they call an unwillingness from top gaming companies to protect voice actors and motion capture workers...}

\entryitemWithDescription{\hskip 0pt{}MrBeast, YouTube's biggest star, acknowledges past `inappropriate language' as controversies swirl}{https://apnews.com/article/742306d7c77e2eca8d895bf439790c69}{NEW YORK (AP) --- MrBeast, YouTube's biggest star and a philanthropic force with nearly unrivaled influence among young audiences, acknowledged Wednesday that he used ``inappropriate language'' in his early online days, as numerous...}

\entryitemWithDescription{\hskip 0pt{}Drag queen in Olympic opening ceremony has no regrets, calls it `a photograph of France in 2024'}{https://apnews.com/article/80ffb114bd84229d4e2b12506871b443}{PARIS (AP) --- As a gay youth growing up in central France, Hugo Bardin never felt he lived in a world that represented who he was --- a world in which he had a place. And that is why Bardin, who performs as the drag queen Paloma, felt it...}

\entryitemWithDescription{\hskip 0pt{}Former ballerina in Florida is convicted of manslaughter in her estranged husband's 2020 shooting}{https://apnews.com/article/ac5bacf9bf958d6bfab322fdbff2effd}{BRADENTON, Fla. (AP) --- A former ballerina has been convicted of manslaughter in the 2020 shooting death of her estranged husband in Florida. A Manatee County jury returned the guilty verdict late Tuesday against Ashley Benefield, court...}

\entryitemWithDescription{\hskip 0pt{}White House chef retires after nearly 30 years, 1st woman and 1st person of color to have the job}{https://apnews.com/article/4f30d444c822863edfcf6c0fdf8ba234}{WASHINGTON (AP) --- The White House's executive chef has retired after nearly three decades of making meals and cooking up state dinners for five different presidents and their families. Cris Comerford is the first woman to hold the job...}

\entryitemWithDescription{\hskip 0pt{}Olympics bet against climate change with Seine swimming. For days, it looked like they would lose}{https://apnews.com/article/22a067bfdc50ba0e6478c008c93311c6}{With plans for athletes to swim the Seine River through the heart of Paris, Olympic organizers essentially bet against climate change's extreme weather. For several days it appeared they would lose --- by ditching the swimming portion of...}