\entryitemWithDescription{\hskip 0pt{}Spirit Airlines cancels dozens of flights to inspect some of its planes. Disruptions will last days}{https://apnews.com/article/5affc1006ab687a6701d47c6d11b2162}{Spirit Airlines canceled about 100 flights on Friday after pulling some planes out of service for inspections, and the airline expects the disruptions to last several days. Spirit did not describe the nature of the inspections and did not...}

\entryitemWithDescription{\hskip 0pt{}Illinois government employee fired after posting antisemitic comments on social media}{https://apnews.com/article/42b9fb4dd66b20e903ca9b8c4515c327}{SPRINGFIELD, Ill. (AP) --- An employee with the Illinois comptroller's office has been fired after she posted vulgar antisemitic comments on social media during an exchange about the latest Israel-Hamas war. A spokesperson for Illinois...}

\entryitemWithDescription{\hskip 0pt{}UK stage and screen star Haydn Gwynne dies at 66 after cancer diagnosis}{https://apnews.com/article/5fb17dbc928656ee7e5678667cff0005}{LONDON (AP) --- Haydn Gwynne, a versatile and acclaimed performer on British stage and screen, has died. She was 66 and had recently been diagnosed with cancer. Gwynne's agent Alex Irwin said the actress died in a London hospital early...}

\entryitemWithDescription{\hskip 0pt{}Italian Premier Meloni announces separation from partner, father of daughter}{https://apnews.com/article/5eeaa4ae2596c5c9c36df20b16fa4614}{ROME (AP) --- Italian Premier Giorgia Meloni announced Friday that she is separating from her partner and the father of their young daughter after nearly a decade together. In a statement posted on social media, Meloni said her...}

\entryitemWithDescription{\hskip 0pt{}What's that bar band playing `Jumpin' Jack Flash'? Oh, it's the Rolling Stones!}{https://apnews.com/article/071ec5fd08fc3005657e4e4f98e81311}{NEW YORK (AP) --- Those miracles of modern science, the Rolling Stones, celebrated the release of their first album of original music in 18 years with a Manhattan club gig on Thursday. Before a celebrity-strewn audience of invited guests...}

\entryitemWithDescription{\hskip 0pt{}Baltimore firefighter dies and 4 others are injured battling rowhouse fire}{https://apnews.com/article/35eb6664afaccebfad9b71cadf19d28c}{BALTIMORE (AP) --- A rapidly intensifying blaze that engulfed multiple rowhouses in northwest Baltimore late Thursday afternoon left one firefighter dead and four others injured, city officials said. The injured firefighters sustained...}

\entryitemWithDescription{\hskip 0pt{}Britney Spears' book `The Woman In Me' makes private details public, and public events personal}{https://apnews.com/article/80d00a6d450d87ae68457bd826843be4}{LOS ANGELES (AP) --- Britney Spears' highly anticipated memoir ``The Woman in Me'' will be released Tuesday, revealing the pop superstar's personal take on events that have played out publicly in her decades as one of the most scrutinized...}

\entryitemWithDescription{\hskip 0pt{}Marlon Wayans says he is being unfairly prosecuted after being racially targeted by gate agent}{https://apnews.com/article/4ec0285ee770867d09d6a749b74e0927}{DENVER (AP) --- Actor and comedian Marlon Wayans says he is being unfairly prosecuted for disturbing the peace over a dispute with an airline employee who he alleges targeted him because of his race. Attorneys for Wayans, who is Black...}

\entryitemWithDescription{\hskip 0pt{}Southern California university mourns loss of four seniors killed in Pacific Coast Highway crash}{https://apnews.com/article/e795a3de43fc240938ed3d6bb040213d}{MALIBU, Calif. (AP) --- A Southern California university wrestling with the deaths of four seniors who were struck by a car sought to comfort students and faculty Thursday in a prayer service that recalled the young women as ``bright...}

\entryitemWithDescription{\hskip 0pt{}Forecast predict an El Nino winter. What does that mean?}{https://apnews.com/article/e5c450e1cb51d186d68aaae1b259b311}{The upcoming United States winter looks likely to be a bit low on snow and extreme cold outbreaks, with federal forecasters predicting the North to get warmer than normal and the South wetter and stormier. A strong El Nino heavily...}

\entryitemWithDescription{\hskip 0pt{}Will Smith joins Jada Pinkett Smith at book talk, calls their relationship brutal and beautiful}{https://apnews.com/article/5fa6987b0fcd31d0b9041f70e22dd1d9}{BALTIMORE (AP) --- Will Smith joined Jada Pinkett Smith on stage as she promoted her new memoir in her Baltimore hometown Wednesday night, pledging lifelong support for her just a week after she revealed that the couple had been separated...}

\entryitemWithDescription{\hskip 0pt{}Marine killed in homicide at Camp Lejeune; second Marine held for suspected involvement}{https://apnews.com/article/6705fcbc3920625c0bea38a1b9909234}{CAMP LEJEUNE, N.C. (AP) --- A Marine was killed in a homicide at Camp Lejeune and a second Marine was held on suspicion of being involved, the base said. Base authorities took the Marine into custody about 10:15 p.m. Wednesday after an...}

\entryitemWithDescription{\hskip 0pt{}Burt Young, Oscar-nominated actor who played Paulie in `Rocky' films, dies at 83}{https://apnews.com/article/6239cda219832f45f75a5de2b2d5577a}{LOS ANGELES (AP) --- Burt Young, the Oscar-nominated actor who played Paulie, the rough-hewn, mumbling-and-grumbling best friend, corner-man and brother-in-law to Sylvester Stallone in the ``Rocky'' franchise, has died. Young died Oct. 8...}