\entryitemWithDescription{\hskip 0pt{}Politicians and dog experts vilify South Dakota governor after she writes about killing her dog}{https://apnews.com/article/5710b302e33f61c697f20ab3b227a19b}{Politicians and dog experts alike are vilifying South Dakota Gov. Kristi Noem after she wrote in a new book about killing a rambunctious puppy, with the reaction bringing questions about whether she is still a viable potential running...}

\entryitemWithDescription{\hskip 0pt{}A horse-shaped nebula gets its close-up in new photos by NASA's Webb telescope}{https://apnews.com/article/be88e5a1fc018f2407536f1d6f6d3c10}{DALLAS (AP) --- NASA's Webb Space Telescope has revealed the sharpest images yet of a portion of a horse-shaped nebula, showing the ``mane'' in finer detail. The Horsehead Nebula, in the constellation Orion, is 1,300 light-years away. A...}

\entryitemWithDescription{\hskip 0pt{}Britney and Jamie Spears settlement avoids long, potentially ugly and revealing trial}{https://apnews.com/article/a8c97644e7e1a531e3666a679115b6ae}{LOS ANGELES (AP) --- Britney Spears and her father Jamie Spears will avoid what could have been a long, ugly and revealing trial with a settlement of the lingering issues in the court conservatorship that controlled her life and financial...}

\entryitemWithDescription{\hskip 0pt{}Jason Kelce will join ESPN and be part of `Monday Night Football' pregame show, AP source says}{https://apnews.com/article/2931648a3ca809ae3c5efde52a7a8464}{Jason Kelce will join ESPN's ``Monday Night Countdown'' after retiring from the Philadelphia Eagles earlier this year, according to a person with knowledge of the deal. The person confirmed the deal to The Associated Press on the...}

\entryitemWithDescription{\hskip 0pt{}Zebras get loose near highway exit, gallop into Washington community before most are corralled}{https://apnews.com/article/0bc48c34c9e90e59db2b218ebc985afb}{NORTH BEND, Wash. (AP) --- It was an unusual wildlife sighting Sunday when four zebras escaped from their trailer and galloped into a Washington neighborhood. Three of the four black-and-white striped animals were quickly captured, but...}

\entryitemWithDescription{\hskip 0pt{}Oregon authorities to reveal winner of \$1.3 billion Powerball jackpot}{https://apnews.com/article/8200b538497c972624ace5e2fddf56e6}{Oregon authorities on Monday are set to publicly reveal the winner of the \$1.3 billion Powerball jackpot. The winning Powerball ticket was sold in early April at a Plaid Pantry convenience store in Portland, ending a winless streak that...}

\entryitemWithDescription{\hskip 0pt{}CBS Sports announces Matt Ryan will join NFL studio show. Longtime analysts Simms and Esiason depart}{https://apnews.com/article/20f9cdd8b2b2ff894f06f3c9443da3b5}{NEW YORK (AP) --- Matt Ryan, who retired last week after 15 years in the NFL, will join CBS Sports as a studio analyst on ``The NFL Today'' and Phil Simms and Boomer Esiason will leave after long runs on the show, the network announced...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift's `The Tortured Poets Department' hits No. 1, experiences largest streaming week ever}{https://apnews.com/article/59cf23c8056e05768b41a0594be984cc}{NEW YORK (AP) --- Taylor Swift continues to dominate in the week following the release of her 11th album, ``The Tortured Poets Department.'' The 31-track album has hit No. 1 on the Billboard 200 chart, tying Swift with Jay-Z for second...}

\entryitemWithDescription{\hskip 0pt{}French media: Police summon actor Gérard Depardieu for questioning about sexual assault allegations}{https://apnews.com/article/1a4970f3b7e177a6682314f87579a5dd}{PARIS (AP) --- French media are reporting that police have summoned actor Gérard Depardieu for questioning about allegations made by two women that he sexually assaulted them on movie sets. Broadcaster BFMTV and the daily Le Parisien both...}

\entryitemWithDescription{\hskip 0pt{}The Rolling Stones show no signs of slowing down as they begin their latest tour with Texas show}{https://apnews.com/article/f0de46c85a29d132e716009f927d6431}{HOUSTON (AP) --- Time marches on and all good things must come to an end. But don't tell that to The Rolling Stones. What many believe to be the greatest rock 'n' roll band in the world showed no signs of slowing down anytime soon as they...}

\entryitemWithDescription{\hskip 0pt{}Pair of giant pandas set to travel from China to San Diego Zoo under conservation partnership}{https://apnews.com/article/4bcf03f868a5e8d2e54d293ba1352b7b}{SAN DIEGO (AP) --- A pair of giant pandas will soon make the journey from China to the U.S., where they will be cared for at the San Diego Zoo as part of an ongoing conservation partnership between the two nations, officials said Monday...}

\entryitemWithDescription{\hskip 0pt{}Revival of vinyl records in Brazil spares a 77-year-old singer – and others – from oblivion}{https://apnews.com/article/002c636f8c25c3874627d7e535a92c48}{SAO PAULO (AP) --- It took almost a half century for Brazilian singer Cátia de França to find her audience, but she finally has --- with the help of a near-obsolete audio technology. Born in Paraíba, a state in Brazil's poor northeast...}

\entryitemWithDescription{\hskip 0pt{}Texans WR Tank Dell shot in Florida, sustains minor wound, team says}{https://apnews.com/article/684a6c204054024ef2b312ff15133b50}{Houston Texans wide receiver Tank Dell was shot in Florida and sustained a minor wound, the team announced on social media. Dell was shot Saturday night in Sanford and has since been released from a hospital ``in good spirits,'' the team...}