\entryitemWithDescription{\hskip 0pt{}Jimmy Carter, 39th US president, in hospice care}{https://apnews.com/article/f4e26c10a7b366f14e62f690da403b0a}{FILE - Former President Jimmy Carter reacts as his wife Rosalynn Carter speaks during a reception to celebrate their 75th wedding anniversary, July 10, 2021, in Plains, Ga. The Carter Center said Saturday, Feb. 18, 2023, that former...}

\entryitemWithDescription{\hskip 0pt{}Blinken: China's balloon incursion 'must never happen again'}{https://apnews.com/article/0f726ea0cd24731658412da3cae9adbf}{United States Secretary of State Antony Blinken sits down for a Meeting of the Transatlantic Quad with the Foreign Ministers of France, Germany and the United Kingdom at the Munich Security Conference in Munich, Saturday, Feb. 18, 2023...}

\entryitemWithDescription{\hskip 0pt{}From a secret safehouse, Peru's Indigenous revolt advances}{https://apnews.com/article/c31f1bf7fed534bab38b0716b7d1801c}{FILE - An Aymara woman, holding a Peruvian national, stands on a pile of dirt serving as a roadblock set up by anti-government protesters, in Acora, southern Peru, Jan. 29, 2023. Peruvians have been protesting since early December, when...}

\entryitemWithDescription{\hskip 0pt{}Fox pit reporter Sims a symbol of NASCAR's diversity goals}{https://apnews.com/article/0ca94dc8e04eb1be914e23dabcee9a4e}{Josh Sims, left, of FOX Sports interviews Alex Bowman after he qualified for the pole position in the NASCAR Daytona 500 auto race at Daytona International Speedway, Wednesday, Feb. 15, 2023, in Daytona Beach, Fla. (AP Photo/John Raoux...}

\entryitemWithDescription{\hskip 0pt{}Republican losses fan election conspiracies in rural Arizona}{https://apnews.com/article/25df40f2b9189dcc597e9315fbc53a53}{Members of the public attend Cochise County Board of Supervisors meeting to provide feedback on the proposed transfer of election functions and duties to the county recorder, Tuesday, Feb. 14, 2023, in Bisbee, Ariz. (AP Photo/Alberto...}

\entryitemWithDescription{\hskip 0pt{}Why sick minks are reigniting worries about bird flu}{https://apnews.com/article/75e5d058e0fda23b5359f66cafb74cdf}{FILE - Municipal workers collect dead pelicans on Santa Maria beach in Lima, Peru, Tuesday, Nov. 30, 2022, as thousands of birds have died in November along the Pacific of Peru from bird flu, according to The National Forest and Wildlife...}

\entryitemWithDescription{\hskip 0pt{}Will Alex Murdaugh testify? Takeaways from his murder trial}{https://apnews.com/article/73ffc8af5e2d97805f87f3c005e65bb7}{Defense attorney Jim Griffin measures Alex Murdaugh during a break in his double murder trial at the Colleton County Courthouse on Thursday, Feb. 16, 2023, in Walterboro, S.C. The 54-year-old attorney is standing trial on two counts of...}

\entryitemWithDescription{\hskip 0pt{}US: Russia has committed crimes against humanity in Ukraine}{https://apnews.com/article/cee87f06cbf3fcdf37e0bb398360c8ee}{Vize President of the United States Kamala Harris arrives for a meeting with French President Emmanuel Macron at the Munich Security Conference in Munich, Germany, Friday, Feb. 17, 2023. (AP Photo/Michael Probst, Pool) MUNICH (AP) --- The...}

\entryitemWithDescription{\hskip 0pt{}FBI records deepen mystery of dig for Civil War-era gold}{https://apnews.com/article/ec6f923036d4da94d0d8b07a6e0e82bb}{Treasure hunter Dennis Parada, owner of Finders Keepers, talks about the FBI\textquotesingle s 2018 dig for Civil War-era gold in an interview at his office in Clearfield, Penn., Jan. 6, 2023. Parada is pressing the FBI to release more...}

\entryitemWithDescription{\hskip 0pt{}Turkish teen filmed 'last moments' from quake-hit apartment}{https://apnews.com/article/872755dc7549dc2e326b59803cf2a0fd}{Taha Erdem, 17, right, his mother Zeliha Erdem, left, and father Ali Erdem stand next to the debris from a building where Tahan was trapped after the earthquake of Feb. 6, in Adiyaman, Turkey, Friday, Feb. 17, 2023. Taha Erdem, a resident...}

\entryitemWithDescription{\hskip 0pt{}Ghana soccer player Christian Atsu dies in Turkey earthquake}{https://apnews.com/article/0c52632d93fbc1ad2fdbee769920fbb9}{FILE - Christian Atsu plays for Newcastle United, Jan. 12, 2019. Search teams have recovered the body of Ghanaian international soccer player Christian Atsu in the ruins of a building that collapsed during the devastating earthquake that...}

\entryitemWithDescription{\hskip 0pt{}North Korea fires missile as US, S. Korea prepare for drills}{https://apnews.com/article/94204c2b70d2f2e6db3e3688e89905cb}{A TV screen shows a file image of North Korea\textquotesingle s missile launch during a news program at the Seoul Railway Station in Seoul, South Korea, Saturday, Feb. 18. 2023. South Korea\textquotesingle s military said North Korea on...}

\entryitemWithDescription{\hskip 0pt{}Nigerian cash crisis brings pain: `Everything is just tough'}{https://apnews.com/article/ea096f5683fe9c5db712a0c78c7c8adb}{Godgift Inemesit, 28, plays with her children inside her room in Abuja, Nigeria, Monday, Feb. 13, 2023. No one in Godgift Inemesit\textquotesingle s family of eight is sure when they will get to eat each day --- except for her three kids...}