\entryitemWithDescription{\hskip 0pt{}Rap artist GloRilla has been charged with drunken driving in Georgia}{https://apnews.com/article/60123dc79edc50dae72f009620604798}{SUWANEE, Ga. (AP) --- The rap artist known as GloRilla has been charged with drunken driving in Georgia, jail records show. GloRilla, whose real name is Gloria Woods, was charged Tuesday with first-offense driving under the influence of...}

\entryitemWithDescription{\hskip 0pt{}Britain's Prince Harry formally confirms he is now a US resident}{https://apnews.com/article/5bad226e20fede037b5ce836cb1e6a60}{LONDON (AP) --- Prince Harry, the son of King Charles III and fifth in line to the British throne, has formally confirmed he is now a U.S. resident. Four years after Harry and his American wife, Meghan, the Duchess of Sussex, decamped to...}

\entryitemWithDescription{\hskip 0pt{}Meta's newest AI model beats some peers. But its amped-up AI agents are confusing Facebook users}{https://apnews.com/article/229b386ebfbdc23f0e9245a68f7eb2d0}{CAMBRIDGE, Mass. (AP) --- Generative AI is advancing so quickly that the latest chatbots available today could be out of date tomorrow. Google, Meta Platforms and OpenAI, along with startups such as Anthropic, Cohere and France's Mistral...}

\entryitemWithDescription{\hskip 0pt{}Allman Brothers Band co-founder and legendary guitarist Dickey Betts dies at 80}{https://apnews.com/article/fe2e01a963d446538b2f10fd134165e8}{Guitar legend Dickey Betts, who co-founded the Allman Brothers Band and wrote their biggest hit, ``Ramblin' Man,'' has died. He was 80. The Rock \& Roll Hall of Famer died at his home in Osprey, Florida, David Spero, Betts' manager of 20...}

\entryitemWithDescription{\hskip 0pt{}An earthquake measuring 5.6 hits central Turkey. No immediate reports of casualties or damage}{https://apnews.com/article/0ac3a839ba943925c6a576834ae7bcc4}{ANKARA, Turkey (AP) --- A moderately-strong earthquake struck central Turkey on Thursday, the country's disaster management agency said. It was not immediately clear if it caused any casualties or damage. The magnitude 5.6 earthquake...}

\entryitemWithDescription{\hskip 0pt{}Long-lost first USS Enterprise model is returned to `Star Trek' creator Gene Roddenberry's son}{https://apnews.com/article/e3cea04b05ae5c24130d144a0b38d051}{DALLAS (AP) --- The first model of the USS Enterprise --- used in the opening credits of the original ``Star Trek'' television series --- has boldly gone back home, returning to creator Gene Roddenberry's son decades after it went...}

\entryitemWithDescription{\hskip 0pt{}Fire in truck carrying lithium ion batteries leads to 3-hour evacuation in Columbus, Ohio}{https://apnews.com/article/2d623595b3312770f791cb41a475fa43}{COLUMBUS, Ohio (AP) --- Authorities evacuated an area of Ohio's capital, Columbus, for several hours on Thursday out of fear that a fire in truck's trailer could have caused lithium ion batteries to explode. Police began evacuating a...}

\entryitemWithDescription{\hskip 0pt{}Starbucks is introducing a cold drink cup made with less plastic}{https://apnews.com/article/90f19ce6ff721c7bf900f1447932dcc0}{Booming sales of cold drinks at Starbucks have created a problem: growing amounts of plastic waste from the single-use cups that Frappuccinos, Refreshers, cold brews and other iced drinks are served in. The coffee giant said Thursday it...}

\entryitemWithDescription{\hskip 0pt{}The Lyrid meteor shower peaks this weekend, but it may be hard to see it}{https://apnews.com/article/1c5b963fb9d76042671fcce1fe3d326d}{WASHINGTON (AP) --- The Lyrid meteor shower is underway. But with a nearly full moon in the sky during the peak, it might be tough to see clearly. The Lyrids occur every year in mid-to-late April. This year's peak activity happens Sunday...}

\entryitemWithDescription{\hskip 0pt{}Law enforcement officials in 4 states report temporary 911 outages}{https://apnews.com/article/cec9cc2ee4ee1cbb72ac163d1533a7d5}{Law enforcement agencies in Nebraska, Nevada, South Dakota and Texas reported temporary outages to 911 services before saying hours later that services had been restored. It was not immediately clear what caused the outages or whether...}

\entryitemWithDescription{\hskip 0pt{}Reuters photographer wins World Press Photo of the Year with poignant shot from Gaza}{https://apnews.com/article/205161b1b447a1bba942f427a5ba24c9}{PARIS (AP) --- Reuters photographer Mohammed Salem captured this year's prestigious World Press Photo of the Year award Thursday with a depiction of loss and sorrow in Gaza, a heartrending photo of a Palestinian woman cradling the body of...}

\entryitemWithDescription{\hskip 0pt{}One Tech Tip: What to do if your personal info has been exposed in a data breach}{https://apnews.com/article/91461eb71bdfa5f29158740efe5fb692}{LONDON (AP) --- Data breaches like the recent one involving millions of AT\&T customers are becoming an almost regular occurrence. As more of our lives move online, our personal data like email addresses, phone numbers, birthdates and...}

\entryitemWithDescription{\hskip 0pt{}After 40 years in Park City, Sundance exploring options for 2027 film festival and beyond}{https://apnews.com/article/37b035548f26fc3106373305397205b9}{PARK CITY, Utah (AP) --- The Sundance Film Festival may not always call Park City, Utah, home. The Sundance Institute has started to explore the possibility of other U.S. locations to host the independent film festival starting in 2027...}