\entryitemWithDescription{\hskip 0pt{}Bob Dylan is giving fans a chance to relive his 1974 tour with the Band on a staggering 27-disc set}{https://apnews.com/article/0e40b3be6e8ecd3189be433d8531e621}{NEW YORK (AP) --- Bob Dylan fans who want to relive his 1974 concert tour with The Band will soon have opportunity to do that --- ample opportunity. He is releasing a staggering 27-disc box set that includes full recordings of 27 of the...}

\entryitemWithDescription{\hskip 0pt{}Joe Bonsall, celebrated tenor in the country and gospel group the Oak Ridge Boys, dies at 76}{https://apnews.com/article/87a2858ee6ca2517604c6d2fce79d663}{Joe Bonsall, Grammy award winner and celebrated tenor of the country and gospel group the Oak Ridge Boys, died Tuesday. He was 76. Bonsall died from complications of the neuromuscular disorder Amyotrophic Lateral Sclerosis, according to a...}

\entryitemWithDescription{\hskip 0pt{}Target will stop accepting personal checks next week. Are the days of the payment method numbered?}{https://apnews.com/article/d42d5e5d1f3c9a5f08c1899526c305bb}{NEW YORK (AP) --- Target will no longer accept personal checks from shoppers as of July 15, another sign of how a once ubiquitous payment method is going the way of outmoded objects like floppy disks and the Rolodex. The Minneapolis-based...}

\entryitemWithDescription{\hskip 0pt{}Delta and an airline that doesn't fly yet say they'll run flights between the US and Saudi Arabia}{https://apnews.com/article/2da149b1cc096d012c15f2f19d05c714}{Delta Air Lines said Tuesday it has entered into a partnership with startup Riyadh Air with the goal of operating flights between the United States and Saudi Arabia. Riyadh Air, which plans to begin passenger flights next summer, is...}

\entryitemWithDescription{\hskip 0pt{}Lawyer calls social media influencer Andrew Tate and his brother serial tax evaders}{https://apnews.com/article/20e5258a513b8d27a2a53557e5314ac7}{LONDON (AP) --- Social media influencer Andrew Tate's taunts over refusing to pay British taxes on millions of pounds in revenue may come back to haunt him and his brother Tristan. An online video of Tate bragging of never paying taxes...}

\entryitemWithDescription{\hskip 0pt{}NHTSA launches recall query into 94,000 Jeep Wranglers as loss of motive power complaints continue}{https://apnews.com/article/42858f73b33e10773b55a8243335e469}{NEW YORK (AP) --- The U.S. government's auto safety agency is investigating a potential ``loss of motive power'' in more than 94,000 Jeep Wrangler 4xe vehicles, after receiving complaints for cars outside the scope of an earlier recall...}

\entryitemWithDescription{\hskip 0pt{}Awwww! Four endangered American red wolf pups 'thriving' since birth at Missouri wildlife reserve}{https://apnews.com/article/40b682f60e186e31eb02a0874c0b7dd5}{ST. LOUIS (AP) --- The world's most endangered wolf species got a big boost at a Missouri wildlife reserve --- four little puppies born this spring. The April 26 birth of a female American red wolf pup named Otter was followed by a litter...}

\entryitemWithDescription{\hskip 0pt{}A woman who received a pig kidney transplant plus a heart pump has died}{https://apnews.com/article/c88fd6e3f72de09ed6e3c929ffdb53bc}{WASHINGTON (AP) --- A woman who received a pig kidney transplant -\/- along with an implanted device to keep her heart beating -- has died, her surgeon announced Tuesday. Lisa Pisano was near death from kidney and heart failure when...}

\entryitemWithDescription{\hskip 0pt{}The body of an American climber buried by an avalanche 22 years ago in Peru has been found}{https://apnews.com/article/6110403becbcb4fc6b1ab26f01f54f7b}{LIMA, Peru (AP) --- Police in Peru said Tuesday they have found the body of an American mountaineer who was buried by an avalanche 22 years ago as he tried to climb one of the highest peaks in the Andes. Police in the Ancash region told...}

\entryitemWithDescription{\hskip 0pt{}Novak Djokovic uses Wimbledon crowd's 'disrespect' as fuel as he moves closer to another title}{https://apnews.com/article/480ccb0ecefb403b9e022a9302159bc2}{LONDON (AP) --- Novak Djokovic is just one example of a superstar athlete who manages to find motivation wherever possible. Serena Williams, Michael Jordan and Tom Brady are others who come to mind. With Djokovic, it often derives...}

\entryitemWithDescription{\hskip 0pt{}Jason Momoa and Lisa Bonet are officially divorced}{https://apnews.com/article/c75db2bc14ad38ac542ac5e7f35902bc}{LOS ANGELES (AP) --- Jason Momoa and Lisa Bonet are officially divorced. A Los Angeles County judge's dissolution of the marriage of the two actors, who had already been separated for years, took effect Tuesday. Bonet and Momoa were...}

\entryitemWithDescription{\hskip 0pt{}Afghan sprinter Kimia Yousofi ready to run at her 3rd Olympics after being selected for Paris Games}{https://apnews.com/article/b5d91fba88ab03c6ad546e3bc6dd2d21}{SYDNEY (AP) --- Afghan sprinter Kimia Yousofi is preparing to compete at her third Olympics after being selected for the Paris Games from her training base in Australia. Yousofi, Afghanistan's flag bearer at the opening ceremony for the...}

\entryitemWithDescription{\hskip 0pt{}United Airlines flight loses wheel after takeoff from Los Angeles and lands safely in Denver}{https://apnews.com/article/777fc7ec8ad1953fe18023b1335b0e47}{LOS ANGELES (AP) --- A United Airlines Boeing jet lost a main landing gear wheel Monday while taking off from Los Angeles and later landed safely in Denver, the airline said. There were no reported injuries on the ground or on board...}