\entryitemWithDescription{\hskip 0pt{}Chiefs get White House invitation to celebrate Super Bowl win. Could Taylor Swift tag along?}{https://apnews.com/article/51326c3ca1647b43480760e70178e473}{WASHINGTON (AP) --- The White House says it's looking forward to hosting the Super Bowl champion Kansas City Chiefs again --- and it isn't ruling out having the team's most-famous fan, Taylor Swift, tag along this time. Asked at Monday's...}

\entryitemWithDescription{\hskip 0pt{}Wreck of ship that sank in 1940 found in Lake Superior}{https://apnews.com/article/e62339cd3347cbe79e26752a48fdc213}{WHITEFISH POINT, Mich. (AP) --- Shipwreck hunters have discovered a merchant ship that sank in Lake Superior in 1940, taking its captain with it, during a storm off Michigan's Upper Peninsula. The Great Lakes Shipwreck Historical Society...}

\entryitemWithDescription{\hskip 0pt{}The Chiefs have achieved dynasty status with their third Super Bowl title in five years}{https://apnews.com/article/d16a308684d97a6be2d269c8d56404be}{LAS VEGAS (AP) --- This was supposed to be the year when the Kansas City Chiefs were vulnerable. Their wide receivers were dropping passes, their offense was committing penalties, Travis Kelce was supposedly getting old and there was no...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl ad for RFK Jr. stirs Democratic and family tension over his independent White House bid}{https://apnews.com/article/e4dee4be456e643be11735c6e4029377}{Robert Kennedy Jr.'s presidential ambitions resulted in public family drama after a political action committee aired a Super Bowl ad invoking the Democratic family's legacy to implicitly compare the independent candidate to his...}

\entryitemWithDescription{\hskip 0pt{}Feel the need for speed? Late president's 75-mph speedboat is up for auction}{https://apnews.com/article/cf4c10752fbe8c6bae47fdfce6f9905f}{KENNEBUNKPORT, Maine (AP) --- It seems former President George H.W. Bush felt the need for speed in the waters off Maine, where he kept a nearly 1,000 horsepower speedboat. And for the right price, someone else can experience its...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé drops new songs `Texas Hold `Em' and '16 Carriages.' New music `Act II' will arrive in March}{https://apnews.com/article/14ab5948ecfb76c283c638162b7a53f7}{LOS ANGELES (AP) --- Beyoncé is back with two new country tracks --- ``Texas Hold `Em'' and ``16 Carriages.'' After a Verizon commercial starring Beyoncé aired during the Super Bowl ended with the superstar saying ``They ready, drop the...}

\entryitemWithDescription{\hskip 0pt{}Review: Usher shines at star-studded 2024 Super Bowl halftime show}{https://apnews.com/article/ccd211bedd0b3a3e5ea90522828f6a13}{LOS ANGELES (AP) --- Usher emerged at Las Vegas' Allegiant Stadium for the 2024 Super Bowl halftime show seated on a throne, joined by a marching band and a trove of Vegas performers --- but stayed its center. It was an immediate...}

\entryitemWithDescription{\hskip 0pt{}Marathon world record-holder Kelvin Kiptum, who was set to be a superstar, has died in a car crash}{https://apnews.com/article/314b41c92c9166a3a698a2860fa3fc15}{NAIROBI, Kenya (AP) --- Marathon world record-holder Kelvin Kiptum, who was set to be a superstar of long-distance running, was killed along with his coach in a car crash in Kenya late Sunday. Kiptum was 24 and had the world record he set...}

\entryitemWithDescription{\hskip 0pt{}Brazil's aluminum can street party brings joy, and a green message, to revelers}{https://apnews.com/article/03a1abdb1a8a57cbee7abcf855523b5f}{MADRE DE DEUS, Brazil (AP) --- They couldn't see it, but they could hear it. Carnival revelers Sunday in northeastern Brazil `s Madre de Deus heard the aluminum can street party before spotting it: More than 30 paraders decked out in...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift planning to watch Travis Kelce and the Chiefs play 49ers in the Super Bowl}{https://apnews.com/article/2cd5b56b6959ed053056cd6f28a82d0a}{LAS VEGAS (AP) --- The great adventure Taylor Swift promised fans in Tokyo continued Sunday at Allegiant Stadium, where the pop star planned to watch boyfriend Travis Kelce and the rest of the Kansas City Chiefs play the San Francisco...}

\entryitemWithDescription{\hskip 0pt{}Ready for this year's Super Bowl commercials? Here are the ads filling game breaks on Sunday}{https://apnews.com/article/2d2c9d275f58624804bcdd36a762b86f}{NEW YORK (AP) --- Super Bowl Sunday is here --- and, as always, there's a vast roster of advertisers ready to vie for fans' attention during game breaks. Airing a Super Bowl commercial is no easy feat. On top of the reported \$7 million...}

\entryitemWithDescription{\hskip 0pt{}UK's King Charles III sends message of thanks for support after revealing he has cancer}{https://apnews.com/article/9a50d47fc0ab665db3f4b2e1ce16b745}{LONDON (AP) --- King Charles III has expressed his thanks for the messages of support he has received since he revealed last week that he had been diagnosed with cancer. In a statement issued late Saturday, the monarch said that such...}

\entryitemWithDescription{\hskip 0pt{}Dexter Scott King remembered during memorial as keeper of his father Martin Luther King Jr.'s dream}{https://apnews.com/article/7e79af96ae0f37a6278c1565e42d9aac}{Dexter Scott King, the late son of Dr. Martin Luther King Jr. and Coretta Scott King, was remembered Saturday as the protector of his family's legacy and the keeper of his father's dream during a memorial service in Atlanta. ``You, my...}