\entryitemWithDescription{\hskip 0pt{}Bob Woodruff returns to Iraq roadside where bomb nearly killed him 17 years ago}{https://apnews.com/article/e74edfb3978510ef29c525b4cd8f8ada}{NEW YORK (AP) --- The physical pain of nearly dying when shrapnel from a roadside bomb in Iraq tore through his head 17 years ago was hard enough for ABC newsman Bob Woodruff. Mentally, it was even worse. That's evident in talking to...}

\entryitemWithDescription{\hskip 0pt{}National Zoo's giant pandas fly home amid uncertainty about future panda exchanges}{https://apnews.com/article/b5923fc76613a15ade02fd332e1330df}{WASHINGTON (AP) --- The day that panda lovers have been dreading has finally come. The National Zoo's three giant pandas, Mei Xiang, Tian Tian and their cub Xiao Qi Ji. on Wednesday began their long trip to China, leaving behind an empty...}

\entryitemWithDescription{\hskip 0pt{}Judging from the level of complaints, air travel is getting worse}{https://apnews.com/article/37169c9ad5e234f1b2bd0bbb1ccc6ab6}{Air travel is getting worse, judging from the number of consumer complaints. Consumer complaints about airlines nearly doubled in the first three months of this year compared with the same period last year and kept soaring in April and...}

\entryitemWithDescription{\hskip 0pt{}3 charged with running sex ring that catered to elected officials, other wealthy clients}{https://apnews.com/article/78c707fea8491665f01e93671b0e6c25}{BOSTON (AP) --- Three people have been charged with running a sophisticated commercial sex ring in Massachusetts and Virginia that catered to well-connected clients such as elected officials and military officers, federal prosecutors said...}

\entryitemWithDescription{\hskip 0pt{}Texas officials issue shelter-in-place order after chemical plant explosion that injured worker}{https://apnews.com/article/7af7d05367da09e33ec84d2f2c9c01d9}{HOUSTON (AP) --- A massive fire at a chemical plant in rural Texas on Wednesday sent a plume of black smoke into the sky as officials closed down a local highway and ordered residents to take shelter. Authorities issued the shelter-in...}

\entryitemWithDescription{\hskip 0pt{}Parents of a terminally ill baby lose UK legal battle to bring her home}{https://apnews.com/article/0caecf4c18336004d4e3b99cfff9c327}{LONDON (AP) --- A judge at Britain's High Court ruled Wednesday that life support for a terminally ill 8-month-old baby should be withdrawn in a hospice or hospital, despite efforts by the infant's parents and the Italian government to...}

\entryitemWithDescription{\hskip 0pt{}Adidas says it may write off remaining unsold Yeezy shoes after breakup with Ye}{https://apnews.com/article/df2df5a6489beba1a23ffefa6acc98c3}{FRANKFURT, Germany (AP) --- Adidas said it might have to write off the remaining 300 million euros (\$320 million) worth of Yeezy shoes left unsold after it cut ties with rapper Ye, formerly known as Kanye West. The company will decide in...}

\entryitemWithDescription{\hskip 0pt{}Sweden's largest egg producer to cull all its chickens following recurrent salmonella outbreaks}{https://apnews.com/article/1c718dfbaa8499551a32675057a30861}{STOCKHOLM (AP) --- Sweden's largest egg producer, which had nearly 1.2 million chickens or 20\% of all laying hens in the country before a salmonella outbreak, has been ordered to euthanize all of them so the facility can be fully...}

\entryitemWithDescription{\hskip 0pt{}To help 2024 voters, Meta says it will begin labeling political ads that use AI-generated imagery}{https://apnews.com/article/c4aec653d5043a09b1c78b4fb5dcd79b}{WASHINGTON (AP) --- Facebook and Instagram will require political ads running on their platforms to disclose if they were created using artificial intelligence, their parent company announced on Wednesday. Under the new policy by Meta...}

\entryitemWithDescription{\hskip 0pt{}General Motors' autonomous vehicle unit recalls cars for software update after dragging a pedestrian}{https://apnews.com/article/bf08c0c6e7914649750b4dde598af5fc}{DETROIT (AP) --- General Motors' Cruise autonomous vehicle unit is recalling all 950 of its cars to update software after one of them dragged a pedestrian to the side of a San Francisco street in early October. The company said in...}

\entryitemWithDescription{\hskip 0pt{}CMA Awards will pay tribute to Jimmy Buffett during a show hosted by Luke Bryan and Peyton Manning}{https://apnews.com/article/d1a3807afd13cd394cb41134dc7fbce8}{NASHVILLE, Tenn. (AP) --- The CMA Awards are back Wednesday to honor the top artists in country music, with Lainey Wilson, Jelly Roll, Ashley McBryde and Morgan Wallen among the acts hitting the stage. Wilson is the leading nominee for...}

\entryitemWithDescription{\hskip 0pt{}Patrick Dempsey named Sexiest Man Alive by People magazine}{https://apnews.com/article/e8e82d2937498fc320c213a784894e95}{LOS ANGELES (AP) --- He's not just ``McDreamy'' anymore --- Patrick Dempsey is now also People magazine's Sexiest Man Alive. The ``Grey's Anatomy'' star and race car driver takes the mantle from ``Captain America'' star Chris Evans, who...}

\entryitemWithDescription{\hskip 0pt{}Tiger Woods to own and play for Florida team in TGL, his tech-infused golf league}{https://apnews.com/article/def01b4d648ed9db0dc3e38e68baebaa}{Tiger Woods couldn't be more involved with prime-time TGL unless he had built the arena. He helped develop the tech-infused golf league. He's playing in it. And now he's a team owner. Woods and his TGR Ventures and David Blitzer, the...}