\entryitemWithDescription{\hskip 0pt{}US tourist from Boston killed in shark attack in Bahamas, police say}{https://apnews.com/article/13611abef5feb616d230345009f55eb5}{SAN JUAN, Puerto Rico (AP) --- A female tourist from Boston was killed Monday by a shark while paddleboarding in the Bahamas, police told reporters. The victim, who was not identified, was attacked less than a mile off the western end of...}

\entryitemWithDescription{\hskip 0pt{}Gloria Allred representing family involved with Josh Giddey case}{https://apnews.com/article/92e9175873c8486c2a69a1ac6caf4903}{OKLAHOMA CITY (AP) --- Attorney Gloria Allred has confirmed that she is representing the family of the girl Oklahoma City Thunder guard Josh Giddey has been accused of having an improper relationship with. Allred has been a famous...}

\entryitemWithDescription{\hskip 0pt{}Whistleblower allegation: Harvard muzzled disinfo team after \$500 million Zuckerberg donation}{https://apnews.com/article/b4716aa988a721dcc1bc651462179f20}{A prominent disinformation scholar who left Harvard University in August has accused the school of muzzling her speech and stifling --- then dismantling --- her research team as it launched a deep dive in late 2021 into a trove of...}

\entryitemWithDescription{\hskip 0pt{}Oxford University Press has named `rizz' as its word of the year}{https://apnews.com/article/2c01871c71fd3632b3c64c07a4d361f3}{LONDON (AP) --- Oxford University Press has named ``rizz″ as its word of the year, highlighting the popularity of a term used by Generation Z to describe someone's ability to attract or seduce another person. It topped ``Swiftie'' (an...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift watches Travis Kelce at Lambeau Field as Packers beat Chiefs}{https://apnews.com/article/2a1a9e791afbf7a3cb86ec458b1aae67}{GREEN BAY, Wis. (AP) --- Taylor Swift was on hand at Lambeau Field to watch Travis Kelce and the Kansas City Chiefs in their Sunday night game against the Green Bay Packers. It was the fifth Chiefs game Swift has attended since the pop...}

\entryitemWithDescription{\hskip 0pt{}Mexican woman killed in shark attack on Pacific coast near the port of Manzanillo}{https://apnews.com/article/a58d3c40db536e0bc39888816cb42913}{MEXICO CITY (AP) --- A Mexican woman died after she was severely bitten in the leg by a shark in the Pacific Ocean off the beach town of Melaque, authorities said Sunday. Rafael Araiza, the head of the local civil defense office, said the...}

\entryitemWithDescription{\hskip 0pt{}49ers linebacker Dre Greenlaw, Eagles security chief Dom DiSandro ejected in NFC title game rematch}{https://apnews.com/article/275ce1b1811cc5eefb39847796a3c071}{PHILADELPHIA (AP) --- San Francisco 49ers linebacker Dre Greenlaw was ejected from Sunday's 42-19 win against Philadelphia for putting his hand in the face of the Eagles' chief security officer. Dom DiSandro, a constant presence on the...}

\entryitemWithDescription{\hskip 0pt{}Review: The long Kiss goodbye ends at New York's Madison Square Garden}{https://apnews.com/article/ee65cd326572ef07f4cd1ce5886b962c}{NEW YORK (AP) --- It's the end of the road for Kiss. But it's not the end of Kiss. The hard-rocking quartet from New York City played final live concerts Friday and Saturday at Madison Square Garden, culminating a half century of rocking...}

\entryitemWithDescription{\hskip 0pt{}Michigan vs. Alabama, Washington vs. Texas in College Football Playoff; unbeaten Florida St left out}{https://apnews.com/article/8b9db687b7cf159779930298d2f1a388}{The final season of the four-team College Football Playoff turned out to be the most controversial with an unprecedented snub. Michigan, Washington, Texas and Alabama were selected Sunday and Florida State became the first unbeaten Power...}

\entryitemWithDescription{\hskip 0pt{}Kennedy Center Honors fetes new inductees, including Queen Latifah, Billy Crystal and Dionne Warwick}{https://apnews.com/article/97ecec2a716c9953af2a45275964fc15}{WASHINGTON (AP) --- The newest group of Kennedy Center honorees, including comedian Billy Crystal and rapper and actor Queen Latifah, were feted at a star-studded event commemorating their lifetime achievement in arts and entertainment...}

\entryitemWithDescription{\hskip 0pt{}Barbie doll honoring Cherokee Nation leader Wilma Mankiller is met with mixed emotions}{https://apnews.com/article/060faaf1d0cc13e401e79497c14b65cc}{OKLAHOMA CITY (AP) --- An iconic chief of the Cherokee Nation, Wilma Mankiller, inspired countless Native American children as a powerful but humble leader who expanded early education and rural healthcare. Her reach is now broadening...}

\entryitemWithDescription{\hskip 0pt{}No. 8 Alabama knocks off No. 1 Georgia 27-24 for SEC title. Both teams await postseason fate}{https://apnews.com/article/2cc4fa17be895cf367a1cd1479f45dff}{ATLANTA (AP) --- After handing Georgia its first loss in nearly two years, Alabama mixed a raucous celebration of its latest Southeastern Conference championship with a whole lot of lobbying for a College Football Playoff spot that no one...}

\entryitemWithDescription{\hskip 0pt{}Ronaldo walks off to chants of `Messi! Messi!' as his team loses 3-0 in Riyadh derby}{https://apnews.com/article/e262460b0b11c7973bdd325f6e3a78ac}{RIYADH, Saudi Arabia (AP) --- Cristiano Ronaldo walked off the field with the gleeful chants of ``Messi! Messi!'' ringing in his ears from delighted Al-Hilal fans who had just watched their Saudi Pro League team beat the Portugal...}