\entryitemWithDescription{\hskip 0pt{}Drug trafficking blamed as homicides soar in Costa Rica}{https://apnews.com/article/4a8f6ecfe7d23fc83708033dc20e05df}{FILE - The body of a man is illuminated by police flashlights as investigators work a crime scene where an alleged thief and a female passenger died in a shootout during a robbery on a bus in San Jose, Costa Rica, Feb. 6, 2023. According...}

\entryitemWithDescription{\hskip 0pt{}Biden and his 2024 campaign: Waiting for some big decisions}{https://apnews.com/article/e64cd5649d9486291715388db3e8e386}{FILE - President Joe Biden speaks from the Treaty Room in the White House on April 14, 2021, about the withdrawal of the remainder of U.S. troops from Afghanistan. (AP Photo/Andrew Harnik, Pool, File) WASHINGTON (AP) --- President Joe...}

\entryitemWithDescription{\hskip 0pt{}After Nashville, Congress confronts limits of new gun law}{https://apnews.com/article/9fb2b460984eb8658b806d0d5126bba8}{FILE - A balloon with names of the victims is seen at a memorial at the entrance to The Covenant School on Wednesday, March 29, 2023, in Nashville, Tenn. Bipartisan gun legislation signed by President Biden in 2022 has already prevented...}

\entryitemWithDescription{\hskip 0pt{}Lanterns and crescents: more retailers court Ramadan buyers}{https://apnews.com/article/4be6f1b7109c8e8bf8077ce4de86a2ca}{Ramadan decorations are displayed at a Party City store in Dearborn, Mich., on Thursday, March 23, 2023. More businesses are selling Ramadan and Eid items, including DIY kits, lanterns and napkin holders. It\textquotesingle s one of the...}

\entryitemWithDescription{\hskip 0pt{}'War of the states': EV, chip makers lavished with subsidies}{https://apnews.com/article/3ac5f11cdbf020e996f6bc8f92bd2bfd}{Workers prepare the site of a \$4 billion Panasonic EV battery plant Thursday, March 30, 2023, near DeSoto, Kan. Economic incentives offered by Kansas state and local governments beat out those offered by neighboring Oklahoma to help lure...}

\entryitemWithDescription{\hskip 0pt{}At least 18 dead after tornadoes rake US Midwest, South}{https://apnews.com/article/79fe2da8a6b8bd92970032530b760d20}{Damage from a late-night tornado is seen in Sullivan, Ind., Saturday, April 1, 2023. Multiple deaths were reported in the area following the storm. (AP Photo/Doug McSchooler) WYNNE, Ark. (AP) --- Storms that dropped possibly dozens of...}

\entryitemWithDescription{\hskip 0pt{}Fatal fire complicates border city's tensions with migrants}{https://apnews.com/article/3bf3782134f6e447b979e2998d3c2cb7}{Irwing Lopez, a 35-year-old migrant construction worker from Venezuela, washes windshields for tips at a stoplight near the U.S. border wall, behind, in Ciudad Juarez, Mexico, Thursday, March 30, 2023. Lopez\textquotesingle s friend and...}

\entryitemWithDescription{\hskip 0pt{}Doomsday plot? After 3 years, slain kids' mom to stand trial}{https://apnews.com/article/19cdf75463402c1838fb6e85f22e7e2c}{FILE - A boy looks at a memorial for Tylee Ryan and Joshua "JJ" Vallow in Rexburg, Idaho, on June 11, 2020. A mother charged with murder in the deaths of her two children is set to stand trial in Idaho. The proceedings against Lori Vallow...}

\entryitemWithDescription{\hskip 0pt{}Alaska Native Scouts feted 67 years after rescuing Navy crew}{https://apnews.com/article/495cfe305972a85ef8b0b93dafc71167}{This March 28, 2023, photo shows townspeople in Gambell, Alaska, waiting in a snowstorm on four-wheelers to transport Alaska National Guard personnel from the air strip to the school for a ceremony. Sixteen Alaska National Guard members...}

\entryitemWithDescription{\hskip 0pt{}Ukrainian court puts Orthodox leader under house arrest}{https://apnews.com/article/d4723c61be8b131ad0a779dc59ae8b00}{Priests of Ukrainian Orthodox Church pray with their supporters after resisting a government order to leave the Kyiv Pechersk Lavra monastery complex in Kyiv, Ukraine, Saturday, April 1, 2023. In a bitter dispute over a famed Orthodox...}

\entryitemWithDescription{\hskip 0pt{}Pope Francis leaves hospital; 'Still alive,' he quips}{https://apnews.com/article/53e6a136fe9f7b64da551e749a44930a}{Pope Francis autographs the plaster cast of a child as he leaves the Agostino Gemelli University Hospital in Rome, Saturday, April 1, 2023, after receiving treatment for bronchitis, The Vatican said. Francis was hospitalized on Wednesday...}

\entryitemWithDescription{\hskip 0pt{}NBA, players reach deal for a new labor agreement}{https://apnews.com/article/0cf524b13e459eeb5853dad9a455e0e0}{Utah Jazz guard Johnny Juzang (33) shoots against the San Antonio Spurs during the second half of an NBA basketball game in San Antonio, Wednesday, March 29, 2023. (AP Photo/Eric Gay) The most financially successful era in NBA history...}

\entryitemWithDescription{\hskip 0pt{}Credit Suisse takeover hits heart of Swiss banking, identity}{https://apnews.com/article/8078ecf2c389deed29ca96068fc53f97}{FILE - A traffic light signals green in front of the logos of the Swiss banks Credit Suisse and UBS in Zurich, Switzerland, on March 19, 2023. Analysts say the UBS takeover of embattled rival Credit Suisse has shaken Switzerland's self...}