\entryitemWithDescription{\hskip 0pt{}Kings probe 'racial bias' claims after rapper E-40 ejected}{https://apnews.com/article/805bf0cce2b990684461218bc68e934e}{FILE - E-40, middle, watches during an NBA basketball game between the Golden State Warriors and the Portland Trail Blazers in San Francisco, Dec. 30, 2022. The Sacramento Kings are investigating allegations from the rapper E-40 that ``...}

\entryitemWithDescription{\hskip 0pt{}Spain's leader apologizes to victims of sexual consent law}{https://apnews.com/article/462b61fe9c57085bcabdafd2ea2605bd}{Spanish Prime Minister Pedro Sanchez speaks during a press conference held at the Spanish embassy in Beijing, Friday, March 31, 2023. (AP Photo/Ng Han Guan) MADRID (AP) --- Spanish Prime Minister Pedro Sánchez on Sunday apologized to the...}

\entryitemWithDescription{\hskip 0pt{}Cleanup begins after freight train derailment, fire in Maine}{https://apnews.com/article/d590c0545b5e21f6ab0b6105f4b3400b}{In this photo provided by the Maine Forest Service, several locomotives and rail cars burn after a freight train derailed Saturday, April 15, 2023, in Sandwich Academy Grant Township, near Rockwood, Maine. Three workers were treated and...}

\entryitemWithDescription{\hskip 0pt{}`Mario' tops charts again; `Beau is Afraid' wins in limited}{https://apnews.com/article/91908c8f2f4b329f0cda1e5b8ab67a92}{This image released by Nintendo and Universal Studios shows Mario, voiced by Chris Pratt, left, and Princess Peach, voiced by Anya Taylor-Joy, in Nintendo\textquotesingle s "The Super Mario Bros. Movie." (Nintendo and Universal Studios...}

\entryitemWithDescription{\hskip 0pt{}Europe's most powerful nuclear reactor kicks off in Finland}{https://apnews.com/article/741341cfdf79e655a2a680e1b1130917}{FILE - The turbine hall of the nuclear power plant Olkiluoto 3 \textquotesingle OL3\textquotesingle{} is pictured under construction in Eurajoki, south-western Finland, March 23, 2011. Finland's much-delayed and costly new nuclear...}

\entryitemWithDescription{\hskip 0pt{}New push on US-run free electronic tax-filing system for all}{https://apnews.com/article/700e54251a39791091966bc0b356d342}{FILE - A portion of the 1040 U.S. Individual Income Tax Return form is shown July 24, 2018, in New York. The IRS has been tasked with looking into how to create a government-operated electronic free-file tax return system for all...}

\entryitemWithDescription{\hskip 0pt{}More than 6,000 troops to play role in Charles' coronation}{https://apnews.com/article/5d5bc8b88196bafc942e57385506ab80}{A general view inside Westminster Abbey in London, Wednesday, April 12, 2023, ahead of the King\textquotesingle s coronation. Westminster Abbey has been used as Britain\textquotesingle s coronation church since William the Conqueror in...}

\entryitemWithDescription{\hskip 0pt{}Former Indian lawmaker, brother fatally shot live on TV}{https://apnews.com/article/78241a08883aa903d3cf7eb6edaa1108}{Police and media surround the area where Gangster-turned-politician Atiq Ahmad and his brother Ashraf were shot in front of the Motilal Nehru medical college in, Prayagraj, India, Saturday, April 15, 2023. Jailed gangster-turned...}

\entryitemWithDescription{\hskip 0pt{}Louisville shooter fires into park crowd; 2 dead, 4 wounded}{https://apnews.com/article/3bc5936845a3b87094a213effa593003}{The remnants of police tape are visible Sunday morning April 16, 2023, near the tennis courts at Chickasaw Park in Louisville, Ky. following a shooting late Saturday night. (Sam Upshaw/Courier Journal via AP) LOUISVILLE, Ky. (AP) --- An...}

\entryitemWithDescription{\hskip 0pt{}Police say 5 people shot, 2 dead at cockfight in Honolulu}{https://apnews.com/article/00fbef19edbb3c589a3a1d700fb2bf6f}{Two victims died after five people were shot during an altercation at a late-night cockfight Friday in Honolulu, police said. Honolulu police responded to a call about shots fired just past midnight Friday and were searching Saturday for...}

\entryitemWithDescription{\hskip 0pt{}Gunmen shoot up resort in central Mexico, killing 7 people}{https://apnews.com/article/3603f74cc4fabb81ba0f7f2d231d7467}{MEXICO CITY (AP) --- A band of gunmen invaded a resort where dozens of vacationers were spending the weekend in central Mexico and opened fire, killing six adults and a 7-year-old, authorities said. Officials in the Cortazar municipality...}

\entryitemWithDescription{\hskip 0pt{}Ferry runs aground near Seattle; no injuries reported}{https://apnews.com/article/bef8a59ba80b7464241195ddd3241d05}{The ferry Walla Walla has run aground in Rich Passage near Bainbridge Island west of Seattle on Saturday, April 15, 2023. There were no immediate reports of injuries or contamination, authorities said. (Mike Reicher/The Seattle Times via...}

\entryitemWithDescription{\hskip 0pt{}Name-that-tune game Heardle dropped by Spotify after a year}{https://apnews.com/article/f0e5671beff2c8c1d03c3dd0a525caa0}{FILE - The Spotify app on an iPad is pictured, March 20, 2018, in Baltimore. Heardle, the name-that-tune game inspired by the Wordle craze, is being dropped by Spotify less than a year after the music-streaming giant acquired it. ``After...}