\entryitemWithDescription{\hskip 0pt{}In Panama, legal rights given to sea turtles, boosting the 'rights of nature' movement}{https://apnews.com/article/44cb77ff472ef99cbac7667bce51d38a}{A member of The Leatherback Project for the conservation of leatherback turtles inspects the health of hatchlings from a nest on a beach near Armila, Panama, Saturday, May 20, 2023. Sea turtles in Panama now have the legal right to live...}

\entryitemWithDescription{\hskip 0pt{}Police: Man who said he was headed to CIA arrested at nearby preschool with AK-47 rifle in car}{https://apnews.com/article/10c490dde8659292634d62b31a9d00b1}{McLEAN, Va. (AP) --- A Florida man who police say had an AK-47 rifle in his car was arrested outside a northern Virginia preschool after he told officers he was headed to CIA headquarters, police said Wednesday. Fairfax County Police said...}

\entryitemWithDescription{\hskip 0pt{}Convicted murderer and ex-attorney Alex Murdaugh facing federal charges of fraud, theft}{https://apnews.com/article/19eb36ecac8a16f92368690148f6be3e}{FILE - Alex Murdaugh speaks with his legal team before he is sentenced to two consecutive life sentences for the murder of his wife and son by Judge Clifton Newman at the Colleton County Courthouse on Friday, March 3, 2023 in in...}

\entryitemWithDescription{\hskip 0pt{}In transition from HBO Max to Max, writer and director credits got lost}{https://apnews.com/article/04ddf7d2c63ae73b589698538fb30aa3}{A picketer walks underneath a billboard highlighting Warner Bros. animated characters during a Writers Guild rally, Monday, May 22, 2023, outside Warner Bros. Studios in Burbank, Calif. (AP Photo/Chris Pizzello) Warner Bros. Discovery...}

\entryitemWithDescription{\hskip 0pt{}Rapper Fetty Wap sentenced to 6 years in prison for drug-trafficking scheme}{https://apnews.com/article/bf8a5e3ebcdb9286ec1048c747428b94}{FILE - Fetty Wap arrives at the 2016 Clive Davis Pre-Grammy Gala at the Beverly Hilton Hotel, Feb. 14, 2016, in Beverly Hills, Calif. Rapper Fetty Wap has been sentenced to six years in federal prison on Wednesday, May 24, 2023, for his...}

\entryitemWithDescription{\hskip 0pt{}NCAA survey shows 58\% of 18- to 22-year-olds are wagering; athlete-only study is set for fall}{https://apnews.com/article/79814cc17a323382a380b4e9a2589239}{FILE - Fans cheer before an NCAA college football game between Iowa and North Texas at Kinnick Stadium in Iowa City, Iowa, Sept. 16, 2017. The University of Iowa announced 26 of its athletes across five sports are alleged to have...}

\entryitemWithDescription{\hskip 0pt{}Yellowstone baby bison put to death after visitor picks it up, leading herd to reject it}{https://apnews.com/article/c52a66aeab1160df091cbec6458c4373}{FILE - A herd of bison grazes in the Lamar Valley of Yellowstone National Park on Aug. 3, 2016. Yellowstone National Park officials say they had to kill a newborn bison because its herd wouldn't take the animal back after a man picked it...}

\entryitemWithDescription{\hskip 0pt{}Authorities capture 1 inmate who escaped Ohio prison, but convicted murderer still on the lam}{https://apnews.com/article/8cbf6d97e2cc16b0851ea9f0c2c9c2c4}{This combo made from photos provided by Ohio Department of Rehabilitation and Correction shows from left, Bradley Gillespie and James Lee. One of two inmates who escaped from an Ohio prison was captured early Wednesday, May 24, 2023 in...}

\entryitemWithDescription{\hskip 0pt{}95-year-old Australian woman dies after police shoot her with stun gun; officer faces charges}{https://apnews.com/article/2fe75117912f8b26500d617ccde32104}{In this image made from video, Clare Nowland reacts following her skydive in Canberra, Australia, April 6, 2008. Nowland, now 95, was in critical condition Friday, May 19, 2023, two days after police shocked her with a stun gun as she...}

\entryitemWithDescription{\hskip 0pt{}German prosecutor says clues to McCann child disappearance possible at Portuguese dam site}{https://apnews.com/article/e0d79fcb035e20d111884dd7d2d20d25}{A police search team walk on the shore of the Arade dam near Silves, Portugal, Wednesday May 24, 2023. Portuguese police aided by German and British officers have resumed their search for Madeleine McCann, the British child who...}

\entryitemWithDescription{\hskip 0pt{}Red Sea corals threatened by mass sea urchin die-off, Israeli researchers say}{https://apnews.com/article/204cffe0a90940ecc37ab05938ea831e}{Dr. Omri Bronstein holds a sea urchin specimen of the long-spined Diadema setosum, found in the Mediterranean, at the Steinhardt Museum of Natural History of Tel Aviv University in Tel Aviv, Israel, Wednesday, May 24, 2023. Tel Aviv...}

\entryitemWithDescription{\hskip 0pt{}Sustainable till death do us part, and 45 days beyond; mushroom coffin a last best wish for some}{https://apnews.com/article/5b211105cc5566c9ada430f2e2e8e3a0}{Director Lonneke Westhoff, right, and founder Bob Hendrikx, left, of Dutch startup Loop Biotech display one of the cocoon-like coffins, grown from local mushrooms and up-cycled hemp fibres, designed to dissolve into the environment amid...}

\entryitemWithDescription{\hskip 0pt{}Brazilians protest outside Spanish consulate after Vinicius Júnior's racism row}{https://apnews.com/article/be7af35a0db3de8afe2280ef25e609e1}{People protest against racism suffered by Brazilian soccer star Vinicius Junior who plays for Spain\textquotesingle s Real Madrid, outside the Spanish Consulate in Sao Paulo, Brazil, Tuesday, May 23, 2023. Vinicius, who is Black, has been...}