\entryitemWithDescription{\hskip 0pt{}Man who threw flagpole at police during Jan. 6 riot gets more than 6 years in prison}{https://apnews.com/article/378d427e81bf5691b403579eac3bc0e0}{WASHINGTON (AP) --- A Tennessee man who wrote on social media about wanting to ``take over the Capitol building'' before the Jan. 6, 2021 riot, where he threw a flagpole at a police officer's head, was sentenced on Wednesday to more than...}

\entryitemWithDescription{\hskip 0pt{}Scientists call fraud on supposed extraterrestrials presented to Mexican Congress}{https://apnews.com/article/af7d54fabf3278ef83c39d899c457c76}{MEXICO CITY (AP) --- Supposed aliens landed in Mexico's Congress but there were no saucer-shaped UFOs hovering over the historic building or bright green invaders like those seen in Hollywood films. The specter of little green men visited...}

\entryitemWithDescription{\hskip 0pt{}After catching escaped murderer, officers took a photo with him. Experts say that was inappropriate}{https://apnews.com/article/1554042a24e1c43c35bf11b6f8d1203e}{PHILADELPHIA (AP) --- A group photo of about two dozen officers in tactical gear posing with escaped murderer Danelo Cavalcante minutes after his capture Wednesday in southeastern Pennsylvania drew criticism from policing reform advocates...}

\entryitemWithDescription{\hskip 0pt{}El Chapo's wife released from US custody after completing 3-year prison sentence}{https://apnews.com/article/b4ba4509ea9a762cfc12de39ac5ea59e}{The wife of Mexican drug kingpin Joaquin ``El Chapo'' Guzman was released from federal custody on Wednesday after completing a three-year sentence for helping him run his multibillion-dollar criminal empire, the federal Bureau of Prisons...}

\entryitemWithDescription{\hskip 0pt{}Environmental groups sue US over sluggish pace in listing the rare ghost orchid as endangered}{https://apnews.com/article/e01714a896b9b6bbc511262986b8b651}{ST. PETERSBURG, Fla. (AP) --- The rare ghost orchid found mainly in Florida and Cuba should be immediately protected by the U.S. as an endangered species, three environmental groups claimed Wednesday in a lawsuit arguing that federal...}

\entryitemWithDescription{\hskip 0pt{}Rep. Boebert escorted from Denver theater during `Beetlejuice' show}{https://apnews.com/article/01ba32a52aa332b087e881905041a318}{DENVER (AP) --- U.S. Rep. Lauren Boebert was kicked out of a ``Beetlejuice'' show in Denver on Sunday, according to security footage. The theater didn't name Boebert, but a spokesperson said Wednesday that the video --- which showed...}

\entryitemWithDescription{\hskip 0pt{}Man already charged in killing has also been indicted in a Lyft driver's slaying}{https://apnews.com/article/4d36939415b860e25d2516ba8efe5147}{BOYNTON BEACH, Fla. (AP) --- A Florida man already charged with murder has been indicted for the killing of a Lyft driver whose car he allegedly stole in an attempt to escape, authorities announced Wednesday. An Okeechobee County grand...}

\entryitemWithDescription{\hskip 0pt{}For several episodes this fall, '60 Minutes' will become 90 minutes}{https://apnews.com/article/d6d0bc6bda3f7266499af6e9ea4664e8}{NEW YORK (AP) --- The iconic stopwatch won't be reset, but for six episodes this fall, ``60 Minutes'' will become 90 minutes. The CBS newsmagazine is stretching on some Sundays when CBS airs an NFL doubleheader, starting Oct. 8. Often...}

\entryitemWithDescription{\hskip 0pt{}Husband of US Rep. Mary Peltola dies in an airplane crash in Alaska}{https://apnews.com/article/2a7bb541aae34f511395e8eebc4389b3}{ANCHORAGE, Alaska (AP) --- U.S. Rep. Mary Peltola's husband has died in an airplane crash in western Alaska, the latest fatality involving politicians or their loved ones in the nation's largest state where flights are common because of a...}

\entryitemWithDescription{\hskip 0pt{}Extortion trial against Joran van der Sloot, suspect in Natalee Holloway disappearance, is delayed}{https://apnews.com/article/c94b41503cd331860edd6d6a20a8a090}{BIRMINGHAM, Ala. (AP) --- A federal judge agreed to delay Joran van der Sloot's trial on extortion charges until later this year in order to give his defense more time to prepare. Van der Sloot, the chief suspect in the 2005 disappearance...}

\entryitemWithDescription{\hskip 0pt{}A fishing vessel in Greenland will try to free a cruise ship that ran aground with 206 people}{https://apnews.com/article/a263cbafe18bd223357501567cb7df42}{COPENHAGEN, Denmark (AP) --- A fishing vessel owned by Greenland's government will attempt to use a high tide to pull free a Bahamas-flagged luxury cruise ship carrying 206 people that ran aground in the world's northernmost national...}

\entryitemWithDescription{\hskip 0pt{}Hudson River swimmer completes 315-mile trek, conquering fatigue, choppy water, rocks and pollution}{https://apnews.com/article/2a35eaba7b371da227023b7f80d5e952}{NEW YORK (AP) --- The Hudson River snakes through forests and rushes over boulders in the Adirondack Mountains before settling into a wide, slow flow closer to New York City. It stretches 315 miles (507 kilometers) from source to end...}

\entryitemWithDescription{\hskip 0pt{}Slave descendants vow to fight on after Georgia county approves larger homes for island enclave}{https://apnews.com/article/3e08bf6e228ea2119d3469381ff5e623}{DARIEN, Ga. (AP) --- Descendants of enslaved people living on a Georgia island vowed to keep fighting Tuesday after county commissioners voted to double the maximum size of homes allowed in their tiny enclave, which residents fear will...}