\entryitemWithDescription{\hskip 0pt{}Catholic bishops in Mexico say they negotiated for possible peace accord with drug cartel leaders}{https://apnews.com/article/ae3054c5885de17229d401aae311ad5f}{MEXICO CITY (AP) --- Four Roman Catholic bishops met with Mexican drug cartel bosses in a bid to negotiate a possible peace accord, one of the bishops said, and President Andrés Manuel López Obrador said Thursday he approves of such...}

\entryitemWithDescription{\hskip 0pt{}Seven Los Angeles firefighters injured in explosion of burning truck's fuel tank}{https://apnews.com/article/893b2d2cccd34e7a6d6fb1d665cdf3df}{LOS ANGELES (AP) --- Seven Los Angeles firefighters were injured, two critically, when an explosion occurred as they responded early Thursday to a truck with pressurized cylinders that were on fire, authorities said. The explosion...}

\entryitemWithDescription{\hskip 0pt{}Ford CEO says company will rethink where it builds vehicles after last year's autoworkers strike}{https://apnews.com/article/ed580b465d99219eb02ffe24bee3d2f7}{DETROIT (AP) --- Last fall's contentious United Auto Workers' strike changed Ford's relationship with the union to the point where it will ``think carefully'' about where it builds future vehicles, Ford's top executive said Thursday. CEO...}

\entryitemWithDescription{\hskip 0pt{}Ben Affleck inspired J.Lo's first album in a decade. She's using it to poke fun at her romantic past}{https://apnews.com/article/58537461308e94dbfb06f563b6fabdb9}{LOS ANGELES (AP) --- Throughout her career, Jennifer Lopez has been hailed as an epochal, prolific and hard-working artist. One adjective not often associated with the pop icon-turned-actor and movie producer, however, is self...}

\entryitemWithDescription{\hskip 0pt{}Power outages hit Boston transit system during morning rush hour, stranding thousands}{https://apnews.com/article/5e336541e39b4c3b73b705855991af84}{BOSTON (AP) --- Thousands of commuters were left stranded around Boston Thursday during the morning rush hour, after power outages hit several lines of the beleaguered transit service. The Massachusetts Bay Transportation Authority took...}

\entryitemWithDescription{\hskip 0pt{}Caitlin Clark is on the cusp of the NCAA women's scoring record. She gets a chance to do it at home}{https://apnews.com/article/12e078352a92fe2effb307888775cdb0}{IOWA CITY, Iowa (AP) --- It shouldn't take long for Caitlin Clark to become the NCAA women's career scoring leader when No. 4 Iowa hosts Michigan. Clark goes into Thursday night's game needing eight points to pass Kelsey Plum's total of...}

\entryitemWithDescription{\hskip 0pt{}Anthony Albanese is Australia's first prime minister to get engaged in office}{https://apnews.com/article/2b1901a32cc10f283885f32b12cd5e8b}{MELBOURNE, Australia (AP) --- Anthony Albanese has become the first Australian prime minister to get engaged while in office, revealing Thursday that his partner accepted his marriage proposal on Valentine's Day. He and Jodie Haydon, a...}

\entryitemWithDescription{\hskip 0pt{}US company's lunar lander rockets toward the moon for a touchdown attempt next week}{https://apnews.com/article/84092096eadf1ec5bb4042c945cdec7e}{CAPE CANAVERAL, Fla. (AP) --- Another private U.S. company took a shot at the moon Thursday, launching a month after a rival's lunar lander missed its mark and came crashing back. NASA, the main sponsor with experiments on board, is...}

\entryitemWithDescription{\hskip 0pt{}Queen Camilla, once shunned by British public, comes to the rescue as Charles is treated for cancer}{https://apnews.com/article/327f833b80e6adab9c5873aadbf236a6}{LONDON (AP) --- What a difference a few decades can make. Queen Camilla, once seen as the scourge of the House of Windsor, the woman at the heart of King Charles III's doomed marriage to the late Princess Diana, has emerged as one of the...}

\entryitemWithDescription{\hskip 0pt{}Thom Browne closes out NY Fashion Week with a black-and-white flourish and a nod to Edgar Allan Poe}{https://apnews.com/article/e3fcadc791770108d671521e69f75491}{NEW YORK (AP) --- Thom Browne, ever the master showman of American fashion, closed out New York Fashion Week on a blustery day with his own wintry landscape, blanketing the floor with fake snow and presenting his latest inventive designs...}

\entryitemWithDescription{\hskip 0pt{}Massive landslide on coastal bluff leaves Southern California mansion on the edge of a cliff}{https://apnews.com/article/ccd4abd729306ca3e3867729fdb4956a}{DANA POINT, Calif. (AP) --- A massive landslide on a coastal bluff has left a Southern California mansion on the edge of a cliff, but authorities have determined that the ocean-view home and neighboring residences are not in immediate...}

\entryitemWithDescription{\hskip 0pt{}William Post, who played a key role in developing Pop-Tarts, dies at 96}{https://apnews.com/article/e4766c7a07d855ee60857f65d3f721cf}{GLEN ARBOR, Mich. (AP) --- William Post, a Michigan man who played an important role in the development of Pop-Tarts, has died at age 96. Post died Saturday, according to a family obituary which provided no details on his death but says...}

\entryitemWithDescription{\hskip 0pt{}Lyft shares rocket 62\% over a typo in the company's earnings release}{https://apnews.com/article/6867a202e0017d75d3631edfb8a9ba15}{Lyft shares jumped 62\% after the closing bell Tuesday thanks in part to a typo in the ride-hailing company's earnings release that appears to have sent investors' auto-trading algorithms --- or ``bots'' --- into a buying frenzy. Lyft's...}