\entryitemAp{\hskip 0pt{}Bills win for Hamlin and eliminate Patriots from playoffs}{https://apnews.com/article/25243cdf2ceb3780419859fc39537ef4}{Buffalo Bills wide receiver John Brown (16) celebrates his touchdown during the second half of an NFL football game against the New England Patriots, Sunday, Jan. 8, 2023, in Orchard Park. (AP Photo/Adrian Kraus) ORCHARD PARK, N.Y...}

\entryitemAp{\hskip 0pt{}McCarthy's next big task: Win GOP support for House rules}{https://apnews.com/article/4922d22689eb79d5d05c1b49ca733123}{Dean of the House Rep. Hal Rogers, R-Ky., swears in Rep. Kevin McCarthy, R-Calif., as House Speaker on the House floor at the U.S. Capitol in Washington, early Saturday, Jan. 7, 2023. (AP Photo/Andrew Harnik) WASHINGTON (AP) --- After an...}

\entryitemAp{\hskip 0pt{}Teacher shot by 6-year-old known as devoted to students}{https://apnews.com/article/2db4662a6d9f711c5bcd27b6142570a8}{Police respond to a shooting at Richneck Elementary School, Friday, Jan. 6, 2023 in Newport News, Va. A shooting at a Virginia elementary school sent a teacher to the hospital and ended with ``an individual'' in custody Friday, police and...}

\entryitemAp{\hskip 0pt{}Adam Rich, former 'Eight Is Enough' child star, dies at 54}{https://apnews.com/article/7294e6bf8061f6c12604c2716d34b722}{FILE - One-time child actor Adam Rich, who starred in the 1970s TV show "Eight is Enough," walks out of a sheriff\textquotesingle s station after posting bail in City of Industry, Calif., Dec. 18, 2002. Rich, the child actor with a...}

\entryitemAp{\hskip 0pt{}Pro-Bolsonaro rioters storm Brazil's top government offices}{https://apnews.com/article/0c03c098a5e2a09ac534412c30ae8355}{Protesters, supporters of Brazil\textquotesingle s former President Jair Bolsonaro, sit in front of police after inside Planalto Palace after storming it, in Brasilia, Brazil, Sunday, Jan. 8, 2023. Planalto is the official workplace of...}

\entryitemAp{\hskip 0pt{}Hamlin in mind, Bills return to action with first-play TD}{https://apnews.com/article/47dc11b56ec33560542cd3847db4de45}{Buffalo Bills running back Taiwan Jones (25) kneels in prayer for safety Damar Hamlin before an NFL football game against the New England Patriots, Sunday, Jan. 8, 2023, in Orchard Park, N.Y. Hamlin remains hospitalized after suffering a...}

\entryitemAp{\hskip 0pt{}Russell Banks, praised author of 'Cloudsplitter,' dies at 82}{https://apnews.com/article/bcec4ba2e2ea96f08341a95555241dcb}{FILE - Russell Banks, author of "Cloudsplitter," delivers a keynote address during the Hemingway \& Winship Awards ceremony at John F. Kennedy Library and Museum in Boston, April, 4, 2004. Banks, an award-winning fiction writer who rooted...}

\entryitemAp{\hskip 0pt{}Alabama woman who joined IS hopes to return from Syria camp}{https://apnews.com/article/dfb3cde1330e15b69a4c18552c837664}{In this image taken from video Hoda Muthana talks during an interview in Roj detention camp in Syria where she is being held by U.S.-allied Kurdish forces, Wednesday, Nov. 9, 2022. Muthana, who ran away from home in Alabama at the age of...}

\entryitemAp{\hskip 0pt{}CES 2023: Smelling, touching take center stage in metaverse}{https://apnews.com/article/c9de16360932e6a1fa7c4dcc8f86832c}{Attendees wear VR headsets while previewing the Caliverse Hyper-Realistic Metaverse experience at the Lotte booth during the CES tech show Friday, Jan. 6, 2023, in Las Vegas. (AP Photo/John Locher) LAS VEGAS (AP) --- Is the metaverse...}

\entryitemAp{\hskip 0pt{}'The money is gone': Bahamas tries to turn page after FTX}{https://apnews.com/article/7de9ee0db46b532b3609a26572e31853}{Bishop Lawrence Rolle performs in front of children and adults at Mt. Carmel Preparatory Academy in Nassau, Bahamas on Thursday, Dec. 8, 2022. Rolle\textquotesingle s ministry received \$50,000 from FTX in early 2022, one of several...}

\entryitemAp{\hskip 0pt{}Russia claims deadly attack, but Kyiv denies anyone killed}{https://apnews.com/article/46a8599f1fa971b8c773af2745326540}{"Sirko", a Ukrainian serviceman of Karpatska Sich battalion tests his AK-74 rifle near the recently retaken town of Lyman, Ukraine, Sunday, Jan. 8, 2023. (AP Photo/Evgeniy Maloletka) KYIV, Ukraine (AP) --- The Russian military claimed...}

\entryitemAp{\hskip 0pt{}Ukrainians honor dead fighter at outdoor funeral in capital}{https://apnews.com/article/1389e0bc90800ce033d344b0bc69bff9}{Ukrainian servicemen pay their last respect at the coffin of their comrade Oleh Yurchenko killed in a battlefield with Russian forces in the Donetsk region during a commemoration ceremony in Independence Square in Kyiv, Ukraine, Sunday...}

\entryitemAp{\hskip 0pt{}State lawmakers turn to creative solutions in speaker fights}{https://apnews.com/article/3e8b547b85fdc3bdeac2d6b13c6bd1bc}{Pennsylvania Speaker of the House Mark Rozzi is photographed at the speaker\textquotesingle s podium, Jan. 3, 2023, at the state Capitol in Harrisburg, Pa. When lawmakers convened to take oaths of office and pick a speaker, a deadlock was...}

\entryitemAp{\hskip 0pt{}Conservatives take aim at tenure for university professors}{https://apnews.com/article/4f0fe0c5c18ed227fabae3744e8ff51d}{Max McCoy, the lone journalism professor at Emporia State University, poses for a photo in front of the school\textquotesingle s administration building Wednesday, Jan. 4, 2023, in Emporia, Kan. McCoy was was one of 33 mostly tenured...}

\entryitemAp{\hskip 0pt{}France's Macron opens up about love to autistic interviewers}{https://apnews.com/article/78d06e0f91c1085f706f87768c5fe885}{FILE. French President Emmanuel Macron and his wife Brigitte Macron attend a national memorial ceremony for Hubert Germain at the Hotel des Invalides, Friday Oct.15, 2021 in Paris. A group of "atypical journalists," on the autism...}

\entryitemAp{\hskip 0pt{}Prince Harry interviews set to raise heat on UK royal family}{https://apnews.com/article/7082bf624e4b43826d0cc39ce69f961f}{This undated screengrab issued by ITV on Friday Jan. 6, 2023 shows Britain\textquotesingle s Prince Harry, left, speaking during an interview with ITV\textquotesingle s Tom Bradby for the programme Harry: The Interview. (Harry: The...}

\entryitemAp{\hskip 0pt{}Boebert's backers urge her to 'tone down the nasty rhetoric'}{https://apnews.com/article/548e31f15bcbd1929cfe25975c200421}{Larry Clark talks outside a supply store on Friday, Dec. 30, 2022, in Grand Junction, Colo. (AP Photo/Jesse Bedayn) RIFLE, Colo. (AP) --- Debbie Hartman voted for Lauren Boebert for Congress in 2020 and again in 2022, delighted by Boebert...}

\entryitemAp{\hskip 0pt{}40 people killed, dozens injured in bus crash in Senegal}{https://apnews.com/article/d04f6550211d40dbf7cbfb07ace108a8}{Two damaged buses are pictured after they collided on a road in Gniby, Senegal, Sunday Jan. 8, 2023. At least 40 people were killed and dozens injured in this bus crash in central Senegal, the country\textquotesingle s president Macky...}

\entryitemAp{\hskip 0pt{}Biden walks stretch of US-Mexico border, amid GOP criticism}{https://apnews.com/article/2e30ea26bbc55c7af509a6e60ad3d33c}{President Joe Biden, second from left, looks towards a large "Welcome to Mexico" sign that is hung over the Bridge of the Americas as he tours the El Paso port of entry a busy port of entry along the U.S.-Mexico border, in El Paso Texas...}

\entryitemAp{\hskip 0pt{}Israel revokes Palestinian FM's travel permit over UN move}{https://apnews.com/article/91ba538476380a16aad4e2cbdae2e235}{Israeli Prime Minister Benjamin Netanyahu convenes a weekly cabinet meeting at the Prime Minister\textquotesingle s office in Jerusalem, Sunday, Jan. 8, 2023. (Ronen Zvulun/Pool Photo via AP) JERUSALEM (AP) --- Israel on Sunday revoked...}

\entryitemAp{\hskip 0pt{}Shiffrin shows her emotions after matching Vonn's record}{https://apnews.com/article/aa16eabb472c4d020dce712ba18530f3}{United States\textquotesingle{} Mikaela Shiffrin is overcome by emotion as she stands on the podium after winning an alpine ski, women\textquotesingle s World Cup giant slalom race, in Kranjska Gora, Slovenia, Sunday, Jan. 8, 2023...}

\entryitemAp{\hskip 0pt{}Public now can see Benedict's tomb at St. Peter's Basilica}{https://apnews.com/article/9e77ccb8c66b4566666e6f0172cff249}{Faithful visit the tomb of late Pope Emeritus Benedict XVI inside the grottos of St. Peter\textquotesingle s Basilica, at the Vatican, Sunday, Jan. 8, 2023. Benedict died at 95 on Dec. 31 in the monastery on the Vatican grounds where he...}

\entryitemAp{\hskip 0pt{}Germany: Iranians held in suspected poison plot after US tip}{https://apnews.com/article/60f78b43bcb21e6aa8b4e43976ec4cb5}{Substances found during the search are examined on the premises of the fire department in Castrop-Rauxel, Sunday, Jan.8, 2023. In Castrop-Rauxel, there was a large-scale operation by the police and fire department on Saturday evening. A...}

\entryitemAp{\hskip 0pt{}AP PHOTOS: Bear costumes, dance at popular Romanian festival}{https://apnews.com/article/ed6285cb85299947a7ccc6ab3931e1c1}{People wearing bear fur costumes prepare to take part in a parade showcasing regional winter traditions in Comanesti, northeastern Romania, Friday, Dec. 30, 2022. Centuries ago, people in what is now northeast Romania would don bear fur...}

\entryitemAp{\hskip 0pt{}Jags return fumble for TD, beat Titans for AFC South title}{https://apnews.com/article/245237965ff4389a7d33ce3e58732333}{Jacksonville Jaguars linebacker Josh Allen (41) returns a fumble for a touchdown as defensive end Arden Key (49) covers in the second half of an NFL football game against the Tennessee Titans, Saturday, Jan. 7, 2023, in Jacksonville...}

\entryitemAp{\hskip 0pt{}Seattle schools sue tech giants over social media harm}{https://apnews.com/article/965a8f373e3bfed8157571912cc3b542}{This combination of 2017-2022 photos shows the logos of Facebook, YouTube, TikTok and Snapchat on mobile devices. On Friday, Jan. 6, 2023, Seattle Public Schools filed a lawsuit in U.S. District Court, suing the tech giants behind TikTok...}

\entryitemAp{\hskip 0pt{}Travelers rush to take advantage of China reopening}{https://apnews.com/article/49e31dedb78fd24c1077b340ebdafa1f}{A woman holding a bouquet of flowers reacts with her relatives surrounded by journalists as she arrives from Hong Kong, at Terminal 3 international arrival hall of the Beijing Capital International Airport in Beijing, Sunday, Jan. 8...}

\entryitemAp{\hskip 0pt{}Mahomes sets record, Chiefs beat Raiders for AFC's top seed}{https://apnews.com/article/5d08f366a1e2319104eb54ce22a570d2}{Kansas City Chiefs quarterback Patrick Mahomes runs with the ball against the Las Vegas Raiders during the first half of an NFL football game Saturday, Jan. 7, 2023, in Las Vegas. (AP Photo/John Locher) LAS VEGAS (AP) --- The Kansas City...}

\entryitemAp{\hskip 0pt{}Subway train collision in Mexico City kills 1, injures 57}{https://apnews.com/article/5f604dfae19afaef940260065cd43e69}{A subway passenger, injured when two subway trains collided, is taken on a stretcher to a waiting ambulance, outside the Raza station in Mexico City, Saturday, Jan. 7, 2023. Authorities announced at least one person was killed and dozens...}

\entryitemAp{\hskip 0pt{}Speaker McCarthy: A weakened leader or emboldened survivor?}{https://apnews.com/article/e986c620149b72030bb418bd5fadb4a2}{House Speaker Kevin McCarthy of Calif., gestures towards the newly installed nameplate at his office after he was sworn in as speaker of the 118th Congress in Washington, early Saturday, Jan. 7, 2023. (AP Photo/ Matt Rourke) House Speaker...}

\entryitemAp{\hskip 0pt{}Golden Globes are back on TV, but are reform efforts enough?}{https://apnews.com/article/9ee1a25e378b0c707dcd1f5f205c405b}{FILE - Event signage appears above the red carpet at the 77th annual Golden Globe Awards on Jan. 5, 2020, in Beverly Hills, Calif. The 80th annual Golden Globe Awards will take place on Tuesday, Jan. 10. (Photo by Jordan Strauss/Invision/...}

\entryitemAp{\hskip 0pt{}Drugstores make slow headway on staffing problems}{https://apnews.com/article/7aa39f8227449cc3b4e1bd2d3b130716}{Jessi Stout, owner of the Table Rock Pharmacy fills a prescription on Friday, Jan. 6, 2023, in Morganton, N.C. Drugstore chains are still trying to find enough employees to put a stop to temporary pharmacy closures. (AP Photo/Chris...}

\entryitemAp{\hskip 0pt{}Mayor: Teacher shot by 6-year-old 'red flag for the country'}{https://apnews.com/article/38beb789647975e2f8f0d7c7447eb777}{Students and police gather outside of Richneck Elementary School after a shooting, Friday, Jan. 6, 2023 in Newport News, Va. A shooting at a Virginia elementary school sent a teacher to the hospital and ended with ``an individual'' in...}

\entryitemAp{\hskip 0pt{}UK palace allies push back against Prince Harry's claims}{https://apnews.com/article/952c0cbaa0c39d18b8338ca651b49394}{This undated screengrab issued by ITV on Friday Jan. 6, 2023 shows Britain\textquotesingle s Prince Harry speaking during an interview with ITV\textquotesingle s Tom Bradby for the programme Harry: The Interview. (Harry: The Interview on...}

\entryitemAp{\hskip 0pt{}W.Va. journalist let go after reporting on abuse allegations}{https://apnews.com/article/af942f587d098b2d996cc6e01991d615}{This undated photo shows former West Virginia Public Broadcasting reporter Amelia Ferrell Knisely. Knisely was let go from her job at WVPB on Dec. 20, 2022, after she wrote about the alleged abuse of people with disabilities at the West...}

\entryitemAp{\hskip 0pt{}A first for reclaimed Kyiv cathedral: Christmas in Ukrainian}{https://apnews.com/article/9bea8791e5eda36a0b01cb3b6da86bd5}{Metropolitan Epiphanius, center right, and priests deliver an Orthodox Christmas service inside the nearly 1,000-year-old Pechersk Lavra Cathedral of Kyiv, Ukraine, Saturday, Jan. 7, 2023. Hundreds of Ukrainians heard the Orthodox...}

\entryitemAp{\hskip 0pt{}Big week for US-Mexico ties going into North American summit}{https://apnews.com/article/599d640834d079503c5dd568c312c19f}{FILE - President Joe Biden speaks as he meets with Mexican President Andrés Manuel López Obrador in the Oval Office of the White House in Washington, July 12, 2022. Biden will become the first U.S. leader to visit Mexico in nearly a...}

\entryitemAp{\hskip 0pt{}EXPLAINER: New drug slows Alzheimer's but comes with caveats}{https://apnews.com/article/b42dc8b32d71f1b6892b07d85e0e7da0}{U.S. health officials have approved a new Alzheimer's drug that modestly slows the brain-robbing disease. (Jan. 6) This Dec. 21, 2022 image provided by Eisai in January 2023, shows vials and packaging for their medication Leqembi. On...}

\entryitemAp{\hskip 0pt{}States target transgender health care in first bills of 2023}{https://apnews.com/article/878a9217fa434f3ecd83738a71e40572}{FILE - The Utah State Capitol is shown on Feb. 1, 2022, in Salt Lake City. After a midterm election and record flow of anti-transgender legislation in 2022, Republican state lawmakers this year are zeroing in on questions of bodily...}

\entryitemAp{\hskip 0pt{}Ukraine hails US military aid as cease-fire said to falter}{https://apnews.com/article/9b3a132b330c90a10e8f031113be241b}{A cupola lies on the ground in front of the Orthodox Church which was destroyed by Russian forces in the recently retaken village of Bogorodychne, Ukraine, Saturday, Jan. 7, 2022. (AP Photo/Evgeniy Maloletka) KYIV, Ukraine (AP...}

\entryitemAp{\hskip 0pt{}AP PHOTOS: Snow is a no-show as Europe feels the winter heat}{https://apnews.com/article/ac556a03360f361496aefb1c3a6569b6}{FILE - People ski on a cross country slope in Ramsau, Austria, Friday, Jan. 6, 2023. Sparse snowfall and unseasonably warm weather in much of Europe is allowing green grass to blanket many mountaintops across the region where snow might...}

\entryitemAp{\hskip 0pt{}Chaos in the House: McCarthy's plea, and begging for votes}{https://apnews.com/article/f2a4a42b4845f2413cca5c1b4c6100dd}{Rep. Richard Hudson, R-N.C., left, pulls Rep. Mike Rogers, R-Ala., back as they talk with Rep. Matt Gaetz, R-Fla., and others during the 14th round of voting for speaker as the House meets for the fourth day to try and elect a speaker and...}

\entryitemAp{\hskip 0pt{}Utah murder-suicide underscores frequency of family killings}{https://apnews.com/article/1e17fba2d7966f7436de96ddc974e530}{Jess, left, sits next to her sister, Cecily, during a press conference regarding the killing of a family in Enoch, Utah on Thursday, Jan. 5, 2023. A Utah man fatally shot his five children, his mother-in-law and his wife, then killed...}

\entryitemAp{\hskip 0pt{}Iran executes 2 more men detained amid nationwide protests}{https://apnews.com/article/f8a6e331d2e47077d44e9ab6f8c62c3a}{FILE - Women protest the death of 22-year-old woman Mahsa Amini who was detained by the morality police, in Tehran, Saturday, Oct. 1, 2022. in this photo taken by an individual not employed by the Associated Press and obtained by the AP...}

\entryitemAp{\hskip 0pt{}Mexican capo's arrest a gesture to US, not signal of change}{https://apnews.com/article/c4b7625503207540c2e821d8bf0e3ca6}{Army soldiers drive past a destroyed vehicle on the streets of Jesus Maria, Mexico, on Saturday, Jan. 7, 2023, the small town where Ovidio Guzman was detained earlier in the week. Thursday\textquotesingle s government operation to detain...}

\entryitemAp{\hskip 0pt{}China suspends social media accounts of COVID policy critics}{https://apnews.com/article/3259cdf2fb41e8dd3d64f6c6d3b7cc80}{A man wearing a face mask shops for Chinese Lunar New Year decorations at a pavement store in Beijing, Saturday, Jan. 7, 2023. China has suspended or closed the social media accounts of more than 1,000 critics of the government...}

\entryitemAp{\hskip 0pt{}Police: 6-year-old shoots teacher in Virginia classroom}{https://apnews.com/article/88dfe91f65173cbbd198a8816a21b5be}{Police respond to a shooting at Richneck Elementary School, Friday, Jan. 6, 2023 in Newport News, Va. A shooting at a Virginia elementary school sent a teacher to the hospital and ended with ``an individual'' in custody Friday, police and...}

\entryitemAp{\hskip 0pt{}Bills' Hamlin breathing on his own, joins team via video}{https://apnews.com/article/b1edba1849b580c3cd9ec2ea39a85d1e}{FILE - Buffalo Bills Damar Hamlin with his helmet off before playing the Los Angeles Rams during an NFL football game, Sept. 8, 2021, in Inglewood, Calif. The scenes of Hamlin\textquotesingle s on-field collapse after suffering cardiac...}

\entryitemAp{\hskip 0pt{}McCarthy elected House speaker in rowdy post-midnight vote}{https://apnews.com/article/0938c7358f41c83759246f8949ac7c15}{Rep. Kevin McCarthy, R-Calif., reacts during the 12th round of voting for speaker in the House chamber as the House meets for the fourth day to elect a speaker and convene the 118th Congress in Washington, Friday, Jan. 6, 2023. (AP Photo/...}

\entryitemAp{\hskip 0pt{}The Year of the Slap: Pop culture moments in 2022}{https://apnews.com/article/6112da82e4b05559f3c67ce1970c15cf}{Taylor Swift was up. Elon Musk was in, out, in and maybe out again. Tom Cruise was back. BTS stepped aside, and so did Serena Williams, and Tom Brady too --- oops, scratch that. But the slap? The slap was everywhere. Ok, so maybe it wasn'...}