\entryitemWithDescription{\hskip 0pt{}MLB opening day offers clocks, shift bans, Ohtani and Judge}{https://apnews.com/article/9bd214d4623d44d59584dd93516189e4}{Los Angeles Angels\textquotesingle{} Shohei Ohtani runs to first as he flies out during the sixth inning of a preseason baseball game against the Los Angeles Dodgers Sunday, March 26, 2023, in Los Angeles. (AP Photo/Mark J. Terrill) A...}

\entryitemWithDescription{\hskip 0pt{}Remembrances, calls for reform at Irvo Otieno's funeral}{https://apnews.com/article/6d8ad78381b751ecb739d69a0ceceaa7}{FILE - This undated photo provided by Ben Crump Law shows Irvo Otieno. The Rev. Al Sharpton\textquotesingle s National Action Network, a civil rights organization, announced Sharpton will deliver a eulogy in the Wednesday, March 29, 2023...}

\entryitemWithDescription{\hskip 0pt{}Children lost in shooting were 'feisty,' a 'shining light'}{https://apnews.com/article/75c11745c54edb9691f3d41455de11c5}{An an entry to Covenant School has become a memorial for shooting victims, Tuesday, March 28, 2023, in Nashville, Tenn. (AP Photo/John Amis) NASHVILLE (AP) --- Details from the rich, full lives of the three adults killed Monday at a...}

\entryitemWithDescription{\hskip 0pt{}Trump grand jury poised to take pre-planned break from case}{https://apnews.com/article/5b3739234786a5a660da6cb5b5ed4d60}{Former President Donald Trump listens as he speaks with reporters while in flight on his plane after a campaign rally at Waco Regional Airport, in Waco, Texas, Saturday, March 25, 2023, while en route to West Palm Beach, Fla. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}Dangerous storms, tornadoes may target Midwest, South}{https://apnews.com/article/4f96e0d296f794cbcf6050646fe17a7a}{FILE - A man, top center, salvages a jacket as he looks over a tornado damaged home, March 26, 2023, in Rolling Fork, Miss. An unusual weather pattern has set in, triggering the devastating tornado that hit Rolling Fork, and...}

\entryitemWithDescription{\hskip 0pt{}First lady, Sheryl Crow expected at Nashville shooting vigil}{https://apnews.com/article/3dfb2fcbb22ff8638074fd90c7b266fd}{People pray during a community vigil held for the people killed during the Covenant School shooting on Tuesday, March 28, 2023, in Mt. Juliet, Tenn. (Andrew Nelles/The Tennessean via AP) NASHVILLE, Tenn. (AP) --- First lady Jill Biden and...}

\entryitemWithDescription{\hskip 0pt{}GOP lawmakers override veto of transgender bill in Kentucky}{https://apnews.com/article/e7c0bfb0e6cdfb1144451efe677108d6}{A woman holds up a sign in protest of Kentucky Senate bill SB150, known as the Transgender Health Bill, during a rally on the lawn of the Kentucky State Capitol in Frankfort, Ky., Wednesday, March 29, 2023. (AP Photo/Timothy D. Easley...}

\entryitemWithDescription{\hskip 0pt{}Musk, scientists call for halt to AI race sparked by ChatGPT}{https://apnews.com/article/534f0298d6304687ed080a5119a69962}{FILE - The OpenAI logo is seen on a mobile phone in front of a computer screen displaying output from ChatGPT, Tuesday, March 21, 2023, in Boston. Are tech companies moving too fast in rolling out powerful artificial intelligence...}

\entryitemWithDescription{\hskip 0pt{}Latest storm piles more snow on California mountains}{https://apnews.com/article/6a3ad89d3118b772d102415796cd80fe}{In this aerial drone image provided by Mammoth Mountain, the ski resort is covered with snow in Mammoth Lakes, Calif., on March 16, 2023. The Mammoth Mountain ski resort in the Eastern Sierra said this has been its snowiest season on...}

\entryitemWithDescription{\hskip 0pt{}A different March Madness: Online hate for the athletes}{https://apnews.com/article/303beb37af19a3d2586db762b7a9a79e}{FILE - Michigan\textquotesingle s Terrance Williams II reacts during an NCAA basketball game between Michigan Wolverines and Kentucky Wildcats at the O2 Arena, in London, Sunday, Dec.4, 2022. The toxic cauldron on social media is one of...}

\entryitemWithDescription{\hskip 0pt{}Capitol riot: FBI informant testifies for Proud Boys defense}{https://apnews.com/article/3324d58c9f7ba9b3c2f4b2fe7743c920}{FILE - Proud Boys leader Henry "Enrique" Tarrio wears a hat that says The War Boys during a rally in Portland, Ore., Sept. 26, 2020. Federal prosecutors have rested their seditious conspiracy case against former Proud Boys leader Enrique...}

\entryitemWithDescription{\hskip 0pt{}Permit to buy handgun no longer required in North Carolina}{https://apnews.com/article/b9d0ee55bf658ca72043bd3f706b128f}{FILE - North Carolina House Speaker Tim Moore speaks in front of the Supreme Court in Washington, Dec. 7, 2022. North Carolina legislators repealed on Wednesday, March 29, 2023, the state's requirement that someone obtain a permit from a...}

\entryitemWithDescription{\hskip 0pt{}Pope Francis hospitalized with respiratory infection}{https://apnews.com/article/1b743492e19762ac4a71cefb556967d0}{Pope Francis hugs a child at the end of his weekly general audience in St. Peter\textquotesingle s Square, at the Vatican, Wednesday, March 29, 2023. (AP Photo/Alessandra Tarantino) VATICAN CITY (AP) --- Pope Francis was hospitalized with...}