\entryitemWithDescription{\hskip 0pt{}Mandisa, Grammy-winning singer and `American Idol' alum, dies at 47}{https://apnews.com/article/4b7ebbcb2b9499c429362de7f7329392}{NASHVILLE, Tenn. (AP) --- Mandisa, a contemporary Christian singer who appeared on ``American Idol'' and won a Grammy for her 2013 album `Overcomer', has died. She was 47. A representative for the singer told The Associated Press that the...}

\entryitemWithDescription{\hskip 0pt{}Catholic priest resigns from Michigan church following protests over his criticism of a gay author}{https://apnews.com/article/2033306cd8937b584a6f1f1c8e70d104}{BEAL CITY, Mich. (AP) --- A Catholic priest has resigned as pastor of a church in a small central Michigan community, the result of weeks of controversy following his publicly expressed regret that a gay author had read a book to...}

\entryitemWithDescription{\hskip 0pt{}Dick Van Dyke earns historic Daytime Emmy nomination at age 98}{https://apnews.com/article/ebba73bcb43c97a9e35b355fa21aa9f6}{LOS ANGELES (AP) --- Dick Van Dyke is vying for a historic Daytime Emmy at age 98. The actor was nominated Friday as guest performer in a daytime drama series for his part as amnesiac Timothy Robicheaux on Peacock's ``Days of Our Lives.''...}

\entryitemWithDescription{\hskip 0pt{}FAA investigating after it says a flight told to cross a runway where another was starting takeoff}{https://apnews.com/article/7eb1e99fdb209d79e3607b58d5e22f1c}{ARLINGTON, Va. (AP) --- The Federal Aviation Administration will investigate after a flight at Ronald Reagan Washington National Airport was instructed to cross a runway where another flight was starting its takeoff, the agency said. A...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift drops 15 new songs on double album, `The Tortured Poets Department: The Anthology'}{https://apnews.com/article/861e98f6074543899159837e3d826a64}{NEW YORK (AP) --- Could there be a Taylor Swift new album rollout without a few additional surprises? No. On Friday, the pop star released her 11th album, ``The Tortured Poets Department,'' an amalgamation of her previous work and...}

\entryitemWithDescription{\hskip 0pt{}Tesla recalling more than 3,000 of its 2024 Cybertrucks due to faulty pedal}{https://apnews.com/article/ff2018b672b1109543c52b0058698499}{Tesla is recalling more than 3,000 of its newly launched 2024 Cybertrucks because of the possibility that a pedal can get stuck and cause the vehicle to accelerate unintentionally, increasing the risk of a crash. Tesla said that the...}

\entryitemWithDescription{\hskip 0pt{}Firefighters to tackle scaffolding dangling outside ruins of fire-ravaged Danish landmark}{https://apnews.com/article/8772dbcf04a1a5aa33d9739076fb9478}{COPENHAGEN, Denmark (AP) --- Firefighters in Copenhagen plan to start taking down scaffolding that is left dangling dangerously Friday outside the ruins of the Danish capital's historic Old Stock Exchange building after a fire tore...}

\entryitemWithDescription{\hskip 0pt{}Finding an apartment may be easier for California pet owners under new legislation}{https://apnews.com/article/8192518ccec2397cdbafcd6df09d8228}{SACRAMENTO, Calif. (AP) --- California pet owners struggling to find a rental that accepts their furry, four-legged family members could have an easier time leasing new housing under proposed state legislation that would ban blanket no...}

\entryitemWithDescription{\hskip 0pt{}Reality TV's Chrisleys are appealing their bank fraud and tax evasion convictions in federal court}{https://apnews.com/article/8f76505e15cceca1c9747087ae01bec4}{ATLANTA (AP) --- Reality TV stars Todd and Julie Chrisley, who are in prison after being convicted on federal charges of bank fraud and tax evasion, are challenging aspects of their convictions and sentences in a federal appeals court...}

\entryitemWithDescription{\hskip 0pt{}Music Review: Taylor Swift's `The Tortured Poets Department' is great sad pop, meditative theater}{https://apnews.com/article/b24d2275df5cf78ffa9069c61b9825ec}{Who knew what Taylor Swift's latest era would bring? Or even what it would sound like? Would it build off the moodiness of ``Midnights'' or the folk of ``evermore''? The country or the `80s pop of her latest re-records? Or its two...}

\entryitemWithDescription{\hskip 0pt{}Coyotes officially leaving Arizona for Salt Lake City following approval of sale to Utah Jazz owners}{https://apnews.com/article/f847c9206632db191463128b01347857}{TEMPE, Ariz. (AP) --- The Arizona Coyotes are officially headed to Salt Lake City. The NHL Board of Governors voted unanimously Thursday to approve a \$1.2 billion sale from Alex Meruelo to Utah Jazz owners Ryan and Ashley Smith, clearing...}

\entryitemWithDescription{\hskip 0pt{}Britain's Prince Harry formally confirms he is now a US resident}{https://apnews.com/article/5bad226e20fede037b5ce836cb1e6a60}{LONDON (AP) --- Prince Harry, the son of King Charles III and fifth in line to the British throne, has formally confirmed he is now a U.S. resident. Four years after Harry and his American wife, Meghan, the Duchess of Sussex, decamped to...}

\entryitemWithDescription{\hskip 0pt{}An earthquake measuring 5.6 hits central Turkey. No immediate reports of casualties or damage}{https://apnews.com/article/0ac3a839ba943925c6a576834ae7bcc4}{ANKARA, Turkey (AP) --- A moderately-strong earthquake struck central Turkey on Thursday, the country's disaster management agency said. It was not immediately clear if it caused any casualties or damage. The magnitude 5.6 earthquake...}