


\ipart{Developers}
\ichapter{Hacker News}
\entryitemTwoLinks{Why did Phreesia share my medical data after I opted out?}{https://news.ycombinator.com/item?id=35484978}{https://www.statnews.com/2023/04/07/medical-data-privacy-phreesia/}

\entryitemTwoLinks{Ask Wirecutter: Can you recommend a not-smart TV for me?}{https://news.ycombinator.com/item?id=35484594}{https://www.nytimes.com/wirecutter/blog/ask-wirecutter-dumb-tvs/}

\entryitemTwoLinks{Yann LeCun and Andrew Ng: Why the 6-Month AI Pause Is a Bad Idea [video]}{https://news.ycombinator.com/item?id=35484093}{https://www.youtube.com/watch?v=BY9KV8uCtj4}

\entryitemTwoLinks{We need to tell people ChatGPT will lie to them, not debate linguistics}{https://news.ycombinator.com/item?id=35483823}{https://simonwillison.net/2023/Apr/7/chatgpt-lies/}

\entryitemTwoLinks{The machines of Tatjana van Vark}{https://news.ycombinator.com/item?id=35483539}{https://craftsmanshipmuseum.com/artisan/tatjana-van-vark/}

\entryitemTwoLinks{Show HN: Building musical synthesizers with SQL queries}{https://news.ycombinator.com/item?id=35482636}{https://github.com/ClickHouse/NoiSQL}

\entryitemTwoLinks{Twitter won't allow retweeting tweets linking to Substack}{https://news.ycombinator.com/item?id=35482222}{https://arstechnica.com/tech-policy/2023/04/the-dumb-reason-twitter-wont-allow-retweeting-tweets-linking-to-substack/}

\entryitemTwoLinks{SpaceX closing in on first Starship Super Heavy launch}{https://news.ycombinator.com/item?id=35481775}{https://spacenews.com/spacex-closing-in-on-first-starship-super-heavy-launch/}

\entryitemTwoLinks{U.S. and China wage war beneath the waves over internet cables}{https://news.ycombinator.com/item?id=35481712}{https://www.reuters.com/investigates/special-report/us-china-tech-cables/}

\entryitemTwoLinks{Flipper Zero banned by Amazon for being a `card skimming device'}{https://news.ycombinator.com/item?id=35481580}{https://www.bleepingcomputer.com/news/technology/flipper-zero-banned-by-amazon-for-being-a-card-skimming-device-/}

\entryitemTwoLinks{NSA created online cybersecurity course with 100s of classes}{https://news.ycombinator.com/item?id=35481456}{https://clark.center/c/nccp}

\entryitemTwoLinks{Perennial rice: Plant once, harvest again and again}{https://news.ycombinator.com/item?id=35481409}{https://www.npr.org/2023/03/23/1165680024/perennial-rice-plant-once-harvest-again-and-again}

\entryitemTwoLinks{The longest straight line in Great Britain without crossing a public road}{https://news.ycombinator.com/item?id=35481380}{http://www.statsmapsnpix.com/2023/04/the-longest-straight-line-in-great.html}

\entryitemTwoLinks{Big Ball of Mud (1999)}{https://news.ycombinator.com/item?id=35481309}{http://www.laputan.org/mud/}

\entryitemTwoLinks{Neovim 0.9}{https://news.ycombinator.com/item?id=35480629}{https://github.com/neovim/neovim/commit/040f1459849ab05b04f6bb1e77b3def16b4c2f2b}

\entryitemTwoLinks{Codeberg – Fast open source alternative to GitHub}{https://news.ycombinator.com/item?id=35480056}{https://codeberg.org/}

\entryitemTwoLinks{Ask HN: What's your best resource for keeping up-to-date on AI developments?}{https://news.ycombinator.com/item?id=35479853}{https://news.ycombinator.com/item?id=35479853}

\entryitemTwoLinks{Database ``sharding'' came from Ultima Online?}{https://news.ycombinator.com/item?id=35479553}{https://www.raphkoster.com/2009/01/08/database-sharding-came-from-uo/}

\entryitemTwoLinks{JavaScript-algorithms: Algorithms and data structures implemented in JavaScript}{https://news.ycombinator.com/item?id=35479378}{https://github.com/trekhleb/javascript-algorithms}

\entryitemTwoLinks{Building GitHub with Ruby on Rails}{https://news.ycombinator.com/item?id=35478884}{https://github.blog/2023-04-06-building-github-with-ruby-and-rails/}\ichapter{Phoronix}
\entryitemGeneric{\hskip 0pt{}Mesa 23.0.2 Released With Dozens Of Fixes}{https://www.phoronix.com/news/Mesa-23.0.2-Released}

\entryitemGeneric{\hskip 0pt{}System76 Making COSMIC Improvements To Their Launcher, Better Performance}{https://www.phoronix.com/news/System76-COSMIC-Spring-2023}

\entryitemGeneric{\hskip 0pt{}Rust Support Is Being Worked On For The Linux Kernel's V4L2/Media Subsystem}{https://www.phoronix.com/news/Rust-V4L2-Linux-Patches}

\entryitemGeneric{\hskip 0pt{}AMD Instinct MI300 "GFX940" Support Merged To Mesa 23.1}{https://www.phoronix.com/news/AMD-MI300-GFX940-Mesa}

\entryitemGeneric{\hskip 0pt{}Intel AMX-COMPLEX Support Added To GNU Binutils}{https://www.phoronix.com/news/Intel-AMX-COMPLEX-GNU-Binutils}

\entryitemGeneric{\hskip 0pt{}Intel oneAPI 2023.1 Released}{https://www.phoronix.com/news/Intel-oneAPI-2023.1}

\entryitemGeneric{\hskip 0pt{}Hangover 0.8.5 Released For Running Windows Apps/Games With Wine On AArch64/POWER}{https://www.phoronix.com/news/Wine-Hangover-0.8.5}

\entryitemGeneric{\hskip 0pt{}Intel Linux Optimizations Help AMD EPYC "Genoa" Improve Scaling To 384 Threads}{https://www.phoronix.com/review/amd-epyc-scaling-384}

\entryitemGeneric{\hskip 0pt{}Free Software Foundation Certifies A \$99 Mini VPN Router}{https://www.phoronix.com/news/FSF-RYF-TPE-R1400}\ichapter{GitHub}
\entryitemWithDescription{\hskip 0pt{}iDvel/rime-ice}{https://github.com/iDvel/rime-ice}{Rime 配置：雾凇拼音 \textbar{} 长期维护的简体词库\\
Language: Go\\
Stars: 2495\\
Forks: 181}

\entryitemWithDescription{\hskip 0pt{}vcheckzen/KeepAliveE5}{https://github.com/vcheckzen/KeepAliveE5}{null\\
Language: Shell\\
Stars: 1082\\
Forks: 296}

\entryitemWithDescription{\hskip 0pt{}slint-ui/slint}{https://github.com/slint-ui/slint}{Slint is a toolkit to efficiently develop fluid graphical user
interfaces for any display: embedded devices and desktop applications.
We support multiple programming languages, such as Rust, C++, or
JavaScript.\\
Language: Rust\\
Stars: 7112\\
Forks: 219}

\entryitemWithDescription{\hskip 0pt{}young-geng/EasyLM}{https://github.com/young-geng/EasyLM}{Large language models (LLMs) made easy, EasyLM is a one stop solution
for pre-training, finetuning, evaluating and serving LLMs in JAX/Flax.\\
Language: Python\\
Stars: 481\\
Forks: 39}

\entryitemWithDescription{\hskip 0pt{}f/awesome-chatgpt-prompts}{https://github.com/f/awesome-chatgpt-prompts}{This repo includes ChatGPT prompt curation to use ChatGPT better.\\
Language: HTML\\
Stars: 62046\\
Forks: 7514}\ichapter{Dribbble}
\entryitemGeneric{\hskip 0pt{}Zelt Website Development}{https://dribbble.com/shots/21118990}

\entryitemGeneric{\hskip 0pt{}Flatfile Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20919358}

\entryitemGeneric{\hskip 0pt{}Zelt graphic assets}{https://dribbble.com/shots/21107854}

\entryitemGeneric{\hskip 0pt{}LogoLounge Book 14 Submitted Logos}{https://dribbble.com/shots/21119947}

\entryitemGeneric{\hskip 0pt{}Brainwave AI UI Kit - Add New List Modal}{https://dribbble.com/shots/21091477}

\entryitemGeneric{\hskip 0pt{}Banking App}{https://dribbble.com/shots/21113553}

\entryitemGeneric{\hskip 0pt{}Sapforce - AI SaaS website design}{https://dribbble.com/shots/21107524}

\entryitemGeneric{\hskip 0pt{}Letter.co Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20918567}

\entryitemGeneric{\hskip 0pt{}Nike Pickleball - April Fools' Day}{https://dribbble.com/shots/21089582}

\entryitemGeneric{\hskip 0pt{}Fokus Coffee}{https://dribbble.com/shots/21122022}

\entryitemGeneric{\hskip 0pt{}Green Vision - Workflow optimization website}{https://dribbble.com/shots/21126264}

\entryitemGeneric{\hskip 0pt{}AVAX Wallet - Page Transitions}{https://dribbble.com/shots/21094836}

\entryitemGeneric{\hskip 0pt{}Guide - AI based 3d software website}{https://dribbble.com/shots/21086080}

\entryitemGeneric{\hskip 0pt{}Finolio Brand Guidelines}{https://dribbble.com/shots/21042784}

\entryitemGeneric{\hskip 0pt{}Visual identity. Branding, corporate brand design}{https://dribbble.com/shots/21091073}

\entryitemGeneric{\hskip 0pt{}Endpoint Web Site Design: Landing Page / Home Page UI}{https://dribbble.com/shots/20919718}

\entryitemGeneric{\hskip 0pt{}Ninox Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20919922}

\entryitemGeneric{\hskip 0pt{}Travell plan ios interaction}{https://dribbble.com/shots/21072561}

\entryitemGeneric{\hskip 0pt{}Brainwave - Pricing \& Checkout Components}{https://dribbble.com/shots/21113954}

\entryitemGeneric{\hskip 0pt{}Proemion Admin Dashboard: Analytics UX UI}{https://dribbble.com/shots/20918772}

\entryitemGeneric{\hskip 0pt{}Brainwave - Hero Header}{https://dribbble.com/shots/21102327}

\entryitemGeneric{\hskip 0pt{}Agency Landing Page Animation}{https://dribbble.com/shots/21131181}

\entryitemGeneric{\hskip 0pt{}Almanac Brand Refresh}{https://dribbble.com/shots/21099112}

\entryitemGeneric{\hskip 0pt{}Hellorep.ai onboarding experience}{https://dribbble.com/shots/21097494}


\ipart{Developers~~~~(zh-Hans)}
\ichapter{Solidot}
\entryitemGeneric{\hskip 0pt{}欧洲去年冬天大幅削减了能源消耗}{https://www.solidot.org/story?sid=74607}

\entryitemGeneric{\hskip 0pt{}ChatGPT 和 Bing Chat 为何擅长捏造故事？}{https://www.solidot.org/story?sid=74606}

\entryitemGeneric{\hskip 0pt{}特斯拉员工是在内部分享客户的私密图像}{https://www.solidot.org/story?sid=74605}

\entryitemGeneric{\hskip 0pt{}PM2.5 颗粒可能会导致肺癌恶化}{https://www.solidot.org/story?sid=74604}

\entryitemGeneric{\hskip 0pt{}哈勃观察到流浪黑洞留下的新生恒星尾迹}{https://www.solidot.org/story?sid=74603}

\entryitemGeneric{\hskip 0pt{}印度要求社交媒体使用政府的事实核查}{https://www.solidot.org/story?sid=74602}

\entryitemGeneric{\hskip 0pt{}Edge 整合 AI 图像生成器}{https://www.solidot.org/story?sid=74601}

\entryitemGeneric{\hskip 0pt{}武汉华南海鲜市场样本中包含大熊猫基因}{https://www.solidot.org/story?sid=74600}

\entryitemGeneric{\hskip 0pt{}Chrome 113 将支持 WebGPU}{https://www.solidot.org/story?sid=74599}

\entryitemGeneric{\hskip 0pt{}Google Pay 的 Bug 给用户返还了大额现金}{https://www.solidot.org/story?sid=74598}

\entryitemGeneric{\hskip 0pt{}AMD 和 JEDEC 标准化 DDR5 MRDIMM}{https://www.solidot.org/story?sid=74597}

\entryitemGeneric{\hskip 0pt{}华为和阿里巴巴准备发布各自的 AI 聊天机器人}{https://www.solidot.org/story?sid=74596}

\entryitemGeneric{\hskip 0pt{}Google 搜索引擎将加入 AI 聊天功能}{https://www.solidot.org/story?sid=74595}

\entryitemGeneric{\hskip 0pt{}Meta 的新 AI 模型能分割出图像中的特定对象}{https://www.solidot.org/story?sid=74594}

\entryitemGeneric{\hskip 0pt{}比特币白皮书隐藏在 macOS Mojave 之后的所有版本中}{https://www.solidot.org/story?sid=74593}

\entryitemGeneric{\hskip 0pt{}研究发现南极冰原的消融速度能达到每天 600 米}{https://www.solidot.org/story?sid=74592}

\entryitemGeneric{\hskip 0pt{}研究揭示寒冷有利于延寿的一个机制}{https://www.solidot.org/story?sid=74591}

\entryitemGeneric{\hskip 0pt{}研究发现错误记忆能在几秒钟内形成}{https://www.solidot.org/story?sid=74590}

\entryitemGeneric{\hskip 0pt{}Google 称其 TPU 超算比英伟达 A100 更快更环保}{https://www.solidot.org/story?sid=74589}

\entryitemGeneric{\hskip 0pt{}全世界最富有的男性和女性都来自奢饰品行业}{https://www.solidot.org/story?sid=74588}\ichapter{V2EX}
\entryitemGeneric{\hskip 0pt{}[程序员] [分享]-推荐一个学 Rust 的频道}{https://www.v2ex.com/t/930731}

\entryitemGeneric{\hskip 0pt{}[程序员] pikpak 下载速度很慢，只有 300K，这是我的网络问题还是 pikpak 的问题？}{https://www.v2ex.com/t/930729}

\entryitemGeneric{\hskip 0pt{}[问与答] 有什么 pc 输入法支持即时翻译的吗}{https://www.v2ex.com/t/930728}

\entryitemGeneric{\hskip 0pt{}[问与答] 在虚拟机 vmware 里舒服使用百度网盘的正确姿势是什么？}{https://www.v2ex.com/t/930727}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 昨天开始一直无法获取 openai 的 token，这是 api 把这个也给封掉了么？}{https://www.v2ex.com/t/930726}

\entryitemGeneric{\hskip 0pt{}[程序员] 你担心 AI 抢你饭碗吗？}{https://www.v2ex.com/t/930725}

\entryitemGeneric{\hskip 0pt{}[程序员] 长期没有上班后如何开始找工作？}{https://www.v2ex.com/t/930724}

\entryitemGeneric{\hskip 0pt{}[macOS] 求推荐 MacOS 出站防火墙软件}{https://www.v2ex.com/t/930723}

\entryitemGeneric{\hskip 0pt{}[Apple] 为什么 applePencil 不能加入 findMyNetwork？}{https://www.v2ex.com/t/930722}

\entryitemGeneric{\hskip 0pt{}[VPS] Racknerd 这种垃圾公司的做法真恶心。快点倒闭吧}{https://www.v2ex.com/t/930721}

\entryitemGeneric{\hskip 0pt{}[MacBook Pro] 15 款 MJLQ2xx/A、MJLT2xx/A、MJLU2xx/A 的参数表}{https://www.v2ex.com/t/930718}

\entryitemGeneric{\hskip 0pt{}[问与答] 哪个笔记软件方便快速添加记录？}{https://www.v2ex.com/t/930717}

\entryitemGeneric{\hskip 0pt{}[程序员] 做一个发布信息和收集文件的公众号功能}{https://www.v2ex.com/t/930716}

\entryitemGeneric{\hskip 0pt{}[macOS] office for Mac 问题}{https://www.v2ex.com/t/930715}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 武汉电信现在还有公网的 IP 可以申请}{https://www.v2ex.com/t/930714}

\entryitemGeneric{\hskip 0pt{}[分享发现] ChatGPT 应用开发小记}{https://www.v2ex.com/t/930713}

\entryitemGeneric{\hskip 0pt{}[macOS] MacOS 13.3 最新系统空格预览 bug}{https://www.v2ex.com/t/930711}

\entryitemGeneric{\hskip 0pt{}[Apple] macbook 选购哪个划算}{https://www.v2ex.com/t/930710}

\entryitemGeneric{\hskip 0pt{}[生活] 被迫买了重疾险，唉，生活好难啊}{https://www.v2ex.com/t/930708}

\entryitemGeneric{\hskip 0pt{}[问与答] 今天下午 ChatGpt 速度突然变慢了。}{https://www.v2ex.com/t/930707}

\entryitemGeneric{\hskip 0pt{}[问与答] 我发现相当一部分上热搜的事都是谣言。}{https://www.v2ex.com/t/930706}

\entryitemGeneric{\hskip 0pt{}[职场话题] 今年找工作也太难了吧，有没有好的想法，一起做点事情}{https://www.v2ex.com/t/930705}

\entryitemGeneric{\hskip 0pt{}[分享创造] [免费] 完美解决 ChatGPT 输入限制问题}{https://www.v2ex.com/t/930703}

\entryitemGeneric{\hskip 0pt{}[问与答] 微信的``通过当前手机号辅助注册''（一个手机号注册两个账号）真的能用了吗？}{https://www.v2ex.com/t/930702}

\entryitemGeneric{\hskip 0pt{}[iOS] IOS 证书在线检测}{https://www.v2ex.com/t/930701}

\entryitemGeneric{\hskip 0pt{}[问与答] 请问哪里可以线上购买音乐？}{https://www.v2ex.com/t/930700}

\entryitemGeneric{\hskip 0pt{}[职场话题] 5 家公司工作了 18 年，分享些工作经验，也写给自己}{https://www.v2ex.com/t/930698}

\entryitemGeneric{\hskip 0pt{}[问与答] win 笔记本有办法只有链接外部显示器,合上才不休眠吗?}{https://www.v2ex.com/t/930697}

\entryitemGeneric{\hskip 0pt{}[数据库] Couchbase 这个数据库大家用的多不？听说性能和扩展性碾压同类 nosql 数据库，做个大型订单类应用不知道有没有人尝试过？}{https://www.v2ex.com/t/930696}

\entryitemGeneric{\hskip 0pt{}[问与答] 趁着假日从北京出发去了西安}{https://www.v2ex.com/t/930695}

\entryitemGeneric{\hskip 0pt{}[生活] 去了一趟绍兴}{https://www.v2ex.com/t/930694}

\entryitemGeneric{\hskip 0pt{}[问与答] 深圳周末去哪里玩呀（自己一个人），有没有线下活动群呀，}{https://www.v2ex.com/t/930693}

\entryitemGeneric{\hskip 0pt{}[求职] 经验不到一年的小前端是不是只能狗着？？}{https://www.v2ex.com/t/930692}

\entryitemGeneric{\hskip 0pt{}[程序员] 免费苹果 ios 在线签名工具}{https://www.v2ex.com/t/930691}

\entryitemGeneric{\hskip 0pt{}[酷工作] [远程/全职]老牌币圈交易所,多个研发岗等你来投}{https://www.v2ex.com/t/930689}

\entryitemGeneric{\hskip 0pt{}[杭州] 家人们，租房好难啊，想租个龙翔桥附近的房子，通勤 30min 之内}{https://www.v2ex.com/t/930688}

\entryitemGeneric{\hskip 0pt{}[Chrome] 浏览器 chrome 选中文本保存为 txt 的实现方法？}{https://www.v2ex.com/t/930687}

\entryitemGeneric{\hskip 0pt{}[全球工单系统] PC 微信无法接收文件、图片}{https://www.v2ex.com/t/930686}

\entryitemGeneric{\hskip 0pt{}[Windows] 甲骨文 ARM 可否安装 Windows 11 ARM 系统？}{https://www.v2ex.com/t/930685}

\entryitemGeneric{\hskip 0pt{}[macOS] Microsoft 这个操作是流氓软件吗？}{https://www.v2ex.com/t/930683}

\entryitemGeneric{\hskip 0pt{}[分享发现] 大家有没有比较便宜一点的接码平台}{https://www.v2ex.com/t/930682}

\entryitemGeneric{\hskip 0pt{}[OpenAI] chatgpt token 计算方式}{https://www.v2ex.com/t/930681}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 我的 chatGPT 是没有账号和密码的，正常吗}{https://www.v2ex.com/t/930680}

\entryitemGeneric{\hskip 0pt{}[问与答] 有没有推荐的运行在服务器上的文件服务？}{https://www.v2ex.com/t/930677}

\entryitemGeneric{\hskip 0pt{}[生活] 话说如果你不想当程序员，想转行干啥呢？}{https://www.v2ex.com/t/930676}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 看了几个新出的大模型，代码能力好像蛮难的都没法达到}{https://www.v2ex.com/t/930675}

\entryitemGeneric{\hskip 0pt{}[问与答] 用 Vim 可以进一步提升操作速度吗？}{https://www.v2ex.com/t/930674}

\entryitemGeneric{\hskip 0pt{}[问与答] 这种这么便宜的流量卡靠谱吗？}{https://www.v2ex.com/t/930672}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 想换 F7607P 光猫，有用过的吗，有几个疑问}{https://www.v2ex.com/t/930671}

\entryitemGeneric{\hskip 0pt{}[分享创造] 我实现了一个 ChatGPT 插件系统}{https://www.v2ex.com/t/930670}


\ipart{Generic News}
\ichapter{AP News}
\entryitemWithDescription{\hskip 0pt{}Judge halts FDA approval of abortion pill mifepristone}{https://apnews.com/article/74cb1c4cfab2c04f6cf2696151bc86ef}{FILE - Boxes of the drug mifepristone sit on a shelf at the West Alabama Women\textquotesingle s Center in Tuscaloosa, Ala., March 16, 2022. A federal judge in Texas on Friday, April 7, 2023, ordered a hold on the U.S. approval of the...}

\entryitemWithDescription{\hskip 0pt{}Brooks Koepka a major presence again, leads the Masters}{https://apnews.com/article/6f4109da771edd946ea8a4c9fa02fe54}{Brooks Koepka waves after his putt on the 13th hole during the second round of the Masters golf tournament at Augusta National Golf Club on Friday, April 7, 2023, in Augusta, Ga. (AP Photo/Charlie Riedel) AUGUSTA, Ga. (AP) --- The notion...}

\entryitemWithDescription{\hskip 0pt{}Army sergeant guilty in fatal Texas shooting of protester}{https://apnews.com/article/304fe24ca6fd5f0399e5157a9294744d}{FILE - Austin police investigate a homicide shooting that occurred at a demonstration against police violence in downtown Austin, Texas, July 25, 2020. A U.S. Army sergeant was convicted of murder for fatally shooting an armed protester...}

\entryitemWithDescription{\hskip 0pt{}Storms bring down trees at Masters, play halted in 2nd round}{https://apnews.com/article/7ca1dadd1fefcc846e71b3600ff5e2f2}{Patrons move away from two trees that blew over on the 17th hole during the second round of the Masters golf tournament at Augusta National Golf Club on Friday, April 7, 2023, in Augusta, Ga. (AP Photo/Mark Baker) AUGUSTA, Ga. (AP...}

\entryitemWithDescription{\hskip 0pt{}Biden sports plan angers transgender advocates, opponents}{https://apnews.com/article/28c6c78e9cd60a4c334de15bfdd624fe}{FILE - Yale\textquotesingle s Iszac Henig, a trans man and competitive swimmer, looks up the scoreboard after swimming in a qualifying heat of the 100-yard freestyle at the Ivy League Women\textquotesingle s Swimming and Diving...}

\entryitemWithDescription{\hskip 0pt{}Uproar in suburbia as New York looks to spur development}{https://apnews.com/article/f16691c1635b0f23cc7efd74c796752a}{A plot of land that is being developed into multifamily housing is seen in East Northport, N.Y., Thursday, March 16, 2023. Some elected officials from Long Island claim their suburban way of life is threatened by New York Gov. Kathy...}

\entryitemWithDescription{\hskip 0pt{}US states consider ban on cosmetics with 'forever chemicals'}{https://apnews.com/article/4a576b96e4014a59b2c736344b2255d0}{FILE - A worker, at left, tends to a customer at a cosmetics shop on Thursday, May 20, 2021, in Los Angeles.A growing number of state legislatures are considering banning the sale of cosmetics and other consumer products that contain the...}

\entryitemWithDescription{\hskip 0pt{}Justice Thomas says he didn't have to disclose luxury trips}{https://apnews.com/article/2c0f59fd1b0d5d3617c1537a767c5325}{FILE - Associate Justice Clarence Thomas joins other members of the Supreme Court as they pose for a new group portrait, at the Supreme Court building in Washington, Oct. 7, 2022. Thomas said Friday, April 7, that he was not required to...}

\entryitemWithDescription{\hskip 0pt{}Report: Russia charges Journal reporter with espionage}{https://apnews.com/article/152e4bc8c9c97c36d263898c9cf44ad9}{FILE - The Wall Street Journal journalist Evan Gershkovich is shown in this undated photo. The U.S. Senate\textquotesingle s top two leaders, in a rare bipartisan statement, demanded on Friday that Russia immediately release Evan...}

\entryitemWithDescription{\hskip 0pt{}Save the date: One year until total solar eclipse sweeps US}{https://apnews.com/article/113061a08d63e579c698017312f7eea0}{FILE - The period of total coverage during the solar eclipse is seen near Hopkinsville, Ky. Monday, Aug. 21, 2017. The location, which is in the path of totality, is also at the point of greatest intensity. It's only a year until a total...}

\entryitemWithDescription{\hskip 0pt{}California lawmaker wants Peeps to change its ingredients}{https://apnews.com/article/d7963c52b6213619672c6f50b32ca548}{Marshmallow Peeps candy is on display at a store in Lafayette, Calif., on March 24, 2023. A California lawmaker wants to ban certain types of chemical additives in food dyes used in popular candies like Skittles and Peeps. They are...}

\entryitemWithDescription{\hskip 0pt{}What's next for Tennessee's expelled lawmakers?}{https://apnews.com/article/2c804e66f48730951375387d24247fc1}{Former Rep. Justin Pearson, D-Memphis, waves to his supporters in the gallery as he delivers his final remarks on the floor of the House chamber as he is expelled from the legislature Thursday, April 6, 2023, in Nashville, Tenn. Tennessee...}

\entryitemWithDescription{\hskip 0pt{}3 new 'Star Wars' movies coming, including Rey's return}{https://apnews.com/article/ba6d94901b67bf76fa0edd6461c1edca}{FILE - Daisy Ridley arrives at the world premiere of "Star Wars: The Rise of Skywalker" on Dec. 16, 2019, in Los Angeles. Lucasfilm announced three new live-action films in the "Star Wars" franchise which includes the return of Ridley as...}\ichapter{Reuters}
\entryitemWithDescription{\hskip 0pt{}One tourist killed, five injured in Tel Aviv attack -officials}{https://www.reuters.com/world/middle-east/one-killed-several-injured-tel-aviv-attack-israeli-officials-2023-04-07/}{Israeli officials work at the scene of a shooting attack in Tel Aviv, Israel April 7, 2023. REUTERS/Nir Elias A general view of the scene of a shooting attack in Tel Aviv, Israel April 7, 2023. REUTERS/Nir Elias Israeli officials work at...}

\entryitemWithDescription{\hskip 0pt{}Harris heads to Tennessee after lawmakers expelled over gun protests}{https://www.reuters.com/world/us/us-vp-harris-meet-lawmakers-tennessee-after-house-expulsion-two-democrats-2023-04-07/}{People exit the building after a vote on to expel two of three Democratic members for their role in a gun control demonstration at the statehouse last week, in Nashville, Tennessee, U.S., April 6, 2023. REUTERS/Cheney Orr U.S. Vice...}

\entryitemWithDescription{\hskip 0pt{}Who is Republican donor and Justice Clarence Thomas' friend Harlan Crow?}{https://www.reuters.com/world/us/who-is-republican-donor-justice-clarence-thomas-friend-harlan-crow-2023-04-07/}{U.S. Supreme Court Associate Justice Clarence Thomas (L) talks with Chief Justice John Roberts as the justices pose for their group portrait at the Supreme Court in Washington, U.S., November 30, 2018. REUTERS/Jim Young/File Photo Real...}

\entryitemWithDescription{\hskip 0pt{}Top U.S. shipping gateway mostly closes due to port worker shortage - employer group}{https://www.reuters.com/world/us/us-west-coast-dockworkers-force-closure-top-container-port-employer-group-2023-04-07/}{Stacked containers and cranes are shown at the Port of Los Angeles in Los Angeles, California, U.S. November 22, 2021. REUTERS/Mike Blake A shortage of West Coast port workers has forced the busiest U.S. ocean trade gateway to largely...}

\entryitemWithDescription{\hskip 0pt{}After bronchitis, cold weather forces pope to skip outdoor service}{https://www.reuters.com/world/europe/pope-francis-skip-good-friday-procession-due-cold-weather-2023-04-07/}{Pope Francis presides over the Good Friday Passion of the Lord service in Saint Peter\textquotesingle s Basilica at the Vatican, April 7, 2023. Vatican Media/­Handout via REUTERS Pope Francis presides the Good Friday Passion of the Lord...}

\entryitemWithDescription{\hskip 0pt{}India asks states to ramp up testing as COVID-19 cases climb}{https://www.reuters.com/world/india/india-asks-states-ramp-up-testing-covid-19-cases-climb-2023-04-07/}{A healthcare worker collects a test swab sample from a child amidst the spread of the coronavirus disease (COVID-19), at a testing centre inside a hospital in New Delhi, India, January 14, 2022. REUTERS/Anushree Fadnavis India...}

\entryitemWithDescription{\hskip 0pt{}U.S. yields climb, S\&P futures close higher after jobs report}{https://www.reuters.com/markets/global-markets-global-markets-2023-04-07/}{Summary: March U.S. payrolls rise by 236,000 vs 239,000 estimate Dollar strengthens, U.S. yields climb Nikkei, S\&P futures close higher Passersby walk past an electric monitor displaying Japan\textquotesingle s Nikkei share average and...}

\entryitemWithDescription{\hskip 0pt{}U.S. Supreme Court Justice Thomas' career marked by controversies}{https://www.reuters.com/world/us/us-supreme-court-justice-thomas-career-marked-by-controversies-2023-04-07/}{Associate Supreme Court Justice Clarence Thomas arrives for the swearing in ceremony of Judge Neil Gorsuch as an Associate Supreme Court Justice in the Rose Garden of the White House in Washington, U.S., April 10, 2017. REUTERS/Joshua...}

\entryitemWithDescription{\hskip 0pt{}Inside the US jobs report: Record-low Black unemployment}{https://www.reuters.com/markets/us/inside-us-jobs-report-record-low-black-unemployment-2023-04-07/}{An "Apply Now" sign stands outside the new Faccia Brutta Bar Pallino looking to hire employees on Newbury Street in Boston, Massachusetts, U.S., April 27, 2022. REUTERS/Brian Snyder The Black unemployment rate hit a record low in March, a...}

\entryitemWithDescription{\hskip 0pt{}Ukraine seeks to prevent military leaks after NATO assistance plans reportedly appear on social media}{https://www.reuters.com/world/ukrainian-forces-cling-onto-besieged-city-china-pressed-help-end-war-2023-04-07/}{Summary: Talks at Ukrainian military HQ aim to forestall leaks Ukraine says documents on social media are disinformation UK report signals Ukrainian forces pressured in Bakhmut Ukrainian military says they are still fighting there Father...}

\entryitemWithDescription{\hskip 0pt{}U.S. Supreme Court Justice Thomas defends trips financed by 'dearest friends'}{https://www.reuters.com/world/us/supreme-court-justice-thomas-says-he-sought-comply-with-disclosure-guidelines-2023-04-07/}{U.S. Supreme Court Associate Justice Clarence Thomas poses during a group portrait at the Supreme Court in Washington, U.S., October 7, 2022. REUTERS/Evelyn Hockstein/File Photo U.S. Supreme Court Justice Clarence Thomas on Friday...}

\entryitemWithDescription{\hskip 0pt{}Russia likely behind U.S. military document leak, U.S. officials say}{https://www.reuters.com/world/us/russia-likely-behind-us-military-document-leak-us-officials-say-2023-04-07/}{The Pentagon building is seen in Arlington, Virginia, U.S, April 6, 2023. REUTERS/Tom Brenner Russia or pro-Russian elements are likely behind the leak of several classified U.S. military documents posted on social media that offer a...}

\entryitemWithDescription{\hskip 0pt{}Exclusive: Saudi delegation to hold ceasefire talks with Yemen's Houthis in Sanaa -sources}{https://www.reuters.com/world/middle-east/saudi-led-coalition-lifts-more-restrictions-yemens-imports-2023-04-07/}{A military helicopter, operated by the Houthis, flies over Sanaa, Yemen September 21, 2022 for the first time since the Saudi-led coalition intervened in Yemen and controlled the country\textquotesingle s airspace in 2015. REUTERS/Khaled...}\ichapter{联合早报}
\entryitemWithDescription{马英九称大陆行让``九二共识又活过来'' 蔡英文：那是1970年代论述}{https://www.zaobao.com/news/china/story20230408-1380631}{台湾现任总统蔡英文（右一）星期五也结束经美国前往中美洲之行，在桃园机场发表讲话。（路透社） 台湾前总统马英九（右）星期五结束大陆行返抵桃园机场，国民党副主席夏立言（左）等人前往接机。（路透社） 台湾前后任总统马英九和蔡英文星期五（4月7日）分别自中国大陆和美国返台，两人对两岸关系定位看法截然不同，双方隔空论述已见，后续效应逐渐发酵……}

\entryitemWithDescription{北京制裁台驻美代表萧美琴等个人及机构}{https://www.zaobao.com/news/china/story20230408-1380632}{中国大陆方面自星期三起在台湾海峡中北部展开联合巡航巡查专项行动。图为星期五一架解放军的武装直升机，飞越福建距离台湾本岛最近的平潭岛上一处旅游景点的上空。（法新社） 台湾总统蔡英文与美国众议院议长麦卡锡会面后，中国大陆官方星期五（4月7日）对美台祭出一系列反制措施，包括对台湾驻美代表萧美琴实施制裁、限制美国的哈德逊研究所和里根图书馆与大陆方面交流，以及对远景基金会和亚洲自由民主联盟采取惩戒措施等……}

\entryitemWithDescription{八孩案``铁链女''丈夫 监九年遭议量刑太轻}{https://www.zaobao.com/news/china/story20230408-1380633}{江苏丰县``八孩案''嫌犯董志民，4月6日在徐州市中级人民法院一审中，被法院认定犯虐待罪，判处有期徒刑六年六个月；犯非法拘禁罪，判处有期徒刑三年，数罪并罚，决定执行有期徒刑九年。（新华社） 徐州市中院以虐待罪和非法拘禁罪，判处生育八孩的``铁链女''小花梅丈夫董志民有期徒刑九年，另外五名被告因拐卖妇女罪，分别被判八年至13年不等刑期。宣判结果引发舆论热议，有网民认为量刑过轻，难以起到警示作用……}

\entryitemWithDescription{中国称澳洲TikTok禁令是``歧视性''措施}{https://www.zaobao.com/news/china/story20230408-1380635}{中国商务部星期五（4月7日）发表声明说，澳大利亚政府禁止在联邦公共部门设备上使用TikTok的``歧视性''限制措施，将损害澳企业和民众的自身利益，并敦促堪培拉公平公正对待各类企业。 商务部美大司负责人说，澳方将TikTok与其他社交媒体平台区别对待，采取歧视性的限制措施，无益于维护澳国家安全，反而有损国际社会对澳营商环境的信心，也将损害澳企业和民众的自身利益……}

\entryitemWithDescription{360掌门人周鸿祎 ``技术性离婚''?}{https://www.zaobao.com/news/china/story20230408-1380636}{奇虎360创始人周鸿祎4月4日宣布离婚，转让公司6.25\%的股份给前妻胡欢，价值近90亿元（人民币，下同，17.36亿新元），被媒体形容为``天价离婚''。 这也是中国一线互联网大佬中的首例离婚，夫妻二人的财产分割备受关注，``可能是A股市场上有史以来最高的离婚费用''引发市场联想，不少人怀疑周鸿祎是为减持套现而作出的``技术性离婚''。 这样的怀疑并非空穴来风……}

\entryitemWithDescription{中国体育总局局长： 坚决打赢反腐攻坚战}{https://www.zaobao.com/news/china/story20230408-1380637}{中国国家体育总局星期四（4月6日）召开``2023年党风廉政建设和反腐败工作会议''，局长高志丹在会上强调，坚决落实打赢反腐败斗争攻坚战持久战部署要求。有关人士分析，打赢体育总局系统反腐败攻坚战，显然是中纪委给体育总局定下的任务，预计体育总局除副局长杜兆才外，还将有高级别官员落马。 国家体育总局原局长苟仲文可能将受牵连坊间消息称，已退休的国家体育总局原局长苟仲文或将受牵连……}

\entryitemWithDescription{乍暖还寒的台湾四月天}{https://www.zaobao.com/news/china/story20230408-1380638}{台湾今年的春天有点不一样，冷气团来得多。最近两周，台北气温有时冷至14摄氏度，有时热到31摄氏度，日夜温差往往多达10摄氏度，天天体会乍暖还寒的滋味。 我依然殷切期待着一树一树花开的人间四月天。趁着台湾儿童节（4月4日）假日的好天气，骑共享脚踏车到大安森林公园欣赏盛开的杜鹃花、也到台湾大学和忠孝东路一带看沿途火焰般怒放的木棉花……}

\entryitemWithDescription{截至1月底已审理逾2200起 港司法机构：约九成反修例案件已结案}{https://www.zaobao.com/news/china/story20230408-1380639}{香港反修例运动期间被捕人数很多，调查、上庭审讯排期均需时间。图为大批民众2月6日在西九龙裁判法院大楼外排队准备旁听47名民主派人士被控违反《香港国安法》案件的审讯。（路透社） 香港司法机构向立法会提交的特别财委会发言稿披露，截至今年1月底，司法机构审理的2200多起反修例案件，约九成已经结案。尚待处理的刑事案件，主要是由区域法院负责，当中大部分已经排期在今年或明年开审……}

\entryitemWithDescription{港``高才通''成功申请者 近95\%来自大陆}{https://www.zaobao.com/news/china/story20230408-1380640}{截至今年2月28日，香港``高端人才通行证计划''一共接获1万4240宗申请，8797宗申请获批，其中8325人来自中国大陆，占整体获批申请者近95\%。 据中新社报道，香港入境事务处是在星期四（4月6日）回复香港立法会特别财委会提问时，披露上述数字……}

\entryitemWithDescription{率美议员团访台立法院 麦考尔：全力协助加速交付武器}{https://www.zaobao.com/news/china/story20230408-1380641}{美国众议院外委会主席麦考尔（中）一行，星期五在台北出席聆听台湾立法院的一场院会质询。（路透社） 美国联邦众议院外交委员会主席麦考尔星期五对媒体表示，他已经尽全力加速交付台湾所采购的美国军备，并建议其他拥有相同武器的国家，可在美国政府批准下转卖给台湾。 综合路透社和中央社报道，麦考尔（Michael McCaul）星期五（4月7日）率跨党派议员团拜会台湾立法院，并进入议场二楼贵宾席观看院会的举行……}

\entryitemWithDescription{注册资本122亿减至1亿 阿里相关人士：非应监管要求减资}{https://www.zaobao.com/news/china/story20230408-1380642}{杭州阿里巴巴网络科技公司变更工商登记，注册资本由122亿人民币（23亿新元）减至约1.05亿人民币，有媒体称这是应监管要求减资。 对此，阿里相关人士回应称，网传消息不实，这是公司正常工商登记变更。 天眼查App显示，杭州阿里巴巴网络科技有限公司发生工商登记变更，公司法定代表人为张勇，由淘宝（中国）软件有限公司全资持股……}

\entryitemWithDescription{蔡麦会登场 台美默契强调民主 北京坚定``内政''自决}{https://www.zaobao.com/news/china/story20230407-1380275}{美国时间4月5日上午，台湾总统蔡英文（右二）与团队，与美国众议院议长麦卡锡（左三）率领的跨党派议员，在加州的里根图书馆会谈。（路透社） 牵动台海局势的蔡麦会在全球瞩目下登场，台湾总统蔡英文在会后感谢美国挺台，并形容民主正受威胁；美国众议院议长麦卡锡则指美台友谊对维持和平稳定至关重要……}

\entryitemWithDescription{通过巡航执法将台海``内海化'' 学者：大陆``面子里子''兼得}{https://www.zaobao.com/news/china/story20230407-1380277}{中国大陆星期三派出``海巡06''轮领衔的海事执法船艇编队，进行为期三天的台湾海峡中北部联合巡航巡查专项行动，对两岸船只实施现场检查。（中新社） 台湾总统蔡英文与美国众议院议长麦卡锡会晤后，中国大陆官媒展开文攻，密集发文警告``倚美谋独''必遭惩戒，北京同时出动海巡船对两岸船只展开执法行动，并派出航母舰队在台海附近航训……}

\entryitemWithDescription{布林肯：北京不应强行改变台海现状}{https://www.zaobao.com/news/china/story20230407-1380278}{美国国务卿布林肯说，北京不应以台湾总统蔡英文在美国过境为借口，采取任何让情势紧张的行动，或进一步推动改变台湾现状。 布林肯星期三（4月5日）在布鲁塞尔出席北约外长会议后，在记者会上试图淡化蔡麦会的重要性。布林肯说，蔡英文过境美国不是什么新鲜事，这样的停留是``私人的''和``非官方的''……}

\entryitemWithDescription{数百上海民众雨中``追马''}{https://www.zaobao.com/news/china/story20230407-1380280}{台湾前总统马英九4月6日到访上海四行仓库抗战纪念馆时，数百民众冒雨在场等待。（陈婧摄） 历时12天，台湾前总统马英九大陆行最后一站依然引发``追马''热潮，数百民众在上海四行仓库抗战纪念馆外冒雨等候他现身。 马英九星期四（4月6日）下午乘车到访四行仓库。尽管上海当天阴雨绵绵，但数百民众仍提前一小时就到场等候。四行仓库外的马路两旁，早早站满了围观民众……}

\entryitemWithDescription{港澳流感疫情呈活跃趋势 医学专家吁市民尽快接种疫苗}{https://www.zaobao.com/news/china/story20230407-1380281}{香港和澳门全面复常后，近来皆进入流感高峰期，感染个案急升。受访的医学专家提醒，市民尤其是高风险人士应尽快接种流感疫苗，以及在人流密集处做好个人卫生。 香港``口罩令''解除一个月后，冠病病毒近日呈现活跃趋势。香港大学发表的数据显示，冠病病毒即时有效繁殖率曾经升破``1''，意味着每名患者平均传染多于一人……}

\entryitemWithDescription{沙特伊朗外长北京会晤 宣布即日起恢复外交关系}{https://www.zaobao.com/news/china/story20230407-1380282}{中国外长秦刚（中）4月6日宴请在北京举行会晤的沙特外交大臣费萨尔（右）和伊朗外长阿卜杜拉希扬（左）。（路透社） 断交七年后，沙特阿拉伯和伊朗两国外长星期四（4月6日）在北京正式会面并签署联合声明，宣布即日起恢复外交关系……}

\entryitemWithDescription{中国测量船停靠南非港口 分析：或令西方更担忧南非靠拢中俄}{https://www.zaobao.com/news/china/story20230407-1380283}{在南非与中国、俄罗斯举行联合海上军事演习不到两个月后，中国``远望五号''测量船本周在南非东部最大港口德班港停靠。有分析认为，这可能加剧西方国家对南非正在向中国和俄罗斯靠拢的担忧。 彭博社收集的资料显示，远望五号在德班港停靠后，已继续向西行驶。据中国官媒《环球时报》此前报道，远望五号今年2月20日离港，赴预定海域执行海上测控任务，不过报道并未透露其他信息……}

\entryitemWithDescription{中印互指对方 给自家记者制造签证麻烦}{https://www.zaobao.com/news/china/story20230407-1380285}{印度和中国星期四（4月6日）爆发新的外交争吵，指责对方为自家记者制造签证麻烦。 据路透社报道，印度媒体本周报道，两名驻北京的印度记者被禁止从印度返回北京。消息人士说，《印度教报》和印度国家广播公司的记者星期二（4月4日）被告知，他们的签证已被冻结……}

\entryitemWithDescription{韩咏红：台湾``双英''出访的高下}{https://www.zaobao.com/news/china/story20230407-1380286}{2024年的台湾总统选举会是关键一役，决定和代价，都将由台湾选民选择与承担……}

\entryitemWithDescription{王缉思：国内政治问题导致关系恶化 中美最坏情境是双方因意外而开战}{https://www.zaobao.com/news/china/story20230407-1380287}{中国著名中美关系学者王缉思（左）星期四（4月6日）下午在南洋理工大学拉惹勒南国际研究院杰出学者公开讲座上演讲。右为拉惹勒南国际研究院院长古玛。（邬福梁摄） 中国著名中美关系学者王缉思说，中美各自国内政治问题是左右双边关系走向、导致两国关系恶化的最关键因素。``要是中美各自国内政治继续沿当前的轨道发展，两国关系恶化的势头将无法逆转……}