\entryitemWithDescription{\hskip 0pt{}Judge halts FDA approval of abortion pill mifepristone}{https://apnews.com/article/74cb1c4cfab2c04f6cf2696151bc86ef}{FILE - Boxes of the drug mifepristone sit on a shelf at the West Alabama Women\textquotesingle s Center in Tuscaloosa, Ala., March 16, 2022. A federal judge in Texas on Friday, April 7, 2023, ordered a hold on the U.S. approval of the...}

\entryitemWithDescription{\hskip 0pt{}Brooks Koepka a major presence again, leads the Masters}{https://apnews.com/article/6f4109da771edd946ea8a4c9fa02fe54}{Brooks Koepka waves after his putt on the 13th hole during the second round of the Masters golf tournament at Augusta National Golf Club on Friday, April 7, 2023, in Augusta, Ga. (AP Photo/Charlie Riedel) AUGUSTA, Ga. (AP) --- The notion...}

\entryitemWithDescription{\hskip 0pt{}Army sergeant guilty in fatal Texas shooting of protester}{https://apnews.com/article/304fe24ca6fd5f0399e5157a9294744d}{FILE - Austin police investigate a homicide shooting that occurred at a demonstration against police violence in downtown Austin, Texas, July 25, 2020. A U.S. Army sergeant was convicted of murder for fatally shooting an armed protester...}

\entryitemWithDescription{\hskip 0pt{}Storms bring down trees at Masters, play halted in 2nd round}{https://apnews.com/article/7ca1dadd1fefcc846e71b3600ff5e2f2}{Patrons move away from two trees that blew over on the 17th hole during the second round of the Masters golf tournament at Augusta National Golf Club on Friday, April 7, 2023, in Augusta, Ga. (AP Photo/Mark Baker) AUGUSTA, Ga. (AP...}

\entryitemWithDescription{\hskip 0pt{}Biden sports plan angers transgender advocates, opponents}{https://apnews.com/article/28c6c78e9cd60a4c334de15bfdd624fe}{FILE - Yale\textquotesingle s Iszac Henig, a trans man and competitive swimmer, looks up the scoreboard after swimming in a qualifying heat of the 100-yard freestyle at the Ivy League Women\textquotesingle s Swimming and Diving...}

\entryitemWithDescription{\hskip 0pt{}Uproar in suburbia as New York looks to spur development}{https://apnews.com/article/f16691c1635b0f23cc7efd74c796752a}{A plot of land that is being developed into multifamily housing is seen in East Northport, N.Y., Thursday, March 16, 2023. Some elected officials from Long Island claim their suburban way of life is threatened by New York Gov. Kathy...}

\entryitemWithDescription{\hskip 0pt{}US states consider ban on cosmetics with 'forever chemicals'}{https://apnews.com/article/4a576b96e4014a59b2c736344b2255d0}{FILE - A worker, at left, tends to a customer at a cosmetics shop on Thursday, May 20, 2021, in Los Angeles.A growing number of state legislatures are considering banning the sale of cosmetics and other consumer products that contain the...}

\entryitemWithDescription{\hskip 0pt{}Justice Thomas says he didn't have to disclose luxury trips}{https://apnews.com/article/2c0f59fd1b0d5d3617c1537a767c5325}{FILE - Associate Justice Clarence Thomas joins other members of the Supreme Court as they pose for a new group portrait, at the Supreme Court building in Washington, Oct. 7, 2022. Thomas said Friday, April 7, that he was not required to...}

\entryitemWithDescription{\hskip 0pt{}Report: Russia charges Journal reporter with espionage}{https://apnews.com/article/152e4bc8c9c97c36d263898c9cf44ad9}{FILE - The Wall Street Journal journalist Evan Gershkovich is shown in this undated photo. The U.S. Senate\textquotesingle s top two leaders, in a rare bipartisan statement, demanded on Friday that Russia immediately release Evan...}

\entryitemWithDescription{\hskip 0pt{}Save the date: One year until total solar eclipse sweeps US}{https://apnews.com/article/113061a08d63e579c698017312f7eea0}{FILE - The period of total coverage during the solar eclipse is seen near Hopkinsville, Ky. Monday, Aug. 21, 2017. The location, which is in the path of totality, is also at the point of greatest intensity. It's only a year until a total...}

\entryitemWithDescription{\hskip 0pt{}California lawmaker wants Peeps to change its ingredients}{https://apnews.com/article/d7963c52b6213619672c6f50b32ca548}{Marshmallow Peeps candy is on display at a store in Lafayette, Calif., on March 24, 2023. A California lawmaker wants to ban certain types of chemical additives in food dyes used in popular candies like Skittles and Peeps. They are...}

\entryitemWithDescription{\hskip 0pt{}What's next for Tennessee's expelled lawmakers?}{https://apnews.com/article/2c804e66f48730951375387d24247fc1}{Former Rep. Justin Pearson, D-Memphis, waves to his supporters in the gallery as he delivers his final remarks on the floor of the House chamber as he is expelled from the legislature Thursday, April 6, 2023, in Nashville, Tenn. Tennessee...}

\entryitemWithDescription{\hskip 0pt{}3 new 'Star Wars' movies coming, including Rey's return}{https://apnews.com/article/ba6d94901b67bf76fa0edd6461c1edca}{FILE - Daisy Ridley arrives at the world premiere of "Star Wars: The Rise of Skywalker" on Dec. 16, 2019, in Los Angeles. Lucasfilm announced three new live-action films in the "Star Wars" franchise which includes the return of Ridley as...}