\entryitemWithDescription{\hskip 0pt{}Court reverses former Nebraska US Rep. Jeff Fortenberry's conviction of lying to federal authorities}{https://apnews.com/article/87ae8166a867b9f98f4c352748c6c521}{LOS ANGELES (AP) --- An appellate court on Tuesday reversed a 2022 federal conviction against former Rep. Jeff Fortenberry of Nebraska, ruling that he should not have been tried in Los Angeles. Fortenberry was convicted in March 2022 on...}

\entryitemWithDescription{\hskip 0pt{}6-year-old boy traveling to visit grandma for Christmas put on wrong Spirit flight}{https://apnews.com/article/573121cfce5d4b1e069289a10cc18e01}{FORT MYERS, Fla. (AP) --- A 6-year-old boy who left on a flight for the Christmas holiday to visit his grandmother in southwest Florida instead was put on the wrong plane and ended up 160 miles away in Orlando, Florida. When the...}

\entryitemWithDescription{\hskip 0pt{}4 young children and their mother were killed in their French home. The father is in custody}{https://apnews.com/article/bdbd246a5acedc11ac64ed17a067c024}{MEAUX, France (AP) --- Four children between nine months and 10 years old and their mother were killed in their apartment east of Paris, in what local authorities called an exceptionally violent crime. The children's father was arrested...}

\entryitemWithDescription{\hskip 0pt{}Stock market today: Wall Street ends higher at the start of a holiday-shortened week}{https://apnews.com/article/c7d9a65f3bbad0c636f500f90b9df066}{Stocks notched more gains Tuesday as Wall Street kicked off what's expected to be a quiet, holiday-shortened week of trading. The S\&P 500 rose 0.4\%, finishing less than 0.5\% below its all-time high set nearly two years ago. The...}

\entryitemWithDescription{\hskip 0pt{}The death toll rises to 18 in a furnace explosion at a Chinese-owned nickel plant in Indonesia}{https://apnews.com/article/e27a80240ab9376273ee906c3d8ecbdb}{PALU, Indonesia (AP) --- The death toll following the explosion of a smelting furnace at a Chinese-owned nickel plant on Indonesia's Sulawesi island rose to 18 on Tuesday, as police ordered the plant to stop operations until an...}

\entryitemWithDescription{\hskip 0pt{}Whisky wooing young Chinese away from `baijiu' as top distillers target a growing market}{https://apnews.com/article/326402208f6e945a5530e5cb7454ad0f}{BEIJING (AP) --- A distillery in southwestern China is aiming to tap a growing taste among young Chinese for whisky in place of the traditional ``baijiu'' liquor used to toast festive occasions. The more than \$100 million distillery...}

\entryitemWithDescription{\hskip 0pt{}TV actor Kamar de los Reyes of `One Life to Live' and `Call of Duty' dies at 56}{https://apnews.com/article/db2cc7e52fbc3f51447ecf603862d316}{Kamar de los Reyes, a television, movie and voice actor best known for playing a gang member-turned-cop in the soap ``One Life to Live'' and a villain in the video game ``Call of Duty: Black Ops II,'' has died in Los Angeles at 56, the...}

\entryitemWithDescription{\hskip 0pt{}Holiday travel is mostly nice, but with some naughty disruptions again on Southwest Airlines}{https://apnews.com/article/527dcf19d1d6389eb3e067acda6221de}{Conditions were mostly nice this year for travelers flying ahead of and on Christmas, but some naughty disruptions again plagued those flying with Southwest Airlines. For millions of people traveling over the holiday, this year was much...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift celebrates Christmas Day by watching Travis Kelce and Chiefs play Las Vegas}{https://apnews.com/article/dd7033682409457a12338edc432b2c04}{KANSAS CITY, Mo. (AP) --- Pop superstar Taylor Swift walked into Arrowhead Stadium alongside Santa Claus on Monday to watch her boyfriend and Kansas City Chiefs tight end Travis Kelce as they played the Las Vegas Raiders in a Christmas...}

\entryitemWithDescription{\hskip 0pt{}The secret life of gift cards: Here's what happens to the billions that go unspent each year}{https://apnews.com/article/e9592f6b4067601a27d0f0199da898c8}{Gift cards make great stocking stuffers --- just as long as you don't stuff them in a drawer and forget about them after the holidays. Americans are expected to spend nearly \$30 billion on gift cards this holiday season, according to the...}

\entryitemWithDescription{\hskip 0pt{}King Charles III's Christmas message reflects a coronation theme and calls for planet's protection}{https://apnews.com/article/659d022ca066c5922fcd1c7b9e970194}{LONDON (AP) --- King Charles III reflected his coronation theme of public service Monday in a Christmas message that he connected to the health of the planet and wars that are raging. In a prerecorded video shot with him standing beside a...}

\entryitemWithDescription{\hskip 0pt{}Mike Nussbaum, prolific Chicago stage actor with film roles including `Field of Dreams,' dies at 99}{https://apnews.com/article/d96ca499c39ff20c18dcf965fd85f18b}{CHICAGO (AP) --- Mike Nussbaum, reputed as the oldest professional actor in America with a prolific stage career and roles in films including ``Field of Dreams'' and ``Men in Black,'' has died. He was 99. He died of old age at his Chicago...}

\entryitemWithDescription{\hskip 0pt{}Finding new dimensions, sisterhood, and healing in `The Color Purple'}{https://apnews.com/article/21c75312a55f8e001a5c1c5947c09bdd}{It's not a secret that Fantasia Barrino did not want to play Celie again. The ``American Idol'' winner hadn't had the best time doing ``The Color Purple'' on Broadway. The protagonist of Alice Walker's Pulitzer Prize-winning novel tells...}