\entryitemWithDescription{\hskip 0pt{}France's president pounds a punching bag on camera, and Europe notices}{https://apnews.com/article/7ee08a530f8b67a9c633e63c47fa3c81}{LONDON (AP) --- The teeth clench. The brow furrows. The bicep bulges. In moody black and white, photos of French President Emmanuel Macron pounding a punching bag arched eyebrows across Europe on Thursday after his official photographer...}

\entryitemWithDescription{\hskip 0pt{}Roller ball candies linked to fatal choking and injury in children, CPSC warns}{https://apnews.com/article/fdd1dfb2208554fb3eb544b2f7ca6a7e}{Candy treats that use roller balls to let kids eat sweet liquid have been linked to choking, including at least one death, and should not be used, a federal safety agency warned Thursday. The U.S. Consumer Product Safety Commission said...}

\entryitemWithDescription{\hskip 0pt{}Report: Italy's Meloni victim of deep fake porn images, seeking symbolic compensation from suspects}{https://apnews.com/article/7d841c8894609c1542714dc7baaaadce}{ROME (AP) --- Italian Premier Giorgia Meloni has been asked to testify in court July 2 in the trial of two men who are accused of making deep fake pornographic images using her face and posting them online, Italian news agency ANSA...}

\entryitemWithDescription{\hskip 0pt{}Apple's regulatory battles in Europe foreshadow what changes US antitrust suit may bring for users}{https://apnews.com/article/9a1d1cd341b4f00ededb5b56d707374a}{LONDON (AP) --- It'll likely take years before the U.S. government's massive antitrust lawsuit against Apple is resolved --- but the iPhone maker's troubles with European regulators offer a glimpse of what changes American customers may...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry says tabloids intercepted phone calls of mother, the late Princess Diana, and father}{https://apnews.com/article/4a41391501ace9b1a49affc85d211d80}{LONDON (AP) --- Prince Harry alleged Thursday that the publisher of The Sun tabloid unlawfully intercepted phone calls of his late mother, Princess Diana, and father, now King Charles III, as he sought to expand his privacy invasion...}

\entryitemWithDescription{\hskip 0pt{}As a frenzy of speculation grips the royal family, a look at recent events that have fueled rumors}{https://apnews.com/article/67954d14e934129ccb8584f53096d5f4}{LONDON (AP) --- 2024 hasn't been a good year for Britain's royals so far. First came the ``royal health shock'' headlines when palace officials announced that King Charles III and Kate, the Princess of Wales, both had health troubles. An...}

\entryitemWithDescription{\hskip 0pt{}Famed battleship USS New Jersey floating down Delaware River to Philadelphia for maintenance}{https://apnews.com/article/5017d97497d4628e6ce9258075e02235}{A famed battleship was floating down the Delaware River on Thursday as the USS New Jersey left its dock in Camden, New Jersey, on its way to the Philadelphia Navy Yard for extensive maintenance work. The vessel, guided by tugboats, was...}

\entryitemWithDescription{\hskip 0pt{}A hot air balloon crashed into a power line and caused a fire, but everyone is OK}{https://apnews.com/article/ca5fc6835065d92a0d1ce9bb5ae4e1ce}{ROCHESTER, Minn. (AP) --- Three people in a hot air balloon in Minnesota escaped largely unscathed after their basket clipped a power line, fell to the ground and caused a brush fire. A Minnesota Department of Transportation traffic...}

\entryitemWithDescription{\hskip 0pt{}In Japan, Ohtani's `perfect person' image could take a hit with firing of interpreter over gambling}{https://apnews.com/article/508e55ca5039ea8ce65cd4ed163ce725}{SEOUL, South Korea (AP) --- Shohei Ohtani is referred to in Japan as ``kanpeki no hito'' --- the perfect person --- because of his manners and impeccable behavior. That image may have taken a hit when the Dodgers fired his good friend and...}

\entryitemWithDescription{\hskip 0pt{}Rich cocoa prices hitting shoppers with bitter chocolate costs as Easter approaches}{https://apnews.com/article/ac64c923e13349c136df380ab5e1c842}{NEW YORK (AP) --- Sweet Easter baskets will likely come at a bitter cost this year for consumers as the price of cocoa climbs to record highs. Cocoa futures have surged this year, roughly doubling since the start of 2024. Rising...}

\entryitemWithDescription{\hskip 0pt{}Ohtani's interpreter is fired by Dodgers after allegations of `massive theft' from Japanese star}{https://apnews.com/article/a86471f296e986ad65634574da504e45}{SEOUL, South Korea. (AP) --- Shohei Ohtani's interpreter and close friend has been fired by the Los Angeles Dodgers following allegations of illegal gambling and theft from the Japanese baseball star. Interpreter Ippei Mizuhara, 39, was...}

\entryitemWithDescription{\hskip 0pt{}Mega Millions jackpot soars to nearly \$1 billion. Here's what to know}{https://apnews.com/article/1b2ab74a356187cafccda905a5936cad}{The winning numbers for a nearly \$1 billion Mega Millions lottery prize will be drawn Friday night, offering sudden riches to any lucky player who matches them and almost certain disappointment for everyone else. Since three months have...}

\entryitemWithDescription{\hskip 0pt{}1 of the few remaining survivors of the attack on Pearl Harbor has died at 102}{https://apnews.com/article/10e93bdb57168d091f2f5ebe85bbadca}{HONOLULU (AP) --- Richard C. ``Dick'' Higgins, one of the few remaining survivors of the Japanese attack on Pearl Harbor, has died, a family member said Wednesday. He was 102. Higgins died at home in Bend, Oregon, on Tuesday of natural...}