\entryitemWithDescription{\hskip 0pt{}Ex-Rep. Cawthorn fined after guilty plea over gun at airport}{https://apnews.com/article/0d9ae4a2146fb77bb9b8e247ef26cd95}{FILE - U.S. Rep. Madison Cawthorn, R-N.C., speaks to supporters and the media at his primary election night watch party in Hendersonville, N.C., on May 17, 2022. Cawthorn pleaded guilty Friday, May 5, 2023, to a misdemeanor after his...}

\entryitemWithDescription{\hskip 0pt{}Biden, Harris mark Cinco de Mayo with quesadilla, churros}{https://apnews.com/article/5e3e77bf4e934ac50fae32dd40f2d375}{President Joe Biden points to members of the media as he and Vice President Kamala Harris visit Taqueria Habanero restaurant on Friday, May 5, 2023, in Washington. (AP Photo/Evan Vucci) WASHINGTON (AP) --- President Joe Biden celebrated...}

\entryitemWithDescription{\hskip 0pt{}School dean who shot student sentenced for racketeering}{https://apnews.com/article/a454323264098bc931352c357eb3676b}{FILE - Shaun Harrison reacts as attorneys give closing arguments in his trial in Suffolk Superior Court in Boston, May 30, 2018. Harrison, a former dean at a Boston high school who is currently serving a 26-year state prison sentence for...}

\entryitemWithDescription{\hskip 0pt{}Germany: Man rescued from woods after sex game goes awry}{https://apnews.com/article/67e336bfce654bdaee8f45ed7ac91a9a}{BERLIN (AP) --- German police say a 51-year-old man who was left tied up in the woods when a sex game went awry had a lucky escape after a cyclist and a hunter heard his screams for help. Police said the man was discovered fully dressed...}

\entryitemWithDescription{\hskip 0pt{}Michigan's Upper Peninsula gets 2 feet of snow, a May record}{https://apnews.com/article/8dc92a1349422292b928df0111a32bc4}{FILE - Snowfall is shown in Marquette, Mich., Monday, May 1, 2023. Hundreds of people were without power in the city of Marquette much of Monday morning during the spring snow storm. A record May snowfall buried parts of Michigan's Upper...}

\entryitemWithDescription{\hskip 0pt{}1st lunar eclipse of 2023 dims full moon ever so slightly}{https://apnews.com/article/c16e3506486af2a1eec6b888b924e7c1}{Roof decorations depicting mythical sacred beasts are silhouetted near a penumbral lunar eclipse partially blocked by clouds during the early hours of Saturday, May 6, 2023 in Beijing. (AP Photo/Ng Han Guan) Stargazers in Asia and...}

\entryitemWithDescription{\hskip 0pt{}'Yellowstone' to end in November, sequel starts in December}{https://apnews.com/article/0edb2533a91802dba654bde71467423a}{This image released by Paramount Network shows Kevin Costner in a scene from "Yellowstone." The popular Paramount network drama ``Yellowstone'' will end in November with a batch of episodes that concludes its fifth season. (Paramount...}

\entryitemWithDescription{\hskip 0pt{}Ed Sheeran to perform 'Subtract' album on Apple Music Live}{https://apnews.com/article/60e49e3f916bb5e84d806e93e504747d}{Ed Sheeran performs at the 2023 New Orleans Jazz \& Heritage Festival on Saturday, April 29, 2023, at the Fair Grounds Race Course in New Orleans. (Photo by Amy Harris/Invision/AP) LOS ANGELES (AP) --- Ed Sheeran will put his new album on...}

\entryitemWithDescription{\hskip 0pt{}TurboTax customers to receive checks for \$141M settlement}{https://apnews.com/article/0c01cf25aa34693163886d135f7a6560}{This is a display of TurboTax on display in a Costco Warehouse in Pittsburgh on Thursday, Jan. 26, 2023. In a settlement agreement last year, TurboTax's owner Intuit Inc. was ordered to pay \$141 million to low-income consumers who were...}

\entryitemWithDescription{\hskip 0pt{}Ford recalls some vehicles for air bag inflator installation}{https://apnews.com/article/8ce2fb46909fa4f428e37881b8ec36d7}{FILE - A Ford sign is shown at a dealership in Springfield, Pa., Tuesday, April 26, 2022. Ford Motor Co. is recalling certain 2004 to 2006 Ranger vehicles, Friday, May 5, 2023, because replacement front passenger air bag inflators may...}

\entryitemWithDescription{\hskip 0pt{}Could AI pen 'Casablanca'? Screenwriters take aim at ChatGPT}{https://apnews.com/article/dc71c4cabcca0ee1b1afe0050d392a36}{Members of the The Writers Guild of America picket outside Fox Studios on Tuesday, May 2, 2023, in Los Angeles. Hollywood writers picketing to preserve pay and job security outside major studios and streamers braced for a long fight at...}

\entryitemWithDescription{\hskip 0pt{}US probes complaint that woman was trapped in flaming SUV}{https://apnews.com/article/04d55aba0e7ccdf84d9751d8da409a24}{FILE- The Dodge logo is seen on a new Dodge RAM 3500 Heavy Duty pickup trucks at sunset at a dealership in Springfield, Ill., Aug. 15, 2010. In documents posted Friday, May 5, 2023, U.S. safety regulators are investigating possible...}

\entryitemWithDescription{\hskip 0pt{}Dog Show 101: What's what at the Westminster Kennel Club}{https://apnews.com/article/7c47c4b53f8a614208cf8d45d4a2dbdd}{FILE - River, a German shepherd, competes for best in show at the 146th Westminster Kennel Club Dog Show, Wednesday, June 22, 2022, in Tarrytown, N.Y. To the casual viewer, competing at the Westminster Kennel Club dog show might look as...}