\entryitemWithDescription{\hskip 0pt{}A 41-year-old pelican and other animals wait for their food at Nepal's only zoo}{https://apnews.com/article/18130dbaf5075150bf7ac67e003222c1}{KATHMANDU, Nepal (AP) --- At the stroke of 10 every morning at the only zoo in Nepal, a 41-year-old pelican arrives at the entrance of the animal kitchen, waiting patiently for program officer Ganesh Koirala to arrive. The pelican knows...}

\entryitemWithDescription{\hskip 0pt{}WWE strikes deal with Logan Paul and KSI's Prime, will feature brand on center of ring mat}{https://apnews.com/article/f0614a7b1307060c332ca6d2a5cb6529}{WWE has struck a deal with Prime, the beverage brand of YouTube stars Logan Paul and KSI, that will see its logo featured on the center of a WWE wrestling ring mat, a first for the sports entertainment company. Financial terms of the...}

\entryitemWithDescription{\hskip 0pt{}A bill that could lead to a nation-wide TikTok ban is gaining momentum. Here's what to know}{https://apnews.com/article/5b5a685e8f1e19d22182d62526bf19b8}{TikTok once again finds itself in a precarious position. This time, it comes in the form of legislation that would ban the popular social media platform if it doesn't break ties with ByteDance, its Beijing-based parent company. On...}

\entryitemWithDescription{\hskip 0pt{}Pentagon study finds no sign of alien life in reported UFO sightings going back decades}{https://apnews.com/article/9a32aba88eb610cf16b2e9f0908704b3}{WASHINGTON (AP) --- A Pentagon study released Friday that examined reported sightings of UFOs over nearly the last century found no evidence of aliens or extraterrestrial intelligence, a conclusion consistent with past U.S. government...}

\entryitemWithDescription{\hskip 0pt{}Driver pleads guilty to reduced charge in Vermont crash that killed actor Treat Williams}{https://apnews.com/article/4e2d267505b885cec60b35a1d43f3cbf}{BENNINGTON, Vt. (AP) --- A Vermont man on Friday pleaded guilty to a reduced charge of negligent driving with death resulting in the June crash that killed actor Treat Williams. Ryan Koss, 35, who knew Williams, was given a one-year...}

\entryitemWithDescription{\hskip 0pt{}New Jersey high school asks court to overturn game it lost on blown call}{https://apnews.com/article/ed641fb2efb6c26714a7b39b72ff8f74}{TRENTON, N.J. (AP) --- New Jersey's acting education commissioner has rejected an appeal from a high school that lost a state basketball tournament game when referees wrongly overturned a buzzer-beating basket, but the school is taking a...}

\entryitemWithDescription{\hskip 0pt{}United Airlines plane rolls off runway in Houston}{https://apnews.com/article/0416c57f1ba5a5a26312554a9fa644ea}{HOUSTON (AP) --- Passengers had to be evacuated from a United Airlines plane after it rolled off a runway and got stuck in the grass in Houston Friday morning. No injuries were reported among the 160 passengers and six crew members...}

\entryitemWithDescription{\hskip 0pt{}Natalie Portman and Benjamin Millepied divorce after 11 years of marriage}{https://apnews.com/article/3d929091e9d905f1602221ad80244791}{NEW YORK (AP) --- Natalie Portman and Benjamin Millepied have divorced after 11 years of marriage and two children. The Oscar-winning actor and Millepied, a choreographer and director, finalized the divorce last month in France, where...}

\entryitemWithDescription{\hskip 0pt{}WWE, a social media powerhouse, tops 100 million subscribers on YouTube}{https://apnews.com/article/0ba7fec79d23a3da9382d47eb2c4b120}{As WWE gears up for its biggest annual premium live event next month, the company continues to harness the power of its social media presence to reach its fans. A key component of that strategy is YouTube, where WWE has hit an important...}

\entryitemWithDescription{\hskip 0pt{}Former US Rep. George Santos, expelled from Congress, says he is running again}{https://apnews.com/article/ebf8c0c87d939ed6def387ab1b56f884}{WASHINGTON (AP) --- Former U.S. Rep. George Santos, who was expelled from Congress in December and faces federal charges of defrauding donors to his 2022 campaign, has announced he is running for the House again. Santos, a Republican who...}

\entryitemWithDescription{\hskip 0pt{}Military's Ospreys are cleared to return to flight, 3 months after latest fatal crash in Japan}{https://apnews.com/article/549cb6173cede2f4ea04b994d67e8603}{WASHINGTON (AP) --- The Osprey, a workhorse aircraft vital to U.S. military missions, has been approved to return to flight after an ``unprecedented'' part failure led to the deaths of eight service members in a crash in Japan in...}

\entryitemWithDescription{\hskip 0pt{}`Dragon Ball' creator Akira Toriyama dies at 68}{https://apnews.com/article/0b2016bf985e1854d3cbcb2985d6e922}{TOKYO (AP) --- Akira Toriyama, the creator of the best-selling Dragon Ball and other popular anime who influenced Japanese comics, has died, his studio said Friday. He was 68. Toriyama's Dragon Ball manga series, which started in 1984, is...}

\entryitemWithDescription{\hskip 0pt{}Civil rights activist Naomi Barber King, a sister-in-law to the Rev. Martin Luther King, Jr., dies}{https://apnews.com/article/5fe722c29168e2a38a2e3cb8c9a65b0b}{ATLANTA (AP) --- Naomi Barber King, a civil rights activist who was married to the younger brother of the Rev. Martin Luther King, Jr., has died at age 92. She died in Atlanta on Thursday, according to family members who issued a...}