\entryitemWithDescription{\hskip 0pt{}Report says former University of Florida president Ben Sasse spent \$1.3 million on social events}{https://apnews.com/article/158b26bb0ba8aa770919904c82221ad1}{GAINESVILLE, Fla. (AP) --- Former University of Florida president Ben Sasse spent over \$1.3 million on private catering for lavish dinners, football tailgates and extravagant social functions in his first year on the job, according to a...}

\entryitemWithDescription{\hskip 0pt{}A man pleads guilty in a shooting outside then-US Rep. Zeldin's New York home}{https://apnews.com/article/1e8afa3e8aa119bb487ce5b80984bd7b}{RIVERHEAD, N.Y. (AP) --- A 20-year-old gang member pleaded guilty in a drive-by shooting that wounded two rival gang members in front of the New York home of then-U.S. Rep. Lee Zeldin, authorities said. Noah Green pleaded guilty Thursday...}

\entryitemWithDescription{\hskip 0pt{}Driver charged with killing NHL's Johnny Gaudreau and his brother had .087 blood-alcohol level}{https://apnews.com/article/68013332a06de68ffb8eb498cd4b99dd}{PHILADELPHIA (AP) --- The driver charged with killing NHL hockey player Johnny Gaudreau and his brother Matthew as they bicycled on a rural road had a blood-alcohol level of .087, above the .08 legal limit in New Jersey, a prosecutor said...}

\entryitemWithDescription{\hskip 0pt{}2 men charged with stealing a famous Banksy image from a London art gallery}{https://apnews.com/article/d5a8000428a79451e62f7aa04ab716fd}{LONDON (AP) --- Two men have been charged with burglary over the theft of an artwork by street artist Banksy from a London gallery, police said Friday. The Metropolitan Police force said Larry Fraser, 47, and James Love, 53, are alleged...}

\entryitemWithDescription{\hskip 0pt{}Cook scores 3 TDs to help Bills rout Dolphins 31-10, Tagovailoa leaves with concussion}{https://apnews.com/article/53ccc2cc4c1c8185d78940054c9e8ed8}{MIAMI GARDENS, Fla. (AP) --- James Cook caught a touchdown pass and ran for two scores and the Buffalo Bills routed Miami 31-10 on Thursday night, with Dolphins quarterback Tua Tagovailoa leaving early because of a concussion. Tagovailoa...}

\entryitemWithDescription{\hskip 0pt{}Actor Chad McQueen, son of Steve McQueen, dies at 63}{https://apnews.com/article/46564c50b5cefee553273ad0e932318b}{Chad McQueen, an actor known for his performances in the ``Karate Kid'' movies and the son of the late actor and race car driver Steve McQueen, has died. He was 63. McQueen's attorney and friend Arthur H. Barens confirmed to The...}

\entryitemWithDescription{\hskip 0pt{}Brazil Indigenous group hails a sacred cloak's homecoming after nearly four centuries in Europe}{https://apnews.com/article/6fbf5074e4b332b4a795e94ed44064b5}{RIO DE JANEIRO (AP) --- Indigenous chants and the rattle of maracas resounded Thursday in a Rio de Janeiro park, where Brazil's Tupinambá people gathered to celebrate the homecoming of a sacred cloak absent for some 380 years. Made of...}

\entryitemWithDescription{\hskip 0pt{}Francis Ford Coppola sues Variety over story alleging `Megalopolis' misconduct}{https://apnews.com/article/f4efba577ae8f25f1bdac4c259ffaecc}{LOS ANGELES (AP) --- Francis Ford Coppola has sued Variety, saying that a July story that said he ran an unprofessional set with impunity and touching and tried to kiss female extras during the production of his film ``Megalopolis'' was...}

\entryitemWithDescription{\hskip 0pt{}`The Roaring Lion' portrait of Winston Churchill stolen from Canadian hotel tracked down in Italy}{https://apnews.com/article/55f30b9f63b95f24fa4280451620cde3}{OTTAWA, Ontario (AP) --- Canadian police say a renowned portrait of Winston Churchill that was reported stolen from an Ottawa hotel has been tracked down in Italy. Investigators will travel to Rome later this month to retrieve the 1941...}

\entryitemWithDescription{\hskip 0pt{}Cardi B reveals birth of third child with Offset and says the newborn is the `prettiest lil thing'}{https://apnews.com/article/f06ab9b383345dc13118792a94b96fde}{LOS ANGELES (AP) --- Cardi B has welcomed her third child into the world. The Grammy winner announced on social media Thursday that she gave birth over the weekend. She posted photos of her holding and breastfeeding the newborn in a...}

\entryitemWithDescription{\hskip 0pt{}Firm offers bets on congressional elections after judge clears way; appeal looms}{https://apnews.com/article/882f1e6e4f434f0e6ac6e5985a5583ce}{ATLANTIC CITY, N.J. (AP) --- You can now do more than just vote in this fall's Congressional elections: You can bet on them, too. A startup company on Thursday began taking what amounts to bets on the outcome of the November Congressional...}

\entryitemWithDescription{\hskip 0pt{}Wreck of French steamship that sunk in 1856 discovered off New England coast}{https://apnews.com/article/7f2b5126562f06c0b7425c69c9641cb3}{PORTLAND, Maine (AP) --- The French steamship Le Lyonnais, a marvel for its time, was feared lost forever when a maritime disaster in 1856 sent her to the bottom of the ocean off Massachusetts. Generations later, a marine salvage crew is...}

\entryitemWithDescription{\hskip 0pt{}DHL sues MyPillow, alleging company founded by Mike Lindell owes \$800,000}{https://apnews.com/article/9538c00cb01f2b251b0aa62f8b2bf02a}{MINNEAPOLIS (AP) --- Package delivery company DHL is suing MyPillow, alleging the company synonymous with its founder, chief pitchman and election denier Mike Lindell owes nearly \$800,000 for unpaid bills. The lawsuit is the latest legal...}