\entryitemWithDescription{\hskip 0pt{}Messi and Putellas voted best players at FIFA awards again}{https://apnews.com/article/d10bea92bd572a2b6326f0a1a15f38fd}{Spanish soccer player Alexia Putellas poses on the green carpet before the ceremony of the Best FIFA Football Awards in Paris, France, Monday, Feb. 27, 2023. (AP Photo/Michel Euler) PARIS (AP) --- World Cup winner Lionel Messi edged...}

\entryitemWithDescription{\hskip 0pt{}TikTok banned on all Canadian government mobile devices}{https://apnews.com/article/43b27a80a1c2bf3b55e5ccf2ce573684}{Canadian Prime Minister Justin Trudeau answers questions at an announcement in Mississauga, Ontario, Monday, Feb. 27, 2023. Canada announced Monday it is banning TikTok from all government-issued mobile devices, reflecting widening...}

\entryitemWithDescription{\hskip 0pt{}Ex-Cardinal McCarrick asks court to dismiss sex assault case}{https://apnews.com/article/6e3a436d2382f4f83e395ceca273f172}{FILE - Former Washington Archbishop, Cardinal Theodore McCarrick listens during a press conference in Washington, May 16, 2006. Lawyers for former Roman Catholic Cardinal McCarrick filed a motion Monday, Feb. 27, 2023, to dismiss a case...}

\entryitemWithDescription{\hskip 0pt{}Mexican president disparages pro-democracy demonstrators}{https://apnews.com/article/02136caaf4142f35c636321bd4ea1d58}{FILE - Mexican President Andres Manuel Lopez Obrador speaks during the North America Summit, at the National Palace in Mexico City, Jan. 10, 2023. Obrador said on Feb. 23, 2023 that he\textquotesingle ll sign a new bill into law that will...}

\entryitemWithDescription{\hskip 0pt{}US women's soccer coach paid 27\% as much as men's coach}{https://apnews.com/article/0d14f9a1796030030f283160aa47940c}{U.S. coach Vlatko Andonovski, right, and forward Megan Rapinoe (15) laugh after the team\textquotesingle s win against Canada during a SheBelieves Cup soccer match Thursday, Feb. 16, 2023, in Orlando, Fla. (AP Photo/Phelan M. Ebenhack...}

\entryitemWithDescription{\hskip 0pt{}Novak Djokovic breaks record for most weeks ranked No. 1}{https://apnews.com/article/6a8b492c05bbec032c2e2485b2394cfb}{FILE - Novak Djokovic of Serbia plays a backhand return to Andrey Rublev of Russia during their quarterfinal match at the Australian Open tennis championship in Melbourne, Australia, Wednesday, Jan. 25, 2023. Djokovic broke the record for...}

\entryitemWithDescription{\hskip 0pt{}Yellen visits Ukraine, underscores US economic support}{https://apnews.com/article/bac3c5470b9c1eb0e459abefc5e34ff4}{Ukrainian President Volodymyr Zelenskyy, left, and U.S. Treasury Secretary Janet Yellen shake hands during their meeting in Kyiv, Ukraine, Monday, Feb. 27, 2023. (Ukrainian Presidential Press Office via AP) KYIV, Ukraine (AP) --- U.S...}

\entryitemWithDescription{\hskip 0pt{}Houston, Alabama top AP Top 25; Marquette climbing, Pitt in}{https://apnews.com/article/d84220ea784756eab615e9d783d75a19}{Houston\textquotesingle s Jarace Walker tries to keep the ball from East Carolina\textquotesingle s RJ Felton (3) and Brandon Johnson, right, during an NCAA college basketball game in Greenville, N.C., Saturday, Feb. 25, 2023. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}Defense at Murdaugh trial says 2 shooters; jury to see scene}{https://apnews.com/article/7c8bde24403b63fc3cf5847705800590}{Jurors in Alex Murdaugh's murder trial in the shooting deaths of his wife and son will get to visit the South Carolina home where the killings took place. Alex Murdaugh listens to testimony during his double murder trial at the Colleton...}

\entryitemWithDescription{\hskip 0pt{}DeSantis takes over Disney district, punishing company}{https://apnews.com/article/36ec16b56ac6e72b9efcce26defdd0d8}{FILE - Florida Gov. Ron DeSantis speaks, Feb. 15, 2023, at Palm Beach Atlantic University in West Palm Beach, Fla. Gov. DeSantis has signed a bill to give himself control of Walt Disney World's self-governing district, punishing the...}

\entryitemWithDescription{\hskip 0pt{}'Take It Down:' a tool for teens to remove explicit images}{https://apnews.com/article/0f31fbd7ab814f8cdb52ca2df6a46123}{A young man checks his phone by the Tagus river at Lisbon\textquotesingle s Comercio square on a sunny winter day, Monday, Jan. 30, 2023. (AP Photo/Armando Franca) ``Once you send that photo, you can\textquotesingle t take it back,'' goes...}

\entryitemWithDescription{\hskip 0pt{}Democrat Elissa Slotkin to seek Michigan's open Senate seat}{https://apnews.com/article/89bdd39d53342b6ed6ccf107d4f2b1d8}{FILE - House Homeland Security Committee member Rep. Elissa Slotkin, D-Mich., asks a question during a House Homeland Security Committee hearing on "Worldwide Threats to the Homeland", at the Capitol in Washington, Nov. 15, 2022. Slotkin...}

\entryitemWithDescription{\hskip 0pt{}Trans people face 'horrifying' rhetoric at statehouses}{https://apnews.com/article/bb6bc7f6e7d5d733c081b2b87e958171}{Gwendolyn Herzig speaks to a reporter at Park West Pharmacy in Little Rock, Arkansas on Wednesday, Feb. 22, 2023. Herzig, who is transgender, was asked about her genitalia by an Arkansas lawmaker when she testified about a bill...}