\entryitemWithDescription{\hskip 0pt{}Firm offers bets on congressional elections after judge clears way; appeal looms}{https://apnews.com/article/882f1e6e4f434f0e6ac6e5985a5583ce}{ATLANTIC CITY, N.J. (AP) --- You can now do more than just vote in this fall's Congressional elections: You can bet on them, too. A startup company on Thursday began taking what amounts to bets on the outcome of the November Congressional...}

\entryitemWithDescription{\hskip 0pt{}Wreck of French steamship that sunk in 1856 discovered off New England coast}{https://apnews.com/article/7f2b5126562f06c0b7425c69c9641cb3}{PORTLAND, Maine (AP) --- The French steamship Le Lyonnais, a marvel for its time, was feared lost forever when a maritime disaster in 1856 sent her to the bottom of the ocean off Massachusetts. Generations later, a marine salvage crew is...}

\entryitemWithDescription{\hskip 0pt{}Solar storms may cause faint auroras overnight in parts of Northern Hemisphere}{https://apnews.com/article/7979db50fb734fee6ed343426d72469f}{NEW YORK (AP) --- Solar storms may bring faint but visible auroras to the Northern Hemisphere starting late Thursday and extending into early Friday morning. But, experts say, don't expect power grids and communications to be disrupted...}

\entryitemWithDescription{\hskip 0pt{}DHL sues MyPillow, alleging company founded by Mike Lindell owes \$800,000}{https://apnews.com/article/9538c00cb01f2b251b0aa62f8b2bf02a}{MINNEAPOLIS (AP) --- Package delivery company DHL is suing MyPillow, alleging the company synonymous with its founder, chief pitchman and election denier Mike Lindell owes nearly \$800,000 for unpaid bills. The lawsuit is the latest legal...}

\entryitemWithDescription{\hskip 0pt{}Kylian Mbappé wins French league ruling for \$61 million in unpaid wages from PSG}{https://apnews.com/article/6a675b27b2813a255cf66f2f2137ed11}{The French league's legal commission has ordered Paris Saint-Germain to pay Kylian Mbappé the 55 million euros (\$61 million) in unpaid wages that he claims he's entitled to, the league said Thursday. The league confirmed the decision to...}

\entryitemWithDescription{\hskip 0pt{}McDonald's extends \$5 deal through December to keep customers coming}{https://apnews.com/article/f8bff378ff06140cdb5a9e519c33184c}{McDonald's is extending its \$5 value meal until December at most U.S. stores, a move that rivals are likely to follow. McDonald's introduced the deal in June after a disappointing first quarter that saw fewer U.S. visits and lower...}

\entryitemWithDescription{\hskip 0pt{}Reggie Bush was at his LA-area home when 3 male suspects attempted to break in}{https://apnews.com/article/c4345ac59baa62e77f3699ce87e27e10}{LOS ANGELES (AP) --- Former football star Reggie Bush was at his Encino home Tuesday night when three male suspects attempted to break in, the Los Angeles Times reported Wednesday. ``Everyone is safe,'' Bush said in a text message to the...}

\entryitemWithDescription{\hskip 0pt{}Pair of rare Amur tiger cubs debuting at Minnesota Zoo are raising hopes for the endangered species}{https://apnews.com/article/746a1b71e731dec1fa7c8256b45cc06a}{APPLE VALLEY, Minn. (AP) --- A pair of rare Amur tiger cubs are making their public debut at the Minnesota Zoo, raising hopes for preserving an endangered species that's native to far eastern Russia and northern China. Andrei and Amaliya...}

\entryitemWithDescription{\hskip 0pt{}Two Black women could make US Senate history this election. But they strive to make a difference}{https://apnews.com/article/54c411e0a0f4d3d84de95246b09be304}{WASHINGTON (AP) --- The Senate has the potential for history-making this fall, with not one, but two, Black women possibly elected to the chamber, a situation never seen in America since Congress was created more than 200 years ago...}

\entryitemWithDescription{\hskip 0pt{}From Chinese to Italians and beyond, maligning a culture via its foods is a longtime American habit}{https://apnews.com/article/e857fcc1ca18c77d1c890ec5e41f4f65}{NEW YORK (AP) --- It's a practice that's about as American as apple pie --- accusing immigrant and minority communities of engaging in bizarre or disgusting behaviors when it comes to what and how they eat and drink, a kind of shorthand...}

\entryitemWithDescription{\hskip 0pt{}Jon Bon Jovi helps talk woman down from ledge on Nashville bridge}{https://apnews.com/article/0079c31b85a35f32c4ecaf31ab23eabc}{NASHVILLE, Tenn. (AP) --- Rock and Roll Hall of Famer Jon Bon Jovi and a video production assistant persuaded a woman standing on the ledge of a pedestrian bridge in Nashville to come back over the railing to safety. Police say the...}

\entryitemWithDescription{\hskip 0pt{}Frankie Beverly, the Maze singer who inspired generations of fans with lasting anthems, dies at 77}{https://apnews.com/article/6571001c1db819c2255045fca5ca504e}{NEW ORLEANS (AP) --- Frankie Beverly, who with his band Maze inspired generations of fans with his smooth, soulful voice and lasting anthems including ``Before I Let Go,'' has died. He was 77. His family said in a post on the band's...}

\entryitemWithDescription{\hskip 0pt{}Justin Timberlake reaches plea deal to resolve drunken driving case, AP source says}{https://apnews.com/article/e274512147f2bea6eb44c6c1b713c175}{NEW YORK (AP) --- Justin Timberlake is scheduled to enter a new plea Friday in his drunken driving case in New York's Hamptons, prosecutors said. Details of the plea weren't disclosed, but a person with knowledge of the deal said...}