\entryitemWithDescription{\hskip 0pt{}Robbie Knievel, daredevil son of Evel Knievel, dies at 60}{https://apnews.com/article/bdc7c49dc0ebf815d99fb0a61b77bfb3}{FILE - Robbie Knievel gives a thumbs up after jumping a train at the Texas State Railroad Park in Palestine, Texas on Feb. 23, 2000. Knievel, an American stunt performer, died early Friday at a hospice in Reno, Nev., with his daughters at...}

\entryitemWithDescription{\hskip 0pt{}Yellen tells Congress US expected to hit debt limit Thursday}{https://apnews.com/article/cf6cf1dcfc3d0d81fb5a20f8ad442f7a}{FILE - Treasury Secretary Janet Yellen speaks with reporters during a visit to the Virginia Innovation Partnership Corporation incubator at the Center for Innovative Technology campus in Herndon, Va., Oct. 21, 2022. Yellen has notified...}

\entryitemWithDescription{\hskip 0pt{}NFL All-Pros: Kelce, Jefferson unanimous; 16 first-timers}{https://apnews.com/article/efe23feab2088737a01ae04eb2a1e9ce}{Kansas City Chiefs quarterback Patrick Mahomes (15) and tight end Travis Kelce (87) celebrate during the first half of an NFL football game against the Seattle Seahawks Saturday, Dec. 24, 2022, in Kansas City, Mo. (AP Photo/Ed Zurga...}

\entryitemWithDescription{\hskip 0pt{}Lisa Marie Presley will be buried at Graceland next to son}{https://apnews.com/article/b5ecc265ceb991bd876bf1f06843b0a9}{FILE - Lisa Marie Presley stands next to her childhood crib displayed with other mementos in the new exhibit "Elvis Through His Daughter\textquotesingle s Eyes," at Graceland in Memphis, Tenn., Jan. 31, 2012. She was born on Feb. 1, 1968...}

\entryitemWithDescription{\hskip 0pt{}School searched 1st-grader's backpack before teacher shot}{https://apnews.com/article/943c4b0ec79c5c7a7c0ebd6acd2f04ec}{Newport News Superintendent of Schools George Parker makes remarks on the safety parameters currently in place at the city\textquotesingle s schools during a press conference at the Newport News School Administration Building in Newport...}

\entryitemWithDescription{\hskip 0pt{}\$1.35B Mega Millions prize drawing set for Friday night}{https://apnews.com/article/99dfe9740d2ec3ca739f075a840b34b1}{A customer at the Cranberry Super Mini Mart in Cranberry, Pa., shows her Mega Millions ticket on Thursday, Jan. 12, 2023. (AP Photo/Gene J. Puskar) DES MOINES, Iowa (AP) --- Mega Millions players will have another chance Friday night to...}

\entryitemWithDescription{\hskip 0pt{}Biden special counsel deepens Justice Dept. in politics fray}{https://apnews.com/article/dd1f488797b060d93ace7c9752c0ad71}{FILE - Then-Principal Associate Deputy Attorney General Robert Hur speaks during a press briefing at the White House in Washington, July 27, 2017. Hur, the former Trump-appointed U.S. attorney in Maryland, will lead the investigation...}

\entryitemWithDescription{\hskip 0pt{}Djokovic receives warm welcome in Melbourne return}{https://apnews.com/article/1e17d6d04703ba8c30b870b01ea0fc9c}{Serbia\textquotesingle s Novak Djokovic swings his towel as he dances between games during an exhibition match against Australia\textquotesingle s Nick Kyrgios on Rod Laver Arena ahead of the Australian Open tennis championship in...}

\entryitemWithDescription{\hskip 0pt{}Russia says it took Soledar, Ukraine denies its capture}{https://apnews.com/article/6b690278cfa76d27d9dc0577ca021a6a}{FILE - Ukrainian army Grad multiple rocket launcher fires rockets at Russian positions in the frontline near Soledar, Donetsk region, Ukraine, Wednesday, Jan. 11, 2023. Russia\textquotesingle s Defense Ministry said Friday Jan. 13, 2023...}

\entryitemWithDescription{\hskip 0pt{}Rifts in Russian military command seen amid Ukraine fighting}{https://apnews.com/article/f2e3f238c9d8ea294e0ed8b1905caba4}{FILE - Smoke billows during fighting between Ukrainian and Russian forces in Soledar, Donetsk region, Ukraine, Wednesday, Jan. 11, 2023. Soledar and Bakhmut again highlighted a bitter rift between the top military brass and Yevgeny...}

\entryitemWithDescription{\hskip 0pt{}Nighttime Israeli arrests haunt Palestinian kids, families}{https://apnews.com/article/68f7590fe86ca7dc7b37e5775e41d711}{Yousef Mesheh, 15, holds a portrait of his brother, Wael in the bedroom where they were sleeping when Israeli forces stormed into their home at 3.a.m., in the Balata Refugee Camp in the northern West Bank, Tuesday, Jan. 10, 2023. They...}

\entryitemWithDescription{\hskip 0pt{}Trump Organization fined \$1.6 million for tax fraud}{https://apnews.com/article/e2f1d01525dafb64be8738c8b4f32085}{Prosecuting and Defense attorneys wait during the sentencing of the Trump Organization at Manhattan Criminal Court on Friday, Jan. 13, 2023, in New York. (Adam Gray/DailyMail via AP, Pool) NEW YORK (AP) --- Donald Trump's company was...}

\entryitemWithDescription{\hskip 0pt{}Wall Street ends higher as company earnings season kicks off}{https://apnews.com/article/b3917258cc51e96adc12ec6849318c46}{People walk past the New York Stock Exchange on Wednesday, June 29, 2022 in New York. Stocks are opening lower across the board on Wall Street, Tuesday, July 5, and crude oil prices are dropping again. Treasury yields also fell as traders...}
