\entryitemWithDescription{\hskip 0pt{}Duke's Scheyer wants the ACC to implement measures to prevent court-storming after Filipowski injury}{https://apnews.com/article/5311b9ab13cab19aee996f70db0bec7a}{Duke coach Jon Scheyer wants the Atlantic Coast Conference to implement measures to prevent court-storming after star big man Kyle Filipowski was hobbled following a collision with a fan during a weekend loss at Wake Forest. Scheyer said...}

\entryitemWithDescription{\hskip 0pt{}Case possibly containing Wayne Gretzky rookie cards sells for \$3.7M at auction}{https://apnews.com/article/66c276443a86e2da698e26bee08519eb}{REGINA, Saskatchewan (AP) --- A case of old hockey cards possibly containing the game's Great One has fetched more than \$3.7 million after it was discovered in a Regina home. Heritage Auctions says the winning bidder bought the case of...}

\entryitemWithDescription{\hskip 0pt{}Eagles' Don Henley quizzed at lyrics trial about time a naked 16-year-old girl overdosed at his home}{https://apnews.com/article/dae5d3c41ae5ad1071a06dbc74a957d7}{NEW YORK (AP) --- Don Henley was confronted in a New York courtroom Monday about a seamy episode from his past: his 1980 arrest after authorities said they found drugs and a naked 16-year-old girl suffering from an overdose at the Eagles...}

\entryitemWithDescription{\hskip 0pt{}Proof copy of Harry Potter book, bought for pennies in 1997, sells for more than \$13,000}{https://apnews.com/article/dacbae821f3a31a7fd9d3e3276d06850}{LONDON (AP) --- A proof copy of the first Harry Potter novel that was bought for pennies in a second-hand bookshop almost 30 years ago has sold at auction for 11,000 pounds (\$13,900.) British auctioneers Hanson's said Monday that the...}

\entryitemWithDescription{\hskip 0pt{}Grenada police say a US couple whose catamaran was hijacked were likely thrown overboard and died}{https://apnews.com/article/94a4ced4f52a1bf537abb813dd8b2623}{SAN JUAN, Puerto Rico (AP) --- Police in Grenada said Monday that they believe an elderly U.S. couple aboard their catamaran that was hijacked by three escaped prisoners last week were killed and thrown into the Caribbean Sea. The...}

\entryitemWithDescription{\hskip 0pt{}From gold records to gold coins. George Michael is now honored with a commemorative minting}{https://apnews.com/article/4427645ce4420724de64a6cfe6f76df2}{LONDON (AP) --- You gotta have more than ``Faith'' to pocket the new George Michael coin. A commemorative minting of coins that rolled out on Monday ranged in price from a couple of banknotes to a small fortune as the late musician...}

\entryitemWithDescription{\hskip 0pt{}French actor Gérard Depardieu faces another sexual assault complaint over alleged groping}{https://apnews.com/article/2b6036dd2b1f5a889a73a4f9c62e2eb5}{PARIS (AP) --- French actor Gérard Depardieu faces another complaint of sexual assault, this time from a movie decorator who alleges he groped her during filming in 2021. In the complaint to the Paris prosecutor's office, she accuses the...}

\entryitemWithDescription{\hskip 0pt{}`The Bear,' `Spider-Verse' among the early winners at Producers Guild awards}{https://apnews.com/article/72ae7634f712b94004edb536df19854a}{BEVERLY HILLS, Calif. (AP) --- With two weeks to go before the Oscars, ``Oppenheimer'' looks unstoppable. Director and producer Christopher Nolan's tale of the life of J. Robert Oppenheimer and the birth of the atomic age won the top...}

\entryitemWithDescription{\hskip 0pt{}Former NFL MVP Cam Newton involved in scuffle at 7-on-7 youth football tournament in Atlanta}{https://apnews.com/article/821f55f5a2477351f8df69b0717ae29b}{A video surfaced Sunday that appeared to show 2015 NFL Most Valuable Player Cam Newton being involved in a scuffle at a 7-on-7 youth football tournament in Atlanta. The video shows Newton, wearing one of his custom-made hats, being shoved...}

\entryitemWithDescription{\hskip 0pt{}Furor erupts over Ronaldo's apparent obscene taunt in Saudi league match}{https://apnews.com/article/77c0a627f6a16d3d3176c6a4e7434457}{RIYADH, Saudi Arabia (AP) --- Cristiano Ronaldo has come under heavy criticism after seemingly making an offensive gesture following Al Nassr's 3-2 victory over Al Shabab in a Saudi Pro League match on Sunday. The Portuguese star scored a...}

\entryitemWithDescription{\hskip 0pt{}`Past Lives,' `American Fiction' and `The Holdovers' are big winners at Independent Spirit Awards}{https://apnews.com/article/d9f5b3d68ba9619873015be4670b69ce}{Celine Song's quiet romance ``Past Lives'' won two of the biggest awards at the Film Independent Spirit Awards Sunday afternoon, including best feature and best director. Other big winners were Cord Jefferson's comedic satire `` American...}

\entryitemWithDescription{\hskip 0pt{}Daniel Suarez edges Blaney, Busch in thrilling 3-wide finish to claim Cup Series win at Atlanta}{https://apnews.com/article/729f777af289b5d082f7e828167c3a59}{HAMPTON, Ga. (AP) --- Daniel Suarez edged Ryan Blaney and Kyle Busch in a three-wide finish to win a crashed-filled NASCAR Cup Series race at Atlanta Motor Speedway on Sunday. Busch, who won Saturday's Trucks race, moved to the middle...}

\entryitemWithDescription{\hskip 0pt{}AT\&T will give \$5 to customers hit by cellphone network outage}{https://apnews.com/article/5fca100330ed57960ac43dc4e3240a21}{DALLAS (AP) --- AT\&T says it will give affected customers \$5 each to compensate for last week's cellphone network outage that left many without service for hours. The Dallas-based company said on its website that customers will get...}