\entryitemWithDescription{\hskip 0pt{}Instagram begins blurring nudity in messages to protect teens and fight sexual extortion}{https://apnews.com/article/7bea9b1244ea023fb85265672bcd6560}{LONDON (AP) --- Instagram said it's deploying new new tools to protect young people and combat sexual extortion, including a feature that will automatically blur nudity in direct messages. The social media platform said in a blog post...}

\entryitemWithDescription{\hskip 0pt{}No inflation here: Affordable Masters' menu still includes \$1.50 pimento cheese sandwiches}{https://apnews.com/article/ae548773b145cd203a82b072a921a0ba}{AUGUSTA, Ga. (AP) --- Jordan Janes knew when he arrived at the Masters for the first time a pimento cheese sandwich was a must-have. He wanted to soak in the Augusta National experience, and that has long included the iconic staple on the...}

\entryitemWithDescription{\hskip 0pt{}In Russia's Far East, a new heavy-lift rocket blasts off into space after two aborted launches}{https://apnews.com/article/2efeca4d3e9b2add42865bf6c6d3b0a6}{MOSCOW (AP) --- Russia on Thursday successfully test-launched a new heavy-lift rocket from its Far Eastern space complex, a lift-off that comes after two aborted attempts earlier this week. The first attempt to launch the Angara-A5 rocket...}

\entryitemWithDescription{\hskip 0pt{}Hawaii-born sumo champion Akebono Taro dies at the age of 54 in Japan}{https://apnews.com/article/6f764e23de505ab6eed3257e33e9e113}{TOKYO (AP) --- Hawaii-born Akebono, one of the greats of sumo wrestling and a former grand champion, has died. He was 54. He was the first foreign-born wrestler to reach the level of ``yokozuna'' --- or grand champion --- in Japan. ``It...}

\entryitemWithDescription{\hskip 0pt{}Universal Pictures teases `Wicked' and announces `Five Nights at Freddy's 2'}{https://apnews.com/article/e9288f25a4adac03ff5ba5d0d321528e}{LAS VEGAS (AP) --- With the dust settled from a big 2023, winning best picture and topping the box office, Universal Pictures is looking to the future. The studio's upcoming releases include the big screen adaptation of ``Wicked,'' ``...}

\entryitemWithDescription{\hskip 0pt{}10 emerging writers each receive \$50,000 Whiting Awards}{https://apnews.com/article/fdd604ee38faaf573a0f458f380b3b64}{NEW YORK (AP) --- Fiction writer Aaliyah Bilal, a National Book Award finalist last fall for her story collection ``Temple Folk,'' is among 10 winners of the Whiting Award for emerging authors. Bilal and the other recipients, who include...}

\entryitemWithDescription{\hskip 0pt{}Water pouring out of rural Utah dam through 60-foot crack, putting nearby town at risk}{https://apnews.com/article/230d25194b967f3b2bcd1e1c050517b8}{SALT LAKE CITY (AP) --- Workers hurriedly tried to shore up a rural Utah dam after a 60-foot (18-meter) crack opened and sent water pouring into a creek and endangering the 1,700 residents of a downstream town. State and local officials...}

\entryitemWithDescription{\hskip 0pt{}Kansas City Chiefs' Rashee Rice facing aggravated assault charge after high-speed crash in Dallas}{https://apnews.com/article/d71cfd66fabfc151111d67ea1bfa0f74}{DALLAS (AP) --- Dallas police said Wednesday that Kansas City Chiefs' wide receiver Rashee Rice faces charges including aggravated assault after he and another speeding driver of a sports car caused a chain-reaction crash on a Dallas...}

\entryitemWithDescription{\hskip 0pt{}Rescuers search off Northern California coast for young gray whale entangled in gill net}{https://apnews.com/article/e82b7ce6e30a6ea84fdee05d20b3214f}{SAN FRANCISCO (AP) --- Rescuers were searching Wednesday for a gray whale last spotted off Northern California's coast with its tail entangled in a massive gill net. The 30-foot (9-meter) whale was spotted Tuesday near San Francisco...}

\entryitemWithDescription{\hskip 0pt{}Guests at the state dinner for Japan's prime minister will share the feel of walking over a koi pond}{https://apnews.com/article/c323a1a6137298ec2d401a9d82a7e1c8}{WASHINGTON (AP) --- Forget about a red carpet. Jill Biden is honoring the friendship between the United States and Japan by transforming the State Floor of the White House into a ``vibrant spring garden'' for the state dinner she and...}

\entryitemWithDescription{\hskip 0pt{}Margot Robbie making `Monopoly' movie and Blumhouse reviving `Blair Witch'}{https://apnews.com/article/c92223edb54e1fd7565476c911a17c3a}{LAS VEGAS (AP) --- Margot Robbie has her sights on another toy. The `` Barbie '' producer and star is making a Monopoly movie, with Hasbro and Lionsgate behind it, the companies announced Wednesday at the CinemaCon conference in Las...}

\entryitemWithDescription{\hskip 0pt{}Japan is giving Washington 250 new cherry trees to replace those to be lost in construction work}{https://apnews.com/article/483e8a004eb197acb5363d619f3e6529}{WASHINGTON (AP) --- Japan is giving the United States 250 new cherry trees to help replace the hundreds that are being ripped out this summer as construction crews work to repair the crumbling seawall around the capital's Tidal Basin...}

\entryitemWithDescription{\hskip 0pt{}Ford recalls nearly 43,000 SUVs due to gas leaks that can cause fires, but remedy won't fix leaks}{https://apnews.com/article/a002bb4d939d59cab10136abbc471fbd}{DETROIT (AP) --- Ford is recalling nearly 43,000 small SUVs because gasoline can leak from the fuel injectors onto hot engine surfaces, increasing the risk of fires. But the recall remedy does not include repairing the fuel leaks. The...}