\entryitemWithDescription{\hskip 0pt{}Ex-``Jackass'' star Bam Margera will spend six months on probation after plea over family altercation}{https://apnews.com/article/eb842909c083b6577f47eb379ce08f88}{WEST CHESTER, Pa. (AP) --- Former ``Jackass'' star Bam Margera will spend six months on probation after pleading guilty to disorderly conduct Wednesday over an altercation at his home near Philadelphia. Margera, 44, had been charged with...}

\entryitemWithDescription{\hskip 0pt{}Feds charge 5, including man acquitted at trial, with attempting to bribe Minnesota juror with \$120K}{https://apnews.com/article/a37cef15106e7c9dbbbcd62f9125613a}{MINNEAPOLIS (AP) --- Five people were charged on Wednesday with trying to bribe a juror in one of the country's largest COVID-19-related fraud cases with a bag of \$120,000 in cash, the U.S. Attorney's Office and the FBI announced...}

\entryitemWithDescription{\hskip 0pt{}Wind-driven wildfire spreads outside a central Oregon community and prompts evacuations}{https://apnews.com/article/0bdfe630d379b6736b7796fbcf7848ef}{LA PINE, Ore. (AP) --- A wind-driven wildfire spread Wednesday outside a central Oregon community, where residents of numerous homes and businesses were urged to evacuate, authorities said. The Darlene 3 Fire grew to nearly 4 square...}

\entryitemWithDescription{\hskip 0pt{}Alex Morgan left off the 18-player U.S. soccer roster headed to the Olympics}{https://apnews.com/article/c6fdd80ab9ce3744fd7138c457bcdefb}{U.S. national team forward Alex Morgan was left off coach Emma Hayes' roster for the Paris Olympics. Morgan, a four-time Olympic veteran, was the most notable absence on the 18-player roster that Hayes announced on Wednesday. The 34-year...}

\entryitemWithDescription{\hskip 0pt{}No charges for London driver who had seizure and plowed into a school, killing 2 children}{https://apnews.com/article/1b0ff0fd96e79ae662a8536af506d8b1}{LONDON (AP) --- The driver of a 4x4 who plowed into a school in southwest London in July, killing two children, suffered a seizure that could not have been predicted and will face no criminal charges, police said Wednesday. London's...}

\entryitemWithDescription{\hskip 0pt{}Cable car collapse in Colombia leaves at least 1 dead and 12 injured, officials say}{https://apnews.com/article/2d1be5aaf13785d0a89b05288d0f4d42}{MEDELLIN, Colombia (AP) --- At least one person died and 12 others were injured Wednesday when a cable car collapsed in Medellín, Colombia's second-largest city, officials said. The manager of the cable car system, Tomás Elejalde, told...}

\entryitemWithDescription{\hskip 0pt{}Closing arguments starting in class-action lawsuit against NFL by `Sunday Ticket' subscribers}{https://apnews.com/article/1a3d5b7d1b10fe0e852f144f2168b834}{LOS ANGELES (AP) --- The jury in the class-action lawsuit filed by ``Sunday Ticket'' subscribers will receive instructions and hear closing arguments on Wednesday before beginning deliberations. U.S. District Judge Philip Gutierrez will...}

\entryitemWithDescription{\hskip 0pt{}Afghanistan-South Africa T20 World Cup semifinal pits cricket's overachievers against underachievers}{https://apnews.com/article/ccf2b0270f5a293847d6d38de214f4ff}{TAROUBA, Trinidad (AP) --- Rashid Khan was hoisted on the shoulders of his celebrating Afghan teammates and then joined in a circle with the squad and took his turn to dance on the field, all beamed live for the TV audience. The joy of...}

\entryitemWithDescription{\hskip 0pt{}Native American ceremony will celebrate birth of white buffalo calf in Yellowstone park}{https://apnews.com/article/801ff8362d3dcae810d179bc4ad146a3}{HELENA, Mont. (AP) --- Ceremonies and celebrations are planned Wednesday near the west entrance of Yellowstone National Park to mark the recent birth of a white buffalo calf in the park, a spiritually significant event for many Native...}

\entryitemWithDescription{\hskip 0pt{}Knicks set to acquire Mikal Bridges in a trade from the Brooklyn Nets, AP sources say}{https://apnews.com/article/ee33432d46ba2214b4d6b3bdc84c1cdb}{NEW YORK (AP) --- Mikal Bridges is being traded by the Brooklyn Nets to the New York Knicks, where he will join Jalen Brunson and his other former Villanova teammates, two people with knowledge of the details said Tuesday. The first trade...}

\entryitemWithDescription{\hskip 0pt{}Gena Rowlands has Alzheimer's, her son Nick Cassavetes says}{https://apnews.com/article/a3d21efc26f418b7dbd2d5d1b8434b0c}{NEW YORK (AP) --- The celebrated actor and honorary Academy Award recipient Gena Rowlands is suffering from Alzheimer's disease, her son, the filmmaker Nick Cassavetes, has revealed. Cassavetes, in an interview with Entertainment Weekly...}

\entryitemWithDescription{\hskip 0pt{}Chanel goes to the opera in a gleaming but designer-less couture collection}{https://apnews.com/article/1b5f090472acd5f26a79720c3f4aa780}{PARIS (AP) --- The show must go on, with aplomb. Chanel's latest couture display Tuesday was a finely executed collection channeling theatricality. Few Parisian fashion houses can fill the Paris Opera and gain applause from Vogue editor...}

\entryitemWithDescription{\hskip 0pt{}Korean Air, Malaysia Airlines flights disrupted by pressurization problems}{https://apnews.com/article/a70a54cc08e5f73943b1e14197de3742}{SEOUL, South Korea (AP) --- A Korean Air flight to Taiwan was forced to return to Incheon airport west of Seoul after a sudden depressurization on the plane, a Boeing 737 Max 8, the transport ministry said Tuesday. The ministry said 19 of...}