\entryitemWithDescription{\hskip 0pt{}Memphis police disband unit that beat Tyre Nichols}{https://apnews.com/article/1b7e8fa4ed7120a897086250d5d6da35}{Memphis authorities released video footage Friday showing Tyre Nichols being beaten by police officers who held the Black motorist down and repeatedly struck him with their fists, boots and batons. (Jan 7) Protesters march down the street...}

\entryitemWithDescription{\hskip 0pt{}California shooting: 3 dead, 4 hurt in ritzy LA neighborhood}{https://apnews.com/article/9aae014fbb6f2edcc54abccfb48a3f66}{Police block the street to a house where three people were killed and four others wounded in a shooing at a short-term rental home in an upscale Los Angeles neighborhood on Saturday Jan. 28, 2023. The shooting occurred about 2:30 a.m. in...}

\entryitemWithDescription{\hskip 0pt{}Election-denying lawmakers hold key election oversight roles}{https://apnews.com/article/6ce58816a74a76c7ff97c64f8a4c85e9}{FILE - State Sen. Cris Dush, R-Jefferson, listens during a news conference in Harrisburg, Pa., Feb. 8, 2022. (AP Photo/Matt Rourke, File) HARRISBURG, Pa. (AP) --- Republican lawmakers who have spread election conspiracy theories and...}

\entryitemWithDescription{\hskip 0pt{}Online system to seek asylum in US is quickly overwhelmed}{https://apnews.com/article/49b38b18869ed3b2260fb6d774153456}{A migrant from Michoacan, Mexico, uses the CBPOne app Tuesday, Jan. 24, 2023, in Tijuana, Mexico. A mobile app for migrants to seek asylum in the United States has been oversaturated since it was introduced this month in one of several...}

\entryitemWithDescription{\hskip 0pt{}Palestinian teen wounds 2, day after 7 killed in Jerusalem}{https://apnews.com/article/6e424c48e20f7b3df67a04aa0957a67a}{Israeli policemen secure a shooting attack site in east Jerusalem, Saturday, Jan. 28, 2023. A Palestinian gunman opened fire in east Jerusalem on Saturday, wounding at least two people less than a day after another attacker killed seven...}

\entryitemWithDescription{\hskip 0pt{}Aryna Sabalenka wins 1st Grand Slam title at Australian Open}{https://apnews.com/article/f242af6442b1f170f1fce64a06578dba}{Aryna Sabalenka of Belarus hugs the Daphne Akhurst Memorial Trophy after defeating Elena Rybakina of Kazakhstan in the women\textquotesingle s singles final at the Australian Open tennis championship in Melbourne, Australia, Saturday...}

\entryitemWithDescription{\hskip 0pt{}`He's close to us': Wheelchair users in Africa await pope}{https://apnews.com/article/7d055409715f46d5a507c476d64af3ea}{Paul Mitemberezi, a market vendor who has been disabled since he was 3 because of polio, leaves his house for the North Kivu Paralympic League, in Goma, democratic Republic of Congo, Tuesday Jan. 17, 2023. When Pope Francis arrives in...}

\entryitemWithDescription{\hskip 0pt{}How to fix a howitzer: US offers help line to Ukraine troops}{https://apnews.com/article/ad79017414930b328094ee124dcea5c8}{FILE - Ukrainian soldiers prepare a U.S.-supplied M777 howitzer to fire at Russian positions in Kherson region, Ukraine, Jan. 9, 2023. A rapidly expanding group of U.S. and allied troops and contractors are using phones and tablets to...}

\entryitemWithDescription{\hskip 0pt{}Trump opens 2024 run, says he's 'more committed' than ever}{https://apnews.com/article/7624d58296aa9b808032e2edbcd166c3}{Former President Donald Trump speaks during the New Hampshire Republican State Committee 2023 annual meeting, Saturday, Jan. 28, 2023, in Salem, N.H. (AP Photo/Reba Saldanha) SALEM, N.H. (AP) --- Former President Donald Trump kicked off...}

\entryitemWithDescription{\hskip 0pt{}Republicans confront bitter divide; no clear path forward}{https://apnews.com/article/77c6e337644955bc3e64e1f7e3a094e5}{Re-elected Republican National Committee Chair Ronna McDaniel holds a gavel while speaking at the committee\textquotesingle s winter meeting in Dana Point, Calif., Friday, Jan. 27, 2023. (AP Photo/Jae C. Hong) DANA POINT, Calif. (AP...}

\entryitemWithDescription{\hskip 0pt{}Japan firm opens whale meat vending machines to push sales}{https://apnews.com/article/54c5606b6cc729191afe850aadbd4487}{Konomu Kubo, a spokesperson for Kyodo Senpaku Co. explains how whale meat is being sold from a vending machine at the firm\textquotesingle s store, Thursday, Jan. 26, 2023, in Yokohama, Japan. The Japanese whaling operator, after...}

\entryitemWithDescription{\hskip 0pt{}Afghan soldier seeking US asylum hopes for 'American dream'}{https://apnews.com/article/f4ba6355be3ceb91c423f1c5a93d1d8e}{Abdul Wasi Safi smiles after a news conference Friday, Jan. 27, 2023, in Houston. Wasi Safi, an intelligence officer for the Afghan National Security Forces who fled Afghanistan following the withdrawal of U.S. forces, was freed this week...}

\entryitemWithDescription{\hskip 0pt{}Police charge 2nd teen in Iowa school shooting that killed 2}{https://apnews.com/article/3287b212e8694f4dc1935ff485c3da22}{A law enforcement officer exits the Starts Right Here building, Monday, Jan. 23, 2023, in Des Moines, Iowa. Police say two students were killed and a teacher was injured in a shooting at the Des Moines school on the edge of the city...}