\entryitemWithDescription{\hskip 0pt{}Biden to graduates of historically Black Howard University: US history hasn't been a 'fairy tale'}{https://apnews.com/article/435ef5385648d0d8e9d00dd5f0248288}{President Joe Biden speaks at Howard University\textquotesingle s commencement in Washington, Saturday, May 13, 2023. (AP Photo/Alex Brandon) WASHINGTON (AP) --- President Joe Biden on Saturday told graduates of a leading historically...}

\entryitemWithDescription{\hskip 0pt{}Kelly Clarkson responds to report accusing her daytime talk show of being a toxic workplace}{https://apnews.com/article/5892ed3967f759997ab9e56d82c7683a}{FILE - Kelly Clarkson performs during a tribute to Icon award winner Pink at the iHeartRadio Music Awards on Monday, March 27, 2023, at the Dolby Theatre in Los Angeles. Clarkson has responded, Saturday, May 13, to a Rolling Stone report...}

\entryitemWithDescription{\hskip 0pt{}Kenya cult death toll hits 200, with more than 600 reported missing}{https://apnews.com/article/23109a5c47e8ab9a4d7b5d528f52d579}{Preacher Paul Mackenzie, center, who was arrested two weeks ago for asking his followers to starve to death in order to meet Jesus, appears at a court in Malindi, Kenya Tuesday, May 2, 2023. The court in Malindi released the pastor and...}

\entryitemWithDescription{\hskip 0pt{}Tennessee police shootout leaves 1 dead, police dog wounded}{https://apnews.com/article/e073df9babd124bdb2d0abb853b98a0a}{This undated photo released by the Sevierville Police Dept. shows K-9 officer Hank. A gunfight between police and a person inside a home in east Tennessee on left one person dead and wounded Hank, a Belgian Malinois, who is recovering...}

\entryitemWithDescription{\hskip 0pt{}One killed as tornado hits south Texas near the Gulf coast, damaging dozens of homes}{https://apnews.com/article/649c4bb3b81a16425f8a3e169627332b}{People salvage items from a home after a tornado hit Saturday, May 13, 2023, in the unincorporated community of Laguna Heights, Texas near South Padre Island. Authorities say one person was killed when a tornado struck the southernmost...}

\entryitemWithDescription{\hskip 0pt{}Thousands along Bangladesh, Myanmar coast told to seek shelter as powerful Cyclone Mocha approaches}{https://apnews.com/article/5c06948384d6afbd7a740a291de6e116}{Locals stand the bank of sea before Cyclone Mocha hits, in Sittwe, Rakhine State, Saturday, May 13, 2023. Authorities in Bangladesh and Myanmar are preparing to evacuate hundreds of thousands of people as they brace for a severe cyclone...}

\entryitemWithDescription{\hskip 0pt{}Vatican experts uncovering gilded glory of Hercules statue struck by lightning}{https://apnews.com/article/7ef7141d4d8abde9f473d6a9134a11db}{Vatican Museum restorer Alice Baltera works on the bronze Hercules statue, in the Round Hall of the Vatican Museums, Thursday, May 11, 2023. Work will continue until December to reveal the 4-meter- (13-foot-) tall Hercules, believed to...}

\entryitemWithDescription{\hskip 0pt{}Unusually early heat wave in Pacific Northwest could break records}{https://apnews.com/article/f258d62d1aefc8d9a625bedfc2d62097}{Children play in a fountain to cool off in downtown Portland, Ore., Friday, May 12, 2023. An early May heat wave this weekend could surpass daily records in parts of the Pacific Northwest and worsen wildfires already burning in western...}

\entryitemWithDescription{\hskip 0pt{}Scabby the Rat gives bite to union protests, but is he at the tail end of his relevancy?}{https://apnews.com/article/88609f4499b019ef84427851f8038420}{Scabby, a giant inflatable rat used by organized labor, stands at a union action outside a Petco on Wednesday, March 29, 2023, in New York. For decades, inflatable rates like Scabby have been looming over union protests, drawing attention...}

\entryitemWithDescription{\hskip 0pt{}Don Denkinger, umpire whose stellar career was overshadowed by blown call, dead at 86}{https://apnews.com/article/ea9c024e09ae5de361447edac08c29d3}{FILE - Umpire Don Denkinger, left, watches as St. Cardinals pitcher Todd Worrell, right, stretches to catch the ball as Kansas City Royals batter Jorge Orta steps on first base during the ninth inning in Game 6 of baseball\textquotesingle...}

\entryitemWithDescription{\hskip 0pt{}Tennessee company refuses US request to recall 67 million potentially dangerous air bag inflators}{https://apnews.com/article/4e2f140c9fe1cf07fbc1a09b74738c7c}{FILE -The ARC Automotive manufacturing plant is seen, July 14, 2015 in Knoxville, Tenn. The National Highway Traffic Safety Administration said Friday, May 12, 2023 that ARC Automotive Inc. of Knoxville should recall 67 million inflators...}

\entryitemWithDescription{\hskip 0pt{}Funeral for slain Wisconsin sheriff's deputy draws 3,000 mourners}{https://apnews.com/article/908c820da1c3c281e1c92e62c045e735}{Law enforcement members comfort each other after St. Croix County Deputy Kaitie Leising\textquotesingle s body was carried into a Baldwin, Wis., funeral home Sunday afternoon, May 7, 2023. Leising was shot and killed during a traffic stop...}

\entryitemWithDescription{\hskip 0pt{}What to know about judge's ruling on age limit for young gun buyers}{https://apnews.com/article/9165143fcab00ea733c703e5572e0730}{FILE - Semi-automatic handguns are displayed at shop in New Castle, Pa., March 25, 2020. A U.S. judge\textquotesingle s ruling Wednesday, May 11, 2023, striking down a federal law that bans licensed federal firearms dealers from selling...}