\entryitemWithDescription{\hskip 0pt{}Scott Rolen elected to baseball's Hall of Fame}{https://apnews.com/article/2bb284d040008395eb8222d2049ff98f}{FILE - St. Louis Cardinals Scott Rolen watches his two-run home run off Houston Astros pitcher Chad Harville in the fifth inning during Game 2 of the National League Championship Series at Busch Stadium in St. Louis, Thursday, Oct. 14...}

\entryitemWithDescription{\hskip 0pt{}War on drugs locked him up; now he's a cannabis entrepreneur}{https://apnews.com/article/a7b5b5e6e9c470a4f89a31b401865073}{Roland Conner holds the first legal purchase of cannabis, bought from his son Darius, far right, in the "pop up" dispensary location of their business Smacked Tuesday, Jan. 24, 2023, in New York. The store is the first Conditional Adult...}

\entryitemWithDescription{\hskip 0pt{}Indigenous hockey cards shed light on First Nations players}{https://apnews.com/article/322663679734b47170caaceba533a315}{FILE - New York Islanders coach Ted Nolan talks with his players during a timeout late in the third period of an NHL hockey game against the Pittsburgh Penguins in Pittsburgh, Thursday, Nov. 15, 2007. Nolan finally has his rookie card...}

\entryitemWithDescription{\hskip 0pt{}Justice Dept. sues Google over digital advertising dominance}{https://apnews.com/article/c6afce17327b30a098b1bd6a7e947b81}{Attorney General Merrick Garland, joined by Associate Attorney General Vanita Gupta and Assistant Attorney General Jonathan Kanter of the Justice Department\textquotesingle s Antitrust Division, speaks at the Department of Justice in...}

\entryitemWithDescription{\hskip 0pt{}In reversal, US poised to approve Abrams tanks for Ukraine}{https://apnews.com/article/249de5c301a9bf83b5f3ac2182076a02}{FILE - A soldier walks past a line of M1 Abrams tanks, Nov. 29, 2016, at Fort Carson in Colorado Springs, Colo. In what would be a reversal, the Biden administration is poised to approve sending M1 Abrams tanks to Ukraine, U.S. officials...}

\entryitemWithDescription{\hskip 0pt{}'When does this stop?' For 2023, an alarmingly bloody start}{https://apnews.com/article/d93ba0560147cbbee3cff9c45fbbc523}{Women pause at a memorial at a vigil honoring the victims of a shooting at the Star Ballroom Dance Studio on Monday, Jan. 23, 2023, in Monterey Park, Calif. A gunman killed multiple people late Saturday amid Lunar New Years celebrations...}

\entryitemWithDescription{\hskip 0pt{}Classified documents at Pence's home, too, his lawyer says}{https://apnews.com/article/791bba57abaf50377f0938f0d293f36e}{FILE - Former Vice President Mike Pence sits for an interview with the Associated Press, Nov. 16, 2022, in New York. Documents with classified markings were discovered in former Vice President Mike Pence\textquotesingle s Indiana Home...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk defiantly defends himself in Tesla tweet trial}{https://apnews.com/article/d40110071eb0c546e393f86cf912207a}{Elon Musk leaves the Phillip Burton Federal Building and United States Court House in San Francisco, Tuesday, Jan. 24, 2023. Musk returned to federal court to defend himself against a class-action lawsuit that alleges he misled Tesla...}

\entryitemWithDescription{\hskip 0pt{}Senators grill Ticketmaster after Taylor Swift fiasco}{https://apnews.com/article/fd6bd24fbe88a259aa83496a898a05f9}{From left, Live Nation Entertainment, Inc. President and Chief Financial Officer Joe Berchtold, SeatGeek, Inc. Chief Executive Officer Jack Groetzinger, Jam Productions LLC Chief Executive Officer and President Jerry Mickelson, The James...}

\entryitemWithDescription{\hskip 0pt{}Netanyahu meets Jordan's king in surprise trip amid tension}{https://apnews.com/article/31f05732e58002152a14730239d0fb02}{FILE - Israeli Prime Minister Benjamin Netanyahu attends a hearing at the Magistrate\textquotesingle s Court in Rishon LeZion, Israel, Monday, Jan. 23, 2023. Netanyahu has made a surprise trip to Jordan to meet with King Abdullah II...}

\entryitemWithDescription{\hskip 0pt{}No more nuggets? School lunch goes farm-to-table — for some}{https://apnews.com/article/c8578122bf8d40351cc4eb99c94d9dbb}{Chef Josh Gjersand prepares a sandwich for Mount Diablo High School students to try during a taste test in Concord, Calif., Friday, Jan. 13, 2023. The school district in suburban San Francisco has been part of a national "farm-to-school"...}

\entryitemWithDescription{\hskip 0pt{}Analysis: Trying to play good NBA defense 'wild, hot mess'}{https://apnews.com/article/798f78c92a51297b9ac9cc07695c4072}{Dallas Mavericks guard Luka Doncic (77) loses his balance while dribbling against Los Angeles Clippers forward Robert Covington (23) during the second half of an NBA basketball game in Dallas, Sunday, Jan. 22, 2023. (AP Photo/LM Otero...}

\entryitemWithDescription{\hskip 0pt{}American skier Shiffrin wins record 83rd World Cup race}{https://apnews.com/article/7d0653200daabc8f7048e00cecc47bb0}{United States\textquotesingle{} Mikaela Shiffrin smiles on the podium after winning an alpine ski, women\textquotesingle s World Cup giant slalom, in Kronplatz, Italy, Tuesday, Jan. 24, 2023. Shiffrin won a record 83rd World Cup race...}