\entryitemWithDescription{\hskip 0pt{}The CDC has relaxed COVID guidelines. Will schools and day cares follow suit?}{https://apnews.com/article/e9a52e7b05db3a8edd21e849acf84258}{Four years after the COVID-19 pandemic closed schools and upended child care, the CDC says parents can start treating the virus like other respiratory illnesses. Gone are mandated isolation periods and masking. But will schools and child...}

\entryitemWithDescription{\hskip 0pt{}Yogurts can make limited claim that the food reduces risk of type 2 diabetes, FDA says}{https://apnews.com/article/06f67fbea87fcb7b35176520f50acbc8}{Yogurt sold in the U.S. can make claims that the food may reduce the risk of type 2 diabetes, based on limited evidence, the U.S. Food and Drug Administration said Friday. The agency agreed that there is some evidence, but not significant...}

\entryitemWithDescription{\hskip 0pt{}Woman convicted of murder conspiracy, coverup, in 2019 disappearance of Connecticut mother}{https://apnews.com/article/5d81c9985561723e714ac788dfbaefa2}{A woman was convicted Friday of conspiring to murder Jennifer Dulos, a mother of five who vanished from a wealthy Connecticut enclave in 2019 and was never found. Michelle Troconis, 49, was found guilty by the Stamford jury following a...}

\entryitemWithDescription{\hskip 0pt{}With trash bins now required in NYC, only the rats are sorry to see the garbage piles go}{https://apnews.com/article/93ccb6f097d8351ffae648ba74221853}{NEW YORK (AP) --- New York City's tradition of piling garbage bags on the sidewalk for pickup is going the way of the dinosaur. As of Friday, all 200,000 businesses in the Big Apple are required to put out their bags of trash in garbage...}

\entryitemWithDescription{\hskip 0pt{}Lobster catch dips to lowest level since 2009 as fishers grapple with climate change, whale rules}{https://apnews.com/article/1ab254ee2e8e2dbc205ce24afce5eb8d}{PORTLAND, Maine (AP) --- America's lobster fishing business dipped in catch while grappling with challenges including a changing ocean environment and new rules designed to protect rare whales. The lobster industry, based mostly in Maine...}

\entryitemWithDescription{\hskip 0pt{}Private plane carrying Grammy winner Karol G makes emergency landing in Los Angeles}{https://apnews.com/article/003035756ea4c089eeed2cfda211fe28}{LOS ANGELES (AP) --- A private airplane carrying singer Karol G made an emergency landing at a Los Angeles airport Thursday evening, a news report said. The aircraft carrying the Grammy winner and others landed at Van Nuys Airport around...}

\entryitemWithDescription{\hskip 0pt{}Artists outraged by removal of groundbreaking work along Des Moines pond}{https://apnews.com/article/e86bf9dd566b7a4ca4ea034ae428d88d}{DES MOINES, Iowa (AP) --- A Des Moines arts organization is preparing to rip out a groundbreaking artwork that lines a pond in a historic city park, surprising the New York artist who created the work decades ago and leading to an...}

\entryitemWithDescription{\hskip 0pt{}Zyn nicotine pouches are all over TikTok, sparking debate among politicians and health experts}{https://apnews.com/article/026cc2789b48c10581a56242f4b23a4a}{WASHINGTON (AP) --- There's nothing complicated about the latest tobacco product trending online: Zyn is a tiny pouch filled with nicotine and flavoring. But it has stoked a debate among politicians, parents and pundits that reflects an...}

\entryitemWithDescription{\hskip 0pt{}Judge holds veteran journalist Catherine Herridge in civil contempt for refusing to divulge source}{https://apnews.com/article/63f6b2cde67fceae192daebe5d11b1a1}{WASHINGTON (AP) --- A federal judge held veteran investigative reporter Catherine Herridge in civil contempt on Thursday for refusing to divulge her source for a series of stories during her time at Fox News about a Chinese American...}

\entryitemWithDescription{\hskip 0pt{}The Philadelphia Phillies are scrapping \$1 hot dog nights following unruly fan behavior}{https://apnews.com/article/889d4ce003734551d2091bca85163d5d}{PHILADELPHIA (AP) --- For more than a quarter-century, Phillies fans considered dollar hot dog night among the best ballpark promotions --- but the team has now decided it was the wurst. Those dog days of April --- when Philly weather is...}

\entryitemWithDescription{\hskip 0pt{}Hatch watch is underway at a California bald eagle nest monitored by a popular online camera feed}{https://apnews.com/article/de288d8c5d3a611cbd93afe27d12fb68}{BIG BEAR LAKE, Calif. (AP) --- Hatch watch is underway in Southern California mountains. Three bald eagle chicks could emerge this week from eggs laid in a nest monitored by nature lovers via a popular online camera feed. The mother...}

\entryitemWithDescription{\hskip 0pt{}Judge upholds decision requiring paternity test of Cowboys owner Jerry Jones}{https://apnews.com/article/e3f77389d9afe8c1574bec2630c548fa}{DALLAS (AP) --- A judge has upheld a decision requiring Dallas Cowboys owner Jerry Jones to take a paternity test as part of a legal dispute with a 27-year-old woman who claims the billionaire is her biological father. A Texas judge on...}

\entryitemWithDescription{\hskip 0pt{}NYC officials clear another storefront illegally housing dozens of migrants in unsafe conditions}{https://apnews.com/article/8656f2f1a56ed0f97ca99c6a2ac08b53}{NEW YORK (AP) --- New York City officials have cleared out a Bronx storefront illegally converted to house dozens of tenants that was run by the same person who operated one hosting as many as 70 migrants in a Queens furniture store. The...}