\entryitemWithDescription{\hskip 0pt{}Tyre Nichols documents: Officer never explained stop to him}{https://apnews.com/article/3c20513e067d2f55786d8f42cf98b3c6}{FILE - In this image from video released and partially redacted by the city of Memphis, Tenn., Tyre Nichols lies on the ground during a brutal attack by Memphis Police officers on Jan. 7, 2023, in Memphis. Officials said Tuesday, Feb. 7...}

\entryitemWithDescription{\hskip 0pt{}Earthquake stuns Syria's Aleppo even after war's horrors}{https://apnews.com/article/5dd29e129a81ed96e9e24bdabe3a4a9d}{FILE - Syrian Civil Defense workers and security forces search through the wreckage of collapsed buildings after a devastating earthquake rocked Syria and Turkey, in Aleppo, Syria, Monday, Feb. 6, 2023. For years, the people of Aleppo...}

\entryitemWithDescription{\hskip 0pt{}Prosecutor: Chasing Horse 'grooming' girls to replace wives}{https://apnews.com/article/3948db3bf83125733cc7fb7690b0fad0}{Nathan Chasing Horse stands in court. Monday, Feb. 6, 2023, in North Las Vegas, Nev. Nathan Chasing Horse appeared in court for the second time after his arrest on charges of sexual assault and human trafficking. (AP Photo/Ty O...}

\entryitemWithDescription{\hskip 0pt{}In earthquake rescues, noisy gear and digging, then silence}{https://apnews.com/article/f4086948f1c77eb519ad07590ae09568}{Firefighters and rescue teams search for people in a destroyed building, in Adana, southern Turkey, Wednesday, Feb. 8, 2023. Nearly two days after the magnitude 7.8 quake struck southeastern Turkey and northern Syria, thinly stretched...}

\entryitemWithDescription{\hskip 0pt{}Day care in Canada struck by city bus; 2 children dead}{https://apnews.com/article/11b871416661547d5d5d5d66937de2f7}{Parents and their children are loaded onto a warming bus as they wait for news after a bus crashed into a daycare centre in Laval, Quebec, on Wednesday, Feb. 8, 2023. (Ryan Remiorz/The Canadian Press via AP) A city bus crashed into a day...}

\entryitemWithDescription{\hskip 0pt{}Analysis: LeBron has defied odds, with no drop-off in sight}{https://apnews.com/article/67c5377787867035b15c41116553cd66}{Los Angeles Lakers forward LeBron James, left, scores to pass Kareem Abdul-Jabbar to become the NBA\textquotesingle s all-time leading scorer as Oklahoma City Thunder guard Josh Giddey, right, and forward Kenrich Williams defend during...}

\entryitemWithDescription{\hskip 0pt{}Microsoft's Activision deal hurts gamers, UK watchdog says}{https://apnews.com/article/021289492e95ad2bf955879fd0ab4eef}{FILE - People walk past a Microsoft office in New York on Nov. 10, 2016. (AP Photo/Swayne B. Hall, File) LONDON (AP) --- Microsoft's stalled \$68.7 billion deal to buy video game company Activision Blizzard has hit a fresh hurdle in the...}

\entryitemWithDescription{\hskip 0pt{}Primary care a hot target; CVS spends \$10.6B on Oak Street}{https://apnews.com/article/1244b36f28b00d45688ced3bdfcb5a79}{A CVS store sign is displayed in Pittsburgh on Friday, Feb. 3, 2023. CVS Health is plunging deeper into primary care services, buying Oak Street Health for approximately \$10.6 billion. The drugstore chain said Wednesday, Feb. 8, 2023, it...}

\entryitemWithDescription{\hskip 0pt{}Stella Jean quits Milan Fashion Week over lack of inclusion}{https://apnews.com/article/15ce3f519ca156ae8a4ecdde5123df5d}{FILE - Designer Stella Jean accepts applause at the end of her womens Spring/Summer 2018/19 fashion collection, presented in Milan, Italy, on Sept. 24, 2017. Stella Jean, the only Black designer belonging to Italy's fashion council is...}

\entryitemWithDescription{\hskip 0pt{}MH17 inquiry: 'Strong indications' Putin OK'd missile supply}{https://apnews.com/article/443d74853abceb3c9eab7770c7a1a6d2}{Digna van Boetzelaer, the Netherlands, Andy Kraag, the Netherlands, David McLean, Australia, Asha Hoe Soo Lian, Malaysia, Eric van der Sypt, Belgium, and Oleksandr Bannyk, Ukraine, take their seats for the Joint Investigation Team (JIT...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl has rare matchup of top 2 regular-season teams}{https://apnews.com/article/12a7ae073e8ae46ca2255c155ad2bc3e}{Kansas City Chiefs quarterback Patrick Mahomes, right, and Philadelphia Eagles quarterback Jalen Hurts speak to the media during the NFL football Super Bowl 57 opening night, Monday, Feb. 6, 2023, in Phoenix. The Kansas City Chiefs will...}

\entryitemWithDescription{\hskip 0pt{}Zelenskyy seeks weaponry in surprise trips to London, Paris}{https://apnews.com/article/52c633390e7b140acb445807bdc7e11e}{Speaker of the House of Commons, Sir Lindsay Hoyle, left, holds the helmet of one of the most successful Ukrainian pilots, inscribed with the words "We have freedom, give us wings to protect it", which was presented to him by Ukrainian...}

\entryitemWithDescription{\hskip 0pt{}Israel steps up Jerusalem home demolitions as violence rises}{https://apnews.com/article/bab35518d9b80ce4c7d1513edb163e2d}{Girls from the Matar family sit near the rubble of their home that housed 11 people before it was demolished by Israeli authorities in the Jabal Mukaber neighborhood of east Jerusalem, Sunday, Jan. 29, 2023. For many Palestinians, the...}