\entryitemWithDescription{\hskip 0pt{}Protest outside UK asylum-seeker hotel ends in 15 arrests}{https://apnews.com/article/66efe65f947cfa5b15eb64d7ec711224}{A burnt out police van after a demonstration outside the Suites Hotel in Knowsley, Merseyside, where people were protesting against asylum seekers staying at the hotel, in Knowsley, England, Friday, Feb. 10, 2023. An anti-migration...}

\entryitemWithDescription{\hskip 0pt{}Jill Biden not shy about her 'Philly girl' sports fandom}{https://apnews.com/article/256e15924e43fde60e476d011afa078d}{FILE - First lady Jill Biden talks with Philadelphia Eagles center Jason Kelce (62) before the coin toss before an NFL football game against the Dallas Cowboys, Oct. 16, 2022, in Philadelphia. (AP Photo/Rich Schultz, File) WASHINGTON...}

\entryitemWithDescription{\hskip 0pt{}Migrants seeking US sponsors find questionable offers online}{https://apnews.com/article/5ec9a3451db3c08e51e9ae03ec26a83a}{FILE - A woman from Cuba waits with other migrants to be processed to seek asylum after crossing the border into the United States, Friday, Jan. 6, 2023, near Yuma, Ariz. An underground market has emerged for migrants seeking U.S...}

\entryitemWithDescription{\hskip 0pt{}Chiefs-Eagles Super Bowl matchup could come down to trenches}{https://apnews.com/article/5b0d08824827f348a55246ddff1d06c3}{Philadelphia Eagles center Jason Kelce (62) and offensive tackle Lane Johnson (65) warm up during an NFL football Super Bowl team practice, Wednesday, Feb. 8, 2023, in Tempe, Ariz. The Eagles will face the Kansas City Chiefs in Super Bowl...}

\entryitemWithDescription{\hskip 0pt{}Minnesota Buddhist temple opens up sacred dance troupe}{https://apnews.com/article/156b1e3d1bfd437338be6d3b3c54d75a}{The Buddhist temple of Watt Munisotaram is seen on snow-covered farmland in Hampton, Minn., on Saturday, Feb. 4, 2023. Started by Cambodian refugees who had fled the Khmer Rouge\textquotesingle s killing fields four decades ago, it...}

\entryitemWithDescription{\hskip 0pt{}3 weeks, dozens of witnesses: Takeaways from Murdaugh trial}{https://apnews.com/article/c528a67536c421f38c37b39d2cc757eb}{Alex Murdaugh listens to his friend Chris Wilson testify during his double murder trial at the Colleton County Courthouse on Thursday, Feb. 9, 2023, in Walterboro, S.C. The 54-year-old attorney is standing trial on two counts of murder in...}

\entryitemWithDescription{\hskip 0pt{}Bickering bogs down Capitol riot trial of Proud Boys leaders}{https://apnews.com/article/20648ad33f958aa2d6f0dbd80a2474ad}{FILE - Proud Boys leader Henry "Enrique" Tarrio wears a hat that says The War Boys during a rally in Portland, Ore., on Sept. 26, 2020. A barrage of bickering between lawyers and the judge has bogged down the seditious conspiracy trial of...}

\entryitemWithDescription{\hskip 0pt{}Survivors still being found as quake death toll tops 28,000}{https://apnews.com/article/c86046a654311d8099d8b7a3dc2b832b}{Ebrahim Zakeriya, left, and his mother Duha Nasrallah, wounded survivors of a devastating earthquake, receive treatment at a hospital in the coastal city of Latakia, Syria, Saturday, Feb. 11, 2023. Syrian state TV said Bashar Assad and...}

\entryitemWithDescription{\hskip 0pt{}Wagner owner says war in Ukraine could drag on for years}{https://apnews.com/article/2145d83f2dabc032fefa294acce0ea48}{The city center damaged by Russian shelling in Bakhmut, Donetsk region, Ukraine, Friday, Feb. 10, 2023. Writing on the wall reads " Bakhmut loves Ukraine". (AP Photo/Libkos) KYIV, Ukraine (AP) --- The owner of the Russian Wagner Group...}

\entryitemWithDescription{\hskip 0pt{}Nearly 1 million French march in 4th day of pension protests}{https://apnews.com/article/5cd08796a71375c71a05c72b356f7769}{Protesters hold a placard with a portrait of Emmanuel Macron during a demonstration against plans to push back France\textquotesingle s retirement age, in Lille, northern France, Saturday, Feb. 11, 2023. France is bracing itself for a...}

\entryitemWithDescription{\hskip 0pt{}Hilltop coal-mining town a tactical prize in Ukraine war}{https://apnews.com/article/e95c0f599a117e2f1b21d077ccd075cf}{In this image from Ukrainian Armed Forces and taken in Feb. 2023 shows damaged Russian tanks in a field after attempting to attack, Vuhledar, Ukraine. The battle for the small coal-mining town of Vuhledar on Ukraine\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Schools become flashpoint for Republicans eyeing White House}{https://apnews.com/article/c65049b0c64206996dd1bea4cee65b81}{FILE - Florida Gov. Ron DeSantis speaks at a news conference on Jan. 26, 2023, in Miami. David McIntosh, the president ofthe influential Club For Growth group, said Tuesday, Feb. 7, that the group has invited a half dozen potential...}

\entryitemWithDescription{\hskip 0pt{}Pence subpoena could set up fight over executive privilege}{https://apnews.com/article/58ce3d93baf0c4e1a9567c4a563b658f}{FILE - In this image from video released by the House Select Committee, Vice President Mike Pence and his wife Karen walk at the Capitol on Jan 6, that the House select committee investigating the Jan. 6 attack on the U.S. Capitol...}