\entryitemWithDescription{\hskip 0pt{}Wet winter gives way to colorful 'Superbloom' in US West}{https://apnews.com/article/00498c2d4a0aeec35572be892f5a237a}{A visitor stands on a field of blooming flowers near the Antelope Valley California Poppy Reserve, Monday, April 10, 2023, in Lancaster, Calif. (AP Photo/Marcio Jose Sanchez) The tiny rain-fed wildflowers, no bigger than a few inches, are...}

\entryitemWithDescription{\hskip 0pt{}Papal official rejects new claims in 'Vatican Girl' mystery}{https://apnews.com/article/57185f27253e8dc9608aba4349cbc97e}{FILE - Pietro Orlandi wears a placard with a picture of his sister Emanuela during a sit-in near Saint Peter\textquotesingle s Basilica, in Rome, Saturday, Jan. 14, 2023. One of the Vatican's enduring mysteries took another twist Friday...}

\entryitemWithDescription{\hskip 0pt{}DA: Suspect in killing of Cash App founder planned attack}{https://apnews.com/article/4429c2d780fb40bca508aaac4814ced7}{Khazar Elyassnia, left, stands in the Hall of Justice in San Francisco on Friday, April 14, 2023, ahead of an appearance by her brother, Nima Momeni, who has been charged with murder in the death of tech entrepreneur Bob Lee. Elyassnia...}

\entryitemWithDescription{\hskip 0pt{}NJ charges itself with damaging land it was bound to protect}{https://apnews.com/article/f848947a4361a944f5170eb58dd1bf8e}{FILE - A red-shouldered hawk fluffs up it\textquotesingle s feathers and spreads wings to facilitate drying after a thunderstorm in Chattanooga, Tenn., on Dec. 31, 2021. On April 6, 2023, the New Jersey Department of Environmental...}

\entryitemWithDescription{\hskip 0pt{}Black church, NHL's Penguins reach historic land-use accord}{https://apnews.com/article/08dfa73ed59ee66d31cfec3a3c5381be}{The Rev. Dale Snyder sits in the pews at Bethel AME Church where he is pastor, in Pittsburgh on Tuesday, April 11, 2023. Bethel, considered Pittsburgh\textquotesingle s oldest Black congregation, lost its previous sanctuary when much of...}

\entryitemWithDescription{\hskip 0pt{}El Chapo sons among 28 Sinaloa cartel members charged by US}{https://apnews.com/article/867532c8cde69d6a8bd1eca4457acfad}{Attorney General Merrick Garland speaks during a news conference at the Justice Department in Washington, Friday, April 14, 2023. The Justice Department has charged 28 members of Mexico's powerful Sinaloa cartel, including sons of...}

\entryitemWithDescription{\hskip 0pt{}Minneapolis OKs dawn Muslim prayer call, 1st for big US city}{https://apnews.com/article/6bc3fe5ca2eb7436fbdf417481821277}{FILE - Yusuf Abdulle, standing, director of the Islamic Association of North America, prays with fellow Muslims at the Abubakar As-Saddique Islamic Center in Minneapolis on Thursday, May 12, 2022. Minneapolis will allow broadcasts of the...}

\entryitemWithDescription{\hskip 0pt{}America's first heroes: Revolutionary War soldiers reburied}{https://apnews.com/article/8a3c28be8f74f7c98bd3a1997e37c24b}{Forensic anthropologists, archeologists and volunteers prepare the remains of an unidentified Revolutionary War soldier killed in the Battle of Camden in 1780 for reburial on Thursday, 14 soldiers were removed from the battlefield...}

\entryitemWithDescription{\hskip 0pt{}'Exhausted' Indiana city waits for all-clear after big fire}{https://apnews.com/article/7939d658a674ad2508f50b531409589a}{Firefighters pour water on an industrial fire in Richmond, Ind., Thursday, April 13, 2023. Multiple fires that began burning Tuesday afternoon were still burning within about 14 acres of various types of plastics stored inside and outside...}

\entryitemWithDescription{\hskip 0pt{}European spacecraft on way to Jupiter and its icy moons}{https://apnews.com/article/75a1b285cd188b9bb9745d40b294e01b}{In this image provided by the European Space Agency, an Ariane rocket carrying the robotic explorer Juice takes off from Europe\textquotesingle s Spaceport in French Guiana, Friday, April 14, 2023. European spacecraft has blasted off on a...}

\entryitemWithDescription{\hskip 0pt{}Florida floods: Businesses, residents begin cleaning up mess}{https://apnews.com/article/376ac512b70ffe1f961d10165cca8cbd}{A Delta baggage train drives on the closed runway at Fort Lauderdale-Hollywood International Airport Friday, April 14, 2023, in Fort Lauderdale, Fla. The airport was able to open one of two runways after heavy rain flooded the runways...}

\entryitemWithDescription{\hskip 0pt{}JPMorgan Chase profits jump 52\% amid banking turmoil}{https://apnews.com/article/999d6033f7dc66bccc97c6e5bc186ade}{A Chase bank sign in Richmond, Va., Wednesday, June 2, 2021. PMorgan reports earnings on Friday, April 14, 2023. (AP Photo/Steve Helber, File) JPMorgan Chase \& Co. posted a 52\% jump in its first-quarter profits, helped by higher...}

\entryitemWithDescription{\hskip 0pt{}Life of Vatican's 'James Bond of exorcists' depicted in Russell Crowe film}{https://apnews.com/article/2eb29491e230d132db331cc8b9c0a717}{This image released by Sony Pictures shows Russell Crowe as Father Gabriele Amorth in a scene from Screen Gems\textquotesingle{} "The Pope\textquotesingle s Exorcist." (Jonathan Hession/Sony Pictures via AP) LOS ANGELES (AP) --- The Rev...}