\entryitemWithDescription{\hskip 0pt{}Actor Bijou Phillips files for divorce from Danny Masterson after rape convictions}{https://apnews.com/article/4a59b23cb4ad6f4ec275d8c5fad1188c}{LOS ANGELES (AP) --- Bijou Phillips has filed for divorce from Danny Masterson, days after the former ``That `70s Show'' star was sentenced to 30 years to life in prison for two rape convictions. Phillips, a 43-year-old actor, filed a...}

\entryitemWithDescription{\hskip 0pt{}Ohtani has elbow surgery. His doctor expects hitting return by opening day '24 and pitching by '25}{https://apnews.com/article/f05408238a4e8389ec500b52bec38154}{ST. PETERSBURG, Fla. (AP) --- Los Angeles Angels star Shohei Ohtani had elbow surgery Tuesday, and his doctor said he expects the two-way star will be available as a hitter on opening day next season and will return to the mound as a...}

\entryitemWithDescription{\hskip 0pt{}Video shows high school band director shocked with stun gun, arrested after refusing to stop music}{https://apnews.com/article/4760c7a3d9deaa2b197ca60b739e0714}{BIRMINGHAM, Ala. (AP) --- Police body camera video shows an Alabama high school band director being shocked with a stun gun and arrested by officers in front of screaming students, in a chaotic scuffle that broke out after he refused to...}

\entryitemWithDescription{\hskip 0pt{}Rihanna, A\$AP Rocky debut photos of their second child, a son named Riot Rose}{https://apnews.com/article/d2d3e078215e5ffe5f3b30b67491c8ad}{NEW YORK (AP) --- Rihanna and A\$AP Rocky are giving the world the first look at their second child together, a boy they've named Riot Rose. The 35-year-old pop star and the 34-year-old rap star dropped photos Tuesday of their family of...}

\entryitemWithDescription{\hskip 0pt{}Deion Sanders condemns death threats against player whose late hit left Hunter with lacerated liver}{https://apnews.com/article/d05cd57e60f8ea01675e3ff02f4abfee}{BOULDER, Colo. (AP) --- Deion Sanders stood up for Henry Blackburn after the Colorado State safety received death threats for a late hit that sent Colorado's two-way star Travis Hunter to the hospital with a lacerated liver. ``That's...}

\entryitemWithDescription{\hskip 0pt{}Did your kids buy gear in Fortnite without asking you? The FTC says you could get a refund}{https://apnews.com/article/1dc3fc39a12e0076a644fa634e4b0371}{WASHINGTON (AP) --- Parents whose kids bought virtual gear without their knowledge on the popular Fortnite video game could soon be able to get a refund. U.S. regulators are starting to notify more than 37 million people by email that...}

\entryitemWithDescription{\hskip 0pt{}Witness said man was punched before he died at a New England Patriots game}{https://apnews.com/article/cf4ee3e9712f252b25a14cae711b135a}{DEDHAM, Mass. (AP) --- Police are investigating the death of a New Hampshire man at a New England Patriots home game, after a witness said he saw a Miami Dolphins fan punching the man in the head. Police and personnel responded to the...}

\entryitemWithDescription{\hskip 0pt{}Google brings its AI chatbot Bard into its inner circle, opening door to Gmail, Maps, YouTube}{https://apnews.com/article/1229638b82d19afb5226c913821fa1ad}{Google is introducing Bard, its artificially intelligent chatbot, to other members of its digital family --- including Gmail, Maps and YouTube --- as it seeks ward off competitive threats posed by similar technology run by Open AI and...}

\entryitemWithDescription{\hskip 0pt{}A bus coach crashes in Austria, killing a woman and injuring 20 others}{https://apnews.com/article/34dffbafa6f644c2c1415b8863b60893}{BERLIN (AP) --- A bus coach traveling through Austria on Tuesday went off the road and crashed on its side, killing a woman and injuring 20 other passengers, Austria's APA agency reported. The accident took place near the village of...}

\entryitemWithDescription{\hskip 0pt{}Nick Chubb suffers another severe knee injury, likely ending the Browns star running back's season}{https://apnews.com/article/870fd6941d28e3b4b7bf3d9c65264a50}{PITTSBURGH (AP) --- Nick Chubb has spent the better part of a decade as the heart and soul of the Cleveland Browns. There is no player more respected in the locker room. No player more committed on the field. All of which made the sight...}

\entryitemWithDescription{\hskip 0pt{}A teen girl found an iPhone in an airplane bathroom. Her family says it was put there to record her}{https://apnews.com/article/1d3a9691f03151f7e4981e9884443d96}{BOSTON (AP) --- The family of a 14-year-old girl who allegedly discovered an iPhone taped to the back of a toilet seat on a recent flight from Charlotte, North Carolina, to Boston said they believe it was put there to record her by a...}

\entryitemWithDescription{\hskip 0pt{}Phil Mickelson says he's done gambling and is on the road to being `the person I want to be'}{https://apnews.com/article/ec4e796fb80d1fdff8825b570bb22d9c}{Phil Mickelson won't be betting on football this year --- much less the Ryder Cup --- saying in a lengthy social media post Monday that he previously crossed the line from moderation into addiction and ``it wasn't any fun.'' ``The money...}

\entryitemWithDescription{\hskip 0pt{}Wild black bear at Walt Disney World in Florida captured after search}{https://apnews.com/article/5d41237ddff81d6a0253faf6210bcca2}{ORLANDO, Fla. (AP) --- It wasn't an escapee from the Country Bear Jamboree attraction, but a wild black bear managed to be the star of its own show Monday at Walt Disney World. The presence of the black bear in a tree in the Magic Kingdom...}