\entryitemWithDescription{\hskip 0pt{}Iowa-UConn women's Final Four match was most-watched hoops game in ESPN history; 14.2M avg. viewers}{https://apnews.com/article/7ac76c353a0d1c2ed7f45c46a91b5ac5}{BRISTOL, Conn. (AP) --- Iowa's 71-69 victory over UConn at the women's Final Four on Friday night averaged 14.2 million viewers on ESPN, making it the most-viewed women's basketball game on record and the largest audience for an ESPN...}

\entryitemWithDescription{\hskip 0pt{}The world's oldest man says the secret to his longevity is luck, plus regular fish and chips}{https://apnews.com/article/cc1a154db05464106c1f05bdb09df73c}{LONDON (AP) --- The world's oldest man says the secret to his long life is luck, moderation --- and fish and chips every Friday. Englishman John Alfred Tinniswood, 111, has been confirmed as the new holder of the title by Guinness World...}

\entryitemWithDescription{\hskip 0pt{}A Virgin Atlantic plane clipped a BA jet at Heathrow but no injuries were reported}{https://apnews.com/article/fb60a9c42624b9fb61d312d346b34614}{LONDON (AP) --- A Virgin Atlantic jet collided with another plane while it was being towed at Heathrow Airport on Saturday, aviation authorities said. There were no reports of injuries. Virgin said its Boeing 787-9 had completed a flight...}

\entryitemWithDescription{\hskip 0pt{}Guardians ace Shane Bieber to have season-ending Tommy John surgery after solid start in 2024}{https://apnews.com/article/18cf94b906d91e02c2d83765f3f0e25d}{CLEVELAND (AP) --- Cleveland Guardians ace Shane Bieber will have season-ending Tommy John elbow surgery, a major blow to the team and the 2020 Cy Young winner. Bieber, who missed several months last season with elbow issues, experienced...}

\entryitemWithDescription{\hskip 0pt{}A second UK lawmaker says he was targeted in a sexting scam. Police are investigating}{https://apnews.com/article/c4b31f9deb06555337b4423396a86930}{LONDON (AP) --- A second British lawmaker has acknowledged receiving explicit messages on his phone in what police are investigating as a malicious phishing attempt against politicians, their staff and journalists. Conservative legislator...}

\entryitemWithDescription{\hskip 0pt{}A Soyuz capsule carrying 3 crew from the International Space Station lands safely in Kazakhstan}{https://apnews.com/article/667d58f9409c5e476f2b1924a87f361b}{MOSCOW (AP) --- A Russian space capsule with two women and one man safely landed in a steppe in Kazakhstan on Saturday after their missions aboard the International Space Station. The Soyuz MS-24 carrying Russia's Oleg Novitsky, NASA's...}

\entryitemWithDescription{\hskip 0pt{}Powerball prize climbs to \$1.3B ahead of next drawing}{https://apnews.com/article/a46a6a91586a397dc7cb632cc4839c23}{DES MOINES, Iowa (AP) --- Lottery players will have another shot Saturday night at a Powerball jackpot that has grown to an estimated \$1.3 billion after more than three months without a winner. There have been 40 consecutive drawings...}

\entryitemWithDescription{\hskip 0pt{}Lawsuit naming Sean `Diddy' Combs as co-defendant alleges his son sexually assaulted woman on yacht}{https://apnews.com/article/9132c5408e81741489a23a2d982cf638}{LOS ANGELES (AP) --- A lawsuit that names Sean ``Diddy'' Combs as a co-defendant alleges that his son Christian ``King'' Combs sexually assaulted a woman working on a yacht chartered by his father. The suit filed Thursday in Los Angeles...}

\entryitemWithDescription{\hskip 0pt{}Sacha Baron Cohen and Isla Fisher say they filed for divorce}{https://apnews.com/article/a3d891690b52684f8f9ac8e8227215da}{Sacha Baron Cohen and Isla Fisher say they filed for divorce last year after more than 20 years together. The English ``Borat'' star and the Australian ``Wedding Crashers'' actor who married in 2010 announced their split Friday in joint...}

\entryitemWithDescription{\hskip 0pt{}P\&G recalls 8.2 million bags of Tide, Gain and other laundry detergents over packaging defect}{https://apnews.com/article/58ee3ebe15ec343892287cee9968cd0b}{NEW YORK (AP) --- Procter \& Gamble is recalling more than 8 million bags of Tide, Gain, Ace and Ariel laundry detergent packets sold in the U.S. and Canada due to a defect in the products' child-resistant packaging. According to Friday...}

\entryitemWithDescription{\hskip 0pt{}What to know about the \$30 million cash heist in Los Angeles}{https://apnews.com/article/d34b769be34cbafcca14a897967d3bb2}{LOS ANGELES (AP) --- A brazen Los Angeles cash heist on Easter weekend in which thieves cracked a safe and got away with as much as \$30 million is believed to be one of the largest such heists in U.S. history. The heist has triggered...}

\entryitemWithDescription{\hskip 0pt{}2 Muslim women were forced to remove hijabs for mug shots. NYC will pay \$17.5M to settle their suit}{https://apnews.com/article/b8c74c66ae5de7c9218ff8f9191d44ba}{NEW YORK (AP) --- New York City has agreed to pay \$17.5 million to settle a lawsuit filed by two Muslim women who were forced to remove their head coverings to be photographed after they were arrested. The class-action lawsuit was filed...}

\entryitemWithDescription{\hskip 0pt{}Small plane clips 2 vehicles as it lands on North Carolina highway, but no injuries are reported}{https://apnews.com/article/cf9c55bc5011992a0a028f3e9346e4c4}{MONCURE, N.C. (AP) --- A small plane experiencing engine problems struck two vehicles as it landed on a highway near a North Carolina airport, but no injuries were reported, authorities said. The single-engine Lancair 360 with only the...}