\entryitemWithDescription{\hskip 0pt{}Caitlin Clark fever is spreading. Indiana is all-in on the excitement.}{https://apnews.com/article/9868eb8d739049c8ac3a43b6060ddcd6}{INDIANAPOLIS (AP) --- Michelle Lennis grew up playing basketball in Indiana as a born-and-raised Purdue fan. But this season, Lennis also found herself cheering for the Iowa women's basketball team led by Caitlin Clark as the college...}

\entryitemWithDescription{\hskip 0pt{}Participant, studio behind `Spotlight,' `An Inconvenient Truth,' shutters after 20 years}{https://apnews.com/article/82407ad88681d01d3318f768dae4567e}{Participant, the activist film and television studio that has financed Oscar winners like ``Spotlight'' and socially conscious documentaries like ``Food, Inc,'' and ``Waiting For Superman'' is closing its doors after 20 years. Billionaire...}

\entryitemWithDescription{\hskip 0pt{}Travis Kelce named host of `Are You Smarter than a Celebrity?' for Prime Video}{https://apnews.com/article/edacd6f3504d892d64772f0d2268f3d4}{Travis Kelce's NFL off-season with the Kansas City Chiefs has been a busy one. The Super Bowl LVIII-winning tight end is the host of a new game show called ``Are You Smarter than a Celebrity?'' for Prime Video, the streaming service...}

\entryitemWithDescription{\hskip 0pt{}A painting of Winston Churchill by an artist whose work he hated is up for auction}{https://apnews.com/article/a3af922ba8c054cd0024f2bdf6919c87}{LONDON (AP) --- A portrait of Winston Churchill by an artist whose work the British leader loathed went on display Tuesday at Churchill's birthplace ahead of an auction in June. The painting by modernist artist Graham Sutherland was made...}

\entryitemWithDescription{\hskip 0pt{}West Virginia transgender sports ban discriminates against teen athlete, appeals court says}{https://apnews.com/article/badf5518ada74d01a3f0a0420d2f4074}{CHARLESTON, W.Va. (AP) --- West Virginia's transgender sports ban violates the rights of a teen athlete under Title IX, the federal civil rights law that prohibits sex-based discrimination in schools, an appeals court ruled Tuesday. The...}

\entryitemWithDescription{\hskip 0pt{}Company believes it found sunken barge in Ohio River near Pittsburgh, one of 26 that got loose}{https://apnews.com/article/48ce86b36212bba72bda15376f728441}{A barge operator believes it has found a sunken barge in the Ohio River near Pittsburgh, one of 26 that broke loose and floated away during weekend flooding, company officials said Tuesday. Crews used sonar to locate an object in a...}

\entryitemWithDescription{\hskip 0pt{}A London court rules against a Muslim girl who wanted to pray at a school known for strict rules}{https://apnews.com/article/80ccac159df27ba8a4762d9f99002cbd}{LONDON (AP) --- A Muslim student who wanted to pray during lunchtime lost a court fight Tuesday against a strict London school that had banned prayer on campus. A High Court judge said the female student had accepted when she enrolled in...}

\entryitemWithDescription{\hskip 0pt{}ABBA, Blondie, and the Notorious B.I.G. enter the National Recording Registry}{https://apnews.com/article/4b6f237694aa1910fcc605ca46159576}{LOS ANGELES (AP) --- ABBA, Biggie, Blondie and Rudolph are entering America's audio canon. New inductees into the National Recording Registry at the Library of Congress include ABBA `s 1976 album ``Visitors,'' The Notorious B.I.G. `s 1994...}

\entryitemWithDescription{\hskip 0pt{}Fire rages through the 17th-century old Stock Exchange in Copenhagen and its spire has collapsed}{https://apnews.com/article/045be0d926a7dd590d4f32e5cea07360}{COPENHAGEN, Denmark (AP) --- One of Copenhagen's oldest buildings is on fire and its iconic spire has collapsed. The fire that began Tuesday in the copper roof of the 17th-century Old Stock Exchange, or Boersen, has now spread to much of...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Paris Olympics venues mix history and modernity and showcase cultural heritage}{https://apnews.com/article/bfec52b5fe8afbb377d5aeca6efa22c5}{PARIS (AP) --- Iconic or historic venues are at the heart of the Paris Olympics --- organizers want the event to be about the spectacle as well as the sports. Athletics stars will speed along an eye-catching new purple track at the Stade...}

\entryitemWithDescription{\hskip 0pt{}Salman Rushdie's `Knife' is unflinching about his brutal stabbing and uncanny in its vital spirit}{https://apnews.com/article/732ebac087e5e0a4fc736373286b3085}{NEW YORK (AP) --- In Salman Rushdie's first book since the 2022 stabbing that hospitalized him and left him blind in one eye, the author wastes no time reliving the day he thought might be his last. ``At a quarter to eleven on August 12...}

\entryitemWithDescription{\hskip 0pt{}A 9-year-old boy's dream of a pet octopus is a sensation as thousands follow Terrance's story online}{https://apnews.com/article/fa9d0c3d8bbadf59d7aa69ce7171dcf4}{The one thing 9-year-old Cal Clifford wanted more than anything since he was a toddler was a pet octopus. The boy's family in rural Edmond, Oklahoma, humored him with toy versions of an eight-legged mollusk, but as Cal got older it became...}

\entryitemWithDescription{\hskip 0pt{}Paris Hilton backs California bill to bring more transparency to youth treatment facilities}{https://apnews.com/article/b3fa67c952c686f7dafe3dddf83c114f}{SACRAMENTO, Calif. (AP) --- Paris Hilton joined California state lawmakers Monday to push for legislation aimed at cracking down on the industry that cares for troubled teens by requiring more transparency from youth treatment facilities...}