\entryitemWithDescription{\hskip 0pt{}Oath Keepers' Rhodes seeks leniency in Jan. 6 sentence}{https://apnews.com/article/ae432a7a4b49284af0b808b27effdf17}{FILE - Stewart Rhodes, founder of the citizen militia group known as the Oath Keepers, speaks during a rally outside the White House in Washington, on June 25, 2017. The Justice Department is seeking 25 years in prison for Rhodes, the...}

\entryitemWithDescription{\hskip 0pt{}Vermont bans owning, running paramilitary training camps}{https://apnews.com/article/03506f22609d9be1d6311ce6b6a5fd6f}{Vermont on Monday made it a crime to own or operate paramilitary training camps in the state after Republican Gov. Phil Scott signed legislation introduced in response to a firearms training facility built without permits that neighbors...}

\entryitemWithDescription{\hskip 0pt{}Grace Bumbry, 1st Black singer at Bayreuth, dies at 86}{https://apnews.com/article/57440bbfa65ebafffa5c302f808199cf}{FILE - Kennedy Center honoree opera singer Grace Bumbry sings the National Anthem at the Kennedy Center Honors gala in Washington on Dec. 6, 2009. Bumbry, 86, a pioneering mezzo-soprano who became the first Black to sing at the Bayreuth...}

\entryitemWithDescription{\hskip 0pt{}Set to host, UK taking Eurovision very seriously this year}{https://apnews.com/article/b75cfda7db690fc53ac092128fc390b8}{FILE - Sam Ryder from United Kingdom singing Space Man performs during the Grand Final of the Eurovision Song Contest at Palaolimpico arena, in Turin, Italy, on May 14, 2022. There's nothing like nearly winning to wake people up. And the...}

\entryitemWithDescription{\hskip 0pt{}AP wins public service, photo Pulitzers for Ukraine coverage}{https://apnews.com/article/e95c689997429071513d377cc209ae4b}{Ukrainian emergency employees and police officers evacuate injured pregnant woman Iryna Kalinina, 32, from a maternity hospital that was damaged by a Russian airstrike in Mariupol, Ukraine, March 9, 2022. The image was part of a series of...}

\entryitemWithDescription{\hskip 0pt{}Out-of-control wildfires cause evacuations in western Canada}{https://apnews.com/article/de8f14beff8c90cd2d43cab032a64535}{In this photo provided by the Government of Alberta Fire Service, a burned section of forest in the area near Edson, Alberta, smolders, Saturday, May 6, 2023. (Government of Alberta Fire Service/The Canadian Press via AP) EDMONTON...}

\entryitemWithDescription{\hskip 0pt{}Deaths from Congo floods approach 400 as search continues}{https://apnews.com/article/f13794e1f93b037f4eda1ca2d42cf3f6}{People walk next to a house destroyed by the floods in the village of Nyamukubi, South Kivu province, in Congo, Saturday, May 6, 2023. The death toll from flash floods and landslides in eastern Congo has risen according to the governor...}

\entryitemWithDescription{\hskip 0pt{}76ers' Harden visits with Michigan State shooting victim}{https://apnews.com/article/802c4d97ae9cf0da7b6486281d4521c5}{Philadelphia 76ers\textquotesingle{} James Harden gives his sneakers to John Hao after Game 4 in an NBA basketball Eastern Conference semifinals playoff series, Sunday, May 7, 2023, in Philadelphia. Harden invited Hao, a student severely...}

\entryitemWithDescription{\hskip 0pt{}UFC's Tony Ferguson arrested following Hollywood crash}{https://apnews.com/article/fa002285a5a12a4eda2432ef25ab8078}{FILE - Tony Ferguson poses during a ceremonial weigh-in for the UFC 229 mixed martial arts fight, Friday, Oct. 5, 2018, in Las Vegas. UFC fighter Ferguson was arrested on a DUI charge in Hollywood early Sunday, May 7, 2023, after his...}

\entryitemWithDescription{\hskip 0pt{}Engineers frustrated with rails even as others get sick time}{https://apnews.com/article/10c5e688b85ef9be4f231499666ab756}{FILE - A worker rides a rail car at a BNSF rail crossing in Saginaw, Texas, Wednesday, Sept. 14, 2022. Tens of thousands of engineers remain frustrated with the lack of paid sick time and the demands railroads like BNSF are making in...}

\entryitemWithDescription{\hskip 0pt{}`Guardians of the Galaxy Vol. 3' opens to \$114 million}{https://apnews.com/article/91c16e18b13f808259d37437ca8ea211}{This image released by Marvel Studios shows, from left, Pom Klementieff as Mantis, Groot (voiced by Vin Diesel), Chris Pratt as Peter Quill/Star-Lord, Dave Bautista as Drax, Karen Gillan as Nebula in a scene from "Guardians of the Galaxy...}

\entryitemWithDescription{\hskip 0pt{}Nick Gilbert, son of Cavaliers owner, dies at 26}{https://apnews.com/article/b7dd01d5e2d29929d793dd6e15cf874d}{FILE - In this May 21, 2013, file photo, Cleveland Cavaliers owner Dan Gilbert congratulates his son, Nick Gilbert, after the team won the NBA basketball draft lottery in New York. Nicolas ``Nick'' Gilbert, who became the team...}

\entryitemWithDescription{\hskip 0pt{}Lionel Richie, Katy Perry sing for royal coronation concert}{https://apnews.com/article/b5669453c120a0309b15a2b9aab27f64}{Katy Perry performs during the concert at Windsor Castle in Windsor, England, Sunday, May 7, 2023, celebrating the coronation of King Charles III. It is one of several events over a three-day weekend of celebrations. (Leon Neal/Pool Photo...}