\entryitemWithDescription{\hskip 0pt{}A trophy followed by tirades and ugly defeats. José Mourinho's turbulent stay at Roma is finished}{https://apnews.com/article/61bca2a938a8856370b88effe60dc0d5}{ROME (AP) --- It started with a big success. It descended into ugly outbursts and devastating defeats. And now José Mourinho's turbulent tenure at Roma is finished. Roma announced on Tuesday that the outspoken coach was leaving the club ``...}

\entryitemWithDescription{\hskip 0pt{}Indian pilgrims throng Nepal's most revered Hindu temple, Pashupatinath}{https://apnews.com/article/2046772f8479e7f77f71d3b8bfa9366f}{KATHMANDU, Nepal (AP) --- Thousands of Indian pilgrims arrive at daybreak at Pashupatinath, the most revered Hindu temple in Nepal, after traveling long distances in buses. Hawkers greet them with hot tea on the cold wintry morning. Many...}

\entryitemWithDescription{\hskip 0pt{}Mayfield throws for 337 yards and 3 TDs to lead Buccaneers to 32-9 NFC wild-card rout of Eagles}{https://apnews.com/article/7af0cddcd3eec07b19a47cc437110b05}{TAMPA, Fla. (AP) --- Baker Mayfield threw for 337 yards and three touchdowns to lead the resurgent Tampa Bay Buccaneers to a 32-9 wild-card playoff victory over Jalen Hurts and the defending NFC champion Philadelphia Eagles on Monday...}

\entryitemWithDescription{\hskip 0pt{}The Baltimore Sun bought by Sinclair media executive}{https://apnews.com/article/9f9cefe838ca6f17830ca051a5c1efcb}{BALTIMORE (AP) --- The Baltimore Sun newspaper has been purchased by David D. Smith, the executive chairman of the media conglomerate Sinclair Inc. Smith told the newspaper he acquired Baltimore Sun Media from the hedge fund Alden Global...}

\entryitemWithDescription{\hskip 0pt{}Josh Allen, Bills dispatch Steelers 31-17 in playoff game delayed a day by snow. Chiefs up next}{https://apnews.com/article/91cf43b74e25f72069e6891cc6af4f61}{ORCHARD PARK, N.Y. (AP) --- It made no difference to Josh Allen what day or time the Buffalo Bills faced the Pittsburgh Steelers. The AFC wild-card playoff game could've been played Sunday as scheduled, in the midst of a lake-effect storm...}

\entryitemWithDescription{\hskip 0pt{}Quinta Brunson, Ayo Edebiri and Rhea Seehorn light up the Emmy Awards silver carpet}{https://apnews.com/article/c7ee0949f967251292d8e8f7401dedc1}{NEW YORK (AP) --- Television's finest brought the silver carpet alive in color, vying with a sea of black, on Monday at the strike-delayed 75th Emmy Awards, including a 3D-molded black look for Ayo Edebiri and sparkly chartreuse for Rhea...}

\entryitemWithDescription{\hskip 0pt{}As Jenni Hermoso looks on, Aitana Bonmatí hails `powerful generation of women'}{https://apnews.com/article/f0ae87db3edc793a1cf9c619a347c327}{LONDON (AP) --- World Cup champion Aitana Bonmatí hailed a ``powerful generation of women'' on Monday in accepting FIFA's award as best female soccer player. Looking on inside the Hammersmith Apollo theater in London was Spain teammate...}

\entryitemWithDescription{\hskip 0pt{}Washington state sues to block proposed merger of Kroger and Albertsons grocery chains}{https://apnews.com/article/35681b212a416d19d24d1a3a8126f4ca}{SEATTLE (AP) --- Washington state Attorney General Bob Ferguson on Monday sued to block the proposed merger of Kroger and Albertsons, two of the nation's largest grocery chains. In the suit filed in King County Superior Court, Ferguson...}

\entryitemWithDescription{\hskip 0pt{}Ground collision of two Boeing planes in Chicago sparks FAA investigation}{https://apnews.com/article/c8d785674aeda46ec5563e03d31f38c5}{CHICAGO (AP) --- A plane taxiing for departure clipped another aircraft at Chicago O'Hare International Airport on Sunday evening, the Federal Aviation Administration said Monday. No injuries were reported, both planes were of Boeing...}

\entryitemWithDescription{\hskip 0pt{}Mother Nature proves no match for Bills fans attending Buffalo's playoff game vs. Steelers}{https://apnews.com/article/1ed462bef47dc3ff772ef368e4d59a3a}{ORCHARD PARK, N.Y. (AP) --- In the end, Mother Nature was no match for Bills Mafia. With the remnants of a lake-effect snowstorm moving north on Monday, the Bills' hearty fanbase took over, helping dig out Highmark Stadium while finding...}

\entryitemWithDescription{\hskip 0pt{}A surgeon general report once cleared the air about smoking. Is it time for one on vaping?}{https://apnews.com/article/db81e873c256e38433734e86d6a50f7e}{NEW YORK (AP) --- Sixty years ago, the U.S. surgeon general released a report that settled a longstanding public debate about the dangers of cigarettes and led to huge changes in smoking in America. Today, some public health experts say a...}

\entryitemWithDescription{\hskip 0pt{}No joke: Feds are banning humorous electronic messages on highways}{https://apnews.com/article/3c7b0d11475d2b255f7edd197af771cc}{PHOENIX (AP) --- It's no joke. Humorous and quirky messages on electronic signs will soon disappear from highways and freeways across the country. The U.S. Federal Highway Administration has given states two years to implement all the...}

\entryitemWithDescription{\hskip 0pt{}This photo shows the moment Maine's record high tide washed away more than 100-year-old fishing shacks}{https://apnews.com/article/1a5d26f2d87e4af3fd8be9be57162af2}{MEREDITH, N.H. (AP) --- A record high tide in Maine washed away three historic fishing shacks that had stood since the 1800s and formed the backdrop of countless photographs. Michelle Erskine said she was visiting fisherman's point at...}