\entryitemWithDescription{\hskip 0pt{}Justice Department looking into PGA Tour deal with LIV's Saudi backers, AP source says}{https://apnews.com/article/95686bda6ad5e080609de16ac5b8ac6f}{FILE - The PGA Tour logo is shown during a press conference in Tokyo, Nov. 20, 2018. The most disruptive year in golf ended Tuesday, June 6, 2023, when the PGA Tour and European tour agreed to a merger with Saudi Arabia\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Al Pacino, 83, is a father for the fourth time, welcoming son Roman with Noor Alfallah}{https://apnews.com/article/366d24e6d6ff18b53425ef1a05f2bacb}{FILE - Al Pacino, winner of the Hollywood supporting actor award for "The Irishman," poses backstage at the 23rd annual Hollywood Film Awards in Beverly Hills, Calif., on Nov. 3, 2019. (Photo by Richard Shotwell/Invision/AP, File) Al...}

\entryitemWithDescription{\hskip 0pt{}Pool deck at collapsed Florida condo building failed to comply with codes, standards, officials say}{https://apnews.com/article/b976aacfb1bb90b8bb41a229f4380b76}{FILE - Rescue personnel work at the remains of the Champlain Towers South condo building, June 25, 2021, in Surfside, Fla. The swimming pool deck of the beachfront South Florida condominium where 98 people died when the building collapsed...}

\entryitemWithDescription{\hskip 0pt{}Republicans in Oregon Senate end six-week walkout that blocked bills on abortion, trans health care}{https://apnews.com/article/e4cf9a17ce536232d158dfe4cc4fc96c}{The Oregon Senate is seen during a vote at the state capitol in Salem, Ore., Thursday, June 15, 2023. Enough Republican members showed up in the Oregon Senate on Thursday to end a six-week walkout that halted the work of the Legislature...}

\entryitemWithDescription{\hskip 0pt{}MLB to start months-long approval process for Oakland Athletics' move to Las Vegas}{https://apnews.com/article/1e413d70856914f1e16550f95969aa22}{FILE - This rendering provided by the Oakland Athletics on May 26, 2023, shows a view of their proposed new ballpark at the Tropicana site in Las Vegas. Major League Baseball laid out a detailed process to approve the Oakland Athletics...}

\entryitemWithDescription{\hskip 0pt{}Florida deputy didn't follow extensive training during Parkland school massacre, supervisor says}{https://apnews.com/article/56ed8f6cabcadc7df36824e11a0cbaae}{Broward Sheriff\textquotesingle s Office Lt. Col. Samuel Samaroo (cq) stands and identifies the various tools on his gun belt while testifying during the trial of former Marjory Stoneman Douglas High School School Resource Officer Scot...}

\entryitemWithDescription{\hskip 0pt{}Man indicted in chokehold death of New York subway rider Jordan Neely, prosecutor confirms}{https://apnews.com/article/de5275030850de9ea7b5a2b710604603}{FILE - Daniel Penny, center, is walked by New York Police Department detectives out of the 5th Precinct, May 12, 2023, in New York. Penny, the man charged with manslaughter for putting an agitated New York City subway rider in a fatal...}

\entryitemWithDescription{\hskip 0pt{}Robert Caro's last book on LBJ likely won't be delayed by editor Robert Gottlieb's death}{https://apnews.com/article/a8c4d210dd1582494a4146505df2d298}{This image released by Sony Pictures Classics shows Robert Caro, left, and Robert Gottlieb in a scene from the documentary "Turn Every Page - The Adventures of Robert Caro and Robert Gottlieb." Gottlieb, the celebrated editor of Caro...}

\entryitemWithDescription{\hskip 0pt{}Theme parks bounced back in 2022 from pandemic lows with revenue, if not attendance}{https://apnews.com/article/0ddc9a18397c01026551769db62913e2}{FILE - In this Jan. 22, 2015 file photo, visitors walk toward the Sleeping Beauty\textquotesingle s Castle in the background at Disneyland Resprt in Anaheim, Calif. Last year, 2022, marked a return to normal for the theme park industry...}

\entryitemWithDescription{\hskip 0pt{}Gloria Estefan, Jeff Lynne, Teddy Riley, Glen Ballard, Liz Rose heading to Songwriters Hall of Fame}{https://apnews.com/article/e778fee15ef6fb196a018a092ebe33d5}{This combination of photos shows, from left. Glen Ballard, Gloria Estefan, Jeff Lynne, Teddy Riley and Liz Rose, who will be inducted into the Songwriters Hall of Fame on Thursday. (AP Photo) NEW YORK (AP) --- Gloria Estefan, Jeff Lynne...}

\entryitemWithDescription{\hskip 0pt{}Noah Kahan writes songs about New England. His vulnerability has far wider appeal}{https://apnews.com/article/0b3ac39ba80971599706a8e0d16f6f70}{Singer-songwriter Noah Kahan poses for a portrait in New York on June 7, 2023, to promote his album "Stick Season." (Photo by Christopher Smith/Invision/AP) NEW YORK (AP) --- Singer-songwriter Noah Kahan\textquotesingle s ``Stick Season''...}

\entryitemWithDescription{\hskip 0pt{}A Vermont man charged with killing his mother at sea over inheritance dies awaiting trial}{https://apnews.com/article/f5bb21fc2815e32dbf2f32532b21e121}{FILE - Nathan Carman arrives in a small boat at the U.S. Coast Guard station, in Boston, on Sept. 27, 2016. The man charged with killing his mother at sea during a 2016 fishing trip off the coast of New England in what prosecutors say was...}

\entryitemWithDescription{\hskip 0pt{}Songwriter, music industry entrepreneur sentenced to life in prison in girlfriend's death}{https://apnews.com/article/5c7384c399e6f5f2f8362d68942dd21d}{This photo provided by Scott County (Iowa) Sheriff's Office shows Justin Wright. Wright, a songwriter and music industry entrepreneur from Atlanta, was sentenced Wednesday, June 14, 2023, to life in prison without parole for killing his...}