\entryitemWithDescription{\hskip 0pt{}EXPLAINER: Carlos Correa's free-agent saga ends with Twins}{https://apnews.com/article/271a482bcf7c704282cfb94f1ccb68c1}{Minnesota Twins\textquotesingle{} Carlos Correa, left, and agent Scott Boras hug following a baseball press conference at Target Field, Wednesday, Jan. 11, 2023, in Minneapolis. The team and Correa agreed to a six-year, \$200 million...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry's memoir opens at a record-setting sales pace}{https://apnews.com/article/01f0449725562644a59e60a16fc9edb3}{Copies of the new book by Prince Harry called "Spare" are displayed at Sherman\textquotesingle s book store in Freeport, Maine, Tuesday, Jan. 10, 2023. Prince Harry\textquotesingle s memoir provides a varied portrait of the Duke of Sussex...}

\entryitemWithDescription{\hskip 0pt{}Jeff Beck, guitar god who influenced generations, dies at 78}{https://apnews.com/article/6fafc82a3f8fe8e27d6f6e39a215e28d}{FILE - British guitarist Jeff Beck performs on the Stravinski hall during the 41st Montreux Jazz Festival in Montreux, Switzerland, late Sunday, July 15, 2007. Beck, a guitar virtuoso who pushed the boundaries of blues, jazz and rock `n'...}

\entryitemWithDescription{\hskip 0pt{}Judge tells Detroit museum: Don't move van Gogh painting}{https://apnews.com/article/52fa81a726d49ccd3b559b88992bc043}{Visitors file past at the Van Gogh painting "Une Liseuse De Romans", also known as "The Novel Reader", during the Van Gogh in America exhibit at the Detroit Institute of Arts, Wednesday, Jan. 11, 2023, in Detroit. (Andy Morrison/Detroit...}

\entryitemWithDescription{\hskip 0pt{}US women's soccer tries to overcome past lack of diversity}{https://apnews.com/article/a7b7fd7f889042bc86039832f4ec19c2}{U.S. national team player Crystal Dunn takes part in a drill during practice for a match against Nigeria Tuesday, Aug. 30, 2022, in Riverside, Mo. Women's soccer in the United States has struggled with diversity, starting with a pay-to...}

\entryitemWithDescription{\hskip 0pt{}Naomi Osaka says she's pregnant, plans tennis return in 2024}{https://apnews.com/article/e922b28d057f76f2e786c483b5f55cd6}{FILE - Naomi Osaka of Japan smiles during her first round match against Camila Osorio of Colombia at the Australian Open tennis championships in Melbourne, Australia, Monday, Jan. 17, 2022. Naomi Osaka is pregnant and plans to return to...}

\entryitemWithDescription{\hskip 0pt{}Brazil authorities brace for possible repeat of uprising}{https://apnews.com/article/9326ee60c21c9ff0abdb81f0c5a9a1ce}{Military police stand guard outside the Supreme Court in Brasilia, Brazil, Wednesday, Jan. 11, 2023, ahead of expected protests called for by supporters of former Brazilian President Jair Bolsonaro. (AP Photo/Eraldo Peres) BRASILIA...}

\entryitemWithDescription{\hskip 0pt{}GOP opens long-promised investigation into Biden family}{https://apnews.com/article/b80e36533fa8da85199fe397d2b50d85}{Rep. James Comer, R-Ky., talks to reporters as he walks to the House chamber, on Capitol Hill in Washington, Monday, Jan. 9, 2023. (AP Photo/Jose Luis Magana) WASHINGTON (AP) --- House Republicans on Wednesday opened their long-promised...}

\entryitemWithDescription{\hskip 0pt{}Going home: Bills' Hamlin released from Buffalo hospital}{https://apnews.com/article/2a2003b201800d81fedec0d65415190b}{FILE - Buffalo Bills safety Damar Hamlin smiles prior to the start of the first half of a preseason NFL football game, Saturday, Aug. 28, 2021, in Orchard Park, N.Y. Hamlin was released from a Buffalo hospital on Wednesday, Jan. 11, 2023...}

\entryitemWithDescription{\hskip 0pt{}George Santos refuses to resign despite political pressure}{https://apnews.com/article/b2bdca89d67a68343073048b922cb4aa}{Rep. George Santos, R-N.Y., departs after attending a House GOP conference meeting on Capitol Hill in Washington, Tuesday, Jan. 10, 2023. (AP Photo/Patrick Semansky) Local Republican leaders in New York called for the resignation of new...}

\entryitemWithDescription{\hskip 0pt{}Film helps renew search for 1st Black Navy pilot's remains}{https://apnews.com/article/48a033d6e8ee38b5ba0140a292d3164e}{FILE - This circa 1950 photo provided by the U.S. Navy shows Jesse Brown in the cockpit of an F4U-4 Corsair fighter at an unidentified location. In December 2022, FedEx founder Fred Smith gifted the proceeds from the film ``Devotion,''...}

\entryitemWithDescription{\hskip 0pt{}Can US avoid a recession? As inflation eases, optimism rises}{https://apnews.com/article/728bf4d2efd02b20de28db3e01ed25ba}{File - A hiring sign is displayed at a job agency in Mount Prospect, Ill., Thursday, Jan. 3, 2023. An economic downturn remains very possible. Yet in recent weeks, with inflation showing widespread signs of easing, a more cheerful view...}

\entryitemWithDescription{\hskip 0pt{}Dish from Harry, one of their own, could fuel royal change}{https://apnews.com/article/5d026ebc3feef3e2195f4c0a929f1dba}{FILE - Copies of the new book by Prince Harry called "Spare" are displayed at a book store in London, Jan. 10, 2023. Prince Harry's explosive memoir, with its damning allegations of a toxic relationship between the monarchy and the press...}
