\entryitemWithDescription{\hskip 0pt{}Meet Crush, the rare orange lobster diverted from dinner plate to aquarium by Denver Broncos fans}{https://apnews.com/article/116b158ee773d84ce0211955f4b47f2a}{The Downtown Aquarium in Denver has a new resident --- a rare orange lobster that was rescued from a shipment of crustaceans delivered to a Red Lobster restaurant in Pueblo, Colorado. A long-term employee who is a dishwasher and head...}

\entryitemWithDescription{\hskip 0pt{}Lou Dobbs, conservative pundit and Fox Business host, dies at 78}{https://apnews.com/article/76c799df42c6b7d4912dece5d180b2de}{NEW YORK (AP) --- Lou Dobbs, the conservative political pundit and TV host who was a nightly presence on Fox Business Network for more than a decade, has died. He was 78. His death was announced Thursday in a post on his official X...}

\entryitemWithDescription{\hskip 0pt{}Shannen Doherty finalizes divorce hours before death}{https://apnews.com/article/0d9fbb475ae64fed1ccdc0a03eb69cf6}{LOS ANGELES (AP) --- Shannen Doherty finalized her split with husband, Kurt Iswarienko, just hours before her death at age 53, and she was granted a rare posthumous divorce two days later. Doherty, the star of ``Beverly Hills, 90210''...}

\entryitemWithDescription{\hskip 0pt{}Netflix's subscriber and earnings growth gather more momentum as password-sharing crackdown pays off}{https://apnews.com/article/d77c9a1f7ce29d1647354a7acf70a7ea}{Netflix's subscriber and earnings growth accelerated in its latest quarter as the video streaming service benefits from a crackdown on freeloading viewers, an expansion into advertising and an acclaimed programming lineup. The results...}

\entryitemWithDescription{\hskip 0pt{}Over 3 million steam cleaners are under recall because they can spew hot water and cause burns}{https://apnews.com/article/9a1d23b8f55cedf236e9d2a9d96ea2b5}{NEW YORK (AP) --- Some 3.3 million steam cleaners are being recalled across North America due to a burn hazard that has resulted in consumers reporting more than 150 injuries. Select models of Bissell-branded ``Steam Shot Handheld Steam...}

\entryitemWithDescription{\hskip 0pt{}After crash that killed 6 teens, NTSB chief says people underestimate marijuana's impact on drivers}{https://apnews.com/article/e25b14eca281d43efbdc6ee100573955}{DETROIT (AP) --- A horrific crash that killed six high school girls in Oklahoma two years ago has the head of the U.S. National Transportation Safety Board urging parents to warn teenagers about the risk of driving after using marijuana...}

\entryitemWithDescription{\hskip 0pt{}Passenger train derails in India, killing at least 2 passengers and injuring 20 others}{https://apnews.com/article/e98303b3f10a9751721791de1bb876c1}{LUCKNOW, India (AP) --- A passenger train derailed on Thursday in northern India, killing at least two passengers and injuring 20 others, a railroad official said. The cause of the accident is being investigated. Naveen Kumar, a state...}

\entryitemWithDescription{\hskip 0pt{}Historic utility AND high fashion. 80-year-old LL Bean staple finds a new audience as a trendy bag}{https://apnews.com/article/47a258dd282cdf3aee27878257b0418a}{FREEPORT, Maine (AP) --- L.L. Bean created it 80 years ago to haul heavy blocks of ice. Now it's a must-have summer fashion accessory. The simple, sturdy canvas bag called the Boat and Tote is having an extended moment 80 years after its...}

\entryitemWithDescription{\hskip 0pt{}Too soon for comedy? After attempted assassination of Trump, US politics feel anything but funny}{https://apnews.com/article/4235bd43f3750c95e0460d158996a0e5}{Political jokes: too soon? The answer from many quarters at midweek was a resounding yes, days after an assassination attempt against Republican former president Donald Trump rattled the nation over political violence that has been...}

\entryitemWithDescription{\hskip 0pt{}Caitlin Clark breaks WNBA's game assist record with 19 in Fever's loss to Wings}{https://apnews.com/article/cf9312845dfd08f6feab10b7da1dc410}{ARLINGTON, Texas (AP) --- Indiana rookie Caitlin Clark broke the WNBA record for assists in a game Wednesday night, finishing with 19 in the Fever's 101-93 loss to the Dallas Wings. ``I just try to set my teammates up for success,'' Clark...}

\entryitemWithDescription{\hskip 0pt{}Philadelphia Union midfielder Cavan Sullivan is the youngest ever in MLS. He's just 14 years old}{https://apnews.com/article/6e920552c38db70fd94bc94614f0e142}{CHESTER, Pa. (AP) --- Fourteen-year-old Philadelphia Union midfielder Cavan Sullivan became the youngest player in Major League Soccer history on Wednesday night --- and probably the youngest to play in any of the biggest professional...}

\entryitemWithDescription{\hskip 0pt{}Tons of dead fish cover major Sao Paulo river after alleged dumping of industrial waste}{https://apnews.com/article/5ecbe68b12e457cee242aebb5fdee509}{TANQUA, Brazil (AP) --- Several tons of fish have died along one of the main rivers in Sao Paulo state after an alleged illegal dumping of industrial waste from a sugar and ethanol plant, environmental authorities and prosecutors said on...}

\entryitemWithDescription{\hskip 0pt{}A meteor streaked across the NYC skyline before disintegrating over New Jersey}{https://apnews.com/article/52545d7d940dc1a63025ab447c3eaab2}{NEW YORK (AP) --- A meteor streaked across the New York City skyline before disintegrating over nearby New Jersey, according to NASA. William Cooke, the head of the space agency's Meteoroid Environments Office, said the fireball was first...}