\entryitemWithDescription{\hskip 0pt{}Prince's puffy `Purple Rain' shirt and other pieces from late singer's wardrobe go up for auction}{https://apnews.com/article/7d5edd9a30413befbffe8111bd28d16c}{BOSTON (AP) --- Fans of Prince, who was known nearly as much for his extravagant wardrobe as for his chart-topping hits, will have a chance to bid on some of the late musician's sartorial splendor in an online auction this week. The...}

\entryitemWithDescription{\hskip 0pt{}Biden honors Stanley Cup champion Vegas Golden Knights in the return of an NHL tradition}{https://apnews.com/article/fe03bd687c233d2794a06c672663a306}{WASHINGTON (AP) --- President Joe Biden joked about ignoring his sagging poll numbers in Nevada and thanked the NHL's Vegas Golden Knights for their role in helping the city recover from the 2017 mass shooting when he honored them Monday...}

\entryitemWithDescription{\hskip 0pt{}Secret Service agents protecting Biden's granddaughter open fire when 3 people try to break into SUV}{https://apnews.com/article/997126378e864c5acd0c9a1c6618c4e2}{WASHINGTON (AP) --- Secret Service agents protecting President Joe Biden's granddaughter opened fire after three people tried to break into an unmarked Secret Service vehicle in the nation's capital, a law enforcement official told The...}

\entryitemWithDescription{\hskip 0pt{}Aaron Rodgers tells NBC he targets a mid-December return from torn Achilles tendon}{https://apnews.com/article/e14f715e302beb3ef6dd53489b720c69}{LAS VEGAS (AP) --- New York Jets quarterback Aaron Rodgers said his goal is to return from a torn Achilles tendon by mid-December, NBC's Melissa Stark reported during the telecast of the Jets' game at Las Vegas on Sunday night. Rodgers...}

\entryitemWithDescription{\hskip 0pt{}Capitol rioter plans 2024 run as a Libertarian candidate in Arizona's 8th congressional district}{https://apnews.com/article/33de9a9f4ff1ea35cd12d9719a2f2987}{PHOENIX (AP) --- Jacob Chansley, the spear-carrying rioter whose horned fur hat, bare chest and face paint made him one of the more recognizable figures in the Jan. 6, 2021, assault on the U.S. Capitol, apparently aspires to be a member...}

\entryitemWithDescription{\hskip 0pt{}Canadian jury finds fashion mogul Nygard guilty of 4 sexual assault charges, acquits him on 2 counts}{https://apnews.com/article/f4858f245f13ae33128978d2d2318d6d}{Peter Nygard, who once led a women's fashion empire, was found guilty of four counts of sexual assault in a Canadian court on Sunday but was acquitted of a fifth count plus a charge of forcible confinement. The jury handed down the...}

\entryitemWithDescription{\hskip 0pt{}AP Top 25: Georgia's No. 1 streak hits 22, second-best ever. Louisville, Oregon State enter top 10}{https://apnews.com/article/93d021b5d341fb1665d9630fd5280819}{Georgia extended its streak of weeks being top-ranked in the AP Top 25 to 22 on Sunday, giving the Bulldogs the second-longest run of being No. 1 in the 87-year history of the college football poll. The Bulldogs received 54 first-place...}

\entryitemWithDescription{\hskip 0pt{}Texas A\&M fires coach Jimbo Fisher, a move that will cost the school \$75M}{https://apnews.com/article/0c58ef59a450d0924cca56410c74bc43}{COLLEGE STATION, Texas (AP) --- Landing Jimbo Fisher, a coach with a national title on his resume, seemed like just what Texas A\&M needed to finally become a championship contender. But Fisher failed to replicate his success at Florida...}

\entryitemWithDescription{\hskip 0pt{}`The Marvels' melts down at the box office, marking a new low for the MCU}{https://apnews.com/article/392f34978d96a5a2bca5e32717d888e8}{NEW YORK (AP) --- Since 2008's ``Iron Man,'' the Marvel machine has been one of the most unstoppable forces in box-office history. Now, though, that aura of invincibility is showing signs of wear and tear. The superhero factory hit a new...}

\entryitemWithDescription{\hskip 0pt{}Former Ghana striker Raphael Dwamena dies after collapsing during Albanian Super League soccer game}{https://apnews.com/article/8b182ccc584c4d57a37bd590b1831f8e}{TIRANA, Albania (AP) --- Former Ghana striker Raphael Dwamena has died after collapsing Saturday during an Albanian Super League soccer match. The Albanian Football Federation confirmed the death of the 28-year-old Dwamena. Footage on...}

\entryitemWithDescription{\hskip 0pt{}Iceland evacuates town and raises aviation alert as concerns rise a volcano may erupt}{https://apnews.com/article/3bb2f4d18cb7c62967a7ce16cc1b70d3}{LONDON (AP) --- Residents of a fishing town in southwestern Iceland left their homes Saturday after increasing concern about a potential volcanic eruption caused civil defense authorities to declare a state of emergency in the region...}

\entryitemWithDescription{\hskip 0pt{}John Bailey, who presided over the film academy during the initial \#MeToo reckoning, dies at 81}{https://apnews.com/article/bfd3a1f7defd334d76d0a9eaf596c839}{LOS ANGELES (AP) --- John Bailey, a cinematographer who led the Academy of Motion Picture Arts and Sciences during the initial \#MeToo reckoning, died Friday at 81. Bailey died ``peacefully in his sleep'' in Los Angeles, his wife, Carol...}

\entryitemWithDescription{\hskip 0pt{}Florida deputies struck intentionally by man driving car recovering after surgeries, sheriff says}{https://apnews.com/article/e6fec98812698b6ff9859760a9871014}{BRANDON, Fla. (AP) --- Two Florida sheriff's deputies remained hospitalized Friday after surgeries for injuries they suffered when a man intentionally plowed into them with his speeding car, authorities said. Hillsborough County Sheriff...}