\entryitemWithDescription{\hskip 0pt{}95-year-old painter threatened with eviction from Cape Cod dune shack wins five-year reprieve}{https://apnews.com/article/a437446ee4394bdbe4261d02d383af81}{PROVINCETOWN, Mass. (AP) --- A 95-year-old painter and his family threatened with eviction from the Provincetown, Massachusetts, dune shack they have helped care for and occupy for nearly eight decades have won a reprieve. A legal team...}

\entryitemWithDescription{\hskip 0pt{}Chicago woman, 104, skydives from plane, aiming for record as the world's oldest skydiver}{https://apnews.com/article/42e50ac6dde302889a4055ecef77ae1b}{OTTAWA, Ill. (AP) --- A 104-year-old Chicago woman is hoping to be certified as the oldest person to ever skydive after leaving her walker on the ground and making a tandem jump in northern Illinois. ``Age is just a number,'' Dorothy...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé's Renaissance World Tour is over. But it's coming to movie theaters soon}{https://apnews.com/article/3ea24a8de2716e08eeaf60999e8c9cd4}{NEW YORK (AP) --- A documentary chronicling Beyoncé\textquotesingle s just-concluded 39-city Renaissance World Tour will premiere in North American theaters Dec. 1, AMC Theaters announced Monday. The film adds a second blockbuster from a...}

\entryitemWithDescription{\hskip 0pt{}Mexico's rescue and drug-sniffing dogs start out at the army's puppy kindergarten}{https://apnews.com/article/b88e40573c47290886f60203c5fee316}{SAN MIGUEL DE LOS JAGÜEYEZ, Mexico (AP) --- In the middle of a military base outside Mexico City, an army colonel runs what he calls a kindergarten for dogs. Puppies that one day will become rescue dogs, or sniffer dogs for drugs or...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift watches Travis Kelce's Chiefs take on the Jets at MetLife Stadium}{https://apnews.com/article/1b1b3ba43139acefcbdf52072b018154}{EAST RUTHERFORD, N.J. (AP) --- Taylor Swift couldn't just shake off another chance to watch Travis Kelce on the football field. The 12-time Grammy Award winner arrived at MetLife Stadium about 40 minutes before kickoff Sunday night to...}

\entryitemWithDescription{\hskip 0pt{}David Beckham reflects on highs and lows in `Beckham' doc, calls it an `emotional rollercoaster'}{https://apnews.com/article/a8ff8abbe9a7d8765dab6dacc19f09b4}{LONDON (AP) --- David Beckham delves back into the hateful treatment he received following his infamous 1998 World Cup red card --- and its impact on him --- in a new Netflix documentary series pegged to the 10th anniversary of his...}

\entryitemWithDescription{\hskip 0pt{}Tim Wakefield, who revived his career and Red Sox trophy case with knuckleball, has died at 57}{https://apnews.com/article/ae1f9bd465fbefede0d030f915b1f988}{BOSTON (AP) --- Tim Wakefield, the knuckleballing workhorse of the Red Sox pitching staff who bounced back after giving up a season-ending home run to the Yankees in the 2003 playoffs to help Boston win its curse-busting World Series...}

\entryitemWithDescription{\hskip 0pt{}Simone Biles leads a dominant US performance at the world gymnastics championships}{https://apnews.com/article/8c8fac3c7229a2383cadf2d16acbca53}{ANTWERP, Belgium (AP) --- Simone Biles led a dominant performance by the U.S. women at the world gymnastics championships, posting an all-around total of 58.865 to lead qualifying through two subdivisions Sunday. The 26-year-old, who is a...}

\entryitemWithDescription{\hskip 0pt{}Buck Showalter fired as New York Mets manager}{https://apnews.com/article/e243ed2e27a207e21bf84cad147209e7}{NEW YORK (AP) --- For the fifth time in six years, the New York Mets are in the market for a manager. Buck Showalter was fired Sunday after a disappointing season in which baseball's highest-spending team tumbled from contention by...}

\entryitemWithDescription{\hskip 0pt{}Jimmy Carter turns 99 at home with Rosalynn and other family as tributes come from around the world}{https://apnews.com/article/19be42d93ca052816aaa06c57c38be1b}{ATLANTA (AP) --- Jimmy Carter has always been a man of discipline and habit. But the former president broke routine Sunday, putting off his practice of quietly watching church services online to instead celebrate his 99th birthday with...}

\entryitemWithDescription{\hskip 0pt{}The Flying Scotsman locomotive collided with another train in Scotland. Several people were injured}{https://apnews.com/article/77f3dd539ccddb0b8c5ca9c4f3d390e3}{LONDON (AP) --- Several people were injured after the Flying Scotsman, the historic steam locomotive that's celebrating its 100th anniversary this year, was involved in a low-speed crash with another heritage train in the Scottish...}

\entryitemWithDescription{\hskip 0pt{}Germany's government and Elon Musk spar on X over migrant rescue ships}{https://apnews.com/article/fab94f0fc68833f80ad5df8ca9a071e1}{BERLIN (AP) --- Germany's government rebuked X owner Elon Musk after he criticized the recent work of migrant rescue ships that German humanitarian groups operate in the Mediterranean Sea. Musk late Friday shared a video that showed...}

\entryitemWithDescription{\hskip 0pt{}Attempt to pass a tanker may have led to the deadly chemical crash in Illinois, official says}{https://apnews.com/article/4e86653cb60515022dea05c45046329d}{SPRINGFIELD, Ill. (AP) --- The tanker truck crash in central Illinois that killed five people may have started when another vehicle tried to pass the chemical-laden truck, a federal transportation official said Sunday. The tanker truck...}