\entryitemWithDescription{\hskip 0pt{}Skiing Santas hit the slopes in Maine}{https://apnews.com/article/d8ee453f249771dd287377539875747c}{NEWRY, Maine (AP) --- Ho ho ho, away they go --- Santa's helpers took the day off on Sunday with a few hundred of the jolly ol' elves hitting the slopes. With beards and stocking caps flapping, some 300 red-suited Santas were lively and...}

\entryitemWithDescription{\hskip 0pt{}Bronny James poised to make college debut for USC nearly 5 months after cardiac arrest}{https://apnews.com/article/3da6b8dafe1b0edc69932b8a257f6673}{LOS ANGELES (AP) --- Bronny James is poised to make his college debut for Southern California nearly five months after he suffered cardiac arrest. The 19-year-old freshman is likely to come off the bench for the Trojans (5-3) on Sunday...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk restores X account of conspiracy theorist Alex Jones}{https://apnews.com/article/90cfc990631dec5e8f337167fbe16372}{Elon Musk has restored the X account of conspiracy theorist Alex Jones, pointing to a poll on the social media platform formerly known as Twitter that came out in favor of the Infowars host who repeatedly called the 2012 Sandy Hook school...}

\entryitemWithDescription{\hskip 0pt{}Shohei Ohtani agrees to record \$700 million, 10-year contract with Dodgers}{https://apnews.com/article/0462c7dcd08a5afedd92912ba69f8e8a}{NEW YORK (AP) --- Shohei Ohtani has set a financial record to go along with his singular on-field performance, getting \$700 million to make a 30-mile move up Interstate 5 to the Los Angeles Dodgers. His agent, Nez Balelo, issued a...}

\entryitemWithDescription{\hskip 0pt{}Thousands descend on NYC for the annual Santa-themed bar crawl SantaCon}{https://apnews.com/article/616ee17f07906fde81d7378f6ba206d5}{NEW YORK (AP) --- Here come Santa Clauses. Again. Throngs of people dressed as jolly Old St. Nick descended on New York City for the annual SantaCon charity pub crawl on Saturday. The booze-fueled stroll, which included no shortage of...}

\entryitemWithDescription{\hskip 0pt{}Eagles security guard DiSandro banned from sideline for Sunday Night Football vs. Cowboys}{https://apnews.com/article/595e6c14141fb055b2a08e36d25902c5}{PHILADELPHIA (AP) --- Eagles security chief Dom DiSandro has been barred by the NFL from being on the sideline Sunday night against the Cowboys after he was ejected in last week's game for a scuffle with 49ers linebacker Dre Greenlaw, the...}

\entryitemWithDescription{\hskip 0pt{}A hospital fire near Rome kills at least 3 and causes an emergency evacuation of all patients}{https://apnews.com/article/512b53b92f03b4c45035be503adcac20}{ROME (AP) --- A fire broke out in a hospital on Rome's outskirts, killing at least three people and forcing the overnight evacuation of the smoke-filled facility and its nearly 200 patients, officials said Saturday. The blaze began in the...}

\entryitemWithDescription{\hskip 0pt{}Ryan O'Neal, star of `Love Story,' `Paper Moon,' `Peyton Place' and `Barry Lyndon,' dies at 82}{https://apnews.com/article/bbb21318db9742d0b1e5e4a51c2fa26d}{LOS ANGELES (AP) --- Ryan O'Neal, the heartthrob actor who went from a TV soap opera to an Oscar-nominated role in ``Love Story'' and delivered a wry performance opposite his charismatic 9-year-old daughter Tatum in ``Paper Moon,'' died...}

\entryitemWithDescription{\hskip 0pt{}With no supermarket for residents of Atlantic City, New Jersey and hospitals create mobile groceries}{https://apnews.com/article/c49c6eaf9be2ad959a6fea61e73c2aa0}{ATLANTIC CITY, N.J. (AP) --- In this seaside resort, where \$5 billion worth of in-person and online gambling gets done each year, there still is not a supermarket. People who live in Atlantic City must either drive off the island to a...}

\entryitemWithDescription{\hskip 0pt{}Jonathan Majors begged accuser to avoid hospital, warning of possible `investigation,' messages show}{https://apnews.com/article/87fb75a5ca50c7d7de4ce99cff3abe15}{NEW YORK (AP) --- The actor Jonathan Majors begged his former girlfriend not to seek medical attention after an incident that left her with a head injury last year, warning she had ``no perspective of what could happen'' if the truth got...}

\entryitemWithDescription{\hskip 0pt{}Spotify's CFO is one of thousands to leave the company — after he moves to sell \$9 million in shares}{https://apnews.com/article/e3cd38dc2952df4b2a7fff9cbafe4950}{NEW YORK (AP) --- Spotify's chief financial officer will step down next year, according to the music streaming service, just days after it announced its third round of layoffs for 2023. In a statement announcing CFO Paul Vogel's...}

\entryitemWithDescription{\hskip 0pt{}Thousands of tons of dead sardines wash ashore in northern Japan}{https://apnews.com/article/88003e085359a88cb1135a818c722c05}{TOKYO (AP) --- Thousands of tons of dead sardines have washed up on a beach in northern Japan for unknown reasons, officials said Friday. The sardines and some mackerel washed ashore in Hakodate on Japan's northernmost main island of...}

\entryitemWithDescription{\hskip 0pt{}Woman charged with attempted arson of Martin Luther King Jr. birthplace in Atlanta}{https://apnews.com/article/a642a0d24866e272d3f7418873ef2702}{ATLANTA (AP) --- Atlanta police have arrested a woman who's accused of trying to burn down the birthplace of the Rev. Martin Luther King Jr. in Atlanta. Officers arrested the 26-year-old woman around 5:45 p.m. Thursday after responding to...}