\entryitemWithDescription{\hskip 0pt{}Minnesota unfurls new state flag atop the capitol for the first time Saturday}{https://apnews.com/article/a467e61517134531e65545e696a48fe1}{ST. PAUL, Minnesota (AP) --- Minnesota officially unfurled its new state flag atop the capitol for the first time Saturday on statehood day. The new flag and accompanying state seal were adopted to replace an old design that Native...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Lotus Lantern Festival draws thousands in Seoul to celebrate upcoming Buddha's birthday}{https://apnews.com/article/aa4c53b33de833bef89c0d1294780a0b}{SEOUL, South Korea (AP) --- Holding umbrellas and pink paper lotus flowers, thousands of South Koreans joyously filled the wet streets of Seoul in an annual festival anticipating Buddha's birthday the coming week. Despite the rain...}

\entryitemWithDescription{\hskip 0pt{}Dog Show 101: What's what at the Westminster Kennel Club}{https://apnews.com/article/b5203dec4c9da40f26d6b4fdb09f1616}{NEW YORK (AP) --- To the casual viewer, competing at the Westminster Kennel Club dog show might look pretty simple: Get a dog. Groom it. Pose it. Lead it around a ring. But there's a lot more involved in reaching the pinnacle of U.S...}

\entryitemWithDescription{\hskip 0pt{}Sam Rubin, beloved LA entertainment anchor and interviewer, dies at 64}{https://apnews.com/article/8bd223a18f19225ab6ecc6b16fdcaead}{LOS ANGELES (AP) --- Sam Rubin, a beloved entertainment anchor and reporter for KTLA in Los Angeles who was on a first-name basis with Hollywood's top stars, has died. He was 64. The station announced that he died unexpectedly on Friday...}

\entryitemWithDescription{\hskip 0pt{}Billy Graham statue for U.S. Capitol to be unveiled next week}{https://apnews.com/article/ec14b84226662fb265ae9c721bcbf2f1}{CHARLOTTE, N.C. (AP) --- A statue of the late Rev. Billy Graham set to stand inside the U.S. Capitol to represent North Carolina will be unveiled next week in a ceremony. House Speaker Mike Johnson, other congressional members and the...}

\entryitemWithDescription{\hskip 0pt{}Teen and Miss USA quit their crowns, citing mental health and personal values}{https://apnews.com/article/d188872c2d4948669e416aa7c6bd9870}{The reigning winners of Miss USA, Noelia Voigt, and Miss Teen USA, UmaSofia Srivastava, resigned from their titles within days of each other this week in a shock to the Miss Universe Organization. The resignations leave the longstanding...}

\entryitemWithDescription{\hskip 0pt{}Here's what to know about conservatorships and how Brian Wilson's case evolved}{https://apnews.com/article/283adf3e04aef5744ac818c36131cf9e}{LOS ANGELES (AP) --- A judge put Beach Boys founder Brian Wilson under a court conservatorship to oversee his personal and medical affairs after the legendary songwriter's doctor reported that he has a major neurocognitive disorder. The...}

\entryitemWithDescription{\hskip 0pt{}Djokovic needs medical attention after getting knocked on the head by a water bottle at Italian Open}{https://apnews.com/article/a72f39ee6658ce1bb592526320d5fdfc}{ROME (AP) --- Novak Djokovic needed medical attention after getting knocked on the head by a water bottle after a win at the Italian Open on Friday. A child was leaning over the railing to hand Djokovic a notebook for a signature and an...}

\entryitemWithDescription{\hskip 0pt{}Flavor Flav is the official hype man for the US women's water polo team in the Paris Olympics}{https://apnews.com/article/e9b87dfc32dcdeeabd3cd97121a83c89}{Maggie Steffens asked for more support for the U.S. women's water polo team, and the captain received one particularly surprising response. From a clock-wearing rap icon. Moved by Steffens' Instagram post, Flavor Flav has stepped forward...}

\entryitemWithDescription{\hskip 0pt{}Civil War General William T. Sherman's sword and other relics to be auctioned off in Ohio}{https://apnews.com/article/e6080cb1c6e52be71e57db85e9087a18}{COLUMBUS, Ohio (AP) --- Bidders will fight with their dollars next week at an Ohio auction house for the sword of the Civil War Union general who led a scored-earth campaign across Georgia and coined the phrase ``War is hell.'' General...}

\entryitemWithDescription{\hskip 0pt{}Liam and Olivia are still the most popular US baby names, and Mateo makes his debut on the list}{https://apnews.com/article/c4973e6d6520fa4ba94eb8d70ec41b6c}{WASHINGTON (AP) --- Liam and Olivia have for a fifth year together topped the list of baby names for brand new boys and girls born in the U.S. in 2023. And Mateo joins the top 10 baby names list for the first time. The Social Security...}

\entryitemWithDescription{\hskip 0pt{}For Israel's contestant, the Eurovision Song Contest comes with tight security, boos and cheers}{https://apnews.com/article/23304985ecffe31100968b020dfc23f3}{MALMO, Sweden (AP) --- Eden Golan is in Sweden for the Eurovision Song Contest, but she is not seeing much of the country. The 20-year-old Israeli singer is surrounded by security as she travels between hotel and the contest venue in the...}

\entryitemWithDescription{\hskip 0pt{}Japanese automaker Honda reports booming profit on sales growth, weak yen}{https://apnews.com/article/9dd30bc34774b6c93937768d1e99d92a}{TOKYO (AP) --- Honda's profit for the fiscal year through March jumped 70\% as vehicle sales grew and a weak yen buoyed overseas earnings, the Japanese automaker reported Friday. Annual profit at Tokyo-based Honda Motor Co. totaled 1.1...}