\entryitemWithDescription{\hskip 0pt{}The Nationals have a new first base coach doo doo doo doo doo doo. It's Gerardo `Baby Shark' Parra}{https://apnews.com/article/4216a784c8c3d516c9fad2c58184d2d4}{WASHINGTON (AP) --- Gerardo Parra --- of ``Baby Shark'' fame --- will be the new first base coach for the Washington Nationals as part of a series of changes to manager Dave Martinez's staff announced by the club on Friday after a fourth...}

\entryitemWithDescription{\hskip 0pt{}The Air Force's new nuclear stealth bomber, the B-21 Raider, has taken its first test flight}{https://apnews.com/article/2004cca92c641981567cfb1a1800c838}{WASHINGTON (AP) --- The B-21 Raider took its first test flight on Friday, moving the futuristic warplane closer to becoming the nation's next nuclear weapons stealth bomber. The Raider flew in Palmdale, California, where it has been under...}

\entryitemWithDescription{\hskip 0pt{}Barbie's Ken is left out again as Cabbage Patch Kids and Fisher-Price Corn Popper make Toy Hall of Fame}{https://apnews.com/article/ce07071adca4eb092ec9b262a12594b3}{ROCHESTER, N.Y. (AP) --- Fans have pushed the Fisher-Price Corn Popper into the National Toy Hall of Fame, elevating it from perpetual finalist to 2023 inductee, alongside baseball cards, Cabbage Patch Kids and NERF foam toys, the hall...}

\entryitemWithDescription{\hskip 0pt{}As a DJ, village priest in Portugal cues up faith and electronic dance music for global youth}{https://apnews.com/article/57fff78e81715f91844b6c557cf99eff}{LAÚNDOS, Portugal (AP) --- Guilherme Peixoto, a village priest in northern Portugal, has been busy this month celebrating Masses at his two parishes, presiding over remembrances for the dead --- and preparing the electronic music set for...}

\entryitemWithDescription{\hskip 0pt{}Hollywood's strikes are over, but a painful industry-wide transition isn't}{https://apnews.com/article/21ae6ed16f99cfdd5379d6da4b7d324b}{NEW YORK (AP) --- Hollywood's months of labor unrest are coming to an end, but the post-strike landscape that awaits actors and writers may be far from happily-ever-after. The film and television industry could rightly celebrate the...}

\entryitemWithDescription{\hskip 0pt{}Palestinian soccer team prepares for World Cup qualifying games against a backdrop of war}{https://apnews.com/article/f133537d93598676570e250d636fa7aa}{Makram Daboub may be struggling to prepare his Palestinian team for the start of 2026 World Cup qualification but he takes some comfort, for now at least, that his players stuck in Gaza are safe. The national soccer team's head coach...}

\entryitemWithDescription{\hskip 0pt{}Wildlife refuge pond in Hawaii mysteriously turns bright pink. Drought may be to blame}{https://apnews.com/article/6004cf6ab89d2d72cb54a631e8f7b768}{HONOLULU (AP) --- A pond in Hawaii has turned so bubble-gum pink it could be from the set of ``Barbie,'' but the bizarre phenomenon is no cause for a dance party. Drought may be to blame for the strange hue, scientists say, and they're...}

\entryitemWithDescription{\hskip 0pt{}Media watchdog says it was just `raising questions' with insinuations about photographers and Hamas}{https://apnews.com/article/200be1ba47361f1c1fc113cdaeb65d04}{The executive director of an Israeli media watchdog organization says it was simply ``raising questions'' by publicly wondering whether Palestinian photojournalists who documented the Oct. 7 Hamas attack in Israel --- and sent some of the...}

\entryitemWithDescription{\hskip 0pt{}Astronaut Frank Borman, commander of the first Apollo mission to the moon, has died at age 95}{https://apnews.com/article/ed5eb4edf26a4076a2fef6cc31881aff}{BILLINGS, Mont. (AP) --- Astronaut Frank Borman, who commanded Apollo 8's historic Christmas 1968 flight that circled the moon 10 times and paved the way for the lunar landing the next year, has died. He was 95. Borman died Tuesday in...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift's Argentina concert takes political turn as presidential election nears}{https://apnews.com/article/2548bc419bcb6ae61a2ff258c3df468a}{BUENOS AIRES, Argentina (AP) --- As thousands of Taylor Swift fans eagerly lined up Thursday for the superstar's first-ever concert in Argentina, they saw themselves surrounded by posters urging them to not vote in favor of right-wing...}

\entryitemWithDescription{\hskip 0pt{}Jury awards \$1.2 million to Robert De Niro's former assistant in gender discrimination lawsuit}{https://apnews.com/article/07b4d5c932667ea1867ba9352946148d}{NEW YORK (AP) --- A jury awarded more than \$1.2 million to Robert De Niro's former personal assistant Thursday, finding one of his companies responsible for subjecting her to a toxic work environment. While the jury found De Niro was not...}

\entryitemWithDescription{\hskip 0pt{}Demonstrators brawl outside LA's Museum of Tolerance after screening of Hamas attack video}{https://apnews.com/article/361a89c041bba0d4bd88220ca59c9f99}{LOS ANGELES (AP) --- Street fights erupted between pro-Israeli and pro-Palestinian demonstrators outside Los Angeles' Museum of Tolerance after a private screening of video showing the Oct. 7 attack on Israel by Hamas militants. The Los...}

\entryitemWithDescription{\hskip 0pt{}Shohei Ohtani is donating 60,000 baseball gloves to Japanese schoolchildren}{https://apnews.com/article/b99e038c20042939001ee8caf87a1534}{ANAHEIM, Calif. (AP) --- Two-way star and coveted free agent Shohei Ohtani is donating about 60,000 baseball gloves to Japanese elementary schools. Ohtani, a free agent who has spent the past six seasons with the Los Angeles Angels...}