\entryitemWithDescription{\hskip 0pt{}AP Source: Lionel Messi set to leave PSG at end of season}{https://apnews.com/article/d196f387d71a53a57ea4158897539649}{PSG\textquotesingle s Lionel Messi reacts during the French League One soccer match between Paris Saint-Germain and Lorient, at the Parc des Princes stadium in Paris, Sunday, April 30, 2023. (AP Photo/Aurelien Morissard) Lionel Messi is...}

\entryitemWithDescription{\hskip 0pt{}Wrongfully convicted Massachusetts man gets \$13M settlement}{https://apnews.com/article/1d91f49d0f99bee60bf32f118b15128d}{Victor Rosario, 65, stands next to a photo of himself at age 24 when he was on trial in 1982 for arson, Wednesday, May 3, 2023, outside the federal courthouse in Boston. Rosario, who spent 32 years in prison after he was wrongfully...}

\entryitemWithDescription{\hskip 0pt{}Sex offender fatally shot 6, then killed self, official says}{https://apnews.com/article/2286716517d004033781a1303e4035dd}{Ashleigh Webster shows a photo of Ivy Webster and Tiffany Guess at her home in Henryetta, Okla., Tuesday, May 2, 2023. (Nathan J. Fish/The Oklahoman via AP) An Oklahoma sex offender who was released from prison early shot his wife, her...}

\entryitemWithDescription{\hskip 0pt{}Ralph Boston, Olympian and 1st to jump 27 feet, dies at 83}{https://apnews.com/article/344c1c35bc89c7814d03d006577b72ed}{FILE - Ralph Boston smiles on the podium at the Summer Olympics in Rome, Italy, Sept. 2, 1960. Ralph Boston, the Olympic long jump champion who broke Jesse Owens\textquotesingle{} record then later had his own mark eclipsed by Bob Beamon...}

\entryitemWithDescription{\hskip 0pt{}Summer Movies: 6 breakout performances to watch}{https://apnews.com/article/fa84d94a22bc3a89aaa89dae1af8ab4b}{This image released by A24 shows Greta Lee, left, and Teo Yoo in a scene from "Past Lives." (Jon Pack/A24 via AP) Anonymity can be an actor's best friend, but this summer several talents are primed to make themselves known in major film...}

\entryitemWithDescription{\hskip 0pt{}Chokehold killed man restrained by NYC subway passengers}{https://apnews.com/article/c1b1383b3163f3f5d2c22a267bc52f41}{New York police officers respond to the scene where a fight was reported on a subway train, Monday, May 1, 2023, in New York. A man suffering an apparent mental health episode aboard a New York City subway died on Monday after being...}

\entryitemWithDescription{\hskip 0pt{}Pompeii chariot stars in Rome exhibit probing ancient roots}{https://apnews.com/article/7957aaecc6edd7d7cada6e79a4c0a6d7}{A view of the exhibition \textquotesingle Between us and the ancients. The instant and eternity\textquotesingle{} in Rome\textquotesingle s Diocletian Baths, Wednesday, May 3, 2023. The exhibition will open to the public from May 4...}

\entryitemWithDescription{\hskip 0pt{}4 dangers that most worry AI pioneer Geoffrey Hinton}{https://apnews.com/article/6e4992e7a87d5bcae787ad45545757db}{File - Computer scientist Geoffrey Hinton poses at Google\textquotesingle s Mountain View, Calif, headquarters on Wednesday, March 25, 2015. Computer scientists who helped build the foundations of today\textquotesingle s artificial...}

\entryitemWithDescription{\hskip 0pt{}3 Colorado teens charged with murder in rock-throwing death}{https://apnews.com/article/25237afd0e502e0478301c769e612a1f}{Defendant Zachary Kwak listens to district court judge Christopher C. Zenisek during an arraignment in Jefferson County district court on Wednesday, May 3, 2023, in Golden, Colo. Kwak along with Joseph Koenig and Nicholas "Mitch" Karol...}

\entryitemWithDescription{\hskip 0pt{}Patrick Mahomes' brother Jackson charged with sexual battery}{https://apnews.com/article/812506d230c0964df8ff7feecf4c359f}{Jackson Mahomes, center, exits the Johnson County jail after being arraigned on three charges of sexual battery on Wednesday, May 3, 2023, in Olathe, Kan. (Nick Wagner/The Kansas City Star via AP) OVERLAND PARK, Kan. (AP) --- Jackson...}

\entryitemWithDescription{\hskip 0pt{}Since his ouster, embarrassing reports on Carlson pile up}{https://apnews.com/article/0ca0ef08799f3d99d88ea953e9dd7dac}{FILE - Tucker Carlson, host of "Tucker Carlson Tonight," poses for photos in a Fox News Channel studio on March 2, 2017, in New York. A racist text message from Tucker Carlson is what helped drive the commentator\textquotesingle s ouster...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk threatens to reassign NPR's Twitter account}{https://apnews.com/article/3804ce1c03926c4255827c00308f1133}{FILE - The headquarters for National Public Radio (NPR) stands on North Capitol Street on April 15, 2013, in Washington. Elon Musk threatened to reassign NPR's Twitter account to ``another company,'' according to the non-profit news...}

\entryitemWithDescription{\hskip 0pt{}McDonald's franchises fined for child labor violations}{https://apnews.com/article/d73da97e7297d334cbad9085f8b802d9}{FILE - A McDonald\textquotesingle s sign at a restaurant in downtown Pittsburgh, April 24, 2017. Federal investigators found more than 300 minors, including the 10-year-olds, were working illegally, the Labor Department said in a...}