


\ipart{Developers}
\ichapter{Hacker News}
\entryitemTwoLinks{Newsmax agrees to pay \$67M in defamation case over bogus 2020 election claims}{https://news.ycombinator.com/item?id=44945925}{https://apnews.com/article/dominion-voting-newsmax-defamation-trump-2020-3b2366dfdae3a8432afe822bf14fe1ef}

\entryitemTwoLinks{Obsidian Bases}{https://news.ycombinator.com/item?id=44945532}{https://help.obsidian.md/bases}

\entryitemTwoLinks{GenAI FOMO has spurred businesses to light nearly \$40B on fire}{https://news.ycombinator.com/item?id=44944620}{https://www.theregister.com/2025/08/18/generative\_ai\_zero\_return\_95\_percent/}

\entryitemTwoLinks{T-Mobile claimed selling location data without consent is legal–judges disagree}{https://news.ycombinator.com/item?id=44944291}{https://arstechnica.com/tech-policy/2025/08/t-mobile-claimed-selling-location-data-without-consent-is-legal-judges-disagree/}

\entryitemTwoLinks{Left to Right Programming}{https://news.ycombinator.com/item?id=44942936}{https://graic.net/p/left-to-right-programming}

\entryitemTwoLinks{Show HN: Whispering – Open-source, local-first dictation you can trust}{https://news.ycombinator.com/item?id=44942731}{https://github.com/epicenter-so/epicenter/tree/main/apps/whispering}

\entryitemTwoLinks{My Retro TVs}{https://news.ycombinator.com/item?id=44942602}{https://www.myretrotvs.com/}

\entryitemTwoLinks{Anna's Archive: An Update from the Team}{https://news.ycombinator.com/item?id=44942501}{https://annas-archive.org/blog/an-update-from-the-team.html}

\entryitemTwoLinks{Who Invented Backpropagation?}{https://news.ycombinator.com/item?id=44941963}{https://people.idsia.ch/~juergen/who-invented-backpropagation.html}

\entryitemTwoLinks{The road that killed Legend Jenkins was working as designed}{https://news.ycombinator.com/item?id=44941766}{https://www.strongtowns.org/journal/2025/8/18/the-road-that-killed-legend-jenkins-was-working-exactly-as-designed}

\entryitemTwoLinks{Counter-Strike: A billion-dollar game built in a dorm room}{https://news.ycombinator.com/item?id=44941369}{https://www.nytimes.com/2025/08/18/arts/counter-strike-half-life-minh-le.html}

\entryitemTwoLinks{95\% of AI Pilots Failing}{https://news.ycombinator.com/item?id=44941118}{https://fortune.com/2025/08/18/mit-report-95-percent-generative-ai-pilots-at-companies-failing-cfo/}

\entryitemTwoLinks{AI is predominantly replacing outsourced, offshore workers}{https://news.ycombinator.com/item?id=44940944}{https://www.axios.com/2025/08/18/ai-jobs-layoffs}

\entryitemTwoLinks{Class-action suit claims Otter AI records private work conversations}{https://news.ycombinator.com/item?id=44940554}{https://www.npr.org/2025/08/15/g-s1-83087/otter-ai-transcription-class-action-lawsuit}

\entryitemTwoLinks{FFmpeg Assembly Language Lessons}{https://news.ycombinator.com/item?id=44940485}{https://github.com/FFmpeg/asm-lessons}

\entryitemTwoLinks{Texas law gives grid operator power to disconnect data centers during crisis}{https://news.ycombinator.com/item?id=44940416}{https://www.utilitydive.com/news/texas-law-gives-grid-operator-power-to-disconnect-data-centers-during-crisi/751587/}

\entryitemTwoLinks{Vibe coding tips and tricks}{https://news.ycombinator.com/item?id=44940089}{https://github.com/awslabs/mcp/blob/main/VIBE\_CODING\_TIPS\_TRICKS.md}

\entryitemTwoLinks{When you're asking AI chatbots for answers, they're data-mining you}{https://news.ycombinator.com/item?id=44939660}{https://www.theregister.com/2025/08/18/opinion\_column\_ai\_surveillance/}

\entryitemTwoLinks{LLMs and coding agents are a security nightmare}{https://news.ycombinator.com/item?id=44939331}{https://garymarcus.substack.com/p/llms-coding-agents-security-nightmare}

\entryitemTwoLinks{Website is served from nine Neovim buffers on my old ThinkPad}{https://news.ycombinator.com/item?id=44939324}{https://vim.gabornyeki.com/}\ichapter{Phoronix}
\entryitemGeneric{\hskip 0pt{}AMD "GFX1250" To Double The Number Of User SGPRs}{https://www.phoronix.com/news/AMD-GFX1250-32-User-SGPRs}

\entryitemGeneric{\hskip 0pt{}AMD ZenDNN 5.1 Released For Enhancing AI Inference Performance On EPYC CPUs}{https://www.phoronix.com/news/AMD-ZenDNN-5.1}

\entryitemGeneric{\hskip 0pt{}Kdenlive 25.08 Preps For Future Hardware Acceleration Features}{https://www.phoronix.com/news/Kdenlive-25.08-Released}

\entryitemGeneric{\hskip 0pt{}Git 2.51 Released With More Changes Preparing For Git 3.0}{https://www.phoronix.com/news/Git-2.51-Released}

\entryitemGeneric{\hskip 0pt{}A Deep Dive Into The Power \& Thermals For The Framework Desktop With AMD Ryzen AI Max}{https://www.phoronix.com/review/framework-desktop-power}

\entryitemGeneric{\hskip 0pt{}AMD Posts Latest Linux Patches For Improving S5 Power Consumption}{https://www.phoronix.com/news/AMD-S5-Power-Optimizations-v6}

\entryitemGeneric{\hskip 0pt{}Firefox 142 Now Available - Allows Browser Extensions/Add-Ons To Use AI LLMs}{https://www.phoronix.com/news/Firefox-142-Extensions-AI-LLMs}

\entryitemGeneric{\hskip 0pt{}GNOME 49 Merges Late Mutter Change To Help Cursor Responsiveness With VRR}{https://www.phoronix.com/news/GNOME-49-VRR-Cursor}

\entryitemGeneric{\hskip 0pt{}Illumos Cafe Hopes To Reinvigorate Interest In Illumos/OpenSolaris Derived Platforms}{https://www.phoronix.com/news/Illumos-Cafe}


\ipart{Developers~~~~(zh-Hans)}
\ichapter{Solidot}
\entryitemGeneric{\hskip 0pt{}一种蛋白质在人体中传递衰老信号}{https://www.solidot.org/story?sid=82070}

\entryitemGeneric{\hskip 0pt{}2025 年雨果奖宣布}{https://www.solidot.org/story?sid=82069}

\entryitemGeneric{\hskip 0pt{}FFmpeg 迁移到 Forgejo}{https://www.solidot.org/story?sid=82068}

\entryitemGeneric{\hskip 0pt{}克罗地亚将数字游民签证有效期延长至三年}{https://www.solidot.org/story?sid=82067}

\entryitemGeneric{\hskip 0pt{}今年前七个月电动汽车销量同比增长 27\%}{https://www.solidot.org/story?sid=82066}

\entryitemGeneric{\hskip 0pt{}PuTTY 有了新官网}{https://www.solidot.org/story?sid=82065}

\entryitemGeneric{\hskip 0pt{}德国最高法院部分推翻广告屏蔽工具不侵犯版权判决}{https://www.solidot.org/story?sid=82064}\ichapter{V2EX}
\entryitemGeneric{\hskip 0pt{}[分享创造] [工具自荐] 花了几天用 claude code 做了个解梦网站。免费用！}{https://www.v2ex.com/t/1153333}

\entryitemGeneric{\hskip 0pt{}[汽车] 你们是怎么确定保养要做的项目的}{https://www.v2ex.com/t/1153332}

\entryitemGeneric{\hskip 0pt{}[程序员] 找人开发一个检测是否为 Ai 图的模型要多少费用}{https://www.v2ex.com/t/1153331}

\entryitemGeneric{\hskip 0pt{}[生活] 看完 1781，分享下我的 3409 天}{https://www.v2ex.com/t/1153330}

\entryitemGeneric{\hskip 0pt{}[问与答] 怎么理解``你戾气真重''}{https://www.v2ex.com/t/1153329}

\entryitemGeneric{\hskip 0pt{}[程序员] 你们在备份数据时会暂停服务以保持数据的一致性吗？}{https://www.v2ex.com/t/1153328}

\entryitemGeneric{\hskip 0pt{}[macOS] Beta7 尝鲜}{https://www.v2ex.com/t/1153327}

\entryitemGeneric{\hskip 0pt{}[Apple] 如何禁止 Siri 打电话？}{https://www.v2ex.com/t/1153326}

\entryitemGeneric{\hskip 0pt{}[汽车] 交强险如果过期没买有什么后果}{https://www.v2ex.com/t/1153325}

\entryitemGeneric{\hskip 0pt{}[问与答] 有家畜生一样的邻居怎么办？}{https://www.v2ex.com/t/1153324}

\entryitemGeneric{\hskip 0pt{}[分享创造] Chrome 插件：推特 Profile 扩展菜单和隐藏窗口功能}{https://www.v2ex.com/t/1153323}

\entryitemGeneric{\hskip 0pt{}[职场话题] 个人目前很迷茫，求老哥指点下方向}{https://www.v2ex.com/t/1153322}

\entryitemGeneric{\hskip 0pt{}[SQLite] 分享适合高并发场景的 SQLite 设置}{https://www.v2ex.com/t/1153321}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 现在本地部署了一个 gpt-oss，有什么好的提示词可以解除它的道德限制吗，可以搞成人相关的东西的}{https://www.v2ex.com/t/1153319}

\entryitemGeneric{\hskip 0pt{}[站长] 收网站：下载站、游戏站、编程站、资源站、教程资源等等}{https://www.v2ex.com/t/1153318}

\entryitemGeneric{\hskip 0pt{}[Solana] 1781 天后\$V2EX 能到什么价位？能到\$17.82 嘛？}{https://www.v2ex.com/t/1153317}

\entryitemGeneric{\hskip 0pt{}[Cloudflare] 网站上 cloudflare 之后的奇怪流量都是哪里来的}{https://www.v2ex.com/t/1153316}

\entryitemGeneric{\hskip 0pt{}[数学] 猜不重复 4 位数，只能回答同位命中多少个，有无最快必胜办法？}{https://www.v2ex.com/t/1153315}

\entryitemGeneric{\hskip 0pt{}[职场话题] 怎么克服找工作面试的恐惧？}{https://www.v2ex.com/t/1153314}

\entryitemGeneric{\hskip 0pt{}[职场话题] 合同续签，五险一金缴纳基数，亏大了}{https://www.v2ex.com/t/1153313}

\entryitemGeneric{\hskip 0pt{}[分享创造] 写了个基于 NPM 的插件系统}{https://www.v2ex.com/t/1153312}

\entryitemGeneric{\hskip 0pt{}[游戏] 云风推荐的桌游 Deep Future 到底是什么游戏？怎么玩？}{https://www.v2ex.com/t/1153311}

\entryitemGeneric{\hskip 0pt{}[ACG] 有人知道遮天的解说大帝为什么没了，还会回来么}{https://www.v2ex.com/t/1153310}

\entryitemGeneric{\hskip 0pt{}[天黑以后] 20250818 午夜俱乐部}{https://www.v2ex.com/t/1153309}

\entryitemGeneric{\hskip 0pt{}[生活] 都来说说国内银行卡被限额的那些事}{https://www.v2ex.com/t/1153307}

\entryitemGeneric{\hskip 0pt{}[职场话题] 后悔的一次跳槽决定}{https://www.v2ex.com/t/1153306}

\entryitemGeneric{\hskip 0pt{}[分享创造] 脚本分享， SpeedUp 长按空格倍速播放视频}{https://www.v2ex.com/t/1153304}

\entryitemGeneric{\hskip 0pt{}[电影] 《碟中谍 8》中的代码片段}{https://www.v2ex.com/t/1153303}

\entryitemGeneric{\hskip 0pt{}[问与答] win 用户切换到 mac 的几个问题想请教一下}{https://www.v2ex.com/t/1153302}

\entryitemGeneric{\hskip 0pt{}[VPS] 请兄弟们推荐 VPS}{https://www.v2ex.com/t/1153301}

\entryitemGeneric{\hskip 0pt{}[YouTube] 油管这么牛比么？这是自动翻译音轨，还是人工的？}{https://www.v2ex.com/t/1153300}

\entryitemGeneric{\hskip 0pt{}[问与答] App 对接聚合广告}{https://www.v2ex.com/t/1153298}

\entryitemGeneric{\hskip 0pt{}[前端开发] 请教大佬 FluentUI Toast 不显示的问题}{https://www.v2ex.com/t/1153297}

\entryitemGeneric{\hskip 0pt{}[问与答] 各位 Gopher 的 IDE 是什么？ VSCode V.S. GoLand}{https://www.v2ex.com/t/1153294}

\entryitemGeneric{\hskip 0pt{}[iOS] 今天晚上或者明天有 iOSBeta7 吗？}{https://www.v2ex.com/t/1153292}

\entryitemGeneric{\hskip 0pt{}[分享创造] 用 Claude Code 做了一个图片增强和去背景网站（免费用）}{https://www.v2ex.com/t/1153291}

\entryitemGeneric{\hskip 0pt{}[Linux] ubuntu/debian 如何才能把 lvm thin 逻辑卷上的分区作为根文件系统？}{https://www.v2ex.com/t/1153290}

\entryitemGeneric{\hskip 0pt{}[问与答] MUJI 的硅胶锅铲有人用过吗，种草了}{https://www.v2ex.com/t/1153289}

\entryitemGeneric{\hskip 0pt{}[数据库] 不限语言，你觉得最好用的框架和 ORM 是什么？}{https://www.v2ex.com/t/1153288}

\entryitemGeneric{\hskip 0pt{}[macOS] 请教 mac 能部署生成图片和视频的本地 ai 么？}{https://www.v2ex.com/t/1153287}

\entryitemGeneric{\hskip 0pt{}[生活] 看完 1781 的校园爱情分手贴，想到十年前自己的小故事}{https://www.v2ex.com/t/1153285}

\entryitemGeneric{\hskip 0pt{}[程序员] [超越 Manus] 超级智能体《imini》聚合 23 款全球 AI 大模型 kimi、GPT、Gemin、Grok、Claude...}{https://www.v2ex.com/t/1153283}

\entryitemGeneric{\hskip 0pt{}[Windows] win11 更新会导致 SSD 掉盘？}{https://www.v2ex.com/t/1153281}

\entryitemGeneric{\hskip 0pt{}[奇思妙想] 在学钢琴或者家里有人弹钢琴的看过来-是不是需要这样一个钢琴助手？}{https://www.v2ex.com/t/1153277}

\entryitemGeneric{\hskip 0pt{}[问与答] 求大佬帮忙推荐装机配置(锁定 983/783+5070ti)！}{https://www.v2ex.com/t/1153276}

\entryitemGeneric{\hskip 0pt{}[问与答] 蹭蹭 1781 天热度，你每个月会给女朋友花多少钱？}{https://www.v2ex.com/t/1153275}

\entryitemGeneric{\hskip 0pt{}[云计算] BUYPASS 终止了 SSL 证书的签发}{https://www.v2ex.com/t/1153273}

\entryitemGeneric{\hskip 0pt{}[问与答] 都是搞技术的、没有玩权力的？}{https://www.v2ex.com/t/1153272}

\entryitemGeneric{\hskip 0pt{}[生活] 这个孙宇晨就像小说的主角，简直开挂了一样}{https://www.v2ex.com/t/1153271}

\entryitemGeneric{\hskip 0pt{}[生活] 2351 天，时间会抹平一切}{https://www.v2ex.com/t/1153270}


\ipart{Generic News}
