\entryitemWithDescription{\hskip 0pt{}EPA orders 'pause' of derailment contaminated waste removal}{https://apnews.com/article/ef698f4bbbcea1e2b7d7e2bad66bbd4e}{FILE - This photo taken with a drone shows portions of a Norfolk Southern freight train that derailed Friday night in East Palestine, Ohio are still on fire at mid-day Saturday, Feb. 4, 2023. Toxic wastewater used to extinguish a fire...}

\entryitemWithDescription{\hskip 0pt{}Rights to 'Crying Indian' ad to go to Native American group}{https://apnews.com/article/97c6b0affacbe64370ad3e1bf7f1c70c}{FILE - Iron Eyes Cody, the \textquotesingle\textquotesingle Crying Indian\textquotesingle\textquotesingle{} whose tearful face in 1970s TV commercials became a powerful symbol of the anti-littering campaign, is pictured in this 1986...}

\entryitemWithDescription{\hskip 0pt{}Jill Biden talks safe sex, condoms with Kenya's young adults}{https://apnews.com/article/a2d1df44f86a36950c6844afdcdb7447}{US first lady Jill Biden, centre, meets youth at Village Creative in Nairobi, Kenya, Saturday, Feb. 25, 2023. Biden is in Kenya on the second and final stop of her trip. (AP Photo/Brian Inganga) NAIROBI, Kenya (AP) --- It was a Saturday...}

\entryitemWithDescription{\hskip 0pt{}Met Opera marks 1st year of Ukraine war with concert}{https://apnews.com/article/037fb5aaf4d3cf6563608c8e0b77f88f}{This photo provided by Metropolitan Opera, Met music director Yannick Nézet-Séguin leads mezzo-soprano Emily D'Angelo, soprano Golda Schultz, tenor Dmytro Popov, and bass-baritone Vladyslav Buialskyi in the National Anthem of Ukraine...}

\entryitemWithDescription{\hskip 0pt{}Bills would let transgender people seal name-change requests}{https://apnews.com/article/c1c8a24a01c5d307bdc2e9037c1b0fd0}{Maia Xiao poses for a portrait in the library of radio station KEXP where she volunteers in Seattle, Feb. 17, 2023. A letter from Xiao prompted a Washington state lawmaker to introduce a bill that would keep out of the public record...}

\entryitemWithDescription{\hskip 0pt{}Inadequate investigation? Takeaways at Murdaugh murder trial}{https://apnews.com/article/13a31ec73cf6da2f65848ac6e016b6be}{Defendant Alex Murdaugh is cross examined by prosecutor Creighton Waters while testifying during his murder trial at the Colleton County Courthouse in Walterboro, S.C., Friday, Feb. 24, 2023. The 54-year-old attorney is standing trial on...}

\entryitemWithDescription{\hskip 0pt{}Ukraine: Zelenskyy seeks more sanctions, fighting grinds on}{https://apnews.com/article/1753e114c499886eecc8d8bb169baeb4}{Ukrainian military fires from a multiple rocket launcher at Russian positions in the Kharkiv area, Ukraine, Saturday, Feb. 25, 2023. The Biden administration declared its Ukraine solidarity with fresh action as well as strong words on...}

\entryitemWithDescription{\hskip 0pt{}Seattle Opera puts story of Afghan women center stage}{https://apnews.com/article/d24f34a260f7eff82e7c4e5248a21b07}{Maureen McKay, left, who portrays Laila, John Moore, who portrays Rasheed, and Karin Mushegain, who portrays Mariam, perform in a dress rehearsal for the opera "A Thousand Splendid Suns," in Seattle, on Wednesday, Feb. 22, 2023. Making...}

\entryitemWithDescription{\hskip 0pt{}Some Democratic-led states seek to bolster voter protections}{https://apnews.com/article/45232bc1b2b64fd822b313e11b1ae3ec}{FILE - A voter drops his ballot in a drop box at Marilyn J. Praisner Community Recreation Center, during Election Day on Nov. 8, 2022, in Burtonsville, Md. Lawmakers in several Democratic-controlled states are pushing sweeping voting...}

\entryitemWithDescription{\hskip 0pt{}G-20 meeting in India ends without consensus on Ukraine war}{https://apnews.com/article/811b1053cc2332663176de5e0b9aef7b}{In this handout photo released by Indian Finance Ministry, Australia\textquotesingle s Treasurer Jim Chalmers, left, meets with Indian Finance Minister Nirmala Sitharaman on the sidelines of G-20 financial conclave on the outskirts of...}

\entryitemWithDescription{\hskip 0pt{}Pipeline debate at center of California carbon capture plans}{https://apnews.com/article/fa16aa985a1badf8e68fdd22914feb6b}{Lupe Martinez, an activist and former farmworker, poses for a photo at his home in Delano, Calif., on Sunday, Feb. 5, 2023. California\textquotesingle s plan to eliminate its carbon emissions by 2045 relies heavily on capturing carbon and...}

\entryitemWithDescription{\hskip 0pt{}Justice Thomas wrote of 'crushing weight' of student loans}{https://apnews.com/article/9c248eeea0e8d8e24445ca95a74ec0dc}{FILE - Associate Justice Clarence Thomas joins other members of the Supreme Court as they pose for a new group portrait, at the Supreme Court building in Washington, Oct. 7, 2022. The Supreme Court won't have far to look for a personal...}

\entryitemWithDescription{\hskip 0pt{}After delays, Nigerians keep watch for key vote's outcome}{https://apnews.com/article/ec70477e2e4354f1ceed6188662bb599}{Party agents and supporters of presidential candidate Peter Obi of the Labour Party cheer as their candidate wins the count at a polling station near to the home of ruling party presidential candidate Bola Tinubu, in Lagos, Nigeria...}