\entryitemWithDescription{\hskip 0pt{}78-year-old bank heist suspect: 'I didn't mean to scare you'}{https://apnews.com/article/fcaa66a6c78eefc0e7bdf1df4a88c8c2}{HARRISONVILLE, Mo. (AP) --- A 78-year-old woman with two past bank robbery convictions faces new charges after authorities allege she handed a teller a note that said ``I didn't mean to scare you'' during a recent Missouri heist. Bonnie...}

\entryitemWithDescription{\hskip 0pt{}Cubans seek solutions and solace in Santería amid crises}{https://apnews.com/article/e7bf183a2c2bdbe2e3ed4ff85a142b31}{A doll depicting the Yoruba deity Yemayá is propped up on a chair before the start of a Santería ceremony in the home of Mandy Arrazcaeta, in Havana, Cuba, Sunday, Nov. 13, 2022. A fusion of African religions and Catholicism, Santería was...}

\entryitemWithDescription{\hskip 0pt{}Blumenthal breaks leg at UConn parade, to undergo surgery}{https://apnews.com/article/57b735f4a2ee7c91390724f1fc994c6f}{FILE - Sen. Richard Blumenthal, D-Conn., speaks during a news conference on Feb. 16, 2023, on Capitol Hill in Washington. Blumenthal said he expects to undergo surgery to repair a broken leg he suffered Saturday, April 8, during a victory...}

\entryitemWithDescription{\hskip 0pt{}3 taken to hospital after Delaware mall shooting}{https://apnews.com/article/361706c3aa2306607adf7674efdb5f87}{CHRISTIANA, Del. (AP) --- A Delaware mall shooting left three people injured and forced shoppers to evacuate as police investigate. Delaware State Police said authorities do not have a suspect in custody in the shooting at the Christiana...}

\entryitemWithDescription{\hskip 0pt{}Browns' Watson scheduled to give deposition in civil lawsuit}{https://apnews.com/article/059e16686f7ab19ba4b33a1dec098362}{FILE - Cleveland Browns quarterback Deshaun Watson (4) look son during an NFL football game against the Cincinnati Bengals, Tuesday, Dec. 13, 2022, in Cincinnati. The Browns quarterback is scheduled to give a deposition on Monday, April...}

\entryitemWithDescription{\hskip 0pt{}Texas gov. seeks to pardon Army sergeant convicted of murder}{https://apnews.com/article/fa7feeadf552fe01bd6394d13de4178d}{FILE - This booking photo provided by the Austin, Texas, Police Department shows U.S. Army Sgt. Daniel Perry. Perry was convicted of murder for fatally shooting an armed protester in 2020 during nationwide protests against police violence...}

\entryitemWithDescription{\hskip 0pt{}Competing abortion pill rulings sow broad alarm, confusion}{https://apnews.com/article/5fd29a4678e7678a6538054eb75b6d15}{FILE - Three members of the Women\textquotesingle s March group protest in support of access to abortion medication outside the Federal Courthouse on Wednesday, March 15, 2023 in Amarillo, Texas. Matthew Kacsmaryk, a Texas judge who...}

\entryitemWithDescription{\hskip 0pt{}Swanson injures left knee in US match against Ireland}{https://apnews.com/article/ff5dc76c0fde891dab5a65da503f6bae}{United States forward Mallory Swanson (9) goes down with an injury during the first half of an international friendly soccer match against Ireland in Austin, Texas, Saturday, April 8, 2023. (AP Photo/Eric Gay) AUSTIN, Texas (AP...}

\entryitemWithDescription{\hskip 0pt{}Cyclist Ethan Boyes dies after being struck in San Francisco}{https://apnews.com/article/716277ca99be6da3b0d29be4e6260562}{Sydney Parcell, right, and Wagner Sousa place a track cycling world champion jersey at a memorial, Thursday, April 6, 2023, in San Francisco, near where friend Ethan Boyes was fatally struck by a vehicle earlier in the week. (Stephen Lam/...}

\entryitemWithDescription{\hskip 0pt{}Show stopper: Singalong fans ejected, 'Bodyguard' halted}{https://apnews.com/article/2732ae0499a1f0c47ea2ef335ae26f27}{FILE - US singer and actress Melody Thornton poses for a photo, Nov. 22, 2021. A British performance of ``The Bodyguard'' musical ended in unrequited love for some audience members who couldn\textquotesingle t refrain from singing along...}

\entryitemWithDescription{\hskip 0pt{}Court backs teacher firing over transgender students' names}{https://apnews.com/article/883b50e19088614d71df25f0f835ed08}{CHICAGO (AP) --- An Indiana school district did not violate a former music teacher\textquotesingle s rights by pushing him to resign after the man refused to use transgender students\textquotesingle{} names and gender pronouns, a federal...}

\entryitemWithDescription{\hskip 0pt{}Report: Florida officials cut key data from vaccine study}{https://apnews.com/article/c498ffcb2393a1fffd692e1687e62e4e}{FILE - Dr. Joseph Ladapo speaks with reporters after the Florida Senate confirmed his appointment as the state\textquotesingle s surgeon general on Feb. 23, 2022, in Tallahassee, Fla. An analysis that was the basis of a highly criticized...}

\entryitemWithDescription{\hskip 0pt{}Iowa won't pay for rape victims' abortions or contraceptives}{https://apnews.com/article/41ad066f0831961eeec57a676b4a67d6}{FILE - Iowa Republican Attorney General candidate Brenna Bird speaks during a Republican Party of Iowa election night rally, Tuesday, Nov. 8, 2022, in Des Moines, Iowa. The Iowa Attorney General\textquotesingle s Office has, at least for...}