\entryitemWithDescription{\hskip 0pt{}New York moves to ban 'addictive' social media feeds for kids}{https://apnews.com/article/82779a3040385dfc26c6ee15f490234e}{ALBANY, N.Y. (AP) --- The New York state Legislature on Friday passed a bill that would allow parents to block their kids from getting social media posts suggested by a platform's algorithm --- a regulation that tries to curtail feeds...}

\entryitemWithDescription{\hskip 0pt{}California law bars ex-LAPD officer Mark Fuhrman, who lied at OJ Simpson trial, from policing}{https://apnews.com/article/3e3e691a5c6b5671dd8aedf06b96b444}{LOS ANGELES (AP) --- Former Los Angeles police detective Mark Fuhrman who was convicted of lying on the witness stand in the O.J. Simpson trial three decades ago, is now barred from law enforcement under a California police reform law...}

\entryitemWithDescription{\hskip 0pt{}Mike Tyson's fight with Jake Paul has been rescheduled for Nov. 15 after Tyson's health episode}{https://apnews.com/article/ee7205dce33864348415718197301796}{Mike Tyson's fight with Jake Paul is now set for Nov. 15 after the former world heavyweight champion fell ill on a flight last month. The fight was originally set for July 20 in Arlington, Texas, home to the NFL's Dallas Cowboys, and will...}

\entryitemWithDescription{\hskip 0pt{}Police won't bring charges after monster truck accident injures several spectators}{https://apnews.com/article/82d3b2f5ae5d026a660a9ec3c304d980}{TOPSHAM, Maine (AP) --- A police investigator concluded no criminal charges were warranted after a lobster-themed monster truck clipped a power line, causing some scary moments with live wires falling to the ground. Two people were taken...}

\entryitemWithDescription{\hskip 0pt{}Prince William is usher at wedding of aristocrat the Duke of Westminster}{https://apnews.com/article/05c2bd9a24ca83fd64e2ce35734e7acb}{LONDON (AP) --- Prince William took a day out from royal duties on Friday to serve as an usher at the wedding of his friend Hugh Grosvenor, the Duke of Westminster. The wedding of 33-year-old Grosvenor, one of Britain's wealthiest...}

\entryitemWithDescription{\hskip 0pt{}At D-Day ceremony, American veteran hugs Ukraine's Zelenskyy and calls him a savior}{https://apnews.com/article/fcdd36467ac276b9998e69e71d5788e0}{OMAHA BEACH, France (AP) --- An American veteran and Ukrainian President Volodymyr Zelenskyy shared an emotional moment at a ceremony to commemorate the 80th anniversary of the D-Day invasion to liberate France in World War II, each...}

\entryitemWithDescription{\hskip 0pt{}James Beard finalists include an East African restaurant in Detroit and Seattle pho shops}{https://apnews.com/article/e7338ba7231b0cb8d8ad63f34b185f62}{CHICAGO (AP) --- An East African eatery in Detroit, longtime family owned Seattle pho shops and a Palestinian chef using ancient cooking techniques in Washington, D.C., are among the dozens of finalists for this year's prestigious James...}

\entryitemWithDescription{\hskip 0pt{}Diana Ross, Eminem and Jack White perform for thousands as former Detroit eyesore returns to life}{https://apnews.com/article/53063694edc548d4d904d6cf62ebe403}{DETROIT (AP) --- A myriad of Detroit's greatest musical exports, including Diana Ross, Eminem and Jack White, took to the stage Thursday night in a pulsating sonic spectacle held on the eve of the historic reopening of an 18-story...}

\entryitemWithDescription{\hskip 0pt{}Celtics rout Mavericks 107-89 in Game 1 of NBA Finals behind Brown, returning Porzingis}{https://apnews.com/article/521bcb5c7ea943a61ecc218e9364cfc8}{BOSTON (AP) --- Kristaps Porzingis didn't want to make predictions about how his body would respond heading into the NBA Finals after he spent more than a month on the sideline with a calf injury. Just fine, it turned out. Jaylen Brown...}

\entryitemWithDescription{\hskip 0pt{}Judge dismisses attempted murder and other charges in state case against Paul Pelosi's attacker}{https://apnews.com/article/1d4d2c95d096a46a1184eca2f12eebe8}{SAN FRANCISCO (AP) --- A judge on Thursday dismissed several state charges against Paul Pelosi's attacker, who was convicted in federal court last month, based on the argument that the counts fall under double jeopardy, according to the...}

\entryitemWithDescription{\hskip 0pt{}`Wheel of Fortune': Vanna White bids an emotional goodbye to Pat Sajak}{https://apnews.com/article/75ba26b39b3a9fdef27c8d02f6669681}{LOS ANGELES (AP) --- Ahead of Pat Sajak's final episode as the host of ``Wheel of Fortune,'' Vanna White paid an emotional tribute to her co-host of more than 40 years. On Thursday's episode of the beloved game show, White honored Sajak's...}

\entryitemWithDescription{\hskip 0pt{}Giraffe's nibble turns into airborne safari adventure for Texas toddler}{https://apnews.com/article/7b93018cf80dfc348b9ebbb615ca48a4}{GLEN ROSE, Texas (AP) --- A Texas family got a brief scare when a nibble from a giraffe turned a 2-year-old's safari visit into an airborne adventure. Paisley Toten was in the bed of a pickup truck on June 1 when her family drove through...}

\entryitemWithDescription{\hskip 0pt{}Records expunged for St. Louis couple who waved guns at protesters. They want their guns back}{https://apnews.com/article/e078710c51815fd00db9ba21b987b5ef}{ST. LOUIS (AP) --- A judge has expunged the misdemeanor convictions of a St. Louis couple who waved guns at racial injustice protesters outside their mansion in 2020. Now they want their guns back. Attorneys Mark and Patricia McCloskey...}