\entryitemWithDescription{\hskip 0pt{}A 9-year-old boy's dream of a pet octopus is a sensation as thousands follow Terrance's story online}{https://apnews.com/article/fa9d0c3d8bbadf59d7aa69ce7171dcf4}{The one thing 9-year-old Cal Clifford wanted more than anything since he was a toddler was a pet octopus. The boy's family in rural Edmond, Oklahoma, humored him with toy versions of an eight-legged mollusk, but as Cal got older it became...}

\entryitemWithDescription{\hskip 0pt{}John Sterling retires from Yankees broadcast booth at age 85 a few weeks into 34th season}{https://apnews.com/article/260ecd8446a63b916344633a6e886094}{NEW YORK (AP) --- John Sterling, the hyperexcitable New York Yankees broadcaster known for decades of indelible, personalized home run calls, announced his immediate retirement Monday at age 85. Sterling made the unexpected decision a few...}

\entryitemWithDescription{\hskip 0pt{}Paris Hilton backs California bill to bring more transparency to youth treatment facilities}{https://apnews.com/article/b3fa67c952c686f7dafe3dddf83c114f}{SACRAMENTO, Calif. (AP) --- Paris Hilton joined California state lawmakers Monday to push for legislation aimed at cracking down on the industry that cares for troubled teens by requiring more transparency from youth treatment facilities...}

\entryitemWithDescription{\hskip 0pt{}Endangered Bornean orangutan born at Busch Gardens in Florida}{https://apnews.com/article/3b45ca5e29b729e693f199737a5494f1}{TAMPA, Fla. (AP) --- An endangered Bornean orangutan baby has been welcomed into the world at Busch Gardens Tampa Bay in Florida. The baby orangutan was delivered by cesarean section on Saturday, weighing just over three pounds (1.3...}

\entryitemWithDescription{\hskip 0pt{}Beyoncé is bringing her fans of color to country music. Will they be welcomed in?}{https://apnews.com/article/4d18971de9d597ac1c7bb2f99f90daa9}{NEW YORK (AP) --- Dusty, worn boots. Horses lapping up water. Sweat dripping from the foreheads of every shade of Black skin as country classics blare through giant speakers. These moments are frequently recreated during Tayhlor Coleman's...}

\entryitemWithDescription{\hskip 0pt{}Tesla is planning to lay off 10\% of its workers after dismal 1Q sales, multiple news outlets report}{https://apnews.com/article/ee35abc216b5aeb222068500b916ef14}{DETROIT (AP) --- After reporting dismal first-quarter sales, Tesla is planning to lay off about a tenth of its workforce as it tries to cut costs, multiple media outlets reported Monday. CEO Elon Musk detailed the plans in a memo sent to...}

\entryitemWithDescription{\hskip 0pt{}Military marchers set out from Hopkinton to start the 128th Boston Marathon}{https://apnews.com/article/d3b4f8b25420a382f82a01887a1202f0}{HOPKINTON, Mass. (AP) --- A group Massachusetts National Guard members early Monday crossed the Boston Marathon start line painted in honor of the town that has hosted the marathon for the past century, launching the 128th edition of the...}

\entryitemWithDescription{\hskip 0pt{}Judge set to hear motion to dismiss rapper Travis Scott from lawsuit over deadly Astroworld concert}{https://apnews.com/article/a29c820f709b121e5968ba87cabf75e3}{A judge in Texas is set to hear arguments Monday in rap star Travis Scott's request to be dismissed from a lawsuit over the deadly 2021 Astroworld festival in Houston. Scott headlined the concert during which 10 people were killed as...}

\entryitemWithDescription{\hskip 0pt{}Seeing purple: Fans get a new track color and maybe record-breaking times at Paris Olympics}{https://apnews.com/article/aa0faed89e710c2281c352efb7777b8a}{PARIS (AP) --- Fans will be seeing purple at the Olympics when athletes try to set records at this summer's Paris Games. In a move away from a more traditional red-brick clay color, an Olympic track is going purple for the first time. The...}

\entryitemWithDescription{\hskip 0pt{}Gene Herrick, AP photographer who covered the Korean war and civil rights, dies at 97}{https://apnews.com/article/99c286e7b6802a626e23655605c7e2a0}{RICH CREEK, Va. (AP) --- Gene Herrick, a retired Associated Press photographer who covered the Korean War and is known for his iconic images of Martin Luther King Jr., Rosa Parks and the trial of the killers of Emmett Till in the early...}

\entryitemWithDescription{\hskip 0pt{}Iowa star Caitlin Clark makes surprise appearance on `Saturday Night Live'}{https://apnews.com/article/3fcb51d9c43ba45627e65628ff9e1bee}{NEW YORK (AP) --- Caitlin Clark made a surprise appearance on ``Saturday Night Live'' during the show's `` Weekend Update '' segment. The Iowa star is in New York for the WNBA draft on Monday night, when she is expected to be the top pick...}

\entryitemWithDescription{\hskip 0pt{}Scheffler carries the lead into the final round of the Masters as play resumes at Augusta National}{https://apnews.com/article/8f9bcddc2f3c8aa4298a83c016286918}{AUGUSTA, Ga. (AP) --- The final round of the Masters got underway at warm, sunny Augusta National on Sunday, where Scottie Scheffler began with a one-shot lead over Collin Morikawa and a two-shot advantage on Max Homa as he chases a...}

\entryitemWithDescription{\hskip 0pt{}The French connection: Paris flame to make first stop in Greece at heart of modern games' founder}{https://apnews.com/article/3d61ba905b606c87456c6cbeab355825}{ANCIENT OLYMPIA, Greece (AP) --- Just outside the site of the ancient Olympic Games, hooting owls break the nighttime silence at a white marble monument containing what's left of a singular Frenchman's heart. Baron Pierre de Coubertin was...}