\entryitemWithDescription{\hskip 0pt{}Texas bans gender-affirming care for minors after governor signs bill}{https://apnews.com/article/c3dd6c3147916e9ff4f2c91172afc1bc}{AUSTIN, Texas (AP) --- Texas has become the most populous state to ban gender-affirming care for minors after Gov. Greg Abbott signed legislation on Friday. Texas joined at least 18 other states that have enacted similar bans. Every major...}

\entryitemWithDescription{\hskip 0pt{}Rain brings much-needed relief to firefighters battling Nova Scotia wildfires}{https://apnews.com/article/fb4a05893fc375ecc1f0db9f37ce18dd}{Department of Natural Resources and Renewables firefighter Kalen MacMullin of Sydney, Nova Scotia, works on a fire in Shelburne County, N.S. on Thursday, June 1, 2023. Rain and a rainy forecast for the weekend have fire officials hopeful...}

\entryitemWithDescription{\hskip 0pt{}Cardinal performs rite to restore Vatican altar desecrated by man's naked protest}{https://apnews.com/article/98c8f3e617c922c2d4939fbf254283af}{CORRECTS CARDINAL NAME - Cardinal Mauro Gambetti, center, blesses the altar of the confession during a penitential rite inside St. Peter\textquotesingle s Basilica, Saturday, June 3, 2023. (AP Photo/Gregorio Borgia) VATICAN CITY (AP...}

\entryitemWithDescription{\hskip 0pt{}Pope warns of risk of corruption in missionary fundraising after AP investigation}{https://apnews.com/article/81ac4d23fb2f6a9a4447df4fc83fc8f9}{Pope Francis meets with pilgrims from Concesio and Sotto il Monte on the 60th anniversary of the death of Pope John XXIII and the election of Paul VI in St. Peter\textquotesingle s Basilica at the Vatican, Saturday, June 3, 2023. Pope...}

\entryitemWithDescription{\hskip 0pt{}Honeybee health blooms at federal facilities across the country}{https://apnews.com/article/0958b05bdb7b7d8ba573056be95f5111}{A bee arrives at a hive on the roof of the Warren Rudman U.S. Court House, Friday, May 5, 2023, in Concord, N.H. (AP Photo/Robert F. Bukaty) CONCORD, N.H. (AP) --- While judges, lawyers and support staff at the federal courthouse in...}

\entryitemWithDescription{\hskip 0pt{}US defense secretary says Washington won't stand for 'coercion and bullying' from China}{https://apnews.com/article/de10a9233bf226288faf86676486eef3}{U.S. Secretary of Defense Lloyd J. Austin III smiles as he speaks during the 20th International Institute for Strategic Studies (IISS) Shangri-La Dialogue, Asia\textquotesingle s annual defense and security forum in Singapore, Saturday...}

\entryitemWithDescription{\hskip 0pt{}Hawaii allows more concealed carry after US Supreme Court ruling, but bans guns in most places}{https://apnews.com/article/72e5ebe107fdea85319a4552dcb23b97}{Hawaii Gov. Josh Green signs gun control legislation in Honolulu on Friday, June 2, 2023 as Leia Kandell, left, age 10, and Cole Kandell, age 7, look on. Green signed legislation that allows more people to carry concealed firearms but at...}

\entryitemWithDescription{\hskip 0pt{}Money laundering trial ends for former Panamanian President Ricardo Martinelli}{https://apnews.com/article/65f54366111db70ab88e7ad3c98f95b0}{FILE - Panama\textquotesingle s former President Ricardo Martinelli talks to reporters near his home, in Panama City, Aug. 9, 2019. Martinelli\textquotesingle s trial and 14 others for alleged money laundering related to their purchase of...}

\entryitemWithDescription{\hskip 0pt{}Brazil's prosecutors block zipline construction at Rio's iconic Sugarloaf Mountain}{https://apnews.com/article/154534aa72031646ca7bf4000de80db9}{FILE - Sugarloaf mountain and the Guanabara Bay are seen in Rio de Janeiro, Brazil, July 8, 2016. Brazil's federal prosecutors blocked a decision on Thursday, June 1, 2023, to authorize the installment of ziplines at Rio de Janeiro's...}

\entryitemWithDescription{\hskip 0pt{}Connecticut lawmakers vote to allow people to use deadly force as the bear population grows}{https://apnews.com/article/9fb879bdde9e38339159f0e1b72c0e98}{FILE - A black bear that had been previously tranquilized and removed from a Waterbury, Conn., neighborhood earlier in the year chews on a garbage container in Wolcott, Conn., Sept. 26, 2006. Connecticut lawmakers voted Friday, June 2...}

\entryitemWithDescription{\hskip 0pt{}Retired Phoenix police officer in landmark Miranda rights case dies at 87}{https://apnews.com/article/eb0453f8239346987404af419732bbc2}{FILE - Retired Phoenix Police Capt. Carroll Cooley demonstrates Wednesday, March 13, 2013, at the Phoenix Police Museum in Phoenix, how Ernesto Miranda was fingerprinted on the same fingerprinting device used on Miranda. Cooley, the...}

\entryitemWithDescription{\hskip 0pt{}What to know about the case of the missing Missouri ER doctor found dead in Arkansas}{https://apnews.com/article/89133547c141e87edd712b5737a2c0f4}{This undated image provided by Jason Musgrave shows Dr. John Forsyth. Dr. John Forsyth, a missing emergency room doctor from Missouri was found dead in Arkansas from an apparent gunshot wound, authorities confirmed Wednesday, May 31, 2023...}

\entryitemWithDescription{\hskip 0pt{}Churchill Downs moves meet to Ellis Park to examine protocols following 12 horse deaths}{https://apnews.com/article/04ace82685afa4b2e1f242d5ab8be961}{FILE - Javier Castellano, atop Mage, third from left, is seen behind with others behind the pack as they make the first turn while competing in the 149th running of the Kentucky Derby horse race at Churchill Downs Saturday, May 6, 2023...}