\entryitemWithDescription{\hskip 0pt{}`Despicable Me 4' reigns at box office, while `Longlegs' gets impressive start}{https://apnews.com/article/0bc33ac564c35a2ef99153430bc187c0}{Gru and the minions celebrated a second week in first place at the North American box office this weekend, while a small horror movie called ``Longlegs'' upset the starry \$100 million ``Fly Me to the Moon.'' The supremacy of ``...}

\entryitemWithDescription{\hskip 0pt{}Jacoby Jones, a star of Baltimore's most recent Super Bowl title run, has died at age 40}{https://apnews.com/article/5755ac95bebaf9f52a853fbe9b2cf048}{BALTIMORE (AP) --- Former NFL receiver Jacoby Jones, whose 108-yard kickoff return in 2013 remains the longest touchdown in Super Bowl history, has died. He was 40. The Houston Texans, Jones' team for the first five seasons of his career...}

\entryitemWithDescription{\hskip 0pt{}Gnatalie is the only green-boned dinosaur found on the planet. She will be on display in LA}{https://apnews.com/article/7b9c0f6e9394345c3a391e68b02dd1a1}{LOS ANGELES (AP) --- The latest dinosaur being mounted at the Natural History Museum in Los Angeles is not only a member of a new species --- it's also the only one found on the planet whose bones are green, according to museum officials...}

\entryitemWithDescription{\hskip 0pt{}Shannen Doherty, `Beverly Hills, 90210' star, dies at 53}{https://apnews.com/article/65b9678241e44d0497e7d24baee49cb5}{LOS ANGELES (AP) --- Shannen Doherty, the ``Beverly Hills, 90210'' star whose life and career were roiled by illness and tabloid stories, has died at 53. After years with breast cancer, Doherty died Saturday, according to a statement from...}

\entryitemWithDescription{\hskip 0pt{}Kate, Princess of Wales, is at Wimbledon in a rare public appearance since revealing she has cancer}{https://apnews.com/article/db06da1f82fdc81a95992b08748b99bf}{LONDON (AP) --- The Princess of Wales arrived at the All England Club on Sunday for the Wimbledon men's final, only her second public appearance since announcing she was diagnosed with cancer. Kate, wife of heir to the throne Prince...}

\entryitemWithDescription{\hskip 0pt{}France's Bastille Day parade meets the Olympic torch relay in an exceptional year}{https://apnews.com/article/d33f90230ffa2a2c3c95873e3e167a36}{PARIS (AP) --- Paris is hosting an extra-special guest for France's national holiday Sunday --- the Olympic flame lighting up the city's grandiose military parade for Bastille Day. Just 12 days before the French capital hosts...}

\entryitemWithDescription{\hskip 0pt{}The first Titanic voyage in 14 years is happening in the wake of submersible tragedy. Hopes are high}{https://apnews.com/article/c0e4a3e3c48362e045a7e784b62b67e3}{PORTLAND, Maine (AP) --- The company that owns the salvage rights to the Titanic is undertaking its first expedition to the ship's wreckage in years, and those involved in the mission said they have both heavy hearts and lofty goals for a...}

\entryitemWithDescription{\hskip 0pt{}Richard Simmons, a fitness guru who mixed laughs and sweat, dies at 76}{https://apnews.com/article/db369da9e7f54f17bbbb1331af43508f}{NEW YORK (AP) --- Richard Simmons, television's hyperactive court jester of physical fitness who built a mini-empire in his trademark tank tops and short shorts by urging the overweight to exercise and eat better, died Saturday. He turned...}

\entryitemWithDescription{\hskip 0pt{}Alec Baldwin thanks supporters in first public comments after early end to trial}{https://apnews.com/article/2d3d036c8f998acb403fa2d4804d527f}{SANTA FE, N.M. (AP) --- Alec Baldwin made his first public comments to thank his supporters Saturday after the stunning early end to his involuntary manslaughter trial. ``There are too many people who have supported me to thank just...}

\entryitemWithDescription{\hskip 0pt{}Dr. Ruth Westheimer, America's diminutive and pioneering sex therapist, dies at 96}{https://apnews.com/article/6d4af57b5f034bf9a90977de41b88735}{NEW YORK (AP) --- Dr. Ruth Westheimer, the diminutive sex therapist who became a pop icon, media star and best-selling author through her frank talk about once-taboo bedroom topics, has died. She was 96. Westheimer died on Friday at her...}

\entryitemWithDescription{\hskip 0pt{}Griff has opened for some of pop's biggest stars. Now she has a debut album of her own to tour}{https://apnews.com/article/8bd628aaa5fedeba05798afa8eb25937}{British singer-songwriter Griff's career has been an undeniable whirlwind. Less than two years after releasing her first single --- and finishing her A-level exams --- she won the Brit Award for Rising Star. Then she opened for Dua Lipa...}

\entryitemWithDescription{\hskip 0pt{}Booming Turkish TV drama industry captures hearts and minds worldwide and boosts tourism}{https://apnews.com/article/d9b908cad575755e1118312cbb0187ad}{ISTANBUL (AP) --- Under the sweltering Turkish sun, tourists wander through sets that recreate Ottoman and Byzantine-era castles, take selfies with actors in traditional Ottoman costumes and watch horseback stunt performances. Among them...}

\entryitemWithDescription{\hskip 0pt{}On NYC beaches, angry birds are fighting drones on patrol for sharks and swimmers}{https://apnews.com/article/c2cbfb6ca03f771082ff57a28701f915}{NEW YORK (AP) --- A fleet of drones patrolling New York City's beaches for signs of sharks and struggling swimmers is drawing backlash from an aggressive group of seaside residents: local shorebirds. Since the drones began flying in May...}