\entryitemWithDescription{\hskip 0pt{}Byron Janis, renowned American classical pianist who overcame debilitating arthritis, dies at 95}{https://apnews.com/article/54ff513441a51ca970dbb80118873d29}{NEW YORK (AP) --- Byron Janis, a renowned American concert pianist and composer who broke barriers as a Cold War era culture ambassador and later overcame severe arthritis that nearly robbed him of his playing abilities, has died. He was...}

\entryitemWithDescription{\hskip 0pt{}`Kung Fu Panda 4' repeats at No. 1 on the box office charts}{https://apnews.com/article/9c08d6a5aa6d0455cfe88e73f15cc9e0}{`` Kung Fu Panda 4 '' stayed at the top of the North American box office in its second weekend in theaters. The Universal and DreamWorks Animation movie earned \$30 million in ticket sales, according to studio estimates Sunday. The...}

\entryitemWithDescription{\hskip 0pt{}Cockney Rebel singer Steve Harley, who had a hit with `Make Me Smile,' dies at 73}{https://apnews.com/article/84f0568f9cfc4de99303117ae58ce942}{LONDON (AP) --- Steve Harley, a British musician whose glam-rock band Cockney Rebel had an enduring hit with the song ``Make Me Smile (Come Up and See Me),'' has died. He was 73. Harley's family said Sunday that he had ``passed away...}

\entryitemWithDescription{\hskip 0pt{}Iceland's latest volcanic eruption is decreasing in power, and defenses are holding}{https://apnews.com/article/09c7ad21aecc02747f8b97ed88f3b740}{GRINDAVIK, Iceland (AP) --- Lava from a volcanic eruption in Iceland flowed Sunday toward defenses around the town of Grindavik, which have so far held the molten rock back from the evacuated community. Scientists said the eruption...}

\entryitemWithDescription{\hskip 0pt{}March Madness is here. Bracket reveal the 1st step in what should be an NCAA Tournament free-for-all}{https://apnews.com/article/e2b9dd2bb2f776a163de389c8e737ab4}{The story of March Madness figures to look a lot like the story of the regular season that led up to it: a healthy cross-section of very good teams, few dominant ones and no strong consensus on who's the best bet to be cutting down nets...}

\entryitemWithDescription{\hskip 0pt{}Usher, Fantasia Barrino, `Color Purple' honored at 55th NAACP Image Awards}{https://apnews.com/article/388036f8663d6485baf4c60f8d85d609}{LOS ANGELES (AP) --- Usher was named entertainer of the year at the 55th annual NAACP Awards on Saturday night, which highlighted works by entertainers and writers of color. After Usher accepted his award at the Shrine Auditorium in Los...}

\entryitemWithDescription{\hskip 0pt{}A volcano in Iceland is erupting for the fourth time in 3 months, sending plumes of lava skywards}{https://apnews.com/article/644e18664ef7fa6de0cfae7853c24223}{GRINDAVIK, Iceland (AP) --- A volcano in Iceland erupted Saturday evening for the fourth time in three months, sending orange jets of lava into the night sky. Iceland's Meteorological Office said the eruption opened a fissure in the earth...}

\entryitemWithDescription{\hskip 0pt{}Mega Millions jackpot soars to \$875 million. Powerball reaches \$600 million}{https://apnews.com/article/a1c037c3dc7bc7a068cdc92e0aacd7db}{FORT LAUDERDALE, Fla. (AP) --- If you're feeling some St. Patrick's Day magic, you might want to buy a lottery ticket. Mega Millions and Powerball have racked up some massive jackpots after weeks of rolloevers. The Mega Ball jackpot is...}

\entryitemWithDescription{\hskip 0pt{}David Breashears, mountaineer and filmmaker who co-produced Mount Everest documentary, dies at 68}{https://apnews.com/article/f0fce6335b03c214af034af278cdcfa3}{MARBLEHEAD, Mass. (AP) --- David Breashears, a mountaineer, author and filmmaker who co-directed and co-produced a 1998 IMAX documentary about climbing Mount Everest, has died, his business manager confirmed Saturday. He was 68...}

\entryitemWithDescription{\hskip 0pt{}Fasting at school? More Muslim students in the US are getting support during Ramadan}{https://apnews.com/article/8504b32049791fbc85eec9a8f68c700f}{DEARBORN, Mich. (AP) --- While Muslim students remain a rarity in many U.S. school districts, they are a major presence in some communities, prompting public schools to be more attentive to their needs during the holy month of Ramadan...}

\entryitemWithDescription{\hskip 0pt{}A warming island's mice are breeding out of control and eating seabirds. An extermination is planned}{https://apnews.com/article/ec4f281f396ca49910c359df5b99b64d}{CAPE TOWN, South Africa (AP) --- Mice accidentally introduced to a remote island near Antarctica 200 years ago are breeding out of control because of climate change, and they are eating seabirds and causing major harm in a special nature...}

\entryitemWithDescription{\hskip 0pt{}When it's St. Patrick's Day in New Orleans, get ready to catch a cabbage}{https://apnews.com/article/adc19a1b6274fea2fc31f1c898480fb1}{NEW ORLEANS (AP) --- The grandly colonnaded old city hall was designed by an Irish architect. A neighborhood near the wharves is still known as the Irish Channel. Landmark towers and spires of Catholic churches built for Irish immigrants...}

\entryitemWithDescription{\hskip 0pt{}America is getting green and giddy for its largest St. Patrick's Day parades}{https://apnews.com/article/9f984e62ddb4447b249d47f9051df9be}{NEW YORK (AP) --- St. Patrick's Day parades across the U.S. are planned for Saturday, promising to turn one river green in the Midwest, commemorate the bicentennial of a parade in the South and put forth the first female leader of a major...}