\entryitemWithDescription{\hskip 0pt{}Ed Sheeran testifies in "Let's Get It On" copyright suit}{https://apnews.com/article/a6079b6d3ebb3b23159efa9c76ffe548}{Ed Sheeran walks into Manhattan federal court, Tuesday, April 25, 2023, in New York. The heirs of Ed Townsend, Marvin Gaye\textquotesingle s co-writer of the 1973 soul classic, sued Sheeran, alleging the English pop star\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Colorado becomes 1st to pass `right to repair' for farmers}{https://apnews.com/article/1da00ea957fd1057bf522cb4725e62d4}{Colorado Gov. Jared Polis, front, waits to sign legislation that forces manufacturers to provide the necessary manuals, tools, parts and even software to farmers so they can fix their own machines, Tuesday, April 25, 2023, during a...}

\entryitemWithDescription{\hskip 0pt{}`Joint' venture: Ben from Ben \& Jerry's starts pot nonprofit}{https://apnews.com/article/f7127929a0039a7889d4397af85e4304}{FILE - Ben Cohen, of Ben and Jerry\textquotesingle s Ice Cream, during a rally at the Statehouse in Concord, N.H., Jan. 21, 2015. Cohen has launched a nonprofit cannabis line with the mission of righting what it calls the wrongs of the...}

\entryitemWithDescription{\hskip 0pt{}Harry Belafonte, activist and entertainer, dies at 96}{https://apnews.com/article/2d8cbdf0043e4383a6c4a85c862cdbe1}{FILE - Actor, singer and activist Harry Belafonte from the documentary film "Sing Your Song," poses for a portrait during the Sundance Film Festival in Park City, Utah on Jan. 21, 2011. Belafonte died Tuesday of congestive heart failure...}

\entryitemWithDescription{\hskip 0pt{}Indigenous competitors celebrate culture and sport in Brazil}{https://apnews.com/article/65fea52cacc3b9c1040ce8d3b91b448e}{An athlete competes in the archery event during the Indigenous Games, in the Tapirema community of Peruibe, Brazil, Saturday, April 22, 2023. Hundreds of Indigenous athletes gather this weekend in the south of Sao Paulo state to hold...}

\entryitemWithDescription{\hskip 0pt{}A play about the making of 'Jaws' swims toward Broadway}{https://apnews.com/article/c7d3f241a16ba2bf1916dd26c8fb34c1}{This image released by Polk \& Co. shows promotional art for "The Shark is Broken," a stage play about the making of the blockbuster movie ``Jaws.'' (Polk \& Co. via AP) NEW YORK (AP) --- A stage play about the making of the blockbuster...}

\entryitemWithDescription{\hskip 0pt{}GM, Samsung plan new EV battery cell factory in US}{https://apnews.com/article/c9a0c619100fe102ffe3c074ae33f746}{FILE - People walk by Samsung SDI Co.\textquotesingle{} booth during the InterBattery 2021, the country\textquotesingle s leading battery exhibition, at COEX in Seoul, South Korea, on June 9, 2021. General Motors and South Korea's Samsung...}

\entryitemWithDescription{\hskip 0pt{}Sudan fighting eclipses new truce as aid groups raise alarm}{https://apnews.com/article/ee77f12ba7bd18a0c1ed1b3bcf241a5b}{A man walks by a house hit in recent fighting in Khartoum, Sudan, Tuesday, April 25, 2023. Sudan\textquotesingle s warring generals have pledged to observe a new three-day truce that was brokered by the United States and Saudi Arabia to...}

\entryitemWithDescription{\hskip 0pt{}As Israel turns 75, its flag unfurls into deep divisions}{https://apnews.com/article/354a807daa5c901823a99419ce1eb638}{Israeli demonstrators are seen through Israel\textquotesingle s national flag during a protest against plans by Prime Minister Benjamin Netanyahu\textquotesingle s government to overhaul the judicial system, in Cesarea, Israel, Friday...}

\entryitemWithDescription{\hskip 0pt{}Ex-UN head Ban Ki-moon urges army to end Myanmar violence}{https://apnews.com/article/ccd5bac23cbcf229cff0bc25574aba2f}{In this photo provided by the Myanmar Military True News Information Team, Senior Gen. Min Aung Hlaing, right, head of the military council, talks with Ban Ki Moon, left, former U.N Secretary-General, during their meeting Monday, April...}

\entryitemWithDescription{\hskip 0pt{}Black history class to undergo changes, College Board says}{https://apnews.com/article/91cf4fecb2fad2697495f7fa71a3c4e5}{FILE - Hundreds participate in the National Action Network demonstration in response to Gov. Ron DeSantis\textquotesingle{} rejection of a high school African American history course, Wednesday, Feb. 15, 2023, in Tallahassee, Fla. In a...}

\entryitemWithDescription{\hskip 0pt{}Clippers' Leonard expected to miss Game 5 vs. Suns}{https://apnews.com/article/9d4bac2fd73fac95701be729aad5a368}{Los Angeles Clippers forward Kawhi Leonard, right, watches from the bench during the first half in Game 4 of a first-round NBA basketball playoff series against the Phoenix Suns Saturday, April 22, 2023, in Los Angeles. (AP Photo/Mark J...}

\entryitemWithDescription{\hskip 0pt{}Ginnie Newhart, wife of comedy legend Bob Newhart, dies}{https://apnews.com/article/a82deaf693cd02ba52dbdb7225fbb10f}{FILE - Actor-comedian Bob Newhart, right and his wife Ginnie attend the Golden Globe Awards on Jan. 26, 1985, in Beverly Hills, Calif. Ginnie Newhart, who was married to comedy legend Bob Newhart for six decades and inspired the classic...}