\entryitemWithDescription{\hskip 0pt{}CNN's Dana Bash replaces King on 'Inside Politics' show}{https://apnews.com/article/e3f007733c642c8dddd295c286e20e83}{FILE - CNN correspondent Dana Bash poses at the premiere of the HBO television series "Winning Time: The Rise of the Lakers Dynasty," on March 2, 2022, in Los Angeles. Bash will replace John King as host of the network\textquotesingle s ``...}

\entryitemWithDescription{\hskip 0pt{}Police say man continued date after fatal shooting over \$40}{https://apnews.com/article/1ab4cc7b4a8488c485f4b66ed683fe83}{This undated mugshot provided by the Houston Police Department shows Erick Aguirre, who was charged with murder in the April 11, 2023, death of 46-year-old Elliot Nix. Authorities allege the Texas man paused his dinner date to fatally...}

\entryitemWithDescription{\hskip 0pt{}Zoonomia: Genetic research reveals all we share with animals}{https://apnews.com/article/f80d1570acf5a97a8ed9e2a1104e74e9}{FILE - Gunnar Kaasen and with his dog Balto, the heroic dogsled team leader, sit for a portrait in the early 1920s. As a part of the Zoonomia Project, with 11 papers published Thursday, April 27, 2023, in the journal Science, by comparing...}

\entryitemWithDescription{\hskip 0pt{}Prosecutors: Man charged with killing wife suspected affair}{https://apnews.com/article/7e343b1c71a723c34c198a241c148db9}{Murder suspect Brian Walshe of Cohasset is arraigned, Thursday April 27, 2023, in Dedham Superior Court in Dedham, Mass. for the death of his wife Anna who disappeared on New Years Day 2023. (Greg Derr/The Patriot Ledger via AP, Pool) The...}

\entryitemWithDescription{\hskip 0pt{}Fed's Powell was tricked by fake call from Russia pranksters}{https://apnews.com/article/a9468d8d23d64e0f91e87cf40f3d312f}{Federal Reserve Chairman Jerome Powell arrives for the plenary of the International Monetary and Financial Committee (IMFC) meeting, during the World Bank/IMF Spring Meetings at the International Monetary Fund (IMF) headquarters in...}

\entryitemWithDescription{\hskip 0pt{}Nate Diaz surrenders after brawl; lawyer says self-defense}{https://apnews.com/article/d0dcfa42fd0518ace09e3f2709ad7140}{FILE -FILE - Welterweight fighter Nate Diaz poses on the scale during a ceremonial weigh-in for the UFC 279 mixed martial arts event on Sept. 9, 2022, in Las Vegas. Mixed martial arts fighter Nate Diaz turned himself in to police in New...}

\entryitemWithDescription{\hskip 0pt{}White woman whose claim caused Emmett Till murder has died}{https://apnews.com/article/1bcfff1c5a29484270d66b224422f112}{FILE - This 1955 file photo shows Carolyn Bryant. Carolyn Bryant Donham, the white woman who accused Black teenager Emmett Till of making improper advances before he was lynched in Mississippi in 1955 has died Tuesday night, April 25, in...}

\entryitemWithDescription{\hskip 0pt{}'Jackass' star Bam Margera in court, denies hitting brother}{https://apnews.com/article/a496fb592ddaab007d162ce8bb284b21}{FILE - This Jan. 14, 2013 file photo shows Bam Margera at the LA premiere of "The Last Stand" at Grauman\textquotesingle s Chinese Theatre in Los Angeles. Margera punched his brother in the face during an altercation at their home in the...}

\entryitemWithDescription{\hskip 0pt{}Foundation prints 3D prosthetics, gives them free in Uruguay}{https://apnews.com/article/411bd8fbec6b2b95c4cd306d9f0646af}{Mia Rodriguez clowns around, wearing her prosthetic hands, next to her little brother Washington before school in Salinas, Uruguay, Friday, April 14, 2023. Mia, whose fingers did not fully develop, got her prosthetic hands from the Manos...}

\entryitemWithDescription{\hskip 0pt{}Pirates star Dick Groat, who also played in NBA, dies at 92}{https://apnews.com/article/f2d885576dc927e3a05a0cf7d994e435}{FILE - Former Pittsburgh Pirates shortstop Dick Groat is shown during pregame ceremonies honoring his lifetime of service to the Pirates organization, before a baseball game against the St. Louis Cardinals in Pittsburgh, Monday, April 1...}

\entryitemWithDescription{\hskip 0pt{}Dolly Parton to rock out at Academy of Country Music Awards}{https://apnews.com/article/703f8e06bc1218524ee3c2995711be5c}{FILE - Dolly Parton poses at the Carnegie Medal of Philanthropy Ceremony in New York on Oct. 13, 2022. Parton will close out the awards show with her performance of ``World On Fire,'' from her record ``Rock Star.'' The ACMs will air on...}

\entryitemWithDescription{\hskip 0pt{}China welcomes Ya Ya the panda home after 20 years abroad}{https://apnews.com/article/e65e1d583cf8781c436ec1c6daadd107}{In this photo released by Xinhua News Agency, workers wearing protective suits check on giant panda Ya Ya, sitting inside a container after arriving at Shanghai Pudong International Airport in Shanghai, Thursday, April 27, 2023. Ya Ya the...}

\entryitemWithDescription{\hskip 0pt{}Spain swelters in temperatures more typical of summer}{https://apnews.com/article/f963305ca8cf0b1aeef93114b0e2957c}{Horses used to pull tourist carriages, drink water at the annual traditional April Fair in Seville, Spain, Thursday, April 27, 2023. Spain\textquotesingle s national weather service said temperatures would "reach values typical of summer"...}