\entryitemWithDescription{\hskip 0pt{}Oh, brother! WWE star, Eagles coach ready for big weekend}{https://apnews.com/article/32d947b65e30df6914d6562791c4401f}{FILE - Philadelphia Eagles linebackers coach Nick Rallis gestures during a preseason NFL football game against the Pittsburgh Steelers, Thursday, Aug. 12, 2021, in Philadelphia. It\textquotesingle s a big weekend for Nick Rallis and big...}

\entryitemWithDescription{\hskip 0pt{}Man who claimed he had bomb near Capitol pleads guilty}{https://apnews.com/article/86e4b4f4e16779a8b7b90db6ce81e9c0}{FILE - A man is apprehended after being in a pickup truck parked on the sidewalk in front of the Library of Congress\textquotesingle{} Thomas Jefferson Building, as seen from a window of the U.S. Capitol, Aug. 19, 2021, in Washington. A...}

\entryitemWithDescription{\hskip 0pt{}DEA's Mexico chief quietly removed over ties to drug lawyers}{https://apnews.com/article/c572727a7e7c740dde5e4da280de40b6}{This portion of a photo posted on Twitter by the DEA\textquotesingle s New York division on Aug 30, 2019 shows Nicholas Palmeri. The U.S. Drug Enforcement Administration quietly removed Palmeri, its top official in Mexico, in 2022 over...}

\entryitemWithDescription{\hskip 0pt{}`A Thousand and One' wins Sundance grand jury prize}{https://apnews.com/article/1110ae998f625f97cdab9ac9aee19b6c}{A poster advertises the 2023 Sundance Film Festival in front of the Egyptian Theatre, Wednesday, Jan. 18, 2023, in Park City, Utah. The annual independent film festival runs from Jan. 19-29. (AP Photo/Chris Pizzello) Associated Press...}

\entryitemWithDescription{\hskip 0pt{}Lots of sound and fury on US debt, but not a crisis — yet}{https://apnews.com/article/deab5331ae441718bc35a7c7aef6ea18}{FILE - The Treasury Department is seen near sunset in Washington, Jan. 18, 2023. The national debt is at the core of a dispute about how to raise the government\textquotesingle s legal borrowing authority, which could come to a head this...}

\entryitemWithDescription{\hskip 0pt{}Video shows struggle for hammer during Pelosi attack}{https://apnews.com/article/c35ecf3131109f69f0cb66b84e986ba2}{This image from video from police body-worn camera footage, released by the San Francisco Police Department, shows Paul Pelosi, right, fighting for control of a hammer with his assailant, David DePape, during a attack at Pelosi...}

\entryitemWithDescription{\hskip 0pt{}Brutality of Russia's Wagner gives it lead in Ukraine war}{https://apnews.com/article/803da2e3ceda5dace7622cac611087fc}{FILE - Visitors wearing military camouflage stand at the entrance of the \textquotesingle PMC Wagner Centre\textquotesingle, which is associated with businessman and founder of the Wagner private military group Yevgeny Prigozhin, during...}

\entryitemWithDescription{\hskip 0pt{}4 of NFL's best TEs on display in conference title games}{https://apnews.com/article/9a1918ebac6e250bb9b005afc4048934}{Kansas City Chiefs tight end Travis Kelce (87) leaps over Denver Broncos cornerback Damarri Mathis after catching a pass during the first half of an NFL football game Sunday, Jan. 1, 2023, in Kansas City, Mo. (AP Photo/Ed Zurga) KANSAS...}

\entryitemWithDescription{\hskip 0pt{}Filipino workers: Oil company abandoned us in Hurricane Ida}{https://apnews.com/article/29373e77e75ea6708a20a608bd6d1f0e}{FILE - In this aerial photo taken with a drone, flood waters surround storm damaged homes on Aug. 31, 2021, in Lafourche Parish, La., as residents try to recover from the effects of Hurricane Ida. Ten Filipino men who worked for a major...}

\entryitemWithDescription{\hskip 0pt{}Green comet zooming our way, last visited 50,000 years ago}{https://apnews.com/article/af15da666c16b784e79f2fead8bc01ac}{This photo provided by Dan Bartlett shows comet C/2022 E3 (ZTF) on Dec. 19, 2022. It last visited during Neanderthal times, according to NASA. It is expected to come within 26 million miles (42 million kilometers) of Earth on Feb. 1...}

\entryitemWithDescription{\hskip 0pt{}FDA moves to ease rules for blood donations from gay men}{https://apnews.com/article/9c11389da42c14ac2e80366f271aa1b7}{FILE - Tubes direct blood from a donor into a bag in Davenport, Iowa, on Friday, Nov. 11, 2022. The U.S. is moving to ease restrictions on blood donations from gay and bisexual men and other groups that traditionally face higher risks of...}

\entryitemWithDescription{\hskip 0pt{}Biden picks Zients as his next White House chief of staff}{https://apnews.com/article/7a5b7ee6af9942ed9ca01d012c046821}{FILE - White House COVID-19 Response Coordinator Jeff Zients speaks during a press briefing at the White House, April 13, 2021, in Washington. (AP Photo/Patrick Semansky, File) WASHINGTON (AP) --- President Joe Biden announced Jeff Zients...}

\entryitemWithDescription{\hskip 0pt{}Memphis anticipates release of video in Tyre Nichols' arrest}{https://apnews.com/article/e3ee8e6698faae16df3f41d09234b09f}{Civil rights Attorney Ben Crump speaks to RowVaughn Wells, mother of Tyre Nichols, who died after being beaten by Memphis police officers, at a news conference with in Memphis, Tenn., Friday, Jan. 27, 2023. (AP Photo/Gerald Herbert) Five...}