\entryitemWithDescription{\hskip 0pt{}Texans WR Tank Dell shot in Florida, sustains minor wound, team says}{https://apnews.com/article/684a6c204054024ef2b312ff15133b50}{Houston Texans wide receiver Tank Dell was shot in Florida and sustained a minor wound, the team announced on social media. Dell was shot Saturday night in Sanford and has since been released from a hospital ``in good spirits,'' the team...}

\entryitemWithDescription{\hskip 0pt{}Zendaya's tennis movie `Challengers' scores at the weekend box office}{https://apnews.com/article/a05571e3e3537630301cebe2f081013a}{The sexy tennis drama `` Challengers '' won the box office this weekend with \$15 million in ticket sales, according to studio estimates Sunday. Zendaya and castmates Mike Faist and Josh O'Connor have been on a globetrotting press tour to...}

\entryitemWithDescription{\hskip 0pt{}Once dominant at CBS News before a bitter departure, Dan Rather makes his first return in 18 years}{https://apnews.com/article/3e95b5b111f4fff7ac3c39c138bce26e}{NEW YORK (AP) --- Dan Rather returned to the CBS News airwaves for the first time since his bitter exit 18 years ago, appearing in a reflective interview on ``CBS Sunday Morning'' days before the debut of a Netflix documentary on the 92...}

\entryitemWithDescription{\hskip 0pt{}Nicole Kidman, who `makes movies better,' gets AFI Life Achievement Award}{https://apnews.com/article/31c5ea6dd66ba4d14b17deda3559b031}{LOS ANGELES (AP) --- Morgan Freeman spoke the words, but pretty much everyone who took the stage at the presentation of the AFI Life Achievement Award agreed: `` Nicole Kidman. She makes movies better.'' The line came in a video parody of...}

\entryitemWithDescription{\hskip 0pt{}A Hindu festival in southwestern Pakistan brings a mountainous region to life}{https://apnews.com/article/bbebc541b403875a15c675bab353821c}{HINGLAJ, Pakistan (AP) --- The ascent of steep mud volcanoes marks the start of Hindu pilgrims' religious rituals in southwestern Pakistan. They climb hundreds of stairs or clamber over rocks to reach the summit, tossing coconuts and rose...}

\entryitemWithDescription{\hskip 0pt{}California Disney characters are unionizing decades after Florida peers. Hollywood plays a role}{https://apnews.com/article/53d3fd8ddfcf104bd70fbfd5f9d64750}{ORLANDO, Fla. (AP) --- During three years of working as a parade performer at the Disneyland Resort in Southern California, Zach Elefante always has had a second or third job to help him earn a living. Unlike the experiences of his peers...}

\entryitemWithDescription{\hskip 0pt{}LeBron scores 30, and the Lakers avoid 1st-round elimination with a 119-108 win over champion Denver}{https://apnews.com/article/0f5deb96aa3bef29b6b6fa996f9bff5b}{LOS ANGELES (AP) --- The Los Angeles Lakers finally cracked the Denver Nuggets' mastery of this rivalry and extended their playoff lives for at least another game. To absolutely nobody's surprise, LeBron James led the way. James scored 30...}

\entryitemWithDescription{\hskip 0pt{}Alaska's Indigenous teens emulate ancestors' Arctic survival skills at the Native Youth Olympics}{https://apnews.com/article/2220b3402c8d782400eb16748e81c508}{ANCHORAGE, Alaska (AP) --- The athletes filling a huge gym in Anchorage, Alaska were ready to compete, cheering and stomping and high-fiving each other as they lined up for the chance to claim the state's top prize in their events. But...}

\entryitemWithDescription{\hskip 0pt{}NFL draft attendance record set with more than 700,00 fans attending the event in Detroit}{https://apnews.com/article/b475546a37aad54c48c4199cc275971f}{DETROIT (AP) --- The NFL draft has a new attendance record after more than 700,000 fans flooded downtown Detroit for the three-day event. Michigan Gov. Gretchen Whitmer broke the news at Campus Martius Park on Saturday during the third...}

\entryitemWithDescription{\hskip 0pt{}News anchor Poppy Harlow is leaving CNN after more than 15 years}{https://apnews.com/article/7f8e1936b8e4331b4c2f956cc6140a2a}{ATLANTA (AP) --- Anchor Poppy Harlow is leaving CNN, according to the network. Harlow, who joined CNN in 2008 and most recently co-hosted ``CNN This Morning,'' announced her parting from the cable news giant in an email to colleagues. She...}

\entryitemWithDescription{\hskip 0pt{}Sean `Diddy' Combs files motion to dismiss some claims in a sexual assault lawsuit}{https://apnews.com/article/3ae5e900993343be862b89270762a12f}{LOS ANGELES (AP) --- Lawyers for Sean ``Diddy'' Combs pushed back against a woman's lawsuit that accused him of sexual assault, filing a motion on Friday to dismiss some claims that were not under law when the alleged incident occurred...}

\entryitemWithDescription{\hskip 0pt{}Long lines form and frustration grows as Cuba runs short of cash}{https://apnews.com/article/1bb0c49c286495c66a94e32feffc042d}{HAVANA (AP) --- Alejandro Fonseca stood in line for several hours outside a bank in Havana hoping to withdraw Cuban pesos from an ATM, but when it was almost his turn, the cash ran out. He angrily hopped on his electric tricycle and...}

\entryitemWithDescription{\hskip 0pt{}Britain's King Charles III will resume public duties next week after cancer treatment, palace says}{https://apnews.com/article/5c3a58df63a6670c17295bff05819a0e}{LONDON (AP) --- King Charles III will resume his public duties next week following treatment for cancer, Buckingham Palace announced Friday. Charles took a break from public appearances almost three months ago to focus on his treatment...}