\entryitemWithDescription{\hskip 0pt{}Oklahoma trooper violently thrown to the ground as vehicle on interstate hits one he'd pulled over}{https://apnews.com/article/887f73f6bcf3eefb775ebdebdfa0dda3}{YUKON, Okla. (AP) --- An Oklahoma trooper who was violently thrown to the ground when a vehicle he'd pulled over for a traffic stop on an interstate highway was struck by another vehicle says he feels lucky that he was able to walk away...}

\entryitemWithDescription{\hskip 0pt{}A Rolex seller meets up with a Facebook Marketplace thief. It goes all wrong from there}{https://apnews.com/article/409863f7c727164d9cedc6c892623750}{Massapequa Park, N.Y. (AP) --- An \$8,000 Facebook Marketplace deal has gone bad on Long Island, with a man who was selling a Rolex watch jumping onto the hood of the thief's car in a quixotic attempt to keep from being robbed. ``I was...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift gets an early reason to celebrate at AFC title game as Travis Kelce makes a TD catch}{https://apnews.com/article/772f0bed35e4e85e3cf4848781a61764}{BALTIMORE (AP) --- Taylor Swift is on hand for boyfriend Travis Kelce's latest NFL playoff game. It did not take long for him to give her a reason to celebrate. Swift and others in a suite in the corner of the stadium could be seen...}

\entryitemWithDescription{\hskip 0pt{}See the moment climate activists throw soup at the `Mona Lisa' in Paris}{https://apnews.com/article/d57ac62eb1e11bd1e2409615c4e52ac0}{PARIS (AP) --- Two climate activists hurled soup Sunday at the glass protecting the ``Mona Lisa'' at the Louvre Museum in Paris and shouted slogans advocating for a sustainable food system. In a video posted on social media, two women...}

\entryitemWithDescription{\hskip 0pt{}EU Commission changes social media post about Auschwitz after protests from Poland}{https://apnews.com/article/c8aeefb1b8dded8109a57ceb6072d527}{WARSAW, Poland (AP) --- Poland on Sunday asked the European Commission to fix a social media post about the Holocaust, saying it wrongly linked the Auschwitz death camp to Poland, rather than Nazi Germany. In a video posted Saturday on...}

\entryitemWithDescription{\hskip 0pt{}James outduels Curry with a triple-double as Lakers take double-OT thriller vs. Warriors 145-144}{https://apnews.com/article/d1e76dfc2d5893ed83214b77209ec1b7}{SAN FRANCISCO (AP) --- LeBron James made a pair of free throws with 1.2 seconds left in the second overtime to cap his triple-double of 36 points, 20 rebounds and 12 assists, outdueling Stephen Curry as the Los Angeles Lakers held off the...}

\entryitemWithDescription{\hskip 0pt{}Spurs mascot The Coyote captures bat with net -- to the delight of Wembanyama}{https://apnews.com/article/245eb5921082659f186cd310702e1bb3}{SAN ANTONIO (AP) --- A bat descended on the court and delayed play after Victor Wembanyama made a 3-pointer two minutes into the San Antonio Spurs' 113-112 victory over the Minnesota Timberwolves on Saturday night. The Spurs' mascot, The...}

\entryitemWithDescription{\hskip 0pt{}Oregon weekly newspaper to relaunch print edition after theft forced it to lay off its entire staff}{https://apnews.com/article/c6d2b677a370afffa26dfc2b5cac5549}{PORTLAND, Ore. (AP) --- An Oregon weekly newspaper that had to lay off its entire staff after its funds were embezzled by a former employee will relaunch its print edition next month, its editor said, a move made possible in large part by...}

\entryitemWithDescription{\hskip 0pt{}A snowboarder spent 15 hours trapped in a ski gondola. She rubbed her hands and feet to keep warm}{https://apnews.com/article/0cdeaac5df9ce655f8b253c804fcd2a8}{SOUTH LAKE TAHOE, Calif. (AP) --- A snowboarder spent 15 hours trapped overnight inside a ski lift gondola amid freezing temperatures at a Lake Tahoe resort, according to officials and media reports. Monica Laso boarded the gondola around...}

\entryitemWithDescription{\hskip 0pt{}`Saltburn' actor Barry Keoghan named Hasty Pudding's Man of the Year}{https://apnews.com/article/b1334bb493311e77f4ea275b7198bff1}{CAMBRIDGE, Mass. (AP) --- Harvard University's Hasty Pudding Theatricals has named Barry Keoghan, best known for his roles in ``Dunkirk,'' ``The Killing of a Sacred Deer,'' ``Eternals,'' and ``The Banshees of Inisherin,'' as the recipient...}

\entryitemWithDescription{\hskip 0pt{}Zebras, camels and flames, oh my! Circus animals rescued after truck catches fire on Indiana highway}{https://apnews.com/article/6e05d02f6382ffc0c2858487b66b4848}{MARION, Ind. (AP) --- A truck hauling zebras and camels for a series of weekend circus performances caught fire early Saturday on a northeastern Indiana highway, prompting a police rescue of the animals, which roamed along the freeway...}

\entryitemWithDescription{\hskip 0pt{}Charges against country singer Chris Young in Nashville bar arrest have been dropped}{https://apnews.com/article/ead6a027aafa8c985cccbec3a34ba750}{NASHVILLE, Tenn. (AP) --- A district attorney in Tennessee has dropped charges against country singer Chris Young stemming from an encounter with Alcoholic Beverage Commission agents who were doing compliance checks. In a statement...}

\entryitemWithDescription{\hskip 0pt{}13 people injured when more than 40 vehicles crash on Chesapeake Bay bridge in Maryland}{https://apnews.com/article/17df78c1204638e7f403b82eccb87f91}{BALTIMORE (AP) --- Crashes involving more than 40 vehicles closed all lanes on the heavily-traveled U.S. 50 Bay Bridge in Maryland on Saturday, injuring 13 people and snarling traffic for about six hours, authorities said. The Maryland...}