\entryitemWithDescription{\hskip 0pt{}Kevin Bacon dances back to `Footloose' high school}{https://apnews.com/article/c15cd35171ed6719f0f09624c95029ee}{PAYSON, Utah (AP) --- Actor Kevin Bacon on Saturday returned to the Utah high school where the cult classic movie ``Footloose'' was filmed more than 40 years. Bacon danced his way to a stage on a Payson High School athletic field Saturday...}

\entryitemWithDescription{\hskip 0pt{}`Civil War' continues box-office campaign at No. 1}{https://apnews.com/article/d8fe8822fdb08c5f4da19d51f1e2bda0}{NEW YORK (AP) --- ``Civil War,'' Alex Garland's ominous American dystopia, remained the top film in theaters in its second week of release, according to studio estimates Sunday. The A24 election-year gamble, the indie studio's biggest...}

\entryitemWithDescription{\hskip 0pt{}Conductor Andrew Davis dies at 80, headed Lyric Opera of Chicago and orchestras on 3 continents}{https://apnews.com/article/b967ff41c7b1720b6d906c150f508bd1}{Andrew Davis, an acclaimed British conductor who was music director of the Lyric Opera of Chicago and orchestras on three continents, has died. He was 80. Davis died Saturday at Rusk Institute in Chicago from leukemia, his manager...}

\entryitemWithDescription{\hskip 0pt{}15 people suffer minor injuries in tram accident at Universal Studios theme park in Los Angeles}{https://apnews.com/article/24432916e9a5d2273674540e55064bbd}{LOS ANGELES (AP) --- A tram accident at Universal Studios Hollywood in Los Angeles injured 15 people Saturday night, authorities and the company said. Los Angeles County Fire Department units were dipatched to the theme park on Lankershim...}

\entryitemWithDescription{\hskip 0pt{}Theater Review: Not everyone will be `Fallin' over Alicia Keys' Broadway musical `Hell's Kitchen'}{https://apnews.com/article/6a9637aa992636c7771b7382263b1f62}{If you were to close Alicia Keys ' big semi-autobiographical musical on Broadway with any of her hit songs, which would it be? Of course, it has to be ``Empire State of Mind.'' That's the natural one, right? It's also as predictable as...}

\entryitemWithDescription{\hskip 0pt{}Will there be a `superbloom' this year in California? Here's what to know}{https://apnews.com/article/3ef5f84eb74fdd6b670032a1ba46cf44}{Carpets of yellow, orange and gold flowers are beginning to cover Southern California's vast deserts, the Bay Area's dramatic bluffs and even near Los Angeles International Airport. But do they add up to a ``superbloom''? There is no...}

\entryitemWithDescription{\hskip 0pt{}Oregon lodge famously featured in `The Shining' will reopen to guests after fire forced evacuations}{https://apnews.com/article/7269bb2b3de02d9553e6e141c34bf583}{GOVERNMENT CAMP, Ore. (AP) --- Oregon's historic Timberline Lodge, which featured in Stanley Kubrick's 1980 film ``The Shining,'' will reopen to guests Sunday after a fire that prompted evacuations but caused only minimal damage. The...}

\entryitemWithDescription{\hskip 0pt{}These photos capture Coachella's highlights so far}{https://apnews.com/article/d332c338d4b9887eb78b797d22073f93}{INDIO, Calif. (AP) --- Thousands of fans flocked to the Southern California desert town of Indio this year for the Coachella Valley Music Festival, now on its second of two weekends. Headline acts for the 2024 edition of the annual bash...}

\entryitemWithDescription{\hskip 0pt{}Roman Gabriel, former NC State and pro quarterback who was the AP NFL MVP in 1969, dies at 83}{https://apnews.com/article/da8608646fe7e576c32e5e05abf5d635}{Roman Gabriel, the former North Carolina State quarterback who was the 1969 NFL MVP with the Los Angeles Rams, died Saturday. He was 83. Gabriel's son, Roman III, announced his father's death in a social-media post, saying he had ``passed...}

\entryitemWithDescription{\hskip 0pt{}Recently arrested Morgan Wallen says he's `not proud' of behavior}{https://apnews.com/article/12788b00384ed365ab75e12d5b166dee}{NASHVILLE, Tenn. (AP) --- Country music star Morgan Wallen, who faces charges stemming in part from accusations that he threw a chair off the rooftop of a six-story bar, says he's ``not proud'' of his behavior and accepts responsibility...}

\entryitemWithDescription{\hskip 0pt{}John Sterling honored by Yankees for 36 seasons and 5,631 games as radio voice}{https://apnews.com/article/556375b9e6c669cc032c3bed90939188}{NEW YORK (AP) --- John Sterling was honored during an on-field ceremony Saturday following his retirement as a New York Yankees broadcaster for 36 seasons. Sterling, who turns 86 on July 4, was presented a jersey with No. 5,631...}

\entryitemWithDescription{\hskip 0pt{}David Pryor, former Arkansas governor and senator, has died at age 89}{https://apnews.com/article/a4ce049c412b4d16b616a18e7c8f9422}{LITTLE ROCK, Ark. (AP) --- Former Arkansas governor and U.S. Sen. David Pryor, a Democrat who was one of the state's most beloved political figures and remained active in public service in the state long after he left office, has died. He...}

\entryitemWithDescription{\hskip 0pt{}Federal officials investigating cockpit visit by Rockies coach during United flight}{https://apnews.com/article/25f5cb92f7178bc327f7feff04eb404c}{DENVER (AP) --- Federal transportation officials are investigating an unauthorized inflight cockpit visit by a coach for the Colorado Rockies during a United Airlines charter flight last week from Denver to Toronto. Video surfaced this...}