\entryitemWithDescription{\hskip 0pt{}Comedian Pete Davidson charged with reckless driving after Beverly Hills crash}{https://apnews.com/article/1e6e21df18668bfbb2cf5a61e6ac4534}{FILE - Comedian Pete Davidson attends the premiere of "Big Time Adolescence," at Metrograph on March 5, 2020, in New York. Los Angeles prosecutors charged former the "Saturday Night Live" star with reckless driving Friday, June 16, 2023...}

\entryitemWithDescription{\hskip 0pt{}Next round of COVID-19 shots in fall will target latest omicron strain}{https://apnews.com/article/21912cf8980ab8a0763625de37cc7704}{FILE - Pfizer, left, and Moderna bivalent COVID-19 vaccines are readied for use at a clinic, Nov. 17, 2022, in Richmond, Va. The Food and Drug Administration on Friday, June 16, 2023, told COVID-19 vaccine makers to update fall shots to...}

\entryitemWithDescription{\hskip 0pt{}Grammys: Only 'human creators' eligible to win, recording academy says response to AI}{https://apnews.com/article/86fd1cf2291abf1d665b91749cd8d494}{FILE - Grammy Awards are displayed at the Grammy Museum Experience at Prudential Center in Newark, N.J. on Oct. 10, 2017. The Recording Academy has announced three new categories to be added to the 2024 Grammy Awards: Best Pop Dance...}

\entryitemWithDescription{\hskip 0pt{}German archeologists find Bronze Age sword so well-preserved it 'almost shines'}{https://apnews.com/article/cb2070fdd128a40ee3f8e3421e80356b}{BERLIN (AP) --- A bronze sword made more than 3,000 years ago that is so well-preserved it ``almost still shines'' has been unearthed in Germany, officials say. Bavaria\textquotesingle s state office for the preservation of historical...}

\entryitemWithDescription{\hskip 0pt{}Unionized UPS workers could strike this summer, scrambling supply chains and home delivery}{https://apnews.com/article/c95fe254530e973e3193a16c3b4d025f}{A UPS truck makes deliveries in Northbrook, Ill., Wednesday, May 10, 2023. Unionized UPS workers voted overwhelmingly on Friday, June 16, to authorize a strike, setting the stage for a potential work stoppage if the package delivery...}

\entryitemWithDescription{\hskip 0pt{}NBA suspends Ja Morant 25 games for 2nd social media video involving a gun}{https://apnews.com/article/b41cba5fd2225eace4a586d7c641a190}{FILE - Memphis Grizzlies guard Ja Morant warms up before an NBA basketball game against the Houston Rockets, Wednesday, March 22, 2023, in Memphis, Tenn. Morant has been suspended for the first 25 games of the upcoming season for his...}

\entryitemWithDescription{\hskip 0pt{}Michael Jordan selling majority ownership stake in Charlotte Hornets}{https://apnews.com/article/527087d134136ef38cae1da8d1c95b01}{FILE - Charlotte Hornets owner Michael Jordan speaks to the media about hosting the NBA All-Star basketball game during a news conference in Charlotte, N.C., Tuesday, Feb. 12, 2019. Michael Jordan is finalizing a deal to sell the majority...}

\entryitemWithDescription{\hskip 0pt{}New Spider-Man film pulled from cinema programs in Arab world, possibly over transgender flag}{https://apnews.com/article/a199f686e2e7fe34d060655d145fd11a}{This image released by Sony Pictures Animation shows Miles Morales as Spider-Man, voiced by Shameik Moore, left, and and Spider-Gwen, voiced by Hailee Steinfeld, in a scene from Columbia Pictures and Sony Pictures Animation...}

\entryitemWithDescription{\hskip 0pt{}Amazon's \$1.7 billion deal to buy Roomba maker iRobot gets UK approval}{https://apnews.com/article/aff145840b5c5706c69f2d14490a6052}{FILE - An Amazon company logo is seen on the facade of a company\textquotesingle s building in Schoenefeld near Berlin, Germany, on March 18, 2022. British antitrust regulators have cleared Amazon's purchase of robot vacuum maker iRobot...}

\entryitemWithDescription{\hskip 0pt{}Swiss cyclist Gino Mäder dies after falling down a ravine in the Tour de Suisse}{https://apnews.com/article/86599c13a67b0f10d01b94abbaae895c}{Gino Mader waits for the start of the 7th stage of the Giro d\textquotesingle Italia, Tour of Italy cycling race, in Notaresco, Italy, on May 14, 2021. Swiss cyclist Gino Mader has died Friday, June 16, 2023 one day after suffering...}

\entryitemWithDescription{\hskip 0pt{}A nun commends Dodgers' handling of Pride Night controversy. Some archbishops call it blasphemy}{https://apnews.com/article/a567e20bb5dc7efe3bd19af412740839}{FILE - Members of the Sisters of Perpetual Indulgence attend a gay Pride parade in West Hollywood, Calif., on Sunday, June 12, 2016. Three prominent Catholic leaders --- including the archbishops of New York and Los Angeles --- said the...}

\entryitemWithDescription{\hskip 0pt{}Mass of rock slides down Swiss mountainside above evacuated village, narrowly missing settlement}{https://apnews.com/article/4a477f902fdec3e2475f9d43808eb357}{General view of part of the village of Brienz-Brinzauls below the rockfall "Brienzer Rutsch", in Switzerland, Friday, June 16, 2023. On Thursday night, a large part of the rock masses fell towards the village. The rock masses just missed...}

\entryitemWithDescription{\hskip 0pt{}German police appeal for images taken of an attack in which Americans were pushed down a steep slope}{https://apnews.com/article/757936f6bd1f8fcb2b01cdb2c4eb8906}{People stay on the Marien-Bridge at Castle Neuschwanstein, a 19th century creation by Bavaria\textquotesingle s fairy tale king Ludwig II and world renowned tourist attraction, is pictured in Hohenschwangau near Fuessen, southern Germany...}