\entryitemWithDescription{\hskip 0pt{}Judge allows Ja Morant's lawyers to argue he acted in self-defense in lawsuit about fight with teen}{https://apnews.com/article/f4b088e4289cc5db417e0177fbbc51ec}{MEMPHIS, Tenn. (AP) --- Lawyers for Memphis Grizzlies guard Ja Morant are allowed to argue that he was acting in self-defense as part of a lawsuit accusing him of assaulting a teenager during a pickup basketball game at the NBA star's...}

\entryitemWithDescription{\hskip 0pt{}New Subaru Forester, Lucid SUV and Toyota Camry are among vehicles on display at L.A. Auto Show}{https://apnews.com/article/0323d2714700765749d6308f6565261b}{LOS ANGELES (AP) --- An all-new Subaru Forester, a Lucid electric SUV, and a revamped Toyota Camry are among the new automobiles that will be on display at the Los Angeles Auto Show starting this week. The public portion of the show runs...}

\entryitemWithDescription{\hskip 0pt{}Officials investigate cause of Atlantic City Boardwalk fire that damaged facade of Resorts casino}{https://apnews.com/article/6c6acc669ca3c0e9455940e4fb5dea63}{ATLANTIC CITY, N.J. (AP) --- Investigators were trying Thursday to determine what touched off a fire on the Atlantic City Boardwalk a day earlier that burned a section of the historic walkway and damaged part of the facade of Resorts...}

\entryitemWithDescription{\hskip 0pt{}Indian manufacturer recalls eyedrops previously cited in FDA warning}{https://apnews.com/article/11624105e31a68102d414594c85766f0}{WASHINGTON (AP) --- An Indian company that recently recalled eyedrops sold in the U.S. had a host of sanitation and manufacturing problems, including barefoot workers, cracked floors and altered records, U.S. health inspectors found. Food...}

\entryitemWithDescription{\hskip 0pt{}Ken Squier, a longtime NASCAR announcer and broadcaster, dies at 88}{https://apnews.com/article/47e0121ff3eafb4a46bf82da445310b3}{Ken Squier, a longtime NASCAR announcer and broadcaster, has died. He was 88. Squier died Wednesday night in Waterbury, Vermont, according to the management of the local WDEV radio, which he owned. ``Though he never sat behind the wheel...}

\entryitemWithDescription{\hskip 0pt{}Here's why heavy rain in Florida has little to do with hurricane season}{https://apnews.com/article/2ee640db9c95a926f00844014131b7ea}{FORT LAUDERDALE, Fla. (AP) --- Why has it been raining so much in South Florida? Experts say the latest windy, rainy storm system has nothing to do with hurricane season --- and it's finally moving on. The storm system that formed over...}

\entryitemWithDescription{\hskip 0pt{}Thousands of Starbucks workers go on a one-day strike, one of busiest days of year for the chain}{https://apnews.com/article/7c07617260ea1c4760410e29b4509b6b}{NEW YORK (AP) --- Workers at more than 200 U.S. Starbucks locations walked off the job Thursday in what organizers said was the largest strike yet in the two-year-old effort to unionize the company's stores. The Workers United union chose...}

\entryitemWithDescription{\hskip 0pt{}Indian rescuers start drilling to reach 40 workers trapped in a collapsed tunnel since the weekend}{https://apnews.com/article/4848a6cd786e6c932636d1ca7ec1c2e1}{LUCKNOW, India (AP) --- Rescuers in northern India supplied food and medicine to 40 construction workers on Thursday as officials started drilling through the rubble to reach the men who have been trapped since a portion of the tunnel...}

\entryitemWithDescription{\hskip 0pt{}NYC raids net knockoff bags, apparel, said to be worth \$1B if items had been real}{https://apnews.com/article/f7889a9bcb38c139d2e8efe6d5aa3d26}{NEW YORK (AP) --- Raids on storage facilities in New York City turned up a huge haul of counterfeit handbags, shoes and other luxury merchandise that could have been worth more than \$1 billion if the knockoffs had been real, federal...}

\entryitemWithDescription{\hskip 0pt{}Roger Waters was denied hotel stays in Argentina and Uruguay over antisemitism allegations, report says}{https://apnews.com/article/cb8b9276dd2f1eea45eaa6111456406b}{RIO DE JANEIRO (AP) --- Hotels in Argentina and Uruguay reportedly rejected reservations for Pink Floyd co-founder Roger Waters over accusations of antisemitism leveled at the British singer known for his pro-Palestinian views. Waters was...}

\entryitemWithDescription{\hskip 0pt{}Gerrit Cole a unanimous winner of his 1st AL Cy Young Award. Blake Snell takes the NL prize}{https://apnews.com/article/5d26ae2fdccb0d6eb6496068d6161deb}{NEW YORK (AP) --- After several close calls, Gerrit Cole finally won his first American League Cy Young Award on the strength of consistent excellence all season. Blake Snell joined a short list of pitching royalty by turning around a...}

\entryitemWithDescription{\hskip 0pt{}A woman is ordered to pay nearly \$39K to American Airlines for interfering with a flight crew}{https://apnews.com/article/b8aeb41da6a9f9a1d195d5f6e2a582f5}{PHOENIX (AP) --- A woman from Hawaii has been ordered to pay nearly \$39,000 in restitution to American Airlines for interfering with a crew on a flight last year, according to authorities. Federal prosecutors said Tuesday that 29-year...}

\entryitemWithDescription{\hskip 0pt{}Magnitude 3.6 earthquake rattles parts of northern Illinois, parts of 3 other states, USGS says}{https://apnews.com/article/8331dc3e71deb6676c6070718aedc479}{STANDARD, Ill. (AP) --- A magnitude 3.6 earthquake rattled northern Illinois and parts of three other states early Wednesday, awakening some residents and spurring reports to 911 about homes shaking, the U.S. Geological Survey and police...}