\entryitemWithDescription{\hskip 0pt{}After 28 years, man wrongfully convicted of murder is free}{https://apnews.com/article/5c4f3e6faadb018aef74685044b882d1}{Lamar Johnson, center, and his attorneys react on Tuesday, Feb. 14, 2023, after St. Louis Circuit Judge David Mason vacated his murder conviction during a hearing in St. Louis, Mo. Johnson served nearly 28 years of a life sentence for a...}

\entryitemWithDescription{\hskip 0pt{}6 fatally shot in small Mississippi town, suspect in custody}{https://apnews.com/article/caf3fbdbfcb31a3f8e4e3c3e777089ee}{Law enforcement personnel work at the scene of a shooting, Friday, Feb. 17, 2023, in Arkabutla, Miss. Six people were fatally shot Friday in the small town in rural Mississippi near the Tennessee state line, and authorities said they had...}

\entryitemWithDescription{\hskip 0pt{}Stella Stevens, star of 'The Nutty Professor,' is dead at 84}{https://apnews.com/article/983825af3914d407c629171aafe18d7a}{FILE - Actress Stella Stevens and actor Robert Vaughn, a nominee for best supporting actor of the year for "The Young Philadelphians," arrive at the Academy Award fashion show which preceded the Oscar presentations in Hollywood, April 4...}

\entryitemWithDescription{\hskip 0pt{}Clinic to open near Ohio derailment as health worries linger}{https://apnews.com/article/ad32648e67289166f9ae1e9d104ca53b}{A tank car sits on a trailer as the cleanup of portions of a Norfolk Southern freight train that derailed over a week ago continues in East Palestine, Ohio, Wednesday, Feb. 15, 2023. (AP Photo/Gene J. Puskar) Ohio Gov. Mike DeWine held a...}

\entryitemWithDescription{\hskip 0pt{}1st class of Ukraine fighters finishes advanced US training}{https://apnews.com/article/afcffd86e422d6a848087cc5160af554}{In this image provided by the U.S. Army, U.S. Soldiers from Battery A, 41st Field Artillery Regiment, 1st Armored Brigade Combat Team, 3rd Infantry Division, conduct live-fire exercises using the M109 Paladins at the Grafenwoehr Training...}

\entryitemWithDescription{\hskip 0pt{}Off camera, Fox hosts doubted 2020 election fraud claims}{https://apnews.com/article/b52914ec21a97dec8b5d878a908d566f}{FILE - A headline about President Donald Trump is displayed outside Fox News studios, on Nov. 28, 2018, in New York. On Thursday, Feb. 16, the voting machine company Dominion filed court papers documenting that numerous Fox News...}

\entryitemWithDescription{\hskip 0pt{}Barstool Sports is acquired by Penn Entertainment}{https://apnews.com/article/9952b602eb4bd3c4d6b5965e98342dbb}{FILE - Barstool Sports founder David Portnoy, attends an NCAA college basketball game Saturday, Jan. 22, 2022, in Coral Gables, Fla. On Friday, Feb. 17, 2023, Penn Entertainment Inc. announced it has closed on its acquisition of Barstool...}

\entryitemWithDescription{\hskip 0pt{}Fetterman case highlights common stroke, depression link}{https://apnews.com/article/654cfe7faa563e8b23149bb56ad9b47f}{Sen. John Fetterman, D-Pa., arrives for President Joe Biden\textquotesingle s State of the Union address to a joint session of Congress at the Capitol, Tuesday, Feb. 7, 2023, in Washington. (AP Photo/Carolyn Kaster) Pennsylvania...}

\entryitemWithDescription{\hskip 0pt{}U-Haul rampage victim died striving for 'American dream'}{https://apnews.com/article/fefa9478b5e407dd78cd5a010482fc3d}{FILE ----Erafin Yaz, 25, looks from his roof at the caution tape covering the corner of Bay Ridge Avenue and 5th Avenue where pedestrians were struck Monday, Feb. 13, 2023, in the Brooklyn borough of New York. Delivery worker YiJie Ye was...}

\entryitemWithDescription{\hskip 0pt{}Military finishes recovering Chinese balloon debris}{https://apnews.com/article/3a6f05a2b3158d104b4921860849495f}{FILE - In this image released by the U.S. Navy, sailors assigned to Assault Craft Unit 4 prepare material recovered off the coast of Myrtle Beach, S.C., in the Atlantic Ocean from the shooting down of a Chinese high-altitude balloon, for...}

\entryitemWithDescription{\hskip 0pt{}Bodies of 18 migrants found in abandoned truck in Bulgaria}{https://apnews.com/article/15705663988ef78c78a0ae8520adfe66}{The bodies of 18 migrants lie on the ground near an abandoned truck, at the village of Lokorsko, near Sofia, Bulgaria, Friday, Feb. 17, 2023. Police in Bulgaria on Friday discovered an abandoned truck containing the bodies of 18 migrants...}

\entryitemWithDescription{\hskip 0pt{}Fed's Barkin: 'Slow progress' on inflation, sees more hikes}{https://apnews.com/article/78862402877ff367d27119614e070065}{FILE- In this Feb. 5, 2018, file photo, the seal of the Board of Governors of the United States Federal Reserve System is displayed in the ground at the Marriner S. Eccles Federal Reserve Board Building in Washington.Richmond Federal...}

\entryitemWithDescription{\hskip 0pt{}Bruce Willis has frontotemporal dementia. What is FTD?}{https://apnews.com/article/fbfdbfca4793bb65ef3f38f31e31bd68}{FILE - Bruce Willis attends a movie premiere in New York on Friday, Oct. 11, 2019. Nearly a year after Bruce Willis' family announced that he would step away from acting after being diagnosed with aphasia, his family says his ``condition...}