\entryitemWithDescription{\hskip 0pt{}Pearl Jam gives details of new album `Dark Matter,' drops first single, announces world tour}{https://apnews.com/article/732bb298914948f1e01579a63b1a391c}{LOS ANGELES (AP) --- Pearl Jam `s forthcoming album is called ``Dark Matter,'' its first single of the same title has been released, and the band will start a world tour in May. The Rock and Roll Hall of Famers revealed the new details on...}

\entryitemWithDescription{\hskip 0pt{}A man has been charged in the theft of a Jackie Robinson statue that was found dismantled and burned}{https://apnews.com/article/c959797761a726fe3611b1b4ee641e8f}{Police announced Tuesday the arrest of a 45-year-old man in the theft of a bronze Jackie Robinson statue that later was found dismantled and burned. Wichita police Lt. Aaron Moses said Ricky Alderete was taken into custody earlier this...}

\entryitemWithDescription{\hskip 0pt{}Notre Dame cathedral's spire revealed in Paris as reconstruction continues after fire}{https://apnews.com/article/80bc7208a3398d06dd55e659d397e4bd}{PARIS (AP) --- Scaffolding that shrouded the top of Notre Dame cathedral following a devastating fire in April 2019 is being removed, marking a milestone in its reconstruction. As the shell at the summit has been taken down in recent...}

\entryitemWithDescription{\hskip 0pt{}More than 1,000 flights already cancelled due to storm, was one of them yours? Here's what to do}{https://apnews.com/article/cfa34ddf5255b2a533cf15fbf3ec61e3}{A nasty storm with 60 mph winds raked parts of the Northeast on Tuesday creating dangerous conditions on the road and snarling airports. More than 1,200 flights were cancelled before noon, mostly along the East Coast, but that is likely...}

\entryitemWithDescription{\hskip 0pt{}A new exhibition aims to bring Yoko Ono's art out of John Lennon's shadow}{https://apnews.com/article/7908545eaa9811aed5d866829bbe03db}{LONDON (AP) --- Before there was John and Yoko --- and after --- there was just Yoko Ono. The Japanese-American artist became a global celebrity through her marriage to John Lennon, her partner for more than a decade until his murder in...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: A look at Mardi Gras festivities in New Orleans through the years}{https://apnews.com/article/e78f1df2900b76e524e4d8cb8244ad46}{NEW ORLEANS (AP) --- Carnival season comes to a close Tuesday with thousands of people expected to crowd the streets of New Orleans and surrounding communities for the annual Mardi Gras celebration complete with parade floats...}

\entryitemWithDescription{\hskip 0pt{}King Charles III returns to London from country retreat for expected cancer treatment}{https://apnews.com/article/35533ca9b2aa10d24826dd222deb76d8}{LONDON (AP) --- King Charles III returned to London from his country retreat on Tuesday for what is expected to be further treatment following his cancer diagnosis. Charles, 75, and his wife Queen Camilla flew by helicopter to Buckingham...}

\entryitemWithDescription{\hskip 0pt{}Don't feed the pandas: Man banned from panda park for life for throwing `objects' into an enclosure}{https://apnews.com/article/ce008e6af75a95f6ecbcc4a740a4e2e1}{BEIJING (AP) --- Don't feed the pandas. That's the rule seemingly broken by a man who was banned for life from one of China's main panda centers after throwing unspecified ``objects'' into an enclosure on Monday. A notice from the Chengdu...}

\entryitemWithDescription{\hskip 0pt{}Love (and 460 million flowers) are in the air for Valentine's Day, but not without a Miami layover}{https://apnews.com/article/35497c75e43eafdc0713f99b18f13409}{MIAMI (AP) --- While Valentine's Day may not be known as a busy time for air travel, it's a busy time at Miami International Airport. where many of the nation's fresh cut flowers arrive from South America. Around 90\% of the roses and...}

\entryitemWithDescription{\hskip 0pt{}Oregon officials report bubonic plague in local resident. They say there's little risk to community}{https://apnews.com/article/bc33b82a23fe60c27c113e72bc05ce32}{BEND, Oregon (AP) --- Public health officials in Oregon have reported a case of bubonic plague in a local resident who they said likely contracted it from a pet cat. All close contacts of the person and the cat have been contacted and...}

\entryitemWithDescription{\hskip 0pt{}Chiefs fans are hoping for a Taylor Swift appearance at victory parade. But her schedule is tight}{https://apnews.com/article/df383f3a00cc813dd0d852058a41e5b2}{KANSAS CITY, Mo. (AP) --- Stacey Stauch has one question on her mind as the Kansas City Chiefs prepare to celebrate their third Super Bowl title in five seasons with a parade. ``We're all wondering: Will Taylor show up?'' the paralegal...}

\entryitemWithDescription{\hskip 0pt{}Former professional wrestler William ``Billy Jack'' Haynes in custody in wife's death in Oregon}{https://apnews.com/article/9bfcf99f4b5ba3d9ed466c90c45ba95a}{PORTLAND, Ore. (AP) --- Former professional wrestler William Albert ``Billy Jack'' Haynes Jr. has been taken into police custody in connection with the death of his wife in Portland, authorities said. Portland police said in a statement...}

\entryitemWithDescription{\hskip 0pt{}Usher and longtime partner Jenn Goicoechea married after the Super Bowl, records show}{https://apnews.com/article/cc6970f2aa2062db581b076cd50af89f}{LAS VEGAS (AP) --- Usher and longtime partner Jenn Goicoechea married in Las Vegas just hours after the R\&B superstar's headline appearance at the Super Bowl halftime show, according to officials and documents. The officiant who wed the...}