\entryitemWithDescription{\hskip 0pt{}NBA suspends Ja Morant 8 games for video showing gun in club}{https://apnews.com/article/8cc82061f6465f96d6c5d0806d92d7d0}{FILE - Memphis Grizzlies\textquotesingle{} Ja Morant is shown during an NBA basketball game against the Los Angeles Lakers, Tuesday, Feb. 28, 2023, in Memphis, Tenn. The NBA has suspended Memphis Grizzilies guard Ja Morant eight games...}

\entryitemWithDescription{\hskip 0pt{}Does 'Ted Lasso' end with season 3? What to ... believe}{https://apnews.com/article/c02abe70284efe943ebb140fc6bceca8}{Brett Goldstein, from left, Toheeb Jimoh, Hannah Waddingham, Jason Sudeikis and Brendan Hunt, all members of the cast of "Ted Lasso," pose for a portrait at the Four Seasons Hotel in Los Angeles on on Monday, March 6, 2023. (Photo by...}

\entryitemWithDescription{\hskip 0pt{}US, Russian military chiefs resume contact to discuss drone}{https://apnews.com/article/7fe21f60da101312f7c174d63c311a01}{Secretary of Defense Lloyd Austin, left, accompanied by Chairman of the Joint Chiefs, Gen. Mark Milley, speaks during a briefing at the Pentagon in Washington, Wednesday, March 15, 2023. (AP Photo/Andrew Harnik) WASHINGTON (AP...}

\entryitemWithDescription{\hskip 0pt{}Stormy Daniels meets with prosecutors investigating Trump}{https://apnews.com/article/d48153fc2d3fe7a656e8a24ad1acd082}{Donald Trump's former lawyer and fixer Michael Cohen is testifying before a Manhattan grand jury investigating hush money payments he arranged and made on the former president's behalf. (March 13) FILE - Adult film actress Stormy Daniels...}

\entryitemWithDescription{\hskip 0pt{}Garcetti confirmed as India ambassador after 20-month fight}{https://apnews.com/article/3c1989656dbec03267a1762bf3da9b9d}{This image provided by Senate Television shows the Senate vote total on Wednesday, March 15, 2023, on the nomination of Eric Garcetti to become the U.S. Ambassador to India. Garretti\textquotesingle s nomination was approved by a vote of...}

\entryitemWithDescription{\hskip 0pt{}Future NASA moonwalkers to sport sleeker spacesuits}{https://apnews.com/article/486bb5722c78c250348e2ab36f312bf6}{Moonwalking astronauts will have sleeker, more flexible spacesuits when they step onto the lunar surface later this decade; An Axiom Space employee modeled a dark spacesuit, doing squats and twisting at an event in Houston. Axiom Space...}

\entryitemWithDescription{\hskip 0pt{}Texas announces takeover of Houston schools, stirring anger}{https://apnews.com/article/eae680bec5fbd3b419c2583fb850d42e}{FILE - People hold up signs at a news conference, Friday, March 3, 2023, in Houston while protesting the proposed takeover of the city\textquotesingle s school district by the Texas Education Agency. Texas officials on Wednesday, March...}

\entryitemWithDescription{\hskip 0pt{}Chinese businessman arrested in \$1 billion fraud conspiracy}{https://apnews.com/article/d49b80f5f78ab30570a67885e91a0a05}{FILE - A Twitter page of Chinese exiled businessman Guo Wengui is seen on a computer screen in Beijing, Aug. 30, 2017. The self-exiled Chinese businessman long sought by the government of China, and known for cultivating ties to Trump...}

\entryitemWithDescription{\hskip 0pt{}What can ChatGPT maker's new AI model GPT-4 do?}{https://apnews.com/article/307e867e3fe4464be9c4f884909f3977}{FILE - Text from the ChatGPT page of the OpenAI website is shown in this photo, in New York, Feb. 2, 2023. The company behind the ChatGPT chatbot has on Wednesday, March 15 rolled out its latest artificial intelligence model, GPT-4, in a...}

\entryitemWithDescription{\hskip 0pt{}Social media madness gives opportunities to Edert and others}{https://apnews.com/article/ef5fe8ef3e482d0f36a4d6cc3bdf2b89}{FILE - St. Peter\textquotesingle s Doug Edert celebrates after defeating Monmouth in an NCAA college basketball game during the championship of the Metro Atlantic Athletic Conference tournament, Saturday, March 12, 2022, in Atlantic City...}

\entryitemWithDescription{\hskip 0pt{}T-Mobile acquires Mint, partially owned by Ryan Reynolds}{https://apnews.com/article/01de71836f8fddab3004bde10f911578}{FILE - Ryan Reynolds arrives at the 36th annual American Cinematheque Awards, Nov. 17, 2022, at the Beverly Hilton Hotel in Beverly Hills, Calif. U.S. wireless carrier T-Mobile announced Wednesday, March 15, 2023, that it is buying...}

\entryitemWithDescription{\hskip 0pt{}US and Russia ratchet up rhetoric over downing of drone}{https://apnews.com/article/9f4b3e8fdd719c0fa91a0683228b9e51}{Defense Secretary Lloyd Austin says Russia acted in a "dangerous, reckless" manner when one of its fighter jets downed an American drone over the Black Sea, and says the US will continue to fly its aircraft despite Russia\textquotesingle...}

\entryitemWithDescription{\hskip 0pt{}Bank fears spread to Europe, drag down shares of big lenders}{https://apnews.com/article/ba1861aa8b61170c00a2789287dc9a08}{FILE - Grey clouds cover the sky over a building of the Credit Suisse bank in Zurich, Switzerland, on Feb. 21, 2022. Battered shares of Credit Suisse lost more than one-quarter of their value Wednesday March 15, 2023, hitting a record low...}