\entryitemWithDescription{\hskip 0pt{}Coach hired, team still required: Soccer's status in the Marshall Islands is a work in progress}{https://apnews.com/article/99d57eb914d3e981700ea063741bb2e2}{BRISBANE, Australia (AP) --- Lloyd Owers recalls with fondness his initial visit from his home in England to the Marshall Islands, a small nation of five islands, 29 atolls and about 60,000 people situated in the western Pacific Ocean...}

\entryitemWithDescription{\hskip 0pt{}Matthew Perry tributes pour in, including fellow `Friends' actors, classmate Justin Trudeau and SNL}{https://apnews.com/article/c4e6ead4b4169652d90ec09f54059b62}{Matthew Perry was widely mourned this weekend by friends, co-stars and some very famous fans, including his childhood classmate, Canadian Prime Minister Justin Trudeau; his ``Friends'' mom Morgan Fairchild; and even Adele. Perry, who...}

\entryitemWithDescription{\hskip 0pt{}How extreme weather in the US may have affected the pumpkins you picked this year for Halloween}{https://apnews.com/article/81905cc284aacf30744b2cb5dbe0a141}{HUDSON, Colo. (AP) --- Alan Mazzotti can see the Rocky Mountains about 30 miles west of his pumpkin patch in northeast Colorado on a clear day. He could tell the snow was abundant last winter, and verified it up close when he floated...}

\entryitemWithDescription{\hskip 0pt{}In Benin, Voodoo's birthplace, believers bemoan steady shrinkage of forests they revere as sacred}{https://apnews.com/article/9c8737ad86d15e1503f3fc908c6c2518}{PORTO-NOVO, Benin (AP) --- For many people in Benin, the forests empowered them before they were born, or in the first months of their lives. Barren women performed Voodoo rituals by sacred trees to get pregnant. Others were brought as...}

\entryitemWithDescription{\hskip 0pt{}Anchorage's oldest building, a Russian Orthodox church, gets new life in restoration project}{https://apnews.com/article/5ab2d9bd06d56f354f815b246fafc2d3}{EKLUTNA, Alaska (AP) --- The Russian Orthodox church on the outskirts of Alaska's biggest city is packed with treasures for the Christian faithful: religious icons gifted by Romanov czars, panels of oil paintings and jewel-studded incense...}

\entryitemWithDescription{\hskip 0pt{}Jagger watches Barcelona wear Stones logo in `clasico' but Beatles fan Bellingham gets Madrid winner}{https://apnews.com/article/bdac04de98f4de81a4c7a8ddd5883898}{BARCELONA, Spain (AP) --- Barcelona aligned with the Rolling Stones for Saturday's ``clasico'' soccer game against Real Madrid when Mick Jagger showed up to see the home team wear special jerseys featuring the iconic logo of his legendary...}

\entryitemWithDescription{\hskip 0pt{}Winner of albinism pageant says Zimbabwe event made her feel beautiful and provided sense of purpose}{https://apnews.com/article/9a8c87824a6be9965e648cdcfd2fec68}{HARARE, Zimbabwe (AP) --- A glittering crown on her head and a bouquet of flowers in her hands, Andreia Solange Sicato Muhitu beamed at being named the co-winner of the the inaugural Mr. and Miss Albinism Southern Africa pageant. The 28...}

\entryitemWithDescription{\hskip 0pt{}In Seattle, phones ding. Killer whales could be close}{https://apnews.com/article/0e86cd0a5403049a74386d66fc0ae8c8}{SEATTLE (AP) --- Peter Bates was dropping his car at the mechanic this month when a notification pinged on his phone: killer whales were approaching his Seattle neighborhood. He hopped on a bus toward the water, then an electric bike. He...}

\entryitemWithDescription{\hskip 0pt{}Canadian fishing boat rescues American fisherman from missing vessel based in Washington state}{https://apnews.com/article/a90d32432832be0c10099445a5f8ccba}{VANCOUVER, British Columbia (AP) --- A Canadian fishing boat rescued an American man one day after the U.S. Coast Guard ended its search for a missing commercial fishing boat from Washington state with two people board, authorities said...}

\entryitemWithDescription{\hskip 0pt{}The White House and Google launch a new virtual tour with audio captions, Spanish translation}{https://apnews.com/article/d422c4ede3424643fc131d6fb24e2636}{WASHINGTON (AP) --- Can't come to Washington? Couldn't get a ticket to tour the White House? Don't worry. The White House, Google Maps and Google Arts \& Culture launched a new virtual tour of the famous mansion on Friday, which is also...}

\entryitemWithDescription{\hskip 0pt{}DC pandas will be returning to China in mid-November, weeks earlier than expected}{https://apnews.com/article/96c106c85143621e29bcc579a24c068d}{WASHINGTON (AP) --- The National Zoo's three celebrity giant pandas will be heading home a little earlier than expected. Zoo officials told The Associated Press on Thursday that adult bears Mei Xiang and Tian Tian and their cub Xiao Qi Ji...}

\entryitemWithDescription{\hskip 0pt{}Arizona Diamondbacks take series of slights into surprise World Series against Texas Rangers}{https://apnews.com/article/fbd22417810138c1cfe396aa7c2bdfbd}{ARLINGTON, Texas (AP) --- Before opening the World Series, the Arizona Diamondbacks wanted to recount a series of slights. Overlooked by oddsmakers and angered by analysts, the Diamondbacks find themselves in a Surprise Series against the...}

\entryitemWithDescription{\hskip 0pt{}Radio host Larry Elder ends Republican presidential campaign and endorses Donald Trump}{https://apnews.com/article/a3d3665cd50d1e0d2071ab8800075482}{Conservative talk radio host Larry Elder announced Thursday that he was ending his 2024 Republican campaign for president and endorsing former President Donald Trump. Elder, who sought to replace California Gov. Gavin Newsom in a failed...}