\entryitemWithDescription{\hskip 0pt{}Colts confirm NFL investigating player for possible gambling}{https://apnews.com/article/3879df41cb2c568b9297d8456f9edf17}{INDIANAPOLIS (AP) --- The Indianapolis Colts said Monday they are aware the NFL has opened a gambling investigation into one of the team's players but would not discuss any additional details. The confirmation came shortly after reports...}

\entryitemWithDescription{\hskip 0pt{}Biden says Chiefs 'building a dynasty' as he hosts Kansas City Super Bowl champs at White House}{https://apnews.com/article/a387573fff4bc6b087277159dcbd0fb3}{President Joe Biden walks with Kansas City Chiefs quarterback Patrick Mahomes as he welcomes the football team to the White House in Washington, Monday, June 5, 2023, to celebrate their championship season and victory in Super Bowl LVII...}

\entryitemWithDescription{\hskip 0pt{}Anna Shay, fan favorite on 'Bling Empire,' dead at 62}{https://apnews.com/article/df05b4e3eb74a0c44f8d1df0d6c03f69}{This image released by Netflix shows Anna Shay in a scene from the series "Bling Empire." Shay, an heiress, philanthropist and breakout star of the Netflix reality series ``Bling Empire,'' died from a stroke, according to a family...}

\entryitemWithDescription{\hskip 0pt{}Hundreds of journalists strike to demand leadership change at biggest US newspaper chain}{https://apnews.com/article/7cb859c29662b0f18e246fd1b56a21bd}{Editorial members of the Austin American-Statesman\textquotesingle s Austin NewsGuild picket along the Congress Avenue bridge in Austin, Texas, Monday, June 5, 2023. The mostly one-day strike aims to protest the company\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Yahya Abdul-Mateen II earns a Tony Award nomination for 'Topdog/Underdog'}{https://apnews.com/article/331d979f90b1a2613a3c6a143354005b}{Yahya Abdul-Mateen II poses for a portrait on Tuesday, May 23, 2023, in New York. Abdul-Mateen is nominated for a Tony Award for lead actor in a play for his role in ``Topdog/Underdog." (Photo by Andy Kropa/Invision/AP) NEW YORK (AP...}

\entryitemWithDescription{\hskip 0pt{}Britain's Princess Eugenie gives birth to second son}{https://apnews.com/article/a8b86e180a95682d36c502b421b325eb}{This is an undated photo released by Buckingham Palace on Monday, June 5, 2023 of Ernest George Ronnie Brooksbank. Buckingham Palace says Princess Eugenie has given birth to a baby boy. Eugenie, the niece of King Charles III, and her...}

\entryitemWithDescription{\hskip 0pt{}Is Outlook down? Thousands of users report problems with Microsoft's email platform}{https://apnews.com/article/ee5430f6a4636b297c64f0c0b695cfc3}{FILE - In this Jan. 10, 2009 file photo, the Microsoft logo is seen in Las Vegas. Thousands of Microsoft Outlook users reported issues with accessing and using the email platform Monday, June 5, 2023. (AP Photo/Paul Sakuma, file...}

\entryitemWithDescription{\hskip 0pt{}Suspect in Natalee Holloway disappearance to challenge extradition from Peru to US, lawyer says}{https://apnews.com/article/fcde656d024dcb706921cc40a1116bd0}{FILE - Joran van der Sloot looks back from his seat after entering the courtroom for the continuation of his murder trial at San Pedro prison in Lima, Peru, Jan. 11, 2012. The Peruvian government said on Monday, June 5, 2023 that Van der...}

\entryitemWithDescription{\hskip 0pt{}Missouri governor denies clemency for man facing execution on Tuesday}{https://apnews.com/article/e4a26eebace4f63ac5da75b6e07a6a16}{FILE - Inmate Michael Tisius, sentenced to death in the killing of two jail officers, shows his tattoos during an interview at Potosi Correctional Center, Missouri\textquotesingle s maximum security prison where condemned men live in the...}

\entryitemWithDescription{\hskip 0pt{}Trump lawyers meet with Justice Dept. officials as charging decision nears in Mar-a-Lago case}{https://apnews.com/article/455e06ae11fecd5fc6aa565bee6b3878}{FILE - Former President Donald Trump speaks at his Mar-a-Lago estate Tuesday, April 4, 2023, in Palm Beach, Fla. Timothy Parlatore, a key lawyer for former President Donald Trump says he\textquotesingle s leaving the legal team, a move...}

\entryitemWithDescription{\hskip 0pt{}Too much information? Jason Isbell believes opening your life to fans builds a stronger bond}{https://apnews.com/article/e9cbffbe9cd5e674c0f130a099a22e8a}{FILE - Jason Isbell, left, and Amanda Shires arrive at 67th Annual BMI Country Awards ceremony on Nov. 12, 2019, in Nashville, Tenn. (Photo by Al Wagner/Invision/AP, File) NEW YORK (AP) --- If Jason Isbell is keeping many more secrets, it...}

\entryitemWithDescription{\hskip 0pt{}Remembering D-Day: Key facts and figures about epochal World War II invasion}{https://apnews.com/article/07094640dd7bb938a23e144cc23f348c}{FILE - U.S. infantrymen wade through the surf as they land at Normandy in the days following the Allies\textquotesingle{} June 1944, D-Day invasion of occupied France. (AP Photo/Bert Brandt, File) OMAHA BEACH, France (AP) --- The D-Day...}

\entryitemWithDescription{\hskip 0pt{}Former Vice President Pence files paperwork launching 2024 presidential bid in challenge to Trump}{https://apnews.com/article/19ee44bb97c7c3131631077917056446}{FILE - Former Vice President Mike Pence talks with local residents during a meet and greet on May 23, 2023, in Des Moines, Iowa. Pence will officially launch his widely expected campaign for the Republican nomination for president in Iowa...}