\entryitemWithDescription{\hskip 0pt{}Minnesota bill legalizing recreational pot passes Senate, heads to governor's desk}{https://apnews.com/article/31a77e46389fe3ed0472ddff672cf22f}{FILE - Marijuana plants grow at a Minnesota Medical Solutions greenhouse on May 5, 2015, in Otsego, Minn. Senators in Minnesota passed a bill Saturday, May 20, 2023, that would legalize recreational marijuana for people over the age of...}

\entryitemWithDescription{\hskip 0pt{}Supreme Court Justice Ketanji Brown Jackson tells law students 'Survivor' offers helpful lessons}{https://apnews.com/article/03a47095975b90ae0e50cd4af45d0e21}{Supreme Court Associate Justice Ketanji Brown Jackson speaks at the commencement ceremony for American University\textquotesingle s Washington College of Law, Saturday, May 20, 2023, in Washington. (AP Photo/Patrick Semansky) WASHINGTON...}

\entryitemWithDescription{\hskip 0pt{}Victims of deadly Oregon highway crash were farmworkers, union says}{https://apnews.com/article/75d7ce29a08113d3030283d03f77da8b}{A damaged vehicle sits on the side of the road on Interstate 5, Northbound on Thursday, May 18, 2023, in Marion County, Ore. Two semi-trucks and a passenger van were involved in a deadly crash, which occurred near the city of Albany in an...}

\entryitemWithDescription{\hskip 0pt{}Pete Brown, co-writer of 'Sunshine of Your Love,' 'White Room' for rock group Cream, dies at 82}{https://apnews.com/article/d347bb5291cab5a8e2321b36d072cf74}{NEW YORK (AP) --- Songwriter and poet Pete Brown, who co-wrote ``Sunshine of Your Love'' and ``White Room'' for the short-lived rock supergroup Cream in the 1960s, has died. He was 82. The London-based Brown died of cancer late Friday...}

\entryitemWithDescription{\hskip 0pt{}Horse trained by Bob Baffert euthanized on track after racing injury on Preakness undercard}{https://apnews.com/article/ec9780ecd9e11e20d36deb02c26dac1c}{A track worker carries the saddle blanket of Havnameltdown away as the horse is euthanized after suffering a catastrophic leg injury during the sixth race prior to the 148th running of the Preakness Stakes horse race at Pimlico Race...}

\entryitemWithDescription{\hskip 0pt{}Shark in Florida Keys bites angler who reeled it in, sending man to hospital}{https://apnews.com/article/fa59e7baa83866ca9ee227e4e06db91c}{SUMMERLAND Key, Fla. (AP) --- A shark in the Florida Keys bit the foot of a fisherman who had reeled it in, sending the man to the hospital, the Monroe County Sheriff\textquotesingle s Office said Saturday. The 35-year-old man was fishing...}

\entryitemWithDescription{\hskip 0pt{}Television's biggest mystery: how long will pipeline for new programming be closed?}{https://apnews.com/article/df880349ffa60b77b5bcdc94d6d5e50b}{FILE - Janelle James, from left, Quinta Brunson, Lisa Ann Walter and Sheryl Lee Ralph pose in the press room with the award for best television series, musical or comedy for "Abbott Elementary" at the 80th annual Golden Globe Awards on...}

\entryitemWithDescription{\hskip 0pt{}Preakness favorite Mage gets stitches for cut above eye, good to run in Triple Crown race}{https://apnews.com/article/88787ad48b9f5bfb4f65eb2a74d23c98}{Staples are seen on the eyelid of Mage as he is groomed ahead of the Preakness Stakes horse race at Pimlico Race Course, Saturday, May 20, 2023, in Baltimore. (AP Photo/Julia Nikhinson) BALTIMORE (AP) --- Preakness favorite Mage is good...}

\entryitemWithDescription{\hskip 0pt{}DeSantis asks that judge be disqualified from Disney's free speech lawsuit}{https://apnews.com/article/ba2580a0677cfa4a9958dc828661cb88}{FILE - People visit the Magic Kingdom Park at Walt Disney World Resort in Lake Buena Vista, Fla., April 18, 2022. Ongoing strength at its theme parks and an improving streaming business propelled The Walt Disney Co. to higher profits and...}

\entryitemWithDescription{\hskip 0pt{}Jonathan Glazer rocks Cannes with a chilling Holocaust drama from a different perspective}{https://apnews.com/article/0e5665079c18a37762cc4de19ddba4a1}{Director Jonathan Glazer poses for photographers at the photo call for the film \textquotesingle The Zone of Interest\textquotesingle{} at the 76th international film festival, Cannes, southern France, Saturday, May 20, 2023. (Photo by...}

\entryitemWithDescription{\hskip 0pt{}Trans girl misses Mississippi graduation after being told to dress like boy}{https://apnews.com/article/871b5f686cf38f2de4cde8c07e2fc5b2}{JACKSON, Miss. (AP) --- A transgender girl in Mississippi is not participating in her high school graduation ceremony because school officials told her to dress like a boy and a federal judge did not block the officials\textquotesingle{}...}

\entryitemWithDescription{\hskip 0pt{}F-18 fighter jet accident at Zaragoza airbase as pilot ejects successfully}{https://apnews.com/article/da141e5bff64ce72e6a54e4bbf5cab43}{Emergency service members work in the area where an F-18 fighter jet crashed in Zaragoza, Spain, Saturday, May 20, 2023. An F-18 fighter jet crashed at an airbase in the Spanish city of Zaragoza but the pilot ejected successfully, the...}

\entryitemWithDescription{\hskip 0pt{}Bob Baffert's National Treasure wins Preakness, hours after another of his horses was euthanized}{https://apnews.com/article/b92b3f851977b7e55df9e3babb34e900}{National Treasure, right, with jockey John Velazquez, edges out Blazing Sevens, with jockey Irad Ortiz Jr., to win the148th running of the Preakness Stakes horse race at Pimlico Race Course, Saturday, May 20, 2023, in Baltimore. (AP Photo/...}