\entryitemWithDescription{\hskip 0pt{}House advances effort to censure Rashida Tlaib over her rhetoric about the Israel-Hamas war}{https://apnews.com/article/8085189047a4c40f2d44ada4604aa076}{WASHINGTON (AP) --- The House is headed for a showdown vote Wednesday on whether to punish Democratic Rep. Rashida Tlaib of Michigan --- the only Palestinian American in Congress --- for her rhetoric about the Israel-Hamas war. A vote to...}

\entryitemWithDescription{\hskip 0pt{}Tiger Woods to own and play for Florida team in TGL, his tech-infused golf league}{https://apnews.com/article/def01b4d648ed9db0dc3e38e68baebaa}{Tiger Woods couldn't be more involved with prime-time TGL unless he had built the arena. He helped develop the tech-infused golf league. He's playing in it. And now he's a team owner. Woods and his TGR Ventures and David Blitzer, the...}

\entryitemWithDescription{\hskip 0pt{}Virginia's governor declares a state of emergency as firefighters battle wildfires}{https://apnews.com/article/cb4c543bed145d4efc15b4b5c0001820}{Virginia Gov. Glenn Youngkin declared a state of emergency Tuesday as firefighters responded to two wildfires that amid dry conditions and high winds. The declaration allows Virginia to mobilize additional resources, staff and equipment...}

\entryitemWithDescription{\hskip 0pt{}Massive World War II-era blimp hangar burns in Southern California}{https://apnews.com/article/8d278fbff167b680f44c169aa708db21}{TUSTIN, Calif. (AP) --- Fire raged Tuesday in a massive World War II-era wooden hangar that was built to house military blimps based in Southern California. The Orange County Fire Authority said in a social media post that allowing the...}

\entryitemWithDescription{\hskip 0pt{}Super fog blankets New Orleans again, as damp fires and smoke close interstate after deadly crash}{https://apnews.com/article/2e17e22172dd872d1d06923f92fffdc2}{NEW ORLEANS (AP) --- Dense smoke reminiscent of last month's ``super fog'' that rolled into Louisiana has led to a deadly crash that shut down Interstate 10 in the New Orleans area early Tuesday, police said. The thoroughfare was closed...}

\entryitemWithDescription{\hskip 0pt{}Shimmering galaxies revealed in new photos by European space telescope}{https://apnews.com/article/def0bf3760856d0c99b3108f0d0d1086}{CAPE CANAVERAL, Fla. (AP) --- Scientists on Tuesday unveiled the first pictures taken by the European space telescope Euclid, a shimmering and stunning collection of galaxies too numerous to count. The photos were revealed by the European...}

\entryitemWithDescription{\hskip 0pt{}Ex-gang leader will get date for murder trial stemming from 1996 killing of Tupac Shakur}{https://apnews.com/article/bb707b9676b04aa53eb660fd0c70f412}{LAS VEGAS (AP) --- A Nevada judge set a June 3 date for the murder trial of a former Southern California street gang leader who has become the only person ever charged in the 1996 killing of hip-hop music icon Tupac Shakur in Las Vegas...}

\entryitemWithDescription{\hskip 0pt{}Exonerated `Central Park Five' member set to win council seat as New York votes in local elections}{https://apnews.com/article/0377cedcbd29f424753c9790551a85de}{Exonerated ``Central Park Five'' member Yusef Salaam is poised to win a seat Tuesday on the New York City Council, marking a stunning reversal of fortune for a political newcomer who was wrongly imprisoned as a teenager in the infamous...}

\entryitemWithDescription{\hskip 0pt{}One of Virginia's key election battlegrounds involves a candidate who endured sex scandal}{https://apnews.com/article/5db9aec5a490a3a4cc9a695c0e1b7a17}{RICHMOND, Va. (AP) --- As Democrats seek to gain control of the Virginia House of Delegates in Tuesday's election, a key race hinges on a candidate whose campaign was upended by revelations she engaged in sex acts with her husband on a...}

\entryitemWithDescription{\hskip 0pt{}With electric vehicle sales growth slowing, Stellantis Ram brand has an answer: An onboard charger}{https://apnews.com/article/ee992ad53623cee6186e8014104f7045}{DETROIT (AP) --- One of the biggest reasons people cite when saying they won't buy an electric vehicle is range anxiety, the fear of running out of juice on the road with nowhere to recharge. Stellantis' Ram brand may have an answer for...}

\entryitemWithDescription{\hskip 0pt{}Celebrities join Prince William on the Singapore green carpet for his Earthshot Prize awards}{https://apnews.com/article/de62be03fe7f1b64f7fdef0ff0ee5d10}{SINGAPORE (AP) --- Celebrities joined Britain's Prince William to walk the ``green carpet'' in Singapore on Tuesday for the third Earthshot Prize awards ceremony, where five winners ranging from solar-powered dryers to combat food waste...}

\entryitemWithDescription{\hskip 0pt{}Tennis legend Serena Williams honored as `fashion icon' at fashion industry's big awards night}{https://apnews.com/article/517a35780c1f17d05c2969a098d77943}{NEW YORK (AP) --- Tennis legend Serena Williams told a glittery fashion industry audience how fashion became a favored mode of expression as she grew up in the public eye, with the tennis court serving as her runway. ``I knew when I was a...}

\entryitemWithDescription{\hskip 0pt{}Nevada high court postpones NFL appeal in Jon Gruden emails lawsuit until January}{https://apnews.com/article/b01af1c56df2e64007ff18df54ec8075}{LAS VEGAS (AP) --- The Nevada Supreme Court has pushed back to Jan. 10 the date for oral arguments in a contract interference and conspiracy lawsuit filed against the NFL by former Las Vegas Raiders coach Jon Gruden. Postponement of the...}