\entryitemWithDescription{\hskip 0pt{}Messi heads to Miami as latest big name to raise soccer's profile in US}{https://apnews.com/article/0cef67f624c3d5094f1ed1f41ee17178}{FILE - Argentina\textquotesingle s Lionel Messi heads the ball next to France\textquotesingle s Kingsley Coman, right, during the World Cup final soccer match between Argentina and France at the Lusail Stadium in Lusail, Qatar, Sunday...}

\entryitemWithDescription{\hskip 0pt{}Richard Snyder, `warrior-king' of publishing who presided over rise of Simon \& Schuster, dead at 90}{https://apnews.com/article/0fde95c4fb744f3da1c2c1faaae1de28}{Former Princess Diane von Furstenburg posing with of Simon \& Schuster executive Richard Snyder on Feb. 28, 1977 celebrating the publication of her new book on beauty. Snyder, a visionary and imperious executive at Simon \& Schuster who...}

\entryitemWithDescription{\hskip 0pt{}The Iron Sheik, charismatic former pro wrestling villain and Twitter personality, dies at 81}{https://apnews.com/article/d06f6c348b084ef37bd2a45fedaaf792}{FILE - The Iron Sheik arrives at the ESPY Awards in Los Angeles on July 15, 2009. The Iron Sheik, born Hossein Khosrow Ali Vaziri, died Wednesday, June 7, 2023, at age 81. (AP Photo/Matt Sayles, File) The Iron Sheik, a former pro wrestler...}

\entryitemWithDescription{\hskip 0pt{}Against all odds, Mexico's endangered vaquita porpoise is hanging on in Gulf of California}{https://apnews.com/article/67630ec1f760b944c05d015b8e76c069}{In this photo courtesy of the Sea Shepherd Conservation Society, a vaquita marina swims in the Biosphere Reserve of the Upper Gulf of California and Colorado River Delta, in the Sea of Cortez, Mexico, May 20, 2023. Experts on the...}

\entryitemWithDescription{\hskip 0pt{}Rory McIlroy, a strong anti-Saudi voice, now feels like 'sacrificial lamb' amid LIV Golf deal}{https://apnews.com/article/35ab51eee07a8def8dd05e7068843272}{Rory McIlroy speaks to the media about the deal merging the PGA Tour and European tour with Saudi Arabia\textquotesingle s golf interests at the Canadian Open golf tournament in Toronto on Wednesday, June 7, 2023. (Nathan Denette/The...}

\entryitemWithDescription{\hskip 0pt{}'Vanderpump' star Lala Kent on Scandoval, ex Randall Emmett and building 'a freaking empire'}{https://apnews.com/article/c5c0a41e76149d091ef5f94854a20f3a}{Lala Kent, a cast member of the Bravo reality series "Vanderpump Rules," poses for a portrait at her office in Los Angeles on Tuesday, May 30, 2023. (AP Photo/Chris Pizzello) Lala Kent would like to thank her ``Vanderpump Rules'' co-stars...}

\entryitemWithDescription{\hskip 0pt{}George Winston, million-selling pianist known for his melodic style, dead at age 73}{https://apnews.com/article/69b395ec7601fa052892b3ddb287c5d1}{FILE - George Winston makes an adjustment on his piano during a sound check before his performance at the Cerritos Center for the Performing Arts in Cerritos, Calif., on Nov. 4, 2004. (AP Photo/Reed Saxon, File) NEW YORK (AP) --- George...}

\entryitemWithDescription{\hskip 0pt{}Owner of funeral homes accused of spraying insecticide at cops, assaulting media at Jan. 6 riot}{https://apnews.com/article/73cd2e36ecc2cc6b82ff7ae8f33848c0}{FILE - Peter Moloney, of Moloney Family Funeral Homes in Lake Ronkonkoma, N.Y., rides his Harley Davidson hearse from the Tombstone Hearse Co. of Alum Bank, Pa., in New York, May 24, 2007. Maloney was arrested Wednesday, June 7, 2023, on...}

\entryitemWithDescription{\hskip 0pt{}Greek island temple complex reveals 'countless' offerings left by ancient worshippers}{https://apnews.com/article/238f05ae4944f5ed2f5356386f076136}{In this undated photo released by the Greek Culture Ministry, on Wednesday, June 7, 2023, clay figurines of boys and girls found during an excavation on the Greek island of Kythonos. Archaeologists excavating a hilltop sanctuary on the...}

\entryitemWithDescription{\hskip 0pt{}Kilauea, one of the world's most active volcanoes, begins erupting after 3-month pause}{https://apnews.com/article/c656045be12586e502e4e7a162f38bdb}{In this photo provided by the National Park Service lava spews from the Kilauea volcano in Hawaii, Wednesday, June 7, 2023. (Janice Wei/National Park Service via AP) HONOLULU (AP) --- Kilauea, one of the most active volcanoes in the...}

\entryitemWithDescription{\hskip 0pt{}Ex-Trump aide testifies before federal grand jury in Florida investigation of Mar-a-Lago documents}{https://apnews.com/article/5d346c69dfb4f9bc07e6f8adc6aa13bc}{Former President Donald Trump visits with campaign volunteers at the Grimes Community Complex Park, Thursday, June 1, 2023, in Des Moines, Iowa. (AP Photo/Charlie Neibergall) WASHINGTON (AP) --- A former top aide to Donald Trump appeared...}

\entryitemWithDescription{\hskip 0pt{}New version of 'The Wiz' will be led by Wayne Brady and Alan Mingo Jr. sharing the title role}{https://apnews.com/article/1850a097a5a4462bbb4517878ddf7c4b}{FILE - Wayne Brady attends the Paramount 2022 Upfront party in New York on May 18, 2022. Brady and Alan Mingo Jr. will star as the Wiz in San Francisco from Jan. 16-Feb. 11 at the Golden Gate Theatre, and in Los Angeles from Feb. 13...}

\entryitemWithDescription{\hskip 0pt{}Platonic co-parenting offers an alternate model for family building}{https://apnews.com/article/0a9dabe9629fcc1686546b30b3c2d4a4}{This May 2020 photo shows Tracy Smith in Tulsa, Okla. Smith has been using the mating site Modamily to find a platonic co-parent. (Jenny White Photography via AP) NEW YORK (AP) --- Nick Farrow wanted what a lot of people do: a child, and...}