\entryitemWithDescription{\hskip 0pt{}Airbnb is banning the use of indoor security cameras in the platform's listings worldwide}{https://apnews.com/article/3f49191f73dc2599ba0d4e10f26f0226}{NEW YORK (AP) --- Airbnb said Monday that it's banning the use of indoor security cameras in listings on its site around the world by the end of next month. The San Francisco-based online rental platform said it is seeking to ``simplify''...}

\entryitemWithDescription{\hskip 0pt{}Brother of LSU guard Flau'jae Johnson arrested after SEC Tournament championship fight}{https://apnews.com/article/3ed0b550373820e9cb415457626749c0}{GREENVILLE, S.C. (AP) --- The brother of LSU guard Flau'jae Johnson was arrested and charged with assault and battery and disorderly conduct by the Greenville Police Department for his role in a fight after his sister was shoved to the...}

\entryitemWithDescription{\hskip 0pt{}`Oppenheimer' crew keeps it low key, other winners revel at Vanity Fair's Oscar after-party}{https://apnews.com/article/358904e3eff95380e79e4c6312980deb}{LOS ANGELES (AP) --- Christopher Nolan stood as staid and nonchalant as ever as crowds surrounded him and music pulsed. His celebration was limited to casually holding a best directing Oscar, his first, and one of seven on the night for...}

\entryitemWithDescription{\hskip 0pt{}Behind the Scenes: What you didn't see at the 2024 Oscars}{https://apnews.com/article/dd6e39858f57a053e73f3deff4a75b10}{LOS ANGELES (AP) --- There is a whole other show that happens offscreen at the Oscars that the home audience doesn't see on television. Here's what The Associated Press saw that the cameras did not capture. THE OSCARS START AT\ldots{}...}

\entryitemWithDescription{\hskip 0pt{}Vanessa Hudgens is pregnant, revealing baby bump at Oscars}{https://apnews.com/article/a33289a96f8184321428cd1663e9866e}{LOS ANGELES (AP) --- Vanessa Hudgens opened the Oscars red carpet pre-show with news of her own: She's expecting. The 35-year-old actor-singer turned to the side, revealing a baby bump under her strapless, long-sleeved black gown on...}

\entryitemWithDescription{\hskip 0pt{}OSCARS PHOTOS: See candid moments from the red carpet}{https://apnews.com/article/42aa222e179b61853626f81226e224d2}{LOS ANGELES (AP) --- The red carpet was back this year at the 96th Academy Awards --- after last year's champagne-colored diversion. A dizzying parade of stars posed in dazzling outfits and waved to myriad photographers and fans. The...}

\entryitemWithDescription{\hskip 0pt{}America Ferrera stuns in sparkly Barbie pink, Rita Moreno waves in statement black on Oscars carpet}{https://apnews.com/article/b227addbde67217bac556ef4cf730cee}{NEW YORK (AP) --- America Ferrera bid a fond awards season farewell to ``Barbie'' on the Oscars red carpet Sunday in a stunning, sparkly Atelier Versace gown in the film's signature pink, while Rita Moreno wore a huge smile and a...}

\entryitemWithDescription{\hskip 0pt{}New Jersey infant killed, parents injured in apparent attack by family dog, police say}{https://apnews.com/article/0b450af6cdb26c4886f81aff4036d30b}{WOODBRIDGE, N.J. (AP) --- An infant was killed and the child's parents injured in an apparent attack by a dog at a New Jersey home over the weekend, authorities said. Middlesex County prosecutors and Woodbridge police said officers...}

\entryitemWithDescription{\hskip 0pt{}`Kung Fu Panda 4' opens No. 1, while `Dune: Part Two' stays strong}{https://apnews.com/article/6a19e8307885dbbc68b7d90db25c7146}{LOS ANGELES (AP) --- As Universal Pictures prepared for a big night at the Academy Awards with ``Oppenheimer,'' the studio also celebrated the No. 1 debut of ``Kung Fu Panda 4,'' which collected \$58.3 million in domestic theaters over...}

\entryitemWithDescription{\hskip 0pt{}2 National Guard soldiers, 1 Border Patrol agent killed in Texas helicopter crash are identified}{https://apnews.com/article/4ef0071f7ab806f93f4f7e1038aa10f5}{LA GRULLA, Texas (AP) --- A National Guard soldier from New York who was seriously injured in the crash of a helicopter flying over the U.S.-Mexico border remained hospitalized Sunday while authorities released the names of the two...}

\entryitemWithDescription{\hskip 0pt{}70-foot sperm whale beached off Florida's Gulf Coast}{https://apnews.com/article/9295ccbf4cb786568f2735b0a3527c71}{VENICE, Fla. (AP) --- Authorities were working to assist a beached sperm whale that is stranded on a sandbar off Florida's Gulf Coast on Sunday morning. The Venice Police Department said in a Facebook post that the 70-foot (21-meter...}

\entryitemWithDescription{\hskip 0pt{}Princess of Wales appears in first photo since surgery amid wild speculation of her whereabouts}{https://apnews.com/article/ca91acf667c87c6c70a7838347d6d4fb}{LONDON (AP) --- The first photo of Kate, the Princess of Wales, since her abdominal surgery nearly two months ago was issued Sunday along with a statement thanking the public for its support. The photo of her in a chair surrounded by her...}

\entryitemWithDescription{\hskip 0pt{}These Barbies partied with Chanel the night before the Oscars}{https://apnews.com/article/22b759292df4dd7b213172f48c1c4321}{BEVERLY HILLS, Calif. (AP) --- The night before the Oscars isn't a time to rest in Hollywood. For quite a few nominees, including ``Barbie'' star Margot Robbie, it meant a stop at the historic Beverly Hills Hotel for the 15th annual...}