\entryitemWithDescription{\hskip 0pt{}Oklahoma court OK's abortion to preserve mother's life}{https://apnews.com/article/7fd43143fa0580460e09a9796ec30a82}{FILE - Abortion-rights supporters rally at the State Capitol on May 3, 2022, in Oklahoma City. A divided Oklahoma Supreme Court on Tuesday, March 21, 2023, overturned a portion of the state's near total ban on abortion, ruling women have...}

\entryitemWithDescription{\hskip 0pt{}Willis Reed, leader on Knicks' 2 title teams, dies at 80}{https://apnews.com/article/7a86a451386ef4a2d65372d7919d930d}{FILE - New York Knicks Hall-of-Famer Willis Reed responds to questions during an interview before an NBA basketball game between the Knicks and the Milwaukee Bucks, Friday, April 5, 2013, in New York. Willis Reed, who dramatically emerged...}

\entryitemWithDescription{\hskip 0pt{}Review: John Wick gets even more stylish in fourth episode}{https://apnews.com/article/d6350c7f8ceda029dd033bb60998f5c8}{This image released by Lionsgate shows Keanu Reeves as John Wick in a scene from "John Wick 4." (Murray Close/Lionsgate via AP) A trip to Paris should be on everyone's bucket list, even John Wick. The Eiffel Tower, the Arc de Triomphe...}

\entryitemWithDescription{\hskip 0pt{}Man gets 4 years for attacking police at Jan. 6 Capitol riot}{https://apnews.com/article/3a20eadafe19c70c3bb36e20de105013}{FILE - Rioters wave flags on the West Front of the U.S. Capitol in Washington on Jan. 6, 2021. Federal prosecutors are employing an unusual strategy to prove leaders of the far-right Proud Boys extremist group orchestrated a violent plot...}

\entryitemWithDescription{\hskip 0pt{}Def Leppard drummer recovering from attack outside hotel}{https://apnews.com/article/074028cc3498d239cfccfc172b48f28a}{FILE - Rick Allen, of Def Leppard, arrives at the Rock \& Roll Hall of Fame induction ceremony at the Barclays Center on Friday, March 29, 2019, in New York. Allen says he recovering from an attack earlier this month, March 2023, outside...}

\entryitemWithDescription{\hskip 0pt{}College hoops staffs specialize to meet roster, NIL demands}{https://apnews.com/article/3dd9f6dc92525993ac7a8d89a0e4a569}{FILE - Houston coach Kelvin reacts to a foul call during the second half of an NCAA college basketball game against Central Florida Saturday, Dec. 31, 2022, in Houston. The way Houston's coach sees it, the people running programs had...}

\entryitemWithDescription{\hskip 0pt{}Fox, Dominion face off over airing of false election claims}{https://apnews.com/article/9f0b4ec94a19fa68c1205864fef277c5}{FILE - A headline about President Donald Trump is displayed outside Fox News studios in New York on Nov. 28, 2018. (AP Photo/Mark Lennihan, File) WILMINGTON, Del. (AP) --- Fox News and a voting machine company that claims the conservative...}

\entryitemWithDescription{\hskip 0pt{}Superbug Candida auris now reported in more than half of states}{https://apnews.com/article/bd20721b4233afd5e3c41432db54ea5f}{FILE - This undated photo made available by the Centers for Disease Control and Prevention shows a strain of Candida auris cultured in a petri dish at a CDC laboratory. In a CDC paper published by the Annals of Internal Medicine on...}

\entryitemWithDescription{\hskip 0pt{}Video shows Irvo Otieno pinned to floor before his death}{https://apnews.com/article/d652f6ae2360ac9ba33a53941246f8c1}{Caroline Ouko, mother of Irvo Otieno, holds a portrait of her son with attorney Ben Crump, left, her older son, Leon Ochieng and attorney Mark Krudys at the Dinwiddie Courthouse in Dinwiddie, Va., on Thursday, March 16, 2023. She said...}

\entryitemWithDescription{\hskip 0pt{}'Winnie the Pooh' slasher film pulled from Hong Kong cinemas}{https://apnews.com/article/613ba02ab3cd453635f851bf1fbb071e}{An image from the film "Winnie the Pooh: Blood and Honey." Public screenings in Hong Kong of a slasher film that features Winnie the Pooh have been scrapped, sparking discussions over increasing censorship in the city. Film distributor...}

\entryitemWithDescription{\hskip 0pt{}Google's artificially intelligent 'Bard' set for next stage}{https://apnews.com/article/5517734a1e135ee5d38b968840663236}{FILE - The Google logo is displayed at their offices on Nov. 1, 2018, in Granary Square, in London. Google announced Tuesday, March 21, 2023, it\textquotesingle s allowing more people to interact with ``Bard,'' the artificially...}

\entryitemWithDescription{\hskip 0pt{}Virginia teacher shot by 6-year-old: 'I thought I had died'}{https://apnews.com/article/ebba31cb2d9064e9475c49f7fe7452df}{This image provided by NBC News, Abby Zwerner, a first-grade teacher who was shot and wounded by a 6-year-old student in Virginia, speaks to Savannah Guthrie on NBC's Today Show, which aired Tuesday March 21, 2023. (NBC News via AP...}

\entryitemWithDescription{\hskip 0pt{}US speeds up Abrams tank delivery to Ukraine war zone}{https://apnews.com/article/94294a9c1e1acc50098afa440bcb4d40}{FILE - A soldier walks past a line of M1 Abrams tanks, Nov. 29, 2016, at Fort Carson in Colorado Springs, Colo. U.S. officials say the Pentagon is speeding up its delivery of Abrams tanks to Ukraine, opting to send a refurbished older...}