\entryitemWithDescription{\hskip 0pt{}Pence will take subpoena fight to Supreme Court if necessary}{https://apnews.com/article/f7078fb20d0bf2097e28b1198f989a77}{Former Vice President Mike Pence, middle right, talks with a young supporter after speaking about his beliefs on parenting rights, Wednesday, Feb. 15, 2023, in Minneapolis. (AP Photo/Abbie Parr) The FBI searched former Vice President Mike...}

\entryitemWithDescription{\hskip 0pt{}Hollywood sex symbol Raquel Welch dies at 82}{https://apnews.com/article/3f6ba36da0bd11edb2973c219cee77e8}{FILE - Raquel Welch appears at the Los Angeles premiere of "How to Be a Latin Lover" on April 26, 2017. Welch, whose emergence from the sea in a skimpy, furry bikini in the film ``One Million Years B.C.'' would propel her to international...}

\entryitemWithDescription{\hskip 0pt{}Agent homed in on Alex Murdaugh inconsistencies after deaths}{https://apnews.com/article/4eb76da4acb636416e19b905689e87e7}{Evidence is shown during Alex Murdaugh\textquotesingle s trial for murder at the Colleton County Courthouse in Walterboro, S.C., on Wednesday, Feb. 15, 2023. The 54-year-old attorney is standing trial on two counts of murder in the...}

\entryitemWithDescription{\hskip 0pt{}Michigan State students' training kicked in during shooting}{https://apnews.com/article/f7ec39881d79038727e2a4b65a3d64eb}{Current and former Michigan State University students rally at the capitol in Lansing, Mich., Wednesday, Feb. 15, 2023. Alexandria Verner, Brian Fraser and Arielle Anderson were killed and other students remain in critical condition after...}

\entryitemWithDescription{\hskip 0pt{}Alaska carbon plan: Boost state coffers without cutting oil}{https://apnews.com/article/c4b94af7f1149172fe06fd4f590e52d8}{People rally in support of renewable energy policies, such as strengthening a renewable energy fund, across from the Alaska Capitol on Friday, Feb. 3, 2023, in Juneau, Alaska. Some environmentalists are skeptical of legislation proposed...}

\entryitemWithDescription{\hskip 0pt{}Panel backs moving opioid antidote Narcan over the counter}{https://apnews.com/article/38ae986009788501bc418fe108593632}{FILE - Attendees practice administering Narcan during an overdose education and Narcan training class at the Onala Recovery Center on the South Shore of Pittsburgh on Monday, Dec. 13, 2021. U.S. health advisers are weighing whether the...}

\entryitemWithDescription{\hskip 0pt{}Skinny robot documents forces eroding Doomsday Glacier}{https://apnews.com/article/ae2b053b434c4dd3767bbec2442d874a}{A robot nicknamed Icefin operates under the sea ice near McMurdo Station in Antarctica in 2020. The pencil-shaped robot is giving scientists their first look at the forces eating away at the Thwaites glacier. Two studies published...}

\entryitemWithDescription{\hskip 0pt{}Rio's first all-female samba school prepares defiant parade}{https://apnews.com/article/b18fd0e84ba3d00d32d8f260e8ec9724}{A member of the Turma da Paz de Madureira, or TPM, samba school plays a drum during a rehearsal in preparation for Rio\textquotesingle s Carnival parade, in Rio de Janeiro, Brazil, Saturday, Feb. 4, 2023. TPM is the first all-female samba...}

\entryitemWithDescription{\hskip 0pt{}At 25, Backyard Bird Count shows power of citizen science}{https://apnews.com/article/8aff018dd0e36c12f9539698d95758d9}{This image provided by Macaulay Library/Cornell Lab of Ornithology shows two girls watching birds through a window with binoculars, bird lists and cameras in Elm Grove, Louisiana, during the Great Backyard Bird Count in February 2022...}

\entryitemWithDescription{\hskip 0pt{}Retail sales jump as Americans defy inflation and rate hikes}{https://apnews.com/article/8a11d7eaec2ede5d45dbc937aaeaba7d}{Shoppers pass an large L.L. Bean boot displayed outside an L.L. Bean store in Pittsburgh on Monday, Jan. 30, 2023. On Wednesday, the Commerce Department releases U.S. retail sales data for January. (AP Photo/Gene J. Puskar) WASHINGTON...}

\entryitemWithDescription{\hskip 0pt{}Hamilton on FIA rule: 'Nothing will stop me from speaking'}{https://apnews.com/article/b8b1307b526d606d18e90e090e41ea0f}{FILE - Mercedes driver Lewis Hamilton of Britain listens to a question during a press conferencein Sao Paulo, Brazil, on Nov. 9, 2022. Seven-time Formula One champion Lewis Hamilton insisted he will not be silenced by offseason rules that...}

\entryitemWithDescription{\hskip 0pt{}Pastors' view: Sermons written by ChatGPT will have no soul}{https://apnews.com/article/65822bf1c46de7630d3441e9ff4ff41a}{Rabbi Joshua Franklin stands inside the sanctuary at the Jewish Center of the Hamptons in East Hampton, New York on Feb. 10, 2023. Franklin expermented writing a sermon for his congregation using artificial intelligence software Chat GPT...}

\entryitemWithDescription{\hskip 0pt{}China threatens US entities over downing of balloon}{https://apnews.com/article/a9edd8db532f6cda9bace43b94051e7a}{FILE - In this photo provided by Chad Fish, the remnants of a large balloon drift above the Atlantic Ocean, just off the coast of South Carolina, with a fighter jet and its contrail seen below it, Feb. 4, 2023. A missile fired on Feb. 5...}