\entryitemWithDescription{\hskip 0pt{}Barbie doll honoring Cherokee Nation leader Wilma Mankiller is met with mixed emotions}{https://apnews.com/article/060faaf1d0cc13e401e79497c14b65cc}{OKLAHOMA CITY (AP) --- An iconic chief of the Cherokee Nation, Wilma Mankiller, inspired countless Native American children as a powerful but humble leader who expanded early education and rural healthcare. Her reach is now broadening...}

\entryitemWithDescription{\hskip 0pt{}Kiss say farewell to live touring, become first US band to go virtual and become digital avatars}{https://apnews.com/article/37a8ae9905099343c7b41654b2344d0c}{On Saturday night, Kiss closed out the final performance of their ``The End of the Road'' farewell tour at New York City's famed Madison Square Garden. But as dedicated fans surely know --- they were never going to call it quits. Not...}

\entryitemWithDescription{\hskip 0pt{}No. 8 Alabama knocks off No. 1 Georgia 27-24 for SEC title. Both teams await postseason fate}{https://apnews.com/article/2cc4fa17be895cf367a1cd1479f45dff}{ATLANTA (AP) --- After handing Georgia its first loss in nearly two years, Alabama mixed a raucous celebration of its latest Southeastern Conference championship with a whole lot of lobbying for a College Football Playoff spot that no one...}

\entryitemWithDescription{\hskip 0pt{}Italian officials secure 12th Century leaning tower in Bologna to prevent collapse}{https://apnews.com/article/9ad6d6160f8cdced7a7c94123007e2ef}{MILAN (AP) --- Officials have secured the area around one of two 12th Century towers that have become symbolic of the northern city of Bologna, fearing its leaning could lead to collapse. The city on Friday announced 4.3 million euros (\$...}

\entryitemWithDescription{\hskip 0pt{}Ronaldo walks off to chants of `Messi! Messi!' as his team loses 3-0 in Riyadh derby}{https://apnews.com/article/e262460b0b11c7973bdd325f6e3a78ac}{RIYADH, Saudi Arabia (AP) --- Cristiano Ronaldo walked off the field with the gleeful chants of ``Messi! Messi!'' ringing in his ears from delighted Al-Hilal fans who had just watched their Saudi Pro League team beat the Portugal...}

\entryitemWithDescription{\hskip 0pt{}Protester critically injured after setting self on fire outside Israeli consulate in Atlanta}{https://apnews.com/article/8f17dd72592f86797a45cda9b60605a5}{ATLANTA (AP) --- A protester was in critical condition Friday after setting themself on fire outside the Israeli consulate in Atlanta, authorities said. A security guard who tried to intervene was also injured. A Palestinian flag found at...}

\entryitemWithDescription{\hskip 0pt{}Philadelphia votes to ban ski masks to decrease crime. Opponents worry it'll unfairly target some}{https://apnews.com/article/4f2213f3551f85dfb94ecb7e7228580c}{PHILADELPHIA (AP) --- Philadelphia City Council passed legislation to ban ski masks in some public spaces, a measure supporters say will increase public safety amid high violent crime, but opponents argue it will unfairly target people...}

\entryitemWithDescription{\hskip 0pt{}NOT REAL NEWS: A look at what didn't happen this week}{https://apnews.com/article/99ccb985d8e06b6cc7cd21fba1689a1c}{A roundup of some of the most popular but completely untrue stories and visuals of the week. None of these are legit, even though they were shared widely on social media. The Associated Press checked them out. Here are the facts: \_\_\_...}

\entryitemWithDescription{\hskip 0pt{}Young humpback whale leaps out of Seattle bay, dazzling onlookers}{https://apnews.com/article/8f0aa5af1b3a94052276f0bcbee7ab51}{SEATTLE (AP) --- A humpback whale visiting the waters off Seattle dazzled onlookers Thursday morning with several breaches in the bay just beyond the city's downtown area. The whale has been spotted for the last three days swimming around...}

\entryitemWithDescription{\hskip 0pt{}Sen. Rand Paul performed Heimlich maneuver on choking Sen. Joni Ernst during GOP lunch}{https://apnews.com/article/6cdde719bef9bb82d96903b5b390a16b}{WASHINGTON (AP) --- Sen. Joni Ernst, a Republican from Iowa, was choking on food during a luncheon Thursday when fellow Republican Sen. Rand Paul of Kentucky performed the Heimlich maneuver on her. The incident occurred during a closed...}

\entryitemWithDescription{\hskip 0pt{}`Killers of the Flower Moon' named best film of 2023 by New York film critics}{https://apnews.com/article/3620e2ea34519d9adf139adcbffc68fe}{NEW YORK (AP) --- Martin Scorsese's ``Killers of the Flower Moon'' has been named the best film of the year by the New York Film Critics Circle. It's the third time that Scorsese has been given the best film award from his hometown's...}

\entryitemWithDescription{\hskip 0pt{}Review: In concert film `Renaissance,' Beyoncé offers glimpse into personal life during world tour}{https://apnews.com/article/f615ffd3bd7c452d6aaa7e75df20c428}{LOS ANGELES (AP) --- In Beyoncé's concert film, she describes her recent Renaissance World Tour as being run like a machine: From lighting to set design, the superstar had a hand in everything production-related to ensure her stadium tour...}

\entryitemWithDescription{\hskip 0pt{}Musk uses expletive to tell audience he doesn't care about advertisers that fled X over hate speech}{https://apnews.com/article/f68bf51e756cce822a691b3badb2050a}{NEW YORK (AP) --- Billionaire Elon Musk said Wednesday that advertisers who have halted spending on his social media platform X in response to antisemitic and other hateful material are engaging in ``blackmail'' and, using a profanity...}