\entryitemWithDescription{\hskip 0pt{}Europe reaches deal for price cap on Russian diesel}{https://apnews.com/article/7f84f7fec9c025ee27fe870366a5837a}{FILE - Cars and trucks drive on a highway in Frankfurt, Germany, Jan. 27, 2023. European Union governments tentatively agreed Friday Feb. 3, 2023, to set a \$100-per-barrel price cap on sales of Russian diesel to coincide with an EU...}

\entryitemWithDescription{\hskip 0pt{}Licenses suspended for 2 fired EMTs in Tyre Nichols death}{https://apnews.com/article/28c478a5583c7aca61b1ea48a2fb41de}{Protesters march Saturday, Jan. 28, 2023, in Memphis, Tenn., over the death of Tyre Nichols, who died after being beaten by Memphis police. (AP Photo/Gerald Herbert) A Tennessee board has suspended the emergency management technician...}

\entryitemWithDescription{\hskip 0pt{}Authorities: 2 arrested in California shooting that killed 6}{https://apnews.com/article/2fcdbf58bc5839e0406bcea0fba028e2}{FILE - In this frame grab from video provided by the Tulare Count Sheriff\textquotesingle s Office, Sheriff Mike Boudreaux speaks to the media near the scene of a fatal shooting in Visalia, Calif., on Jan. 16, 2023. Boudreaux said Friday...}

\entryitemWithDescription{\hskip 0pt{}Why is R\\&B music more explicit than ever? It's complicated.}{https://apnews.com/article/e52ac28dde0944077db9e8c5bea25807}{This combination of photos show music artists, top row from left, Ashanti, Babyface, Chloe Bailey, Yung Bleu, Mary J. Blige, and Lucky Daye, bottom row from left, Robert Glasper, Muni Long, Rico Love, PJ Morton, T-Pain and Tank. (AP...}

\entryitemWithDescription{\hskip 0pt{}New rules would limit sugar in school meals for first time}{https://apnews.com/article/30963aeb9f56aae0ee743c26f1117f19}{FILE - Second-grade students select their meals during lunch break in the cafeteria at an elementary school in Scottsdale, Ariz., Dec. 12, 2022. On Friday, Feb. 3, 2023, U.S. agriculture officials proposed new nutrition standards for...}

\entryitemWithDescription{\hskip 0pt{}An unexpected job surge confounds the Fed's economic models}{https://apnews.com/article/4bbfab5f0c89ec0c1d870a3eef5e56c5}{A construction worker pauses at a building site, Thursday, Jan. 26, 2023, in Boston. America\textquotesingle s employers added a robust 517,000 jobs in January, a surprisingly strong gain in the face of the Federal Reserve\textquotesingle...}

\entryitemWithDescription{\hskip 0pt{}Boyhood collides with masculinity in Oscar-nominated 'Close'}{https://apnews.com/article/bd77b4b4418eec7023af64564ac80369}{This image released by A24 shows Eden Dambrine, foreground right, and Gustav De Waele in a scene from "Close." (A24 via AP) NEW YORK (AP) --- When Lukas Dhont was 12, a camera was thrust into his hands. For Dhont, who would come out as...}

\entryitemWithDescription{\hskip 0pt{}US may lift protections for Yellowstone, Glacier grizzlies}{https://apnews.com/article/ff09eccea665e580248c44692d46115d}{FILE - In this July 6, 2011, file photo, a grizzly bear roams near Beaver Lake in Yellowstone National Park, Wyo. The Biden administration on Friday, Feb.3, 2023, took a first step toward ending federal protections for grizzly bears in...}

\entryitemWithDescription{\hskip 0pt{}Advocates: Black cops not exempt from anti-Black policing}{https://apnews.com/article/c36c88bdca39d801eee9bd247fcc0c71}{This combo of images provided by the Memphis Police Department shows, from top row from left, officers Tadarrius Bean, Demetrius Haley, Emmitt Martin III, bottom row, from left, Desmond Mills, Jr. and Justin Smith. The five former Memphis...}

\entryitemWithDescription{\hskip 0pt{}Google, Apple, Amazon give investors reason to fret}{https://apnews.com/article/6790beec01dd04fbc8c97c9d6bff8974}{FILE- In this Feb. 14, 2018, file photo the logo for Alphabet appears on a screen at the Nasdaq MarketSite in New York. Alphabet Inc. reports financial earnings on Thursday, Feb. 2, 2023. (AP Photo/Richard Drew, File) Wall Street has its...}

\entryitemWithDescription{\hskip 0pt{}Q\\&A: Shania Twain talks rebuilding confidence with new album}{https://apnews.com/article/9577110d73cc7dead0629dba6eb2790a}{Shania Twain poses for a portrait at Ticketmaster in West Hollywood, Calif., on on Jan 18, 2023, to promote her new album "Queen of Me." (Photo by Rebecca Cabage/Invision/AP) Grammy winner Shania Twain faced down fear of self-criticism to...}

\entryitemWithDescription{\hskip 0pt{}Street honoring KKK leader renamed after student-led effort}{https://apnews.com/article/e78dd23dfa9036771a98957da933edea}{MALVERNE, N.Y. (AP) --- A street that honored a leader of the Ku Klux Klan in New York has a new name after a yearslong campaign led by high school students. The village board of Malverne, on Long Island, voted last year to rename Lindner...}

\entryitemWithDescription{\hskip 0pt{}In Mexico, worry that Maya Train will destroy jungle}{https://apnews.com/article/65808b5a88d76c639a540385da073b4d}{Omar Hernandez walks with his daughters on land he sold for the construction of a section of the Maya Train, near the Calakmul Biosphere Reserve in the Yucatan Peninsula of Mexico on Wednesday, Jan. 11, 2023. Hernandez hopes to sell...}