\entryitemWithDescription{\hskip 0pt{}Ryan Reynolds, Snoop Dogg in mix to buy Ottawa's NHL team?}{https://apnews.com/article/cd39ff14d5006da05d9840c2e93e5354}{Rapper Snoop Dogg arrives at the premiere of the FX docuseries "Dear Mama," Tuesday, April 18, 2023, at The Ted Mann Theater in Los Angeles. The series explores the legacies of rapper Tupac Shakur and his mother Afeni. (AP Photo/Chris...}

\entryitemWithDescription{\hskip 0pt{}At least 6 dead after dust storm causes crashes in Illinois}{https://apnews.com/article/14cf5174d293741f94a17eed9d8f4a2d}{Smoldering wreckage is seen after a crash involving at least 20 vehicles shut down a highway in Illinois, Monday, May 1, 2023. Illinois State Police say a windstorm that kicked up clouds of dust in south-central Illinois led to numerous...}

\entryitemWithDescription{\hskip 0pt{}CNN says Trump to appear in New Hampshire town hall}{https://apnews.com/article/b78dcb61df21b93e2abfaba0c561e72b}{Former President Donald Trump speaks at a campaign event Thursday, April 27, 2023, in Manchester, N.H. (AP Photo/Charles Krupa) NEW YORK (AP) --- As president, Donald Trump frequently derided CNN as ``fake news.'' Now that he...}

\entryitemWithDescription{\hskip 0pt{}Bill would allow 14-year-olds to serve alcohol in Wisconsin}{https://apnews.com/article/31e0c73786d5489c626250a279760420}{FILE - Patrons sit in a hotel bar in Eau Claire, Wis., May 1, 2019. Fourteen-year-olds in Wisconsin could serve alcohol to seated customers in bars and restaurants under a bill circulated for cosponsors Monday, May 1, 2023, by a pair of...}

\entryitemWithDescription{\hskip 0pt{}Gwyneth Paltrow won't recoup attorney fees in ski crash suit}{https://apnews.com/article/38ee255a616afac432baaa37fba01c8c}{FILE - Gwyneth Paltrow reacts to the verdict in her trial on March 30, 2023, in Park City, Utah. In a judgement published on Saturday, April 29, 2023, the court affirmed the jury\textquotesingle s verdict finding Paltrow not at fault for...}

\entryitemWithDescription{\hskip 0pt{}Democratic Sen. Cardin of Maryland retiring after 3 terms}{https://apnews.com/article/e275c8bfa30dbe42dfc40c32fea4cd4b}{FILE - Sen. Ben Cardin, D-Md., attends a news conference at the Capitol in Washington, Thursday, April 27, 2023. Cardin of Maryland is expected to announce his retirement Monday, May 1, after serving three terms, opening a rare vacancy in...}

\entryitemWithDescription{\hskip 0pt{}Pas de chat: Lagerfeld's cat Choupette won't be at Met Gala}{https://apnews.com/article/7a5e1194c06b3d0bd2a0ac9956dd7404}{FILE - German designer Karl Lagerfeld joins models, from left, American Cindy Crawford, Canadian Linda Evangelista and Claudia Schiffer of Germany after the presentation of his 1996 spring-summer ready-to-wear fashion collection for...}

\entryitemWithDescription{\hskip 0pt{}'Cheers' bar, 'Tonight Show' set among TV history at auction}{https://apnews.com/article/c51ffa8c7915d5d0fe53a92327229a3e}{James Comisar holds a pair of shoes once used by actor Barbara Eden in the television show, "I Dream of Jeannie", Thursday, April 27, 2023, in Irving, Texas. A dizzying number of props, sets, and costumes from television shows beloved by...}

\entryitemWithDescription{\hskip 0pt{}Pilots at American, Southwest, ratchet up strike threats}{https://apnews.com/article/943aff357add4717489db17fe12df7b0}{FILE - The American Airlines logo on top of the American Airlines Center in Dallas, Texas, is pictured on Dec. 19, 2017. Pilots at American Airlines are voting to authorize a strike. That doesn\textquotesingle t mean they\textquotesingle...}

\entryitemWithDescription{\hskip 0pt{}DeSantis board approves suing Disney in latest tug-of-war}{https://apnews.com/article/8e650a78aec6d882921f61947b5ce31f}{FILE - A statue of Walt Disney and Micky Mouse stands in front of the Cinderella Castle at the Magic Kingdom at Walt Disney World in Lake Buena Vista, Fla., Jan. 9, 2019. Florida Gov. Ron DeSantis' oversight board of Disney World has...}

\entryitemWithDescription{\hskip 0pt{}Barbie unveils Anna May Wong doll for AAPI Heritage Month}{https://apnews.com/article/313733970f9acb4505c29d53e8cf5c3b}{This image released by Mattel shows a Barbie doll in the image of Asian American Hollywood trailblazer Anna May Wong, part of their Inspiring Women Series. The doll is dressed in a frock inspired by Wong\textquotesingle s appearance in...}

\entryitemWithDescription{\hskip 0pt{}Aerosmith announces farewell tour starting in September}{https://apnews.com/article/677eefa072c57f19875e254264fda04e}{FILE - Tom Hamilton, from left, Steven Tyler, Joe Perry, John Douglas and Brad Whitford of Aerosmith, perform on Sept. 8, 2022, at Fenway Park in Boston. Aerosmith will be touring a city near you for the last time to celebrate their 50...}

\entryitemWithDescription{\hskip 0pt{}Mississippi River crests at Davenport, testing barriers}{https://apnews.com/article/c5f8b1f2e9e0b83e46123470e21dd5d7}{A business sits in floodwaters from the nearby Mississippi River, Monday, May 1, 2023, in Buffalo, Iowa. (AP Photo/Charlie Neibergall) BUFFALO, Iowa (AP) --- Dale O'Donnell bought his small brick home only 100 yards or so from the...}