\entryitemWithDescription{\hskip 0pt{}Source: Lawyer invited to testify before Trump grand jury}{https://apnews.com/article/5eaeae46af595ba012272cc10085ee8f}{Former President Donald J. Trump watches the NCAA Wrestling Championships, Saturday, March 18, 2023, in Tulsa, Okla. (AP Photo/Sue Ogrocki) WASHINGTON (AP) --- A lawyer who previously advised Michael Cohen, the key government witness in...}

\entryitemWithDescription{\hskip 0pt{}DA leading Trump case says rhetoric won't intimidate office}{https://apnews.com/article/4d15a073b0500d4cd47e7371f45d27d7}{FILE - Manhattan District Attorney Alvin Bragg participates in a news conference in New York, Tuesday, Feb. 7, 2023. Bragg is standing firm against former President Donald Trump's increasingly hostile rhetoric, telling his staff that the...}

\entryitemWithDescription{\hskip 0pt{}Miami Beach sets spring break curfew after 2 fatal shootings}{https://apnews.com/article/67a77b4b8954ace2f29d9f19fbe1272b}{Crowds gather at Ocean Drive and 8th during spring break on Saturday, March 18, 2023, in Miami Beach, Fla. Miami Beach officials imposed a curfew beginning Sunday night, March 19, after two fatal shootings and rowdy, chaotic crowds that...}

\entryitemWithDescription{\hskip 0pt{}Xavier beats Pitt 84-73, reaches 1st Sweet 16 since 2017}{https://apnews.com/article/65b0f41f9dbe4543d4c2bf7859777232}{Xavier forward Jack Nunge scores against Pittsburgh forward Guillermo Diaz Graham during the second half of a second-round college basketball game in the NCAA Tournament on Sunday, March 19, 2023, in Greensboro, N.C. (AP Photo/Chris...}

\entryitemWithDescription{\hskip 0pt{}California to ask voters to approve new mental health beds}{https://apnews.com/article/973f909040691479c40be2a4aa14b5dd}{California Gov. Gavin Newsom discusses his plans to build 1,200 small homes across the state to reduce homelessness, during the first of a four-day tour of the state in Sacramento Calif., on Thursday, March 16, 2023. (AP Photo/Rich...}

\entryitemWithDescription{\hskip 0pt{}UBS to buy Credit Suisse for nearly \$3.25B to calm turmoil}{https://apnews.com/article/1a06bc96cbca9be4fbfd20a8f008ab8f}{Axel Lehmann, Chairman Credit Suisse, speaks during a press conference in Bern, Switzerland, Sunday March 19, 2023. Banking giant UBS is acquiring its smaller rival Credit Suisse in an effort to avoid further market-shaking turmoil in...}

\entryitemWithDescription{\hskip 0pt{}New law allows anti-abortion monument at Arkansas Capitol}{https://apnews.com/article/9efa40bd10d3f3a1c6a9c70ed4986ae5}{FILE - Then-Arkansas Gov.-elect Sarah Huckabee Sanders answers a question during a Republican Governors Association conference on Nov. 16, 2022, in Orlando, Fla. Gov. Huckabee Sanders has signed a new law that will allow an anti-abortion...}

\entryitemWithDescription{\hskip 0pt{}GOP donor faces trial on charges of sex trafficking minors}{https://apnews.com/article/db1e3ac444fe3c289adddb4b924b9092}{FILE - This booking photo released by Sherburne County Jail shows Anton Lazzaro. The formerly well-connected Republican donor goes on trial in Minnesota on Tuesday, March 21, 2023, on federal charges of sex trafficking minors. (Sherburne...}

\entryitemWithDescription{\hskip 0pt{}Pakistani police file terrorism charges against ex-PM Khan}{https://apnews.com/article/925f30a4b63bf828b7a5ee90ec71a8b7}{Supporters of former Prime Minister Imran Khan gather outside of the Khan house in Lahore, Pakistan, Sunday, March 19, 2023. Police in the Pakistani capital filed charges Sunday against former Prime Minister Imran Khan and 17 of his aides...}

\entryitemWithDescription{\hskip 0pt{}Republican bills push cash bail, subvert Democratic changes}{https://apnews.com/article/348362a8484828500e01a545ec58e28f}{FILE - The Palm Beach County Main Detention Center is pictured on June 4, 2021, in West Palm Beach, Fla. Republican lawmakers in Florida and other states are pushing to increase the use of cash bail and pretrial detention. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}How to shop for new insurance if you lose Medicaid coverage}{https://apnews.com/article/ff32b273b892186de86aafb3f42222de}{FILE - A sign points visitors toward the financial services department at a hospital, Friday, Jan. 24, 2014. Medicaid coverage will end for millions of Americans in 2023, and that pushes many into unfamiliar territory: the health...}

\entryitemWithDescription{\hskip 0pt{}Nations approve key UN science report on climate change}{https://apnews.com/article/e3469f69980fe949eb21b4bc25cb018f}{FILE - People walk through floodwaters after heavy rainfall in Hadeja, Nigeria, Sept 19, 2022. Publication of a major new United Nations report on climate change is being held up by a battle between rich and developing countries over...}

\entryitemWithDescription{\hskip 0pt{}Higher cancer rates found in military pilots, ground crews}{https://apnews.com/article/298f70c4f7581fe5e08637fcb61abc71}{This image provided by Betty Seaman shows Navy A-6 Intruder pilot Jim Seaman. Navy Capt. Jim Seaman died of lung cancer at the age of 61. His widow Betty Seaman has been part of a large group of aviators and their surviving spouses who...}