\entryitemWithDescription{\hskip 0pt{}Texas Attorney General Paxton sues to block gun ban at the sprawling State Fair of Texas}{https://apnews.com/article/7eedbf9ee55ea9c624e0db4e71dc0e4d}{DALLAS (AP) --- Texas Attorney General Ken Paxton filed a lawsuit Thursday seeking to block a ban on firearms at the State Fair of Texas, one of the state's biggest annual celebrations. Fair organizers earlier this month announced a ban...}

\entryitemWithDescription{\hskip 0pt{}NASA record holder can relate to astronauts stuck in space. He was, too}{https://apnews.com/article/91629ab00e5ccb5ede28898b876aaad8}{NASA's record-holding astronaut is urging his two stuck-in-space colleagues to stay positive and ``keep up the good work.'' Frank Rubio knows firsthand about unexpectedly long spaceflights. His own visit to the International Space Station...}

\entryitemWithDescription{\hskip 0pt{}Criminal charges weighed against a man after a country music star stops show over an alleged assault}{https://apnews.com/article/605aba47486b4dc5b314384e85cd97ae}{PUEBLO, Colo. (AP) --- Criminal charges are being considered for a man suspected of hitting a woman during a concert at the Colorado State Fair, authorities said Thursday, in an incident that prompted country music star Scotty McCreery to...}

\entryitemWithDescription{\hskip 0pt{}A 4-year-old broke a 3,500-year-old jar at an Israeli museum. Forgiven, he's invited back}{https://apnews.com/article/264506ceead5a73833a959c51ba90e75}{HAIFA, Israel (AP) --- A 4-year-old boy who accidentally broke a rare 3,500-year-old jar in an Israeli museum has been forgiven and even invited back, as curators hope to turn the disaster into a teachable moment. Alex Geller, the boy's...}

\entryitemWithDescription{\hskip 0pt{}Former New Jersey Gov. Chris Christie will teach a course on running for office at Yale}{https://apnews.com/article/667fa5d955fdef4d98478a765f75e945}{NEW HAVEN, Conn. (AP) --- Former New Jersey governor and unsuccessful Republican presidential candidate Chris Christie will teach a course on running for office at Yale University this semester. The weekly seminar taught by Christie is...}

\entryitemWithDescription{\hskip 0pt{}High winds, possibly from a tornado, derail 43 train cars in North Dakota}{https://apnews.com/article/ce8ed6f6d466a4b2a8f872821d6c67b8}{STEELE, N.D. (AP) --- Strong winds knocked nearly four dozen train cars off a track in North Dakota, part of a storm system that spurred reports of five tornadoes across the Dakotas. BNSF Railway spokesperson Kendall Sloan said a train...}

\entryitemWithDescription{\hskip 0pt{}Children's book to blame for fire inside car, North Carolina officials say}{https://apnews.com/article/7b06d4ead481a90d54b8642b9720504e}{BURKE COUNTY, N.C. (AP) --- North Carolina officials determined the cause of a fire inside a car in Burke County was a children's book. A child's car seat was set ablaze when a ``button battery'' in a children's book caught fire after...}

\entryitemWithDescription{\hskip 0pt{}A strong wave likely capsized a Viking replica ship off Norway, police say}{https://apnews.com/article/bdfaa7e42a9cf4003efe354a2fcdf3a1}{COPENHAGEN, Denmark (AP) --- A strong wave was likely responsible for the capsizing of a Viking ship replica earlier this week off Norway's coast that killed a U.S. citizen, police said Thursday, describing it as a ``tragic accident''...}

\entryitemWithDescription{\hskip 0pt{}Jaguar tells owners of older I-Pace electric SUVs to park them outdoors due to battery fire risk}{https://apnews.com/article/0eb914d204d8ef1d1c82b5847c91f648}{DETROIT (AP) --- Jaguar is telling owners of about 3,000 electric SUVs to park them outdoors and away from structures due to the risk of battery fires. The British automaker is recalling I-Pace SUVs from the 2019 model year, but has not...}

\entryitemWithDescription{\hskip 0pt{}A sinkhole swallows an SUV in South Korea, injuring 2 people}{https://apnews.com/article/14889642a3c33a6415ef9f7e7a258c49}{SEOUL, South Korea (AP) --- A sinkhole suddenly opened and swallowed an SUV in South Korea's capital on Thursday, injuring the two occupants, emergency workers said. Photos from the scene showed a white sport utility vehicle engulfed in...}

\entryitemWithDescription{\hskip 0pt{}Newborn rattlesnakes at a Colorado `mega den' are making their live debut}{https://apnews.com/article/34763e0416d849aaa9f818423b9da98f}{CHEYENNE, Wyo. (AP) --- A ``mega den'' of hundreds of rattlesnakes in Colorado is getting even bigger now that late summer is here and babies are being born. Thanks to livestream video, scientists studying the den on a craggy hillside in...}

\entryitemWithDescription{\hskip 0pt{}AP PHOTOS: Olympic highlights from the Opening Ceremony of the Paralympic Games in Paris}{https://apnews.com/article/301f298d0ed3b97d00af3b732c3a4509}{Paris (AP) --- A gallery of highlights from the Opening Ceremony of the Paralympics captured by AP photographers at the Paris Games. \_\_\_ AP Paralympics: https://apnews.com/hub/paralympic-games Follow AP visual journalism: AP Images...}

\entryitemWithDescription{\hskip 0pt{}A second elephant calf in 2 weeks is born at a California zoo}{https://apnews.com/article/2d4a0d3ae783479cefb03f5428d53ecb}{FRESNO, Calif. (AP) --- The second elephant calf in two weeks has been born at a California zoo. African elephant Amahle gave birth early Monday morning, according to the Fresno Chaffee Zoo. The event came 10 days after Amahle's mother...}