


\ipart{Developers}
\ichapter{Hacker News}
\entryitemTwoLinks{Ask HN: How did Sam Altman fail upward so well?}{https://news.ycombinator.com/item?id=34471720}{https://news.ycombinator.com/item?id=34471720}

\entryitemTwoLinks{ECC RAM should be a human right}{https://news.ycombinator.com/item?id=34470900}{https://dmitrybrant.com/2023/01/21/ecc-ram-should-be-a-human-right}

\entryitemTwoLinks{Official Warning: Zero3K}{https://news.ycombinator.com/item?id=34470767}{https://reactos.org/forum/viewtopic.php?t=21714}

\entryitemTwoLinks{Is Apple checking images we view in the Finder?}{https://news.ycombinator.com/item?id=34469204}{https://eclecticlight.co/2023/01/18/is-apple-checking-images-we-view-in-the-finder/}

\entryitemTwoLinks{Vikunja – Open-source, self-hostable to-do app}{https://news.ycombinator.com/item?id=34469078}{https://vikunja.io/}

\entryitemTwoLinks{Buy hi-resolution satellite images of any place on earth}{https://news.ycombinator.com/item?id=34468644}{https://www.skyfi.com/pricing}

\entryitemTwoLinks{Quiet, ultrathin AirJet solid state active cooling chips could replace fans}{https://news.ycombinator.com/item?id=34467937}{https://www.cnx-software.com/2023/01/20/quiet-ultrathin-airjet-solid-state-active-cooling-could-replace-fans/}

\entryitemTwoLinks{What to do when you 've ruined your life}{https://news.ycombinator.com/item?id=34467931}{https://www.bigfeels.club/public-articles/what-to-do-when-youve-ruined-your-life}

\entryitemTwoLinks{Capital One axes 1k tech roles}{https://news.ycombinator.com/item?id=34467928}{https://www.theregister.com/2023/01/20/capital\_one/}

\entryitemTwoLinks{Amazon Smile Gets a Frown}{https://news.ycombinator.com/item?id=34467636}{https://seths.blog/2023/01/amazon-smile-gets-a-frown/}

\entryitemTwoLinks{An unexpected benefit of unit tests}{https://news.ycombinator.com/item?id=34467523}{https://matthewc.dev/musings/unit-tests/}

\entryitemTwoLinks{My husband was right about DVDs}{https://news.ycombinator.com/item?id=34467490}{https://slate.com/technology/2023/01/streaming-libraries-dvds-blu-rays.html}

\entryitemTwoLinks{Direct Memory Access computing machine RP2040}{https://news.ycombinator.com/item?id=34466985}{https://people.ece.cornell.edu/land/courses/ece4760/RP2040/C\_SDK\_DMA\_machine/DMA\_machine\_rp2040.html}

\entryitemTwoLinks{US Pilot Shot Down Four Soviet MiGs in 30 minutes – A secret for 50 years}{https://news.ycombinator.com/item?id=34466934}{https://www.cnn.com/2023/01/20/asia/korean-war-fighter-pilot-soviet-shootdown-intl-hnk-ml/index.html}

\entryitemTwoLinks{The Website Obesity Crisis (2015)}{https://news.ycombinator.com/item?id=34466910}{https://idlewords.com/talks/website\_obesity.htm}

\entryitemTwoLinks{Area 120, Google's in-house incubator, severely impacted by Alphabet mass layoff}{https://news.ycombinator.com/item?id=34466766}{https://techcrunch.com/2023/01/20/area-120-googles-in-house-incubator-severely-impacted-by-alphabet-mass-layoffs/}

\entryitemTwoLinks{A Dump of the Raw Stadia Controller BT Firmware}{https://news.ycombinator.com/item?id=34466747}{https://github.com/Scyne/stadiaRawBtFw}

\entryitemTwoLinks{VSCode Swift 1.0}{https://news.ycombinator.com/item?id=34466693}{https://forums.swift.org/t/vscode-swift-v1-0-0/62668}

\entryitemTwoLinks{Microsoft is checking everyone's bags for unsupported Office installs}{https://news.ycombinator.com/item?id=34465941}{https://www.theregister.com/2023/01/21/microsoft\_office\_count\_update/}

\entryitemTwoLinks{Make up a guy}{https://news.ycombinator.com/item?id=34465008}{https://www.antipope.org/charlie/blog-static/2023/01/make-up-a-guy.html}
\ichapter{Phoronix}
\entryitemGeneric{\hskip 0pt{}helloSystem 0.8 Released As macOS Inspired FreeBSD Desktop OS}{https://www.phoronix.com/news/helloSystem-0.8-Released}

\entryitemGeneric{\hskip 0pt{}AMDGPU Linux 6.3 Addition To Help With Optimized Buffer Placement}{https://www.phoronix.com/news/Linux-6.3-AMDGPU-New-uAPI}

\entryitemGeneric{\hskip 0pt{}NVIDIA Contributes linux\_dmabuf v4 Feedback Support To XWayland}{https://www.phoronix.com/news/XWayland-linux\_dmabuf-v4}

\entryitemGeneric{\hskip 0pt{}IBM Looks To Squeeze Support For Future Power "Dense Math" CPUs Into GCC 13}{https://www.phoronix.com/news/IBM-Future-Power-DM-GCC-13}

\entryitemGeneric{\hskip 0pt{}DualShock 4 Controller Support Being Dropped From HID-Sony In Favor Of New Driver}{https://www.phoronix.com/news/HID-Sony-Dropping-DS4}

\entryitemGeneric{\hskip 0pt{}More Improvements Come To KDE Plasma Wayland, KF6 Development Enters Next Phase}{https://www.phoronix.com/news/KDE-KF6-Next-Phase}

\entryitemGeneric{\hskip 0pt{}OpenZFS 2.1.8 Released With Linux 6.1~6.2 Compatibility Updates, Bug Fixes}{https://www.phoronix.com/news/OpenZFS-2.1.8-Released}

\entryitemGeneric{\hskip 0pt{}Wine 8.0-rc5 Released With Just Nine Bugs Fixed}{https://www.phoronix.com/news/Wine-8.0-rc5-Released}

\entryitemGeneric{\hskip 0pt{}RADV Receives Patches To Help With Less Stuttering For Zink}{https://www.phoronix.com/news/RADV-Full-DS3-Zink-Less-Stutter}\ichapter{GitHub}
\entryitemWithDescription{\hskip 0pt{}DovAmir/awesome-design-patterns}{https://github.com/DovAmir/awesome-design-patterns}{A curated list of software and architecture related design patterns.\\
Language: Unknown\\
Stars: 25713\\
Forks: 2108}

\entryitemWithDescription{\hskip 0pt{}Dimillian/IceCubesApp}{https://github.com/Dimillian/IceCubesApp}{A SwiftUI Mastodon client\\
Language: Swift\\
Stars: 1046\\
Forks: 70}

\entryitemWithDescription{\hskip 0pt{}psf/black}{https://github.com/psf/black}{The uncompromising Python code formatter\\
Language: Python\\
Stars: 30987\\
Forks: 1982}

\entryitemWithDescription{\hskip 0pt{}python/mypy}{https://github.com/python/mypy}{Optional static typing for Python\\
Language: Python\\
Stars: 14648\\
Forks: 2415}
\ichapter{Dribbble}
\entryitemGeneric{\hskip 0pt{}Flatfile Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20204156}

\entryitemGeneric{\hskip 0pt{}L.A. Public Library 150th Anniversary Poster}{https://dribbble.com/shots/20420912}

\entryitemGeneric{\hskip 0pt{}Apres — Home page web design}{https://dribbble.com/shots/20394039}

\entryitemGeneric{\hskip 0pt{}Crypto Trading - Animation}{https://dribbble.com/shots/20415217}

\entryitemGeneric{\hskip 0pt{}Midland Appliance}{https://dribbble.com/shots/20425768}

\entryitemGeneric{\hskip 0pt{}Happiness App Redesign}{https://dribbble.com/shots/20407073}

\entryitemGeneric{\hskip 0pt{}SafePal Branding}{https://dribbble.com/shots/20421178}

\entryitemGeneric{\hskip 0pt{}Swych Website Development}{https://dribbble.com/shots/20394918}

\entryitemGeneric{\hskip 0pt{}Website design for Marketing Agency}{https://dribbble.com/shots/20428609}

\entryitemGeneric{\hskip 0pt{}Rootcube Logo Design and Branding}{https://dribbble.com/shots/20407630}

\entryitemGeneric{\hskip 0pt{}The Smart Suitcase App - Ziggo}{https://dribbble.com/shots/20395008}

\entryitemGeneric{\hskip 0pt{}Studies Website Design: business landing web page, site designer}{https://dribbble.com/shots/20247071}

\entryitemGeneric{\hskip 0pt{}Proemion Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20246067}

\entryitemGeneric{\hskip 0pt{}Cocoon Brand}{https://dribbble.com/shots/20335245}

\entryitemGeneric{\hskip 0pt{}Sticker Illustrations}{https://dribbble.com/shots/20263965}

\entryitemGeneric{\hskip 0pt{}Assetly Branding, visual identity, corporate brand design}{https://dribbble.com/shots/20247110}

\entryitemGeneric{\hskip 0pt{}Grow // Website}{https://dribbble.com/shots/20394194}

\entryitemGeneric{\hskip 0pt{}UI Design}{https://dribbble.com/shots/20402856}

\entryitemGeneric{\hskip 0pt{}Savoree - Social Dining App}{https://dribbble.com/shots/20399523}

\entryitemGeneric{\hskip 0pt{}Rebranding Malbon, an Insight into my Process 4.}{https://dribbble.com/shots/20404914}

\entryitemGeneric{\hskip 0pt{}Bankex Brand Identity}{https://dribbble.com/shots/20395458}

\entryitemGeneric{\hskip 0pt{}Payment mobile app design}{https://dribbble.com/shots/20398966}

\entryitemGeneric{\hskip 0pt{}[P] 1 → N}{https://dribbble.com/shots/20352105}

\entryitemGeneric{\hskip 0pt{}Seven Summits}{https://dribbble.com/shots/20439111}


\ipart{Developers~~~~(zh-Hans)}
\ichapter{Solidot}
\entryitemGeneric{\hskip 0pt{}GitHub 将停止支持 Subversion}{https://www.solidot.org/story?sid=73939}

\entryitemGeneric{\hskip 0pt{}微生物群在室友家人之间的共享}{https://www.solidot.org/story?sid=73938}

\entryitemGeneric{\hskip 0pt{}Google 联合创始人就 ChatGPT 召开会议讨论}{https://www.solidot.org/story?sid=73937}

\entryitemGeneric{\hskip 0pt{}CNET 暂停 AI 辅助撰写文章}{https://www.solidot.org/story?sid=73936}

\entryitemGeneric{\hskip 0pt{}暗网市场 Solaris 被竞争对手劫持}{https://www.solidot.org/story?sid=73935}

\entryitemGeneric{\hskip 0pt{}苹果公开 Lisa 操作系统源代码}{https://www.solidot.org/story?sid=73934}

\entryitemGeneric{\hskip 0pt{}Google 将裁员 1.2 万人}{https://www.solidot.org/story?sid=73933}

\entryitemGeneric{\hskip 0pt{}因夜晚亮度增加肉眼能看到的星星在减少}{https://www.solidot.org/story?sid=73932}

\entryitemGeneric{\hskip 0pt{}社交网络上虚假信息传播的关键原因是其奖励机制}{https://www.solidot.org/story?sid=73931}

\entryitemGeneric{\hskip 0pt{}研究发现在电视上打广告的药品治疗价值低}{https://www.solidot.org/story?sid=73930}

\entryitemGeneric{\hskip 0pt{}美国国务院淘汰 Times New Roman 字体}{https://www.solidot.org/story?sid=73929}

\entryitemGeneric{\hskip 0pt{}当 ChatGPT 被列为论文署名作者}{https://www.solidot.org/story?sid=73928}

\entryitemGeneric{\hskip 0pt{}波士顿动力演示双足机器人抓抛物品的能力}{https://www.solidot.org/story?sid=73927}

\entryitemGeneric{\hskip 0pt{}Twitter 拍卖总部办公用品 }{https://www.solidot.org/story?sid=73926}

\entryitemGeneric{\hskip 0pt{}微软宣布裁员一万人}{https://www.solidot.org/story?sid=73925}

\entryitemGeneric{\hskip 0pt{}维基百科启用新界面}{https://www.solidot.org/story?sid=73924}

\entryitemGeneric{\hskip 0pt{}亚马逊关闭 AmazonSmile 慈善项目}{https://www.solidot.org/story?sid=73923}\ichapter{V2EX}
\entryitemGeneric{\hskip 0pt{}[酷工作] 谷歌等大厂裁员，长远来看对我等升斗小民有什么影响？}{https://www.v2ex.com/t/910221}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 广东这边的 4837 的出国 QoS 是有啥问题？}{https://www.v2ex.com/t/910220}

\entryitemGeneric{\hskip 0pt{}[问与答] 我的 github 账号被封了怎么办}{https://www.v2ex.com/t/910219}

\entryitemGeneric{\hskip 0pt{}[Apple] 发现一个很有趣的 Mac AirDrop 对"只限联系人"的判定与 iOS 不同}{https://www.v2ex.com/t/910218}

\entryitemGeneric{\hskip 0pt{}[问与答] Mac 版的 office 可以用 KMS 激活吗？}{https://www.v2ex.com/t/910217}

\entryitemGeneric{\hskip 0pt{}[DNS] 8.8.8.8 抽风了？}{https://www.v2ex.com/t/910216}

\entryitemGeneric{\hskip 0pt{}[随想] 一个很有趣的发现}{https://www.v2ex.com/t/910215}

\entryitemGeneric{\hskip 0pt{}[Safari] safari 不会用不会用备用 dns 解析吗}{https://www.v2ex.com/t/910214}

\entryitemGeneric{\hskip 0pt{}[问与答] Win11 下好用的日语输入法？}{https://www.v2ex.com/t/910213}

\entryitemGeneric{\hskip 0pt{}[加密货币] Coinbase 的两步验证完全忘记了，现在人工审核需要我提供英文版的身份证明}{https://www.v2ex.com/t/910212}

\entryitemGeneric{\hskip 0pt{}[生活] 猛虎归山辞旧岁，玉兔携福迎新春}{https://www.v2ex.com/t/910211}

\entryitemGeneric{\hskip 0pt{}[问与答] 老哥们给推荐点有趣的爱好吧！}{https://www.v2ex.com/t/910210}

\entryitemGeneric{\hskip 0pt{}[生活] 跨年快乐}{https://www.v2ex.com/t/910209}

\entryitemGeneric{\hskip 0pt{}[问与答] 新年好！请教，如何提高 Alist 资源获取速度}{https://www.v2ex.com/t/910208}

\entryitemGeneric{\hskip 0pt{}[问与答] 浏览器里面的字体有时候很奇怪，是 windows 的问题吗？}{https://www.v2ex.com/t/910207}

\entryitemGeneric{\hskip 0pt{}[程序员] 迅游加速器那种口令是怎么生成的？}{https://www.v2ex.com/t/910206}

\entryitemGeneric{\hskip 0pt{}[路由器] Intel 226 仍然有断流现象}{https://www.v2ex.com/t/910205}

\entryitemGeneric{\hskip 0pt{}[问与答] 2023 请大家帮我推荐一些 mac 软件/技巧/效率 订阅源}{https://www.v2ex.com/t/910203}

\entryitemGeneric{\hskip 0pt{}[天黑以后] 20230121 午夜俱乐部}{https://www.v2ex.com/t/910202}

\entryitemGeneric{\hskip 0pt{}[Apple] M2 Mac Mini 256G 有实锤说会阉割读写速度吗？}{https://www.v2ex.com/t/910201}

\entryitemGeneric{\hskip 0pt{}[MacBook Pro] M1 Pro 2021 被砸了，维修咨询。}{https://www.v2ex.com/t/910200}

\entryitemGeneric{\hskip 0pt{}[NAS] 好用的私有云相册部署求推荐}{https://www.v2ex.com/t/910199}

\entryitemGeneric{\hskip 0pt{}[分享创造] 人手一个导航站 devbase.fyi，专注开发者服务}{https://www.v2ex.com/t/910198}

\entryitemGeneric{\hskip 0pt{}[问与答] 以前地方台春晚不是除夕晚上播吗？为什么今年没有了，还是我记错了？}{https://www.v2ex.com/t/910197}

\entryitemGeneric{\hskip 0pt{}[Docker] docker hub 自动构建收费了？}{https://www.v2ex.com/t/910196}

\entryitemGeneric{\hskip 0pt{}[生活] 可怕的古老节日禁忌}{https://www.v2ex.com/t/910195}

\entryitemGeneric{\hskip 0pt{}[生活] 又是一个夜班。}{https://www.v2ex.com/t/910194}

\entryitemGeneric{\hskip 0pt{}[Apple] 大年三十忍不住吐槽下 Apple}{https://www.v2ex.com/t/910193}

\entryitemGeneric{\hskip 0pt{}[程序员] 由于年终奖和涨薪打骨折准备年后跳槽 总结了一下今年都干了什么}{https://www.v2ex.com/t/910192}

\entryitemGeneric{\hskip 0pt{}[Intel] 12/13 代 i7/i9 CPU 大概会比 M1 Pro 强多少？}{https://www.v2ex.com/t/910191}

\entryitemGeneric{\hskip 0pt{}[生活] 没人告诉我除夕夜外卖关门导致我要饿肚子一晚}{https://www.v2ex.com/t/910190}

\entryitemGeneric{\hskip 0pt{}[硬件] 移动硬盘摔了几次，现在经常读不出来}{https://www.v2ex.com/t/910189}

\entryitemGeneric{\hskip 0pt{}[路由器] 小米路由器怎么了}{https://www.v2ex.com/t/910188}

\entryitemGeneric{\hskip 0pt{}[酷工作] 阿里云日志大数据团队，负责阿里集团百 PB 级日志基础设施及阿里云发展最快速的产品-SLS（日志服务）2024 暑期实习生招聘开始啦}{https://www.v2ex.com/t/910186}

\entryitemGeneric{\hskip 0pt{}[程序员] www 域名前缀过时了吗？你需要知道的一切}{https://www.v2ex.com/t/910185}

\entryitemGeneric{\hskip 0pt{}[问与答] 请问港股证券开户哪家门槛低？}{https://www.v2ex.com/t/910184}

\entryitemGeneric{\hskip 0pt{}[macOS] Ventura 从睡眠中苏醒不过来，一直黑屏，怎么办？}{https://www.v2ex.com/t/910182}

\entryitemGeneric{\hskip 0pt{}[Apple] Macbook 唤醒是不是和 HDMI 也有关系啊？}{https://www.v2ex.com/t/910181}

\entryitemGeneric{\hskip 0pt{}[硬件] 求帮忙评判下这个装机配置 https://diy.m.jd.com/?/\#/my/detail?t=1674296193538\&skuIds=100040185491,100040431267,100014959068,1000456276}{https://www.v2ex.com/t/910179}

\entryitemGeneric{\hskip 0pt{}[问与答] 虽然春晚不好看，但是求 春晚 4K HDR 高刷的播放入口或者直播源}{https://www.v2ex.com/t/910178}

\entryitemGeneric{\hskip 0pt{}[问与答] 有没有您值得分享的程序员特色拜年祝词分享啊}{https://www.v2ex.com/t/910177}

\entryitemGeneric{\hskip 0pt{}[问与答] 好几年没看春晚了，今年也不打算看，你们看吗}{https://www.v2ex.com/t/910176}

\entryitemGeneric{\hskip 0pt{}[Android] 有没有办法修改 Android，让所有软件都不能读取/sdcard（/storage/emulated/0）?，包括 adb}{https://www.v2ex.com/t/910174}

\entryitemGeneric{\hskip 0pt{}[问与答] 10 年老车目前油耗 13。高速油耗 8。这个开起来要注意什么会省油一些呀？}{https://www.v2ex.com/t/910173}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 问下大家， IPTV 好用吗，有没有什么限制？}{https://www.v2ex.com/t/910172}

\entryitemGeneric{\hskip 0pt{}[iPhone] 面容 id 经常很慢或者失败，而且 facetime 的拟我表情也经常失败。}{https://www.v2ex.com/t/910170}

\entryitemGeneric{\hskip 0pt{}[分享创造] 红包封面又续了 1000，七彩祥云兔}{https://www.v2ex.com/t/910169}

\entryitemGeneric{\hskip 0pt{}[程序员] 有什么 iOS Safari 上不会弹窗申请运动传感器权限的接口可以实现监听摇一摇事件的功能？}{https://www.v2ex.com/t/910167}

\entryitemGeneric{\hskip 0pt{}[OpenWrt] iMac 上通过 pd 或者 vmware 安装群晖、openwrt 做 nas 如何}{https://www.v2ex.com/t/910165}

\entryitemGeneric{\hskip 0pt{}[NAS] 存储空间已损毁，还有救？}{https://www.v2ex.com/t/910164}


\ipart{Generic News}
\ichapter{AP News}
\entryitemWithDescription{\hskip 0pt{}Walmart shooting victim's mom: Gunman threatened daughter}{https://apnews.com/article/552a1b2fce5a5c75acebee597c0666a5}{An image of Ronald Ray Mosley II, 25, is displayed on a monitor during a press conference, Friday afternoon, Jan. 20, 2023, related to the ongoing investigation of a shooting at the West Side Walmart in Evansville, Ind. Police identified...}

\entryitemWithDescription{\hskip 0pt{}Top Biden aide Ron Klain expected to soon leave White House}{https://apnews.com/article/859543dcbbcbe3e2ef987e88f7b4ff34}{FILE - White House chief of staff Ron Klain walks to the South Lawn of the White House to attend an event celebrating the confirmation of Judge Ketanji Brown Jackson as the first Black woman to reach the Supreme Court in Washington, April...}

\entryitemWithDescription{\hskip 0pt{}Sundance doc looks into Brett Kavanaugh investigation}{https://apnews.com/article/312b5e1d318094f005aae4bf41f9d38a}{FILE - Supreme Court Associate Justice Brett Kavanaugh watches as President Donald Trump arrives to give his State of the Union address to a joint session on Congress at the Capitol in Washington, on Feb. 5, 2019. A new documentary looks...}

\entryitemWithDescription{\hskip 0pt{}Brazil's army chief fired in aftermath of capital uprising}{https://apnews.com/article/42151a9c0ea511391b990a9527754c1e}{An agent walks past the head of a statue depicting the Greek goddess Themis, outside the Brazilian Supreme Court building that was damaged by supporters of Brazil\textquotesingle s former President Jair Bolsonaro, in Brasilia, Brazil...}

\entryitemWithDescription{\hskip 0pt{}The AP Interview: Yellen says debt standoff risks `calamity'}{https://apnews.com/article/0f7f0d85ed38353940a18cd262de8b09}{In this image taken from a video, Treasury Secretary Janet Yellen speaks during an interview with The Associated Press on Saturday, Jan. 21, 2023, in Dakar, Senegal. (AP Photo/Yesica Fisch) DAKAR, Senegal (AP) --- U.S. Treasury Secretary...}

\entryitemWithDescription{\hskip 0pt{}Venezuela frees former spy chief who defied Nicolás Maduro}{https://apnews.com/article/8e1c141d769aef41b2309e9a46d25349}{FILE - In this April 26, 2017 photo, former Venezuelan Interior Minister Miguel Rodriguez Torres poses for a photo during an interview at his office in Caracas, Venezuela. On Saturday, Jan. 21, 2023, Venezuela\textquotesingle s government...}

\entryitemWithDescription{\hskip 0pt{}Gyms that survived pandemic steadily get back in shape}{https://apnews.com/article/6624e5c1c4b8981d1539b258a470d383}{Fuel Training Studio owners Julie Bokat, left, and Jeanne Carter watch a fitness class inside their gym, Thursday, Jan. 19, 2023, in Newburyport, Mass. Gyms and fitness studios were among the hardest hit businesses during the pandemic...}

\entryitemWithDescription{\hskip 0pt{}Brazil's right-wing movement persists without Bolsonaro}{https://apnews.com/article/8d7e202b93b6cba7196c4baba32b6452}{FILE - A supporter of Brazilian President Jair Bolsonaro salutes while singing the nation\textquotesingle s anthem outside a military base during a protest against his reelection defeat in Sao Paulo, Brazil, Nov. 3, 2022. The capital...}

\entryitemWithDescription{\hskip 0pt{}Big waves to deliver storied Hawaii surf contest The Eddie}{https://apnews.com/article/691d0c11ab910bde4f51679178135b44}{FILE - Jamie Mitchell, right, and Ross Clarke-Jones, both of Australia, surf in the Eddie Aikau big-wave surfing contest in Waimea Bay near Haliewa, Hawaii on Feb. 25, 2016. One of the world\textquotesingle s most prestigious and storied...}

\entryitemWithDescription{\hskip 0pt{}GOP investigations of Biden to test Chairman Comer's power}{https://apnews.com/article/d68267048aa4f42d244130e81d3e9c30}{FILE - Rep. James Comer, R-Ky., talks to reporters as he walks to the House chamber, on Capitol Hill in Washington, Jan. 12, 2023. (AP Photo/Jose Luis Magana, File) WASHINGTON (AP) --- In early 2017, freshman Rep. James Comer found...}

\entryitemWithDescription{\hskip 0pt{}Afghan soldier seeks asylum after arrest at US-Mexico border}{https://apnews.com/article/fa6df3564a022d13fc3046a65e2c7795}{Photographs of Abdul Wasi Safi sit on a table as his brother, Sami-ullah Safi talks about his brother\textquotesingle s journey to the U.S. during an interview Wednesday, Jan. 18, 2023, in Houston. Abdul Wasi Safi was an intelligence...}

\entryitemWithDescription{\hskip 0pt{}Schools face pressure to take harder line on discipline}{https://apnews.com/article/124a978f3f76f53f1cb90ae4da21da4a}{FILE - Djifa Lee, a second-grade teacher at Saunders Elementary, center, stands with her daughter as she speaks in front of the Newport News School Board at the Newport News Public Schools Administration building on Jan. 17, 2023, in...}

\entryitemWithDescription{\hskip 0pt{}Sections of Balkan river become floating garbage dump}{https://apnews.com/article/1f40635991a1f223c9dadb58c8a2c6c1}{Aerial view of waste floating in the Drina river near Visegrad, Bosnia, Friday, Jan. 20, 2023. Tons of waste dumped in poorly regulated riverside landfills or directly into the rivers across three Western Balkan countries end up...}
\ichapter{联合早报}
\entryitemGeneric{\hskip 0pt{}针对冠病奥密克戎变异株 国药研发mRNA疫苗 获准临床试验}{https://www.zaobao.com/news/china/story20230121-1355495}

\entryitemGeneric{\hskip 0pt{}新闻人间：一点都不像``看守阁揆''的 苏贞昌}{https://www.zaobao.com/news/china/story20230121-1355496}

\entryitemGeneric{\hskip 0pt{}三兔共耳同享好年}{https://www.zaobao.com/news/china/story20230121-1355497}

\entryitemGeneric{\hskip 0pt{}马云抵港会见财经界人士}{https://www.zaobao.com/news/china/story20230121-1355498}

\entryitemGeneric{\hskip 0pt{}世卫：冠病确诊入院人数 中国上周达疫情来最高水平}{https://www.zaobao.com/news/china/story20230121-1355500}

\entryitemGeneric{\hskip 0pt{}邻近居民指侵犯隐私 中国驻葡使馆调移闭路摄像机}{https://www.zaobao.com/news/china/story20230121-1355501}

\entryitemGeneric{\hskip 0pt{}庄慧良：赖清德要开创新局的困境}{https://www.zaobao.com/news/china/story20230121-1355502}

\entryitemGeneric{\hskip 0pt{}中国将恢复旅行社出境团业务 试点旅游目的国包括新加坡等}{https://www.zaobao.com/news/china/story20230121-1355503}

\entryitemGeneric{\hskip 0pt{}大理丽江三亚春节广受国内游客青睐 酒店房价涨数倍仍一房难求}{https://www.zaobao.com/news/china/story20230121-1355504}

\entryitemGeneric{\hskip 0pt{}中国卫健委：各省已度过``三高峰'' 医疗资源紧张已缓解}{https://www.zaobao.com/news/china/story20230120-1355118}

\entryitemGeneric{\hskip 0pt{}港月底取消确诊者隔离令 快筛呈阳性者无须申报}{https://www.zaobao.com/news/china/story20230120-1355119}

\entryitemGeneric{\hskip 0pt{}学者：或循王岐山先例 韩正可能出任中国国家副主席}{https://www.zaobao.com/news/china/story20230120-1355120}

\entryitemGeneric{\hskip 0pt{}殷勇当选北京市市长 中国31省级政府中最年轻``一把手''}{https://www.zaobao.com/news/china/story20230120-1355122}

\entryitemGeneric{\hskip 0pt{}李克强：将再优化工作许可等政策 中国欢迎更多外国人才赴华工作}{https://www.zaobao.com/news/china/story20230120-1355123}

\entryitemGeneric{\hskip 0pt{}澳籍华裔作家间谍案判决再延期 澳外长发声明对事态表示担忧}{https://www.zaobao.com/news/china/story20230120-1355124}

\entryitemGeneric{\hskip 0pt{}西藏一隧道口雪崩 八人罹难多车被掩埋}{https://www.zaobao.com/news/china/story20230120-1355125}

\entryitemGeneric{\hskip 0pt{}早说}{https://www.zaobao.com/news/china/story20230120-1355126}

\entryitemGeneric{\hskip 0pt{}韩咏红：Z世代与他们的未来}{https://www.zaobao.com/news/china/story20230120-1355127}

\entryitemGeneric{\hskip 0pt{}台行政院长苏贞昌请辞并将率阁员总辞 蔡英文宣布农历新年期间``调整''内阁}{https://www.zaobao.com/news/china/story20230120-1355128}

\entryitemGeneric{\hskip 0pt{}中国医保局：冠病药Paxlovid未能纳入医保 ​原因是与厂商辉瑞​价格谈判破裂}{https://www.zaobao.com/news/china/story20230120-1355129}

\entryitemGeneric{\hskip 0pt{}网信办启动春节专项行动 营造网上喜庆祥和舆论氛围}{https://www.zaobao.com/news/china/story20230120-1355130}