\entryitemAp{\hskip 0pt{}Walmart shooting victim's mom: Gunman threatened daughter}{https://apnews.com/article/552a1b2fce5a5c75acebee597c0666a5}{An image of Ronald Ray Mosley II, 25, is displayed on a monitor during a press conference, Friday afternoon, Jan. 20, 2023, related to the ongoing investigation of a shooting at the West Side Walmart in Evansville, Ind. Police identified...}

\entryitemAp{\hskip 0pt{}Top Biden aide Ron Klain expected to soon leave White House}{https://apnews.com/article/859543dcbbcbe3e2ef987e88f7b4ff34}{FILE - White House chief of staff Ron Klain walks to the South Lawn of the White House to attend an event celebrating the confirmation of Judge Ketanji Brown Jackson as the first Black woman to reach the Supreme Court in Washington, April...}

\entryitemAp{\hskip 0pt{}Sundance doc looks into Brett Kavanaugh investigation}{https://apnews.com/article/312b5e1d318094f005aae4bf41f9d38a}{FILE - Supreme Court Associate Justice Brett Kavanaugh watches as President Donald Trump arrives to give his State of the Union address to a joint session on Congress at the Capitol in Washington, on Feb. 5, 2019. A new documentary looks...}

\entryitemAp{\hskip 0pt{}Brazil's army chief fired in aftermath of capital uprising}{https://apnews.com/article/42151a9c0ea511391b990a9527754c1e}{An agent walks past the head of a statue depicting the Greek goddess Themis, outside the Brazilian Supreme Court building that was damaged by supporters of Brazil\textquotesingle s former President Jair Bolsonaro, in Brasilia, Brazil...}

\entryitemAp{\hskip 0pt{}The AP Interview: Yellen says debt standoff risks `calamity'}{https://apnews.com/article/0f7f0d85ed38353940a18cd262de8b09}{In this image taken from a video, Treasury Secretary Janet Yellen speaks during an interview with The Associated Press on Saturday, Jan. 21, 2023, in Dakar, Senegal. (AP Photo/Yesica Fisch) DAKAR, Senegal (AP) --- U.S. Treasury Secretary...}

\entryitemAp{\hskip 0pt{}Venezuela frees former spy chief who defied Nicolás Maduro}{https://apnews.com/article/8e1c141d769aef41b2309e9a46d25349}{FILE - In this April 26, 2017 photo, former Venezuelan Interior Minister Miguel Rodriguez Torres poses for a photo during an interview at his office in Caracas, Venezuela. On Saturday, Jan. 21, 2023, Venezuela\textquotesingle s government...}

\entryitemAp{\hskip 0pt{}Gyms that survived pandemic steadily get back in shape}{https://apnews.com/article/6624e5c1c4b8981d1539b258a470d383}{Fuel Training Studio owners Julie Bokat, left, and Jeanne Carter watch a fitness class inside their gym, Thursday, Jan. 19, 2023, in Newburyport, Mass. Gyms and fitness studios were among the hardest hit businesses during the pandemic...}

\entryitemAp{\hskip 0pt{}Brazil's right-wing movement persists without Bolsonaro}{https://apnews.com/article/8d7e202b93b6cba7196c4baba32b6452}{FILE - A supporter of Brazilian President Jair Bolsonaro salutes while singing the nation\textquotesingle s anthem outside a military base during a protest against his reelection defeat in Sao Paulo, Brazil, Nov. 3, 2022. The capital...}

\entryitemAp{\hskip 0pt{}Big waves to deliver storied Hawaii surf contest The Eddie}{https://apnews.com/article/691d0c11ab910bde4f51679178135b44}{FILE - Jamie Mitchell, right, and Ross Clarke-Jones, both of Australia, surf in the Eddie Aikau big-wave surfing contest in Waimea Bay near Haliewa, Hawaii on Feb. 25, 2016. One of the world\textquotesingle s most prestigious and storied...}

\entryitemAp{\hskip 0pt{}GOP investigations of Biden to test Chairman Comer's power}{https://apnews.com/article/d68267048aa4f42d244130e81d3e9c30}{FILE - Rep. James Comer, R-Ky., talks to reporters as he walks to the House chamber, on Capitol Hill in Washington, Jan. 12, 2023. (AP Photo/Jose Luis Magana, File) WASHINGTON (AP) --- In early 2017, freshman Rep. James Comer found...}

\entryitemAp{\hskip 0pt{}Afghan soldier seeks asylum after arrest at US-Mexico border}{https://apnews.com/article/fa6df3564a022d13fc3046a65e2c7795}{Photographs of Abdul Wasi Safi sit on a table as his brother, Sami-ullah Safi talks about his brother\textquotesingle s journey to the U.S. during an interview Wednesday, Jan. 18, 2023, in Houston. Abdul Wasi Safi was an intelligence...}

\entryitemAp{\hskip 0pt{}Schools face pressure to take harder line on discipline}{https://apnews.com/article/124a978f3f76f53f1cb90ae4da21da4a}{FILE - Djifa Lee, a second-grade teacher at Saunders Elementary, center, stands with her daughter as she speaks in front of the Newport News School Board at the Newport News Public Schools Administration building on Jan. 17, 2023, in...}

\entryitemAp{\hskip 0pt{}Sections of Balkan river become floating garbage dump}{https://apnews.com/article/1f40635991a1f223c9dadb58c8a2c6c1}{Aerial view of waste floating in the Drina river near Visegrad, Bosnia, Friday, Jan. 20, 2023. Tons of waste dumped in poorly regulated riverside landfills or directly into the rivers across three Western Balkan countries end up...}