\entryitemWithDescription{\hskip 0pt{}Caitlin Clark's 33-point game moves her past Lynette Woodard for the major college scoring record}{https://apnews.com/article/6bad1ecd9fba1da853483e98ab84c632}{MINNEAPOLIS (AP) --- Caitlin Clark has another career record on her astounding resume: the most points by any major college women's player to ever take the court. Iowa's superstar guard scored 33 points to lead the sixth-ranked Hawkeyes...}

\entryitemWithDescription{\hskip 0pt{}Cristiano Ronaldo suspended for one match over alleged offensive gesture in Saudi league game}{https://apnews.com/article/47bf6c5600e477122aebb63f38fc5be1}{Cristiano Ronaldo has been suspended for one match for making an alleged offensive gesture during a Saudi Arabia league game while playing for Al Nassr in the Saudi Pro League. After Al-Nassr defeated Riyadh rival Al-Shabab 3-2 on Sunday...}

\entryitemWithDescription{\hskip 0pt{}Visitors line up to see and smell a corpse flower's stinking bloom in San Francisco}{https://apnews.com/article/287afa48df86264ea75b05ec8ace0bc4}{SAN FRANCISCO (AP) --- Crowds lined up in San Francisco on Wednesday to see --- and smell --- the blooming of an endangered tropical flower that releases a pungent odor when it opens once every several years. An Amorphophallus titanum...}

\entryitemWithDescription{\hskip 0pt{}Don Henley says lyrics to `Hotel California' and other Eagles songs were always his sole property}{https://apnews.com/article/01d778228e5f7450a2579238798c4f38}{NEW YORK (AP) --- The lyrics to ``Hotel California'' and other classic Eagles songs should never have ended up at auction, Don Henley told a court Wednesday. ``I always knew those lyrics were my property. I never gifted them or gave them...}

\entryitemWithDescription{\hskip 0pt{}Stacy Wakefield dies less than 5 months after her husband, World Series champion Tim Wakefield}{https://apnews.com/article/6504d307ab00daf4a4db4638bfaed632}{Stacy Wakefield, the widow of former Boston Red Sox pitcher and two-time World Series champion Tim Wakefield, has died. Her family said in a statement released through the Red Sox that she died Wednesday at her Massachusetts home, less...}

\entryitemWithDescription{\hskip 0pt{}Humorously morose comedian Richard Lewis, who recently starred on `Curb Your Enthusiasm,' dies at 76}{https://apnews.com/article/c4f69a5ecc8f03850222f8f2145f55ce}{NEW YORK (AP) --- Richard Lewis, an acclaimed comedian known for exploring his neuroses in frantic, stream-of-consciousness diatribes while dressed in all-black, leading to his nickname ``The Prince of Pain,'' has died. He was 76. Lewis...}

\entryitemWithDescription{\hskip 0pt{}Mexico's Popocatépetl volcano erupts 13 times in past day, prompting airport delays}{https://apnews.com/article/67a11616283ae80d23470fc9b70a35c3}{MEXICO CITY (AP) --- Mexico's National Disaster Prevention Center said Wednesday the Popocatépetl volcano, located just 50 miles from the country's capital, has erupted 13 times in the past day and urged people to not try to climb it due...}

\entryitemWithDescription{\hskip 0pt{}Social media influencer says Dolphins' Tyreek Hill broke her leg during football drill at his home}{https://apnews.com/article/75f9dc48fbf4535f7239a14e8d6a44f5}{A social media influencer is suing Miami Dolphins wide receiver Tyreek Hill over an alleged incident that happened at the NFL star's South Florida home last summer. In a lawsuit that Sophie Hall's attorneys filed in Broward County circuit...}

\entryitemWithDescription{\hskip 0pt{}Baby pig that was tossed like a football is adopted and pardoned at Louisiana Capitol}{https://apnews.com/article/6c63c564854bc9c4082cecab27fc9c03}{BATON ROUGE, La. (AP) --- A baby pig that was rescued after being tossed like a football near a Mardi Gras event in New Orleans was ``pardoned'' Wednesday and has found a permanent home with a Louisiana lawmaker. The weeks-old little pink...}

\entryitemWithDescription{\hskip 0pt{}Helicopter's thermal imaging camera helps deputies find child in Florida swamp}{https://apnews.com/article/5071c8faca0dfecd8a7a25e06b5060aa}{TAMPA, Fla. (AP) --- A sheriff's aviation unit used thermal imaging to guide deputies to a missing 5-year-old who had gone missing in a swamp near Tampa. The autistic girl wandered away from her home Monday evening and was quickly...}

\entryitemWithDescription{\hskip 0pt{}Ryan Gosling, Billie Eilish, Jon Batiste set to perform at the Oscars}{https://apnews.com/article/f8e233ed309521fa042c813a8a17f41f}{The Oscars just got an infusion of Kenergy. Ryan Gosling will sing the pop power ballad `` I'm Just Ken '' at the show on March 10, the show's producers announced Wednesday. Others set to perform their nominated original songs include...}

\entryitemWithDescription{\hskip 0pt{}Dubai's sky-high aspirations find a new outlet as it hosts a jet suit race for `Iron Man' pilots}{https://apnews.com/article/b08cced1c6d2cc36cc1da169f2df6b56}{DUBAI, United Arab Emirates (AP) --- Pilots lined up on a runway in Dubai on Wednesday and fired up their seven jet engines with an ear-splitting roar. But they weren't preparing to fly an airplane --- they were the aircraft. This city...}

\entryitemWithDescription{\hskip 0pt{}Wendy's says it has no plans to raise prices during the busiest times at its restaurants}{https://apnews.com/article/ef75fa9214beddbd0d9d459f37722638}{Wendy's says that it has no plans to increase prices during the busiest times at its restaurants. The burger chain clarified its stance on how it will approach pricing after media picked up on comments by CEO Kirk Tanner that the company...}