\entryitemWithDescription{\hskip 0pt{}Lifetime's Wendy Williams documentary will air this weekend after effort to block broadcast fails}{https://apnews.com/article/53ab1058f97c18b7a77fae307b7db356}{NEW YORK (AP) --- Lifetime's ``Where is Wendy Williams?'' documentary will air this weekend as scheduled after a New York court rejected an attempt to block the broadcast. The order signed Friday by a New York appellate judge says...}

\entryitemWithDescription{\hskip 0pt{}Backstory of disputed `Hotel California' lyrics pages `just felt thin,' ex-auction exec tells court}{https://apnews.com/article/055fb4a490783c3080943f1cb2c9e8ae}{NEW YORK (AP) --- The explanation given for the source of 13 pages of drafts of lyrics to the Eagles' ``Hotel California'' raised red flags to a prominent auction house, a former executive testified Friday at a criminal trial surrounding...}

\entryitemWithDescription{\hskip 0pt{}Watch melted during atomic blast over Hiroshima sells for more than \$31,000}{https://apnews.com/article/6252c36c669b6f148b331d83ca828677}{BOSTON (AP) --- A watch melted during the August 6, 1945 bombing of Hiroshima has sold for more than \$31,000 at auction. The watch is frozen in time at the moment of the detonation of an atomic bomb over the Japanese city --- 8:15 a...}

\entryitemWithDescription{\hskip 0pt{}3 University of Wyoming swimmers killed in highway crash in Colorado}{https://apnews.com/article/72d6ca68c5e8a72b7dc6ed344705b65a}{CHEYENNE, Wyo. (AP) --- Three members of the University of Wyoming swimming and diving team were killed in a highway crash in northern Colorado. The crash happened Thursday afternoon on U.S. 287 about 10 miles (16 kilometers) south of the...}

\entryitemWithDescription{\hskip 0pt{}Unexploded WWII bomb in English city of Plymouth to be transported by convoy and disposed of at sea}{https://apnews.com/article/f46b89a68adf7e716cec91bcf718bceb}{LONDON (AP) --- An unexploded World War II bomb was being transported Friday through the southwestern English port city of Plymouth by a military convoy and disposed of at sea, prompting one of the largest evacuations in the United...}

\entryitemWithDescription{\hskip 0pt{}IS bride loses her appeal over the removal of her UK citizenship}{https://apnews.com/article/5d6de3ac785ecb7d3a2b46f79e037777}{LONDON (AP) --- A woman who traveled to Syria as a teenager to join the Islamic State group lost her appeal Friday against the British government's decision to revoke her U.K. citizenship, with judges saying that it wasn't for them to...}

\entryitemWithDescription{\hskip 0pt{}French actresses denounce abuse by directors when they were teenagers in new \#MeToo step}{https://apnews.com/article/e215e51b38c9500c9ac032be99d4e0f0}{PARIS (AP) --- As French cinema basks in Academy Awards attention, actors who allege they were teenage victims of sexual and physical abuse by directors decades older than them are shining the light on the repulsive underside of the...}

\entryitemWithDescription{\hskip 0pt{}Vice Media says `several hundred' staff members will be laid off, Vice.com news site shuttered}{https://apnews.com/article/3439e54142c88530a5825642a81aeec5}{NEW YORK (AP) --- Vice Media plans to lay off several hundred employees and no longer publish material on its Vice.com website, the company's CEO said in a memo to staff Thursday. Vice, which filed for bankruptcy last year before being...}

\entryitemWithDescription{\hskip 0pt{}Atlanta is the only place in US to see pandas for now. But dozens of spots abroad have them}{https://apnews.com/article/235de70dec5e6c6f11cd16f53547cfb8}{SAN DIEGO (AP) --- It will still be months before the San Diego Zoo gets new pandas, the first such bears sent to the United States by China in decades. For now, the only U.S. zoo left with any is in Atlanta. But globally there are many...}

\entryitemWithDescription{\hskip 0pt{}MLB players miffed at sport's new see-through pants, relaying concerns to league}{https://apnews.com/article/52ccd5bcc81043f1623d2480bf5db39b}{PEORIA, Ariz. (AP) --- MLB's new uniform reveal hasn't gone very well. Now some of the rampant criticism has moved below the belt. Major League Baseball Players Association deputy executive director Bruce Meyer confirmed on Thursday that...}

\entryitemWithDescription{\hskip 0pt{}University of Georgia cancels classes after woman found dead on campus}{https://apnews.com/article/a7a654367dc8b815d45384a7f853626d}{ATHENS, Ga. (AP) --- A woman was found dead Thursday on the campus of the University of Georgia after a friend told police she had not returned from a morning run, authorities said. The woman was not a student at the university, the...}

\entryitemWithDescription{\hskip 0pt{}Wendy Williams diagnosed with same form of dementia as Bruce Willis}{https://apnews.com/article/d3cebb8c20f750a623f9d180a50c03e8}{LOS ANGELES (AP) --- Former talk show host Wendy Williams has been diagnosed with the same form of dementia that actor Bruce Willis has, a statement released Thursday on behalf of her caretakers says. The statement said the 59-year-old's...}

\entryitemWithDescription{\hskip 0pt{}Herbstreit, Fowler to be voices in EA Sports college football game that will feature every FBS team}{https://apnews.com/article/4f78e19893ee1b361a131ebf536aa4ad}{Kirk Herbstreit and Chris Fowler are in the game. ESPN ``College GameDay'' analyst Herbstreit and network broadcaster Fowler announced Thursday on social media they will be voices in EA Sports' upcoming college football video game...}