\entryitemWithDescription{\hskip 0pt{}Florida's population passes 23 million for the first time due to residents moving from other states}{https://apnews.com/article/873f4923ae7fb7394ba17a49068bd79c}{ORLANDO, Fla. (AP) --- Florida's population crossed the 23 million residents mark for the first time this year because of the influx of people moving from other states, according to state demographic estimates. As of April 1 of this year...}

\entryitemWithDescription{\hskip 0pt{}Oscar Mayer Wienermobile flips onto its side after crash along suburban Chicago highway}{https://apnews.com/article/b81452ebaa5ae0823871eabbf06135cd}{OAK BROOK, Ill. (AP) --- One of Oscar Mayer's hot dog-shaped Wienermobiles ended up flipped onto its side after crashing on a suburban Chicago highway, police said. The Wienermobile hit a car Monday morning along Interstate 294 and its...}

\entryitemWithDescription{\hskip 0pt{}Google makes abrupt U-turn by dropping plan to remove ad-tracking cookies on Chrome browser}{https://apnews.com/article/bffdd0ca0af9ba7a94e95c2c7a11e4d2}{LONDON (AP) --- Google is dropping plans to eliminate cookies from its Chrome web browser, making a sudden U-turn on four years of work to phase out a technology that helps businesses tracks users online. The company had been working on...}

\entryitemWithDescription{\hskip 0pt{}US is investigating Delta's flight cancellations and faltering response to global tech outage}{https://apnews.com/article/7361e641fe2c656d7fba06e4a0424c6a}{U.S. regulators are investigating how Delta Air Lines is treating passengers affected by canceled and delayed flights as the airline struggles to recover from a global technology outage. Transportation Secretary Pete Buttigieg announced...}

\entryitemWithDescription{\hskip 0pt{}Colombian bullfighters decry new ban on the centuries-old tradition and vow to keep it alive}{https://apnews.com/article/3d36d524d589c89d3c63f070abed8680}{CHOACHI, Colombia (AP) --- Sebastián Caqueza says a new law to ban bullfighting in Colombia by mid-2027 will not dampen his passion for the sport that he has been practicing since has was a small boy. Caqueza became a professional matador...}

\entryitemWithDescription{\hskip 0pt{}Wildfires near Canada's Jasper National Park prompt evacuation order}{https://apnews.com/article/167dcc0e03984672584f9770799c2fb8}{EDMONTON, Alberta (AP) --- Multiple wildfires have flared up in the Canadian Rockies' largest national park, forcing visitors along with thousands of residents to evacuate and flee west over mountain roads through darkness, soot, and ash...}

\entryitemWithDescription{\hskip 0pt{}Wembanyama returns home for Olympics. The basketball star will be one of Paris' biggest attractions}{https://apnews.com/article/8a9afa35933b178e3d40752eeba4ff62}{PARIS (AP) --- Sports often are a secondary attraction in Paris, with athletes having a difficult time standing out in a cultural sphere driven largely by food, fashion and the arts. Victor Wembanyama may use the Paris Olympics to be the...}

\entryitemWithDescription{\hskip 0pt{}Horses take to the air with passports and carryons ahead of equestrian eventing at Paris Olympics}{https://apnews.com/article/b562b67a362e77e7ebf3f9255ae33557}{PARIS (AP) --- Welcome aboard, hope you are standing comfortably. For the horses on the U.S. eventing team, the journey to France for the Paris Olympics was --- quite literally --- a four-legged journey. Their trek began on a farm in...}

\entryitemWithDescription{\hskip 0pt{}Jon Stewart pushes VA to help veterans sickened after post-9/11 exposure to uranium}{https://apnews.com/article/5e7b971f527088e85c58bfd370deb66f}{WASHINGTON (AP) --- Comedian Jon Stewart is pressing the Biden administration to fix a loophole in a massive veterans aid bill that left out some of the first U.S. troops who responded after the Sept. 11 attacks and got sick after...}

\entryitemWithDescription{\hskip 0pt{}Eminem brings Taylor Swift's historic reign at No. 1 to an end, Stevie Wonder's record stays intact}{https://apnews.com/article/6293aab7b77be26c4a7ecd8b14f43302}{Eminem's 12th studio album, ``The Death of Slim Shady (Coup de Grâce),'' has debuted at No. 1 on the Billboard 200, unseating Taylor Swift's ``The Tortured Poets Department'' after 12 weeks. In its first week, ``The Tortured Poets...}

\entryitemWithDescription{\hskip 0pt{}Calls for Maya Rudolph to reprise her Kamala Harris on `SNL' are flooding in on social media}{https://apnews.com/article/1b7649f6ab82fb0d784e9ae05c6a3153}{NEW YORK (AP) --- Will Maya Rudolph's ``funt,'' aka Vice President Kamala Harris, be back on ``Saturday Night Live?'' Speculation has been running hot since Sunday, when President Joe Biden dropped his election news, but the ``SNL'' alum...}

\entryitemWithDescription{\hskip 0pt{}Defamation suit against Fox News by head of dismantled disinformation board tossed by federal judge}{https://apnews.com/article/1787f545af859a596fc9cd3f950a4c3c}{A defamation suit against Fox News by a government official who served on a short-lived U.S. government media disinformation board was dismissed Monday by a federal judge. The lawsuit from Nina Jankowicz alleged that Fox had defamed her...}

\entryitemWithDescription{\hskip 0pt{}Self-professed `Wolf of Airbnb' sentenced to over 4 years in prison for defrauding landlords}{https://apnews.com/article/7817a88d62e962b952de5c878f3ddb42}{NEW YORK (AP) --- A Florida man who boasted that he was the ``Wolf of Airbnb'' was sentenced Monday to over four years in prison for defrauding New York City landlords and a federal pandemic-relief government program. Konrad Bicher, 32...}