\entryitemWithDescription{\hskip 0pt{}Pigs run loose on metro highway after semitruck tips over in Minnesota}{https://apnews.com/article/b0ee5418902e3d0df009bbb48ea34520}{This photo provided by the Minnesota State Patrol shows pigs running loose on a metro highway after a semitrailer truck that was carrying them overturned, causing an hours-long shutdown Friday morning, June 9, 2023, in Little Canada...}

\entryitemWithDescription{\hskip 0pt{}Florida's 'Dr. Deep' resurfaces after a record 100 days living underwater}{https://apnews.com/article/1000d227a775ce522d44b231ad439532}{In this photo provided by the Florida Keys News Bureau, diving explorer and medical researcher Dr. Joseph Dituri points to his watch Friday, June 9, 2023, indicating that it is time to surface after spending 100 days in the Jules...}

\entryitemWithDescription{\hskip 0pt{}Chelsea Peretti on her directorial debut 'First Time Female Director,' premiering at Tribeca}{https://apnews.com/article/442934f978872423ed40eaafa8f3e542}{Writer/director Chelsea Peretti poses for a portrait to promote the film "First Time Female Director" on Friday, June 9, 2023, in New York. (Photo by Matt Licari/Invision/AP) NEW YORK (AP) --- Chelsea Peretti plays a first-time director...}

\entryitemWithDescription{\hskip 0pt{}Rep. Santos says he's protecting family members by seeking to keep bond cosigners secret}{https://apnews.com/article/15feeec07af7ce58f2d0645fc89bd12d}{FILE - Rep. George Santos, R-N.Y., speaks to reporters outside after an effort to expel him from the House, at the Capitol in Washington, Wednesday, May 17, 2023. Santos wants to protect family members by asking that the courts keep his...}

\entryitemWithDescription{\hskip 0pt{}Body of Alaska fishing captain recovered 11 days after partially submerged boat found}{https://apnews.com/article/4aea31df85e9f106a1bd09ae384c4e12}{A harbor seal pokes its head up near Low Island in Sitka Sound, Thursday, June 1, 2023. The area was the site of a fatal charter boat accident, Sunday, May 28. (James Poulson/The Daily Sitka Sentinel via AP) JUNEAU, Alaska (AP...}

\entryitemWithDescription{\hskip 0pt{}Florida woman who fatally shot neighbor granted \$154,000 bond}{https://apnews.com/article/1bc7189999056813593c19457879f828}{Tmika Wilkerson, left, and Kimberly Wilkerson pray as mourners gather for a remembrance service at Immerse Church of Ocala for Ajike Owens, Thursday, June 8, 2023, in Ocala, Fla. Owens was fatally shot by her neighbor Susan Lorincz when...}

\entryitemWithDescription{\hskip 0pt{}Tom Brady still has a full plate and plenty of drive after retirement}{https://apnews.com/article/e333c03467eb2501f8effedeb829ed3a}{FILE - Then-New England Patriots quarterback Tom Brady holds a Super Bowl trophy, between others the team previously had won, during a rally in Boston to celebrate the team\textquotesingle s 34-28 win over the Atlanta Falcons in the NFL...}

\entryitemWithDescription{\hskip 0pt{}Man pleads guilty to helping 2 others accused in the fatal shooting of rapper Young Dolph in Memphis}{https://apnews.com/article/fec02d3b8ac947d1674603a807a4fc11}{FILE - Young Dolph performs at The Parking Lot Concert in Atlanta on Aug. 23, 2020. Jermarcus Johnson pleaded guilty Friday, June 9, 2023 to helping two other men charged with fatally shooting rapper Young Dolph in a daytime ambush at a...}

\entryitemWithDescription{\hskip 0pt{}Businessman linked to Texas AG Ken Paxton's impeachment charged with lying to get \$172M in loans}{https://apnews.com/article/b3fabca88d1f55f231c36bca10a34226}{This undated photo provided by the Austin Police Department shows Nate Paul. Paul, the businessman at the center of the scandal that led to Texas Attorney General Ken Paxton's historic impeachment, is set to make an initial appearance in...}

\entryitemWithDescription{\hskip 0pt{}Missouri Supreme Court declines to halt August execution of man convicted of killing child}{https://apnews.com/article/052a2b3c6a25f14ef51ce35c59935084}{This undated photo provided by the Missouri Department of Corrections shows Johnny Johnson. The Missouri Supreme Court on Friday, June 9, 2023, has turned aside an appeal by Johnson, who is scheduled to be executed in August for killing a...}

\entryitemWithDescription{\hskip 0pt{}Natalee Holloway disappearance suspect in court, charged with extorting victim's mother}{https://apnews.com/article/c69b0d1606980df065b954e94da9ac01}{Dutch citizen Joran van der Sloot is driven in a police vehicle from the Ancon I maximum-security prison, outskirts of Lima, Peru, Thursday, June 8, 2023. The main suspect in the unsolved 2005 disappearance of American student Natalee...}

\entryitemWithDescription{\hskip 0pt{}Giant inflatable ducks make a splash in Hong Kong as pop-art project returns after 10 years}{https://apnews.com/article/62983d6020e4065afcb3485bd46fb060}{Members of the public photograph an art installation called "Double Ducks" by Dutch artist Florentijn Hofman at Victoria Harbour in Hong Kong, Friday, June 9, 2023. Two giant inflatable ducks made a splash in Hong Kong\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Philippines evacuates people near Mayon Volcano, where more unrest indicates eruption may be coming}{https://apnews.com/article/49a2623acb28a3779607bcb77bef26ea}{Mayon Volcano spews white smoke as seen from Daraga, Albay province, central Philippines on Thursday June 8, 2023. The Philippine Institute of Volcanology and Seismology raised Thursday the status of Mayon Volcano in Albay to Alert Level...}