\entryitemWithDescription{\hskip 0pt{}May the Fourth be 'I do': Ohio city has 'Star Wars' weddings}{https://apnews.com/article/dd6ad971a7af909cc7b48f99c2a6a439}{Julia and Robert Jones exchange vows during their wedding ceremony in Akron, Ohio, on Thursday, May 4, 2023. Couples celebrated May the Fourth with a "Star Wars" themed wedding. (AP Photo/Patrick Orsagos) AKRON, Ohio (AP) --- When Julia...}

\entryitemWithDescription{\hskip 0pt{}Purple lanes: Minnesota highway signs to honor Prince}{https://apnews.com/article/a1ac515d07ce850f18f56e63eb8bcef1}{Sharon Nelson, oldest sister of the late pop superstar Prince, speaks to reporters at the Minnesota Capitol, Thursday, May 4, 2023, in St. Paul, Minn. She appeared after the Minnesota Senate voted to honor him by designating the highway...}

\entryitemWithDescription{\hskip 0pt{}Former California college student arrested in 3 stabbings}{https://apnews.com/article/e85b0e6367a5fcf9d4d4ccba99115457}{Police investigators are seen at the home of stabbing suspect Carlos Dominguez, 21, on Hawthorn Lane in Davis, Calif., on Thursday, May 4, 2023. A 21-year-old who had been a student at the University of California, Davis, until last week...}

\entryitemWithDescription{\hskip 0pt{}COVID dropped to 4th leading cause of death in US last year}{https://apnews.com/article/99b24aeb572e3a59effc082389be8009}{FILE - A man walks through the snow covered Mount Lebanon Cemetery in Mount Lebanon, Pa., on Monday, Jan. 23, 2023. U.S. deaths fell in 2022, as COVID-19 fatalities dropped by half from 2021 and the coronavirus dropped from being the...}

\entryitemWithDescription{\hskip 0pt{}Sons of 'El Chapo' deny US fentanyl indictment allegations}{https://apnews.com/article/76018d40f2af1fb81c9a681cb814b829}{FILE - Police and military patrol Culiacan, Sinaloa state, Mexico, Jan. 6, 2023, the day after the government detained Ovidio Guzman, the son of imprisoned drug lord Joaquin "El Chapo" Guzman, which unleashed deadly firefights between the...}

\entryitemWithDescription{\hskip 0pt{}Tyre Nichols died of blows to the head, autopsy shows}{https://apnews.com/article/c420e7607060f155bb39aa9c44b304aa}{FILE - The screen at the Smoothie King Center in New Orleans honors Tyre Nichols before an NBA basketball game between the New Orleans Pelicans and the Washington Wizards, Jan. 28, 2023. The family of Tyre Nichols has sued the city of...}

\entryitemWithDescription{\hskip 0pt{}Ex-NBA star Shawn Kemp pleads not guilty to shooting charge}{https://apnews.com/article/2da800423c212c787626bffd6d7362e5}{Former Seattle Supersonics basketball player Shawn Kemp appears in Pierce County Superior Court in Tacoma, Washington, on Thursday, May 4, 2023, to be arraigned on charge of first-degree assault for a March 8 shooting at the Tacoma Mall...}

\entryitemWithDescription{\hskip 0pt{}Prince William pours a pint, meets public before coronation}{https://apnews.com/article/d2bde37dcfa4751687570eb1d1e21f74}{Britain\textquotesingle s Prince William pulls the first pint of Kingmaker, a new brew celebrating the coronation of King Charles III, as he and the Princess of Wales visit the Dog \& Duck pub in London, Thursday, May 4, 2023, to hear how...}

\entryitemWithDescription{\hskip 0pt{}Bud Light boosts spending in US to counter sales declines}{https://apnews.com/article/d489fb60d04ebd02486f80169cfc4474}{FILE - Bottles of Bud Light beer sit on a shelf at a grocery store on April 25, 2023, in Glenview, Ill. Bud Light\textquotesingle s parent company said Thursday, May 4, that it will triple its marketing spending in the U.S. this summer as...}

\entryitemWithDescription{\hskip 0pt{}Judge gives Trump time to decide on testifying at rape trial}{https://apnews.com/article/765e105fb21896b147ef9bf380487af7}{In this courtroom sketch, Carol Martin, right, a friend of E. Jean Carroll\textquotesingle s, testifies on direct examination by Roberta Kaplan in Manhattan federal court, Thursday, May 4, 2023 in New York. Martin testified that Carroll...}

\entryitemWithDescription{\hskip 0pt{}Norway climber aims to be fastest to scale 14 tallest peaks}{https://apnews.com/article/4533ac8507877f0e2b36558299747ae4}{Norwegian climber Kristin Harila, 37, smiles after arriving in Kathmandu, Nepal, Thursday, May 4, 2023. Harila who just became the fastest female climber to scale the 14 highest mountains in the world is now aiming to become the fastest...}

\entryitemWithDescription{\hskip 0pt{}Sandy León recalls harrowing day young daughter fell in pool}{https://apnews.com/article/185ac0734f802bc9ce1e216e41d2345e}{Texas Rangers\textquotesingle{} Sandy Leon (12) stands at bat during a baseball game against the Arizona Diamondbacks in Arlington, Texas, Wednesday, May 3, 2023. Veteran big league catcher Sandy León changed his uniform to No. 12 this...}

\entryitemWithDescription{\hskip 0pt{}BMW: Don't drive older models with Takata air bag inflators}{https://apnews.com/article/0167b6f727a20595a3c9a710faf1f660}{FILE - The logo of the German car manufacturer BMW is displayed on the headquarters in Munich, Germany, March 21, 2018. BMW is warning the owners of about 90,000 older vehicles in the U.S. not to drive them due to an increasing threat...}