\entryitemWithDescription{\hskip 0pt{}New York City police commissioner, first woman to lead department, resigns after 18 months}{https://apnews.com/article/511a218b2b051ea0993c6588a53d0ed3}{FILE - New York City Police Commissioner Keechant Sewell stands in New York\textquotesingle s Times Square during a news conference about New Year\textquotesingle s Eve security, Dec. 30, 2022. Sewell, the first woman to hold the...}

\entryitemWithDescription{\hskip 0pt{}Mexico's top diplomat resigns to enter primary race for 2024 presidential election}{https://apnews.com/article/331d292e5a1e84dd962ebb94181b445c}{Former Mexican Foreign Minster Marcelo Ebrard, center, shares a laugh with supporters after a news conference at a library in Mexico City, Monday, June 12, 2023. The top diplomat has resigned his post to enter the primary race for the...}

\entryitemWithDescription{\hskip 0pt{}Black Florida mother killed by white neighbor remembered for faith, devotion to 4 kids}{https://apnews.com/article/6986f11d0aeed6a9aaf147354ae85c1c}{Pamela Dias, the mother of Ajike Owens, left, attorney Ben Crump and Africa Owens leave after the funeral for Owens on Monday, June 12, 2023, at Meadowbrook Church in Ocala, Fla. Owens was fatally shot by her neighbor Susan Lorincz when...}

\entryitemWithDescription{\hskip 0pt{}Rachel Maddow's 'Deja News' podcast a boon to fans who like her historical tangents}{https://apnews.com/article/cfa848cb18e84979b686c8e51023db69}{FILE - MSNBC television anchor Rachel Maddow, host of "The Rachel Maddow Show," moderates a panel at the John F. Kennedy School of Government, at Harvard University, in Cambridge, Mass., on Oct. 16, 2017. Maddow\textquotesingle s "Deja...}

\entryitemWithDescription{\hskip 0pt{}Supreme Court won't review North Carolina's decision to nix license plates with Confederate flag}{https://apnews.com/article/6042b7db4218798b93dbaa8924272cec}{FILE - The Supreme Court is seen on April 21, 2023, in Washington. (AP Photo/Alex Brandon, File) WASHINGTON (AP) --- The Supreme Court said Monday it won\textquotesingle t review North Carolina\textquotesingle s decision to stop issuing...}

\entryitemWithDescription{\hskip 0pt{}Mother of 6-year-old who shot teacher pleads guilty to using marijuana while having a firearm}{https://apnews.com/article/d4d2c462c76ed142d8fb5e24e59c0824}{FILE - Signs stand outside Richneck Elementary School in Newport News, Va., Jan. 25, 2023. The mother of a 6-year-old boy who shot his teacher at the Virginia school is expected to plead guilty in federal court Monday, June 12, 2023, to...}

\entryitemWithDescription{\hskip 0pt{}Jeffrey Epstein victims settle sex trafficking lawsuit against JPMorgan for \$290 million}{https://apnews.com/article/ddb90e634536bc1828bf5d05608b39f1}{FILE - The logo of JPMorgan bank is pictured at the new French headquarters of JP Morgan bank, Tuesday, June 29, 2021, in Paris. JPMorgan Chase is defending itself against a lawsuit by the U.S. Virgin Islands accusing it of empowering...}

\entryitemWithDescription{\hskip 0pt{}Inside the Tony Awards: No script, but plenty of song, dance, high spirits and history}{https://apnews.com/article/a024df8972c9aca0f4153a0f8049f861}{Host Ariana DeBose, third right, performs at the 76th annual Tony Awards on Sunday, June 11, 2023, at the United Palace theater in New York. (Photo by Charles Sykes/Invision/AP) NEW YORK (AP) --- No script? No problem! There was plenty of...}

\entryitemWithDescription{\hskip 0pt{}British man detained after climbing 72nd floor of Seoul skyscraper}{https://apnews.com/article/27e5e133633521218539efbf8a71e861}{This photo provided by the Seoul Metropolitan Fire and Disaster Management Headquarters, shows an unidentified British man climbing Lotte World Tower, the tallest skyscraper in the country, in Seoul, South Korea, Monday, June 12, 2023...}

\entryitemWithDescription{\hskip 0pt{}Kouri Richins, Utah mom accused of killing husband and then writing book about grief, denied bail}{https://apnews.com/article/0d468b50b3b8438f2cda1c2141a8bd59}{Kouri Richins, a Utah mother of three who authorities say fatally poisoned her husband then wrote a children\textquotesingle s book about grieving, looks on during a bail hearing Monday, June 12, 2023, in Park City, Utah. A judge ruled to...}

\entryitemWithDescription{\hskip 0pt{}Philippines' Mayon Volcano spews lava in gentle eruption, thousands warned to be ready to flee}{https://apnews.com/article/27f6e00836599b7e83aa933f7775cf02}{Mayon Volcano is seen from Guinobatan, Albay province, northeastern Philippines, Monday, June 12, 2023. The Philippines\textquotesingle{} most active volcano was gently spewing lava down its slopes Monday, alerting tens of thousands of...}

\entryitemWithDescription{\hskip 0pt{}Report: Billionaire investor, philanthropist George Soros cedes control of empire to a younger son}{https://apnews.com/article/95e7a9858981b8a0b303402176025cb5}{FILE - George Soros, founder and chairman of the Open Society Foundations, attends the Joseph A. Schumpeter Award ceremony in Vienna, Austria, June 21, 2019. The billionaire investor turned philanthropist is ceding control of his \$25...}

\entryitemWithDescription{\hskip 0pt{}Phoenix Mercury make travel 'adjustments' following airport incident with Brittney Griner}{https://apnews.com/article/70b4daf5e5369b14f8e8c3abc7388a68}{Phoenix Mercury center Brittney Griner (42) grabs a rebound in front of Phoenix Mercury forward Brianna Turner, right, during the second half of a WNBA basketball basketball game in Arlington, Texas, Friday, June 9, 2023. (AP Photo/LM...}