\entryitemWithDescription{\hskip 0pt{}They're not aliens. That's the verdict from Peru officials who seized 2 doll-like figures}{https://apnews.com/article/2ab059d55d3d0352e41ad2a4c312d1ed}{LIMA, Peru (AP) --- Aliens they are not. That's what forensic experts in Peru said Friday about two doll-like figures and an alleged three-fingered hand that customs authorities in the South American country seized last year from a...}

\entryitemWithDescription{\hskip 0pt{}A refugee bear from a bombed-out Ukraine zoo finds a new home in Scotland}{https://apnews.com/article/d0a3be03869ce72e7362749722856387}{LONDON (AP) --- An unlikely refugee from the war in Ukraine --- a rare black bear --- arrived at his new home in Scotland on Friday and quickly took to a meal of cucumbers and watermelon. The 12-year-old Yampil was named for a village in...}

\entryitemWithDescription{\hskip 0pt{}Brunei's Prince Abdul Mateen weds fiancee in lavish 10-day ceremony}{https://apnews.com/article/65729c4afbd35772c401166e50e1e6d9}{KUALA LUMPUR, Malaysia (AP) --- Brunei's Prince Abdul Mateen, one of Asia's most popular royal figures, has married his fiancee in an elaborate 10-day ceremony. The 32-year-old prince, once dubbed one of Asia's most eligible bachelors...}

\entryitemWithDescription{\hskip 0pt{}Daniel Day-Lewis breaks from retirement to fete Martin Scorsese at National Board of Review Awards}{https://apnews.com/article/4b7f3827bd70dea94f564b4b89ecea61}{NEW YORK (AP) --- Daniel Day-Lewis took a break from retirement to present Martin Scorsese the award for best director at the National Board of Review Awards in midtown Manhattan on Thursday night. Scorsese's Osage epic, `` Killers of the...}

\entryitemWithDescription{\hskip 0pt{}Playoff game behind a Peacock paywall is a new frontier in NFL's embrace of streaming}{https://apnews.com/article/ec5dbea43d670eabae73401b79dfc269}{The quarterback matchup between Miami's Tua Tagovailoa and Kansas City's Patrick Mahomes isn't the only major storyline going into their AFC wild card game. Another question is how many fans will pay to watch one of the NFL's important...}

\entryitemWithDescription{\hskip 0pt{}Fruit Stripe Gum to bite the dust after a half century of highly abbreviated rainbow flavors}{https://apnews.com/article/624b16ee0066c638154464bf47c4ac9d}{SAN FRANCISCO (AP) --- Fruit Stripe Gum, something of a childhood icon for many gum chewers over the past five decades, will soon head over the rainbow with its multicolored zebra mascot Yipes --- seemingly for good. The manufacturer of...}

\entryitemWithDescription{\hskip 0pt{}NFL Hall of Famer Michael Strahan's 19-year-old daughter is fighting cancer}{https://apnews.com/article/409bcb47af9293d6c831523c23635021}{The 19-year-old daughter of NFL Hall of Famer and ``Good Morning America'' co-anchor Michael Strahan is undergoing treatment for brain cancer. Isabella Strahan appeared on a prerecorded videotape segment sitting next to her father while...}

\entryitemWithDescription{\hskip 0pt{}Rome opens new archaeological park and museum in shadow of Colosseum}{https://apnews.com/article/ab0fd4d62cbf5742f053fd1d8d375184}{ROME (AP) --- Rome authorities on Thursday inaugurated a new archaeological park and museum in the shadow of the Colosseum that features an original marble map of Ancient Rome that visitors can literally walk over. The opening of the...}

\entryitemWithDescription{\hskip 0pt{}Archeologists map lost cities in Ecuadorian Amazon, settlements that lasted 1,000 years}{https://apnews.com/article/8e48942ff8fd1c52611158696b74e214}{WASHINGTON (AP) --- Archeologists have uncovered a cluster of lost cities in the Amazon rainforest that was home to at least 10,000 farmers around 2,000 years ago. A series of earthen mounds and buried roads in Ecuador was first noticed...}

\entryitemWithDescription{\hskip 0pt{}The Patriots don't just need a new coach. They need a quarterback and talent to put around him}{https://apnews.com/article/3273ca9006d072986d14faef2b469009}{New England Patriots owner Robert Kraft will cringe when he turns on the TV --- or perhaps even looks at the other Gillette Stadium sideline --- and sees Bill Belichick wearing a ratty sweatshirt with another team's colors. But he has...}

\entryitemWithDescription{\hskip 0pt{}Drugs like Ozempic and Wegovy show no link with suicide, FDA says}{https://apnews.com/article/fbe7b158e78c199f8f8d3a551dcaa60d}{A preliminary review of side effects from popular drugs used to treat diabetes and obesity shows no link with suicidal thoughts or actions, the U.S. Food and Drug Administration said Thursday. But the agency also said officials cannot...}

\entryitemWithDescription{\hskip 0pt{}This week's storm damaged the lighthouse on Maine's state quarter. Caretakers say they can rebuild}{https://apnews.com/article/46e74761b89783a1299607cb3c62e95d}{PORTLAND, Maine (AP) --- The caretakers of part of one of Maine's most beloved lighthouses said Thursday they believe they can rebuild a portion of the structure that was damaged in a storm this week. The strong storm that brought high...}

\entryitemWithDescription{\hskip 0pt{}Here are the `Worst in Show' CES products, according to consumer and privacy advocates}{https://apnews.com/article/aa17a5edaaf94f776d7495714a984023}{The best CES products pierce through the haze of marketing hype at the Las Vegas gadget show to reveal innovations that could improve lives. The worst could harm us or our society and the planet in such ``innovatively bad'' ways that a...}