\entryitemWithDescription{\hskip 0pt{}Read the transcript of Kate's video announcement about her cancer diagnosis}{https://apnews.com/article/6b41bfd5419159b0bedb17a3b3512c87}{LONDON (AP) --- Kate, Princess of Wales, has released a statement saying she has been diagnosed with cancer. In it, she said she wanted to thank people for their messages of support after her abdominal surgery in January. She said her...}

\entryitemWithDescription{\hskip 0pt{}A Romanian court rejects Andrew Tate's bid to get his confiscated assets returned}{https://apnews.com/article/a90b9ee6e91b0a2a4c58eeb3d8fd3304}{Associated Press (AP) --- A court in Romania's capital on Friday denied a request by online influencer Andrew Tate to return assets that were seized during investigations into the case in which he is charged with human trafficking, rape...}

\entryitemWithDescription{\hskip 0pt{}Auction of Pattie Boyd's trove of treasures surpasses expectations as it nets \$3.6 million}{https://apnews.com/article/112a13c039c162bfeff4133fb0bcb3a0}{LONDON (AP) --- The online auction of a trove of letters, photos and other items that Pattie Boyd, who was at the heart of the Swinging 60s, concluded Friday --- and it's safe to say that it really surpassed all expectations. Christie's...}

\entryitemWithDescription{\hskip 0pt{}British man who poisoned couple with fentanyl and monitored their death via app sentenced to life}{https://apnews.com/article/6d91b766b7db2cb55d9c643ec95f91f2}{LONDON (AP) --- A British IT worker who befriended and worked for an older couple, poisoned them with fentanyl and monitored their death with his cellphone was sentenced Friday to a minimum 37 years in prison. The sentencing of Luke D'...}

\entryitemWithDescription{\hskip 0pt{}More than 440,000 Starbucks-branded mugs recalled due to burn, laceration risk}{https://apnews.com/article/0a30ce4543c86b04f270650c91231ae5}{NEW YORK (AP) --- More than 440,000 Starbucks-branded mugs made by Nestle and sold during the winter holidays are being recalled after reports of some users receiving burns or lacerations, according to a federal safety agency. The U.S...}

\entryitemWithDescription{\hskip 0pt{}What is Truth Social, Donald Trump's social media platform?}{https://apnews.com/article/7437d5dcc491a1459a078195ae547987}{SAN FRANCISCO (AP) --- Former President Donald Trump launched his social media platform, Truth Social, in early 2022, after he was banned from major sites such as Facebook and the platform formerly known as Twitter following the Jan. 6...}

\entryitemWithDescription{\hskip 0pt{}Stellantis recalls nearly 318,000 cars to replace side air bags that can explode and hurl shrapnel}{https://apnews.com/article/890aa14d1932f1581a8b425c11ed35dd}{DETROIT (AP) --- Stellantis is recalling nearly 318,000 Dodge and Chrysler sedans worldwide because the side air bag inflators can explode with too much force and hurl metal fragments at drivers and passengers. The recall covers air bag...}

\entryitemWithDescription{\hskip 0pt{}Drawing nears for \$997M Mega Millions jackpot}{https://apnews.com/article/252d67e8576ea1fb61ca813389a0af49}{DES MOINES, Iowa (AP) --- A nearly \$1 billion Mega Millions jackpot will be up for grabs Friday night, offering the prospect of instant riches for a lucky player after more than three months without a big winner. The numbers will be...}

\entryitemWithDescription{\hskip 0pt{}Cheating on your spouse is a crime in New York. The 1907 law may finally be repealed}{https://apnews.com/article/1012af35f2f79e599689e58b2e23e5fe}{ALBANY, N.Y. (AP) --- For more than a century, it has been a crime to cheat on your spouse in New York. But adultery may soon be legal in the Empire State thanks to a bill working its way through the New York Legislature, which would...}

\entryitemWithDescription{\hskip 0pt{}Bird flu is causing thousands of seal deaths. Scientists aren't sure how to slow it down}{https://apnews.com/article/80184a8793fbcc21fab01b1c90b0d71b}{PORTLAND, Maine (AP) --- Avian influenza is killing tens of thousands of seals and sea lions in different corners of the world, disrupting ecosystems and flummoxing scientists who don't see a clear way to slow the devastating virus. The...}

\entryitemWithDescription{\hskip 0pt{}Lorrie Moore wins National Book Critics Circle award for fiction, Judy Blume also honored}{https://apnews.com/article/400ebddb8e19b718d70caef00bf3bb57}{NEW YORK (AP) --- Lorrie Moore won the prize for fiction on Thursday, while Judy Blume and her longtime ally in the fight against book bans, the American Library Association were given honorary prizes by the National Book Critics Circle...}

\entryitemWithDescription{\hskip 0pt{}Alabama woman who faked kidnapping pleads guilty to false reporting}{https://apnews.com/article/a78891a5dd2fe93722e28a048788baf7}{BIRMINGHAM, Ala. (AP) --- An Alabama woman who claimed she was abducted after stopping her car to check on a wandering toddler on Thursday pleaded guilty to charges of giving false information to law enforcement. News outlets reported...}

\entryitemWithDescription{\hskip 0pt{}Roller ball candies linked to fatal choking and injury in children, CPSC warns}{https://apnews.com/article/fdd1dfb2208554fb3eb544b2f7ca6a7e}{Candy treats that use roller balls to let kids eat sweet liquid have been linked to choking, including at least one death, and should not be used, a federal safety agency warned Thursday. The U.S. Consumer Product Safety Commission said...}