\entryitemWithDescription{\hskip 0pt{}Laurent de Brunhoff, `Babar' heir and author, dies at age 98}{https://apnews.com/article/11e154513ae7406ea245be2789bc65e8}{NEW YORK (AP) --- ``Babar'' author Laurent de Brunhoff, who revived his father's popular picture book series about an elephant-king and presided over its rise to a global, multimedia franchise, has died. He was 98. De Brunhoff, a Paris...}

\entryitemWithDescription{\hskip 0pt{}Cameron Diaz and Benji Madden announce birth of baby boy named Cardinal}{https://apnews.com/article/ce5ed9f6e2735301dc8fd37b360d26f1}{Actress Cameron Diaz and her musician husband, Benji Madden, say they are ``blessed and grateful'' to have welcomed a baby boy --- Cardinal Madden --- to their family. The couple announced the arrival of their son in an Instagram post...}

\entryitemWithDescription{\hskip 0pt{}2 crew members die during `incident' on Holland America cruise ship}{https://apnews.com/article/f2f021eae8cab30cc03b356c77bb96fa}{FORT LAUDERDALE, Fla. (AP) --- Two crew members on a Holland America cruise ship died during an ``incident'' in the ship's engineering space, the cruise line said. The unidentified crew members died Friday while the Florida-based Nieuw...}

\entryitemWithDescription{\hskip 0pt{}Museum, historical group launch search for wreckage of ace pilot Richard Bong's crashed plane}{https://apnews.com/article/b9bfcbf584d7e6987f65d0cc6d571bde}{SUPERIOR, Wis. (AP) --- A Wisconsin museum is partnering with a historical preservation group in a search for the wreckage of World War II ace Richard Bong's plane in the South Pacific. The Richard I. Bong Veterans Historical Center in...}

\entryitemWithDescription{\hskip 0pt{}Endangered dolphins on course prevent racing at SailGP New Zealand in Christchurch}{https://apnews.com/article/d2698f9737dd09d0b508f14430031e99}{The presence of an endangered species of dolphins on the race course prevented sailing on the first day of the New Zealand leg of the SailGP series on Saturday. The race venue on Lyttelton Harbour near Christchurch on the South Island is...}

\entryitemWithDescription{\hskip 0pt{}Is there a winner of the \$977M Mega Millions jackpot? Numbers have been drawn and it's time to wait}{https://apnews.com/article/c0c579d6d29716483756f81646a7430f}{DES MOINES, Iowa (AP) --- The numbers were drawn Friday night for a nearly \$1 billion Mega Millions jackpot offering the prospect of instant riches for a lucky player after more than three months without a big winner. The numbers drawn...}

\entryitemWithDescription{\hskip 0pt{}A Romanian court rejects Andrew Tate's bid to get his confiscated assets returned}{https://apnews.com/article/a90b9ee6e91b0a2a4c58eeb3d8fd3304}{Associated Press (AP) --- A court in Romania's capital on Friday denied a request by online influencer Andrew Tate to return assets that were seized during investigations into the case in which he is charged with human trafficking, rape...}

\entryitemWithDescription{\hskip 0pt{}Auction of Pattie Boyd's trove of treasures surpasses expectations as it nets \$3.6 million}{https://apnews.com/article/112a13c039c162bfeff4133fb0bcb3a0}{LONDON (AP) --- The online auction of a trove of letters, photos and other items that Pattie Boyd, who was at the heart of the Swinging 60s, concluded Friday --- and it's safe to say that it really surpassed all expectations. Christie's...}

\entryitemWithDescription{\hskip 0pt{}British man who poisoned couple with fentanyl and monitored their death via app sentenced to life}{https://apnews.com/article/6d91b766b7db2cb55d9c643ec95f91f2}{LONDON (AP) --- A British IT worker who befriended and worked for an older couple, poisoned them with fentanyl and monitored their death with his cellphone was sentenced Friday to a minimum 37 years in prison. The sentencing of Luke D'...}

\entryitemWithDescription{\hskip 0pt{}More than 440,000 Starbucks-branded mugs recalled due to burn, laceration risk}{https://apnews.com/article/0a30ce4543c86b04f270650c91231ae5}{NEW YORK (AP) --- More than 440,000 Starbucks-branded mugs made by Nestle and sold during the winter holidays are being recalled after reports of some users receiving burns or lacerations, according to a federal safety agency. The U.S...}

\entryitemWithDescription{\hskip 0pt{}Stellantis recalls nearly 318,000 cars to replace side air bags that can explode and hurl shrapnel}{https://apnews.com/article/890aa14d1932f1581a8b425c11ed35dd}{DETROIT (AP) --- Stellantis is recalling nearly 318,000 Dodge and Chrysler sedans worldwide because the side air bag inflators can explode with too much force and hurl metal fragments at drivers and passengers. The recall covers air bag...}

\entryitemWithDescription{\hskip 0pt{}Drawing nears for \$997M Mega Millions jackpot}{https://apnews.com/article/252d67e8576ea1fb61ca813389a0af49}{DES MOINES, Iowa (AP) --- A nearly \$1 billion Mega Millions jackpot will be up for grabs Friday night, offering the prospect of instant riches for a lucky player after more than three months without a big winner. The numbers will be...}

\entryitemWithDescription{\hskip 0pt{}Cheating on your spouse is a crime in New York. The 1907 law may finally be repealed}{https://apnews.com/article/1012af35f2f79e599689e58b2e23e5fe}{ALBANY, N.Y. (AP) --- For more than a century, it has been a crime to cheat on your spouse in New York. But adultery may soon be legal in the Empire State thanks to a bill working its way through the New York Legislature, which would...}