\entryitemWithDescription{\hskip 0pt{}Andre Braugher died from lung cancer, rep for `Brooklyn Nine-Nine' and `Homicide' star says}{https://apnews.com/article/6aa6f46c6cf4c20500a8a96bfa1831cb}{LOS ANGELES (AP) --- Andre Braugher died from lung cancer, a representative said Thursday. When the Emmy-winning actor who starred in the series ``Brooklyn Nine-Nine'' and ``Homicide: Life on the Street'' died Monday at age 61, his...}

\entryitemWithDescription{\hskip 0pt{}A 4-month-old survived after a Tennessee tornado tossed him. His parents found him in a downed tree}{https://apnews.com/article/78b30d60f5e03c88837357b2cc85ec7e}{CLARKSVILLE, Tenn. (AP) --- A 4-month-old boy has survived after a tornado in Tennessee sucked him up from his family's mobile home, which was demolished in the storm. Sydney Moore told WSMV-TV that when the tornado hit their home in...}

\entryitemWithDescription{\hskip 0pt{}Air Jordans made for filmmaker Spike Lee are up for auction after being donated to Oregon shelter}{https://apnews.com/article/fd39eb136fae73dd8993398be8ae7564}{PORTLAND, Ore. (AP) --- The shiny, gold Nike sneakers were hard to miss in the donation pile at a shelter in Portland, Oregon, earlier this year. They were Air Jordan 3s, size 12 1/2, and one of just a few custom pairs that had been made...}

\entryitemWithDescription{\hskip 0pt{}Miljenko `Mike' Grgich, an immigrant who put Napa Valley on the world's wine map, dies at 100}{https://apnews.com/article/d96da71ce701b3e70d8a0a5ca37994c2}{Miljenko ``Mike'' Grgich, a celebrated winemaker who helped establish Napa Valley as one of the world's premier wine-making regions, has died. He was 100. Grgich died in his sleep Wednesday morning at his home in Calistoga, California...}

\entryitemWithDescription{\hskip 0pt{}Senator's son faces upgraded homicide charge in crash that killed North Dakota sheriff's deputy}{https://apnews.com/article/823c204771490facff9d611f8da39a3b}{BISMARCK, N.D. (AP) --- New charges approved Thursday against the 42-year-old son of U.S. Sen. Kevin Cramer included an upgraded homicide count in a crash that killed a North Dakota sheriff's deputy. Ian Cramer initially faced a...}

\entryitemWithDescription{\hskip 0pt{}Jury deliberating whether actor Jonathan Majors assaulted a girlfriend in New York last spring}{https://apnews.com/article/d60a7367c96cf36ca9f0661e798532f9}{NEW YORK (AP) --- A Manhattan jury will soon decide if Jonathan Majors is guilty of assaulting his girlfriend following two weeks of clashing narratives about whether the rising Hollywood star was the aggressor or victim during a chaotic...}

\entryitemWithDescription{\hskip 0pt{}Set of 6 Messi World Cup shirts sells for \$7.8 million at auction in New York}{https://apnews.com/article/7bfe6ccbddd25ea210ee651ae4ae9c1b}{NEW YORK (AP) --- Six jerseys worn by soccer superstar Lionel Messi during Argentina's winning run at last year's World Cup sold Thursday for \$7.8 million, the auction house Sotheby's announced. The final price for the shirts, each worn...}

\entryitemWithDescription{\hskip 0pt{}Former NFL player Adam `Pacman' Jones reaches plea deal over airport incident}{https://apnews.com/article/ac2907a52b0c277062c1bb9f9bf4ee05}{BURLINGTON, Ky. (AP) --- Former NFL player Adam ``Pacman'' Jones reached a plea agreement on a disorderly conduct charge Thursday after he was removed from a plane before takeoff at the Cincinnati/Northern Kentucky Airport in September...}

\entryitemWithDescription{\hskip 0pt{}A bull on the tracks at Newark station delays train traffic outside New York}{https://apnews.com/article/2618b54237d48fb944d146221b0d0798}{NEWARK, N.J. (AP) --- A loose bull in New Jersey's largest city found its way onto train tracks, snarling rail traffic for a while Thursday before it was captured, authorities said. The ruddy brown bull with long, dark-tipped horns stood...}

\entryitemWithDescription{\hskip 0pt{}The family of a Chicago woman who died in a hotel freezer agrees to a \$10 million settlement}{https://apnews.com/article/ecd3bd9d2fef9dac73d38af6a2f67b71}{CHICAGO (AP) --- The family of a Chicago woman who froze to death after she became locked in a hotel freezer has agreed to a \$10 million legal settlement. Kenneka Jenkins' mother, Tereasa Martin, will receive about \$3.7 million...}

\entryitemWithDescription{\hskip 0pt{}Warriors star Draymond Green suspended indefinitely by NBA}{https://apnews.com/article/39183c7c852b3492651c5b320349d019}{SAN FRANCISCO (AP) --- Golden State Warriors forward Draymond Green was suspended indefinitely by the NBA on Wednesday, less than 24 hours after he hit Phoenix Suns center Jusuf Nurkic in the face and received a Flagrant 2 foul and...}

\entryitemWithDescription{\hskip 0pt{}Pennsylvania is in its Taylor Swift era, her home state decides}{https://apnews.com/article/fadc2c3680d4ef82e905886bb90ed0c9}{HARRISBURG, Pa. (AP) --- She's Time magazine's person of the year. She's the most-played artist globally on Spotify. She's helmed the first tour to gross more than \$1 billion and then the highest-grossing concert film of all time. And...}

\entryitemWithDescription{\hskip 0pt{}Oprah Winfrey portrait — featuring the color purple — unveiled at National Portrait Gallery}{https://apnews.com/article/c6308c54b4d22a3c6e5c6408309e8a2a}{WASHINGTON (AP) --- It seemed only fitting that Oprah Winfrey chose to wear a flowing, full-length purple dress for her portrait unveiled Wednesday at the Smithsonian's National Portrait Gallery. She told the assembled crowd that she wore...}