\entryitemWithDescription{\hskip 0pt{}US Virgin Islands says it can't find Elon Musk to serve a subpoena in Jeffrey Epstein lawsuit}{https://apnews.com/article/bd53a39e1329e4616c84762a61552032}{NEW YORK (AP) --- The government of the U.S. Virgin Islands told a federal judge Monday that it can\textquotesingle t find billionaire Elon Musk to serve him with a subpoena for documents in its lawsuit seeking to hold JPMorgan Chase...}

\entryitemWithDescription{\hskip 0pt{}Court order that could end US health law's preventative care mandate put on hold}{https://apnews.com/article/9810503de44940b116329480e784a84d}{FILE - The healthcare.gov website is seen on Dec. 14, 2021, in Fort Washington, Md. A federal judge\textquotesingle s ruling striking down a part of the Affordable Care Act requiring most insurers to cover preventive care including...}

\entryitemWithDescription{\hskip 0pt{}Vice Media files for Chapter 11 bankruptcy, the latest in a string of digital media setbacks}{https://apnews.com/article/7eb3546352dc730050ef4dbe77d65c53}{Vice Media\textquotesingle s office building is seen in Los Angeles, Monday, May 15, 2023. Vice Media is filing for Chapter 11 bankruptcy protection, the latest digital media company to falter after a meteoric rise. (AP Photo/Jae C. Hong...}

\entryitemWithDescription{\hskip 0pt{}Pieces that may be from wetsuit, surfboard found after surfer attacked by shark off South Australia}{https://apnews.com/article/e1f32cea848416cc3b065de1fd890f2b}{In this image from a video, searchers on boats conduct an operation in waters in Elliston, Australia Saturday, May 13, 2023. Police continued to search Monday for remains of a 46-year-old surfer who was attacked by a shark off the south...}

\entryitemWithDescription{\hskip 0pt{}Five years after his Obama portrait, Kehinde Wiley is taking his art everywhere all at once}{https://apnews.com/article/cb7dfb58be7eb728203859b4e6063cd8}{Kehinde Wiley poses for a portrait at Sean Kelly Gallery, Thursday, April 27, 2023, in New York. (Photo by Charles Sykes/Invision/AP) NEW YORK (AP) --- Kehinde Wiley was already well into his influential art career when his portrait of...}

\entryitemWithDescription{\hskip 0pt{}World's oldest dog celebrates 31st birthday}{https://apnews.com/article/a240a83836d6909e6bc9d6926c9cde32}{This image provided by Guinness World Records shows Bobi. Guinness World Records says the world's oldest dog recently celebrated his 31st birthday. Bobi\textquotesingle s owner says a party was held Saturday, May 13, 2023 for the purebred...}

\entryitemWithDescription{\hskip 0pt{}2-time world champion Doyle Brunson, called the Godfather of Poker, dies at 89}{https://apnews.com/article/c2fbe4bcdbf56bb8331a2e84e5874462}{FILE - Doyle Brunson is pictured prior to play at the final table of the World Series of Poker on Nov. 8, 2011, in Las Vegas. Brunson, one of the most influential poker players of all time and a two-time world champion, died Sunday, May...}

\entryitemWithDescription{\hskip 0pt{}Horse dies at Churchill Downs, 8th recent fatality at home of Kentucky Derby}{https://apnews.com/article/6de38601fd41fb946c126fc5f780e3bc}{Horses come through the first turn during the 149th running of the Kentucky Derby horse race at Churchill Downs Saturday, May 6, 2023, in Louisville, Ky. (AP Photo/Julio Cortez) LOUISVILLE, Ky. (AP) --- A horse died Sunday after a race at...}

\entryitemWithDescription{\hskip 0pt{}Herders in Kenya kill 10 lions, including Loonkiito, one of the country's oldest}{https://apnews.com/article/dfde18abce78e71e8ec3ddd44c8b4269}{This photo provided by Lion Guardians shows the male lion named "Loonkiito" in Amboseli National Park, in southern Kenya on Feb. 20, 2023. One of Kenya\textquotesingle s oldest wild lions, Loonkiito, 19, was killed by herders and the...}

\entryitemWithDescription{\hskip 0pt{}Border crossings off from last week's highs as US pins hopes for order on mobile app}{https://apnews.com/article/410698368cdaa9b8adc820543d9b7bbc}{Venezuelan migrants rest inside their tents on the bank of the Rio Grande in Matamoros, Mexico, Sunday, May 14, 2023. As the U.S. ended its pandemic-era immigration restrictions, migrants are adapting to new asylum rules and legal...}

\entryitemWithDescription{\hskip 0pt{}Rockies' Feltner released from hospital after skull fracture, concussion from line drive}{https://apnews.com/article/902fcb5a8282c3306279b83efff1e482}{Colorado Rockies starting pitcher Ryan Feltner lies on the mound after getting hit by a single by Philadelphia Phillies\textquotesingle{} Nick Castellanos during the second inning of a baseball game Saturday, May 13, 2023, in Denver. (AP...}

\entryitemWithDescription{\hskip 0pt{}A Florida man living underwater won't resurface even after breaking the record}{https://apnews.com/article/1b7657c223a738c7a7b6b129dc4a928b}{In this photo provided by the Florida Keys News Bureau, diving explorer and medical researcher Dr. Joseph Dituri peers out of a large porthole, Saturday, May 13, 2023, at Jules\textquotesingle{} Undersea Lodge positioned at the bottom of...}

\entryitemWithDescription{\hskip 0pt{}Grizzlies suspend Ja Morant after another gun video appears on social media}{https://apnews.com/article/7fe15dae343f85d0366a4c959d5313b3}{Memphis Grizzlies guards Desmond Bane, left, and Ja Morant (12) laugh on the bench during the second half of Game 5 of the team\textquotesingle s first-round NBA basketball playoff series against the Los Angeles Lakers on Wednesday, April...}