\entryitemWithDescription{\hskip 0pt{}West Virginia's Huggins agrees to \$1M pay cut, 3-game suspension for homophobic slur}{https://apnews.com/article/77ce70b41112a0062421ad9405558473}{FILE - West Virginia head coach Bob Huggins calls to his players in the second half of a first-round college basketball game against Maryland in the NCAA Tournament in Birmingham, Ala., March 16, 2023. Huggins apologized Monday, May 8...}

\entryitemWithDescription{\hskip 0pt{}FDA panel backs over-the-counter sales of birth control pill}{https://apnews.com/article/d6e863b0d41a8c6c783c569773efa349}{This illustration provided by Perrigo in May 2023, depicts proposed packaging for the company\textquotesingle s birth control medication Opill. Federal health advisers said Wednesday, May 10, 2023, that the decades-old birth control pill...}

\entryitemWithDescription{\hskip 0pt{}`Please, man, don't shoot us': Witness says man shot 3 people, killing 1, in dispute over \$4}{https://apnews.com/article/ff4b54c105403173480ecd1d8aa78e82}{A gas station remains closed less than a week after a fatal shooting in Detroit, Michigan, Wednesday, May 10, 2023. Authorities in Detroit say a man fatally shot another customer inside a gas station and wounded two more in a dispute over...}

\entryitemWithDescription{\hskip 0pt{}Ex-Raider Henry Ruggs pleads guilty to driving drunk at 156 mph, causing fatal crash}{https://apnews.com/article/4f4fdd413e0f483ce07146be7ddde9a9}{Former Las Vegas Raiders player Henry Ruggs appears in court Wednesday, May 10, 2023, in Las Vegas. Ruggs plead guilty to driving his car drunk before causing a fiery crash that killed a woman. (AP Photo/John Locher) LAS VEGAS (AP) --- Ex...}

\entryitemWithDescription{\hskip 0pt{}Martin Scorsese set to stir Cannes again, 47 years after 'Taxi Driver'}{https://apnews.com/article/529f5f118fe0fed0ea1b07bd15220d93}{FILE - Martin Scorsese, left, and Robbie Robertson before they presented the film "Last Waltz," at the 31st Cannes International Film Festival. When Martin Scorsese premieres his latest film, "Killers of the Flower Moon," at the Cannes...}

\entryitemWithDescription{\hskip 0pt{}Topless protester briefly disrupts VW annual meeting}{https://apnews.com/article/e89a2d11bc7c30dc64ab01bceba96af9}{Climate activists are taken out of the venue of the annual shareholders\textquotesingle{} meeting of the Volkswagen AG in Berlin, Germany, Wednesday, May 10, 2023. (Britta Pedersen/dpa via AP) FRANKFURT, Germany (AP) --- Volkswagen...}

\entryitemWithDescription{\hskip 0pt{}Oprah teams with Arthur C. Brooks on book about happiness}{https://apnews.com/article/ca2de42e17c14af928ed90f8c2764667}{This cover image released by Portfolio Books shows ``Build the Life You Want: The Art and Science of Getting Happier,'' by Arthur C. Brooks and Oprah Winfrey, to be published Sept. 12 by Portfolio Books (Portfolio Books via AP) NEW YORK...}

\entryitemWithDescription{\hskip 0pt{}Long popular in Asia, floating solar catches on in US}{https://apnews.com/article/7316dbfe9db23363aacadcd133cbd408}{The sun rises over floating solar panels on May 3, 2023, in Selangor, Malaysia. Floating solar panel farms are beginning to boom in the United States after rapid growth in Asia. They\textquotesingle re attractive not just for their clean...}

\entryitemWithDescription{\hskip 0pt{}Disney board banned X-rated stores and liquor shops from property, overlooking prisons}{https://apnews.com/article/d0561ff56fd3aa40ebdb765b4a7896fc}{FILE - In this Jan. 9, 2019 photo, a statue of Walt Disney and Micky Mouse stands in front of the Cinderella Castle at the Magic Kingdom at Walt Disney World in Lake Buena Vista, Fla. The Walt Disney Co. will be laying off several...}

\entryitemWithDescription{\hskip 0pt{}1st babies born in Britain using DNA from 3 people}{https://apnews.com/article/6d826809d66a4474bc9dc455c475ad58}{FILE - An embryologist works on a petri dish at the Create Health fertility clinic in south London, Thursday, Aug. 14, 2013. Britain\textquotesingle s fertility regulator said the first babies created using an experimental technique...}

\entryitemWithDescription{\hskip 0pt{}Swiss villagers told to evacuate over Alpine rockslide alert}{https://apnews.com/article/59496f3e37ce0da985e11914dc040f51}{View of the village and the "Brienzer Rutsch", taken on Tuesday, 9 May 2023, in Brienz-Brinzauls, Switzerland. Authorities in eastern Switzerland have ordered residents of the tiny village of Brienz to evacuate by Friday evening because...}

\entryitemWithDescription{\hskip 0pt{}Fears over scores of zoo animals caught in Sudan crossfire}{https://apnews.com/article/cc77fd7ba679ebcd2c36e8163a649918}{In this undated photo released by Sara Abdalla, director of the zoological park at the University of Khartoum, a vervet monkey is pictured inside its enclosure in Khartoum, Sudan. The animal is one of dozens feared dead or missing inside...}

\entryitemWithDescription{\hskip 0pt{}Days after Texas bus stop crash, little info on the victims}{https://apnews.com/article/8fb9ba8f8bed0d1a77847fe85171fe9b}{Migrants hold flowers and listen to speakers during a vigil for the eight migrants that were killed and several others that were injured the day before while waiting at a bus stop, in Brownsville, Texas, Monday, May 8, 2023. (AP Photo/...}