\entryitemWithDescription{\hskip 0pt{}Armie Hammer avoids charges after sex assault investigation, says 'name has been cleared'}{https://apnews.com/article/9cf9ea7272a87041d7c7d01d52a33e12}{FILE - Armie Hammer appears at the Hollywood Film Awards in Beverly Hills, Calif., on Nov. 4, 2018. Hammer will not be charged after a long investigation of a woman\textquotesingle s allegation that he sexually assaulted her in 2017, Los...}

\entryitemWithDescription{\hskip 0pt{}Top speller in English to be crowned at Scripps National Spelling Bee finals}{https://apnews.com/article/1b09d39ba7631d26f3a3c833f7aeefea}{The 11 finalists for the Scripps National Spelling Bee pose for a picture after the day\textquotesingle s competition, Wednesday, May 31, 2023, in Oxon Hill, Md. Left to right-Shradha Rachamreddy, 13, from San Jose, Calif., Aryan Khedkar...}

\entryitemWithDescription{\hskip 0pt{}White House says Biden is 'fine' after he tripped and fell on stage at Air Force graduation}{https://apnews.com/article/79427949848742048600171770e33bc9}{President Joe Biden falls on stage during the 2023 United States Air Force Academy Graduation Ceremony at Falcon Stadium, Thursday, June 1, 2023, at the United States Air Force Academy in Colorado Springs, Colo. (AP Photo/Andrew Harnik...}

\entryitemWithDescription{\hskip 0pt{}Baseball legend Steve Garvey considering US Senate bid in California, energizing beleaguered GOP}{https://apnews.com/article/b36dfeab92966a1f6c9b6b23d191696c}{FILE - Former San Diego Padres Steve Garvey waves to fans before a baseball game against the St. Louis Cardinals Saturday, June 29, 2019, in San Diego. Garvey, who played in Los Angeles and San Diego, is considering entering California...}

\entryitemWithDescription{\hskip 0pt{}Charges dropped against man who served 21 years in prison for deaths of 2 Michigan hunters}{https://apnews.com/article/dcc72cef9f785cf95189162515627e2c}{DETROIT (AP) --- Prosecutors dropped murder charges Thursday against a man who spent nearly 21 years in prison for the fatal shooting of two Michigan hunters. Jeff Titus was released in February when authorities acknowledged that critical...}

\entryitemWithDescription{\hskip 0pt{}'Diablo IV' is almost here. What to know about the video game's coming release}{https://apnews.com/article/12d18dd3b42bd559fe53ca78ecd37fb0}{FILE - The Activision Blizzard Booth appears during the Electronic Entertainment Expo in Los Angeles on June 13, 2013. The release of ``Diablo IV'' is right around the corner. Early access for the highly anticipated action role-playing...}

\entryitemWithDescription{\hskip 0pt{}Authorities recover bodies of 2 sisters after vessel found submerged in Alaska; 2 still missing}{https://apnews.com/article/06b0767ef0399f28f77b6c4ea368604d}{This undated photo provided by James Solis shows Robert Solis, left and his partner Brandi Tyau, right. Robert Solis and Tyau were aboard the charter fishing vessel Awakin when it was scuttled Sunday in rough seas off the coast of...}

\entryitemWithDescription{\hskip 0pt{}New footprints revive hope in Colombia of finding four children missing in jungle}{https://apnews.com/article/4439c922047d8a72d0a0a3493869db4d}{Indigenous people line up upon arrival at the airport in San Jose del Guaviare, Colombia, to help search for four Indigenous children missing after a deadly plane crash, Sunday, May 21, 2023. The May 30 discovery of footprints of a small...}

\entryitemWithDescription{\hskip 0pt{}Tommy Prine doesn't dodge his father's legacy but makes his own way in compelling debut}{https://apnews.com/article/6132d674768cbb1c359ee95fbfffdff8}{Tommy Prine poses for a portrait in Nashville, Tenn., on April 25, 2023, to promote his debut album ``This Far South,'' set for release on June 23. (AP Photo/George Walker IV) NASHVILLE, Tenn. (AP) --- Standing before a packed house at...}

\entryitemWithDescription{\hskip 0pt{}Average long-term US mortgage rate climbs to 6.79\% this week, highest level since November}{https://apnews.com/article/319410c1539ec119f061744412a5f5de}{Homes in a new development in Eagleville, Pa., are shown on Friday, April 28, 2023. On Thursday, Freddie Mac reports on this week\textquotesingle s average U.S. mortgage rates. (AP Photo/Matt Rourke) LOS ANGELES (AP) --- The average long...}

\entryitemWithDescription{\hskip 0pt{}German soccer mourns death of 15-year-old player who died after tournament brawl}{https://apnews.com/article/724a0b6282eef694da2fc68ccd8fa965}{Players observe a minute\textquotesingle s silence in honor of the 15-year-old who died during a youth soccer tournament, before the first leg of the German Bundesliga relegation soccer match between Stuttgart and Hamburger at the...}

\entryitemWithDescription{\hskip 0pt{}Store owner charged with killing a teen shot at people he suspected of shoplifting before}{https://apnews.com/article/5740e9443bd1c3bd981d03bb57e0d2f7}{Mourners stop by a memorial to Cyrus Carmack-Belton on Thursday, June 1, 2023, in Columbia, S.C. Authorities said Carmack-Belton, 14, was shot and killed by a store owner who wrongly suspected him of shoplifting. (AP Photo/Jeffrey...}

\entryitemWithDescription{\hskip 0pt{}'Do I have regrets? ... Hell yeah,' says Davenport mayor after partial collapse of Iowa building}{https://apnews.com/article/3c07ad16dd48457e2adcaf41f000fc77}{After asking a group of about 50 people gathered for a vigil to remain silent for five minutes in honor of the five people still unaccounted for, Raquel Sipp kneels with a candle at the scene of where an apartment building partially...}