\entryitemWithDescription{\hskip 0pt{}North Korea tests submarine-launched missile, Seoul says}{https://apnews.com/article/a08750c243ebeb6c0c444f9b18aa5ab3}{SEOUL, South Korea (AP) --- North Korea said Monday it test-fired two cruise missiles from a submarine off its east coast, the latest in the country\textquotesingle s series of weapons tests. The test on Sunday came a day before the U.S...}

\entryitemWithDescription{\hskip 0pt{}As Biden weighs Willow, he blocks other Alaska oil drilling}{https://apnews.com/article/ff58d8a7fda5a00a1b4bbbbebd7d8781}{FILE - This 2019 aerial photo provided by ConocoPhillips shows an exploratory drilling camp at the proposed site of the Willow oil project on Alaska\textquotesingle s North Slope. Pressure is building on the social media platform TikTok...}

\entryitemWithDescription{\hskip 0pt{}How does Oscars voting work? This is how winners are decided}{https://apnews.com/article/f50a08ec58233f666ad16598c7f3162b}{Antje Menikheim, left, lead scenic painter for Sunday\textquotesingle s 95th Academy Awards, and scenic artist Michael Thomas prepare Oscar statues for the event, Wednesday, March 8, 2023, near the Dolby Theatre in Los Angeles. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}8 dead after smuggling boats capsize off San Diego coast}{https://apnews.com/article/d98169e8b193a0a00cee403617d59a10}{Two boats, one overturned, sit on Blacks Beach, Sunday, March 12, 2023, in San Diego. Authorities say multiple people were killed when two suspected smuggling boats overturned off the coast San Diego, and crews were searching for other...}

\entryitemWithDescription{\hskip 0pt{}Sister grieves for American killed in Mexico kidnapping}{https://apnews.com/article/34a01e7ad5f6a5ece33a3f086796de9c}{Elder Sharon Hammond uses a tissue during a vigil for a group of Americans recently kidnapped in Mexico, at Word of God Ministries in Scranton, S.C., Wednesday, March 8, 2023. Two of the four Americans, all from South Carolina, were...}

\entryitemWithDescription{\hskip 0pt{}As atmospheric river exits, another awaits to hit California}{https://apnews.com/article/aad89f72c48576f28afa907e332f2992}{A Northern California agricultural community famous for its strawberry crop has been forced to evacuate after the Pajaro River's levee was breached by flooding from a new atmospheric river that pummeled the state. (March 11) A boy and a...}

\entryitemWithDescription{\hskip 0pt{}US calls Iran's prisoner swap claim a 'cruel lie'}{https://apnews.com/article/18a94bad395c31990b7d5afe52ea5396}{This is a locator map for Iran with its capital, Tehran. (AP Photo) DUBAI, United Arab Emirates (AP) --- Iran\textquotesingle s top diplomat claimed Sunday that a prisoner swap was near with the U.S., though he offered no evidence to...}

\entryitemWithDescription{\hskip 0pt{}Gun bills coming in Michigan after 2nd school mass shooting}{https://apnews.com/article/4ec6ceac1459d0d9a2af94af6a753d96}{FILE - Michigan state Rep. Brenda Carter, D-Pontiac, left, and state Sen. Rosemary Bayer, D-Keego Harbor, join hands during a news conference to call for gun reform, Feb. 20, 2023, in Lansing, Mich. Michigan Democrats are poised to bring...}

\entryitemWithDescription{\hskip 0pt{}Yellen: No federal bailout for collapsed Silicon Valley Bank}{https://apnews.com/article/94f2185742981daf337c4691bbb9ec1e}{Treasury Secretary Janet Yellen listens as she testifies during a House Ways and Means committee hearing on President Joe Biden\textquotesingle s fiscal year 2024 budget request, Friday, March 10, 2023, on Capitol Hill in Washington. (AP...}

\entryitemWithDescription{\hskip 0pt{}How BBC host's tweet, suspension upended UK's sports weekend}{https://apnews.com/article/edb71aac173bee73d279af6c30eed7c1}{Soccer broadcaster Gary Lineker arrives ahead of the English Premier League soccer match between Leicester City and Chelsea, at the King Power Stadium, in Leicester, England, Saturday, March 11, 2023. (Mike Egerton/PA via AP) LONDON...}

\entryitemWithDescription{\hskip 0pt{}Youngkin scores some legislative wins as he eyes White House}{https://apnews.com/article/95a823d446c21524d17cbe6fb05614df}{FILE - Virginia Gov. Glenn Youngkin speaks to members of the press inside the Rotunda of the state Capitol building on Feb. 25, 2023, in Richmond, Va. In two years as Virginia\textquotesingle s governor, Republican Glenn Youngkin has gone...}

\entryitemWithDescription{\hskip 0pt{}Iraqi PM promises action to tackle crippling climate change}{https://apnews.com/article/a110e41a9f1c70b61ab5fa363992a624}{FILE - Water buffalo herders in the marshes of Chibayish feed their animals after back to back drought severely reduced available food stocks in Dhi Qar province, Iraq, on Nov. 19, 2022. Iraq\textquotesingle s prime minister Sunday March...}

\entryitemWithDescription{\hskip 0pt{}Saudi Arabia's golf case threatens to spill kingdom secrets}{https://apnews.com/article/edcd86df5ff12fa067505afd98b18a84}{FILE - Former President Donald Trump, left, talks with Yasir Al-Rumayyan, governor of Saudi Arabia\textquotesingle s Public Investment Fund, center, and Majed Al-Sorour, CEO of Golf Saudi, on the 16th hole during the first round of the...}