\entryitemWithDescription{\hskip 0pt{}Fatal crash sparks fire on major Connecticut highway bridge}{https://apnews.com/article/5f73b77008ae718f4919646583474e40}{In this photo provided by the Connecticut State Police, massive plumes of smoke rise from a fire resulting from crash involving a fuel truck and a car on the Gold Star Memorial Bridge in Groton, CT., Friday, April 21, 2023. Flames spread...}

\entryitemWithDescription{\hskip 0pt{}Vermont governor signs bill raising marriage age to 18}{https://apnews.com/article/f79af8798cd4f5adfa96fdb15f297275}{MONTPELIER, Vt. (AP) --- A new Vermont law that raises the eligibility age for marriage to 18 takes effect in July. Republican Gov. Phil Scott signed the legislation on Thursday, making Vermont the eighth state in the country to end child...}

\entryitemWithDescription{\hskip 0pt{}Feds get first guilty plea in Michigan marijuana board probe}{https://apnews.com/article/d811aa7617dadbe1e8244afd010012db}{FILE - Rick Johnson chairs the committee as it meets before a capacity crowd in Lansing, Mich., June 26, 2017, at the first open meeting of the Michigan Medical Marijuana Board. Federal authorities said Thursday, April 6, 2023, that...}

\entryitemWithDescription{\hskip 0pt{}NFL suspends 5 players for violating gambling policy}{https://apnews.com/article/3dc7890fc340b58ff6fcdd88cb9c939d}{FILE - Detroit Lions defensive back C.J. Moore (38), on special teams, reacts after running out of bounds on a fake punt during the second half of an NFL football game against the Los Angeles Rams Sunday, Oct. 24, 2021, in Inglewood...}

\entryitemWithDescription{\hskip 0pt{}Early morning fire destroys wing of Idaho high school}{https://apnews.com/article/cd0c0edfb2200358590d0b2d301fdb69}{In this image taken from video from KIFI Local News 8, firefighters work on the scene of an early morning fire at a large high school in Pocatello, Idaho, Friday, April 21, 2023. The Pocatello Fire Department said the fire at Highland...}

\entryitemWithDescription{\hskip 0pt{}Toronto fires Nick Nurse, who led Raptors to 2019 NBA title}{https://apnews.com/article/c2b7dc404915ee3ae12fe1a52e589830}{Toronto Raptors head coach Nick Nurse directs his team during the first half of an NBA basketball game against the Charlotte Hornets in Charlotte, N.C., Sunday, April 2, 2023. Toronto won 128-108. (AP Photo/Nell Redmond) TORONTO (AP...}

\entryitemWithDescription{\hskip 0pt{}Wrexham and Ryan Reynolds looking for Hollywood ending}{https://apnews.com/article/3ce5b60b2b0dbd88660d2772c8692f39}{FILE - Wrexham owners Ryan Reynolds, center right, and Rob McElhenney, center left, react during the National League match between Wrexham and Notts County at the Racecourse Ground, Wrexham, Wales, Monday April 10, 2023. It...}

\entryitemWithDescription{\hskip 0pt{}Dame Edna actor Barry Humphries stable in Sydney hospital}{https://apnews.com/article/9211136232cdb59be4a08768de4c80a7}{Barry Humphries arrives for the Oldie of the Year awards, at Simpsons-in-the-Strand, London, on Feb. 2, 2016. Tony Award-winning comedian Barry Humphries, renowned for his garish stage persona Dame Edna Everage, a condescending and...}

\entryitemWithDescription{\hskip 0pt{}4 million apply for tickets for Paris Olympics in lottery}{https://apnews.com/article/ba13450b8854210860cd463db2db36f9}{Tony Estanguet, president of the Paris 2024 Olympics organizing committee, rides a boat down the Seine River on the route that will be used for the opening ceremony of the Games, in Paris, Friday, April 14, 2023. Officials say more than...}

\entryitemWithDescription{\hskip 0pt{}Belgian foundation to exhibit auctioned T. rex in Antwerp}{https://apnews.com/article/dcdad6d6c0c5a94bda7b4980a30c5f30}{Cyril Koller, CEO of auction house Koller, stands next to the head of the skeleton of a Tyrannosaurus rex named Trinity, during an auction in Zurich, Switzerland on Tuesday, April 18, 2023. The 293 T. rex bones were assembled into a...}

\entryitemWithDescription{\hskip 0pt{}Emily in Paris: Parisians face influx of Netflix hero's fans}{https://apnews.com/article/0df557a019cb245013ac399282be8adf}{People walk past the "Modern bakery", Place de d\textquotesingle Estrapade, in Paris, Wednesday, April 19, 2023. The immense success of the Netflix series "Emily in Paris" has transformed a quiet, untouched square in the French capital...}

\entryitemWithDescription{\hskip 0pt{}Family joins rescued Indian climber being treated in Nepal}{https://apnews.com/article/d0dfd2935b31b83a7b82b5a1366e5002}{Family members react as an injured Indian climber Anurag Maloo who was rescued from Annapurna region is airlifted to Medicity hospital in Kathmandu, Nepal, Thursday, April 20, 2023. The Indian climber who fell into a 300-meter (980-foot...}

\entryitemWithDescription{\hskip 0pt{}Toyota's new president vows to step up electric vehicle push}{https://apnews.com/article/4bf350ee9df04d55815e01901e634040}{Koji Sato, President of Toyota Motor Co., poses for a photo at Toyota's office in Tokyo, Friday, April 21, 2023. Toyota's new president Sato has promised what he called an aggressive shift on ``electrification,'' while acknowledging...}