\entryitemWithDescription{\hskip 0pt{}NASA spacecraft discovers tiny moon around asteroid during close flyby}{https://apnews.com/article/bc24131a8bd9dc9161ab8793e7693f45}{CAPE CANAVERAL, Fla. (AP) --- The little asteroid visited by NASA's Lucy spacecraft this week had a big surprise for scientists. It turns out that the asteroid Dinkinesh has a dinky sidekick --- a mini moon. The discovery was made during...}

\entryitemWithDescription{\hskip 0pt{}Businessman sentenced in \$180 million bank fraud that paid for lavish lifestyle, classic cars}{https://apnews.com/article/d0c9a4a2a66fb88a832a613a8560c49c}{CLEVELAND (AP) --- A businessman who orchestrated a \$180 million check-kiting scheme and used the proceeds to live a lavish lifestyle and amass one of the world's most revered classic car collections has been sentenced to more than eight...}

\entryitemWithDescription{\hskip 0pt{}Car crashes through gate at South Carolina nuclear plant before pop-up barrier stops it}{https://apnews.com/article/9cd18a2f7b883a4af27c669c8d0dfb26}{SENECA, S.C. (AP) --- A driver tried to crash through the exit gates of a South Carolina nuclear plant Thursday night about an hour after security asked the same car to leave when it tried to enter, authorities said. A pop-up security...}

\entryitemWithDescription{\hskip 0pt{}Winds from Storm Ciarán whip up a wildfire in eastern Spain as 850 people are evacuated}{https://apnews.com/article/1381dedd0b283864c63af34e002cf81c}{MADRID (AP) --- A wildfire abetted by storm winds in eastern Spain has burned some 2,000 hectares (4,900 acres) of land and forced the evacuation of 850 people from four towns, officials said Friday. Some 200 firefighters and army...}

\entryitemWithDescription{\hskip 0pt{}World Series averaged 9.11 million viewers, making it the least-watched Fall Classic in TV history}{https://apnews.com/article/f0eb9837a3d8bfa529fed811a6417057}{The Texas Rangers 5-0 victory over the Arizona Diamondbacks for their first championship on Wednesday night drew the largest audience of this World Series. However, it was not enough to prevent the five-game series from being the least...}

\entryitemWithDescription{\hskip 0pt{}Utah woman's leg amputated after she was attacked by her son's dogs in her own backyard}{https://apnews.com/article/91fd2e4174717e804756107759ac1fa0}{TAYLORSVILLE, Utah (AP) --- A 63-year-old Utah woman had a leg amputated after being attacked by her son's dogs in her own backyard in a Salt Lake City suburb. Officers who arrived at the home in Taylorsville had to shoot and kill one of...}

\entryitemWithDescription{\hskip 0pt{}Listen to the last new Beatles' song with John, Paul, George, Ringo and AI tech}{https://apnews.com/article/fbce70071b4624f0d90bd18347f20fc6}{LOS ANGELES (AP) --- The final Beatles recording is here. Titled ``Now and Then,'' the almost impossible-to-believe track is four minutes and eight seconds of the first and only original Beatles recording of the 21st century. There's a...}

\entryitemWithDescription{\hskip 0pt{}Uber and Lyft to pay \$328 million to settle dispute over taxes and fees paid by New York drivers}{https://apnews.com/article/9ae3f629cf32d3f2fb6c39b8ffcc6cc6}{ALBANY, N.Y. (AP) --- Uber and Lyft will pay a combined \$328 million to settle complaints that they improperly saddled their New York drivers with taxes and fees that should have been been paid by passengers, state Attorney General...}

\entryitemWithDescription{\hskip 0pt{}Cedar Fair and Six Flags will merge to create a playtime powerhouse in North America}{https://apnews.com/article/3c7cb2fcce6b3125385fdedb1539199c}{Cedar Fair and Six Flags are merging to create an expansive amusement park operator with operations spread across 17 U.S. states and three countries. The combined company, worth more than \$3.5 billion, will boast 27 amusement parks, 15...}

\entryitemWithDescription{\hskip 0pt{}Asia's first Gay Games to kick off in Hong Kong, fostering hopes for wider LGBTQ+ inclusion}{https://apnews.com/article/b7f01cd492f445d04aa9d1eb2ae7ff05}{HONG KONG (AP) --- Football enthusiast Gina Benjamin is not just training for victory in the upcoming Gay Games in Hong Kong, but she's also on a mission to help push for legal reform for same-sex marriage. After moving to Hong Kong from...}

\entryitemWithDescription{\hskip 0pt{}A lunch host is accused of killing her ex-husband's parents and aunt with poisonous mushrooms}{https://apnews.com/article/18b4537159dc172592f8c58f4261031f}{CANBERRA, Australia (AP) --- The host of a weekend family lunch at her Australian country home was charged Thursday with murdering her ex-husband's parents and aunt with poisonous mushrooms and attempting to murder a fourth guest, police...}

\entryitemWithDescription{\hskip 0pt{}Birds in North America will be renamed to avoid any `harmful' historical associations with people}{https://apnews.com/article/aee0f0b0d1cc9ae3326bc44a2d1f55e8}{Birds in North America will no longer be named after people, the American Ornithological Society announced Wednesday. Next year, the organization will begin to rename around 80 species found in the U.S. and Canada. ``There is power in a...}

\entryitemWithDescription{\hskip 0pt{}Bob Knight, Indiana's combustible coaching giant, dies at age 83}{https://apnews.com/article/c29a7cb601f64e9181564037e8c78758}{BLOOMINGTON, Ind. (AP) --- Bob Knight, the brilliant and combustible coach who won three NCAA titles at Indiana and for years was the scowling face of college basketball, has died. He was 83. Knight's family made the announcement on...}