\entryitemWithDescription{\hskip 0pt{}Connecticut lawmakers vote to allow people to use deadly force as the bear population grows}{https://apnews.com/article/9fb879bdde9e38339159f0e1b72c0e98}{FILE - A black bear that had been previously tranquilized and removed from a Waterbury, Conn., neighborhood earlier in the year chews on a garbage container in Wolcott, Conn., Sept. 26, 2006. Connecticut lawmakers voted Friday, June 2...}

\entryitemWithDescription{\hskip 0pt{}Retired Phoenix police officer in landmark Miranda rights case dies at 87}{https://apnews.com/article/eb0453f8239346987404af419732bbc2}{FILE - Retired Phoenix Police Capt. Carroll Cooley demonstrates Wednesday, March 13, 2013, at the Phoenix Police Museum in Phoenix, how Ernesto Miranda was fingerprinted on the same fingerprinting device used on Miranda. Cooley, the...}

\entryitemWithDescription{\hskip 0pt{}Churchill Downs moves meet to Ellis Park to examine protocols following 12 horse deaths}{https://apnews.com/article/04ace82685afa4b2e1f242d5ab8be961}{FILE - Javier Castellano, atop Mage, third from left, is seen behind with others behind the pack as they make the first turn while competing in the 149th running of the Kentucky Derby horse race at Churchill Downs Saturday, May 6, 2023...}

\entryitemWithDescription{\hskip 0pt{}Community mourns teenager's death after gas station owner charged with murder}{https://apnews.com/article/90a9781fa0be00ffb17647d32d5d42f4}{A memorial for Cyrus Carmack-Belton is seen on Thursday, June 1, 2023, in Columbia, S.C. Authorities said Carmack-Belton, 14, was shot and killed by a store owner who wrongly suspected him of shoplifting. (AP Photo/Jeffrey Collins...}

\entryitemWithDescription{\hskip 0pt{}Missouri professor not guilty by reason of insanity in stabbing death of colleague}{https://apnews.com/article/6dc50db3584e4f7bf4ade5799ea30d92}{Missouri State history instructor Edward Gutting was found not guilty of first-degree murder of the stabbing death of colleague Marc Cooper by reason of mental disease or defect by Greene County Judge David Jones on Friday, June 2, 2023...}

\entryitemWithDescription{\hskip 0pt{}French Open lets Belarus' Sabalenka skip standard news conference after questions about Ukraine war}{https://apnews.com/article/6ac559852adb80d3922e296be67ed2a5}{Aryna Sabalenka of Belarus reacts during her third round match of the French Open tennis tournament against Russia\textquotesingle s Kamilla Rakhimova, at the Roland Garros stadium in Paris, Friday, June 2, 2023. (AP Photo/Thibault Camus...}

\entryitemWithDescription{\hskip 0pt{}8 construction workers injured as building partially collapses during concrete mishap in New Haven}{https://apnews.com/article/88c3d359db65680790243e54b6ebabe2}{Firefighters rescue a worker after the partial collapse of a building under construction, Friday, June 2, 2023, in New Haven, Conn. The building, near the Yale School of Medicine, partially collapsed when a concrete pour went awry...}

\entryitemWithDescription{\hskip 0pt{}British teen reported to anti-terror police by mother gets life sentence with minimum 6-year term}{https://apnews.com/article/b58f21b238bcfc71d6e4bab8579210c6}{Undated handout photo issued by the Metropolitan Police of Matthew King, 19, from Wickford in Essex, Britain. A teenage man who was reported to British anti-terror authorities by his mother was jailed for life on Friday, June 2, 2023...}

\entryitemWithDescription{\hskip 0pt{}Disney lawsuit judge removes himself from case but not for reasons cited by DeSantis}{https://apnews.com/article/f3d96990884dc7f5b85e26e785f3a8d9}{Travelers check out a jumbo screen projecting images of Walt Disney World in the east hall atrium at Orlando International Airport, Thursday, May 25, 2023 in Orlando, Fla. Auto club AAA said this summer could be ``one for the record...}

\entryitemWithDescription{\hskip 0pt{}Haitian businessman gets life sentence in 2021 assassination of Haiti's president}{https://apnews.com/article/3b1803079ec5972e92f829fbd6f8fc7a}{FILE - An image of Haitian President Jovenel Moïse is displayed at a news conference, Feb. 14, 2023, in Miami. Rodolphe Jaar, a dual Haitian-Chilean businessman who helped former Colombian soldiers obtain weapons to assassinate Moïse in...}

\entryitemWithDescription{\hskip 0pt{}Cynthia Weil, Grammy winning lyricist who had hits with husband Barry Mann, dead at 82}{https://apnews.com/article/8fed882b68674e76aca9f711fd56495f}{FILE - Barry Mann, left, and Cynthia Weil accept the BMI Icon award at the 64th annual BMI Pop Awards on, May 10, 2016, in Beverly Hills, Calif. Weil, a Grammy-winning lyricist of great range and endurance who enjoyed a decades-long...}

\entryitemWithDescription{\hskip 0pt{}Chase says online banking issue now resolved after bug causes double transactions and fees}{https://apnews.com/article/fe9a4dbe66a677c8c7ca8efcb6be88f6}{FILE - Chase Bank ATMs are shown, Thursday, March 25, 2021, in New York. Customers of Chase's online banking services were seeing double transactions, fees and/or payments in their accounts, with the situation not immediately being...}

\entryitemWithDescription{\hskip 0pt{}Wegmans is closing one of its largest grocery stores. Its unusual location hurt business}{https://apnews.com/article/508bbf4866262825cac1d5fbdf04c391}{CORRECTS DATE OF ANNOUNCEMENT - FILE - A Wegmans sign is attached to the outside of a Wegmans supermarket location, Tuesday, Dec. 20, 2022, in Westwood, Mass. The Wegmans supermarket chain is closing one of its largest and most unusual...}