\entryitemAp{\hskip 0pt{}T-Mobile says data on 37 million customers stolen}{https://apnews.com/article/87d107f039a2aeb8ad5e4b215c66eead}{FILE - The T-Mobile logo is seen on a storefront, Oct. 14, 2022, in Boston. The U.S. wireless carrier T-Mobile said Thursday, Jan. 19, 2023, that an unidentified malicious intruder breached its network in late November and stole data on...}

\entryitemAp{\hskip 0pt{}Biden on classified docs discovery: 'There's no there there'}{https://apnews.com/article/f2384a87dcddbd38796f63e1269c6baf}{President Joe Biden returns a salute as he boards Air Force One at Andrews Air Force Base, Md., Thursday, Jan. 19, 2023, en route to California. (AP Photo/Jess Rapfogel) APTOS, Calif. (AP) --- A frustrated President Joe Biden said...}

\entryitemAp{\hskip 0pt{}Polar bear emerged unseen from squall to kill mother, son}{https://apnews.com/article/d4269df76e01a894e86c7f2ea0c66711}{The view from the front of the school in in Wales, Alaska, where a 24-year-old woman and her 1-year-old son were killed in an encounter with a polar bear on Tuesday, Jan. 17, 2023, is seen in this photo taken on Sunday, Jan. 15, 2023, by...}

\entryitemAp{\hskip 0pt{}Oregon's drug decriminalization gets poor marks on audit}{https://apnews.com/article/8629d6e62bff151afbbdb3a37c2206ae}{FILE - A woman enters the Great Circle drug treatment center in Salem, Ore., on March 8, 2022. Two years ago, Oregonians voted to decriminalize drugs and dedicate hundreds of millions of dollars to treatment services, but the state...}

\entryitemAp{\hskip 0pt{}Supreme Court has failed to find leaker of abortion opinion}{https://apnews.com/article/59a40974e39a67c2ab859ba0c21c785e}{FILE - Light illuminates part of the Supreme Court building at dusk on Capitol Hill in Washington, Nov. 16, 2022. The Supreme Court said Thursday, Jan. 19, 2023, that it has not determined who leaked a draft of the court\textquotesingle s...}

\entryitemAp{\hskip 0pt{}Investigation? Review? Biden faces a messaging dilemma}{https://apnews.com/article/58228d94cdcfe4ebe00521b049037868}{White House press secretary Karine Jean-Pierre speaks during the daily briefing at the White House in Washington, Wednesday, Jan. 18, 2023. (AP Photo/Susan Walsh) WASHINGTON (AP) --- When Hillary Clinton was running for president, her...}

\entryitemAp{\hskip 0pt{}Twinkle, twinkle fading stars: Hiding in our brighter skies}{https://apnews.com/article/e8ff324175e57a7de092859941f57499}{FILE - Dave Cooke observes the Milky Way over a frozen fish sanctuary in central Ontario, north of Highway 36 in Kawartha Lakes, Ontario, Canada, early Sunday, March 21, 2021. According to research published in the journal Science on...}

\entryitemAp{\hskip 0pt{}Say cheese! Galactic photo shoot captures 3 billion stars}{https://apnews.com/article/60fecb7e18e0ad9b247b8d7aa75a4b3c}{This image made available by the National Science Foundation\textquotesingle s NOIRLab in January 2023 shows the galactic plane of the Milky Way galaxy. Astronomers have captured more than 3 billion stars and galaxies in one of the...}

\entryitemAp{\hskip 0pt{}By the numbers: President Biden at the two-year mark}{https://apnews.com/article/fc93b564f7d721e4680861c261420afa}{FILE - Joe Biden is sworn in as the 46th president of the United States by Chief Justice John Roberts as Jill Biden holds the Bible during the 59th Presidential Inauguration at the U.S. Capitol in Washington, Jan. 20, 2021. (AP Photo/...}

\entryitemAp{\hskip 0pt{}Religious leaders sue to block Missouri's abortion ban}{https://apnews.com/article/05d21a1234877ffcd358ad74bebe4472}{Clergy who filed suit seeking to overturn Missouri's abortion law and other opponents of the law hold a March through downtown St. Louis on Thursday, Jan. 19, 2023. The suit says Missouri legislators invoked their religious beliefs while...}

\entryitemAp{\hskip 0pt{}Alec Baldwin to be charged with manslaughter in set shooting}{https://apnews.com/article/8c76eddb8a6418419078903d24ec3813}{FILE - Actor Alec Baldwin attends a news conference at United Nations headquarters, on Sept. 21, 2015. A Santa Fe district attorney is prepared to announce whether to press charges in the fatal 2021 film-set shooting of a cinematographer...}

\entryitemAp{\hskip 0pt{}AI tools can create new images, but who is the real artist?}{https://apnews.com/article/1c6d9e0e260e2d135a3e3bf98d5493df}{A visitor looks at artist Refik Anadol\textquotesingle s "Unsupervised" exhibit at the Museum of Modern Art, Wednesday, Jan. 11, 2023, in New York. The new AI-generated installation is meant to be a thought-provoking interpretation of the...}

\entryitemAp{\hskip 0pt{}Cardinal says book by Benedict XVI's secretary 'unseemly'}{https://apnews.com/article/ac8dbaf0a4ed457d06ae964d08cac3c2}{FILE - Cardinal Christoph Schoenborn attends a press conference to present the post-synodal apostolic exhortation \textquotesingle{} Amoris Laetitia \textquotesingle{} (The Joy of Love), at the Vatican, on April 8, 2016. The archbishop of...}