\entryitemWithDescription{\hskip 0pt{}Queen Camilla: Charles' wife gets title on coronation invite}{https://apnews.com/article/0f06f30d457482cd7f26e14cbff3f5ca}{This photo released by Buckingham Palace on Tuesday, April 4, 2023 displays the invitation to the Coronation of Britain\textquotesingle s King Charles III in Westminster Abbey. King Charles III's wife has been officially identified as...}

\entryitemWithDescription{\hskip 0pt{}Catan board game creator, Klaus Teuber, dies at 70}{https://apnews.com/article/83bcfb293a020fae2b3b25e95171f9e4}{FILE - Klaus Teuber, a dental technician from Darmstadt, presents his game "The Settlers of Catan", Friday, Sept. 29, 1995, in Frankfurt, Germany. Teuber, creator of the hugely popular Catan board game in which players compete to build...}

\entryitemWithDescription{\hskip 0pt{}Transgender bathroom bill approved in Kansas; veto expected}{https://apnews.com/article/cbdc14be5bf1fb6e1a0749cad52e8ebc}{Ian Benalcazar, far right, a 13-year-old transgender boy from Lawrence, Kan., speaks outside the Kansas Statehouse during a rally on Transgender Day of Visibility, Friday, March 31, 2023, in Topeka, Kan. Ian is among more than 100 people...}

\entryitemWithDescription{\hskip 0pt{}Funeral held for custodian killed in Nashville attack}{https://apnews.com/article/51fe8cbb5b5cb398f7dc2b2009862d41}{FILE - This photo provided by the family of Michael Hill in March 2023 shows Adriene Joy Hill, left, with Michael Hill. Family and friends of Michael Hill, the 61-year-old custodian killed during a shooting on Monday, March 27, at a small...}

\entryitemWithDescription{\hskip 0pt{}New IRS leader promises faster, easier tax filing process}{https://apnews.com/article/ab6ef1d350e0de5f1a64a5b3ba140661}{Treasury Secretary Janet Yellen congratulates new IRS commissioner Danny Werfel after the swearing-in at the IRS headquarters in Washington, Tuesday, April 4, 2023. (AP Photo/Jose Luis Magana) WASHINGTON (AP) --- New IRS Commissioner...}

\entryitemWithDescription{\hskip 0pt{}In a first, EPA survey puts a number on lead pipes around US}{https://apnews.com/article/55dc1a30936940312778bc5143166e8e}{FILE - A lead water service line from 1927 lays on the ground on a residential street after being removed on June 17, 2021, in Denver. Some 9.2 million lead pipes carry water into homes across the U.S., with more in Florida than any other...}

\entryitemWithDescription{\hskip 0pt{}Eyedrops maker couldn't ensure factory was sterile, FDA says}{https://apnews.com/article/1e266befa854dc7c0ce65def0da9a0bc}{This image provided by Global Pharma Healthcare on Feb. 2, 2023 shows packaging for their Artificial Tears Lubricant Eye Drops product, distributed by EzriCare. Global Pharma Healthcare, the manufacturer of eyedrops recently linked to...}

\entryitemWithDescription{\hskip 0pt{}Kentucky high school football player dies after head injury}{https://apnews.com/article/23375e7e485c4aa4028ef3ad5c744386}{SOMERSET, Ky. (AP) --- A Kentucky high school football player who suffered a head injury during a scrimmage last week has died. The Kentucky High School Athletic Association said Monday in a statement on Facebook that it joined family...}

\entryitemWithDescription{\hskip 0pt{}About 5K GM salaried workers take buyouts, avoiding layoffs}{https://apnews.com/article/ac267adabc4ef6698868666ec04a8903}{FILE - The General Motors logo is displayed outside the General Motors Detroit-Hamtramck Assembly plant, Jan. 27, 2020, in Hamtramck, Mich. General Motors is offering buyouts to most of its U.S. salaried workforce and some global...}

\entryitemWithDescription{\hskip 0pt{}Rory McIlroy returns to Masters in search of green jacket}{https://apnews.com/article/505c28012ee678607ae1b48056924199}{Rory McIlroy, of Northern Ireland, walks on the 15th hole during a practice for the Masters golf tournament at Augusta National Golf Club, Monday, April 3, 2023, in Augusta, Ga. (AP Photo/Jae C. Hong) AUGUSTA, Ga. (AP) --- Rory McIlroy...}

\entryitemWithDescription{\hskip 0pt{}`He's a war criminal': Elite Putin security officer defects}{https://apnews.com/article/845421fe06ed9cfa1962ad4f98a2e413}{In this image from video provided by the Dossier Center, a London-based investigative group funded by Russian opposition figure Mikhail Khodorkovsky, Gleb Karakulov speaks during an interview in Turkey in December 2022. Karakulov, who was...}

\entryitemWithDescription{\hskip 0pt{}NHL's Pride nights collide with LGBTQ+ political climate}{https://apnews.com/article/c19fa347d514e2f11f7277969a13a4a9}{Screens display "Blackhawks Pride Night" outside United Center before an NHL hockey game between the Vancouver Canucks and the Chicago Blackhawks in Chicago, Sunday, March 26, 2023. (AP Photo/Nam Y. Huh) Sports leagues and teams often use...}

\entryitemWithDescription{\hskip 0pt{}New images from inside Fukushima reactor spark safety worry}{https://apnews.com/article/46f47feac0133640b9b72f7700b21f32}{A spokesperson of the Tokyo Electric Power Company Holdings (TEPCO) shows photos captured by a robotic probe inside one of the three melted reactors at the tsunami-wrecked Fukushima nuclear power plant, during a news conference at the...}