\entryitemWithDescription{\hskip 0pt{}Mount Washington experiences record-setting wind chill}{https://apnews.com/article/96b71f553494730304ce1e20aa376ce4}{A man walks on sea wall near Spring Point Ledge Light, Saturday, Feb. 4, 2023, in South Portland, Maine. The morning temperature was about -10 degrees Fahrenheit. (AP Photo/Robert F. Bukaty) BOSTON (AP) --- The Arctic air that descended...}

\entryitemWithDescription{\hskip 0pt{}Route to Super Bowl dangerous for Mexico's avocado haulers}{https://apnews.com/article/90d19f78c27a8e934e5edd66c8647864}{A man works at an avocado orchard in Santa Ana Zirosto, Michoacan state, Mexico, Thursday, Jan. 26, 2023. (AP Photo/Armando Solis) SANTA ANA ZIROSTO, Mexico (AP) --- It is a long and sometimes dangerous journey for truckers transporting...}

\entryitemWithDescription{\hskip 0pt{}In Tyre Nichols' neighborhood, Black residents fear police}{https://apnews.com/article/1844a7b20e3c7745db2b84677b86abee}{Community organizer Chase Madkins stands on the porch of the Mississippi Boulevard Christian Church in Memphis, Tenn., on Wednesday, Feb. 1, 2023. Madkins attended the funeral of Tyre Nichols, who died of injuries following a traffic stop...}

\entryitemWithDescription{\hskip 0pt{}'Died suddenly' posts twist tragedies to push vaccine lies}{https://apnews.com/article/a8e3a80a015ba9bf78b6bd4f3c271f58}{Jessica Day-Weaver poses next to a picture collage made for her daughter, Anastasia, at her home, Thursday, Feb. 2, 2022, in Boardman, Ohio. (AP Photo/Nick Cammett) Results from 6-year-old Anastasia Weaver's autopsy may take weeks. But...}

\entryitemWithDescription{\hskip 0pt{}Electronic pollbook security raises concerns going into 2024}{https://apnews.com/article/651d0e923973daf28ff3b9d6105b4d74}{FILE - Mark Splonskowski assembles electronic poll book kits that voters will uses to sign in at polling locations at the Albany County Board of Elections building, Oct. 14, 2020, in Albany, N.Y. Attempts to develop the first-ever...}

\entryitemWithDescription{\hskip 0pt{}Why a new Alzheimer's drug is having a slow US debut}{https://apnews.com/article/aa65c9f4640765358bf0dbb68e4bdde9}{FILE - This Dec. 21, 2022, image provided by Eisai in January 2023 shows vials and packaging for their medication Leqembi. Leqembi, the first drug to show that it slows Alzheimer's, was approved by the U.S. Food and Drug Administration in...}

\entryitemWithDescription{\hskip 0pt{}State of the Union: Biden sees economic glow, GOP sees gloom}{https://apnews.com/article/4496d9470c90e86d3642521482cd0e19}{FILE - President Joe Biden speaks on the January jobs report in the Eisenhower Executive Office Building on the White House complex, Friday, Feb. 3, 2023, in Washington. Going into Tuesday\textquotesingle s State of the Union address...}

\entryitemWithDescription{\hskip 0pt{}Dozens of soldiers freed in Russia-Ukraine prisoner swap}{https://apnews.com/article/dbb56b9e4560417e358c964d4846617d}{A woman lights up the road with a flashlight during blackout in Kyiv, Ukraine, Friday, Feb. 3, 2023. (AP Photo/Evgeniy Maloletka) KYIV, Ukraine (AP) --- Dozens of Russian and Ukrainian prisoners of war have returned home following a...}

\entryitemWithDescription{\hskip 0pt{}US downs Chinese balloon over ocean, moves to recover debris}{https://apnews.com/article/51e49202f2a0a50541cde059934c4cfb}{CORRECTS TO KINGSTOWN, NOT KINGSTON - In this photo provided by Brian Branch, a large balloon drifts above the Kingstown, N.C. area, with an airplane and its contrail seen below it. The United States says it is a Chinese spy balloon...}

\entryitemWithDescription{\hskip 0pt{}Qatar boosts influence in Lebanon amid multiple crises}{https://apnews.com/article/b6b7c51ec89aaf1d21eca6301c788d7f}{FILE - Qatar\textquotesingle s Emir Sheikh Tamim bin Hamad Al Thani reviews the honor guard as he arrives at the Rafik Hariri international airport in Beirut, Lebanon, Sunday, Jan. 20, 2019. (AP Photo/Hussein Malla, File) BEIRUT (AP...}

\entryitemWithDescription{\hskip 0pt{}50-car train derailment causes big fire, evacuations in Ohio}{https://apnews.com/article/5d399dc745f51ef746e22828083d8591}{This photo taken with a drone shows portions of a Norfolk and Southern freight train that derailed Friday night in East Palestine, Ohio are still on fire at mid-day Saturday, Feb. 4, 2023. (AP Photo/Gene J. Puskar) EAST PALESTINE, Ohio...}

\entryitemWithDescription{\hskip 0pt{}Pope says South Sudan's future depends on treatment of women}{https://apnews.com/article/e1ade89d06941dd0d8d654d7e3e0978d}{Pope Francis meets with a group of the Catholic faithful from the town of Rumbek, who had walked for more than a week to reach the capital, after he addressed clergy at the St. Theresa Cathedral in Juba, South Sudan Saturday, Feb. 4...}

\entryitemWithDescription{\hskip 0pt{}Biden makes progress on 'unity agenda' outlined in 2022}{https://apnews.com/article/e0c789041281c9ca231d685186c50b6e}{FILE - President Joe Biden delivers his first State of the Union address to a joint session of Congress at the Capitol, March 1, 2022, in Washington. A year ago, President Joe Biden used his first State of the Union address to push top...}