\entryitemWithDescription{\hskip 0pt{}Authorities arrest ex-sheriff's deputy who fatally shot a Black airman at his home}{https://apnews.com/article/850414e0baea006d36f2ed9b2f4a385d}{A former Florida sheriff's deputy charged with killing a Black U.S. Air Force senior airman who answered his apartment door while holding a gun pointed toward the ground was arrested Monday, officials said. Former Okaloosa County deputy...}

\entryitemWithDescription{\hskip 0pt{}Diddy seeks to have producer's lawsuit tossed, says it's full of `blatant falsehoods'}{https://apnews.com/article/7ea05a3df7b1e70bc91174f6b3ecae42}{Sean ``Diddy'' Combs asked a federal judge Monday to throw out a lawsuit from a music producer who accused the music mogul of a broad pattern of sexual abuse and other misconduct. The lawsuit filed in February by Rodney ``Lil Rod''...}

\entryitemWithDescription{\hskip 0pt{}Double-duty Danny Jansen plays for both teams in one MLB game. Here's how}{https://apnews.com/article/c7ac515faa738ee37f444e46367ef439}{BOSTON (AP) --- Blue Jays-turned-Red Sox catcher Danny Jansen didn't just play for both teams in the same game --- a first in major league baseball history. He played for both teams in the same inning. Jansen became the first major...}

\entryitemWithDescription{\hskip 0pt{}Sven-Goran Eriksson, Swedish soccer coach who was first foreigner to lead England team, dies at 76}{https://apnews.com/article/5cd5b69de425fd0129cf21428b8dde1b}{Sven-Goran Eriksson, the Swedish soccer manager who spent five years as England's first ever foreign-born coach after making his name winning trophies at club level in Italy, Portugal and Sweden, has died. He was 76. Eriksson died Monday...}

\entryitemWithDescription{\hskip 0pt{}Traveling over Labor Day weekend? Have a back-up plan for cancellations and delays, and be patient}{https://apnews.com/article/81c40a034787764631c4bb640861f7c3}{Many children have gone back to school in the U.S., and the days are getting shorter, but there is still one more excuse to use the swimsuits and beach towels before packing them up: Labor Day. Airports, highways, beaches and theme parks...}

\entryitemWithDescription{\hskip 0pt{}French DJ and LGBTQ+ icon carries Paralympic torch to defy hate she endured over Olympics ceremony}{https://apnews.com/article/d873e312bd1b4aba0f79732942f90e6f}{PARIS (AP) --- French performer Barbara Butch carried the Paralympic torch Sunday evening in an act of defiance after being targeted by hate speech over her appearance in the opening ceremony of the Olympic Games. ``I chose not to be...}

\entryitemWithDescription{\hskip 0pt{}Ice cave collapse in Iceland kills 1 tourist, and 2 are still missing}{https://apnews.com/article/8d6a45480717589a4699f75f976e3df3}{BERLIN (AP) --- At least one person has died and two others are still missing after an ice cave partially collapsed as a group of tourists was visiting the Breidamerkurjokull glacier in southern Iceland. In a statement posted on social...}

\entryitemWithDescription{\hskip 0pt{}Venice Film Festival: From `Joker 2' to `Queer,' here are 10 movies to get excited about}{https://apnews.com/article/309c97d0d2a8cd103a8f79f3c5d36792}{VENICE, Italy (AP) --- Some of Hollywood's biggest stars are getting ready to descend on the Venice Film Festival this week, from George Clooney and Angelina Jolie to Lady Gaga and Brad Pitt. But while the allure of A-listers on those...}

\entryitemWithDescription{\hskip 0pt{}US national parks are receiving record-high gift of \$100M}{https://apnews.com/article/9fb09b8cc54a9cd7265024e87dea020a}{PORTLAND, Maine (AP) --- The official nonprofit organization of the National Park Service is set to receive the largest grant in its history, a \$100 million gift the fundraising group described as transformative for the country's...}

\entryitemWithDescription{\hskip 0pt{}Walmart recalls apple juice sold in 25 states due to elevated arsenic levels}{https://apnews.com/article/e4c185fd48af2438023ea94b3f6b2b74}{WASHINGTON (AP) --- Walmart has recalled nearly 10,000 cases of apple juice sold in stores across the U.S. that were found to contain potentially harmful levels of inorganic arsenic. The U.S. Food and Drug Administration gave the recall a...}

\entryitemWithDescription{\hskip 0pt{}Famed Coney Island Cyclone roller coaster is shut down after mid-ride malfunction}{https://apnews.com/article/32077ca8078705aba01927c0dbc2569b}{NEW YORK (AP) --- The famous Coney Island Cyclone roller coaster in New York City was shut down indefinitely after coming to a stop mid-ride this week. The 97-year-old wooden roller coaster at Luna Park was on its ascent on Thursday when...}

\entryitemWithDescription{\hskip 0pt{}Search continues for woman missing after Colorado River flash flood at Grand Canyon National Park}{https://apnews.com/article/ae0ae8e8aed57f6070cd40182e720db1}{SUPAI, Ariz. (AP) --- Search crews again Sunday were combing the Colorado River at Grand Canyon National Park for an Arizona woman missing after a flash flood days earlier. National Park Service officials said Chenoa Nickerson, 33, was...}

\entryitemWithDescription{\hskip 0pt{}Former five-time Lebanese prime minister Salim Hoss dies at 94}{https://apnews.com/article/2612d4cc9d551c9fd9c319a78ebb8dd9}{BEIRUT (AP) --- Five-time former Lebanese Prime Minister Salim Hoss, who served during some of the most tumultuous years of his country's modern history, died Sunday at age 94, the current premier said. Caretaker Prime Minister Najib...}