\entryitemWithDescription{\hskip 0pt{}Hugh Jackman and Deborra-lee Jackman separate after 27 years of marriage}{https://apnews.com/article/f1fa97cf97b15a461fc479f4632cfa47}{NEW YORK (AP) --- Hugh Jackman and Deborra-lee Jackman have decided to end their marriage after 27 years and two children. ``We have been blessed to share almost 3 decades together as husband and wife in a wonderful, loving marriage. Our...}

\entryitemWithDescription{\hskip 0pt{}British neonatal nurse found guilty of murdering 7 babies launches bid to appeal her convictions}{https://apnews.com/article/6878518520a4d638c9ca3ef1000aca67}{LONDON (AP) --- A British neonatal nurse who was found guilty of murdering seven babies and the attempted murder of six others has launched a bid to appeal her convictions, officials said Friday. Lucy Letby, 33, was sentenced last month...}

\entryitemWithDescription{\hskip 0pt{}Alaska lawmaker's husband was flying meat from hunting camp when crash occurred, authorities say}{https://apnews.com/article/c28e0d1d496fc1465cb9c95a59e1d3f3}{ANCHORAGE, Alaska (AP) --- The plane flown by the husband of Alaska U.S. Rep. Mary Peltola was carrying a load of moose meat from a remote hunting camp when it crashed, killing him earlier this week, authorities said. Eugene Peltola Jr...}

\entryitemWithDescription{\hskip 0pt{}Tony Award-winner Michael McGrath, mourned as `adorable, mischievous, brilliant,' dies at 65}{https://apnews.com/article/f5fc39b08a95107c74fc6fb7250c33b4}{NEW YORK (AP) --- Michael McGrath, a Broadway character actor who shined in zany, feel-good musicals and won a Tony Award for ``Nice Work If You Can Get It,'' has died. He was 65. McGrath died Thursday at his home in Bloomfield, New...}

\entryitemWithDescription{\hskip 0pt{}Video appears to show Rep. Lauren Boebert vaping at `Beetlejuice' show before she was ejected}{https://apnews.com/article/186d748f754d87a7441268744b0076cf}{DENVER (AP) --- Newly released surveillance video from a Denver theater appears to show Republican Rep. Lauren Boebert vaping during a ``Beetlejuice'' musical play --- the one thing she denied doing while acknowledging earlier this week...}

\entryitemWithDescription{\hskip 0pt{}One American, two Russians ride Russian capsule to the International Space Station}{https://apnews.com/article/ccfa726fa1b87462881e0ded14781536}{MOSCOW (AP) --- One American and two Russians made a quick trip Friday to the International Space aboard a Russian capsule. NASA astronaut Loral O'Hara and Roscosmos cosmonauts Oleg Kononenko and Nikolai Chub blasted off from the Baikonur...}

\entryitemWithDescription{\hskip 0pt{}Princess Diana's sheep sweater smashes records to sell for \$1.1 million}{https://apnews.com/article/9de2d082db42b472dbe995c87fe283d8}{LONDON (AP) --- A red sweater adorned with a flock of sheep worn by the young Princess Diana has sold at auction for \$1.1 million, many times its presale estimate and a record for an item owned by the late royal. The playfully patterned...}

\entryitemWithDescription{\hskip 0pt{}After attacks, British prime minister says American XL Bully dogs are dangerous and will be banned}{https://apnews.com/article/54fd3bd424d36af19f58d2ddcceea852}{LONDON (AP) --- British Prime Minister Rishi Sunak on Friday described American XL Bully dogs as a ``danger to our communities'' and announced plans to ban the breed following a public outcry after a series of recent attacks. Sunak said...}

\entryitemWithDescription{\hskip 0pt{}Apple will update iPhone 12 in France after regulators said it emitted too much radiation}{https://apnews.com/article/f831e1a108b1c9b0f3a46b4525253b78}{PARIS (AP) --- Apple has agreed to install updates for the iPhone 12 in France after French regulators ordered the company to stop selling the model because it emits electromagnetic radiation levels that exceed European Union standards...}

\entryitemWithDescription{\hskip 0pt{}A German tailor who specializes in bespoke lederhosen is in high demand ahead of Oktoberfest}{https://apnews.com/article/6afc8328f6e3139d81c83f9bffd9b31c}{BAD HINDELANG, Germany (AP) --- As Germany's city of Munich prepares to tap the kegs for Oktoberfest this weekend, Bavaria state residents and foreign regulars of the world's most conspicuous beer party are getting ready to drink and...}

\entryitemWithDescription{\hskip 0pt{}In a court filing, a Tennessee couple fights allegations that they got rich off Michael Oher}{https://apnews.com/article/6cc3b7643652f6dfa9c1cba37dffd1b3}{MEMPHIS, Tenn. (AP) --- A Memphis couple who took in former NFL offensive lineman Michael Oher when he was in high school denied in court documents filed Thursday that they used a legal agreement between them to get rich at his expense...}

\entryitemWithDescription{\hskip 0pt{}Psychedelic drug MDMA eases PTSD symptoms in a study that paves the way for possible US approval}{https://apnews.com/article/1155a374305027567d5f41910022022d}{The psychedelic drug MDMA can reduce symptoms of post-traumatic stress disorder, researchers reported in a new study published Thursday. The company sponsoring the research said it plans later this year to seek U.S. approval to market the...}

\entryitemWithDescription{\hskip 0pt{}Israel's Netanyahu is to meet Elon Musk. Their sit-down comes as X faces antisemitism controversy}{https://apnews.com/article/8b9b625713ffe2e244945980c1caf8bc}{JERUSALEM (AP) --- Prime Minister Benjamin Netanyahu will meet billionaire businessman Elon Musk during a trip to the United States next week, the Israeli leader's office said Thursday. Netanyahu's office said their meeting, which is...}