\entryitemWithDescription{\hskip 0pt{}Jagger watches Barcelona wear Stones logo in `clasico' but Beatles fan Bellingham gets Madrid winner}{https://apnews.com/article/bdac04de98f4de81a4c7a8ddd5883898}{BARCELONA, Spain (AP) --- Barcelona aligned with the Rolling Stones for Saturday's ``clasico'' soccer game against Real Madrid when Mick Jagger showed up to see the home team wear special jerseys featuring the iconic logo of his legendary...}

\entryitemWithDescription{\hskip 0pt{}Winner of albinism pageant says Zimbabwe event made her feel beautiful and provided sense of purpose}{https://apnews.com/article/9a8c87824a6be9965e648cdcfd2fec68}{HARARE, Zimbabwe (AP) --- A glittering crown on her head and a bouquet of flowers in her hands, Andreia Solange Sicato Muhitu beamed at being named the co-winner of the the inaugural Mr. and Miss Albinism Southern Africa pageant. The 28...}

\entryitemWithDescription{\hskip 0pt{}In Seattle, phones ding. Killer whales could be close}{https://apnews.com/article/0e86cd0a5403049a74386d66fc0ae8c8}{SEATTLE (AP) --- Peter Bates was dropping his car at the mechanic this month when a notification pinged on his phone: killer whales were approaching his Seattle neighborhood. He hopped on a bus toward the water, then an electric bike. He...}

\entryitemWithDescription{\hskip 0pt{}Canadian fishing boat rescues American fisherman from missing vessel based in Washington state}{https://apnews.com/article/a90d32432832be0c10099445a5f8ccba}{VANCOUVER, British Columbia (AP) --- A Canadian fishing boat rescued an American man one day after the U.S. Coast Guard ended its search for a missing commercial fishing boat from Washington state with two people board, authorities said...}

\entryitemWithDescription{\hskip 0pt{}A salty problem for people near the mouth of the Mississippi is a wakeup call for New Orleans}{https://apnews.com/article/1a55ad43ce83419247642929629377b2}{NEW ORLEANS (AP) --- The heating element removed from Monique Plaisance's water heater in September was disintegrating, streaked with rust and covered in a dry crust. She blamed the corrosion on the water piped in from the area's longtime...}

\entryitemWithDescription{\hskip 0pt{}The White House and Google launch a new virtual tour with audio captions, Spanish translation}{https://apnews.com/article/d422c4ede3424643fc131d6fb24e2636}{WASHINGTON (AP) --- Can't come to Washington? Couldn't get a ticket to tour the White House? Don't worry. The White House, Google Maps and Google Arts \& Culture launched a new virtual tour of the famous mansion on Friday, which is also...}

\entryitemWithDescription{\hskip 0pt{}DC pandas will be returning to China in mid-November, weeks earlier than expected}{https://apnews.com/article/96c106c85143621e29bcc579a24c068d}{WASHINGTON (AP) --- The National Zoo's three celebrity giant pandas will be heading home a little earlier than expected. Zoo officials told The Associated Press on Thursday that adult bears Mei Xiang and Tian Tian and their cub Xiao Qi Ji...}

\entryitemWithDescription{\hskip 0pt{}Arizona Diamondbacks take series of slights into surprise World Series against Texas Rangers}{https://apnews.com/article/fbd22417810138c1cfe396aa7c2bdfbd}{ARLINGTON, Texas (AP) --- Before opening the World Series, the Arizona Diamondbacks wanted to recount a series of slights. Overlooked by oddsmakers and angered by analysts, the Diamondbacks find themselves in a Surprise Series against the...}

\entryitemWithDescription{\hskip 0pt{}Radio host Larry Elder ends Republican presidential campaign and endorses Donald Trump}{https://apnews.com/article/a3d3665cd50d1e0d2071ab8800075482}{Conservative talk radio host Larry Elder announced Thursday that he was ending his 2024 Republican campaign for president and endorsing former President Donald Trump. Elder, who sought to replace California Gov. Gavin Newsom in a failed...}

\entryitemWithDescription{\hskip 0pt{}Ottawa's Shane Pinto suspended 41 games, becomes the 1st modern NHL player banned for gambling}{https://apnews.com/article/09cbedc1d9257fede6ec59251e76a914}{The NHL suspended Ottawa Senators forward Shane Pinto for 41 games on Thursday, making the 22-year-old American the first modern-day hockey player banned for sports gambling. The league said the half-season ban was for ``activities...}

\entryitemWithDescription{\hskip 0pt{}The last new Beatles song, `Now And Then,' will be released next week}{https://apnews.com/article/e7b3a349b0e1e58b8668e98ba2d9cd0b}{NEW YORK (AP) --- Sixty years after the onset of Beatlemania and with two of the quartet now dead, artificial intelligence has enabled the release next week of what is promised to be the last ``new'' Beatles song. The track, called ``Now...}

\entryitemWithDescription{\hskip 0pt{}No. 1 pick Wembanyama scores 15 points in NBA debut as Spurs fall to Mavericks in opener}{https://apnews.com/article/a0d4aa8851311110a55b59da9eb84023}{SAN ANTONIO (AP) --- The Victor Wembanyama era is underway in San Antonio. Wembanyama made his NBA debut with the Spurs against the Dallas Mavericks on Wednesday night and made an immediate splash. ``He's going to be amazing, he already...}

\entryitemWithDescription{\hskip 0pt{}Rep. Bowman of New York charged with misdemeanor, to pay fine after triggering House fire alarm}{https://apnews.com/article/1b9f8559a741a982116f7e8a4b6c6ac5}{WASHINGTON (AP) --- Democratic Rep. Jamaal Bowman was charged Wednesday with a misdemeanor for triggering a fire alarm as lawmakers scrambled to pass a funding bill before a government shutdown deadline in September. He is expected to...}