\entryitemWithDescription{\hskip 0pt{}Man says his emotional support alligator, known for its big social media audience, has gone missing}{https://apnews.com/article/84f4e843061e5b54a6880db479532c82}{BRUNSWICK, Ga. (AP) --- A Pennsylvania man who credits an alligator named Wally for helping relieve his depression for nearly a decade says he is searching for the reptile after it went missing during a vacation to the coast of Georgia...}

\entryitemWithDescription{\hskip 0pt{}Want to spend the night in a Paris museum or a house owned by Prince? Airbnb plans to list them}{https://apnews.com/article/5ed3cc2ab754814897c40d5172931000}{In a mad mix of game-show glitter and marketing flash, Airbnb is offering customers a chance to spend a night in a Paris museum, stay in houses mocked up to look like movie settings, or sleep surrounded by eight Ferrari racing cars. Those...}

\entryitemWithDescription{\hskip 0pt{}George W. Bush's portraits of veterans are heading to Disney World}{https://apnews.com/article/e634bed15861a9600ced0383964fcdf2}{LAKE BUENA VISTA, Fla. (AP) --- Walt Disney World will host dozens of portraits of service members and veterans from the nation's Painter-in-Chief. The George W. Bush Institute will loan the 60 color portraits by the former U.S. president...}

\entryitemWithDescription{\hskip 0pt{}Wrexham owners Ryan Reynolds and Rob McElhenney want to expand stadium capacity to 55,000}{https://apnews.com/article/df0db2375ba84053013d914790d1416a}{Ryan Reynolds and Rob McElhenney have given an insight into their long-term ambitions for Welsh soccer team Wrexham, which they hope could eventually see the capacity of its Racecourse Ground stadium increase massively to 55,000. The...}

\entryitemWithDescription{\hskip 0pt{}Trump awarded 36 million more Trump Media shares worth \$1.8 billion after hitting price benchmarks}{https://apnews.com/article/a196a9134e123801a94a21df3a8ad0bf}{WASHINGTON (AP) --- Former President Donald Trump has secured an additional \$1.8 billion worth of shares in Trump Media, according to a regulatory filing this week. Based on the company's stock hitting certain price benchmarks, Trump was...}

\entryitemWithDescription{\hskip 0pt{}Tennis legend Boris Becker discharged from bankruptcy court in England}{https://apnews.com/article/d30c0ad3edb216f076b4da4fbb3e9b99}{LONDON (AP) --- German tennis legend Boris Becker was discharged from bankruptcy court in London after a judge found Wednesday he had done ``all that he reasonably could do'' to repay creditors tens of millions of pounds. Becker fell far...}

\entryitemWithDescription{\hskip 0pt{}Ford recalls Maverick pickups in US because tail lights can go dark, increasing the risk of a crash}{https://apnews.com/article/f1218640746192332e42088d83930261}{DEARBORN, Mich. (AP) --- Ford is recalling nearly 243,000 Maverick small pickup trucks in the U.S. because the tail lights may not illuminate. The company says a computer can falsely detect too much current on one or both of the tail...}

\entryitemWithDescription{\hskip 0pt{}Indonesia's Ruang volcano spews more hot clouds after eruption forces closure of schools, airports}{https://apnews.com/article/03d5f20a025de8c3f741631d33fc284d}{MANADO, Indonesia (AP) --- Indonesia's Mount Ruang volcano spewed more hot clouds on Wednesday after an eruption the previous day forced the closure of schools and airports, pelted villages with volcanic debris and prompted hundreds of...}

\entryitemWithDescription{\hskip 0pt{}Ryan Gosling and Mikey Day reprise viral Beavis and Butt-Head characters at `Fall Guy' premiere}{https://apnews.com/article/f9fbf1a670781788b5a088ce11b1f0c7}{LOS ANGELES (AP) --- Ryan Gosling and Mikey Day aren't done playing Beavis and Butt-Head yet --- the pair appeared as the characters at the premiere of Gosling's latest film. Gosling, who stars in ``The Fall Guy'' opposite Emily Blunt...}

\entryitemWithDescription{\hskip 0pt{}Over 500 baby sea turtles washed ashore in a big storm off South Africa. Here's the rescue effort}{https://apnews.com/article/89f572cbe7f351f65ec9be1b55b902e3}{CAPE TOWN, South Africa (AP) --- An aquarium in South Africa is stretched beyond capacity after more than 500 baby sea turtles were washed up on beaches by a rare and powerful storm and rescued by members of the public. The little turtles...}

\entryitemWithDescription{\hskip 0pt{}Bee delay: Dodgers and Diamondbacks start pushed back by bee swarm}{https://apnews.com/article/918d16454ab13d0154c4c3d8f6956b59}{PHOENIX (AP) --- The Los Angeles Dodgers and Arizona Diamondbacks are in a bee delay. The start of Tuesday night's game at Chase Field was delayed after bees swarmed the top of the protective netting directly behind home plate. Bee swarms...}

\entryitemWithDescription{\hskip 0pt{}Alicia Keys, Brian d'Arcy James, Daniel Radcliffe and more react to earning Tony Award nominations}{https://apnews.com/article/9e6f58cd93235a7629b23685a7f7cb75}{Singer Alicia Keys says she was unable to speak after her semi-autobiographical show ``Hell's Kitchen'' earned 13 nods when the nominations for the 2024 Tony Awards were announced Tuesday. ``These are very, very special moments,'...}

\entryitemWithDescription{\hskip 0pt{}2 men are charged with cutting down famous 150-year-old tree near Hadrian's Wall in England}{https://apnews.com/article/cfd4e6d5bec32f5b89fc40b459b89cb1}{LONDON (AP) --- Two men have been charged with cutting down the popular 150-year-old Sycamore Gap tree next to Hadrian's Wall last year in northern England, prosecutors said Tuesday. Daniel Graham, 38, and Adam Carruthers, 31, were...}