\entryitemWithDescription{\hskip 0pt{}Man arrested near Taylor Swift's NYC townhouse after reported break-in attempt}{https://apnews.com/article/c3d2f6c4aaea4f775e06c5bcf6b14152}{NEW YORK (AP) --- Taylor Swift's townhouse in New York City appears to have been the target of another break-in attempt, this time by a man who was arrested near the singer's Tribeca home Saturday as police responded to a report of a...}

\entryitemWithDescription{\hskip 0pt{}Mary Weiss, lead singer of the Shangri-Las, dies at 75}{https://apnews.com/article/f8287d8251bcfe482c8d21f2f1c9b6d9}{Mary Weiss, the lead singer of the 1960s pop group the Shangri-Las, whose hits included ``Leader of the Pack,'' has died. She was 75. Miriam Linna, founder of Weiss' label, Norton Records, said Sunday that Weiss died Friday in Palm...}

\entryitemWithDescription{\hskip 0pt{}`Burn, beetle, burn': Hundreds of people torch an effigy of destructive bug in South Dakota town}{https://apnews.com/article/e830ab98185946308de708ca9d1b522b}{RAPID CITY, S.D. (AP) --- In what's become an annual winter tradition, hundreds of people carrying torches set fire to a giant wooden beetle effigy in Custer, South Dakota, to raise awareness of the destructive impact of the mountain pine...}

\entryitemWithDescription{\hskip 0pt{}Sarah, the Duchess of York, diagnosed with malignant melanoma found during breast cancer treatment}{https://apnews.com/article/40e44cf65507970c30c952f039c0373a}{LONDON (AP) --- Sarah, the Duchess of York, has been diagnosed with a malignant skin cancer that was discovered during her treatment for breast cancer, a spokesperson said. The melanoma was found after several moles were removed while she...}

\entryitemWithDescription{\hskip 0pt{}Marlena Shaw, `California Soul' singer, dead at 81}{https://apnews.com/article/8b8dc18587b85d6e0d47dc4bed9bd662}{Marlena Shaw, the jazz and R\&B vocalist whose ``California Soul'' was one of the defining soul songs of the late 1960s, has died. She was 81. Shaw's daughter, Marla Bradshaw, announced the singer's death Friday in a video posted on...}

\entryitemWithDescription{\hskip 0pt{}`Mean Girls' fetches \$11.7M in second weekend to stay No. 1 at box office}{https://apnews.com/article/3b07493452787d5aeab53e474005e4b2}{NEW YORK (AP) --- On a quiet weekend in movie theaters, ``Mean Girls'' repeated atop the box office with \$11.7 million in ticket sales, according to studio estimates Sunday, while a handful of awards contenders sought to make an impact...}

\entryitemWithDescription{\hskip 0pt{}Inside Pitchfork's absorption into GQ: When `music media' becomes `men's media,' what's lost?}{https://apnews.com/article/ecaef9445b5d9f86d9990c181306cb71}{LOS ANGELES (AP) --- Nearly three decades after it was established, Pitchfork, the most influential music publication of the internet age with the power to make or break an artist, is being absorbed by another entity --- a men's fashion...}

\entryitemWithDescription{\hskip 0pt{}Christian McCaffrey's 2nd TD rallies the 49ers to 24-21 playoff win over Jordan Love and the Packers}{https://apnews.com/article/6cafbf31de6393cf5c6db49f71c0998b}{SANTA CLARA, Calif. (AP) --- Brock Purdy's throws were off-target all night. The San Francisco defense kept giving up big plays. There were even a couple of special teams blunders. Just when it seemed like the top-seeded 49ers might be...}

\entryitemWithDescription{\hskip 0pt{}Adam Harrison, a son of `Pawn Stars' celebrity Rick Harrison, has died in Las Vegas at age 39}{https://apnews.com/article/c8b29fd45c36327945e15010511288c9}{LAS VEGAS (AP) --- Adam Harrison, one of three sons of reality TV show ``Pawn Stars'' celebrity Richard ``Rick'' Harrison, has died in Las Vegas, a family representative said Saturday. He was 39. Harrison family spokesperson Laura...}

\entryitemWithDescription{\hskip 0pt{}Judge orders release of `Newburgh Four' defendant and blasts FBI's role in terror sting}{https://apnews.com/article/40f7e967468de02b4b7ec2d331b0511e}{A man convicted in a post-9/11 terrorism sting was ordered freed from prison by a judge who criticized the FBI for relying on an ``unsavory'' confidential informant for an agency-invented conspiracy to blow up New York synagogues and...}

\entryitemWithDescription{\hskip 0pt{}Alec Baldwin's grand jury indictment opens up two paths for prosecutors}{https://apnews.com/article/866e52839780c1f6d75876298b191d91}{SANTA FE, N.M. (AP) --- Alec Baldwin once again is staring down a felony involuntary manslaughter charge after a grand jury indicted the actor in connection with the fatal 2021 shooting of a cinematographer on the set of a Western movie...}

\entryitemWithDescription{\hskip 0pt{}The Ravens are ready to give Dalvin Cook a shot, but there's no telling what to expect}{https://apnews.com/article/c8e41f7bbb016f21dd622001b4d4f8d2}{OWINGS MILLS, Md. (AP) --- Even John Harbaugh isn't sure what to expect from Dalvin Cook this weekend. The Baltimore coach sounds ready to put him on the field and find out. ``It's new. We haven't seen him out there,'' Harbaugh told...}

\entryitemWithDescription{\hskip 0pt{}Plane makes emergency landing on a northern Virginia highway after taking off from Dulles airport}{https://apnews.com/article/c06e393a6b5a1f67c64098324e411d66}{DULLES, Va. (AP) --- A small passenger plane made an emergency landing on a northern Virginia highway after taking off from nearby Washington Dulles International Airport on Friday afternoon, but no injuries were reported, authorities...}