\entryitemWithDescription{\hskip 0pt{}AP source: Kyrie Irving going to the Dallas Mavericks}{https://apnews.com/article/04a54cb3ecf504152a3dd714d064d22a}{FILE - Brooklyn Nets\textquotesingle{} Kyrie Irving reacts during the second half of the team\textquotesingle s NBA basketball game against the Detroit Pistons Thursday, Jan. 26, 2023 in New York. All-Star guard Kyrie Irving has asked the...}

\entryitemWithDescription{\hskip 0pt{}Amid crisis, Haitians find solace in an unlikely place: soup}{https://apnews.com/article/ae2f698a04fa4fa393661a3d697db10f}{Mireille Lerebours serves traditional soup joumou at a restaurant in the Delmas district of Port-au-Prince, Haiti, Sunday, Feb. 5, 2023. In 2021, the same year the country spiraled into chaos following the assassination of its president...}

\entryitemWithDescription{\hskip 0pt{}US officials offer Congress briefing on Trump, Biden papers}{https://apnews.com/article/d6ce5c8f83a3cec3307f0f9f8311b8d7}{FILE - An aerial view of former President Donald Trump\textquotesingle s Mar-a-Lago club in Palm Beach, Fla., on Aug. 31, 2022. The Justice Department issued a subpoena for the return of classified documents that Trump had refused to give...}

\entryitemWithDescription{\hskip 0pt{}Northeast temperatures soar a day after bone-numbing cold}{https://apnews.com/article/c65d6cd34e8e9fa521459a89abcb0cad}{Spring Point Ledge Light is surrounded by arctic sea smoke while emissions from the Wyman Power plant, background, are blown horizontal by the fierce wind, Saturday, Feb. 4, 2023, in South Portland, Maine. The morning temperature was...}

\entryitemWithDescription{\hskip 0pt{}Balloon bickering over Biden's actions, China's intentions}{https://apnews.com/article/19e1f66a6db19f44548c402d81facc8e}{In this photo provided by Chad Fish, the remnants of a large balloon drift above the Atlantic Ocean, just off the coast of South Carolina, with a fighter jet and its contrail seen below it, Saturday, Feb. 4, 2023. The downing of the...}

\entryitemWithDescription{\hskip 0pt{}Pope, Anglican, Presbyterian leaders denounce anti-gay laws}{https://apnews.com/article/ddd1e52de12a95216e798a9ddd103ade}{The Archbishop of Canterbury Justin Welby, right, Pope Francis,left, and the Moderator of the General Assembly of the Church of Scotland Iain Greenshields meet the journalists during an airborne press conference aboard the airplane...}

\entryitemWithDescription{\hskip 0pt{}Cubans respond with zeal to new US migration policy}{https://apnews.com/article/d8196aa4b003f22a66d9847b3e37dcff}{Marcos Marzo hugs two of his friends who came to say goodbye upon receiving the news that he had obtained a permit to travel to the United States, in Havana, Cuba, Wednesday, Jan 25, 2023. Now in the U.S., his dream is to do a master's...}

\entryitemWithDescription{\hskip 0pt{}How the cases in Alex Murdaugh's murder trial are shaping up}{https://apnews.com/article/7f3f524b02ccbea2165c3c9fce8a5c43}{Alex Murdaugh, right, leans over to talk with his attorney Jim Griffin in his double murder trial at the Colleton County Courthouse in Walterboro, S.C., Friday, Feb. 3, 2023. The 54-year-old attorney is standing trial on two counts of...}

\entryitemWithDescription{\hskip 0pt{}Tyre Nichols' mom, chief: Women on two sides of a tragedy}{https://apnews.com/article/dac96c2c6a4e319fc68fa102dec1fc6c}{RowVaughn Wells, mother of Tyre Nichols, pauses as she listens during a news conference about the death of her son Tuesday, Jan. 31, 2023, at Mason Temple in Memphis, Tenn. A funeral service for Nichols, who died after being beaten by...}

\entryitemWithDescription{\hskip 0pt{}Turmoil risks financial stability Peru long took for granted}{https://apnews.com/article/cdaa782b20ed607d44a02573f0965de4}{Residents protest as they wait outside a gas plant to buy propane for cooking in downtown Cusco, Peru, Friday, Feb. 3, 2023. Gas delivery trucks have been affected by anti-government demonstrators blocking highways across the country...}

\entryitemWithDescription{\hskip 0pt{}Ukraine defense minister expects help from West on warplanes}{https://apnews.com/article/5a6bd8f0f8883eba460be07c6b3cf7a7}{An injured man evacuates with family members from a residential building which was hit by a Russian rocket at the city center of Kharkiv, Ukraine, Sunday, Feb. 5, 2023. (AP Photo/Andrii Marienko) KYIV, Ukraine (AP) --- Ukraine...}

\entryitemWithDescription{\hskip 0pt{}Europe bans Russian diesel, other oil products over Ukraine}{https://apnews.com/article/a855facf78132a8805c9ba52dd0fab60}{FILE - A fuel trucks drives along a highway in Frankfurt, Germany, Jan. 27, 2023. European Union governments tentatively agreed Friday Feb. 3, 2023, to set a \$100-per-barrel price cap on sales of Russian diesel to coincide with an EU...}

\entryitemWithDescription{\hskip 0pt{}Election skeptics slow to get sweeping changes in GOP states}{https://apnews.com/article/698d704ddb103c36b077d74dcd7e1a55}{FILE - Then-Republican candidate for Indiana Secretary of State Diego Morales speaks during an interview in Indianapolis, Sept. 20, 2022. Republicans in a handful of red states won their campaigns for secretary of state last year after...}