\entryitemWithDescription{\hskip 0pt{}Justice Department sues TikTok, accusing the company of illegally collecting children's data}{https://apnews.com/article/eb0110e6f2281d8b9a7d2cad0af2e525}{The Justice Department sued TikTok on Friday, accusing the company of violating children's online privacy law and running afoul of a settlement it had reached with another federal agency. The complaint, filed together with the Federal...}

\entryitemWithDescription{\hskip 0pt{}Federal judge overturns \$4.7 billion jury verdict in `Sunday Ticket' lawsuit and rules for NFL}{https://apnews.com/article/f91c35820a1e59b3419d5bb1b88f9a08}{LOS ANGELES (AP) --- A federal judge has overturned a jury's \$4.7 billion verdict in the class-action lawsuit filed by ``Sunday Ticket'' subscribers against the NFL and has granted judgment to the NFL. U.S. District Judge Philip...}

\entryitemWithDescription{\hskip 0pt{}Sunisa Lee's long road back to the Olympics ended in a familiar spot: the medal stand}{https://apnews.com/article/d9b474fece0c1f1506373894c291759d}{PARIS (AP) --- Sunisa Lee called coach Jess Graba not long ago and told him it was over. The process of trying to navigate two kidney diseases that made the 2020 Olympic gymnastics champion's weight yo-yo had become too much. The...}

\entryitemWithDescription{\hskip 0pt{}Jimmy Carter's 100th birthday to be celebrated with musical gala at Atlanta's Fox Theatre}{https://apnews.com/article/ea362d89fb2e86da3b14120473f63827}{ATLANTA (AP) --- Former President Jimmy Carter will be honored next month, ahead of his 100th birthday, with a musical gala at the Fox Theatre in Atlanta, The Carter Center announced Thursday. The Sept. 17 event --- ``Jimmy Carter 100: A...}

\entryitemWithDescription{\hskip 0pt{}Bookmaker to plead guilty in gambling case tied to baseball star Shohei Ohtani's ex-interpreter}{https://apnews.com/article/65a16913c1dd5b428581d6863df777e8}{LOS ANGELES (AP) --- A Southern California bookmaker who took thousands of sports bets from the ex-interpreter for baseball star Shohei Ohtani has agreed to plead guilty to running an illegal gambling business, U.S. authorities announced...}

\entryitemWithDescription{\hskip 0pt{}Remember the ice bucket challenge? 10 years later, the viral campaign is again fundraising for ALS}{https://apnews.com/article/98578d550efff9923eb1db945099ebbc}{BOSTON (AP) --- Dozens of people, including the Massachusetts governor and several sports stars, dumped cold water on themselves at Fenway Park Thursday to mark the 10th anniversary of the ALS ice bucket challenge. The event is part of an...}

\entryitemWithDescription{\hskip 0pt{}Cardi B files for divorce from Offset, posts she's pregnant with their third child on Instagram}{https://apnews.com/article/b2b33367c6da8ca33e0ac53de3d1c006}{NEW YORK (AP) --- Cardi B has filed for divorce from her husband, Migos' rapper Offset. A representative for Cardi B confirmed the news to The Associated Press, writing, ``This is not based on any one particular incident, it has been a...}

\entryitemWithDescription{\hskip 0pt{}Who is Yusuf Dikec, the Turkish shooter who went viral at the 2024 Olympics?}{https://apnews.com/article/a7890124304080a48e7ee4294004d306}{CHATEAUROUX, France (AP) --- Turkish pistol shooter Yusuf Dikec has gone viral on social media for his seemingly casual attitude while shooting his way to a silver medal at the 2024 Olympics. The most-shared images show Dikec shooting in...}

\entryitemWithDescription{\hskip 0pt{}Tahiti's youth surf culture gets a boost as island hosts the Paris Olympics}{https://apnews.com/article/0d6aa6aa6bea29f8df122037a0c14d33}{TEAHUPO'O, Tahiti (AP) --- As the heavy, barrel-shaped waves of Teahupo'o, Tahiti --- where the Paris Olympics surfing competition is being held --- crashed in the distance, another, smaller surf session was underway just off the shore. ``...}

\entryitemWithDescription{\hskip 0pt{}Don't panic! Taylor Swift warns fans to expect sirens for WWII anniversary in Warsaw before concert}{https://apnews.com/article/7a7fb64f2b37e74d9feb60f1ccf7bedf}{WARSAW, Poland (AP) --- Taylor Swift is telling fans traveling to her concert in Warsaw on Thursday to not panic, and expect to hear loud sirens in the afternoon honoring a key World War II anniversary. The Polish capital is holding...}

\entryitemWithDescription{\hskip 0pt{}MrBeast, YouTube's biggest star, acknowledges past `inappropriate language' as controversies swirl}{https://apnews.com/article/742306d7c77e2eca8d895bf439790c69}{NEW YORK (AP) --- MrBeast, YouTube's biggest star and a philanthropic force with nearly unrivaled influence among young audiences, acknowledged Wednesday that he used ``inappropriate language'' in his early online days, as numerous...}

\entryitemWithDescription{\hskip 0pt{}Former ballerina is convicted of manslaughter in her estranged husband's 2020 shooting}{https://apnews.com/article/ac5bacf9bf958d6bfab322fdbff2effd}{BRADENTON, Fla. (AP) --- A former ballerina has been convicted of manslaughter in the 2020 shooting death of her estranged husband in Florida. A Manatee County jury returned the guilty verdict late Tuesday against Ashley Benefield, court...}

\entryitemWithDescription{\hskip 0pt{}White House chef retires after nearly 30 years, 1st woman and 1st person of color to have the job}{https://apnews.com/article/4f30d444c822863edfcf6c0fdf8ba234}{WASHINGTON (AP) --- The White House's executive chef has retired after nearly three decades of making meals and cooking up state dinners for five different presidents and their families. Cris Comerford is the first woman to hold the job...}