\entryitemWithDescription{\hskip 0pt{}Mega Millions jackpot soars to \$875 million. Powerball reaches \$600 million}{https://apnews.com/article/a1c037c3dc7bc7a068cdc92e0aacd7db}{FORT LAUDERDALE, Fla. (AP) --- If you're feeling some St. Patrick's Day magic, you might want to buy a lottery ticket. Mega Millions and Powerball have racked up some massive jackpots after weeks of rolloevers. The Mega Ball jackpot is...}

\entryitemWithDescription{\hskip 0pt{}David Breashears, mountaineer and filmmaker who co-produced Mount Everest documentary, dies at 68}{https://apnews.com/article/f0fce6335b03c214af034af278cdcfa3}{MARBLEHEAD, Mass. (AP) --- David Breashears, a mountaineer, author and filmmaker who co-directed and co-produced a 1998 IMAX documentary about climbing Mount Everest, has died, his business manager confirmed Saturday. He was 68...}

\entryitemWithDescription{\hskip 0pt{}When it's St. Patrick's Day in New Orleans, get ready to catch a cabbage}{https://apnews.com/article/adc19a1b6274fea2fc31f1c898480fb1}{NEW ORLEANS (AP) --- The grandly colonnaded old city hall was designed by an Irish architect. A neighborhood near the wharves is still known as the Irish Channel. Landmark towers and spires of Catholic churches built for Irish immigrants...}

\entryitemWithDescription{\hskip 0pt{}Bernie Sanders wants the US to adopt a 32-hour workweek. Could workers and companies benefit?}{https://apnews.com/article/076c14dd52c7938bfb41e988a9a6d347}{The 40-hour workweek has been standard in the U.S. for more than eight decades. Now some members of Congress want to give hourly workers an extra day off. Sen. Bernie Sanders, the far-left independent from Vermont, this week introduced a...}

\entryitemWithDescription{\hskip 0pt{}North Dakota voters will decide whether 81 is too old to serve in Congress}{https://apnews.com/article/455d21a9a8e2cbfb76c0e663410ec1a9}{BISMARCK, N.D. (AP) --- North Dakota voters will decide this June whether to prevent people from running for Congress if they're old enough to turn 81 during their House or Senate term. A signature drive has succeeded in adding the...}

\entryitemWithDescription{\hskip 0pt{}Los Angeles home that appears to belong to model and actor Cara Delevingne is destroyed in fire}{https://apnews.com/article/e4fb9dbc5c0fb3c88b7f27e81a71eae5}{LOS ANGELES (AP) --- A Los Angeles home that appears to belong to model and actor Cara Delevingne was destroyed in a fire Friday. One firefighter was taken to a hospital in fair condition with unspecified injuries, and one unidentified...}

\entryitemWithDescription{\hskip 0pt{}Steelers trade Kenny Pickett to the Eagles after signing Russell Wilson, sources tell the AP}{https://apnews.com/article/85f24514b39b6b810dcd520aaefe7ed2}{PITTSBURGH (AP) --- The brief and tumultuous Kenny Pickett era in Pittsburgh is over. The Steelers are trading the quarterback to the Philadelphia Eagles, multiple sources told The Associated Press. The sources spoke on condition of...}

\entryitemWithDescription{\hskip 0pt{}Riders can climb `halfway to the stars' on San Francisco cable car dedicated to late Tony Bennett}{https://apnews.com/article/4d8598ffbb4e7dfde5e6a0dd24a1a03e}{SAN FRANCISCO (AP) --- A cable car recently dedicated to the late Tony Bennett rolls past the landmark Fairmont hotel where the singer in 1961 first performed the song that would forever tie him to San Francisco. San Francisco officials...}

\entryitemWithDescription{\hskip 0pt{}Aaron Donald announces his retirement after a standout 10-year career with the Rams}{https://apnews.com/article/87dc21efe0449a4d29f587e743482c65}{LOS ANGELES (AP) --- Defensive lineman Aaron Donald has announced his retirement after a standout 10-year career with the Los Angeles Rams. The three-time AP NFL Defensive Player of the Year made his surprising announcement on social...}

\entryitemWithDescription{\hskip 0pt{}Jim McAndrew, who pitched for the 1969 and 1973 New York Mets, dies at 80}{https://apnews.com/article/07c689bb7281fd82e0e84be4e1e35e23}{NEW YORK (AP) --- Jim McAndrew, who lost his major league debut to Bob Gibson in a 1968 spot start for the New York Mets when Nolan Ryan was called away to military duty, then beat Steve Carlton a month later for his first win, has died...}

\entryitemWithDescription{\hskip 0pt{}Best Buy recalls over 287,000 air fryers due to overheating issue that can melt or shatter parts}{https://apnews.com/article/256b5536484c8bab25813869d900264b}{NEW YORK (AP) --- Best Buy is recalling more than 287,000 air fryers and air fryer ovens due to an overheating issue that can cause the products' parts to melt or shatter, posing fire and laceration risks. According to a Thursday notice...}

\entryitemWithDescription{\hskip 0pt{}Colorado snowstorm closes highways and schools for a second day}{https://apnews.com/article/4a7e73a203f94f815c8ea9f5aaffffc4}{DENVER (AP) --- Thousands in Colorado were without power as authorities closed highways and schools during a winter storm that pummeled the Denver area and threatened to drop another half foot there overnight into Friday. The storm comes...}

\entryitemWithDescription{\hskip 0pt{}Seat belt saved passenger's life on Boeing 737 jet that suffered a blowout, new lawsuit says}{https://apnews.com/article/cdc4af3e0047723cdfc4bae301243367}{SEATTLE (AP) --- More passengers who were aboard an Alaska Airlines Boeing 737 jet when part of its fuselage blew out in January are suing --- including one who says his life was saved by a seat belt. The latest lawsuit, representing...}