\entryitemWithDescription{\hskip 0pt{}Angelina Jolie unveils fashion venture aimed at sustainability, assisting refugees}{https://apnews.com/article/194d2c476a1ca5711df3429c42f6a302}{FILE - Angelina Jolie poses for photographers upon arrival at the premiere of the film \textquotesingle Eternals\textquotesingle{} on Oct. 27, 2021, in London. Jolie announced a new fashion venture Wednesday aimed at allowing customers to...}

\entryitemWithDescription{\hskip 0pt{}Daytime Emmy Awards postponed because of writers strike}{https://apnews.com/article/84361a0f337cdbbc981800bbeef1438e}{FILE - An Emmy statue appears one stage at the 49th annual Daytime Emmy Awards in Pasadena, Calif., on June 24, 2022. This year\textquotesingle s show, set for June 16 in Los Angeles, is being postponed indefinitely because of the strike...}

\entryitemWithDescription{\hskip 0pt{}Death toll up to 7 after hippo capsized canoe in Malawi; 17 missing}{https://apnews.com/article/d4b3679e4a67271781e3eddd0aac3bd8}{CAPTION CORRECTS LEFT AND RIGHT AND JOB TITLES Malawi\textquotesingle s Minister of Water and Sanitation Abida Mia, left, waits with local Member of Parliament Gladys Ganda, right,for news updates from the rescue party on the banks of...}

\entryitemWithDescription{\hskip 0pt{}CNN names Kaitlan Collins to fill prime-time vacancy in Chris Cuomo's old slot}{https://apnews.com/article/09f81bc8406a3067e077ef9ac632ae23}{FILE - Journalist Kaitlan Collins poses for photographers as she arrives at the annual White House Correspondents\textquotesingle{} Association Dinner in Washington, on April 29, 2023. Collins will host a new show at the center of its...}

\entryitemWithDescription{\hskip 0pt{}Pale Male, red-tailed hawk who nested above NYC's Fifth Avenue for 30 years, dies at 33}{https://apnews.com/article/c8b4816e885aee9ad5d0ad9522109099}{FILE - Pale Male, a red tailed hawk, leaves his nest with a rat he just caught hanging from his beak, Thursday, Feb. 17, 2005, in New York. Pale Male, who brought a touch of the wild to swanky Manhattan as he nested above Fifth Avenue...}

\entryitemWithDescription{\hskip 0pt{}Movie Review: A delicious Jason Momoa saves 'Fast X' from furiously speeding off into numbness}{https://apnews.com/article/ed1e7eaebf3bae063a8bf8c6c780469a}{This image released by Universal Pictures shows Vin Diesel in a scene from "Fast X." (Peter Mountain/Universal Pictures via AP) Fans and critics may disagree over when exactly the ``Fast \& Furious'' franchise jumped the shark, but there...}

\entryitemWithDescription{\hskip 0pt{}Justice Department watchdog finds US attorney in Massachusetts tried to influence DA election}{https://apnews.com/article/7ff37567c0d8f7e906ffd1f609a404f3}{FILE - Massachusetts U.S. Attorney Rachael Rollins addresses the media at the Moakley Federal Courthouse, May 24, 2022, in Boston. Rollins will resign after a monthslong ethics investigation by the Justice Department\textquotesingle s...}

\entryitemWithDescription{\hskip 0pt{}Drug overdoses in the US slightly increased last year. But experts see hopeful signs}{https://apnews.com/article/3c3848da5f8aa01d7b9f232ba5a34152}{FILE - Forensic assistant Laurentiu Bigu, left, and investigator Ryan Parraz from the Los Angeles County coroner\textquotesingle s office cover the body of a homeless man found dead on a sidewalk in Los Angeles on April 18, 2022. The 60...}

\entryitemWithDescription{\hskip 0pt{}2nd escaped inmate captured after breaking out of Philadelphia prison}{https://apnews.com/article/aaf3cb0b0ec708ed83f8d6156dd150d9}{This photo provided by Philadelphia Dept. of Prisons shows Ameen Hurst. The second of two inmates who escaped from a Philadelphia prison earlier this month was captured Wednesday, May 17, 2023, authorities said. City police Commissioner...}

\entryitemWithDescription{\hskip 0pt{}PEN America, Penguin Random House sue Florida school district over book bans}{https://apnews.com/article/5e648efdf241e333c9d5b042e65a7be6}{FILE - Amanda Darrow, director of youth, family and education programs at the Utah Pride Center, poses with books, including "The Bluest Eye," by Toni Morrison, that have been the subject of complaints from parents, on Dec. 16, 2021, in...}

\entryitemWithDescription{\hskip 0pt{}At Cannes Film Festival, Johnny Depp says he has no 'further need for Hollywood'}{https://apnews.com/article/fa8910ca4f67ee1207cd2ebf4cd71f9b}{Johnny Depp, left, and director Maiwenn pose for photographers at the photo call for the film \textquotesingle Jeanne du Barry\textquotesingle{} at the 76th international film festival, Cannes, southern France, Wednesday, May 17, 2023...}

\entryitemWithDescription{\hskip 0pt{}Ford recalls 310,000 trucks to fix problem with driver's front air bag}{https://apnews.com/article/1dfe55432c65a7900f4c987b29ef30ca}{FILE - A Ford sign is shown at a dealership in Springfield, Pa., Tuesday, April 26, 2022. Ford Motor Co. is recalling certain 2004 to 2006 Ranger vehicles, Friday, May 5, 2023, because replacement front passenger air bag inflators may...}

\entryitemWithDescription{\hskip 0pt{}Danish Supreme Court says newspaper did not violate copyright of Little Mermaid statue}{https://apnews.com/article/ce2ed85c43aa0ab910bf1c80295b821c}{FILE - People enjoy the warm sunny weather on a bench in front of the little mermaid statue in Copenhagen, Denmark, on June 10, 2021. Denmark's Supreme Court on Wednesday May 17, 2023 overruled two lower courts, saying a cartoon depicting...}