\entryitemWithDescription{\hskip 0pt{}National Book Awards drop Drew Barrymore as host after her talk show resumes despite strike}{https://apnews.com/article/4f2f4f64ed8703a2415a83b83f965616}{NEW YORK (AP) --- The National Book Awards dropped Drew Barrymore as the host for this year's ceremony on Tuesday, a day after her talk show taped its first episode since the Hollywood writers strike began. ``The National Book Awards is...}

\entryitemWithDescription{\hskip 0pt{}FACT FOCUS: Critics twist California bill that would weigh gender-identity support in custody cases}{https://apnews.com/article/3cc6d2b5282d6b0e8ba9d1ffc55edeb7}{Democratic California lawmakers have approved a bill that would instruct courts to consider, among many other factors, whether a parent affirms a child's gender identity when making custody and visitation decisions. But critics online are...}

\entryitemWithDescription{\hskip 0pt{}Looking for a refill? McDonald's is saying goodbye to self-serve soda in the coming years}{https://apnews.com/article/d7aa46b38c30fad5e42fe33fbb1f6bd1}{NEW YORK (AP) --- Say goodbye to refilling that Coke. McDonald's is getting rid of self-served soda. The Chicago-based fast food chain plans to eliminate self-service soda machines at its U.S. restaurants by 2032, McDonald's confirmed...}

\entryitemWithDescription{\hskip 0pt{}Popular nasal decongestant doesn't actually relieve congestion, FDA advisers say}{https://apnews.com/article/0f140bafae9a500c5fba05fe764ecb66}{WASHINGTON (AP) --- The leading decongestant used by millions of Americans looking for relief from a stuffy nose is no better than a dummy pill, according to government experts who reviewed the latest research on the long-questioned drug...}

\entryitemWithDescription{\hskip 0pt{}NASA astronaut Frank Rubio breaks US record for longest spaceflight}{https://apnews.com/article/c3a0f36bb3b44d038f9fc0af99425c16}{NASA astronaut Frank Rubio now holds the record for the longest U.S. spaceflight. Rubio surpassed the U.S. space endurance record of 355 days on Monday at the International Space Station. He arrived at the outpost last September with two...}

\entryitemWithDescription{\hskip 0pt{}Holocaust survivor Eva Fahidi-Pusztai, who warned of far-right populism in Europe, dies at age 97}{https://apnews.com/article/73c960d01b59adfaeeed1f66d409653a}{BERLIN (AP) --- Eva Fahidi-Pusztai, a Holocaust survivor who spent the late years of her life warning of the re-emergence of far-right populism and discrimination against minorities across Europe, has died. She was 97. The International...}

\entryitemWithDescription{\hskip 0pt{}Aerosmith postpones shows after frontman Steven Tyler suffers vocal cord damage}{https://apnews.com/article/a51ab3ee0b279d5d70957eb07f931793}{PHILADELPHIA (AP) --- Aerosmith has postponed a half-dozen dates on their farewell tour because frontman Steven Tyler injured his vocal cords during a performance, Tyler announced Monday. ``I'm heartbroken to say I have received strict...}

\entryitemWithDescription{\hskip 0pt{}Candidate in high-stakes Virginia election performed sex acts with husband in live videos}{https://apnews.com/article/9e0fa844a3ba176f79109f7393073454}{RICHMOND, Va. (AP) --- A candidate in a high-stakes legislative contest in Virginia had sex with her husband in live videos posted on a pornographic website and asked viewers to pay them money in return for carrying out specific sex acts...}

\entryitemWithDescription{\hskip 0pt{}Spicy food challenges have a long history. Have they become too extreme?}{https://apnews.com/article/369f295714ac7f856c815ffe5ad4e961}{NEW YORK (AP) --- A tortilla chip maker's decision to pull its extremely spicy product sold as a ``One Chip Challenge'' from store shelves following the death of a Massachusetts teen has renewed attention on the popularity --- and...}

\entryitemWithDescription{\hskip 0pt{}Michael Kors pays tribute to late mother with waterfront runway show set to Bacharach tunes}{https://apnews.com/article/36c0755b11a5e3e8a723474dfe758529}{NEW YORK (AP) --- On a waterfront promenade lined with pink flowers and facing Manhattan's majestic skyline, designer Michael Kors paid tribute to his late mother with a show honoring the travels the two enjoyed together. As always, Kors...}

\entryitemWithDescription{\hskip 0pt{}DraftKings apologizes for sports betting offer referencing 9/11 terror attacks}{https://apnews.com/article/8677a604567df6e6cab678bf148f2795}{ATLANTIC CITY, N.J. (AP) --- Sports betting company DraftKings apologized Monday after using the Sept. 11, 2001, terror attacks to entice people to bet on baseball and football games on the anniversary of the tragedy that killed nearly...}

\entryitemWithDescription{\hskip 0pt{}Sarah Burton, who designed Kate's royal wedding dress, to step down from Alexander McQueen}{https://apnews.com/article/a0bb29f4c656dff2b9718b2ba9e68de5}{LONDON (AP) --- The fashion designer who created the wedding dress of Kate, the Princess of Wales, is stepping down as creative director at Alexander McQueen after two decades at the brand, luxury group Kering said Monday. Designer Sarah...}

\entryitemWithDescription{\hskip 0pt{}Hawaii's Kilauea volcano alert level is downgraded after latest eruption}{https://apnews.com/article/acbd84358872fafe63b3244af7d4d2a9}{HONOLULU (AP) --- The alert level on Kilauea, one of the most active volcanoes in the world, was downgraded Monday with no infrastructure threatened and no threat of significant ash emission into the atmosphere outside a limited area...}