\entryitemWithDescription{\hskip 0pt{}'Cocaine Bear' is here to strike a blow to staid Hollywood}{https://apnews.com/article/979a7487b458db6445b424e349f5492f}{This image released by Universal Pictures shows Keri Russell in a scene from "Cocaine Bear," directed by Elizabeth Banks. (Pat Redmond/Universal Pictures via AP) NEW YORK (AP) --- On Dec. 22, 1985, The Associated Press reported the...}

\entryitemWithDescription{\hskip 0pt{}Jimmy Carter enters hospice care. What is it?}{https://apnews.com/article/86b6d73e53eec03ab3cb9980c71bbb32}{FILE - Former President Jimmy Carter sits on the Atlanta Falcons bench before the first half of an NFL football game between the Atlanta Falcons and the San Diego Chargers, Oct. 23, 2016, in Atlanta. Carter has entered home hospice care...}

\entryitemWithDescription{\hskip 0pt{}Mexico's ex-public security chief convicted in US drug case}{https://apnews.com/article/a4536784e319b390a4d6e66a3ab044d8}{A demonstrators holds a sign that reads "GARCIA LUNA ES CULPABLE," or "GARCIA LUNA IS GUILTY" outside federal court moments before Genaro García Luna was found guilty of taking massive bribes to protect the violent drug cartels he was...}

\entryitemWithDescription{\hskip 0pt{}New START: last US-Russia arms control treaty in jeopardy}{https://apnews.com/article/48e7bfc8ff41c46c1f7797a941129ab3}{Russian President Vladimir Putin gestures as he gives his annual state of the nation address in Moscow, Russia, Tuesday, Feb. 21, 2023. (Dmitry Astakhov, Sputnik, Kremlin Pool Photo via AP) Russian President Vladimir Putin has accused...}

\entryitemWithDescription{\hskip 0pt{}Brittney Griner re-signs with Phoenix Mercury}{https://apnews.com/article/c140d11b46c519f97b6b44b1ceea7f9a}{FILE - Phoenix Mercury\textquotesingle s Brittney Griner (42) shoots over Seattle Storm\textquotesingle s Mercedes Russell in the first half of the second round of the WNBA basketball playoffs Sunday, Sept. 26, 2021, in Everett, Wash...}

\entryitemWithDescription{\hskip 0pt{}EPA orders Norfolk Southern to clean up toxic derailment}{https://apnews.com/article/61ff5fec89c452f4ff7f56b5b8b4e44e}{Environmental Protection Agency Administrator Michael Regan speaks during a news conference in East Palestine, Ohio, Tuesday, Feb. 21, 2023. Regan announced the agency will hold Norfolk Southern accountable for the costs of the cleanup of...}

\entryitemWithDescription{\hskip 0pt{}Seattle Council to vote on outlawing caste discrimination}{https://apnews.com/article/077737f6a251db30b6bca3edd4a83844}{Supporters and opponents of a proposed ordinance to add caste to Seattle\textquotesingle s anti-discrimination laws rally on the steps of Seattle City Hall, Tuesday, Feb. 21, 2023, in Seattle. Council Member Kshama Sawant proposed the...}

\entryitemWithDescription{\hskip 0pt{}'Night Court' reboot returns favorite but set in modern day}{https://apnews.com/article/5c47c75728e1ae12dfb9b2648bc4a23d}{This image released by NBC shows, foreground from left, Melissa Rauch, India de Beaufort and John Larroquette in a scene from the comedy series "Night Court." (Jordin Althaus/NBC/Warner Bros. Television via AP) NEW YORK (AP) --- You can...}

\entryitemWithDescription{\hskip 0pt{}Upper Midwest braces for blizzard, nearly 2 feet of snow}{https://apnews.com/article/d910bb29788ec852255aead97cb2d242}{David Smith shovels the sidewalk as the first snow falls ahead of a winter storm on Tuesday, Feb. 21, 2023, in Sioux Falls, S.D. A wide swath of the Upper Midwest is bracing for a historic winter storm. The system is expected to bury...}

\entryitemWithDescription{\hskip 0pt{}4-day workweek trial: Shorter hours, happier employees}{https://apnews.com/article/d114ef8be69e1665fd22c39515bdaecf}{FILE - A woman types on a laptop while on a train in New Jersey, May 18, 2021. A trial of a four-day workweek in Britain, billed as the world\textquotesingle s largest, has found that an overwhelming majority of the 61 companies that...}

\entryitemWithDescription{\hskip 0pt{}Former US Rep. Adam Kinzinger to release book in October}{https://apnews.com/article/c221d4ba44b66bb240bfbcd24cc8c919}{FILE - Rep. Adam Kinzinger, R-Ill., speaks as the House select committee investigating the Jan. 6 attack on the U.S. Capitol Hill in Washington on Dec. 19, 2022. The Open Field, a Penguin Random House imprint overseen by Maria Shriver...}

\entryitemWithDescription{\hskip 0pt{}Pay-Per-Chew: More restaurants trying subscription programs}{https://apnews.com/article/7012f0ee968e761b257818658c515648}{Matt Baker, chef and owner of Gravitas, poses for a portrait inside the restaurant, Tuesday, Feb. 14, 2023, in Washington. Gravitas has a subscription service offering a monthly meal for two. (AP Photo/Jacquelyn Martin) Consumers are...}

\entryitemWithDescription{\hskip 0pt{}Russia suspends only remaining major nuclear treaty with US}{https://apnews.com/article/23cc21a1f42798177a40d4e53204b054}{Russian President Vladimir Putin gives his annual state of the nation address in Moscow, Russia, Tuesday, Feb. 21, 2023. (Maxim Blinov, Sputnik, Kremlin Pool Photo via AP) MOSCOW (AP) --- Russian President Vladimir Putin declared Tuesday...}