\entryitemWithDescription{\hskip 0pt{}Mardi Gras is coming. Here's what to know about New Orleans' parades and parties}{https://apnews.com/article/76b07c5cab490589b53b3f79e06ea228}{NEW ORLEANS (AP) --- Carnival season 2024 entered its final days in New Orleans on Friday as a parade of ``fabulous women and the men who support them'' walked the narrow streets of the old French Quarter handing out hand-decorated bras...}

\entryitemWithDescription{\hskip 0pt{}Magnitude 5.7 earthquake strikes Mauna Loa volcano on Hawaii's Big Island; no tsunami expected}{https://apnews.com/article/eaba3c465f0fd3269372c785e27f117f}{HONOLULU (AP) --- A magnitude 5.7 earthquake struck the world's largest active volcano on Friday --- Mauna Loa on the Big Island of Hawaii --- knocking items off shelves in nearby towns but not immediately prompting reports of serious...}

\entryitemWithDescription{\hskip 0pt{}Drug possession charge against rapper Kodak Black dismissed in Florida}{https://apnews.com/article/1c21974ad331329fb7bb25692717b740}{FORT LAUDERDALE, Fla. (AP) --- A drug possession charge against South Florida rapper Kodak Black was dismissed Friday, two months after an arrest, though a drug trafficking case from 2022 remains ongoing. Broward County Circuit Judge...}

\entryitemWithDescription{\hskip 0pt{}Fire causes extensive damage to iconic Chicago restaurant known for its breakfasts}{https://apnews.com/article/374ef1c77a6803d285ae6e6ae0937ff4}{CHICAGO (AP) --- An overnight fire caused extensive damage to an iconic Chicago restaurant that's known for its breakfasts and is filled with decades of memorabilia, authorities said. Firefighters were called to the Palace Grill around 10...}

\entryitemWithDescription{\hskip 0pt{}An Oklahoma judge who sent more than 500 texts during a murder trial resigns}{https://apnews.com/article/b17209b610432c017887678cc587dbc6}{OKLAHOMA CITY (AP) --- An Oklahoma judge who sent more than 500 texts to her bailiff during a murder trial will resign, according to a court filing. In a proposed settlement agreement filed Thursday with the Oklahoma Court on the...}

\entryitemWithDescription{\hskip 0pt{}Meta removes Instagram and Facebook accounts for Iran's Supreme Leader Ayatollah Ali Khamenei}{https://apnews.com/article/cb6a0551528903b6b1531afe39ee79cb}{DUBAI, United Arab Emirates (AP) --- Meta has removed Instagram and Facebook accounts run on behalf of Iran's Supreme Leader Ayatollah Ali Khamenei after criticism over his support for Hamas after its Oct. 7 attack on Israel that sparked...}

\entryitemWithDescription{\hskip 0pt{}Astronauts from Turkey, Italy and Sweden return to Earth, ending private space station trip}{https://apnews.com/article/71094fbdd0e7a43f17d2f44f4baf667a}{CAPE CANAVERAL, Fla. (AP) --- Astronauts from Turkey, Italy and Sweden returned to Earth on Friday, ending a private three-week mission to the International Space Station. The trio were accompanied by a retired NASA astronaut who now...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry settles a case against a UK tabloid publisher that hacked his phone}{https://apnews.com/article/a19a1b730cd1c2cff7a2930db973316a}{LONDON (AP) --- A British newspaper publisher has agreed to pay Price Harry a ``substantial'' sum in costs and damages for invading his privacy with phone hacking and other illegal snooping, Harry's lawyer said Friday. Attorney David...}

\entryitemWithDescription{\hskip 0pt{}Volcanic eruption in Iceland subsides, though scientists warn more activity may follow.}{https://apnews.com/article/f6f4405f9ae520d8ea637dccd2a7fa7a}{LONDON (AP) --- A volcanic eruption in southwestern Iceland appears to have subsided, though scientists are warning that the area may experience further eruptions in the coming months. Iceland's Meteorological Office said late Thursday...}

\entryitemWithDescription{\hskip 0pt{}Superstar DJ Tiësto says he has to pull out of Super Bowl show for family reasons}{https://apnews.com/article/acb1868192b946befd629701afc19f08}{THE HAGUE (AP) --- Dutch music producer DJ Tiësto has withdrawn from performing at Sunday's Super Bowl due to an undisclosed family matter. Tiësto, whose real name is Tijs Verwest, wrote on social media on Thursday he would miss the...}

\entryitemWithDescription{\hskip 0pt{}McCaffrey wins AP Offensive Player of the Year, Garrett wins AP Defensive Player of the Year}{https://apnews.com/article/93a7eeac1dd0a0efd13260690c73314b}{LAS VEGAS (AP) --- Christian McCaffrey ran away with the AP Offensive Player of the Year award announced at NFL Honors on Thursday night. San Francisco's All-Pro running back received 39 of 50 first-place votes and earned 222 points...}

\entryitemWithDescription{\hskip 0pt{}Damar Hamlin on a lesson of the past year: `Trust what you know and trust what got you here'}{https://apnews.com/article/c3a4259400c949877a56b3da4f03bf4e}{LAS VEGAS (AP) --- Damar Hamlin learned a lot about himself over the past year. That's no surprise after his near-death experience on the field about 13 months ago. Hamlin spoke for a few minutes Thursday on a platform overlooking radio...}

\entryitemWithDescription{\hskip 0pt{}Kobe Bryant immortalized with a 19-foot bronze statue outside the Lakers' downtown arena}{https://apnews.com/article/91ebea04b65df3bd0eac078f472577be}{LOS ANGELES (AP) --- The Los Angeles Lakers unveiled a statue of Kobe Bryant on Thursday, honoring their late superstar with a 19-foot bronze likeness outside their downtown arena. The 4,000-pound statue depicts Bryant in his white No. 8...}