\entryitemWithDescription{\hskip 0pt{}Marvel returns to Comic-Con with hotly anticipated panel about its post-'Deadpool \& Wolverine' plans}{https://apnews.com/article/c166d593d55e43825e3c8b397e5038ed}{SAN DIEGO (AP) --- Marvel Studios is returning to San Diego Comic-Con for its iconic Saturday night panel, which is expected to feature big announcements and surprise guests. After Marvel skipped the convention last year due to the...}

\entryitemWithDescription{\hskip 0pt{}Justin Timberlake's lawyer says pop singer wasn't intoxicated, argues DUI charges should be dropped}{https://apnews.com/article/73460ad0724553143b2dc4a3d247e065}{Justin Timberlake 's lawyer said Friday that the pop singer wasn't intoxicated during a traffic stop last month, as he seeks to get his drunken driving charge in New York's Hamptons dismissed, citing errors in documents submitted by...}

\entryitemWithDescription{\hskip 0pt{}Wreckage of schooner that sank in 1893 found in Lake Michigan}{https://apnews.com/article/a8ff26fb53bffc669ce6841fb1c45fa5}{ALGOMA, Wis. (AP) --- Marine archaeologists have discovered the wreckage of schooner that sank in Lake Michigan in the late 1800s. The Wisconsin Underwater Archaeology Association announced this month that its searchers found the Margaret...}

\entryitemWithDescription{\hskip 0pt{}A missing 12-year-old Georgia girl is found in Ohio after her community galvanized to locate her}{https://apnews.com/article/5dc5e84161d29a11a87910d0c8d363f9}{ATLANTA (AP) --- A 12-year-old girl whose disappearance galvanized a Georgia community has been found in Ohio. Hall County Sheriff Gerald Couch said Friday that Maria Gomez-Perez was found Thursday in Dover, about 70 miles (110...}

\entryitemWithDescription{\hskip 0pt{}Kevin Spacey's waterfront Baltimore condo sold at auction after foreclosure}{https://apnews.com/article/7b182542fa01b88258a4a17818333552}{BALTIMORE (AP) --- Kevin Spacey's \$5.6 million waterfront condominium in Baltimore has been sold at auction amid the disgraced actor's financial struggles following a slew of sexual misconduct allegations. Last summer, a London jury...}

\entryitemWithDescription{\hskip 0pt{}Former Chiefs lineman Isaiah Buggs sentenced to hard labor in Alabama on animal cruelty charges}{https://apnews.com/article/cb03b8a8ed9ce7e93c0e81e7c3ddb9ce}{TUSCALOOSA, Ala. (AP) --- Former Kansas City Chiefs defensive lineman Isaiah Buggs has been convicted on two counts of misdemeanor animal cruelty charges. Tuscaloosa County District Judge Joanne Jannik sentenced Buggs on July 19 to a year...}

\entryitemWithDescription{\hskip 0pt{}They expected an Olympic boon. But some Paris businesses are experiencing a bust}{https://apnews.com/article/4eeff4e9943d1b7276d2818d036435e3}{PARIS (AP) --- On a typical summer day, tourists flock to the historic Marais district of Paris, wandering its charming medieval streets dotted with ultra-chic boutiques, gazing at stunning private mansions, strolling through the elegant...}

\entryitemWithDescription{\hskip 0pt{}Sunken treasure: Is the champagne nestled in a 19th-century shipwreck still fit for a toast?}{https://apnews.com/article/7f28b2f65897804afed35bc682e48938}{WARSAW, Poland (AP) --- Is the 19th century Champagne on the bottom of the Baltic Sea still fit for a toast? A team of Polish divers has discovered the wreckage of an old sailing ship loaded ``to the brim'' with luxury goods including...}

\entryitemWithDescription{\hskip 0pt{}Harvey Weinstein hospitalized with COVID-19 and pneumonia}{https://apnews.com/article/7eeaca45b029e5735fde50eef93eb18c}{NEW YORK (AP) --- Former film mogul Harvey Weinstein has been transferred from a New York City jail to a hospital to undergo treatment for a variety of health problems including COVID-19 and pneumonia in both lungs, his representatives...}

\entryitemWithDescription{\hskip 0pt{}WWII veteran killed in Germany returns home to California}{https://apnews.com/article/7df0b780b245673a1f58b96c018a5af7}{LOS ANGELES (AP) --- After 80 years, a World War II sergeant killed in Germany has returned home to California. On Thursday, community members lined the roads to honor U.S. Army Air Force Tech. Sgt. Donald V. Banta as he was brought from...}

\entryitemWithDescription{\hskip 0pt{}Rescued walrus calf `sassy' and alert after seemingly being left by her herd in Alaska}{https://apnews.com/article/2e76b9c3917c5dedc11b3ded7393007d}{JUNEAU, Alaska (AP) --- A walrus calf seemingly left behind by her herd near Alaska's northernmost city is alert and ``sassy'' as she receives care at a nonprofit wildlife response center hundreds of miles away following her recent...}

\entryitemWithDescription{\hskip 0pt{}Gizmo the dog went missing in Las Vegas in 2015. He's been found alive after 9 years}{https://apnews.com/article/cb3114985d43e2ac12a5062c48447794}{LAS VEGAS (AP) --- Judith Monarrez crumpled onto her kitchen floor and wept when the news arrived in an email: Gizmo, her pet dog missing for nine years, had been found alive. Monarrez was 28 and living with her parents in 2015 when...}

\entryitemWithDescription{\hskip 0pt{}Hulk Hogan visits Detroit Lions camp, says coach Dan Campbell missed his calling as a wrestler}{https://apnews.com/article/c0ae32309c25323e4a74b8def0390700}{ALLEN PARK, Mich. (AP) --- Hulk Hogan, visiting Detroit Lions practice, said coach Dan Campbell would have been good in the squared circle. The pro wrestling great even came up with a nickname for Campbell: ``Dirty Dan.'' ``He probably...}