\entryitemWithDescription{\hskip 0pt{}New Jersey infant killed, parents injured in apparent attack by family dog, police say}{https://apnews.com/article/0b450af6cdb26c4886f81aff4036d30b}{WOODBRIDGE, N.J. (AP) --- An infant was killed and the child's parents injured in an apparent attack by a dog at a New Jersey home over the weekend, authorities said. Middlesex County prosecutors and Woodbridge police said officers...}

\entryitemWithDescription{\hskip 0pt{}`Kung Fu Panda 4' opens No. 1, while `Dune: Part Two' stays strong}{https://apnews.com/article/6a19e8307885dbbc68b7d90db25c7146}{LOS ANGELES (AP) --- As Universal Pictures prepared for a big night at the Academy Awards with ``Oppenheimer,'' the studio also celebrated the No. 1 debut of ``Kung Fu Panda 4,'' which collected \$58.3 million in domestic theaters over...}

\entryitemWithDescription{\hskip 0pt{}2 National Guard soldiers, 1 Border Patrol agent killed in Texas helicopter crash are identified}{https://apnews.com/article/4ef0071f7ab806f93f4f7e1038aa10f5}{LA GRULLA, Texas (AP) --- A National Guard soldier from New York who was seriously injured in the crash of a helicopter flying over the U.S.-Mexico border remained hospitalized Sunday while authorities released the names of the two...}

\entryitemWithDescription{\hskip 0pt{}Princess of Wales appears in first photo since surgery amid wild speculation of her whereabouts}{https://apnews.com/article/ca91acf667c87c6c70a7838347d6d4fb}{LONDON (AP) --- The first photo of Kate, the Princess of Wales, since her abdominal surgery nearly two months ago was issued Sunday along with a statement thanking the public for its support. The photo of her in a chair surrounded by her...}

\entryitemWithDescription{\hskip 0pt{}These Barbies partied with Chanel the night before the Oscars}{https://apnews.com/article/22b759292df4dd7b213172f48c1c4321}{BEVERLY HILLS, Calif. (AP) --- The night before the Oscars isn't a time to rest in Hollywood. For quite a few nominees, including ``Barbie'' star Margot Robbie, it meant a stop at the historic Beverly Hills Hotel for the 15th annual...}

\entryitemWithDescription{\hskip 0pt{}Rescue effort launched to assist 3 people at New Hampshire's Tuckerman Ravine ski area}{https://apnews.com/article/0b5e8954f38c6fa68cef0220b0b78172}{SARGENT'S PURCHASE, N.H. (AP) --- Two people were rescued and emergency crews were attempting to rescue a third Saturday at a ski area on the Northeast's highest mountain, a news report said. The New Hampshire State Police told WMUR-TV...}

\entryitemWithDescription{\hskip 0pt{}Czech Republic's Krystyna Pyszková is crowned Miss World in India}{https://apnews.com/article/f86dc7b37e2a96467916d73a4d4a3986}{MUMBAI, India (AP) --- Krystyna Pyszková of the Czech Republic was crowned Miss World at a glittering contest held in India on Saturday night. Yasmina Zaytoun of Lebanon was the first runner-up among 112 contestants in the competition...}

\entryitemWithDescription{\hskip 0pt{}Auburn student makes a 94-foot, length-of-the-court putt and wins a car}{https://apnews.com/article/8e9c34df0fcb95beb77d162577c90408}{AUBURN, Ala. (AP) --- An Auburn University student connected on a long-distance shot, draining a length-of-the-basketball court putt on Saturday to win a car. Conor Boyle made the 94-foot putt, rolling a golf ball from one baseline and...}

\entryitemWithDescription{\hskip 0pt{}Rupert Murdoch, 92, plans to marry for 5th time}{https://apnews.com/article/7d3c45deb7e48a462135b9633fa5a342}{Media magnate Rupert Murdoch, who turns 93 next week, has been married four times --- and is engaged again, his representative said Saturday. He plans to marry Elena Zhukova, 67, a Russian-born retired scientist he met last year. Her ex...}

\entryitemWithDescription{\hskip 0pt{}2 women drove a man's body to a bank to withdraw his money, Ohio police say}{https://apnews.com/article/d08513648021ffa4147148d46daa266b}{ASHTABULA, Ohio (AP) --- Two Ohio women have been accused of driving the body of a deceased 80-year-old man to a bank to withdraw money from his account before dropping his body off at a hospital. Karen Casbohm, 63, and Loreen Bea Feralo...}

\entryitemWithDescription{\hskip 0pt{}Alabama woman set for a plea hearing months after police say she faked her own kidnapping}{https://apnews.com/article/3ed50ab5e64a7935cce1a97a496df293}{BESSEMER, Ala. (AP) --- A new plea hearing has been set for an Alabama woman accused of falsely telling police she was abducted last summer after stopping her car to check on a toddler wandering near a highway. Carlee Russell's two-day...}

\entryitemWithDescription{\hskip 0pt{}Weather beatdown leaves towering Maine landmark surrounded by crime scene tape}{https://apnews.com/article/bda1bd6d55ba783e0211560f5fbe5665}{SKOWHEGAN, Maine (AP) --- Crime scene tape surrounds the Skowhegan Indian, a local landmark in Maine, after an assault by Mother Nature. The towering wooden sculpture is missing part of its face and arm, as well as a spear. The damage is...}

\entryitemWithDescription{\hskip 0pt{}WWE strikes deal with Logan Paul and KSI's Prime, will feature brand on center of ring mat}{https://apnews.com/article/f0614a7b1307060c332ca6d2a5cb6529}{WWE has struck a deal with Prime, the beverage brand of YouTube stars Logan Paul and KSI, that will see its logo featured on the center of a WWE wrestling ring mat, a first for the sports entertainment company. Financial terms of the...}