\entryitemWithDescription{\hskip 0pt{}A'ja Wilson and Caitlin Clark lead WNBA All-Star fan vote}{https://apnews.com/article/0b9b46d1403accb1d26511a769c3857a}{NEW YORK (AP) --- A'ja Wilson leads Caitlin Clark by just over a thousand votes in early fan voting for the WNBA All-Star Game, the league announced Friday. Clark's Indiana teammate Aliyah Boston is third, about 40,000 votes behind the...}

\entryitemWithDescription{\hskip 0pt{}38 dogs were close to drowning on a Mississippi lake. But some fishermen had quite a catch}{https://apnews.com/article/0fad270987a5750ebfecfc46fb62644c}{ATLANTA (AP) --- By the time fishermen spotted the first head bobbing above the water, the 38 dogs were exhausted and struggling to stay alive. The hound dogs had plunged into a large Mississippi lake while chasing a deer, a diversion...}

\entryitemWithDescription{\hskip 0pt{}Shiny monolith removed from mountains outside Las Vegas. How it got there still is a mystery}{https://apnews.com/article/ae6c044a719d9aee09916c59e886e04b}{LAS VEGAS (AP) --- A strange monolith found jutting out of the rocks in a remote mountain range near Las Vegas has been taken down by authorities. How it got there is still a mystery. ``It remains unknown how the item got to its location...}

\entryitemWithDescription{\hskip 0pt{}Florida Panthers have their 3rd chance to win the Stanley Cup in Game 6 at the Edmonton Oilers}{https://apnews.com/article/9918dd9b3630086df2cdf194e3f945be}{EDMONTON, Alberta (AP) --- The Stanley Cup will be in the building once again on Friday night with the Florida Panthers getting their third chance to win the first championship in franchise history in Game 6 against the Edmonton Oilers...}

\entryitemWithDescription{\hskip 0pt{}Retired Azzurri star Roberto Baggio robbed at home during Italy's loss to Spain}{https://apnews.com/article/3c3942887efd86af78b46c0bfb53d484}{ROME (AP) --- Retired Italy star Roberto Baggio was robbed at gunpoint at his home while watching the national team's game against Spain at the European Championship At least five armed robbers burst into Baggio's villa near the northern...}

\entryitemWithDescription{\hskip 0pt{}UK fans wonder if Taylor Swift will say 'So long, London' after Eras Tour}{https://apnews.com/article/6b25a44d14749d93d607064c77523151}{LONDON (AP) --- Taylor Swift fans enjoy parsing the singer-songwriter's lyrics for references to her romantic life and insights into her state of her mind. But the pop superstar's fans in the U.K. didn't have to listen closely to her...}

\entryitemWithDescription{\hskip 0pt{}Hawaii settles climate change lawsuit filed by youth plaintiffs}{https://apnews.com/article/9244eb020ee3259c5bc34c4580e7df60}{HONOLULU (AP) --- Hawaii's governor and lawyers for youth plaintiffs on Thursday announced they settled a lawsuit alleging Hawaii violated the state constitution by operating a transportation system that harmed the climate and infringed...}

\entryitemWithDescription{\hskip 0pt{}New Mexico judge weighs whether to compel testimony from movie armorer in Alec Baldwin trial}{https://apnews.com/article/e17f731100ee8635ead5bfa84cd7f802}{SANTA FE, N.M. (AP) --- A New Mexico judge is scheduled to consider at a Friday hearing whether to compel a movie set armorer to testify at actor Alec Baldwin's involuntary manslaughter trial for the fatal shooting nearly three years ago...}

\entryitemWithDescription{\hskip 0pt{}Celebrations honor Willie Mays and Negro League players ahead of MLB game at Rickwood Field}{https://apnews.com/article/bea3c97ca31d0b3f8caa9c17befa1dc1}{BIRMINGHAM, Ala. (AP) --- As Ajay Stone strolled around historic Rickwood Field and gazed at tributes displayed in honor of Willie Mays and other Negro Leaguers, he clutched a cherished memory under his arm. It was a picture from 2004 of...}

\entryitemWithDescription{\hskip 0pt{}Donald Sutherland, the towering actor whose career spanned `M.A.S.H.' to `Hunger Games,' dies at 88}{https://apnews.com/article/68b0713a89774964b88ce0a1cc55cc18}{NEW YORK (AP) --- Donald Sutherland, the prolific film and television actor whose long career stretched from ``M.A.S.H.'' to ``The Hunger Games,'' has died. He was 88. Kiefer Sutherland, the actor's son, confirmed his father's death...}

\entryitemWithDescription{\hskip 0pt{}Rapper Travis Scott arrested in Miami Beach for misdemeanor trespassing and public intoxication}{https://apnews.com/article/fc1485b36ee9f069e6ead5b4d8f3137b}{MIAMI BEACH, Fla. (AP) --- Rapper Travis Scott was arrested by Miami Beach police early Thursday on misdemeanor charges of trespassing and public intoxication. Miami Beach police confirmed the arrest, but did not immediately provide any...}

\entryitemWithDescription{\hskip 0pt{}Stonehenge not visibly damaged by protest paint. It's clean and ready to rock the solstice.}{https://apnews.com/article/f93506fdd75d9b5b8be1725f11ad8b33}{LONDON (AP) --- Stonehenge monuments that have stood for thousands of years appear unscathed after climate protesters were arrested for spraying orange paint on them, an official said Thursday. Workers cleaned the stones and the roughly...}

\entryitemWithDescription{\hskip 0pt{}Issey Miyake's wind-inspired show takes flight at Paris Fashion Week}{https://apnews.com/article/a19170ad46886266df4a6e90c4b49d60}{PARIS (AP) --- Diaphanous origami-like sculptures that floated like spring seeds caught in the wind captured the essence of the subtle, rich, and exquisite display from Issey Miyake at Paris Fashion Week --- one of the strongest in...}