\entryitemWithDescription{\hskip 0pt{}Italian officials secure 12th Century leaning tower in Bologna to prevent collapse}{https://apnews.com/article/9ad6d6160f8cdced7a7c94123007e2ef}{MILAN (AP) --- Officials have secured the area around one of two 12th Century towers that have become symbolic of the northern city of Bologna, fearing its leaning could lead to collapse. The city on Friday announced 4.3 million euros (\$...}

\entryitemWithDescription{\hskip 0pt{}Police raid Moscow gay bars after a Supreme Court ruling labeled LGBTQ+ movement `extremist'}{https://apnews.com/article/33e1b9a0110bf22dc2ebc7c42efe6335}{Russian security forces raided gay clubs and bars across Moscow Friday night, less than 48 hours after the country's top court banned what it called the ``global LGBTQ+ movement'' as an extremist organization. Police searched venues...}

\entryitemWithDescription{\hskip 0pt{}Ronaldo walks off to chants of `Messi! Messi!' as his team loses 3-0 in Riyadh derby}{https://apnews.com/article/e262460b0b11c7973bdd325f6e3a78ac}{RIYADH, Saudi Arabia (AP) --- Cristiano Ronaldo walked off the field with the gleeful chants of ``Messi! Messi!'' ringing in his ears from delighted Al-Hilal fans who had just watched their Saudi Pro League team beat the Portugal...}

\entryitemWithDescription{\hskip 0pt{}Protester critically injured after setting self on fire outside Israeli consulate in Atlanta}{https://apnews.com/article/8f17dd72592f86797a45cda9b60605a5}{ATLANTA (AP) --- A protester was in critical condition Friday after setting themself on fire outside the Israeli consulate in Atlanta, authorities said. A security guard who tried to intervene was also injured. A Palestinian flag found at...}

\entryitemWithDescription{\hskip 0pt{}Philadelphia votes to ban ski masks to decrease crime. Opponents worry it'll unfairly target some}{https://apnews.com/article/4f2213f3551f85dfb94ecb7e7228580c}{PHILADELPHIA (AP) --- Philadelphia City Council passed legislation to ban ski masks in some public spaces, a measure supporters say will increase public safety amid high violent crime, but opponents argue it will unfairly target people...}

\entryitemWithDescription{\hskip 0pt{}NOT REAL NEWS: A look at what didn't happen this week}{https://apnews.com/article/99ccb985d8e06b6cc7cd21fba1689a1c}{A roundup of some of the most popular but completely untrue stories and visuals of the week. None of these are legit, even though they were shared widely on social media. The Associated Press checked them out. Here are the facts: \_\_\_...}

\entryitemWithDescription{\hskip 0pt{}Young humpback whale leaps out of Seattle bay, dazzling onlookers}{https://apnews.com/article/8f0aa5af1b3a94052276f0bcbee7ab51}{SEATTLE (AP) --- A humpback whale visiting the waters off Seattle dazzled onlookers Thursday morning with several breaches in the bay just beyond the city's downtown area. The whale has been spotted for the last three days swimming around...}

\entryitemWithDescription{\hskip 0pt{}Sen. Rand Paul performed Heimlich maneuver on choking Sen. Joni Ernst during GOP lunch}{https://apnews.com/article/6cdde719bef9bb82d96903b5b390a16b}{WASHINGTON (AP) --- Sen. Joni Ernst, a Republican from Iowa, was choking on food during a luncheon Thursday when fellow Republican Sen. Rand Paul of Kentucky performed the Heimlich maneuver on her. The incident occurred during a closed...}

\entryitemWithDescription{\hskip 0pt{}`Killers of the Flower Moon' named best film of 2023 by New York film critics}{https://apnews.com/article/3620e2ea34519d9adf139adcbffc68fe}{NEW YORK (AP) --- Martin Scorsese's ``Killers of the Flower Moon'' has been named the best film of the year by the New York Film Critics Circle. It's the third time that Scorsese has been given the best film award from his hometown's...}

\entryitemWithDescription{\hskip 0pt{}Bills linebacker Von Miller turns himself in on felony domestic violence charge}{https://apnews.com/article/2d634ebf2d4824e71cf1f486ba96e612}{DALLAS (AP) --- Buffalo Bills linebacker Von Miller turned himself in to police in a Dallas suburb on Thursday after he was charged in a warrant with domestic violence against the mother of his children, who is pregnant, police said...}

\entryitemWithDescription{\hskip 0pt{}Cristiano Ronaldo faces a \$1 billion class-action lawsuit after promoting Binance NFTs}{https://apnews.com/article/09a034a90785390800cbc254ce0a2f68}{NEW YORK (AP) --- Portuguese soccer star Cristiano Ronaldo has been hit with class-action lawsuit seeking at least \$1 billion in damages for his role in promoting cryptocurrency-related ``non-fungible tokens,'' or NFTs, issued by the...}

\entryitemWithDescription{\hskip 0pt{}Musk uses expletive to tell audience he doesn't care about advertisers that fled X over hate speech}{https://apnews.com/article/f68bf51e756cce822a691b3badb2050a}{NEW YORK (AP) --- Billionaire Elon Musk said Wednesday that advertisers who have halted spending on his social media platform X in response to antisemitic and other hateful material are engaging in ``blackmail'' and, using a profanity...}

\entryitemWithDescription{\hskip 0pt{}Safety officials release details of their investigation into a close call between planes in Texas}{https://apnews.com/article/30544386553310b69dba7f490ed93d17}{DALLAS (AP) --- The air traffic controller on duty when FedEx and Southwest planes nearly collided earlier this year in Texas told investigators that he expected the airliner to take off more quickly --- before the incoming FedEx plane...}