\entryitemWithDescription{\hskip 0pt{}Judge declines to dismiss lawsuits filed against rapper Travis Scott over deadly Astroworld concert}{https://apnews.com/article/36b504c7d03483e7960fd31636cccecc}{HOUSTON (AP) --- A judge has declined to dismiss hundreds of lawsuits filed against rap star Travis Scott over his role in the deadly 2021 Astroworld festival in which 10 people were killed in a crowd surge. State District Judge Kristen...}

\entryitemWithDescription{\hskip 0pt{}Chicago's `rat hole' removed after city determines sidewalk with animal impression was damaged}{https://apnews.com/article/ac59434dcb7a72e93e6420b6e59ab56b}{CHICAGO (AP) --- The ``rat hole'' is gone. A Chicago sidewalk landmark some residents affectionately called the ``rat hole'' was removed Wednesday after city officials determined the section bearing the imprint of an animal was damaged...}

\entryitemWithDescription{\hskip 0pt{}Ex-minor league umpire sues MLB, says he was harassed by female ump, fired for being bisexual man}{https://apnews.com/article/47ef2f5f8ef41b4e4b1960aa509c4884}{NEW YORK (AP) --- A fired minor league umpire sued Major League Baseball on Wednesday, claiming he was sexually harassed by a female umpire and discriminated against because he is male and bisexual. Brandon Cooper, an umpire who worked in...}

\entryitemWithDescription{\hskip 0pt{}100-year-old British D-Day veteran dies before he can honor fallen comrades one more time}{https://apnews.com/article/712c76e0cf919e8060992e9a7b2c5b49}{LONDON (AP) --- British army veteran Bill Gladden, who survived a glider landing on D-Day and a bullet that tore through his ankle a few days later, wanted to return to France for the 80th anniversary of the invasion so he could honor the...}

\entryitemWithDescription{\hskip 0pt{}A portrait by Gustav Klimt has been sold for \$32 million at an auction in Vienna}{https://apnews.com/article/a2935ec7ab5f2777f01c1de727540f76}{VIENNA (AP) --- A portrait of a young woman by Gustav Klimt that was long believed to be lost was sold at an auction in Vienna on Wednesday for 30 million euros (\$32 million). The Austrian modernist artist started work on the ``Portrait...}

\entryitemWithDescription{\hskip 0pt{}London police contain 2 horses that were on the loose in the city. It's still a mystery as to why}{https://apnews.com/article/d0525d510fac63e28e1f6ea663e2c786}{LONDON (AP) --- London police have contained two horses that were seen running around loose without riders in the heart of the U.K. capital on Wednesday morning. City of London police said officers were waiting for a horse box from the...}

\entryitemWithDescription{\hskip 0pt{}Japan's moon lander wasn't built to survive a weekslong lunar night. It's still going after 3}{https://apnews.com/article/78edbd90fd46837d272277700431ed95}{TOKYO (AP) --- Japan's first moon lander has survived a third freezing lunar night, Japan's space agency said Wednesday after receiving an image from the device three months after it landed on the moon. The Japan Aerospace Exploration...}

\entryitemWithDescription{\hskip 0pt{}Olympian Kristi Yamaguchi is `tickled pink' to inspire a Barbie doll}{https://apnews.com/article/05138c29e0996592f5e5a052980b8c9a}{Like many little girls, a young Kristi Yamaguchi loved playing with Barbie. With a schedule packed with ice skating practices, her Barbie dolls became her ``best friends.'' So, it's surreal for the decorated Olympian figure skater to now...}

\entryitemWithDescription{\hskip 0pt{}Korean War veteran from Minnesota will finally get his Purple Heart medal, 73 years late}{https://apnews.com/article/b73bb193467cbcdf3cef08d2fcf0e804}{MINNEAPOLIS (AP) --- A Korean War veteran from Minnesota who still carries shrapnel in his leg from when he was wounded in combat will finally get his Purple Heart medal, 73 years late. The U.S. Army notified Earl Meyer, 96, of St. Peter...}

\entryitemWithDescription{\hskip 0pt{}George Santos ends comeback bid for Congress after raising no money}{https://apnews.com/article/a4c4cc2ea7cb52a13ec9f8dfc5ede86c}{Former U.S. Rep. George Santos on Tuesday said he is dropping his longshot bid to return to Congress, months after he was expelled from the House while facing a slew of federal fraud charges. Santos, who was running as an independent...}

\entryitemWithDescription{\hskip 0pt{}Crew members injured in crash on Georgia set of Eddie Murphy Amazon MGM movie `The Pickup'}{https://apnews.com/article/9bc583f5c0eb75875e31712b1c9b5ed9}{Several crew members were injured and two were hospitalized when a car and truck collided during shooting of the Eddie Murphy film ``The Pickup'' from Amazon MGM Studios, the studio and a person close to the production said Tuesday. A...}

\entryitemWithDescription{\hskip 0pt{}Nikola Jokic's brother reportedly involved in an altercation after the Nuggets beat the Lakers}{https://apnews.com/article/5996b1a3b158bf9f476f6553dbe7e124}{DENVER (AP) --- The NBA and Denver police are looking into an incident in which a man reported to be one of the brothers of Denver Nuggets star Nikola Jokic was seen punching a fan after the team's buzzer-beating 101-99 victory over the...}

\entryitemWithDescription{\hskip 0pt{}Martian skies over Athens? Greece's capital turns an orange hue with dust clouds from North Africa}{https://apnews.com/article/3593a433a6e630fe3fb8ed278134837a}{ATHENS, Greece (AP) --- Skies over southern Greece turned an orange hue on Tuesday as dust clouds blown across the Mediterranean Sea from North Africa engulfed the Acropolis and other Athens landmarks. Strong southerly winds carried the...}