\entryitemWithDescription{\hskip 0pt{}Colorado funeral home with ``green'' burials under investigation after improperly stored bodies found}{https://apnews.com/article/945ad85c3609bfa66987b47c2b20b315}{PENROSE, Colo. (AP) --- Authorities said Thursday they were investigating the improper storage of human remains at a southern Colorado funeral home that performs what they call ``green'' burials without embalming chemicals or metal...}

\entryitemWithDescription{\hskip 0pt{}Indianapolis police capture a cheeky monkey that escaped and went on the lam}{https://apnews.com/article/9bf9a16b22371ffb0dc863d00c6097d8}{INDIANAPOLIS (AP) --- Momo the monkey's taste of freedom is over. The primate spurred an hourslong search on Indianapolis' east side after he escaped Wednesday evening from his owner's property. But the male patas monkey was finally...}

\entryitemWithDescription{\hskip 0pt{}X removes article headlines in latest platform update, widening a rift with news media}{https://apnews.com/article/bebab0753b583929fda7e581625e7a55}{SAN FRANCISCO (AP) --- X, formerly known as Twitter, has stopped showing headlines on articles shared on the platform. Now, X only displays an article's lead image and a link to the story. Plans for the change were first reported by...}

\entryitemWithDescription{\hskip 0pt{}FedEx plane without landing gear skids off runway, but lands safely at Tennessee airport}{https://apnews.com/article/d57861fdd9d0febacc18324514ad3726}{CHATTANOOGA, Tenn. (AP) --- A FedEx plane skidded off the runway during a crash landing at a Tennessee airport when its landing gear did not descend, but no one was injured, officials said. Public safety agencies rushed to the Chattanooga...}

\entryitemWithDescription{\hskip 0pt{}Battery technology in the crashed Venice bus made it less prone to catastrophic fires, experts say}{https://apnews.com/article/998d73a2a36fac82c3d87df69eafb530}{MILAN (AP) --- Italy's transport minister is questioning the spread of electric vehicle technology following the fiery crash of a fully electric shuttle bus that killed 21 people in mainland Venice. But the battery chemistry used by the...}

\entryitemWithDescription{\hskip 0pt{}AT\&T and Gallaudet University unveil a football helmet for deaf and hard of hearing quarterbacks}{https://apnews.com/article/0f1fd5001c7d95953c2a836de2c0c219}{WASHINGTON (AP) --- AT\&T and Gallaudet University have developed a football helmet for players who are deaf or hard of hearing and communicate using American Sign Language. The company and Washington-based school for students who are...}

\entryitemWithDescription{\hskip 0pt{}Biden's dog Commander no longer at White House after biting incidents}{https://apnews.com/article/e2592d3996381ea82e24a13d6666de77}{WASHINGTON (AP) --- President Joe Biden's dog, Commander, is ``not presently on the White House campus'' following a series of biting incidents involving White House staff and U.S. Secret Service officers, a spokesperson for first lady...}

\entryitemWithDescription{\hskip 0pt{}King Charles III's image to appear on Australian coins this year}{https://apnews.com/article/67a6e515053b8da665488b1b5e36cefa}{CANBERRA, Australia (AP) --- An image of King Charles III will soon appear on Australian coins, more than a year after the death of his mother Queen Elizabeth II, officials said Thursday. The gold Australian dollar coin will be the first...}

\entryitemWithDescription{\hskip 0pt{}Too much Taylor? Travis Kelce says NFL TV coverage is `overdoing it' with Swift during games}{https://apnews.com/article/0c02652993a9a4da7762ed304dbff7f8}{Maybe there's too much Taylor, not enough Travis. Travis Kelce agreed Wednesday with the idea that NFL TV coverage has been ``overdoing it'' with the amount of times Taylor Swift has been on screen while attending his Kansas City Chiefs'...}

\entryitemWithDescription{\hskip 0pt{}First leopard cubs born in captivity in Peru climb trees and greet visitors at a Lima zoo}{https://apnews.com/article/7fb8decad4f704e1efb6e0a662b8f460}{LIMA, Peru (AP) --- The first two leopard cubs born in captivity in Peru began climbing trees inside their cages at a Lima zoo Wednesday in their first appearance before the public. The cubs --- a male and a female --- walked in circles...}

\entryitemWithDescription{\hskip 0pt{}Apple releases fix for issue causing the iPhone 15 to run `warmer than expected'}{https://apnews.com/article/e06c75f5e67ea4332af5f0bd3ca259f2}{Apple has released an iOS 17 system update that includes a fix to prevent the iPhone 15 lineup from becoming uncomfortably hot. According to the release's accompanying patch notes, iOS 17.0.3 ``addresses an issue that may cause iPhone to...}

\entryitemWithDescription{\hskip 0pt{}Brett Favre will testify under oath in Mississippi welfare scandal civil case}{https://apnews.com/article/aeb57f694fef0e5647bd30034304ad1e}{JACKSON, Miss. (AP) --- Retired NFL quarterback Brett Favre will answer questions under oath about the misspending of federal welfare money in Mississippi, where public money intended to help some of the nation's poorest people was used...}

\entryitemWithDescription{\hskip 0pt{}Powerball jackpot up to \$1.4 billion after no one matches all the numbers and hits it rich}{https://apnews.com/article/79e5d5541adc5094ad92f7bd71b22421}{PINEVILLE, N.C. (AP) --- The Powerball jackpot climbed to an estimated \$1.4 billion after no players matched all six numbers and hit it rich Wednesday night. The winning numbers announced were: 9, 35, 54, 63, 64 and the Powerball 1...}