\entryitemWithDescription{\hskip 0pt{}Philadelphia LGBTQ leaders arrested in traffic stop the mayor calls `concerning'}{https://apnews.com/article/1aa7d61273b32fd5917767ddd6c6b9c7}{PHILADELPHIA (AP) --- The arrest of two of Philadelphia's LGBTQ leaders by a state trooper during a fraught highway traffic stop is ``very concerning,'' the city's mayor said after a video showing some of what happened circulated on...}

\entryitemWithDescription{\hskip 0pt{}Brothers Travis and Jason Kelce honored with bobblehead giveaway at Cavs-Celtics game}{https://apnews.com/article/8c0272756acdc5613b9d4b2100abc5a0}{CLEVELAND (AP) --- Taylor Swift's boyfriend has taken shaking it off to another level. Travis Kelce, the Kansas City Chiefs tight end who began dating the pop music superstar during this past season, will be honored Tuesday night with a...}

\entryitemWithDescription{\hskip 0pt{}LeBron's 40,000-point club won't see anyone else joining for a long time. Maybe never. Here's why.}{https://apnews.com/article/b0ba6a7a8f5493b0c0960bf7e10bc98e}{Never say never. There's a slim chance that someone will one day join LeBron James in the NBA's 40,000-point club. James crossed the 40,000-point mark on Saturday night, extending the NBA all-time scoring record that he claimed from...}

\entryitemWithDescription{\hskip 0pt{}Two fragile DC neighborhoods hang in the balance as the Wizards and Capitals consider leaving town}{https://apnews.com/article/527ac940c1743363b1afcddd1a1c6dee}{WASHINGTON (AP) --- Already struggling to keep his Chinatown bar afloat, Yousef Tellawi felt a sense of impending doom when he learned that the owner of Washington's Capitals and Wizards wanted to move the teams out of the neighborhood...}

\entryitemWithDescription{\hskip 0pt{}4 new astronauts head to the International Space Station for a 6-month stay}{https://apnews.com/article/f8d61b5b432f2b6bb7a3084e47c84d7a}{CAPE CANAVERAL, Fla. (AP) --- Four astronauts headed to the International Space Station on Sunday where they will oversee the arrivals of two new rocketships during their half-year stint. SpaceX's Falcon rocket blasted off from Kennedy...}

\entryitemWithDescription{\hskip 0pt{}Chris Mortensen, an award-winning reporter who covered the NFL, dies at 72}{https://apnews.com/article/65a48aadadfa4740dab65eba77a01e3c}{Chris Mortensen, the award-winning journalist who covered the NFL for close to four decades, including 32 as a senior analyst at ESPN, died Sunday morning. He was 72. ESPN confirmed Mortensen's death on Sunday. There was no immediate word...}

\entryitemWithDescription{\hskip 0pt{}Volcano on uninhabited Galapagos island erupts, sends lava flowing to sea}{https://apnews.com/article/599450a7a77ceb582edf1d7e5c07cb94}{QUITO, Ecuador (AP) --- A volcano on an uninhabited island in the Galapagos has begun erupting, lighting up the nighttime sky as lava tumbled down its sides toward the sea. The La Cumbre volcano on Fernandina island began erupting...}

\entryitemWithDescription{\hskip 0pt{}Trader Joe's chicken soup dumplings recalled for possibly containing permanent marker plastic}{https://apnews.com/article/74d677e020d8f55bab6635508305e459}{NEW YORK (AP) --- More than 61,000 pounds of steamed chicken soup dumplings sold at Trader Joe's are being recalled for possibly containing hard plastic, U.S. regulators announced Saturday. The Agriculture Department's Food Safety and...}

\entryitemWithDescription{\hskip 0pt{}Fans gather to say goodbye to Flaco the owl in New York City memorial}{https://apnews.com/article/17e7f1aedc181d905880a73b37f8a5ae}{NEW YORK (AP) --- Mournful fans of Flaco the Eurasian eagle-owl were gathering in New York City on Sunday to say goodbye to the beloved celebrity creature who became an inspiration and joy to many as he flew around Manhattan after someone...}

\entryitemWithDescription{\hskip 0pt{}Surfers from Brazil and Australia win final Olympic qualifier in warm and windy Puerto Rico}{https://apnews.com/article/c1996c9ed0b024b277d80c3faae72973}{ARECIBO, Puerto Rico (AP) --- Top surfers Gabriel Medina of Brazil and Sally Fitzgibbons of Australia won the final qualifier for the upcoming Olympics on Sunday following nine days in which scores of competitors faced volatile weather...}

\entryitemWithDescription{\hskip 0pt{}`Dune: Part Two' brings spice power to the box office with \$81.5 million debut}{https://apnews.com/article/6d03d6b9aa6210ae4a517e124acf46de}{Movie theaters were looking for a savior and `` Dune: Part Two '' is delivering on the promise. Armed with sandworms, big screen spectacle and the star power of Timothée Chalamet, Denis Villeneuve 's science fiction epic stormed the North...}

\entryitemWithDescription{\hskip 0pt{}Caitlin Clark is poised to celebrate Iowa senior day by breaking Pete Maravich's NCAA scoring record}{https://apnews.com/article/8d2a9bc33a9fdc59177a5ca4fe7221a9}{The stage is set for the coronation of Caitlin Clark as the all-time NCAA Division I scoring leader when sixth-ranked Iowa closes the regular season against No. 2 Ohio State at Carver-Hawkeye Arena on Sunday. Four days after she broke...}

\entryitemWithDescription{\hskip 0pt{}A bridge where firefighters rescued the driver of a semi dangling over the Ohio River remains closed}{https://apnews.com/article/1f352e8c40145dc5cd6c92a903e03f24}{LOUISVILLE, Ky. (AP) --- A bridge connecting Kentucky and Indiana remained closed Saturday following a harrowing crash and rescue of a tractor-trailer driver left hanging over the bridge's edge. Dramatic photos and video captured the...}