\entryitemWithDescription{\hskip 0pt{}Lawsuit accuses Sean Combs, 2 others of raping 17-year-old girl in 2003; Combs denies allegations}{https://apnews.com/article/53e664171385e8704a9c4135262b888a}{NEW YORK (AP) --- A woman sued the hip-hop mogul Sean ``Diddy'' Combs on Wednesday, claiming he and two other men raped her 20 years ago in a New York City recording studio when she was 17. The woman, whose name wasn't disclosed in the...}

\entryitemWithDescription{\hskip 0pt{}52 sea turtles experiencing `cold stun' in New England flown to rehab in Florida}{https://apnews.com/article/dd3927953123b610edf7f4329c634f4f}{CLEARWATER, Fla. (AP) --- Fifty-two endangered Kemp's ridley sea turtles suffering from ``cold stun'' are rehabbing at four facilities in Florida after a flight on a private plane from the New England Aquarium in Massachusetts. The...}

\entryitemWithDescription{\hskip 0pt{}2 bodies found in creeks as atmospheric river drops record-breaking rain in Pacific Northwest}{https://apnews.com/article/17d983781b3b1516265c82bcc2dddd5b}{PORTLAND, Ore. (AP) --- Authorities in Oregon were investigating the deaths of two people whose bodies were found in creeks this week as an atmospheric river brought heavy rain, flooding and unseasonably warm temperatures to the Pacific...}

\entryitemWithDescription{\hskip 0pt{}Bills GM says edge rusher Von Miller to practice and play while facing domestic violence charge}{https://apnews.com/article/d9a009a8cb1b23819477a0d5b4bfedaa}{ORCHARD PARK, N.Y. (AP) --- Though disappointed in the allegations of domestic violence made against Von Miller, Buffalo Bills general manager Brandon Beane stressed on Wednesday that he wants the legal process to play out and not rush to...}

\entryitemWithDescription{\hskip 0pt{}McDonald's testing new CosMc's chain amid unprecedented global expansion}{https://apnews.com/article/617fb9859fc67e3a8ab4c1440f0ce434}{McDonald's is testing a new restaurant format with customizable drinks and treats designed to appeal to afternoon snackers --- and grab sales from competitors like Starbucks and Dunkin'. The company said Wednesday it will open 10 CosMc's...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift is named Time magazine's person of the year}{https://apnews.com/article/6c8ce1275db4cc326fe6ac94ea20bace}{NEW YORK (AP) --- Is the year of Taylor Swift over now? Not yet. Time magazine named Swift its person of the year on Wednesday, a week after Spotify announced she was the most-played artist on the streaming platform. Swift was picked from...}

\entryitemWithDescription{\hskip 0pt{}When is St. Nicholas Day? And how did this Christian saint inspire the Santa Claus legend?}{https://apnews.com/article/fe4aa5607763558f48171b44036b806d}{NEW YORK (AP) --- The white-bearded Christian saint whose acts of generosity inspired America's secular Santa Claus figure is known worldwide --- but Saint Nicholas' origin story is not. The legends surrounding jolly old St. Nicholas...}

\entryitemWithDescription{\hskip 0pt{}A young nurse suffered cardiac arrest while training on the condition. Fellow nurses saved her life}{https://apnews.com/article/644e02d0491fa3e9a95dcbb65769b3aa}{CONCORD, N.H. (AP) --- Andy Hoang eagerly began her first nursing job this year in New Hampshire, with a desire to specialize in cardiac care. She was excited about attending a November practice session on how to respond to someone in...}

\entryitemWithDescription{\hskip 0pt{}From Barbie's unexpected wisdom to dissent among Kennedys, these are the top quotes of 2023}{https://apnews.com/article/33f2e941b3c719b885284ed441ff85a7}{HARTFORD, Conn. (AP) --- From dissent within the Kennedy family to the unexpected wisdom of Barbie, Yale's 2023 list of notable quotations have something for just about everyone. This year's list is topped by Robert F. Kennedy Jr...}

\entryitemWithDescription{\hskip 0pt{}4 more members of K-pop supergroup BTS to begin mandatory South Korean military service}{https://apnews.com/article/36674ad16a37fc64d76c5b2aae043fad}{SEOUL, South Korea (AP) --- Four more members of the K-pop supergroup BTS are to begin their mandatory South Korean military duties soon, their management agency said. Big Hit Music said in a statement Tuesday that the enlistments are ``...}

\entryitemWithDescription{\hskip 0pt{}Actors vote to approve deal that ended strike, bringing relief to union leaders and Hollywood}{https://apnews.com/article/a7a529acaf6b5b38aac93722db54c193}{LOS ANGELES (AP) --- Hollywood's actors have voted to ratify the deal with studios that ended their strike after nearly four months, bringing an official finish to the labor strife that shook the entertainment industry for most of 2023...}

\entryitemWithDescription{\hskip 0pt{}A pregnant Texas woman is asking a court to let her have an abortion under exceptions to state's ban}{https://apnews.com/article/dc5f97fdccf801f572bb5acffac3ad45}{AUSTIN, Texas (AP) --- A pregnant Texas woman whose fetus has a fatal diagnosis asked a court Tuesday to let her have an abortion, bringing what her attorneys say is the first lawsuit of its kind in the U.S. since Roe v. Wade was...}

\entryitemWithDescription{\hskip 0pt{}Shohei Ohtani met with the Dodgers in LA for 2-3 hours, manager Dave Roberts says}{https://apnews.com/article/3e7b3f092628402bd65503ea9aa41450}{NASHVILLE, Tenn. (AP) --- Shohei Ohtani met with the Los Angeles Dodgers a few days ago at Dodger Stadium, manager Dave Roberts revealed Tuesday at the winter meetings. The two-way star is expected to command a record contract of \$500...}