\entryitemWithDescription{\hskip 0pt{}2 Capitol riot defendants sought by FBI after disappearing}{https://apnews.com/article/c5e18267f95c2a5873f6d4fd80ee283f}{FILE - The FBI seal is pictured in Omaha, Neb., Aug. 10, 2022. The FBI is searching for a Florida woman who was supposed to stand trial Monday, March 6, 2023, on charges stemming from the Jan. 6, 2021, Capitol attack as well as another...}

\entryitemWithDescription{\hskip 0pt{}Tesla price cuts: Flagging demand or tactic to boost sales?}{https://apnews.com/article/f5e5c4b8e2bb8916a384d32ee6f816f2}{FILE - A Tesla logo is seen on a vehicle on display in Austin, Texas, Wednesday, Feb. 22, 2023. On Wednesday, March 1, Tesla executives said the company will use innovative manufacturing techniques and smaller factories to cut the cost of...}

\entryitemWithDescription{\hskip 0pt{}Several GOP states pull out of effort to thwart voter fraud}{https://apnews.com/article/35dc8ffcb754492b67d4bebde16bd6b2}{FILE - Missouri Secretary of State Jay Ashcroft speaks to reporters on June 29, 2022, at his Capitol office in Jefferson City, Mo. In an interview, Ashcroft said he wants the Electronic Registration Information Center, a voluntary system...}

\entryitemWithDescription{\hskip 0pt{}Self-taught chefs win coveted stars from Michelin Guide}{https://apnews.com/article/e02e09e2a0904bbf08a774eec8b419f2}{Georgiana Viou celebrates her star during the 2023 Michelin Guide ceremony in Strasbourg, eastern France, Monday, March 6, 2023. The self-taught chef from the west African country Benin, whose dream was to go to France to become an...}

\entryitemWithDescription{\hskip 0pt{}Florida blogger registration bill 'insane,' Gingrich tweets}{https://apnews.com/article/07f3fa45848f351a0b2696455d0c4372}{State Sen. Jason Brodeur, R-Sanford, stis at his desk in the Florida Senate, May 24, 2022 at the Capitol in Tallahassee, Fla. The Republican lawmaker wants bloggers who write about elected officials to register with the state. The bill...}

\entryitemWithDescription{\hskip 0pt{}Biden's budget and political messages blending for 2024}{https://apnews.com/article/46a5cc7b4ef49d6bc4bf3319930e3d48}{President Joe Biden delivers remarks to the 2023 International Association of Fire Fighters Legislative Conference, Monday, March 6, 2023, in Washington. (AP Photo/Evan Vucci) WASHINGTON (AP) --- With an eye on 2024, President Joe Biden...}

\entryitemWithDescription{\hskip 0pt{}Toblerone drops iconic design due to rules on 'Swissness'}{https://apnews.com/article/a6613a366030282aacb4f140728b13d5}{Two bars of the Toblerone Swiss chocolate are shown, at front is the new style 150 gram bar showing the reduction in triangular pieces, in the background is the older style 360 gram bar, pictured in London, on Nov. 8, 2016. The makers of...}

\entryitemWithDescription{\hskip 0pt{}Cartoonists criticize 'Dilbert' creator over racist remarks}{https://apnews.com/article/109cb1a6dea03e931e2e6e3814bc743a}{FILE - Scott Adams, creator of the comic strip Dilbert, talks about his work at his studio in Dublin, Calif., on Oct. 26, 2006. Adams experienced possibly the biggest repercussion of his recent comments about race when distributor Andrews...}

\entryitemWithDescription{\hskip 0pt{}Twitter glitches as links, images fail to load}{https://apnews.com/article/7aae44fde817bdac8792bbee785f6b03}{FILE - A Twitter logo hangs outside the company\textquotesingle s offices in San Francisco, on Dec. 19, 2022. Twitter experienced a bevy of glitches Monday, March 6, 2023 as links stopped working, some users were unable to log in and...}

\entryitemWithDescription{\hskip 0pt{}Houston, UCLA, Kansas top latest AP Top 25; Duke back in}{https://apnews.com/article/f5bf07b32b4ea077724488e5b935ad13}{UCLA guard Jaime Jaquez Jr., left, drives against Arizona guard Pelle Larsson during the first half of an NCAA college basketball game Saturday, March 4, 2023, in Los Angeles. (AP Photo/Ringo H.W. Chiu) UCLA is surging, both toward the...}

\entryitemWithDescription{\hskip 0pt{}Made in the USA? Proposed rule clarifies grocery meat labels}{https://apnews.com/article/290b54baa34844011c71d7ef4b4e046f}{FILE - In this photo made on June 16, 2022, rows of fresh cut beef is in the coolers of the retail section at the Wight\textquotesingle s Meat Packing facility in Fombell, Pa. Federal agriculture officials on Monday, March 6, 2023...}

\entryitemWithDescription{\hskip 0pt{}The way we eat could add nearly 1 degree of warming by 2100}{https://apnews.com/article/3980deda0d27c16258c1e79bbf4e1481}{FILE- A line of Holstein dairy cows feed through a fence at a dairy farm on March 11, 2009, outside Jerome, Idaho. Greenhouse gas emissions from the way humans consume food could add nearly one degree of warming to the Earth's climate by...}

\entryitemWithDescription{\hskip 0pt{}Murdaugh testimony only confirmed his guilt, jurors say}{https://apnews.com/article/b7f990117621fbbf670ddf9e57e117b2}{A judge has sentenced South Carolina attorney Alex Murdaugh to life in prison a day after he was convicted of murder in the shooting deaths of his wife and son. The sentence issued Friday carries no chance of parole or early release...}