\entryitemWithDescription{\hskip 0pt{}Texas border city struggles with large arrival of migrants}{https://apnews.com/article/86bd7acbf3f13167db8d2197607fa940}{A group of people leave a welcome center for migrants in Brownsville, Texas, Friday, April 28, 2023. The city of Brownsville signed a disaster declaration after nearly 15,000 migrants crossed through the area, with many of them screened...}

\entryitemWithDescription{\hskip 0pt{}California man gets 4 1/2 years for role in US Capitol riot}{https://apnews.com/article/ba436979d4b21608f39aca61f5f8f6cd}{FILE - People loyal to President Donald Trump storm the U.S. Capitol on Jan. 6, 2021, in Washington. Federal authorities say a Southern California man who assaulted police with pepper spray during the storming of the U.S. Capitol was...}

\entryitemWithDescription{\hskip 0pt{}General Mills issues flour recall after salmonella discovery}{https://apnews.com/article/7a67fb9fd3238ed7d4a23b18730cfc2c}{MINNEAPOLIS, Minn. (AP) --- General Mills has issued a nationwide recall of its bleached and unbleached flour after discovering salmonella during a sampling of a 5-pound (2.3-kilogram) bag. The company is recalling 2-, 5- and 10-pound (0...}

\entryitemWithDescription{\hskip 0pt{}NYC partly shutters 4 parking garages after deadly collapse}{https://apnews.com/article/8b6c06aaf3382508642b255b18f47a8c}{FILE --- Cars are seen piled on top of each other at the scene of a partial collapse of a parking garage in the Financial District of New York, April 18, 2023, in New York. After the deadly collapse of a parking structure in lower...}

\entryitemWithDescription{\hskip 0pt{}Louis Vuitton turns Seoul bridge into massive runway}{https://apnews.com/article/0a07703424d05256cf2d5c3b51c8aff4}{Models wear creations for the Louis Vuitton Pre-Fall 2023 show in Seoul, South Korea, Saturday, April 29, 2023. (AP Photo/Lee Jin-man) SEOUL, South Korea (AP) --- Louis Vuitton transformed a bridge spanning the Han River into a massive...}

\entryitemWithDescription{\hskip 0pt{}Life-size sculpture of euthanized walrus unveiled in Norway}{https://apnews.com/article/1af450cc32a4000ca7364e8d80edf099}{The sculpture of the walrus \textquotesingle Freya\textquotesingle{} is unveiled in Oslo, Norway, Saturday, April 29, 2023. The walrus Freya was euthanized by the Directorate of Fisheries in August 2022. The reason was that the public did...}

\entryitemWithDescription{\hskip 0pt{}Wrongfully convicted Kansas man to get \$7.5 million payment}{https://apnews.com/article/22a857b620b37503f7cda5ffcb667c09}{FILE - In this Jan. 28, 2016, file photo, Floyd Bledsoe, whose convictions for murder and kidnapping were vacated in 2015, speaks in favor of abolishing the death penalty in Kansas at the Statehouse in Topeka. A Kansas county will pay \$7...}

\entryitemWithDescription{\hskip 0pt{}3 killed, 1 wounded in Philadelphia shooting; 2 in custody}{https://apnews.com/article/c7b66a17a98952890a2a940c0cb2a4e9}{Law enforcement gather at the scene of a fatal shooting in Philadelphia, Friday, April 28, 2023. Two teenagers have been charged with firearms and related offenses following the slaying of three people and the wounding of a fourth person...}

\entryitemWithDescription{\hskip 0pt{}NYC transit agency pulls the brake on Twitter service alerts}{https://apnews.com/article/b1a95fe6893659cebf7d1454ede76719}{FILE - The Twitter app icon is displayed on a smartphone, Feb. 28, 2023, in Marple Township, Pa. The transit authority that runs subways, commuter trains and buses in New York City is giving up on a system that sent automated alerts about...}

\entryitemWithDescription{\hskip 0pt{}Jack Nicholson returns to courtside for Lakers' playoff game}{https://apnews.com/article/7a5e4d2543c4c462b3aedbdede832059}{Actor Jack Nicholson attends Game 6 of a first-round NBA basketball playoff series between the Los Angeles Lakers and the Memphis Grizzlies on Friday, April 28, 2023, in Los Angeles. (AP Photo/Jae C. Hong) LOS ANGELES (AP) --- Jack is...}

\entryitemWithDescription{\hskip 0pt{}Lions, a bear and a camel say goodbye to Puerto Rico's zoo}{https://apnews.com/article/e384b5d435245e30b360a5bfaaa583b8}{Patrick Craig from The Wild Animal Sanctuary looks after a sedated lion before its transfer, in Puerto Rico\textquotesingle s only zoo, in Mayaguez, Puerto Rico, Friday, April 28, 2023. Puerto Rico is closing the U.S. territory...}

\entryitemWithDescription{\hskip 0pt{}California man guilty of killing 3 after doorbell prank}{https://apnews.com/article/a674a48fa95f2e6c79fdd5540523c10f}{FILE - An officer with the California Highway Patrol\textquotesingle s (CHP) Multidisciplinary Accident Investigation Team (MAIT) investigates the scene of a deadly crash in the Temescal Valley, south of Corona, Calif., Monday, Jan. 20...}

\entryitemWithDescription{\hskip 0pt{}Report: FAA overruled engineers, let Boeing Max keep flying}{https://apnews.com/article/ea8fac0ad2758b08c58d2d64756fbf37}{FILE - A Boeing 737 Max jet prepares to land at Boeing Field following a test flight in Seattle, Sept. 30, 2020. Some engineers for the Federal Aviation Administration wanted to ground the Boeing 737 Max soon after a second deadly crash...}