\entryitemWithDescription{\hskip 0pt{}Sabres hire Lindy Ruff as coach. He guided Buffalo to the playoffs in 2011}{https://apnews.com/article/be36b05952c5c8b126343f3ec5124f74}{Lindy Ruff is returning to Buffalo for a second stint as coach of the Sabres. General manager Kevyn Adams announced the hiring Monday. Adams had strongly hinted at bringing Ruff back into the fold when talking about hiring a coach with...}

\entryitemWithDescription{\hskip 0pt{}An adored ostrich at a Kansas zoo has died after swallowing a staff member's keys}{https://apnews.com/article/cfe6656e90314a90ed465399b9310e3b}{TOPEKA, Kan. (AP) --- A beloved ostrich at the Topeka Zoo \& Conservation Center in Kansas has died after swallowing a staff member's keys. The zoo announced in a social media post on Friday that the 5-year-old ostrich named Karen had...}

\entryitemWithDescription{\hskip 0pt{}Jets trade quarterback Zach Wilson to the Broncos, AP source says}{https://apnews.com/article/0f36a1ec7cd75358ccdd7d51f19791ee}{Zach Wilson was expected to be the face of the franchise for the New York Jets. Instead, he became a symbol of disappointment. And now, the 2021 second overall draft pick will get the chance to rejuvenate his career with the Denver...}

\entryitemWithDescription{\hskip 0pt{}PEN America calls off awards ceremony amid criticism over its response to Israel-Hamas war}{https://apnews.com/article/41706ebf7fe1154a12e6de8acd529a30}{NEW YORK (AP) --- Facing widespread unhappiness over its response to the Israel-Hamas war, the writers' group PEN America has called off its annual awards ceremony. Dozens of nominees had dropped out of the event, which was to have taken...}

\entryitemWithDescription{\hskip 0pt{}European Space Agency adds 5 new astronauts in only fourth class since 1978. Over 20,000 applied}{https://apnews.com/article/722d4a59d3958f3ff3d53bcf032d034c}{COLOGNE, Germany (AP) --- For the past year, five fit, academically superior men and women have been spun in centrifuges, submerged for hours, deprived temporarily of oxygen, taught to camp in the snow, and schooled in physiology...}

\entryitemWithDescription{\hskip 0pt{}Diver pinned under water by an alligator figured he had choice. Lose his arm or lose his life}{https://apnews.com/article/f39e18f7dd4e785754daadcfe49bd2c8}{GOOSE CREEK, S.C. (AP) --- Out of air and pinned by an alligator to the bottom of the Cooper River in South Carolina, Will Georgitis decided his only chance to survive might be to lose his arm. The alligator had fixed his jaws around...}

\entryitemWithDescription{\hskip 0pt{}4 Germans caught marking Hitler's birthday outside Nazi dictator's birthplace in Austria}{https://apnews.com/article/9175db2ddee362ea1d46b7b03c046666}{BERLIN (AP) --- Four Germans were caught laying white roses in memory of Adolf Hitler at the house where the Nazi dictator was born in western Austria on the anniversary of his birth, and one gave a Hitler salute as they posed for photos...}

\entryitemWithDescription{\hskip 0pt{}Yoko Ono to receive Edward MacDowell Medal for lifetime achievement}{https://apnews.com/article/c074763fad3b55620f34f20e0a1219e7}{NEW YORK (AP) --- One of the country's leading artist residency programs, MacDowell, has awarded a lifetime achievement prize to Yoko Ono. The groundbreaking artist, filmmaker and musician is this year's recipient of the Edward MacDowell...}

\entryitemWithDescription{\hskip 0pt{}Mary J. Blige, Cher, Ozzy Osbourne, A Tribe Called Quest and Foreigner get into Rock Hall}{https://apnews.com/article/65c09d0b774417cb6d9ffece252da8a4}{NEW YORK (AP) --- Mary J. Blige,Cher, Foreigner, A Tribe Called Quest, Kool \& The Gang and Ozzy Osbourne have been inducted into the Rock \& Roll Hall of Fame, a class that also includes folk-rockers Dave Matthews Band and singer...}

\entryitemWithDescription{\hskip 0pt{}Tesla cuts the price of its ``Full Self Driving'' system by a third to \$8,000}{https://apnews.com/article/ecb9fd9367dabe26a71a9dbfd72c37ff}{NEW YORK (AP) --- Tesla knocked roughly a third off the price of its ``Full Self Driving'' system --- which can't drive itself and so drivers must remain alert and be ready to intervene --- to \$8,000 from \$12,000, according to the...}

\entryitemWithDescription{\hskip 0pt{}Theater Review: Not everyone will be `Fallin' over Alicia Keys' Broadway musical `Hell's Kitchen'}{https://apnews.com/article/6a9637aa992636c7771b7382263b1f62}{If you were to close Alicia Keys ' big semi-autobiographical musical on Broadway with any of her hit songs, which would it be? Of course, it has to be ``Empire State of Mind.'' That's the natural one, right? It's also as predictable as...}

\entryitemWithDescription{\hskip 0pt{}Will there be a `superbloom' this year in California? Here's what to know}{https://apnews.com/article/3ef5f84eb74fdd6b670032a1ba46cf44}{Carpets of yellow, orange and gold flowers are beginning to cover Southern California's vast deserts, the Bay Area's dramatic bluffs and even near Los Angeles International Airport. But do they add up to a ``superbloom''? There is no...}

\entryitemWithDescription{\hskip 0pt{}Oregon lodge famously featured in `The Shining' will reopen to guests after fire forced evacuations}{https://apnews.com/article/7269bb2b3de02d9553e6e141c34bf583}{GOVERNMENT CAMP, Ore. (AP) --- Oregon's historic Timberline Lodge, which featured in Stanley Kubrick's 1980 film ``The Shining,'' will reopen to guests Sunday after a fire that prompted evacuations but caused only minimal damage. The...}