\entryitemWithDescription{\hskip 0pt{}A strike at the Eiffel Tower turns visitors away for the second day}{https://apnews.com/article/d7f3d48dc51bba033e0d6ad19edb2dea}{PARIS (AP) --- A strike at the Eiffel Tower over poor financial management turned away visitors on Tuesday for the second consecutive day. Denis Vavassori of the CGT union, which represents a large number of the Eiffel Tower's employees...}

\entryitemWithDescription{\hskip 0pt{}Welcome to the `Hotel California' case: The trial over handwritten lyrics to an Eagles classic}{https://apnews.com/article/973e74e795416821e6f022895b47b78e}{NEW YORK (AP) --- In the mid-1970s, the Eagles were working on a spooky, cryptic new song. On a lined yellow pad, Don Henley, with input from band co-founder Glenn Frey, jotted thoughts about ``a dark desert highway'' and ``a lovely...}

\entryitemWithDescription{\hskip 0pt{}Once banned by communists, Poland's stately 18th century dance garners UNESCO honors}{https://apnews.com/article/be337d9a1941d404f6ef1a1cee364e22}{WARSAW, Poland (AP) --- Once banned by rulers dispatched from Moscow, Poland's stately polonaise dance that nurtured the country's spirit even through the dark years of its partition is now honored by UNESCO. This 18th century dance has...}

\entryitemWithDescription{\hskip 0pt{}Hundreds are set to descend on Tahiti for Olympic surfing. Can locals protect their way of life?}{https://apnews.com/article/c4ceff2ccaaf4cd4e0b9f554093bd54b}{TEAHUPO'O, French Polynesia (AP) --- Peva Levy said he felt a powerful, natural energy known as ``mana'' when he surfed Teahupo'o's waves on a piece of plywood for the first time, rushing down a crumbling white surf in front of an...}

\entryitemWithDescription{\hskip 0pt{}The Wild made their win over the Canucks a perfect 10, setting the team record for goals}{https://apnews.com/article/984497a824adbe9c4e8063fb9508ad1f}{ST. PAUL, Minn. (AP) --- When the Minnesota Wild faced their second three-goal deficit of the second period, boos were audible from a home crowd that was well on the way to emptying out early for this holiday matinee. Patience was...}

\entryitemWithDescription{\hskip 0pt{}Cyclist in Washington state sustains injuries after a cougar `latched onto' her}{https://apnews.com/article/aec1f25d254e2735492fb9dab730e432}{SEATTLE (AP) --- A woman suffered injuries to her face and neck after a cougar leapt out and ``latched onto'' her while she was cycling with a group on a trail in Washington state, authorities said. The incident happened Saturday on a...}

\entryitemWithDescription{\hskip 0pt{}Naomi Campbell walks for star-studded Burberry show at London Fashion Week}{https://apnews.com/article/c1bf58850346dc92e5f6e236ae0d23a6}{LONDON (AP) --- For Londoners, rain is simply a fact of life. But for Burberry, it's the inspiration for seemingly endless variations of luxurious outerwear, from the heritage brand's best-selling trench coat to oversized duffels and fur...}

\entryitemWithDescription{\hskip 0pt{}William Byron wins Daytona 500}{https://apnews.com/article/48289da3b426fc3ee6942e198fcca813}{DAYTONA BEACH, Fla. (AP) --- The goal was obvious to William Byron: put the No. 24 Chevrolet in victory lane in the 2024 Daytona 500 to launch Hendrick Motorsports' 40th anniversary season. Mission accomplished, even if Byron had to...}

\entryitemWithDescription{\hskip 0pt{}A ship carrying 19,000 cattle caused a big stink in the South African city of Cape Town}{https://apnews.com/article/f72c017b48d330372fb22f50d341f8fa}{CAPE TOWN, South Africa (AP) --- What stinks? Authorities in Cape Town launched an investigation Monday after a foul stench swept over the South African city. City officials inspected sewage facilities for leaks and an environmental...}

\entryitemWithDescription{\hskip 0pt{}Astronomers find what may be the universe's brightest object with a black hole devouring a sun a day}{https://apnews.com/article/46ecf903335014ee870ab1adcf70235b}{CAPE CANAVERAL, Fla. (AP) --- Astronomers have discovered what may be the brightest object in the universe, a quasar with a black hole at its heart growing so fast that it swallows the equivalent of a sun a day. The record-breaking quasar...}

\entryitemWithDescription{\hskip 0pt{}Strike at the Eiffel Tower closes one of the world's most popular monuments to visitors}{https://apnews.com/article/2cb788d0648f282ca57a0933bd792c52}{PARIS (AP) --- Visitors to the Eiffel Tower were turned away on Monday because of a strike over poor financial management at one of the world's most-visited sites. A sign was posted at the entrance in English, saying, ``Due to strike, the...}

\entryitemWithDescription{\hskip 0pt{}Points records fall at the All-Star Game, with the East beating the West 211-186}{https://apnews.com/article/a1360d4bd306468522ee22dc9bf59da2}{INDIANAPOLIS (AP) --- The NBA wanted more competition. It got more points instead --- more than ever before. And once again, the All-Star Game was all offense. All-Star MVP Damian Lillard of the Milwaukee Bucks scored 39 points and the...}

\entryitemWithDescription{\hskip 0pt{}Jaromir Jagr's return to Pittsburgh ends with his No. 68 being retired — and catharsis}{https://apnews.com/article/7f5887d92045350753f3ccf8d001f9bc}{PITTSBURGH (AP) --- There were jokes. And laughter. And catharsis. Just no tears. At least none from Jaromir Jagr. Maybe because they were unnecessary when the Pittsburgh Penguins retired his iconic No. 68 on Sunday. The look on Jagr's...}