\entryitemWithDescription{\hskip 0pt{}Memphis' SCORPION unit among many to draw scrutiny in US}{https://apnews.com/article/cd977af56806aedf5074d432172a4bc5}{FILE - In this image from video released and partially redacted by the City of Memphis, Tyre Nichols lies on the ground during a brutal attack by Memphis police officers on Jan. 7, 2023, in Memphis, Tenn. The beating and death of Nichols...}

\entryitemWithDescription{\hskip 0pt{}Feds drop lobbying probe of retired general, lawyer says}{https://apnews.com/article/404fd7b5f6458c175938bdf551b617a5}{FILE - Marine Gen. John Allen, the top U.S. commander in Afghanistan, testifies on Capitol Hill in Washington on March 20, 2012. The Justice Department has dropped its probe of Allen, a retired four-star general, for his role in an...}

\entryitemWithDescription{\hskip 0pt{}Cheaters beware: ChatGPT maker releases AI detection tool}{https://apnews.com/article/a0ab654549de387316404a7be019116b}{The logo for OpenAI, the maker of ChatGPT, appears on a mobile phone, in New York, Tuesday, Jan. 31, 2023. OpenAI is launching a new tool in an effort to curb its reputation as a freewheeling cheating machine with a new tool Tuesday that...}

\entryitemWithDescription{\hskip 0pt{}Bring back dodo? Ambitious plan draws investors, critics}{https://apnews.com/article/d6ebba58ba92c03c46418c0c68276ed8}{FILE - A rare fragment of a Dodo femur bone is displayed for photographs next to an image of a member of the extinct bird species at Christie\textquotesingle s auction house\textquotesingle s premises in London, March 27, 2013. Colossal...}

\entryitemWithDescription{\hskip 0pt{}Santos steps down from House panels amid ethics issues}{https://apnews.com/article/6e46e2badad39fb190d38105a800236f}{FILE - Rep. George Santos, R-N.Y., leaves a House GOP conference meeting on Capitol Hill in Washington, Jan. 25, 2023. Santos told colleagues in a closed-door meeting Tuesday that he is temporarily stepping down from his two congressional...}

\entryitemWithDescription{\hskip 0pt{}Durenberger, former US senator from Minnesota, dies at 88}{https://apnews.com/article/7aaf34d06bd0b5c032daa2b245eb45ed}{FILE - Former U.S. Sen. David Durenberger is seen in a November 1995 photo. Durenberger, a Minnesota Republican who espoused a progressive brand of politics and criticized the GOP after his political career, died Tuesday, Jan. 31, 2023...}

\entryitemWithDescription{\hskip 0pt{}Winter weather cancels flights, leads to death in Texas}{https://apnews.com/article/bfb243c2820836796d5dc5b339cf5756}{A vehicle rests on a barricade as the driver lost control and slid off Highway 6 on Tuesday Jan. 31, 2023 in Waco, Texas. Winter weather brought ice to Texas and nearby states Tuesday. (Jerry Larson/Waco Tribune-Herald via AP) AUSTIN...}

\entryitemWithDescription{\hskip 0pt{}In Haiti, gangs take control as democracy withers}{https://apnews.com/article/7ddcea955fdd364e2b574e28daa71d03}{Jimmy Cherizier, the leader of the "G9 et Famille" gang, talks with members of his gang while taking a ride on the back of a motorcycle in his district of Delmas 6 in Port-au-Prince, Haiti, Tuesday, Jan. 24, 2023. Cherizier, best known by...}

\entryitemWithDescription{\hskip 0pt{}Justice Department seeks Tesla automated driving documents}{https://apnews.com/article/f4f59a574cbe3fe2214c573ab81d47d3}{FILE - Elon Musk departs the Phillip Burton Federal Building and United States Court House in San Francisco, on Tuesday, Jan. 24, 2023. Tesla has received requests from the Justice Department for documents related to its Autopilot and ``...}

\entryitemWithDescription{\hskip 0pt{}US wage growth slowed in the final quarter of 2022}{https://apnews.com/article/4d4a328c345dd4a2e04fbc222d101ac7}{FILE - Hiring signs are displayed at a grocery store in Arlington Heights, Ill., Friday, Jan. 13, 2023. On Tuesday, the Labor Department reports on wages and benefits for U.S. workers during the October-December quarter. (AP Photo/Nam Y...}

\entryitemWithDescription{\hskip 0pt{}Child welfare algorithm faces Justice Department scrutiny}{https://apnews.com/article/4f61f45bfc3245fd2556e886c2da988b}{FILE - Case work supervisor Jessie Schemm looks over the first screen of software used by workers who field calls at an intake call screening center for the Allegheny County Children and Youth Services, in Penn Hills, Pa. The Justice...}

\entryitemWithDescription{\hskip 0pt{}Blinken Mideast visit highlights US limitations in region}{https://apnews.com/article/5587248b5b35929416b0400edd617dd9}{U.S. Secretary of State Antony Blinken, center, meets representatives of the Palestinian civil society in Ramallah in the occupied West Bank, on Tuesday, Jan. 31, 2023. Blinken is wrapping up a two-day visit to Israel and the West Bank...}

\entryitemWithDescription{\hskip 0pt{}China accuses Washington of wanting 'technology hegemony'}{https://apnews.com/article/ab63a8f31847f23b691fa705f8a4a8e2}{FILE - Visitors walk past a booth for Chinese technology firm Huawei at the PT Expo in Beijing on Sept. 28, 2021. China's government accused Washington on Tuesday, Jan. 31, 2023, of pursuing ``technology hegemony'' following news reports...}