\entryitemWithDescription{\hskip 0pt{}Butler's buzzer-beater sends San Diego State to title game}{https://apnews.com/article/a09ac609c57b6c996ddd1f2ef19a35b8}{San Diego State guard Lamont Butler drives up court against Florida Atlantic during the first half of a Final Four college basketball game in the NCAA Tournament on Saturday, April 1, 2023, in Houston. (AP Photo/Godofredo A. Vasquez...}

\entryitemWithDescription{\hskip 0pt{}Tornado survivors recount flying debris, destroyed buildings}{https://apnews.com/article/f12fead43d19c0095d42f8a6e61c7a4f}{Debris covers the ground around damaged homes in Wynne, Ark., on Saturday, April 1, 2023. Unrelenting tornadoes that tore through parts of the South and Midwest that shredded homes and shopping centers. (AP Photo/Adrian Sainz) WYNNE...}

\entryitemWithDescription{\hskip 0pt{}Kaley Cuoco has 1st child, a daughter, with Tom Pelphrey}{https://apnews.com/article/6dbf8c7791f1d18129c076a6040e5c34}{FILE - Kaley Cuoco arrives at the 74th Primetime Emmy Awards, Sept. 12, 2022, at the Microsoft Theater in Los Angeles. Cuoco, star of ``The Flight Attendant'' and ``The Big Bang Theory,'' posted to Instagram on Saturday, April 1, 2023...}

\entryitemWithDescription{\hskip 0pt{}Drug trafficking blamed as homicides soar in Costa Rica}{https://apnews.com/article/4a8f6ecfe7d23fc83708033dc20e05df}{FILE - The body of a man is illuminated by police flashlights as investigators work a crime scene where an alleged thief and a female passenger died in a shootout during a robbery on a bus in San Jose, Costa Rica, Feb. 6, 2023. According...}

\entryitemWithDescription{\hskip 0pt{}Biden and his 2024 campaign: Waiting for some big decisions}{https://apnews.com/article/e64cd5649d9486291715388db3e8e386}{FILE - President Joe Biden speaks from the Treaty Room in the White House on April 14, 2021, about the withdrawal of the remainder of U.S. troops from Afghanistan. (AP Photo/Andrew Harnik, Pool, File) WASHINGTON (AP) --- President Joe...}

\entryitemWithDescription{\hskip 0pt{}After Nashville, Congress confronts limits of new gun law}{https://apnews.com/article/9fb2b460984eb8658b806d0d5126bba8}{FILE - A balloon with names of the victims is seen at a memorial at the entrance to The Covenant School on Wednesday, March 29, 2023, in Nashville, Tenn. Bipartisan gun legislation signed by President Biden in 2022 has already prevented...}

\entryitemWithDescription{\hskip 0pt{}Lanterns and crescents: more retailers court Ramadan buyers}{https://apnews.com/article/4be6f1b7109c8e8bf8077ce4de86a2ca}{Ramadan decorations are displayed at a Party City store in Dearborn, Mich., on Thursday, March 23, 2023. More businesses are selling Ramadan and Eid items, including DIY kits, lanterns and napkin holders. It\textquotesingle s one of the...}

\entryitemWithDescription{\hskip 0pt{}'War of the states': EV, chip makers lavished with subsidies}{https://apnews.com/article/3ac5f11cdbf020e996f6bc8f92bd2bfd}{Workers prepare the site of a \$4 billion Panasonic EV battery plant Thursday, March 30, 2023, near DeSoto, Kan. Economic incentives offered by Kansas state and local governments beat out those offered by neighboring Oklahoma to help lure...}

\entryitemWithDescription{\hskip 0pt{}At least 21 dead after tornadoes rake US Midwest, South}{https://apnews.com/article/79fe2da8a6b8bd92970032530b760d20}{Damage from a late-night tornado is seen in Sullivan, Ind., Saturday, April 1, 2023. Multiple deaths were reported in the area following the storm. (AP Photo/Doug McSchooler) WYNNE, Ark. (AP) --- Storms that dropped possibly dozens of...}

\entryitemWithDescription{\hskip 0pt{}Fatal fire complicates border city's tensions with migrants}{https://apnews.com/article/3bf3782134f6e447b979e2998d3c2cb7}{Irwing Lopez, a 35-year-old migrant construction worker from Venezuela, washes windshields for tips at a stoplight near the U.S. border wall, behind, in Ciudad Juarez, Mexico, Thursday, March 30, 2023. Lopez\textquotesingle s friend and...}

\entryitemWithDescription{\hskip 0pt{}Doomsday plot? After 3 years, slain kids' mom to stand trial}{https://apnews.com/article/19cdf75463402c1838fb6e85f22e7e2c}{FILE - A boy looks at a memorial for Tylee Ryan and Joshua "JJ" Vallow in Rexburg, Idaho, on June 11, 2020. A mother charged with murder in the deaths of her two children is set to stand trial in Idaho. The proceedings against Lori Vallow...}

\entryitemWithDescription{\hskip 0pt{}Alaska Natives rescued Navy crew in 1955. Their medals have arrived}{https://apnews.com/article/495cfe305972a85ef8b0b93dafc71167}{This March 28, 2023, photo shows townspeople in Gambell, Alaska, waiting in a snowstorm on four-wheelers to transport Alaska National Guard personnel from the air strip to the school for a ceremony. Sixteen Alaska National Guard members...}

\entryitemWithDescription{\hskip 0pt{}Ukrainian court puts an Orthodox leader under house arrest}{https://apnews.com/article/d4723c61be8b131ad0a779dc59ae8b00}{Metropolitan Pavel, the abbot of the Kyiv-Pechersk Lavra monastery waits for the court desigion in Kyiv, Ukraine, Saturday, April 1, 2023. Court sentences for home arrest a Ukrainian Orthodox Church Leader Metropolitan Pavel for 60 days...}