\entryitemWithDescription{\hskip 0pt{}Dexter Scott King remembered during memorial as keeper of his father Martin Luther King Jr.'s dream}{https://apnews.com/article/7e79af96ae0f37a6278c1565e42d9aac}{Dexter Scott King, the late son of Dr. Martin Luther King Jr. and Coretta Scott King, was remembered Saturday as the protector of his family's legacy and the keeper of his father's dream during a memorial service in Atlanta. ``You, my...}

\entryitemWithDescription{\hskip 0pt{}From SpongeBob to TikTok, leagues and broadcasters using many methods to attract, retain young fans}{https://apnews.com/article/8ceff4f753d8e3e58e5f818aa0ac1a79}{There were plenty of critics when CBS announced four years ago that it would produce a kids-centric broadcast of an NFL playoff game on Nickelodeon. Now, if a league or network isn't doing something to appeal to younger fans, they are...}

\entryitemWithDescription{\hskip 0pt{}Jimmy Van Eaton, an early rock `n' roll drummer who played at Sun Records, dies at 86}{https://apnews.com/article/38dfdf18a1cdbbaa5d90dd0726b265ff}{MEMPHIS, Tenn. (AP) --- J.M. ``Jimmy'' Van Eaton, a pioneering rock `n' roll drummer who played behind the likes of Jerry Lee Lewis and Billy Lee Riley at Sun Records in Memphis, Tennessee, died Friday at age 86, a family member said. Van...}

\entryitemWithDescription{\hskip 0pt{}Chiefs and 49ers have high-profile offenses, but defense should decide the Super Bowl winner}{https://apnews.com/article/c693b5d4d1e5105ad346da54e626ad41}{LAS VEGAS (AP) --- The Chiefs go as far as Patrick Mahomes takes them. The 49ers have Christian McCaffrey, Deebo Samuel, George Kittle and a star-studded group surrounding Brock Purdy. This Super Bowl will come down to the other side of...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk's Neuralink moves legal home to Nevada after Delaware judge invalidates his Tesla pay deal}{https://apnews.com/article/09c2eee269beebccf9a701f21ea2b9f7}{Elon Musk's brain implant company Neuralink has moved its legal corporate home from Delaware to Nevada after a Delaware judge struck down Musk's \$55.8 billion pay package as CEO of Tesla. Neuralink, which has its physical headquarters in...}

\entryitemWithDescription{\hskip 0pt{}Mary J. Blige, Mariah Carey, Cher, Sade, Oasis and Ozzy Osbourne among Rock Hall nominees for '24}{https://apnews.com/article/92e783daf67e2ee50472099f6dab14c8}{NEW YORK (AP) --- Mary J. Blige, Mariah Carey, Cher, Lenny Kravitz, the late Sinéad O'Connor and heavy metal's so-called Prince of Darkness are some the 2024 nominees for induction into the Rock \& Roll Hall of Fame, a wide musical net...}

\entryitemWithDescription{\hskip 0pt{}How to defend against food poisoning at your Super Bowl party}{https://apnews.com/article/13d5a5231be21618c97de78c55e4e1b9}{When Americans gather to watch the Super Bowl on Sunday, the culinary choices may be as important as the final score. Because the event can stretch for more than four hours, that raises the risks of foodborne illness if party hosts and...}

\entryitemWithDescription{\hskip 0pt{}Wayne Kramer, late guitarist of rock band MC5, also leaves legacy of bringing music to prisons}{https://apnews.com/article/b7ac001d1fd51fc018b8b94e78f4e9f0}{LOS ANGELES (AP) --- The tributes that poured in following Wayne Kramer's death last week came from musicians praising the MC5 guitarist's contributions to rock music, as well as from prison reform advocates who extolled his legacy of...}

\entryitemWithDescription{\hskip 0pt{}Nurse acquitted of involuntary manslaughter in 2019 death of a 24-year-old California jail inmate}{https://apnews.com/article/56b4441032b33f8bea28d4793cbc2257}{EL CAJON, Calif. (AP) --- A nurse at a California jail was found not guilty of involuntary manslaughter Friday in the November 2019 death of an inmate who collapsed in her cell. But jurors deadlocked on charges against a jail doctor...}

\entryitemWithDescription{\hskip 0pt{}Drug possession charge against rapper Kodak Black dismissed in Florida}{https://apnews.com/article/1c21974ad331329fb7bb25692717b740}{FORT LAUDERDALE, Fla. (AP) --- A drug possession charge against South Florida rapper Kodak Black was dismissed Friday, two months after an arrest, though a drug trafficking case from 2022 remains ongoing. Broward County Circuit Judge...}

\entryitemWithDescription{\hskip 0pt{}Record cocoa prices heading into Valentines Day proves to be a headache for sweets king Hershey}{https://apnews.com/article/8c3e04f080b7d773470987dff1f9ca29}{Hershey is cautioning on its 2024 profit growth as the company contends with rising cocoa costs that are leading to higher prices for chocolate. Cocoa futures prices have doubled over the past year and hit an all-time high of \$5,874 per...}

\entryitemWithDescription{\hskip 0pt{}Fire causes extensive damage to iconic Chicago restaurant known for its breakfasts}{https://apnews.com/article/374ef1c77a6803d285ae6e6ae0937ff4}{CHICAGO (AP) --- An overnight fire caused extensive damage to an iconic Chicago restaurant that's known for its breakfasts and is filled with decades of memorabilia, authorities said. Firefighters were called to the Palace Grill around 10...}

\entryitemWithDescription{\hskip 0pt{}An Oklahoma judge who sent more than 500 texts during a murder trial resigns}{https://apnews.com/article/b17209b610432c017887678cc587dbc6}{OKLAHOMA CITY (AP) --- An Oklahoma judge who sent more than 500 texts to her bailiff during a murder trial will resign, according to a court filing. In a proposed settlement agreement filed Thursday with the Oklahoma Court on the...}