\entryitemWithDescription{\hskip 0pt{}Bolsonaro eyes early return to Brazil as US stay irks Biden}{https://apnews.com/article/5d5f0fb703ddc7de29fdad93a0149435}{FILE - Brazilian President Jair Bolsonaro looks on after speaking from his official residence the Alvorada Palace in Brasilia, Brazil, Nov. 1, 2022. His absence on Inauguration Day will mark a break with tradition and remains unclear who...}

\entryitemWithDescription{\hskip 0pt{}Political vacuum in Haiti deepens as senators' terms expire}{https://apnews.com/article/36dad35dce439953e59af39a449206c0}{A protester carries a piece of wood simulating a weapon during a protest demanding the resignation of Prime Minister Ariel Henry, in the Petion-Ville area of Port-au-Prince, Haiti, on Oct. 3, 2022. (AP Photo/Odelyn Joseph) PORT-AU-PRINCE...}

\entryitemWithDescription{\hskip 0pt{}Santos probe sought by Democrats over House ethics}{https://apnews.com/article/17bfaa6420fb5bf1f8b0c20ffbeac2e9}{Rep. George Santos, R-N.Y., departs after attending a House GOP conference meeting on Capitol Hill in Washington, Tuesday, Jan. 10, 2023. (AP Photo/Patrick Semansky) WASHINGTON (AP) --- The House Ethics Committee was asked Tuesday to...}

\entryitemWithDescription{\hskip 0pt{}AP source: Correa spurns Mets, reaches \$200M deal with Twins}{https://apnews.com/article/9bfbe5088907863eb3a604ae3cca6307}{FILE - Minnesota Twins\textquotesingle{} Carlos Correa reacts while batting during the first inning of a baseball game against the Chicago White Sox, Thursday, Sept. 29, 2022, in Minneapolis. Carlos Correa reversed course for a second...}

\entryitemWithDescription{\hskip 0pt{}'Diamond,' of pro-Trump duo Diamond and Silk, dies at 51}{https://apnews.com/article/7ba302111687a71e7686dad3b0f57a43}{FILE - Lynnette Hardaway, left, and Rochelle Richardson, a.k.a. Diamond and Silk, arrive at the LA Premiere of "Death of a Nation" at the Regal Cinemas at L.A. Live on July 31, 2018, in Los Angeles. Hardaway, known by the moniker ``...}

\entryitemWithDescription{\hskip 0pt{}GOP requests intel 'damage assessment' of Biden documents}{https://apnews.com/article/a45855907a73acb256bb7c4dd5a91610}{FILE - President Joe Biden waves before boarding Air Force One at El Paso International Airport in El Paso, Texas, Sunday, Jan. 8, 2023, to travel to Mexico City, Mexico. The Justice Department is reviewing a batch of potentially...}

\entryitemWithDescription{\hskip 0pt{}Rep. Katie Porter seeking Feinstein's Senate seat in 2024}{https://apnews.com/article/172759fa83faa0a70a2195a91dedb6f3}{FILE - Rep. Katie Porter, D-Calif., speaks during a House Committee on Oversight and Reform hearing on gun violence on Capitol Hill in Washington, June 8, 2022. Porter of says she will seek the Senate seat currently held by Sen. Dianne...}

\entryitemWithDescription{\hskip 0pt{}NOAA: Ian, drought supercharged US weather extremes in 2022}{https://apnews.com/article/99e53454edecb6d286e979f46ceb8dcb}{FILE - A man walks by a formerly sunken boat standing upright into the air with its stern buried in the mud along the shoreline of Lake Mead amid a drought at the Lake Mead National Recreation Area near Boulder City, Nev., June 22, 2022...}

\entryitemWithDescription{\hskip 0pt{}Mega Millions swells to \$1.1B after 3-month losing trend}{https://apnews.com/article/3903b40088f0aaf80e06d0d7179227f3}{A Mega Millions customer displays her ticket for the estimated jackpot of \$1.1 Billion at the Fuel On Convenience Store in Pittsburgh, Monday, Jan. 9, 2023. (AP Photo/Gene J. Puskar) CHICAGO (AP) --- After nearly three months of lottery...}

\entryitemWithDescription{\hskip 0pt{}World Bank: Recession a looming threat for global economy}{https://apnews.com/article/391bd23625e205a0d94c1d1c224892a8}{FILE - Container cranes at a port in New Jersey appear behind the Statue of Liberty, Sunday, Nov. 20, 2022, in New York. The global economy will come "perilously close" to a recession this year, led by weaker growth in all the world...}

\entryitemWithDescription{\hskip 0pt{}Iran sentences Belgian aid worker to prison, lashes}{https://apnews.com/article/5ae7ee103dc4cf4e06cccf7b77c6a59c}{This is a locator map for Iran with its capital, Tehran. (AP Photo) DUBAI, United Arab Emirates (AP) --- Iran has sentenced a Belgian aid worker to a lengthy prison term and 74 lashes after convicting him of espionage charges in a closed...}

\entryitemWithDescription{\hskip 0pt{}After hype, readers get hands on Prince Harry's 'Spare'}{https://apnews.com/article/bd8f96d38d46fb46c8ddfad3f9526002}{A couple take a photograph in front of a display in the window of a book shop in London, Tuesday, Jan. 10, 2023. After weeks of hype and days of leaks, readers have the chance to judge Prince Harry\textquotesingle s book for themselves. "...}

\entryitemWithDescription{\hskip 0pt{}Newly restored house in Pompeii offers glimpse of elite life}{https://apnews.com/article/4f7d78b61fb39b5fd3f71cd07ff3eded}{Colums frame the \textquotesingle peristylium\textquotesingle, or courtyard, in the center of the Ancient Roman Domus Vettiorum, House of Vettii, in the Pompeii Archeological Park, near Naples, southern Italy, Wednesday, Dec. 14, 2022...}

\entryitemWithDescription{\hskip 0pt{}Feds propose 'student loan safety net' alongside forgiveness}{https://apnews.com/article/73dcbf54ddb3b53c9c3c5468cfdec3b9}{FILE - President Joe Biden speaks about student loan debt forgiveness in the Roosevelt Room of the White House, on Aug. 24, 2022, in Washington. Education Secretary Miguel Cardona listens at right. The White House is moving forward with a...}

\entryitemWithDescription{\hskip 0pt{}`What madness looks like': Russia intensifies Bakhmut attack}{https://apnews.com/article/1643b607f7424aa58637514c59e22b35}{Ukrainian military medics carry an injured Ukrainian serviceman evacuated from the battlefield into a hospital in Donetsk region, Ukraine, Monday, Jan. 9, 2023. The serviceman did not survive. (AP Photo/Evgeniy Maloletka) KYIV, Ukraine...}

\entryitemWithDescription{\hskip 0pt{}Landslides, sinkholes, floodwaters plague soggy California}{https://apnews.com/article/21b103e791710f4af6ca0ce45c6030b5}{Sacramento residents on Monday were cleaning up and surveying the damage caused by heavy rain and powerful winds that knocked down tall trees throughout the state Capitol, crushing homes and vehicles. (Jan.9) (AP Video/Terry Chea) Howard...}

\entryitemWithDescription{\hskip 0pt{}Romanian court upholds arrest of influencer Andrew Tate}{https://apnews.com/article/120e3499f9d9a0165517773ca40b40ed}{Andrew Tate, center, and his brother Tristan, leave after appearing at the Court of Appeal, in Bucharest, Romania, Tuesday, Jan.10, 2023. The divisive social media personality Andrew Tate arrived at a court in Romania in handcuffs on...}

\entryitemWithDescription{\hskip 0pt{}Trump executive Allen Weisselberg gets 5-month jail sentence}{https://apnews.com/article/ad4cfbc71bb696b9a3fa6343de393613}{Trump Organization\textquotesingle s former Chief Financial Officer Allen Weisselberg arrives to court, Tuesday, Jan. 10, 2023, in New York. The longtime Donald Trump lieutenant who became a star prosecution witness and helped convict the...}

\entryitemWithDescription{\hskip 0pt{}Birth control ruling to see fresh scrutiny at Texas Capitol}{https://apnews.com/article/7ba70ebde39cb2d992eeb7e5f32603ca}{Texas Gov. Greg Abbott addresses the House Chamber at the Texas Capitol during the first day of the 88th Texas Legislative Session in Austin, Texas, Tuesday, Jan. 10, 2023. (AP Photo/Eric Gay) AUSTIN, Texas (AP) --- Samantha Sorsby-Jones...}

\entryitemWithDescription{\hskip 0pt{}'No amnesty!': Brazilian protests demand jail for rioters}{https://apnews.com/article/b62784248fee194c650df5c1da0fd120}{Demonstrators march holding a banner that reads in Portuguese "We are Democracy" during a protest calling for protection of the nation\textquotesingle s democracy in Sao Paulo, Brazil, Monday, Jan. 9, 2023, a day after supporters of...}

\entryitemWithDescription{\hskip 0pt{}China halts visas for Japan, South Korea in COVID-19 spat}{https://apnews.com/article/adef59403f10ba60b1a4cc9deb014a0f}{FILE - A woman arriving from China enters a COVID-19 testing center at the Incheon International Airport In Incheon, South Korea, Thursday, Jan. 5, 2023. China suspended visas Tuesday for South Koreans to come to the country for tourism...}

\entryitemWithDescription{\hskip 0pt{}Georgia becomes 12th back-to-back champ in AP Top 25 history}{https://apnews.com/article/c39f06f53309b656b3e59325b1c0dd7f}{Georgia players celebrate a win over TCU after the national championship NCAA College Football Playoff game, Monday, Jan. 9, 2023, in Inglewood, Calif. Georgia won 65-7. (AP Photo/Ashley Landis) INGLEWOOD, Calif. (AP) --- Georgia was No...}

\entryitemWithDescription{\hskip 0pt{}Saudi Arabia: Hajj pilgrimage returning to pre-COVID levels}{https://apnews.com/article/ffd5a032b33d2814f333e5a960d74c1d}{FILE - Muslim pilgrims walk around the Kaaba, the cubic building at the Grand Mosque, during the annual hajj pilgrimage, in Mecca, Saudi Arabia, on July 10, 2022. Islam\textquotesingle s annual hajj pilgrimage in Saudi Arabia will return...}

\entryitemWithDescription{\hskip 0pt{}The Golden Globes return Tuesday in a 1-year audition}{https://apnews.com/article/38f7af2fc28d44729beed3c4a1527ca0}{FILE - In this Jan.. 6, 2009, file photo, Golden Globe statuettes are seen during a news conference at the Beverly Hilton Hotel in Beverly Hills, Calif. The 80th annual Golden Globe Awards will take place on Tuesday, Jan. 10. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}China economy recovering but hampered by virus outbreaks}{https://apnews.com/article/337dd313fdc7037c34caf55dc2c80acd}{A man and a child wearing face masks walk by shuttered stores on Jan. 3, 2023, which would be selling souvenirs in Qianmen, a popular tourist spot in Beijing. China's business and consumer activity might revive as early as the first...}

\entryitemWithDescription{\hskip 0pt{}Cries for help pour into 988 mental health, suicide line}{https://apnews.com/article/313c20b2098469f04ccadcccdfd46b1b}{988 Call Center Director Jamieson Brill poses for a photo in front of a desk where work workers take calls around the clock at a facility in Hyattsville, Md., Oct. 7, 2022. Brill works in one of more than 200 call centers fanned out...}

\entryitemWithDescription{\hskip 0pt{}Biden, Trudeau talk Haiti, trade at Mexico City summit}{https://apnews.com/article/d6f622d986bc07fae93fa4c53bfaaef9}{President Joe Biden, Mexican President Andres Manuel Lopez Obrador, and Canadian Prime Minister Justin Trudeau meet at the 10th North American Leaders\textquotesingle{} Summit at the National Palace in Mexico City, Mexico, Tuesday, Jan...}

\entryitemWithDescription{\hskip 0pt{}No. 1 Georgia bullies TCU 65-7 to win 2nd consecutive title}{https://apnews.com/article/78edb8a1cda7a4f57323defcfa20614c}{Georgia head coach Kirby Smart kisses the championship trophy after the national championship NCAA College Football Playoff game against TCU, Monday, Jan. 9, 2023, in Inglewood, Calif. Georgia won 65-7. (AP Photo/Ashley Landis) INGLEWOOD...}

\entryitemWithDescription{\hskip 0pt{}House GOP kicks off majority with vote to slash IRS funding}{https://apnews.com/article/64692090ef20e35a59ba1ea7d21a9eea}{Speaker of the House Kevin McCarthy, R-Calif., talks to reporters as he walks to the House chamber at the Capitol in Washington, Monday, Jan. 9, 2023. (AP Photo/Jose Luis Magana) WASHINGTON (AP) --- House Republicans began their tenure in...}

\entryitemWithDescription{\hskip 0pt{}`Spare' but not stingy: takeaways from Prince Harry's memoir}{https://apnews.com/article/0f60db708cfc266e247c1efa7c98877b}{Copies of the new book by Prince Harry called "Spare" are placed on a shelf by a member of staff of a book store during a midnight opening in London, Tuesday, Jan. 10, 2023. Prince Harry\textquotesingle s memoir ``Spare'' arrives in...}

\entryitemWithDescription{\hskip 0pt{}Charles Simic, acclaimed poet adept at wordplay, dies at 84}{https://apnews.com/article/3c3114c0f390d2a50b5a0e1883211bca}{FILE - Poet Charles Simic is photographed at the City University of New York, May 13, 2003. Simic, the Pulitzer Prize-winning poet who awed critics and readers with his singular blend of lyricism and economy, tragic insight and disruptive...}

\entryitemWithDescription{\hskip 0pt{}EXPLAINER: Roots of the Brazilian capital's chaotic uprising}{https://apnews.com/article/29fad1e6c79a5737641932c939021e62}{Guarani Indigenous women protest calling for protection of the nation\textquotesingle s democracy in Sao Paulo, Brazil, Monday, Jan. 9, 2023, a day after supporters of former President Jair Bolsonaro stormed government buildings in the...}

\entryitemWithDescription{\hskip 0pt{}Brazil and Jan. 6 in US: Parallel attacks, but not identical}{https://apnews.com/article/22a083f0d08bb9d1d93b67871a103b0c}{FILE - Protesters, supporters of Brazil\textquotesingle s former President Jair Bolsonaro, stand on the roof of the National Congress building after they stormed it, in Brasilia, Brazil, Sunday, Jan. 8, 2023. (AP Photo/Eraldo Peres, File...}

\entryitemWithDescription{\hskip 0pt{}DOJ reviewing potentially classified docs at Biden center}{https://apnews.com/article/812ef44a5333f6d93423a67a683fa024}{FILE - President Joe Biden waves before boarding Air Force One at El Paso International Airport in El Paso, Texas, Sunday, Jan. 8, 2023, to travel to Mexico City, Mexico. The Justice Department is reviewing a batch of potentially...}

\entryitemWithDescription{\hskip 0pt{}Having elected House speaker, Republicans try governing}{https://apnews.com/article/b9fcfd11427a695fe2eb49e36988f1a0}{Speaker of the House Kevin McCarthy, R-Calif., talks to reporters as he walks to the speaker\textquotesingle s ceremonial office at the Capitol in Washington, Monday, Jan. 9, 2023. (AP Photo/Jose Luis Magana) WASHINGTON (AP) --- Electing...}

\entryitemWithDescription{\hskip 0pt{}How Republicans are transforming the House in the majority}{https://apnews.com/article/60b4f098523b982b549823f4b3e8f9e4}{Newly-elected Speaker of the House Kevin McCarthy, R-Calif., walks to his office from the chamber after a contentious battle to lead the GOP majority in the 118th Congress, at the Capitol in Washington, Saturday, Jan. 7, 2023. (AP Photo/...}

\entryitemWithDescription{\hskip 0pt{}\$1.1B Mega Millions prize also can be winner for retailers}{https://apnews.com/article/cf5a7fc41ee94466bbe5894e1ec48615}{FILE - Mega Millions lottery tickets and a wager slip are displayed, Friday, Jan. 6, 2023, in Derry, N.H. An estimated \$1.1 billion Mega Millions jackpot drawing Tuesday, Jan. 10, 2023, has people lined up at convenience stores...}

\entryitemWithDescription{\hskip 0pt{}Bills safety Hamlin back in Buffalo to continue recovery}{https://apnews.com/article/35005f5e4ac87eca56e7d99d49eaec65}{FILE - Buffalo Bills defensive back Damar Hamlin (3) leaves the field after an NFL football game against the New England Patriots, Thursday, Dec. 1, 2022, in Foxborough, Mass. Quick on-the-field emergency care from well-rehearsed medical...}

\entryitemWithDescription{\hskip 0pt{}As Brazil reels from riots, Bolsonaro finds home in Florida}{https://apnews.com/article/099db80c6511119b534ca17747f871fe}{Former Brazil President Jair Bolsonaro, center, meets with supporters outside a vacation home where he is staying near Orlando, Fla., on Wednesday, Jan. 4, 2023. (Skyler Swisher/Orlando Sentinel via AP) KISSIMMEE, Fla. (AP) --- As Brazil...}

\entryitemWithDescription{\hskip 0pt{}Israel's Netanyahu races ahead with hard-line agenda}{https://apnews.com/article/c3419b07e43f853e9a8d44d55fc4a886}{Israeli Prime Minister Benjamin Netanyahu convenes a weekly cabinet meeting at the Prime Minister\textquotesingle s office in Jerusalem, Sunday, Jan. 8, 2023. (Ronen Zvulun/Pool Photo via AP) Prime Minister Benjamin Netanyahu's new...}

\entryitemWithDescription{\hskip 0pt{}California deluge forces mass evacuations, boy swept away}{https://apnews.com/article/7c151eeaf3f567a125d74245173327f1}{Sacramento residents on Monday were cleaning up and surveying the damage caused by heavy rain and powerful winds that knocked down tall trees throughout the state Capitol, crushing homes and vehicles. (Jan.9) (AP Video/Terry Chea) People...}

\entryitemWithDescription{\hskip 0pt{}Georgia grand jury ends probe of Trump, 2020 election}{https://apnews.com/article/fc08d39209ce3be768d933f96a434abf}{FILE - Former President Donald Trump speaks as he announces a third run for president, at Mar-a-Lago in Palm Beach, Fla., Nov. 15, 2022. The special grand jury investigating whether then-President Donald Trump and his allies committed any...}

\entryitemWithDescription{\hskip 0pt{}Virgin Orbit reports 'anomaly' in satellite launch from UK}{https://apnews.com/article/b17357dddb4bb75fd13a088534a4c5a2}{Virgin Atlantic Cosmic Girl, a repurposed Virgin Atlantic Boeing 747 aircraft carrying a rocket, is parked at Spaceport Cornwall, at Cornwall Airport in Newquay, England, Monday, Jan. 9, 2023. Engineers are making final preparations for...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry accuses Camilla of 'dangerous' leaks to media}{https://apnews.com/article/4141be64bcd1521d1d5cf0f9b65e20b5}{A poster advertises the midnight opening of a store to sell the new book by Prince Harry called \textquotesingle Spare\textquotesingle{} in London, Monday, Jan. 9, 2023. Prince Harry has defended his memoir that lays bare rifts inside...}

\entryitemWithDescription{\hskip 0pt{}Biden, López Obrador open Mexico meetings with brusque talk}{https://apnews.com/article/871328ff21fc6a87b698742f6e9ed3d4}{President Joe Biden walks with Mexican President Andres Manuel Lopez Obrador as he arrives at the National Palace in Mexico City, Mexico, Monday, Jan. 9, 2023. (AP Photo/Andrew Harnik) Mexican President Andres Manuel López Obrador...}

\entryitemWithDescription{\hskip 0pt{}Nurses go on strike at 2 big New York City hospitals}{https://apnews.com/article/d81f32cb7ac709404eb795a6d8822b34}{Nurses stage a strike in front of Mt. Sinai Hospital in the Manhattan borough of New York Monday, Jan. 9, 2023, after negotiations broke down hours earlier. (AP Photo/Craig Ruttle) Thousands of nurses are on strike at two major New York...}

\entryitemWithDescription{\hskip 0pt{}Asian stock markets mixed ahead of US inflation update}{https://apnews.com/article/adddcec61c0b2b377a9a38ccb10d0783}{A person wearing a protective mask walks in front of an electronic stock board showing Japan\textquotesingle s Nikkei 225 index at a securities firm Tuesday, Jan. 10, 2023, in Tokyo. Stock markets were mixed Tuesday ahead of a U.S...}

\entryitemWithDescription{\hskip 0pt{}Authorities probe who was behind uprising in Brazil capital}{https://apnews.com/article/8766c0ad2fcc4ae7c8bf1aa7f9aaa0ec}{Police officers take position as supporters of Brazil\textquotesingle s former President Jair Bolsonaro leave a camp outside the Army headquarters in Brasilia, Brazil, Monday, Jan. 9, 2023. Since Bolsonaro lost re-election to Luiz Inácio...}

\entryitemWithDescription{\hskip 0pt{}New guidance: Use drugs, surgery early for obesity in kids}{https://apnews.com/article/c48d5896114beea7eda31d7b8b25461d}{This image provided by Novo Nordisk in January 2023, shows packaging for the company\textquotesingle s Wegovy drug. Children struggling with obesity should be evaluated and treated early and aggressively, with medications for kids as...}

\entryitemWithDescription{\hskip 0pt{}NFL playoffs: Brady's back to try for 8th Super Bowl win}{https://apnews.com/article/05b7768e4388d57e68983ceacaedf6ab}{Tampa Bay Buccaneers quarterback Tom Brady (12) sets back to pass during the first half of an NFL football game against the Atlanta Falcons, Sunday, Jan. 8, 2023, in Atlanta. (AP Photo/John Bazemore) Seven of the 14 teams in this year...}
