


\ipart{Developers}
\ichapter{Hacker News}
\entryitemTwoLinks{Language models can explain neurons in language models}{https://news.ycombinator.com/item?id=35877402}{https://openai.com/research/language-models-can-explain-neurons-in-language-models}

\entryitemTwoLinks{Downtown SF has 18.4M square feet of empty office space. We mapped every vacancy}{https://news.ycombinator.com/item?id=35877146}{https://www.sfchronicle.com/sf/article/downtown-empty-offices-business-tech-17911258.php}

\entryitemTwoLinks{Study finds elevated levels of toxic metals in some juices and soft drinks}{https://news.ycombinator.com/item?id=35876506}{https://news.tulane.edu/pr/study-finds-elevated-levels-toxic-metals-some-mixed-fruit-juices-and-soft-drinks}

\entryitemTwoLinks{Many people living in the 'Diabetes Belt' are plagued with medical debt}{https://news.ycombinator.com/item?id=35876150}{https://text.npr.org/1173439205}

\entryitemTwoLinks{Reduced cancer mortality with daily Vitamin D intake}{https://news.ycombinator.com/item?id=35876062}{https://www.dkfz.de/en/presse/pressemitteilungen/2023/dkfz-pm-23-27-Reduced-cancer-mortality-with-daily-vitamin-D-intake.php}

\entryitemTwoLinks{Ex-Apple VP Mike Abbott Joins General Motors as Exec Vice President, Software}{https://news.ycombinator.com/item?id=35875477}{https://investor.gm.com/news-releases/news-release-details/tech-industry-innovator-mike-abbott-joins-general-motors/}

\entryitemTwoLinks{US on track to set record in 2023 for mass killings after series of shootings}{https://news.ycombinator.com/item?id=35875434}{https://www.theguardian.com/us-news/2023/may/09/us-on-track-set-record-mass-killings-2023}

\entryitemTwoLinks{James Webb Space Telescope reveals Fomalhaut's disk in detail}{https://news.ycombinator.com/item?id=35874704}{https://skyandtelescope.org/astronomy-news/the-james-webb-space-telescope-reveals-fomalhauts-disk-in-unprecedented-detail/}

\entryitemTwoLinks{Health advisory on social media use in adolescence}{https://news.ycombinator.com/item?id=35874670}{https://www.apa.org/topics/social-media-internet/health-advisory-adolescent-social-media-use}

\entryitemTwoLinks{Students can't get off their phones. Schools have had enough}{https://news.ycombinator.com/item?id=35874246}{https://www.washingtonpost.com/education/2023/05/09/school-cellphone-ban-yondr/}

\entryitemTwoLinks{Total Crap – A magazine written by AI}{https://news.ycombinator.com/item?id=35874171}{https://www.mcsweeneys.net/articles/introducing-total-crap-the-first-magazine-written-entirely-by-ai}

\entryitemTwoLinks{Google promised to delete sensitive data. It logged my abortion clinic visit}{https://news.ycombinator.com/item?id=35873836}{https://www.washingtonpost.com/technology/2023/05/09/google-privacy-abortion-data/}

\entryitemTwoLinks{Apple brings Final Cut Pro and Logic Pro to iPad}{https://news.ycombinator.com/item?id=35873732}{https://www.apple.com/newsroom/2023/05/apple-brings-final-cut-pro-and-logic-pro-to-ipad/}

\entryitemTwoLinks{CheerpJ 3.0: a JVM replacement in HTML5 and WASM to run Java on modern browsers}{https://news.ycombinator.com/item?id=35873552}{https://leaningtech.com/announcing-cheerpj-3-0-a-jvm-replacement-in-html5-and-webassembly-to-run-java-applications-and-applets-on-modern-browsers/}

\entryitemTwoLinks{GitHub incident: ongoing issues with Actions, Issues and other Git operations}{https://news.ycombinator.com/item?id=35872835}{https://www.githubstatus.com/incidents/f0mhbz9xn497}

\entryitemTwoLinks{What is permaculture? (2015)}{https://news.ycombinator.com/item?id=35872647}{https://www.permaculturedesignmagazine.com/what-is-permaculture}

\entryitemTwoLinks{UN Human Rights Chief Urges UK to Reverse `Deeply Troubling' Public Order Bill}{https://news.ycombinator.com/item?id=35871394}{https://www.ohchr.org/en/press-releases/2023/04/un-human-rights-chief-urges-uk-reverse-deeply-troubling-public-order-bill}

\entryitemTwoLinks{Ask HN: Fired for Using Firefox}{https://news.ycombinator.com/item?id=35870824}{https://news.ycombinator.com/item?id=35870824}

\entryitemTwoLinks{Learning DNS in 10 Years}{https://news.ycombinator.com/item?id=35870654}{https://jvns.ca/blog/2023/05/08/new-talk-learning-dns-in-10-years/}

\entryitemTwoLinks{Google keeps failing its Nest customers}{https://news.ycombinator.com/item?id=35870393}{https://9to5google.com/2023/05/07/google-failing-nest/}\ichapter{Phoronix}
\entryitemGeneric{\hskip 0pt{}Alpine Linux 3.18 Released - Powered By Linux 6.1 LTS, Musl Libc 1.2.4}{https://www.phoronix.com/news/Alpine-Linux-3.18}

\entryitemGeneric{\hskip 0pt{}Corsair MP700: PCIe 5.0 NVMe SSD But Not Without Issues}{https://www.phoronix.com/review/corsair-mp700-pcie5}

\entryitemGeneric{\hskip 0pt{}Intel Linux Graphics Driver Affected By Privilege Escalation Vulnerability}{https://www.phoronix.com/news/Intel-CVE-2023-28410}

\entryitemGeneric{\hskip 0pt{}Intel's Experimental Xe Driver For Linux Lacking HuC Media Support For DG2/Alchenist}{https://www.phoronix.com/news/Intel-Xe-DG2-No-HuC}

\entryitemGeneric{\hskip 0pt{}ASUS ROG CROSSHAIR X670E Hero Sensor Monitoring To Come With Linux 6.5}{https://www.phoronix.com/news/ASUS-X670E-Hero-Linux-Sensors}

\entryitemGeneric{\hskip 0pt{}PipeWire Audio Backend Comes To QEMU}{https://www.phoronix.com/news/QEMU-8.1-Adds-PipeWire}

\entryitemGeneric{\hskip 0pt{}Linux Patches Updated For Parallel CPU Bring-Up}{https://www.phoronix.com/news/Linux-Parallel-CPU-Bring-Up-v3}

\entryitemGeneric{\hskip 0pt{}Firefox 113 Available With Animated AV1 Image Support (AVIS)}{https://www.phoronix.com/news/Mozilla-Firefox-113}

\entryitemGeneric{\hskip 0pt{}AMD Is Hiring For Another Open-Source Linux/Mesa Developer}{https://www.phoronix.com/news/AMD-Another-Mesa-Dev-2023}\ichapter{GitHub}
\entryitemWithDescription{\hskip 0pt{}krahets/hello-algo}{https://github.com/krahets/hello-algo}{《Hello 算法》是一本动画图解、能运行、可提问的数据结构与算法入门书，支持
Java, C++, Python, Go, JS, TS, C\#, Swift, Zig 等语言。\\
Language: Java\\
Stars: 10578\\
Forks: 1155}

\entryitemWithDescription{\hskip 0pt{}zhayujie/chatgpt-on-wechat}{https://github.com/zhayujie/chatgpt-on-wechat}{Wechat robot based on ChatGPT, which using OpenAI api and itchat
library. 使用ChatGPT搭建微信聊天机器人，基于GPT3.5/4.0
API实现，支持个人微信、公众号、企业微信部署，能处理文本、语音和图片，访问操作系统和互联网。\\
Language: Python\\
Stars: 11258\\
Forks: 2894}

\entryitemWithDescription{\hskip 0pt{}pineappleEA/pineapple-src}{https://github.com/pineappleEA/pineapple-src}{yuzu Early Access source code\\
Language: C++\\
Stars: 1949\\
Forks: 182}

\entryitemWithDescription{\hskip 0pt{}hwchase17/langchain}{https://github.com/hwchase17/langchain}{⚡ Building applications with LLMs through composability ⚡\\
Language: Python\\
Stars: 36507\\
Forks: 3993}

\entryitemWithDescription{\hskip 0pt{}qdrant/qdrant}{https://github.com/qdrant/qdrant}{Qdrant - Vector Database for the next generation of AI applications.
Also available in the cloud https://cloud.qdrant.io/\\
Language: Rust\\
Stars: 8859\\
Forks: 427}\ichapter{Dribbble}
\entryitemGeneric{\hskip 0pt{}Pixie / Design Lab}{https://dribbble.com/shots/21370265}

\entryitemGeneric{\hskip 0pt{}Core Dashboard Builder - Components}{https://dribbble.com/shots/21354273}

\entryitemGeneric{\hskip 0pt{}Brainwave - AI Landing Page Kit}{https://dribbble.com/shots/21398428}

\entryitemGeneric{\hskip 0pt{}Core Dashboard Builder}{https://dribbble.com/shots/21361934}

\entryitemGeneric{\hskip 0pt{}X-Leap - website for blockchain-based payment platform}{https://dribbble.com/shots/21412313}

\entryitemGeneric{\hskip 0pt{}Cycode Branding}{https://dribbble.com/shots/21255104}

\entryitemGeneric{\hskip 0pt{}Micromobility Admin Dashboard: Analytics UX UI}{https://dribbble.com/shots/21205127}

\entryitemGeneric{\hskip 0pt{}Mavryk Visual Identity}{https://dribbble.com/shots/21401703}

\entryitemGeneric{\hskip 0pt{}OpenColony Website Design: business landing web page, site}{https://dribbble.com/shots/21205619}

\entryitemGeneric{\hskip 0pt{}Abstract Art Lotus 3D}{https://dribbble.com/shots/21365026}

\entryitemGeneric{\hskip 0pt{}3D printing: platform, app design, ui/ux, dashboard}{https://dribbble.com/shots/21395995}

\entryitemGeneric{\hskip 0pt{}Zircoin}{https://dribbble.com/shots/21377850}

\entryitemGeneric{\hskip 0pt{}Xylograph}{https://dribbble.com/shots/21358273}

\entryitemGeneric{\hskip 0pt{}Razer - Custom Wordmark}{https://dribbble.com/shots/21371571}

\entryitemGeneric{\hskip 0pt{}Runamok Motors\_Motorheads}{https://dribbble.com/shots/21363916}

\entryitemGeneric{\hskip 0pt{}Number 2. 36 Days of Type. Day 29}{https://dribbble.com/shots/21400200}

\entryitemGeneric{\hskip 0pt{}[P] 1 → N}{https://dribbble.com/shots/21331846}

\entryitemGeneric{\hskip 0pt{}Task Management Product Sneak Peeks}{https://dribbble.com/shots/21360781}

\entryitemGeneric{\hskip 0pt{}Anti-Oedipus ✦ Symbol}{https://dribbble.com/shots/21374875}

\entryitemGeneric{\hskip 0pt{}FlagPeak}{https://dribbble.com/shots/21371413}

\entryitemGeneric{\hskip 0pt{}Palms up}{https://dribbble.com/shots/21394851}

\entryitemGeneric{\hskip 0pt{}Windy – Logo Design}{https://dribbble.com/shots/21386037}

\entryitemGeneric{\hskip 0pt{}Globe Web3 - Logo Design}{https://dribbble.com/shots/21410379}

\entryitemGeneric{\hskip 0pt{}Booking Service Mobile App design: iOS Android ux ui designer}{https://dribbble.com/shots/21206100}


\ipart{Developers~~~~(zh-Hans)}
\ichapter{Solidot}
\entryitemGeneric{\hskip 0pt{}Facebook 的 30 亿用户年龄渐长}{https://www.solidot.org/story?sid=74913}

\entryitemGeneric{\hskip 0pt{}领英将关闭中国求职应用 InCareer}{https://www.solidot.org/story?sid=74912}

\entryitemGeneric{\hskip 0pt{}微软给 Windows 11 设置面板加入了广告}{https://www.solidot.org/story?sid=74911}

\entryitemGeneric{\hskip 0pt{}DEF CON 将举办大语言模型黑客马拉松}{https://www.solidot.org/story?sid=74910}

\entryitemGeneric{\hskip 0pt{}亚裔美国人有异常高比例的心血管和糖尿病发生率}{https://www.solidot.org/story?sid=74909}

\entryitemGeneric{\hskip 0pt{}RHEL 10 将不包含 Xorg}{https://www.solidot.org/story?sid=74908}

\entryitemGeneric{\hskip 0pt{}邓宁-克鲁格效应可能只是一种统计偏差}{https://www.solidot.org/story?sid=74907}

\entryitemGeneric{\hskip 0pt{}Twitter 将清除不活跃用户账号}{https://www.solidot.org/story?sid=74906}

\entryitemGeneric{\hskip 0pt{}GitHub 新代码搜索 GA}{https://www.solidot.org/story?sid=74905}

\entryitemGeneric{\hskip 0pt{}AMD 计划到 2026 年用开源的 openSIL 取代 AGESA 固件}{https://www.solidot.org/story?sid=74904}

\entryitemGeneric{\hskip 0pt{}基于 Unity 引擎的 RPG 制作大师发布}{https://www.solidot.org/story?sid=74903}

\entryitemGeneric{\hskip 0pt{}中国公司寻求不依赖最先进芯片开发 AI}{https://www.solidot.org/story?sid=74902}

\entryitemGeneric{\hskip 0pt{}宝德推出规格与英特尔 10 代处理器基本相同的芯片暴芯}{https://www.solidot.org/story?sid=74901}

\entryitemGeneric{\hskip 0pt{}美国更多地方图书馆取消逾期罚款}{https://www.solidot.org/story?sid=74900}

\entryitemGeneric{\hskip 0pt{}科学家发现光合作用和玻色爱因斯坦凝聚态存在关联}{https://www.solidot.org/story?sid=74899}

\entryitemGeneric{\hskip 0pt{}Mail.ru 的邮件应用被发现传输用户明文密码}{https://www.solidot.org/story?sid=74898}

\entryitemGeneric{\hskip 0pt{}揭秘月壤中的玻璃物质}{https://www.solidot.org/story?sid=74897}

\entryitemGeneric{\hskip 0pt{}中国可重复使用试验航天器在轨飞行 276 天后着陆 }{https://www.solidot.org/story?sid=74896}

\entryitemGeneric{\hskip 0pt{}医生谈新冠二次感染风险}{https://www.solidot.org/story?sid=74895}

\entryitemGeneric{\hskip 0pt{}西部数据称黑客在 3 月的网络攻击中窃取了客户数据}{https://www.solidot.org/story?sid=74894}\ichapter{V2EX}
\entryitemGeneric{\hskip 0pt{}[MacBook Pro] 14 寸的 M2 Pro 有必要加到 32G 吗}{https://www.v2ex.com/t/938754}

\entryitemGeneric{\hskip 0pt{}[北京] 北京学日语可以去学校旁听吗？五十音图}{https://www.v2ex.com/t/938753}

\entryitemGeneric{\hskip 0pt{}[分享发现] 怎样成为优秀的后端工程师}{https://www.v2ex.com/t/938750}

\entryitemGeneric{\hskip 0pt{}[分享发现] 星火认知、文心一言、ChatGPT 哪个强？简单测了一下。}{https://www.v2ex.com/t/938749}

\entryitemGeneric{\hskip 0pt{}[OpenAI] onekey 卡充值 gpt4 自制保姆级视频教程}{https://www.v2ex.com/t/938748}

\entryitemGeneric{\hskip 0pt{}[问与答] Auth0 在 OpenAI 这种体量下是否经济}{https://www.v2ex.com/t/938746}

\entryitemGeneric{\hskip 0pt{}[问与答] 邻居大爷抽烟肺癌，卖房卖车太惨了，你们给父母配防癌险了吗？}{https://www.v2ex.com/t/938745}

\entryitemGeneric{\hskip 0pt{}[问与答] 谁能告诉我这个表情包怎么联想到 zz 的}{https://www.v2ex.com/t/938744}

\entryitemGeneric{\hskip 0pt{}[程序员] 技能交换}{https://www.v2ex.com/t/938742}

\entryitemGeneric{\hskip 0pt{}[问与答] 被电工坑了 900 块之后的人生回马灯}{https://www.v2ex.com/t/938741}

\entryitemGeneric{\hskip 0pt{}[生活] 犯病了}{https://www.v2ex.com/t/938740}

\entryitemGeneric{\hskip 0pt{}[生活] 夏天到了，厨房很多蟑螂你是怎么处理的？}{https://www.v2ex.com/t/938739}

\entryitemGeneric{\hskip 0pt{}[深圳] 分享一下在外地使用深圳医保的流程}{https://www.v2ex.com/t/938738}

\entryitemGeneric{\hskip 0pt{}[酷工作] 外企 内推 薪资接得住任何大厂 大量 hc Java (p6,p7p8) 机器学习}{https://www.v2ex.com/t/938737}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 域名被 google 标记为诈骗网站}{https://www.v2ex.com/t/938736}

\entryitemGeneric{\hskip 0pt{}[创业组队] 这里有没有天使投资人?}{https://www.v2ex.com/t/938732}

\entryitemGeneric{\hskip 0pt{}[JavaScript] 有关 Javascript 的 event loop 和 async function，我始终没有弄明白。}{https://www.v2ex.com/t/938730}

\entryitemGeneric{\hskip 0pt{}[问与答] 很严肃的问一个问题，假如我在公共场合， 互联网平台说， 某某开发商的有部分人值得信任，很用心服务， 不是王八蛋， 不是流氓， 不是奸商， 从法律上，我这句话有没有问题。}{https://www.v2ex.com/t/938729}

\entryitemGeneric{\hskip 0pt{}[问与答] 服务器代理有什么好的方式?}{https://www.v2ex.com/t/938728}

\entryitemGeneric{\hskip 0pt{}[职场话题] 今天 boss 上遇到一个外包职位。说可以把我注册成个体户，可以少缴税。唉。。。}{https://www.v2ex.com/t/938727}

\entryitemGeneric{\hskip 0pt{}[分享创造] 让 gpt 给 oh-my-zsh 修了个陈年 bug}{https://www.v2ex.com/t/938726}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 我尝试用了科大讯飞的星火模型，感觉国内的 Chatgpt 要崛起了！}{https://www.v2ex.com/t/938725}

\entryitemGeneric{\hskip 0pt{}[程序员] 文心一言跟讯飞星火在浏览器端启用调试模式页面就空白，这是什么原理}{https://www.v2ex.com/t/938724}

\entryitemGeneric{\hskip 0pt{}[GitHub Copilot] Github Copilot X 申请通过了！}{https://www.v2ex.com/t/938723}

\entryitemGeneric{\hskip 0pt{}[iPhone] 蹲一部无锁 13mini 256 靓机}{https://www.v2ex.com/t/938722}

\entryitemGeneric{\hskip 0pt{}[正则表达式] 有对 posix-正则 有研究的吗？问下}{https://www.v2ex.com/t/938721}

\entryitemGeneric{\hskip 0pt{}[Apple] Final Cut Pro 和 Logic Pro 都出 iPadOS 版了，居然不在 WWDC 上发……}{https://www.v2ex.com/t/938719}

\entryitemGeneric{\hskip 0pt{}[问与答] 开车之后感觉国骂越来越频繁了}{https://www.v2ex.com/t/938718}

\entryitemGeneric{\hskip 0pt{}[问与答] wifi 用联发科 mtk 芯片对 iPhone 支持不好吗？}{https://www.v2ex.com/t/938717}

\entryitemGeneric{\hskip 0pt{}[全球工单系统] 腾讯云的备案检查已经严苛到这种地步了吗}{https://www.v2ex.com/t/938716}

\entryitemGeneric{\hskip 0pt{}[智能家电] 有没有懂电视的大佬 参考一下}{https://www.v2ex.com/t/938713}

\entryitemGeneric{\hskip 0pt{}[问与答] MBP Early2015 Kernel\_task 占用特别高的 cpu，导致系统卡死}{https://www.v2ex.com/t/938711}

\entryitemGeneric{\hskip 0pt{}[问与答] 是什么让选择处理问题的方式越来越极端？}{https://www.v2ex.com/t/938710}

\entryitemGeneric{\hskip 0pt{}[问与答] iRime 输入法怎么隐藏左上角这个"R"图标？}{https://www.v2ex.com/t/938709}

\entryitemGeneric{\hskip 0pt{}[日本] [全职] [正式员工] 日本华人 IT 培训招教务讲师}{https://www.v2ex.com/t/938708}

\entryitemGeneric{\hskip 0pt{}[信息安全] 观 Apple ID 被盗 请教大家几个问题}{https://www.v2ex.com/t/938707}

\entryitemGeneric{\hskip 0pt{}[程序员] 企业监管 MacBook Pro 有翻车的吗？}{https://www.v2ex.com/t/938706}

\entryitemGeneric{\hskip 0pt{}[宽带症候群] 请问大佬，收了 vultr BGP 全表，如何通过 RouterOS 转发到家里呢？}{https://www.v2ex.com/t/938705}

\entryitemGeneric{\hskip 0pt{}[GitHub] GitHub 挂了}{https://www.v2ex.com/t/938701}

\entryitemGeneric{\hskip 0pt{}[GitHub] Github 出问题了？不能推代码}{https://www.v2ex.com/t/938699}

\entryitemGeneric{\hskip 0pt{}[酷工作] 交易所 CEO COO,base 新加坡}{https://www.v2ex.com/t/938698}

\entryitemGeneric{\hskip 0pt{}[区块链] OpenAI 创始人 Sam 开发的区块链项目 WorldCoin 正式发布 App, 可以下载体验!}{https://www.v2ex.com/t/938697}

\entryitemGeneric{\hskip 0pt{}[OpenAI] 熊猫吃短信的作者更新了 ChatGPT 客户端，免 API 2.99 美元一个月划算吗？}{https://www.v2ex.com/t/938695}

\entryitemGeneric{\hskip 0pt{}[问与答] Android Studio 小白求问}{https://www.v2ex.com/t/938694}

\entryitemGeneric{\hskip 0pt{}[深圳] 为什么深圳的公司都有着深厚的让自己的用户成为自己的水军的传统}{https://www.v2ex.com/t/938693}

\entryitemGeneric{\hskip 0pt{}[iOS] iOS 设备安装测试包，不能直接 xcode 安装前提下，必须开通开发者账号才行吗？}{https://www.v2ex.com/t/938692}

\entryitemGeneric{\hskip 0pt{}[职场话题] 2022 年城镇私营单位就业人员年平均工资 65237 元}{https://www.v2ex.com/t/938691}

\entryitemGeneric{\hskip 0pt{}[求职] [远程]高级安卓 1 名 20~25K}{https://www.v2ex.com/t/938690}

\entryitemGeneric{\hskip 0pt{}[路由器] 有知道 ubuntu/ Linux 如何连接斐讯 K3 路由器上的外界 U 盘吗}{https://www.v2ex.com/t/938689}

\entryitemGeneric{\hskip 0pt{}[VPS] Digitalocean/Linode、腾讯云/阿里云海外节点，跨境电商怎么选择？}{https://www.v2ex.com/t/938688}


\ipart{Generic News}
\ichapter{AP News}
\entryitemWithDescription{\hskip 0pt{}Feinstein returning to Senate after facing resignation calls}{https://apnews.com/article/49374eadf516a1fb521cac466bb5d18f}{FILE - Sen. Dianne Feinstein, D-Calif., walks through a Senate corridor at the Capitol in Washington, Feb. 14, 2023. Feinstein is returning to Washington after a more than two month absence led to calls from within her own party for the...}

\entryitemWithDescription{\hskip 0pt{}She wrote book on husband's death; police say she killed him}{https://apnews.com/article/d26a40d5b90f1ca6e6da8f46104afce1}{This photo provided by KPCW.org shows Kouri Richins at the KPCW studio in Park City, Utah, April 12, 2023. Richins was arrested on Monday, May 8, in Utah and is accused in charging documents of poisoning her husband with a lethal dose of...}

\entryitemWithDescription{\hskip 0pt{}Robert De Niro, at 79, becomes a father for the 7th time}{https://apnews.com/article/68296f887ee3892e28ecc4a0fe596ffa}{FILE - Robert De Niro attends the world premiere of "Amsterdam" at Alice Tully Hall on Sunday, Sept. 18, 2022, in New York. De Niro has welcomed another child. The 79-year-old is now the father of seven. A representative for De Niro...}

\entryitemWithDescription{\hskip 0pt{}Signed in purple ink, Minnesota dedicates highway to Prince}{https://apnews.com/article/45220b9307ba1dee12512c84c71063c1}{FILE - Prince performs during the halftime show at the Super Bowl XLI football game in Miami, Feb. 4, 2007. The late pop superstar Prince will have a highway named after him, thanks to Minnesota lawmakers who voted Thursday, May 4, 2023...}

\entryitemWithDescription{\hskip 0pt{}What to know as UK hosts Eurovision Song Contest for Ukraine}{https://apnews.com/article/ef0005c0ddb68eebe2a4599d95147859}{Alyosha of Ukraine performs during a dress rehearsal at the Eurovision Song Contest at the M\&S Bank Arena in Liverpool, England, Monday, May 8, 2023. (AP Photo/Martin Meissner) LONDON (AP) --- Last week, Britain crowned a king. This...}

\entryitemWithDescription{\hskip 0pt{}Rita Lee, Brazil's long-reigning Queen of Rock, dies at 75}{https://apnews.com/article/cc5a47525b592657fb0155e0f65e1922}{FILE - Brazilian singer Rita Lee performs in concert in Buenos Aires, Argentina, Nov. 23, 2002. Brazil's million-selling ``Queen of Rock'' who gained an international following through her colorful and candid style has died at the age 75...}

\entryitemWithDescription{\hskip 0pt{}Hyundai and Kia thefts keep rising despite security fix}{https://apnews.com/article/8e0a353d24be0e7bce36e34c5e4dac51}{A line of 2022 Santa Fe SUV\textquotesingle s sit outside a Hyundai dealership Sunday, Sept. 12, 2021, in Littleton, Colo. Nearly three months after Hyundai and Kia rolled out new software designed to thwart rampant auto thefts, crooks...}

\entryitemWithDescription{\hskip 0pt{}Christie's sale of Austrian heiress' jewels stirs criticism}{https://apnews.com/article/d5cfad3f098b84b52aed090a053079a7}{An employee of Christie\textquotesingle s displays the Great Mogul Emerald and Diamond Necklace by Harry Winston, estimated between 450,000 - 640,000 CHF (Swiss Francs), in display case, during the preview of "The World of Heidi Horten"...}

\entryitemWithDescription{\hskip 0pt{}Tempur Sealy to buy Mattress Firm in \$4 billion deal}{https://apnews.com/article/a4973adf7d958e2e358b902d3f4f9b42}{A passer-by walks near the front of a Tempur-Pedic mattress store location, Tuesday, May 9, 2023, in Dedham, Mass. Tempur Sealy, the parent company of Tempur-Pedic, has agreed to acquire Mattress Firm in a cash-and-stock transaction...}

\entryitemWithDescription{\hskip 0pt{}Truck slams into Polish bus in Germany, injuring dozens}{https://apnews.com/article/8d4cbd2f16b090d0d650ea7e901d5e64}{A polish coach stands damaged on the A12 highway after a serious accident in Dannenreich, near Berlin, Germany, Tuesday, May 9, 2023. A highway collision between a long-distance Polish bus and a truck has injured dozens of people in...}

\entryitemWithDescription{\hskip 0pt{}Perimeter guards absent as 2 men escaped Philadelphia prison}{https://apnews.com/article/b27231abb0254c0d2a6b03bcebe10f38}{This combo from photos provided by Philadelphia Dept. of Prisons shows from left, Nasir Grant, left, and Ameen Hurst. Authorities searched Tuesday, May 9, 2023, for two inmates, one accused of killing four people, who were gone from a...}

\entryitemWithDescription{\hskip 0pt{}Chinese woman appeals in fight for right to freeze her eggs}{https://apnews.com/article/b78d4b9fe274847a83f6a077f5317f2c}{Teresa Xu speaks to journalists before her appeal hearing in Beijing, Tuesday, May 9, 2023. The unmarried Chinese woman on Tuesday began her final appeal of a hospital\textquotesingle s denial of access to freeze her eggs five years ago...}

\entryitemWithDescription{\hskip 0pt{}Judge seems skeptical of Tiger Woods' ex-girlfriend's claims}{https://apnews.com/article/6dbca62faa201a877c43b62c736fbbc8}{FILE - Tiger Woods, right, with his daughter Sam Alexis Woods, left, and his girlfriend Erica Herman, center, walk along the Colonnade following a ceremony where President Donald Trump awarded the Presidential Medal of Freedom to Tiger...}\ichapter{Reuters}
\entryitemWithDescription{\hskip 0pt{}Embattled Republican Rep. George Santos to face federal charges -CNN}{https://www.reuters.com/world/us/us-prosecutors-file-criminal-charges-against-republican-lawmaker-santos-cnn-2023-05-09/}{U.S. Representative George Santos (R-NY) departs after a Republican conference meeting on Capitol in Washington, U.S. January 10, 2023. REUTERS/Jonathan Ernst U.S. federal prosecutors have filed criminal charges against George Santos, the...}

\entryitemWithDescription{\hskip 0pt{}Gunman who killed 8 at Texas shopping mall had 'neo-Nazi ideation,' officials say}{https://www.reuters.com/world/us/texas-gunman-had-neo-nazi-ideation-officials-say-2023-05-09/}{Officers with the Allen Police Department man the mobile command post the day after a gunman shot multiple people at the Dallas-area Allen Premium Outlets mall in Allen, Texas, U.S. May 7, 2023. REUTERS/Jeremy Lock The man who shot eight...}

\entryitemWithDescription{\hskip 0pt{}Migrants amass along US-Mexico border as COVID-era restrictions near end}{https://www.reuters.com/world/migrants-amass-along-us-mexico-border-covid-era-restrictions-near-end-2023-05-09/}{U.S. Border Patrol organize migrants after they gathered between primary and secondary border fences as the United States prepares to lift COVID-19 era Title 42 restrictions that have blocked migrants at the U.S.-Mexico border from...}

\entryitemWithDescription{\hskip 0pt{}Former Fox News host Tucker Carlson says he will relaunch his show on Twitter}{https://www.reuters.com/business/media-telecom/former-fox-news-host-tucker-carlson-says-will-relaunch-his-show-twitter-2023-05-09/}{Fox personality Tucker Carlson speaks at the 2017 Business Insider Ignition: Future of Media conference in New York, U.S., November 30, 2017. REUTERS/Lucas Jackson Former Fox News host Tucker Carlson, who was taken off the air by the...}

\entryitemWithDescription{\hskip 0pt{}Russia marks Victory Day with new strikes on Ukraine, but pared-back parade}{https://www.reuters.com/world/europe/russia-launches-new-attack-ukraine-moscows-sacred-day-2023-05-09/}{Summary: Putin says West has unleashed war on Russia EU executive leader visits Ukraine for Europe Day Kyiv says most missiles in new Russian volley shot down China: In touch with all sides in seeking ceasefire A Russian Yars...}

\entryitemWithDescription{\hskip 0pt{}Captagon: the drug fuelling the Gulf party scene - and Syria's finances}{https://www.reuters.com/world/middle-east/captagon-drug-fuelling-gulf-party-scene-syrias-finances-2023-05-09/}{FILE PHOTO: A customs officer displays Captagon pills, part of the 789 kilograms (1739 pounds) of confiscated drugs, before its incineration in Sofia, 12, 2007. REUTERS/Nikolay Doychinov (BULGARIA) From bloody frontlines to buzzing...}

\entryitemWithDescription{\hskip 0pt{}FBI says it has sabotaged hacking tool created by elite Russian spies}{https://www.reuters.com/world/fbi-says-it-has-sabotaged-hacking-tool-created-by-elite-russian-spies-2023-05-09/}{A Russian flag is seen on the laptop screen in front of a computer screen on which cyber code is displayed, in this illustration picture. REUTERS/Kacper Pempel/Illustration The FBI has sabotaged a suite of malicious software used by elite...}

\entryitemWithDescription{\hskip 0pt{}Six notable moments from Trump's sexual abuse trial}{https://www.reuters.com/world/us/six-notable-moments-trumps-civil-rape-trial-2023-05-09/}{Roberta Kaplan, lawyer of former Elle magazine advice columnist E. Jean Carroll, makes closing arguments during a civil trial where Carroll accuses former U.S. president Donald Trump of raping her in a department store dressing room in...}

\entryitemWithDescription{\hskip 0pt{}Analysis: Erdogan again? Amid rubble of Turkey's quake, voters demand to be heard}{https://www.reuters.com/world/middle-east/erdogan-again-amid-rubble-turkeys-quake-voters-demand-be-heard-2023-05-09/}{Summary: More than 50,000 killed, millions made homeless by quake Three months on, Antakya struggling for semblance of normality Disaster added to challenge faced by Erdogan in elections Amid criticism of quake response, views remain...}

\entryitemWithDescription{\hskip 0pt{}Factbox: An overview of Donald Trump's legal troubles}{https://www.reuters.com/world/us/an-overview-donald-trumps-legal-troubles-2023-05-09/}{Former Elle magazine advice columnist E. Jean Carroll watches as a former U.S. president Donald Trump\textquotesingle s video deposition is played in court during a civil trial where Carroll accuses the former U.S. president in a civil...}

\entryitemWithDescription{\hskip 0pt{}Factbox: What is the corruption case against Pakistan's Khan?}{https://www.reuters.com/world/asia-pacific/what-is-corruption-case-against-pakistans-khan-2023-05-09/}{Former Pakistani Prime Minister Imran Khan, gestures as he speaks with Reuters during an interview, in Lahore, Pakistan March 17, 2023. REUTERS/Akhtar Soomro Pakistan\textquotesingle s former Prime Minister Imran Khan was arrested on...}

\entryitemWithDescription{\hskip 0pt{}Pope says Argentina government wanted 'my head' when he was in Buenos Aires}{https://www.reuters.com/world/americas/pope-says-argentina-government-wanted-my-head-when-he-was-buenos-aires-2023-05-09/}{Pope Francis meets Argentina\textquotesingle s President Cristina Fernandez de Kirchner (L) during a private audience at the Vatican June 7, 2015. REUTERS/Angelo Carconi/Pool Pope Francis speaks as he attends the weekly general audience...}

\entryitemWithDescription{\hskip 0pt{}Russian mercenary chief says he's been told to stay in Bakhmut or be branded traitor}{https://www.reuters.com/world/europe/head-russias-wagner-group-says-still-no-sign-promised-ammunition-2023-05-09/}{Summary: Mercenary boss issues new tirade against top brass Says still does not have the ammo he needs Again raises spectre of exit from Bakhmut Says he\textquotesingle s been told his exit would be a betrayal Founder of Wagner private...}\ichapter{联合早报}
\entryitemWithDescription{郭台铭透露更多台湾总统蔡英文不准他采购BNT疫苗辛秘}{https://www.zaobao.com/news/china/story20230509-1392745}{鸿海集团创办人郭台铭透露更多有关前年时任台湾总统府秘书长李大维代总统蔡英文传话，阻挡他采购BNT疫苗的辛秘。现任海基会董事长李大维矢口否认，反指郭台铭是为了台湾总统选举而这么说。 郭台铭目前正积极争取在野国民党的总统提名。据国民党立委陈玉珍等人星期一（5月8日）晚上与郭台铭餐叙后转述，郭当时想买BNT疫苗（也称辉瑞疫苗）给台湾民众施打……}

\entryitemWithDescription{中加相互驱逐外交人员 学者：两国关系近冰点}{https://www.zaobao.com/news/china/story20230509-1392741}{中国宣布把加拿大驻上海总领馆领事甄逸慧（Jennifer Lynn Lalonde）列为``不受欢迎的人''，并要求她5月13日前离开中国。（取自甄逸慧推特） 加拿大政府宣布驱逐一名中国外交人员后，中国隔天采取反制措施，把加拿大驻上海总领馆领事甄逸慧（Jennifer Lynn Lalonde）列为``不受欢迎的人''，并要求她星期六（5月13日）前离开中国……}

\entryitemWithDescription{中国首例单身女性冻卵案二审 法院未当庭宣判}{https://www.zaobao.com/news/china/story20230509-1392737}{徐枣枣（化名）星期二（9日）进入北京市第三中级人民法院出席冻卵案二审。（路透社） 中国首例``单身女性冻卵案''星期二（5月9日）在北京市开庭二审，不过和一审一样，法院并没有当庭宣判。 根据界面新闻、澎湃新闻报道，现年35岁当事人徐枣枣（化名）在北京市第三中级人民法院出席庭讯后，告诉媒体：``此次庭审主要辩论点还是（医院拒绝冻卵）是否构成人格权侵害'等问题……}

\entryitemWithDescription{美国务院：驻华大使向中国传达一中政策保持不变信息}{https://www.zaobao.com/news/china/story20230509-1392724}{美国国务院宣称驻中国大使伯恩斯已向北京说明美国对华政策，特别是一个中国政策保持不变的信息，并表示国务卿布林肯希望能访问中国。 路透社报道，美国国务院发言人帕特尔（Vedant Patel）星期一（5月8日）在记者会上说，伯恩斯（Nicholas Burns）私下传达：美国对华政策没有改变，华盛顿在外交上正式承认北京，而不是台北……}

\entryitemWithDescription{港警降入职要求 投考人数增逾三倍}{https://www.zaobao.com/news/china/story20230509-1392721}{香港警察部队宣布降低三项入职要求后，一周内吸引385人投考警队，每天平均投考人数是调降要求前的三倍多。 警务处人事部招募组警司陈杰峰星期一（5月8日）在一个香港电视节目中透露，自上周五（5日）调整入职要求后，平均每天有58人投考警队。``其中有40多岁的运输司机，本身因身高161公分而不达标，如今可以实践儿时抱负……}

\entryitemWithDescription{广东超高清视频产业规模占全国约五分之一}{https://www.zaobao.com/news/china/story20230509-1392720}{中国电子信息产业发展研究院星期二（5月9日）发布的产业发展白皮书显示，截至2022年，中国超高清视频产业规模超过3万亿元（人民币，下同，5747亿新元），其中广东省产业营收逾6000亿元，规模约占全国五分之一……}

\entryitemWithDescription{英国高官再访港 中英关系似有改善}{https://www.zaobao.com/news/china/story20230509-1392715}{中英关系近来似有改善迹象。英国商业及贸易部国务部长约翰逊（Dominic Johnson，港译庄敦文）从周一（5月8日）起一连两天访问香港，是自2018年后英国再次有同等级别官员访港。但有学者认为，英国的外交政策一向跟随美国，目前美国全面抑制中国，中英和港英关系恐难以有改善……}

\entryitemWithDescription{欧盟驻中国大使对在华咨询公司被查表担忧}{https://www.zaobao.com/news/china/story20230509-1392702}{欧盟驻中国大使对近期在华经营的咨询公司受到调查和新修订的《反间谍法》表示担忧，但同时也肯定了中国在促进欧洲和平上的努力。 据路透社星期二（5月9日）报道，欧盟驻华大使庹尧诲（Jorge Toledo Albinana）在北京召开的记者会上说，修订后的中国《反间谍法》可能不利于实现中国经济吸引更多外来投资目标。 他也对一家咨询公司受到调查表达关切。他说：``打击咨询公司的最新信息不是好消息……}

\entryitemWithDescription{加拿大多所顶尖大学宣布终止与华为的研究合作}{https://www.zaobao.com/news/china/story20230509-1392686}{多所加拿大顶尖大学一周内相继宣布，跟中国通讯设备制造商华为终止研究合作关系，或不再签订新的研究协议……}

\entryitemWithDescription{中国早点：香港泛民还会参加区选吗？}{https://www.zaobao.com/news/china/story20230509-1392482}{港府继两年前修改立法会选举游戏规则后，上星期又公布以``爱国者治港''原则为基础的区议会改组方案，锐意翻天地覆改变区议会的组成和选举方式。民主派阵营今年年底还会不会参加新一届区议会选举，连日来备受政界关注。 区议会在香港只是一个地区性咨询组织，但由于成员是经市民一人一票选举产生，具有相当大的民意基础，在九七年回归后，成为立法会以外另一个表达政治诉求的平台……}

\entryitemWithDescription{中国咨询企业龙头 被指``沦为境外情报机构的帮凶''}{https://www.zaobao.com/news/china/story20230508-1392337}{中国国家安全机关对中国大陆境内的咨询行业龙头企业进行公开执法，指其``沦为境外情报机构的帮凶''。 据央视新闻客户端星期一（5月8日）晚上播出的《焦点访谈》节目，这家公司是凯盛融英信息科技有限公司。上海市国家安全局一名干警接受《焦点访谈》节目访问时说，凯盛融英``拥有1000多家客户，遍布境内境外。业务分为三大块，其中专家访谈占了凯盛融英业务总量的80\%，专家访谈就是以专家电话访谈形式为主……}

\entryitemWithDescription{数月来中美最高层级接触 秦刚会见美驻华大使}{https://www.zaobao.com/news/china/story20230508-1392332}{中国国务委员兼外长秦刚（右二）星期一（5月8日）在北京会见美国驻华大使伯恩斯（左二）。（中国外交部官网） 中国国务委员兼外长秦刚星期一（5月8日）在北京会见美国驻华大使伯恩斯，强调当务之急是稳定中美关系、避免螺旋式下滑。学者分析认为，这显示北京已准备好修补与拜登政府的关系，并可能愿为重新安排美国国务卿布林肯访华铺路。 刚结束外访的秦刚星期一会见伯恩斯，是他去年底出任中国外长后首次会见美驻华大使……}

\entryitemWithDescription{柯文哲登记民众党2024年总统初选 直言``蓝白合''难度高}{https://www.zaobao.com/news/china/story20230508-1392325}{台湾在野民众党主席柯文哲星期一（5月8日）到民众党中央党部登记参加2024年总统初选。（自由时报） 台湾在野民众党主席柯文哲星期一（5月8日）到民众党中央党部登记参选2024年总统，他对于和最大在野国民党合作一事表示，彼此DNA不同，很难结合。他三度强调，两党合作最重要的是理念价值相同，否则就会流于密室政治的权力分配，老百姓也不会支持……}

\entryitemWithDescription{台湾借贷平台imB爆发诈骗风暴 冲击民进党政府``打诈''形象}{https://www.zaobao.com/news/china/story20230508-1392322}{台湾借贷平台im.B爆发25亿元（新台币，约1亿零800万新元）诈骗风暴，受害者超过5000人。嫌犯落网后，坊间出现他与不少民进党高层的合照，冲击政府``打诈''形象。 受访专家指出，诈骗猖獗是民众切身之痛，官员与嫌犯同框确实给人负面观感。但如果在野党无法挖出官商勾结的具体证据，很快就会被淡忘，政治效应未必扩大……}

\entryitemWithDescription{韩国抗议《环时》观点 中国外交部指非官方立场}{https://www.zaobao.com/news/china/story20230508-1392303}{中国《环球时报》上月批评韩国总统尹锡悦访问美国前后涉及台湾的言论，引发韩国驻华大使馆抗议。中国外交部星期一（5月8日）表示，《环时》观点不代表中国政府的立场，但反映了中国国内民意。 尹锡悦4月19日接受路透社访问时说，台海出现紧张局势是因试图用武力改变现状，台湾问题不仅是中国（大陆）和台湾之间的问题，和朝鲜问题一样是全球问题……}

\entryitemWithDescription{中国军事专家：中国航舰已具备近海防御与远海护卫能力}{https://www.zaobao.com/news/china/story20230508-1392299}{第21届中国国际模型博览会4月21日在北京展览馆开幕。图为观众参观中国海军山东舰航母战斗群模型。（香港中通社） 中国山东舰航母编队已完成远海战备训练返回母港。军事专家认为，航舰编队能够从第一岛链进行远海训练，显示中国国产航舰已具备在远海执行军事任务的能力。 据中国央视军事上星期六（5月6日）在官微发布消息称，山东舰航母编队赴台湾岛以东海空域开展远海战备训练，演练历时近月，近日返回母港……}

\entryitemWithDescription{深圳自媒体用AI虚构新闻 被采取刑事强制措施}{https://www.zaobao.com/news/china/story20230508-1392287}{深圳一家自媒体负责人，涉嫌利用ChatGPT人工智能软件，修改及编辑搜集到的新闻要素后上传互联网，涉嫌寻衅滋事罪，被甘肃警方采取刑事强制措施。 这是中国1月10日颁布实施《互联网信息服务深度合成管理规定》后，甘肃省侦办的第一起利用人工智能（AI）技术炮制虚假不实信息的案件……}

\entryitemWithDescription{美国智库报告促中国收紧海外机构访问数据库}{https://www.zaobao.com/news/china/story20230508-1392277}{美国媒体引述知情人士透露，中国最近加大力度限制海外机构访问中国数据库，一定程度是因部分美国智库报告提及中国敏感领域，引起官方警惕。 据《华尔街日报》报道，中国政府上月通过的新版《反间谍法》，扩大了法律适用范围和执行权力。官方近来也加紧对专门收集信息的外国企业施压，并收紧外国智库、研究公司等机构对中国数据库的访问……}

\entryitemWithDescription{深圳艺术展开幕四天突闭馆 疑涉上海封城作品}{https://www.zaobao.com/news/china/story20230508-1392274}{中国深圳一场艺术展览疑似因展出上海封城相关作品，开展四天后突然宣布闭馆。 这场名为``2023湾区当代艺术联展''的展览，上星期二（5月2日）开展。展览主题为``时间的分岔''，探讨后疫情时代里文化和艺术语境中的生态变化以及心理转向。展览邀请了23位艺术家参与，共计展出70余件作品……}

\entryitemWithDescription{港经济学家刘遵义：中国现行退休年龄过低 强迫退休是浪费资源}{https://www.zaobao.com/news/china/story20230508-1392272}{老人们4月20日在中国河北省平乡县寻召村``幸福小院''内下象棋。（新华社） 香港著名经济学家刘遵义认为，中国大陆目前法定的男女退休年龄过低，强迫退休是``浪费资源''，如能延迟退休，可以鼓励更多人进入劳动市场……}

\entryitemWithDescription{中国早点：冠病疫情终于画上了句号}{https://www.zaobao.com/news/china/story20230508-1392061}{世界卫生组织总干事谭德塞5月5日宣布，冠病疫情全球卫生紧急状态结束，不再构成``国际关注的突发公共卫生事件（PHEIC）''。有中国媒体形象地将此称为世卫组织已对冠病疫情``取关（取消关注）'' 2020年1月30日，冠病疫情在武汉等地失控之后，世卫组织宣布冠病疫情构成``国际关注的突发公共卫生事件''。世卫组织数据显示，过去三年全球累计报告确诊病例逾7亿6000万，死亡病例超过690万……}

\entryitemWithDescription{中阿巴外长举行对话 同意加强反恐合作}{https://www.zaobao.com/news/china/story20230507-1391912}{中国国务委员兼外长秦刚（左一）在巴基斯坦伊斯兰堡出席第五次中阿巴三方外长对话。巴基斯坦外长比拉瓦尔（中）主持，阿富汗临时政府代理外长穆塔基（右一）出席。（新华社） 中国、阿富汗、巴基斯坦三国外长同意加强反恐合作，重启外长对话机制。三方也同意，推进共建一带一路合作，支持中巴经济走廊向阿富汗延伸……}