\entryitemWithDescription{\hskip 0pt{}Feinstein returning to Senate after facing resignation calls}{https://apnews.com/article/49374eadf516a1fb521cac466bb5d18f}{FILE - Sen. Dianne Feinstein, D-Calif., walks through a Senate corridor at the Capitol in Washington, Feb. 14, 2023. Feinstein is returning to Washington after a more than two month absence led to calls from within her own party for the...}

\entryitemWithDescription{\hskip 0pt{}She wrote book on husband's death; police say she killed him}{https://apnews.com/article/d26a40d5b90f1ca6e6da8f46104afce1}{This photo provided by KPCW.org shows Kouri Richins at the KPCW studio in Park City, Utah, April 12, 2023. Richins was arrested on Monday, May 8, in Utah and is accused in charging documents of poisoning her husband with a lethal dose of...}

\entryitemWithDescription{\hskip 0pt{}Robert De Niro, at 79, becomes a father for the 7th time}{https://apnews.com/article/68296f887ee3892e28ecc4a0fe596ffa}{FILE - Robert De Niro attends the world premiere of "Amsterdam" at Alice Tully Hall on Sunday, Sept. 18, 2022, in New York. De Niro has welcomed another child. The 79-year-old is now the father of seven. A representative for De Niro...}

\entryitemWithDescription{\hskip 0pt{}Signed in purple ink, Minnesota dedicates highway to Prince}{https://apnews.com/article/45220b9307ba1dee12512c84c71063c1}{FILE - Prince performs during the halftime show at the Super Bowl XLI football game in Miami, Feb. 4, 2007. The late pop superstar Prince will have a highway named after him, thanks to Minnesota lawmakers who voted Thursday, May 4, 2023...}

\entryitemWithDescription{\hskip 0pt{}What to know as UK hosts Eurovision Song Contest for Ukraine}{https://apnews.com/article/ef0005c0ddb68eebe2a4599d95147859}{Alyosha of Ukraine performs during a dress rehearsal at the Eurovision Song Contest at the M\&S Bank Arena in Liverpool, England, Monday, May 8, 2023. (AP Photo/Martin Meissner) LONDON (AP) --- Last week, Britain crowned a king. This...}

\entryitemWithDescription{\hskip 0pt{}Rita Lee, Brazil's long-reigning Queen of Rock, dies at 75}{https://apnews.com/article/cc5a47525b592657fb0155e0f65e1922}{FILE - Brazilian singer Rita Lee performs in concert in Buenos Aires, Argentina, Nov. 23, 2002. Brazil's million-selling ``Queen of Rock'' who gained an international following through her colorful and candid style has died at the age 75...}

\entryitemWithDescription{\hskip 0pt{}Hyundai and Kia thefts keep rising despite security fix}{https://apnews.com/article/8e0a353d24be0e7bce36e34c5e4dac51}{A line of 2022 Santa Fe SUV\textquotesingle s sit outside a Hyundai dealership Sunday, Sept. 12, 2021, in Littleton, Colo. Nearly three months after Hyundai and Kia rolled out new software designed to thwart rampant auto thefts, crooks...}

\entryitemWithDescription{\hskip 0pt{}Christie's sale of Austrian heiress' jewels stirs criticism}{https://apnews.com/article/d5cfad3f098b84b52aed090a053079a7}{An employee of Christie\textquotesingle s displays the Great Mogul Emerald and Diamond Necklace by Harry Winston, estimated between 450,000 - 640,000 CHF (Swiss Francs), in display case, during the preview of "The World of Heidi Horten"...}

\entryitemWithDescription{\hskip 0pt{}Tempur Sealy to buy Mattress Firm in \$4 billion deal}{https://apnews.com/article/a4973adf7d958e2e358b902d3f4f9b42}{A passer-by walks near the front of a Tempur-Pedic mattress store location, Tuesday, May 9, 2023, in Dedham, Mass. Tempur Sealy, the parent company of Tempur-Pedic, has agreed to acquire Mattress Firm in a cash-and-stock transaction...}

\entryitemWithDescription{\hskip 0pt{}Truck slams into Polish bus in Germany, injuring dozens}{https://apnews.com/article/8d4cbd2f16b090d0d650ea7e901d5e64}{A polish coach stands damaged on the A12 highway after a serious accident in Dannenreich, near Berlin, Germany, Tuesday, May 9, 2023. A highway collision between a long-distance Polish bus and a truck has injured dozens of people in...}

\entryitemWithDescription{\hskip 0pt{}Perimeter guards absent as 2 men escaped Philadelphia prison}{https://apnews.com/article/b27231abb0254c0d2a6b03bcebe10f38}{This combo from photos provided by Philadelphia Dept. of Prisons shows from left, Nasir Grant, left, and Ameen Hurst. Authorities searched Tuesday, May 9, 2023, for two inmates, one accused of killing four people, who were gone from a...}

\entryitemWithDescription{\hskip 0pt{}Chinese woman appeals in fight for right to freeze her eggs}{https://apnews.com/article/b78d4b9fe274847a83f6a077f5317f2c}{Teresa Xu speaks to journalists before her appeal hearing in Beijing, Tuesday, May 9, 2023. The unmarried Chinese woman on Tuesday began her final appeal of a hospital\textquotesingle s denial of access to freeze her eggs five years ago...}

\entryitemWithDescription{\hskip 0pt{}Judge seems skeptical of Tiger Woods' ex-girlfriend's claims}{https://apnews.com/article/6dbca62faa201a877c43b62c736fbbc8}{FILE - Tiger Woods, right, with his daughter Sam Alexis Woods, left, and his girlfriend Erica Herman, center, walk along the Colonnade following a ceremony where President Donald Trump awarded the Presidential Medal of Freedom to Tiger...}