\entryitemWithDescription{\hskip 0pt{}Richonne rises in `The Walking Dead: The Ones Who Live' starring Andrew Lincoln and Danai Gurira}{https://apnews.com/article/76b8c3faf45b565fc5ff3149aa51c31a}{PASADENA, Calif. (AP) --- Danai Gurira remembers a moment filming `` The Walking Dead '' which she now believes contributed to the future pairing of her character Michonne with Andrew Lincoln's Rick. It was during season three, Gurira's...}

\entryitemWithDescription{\hskip 0pt{}To keep whales safe, Coast Guard launches boat alert system in Seattle}{https://apnews.com/article/ca034b8cb584f9aca7200a83a51cd0a2}{SEATTLE (AP) --- Photographer Matt McDonald had lived on Puget Sound for years, but had never seen a whale, so he was elated when he spotted a giant marine mammal just off Seattle's waterfront one evening. The excitement was short-lived...}

\entryitemWithDescription{\hskip 0pt{}An unusual criminal case over handwritten lyrics to `Hotel California' goes to trial Wednesday}{https://apnews.com/article/8ec3a28657365ecce6bfd4003ead494a}{NEW YORK (AP) --- A curious criminal case involving handwritten lyrics to the classic rock megahit ``Hotel California'' and other Eagles favorites is going to trial in a New York courtroom, with opening statements set for Wednesday. The...}

\entryitemWithDescription{\hskip 0pt{}It's an election year, and Biden's team is signaling a more aggressive posture toward the press}{https://apnews.com/article/3bda702e68181e58ead973e7c8eae0c7}{NEW YORK (AP) --- Occupants of the White House have grumbled over news coverage practically since the place was built. Now it's Joe Biden's turn: With a reelection campaign underway, there are signs that those behind the president are...}

\entryitemWithDescription{\hskip 0pt{}Jury selection begins for trial of ``Rust'' armorer in fatal 2021 shooting by Alec Baldwin}{https://apnews.com/article/b76e96b11f6452e61e3fb754054e94a1}{SANTA FE, N.M. (AP) --- Prosecutors in New Mexico want more accountability for the 2021 death of a cinematographer who was fatally shot by actor Alec Baldwin during a rehearsal for the Western film ``Rust.'' Before Baldwin's case...}

\entryitemWithDescription{\hskip 0pt{}In Teahupo'o, Tahiti, coastal village life thrives among powerful waves}{https://apnews.com/article/902555e439a1572a35f316c6a7abdd92}{TEAHUPO'O, French Polynesia (AP) --- In Teahupo'o, the ocean is the heart of village life. Boats bob in the lagoon in the south of Tahiti at sunrise before fishers start their day. Many set out early with poles or spears to catch fish...}

\entryitemWithDescription{\hskip 0pt{}Young girl killed when a hole she dug in the sand collapsed on a Florida beach, authorities said}{https://apnews.com/article/a8d096befccae2db76c9d5abe791b357}{FORT LAUDERDALE, Fla. (AP) --- A young girl was buried in sand and died Tuesday when a deep hole she was digging with a little boy collapsed on them both at a south Florida beach, authorities said. Emergency crews responding around 3 p.m...}

\entryitemWithDescription{\hskip 0pt{}Divorce of Kevin Costner and Christine Baumgartner is finalized, officially ending their marriage}{https://apnews.com/article/1546a358fdaa4f5f8f3d71099d433916}{SANTA BARBARA, Calif. (AP) --- A judge has declared that Kevin Costner and his wife of nearly two decades, Christine Baumgartner, are now legally divorced, according to court records filed Tuesday. The couple's marriage ended, and both...}

\entryitemWithDescription{\hskip 0pt{}A Colorado man is dead after a pet Gila monster bite}{https://apnews.com/article/6b15c382d9ac61c20dc3a28cac87a518}{A Colorado man has died after being bitten by his pet Gila monster in what would be a rare death by one of the desert lizards if the creature's venom turns out to have been the cause. Christopher Ward, 34, was taken to a hospital shortly...}

\entryitemWithDescription{\hskip 0pt{}George H.W. Bush's speedboat fetches \$435,000 at benefit auction}{https://apnews.com/article/8790e7756da9c6e8a3705ecee6577435}{HOUSTON (AP) --- Former President George H.W. Bush's speedboat has a new owner. The 38-foot (11.5-meter) ``Fidelity V'' was auctioned for \$435,000 during the George and Barbara Bush Foundation's 2024 Presidential Salute benefiting the...}

\entryitemWithDescription{\hskip 0pt{}United flight from San Francisco to Boston diverted due to damage to one of its wings}{https://apnews.com/article/3d9d45026a86360fb276d6e4f72099d1}{SAN FRANCISCO (AP) --- United Airlines says a flight heading from San Francisco to Boston had to be diverted after the plane suffered damage to one of its wings. United said Tuesday that the Boeing 757-200 with 165 passengers aboard...}

\entryitemWithDescription{\hskip 0pt{}Beatles to get a Fab Four of biopics, with a movie each for Paul, John, George and Ringo}{https://apnews.com/article/3f3f74076d78f16ac420820638e05de3}{NEW YORK (AP) --- The Beatles are getting the big-screen biopic treatment in not just one film, but a Fab Four of movies that will give each band member their own spotlight --- all of which are to be directed by Sam Mendes. For the first...}

\entryitemWithDescription{\hskip 0pt{}Welcome to the `Hotel California' case: The trial over handwritten lyrics to an Eagles classic}{https://apnews.com/article/973e74e795416821e6f022895b47b78e}{NEW YORK (AP) --- In the mid-1970s, the Eagles were working on a spooky, cryptic new song. On a lined yellow pad, Don Henley, with input from band co-founder Glenn Frey, jotted thoughts about ``a dark desert highway'' and ``a lovely...}