\entryitemWithDescription{\hskip 0pt{}FBI: `Little rascals' trio, ages 11, 12 and 16, arrested for robbing a Houston bank}{https://apnews.com/article/768ed68c70bac044b1757504ab553a30}{HOUSTON (AP) --- Three boys, ages 11, 12 and 16, and dubbed the ``Little Rascals,'' have been arrested for robbing a bank in Houston, authorities confirmed on Wednesday. Harris County Sheriff Ed Gonzalez said the youngsters are in custody...}

\entryitemWithDescription{\hskip 0pt{}A New York man's pet alligator was seized after 30 years. Now, he wants Albert back}{https://apnews.com/article/0fb6a00ffc1bed34ce2ff9a753a2d893}{HAMBURG, N.Y. (AP) --- The owner of an alligator recently seized by conservation officers in New York is fighting for its return, saying the reptile he named Albert and has shared a home with for more than three decades is a gentle giant...}

\entryitemWithDescription{\hskip 0pt{}Detroit Lions' defensive back Cameron Sutton sought in Florida domestic violence warrant}{https://apnews.com/article/83dda4abdb32da36bea2ad2cd44facb0}{TAMPA, Fla. (AP) --- Detroit Lions defensive back Cameron Sutton is wanted on a domestic violence warrant in Florida, where authorities on Wednesday asked for tips to help find him. The Hillsborough County Sheriff's Office, which includes...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry's lawyer implicates Rupert Murdoch in cover-up of unlawful snooping by his tabloids}{https://apnews.com/article/7f34d7d405147a294003bb920ac3d681}{LONDON (AP) --- Prince Harry's lawyer leveled explosive new allegations Wednesday that Rupert Murdoch was aware of cover-ups at his British tabloids that used unlawful techniques to spy on the Duke of Sussex and others. Attorney David...}

\entryitemWithDescription{\hskip 0pt{}Battleship on the Delaware River: USS New Jersey traveling to Philadelphia for repairs}{https://apnews.com/article/16e9cfcc880f7debfbedc1daf688071e}{CAMDEN, N.J. (AP) --- Residents in the Philadelphia area are about to see a rare site --- a battleship floating down the Delaware River. The USS New Jersey is scheduled to move from its dock in Camden on Thursday, when it will head to the...}

\entryitemWithDescription{\hskip 0pt{}Police in Idaho involved in hospital shooting are searching for an escaped inmate and 2nd suspect}{https://apnews.com/article/e7381ac66bbf4c5d8ea9eebb51a70ab0}{BOISE, Idaho (AP) --- Police in Boise, Idaho, said officers were involved in a shooting at a hospital early Wednesday and are searching for two suspects, one of them a prison inmate who escaped from the campus. Saint Alphonsus Regional...}

\entryitemWithDescription{\hskip 0pt{}Ohtani and Dodgers rally to beat Padres 5-2 in season opener, first MLB game in South Korea}{https://apnews.com/article/a532a3eac37bd7517e0d1b65828c85a4}{SEOUL, South Korea (AP) --- Shohei Ohtani's RBI single capped a four-run eighth-inning rally in his Dodgers debut, and Los Angeles beat the San Diego Padres 5-2 in Wednesday night's major league opener, the sport's first game in South...}

\entryitemWithDescription{\hskip 0pt{}New rankings show French bulldogs reign on as top US breed, making many fans shudder}{https://apnews.com/article/b8faa0214c160d00117ef1ef15d21f43}{NEW YORK (AP) --- French bulldogs. U.S. dog owners. C'est l'amour. Frenchies remained the United States' most commonly registered purebred dogs last year, according to American Kennel Club rankings released Wednesday. The club calls the...}

\entryitemWithDescription{\hskip 0pt{}Microsoft hires influential AI figure Mustafa Suleyman to head up consumer AI business}{https://apnews.com/article/3e56e7ace8eb5664f4239e7f9c92e7d5}{LONDON (AP) --- Microsoft has hired Mustafa Suleyman to head up its consumer artificial intelligence business, adding to its ranks an influential figure in the artificial intelligence world to cement its position at the forefront of the...}

\entryitemWithDescription{\hskip 0pt{}Mega Millions jackpot reaches an astounding \$977M after no one wins Tuesday's drawing}{https://apnews.com/article/798a3c138c8e5dc0ddbb743c6b1d5345}{FORT LAUDERDALE, Fla. (AP) --- The Mega Millions jackpot has reached an astounding \$977 million for Friday night's drawing after no tickets matched all six numbers drawn on Tuesday night. The winning numbers drawn on Tuesday were 24, 46...}

\entryitemWithDescription{\hskip 0pt{}AI-aided virtual conversations with WWII vets are latest feature at New Orleans museum}{https://apnews.com/article/d4ad6a019125c864e7076dfa37039d43}{NEW ORLEANS (AP) --- An interactive exhibit opening Wednesday at the National WWII Museum will use artificial intelligence to let visitors hold virtual conversations with images of veterans, including a Medal of Honor winner who died in...}

\entryitemWithDescription{\hskip 0pt{}New Zealand will ban disposable e-cigarettes in a bid to prevent minors from taking up the habit}{https://apnews.com/article/d74821c351aef9a1c086c0d9089b847b}{WELLINGTON, New Zealand (AP) --- New Zealand said Wednesday it will ban disposable e-cigarettes, or vapes, and raise financial penalties for those who sell such products to minors. The move comes less than a month after the government...}

\entryitemWithDescription{\hskip 0pt{}Historic covered bridges are under threat by truck drivers relying on GPS meant for cars}{https://apnews.com/article/906e3379e07b20dbcdbe16e7cf5e5d6d}{LYNDON, Vt. (AP) --- One of Vermont's historic covered bridges has fallen under threat from modern technology. Box truck drivers relying on GPS continually crash through Lyndon's 140-year-old Miller's Run bridge despite signs, including a...}