\entryitemWithDescription{\hskip 0pt{}Tigers acquire veteran outfielder Mark Canha from Brewers in exchange for minor league pitcher}{https://apnews.com/article/ffc2a7cbdd52f6f0e074f8513f0eec57}{MILWAUKEE (AP) --- Veteran outfielder Mark Canha is on the move again, with the Milwaukee Brewers trading him to the Detroit Tigers on Saturday rather than picking up his option for the 2024 season. The Brewers acquired minor league...}

\entryitemWithDescription{\hskip 0pt{}Phoenix finishes clearing downtown homeless encampment after finding shelter for more than 500}{https://apnews.com/article/b0ccbe6bc03ee1592b4e6a087c839417}{PHOENIX (AP) --- The city of Phoenix has successfully cleared out a massive downtown homeless encampment by Saturday's court ordered deadline by helping more than 500 people find beds in shelters and motels. The hundreds of tents that...}

\entryitemWithDescription{\hskip 0pt{}Leroy Stover, Birmingham's first Black police officer, dies at 90}{https://apnews.com/article/cfbe9c34792833da197b8f7659e918a7}{BIRMINGHAM, Ala. (AP) --- The City of Birmingham's first Black police officer, Leroy Stover, has died. He was 90. Birmingham Police on Friday posted about Stover's death on X, formerly known as Twitter. ``Today, our hearts are heavy as we...}

\entryitemWithDescription{\hskip 0pt{}Arkansas man arrested after trying to crash through gates at South Carolina nuclear plant}{https://apnews.com/article/74193ea7e613b0528c84e590cfc9873b}{WALHALLA, S.C. (AP) --- An Arkansas man has been arrested for trying to crash through the exit gates of a South Carolina nuclear plant, authorities said. Doyle Wayne Whisenhunt, of Lockesburg, Arkansas, was taken into custody Friday night...}

\entryitemWithDescription{\hskip 0pt{}Illinois city tickets reporter for asking too many questions, in latest First Amendment dustup}{https://apnews.com/article/999a872f6fd45962547af94318e92950}{SPRINGFIELD, Ill. (AP) --- Officials in a suburban Chicago community have issued municipal citations to a local news reporter for what they say were persistent contacts with city officials seeking comment on treacherous fall flooding. The...}

\entryitemWithDescription{\hskip 0pt{}Tupac Shakur has an Oakland street named for him 27 years after his death}{https://apnews.com/article/e9705d56b9e01b838987e1b439cd0b8b}{OAKLAND, Calif. (AP) --- A stretch of street in Oakland, California, was renamed Friday for Tupac Shakur, 27 years after the killing of the hip-hop luminary. A section of MacArthur Boulevard near where he lived in the 1990s became Tupac...}

\entryitemWithDescription{\hskip 0pt{}NASA spacecraft discovers tiny moon around asteroid during close flyby}{https://apnews.com/article/bc24131a8bd9dc9161ab8793e7693f45}{CAPE CANAVERAL, Fla. (AP) --- The little asteroid visited by NASA's Lucy spacecraft this week had a big surprise for scientists. It turns out that the asteroid Dinkinesh has a dinky sidekick --- a mini moon. The discovery was made during...}

\entryitemWithDescription{\hskip 0pt{}Businessman sentenced in \$180 million bank fraud that paid for lavish lifestyle, classic cars}{https://apnews.com/article/d0c9a4a2a66fb88a832a613a8560c49c}{CLEVELAND (AP) --- A businessman who orchestrated a \$180 million check-kiting scheme and used the proceeds to live a lavish lifestyle and amass one of the world's most revered classic car collections has been sentenced to more than eight...}

\entryitemWithDescription{\hskip 0pt{}Car crashes through gate at South Carolina nuclear plant before pop-up barrier stops it}{https://apnews.com/article/9cd18a2f7b883a4af27c669c8d0dfb26}{SENECA, S.C. (AP) --- A driver tried to crash through the exit gates of a South Carolina nuclear plant Thursday night about an hour after security asked the same car to leave when it tried to enter, authorities said. A pop-up security...}

\entryitemWithDescription{\hskip 0pt{}Winds from Storm Ciarán whip up a wildfire in eastern Spain as 850 people are evacuated}{https://apnews.com/article/1381dedd0b283864c63af34e002cf81c}{MADRID (AP) --- A wildfire abetted by storm winds in eastern Spain has burned some 2,000 hectares (4,900 acres) of land and forced the evacuation of 850 people from four towns, officials said Friday. Some 200 firefighters and army...}

\entryitemWithDescription{\hskip 0pt{}Fall back: How daylight saving time can seriously affect your health}{https://apnews.com/article/a3738d5c74301b8068825927c49fc6b4}{CHICAGO (AP) --- Brunch dates and flag football games might be a little easier to get to this Sunday, when phones grace early-risers with an extra hour of rest before alarm clocks go off. The downside: Next week across most of the U.S...}

\entryitemWithDescription{\hskip 0pt{}World Series averaged 9.11 million viewers, making it the least-watched Fall Classic in TV history}{https://apnews.com/article/f0eb9837a3d8bfa529fed811a6417057}{The Texas Rangers 5-0 victory over the Arizona Diamondbacks for their first championship on Wednesday night drew the largest audience of this World Series. However, it was not enough to prevent the five-game series from being the least...}

\entryitemWithDescription{\hskip 0pt{}Utah woman's leg amputated after she was attacked by her son's dogs in her own backyard}{https://apnews.com/article/91fd2e4174717e804756107759ac1fa0}{TAYLORSVILLE, Utah (AP) --- A 63-year-old Utah woman had a leg amputated after being attacked by her son's dogs in her own backyard in a Salt Lake City suburb. Officers who arrived at the home in Taylorsville had to shoot and kill one of...}