\entryitemWithDescription{\hskip 0pt{}Former first daughter Barbara Bush tells AP about helping lead NBA's social responsibility efforts}{https://apnews.com/article/a3086bbd203ace9a1da32bf30cb0e92c}{Barbara Bush never got to any of the NBA championship celebrations held at the White House when her grandfather was president of the United States. Never got to one when her father occupied the Oval Office, either. She got to the one held...}

\entryitemWithDescription{\hskip 0pt{}Winner of last month's \$1.6 billion Mega Millions jackpot claims prize in Florida}{https://apnews.com/article/8c86594edcd16cdcda7521059ef7c7ed}{FORT LAUDERDALE, Fla. (AP) --- The winner of last month's \$1.6 billion Mega Millions jackpot --- the third-largest in U.S. history --- has come forward to claim the prize, officials said Wednesday. In all, Mega Millions has had five...}

\entryitemWithDescription{\hskip 0pt{}Bruce Springsteen postpones all 2023 tour dates until 2024 as he recovers from peptic ulcer disease}{https://apnews.com/article/c0f398e3b6377d88291aee87ca270451}{LOS ANGELES (AP) --- Bruce Springsteen and the E Street Band's 2023 tour will be postponed until 2024, citing doctor's advice. The Boss, who last week celebrated his 74th birthday, is ``steadily recovering'' from peptic ulcer disease, a...}

\entryitemWithDescription{\hskip 0pt{}Travis Kelce notes Taylor Swift's `bold' appearance at Chiefs game but is mum about any relationship}{https://apnews.com/article/faf0793263d3cbd7052dbeede45a3b3f}{Kansas City tight end Travis Kelce calls Taylor Swift's appearance at the Chiefs' victory over the Chicago Bears ``pretty bold'' but wants to remain private about any relationship with the superstar singer. Speaking on his podcast ``New...}

\entryitemWithDescription{\hskip 0pt{}Authorities make arrests in the case of Kentucky woman reported missing 8 years ago}{https://apnews.com/article/0161895fe56ea1acc6ea0d02c08330a0}{LOUISVILLE, Ky. (AP) --- The former boyfriend of a central Kentucky woman who disappeared more than eight years ago has been arrested on charges stemming from the investigation, the FBI and Kentucky State Police said Wednesday in a...}

\entryitemWithDescription{\hskip 0pt{}Powerball jackpot up to \$850 million after months without a big winner}{https://apnews.com/article/567d816f973f169e6a56d93c924b447a}{DES MOINES, Iowa (AP) --- An estimated \$850 million Powerball jackpot will be up for grabs Wednesday night for players willing to risk a couple dollars and brave incredibly long odds. The jackpot is the world's ninth-largest lottery...}

\entryitemWithDescription{\hskip 0pt{}Hyundai and Kia recall nearly 3.4 million vehicles due to fire risk and urge owners to park outdoors}{https://apnews.com/article/93d012a52e7b884889cdaf2e6c22a458}{DETROIT (AP) --- Hyundai and Kia are recalling nearly 3.4 million vehicles in the U.S. and telling owners to park them outside due to the risk of engine compartment fires. The recalls cover multiple car and SUV models from the 2010...}

\entryitemWithDescription{\hskip 0pt{}Three astronauts return to Earth after a year in space. NASA's Frank Rubio sets US space record}{https://apnews.com/article/7826312581aa71a969781fbbb2dd9435}{A NASA astronaut and two Russian cosmonauts returned to Earth on Wednesday after being stuck in space for just over a year. American Frank Rubio set a record for the longest U.S. spaceflight --- a result of the extended stay. The trio...}

\entryitemWithDescription{\hskip 0pt{}Giant panda Fan Xing leaves a Dutch zoo for her home country China}{https://apnews.com/article/9711f2f8bca3c115946347c4b7144400}{RHENEN, Netherlands (AP) --- Giant panda Fan Xing began a long journey home on Wednesday --- to a country she has never visited. The 3-year-old was given a ceremonial send off Wednesday from Ouwehands Zoo in the Netherlands, where she was...}

\entryitemWithDescription{\hskip 0pt{}Brooks Robinson, Orioles third baseman with 16 Gold Gloves, has died. He was 86}{https://apnews.com/article/6bbfb514ab91429db8aed53e8c17861d}{BALTIMORE (AP) --- Hall of Fame third baseman Brooks Robinson, whose deft glovework and folksy manner made him one of the most beloved and accomplished athletes in Baltimore history, has died. He was 86. The Orioles announced his death in...}

\entryitemWithDescription{\hskip 0pt{}Sophia Loren after leg-fracture surgery: `Thanks for all the affection, I'm better,' just need rest}{https://apnews.com/article/b290136ea53528ea7742e951a93cdb52}{ROME (AP) --- Sophia Loren is expressing gratitude for all the affection she received following surgery needed after the film star fractured a hip and thigh bone in a bathroom fall, her agent said Tuesday. Andrea Giusti quoted the...}

\entryitemWithDescription{\hskip 0pt{}Police are investigating if unprescribed drugs factored into death of ex-NFL player Mike Williams}{https://apnews.com/article/3a9c1ca31161e8c550b10b8943ef86da}{TAMPA, Fla. (AP) --- Police are investigating the death of former NFL player Mike Williams in Tampa after getting information that he may have received unprescribed drugs from someone while hospitalized after a construction site accident...}

\entryitemWithDescription{\hskip 0pt{}London's Gatwick Airport limits flights this week due to staff illness, including COVID-19}{https://apnews.com/article/c27a62e268b29c07c616a14b19afb5d8}{LONDON (AP) --- Gatwick Airport, London's second-busiest, is limiting flights this week, partly because of an outbreak of COVID-19 within air traffic control. In a statement late Monday, the airport said a daily 800-flight limit...}