\entryitemWithDescription{\hskip 0pt{}Florida's rejection of Black history course stirs debate}{https://apnews.com/article/6603c0aa4de0098423eb7b6c04846d0c}{FILE - Florida Gov. Ron DeSantis speaks at an annual leadership meeting of the Republican Jewish Coalition on Nov. 19, 2022, in Las Vegas. DeSantis reiterated Monday, Jan. 23, 2023, that the state\textquotesingle s rejection of a proposed...}

\entryitemWithDescription{\hskip 0pt{}Police: 2 students dead, adult hurt in Des Moines shooting}{https://apnews.com/article/20965fba395ba2a48b57cb37355e0ac7}{A law enforcement officer exits the Starts Right Here building, Monday, Jan. 23, 2023, in Des Moines, Iowa. Police say two students were killed and a teacher was injured in a shooting at the Des Moines school on the edge of the city...}

\entryitemWithDescription{\hskip 0pt{}Four Oath Keepers convicted of Jan. 6 seditious conspiracy}{https://apnews.com/article/2b9fb724c9839524d00ee389959e0e62}{FILE - Members of the Oath Keepers extremist group stand on the East Front of the U.S. Capitol on Jan. 6, 2021, in Washington. The Capitol riot was the culmination of weeks of preparation and a moment of triumph for the Oath Keepers...}

\entryitemWithDescription{\hskip 0pt{}In '20 Days in Mariupol' doc, the horrors of war illuminated}{https://apnews.com/article/4e40d392acb75d2020dcedef7c0992b3}{Director Mstyslav Chernov poses for a portrait to promote the film "20 Days in Mariupol" at the Latinx House during the Sundance Film Festival on Sunday, Jan. 22, 2023, in Park City, Utah. (Photo by Taylor Jewell/Invision/AP) Associated...}

\entryitemWithDescription{\hskip 0pt{}US proposes once-a-year COVID shots for most Americans}{https://apnews.com/article/cdd627b7daee5c2f7ebc984a3d9357db}{FILE - A nurse prepares a syringe of a COVID-19 vaccine at an inoculation station in Jackson, Miss., July 19, 2022. U.S. health officials are proposing a simplified approach to COVID-19 vaccinations, which would allow most adults and...}

\entryitemWithDescription{\hskip 0pt{}Man who propped feet on Pelosi desk guilty in Jan. 6 case}{https://apnews.com/article/1b438dad382b530e0aadc195c9b51492}{FILE - Richard Barnett, an Arkansas man who was photographed with his feet on a desk in former House Speaker Nancy Pelosi\textquotesingle s office during the Jan. 6 U.S. Capitol riot, arrives at federal court in Washington, Jan. 10, 2023...}

\entryitemWithDescription{\hskip 0pt{}Purdue back at No. 1 in AP Top 25, Alabama right behind}{https://apnews.com/article/785fbff2d7824e9baf0d137bf2e1ecd8}{Purdue center Zach Edey (15) shoots over Maryland forward Julian Reese (10) during the second half of an NCAA college basketball game in West Lafayette, Ind., Sunday, Jan. 22, 2023. Purdue defeated Maryland 58-55. (AP Photo/Michael...}

\entryitemWithDescription{\hskip 0pt{}US: Ex-FBI counterintelligence agent aided Russian oligarch}{https://apnews.com/article/62b7235c9d6b7cf11af41ffc16caa38e}{Charles McGonigal, former special agent in charge of the FBI\textquotesingle s counterintelligence division in New York, leaves court, Monday, Jan. 23, 2023, in New York. The former high-ranking FBI counterintelligence official has been...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk: Tweets about taking Tesla private weren't fraud}{https://apnews.com/article/dc203e6eefa40cb29db82d31308b372a}{In this courtroom sketch is Elon Musk, left, with shareholder attorney Nicholas Porritt appears in federal court in San Francisco, Monday, Jan. 23, 2023. Musk returned to court Monday, testifying that he believed he had locked up...}

\entryitemWithDescription{\hskip 0pt{}Scandals highlight lack of women coaches at top of US soccer}{https://apnews.com/article/9c34b95ea1004d92fb3cd6151cea3e4e}{FILE -Twila Kilgore, assistant coach on the U.S. team watches players warm up prior to a CONCACAF Women\textquotesingle s Championship soccer semifinal match against Costa Rica in Monterrey, Mexico, Thursday, July 14, 2022. Kilgore, is an...}

\entryitemWithDescription{\hskip 0pt{}Attorneys liken Tyre Nichols' arrest to Rodney King beating}{https://apnews.com/article/2ee34c06788c350f650f5fb5ce87134a}{RowVaugn Wells, mother of Tyre Nichols, who died after being beaten by Memphis police officers, calls out his name as she is comforted by Tyre\textquotesingle s stepfather Rodney Wells, at a news conference with civil rights Attorney Ben...}

\entryitemWithDescription{\hskip 0pt{}South Dakota tribe: Storm deaths 'could have been prevented'}{https://apnews.com/article/881af98309578627a6644c9a5b22865a}{A South Dakota state snow plow clears a shoulder along Highway 50 on the north edge of Yankton, S.D., on Thursday, Dec. 15, 2022, as light snow swept by strong winds reduced visibility to a quarter-mile at times. Yankton is about 200...}

\entryitemWithDescription{\hskip 0pt{}Is tipping getting out of control? Many consumers say yes}{https://apnews.com/article/c4ae9d440610dae5e8ff4d4df0f88c35}{X-Golf manager J.W. Park, left, helps Ashley Moreno to check out at X-Golf indoor golf in Glenview, Ill., Friday, Jan. 20, 2023. Tipping fatigue, it seems, is swarming America as more businesses adopt digital payment methods that...}