\entryitemWithDescription{\hskip 0pt{}From wine country to London, bank's failure shakes worldwide}{https://apnews.com/article/ec0148382edb344c27c0bdfdcbd3cf66}{Tech startups are facing serious financial trouble after the failure of Silicon Valley Bank. Regulators rushed Friday to seize the assets of the nation\textquotesingle s 16th largest bank after depositors rushed to withdraw their money...}

\entryitemWithDescription{\hskip 0pt{}Jehovah's Witnesses shocked by Hamburg attack, thank police}{https://apnews.com/article/7de0ba9bc8dfb3475bbf29fd42f3d066}{Investigators and forensic experts stand outside a Jehovah\textquotesingle s Witness building in Hamburg, Germany Friday, March 10, 2023. Shots were fired inside the building used by Jehovah\textquotesingle s Witnesses in the northern...}

\entryitemWithDescription{\hskip 0pt{}Burning eyes, dead fish; red tide flares up on Florida coast}{https://apnews.com/article/842c0576451b2a007d57abd44448e03e}{Red tide is observed near Pinellas County beaches off Redington Beach, Fla., during a flight with SouthWings volunteers on Friday, March 10, 2023. Florida\textquotesingle s southwest coast experienced a flare-up of the toxic red tide...}

\entryitemWithDescription{\hskip 0pt{}Bud Grant, stoic coach of powerful Vikings teams, dies at 95}{https://apnews.com/article/cb2e284ca0b811ed9b143c219cee77e8}{Former Minnesota Vikings Hall of Fame coach Bud Grant waves a final goodbye to the Metrodome during ceremonies following the Vikings NFL football against the Detroit Lions, Sunday, Dec. 29, 2013, in Minneapolis. Grant, the stoic and...}

\entryitemWithDescription{\hskip 0pt{}Relentless winter brings pros, cons for Tahoe ski resorts}{https://apnews.com/article/230c1bedc486c16012f156c46f09e9de}{FILE -This photo provided by Palisades Tahoe shows a freshly covered snowfall on a ski run at Palisades Tahoe ski resort in Olympic Valley, Calif., on Wednesday, March 1, 2023. (Blake Kessler/Palisades Tahoe via AP,File) RENO, Nev...}

\entryitemWithDescription{\hskip 0pt{}Oregon eyes mandate for climate change lessons in schools}{https://apnews.com/article/376bed4c1b916bcf038ca9e89302401e}{Sarah Stapleton, a University of Oregon education professor, holds drawings and letters from elementary school students asking lawmakers to stop climate change, after testifying at a hearing at the Oregon State Capitol in Salem, Ore...}

\entryitemWithDescription{\hskip 0pt{}Storm breaches California river's levee, thousands evacuate}{https://apnews.com/article/2677c9eeb138f2a672a2596ef4b1563e}{More than 9,000 California residents were under evacuation orders Friday as a new atmospheric river brought heavy rain, thunderstorms and strong winds, swelling rivers and creeks and flooding several major highways during the morning...}

\entryitemWithDescription{\hskip 0pt{}Americans' fun road trip to Mexico became days of horror}{https://apnews.com/article/791fec6c16d14303ea29af4bf1f86536}{Today would have been Shaeed Woodard's 34th birthday, according to his father, James Woodard. (March 9) Motorists pay a bridge toll at Gateway International Bridge on Monday, March 6, 2023, in Brownsville, Texas, to cross into Matamoros...}

\entryitemWithDescription{\hskip 0pt{}Oscars race: Clock ticks for buffs to binge nominated films}{https://apnews.com/article/fb330e478a67c7571efe5fe8d2352e36}{Workers prepare a backdrop during preparations for Sunday\textquotesingle s 95th Academy Awards, Friday, March 10, 2023, in Los Angeles. (AP Photo/Ashley Landis) NEW YORK (AP) --- A film buff from Oklahoma City, Elyssa Mann has scant time...}

\entryitemWithDescription{\hskip 0pt{}Italy's coast guard, navy, bring hundreds of migrants ashore}{https://apnews.com/article/f564a4d859d6c8dda2d711f916d149a0}{Police check a fishing boat with some 500 migrants in the southern Italian port of Crotone, early Saturday, March 11, 2023. The Italian coast guard was responding to three smugglers boats carrying more than 1,300 migrants ``in danger''...}

\entryitemWithDescription{\hskip 0pt{}Aches, rashes and fear: Trauma remains after Ohio derailment}{https://apnews.com/article/fc68b402096a4f5f8598a657f7e399f8}{Heather Bable and her son Ashton poses for a photograph, Feb. 25, 2023 at Sprinklz On Top restaurant in East Palestine, Ohio. Bable and her children live less than a half-mile from where a train derailed in a fiery crash Feb. 3, forcing...}

\entryitemWithDescription{\hskip 0pt{}'It's hard to focus': Schools say American kids are hungry}{https://apnews.com/article/7d38b5a84e533129f507d76cc05c622f}{Students select their meal during lunch break in the cafeteria at V. H. Lassen Academy of Science and Nutrition in Phoenix, Tuesday, Jan. 31, 2023. (AP Photo/Alberto Mariani) PHOENIX (AP) --- America\textquotesingle s schools say kids are...}

\entryitemWithDescription{\hskip 0pt{}Will it take market crash for Congress to raise debt limit?}{https://apnews.com/article/d3457c2b464e826bb7672f7f8a2707fd}{FILE - President Joe Biden speaks about the February jobs report from the Roosevelt Room of the White House, March 10, 2023, in Washington. Republicans and Democrats have been dancing around each other about the need to raise the...}