\entryitemWithDescription{\hskip 0pt{}WWE's `Raw' is moving to Netflix next year in a major streaming deal worth more than \$5 billion}{https://apnews.com/article/9d7a05167e338aeb54035a9ae2868f5c}{WWE's weekly television show ``Raw'' will move to Netflix next year as part of a major streaming deal worth more than \$5 billion. TKO Group Holdings Inc., which houses WWE and UFC, said in a regulatory filing on Tuesday that the...}

\entryitemWithDescription{\hskip 0pt{}United Airlines CEO says the airline will consider alternatives to Boeing's next airplane}{https://apnews.com/article/4090ea6176ef59e382dd18e9522596bc}{The United Airlines CEO says he is ``disappointed'' in ongoing manufacturing problems at Boeing that have led to the grounding of dozens of United jetliners, and the airline will consider alternatives to buying a future, larger version of...}

\entryitemWithDescription{\hskip 0pt{}Dwayne `The Rock' Johnson gets rights to one of the most famous nicknames in entertainment, his own}{https://apnews.com/article/2baf0b666a334f01dce42b4e2d08e148}{It is a name that has become almost synonymous with professional wrestling but its bearer, Dwayne Johnson, has never legally owned ``The Rock.'' That will change under a new agreement with the WWE under which Johnson will also join the...}

\entryitemWithDescription{\hskip 0pt{}Madrid to host F1 race from 2026. New track could have banked turn and indoor section}{https://apnews.com/article/f4c3e7dc190aeb4cd180ab66080796a6}{MADRID (AP) --- Formula One will return to Madrid after 45 years when the city stages a grand prix from 2026 on a track including street and non-street sections. F1 president Stefano Domenicali was in Madrid for the official announcement...}

\entryitemWithDescription{\hskip 0pt{}Chinese state media say 20 people dead and 24 missing after landslide}{https://apnews.com/article/05ca69c9b3aa567ad58f57a6918cd7d2}{BEIJING (AP) --- Twenty people are confirmed dead and 24 remain missing after a landslide in a remote, mountainous part of China's southwestern province of Yunnan, Chinese state media reported Tuesday. The disaster struck just before 6 a...}

\entryitemWithDescription{\hskip 0pt{}Woman charged with killing Hollywood consultant Michael Latt pleads not guilty}{https://apnews.com/article/12547e7bb21f80a9e5d8c87952c97216}{LOS ANGELES (AP) --- A woman charged with killing a high-profile marketing consultant and social justice advocate in film pleaded not guilty Monday. Jameelah Elena Michl, 36, entered the plea in Los Angeles Superior Court to charges of...}

\entryitemWithDescription{\hskip 0pt{}Norman Jewison, acclaimed director of `In the Heat of the Night' and `Moonstruck,' dead at 97}{https://apnews.com/article/abd93f2b671b416aabdd83829822e14a}{NEW YORK (AP) --- Norman Jewison, the acclaimed and versatile Canadian-born director whose Hollywood films ranged from Doris Day comedies and ``Moonstruck'' to such social dramas as the Oscar-winning ``In the Heat of the Night,'' has died...}

\entryitemWithDescription{\hskip 0pt{}Hall of Fame second baseman Ryne Sandberg says he has metastatic prostate cancer}{https://apnews.com/article/2a93ba13027274b08dfe52379c2c9ee7}{CHICAGO (AP) --- Hall of Fame second baseman Ryne Sandberg has been diagnosed with metastatic prostate cancer. The 64-year-old Sandberg said Monday in a release put out by the Baseball Hall of Fame that he has started treatment. ``I am...}

\entryitemWithDescription{\hskip 0pt{}Dexter Scott King, son of the Rev. Martin Luther King Jr., dies of cancer at 62}{https://apnews.com/article/4ac3c27382771b0ff26cd340918f5a16}{ATLANTA (AP) --- Dexter Scott King, who dedicated much of his life to shepherding the civil rights legacy of his parents, the Rev. Martin Luther King Jr. and Coretta Scott King, died Monday after battling prostate cancer. He was 62. The...}

\entryitemWithDescription{\hskip 0pt{}Dior and Schiaparelli bring historical reverence to Haute Couture Week in Paris}{https://apnews.com/article/ef31847879cb65abad54809db20bea3d}{PARIS (AP) --- Dior's couture show at Paris' Musee Rodin wove an intricate Ottoman tapestry for spring and attracted a tapestry of stars to rival it Monday. Rihanna, Natalie Portman, Elizabeth Debicki, Ali Wong, Felicity Jones, Glenn...}

\entryitemWithDescription{\hskip 0pt{}Elon Musk visits Auschwitz after uproar over antisemitic messages on X}{https://apnews.com/article/64de614f79ab70de0c9f2ac8d509168e}{KRAKOW, Poland (AP) --- Elon Musk, who has been accused of allowing antisemitic messages on his social media platform, X, visited the site of the Auschwitz-Birkenau death camp on Monday, saying afterwards that the tragedy of the...}

\entryitemWithDescription{\hskip 0pt{}Protester throws papers on court, briefly disrupts Australian Open match between Zverev and Norrie}{https://apnews.com/article/0c4c493aa69faab3ffd8ad2c7f336a2f}{MELBOURNE, Australia (AP) --- A pro-Palestinian protester threw papers onto an Australian Open court and briefly disrupted a match between Alexander Zverev and Cameron Norrie on Monday before being stopped by other spectators. Olympic...}

\entryitemWithDescription{\hskip 0pt{}Jared Goff throws 2 TD passes, Lions advance to NFC title game with 31-23 win over Buccaneers}{https://apnews.com/article/ce78432d1b23d96ab7552efc1ab8c56a}{DETROIT (AP) --- Jared Goff is good enough for Detroit, as his coach recently reminded him. Cast away by the Los Angeles Rams three years ago in a trade for Matthew Stafford, the quarterback was welcomed by the Lions and has since become...}