\entryitemWithDescription{\hskip 0pt{}Photographer alleges he was forced to watch Megan Thee Stallion have sex and was unfairly fired}{https://apnews.com/article/56fa11e5c1e7423086fd2f0660d1b391}{LOS ANGELES (AP) --- A photographer who worked for Megan Thee Stallion said in a lawsuit filed Tuesday that he was forced to watch her have sex, was unfairly fired soon after and was abused as her employee. In the suit filed in Los...}

\entryitemWithDescription{\hskip 0pt{}Alligator on runway at MacDill Air Force Base in Florida captured, released into nearby river}{https://apnews.com/article/d7ef350f6baab46bf9e4a54d5554fbc2}{TAMPA, Fla. (AP) --- A large alligator made its way onto the runway at MacDill Air Force Base in Florida where it had to be captured and taken away for release in a nearby river, officials said. The toothy reptile was spotted Monday...}

\entryitemWithDescription{\hskip 0pt{}Crew members injured in crash on Georgia set of Eddie Murphy Amazon MGM movie `The Pickup'}{https://apnews.com/article/9bc583f5c0eb75875e31712b1c9b5ed9}{Several crew members were injured and two were hospitalized when a car and truck collided during shooting of the Eddie Murphy film ``The Pickup'' from Amazon MGM Studios, the studio and a person close to the production said Tuesday. A...}

\entryitemWithDescription{\hskip 0pt{}Phish fans are famously dedicated. What happens when they enter the Sphere?}{https://apnews.com/article/59dacda9ed6e26b37df86c69a33e67ff}{LAS VEGAS (AP) --- Adele, Mariah Carey and Garth Brooks tower over the Las Vegas Strip, peering out from billboards advertising their various casino residencies. But the 20,000 fans marching toward the glowing Sphere last week were there...}

\entryitemWithDescription{\hskip 0pt{}Nikola Jokic's brother reportedly involved in an altercation after the Nuggets beat the Lakers}{https://apnews.com/article/5996b1a3b158bf9f476f6553dbe7e124}{DENVER (AP) --- The NBA and Denver police are looking into an incident in which a man reported to be one of the brothers of Denver Nuggets star Nikola Jokic was seen punching a fan after the team's buzzer-beating 101-99 victory over the...}

\entryitemWithDescription{\hskip 0pt{}Martian skies over Athens? Greece's capital turns an orange hue with dust clouds from North Africa}{https://apnews.com/article/3593a433a6e630fe3fb8ed278134837a}{ATHENS, Greece (AP) --- Skies over southern Greece turned an orange hue on Tuesday as dust clouds blown across the Mediterranean Sea from North Africa engulfed the Acropolis and other Athens landmarks. Strong southerly winds carried the...}

\entryitemWithDescription{\hskip 0pt{}UnitedHealth says wide swath of patient files may have been taken in Change cyberattack}{https://apnews.com/article/50e7e86ace92e95711dfbf8914d27db1}{UnitedHealth says files with personal information that could cover a ``substantial portion of people in America'' may have been taken in the cyberattack earlier this year on its Change Healthcare business. The company said Monday after...}

\entryitemWithDescription{\hskip 0pt{}Murder charges filed against woman who crashed into building hosting birthday party, killing 2 kids}{https://apnews.com/article/6d90ff4a6382a1738f79a03c8b9adfb0}{BERLIN TOWNSHIP, Mich. (AP) --- A Michigan woman was charged Tuesday with second-degree murder and other crimes after prosecutors say she drunkenly smashed her SUV into a boat club that was hosting a birthday party, killing two young...}

\entryitemWithDescription{\hskip 0pt{}Aboriginal spears taken by Captain Cook in 1770 are returned to Australia's Indigenous people}{https://apnews.com/article/a4e9406e64b991eb1d916b4598e28033}{LONDON (AP) --- Four Aboriginal spears that were taken to England by Captain James Cook more than 250 years ago were returned Tuesday to Australia's Indigenous community at a ceremony in Cambridge University. The artifacts were all that...}

\entryitemWithDescription{\hskip 0pt{}Wall Street is looking to Tesla's earnings for clues to Musk's plan to restore company's wild growth}{https://apnews.com/article/b60696cb69d7735983abcf51aee7f743}{Faced with falling global sales and a diving stock price, Tesla has slashed prices again on some of its electric vehicles and its ``Full Self Driving'' system in an apparent effort to boost the company's earnings growth. But Wall Street...}

\entryitemWithDescription{\hskip 0pt{}LeBron James rants at NBA's replay center for calls, Lakers lose on buzzer-beater, trail Denver 2-0}{https://apnews.com/article/852aa29e2f83f98414c806ec203af643}{DENVER (AP) --- LeBron James was seeing red after the Los Angeles Lakers watched a golden opportunity slip away. His frustration wasn't so much centered on blowing a 20-point lead. Or his late missed 3-pointer that rimmed out with the...}

\entryitemWithDescription{\hskip 0pt{}America's child care crisis is holding back moms without college degrees}{https://apnews.com/article/ac72f1227844eae0281305835e07273b}{AUBURN, Wash. (AP) --- After a series of lower-paying jobs, Nicole Slemp finally landed one she loved. She was a secretary for Washington's child services department, a job that came with her own cubicle, and she had a knack for working...}

\entryitemWithDescription{\hskip 0pt{}Chicago Bears schedule a Wednesday announcement on new stadium near lakefront}{https://apnews.com/article/2aa8066e7cc2b5894b661681911be10a}{CHICAGO (AP) --- The Chicago Bears have scheduled a Wednesday news conference to announce plans for ``a state-of-the-art, publicly owned enclosed stadium'' on the city's Museum Campus near Lake Michigan. The announcement Monday said the...}