\entryitemWithDescription{\hskip 0pt{}2 women charged in Lululemon shoplifting scheme in Minneapolis}{https://apnews.com/article/5d66d6ed4f517eb1e5c3c0ab984bfd4d}{MINNEAPOLIS (AP) --- Two Minnesota women are charged with organizing thefts of several thousand dollars' worth of merchandise from a Lululemon store in Minneapolis and then funneling the stolen goods through a suburban nail salon. My...}

\entryitemWithDescription{\hskip 0pt{}NASA cuts 2 from next SpaceX flight to make room for astronauts stuck at space station}{https://apnews.com/article/6c2db96fa6c6859a48a8c26438fab1d5}{NASA on Friday cut two astronauts from the next crew to make room on the return trip for the two stuck at the International Space Station. NASA's Nick Hague and Russian Aleksandr Gorbunov will launch in September aboard a SpaceX rocket...}

\entryitemWithDescription{\hskip 0pt{}Neighbor held in disappearance of couple from California nudist resort. Both believed to be dead}{https://apnews.com/article/465c6f180aef2f103967bf97da728193}{REDLANDS, Calif. (AP) --- A next-door neighbor was arrested in connection with the disappearance of a couple from their home at a Southern California nudist resort, police said Friday. Investigators have reason to believe the couple are...}

\entryitemWithDescription{\hskip 0pt{}`Dancing With the Stars' pro Artem Chigvintsev arrested on domestic violence charge in California}{https://apnews.com/article/9447fbe21daa2bbd3f8ff5ce453e201f}{YOUNTVILLE, Calif. (AP) --- ``Dancing With the Stars'' pro Artem Chigvintsev was arrested Thursday and booked on a domestic violence charge in northern California, according to the local sheriff's office. When Napa County Sheriff's...}

\entryitemWithDescription{\hskip 0pt{}Man pleads guilty to killing Baltimore tech entrepreneur in attack that shocked the city}{https://apnews.com/article/9a7f890e86556c212f3e74e062b9b081}{BALTIMORE (AP) --- A man pleaded guilty Friday to killing Baltimore tech entrepreneur Pava LaPere last September in an apparently random attack that shocked the city. Jason Billingsley, 33, entered the guilty plea instead of going to...}

\entryitemWithDescription{\hskip 0pt{}Sheriff's office quickly dispels active shooter rumor at Disney World after fight and popping sound}{https://apnews.com/article/7fdb3d75210e9141b676391ea18d81a7}{ORLANDO, Fla. (AP) --- A fight at Disney World's Magic Kingdom Park and a ``popping'' sound caused a disruption among visitors and rumors of an active shooter that were quickly put to rest by the county sheriff's office. The Orange County...}

\entryitemWithDescription{\hskip 0pt{}She's a Norwegian princess. He's an American self-professed shaman. Their wedding is this weekend}{https://apnews.com/article/569029b62d419529ed5bb881a47a5216}{COPENHAGEN, Denmark (AP) --- The Norwegian king's eldest child, Princess Märtha Louise, will marry American self-professed shaman Durek Verret on Saturday in a picturesque corner of southern Norway. The wedding comes amid widespread...}

\entryitemWithDescription{\hskip 0pt{}Swiss city of Basel is chosen to host next year's Eurovision Song Contest}{https://apnews.com/article/d0e191d760f2a8ba7ac2a4b80f2da92b}{GENEVA (AP) --- The Swiss city of Basel will host next year's Eurovision Song Contest from May 13 to 17, organizers announced Friday. The mostly German-speaking city on the Rhine River was selected over Geneva in a faceoff that generated...}

\entryitemWithDescription{\hskip 0pt{}Taipei zoo's veteran giant panda Yuanyuan celebrates her 20th birthday}{https://apnews.com/article/9d34f6a06d0e0eaaae78257536bb8462}{TAIPEI, Taiwan (AP) --- With politics set aside, well-wishers gathered to wish the Taipei zoo's senior panda a happy 20th birthday. Visitors crowded around Yuanyuan's enclosure to take photos of her with a birthday cake in the shape of...}

\entryitemWithDescription{\hskip 0pt{}`K-pop Idols' documentary looks at how the K-pop industry is embracing diversity}{https://apnews.com/article/4c54e6df091d90a4bb8e12e5365928a1}{SEOUL, South Korea (AP) --- An Apple TV+ documentary series, ``K-pop Idols,'' premiering Friday, offers an intimate look at how the K-pop industry is embracing diversity while grappling with challenges in a field that demands perfection...}

\entryitemWithDescription{\hskip 0pt{}Hiker left on Colorado mountain by coworkers stranded overnight in freezing rain, high winds}{https://apnews.com/article/38e84ad5400be5e98de51c6eacd7afe9}{SALIDA, Colo. (AP) --- A man left by his group of office coworkers to complete his final push to the summit of a Colorado mountain became disoriented and fell multiple times during a night on the mountain in freezing rain and high winds...}

\entryitemWithDescription{\hskip 0pt{}Texas Attorney General Paxton sues to block gun ban at the sprawling State Fair of Texas}{https://apnews.com/article/7eedbf9ee55ea9c624e0db4e71dc0e4d}{DALLAS (AP) --- Texas Attorney General Ken Paxton filed a lawsuit Thursday seeking to block a ban on firearms at the State Fair of Texas, one of the state's biggest annual celebrations. Fair organizers earlier this month announced a ban...}

\entryitemWithDescription{\hskip 0pt{}NASA record holder can relate to astronauts stuck in space. He was, too}{https://apnews.com/article/91629ab00e5ccb5ede28898b876aaad8}{NASA's record-holding astronaut is urging his two stuck-in-space colleagues to stay positive and ``keep up the good work.'' Frank Rubio knows firsthand about unexpectedly long spaceflights. His own visit to the International Space Station...}