\entryitemWithDescription{\hskip 0pt{}AP source: Hamlin visits teammates for 1st time since injury}{https://apnews.com/article/4fc957f553133ad5c043849ea5c549a3}{FILE - Buffalo Bills safety Damar Hamlin (31) is shown before an NFL football game against the Tennessee Titans on Monday, Oct. 18, 2021, in Nashville, Tenn. Hamlin was released from a Buffalo hospital on Wednesday, Jan. 11, 2023, more...}

\entryitemWithDescription{\hskip 0pt{}India's 'RRR' an unlikely underdog in Hollywood awards race}{https://apnews.com/article/94ef645840556bd14a49f4b0f69e68a1}{Indian stars N.T. Rama Rao Jr. and Ram Charan hope hit movie "RRR" will help kickstart collaborations between Eastern and Western cinema. (Jan. 10) Indian actors N. T. Rama Rao Jr., left, and Ram Charan pose for a photo to promote their...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry: Memoir is about saving royals from themselves}{https://apnews.com/article/3a5ea1df04bc0ece960d7aaca469323c}{Copies of the new book by Prince Harry called "Spare" are displayed at a book store in Berlin, Germany, Tuesday, Jan. 10, 2023. Prince Harry\textquotesingle s memoir "Spare" went on sale in bookstores on Tuesday, providing a varied...}

\entryitemWithDescription{\hskip 0pt{}More classified documents found at Biden's home by lawyers}{https://apnews.com/article/0574fd762159e8cb5f31c85205df3dc0}{Attorney General Merrick Garland has appointed a special counsel to investigate the presence of documents with classified markings found at President Joe Biden's home in Wilmington, Delaware, and at an office in Washington. (Jan. 12...}

\entryitemWithDescription{\hskip 0pt{}Buttigieg finds himself in the spotlight for better or worse}{https://apnews.com/article/925daa37b03447be8c35299e4395fb64}{FILE - Transportation Secretary Pete Buttigieg, speaks to the Transportation Research Board gathering in Washington, Jan. 11, 2023. (AP Photo/Manuel Balce Ceneta, File) Transportation Secretary Pete Buttigieg says "safety is going to be...}

\entryitemWithDescription{\hskip 0pt{}Lisa Marie carved her musical path as she bore Elvis' legacy}{https://apnews.com/article/71d8b763f38c75b389aab331d5cbe468}{FILE - Lisa Marie Presley performs during her Storm \& Grace tour on June 20, 2012, at the Bottom Lounge in Chicago. She was dubbed a ``rock princess,'' but Lisa Marie Presley staked her own musical claim as a singer-songwriter, allowing...}

\entryitemWithDescription{\hskip 0pt{}University: Student stabbed on bus because she is Asian}{https://apnews.com/article/a8fcd4c2a24a844522ec2b7aae0098f5}{This photo provided by Bloomington Police Department shows Billie Davis. Davis has been charged after an 18-year-old Indiana University student repeatedly was stabbed in the head on a public bus in an attack the school says was because...}

\entryitemWithDescription{\hskip 0pt{}Taliban ban on female aid workers poses big dilemma for US}{https://apnews.com/article/ec5ff004c809618030539ddd9c91bba1}{FILE - A Save the Children midwife provides Zarmina, 25, who is five months pregnant, with a pre-natal check-up in Jawzjan province in northern Afghanistan, Sunday, Oct. 2, 2022. (Save the Children via AP, File) WASHINGTON (AP) --- For an...}

\entryitemWithDescription{\hskip 0pt{}Thousands protest in Germany against coal mine expansion}{https://apnews.com/article/15d530f7c29d05d6f3b89e5eacd41d1d}{Police officers push back demonstrators on the edge of the opencast lignite mine Garzweiler at the village Luetzerath near Erkelenz, Germany, Saturday, Jan. 14, 2023. ( Oliver Berg/dpa via AP) ERKELENZ, Germany (AP) --- Thousands of...}

\entryitemWithDescription{\hskip 0pt{}Claim of mammoth bones brings treasure hunters to NYC river}{https://apnews.com/article/7658ee7e20ed3495a17b42727cee584c}{"Effie," the mummified remains of a baby woolly mammoth found in in Alaska in 1948 is on display at the American Museum of Natural History, Friday, Jan. 13, 2023, in New York. The 21,000-year-old specimen is a rare natural mummy, complete...}

\entryitemWithDescription{\hskip 0pt{}Vatican holds funeral for cardinal who decried Francis' rule}{https://apnews.com/article/c72b63862523139eb6352dc9fe12cf2f}{Cardinals and bishops pray during the funeral ceremony of Australian Cardinal George Pell in St. Peter\textquotesingle s Basilica at the Vatican, Saturday Jan. 14, 2023. Cardinal Pell died on Tuesday at a Rome hospital of heart...}

\entryitemWithDescription{\hskip 0pt{}China reports 60,000 COVID-related deaths, says peak passed}{https://apnews.com/article/425a5de577126b042d4eea915c174bc0}{Travelers wearing face masks walk toward the entrance of the Beijing Railway Station in Beijing, Saturday, Jan. 14, 2023. Millions of Chinese are expected to travel during the Lunar New Year holiday period this year. (AP Photo/Mark...}

\entryitemWithDescription{\hskip 0pt{}UK to supply tanks; Russian missiles hit across Ukraine}{https://apnews.com/article/401d8116d95d67e3afbe8de8eb8cf65a}{In this photo released by the Dnipro Regional Administration, smoke rises after a Russian rocket hit a multistory building leaving many people under debris in Dnipro, Ukraine, Saturday, Jan. 14, 2023. (Dnipro Regional Administration via...}
