\entryitemWithDescription{\hskip 0pt{}Judge dismisses attempted murder and other charges in state case against Paul Pelosi's attacker}{https://apnews.com/article/1d4d2c95d096a46a1184eca2f12eebe8}{SAN FRANCISCO (AP) --- A judge on Thursday dismissed several state charges against Paul Pelosi's attacker, who was convicted in federal court last month, based on the argument that the counts fall under double jeopardy, according to the...}

\entryitemWithDescription{\hskip 0pt{}`Wheel of Fortune': Vanna White bids an emotional goodbye to Pat Sajak}{https://apnews.com/article/75ba26b39b3a9fdef27c8d02f6669681}{LOS ANGELES (AP) --- Ahead of Pat Sajak's final episode as the host of ``Wheel of Fortune,'' Vanna White paid an emotional tribute to her co-host of more than 40 years. On Thursday's episode of the beloved game show, White honored Sajak's...}

\entryitemWithDescription{\hskip 0pt{}Giraffe's nibble turns into airborne safari adventure for Texas toddler}{https://apnews.com/article/7b93018cf80dfc348b9ebbb615ca48a4}{GLEN ROSE, Texas (AP) --- A Texas family got a brief scare when a nibble from a giraffe turned a 2-year-old's safari visit into an airborne adventure. Paisley Toten was in the bed of a pickup truck on June 1 when her family drove through...}

\entryitemWithDescription{\hskip 0pt{}Records expunged for St. Louis couple who waved guns at protesters. They want their guns back}{https://apnews.com/article/e078710c51815fd00db9ba21b987b5ef}{ST. LOUIS (AP) --- A judge has expunged the misdemeanor convictions of a St. Louis couple who waved guns at racial injustice protesters outside their mansion in 2020. Now they want their guns back. Attorneys Mark and Patricia McCloskey...}

\entryitemWithDescription{\hskip 0pt{}Dolly Parton plans for a musical on her life using her songs to land on Broadway in 2026}{https://apnews.com/article/52de99e2cb7e47cac2f49bf57ef8be54}{NEW YORK (AP) --- Broadway has had great success with ``Hello, Dolly.'' Now get ready for ``Hello, I'm Dolly.'' Dolly Parton is writing new songs to go along with some of her past hits and co-writing a stage story inspired by her life for...}

\entryitemWithDescription{\hskip 0pt{}US wins toss, elects to field against Pakistan in cricket's T20 World Cup}{https://apnews.com/article/e1d790f59816588d4e3780f04d71cc79}{GRAND PRAIRIE, Texas (AP) --- The United States won the toss and elected to field against Pakistan in their Group A game at the T20 World Cup on Thursday. The U.S. made a winning start to the tournament by beating Canada by seven wickets...}

\entryitemWithDescription{\hskip 0pt{}NTSB begins considering probable cause in a near-collision between FedEx and Southwest planes}{https://apnews.com/article/2171cddd3c38b762872b5919344d3a02}{Investigators said Thursday that an incoming FedEx cargo plane came within less than 200 feet of hitting a Southwest Airlines jet last year in Austin, Texas, after both were cleared to use the same runway. The FedEx co-pilot saw the...}

\entryitemWithDescription{\hskip 0pt{}SpaceX's mega rocket makes its fourth test flight from Texas}{https://apnews.com/article/81c9279f30ca98be1c01b84ceb895e90}{SpaceX's mega Starship rocket blasted off from Texas on Thursday, the fourth test flight for the spaceship that NASA and Elon Musk are counting on to get humanity to the moon and Mars. The world's largest and most powerful rocket...}

\entryitemWithDescription{\hskip 0pt{}Boeing's space capsule springs more helium leaks on its first test flight with astronauts}{https://apnews.com/article/fc55af012efeb32cbeaa4d264ab85e11}{CAPE CANAVERAL, Fla. (AP) --- Boeing's space capsule developed more leaks during its first test flight with astronauts as it closed in on the International Space Station on Thursday. The Starliner capsule already had one small helium leak...}

\entryitemWithDescription{\hskip 0pt{}Suzanne Collins is releasing a new 'Hunger Games' novel, 'Sunrise on the Reaping,' next year}{https://apnews.com/article/b30163b4707f4db55eb68513f197affc}{NEW YORK (AP) --- Inspired by an 18th century Scottish philosopher and the modern scourge of misinformation, Suzanne Collins is returning to the ravaged, post-apocalyptic land of Panem for a new ``The Hunger Games'' novel. Scholastic...}

\entryitemWithDescription{\hskip 0pt{}Opening arguments starting in class-action lawsuit against NFL by `Sunday Ticket' subscribers}{https://apnews.com/article/ab29c60b2cc7e05cafcaeafa7f7e285e}{LOS ANGELES (AP) --- Opening arguments were expected to begin Thursday in federal court in a class-action lawsuit filed by ``Sunday Ticket'' subscribers claiming the NFL broke antitrust laws. The lawsuit was filed in 2015 and has...}

\entryitemWithDescription{\hskip 0pt{}Man in Mexico died of a bird flu strain that hadn't been confirmed before in a human, WHO says}{https://apnews.com/article/54bcefacdc1fe4a35298d3577c64cb7d}{WASHINGTON (AP) --- A man's death in Mexico was caused by a strain of bird flu called H5N2 that has never before been found in a human, the World Health Organization said Wednesday. The WHO said it wasn't clear how the man became...}

\entryitemWithDescription{\hskip 0pt{}FDA advisers urge targeting JN.1 strain in recipe for fall's COVID vaccines}{https://apnews.com/article/72c2c5fafc46ccc9f2fd89fcda5d99df}{WASHINGTON (AP) --- Government advisers Wednesday said it's time to update the recipe for the COVID-19 vaccines Americans will receive in the fall -\/- targeting a version of the ever-evolving coronavirus called JN.1. While COVID-19 cases...}