\entryitemWithDescription{\hskip 0pt{}Man agrees to plead guilty in Basquiat artwork fraud scheme}{https://apnews.com/article/a70f798c427aed5df958fecc6046b03f}{LOS ANGELES (AP) --- A former Los Angeles auctioneer has agreed to plead guilty in a cross-country art fraud scheme where he created fake artwork and falsely attributed the paintings to artist Jean-Michel Basquiat, federal prosecutors...}

\entryitemWithDescription{\hskip 0pt{}3 hurt in floor collapse in Savannah's 1899 US courthouse}{https://apnews.com/article/a958f9e611914feda86bf36d9e33f3d2}{A firetruck sits outside the historic federal courthouse on Tuesday, April 11, 2023, in Savannah, Ga., after part of an upper floor collapsed and injured three construction workers. The U.S. government building, which dates to 1899, has...}

\entryitemWithDescription{\hskip 0pt{}To fight cancer, EPA wants sterilizer companies to emit less}{https://apnews.com/article/6a17e10fea4c1f01a73968b2a4d84c0b}{FILE - A syringe is prepared at a clinic in Norristown, Pa., Dec. 7, 2021. The Environmental Protection Agency proposed Tuesday, April 11, 2023, to limit the use of the chemical ethylene oxide after finding higher than expected cancer...}

\entryitemWithDescription{\hskip 0pt{}Virginia Rep. Jennifer Wexton reveals Parkinson's diagnosis}{https://apnews.com/article/823e9ee7ca2691a8ed1ab624a6a463ab}{FILE - Rep. Jennifer Wexton, D-Va, speaks with reporters on Oct. 20, 2022, in Leesburg, Va. Wexton announced Tuesday, April 11, 2023, she has been diagnosed with Parkinson\textquotesingle s disease. She is vowing to continue her work in...}

\entryitemWithDescription{\hskip 0pt{}Natalie Merchant emerges from darkness with nothing but love}{https://apnews.com/article/36d33936e3b84e4e4a6979a82e5fed1a}{FILE - Natalie Merchant performs at Cyndi Lauper\textquotesingle s 8th Annual "Home for the Holidays" benefit concert in New York on Dec. 8, 2018. Merchant\textquotesingle s latest album, "Keep Your Courage," releases on Friday. (Photo by...}

\entryitemWithDescription{\hskip 0pt{}Florida fight over 'baby boxes' part of bigger culture war}{https://apnews.com/article/7a6dd3598f9c8a37be5c913572abdd62}{FILE --- Monica Kelsey and the town of Woodburn, Ind., dedicated the first Safe Haven Baby Box of its kind on April 26, 2016, at the Woodburn Volunteer Fire Department. A fight is developing in Florida\textquotesingle s legislature over a...}

\entryitemWithDescription{\hskip 0pt{}Germany launches plan to relax rigid family name system}{https://apnews.com/article/048ac6153e26c2c70311eec01cf27dbc}{FILE -\/- This June 14, 2008 file photo shows a family walking through the fields in the village of Gaiberg, near Heidelberg, southwestern Germany. Germany's justice minister has launched plans to relax the country's strict restrictions...}

\entryitemWithDescription{\hskip 0pt{}When planting a meadow, heed conditions in your garden, yard}{https://apnews.com/article/825223ef71709a22ac34a2c11caecd8d}{This image provided by American Meadows Inc. shows a lush wildflower meadow growing in place of a residential lawn. (American Meadows Inc. via AP) Wildflower meadows have been growing in popularity among gardeners, and for good reason...}

\entryitemWithDescription{\hskip 0pt{}Volcano eruption in Russia's Kamchatka spews vast ash clouds}{https://apnews.com/article/bd7c09dfd583d2461e537ecae113936d}{Smoke and ash are visible during the the Shiveluch volcano\textquotesingle s eruption on the Kamchatka Peninsula in Russia, Tuesday, April 11, 2023. Shiveluch, one of Russia\textquotesingle s most active volcanoes, erupted Tuesday...}

\entryitemWithDescription{\hskip 0pt{}Colombian convicted for racism directed at nation's Black VP}{https://apnews.com/article/6716a605869dce0cbec9be34f92bcb3e}{BOGOTA, Colombia (AP) --- A 62-year-old woman was convicted of discrimination and harassment on Monday for making racist comments about Colombia\textquotesingle s first Black vice president during an antigovernment protest last year. Luz...}

\entryitemWithDescription{\hskip 0pt{}Biden ends COVID national emergency after Congress acts}{https://apnews.com/article/e3a52722b57a6b4f24187426c27b3b39}{FILE - President Joe Biden speaks during a meeting with the President\textquotesingle s Council of Advisors on Science and Technology in the State Dining Room of the White House on April 4, 2023, in Washington. The U.S. national emergency...}

\entryitemWithDescription{\hskip 0pt{}Al Jaffee, longtime Mad magazine cartoonist, dead at 102}{https://apnews.com/article/f676fbeb190b44c8aa4abcb0daa5d571}{FILE - Mad Magazine cartoonist Al Jaffee attends an event to honor veteran contributors of MAD Magazine at the Savannah College of Art and Design and the National Cartoonists Society on Oct. 11, 2011 in Savannah, Ga. Jaffee died Monday at...}

\entryitemWithDescription{\hskip 0pt{}Mexican ballad singer Julián Figueroa dies at 27}{https://apnews.com/article/7305055b1a1dee97ce62aef94427b4fd}{FILE - Mexican musician and actor Julian Figueroa, the son of Mexican ballad singer Joan Sebastian and singer Maribel Guardia, stands amongst guests during his father\textquotesingle s wake at their home in Teacalco, Mexico, July 14...}