\entryitemAp{\hskip 0pt{}Elon Musk takes witness stand to defend Tesla buyout tweets}{https://apnews.com/article/506e98a2f98fb10e9a6477befdaa9627}{Documents related to the class-action lawsuit on behalf of investors who owned Tesla stock in August 2018 are carried toward a federal courthouse in San Francisco, Friday, Jan. 20, 2023. (AP Photo/Jeff Chiu) SAN FRANCISCO (AP) --- Elon...}

\entryitemAp{\hskip 0pt{}Prosecutors seek justice in Baldwin case, regardless of fame}{https://apnews.com/article/f4f2e9d7c407e2b7d21e9c2f70cb7293}{FILE - This aerial photo shows the Bonanza Creek Ranch in Santa Fe, N.M., on Saturday, Oct. 23, 2021. A Santa Fe district attorney is prepared to announce whether to press charges in the fatal 2021 film-set shooting of a cinematographer...}

\entryitemAp{\hskip 0pt{}Chris Hipkins to be New Zealand's next prime minister}{https://apnews.com/article/4b73db6d84e5e2e9b0875889cc462065}{FILE - New Zealand\textquotesingle s COVID-19 Response Minister Chris Hipkins speaks during a press conference in Wellington, New Zealand on Oct. 28, 2021. Education Minister Chris Hipkins is set to become New Zealand\textquotesingle s...}

\entryitemAp{\hskip 0pt{}Rare attack in Alaska renews interest in polar bear patrols}{https://apnews.com/article/1b9b5745eb5f9b2b273588f019336e24}{FILE - In this June 15, 2014, file photo released by the U.S. Geological Survey, a polar bear dries off after taking a swim in the Chukchi Sea in Alaska. A polar bear has attacked and killed two people in a remote village in western...}

\entryitemAp{\hskip 0pt{}Prosecutor suspended by DeSantis loses bid to get job back}{https://apnews.com/article/80eb877b3db82e831dd16ea4059b5ae5}{Former State Attorney Andrew Warren speaks during a news conference Friday, Jan. 20, 2023 in Tampa. A federal judge ruled Friday that Florida Gov. Ron DeSantis violated the First Amendment and the Florida Constitution by removing Warren...}

\entryitemAp{\hskip 0pt{}3 active-duty Marines charged in Jan. 6 Capitol riot}{https://apnews.com/article/8fc62a5cb27f91b0f9c9447052ffa25d}{FILE - Insurrectionists loyal to President Donald Trump try to open a door of the U.S. Capitol as they riot in Washington, Jan. 6, 2021. Three active-duty Marines have been charged in the riot at the U.S. Capitol. Court records show that...}

\entryitemAp{\hskip 0pt{}Historic Black churches receive \$4M in preservation grants}{https://apnews.com/article/886d6003ec5d939c6fd5f6ce758810c2}{A rusted fence surrounds the Varick Memorial AME Zion Church, Thursday, Jan. 19, 2023, in the Brooklyn borough of New York. On Friday, a fund established to preserve historic Black churches in the United States formally revealed the first...}

\entryitemAp{\hskip 0pt{}Tech industry job cuts come rapidly and in big numbers}{https://apnews.com/article/5012d95678b50f699498cb11b5f3913d}{Operarios montan un cartel publicitario de Google en el Centro de Convenciones de Las Vegas antes de la feria tecnológica CES, el 2 de enero de 2023, en Las Vegas. (AP Foto/John Locher) In just the past month there have been nearly 50,000...}

\entryitemAp{\hskip 0pt{}In soaked California, few homeowners have flood insurance}{https://apnews.com/article/b71eadd83be6176d45f7a1baf7bb2576}{FILE - Brenda Ortega, 15, salvages items from her flooded Merced, Calif., home on Tuesday, Jan. 10, 2023. In California, only about 230,000 homes and other buildings have flood insurance policies, which are separate from homeowners...}

\entryitemAp{\hskip 0pt{}Here's what to expect from Tuesday's Oscar nominations}{https://apnews.com/article/c8177c672de869f0a316d32c65b4f8dc}{This image released by Paramount Pictures shows Tom Cruise portraying Capt. Pete "Maverick" Mitchell in a scene from "Top Gun: Maverick." (Scott Garfield/Paramount Pictures via AP) When Oscar nominations are announced Tuesday, popcorn...}

\entryitemAp{\hskip 0pt{}Romanian judge grants 30-day extension of Tate detention}{https://apnews.com/article/b09236fcae9f60b0fae663488356f6e1}{FILE - Andrew Tate leaves the Court of Appeal, in Bucharest, Romania, Tuesday, Jan. 10, 2023. A Romanian official says a judge in Romania has granted prosecutors another request to extend by 30 days the arrest of Andrew Tate it was...}

\entryitemAp{\hskip 0pt{}Google axes 12,000 jobs as layoffs spread across tech sector}{https://apnews.com/article/c85c45231712709582b1d3fe46be5ffe}{FILE - The logo of Google is displayed on a carpet at the entrance hall of Google France in Paris, on Nov. 18, 2019. Google said Friday, jan. 20, 2023, it's laying off 12,000 workers, becoming the latest tech company to trim staff after...}

\entryitemAp{\hskip 0pt{}Church of England apologizes for treatment of LGBTQ people}{https://apnews.com/article/f645680c8cecd031bbcfdde9cc0c3628}{LONDON (AP) --- The Church of England formally apologized Friday for its treatment of LGBTQ people, even as it said that same-sex couples still won\textquotesingle t be allowed to marry in its churches. The apology from the church...}