\entryitemWithDescription{\hskip 0pt{}New quake hits battered Turkey, Syria; 3 dead, hundreds hurt}{https://apnews.com/article/c06d3009207b71df8a8792d4a68296a2}{A soldier carries a man after being injured in the latest earthquake in Hatay, Turkey, Monday, Feb. 20, 2023. A new 6.4 magnitude earthquake on Monday killed three people and injured more than 200 in parts of Turkey that were laid waste...}

\entryitemWithDescription{\hskip 0pt{}5-year firearms enhancement dropped in Baldwin shooting case}{https://apnews.com/article/e9391bd29426e8ffb839c031517d59e7}{FILE - Actor Alec Baldwin attends a news conference at United Nations headquarters, on Sept. 21, 2015. Prosecutors have dropped the possibility of a sentence enhancement that could have carried a mandatory five-year sentence against...}

\entryitemWithDescription{\hskip 0pt{}Students, faculty return to Michigan State after shooting}{https://apnews.com/article/28ed329e46379f9ac54847b9ecae72bc}{Michigan State international students Dheeraj Thota, left, and Chirag Bhansari, both freshman studying computer science, found a single rose on their walk to class as campus opens back up for the first day of classes on Monday, Feb. 20...}

\entryitemWithDescription{\hskip 0pt{}Arrest made in killing of Catholic bishop in California}{https://apnews.com/article/66c3d690faebae98f272b3ae775b9fd5}{FILE - Bishop David O\textquotesingle Connell, of the Archdiocese of Los Angeles, attends a news conference at the Fall General Assembly meeting of the United States Conference of Catholic Bishops, on Nov. 17, 2021, in Baltimore. O...}

\entryitemWithDescription{\hskip 0pt{}Major league teams searching for advantages with new rules}{https://apnews.com/article/a0ff698a43baaddf84bc69a5b0cbc828}{The new, larger base sits next to the older, smaller base at TD Ballpark Wednesday, Feb. 15, 2023, in Dunedin, Fla. Opening day will feature three of the biggest changes in baseball since 1969: Two infielders will be required to be on...}

\entryitemWithDescription{\hskip 0pt{}Brazil deluge kills 36; search continues for dozens missing}{https://apnews.com/article/386188b8810a057d300bf911599d660a}{Brazilian authorities said at least 26 people died in two cities in north Sao Paulo state amid floods and landslides, and the number could rise (Feb. 20) Rescue workers search for survivors after flooding triggered deadly landslides near...}

\entryitemWithDescription{\hskip 0pt{}FDA's own reputation could be restraining its misinfo fight}{https://apnews.com/article/8f8a388720f1ec51b46730eb7828f9d1}{FILE - Food and Drug Administration Commissioner Robert Califf testifies via video during a House Commerce Oversight and Investigations subcommittee hybrid hearing on the nationwide baby formula shortage on Wednesday, May 25, 2022, in...}

\entryitemWithDescription{\hskip 0pt{}For poor schools, building repairs zap COVID relief money}{https://apnews.com/article/29ffa0a888d3a62d7cd0e72a63c18c59}{Jim Hill High School principal Bobby Brown, points out one of the outdated air-condition units that are installed throughout the Jackson, Miss., school, Jan. 12, 2023. A litany of infrastructure issues in the nearly 60-year-old school...}

\entryitemWithDescription{\hskip 0pt{}Seattle considers historic law barring caste discrimination}{https://apnews.com/article/49843c779c8f3d60720bc1e2c71a952a}{FILE - New Seattle City Councilmember Kshama Sawant speaks during an inauguration ceremony for city officials Monday, Jan. 6, 2014, in Seattle. One of Sawant's earliest memories of the caste system was hearing her grandfather -- a man...}

\entryitemWithDescription{\hskip 0pt{}Key developments in the aftermath of the Turkey, Syria quake}{https://apnews.com/article/8ce37276b676db5d011dd52e4de8cd0d}{Turkish President Recep Tayyip Erdogan, left, talks to U.S. Secretary of State Antony Blinken during their meeting at Esenboga airport in Ankara, Turkey, Monday, Feb. 20, 2023. (AP Photo/Burhan Ozbilici, Pool) ANKARA, Turkey (AP...}

\entryitemWithDescription{\hskip 0pt{}Celtics stars Tatum and Brown put on quite an All-Star show}{https://apnews.com/article/cdf10e6b1a6a17ccd6bd2354c6d19951}{Team Giannis forward Jayson Tatum (0) dunks during the second half of the NBA basketball All-Star game Sunday, Feb. 19, 2023, in Salt Lake City. (AP Photo/Rob Gray) SALT LAKE CITY (AP) --- Best record in the NBA. A team that won the...}

\entryitemWithDescription{\hskip 0pt{}Biden declares 'Kyiv stands' in surprise visit to Ukraine}{https://apnews.com/article/f00af220669457d5ba07127c7e57a27b}{US President Joe Biden, left, walks with Ukrainian President Volodymyr Zelenskyy at St. Michaels Golden-Domed Cathedral during an unannounced visit, in Kyiv, Ukraine, Monday, Feb. 20, 2023. (AP Photo/Evan Vucci) Biden makes surprise visit...}

\entryitemWithDescription{\hskip 0pt{}Israel's Netanyahu advances judicial changes despite uproar}{https://apnews.com/article/5d586384e4eff2b60c4af8e5245fc283}{Israelis protest against plans by Prime Minister Benjamin Netanyahu\textquotesingle s new government to overhaul the judicial system outside the Knesset, Israel\textquotesingle s parliament in Jerusalem, Monday, Feb. 20, 2023. Israel...}