\entryitemWithDescription{\hskip 0pt{}Company that sent AI calls mimicking Joe Biden to New Hampshire voters agrees to pay \$1 million fine}{https://apnews.com/article/33bab2049c12f952eb683a83039ddbba}{MEREDITH, N.H. (AP) --- A company that sent deceptive calls to New Hampshire voters using artificial intelligence to mimic President Joe Biden's voice agreed Wednesday to pay a \$1 million fine, federal regulators said. Lingo Telecom, the...}

\entryitemWithDescription{\hskip 0pt{}College town's police say they don't need help with cleanup after beer spill}{https://apnews.com/article/894c8cf75c12f3c17c21cd862a56a676}{OXFORD, Miss. (AP) --- A college town in Mississippi temporarily closed a street Wednesday after a delivery truck dropped dozens of cases of beer. The spill happened in Oxford, home of the University of Mississippi. The Oxford Police...}

\entryitemWithDescription{\hskip 0pt{}Detroit judge is sued after putting teen in handcuffs, jail clothes during field trip}{https://apnews.com/article/c5f8f0a1f0c4ac13a776c203527924d6}{DETROIT (AP) --- Attorneys for a teenager who was ordered into jail clothes and handcuffs during a field trip to a Detroit court filed a lawsuit against a judge Wednesday, accusing him of humiliation, false arrest and unlawful detention...}

\entryitemWithDescription{\hskip 0pt{}Florida quietly removes LGBTQ+ travel info from state website}{https://apnews.com/article/c16c8ad8c057331a7f43d14c141c5d78}{TALLAHASSEE, Fla. (AP) --- Key West, Fort Lauderdale, Wilton Manors and St. Petersburg are among several Florida cities that have long been top U.S. destinations for LGBTQ+ tourists. So it came as a surprise this week when travelers...}

\entryitemWithDescription{\hskip 0pt{}Sam Sam the Kittycat Man ran away. Thanks to a microchip, he was found close by — 11 years later}{https://apnews.com/article/b06b433f5f395bb9848a8e5ac136d6a2}{After Sam Sam the Kittycat Man disappeared 11 years ago, Jennifer Ravenel couldn't hold another cat in her lap. Her heart never could overcome the loss of that feral kitten she had rescued from the crook of a tree on her South Carolina...}

\entryitemWithDescription{\hskip 0pt{}The price of gold is at a record high. Here's why}{https://apnews.com/article/3644f0689b92b7646eb11c2e88e3f084}{NEW YORK (AP) --- A gold rush is here. The precious metal hit an all time high this week. The spot price for gold closed Tuesday above \$2,514, according to data from FactSet. That's the highest closing price recorded for the commodity to...}

\entryitemWithDescription{\hskip 0pt{}23 indicted in alleged schemes to smuggle drugs, phones into Georgia prisons with drones}{https://apnews.com/article/ceb3bf678b0aa3b836975f3fc4f13bfe}{STATESBORO, Ga. (AP) --- Federal prosecutors have indicted 23 people, most of them current and former inmates, in what authorities said Wednesday were schemes to smuggle drugs and cellphones into Georgia state prisons using drones...}

\entryitemWithDescription{\hskip 0pt{}Subadult loggerhead sea turtle returns to Atlantic Ocean in Florida after rehabilitation}{https://apnews.com/article/2ea568c2893f3a48a7fd31be503c218d}{JUNO BEACH, Fla. (AP) --- A rehabilitated sea turtle was released back into the Atlantic Ocean from a Florida beach Wednesday morning. Willow, a subadult loggerhead, was set free in the area behind the Loggerhead Marinelife Center in Juno...}

\entryitemWithDescription{\hskip 0pt{}2 injured Russian climbers rescued after 6 days stranded on Pakistan peak}{https://apnews.com/article/e614f7842fa4bf04c7d0365e2e191fa0}{ISLAMABAD (AP) --- After six days of being stranded on a remote peak in Pakistan's northeast, two injured Russian climbers were finally rescued, while another remains missing and is presumed dead, a mountaineering official said Wednesday...}

\entryitemWithDescription{\hskip 0pt{}Your audience is filled with Republicans. The Democratic convention is underway. How to cover it?}{https://apnews.com/article/33db0a7ffb9b1c14236fd799d4196331}{The Democratic convention presents Fox News Channel with a delicate challenge: how to cover a party suddenly enthused about its election chances when much of the network's audience has a different political viewpoint. During the...}

\entryitemWithDescription{\hskip 0pt{}She didn't see her Black heritage in crossword puzzles. So she started publishing her own}{https://apnews.com/article/118dcde72765334324233bfdf502e6c2}{NEW YORK (AP) --- It started a couple of years ago when Juliana Pache was doing a crossword puzzle and got stuck. She was unfamiliar with the reference that the clue made. It made her think about what a crossword puzzle would look like if...}

\entryitemWithDescription{\hskip 0pt{}Two killed in West Texas plane crash that set off a fire and injured a woman}{https://apnews.com/article/bef5f78e4cb0597d3d65da278859e3cb}{ODESSA, Texas (AP) --- A small plane crashed in a West Texas neighborhood Tuesday, killing the pilot and a passenger and setting off a large fire on the ground that injured a woman, authorities said. Witnesses said the plane struggled to...}

\entryitemWithDescription{\hskip 0pt{}Jennifer Lopez files for divorce from Ben Affleck after 2 years of marriage}{https://apnews.com/article/565c537d5956b6d539d887e93e9b2d91}{LOS ANGELES (AP) --- After a relationship that spanned two decades, two engagements, two weddings and headlines too numerous to count, Jennifer Lopez has filed for divorce from Ben Affleck. The filing Tuesday in Los Angeles Superior Court...}