\entryitemWithDescription{\hskip 0pt{}Paris' traffic-clogged Champs-Elysees turned into a mass picnic blanket for an unusual meal}{https://apnews.com/article/82b6afa486a40a50d777f762c427f995}{PARIS (AP) --- The French capital's most famous street, the Champs-Élysées, transformed into a massive picnic blanket Sunday as around 4,000 people sat in the sun enjoying an al fresco meal. The lucky picnickers were selected via a draw...}

\entryitemWithDescription{\hskip 0pt{}`Furiosa,' `Garfield' lead slowest Memorial Day box office in decades}{https://apnews.com/article/1b2a9c0aefec99b5105a09bfaf15679b}{Movie theaters are looking more and more like a wasteland this summer. Neither `` Furiosa: A Mad Max Saga '' nor `` The Garfield Movie '' could save Memorial Day weekend, which is cruising towards a two-decade low. `` Furiosa,'' the Mad...}

\entryitemWithDescription{\hskip 0pt{}12 people injured after Qatar Airways plan hits turbulence on way to Dublin}{https://apnews.com/article/ad4d17adc46ac91fea8f214c7ef72541}{LONDON (AP) --- Twelve people were injured when a Qatar Airways plane flying from Doha to Dublin on Sunday hit turbulence, airport authorities said. Dublin Airport said in a statement that the plane landed safely as scheduled before 1 p...}

\entryitemWithDescription{\hskip 0pt{}The dreams of a 60-year-old beauty contestant come to an abrupt end in Argentina}{https://apnews.com/article/30aef40c681708b761e87c308b1d2303}{BUENOS AIRES, Argentina (AP) --- A 60-year-old woman saw her dreams of becoming the oldest Miss Universe contestant in history melt away in a haze of sequins and selfies Saturday at Argentina's annual beauty pageant. Alejandra Marisa Rodrí...}

\entryitemWithDescription{\hskip 0pt{}Harrison Butker has no regrets about expressing his beliefs during recent commencement speech}{https://apnews.com/article/9da2604b6d37fb491a70b5048e1688b4}{Kansas City Chiefs kicker Harrison Butker has no regrets about expressing his beliefs in a recent commencement speech and he said he has received support as well as ``a shocking level of hate'' from others. Butker spoke Friday night at...}

\entryitemWithDescription{\hskip 0pt{}Rapper Nicki Minaj says Dutch police told her they found pot in bags}{https://apnews.com/article/f7c05e8ce6ddfc5482dbe37ba368038a}{AMSTERDAM (AP) --- Rapper Nicki Minaj said Saturday that police in the Netherlands discovered marijuana in her bags as she was preparing to leave the country for her next concert. Minaj tweeted that she was stopped at the Amsterdam...}

\entryitemWithDescription{\hskip 0pt{}What's open and closed on Memorial Day?}{https://apnews.com/article/a6b95939113efd509c5a31b6dde3035d}{In what had long been celebrated every May 30 to honor America's fallen soldiers, Memorial Day officially became a federal holiday in 1971, observed on the last Monday in May. Businesses increasingly have chosen to stay open on the...}

\entryitemWithDescription{\hskip 0pt{}What will win the Palme d'Or? Cannes closes Saturday with awards and a tribute to George Lucas}{https://apnews.com/article/53443a0e2526459b933f589ed0f498b5}{The 77th Cannes Film Festival draws to a close Saturday with the presentation of its top award, the Palme d'Or, along with an honorary tribute for George Lucas. The closing ceremony is set to begin at 6:45 p.m. local time, 12:45 p.m. U.S...}

\entryitemWithDescription{\hskip 0pt{}Boeing's 1st astronaut flight now set for June after a review of small leak on new capsule}{https://apnews.com/article/77576e1f9fb4354a7ba6e205566c1d27}{CAPE CANAVERAL, Fla. (AP) --- Boeing is now aiming for its first astronaut launch at the beginning of June, after spending the past few weeks struggling with more problems on the space capsule. Officials for the company and NASA said...}

\entryitemWithDescription{\hskip 0pt{}The Shiba Inu that became meme famous as the face of dogecoin has died. Kabosu was 18}{https://apnews.com/article/0c51b88ae457dd6eb61b05c7e87174d9}{The dog that skyrocketed to internet fame and became the face of the cryptocurrency dogecoin has died. The Shiba Inu named Kabosu passed away in Japan at 18 years old, a number of outlets reported. The dog's owner, Atsuko Sato, said in a...}

\entryitemWithDescription{\hskip 0pt{}The Beach Boys, going into the sunset, look back on years of harmony and heartache in documentary}{https://apnews.com/article/ceb664cc94dc979f7a5f856f749a7e23}{Both the Beach Boys and ``The Beach Boys'' --- the new documentary dropping Friday on Disney+ --- are all about blending a range of voices. The three Wilson brothers --- Brian, Carl and Dennis --- along with cousin Mike Love and friend Al...}

\entryitemWithDescription{\hskip 0pt{}Colorado governor signs bills regulating funeral homes after discovery of 190 rotting bodies}{https://apnews.com/article/219e6603ea99a1ab4fb3f1b78627611d}{DENVER (AP) --- Colorado Gov. Jared Polis signed two bills into law Friday that overhaul state oversight of the funeral home industry after a series of gruesome discoveries, including 190 discomposing bodies in a facility, families being...}

\entryitemWithDescription{\hskip 0pt{}UK lawmaker who wanted to be known as the `bionic MP' says he has decided not to run for re-election}{https://apnews.com/article/bb4673366bbf25de32add1d87aec462e}{LONDON (AP) --- A British lawmaker who returned to work this week after losing his hands and feet to sepsis announced Friday that he will not run in the July 4 election. Conservative legislator Craig Mackinlay was welcomed with a standing...}