\entryitemWithDescription{\hskip 0pt{}McDonald's plans \$5 US meal deal next month to counter customer frustration over high prices}{https://apnews.com/article/bda434c5a939b610a9c1fc09446a38d1}{McDonald's plans to introduce a \$5 meal deal in the U.S. next month to counter slowing sales and customers' frustration with high prices. The deal would let customers get a four-piece McNugget, small fries, a small drink and either a...}

\entryitemWithDescription{\hskip 0pt{}The Rev. Billy Graham is immortalized temporally with statue at US Capitol}{https://apnews.com/article/f09c82dedf4126a929bcd27147dedb8e}{A bronzed sculpture of the late Rev. Billy Graham standing in the U.S. Capitol on behalf of his native North Carolina was unveiled at a Thursday ceremony, immortalizing temporally the prolific evangelist also known as ``America's...}

\entryitemWithDescription{\hskip 0pt{}EA Sports College Football 25 comes out on July 19. Edwards, Ewers, Hunter are on standard cover}{https://apnews.com/article/0b3a0dcdc6fc85b263a842b13a4da023}{EA Sports revealed a release date of the College Football 25 video game on Thursday and a cover image that features Michigan running back Donovan Edwards, Texas quarterback Quinn Ewers and Colorado two-way player Travis Hunter. The game...}

\entryitemWithDescription{\hskip 0pt{}Teen died from eating a spicy chip as part of social media challenge, autopsy report concludes}{https://apnews.com/article/f81c220c549ec497bcc626dec4fc2be4}{BOSTON (AP) --- A medical examiner says a Massachusetts teen who participated in a spicy tortilla chip challenge died from ingesting a substance ``with a high capsaicin concentration.'' Capsaicin is a chili pepper extract. The Associated...}

\entryitemWithDescription{\hskip 0pt{}Simone Biles is stepping into the Olympic spotlight again. She is better prepared for the pressure}{https://apnews.com/article/1c7d4352a67c062bcc65fb7f56c9a1a3}{SPRING, Texas (AP) --- Simone Biles is not ``cured.'' Let's start there. A cure implies finality. An ultimate and decisive victory. If the gymnastics superstar has learned anything in the three years since those strange, uncertain days in...}

\entryitemWithDescription{\hskip 0pt{}Bad Bunny sports agency sues baseball players' union, trying to overturn ban}{https://apnews.com/article/f36becf10af76e69d9aab73b8ee8000d}{NEW YORK (AP) --- Bad Bunny's sports representation firm sued the baseball players' association Thursday, asking for a restraining order against the union that would allow it to keep working with the company's clients. Rimas Sports, under...}

\entryitemWithDescription{\hskip 0pt{}NFL schedule makers didn't seek out a Chiefs game close to a Taylor Swift concert}{https://apnews.com/article/f257f117ab001883fcb4cf6070a903d2}{Creating the NFL schedule is a complicated process that requires tens of thousands of computers coming up with countless possibilities over a process that lasts about four months. There are several sometimes competing factors at play from...}

\entryitemWithDescription{\hskip 0pt{}Hawaii native Savannah Gankiewicz crowned Miss USA after the previous winner resigned}{https://apnews.com/article/24fabf1b11fded33b8a8594faf258198}{Savannah Gankiewicz of Hawaii was crowned Miss USA 2023 on Wednesday, more than a week after the previous titleholder resigned citing her mental health. Gankiewicz, a model who leads a female empowerment nonprofit, will hold the title...}

\entryitemWithDescription{\hskip 0pt{}A cricket World Cup is coming to NYC's suburbs, where the sport thrives among immigrant communities}{https://apnews.com/article/d874f32cba4b396c21f131f6783b5e0f}{EAST MEADOW, N.Y. (AP) --- A towering stadium boasting 34,000 seats and a precisely trimmed field of soft Kentucky bluegrass is rising in a suburban New York park that will host one of the world's top cricket tournaments next month. But...}

\entryitemWithDescription{\hskip 0pt{}PGA Championship begins with sunshine and soft turf at Valhalla in Kentucky}{https://apnews.com/article/d0421ebb2e61aeff9c95a1bb87ee1a72}{LOUISVILLE, Ky. (AP) --- A PGA Championship filled with various layers of intrigue began Thursday after a 10-minute delay for fog, which quickly gave way to sunshine and a morning that figures to set the tone for Rory McIlroy, Tiger Woods...}

\entryitemWithDescription{\hskip 0pt{}The Academy of Country Music Awards are here; Luke Combs leads the nominations}{https://apnews.com/article/cfe844ff105cb9bbd7baf3b72d17033d}{Reba McEntire is hosting Thursday's Academy of Country Music Awards, promising a night of memorable performances, including a tribute to Toby Keith. When McEntire takes the stage at the Ford Center at The Star in Frisco, Texas, just north...}

\entryitemWithDescription{\hskip 0pt{}The first Mexican taco stand to get a Michelin star is a tiny business where the heat makes the meat}{https://apnews.com/article/6a4a89f27aa13d46246030b94bcffa56}{MEXICO CITY (AP) --- Newly minted Michelin-starred chef Arturo Rivera Martínez stood over an insanely hot grill Wednesday at the first Mexican taco stand ever to get a coveted star from the French dining guide, and did exactly the same...}

\entryitemWithDescription{\hskip 0pt{}Angie Harmon is suing an Instacart shopper who shot and killed her dog, Oliver}{https://apnews.com/article/75ef65e2ebcd857eaa3d4904d88d96a1}{CHARLOTTE, N.C. (AP) --- Actor Angie Harmon has filed a lawsuit against Instacart and one of its former shoppers who fatally shot her dog in March while delivering groceries at her North Carolina home. The lawsuit filed late last week in...}