\entryitemWithDescription{\hskip 0pt{}Judge vacates conviction of man imprisoned nearly 3 decades}{https://apnews.com/article/3eb7e5fbe6210dbc38b11995902b9947}{Lamar Johnson, center and his attorneys react on Tuesday, Feb. 14, 2023, after St. Louis Circuit Judge David Mason vacated his murder conviction during a hearing in St. Louis, Mo. Johnson served nearly 28 years of a life sentence for a...}

\entryitemWithDescription{\hskip 0pt{}California Sen. Feinstein says she won't run for reelection}{https://apnews.com/article/1140a033b78e63687633bc154bc358ff}{FILE - Sen. Dianne Feinstein, D-Calif., attends the Senate Judiciary Committee confirmation hearing in Dirksen Senate Office Building in Washington, April 28, 2021. Feinstein is not seeking reelection in 2024. Her announcement Tuesday...}

\entryitemWithDescription{\hskip 0pt{}Michigan State urges: `Run, Hide, Fight' as gunfire erupts}{https://apnews.com/article/cb91b1f2a03bde7ea240b4e1be124d1f}{First responders stage outside Berkey Hall following shootings on the campus of Michigan State University, Monday, Feb. 13, 2023, in East Lansing, Mich. (AP Photo/Al Goldis) EAST LANSING, Mich. (AP) --- They broke out windows to escape...}

\entryitemWithDescription{\hskip 0pt{}Review: A Marvel villain comes into focus in `Ant-Man 3'}{https://apnews.com/article/b1bea5a54041bb6a4aed34f3d0569c90}{This image released by Disney shows Paul Rudd, from left, Kathryn Newton and Evangeline Lilly in a scene from "Ant-Man and the Wasp: Quantumania." (Disney/Marvel Studios via AP) Peyton Reed's ``Ant-Man'' films have generally served as a...}

\entryitemWithDescription{\hskip 0pt{}Pence to fight special counsel subpoena on 2020 election}{https://apnews.com/article/3d91f095101d4eca30c22582341f8422}{FILE - Former Vice President Mike Pence speaks during an interview with The Associated Press, Nov. 16, 2022, in New York. The FBI is searching Pence\textquotesingle s Indiana home on Feb. 10, 20223, as part of a classified records probe...}

\entryitemWithDescription{\hskip 0pt{}Valentine's Day tips for talking about money as a couple}{https://apnews.com/article/2a33b65b5efc9e63c8c558d18f5adc6b}{Ryan Johnson, left, poses with Anna Craven outside their home, Friday, Feb. 10, 2023, in Nashua, N.H. The recently engaged couple have also established a transparent financial relationship including being open about individual budgets and...}

\entryitemWithDescription{\hskip 0pt{}Latest downed objects could well be 'benign,' US says}{https://apnews.com/article/8d60c429b1bf549a791434f8bd1bcc81}{Gen. Glen VanHerck, commander of the North American Aerospace Defense Command and United States Northern Command, walks to a secure are as lawmakers and intelligence advisers arrive for a closed briefing on the unknown aerial objects the...}

\entryitemWithDescription{\hskip 0pt{}Colts hire Eagles OC Shane Steichen as their head coach}{https://apnews.com/article/5afb2eb0265e6f2fbf09d6de4124a46c}{Shane Steichen shakes hand with Indianapolis Colts owner Jim Irsay during a news conference, Tuesday, Feb. 14, 2023, in Indianapolis. Steichen was introduced as the Colts new head coach. (AP Photo/Darron Cummings) INDIANAPOLIS (AP...}

\entryitemWithDescription{\hskip 0pt{}Tory Burch deconstructs classic style in new NYFW collection}{https://apnews.com/article/6b9d3734e806c4221ff6032453df1d15}{The Tory Burch collection is modeled during Fashion Week, Monday, Feb. 13, 2023, in New York. (AP Photo/Mary Altaffer) Tory Burch focuses on the unexpected with her Fall/Winter 2023 collection featuring deconstructed conventional looks in...}

\entryitemWithDescription{\hskip 0pt{}Nikki Haley announces run for president, challenging Trump}{https://apnews.com/article/f28052019e8ac3846cd125b3d9614d4f}{FILE - U.S. Ambassador to the United Nations Nikki Haley speaks during a news briefing at the White House, in Washington, Sept. 15, 2017. Haley, the former South Carolina governor and United Nations ambassador, announced her candidacy for...}

\entryitemWithDescription{\hskip 0pt{}Gunmen storm hospital of newborn saved from quake in Syria}{https://apnews.com/article/83f86ffde9dbd9d65f2745c56f338c35}{A baby girl who was born under the rubble caused by an earthquake that hit Syria and Turkey receives treatment inside an incubator at a children\textquotesingle s hospital in the town of Afrin, Aleppo province, Syria, Tuesday, Feb. 7...}

\entryitemWithDescription{\hskip 0pt{}Amid ChatGPT outcry, some teachers are inviting AI to class}{https://apnews.com/article/7bc171932ff9b994e04f6eaefc09319f}{Bella Whitice talks with classmate Katherine McCormick as they try and outwit the "robot" that was creating writing assignments in Donnie Piercey\textquotesingle s class at Stonewall Elementary in Lexington, Ky., Monday, Feb. 6, 2023.The...}

\entryitemWithDescription{\hskip 0pt{}Russia denies claims it plans to destabilize Moldova}{https://apnews.com/article/5d91576cf6878de3dd5250e5e618e2df}{FILE - Russian Foreign Ministry spokeswoman Maria Zakharova attends Russian Foreign Minister Sergey Lavrov\textquotesingle s annual news conference in Moscow, Jan. 18, 2023. Russia on Tuesday, Feb. 14, 2023 angrily rejected the Moldovan...}