\entryitemWithDescription{\hskip 0pt{}Travis Kelce says he shouldn't have bumped Chiefs coach Andy Reid during the Super Bowl}{https://apnews.com/article/711a0349ee177c9c10819303c581ebda}{Kansas City Chiefs tight end Travis Kelce said he went too far when he bumped into coach Andy Reid and screamed at him during the Super Bowl. Kelce addressed the situation Wednesday on New Heights, his podcast with his brother, longtime...}

\entryitemWithDescription{\hskip 0pt{}William Post, who played a key role in developing Pop-Tarts, dies at 96}{https://apnews.com/article/e4766c7a07d855ee60857f65d3f721cf}{GLEN ARBOR, Mich. (AP) --- William Post, a Michigan man who played an important role in the development of Pop-Tarts, has died at age 96. Post died Saturday, according to a family obituary which provided no details on his death but says...}

\entryitemWithDescription{\hskip 0pt{}Lyft shares rocket 62\% over a typo in the company's earnings release}{https://apnews.com/article/6867a202e0017d75d3631edfb8a9ba15}{Lyft shares jumped 62\% after the closing bell Tuesday thanks in part to a typo in the ride-hailing company's earnings release that appears to have sent investors' auto-trading algorithms --- or ``bots'' --- into a buying frenzy. Lyft's...}

\entryitemWithDescription{\hskip 0pt{}Airplane bumps into fence in third mishap in 2 weeks at Norway's main airport}{https://apnews.com/article/1f441e51d9fe7539515c5763c3a48b17}{COPENHAGEN, Denmark (AP) --- A Scandinavian Airlines plane struck a fence at the Oslo airport on Wednesday, causing minor damage to the aircraft and no injuries, the airline said. It was the third mishap in two weeks reported at Norway's...}

\entryitemWithDescription{\hskip 0pt{}Kansas lawmakers look to increase penalties for harming police dogs}{https://apnews.com/article/8e47eddc6193557b762e8245a55815f1}{TOPEKA, Kan. (AP) --- Kansas legislators are moving to impose tougher prison sentences for harming or killing police dogs, and the measure has bipartisan support despite questions elsewhere over how the animals are used in law...}

\entryitemWithDescription{\hskip 0pt{}Pond hockey in New Hampshire brightens winter for hundreds. But climate change threatens the sport}{https://apnews.com/article/89538fe220dfaade48bba5ea0abaff6d}{MEREDITH, N.H. (AP) --- Every winter, Pete Kibble and the guys he plays social hockey with in Massachusetts make the trek up to New Hampshire to play in an outdoor tournament many believe embodies the sport in its purest form. They are...}

\entryitemWithDescription{\hskip 0pt{}Thousands of US Uber and Lyft drivers plan Valentine's Day strikes}{https://apnews.com/article/e22eee6bb6c008a7dc05a32061e8ab55}{Thousands of U.S. ride-hailing workers plan to park their cars and picket at major U.S. airports Wednesday in what organizers say is their largest strike yet in a drive for better pay and benefits. Uber and Lyft drivers plan daylong...}

\entryitemWithDescription{\hskip 0pt{}1 person killed and 10 injured when vehicle crashes into emergency room in Austin, Texas}{https://apnews.com/article/1ff2b8b13e1267d05c30357750dc9eec}{AUSTIN, Texas (AP) --- A car crashed into a Texas hospital's emergency room Tuesday, killing the driver and injuring five other people, including a child with life-threatening injuries, authorities said. The car smashed into the lobby of...}

\entryitemWithDescription{\hskip 0pt{}Plush wars? Squishmallows toy maker and Build-A-Bear sue each other over `copycat' accusations}{https://apnews.com/article/188b5760d9217cbac25890d06dcf592d}{NEW YORK (AP) --- It turns out there are lots of sharp elbows in the plush toy business. Build-A-Bear and the makers of Squishmallows are facing off in federal court. Kelly Toys and its Berkshire Hathaway -controlled parent company...}

\entryitemWithDescription{\hskip 0pt{}A man has been charged in the theft of a Jackie Robinson statue that was found dismantled and burned}{https://apnews.com/article/c959797761a726fe3611b1b4ee641e8f}{Police announced Tuesday the arrest of a 45-year-old man in the theft of a bronze Jackie Robinson statue that later was found dismantled and burned. Wichita police Lt. Aaron Moses said Ricky Alderete was taken into custody earlier this...}

\entryitemWithDescription{\hskip 0pt{}Notre Dame cathedral's spire revealed in Paris as reconstruction continues after fire}{https://apnews.com/article/80bc7208a3398d06dd55e659d397e4bd}{PARIS (AP) --- Scaffolding that shrouded the top of Notre Dame cathedral following a devastating fire in April 2019 is being removed, marking a milestone in its reconstruction. As the shell at the summit has been taken down in recent...}

\entryitemWithDescription{\hskip 0pt{}Does soon-to-be NCAA scoring leader Caitlin Clark need a title to be among game's best?}{https://apnews.com/article/462a6db5ec8aac5dae950b884349400c}{Iowa's Caitlin Clark will soon be the NCAA's all-time scoring leader in women's basketball. That, in many minds, is enough to put the 22-year-old Iowa star among the greats of college basketball. But even after passing Kelsey Plum atop...}

\entryitemWithDescription{\hskip 0pt{}A new exhibition aims to bring Yoko Ono's art out of John Lennon's shadow}{https://apnews.com/article/7908545eaa9811aed5d866829bbe03db}{LONDON (AP) --- Before there was John and Yoko --- and after --- there was just Yoko Ono. The Japanese-American artist became a global celebrity through her marriage to John Lennon, her partner for more than a decade until his murder in...}