\entryitemWithDescription{\hskip 0pt{}Billy Ray Cyrus files for divorce from Firerose after 7 months of marriage}{https://apnews.com/article/9d1ece1ca2969c1bcc716cb80b04e3a5}{LOS ANGELES (AP) --- Billy Ray Cyrus has filed for divorce from singer Firerose after seven months of marriage. The 62-year-old country musician filed for divorce from the 36-year-old whose legal name is Johanna Rose Hodges in a Tennessee...}

\entryitemWithDescription{\hskip 0pt{}The US cricket team is closing in on a major achievement at the Twenty20 World Cup}{https://apnews.com/article/c4122d36463276b5756f2ea57efccea3}{The sport of cricket is as foreign to most Americans as driving on the left-hand side of the road or drinking warm beer. This year, though, the United States is getting a close-up view of the bat-and-ball sport originally from England...}

\entryitemWithDescription{\hskip 0pt{}Joey Chestnut out of Nathan's July 4 hot dog eating contest}{https://apnews.com/article/c1d4ac988ca44ffc1bd5ea691dc161ac}{NEW YORK (AP) --- America's perennial hot dog swallowing champion won't compete in this year's Independence Day competition due to a contract dispute, organizers said Tuesday. Joey ``Jaws'' Chestnut, 40, has been competing since 2005 and...}

\entryitemWithDescription{\hskip 0pt{}Jay-Z's Roc Nation to drum up support for private school vouchers in Philadelphia}{https://apnews.com/article/78bc4315c95330031aa1d63e3b881f01}{PHILADELPHIA (AP) --- Jay-Z is putting his weight behind an effort to fund private school vouchers in Philadelphia. The entertainment mogul's Roc Nation announced it is funding a campaign this month to drum up support for the Pennsylvania...}

\entryitemWithDescription{\hskip 0pt{}Oregon man who drugged daughter's friends with insomnia medication at sleepover gets prison term}{https://apnews.com/article/59448423b7a0cca253ed46112c0514ec}{PORTLAND, Ore. (AP) --- An Oregon man who drugged his daughter and her friends with fruit smoothies laced with a sleeping medication after they didn't go to bed during a sleepover was sentenced to two years in prison. Michael Meyden, a 57...}

\entryitemWithDescription{\hskip 0pt{}Singer sues hospital, says staff thought he was mentally ill and wasn't member of Four Tops}{https://apnews.com/article/46e94b0f63ad3b4291e72a087c6d2c05}{WARREN, Mich. (AP) --- The lead singer of the Four Tops said a Detroit-area hospital restrained him and ordered a psychological exam after refusing to believe that he was part of the Motown music group. Alexander Morris, who is Black...}

\entryitemWithDescription{\hskip 0pt{}Michigan couple, attorney announced as winners of \$842.4 million Powerball jackpot}{https://apnews.com/article/6613ed1ebc27930f9cf920c212af573b}{GRAND BLANC TOWNSHIP, Mich. (AP) --- A mid-Michigan couple and a lawyer from the west side of the state were announced Tuesday as winners of an \$842.4 million Powerball lottery jackpot from a ticket purchased on New Year's Day. The...}

\entryitemWithDescription{\hskip 0pt{}Crew finds submerged wreckage of missing jet that mysteriously disappeared more 50 years ago}{https://apnews.com/article/9abdce0c88644e0b441034b16bfb850e}{Fifty-three years after a private plane carrying five men disappeared on a snowy Vermont night, experts believe they have found the wreckage of the long lost jet in Lake Champlain. The corporate jet disappeared shortly after departing the...}

\entryitemWithDescription{\hskip 0pt{}Key new features coming to Apple's iOS18 this fall}{https://apnews.com/article/da497f4fd3b7cbb49f1970690d901cd7}{Apple announced a slew of new features for iOS 18 at Monday's developers conference event, many of which are designed to enhance the Siri assistant and bring artificial intelligence tools to iPhone users. The AI-packed updates coming in...}

\entryitemWithDescription{\hskip 0pt{}Union: 4 Florida police officers indicted for 2019 shootout that left UPS driver and passerby dead}{https://apnews.com/article/7f7a450fbbd46453401b511c7e7613aa}{FORT LAUDERDALE, Fla. (AP) --- Four Florida police officers have been indicted in connection with a 2019 shootout on a busy street that left a UPS driver, the two robbers who hijacked him and a nearby driver dead, their union confirmed...}

\entryitemWithDescription{\hskip 0pt{}Panthers now 2 wins from the Stanley Cup, top Oilers 4-1 for 2-0 lead in title series}{https://apnews.com/article/02733a3e84c544f3250b411f660855b0}{SUNRISE, Fla. (AP) --- Evan Rodrigues had two goals in the third period, Niko Mikkola and Aaron Ekblad also scored and the Florida Panthers beat the Edmonton Oilers 4-1 on Monday night to take a 2-0 lead in the Stanley Cup Final. Sergei...}

\entryitemWithDescription{\hskip 0pt{}California socialite sentenced to 15 years to life for 2020 hit-and-run deaths of two young brothers}{https://apnews.com/article/81d60eaa0272c6f9c808e69b771b01ce}{LOS ANGELES (AP) --- A Southern California socialite was sentenced Monday to 15 years to life in prison for the hit-and-run deaths of two young brothers in a crosswalk more than three years ago. Authorities said Rebecca Grossman, wife of...}

\entryitemWithDescription{\hskip 0pt{}Library of Congress launches new 'Collecting Memories' exhibit in a bid to draw more tourists}{https://apnews.com/article/78f757a3097266a18e61385b0d8ca977}{WASHINGTON (AP) --- The Library of Congress is unveiling an eclectic new exhibit drawing on the institution's vast historical archives and designed to make the library a more popular and accessible destination for visitors and tourists. ``...}