\entryitemWithDescription{\hskip 0pt{}Fans raise a red Solo cup to honor Toby Keith, who immortalized the humble cup in song}{https://apnews.com/article/91bd3db5f4c1dec0618ab380bed58b66}{Red Solo cups -- a staple of barbecues and beer pong -- are usually synonymous with good times. But on Tuesday, as word of country singer Toby Keith's death spread, many were raising their red Solos in sad tribute to the singer, who...}

\entryitemWithDescription{\hskip 0pt{}A SWAT team sniper killed a bank hostage-taker armed with a knife, sheriff says}{https://apnews.com/article/3e1e0f5e8b37e972f2adb3691ed5b070}{FORT MYERS, Fla. (AP) --- A deputy shot and killed a man Tuesday after he took people hostage and claimed to have a bomb at a Florida bank, authorities said. The Lee County Sheriff's Office responded to a Bank of America branch in Fort...}

\entryitemWithDescription{\hskip 0pt{}Meta says it will label AI-generated images on Facebook and Instagram}{https://apnews.com/article/415163d053ed915042a04f1ec3d9eafa}{Facebook and Instagram users will start seeing labels on AI-generated images that appear on their social media feeds, part of a broader tech industry initiative to sort between what's real and not. Meta said Tuesday it's working with...}

\entryitemWithDescription{\hskip 0pt{}Not wearing a mask during COVID-19 health emergency isn't a free speech right, appeals court says}{https://apnews.com/article/108abf877288999f34d1c604b731d34c}{TRENTON, N.J. (AP) --- A federal appeals court shot down claims Monday that New Jersey residents' refusal to wear face masks at school board meetings during the COVID-19 outbreak constituted protected speech under the First Amendment. The...}

\entryitemWithDescription{\hskip 0pt{}Killer Mike says arrest at Grammys stems from altercation with an `over-zealous' security guard}{https://apnews.com/article/7c95ddb7a5180de4dd13b6b2cd415bb7}{LOS ANGELES (AP) --- Killer Mike says an ``over-zealous'' security guard contributed to the physical altercation that led to his arrest after the rapper and activist won three awards at the Grammys. ``As you can imagine, there was a lot...}

\entryitemWithDescription{\hskip 0pt{}At 102 years old, veteran WWII pilot takes to the skies on a delightfully bumpy ride for charity}{https://apnews.com/article/14f1a50664e2cb4ef1269e1f05fb089c}{LONDON (AP) --- A former Royal Air Forces pilot has taken to the skies in a Spitfire at 102 years old. Jack Hemmings, an ex-squadron leader with Britain's air force, is believed to be the oldest pilot to fly the World War II plane. His 20...}

\entryitemWithDescription{\hskip 0pt{}Gigantic replica of Emperor Constantine looks out over Rome as 3D technology brings past to life}{https://apnews.com/article/b1c5418d16b4911c0c623acdcc80c7a2}{ROME (AP) --- Emperor Constantine, the 4th century ruler whose embrace of Christianity helped spread the Christian faith throughout the Roman Empire, now has a reconstructed statue befitting his larger-than-life role in history. Rome...}

\entryitemWithDescription{\hskip 0pt{}General Motors is recalling over 323,000 heavy-duty pickups because tailgates can open unexpectedly}{https://apnews.com/article/bc1cc539e1ad4a0be8d347ff80c0816f}{General Motors is recalling more than 323,000 heavy-duty pickup trucks in the U.S. because the electronic tailgate release switches can short circuit and open the gates while the vehicles are in park. The recall covers certain Chevrolet...}

\entryitemWithDescription{\hskip 0pt{}Honda is recalling more than 750,000 vehicles to fix faulty passenger seat air bag sensor}{https://apnews.com/article/80ab027fc7f0991ba509fc93e0176e99}{DETROIT (AP) --- Honda is recalling more than three quarters of a million vehicles in the U.S. because a faulty sensor may cause the front passenger air bags to inflate when they're not supposed to. The recall covers certain Honda Pilot...}

\entryitemWithDescription{\hskip 0pt{}California could legalize psychedelic therapy after rejecting `magic mushroom' decriminalization}{https://apnews.com/article/64741f803176bd5ff4d0330917c00fac}{SACRAMENTO, Calif. (AP) --- A pair of California lawmakers introduced a bipartisan bill on Tuesday to allow people 21 and older to consume psychedelic mushrooms under professional supervision as part of an agenda to tackle the state's...}

\entryitemWithDescription{\hskip 0pt{}A blaze in a fireworks factory in central India has killed six people and injured scores of others}{https://apnews.com/article/7655311e911065311ab49703c914cdcf}{NEW DELHI (AP) --- A fire raced through a firecracker factory in central India on Tuesday, killing six people and injuring about 40 others as it sparked other explosions, officials said. Videos on social media showed smoke and flames...}

\entryitemWithDescription{\hskip 0pt{}Thousands of vehicles stuck on highways in China as snow snarls Lunar New Year travel}{https://apnews.com/article/ed6ce9c3fe8167b47d29177f367b769e}{BEIJING (AP) --- Thousands of motorists were stuck on highways in central China as heavy snow snarled travel during the annual Lunar New Year rush. Aerial images showed long traffic back-ups in Hubei province on Monday night. About 4,000...}

\entryitemWithDescription{\hskip 0pt{}Messi says he ``feels much better'' and hopeful of playing in Tokyo after PR disaster in Hong Kong}{https://apnews.com/article/1930d0d59b0eea2ca1858ff8c44aff33}{TOKYO (AP) --- Look for Lionel Messi to play in Wednesday's friendly in Tokyo with Inter Miami facing Japanese club Vissel Kobe. And don't look for another public-relations disaster as happened on Sunday when Argentina's World Cup-winning...}