\entryitemWithDescription{\hskip 0pt{}Alec Baldwin says part of shooting charge unconstitutional}{https://apnews.com/article/089584785158a600ca5437ac5c98c48c}{FILE - Actor Alec Baldwin, speaks to supporters of Amanda Pohl, candidate for Virginia Senate District 11 in her home in Midlothian, Va., Tuesday, Oct. 22, 2019. Prosecutors announced Thursday, Jan. 19, 2023 they are charging Baldwin with...}

\entryitemWithDescription{\hskip 0pt{}Florida backs off athlete menstrual data, but debate lingers}{https://apnews.com/article/497fbf37a7ca0c6ad28e2f491abe6e92}{FILE - The goalkeeper guards the net as girls take part in the first day of tryouts for the Fort Walton Beach High School girls\textquotesingle{} soccer team in Fort Walton Beach, Fla., on Oct. 10, 2012. Questions about female athletes'...}

\entryitemWithDescription{\hskip 0pt{}Super Bowl Guide: Where to watch and who to watch}{https://apnews.com/article/5a82dbeafd3f139e670c0e450dcc5065}{Workers prepare for the NFL Super Bowl LVII football game outside State Farm Stadium, Wednesday, Feb. 1, 2023, in Glendale, Ariz. (AP Photo/Matt York) PHOENIX (AP) --- The Super Bowl between the Philadelphia Eagles and Kansas City Chiefs...}

\entryitemWithDescription{\hskip 0pt{}US jet shoots down unknown object flying off Alaska coast}{https://apnews.com/article/175f9078d1df36e392b2956ba771001e}{National Security Council spokesman John Kirby speaks during the daily briefing at the White House in Washington, Friday, Feb. 10, 2023. (AP Photo/Susan Walsh) A U.S. military fighter jet shot down an unknown object flying off the coast...}

\entryitemWithDescription{\hskip 0pt{}Nicaraguan judge sentences Catholic bishop to 26 years}{https://apnews.com/article/c7930c6340472867148ca7e79e09f1eb}{FILE - A poster featuring Bishop Rolando Alvarez and Pope Francis hangs inside the Cathedral in Matagalpa, Nicaragua, Aug. 19, 2022. Five Catholic priests were sentenced to 10 years in prison in Managua, on Monday, Feb. 6, 2023, accused...}

\entryitemWithDescription{\hskip 0pt{}Marines, bonded by kidney donation, now head to Super Bowl}{https://apnews.com/article/82c4ac325e9cdaca94fc3a4738175896}{In this image provided by NBC News' TODAY, Philadelphia Eagles fan Billy Welsh and Kansas City Chiefs fan John Gladwell sit together during a broadcast of the show, Wednesday, Feb. 8, 2023, in New York. The two former Marines bonded by a...}

\entryitemWithDescription{\hskip 0pt{}New classified document found in FBI search of Pence home}{https://apnews.com/article/7b3bfba7cdd8d9d8fd828045ab3208e6}{FILE - Former Vice President Mike Pence speaks during an interview with The Associated Press, Nov. 16, 2022, in New York. The FBI is searching Pence\textquotesingle s Indiana home on Feb. 10, 20223, as part of a classified records probe...}

\entryitemWithDescription{\hskip 0pt{}Don't feed the bears! But birds OK, new Tahoe research shows}{https://apnews.com/article/99b2971884975062712acb75b69c4765}{This photo provided by the University of Nevada, Reno shows University of Nevada, Reno student Michelle Werdann feeds a wild Mountain Chickadee pine nuts at Chickadee Ridge in Mount Rose Meadows, Nevada, Friday, Jan. 6, 2023.(Jennifer...}

\entryitemWithDescription{\hskip 0pt{}Danielle Deadwyler cites racism, misogynoir in Oscar snub}{https://apnews.com/article/12db71a080acf7a4bb3b1407f497e79e}{Danielle Deadwyler arrives at the 28th annual Critics Choice Awards at The Fairmont Century Plaza Hotel on Sunday, Jan. 15, 2023, in Los Angeles. (Photo by Jordan Strauss/Invision/AP) NEW YORK (AP) --- Danielle Deadwyler says racism and...}

\entryitemWithDescription{\hskip 0pt{}Abortion pill could be pulled off market by Texas lawsuit}{https://apnews.com/article/bdd99c39613c71f62d10dfc2f2d1bf07}{FILE - Boxes of the drug mifepristone sit on a shelf at the West Alabama Women\textquotesingle s Center in Tuscaloosa, Ala., on March 16, 2022. Attorney generals in 20 conservative-led states warned CVS and Walgreens on Wednesday, Feb. 1...}

\entryitemWithDescription{\hskip 0pt{}How the 'boneless wing' became a tasty culinary lie}{https://apnews.com/article/7bae0f861af227f53318e5ddfcce771f}{An order of "boneless chicken wings" is shown at a restaurant in Willow Grove, Pa., Wednesday, Feb. 8, 2023. With the Super Bowl at hand, behold the cheerful untruth that has been perpetrated upon (and generally with the blessing of) the...}

\entryitemWithDescription{\hskip 0pt{}Japan's earthquake recovery offers hard lessons for Turkey}{https://apnews.com/article/4547c9e6d98bc8cfecd2fc0c99fa1a83}{FILE - Emergency teams search for people in the rubble of a destroyed building in Adana, southern Turkey, Tuesday, Feb. 7, 2023. The 2011 quake, tsunami and nuclear meltdown in northern Japan provides a glimpse of what Turkey and Syria...}

\entryitemWithDescription{\hskip 0pt{}Pro-Western Recean set to succeed Moldova's PM who resigned}{https://apnews.com/article/69a879ddc1a6e9b04523acf6c5913f4d}{Moldovan Prime Minister designate Dorin Recean waits as President Maia Sandu, left, announces he is appointed to form a new government in Chisinau, Moldova, Friday, Feb 10, 2023. Moldova\textquotesingle s government collapsed Friday as...}