\entryitemAp{\hskip 0pt{}'Dangerous' Alabama tornado slams buildings, uproots trees}{https://apnews.com/article/37e05f4ae4bc39a61a50243c92b2b82f}{A damaged home is seen in the aftermath of severe weather, Thursday, Jan. 12, 2023, near Prattville, Ala. A large tornado damaged homes and uprooted trees in Alabama on Thursday as a powerful storm system pushed through the South. (AP...}

\entryitemAp{\hskip 0pt{}Study: Exxon Mobil accurately predicted warming since 1970s}{https://apnews.com/article/e9594dc9adb504a81ec82f4ac2b72ef9}{FILE - Exxon Mobil Billings Refinery sits in Billings, Mont. Exxon Mobil's scientists were remarkably accurate in their predictions about global warming, even as the company made public statements that contradicted its own scientists...}

\entryitemAp{\hskip 0pt{}US kindergarten vaccination rate dropped again, data shows}{https://apnews.com/article/acba3eb975fdfcd41732ed87511387f2}{FILE - Socially distanced kindergarten students wait for their parents to pick them up on the first day of in-person learning at Maurice Sendak Elementary School on April 13, 2021, in Los Angeles. Vaccination rates for U.S...}

\entryitemAp{\hskip 0pt{}Bank to pay \$31M redlining settlement, DOJ's largest ever}{https://apnews.com/article/b55eade5ccdbf0974ff77f011a5d8af9}{Assistant Attorney General of the U.S. Department of Justice\textquotesingle s Civil Rights Division Kristen Clarke, left, listens as United States Attorney Martin Estrada, of the California central division, speaks while announcing the...}

\entryitemAp{\hskip 0pt{}2022 was fifth or sixth warmest on record as Earth heats up}{https://apnews.com/article/af0300e0682b4fa0bdc7f0c039adeb9f}{FILE - People cool off in the water on a hot and sunny day at the beach in Barcelona, Spain, July 15, 2022. Earth's fever persisted last year, not quite spiking to a record high but still in the top five or six warmest on record...}

\entryitemAp{\hskip 0pt{}Garland appoints special counsel to investigate Biden docs}{https://apnews.com/article/33479d12c7cf0a822adb2f44c32b88fd}{Attorney General Merrick Garland speaks during a news conference at the Department of Justice, Thursday, Jan. 12, 2023, in Washington, as John Lausch, the U.S. Attorney in Chicago, looks on. (AP Photo/Manuel Balce Ceneta) President Joe...}

\entryitemAp{\hskip 0pt{}US air travel returns to normal after technology breakdown}{https://apnews.com/article/c297503ed677e7354cbd750119ac9db6}{Flight status boards show delayed and cancelled flights at Harry Reid International Airport, Wednesday, Jan. 11, 2023, in Las Vegas. Delays and cancellations among flights across the United States were minimal on Thursday, a day after a...}

\entryitemAp{\hskip 0pt{}Prosecutor: Proud Boys attacked 'heart' of democracy on 1/6}{https://apnews.com/article/9db4507b29d7102e40f24af7262ae7d2}{FILE - Proud Boys leader Henry "Enrique" Tarrio wears a hat that says The War Boys during a rally in Portland, Ore., on Sept. 26, 2020. The seditious conspiracy trial of Proud Boys leader Enrique Tarrio and four lieutenants is coming at a...}

\entryitemAp{\hskip 0pt{}New, taller Barbie doll is aimed at kids as young as 3}{https://apnews.com/article/602a39186e00d48fcdb047f0de8bdb2c}{CORRECTS SPELLING TO WAIST INSTEAD OF WASTE - This combination of photos shows My First Barbie dolls, from left, Brooklyn, Teresa and Renee. My First Barbie, made specifically for children as young as 3, is 13.5 inches tall, with a...}

\entryitemAp{\hskip 0pt{}Russian forces press deadly assault for breakthrough in east}{https://apnews.com/article/e08a21609de2e65f84873e138968405a}{Nina Klinkova reacts to a sound of an explosion as she looks for humanitarian aid in Siversk, Donetsk region, Ukraine, Thursday, Jan. 12, 2023. (AP Photo/Evgeniy Maloletka) Mortar fire on the frontline in Ukraine KYIV, Ukraine (AP...}

\entryitemAp{\hskip 0pt{}Harvick: 'It's just time,' racer says of 2023 final season}{https://apnews.com/article/505a2b8ff631c52f795455fd39e75acc}{FILE - Kevin Harvick celebrates after winning the NASCAR Sprint Cup championship series auto race, Sunday, Nov. 16, 2014, in Homestead, Fla. Kevin Harvick said Thursday, Jan. 12, 2023, he will retire from NASCAR competition at the end of...}

\entryitemAp{\hskip 0pt{}Nurses at 2 NYC hospitals return to work as deal ends strike}{https://apnews.com/article/f3ff892526a6fa573feef2ee001289c9}{People enter Mount Sinai Hospital in New York, Thursday, Jan. 12, 2023. Two New York City hospitals have reached a tentative contract agreement with thousands of striking nurses that ends the walkout, the nurses\textquotesingle{} union...}

\entryitemAp{\hskip 0pt{}'Catastrophe': Cardinal Pell's secret memo blasts Francis}{https://apnews.com/article/9253a16c95f7870a07fd58b00b266f1e}{FILE - Cardinal George Pell answers a journalist\textquotesingle s question during an interview with The Associated Press inside his residence near the Vatican in Rome, Nov. 30, 2020. Pell, who was the most senior Catholic cleric to be...}