\entryitemWithDescription{\hskip 0pt{}DeSantis and Newsom to go head-to-head in November Fox News debate moderated by Sean Hannity}{https://apnews.com/article/4a7081f6778872eb088660209552480c}{NEW YORK (AP) --- Florida Gov. Ron DeSantis will take time out from debating fellow Republicans in two months to take on a Democrat, California Gov. Gavin Newsom. Fox News said Monday that the two politicians will appear in a 90-minute...}

\entryitemWithDescription{\hskip 0pt{}Milan fashion celebrated diversity and inclusion with refrain: Make more space for color, curves}{https://apnews.com/article/992da174c7299495a7f673f304464d09}{MILAN (AP) --- More curvy models than ever showed up on Milan runways this season, due mostly to a single show by Brazilian designer Karoline Vitto, while designers of color showcased their work at collateral events meant to promote their...}

\entryitemWithDescription{\hskip 0pt{}UK police open sexual offenses investigation after allegations about Russell Brand}{https://apnews.com/article/1ca6adf91cfac7c92b42e9329cd53c44}{LONDON (AP) --- British police have opened a sex crimes investigation triggered by news reports about comedian Russell Brand. London's Metropolitan Police force said Monday that it had ``received a number of allegations of sexual...}

\entryitemWithDescription{\hskip 0pt{}Monday night's \$785M Powerball jackpot is ninth largest lottery prize. Odds of winning are miserable}{https://apnews.com/article/55e424dbafde3524dfb636e5f6768bfc}{DES MOINES, Iowa (AP) --- The ninth-largest lottery jackpot will be on the line Monday night when numbers are drawn for a \$785 million Powerball prize. The payout has grown so large because it has been building for more than two months...}

\entryitemWithDescription{\hskip 0pt{}Call for sanctions as homophobic chants again overshadow French soccer's biggest game}{https://apnews.com/article/c0a4e69f11059c37ea3616ae0e1499dc}{Homophobic chanting by sections of Paris Saint-Germain fans targeting Marseille players has again marred the biggest game in French soccer, prompting calls for sanctions. Olivier Klein, the inter-ministerial delegate for the fight against...}

\entryitemWithDescription{\hskip 0pt{}Amazon is investing up to \$4 billion in AI startup Anthropic in growing tech battle}{https://apnews.com/article/72d21e6c663d506dbf968f50628e7ded}{Amazon is investing up to \$4 billion in Anthropic and taking a minority stake in the artificial intelligence startup, the two companies said Monday. The investment underscores how Big Tech companies are pouring money into AI as they race...}

\entryitemWithDescription{\hskip 0pt{}Toymaker Lego will stick to its quest to find sustainable materials despite failed recycle attempt}{https://apnews.com/article/a523a39117eed52b57622b07d07d9fd6}{COPENHAGEN, Denmark (AP) --- Denmark's Lego said on Monday that it remains committed to its quest to find sustainable materials to reduce carbon emissions, even after an experiment by the world's largest toymaker to use recycled bottles...}

\entryitemWithDescription{\hskip 0pt{}On the run for decades, convicted Mafia boss Messina Denaro dies in hospital months after capture}{https://apnews.com/article/6c0a6acfa6c47aaa6107743d8b9e4419}{L'AQUILA, Italy (AP) --- Matteo Messina Denaro, a convicted mastermind of some of the Sicilian Mafia's most heinous slayings, died on Monday in a hospital prison ward, several months after being captured as Italy's No. 1 fugitive and...}

\entryitemWithDescription{\hskip 0pt{}AI is on the world's mind. Is the UN the place to figure out what to do about it?}{https://apnews.com/article/b9ef875a98e7d6ceb8d4c61b1cbbb904}{UNITED NATIONS (AP) --- Just a few years ago, artificial intelligence got barely a mention at the U.N. General Assembly's convocation of world leaders. But after the release of ChatGPT last fall turbocharged both excitement and anxieties...}

\entryitemWithDescription{\hskip 0pt{}Leader of Canada's House of Commons apologizes for honoring man who fought for Nazis}{https://apnews.com/article/eedc22e1d810011c412953168a4cee46}{TORONTO (AP) --- The speaker of Canada's House of Commons apologized Sunday for recognizing a man who fought for a Nazi military unit during World War II. Just after Ukrainian President Volodymyr Zelenskyy delivered an address in the...}

\entryitemWithDescription{\hskip 0pt{}Taylor Swift turns out to see Travis Kelce, Kansas City Chiefs play Chicago Bears}{https://apnews.com/article/891e7df84295f5b35cfa97a5ec427721}{KANSAS CITY, Mo. (AP) --- Travis Kelce put the ball in Taylor Swift's court, and she wound up bringing it to Arrowhead Stadium after all. The 12-time Grammy Award winner took advantage of an invitation from the All-Pro tight end to see...}

\entryitemWithDescription{\hskip 0pt{}Usher to headline the 2024 Super Bowl halftime show in Las Vegas}{https://apnews.com/article/05a21fe7663feff1368bba8e8ba7c47b}{LOS ANGELES (AP) --- Usher has a new confession: The Grammy winner will headline the Apple Music Super Bowl Halftime Show in Las Vegas. The NFL, Apple Music and Roc Nation announced Sunday that Usher would lead the halftime festivities...}

\entryitemWithDescription{\hskip 0pt{}NASA's first asteroid samples land on Earth after release from spacecraft}{https://apnews.com/article/9918c2c13b689e01800de4ea42d60188}{NASA's first asteroid samples fetched from deep space parachuted into the Utah desert Sunday to cap a seven-year journey. In a flyby of Earth, the Osiris-Rex spacecraft released the sample capsule from 63,000 miles (100,000 kilometers...}