\entryitemWithDescription{\hskip 0pt{}Prince Harry and Meghan meet with Afro-Colombian leaders to wrap up their first visit to Colombia}{https://apnews.com/article/babe9c2743f15d8978de178e1fbfedd7}{CALI, Colombia (AP) --- Prince Harry and his wife Meghan wrapped up their visit to Colombia on Sunday by participating in a forum on the challenges facing women of African descent as they participate in politics. The couple also met with...}

\entryitemWithDescription{\hskip 0pt{}`Alien: Romulus' bites off \$41.5 million to top box office charts}{https://apnews.com/article/28c4fd61a993e63313445d6c5785dc29}{`` Alien: Romulus,'' the latest installment in the 45-year-old franchise, opened in first place at the North American box office. The 20th Century Studios release earned an estimated \$41.5 million in its first weekend, where it was...}

\entryitemWithDescription{\hskip 0pt{}`Banksy woz ere.' London Zoo is the latest to remove street artist's animal mural for protection}{https://apnews.com/article/9a883eefbeb7bbbfc249eb8a6022e6a0}{LONDON (AP) --- The gorilla and other animals that appeared to have escaped from the London Zoo in Banksy `s most recent work have been taken into safekeeping. The zoo said it removed the elusive street artist's mural on its gate Friday...}

\entryitemWithDescription{\hskip 0pt{}At least 23 injured when fire breaks out on a Ferris wheel in eastern Germany}{https://apnews.com/article/fb54a0879f6f2236650c0f0219e721d3}{BERLIN (AP) --- At least 23 people were injured when two gondolas of a Ferris wheel caught fire at a music festival near Leipzig in eastern Germany, news agency dpa reported Sunday. The fire started in one gondola and then spread to a...}

\entryitemWithDescription{\hskip 0pt{}French actor and heartthrob Alain Delon dies at 88}{https://apnews.com/article/890a18cca5084cd49e4809dc44d6e520}{PARIS (AP) --- Alain Delon, the internationally acclaimed French actor who embodied both the bad guy and the policeman and made hearts throb around the world, died at age 88, French media reported. With his handsome looks and tender...}

\entryitemWithDescription{\hskip 0pt{}South Africa's du Plessis retains middleweight UFC title}{https://apnews.com/article/74d389b1d695bd4605a3fad73d238ee9}{PERTH, Australia (AP) --- South African Dricus du Plessis took a flurry of body hits across four rounds before defeating Israel Adesanya by submission to retain his middleweight championship at UFC 305 on Sunday. After scoring some early...}

\entryitemWithDescription{\hskip 0pt{}Trump again decries two gold medalist Olympic athletes, falsely labeling the female boxers as men}{https://apnews.com/article/57afb62e90968c06277118135e47e759}{WASHINGTON (AP) --- Former President Donald Trump on Saturday again decried two gold medalist Olympic athletes, falsely labeling the female boxers as men. Trump made the comments while speaking at a campaign rally in Pennsylvania and...}

\entryitemWithDescription{\hskip 0pt{}Powerful earthquake hits off far east coast of Russia, though no early reports of damage}{https://apnews.com/article/e4571ea33f8f9e169a5f128f639f1ddb}{PETROPAVOVSK-KAMCHATSKY, Russia (AP) --- A powerful earthquake with a preliminary magnitude of 7.0 struck in the Pacific off the far eastern coast of Russia near a major naval base early Sunday, but there were no early reports of damage...}

\entryitemWithDescription{\hskip 0pt{}Indiana Jones' iconic felt fedora fetches \$630,000 at auction}{https://apnews.com/article/b71e3ac1ddc1090934f528522a413f6c}{LOS ANGELES (AP) --- The brown felt fedora worn by actor Harrison Ford in the second installment of the Indiana Jones movies sold for \$630,000 at auction, film and TV memorabilia company Propstore announced Friday. The hat featured in...}

\entryitemWithDescription{\hskip 0pt{}Keith Urban plays free pop-up concert outside a Buc-ee's store in Alabama}{https://apnews.com/article/1a755465e22dbfc3e432b356ecdb8cf0}{ATHENS, Ala. (AP) --- Country singer Keith Urban gave just a few hours' notice before performing a free concert Friday night in the parking lot of a large convenience store and gas station in north Alabama. Hundreds of people turned out...}

\entryitemWithDescription{\hskip 0pt{}Maurice Williams, writer and lead singer of `Stay,' dead at 86}{https://apnews.com/article/0f218ab3aef6476982a9772ba6c9f5fd}{NEW YORK (AP) --- Maurice Williams, a rhythm and blues singer and composer who with his backing group the Zodiacs became one of music's great one-shot acts with the classic ballad ``Stay,'' has died. He was 86. Williams died Aug. 6...}

\entryitemWithDescription{\hskip 0pt{}`Shoot me up with a big one': A timeline of the last days of Matthew Perry}{https://apnews.com/article/411a3365195c4b65bbb41cc510cb9341}{LOS ANGELES (AP) --- The arrest of five people in the overdose death of Matthew Perry has revealed key details about the final days of the ``Friends'' star, most of them spent in the throes of an addiction to the surgical anesthetic...}

\entryitemWithDescription{\hskip 0pt{}Michael Brown's death transformed a nation and sparked a decade of American reckoning on race}{https://apnews.com/article/06773aab70c16bbbfd4835be1bf6037c}{Kayla Reed was born in a predominantly African American section of St. Louis where, like her own kin, many Black families had been transplanted out of the Deep South. After the death of her grandmother, Reed moved with her father from the...}