\entryitemWithDescription{\hskip 0pt{}Trump indictment would be unprecedented moment in US history}{https://apnews.com/article/fec69a819de645549f10c0ab61f3ea72}{FILE - Former President Donald J. Trump watches the NCAA Wrestling Championships, Saturday, March 18, 2023, in Tulsa, Okla. Trump's calls for protests ahead of his anticipated indictment in New York have generated mostly muted reactions...}

\entryitemWithDescription{\hskip 0pt{}Hall of Fame coach Rick Pitino accepts job at St. John's}{https://apnews.com/article/e705cbdf6f60028c392ecaf670199b5a}{Iona head coach Rick Pitino calls out during the second half of an NCAA college basketball game against the Marist in the championship of the Metro Atlantic Athletic Conference Tournament, Saturday, March 11, 2023, in Atlantic City N.J...}

\entryitemWithDescription{\hskip 0pt{}Idaho poised to allow firing-squad executions in some cases}{https://apnews.com/article/410bd284ffbdb50d3b4a162fe8088dad}{FILE - The execution chamber at the Idaho Maximum Security Institution is shown as Security Institution Warden Randy Blades look on in Boise, Idaho on Oct. 20, 2011. A bill that would allow Idaho to kill condemned inmates by firing squad...}

\entryitemWithDescription{\hskip 0pt{}Pay transparency is spreading. Here's what you need to know}{https://apnews.com/article/0e4b2754b08d4e1ab4ffd2708cd759f7}{FILE - Hiring signs are displayed at a grocery store in Arlington Heights, Ill., Jan. 13, 2023. Employers are increasingly posting salary ranges for job openings, even in states where it\textquotesingle s not mandated by law, according to...}

\entryitemWithDescription{\hskip 0pt{}Biden issues first veto, taking on new Republican House}{https://apnews.com/article/5971f2ee28c04b7dd8727606185cc53f}{President Joe Biden waves as he walks to Marine One upon departure from the South Lawn of the White House, Friday, March 17, 2023, in Washington. Biden is headed to Delaware. (AP Photo/Alex Brandon) WASHINGTON (AP) --- President Joe Biden...}

\entryitemWithDescription{\hskip 0pt{}Jury convicts 3 of murder in death of rapper XXXTentacion}{https://apnews.com/article/56ba2e060ff65d639d0a87ffb04e63fa}{Trayvon Newsome, left, Dedrick Williams and Michael Boatwright were found guilty of first-degree murder of XXXTentacion at the Broward County Courthouse in Fort Lauderdale on Monday, March 20, 2023. (Carline Jean/South Florida Sun...}

\entryitemWithDescription{\hskip 0pt{}Will the Credit Suisse bank takeover calm financial fears?}{https://apnews.com/article/4eb7f8e70849072b13d067382230d448}{The logos of the Swiss banks UBS and Credit Suisse are displayed on different buildings in Geneva, Switzerland, Monday, March 20, 2023. Shares of Credit Suisse plunged 60.5\% on Monday after banking giant UBS said it would buy its...}

\entryitemWithDescription{\hskip 0pt{}The big problem for endangered orcas? Inbreeding}{https://apnews.com/article/fea3de9d4d20ff6e4ee8d37b1c5a78f2}{FILE - This Sept. 2015, photo provided by NOAA Fisheries shows an aerial view of adult female Southern Resident killer whale (J16) swimming with her calf (J50). New research suggests that inbreeding may be a key reason that the Pacific...}

\entryitemWithDescription{\hskip 0pt{}Miami Beach struggles with spring break violence, big crowds}{https://apnews.com/article/8b72d3ad074f087025fbcd828ce6c79c}{Crowds walk up and down Ocean Drive during spring break on Saturday, March 18, 2023, in Miami Beach, Fla. Miami Beach officials imposed a curfew beginning Sunday night, March 19, after two fatal shootings and rowdy, chaotic crowds that...}

\entryitemWithDescription{\hskip 0pt{}US: War crimes on all sides in Ethiopia's Tigray conflict}{https://apnews.com/article/da5d9ac7c900c58cc34b9ca5d4156667}{Secretary of State Antony Blinken departs a briefing on the 2022 Country Reports on Human Rights Practices at the State Department in Washington, Monday, March 20, 2023. (AP Photo/Andrew Harnik) WASHINGTON (AP) --- The Biden...}

\entryitemWithDescription{\hskip 0pt{}Paris aims to keep Olympians cool without air conditioners}{https://apnews.com/article/78b47a6f1bf0e1fcae9889cce9debcd9}{The Olympic athletes\textquotesingle{} village construction site is pictured In Saint Denis, outside Paris, Saturday, March 18, 2023. Some Paris 2024 Olympic hopefuls have expressed concern over the lack of air conditioning units in the...}

\entryitemWithDescription{\hskip 0pt{}Amazon cuts 9,000 more jobs, bringing 2023 total to 27,000}{https://apnews.com/article/0e857f39702de134c8f677c5b5731688}{FILE - An Amazon logo appears on a delivery van, Oct. 1, 2020, in Boston. Amazon plans to eliminate 9,000 more jobs in the next few weeks, the company\textquotesingle s CEO Andy Jassy said in a memo to staff on Monday, March 20, 2023. The...}

\entryitemWithDescription{\hskip 0pt{}US aid worker and French journalist freed in West Africa}{https://apnews.com/article/b94936724080252ad5a1a3070b986d2a}{French journalist Olivier Dubois, left, and American aid worker Jeffery Woodke, center, arrive at the VIP lounge at the airport in Niamey, Niger, Monday March 20, 2023. Woodke was held by Islamic extremists in West Africa for more than...}