\entryitemWithDescription{\hskip 0pt{}TikTok CEO Shou Zi Chew: 3 things to know}{https://apnews.com/article/7927b1915db270aac67ca6f4ca31d6f3}{TikTok CEO Shou Zi Chew testifies during a hearing of the House Energy and Commerce Committee, on the platform\textquotesingle s consumer privacy and data security practices and impact on children, Thursday, March 23, 2023, on Capitol...}

\entryitemWithDescription{\hskip 0pt{}Large asteroid coming close, but zero chance of hitting us}{https://apnews.com/article/41b098de72903cbfdfe3b416ad02c712}{This photo provided by Gianluca Masi shows asteroid 2023 DZ2, indicated by arrow at center, about 1.8 million kilometers (1.1 million miles) away from the Earth on March 22, 2023. On Saturday, March 25, 2023, the asteroid, big enough to...}

\entryitemWithDescription{\hskip 0pt{}Rioter charged in Pelosi laptop theft sentenced to prison}{https://apnews.com/article/19b5423e4fc70b2a698b140f13ead1be}{FILE - Riley June Williams, of Harrisburg, Pa., leaves Dauphin County Prison after being released on Jan. 21, 2021, in Harrisburg. Williams, a Pennsylvania woman linked to a far-right extremist movement, was sentenced on Thursday, March...}

\entryitemWithDescription{\hskip 0pt{}Feel your pain? Even fish can show they care}{https://apnews.com/article/800d30fd9058df836e12e70cf5311b9f}{In this photo provided by researcher Rui F. Oliveira, a zebrafish, bottom, is monitored to see its reaction to a video of another at a laboratory in Oeiras, Portugal in March 2023. A study published on Thursday, March 23, 2023, in the...}

\entryitemWithDescription{\hskip 0pt{}Track bans transgender athletes, tightens rules for Semenya}{https://apnews.com/article/f3499b00b932948f96838adb3b010f11}{FILE - South African long distance athlete Caster Semenya on her way to winning the 5,000 meters at the South African national championships in Pretoria, South Africa, Thursday, April 15, 2021. Track and field banned transgender athletes...}

\entryitemWithDescription{\hskip 0pt{}Trump arrested? Putin jailed? Fake AI images spread online}{https://apnews.com/article/42ac9c41c5504d05412b492e48bcaded}{Images created by Eliot Higgins with the use of artificial intelligence show a fictitious skirmish with Donald Trump and New York City police officers posted on Higgins\textquotesingle{} Twitter account, as photographed on an iPhone in...}

\entryitemWithDescription{\hskip 0pt{}Autism now more common among Black, Hispanic kids in US}{https://apnews.com/article/e38179682e2759b0aff9c017bf7ebf61}{FILE - Deleah Payne, 12, center, spends time with her mother Delisa, right, and 6-year-old sister Delynn, left, as they watch movie clips on their living room television in Evansville, Ind., Tuesday evening, Aug. 27, 2019. Deleah and...}

\entryitemWithDescription{\hskip 0pt{}DeSantis walks back 'territorial dispute' remark on Ukraine}{https://apnews.com/article/f44acc03f772f393b7f8d452ee26508a}{FILE - Florida Gov. Ron DeSantis answers questions from the media in the Florida Cabinet following his State of the State address during a joint session of the Senate and House of Representatives, Tuesday, March 7, 2023, at the state...}

\entryitemWithDescription{\hskip 0pt{}Authorities: 1 person fatally shot during rescue of migrants}{https://apnews.com/article/a800f9297f3b0ff58e19c5cea9854a4e}{The FBI works on the scene of a shooting, Thursday, March 23, 2023 in north Houston. Officials say one person has been fatally shot during a hostage rescue in Houston. In a statement, the FBI\textquotesingle s Houston office said agents...}

\entryitemWithDescription{\hskip 0pt{}Fetterman expected back 'soon,' but no certain timeline yet}{https://apnews.com/article/92389fd53a868388c8caeed1410638c4}{FILE - Sen. John Fetterman, D-Pa., leaves an intelligence briefing on the unknown aerial objects the U.S. military shot down this weekend at the Capitol in Washington, Feb. 14, 2023. Fetterman\textquotesingle s office expects him to...}

\entryitemWithDescription{\hskip 0pt{}South Carolina's top accountant to resign after \$3.5B error}{https://apnews.com/article/fc484da73385fcdf3d2ef52d8a8d5576}{FILE - South Carolina Comptroller General Richard Eckstrom holds up a book he wanted to present to his new Chief of Staff James Holly during his introduction at the Budget and Control Board meeting, Aug. 13, 2009, in Columbia, S.C...}

\entryitemWithDescription{\hskip 0pt{}Oxford school shooter's parents can face manslaughter trial}{https://apnews.com/article/654c839914eb3a36ae43a7bc8dd9bacd}{FILE - Jennifer Crumbley, left, and James Crumbley, right, the parents of Ethan Crumbley, a teenager accused of killing four students in a shooting at Oxford High School in Oxford, Mich., appear in court for a preliminary examination on...}

\entryitemWithDescription{\hskip 0pt{}Nebraska trans health bill advances, despite filibuster vow}{https://apnews.com/article/64a472a752c9e8e156e7bca929d90a34}{From left, Nebraska Sens. Jen Day and Danielle Conrad hug on the floor of the Nebraska Legislature during emotional debate of a bill that would ban gender-affirming care for anyone 18 and younger in the state on Thursday, March 23, 2023...}