\entryitemAp{\hskip 0pt{}On King's holiday, daughter calls for bold action over words}{https://apnews.com/article/23561f7530a214e0a5920e915c836a13}{A large group gathers to watch a wreath-laying ceremony at the Martin Luther King Jr. Memorial on Martin Luther King Jr. Day in Washington, Monday, Jan. 16, 2023. (AP Photo/Andrew Harnik) President Joe Biden attended a Martin Luther King...}

\entryitemAp{\hskip 0pt{}More rain, snow in California from ninth in series of storms}{https://apnews.com/article/65002e8533c845b6b21c5eaf9a122ce9}{Ryan Orosco, of Brentwood, carries his wife Amanda Orosco, from their flooded home on Bixler Road in Brentwood, Calif., on Monday, Jan. 16, 2023. The last in a three-week series of major winter storms is churning through California. (Jose...}

\entryitemAp{\hskip 0pt{}Baby, teen mom among 6 killed in shooting at California home}{https://apnews.com/article/7211a6a632693ee5116517ee35944575}{Six people --- including a 17-year-old mother and her 6-month-old baby --- were killed in a shooting early Monday at a home in central California, and authorities are searching for at least two suspects, sheriff\textquotesingle s...}

\entryitemAp{\hskip 0pt{}Houston, KU stay atop Top 25 while FAU enters for 1st time}{https://apnews.com/article/847e686192fe691ff233791e7cbd72b1}{Houston\textquotesingle s Marcus Sasser (0) celebrates with Jamal Shead (1) after making a basket while being fouled during the second half of an NCAA college basketball game against the South Florida Wednesday, Jan. 11, 2023, in Houston...}

\entryitemAp{\hskip 0pt{}Embattled actor Kevin Spacey in Italy to receive award}{https://apnews.com/article/620649f2f4ca00ef0fc4b853ba16c9b2}{Actor Kevin Spacey smiles as he arrives at the Cinema Massimo in Turin, Italy, Monday, Jan. 16, 2023. Kevin Spacey was in the northern Italian city of Turin on Monday to receive the lifetime achievement award, teach a master class and...}

\entryitemAp{\hskip 0pt{}Jill Biden's skin cancer could fuel advocacy in cancer fight}{https://apnews.com/article/5a441b53e825895d029d0255c10816d3}{FILE - First Lady Jill Biden hosts a conversation on women\textquotesingle s empowerment at the residence of the US ambassador in Mexico City, on Jan. 9, 2023. (AP Photo/Ginnette Riquelme, File) WASHINGTON (AP) --- Jill Biden...}

\entryitemAp{\hskip 0pt{}Economic woes, war, climate change on tap for Davos meeting}{https://apnews.com/article/25e850c634345a57ac2621019b90edf9}{A police officer stands on the roof of a hotel and monitore the are with a binocular in Davos, Switzerland Monday, Jan. 16, 2023. The annual meeting of the World Economic Forum is taking place in Davos from Jan. 16 until Jan. 20, 2023...}

\entryitemAp{\hskip 0pt{}Elon Musk's next drama: a trial over his tweets about Tesla}{https://apnews.com/article/f6f0e8de56e2ac55a7a0d4ab9d6f1758}{FILE - Tesla and SpaceX Chief Executive Officer Elon Musk speaks at the SATELLITE Conference and Exhibition in Washington. A federal judge on Friday, Jan. 13 2023 rejected Tesla CEO Elon Musk's bid to move or delay a trial over a...}

\entryitemAp{\hskip 0pt{}Arizona dad seeking answers after son dies in state care}{https://apnews.com/article/3d62d90cd53136510122df5df0c563b4}{This 2022 photo provided by Richard Blodgett shows Blodgett and his son, Jakob. Blodgett was arrested in December, and Jakob was placed in a foster home under the Arizona Department of Child Safety where he developed complications from...}

\entryitemAp{\hskip 0pt{}In India, deity decorating a calling for Hindu temple artist}{https://apnews.com/article/b923af321098373475913c2619214f2d}{S. Goutham lays the foundation for an elaborate decoration of a deity at the Anantha Padmanabha Swamy Temple in Chennai, India, on Nov. 29, 2022. Goutham is a fifth-generation practitioner of this millennia-old spiritual art of decorating...}

\entryitemAp{\hskip 0pt{}Italian film legend Gina Lollobrigida dies at age 95}{https://apnews.com/article/35ab673787e5ce2c2c6f5fdf96bb0f59}{FILE - German actor Horst Buchholz kisses the hand of Italian actress Gina Lollobrigida, during the International Film Festival (Berlinale) in Berlin, Germany, July 5, 1958. (AP Photo/Werner Kreusch, File) Lollobrigida has died in Rome at...}

\entryitemAp{\hskip 0pt{}As elites arrive in Davos, conspiracy theories thrive online}{https://apnews.com/article/0193732c04074e595852c160d7ca1c86}{People set up the stage at the eve of the opening of the World Economic Forum in Davos, Switzerland, Sunday, Jan. 15, 2023. The annual meeting of the World Economic Forum is taking place in Davos from Jan. 16 until Jan. 20, 2023. (AP...}

\entryitemAp{\hskip 0pt{}Thousands turn out to bid farewell to Greece's former king}{https://apnews.com/article/30e833f63141628673dcb273d4fb76fb}{A man holds a picture of the former king of Greece Constantine with his wife, as others wait to enter in the Chapel of Saint Eleftherios as the coffin of the former king of Greece Constantine lies in repose in Athens, Monday, Jan. 16...}