\entryitemWithDescription{\hskip 0pt{}'Super Mario Bros. Movie' hits \$1B, is No. 1 for 4 weeks}{https://apnews.com/article/056f67aaca51962f3ef33e5aca06666c}{This image released by Nintendo and Universal Studios shows Mario, voiced by Chris Pratt, left, and Luigi, voiced by Charlie Day in Nintendo\textquotesingle s "The Super Mario Bros. Movie." (Nintendo and Universal Studios via AP) NEW...}

\entryitemWithDescription{\hskip 0pt{}Willie Nelson inhales the love at 90th birthday concert}{https://apnews.com/article/0ceb4d12f0362a910eb920cbf53d781b}{Country music legend Willie Nelson finishes his set at the Outlaws \& Legends Music Fest in Abilene, Texas, on Saturday, April 1, 2023. Nelson, who will turn 90 this month, was the headlining act for the two-day festival, fulfilling a...}

\entryitemWithDescription{\hskip 0pt{}Chinese who reported on COVID to be released after 3 years}{https://apnews.com/article/b540f6458bc782b916dcd3aaa3571c12}{Visitors gather near a portrait of Sun Yat-sen, who is widely regarded as the founding father of modern China, at Tiananmen Square during the May Day holiday period in Beijing, Sunday, April 30, 2023. (AP Photo/Andy Wong) HONG KONG...}

\entryitemWithDescription{\hskip 0pt{}Pope in final Mass in Budapest urges Hungary to open doors}{https://apnews.com/article/95ecb5c9d714c75a39553707c6f2075e}{Pope Francis arrives for a mass in Kossuth Lajos\textquotesingle{} Square in Budapest, Hungary, Sunday, April 30, 2023. (AP Photo/Darko Vojinovic) BUDAPEST, Hungary (AP) --- Pope Francis urged Hungarians to open their doors to others on...}

\entryitemWithDescription{\hskip 0pt{}`Woolly delinquents' celebrate Charles' coronation in yarn}{https://apnews.com/article/8c85f520b653e95dac3ee996ec79388f}{Heather and David Howarth adjust a knitted figure of Britain\textquotesingle s King Charles III fitted to a post during a pre-coronation \textquotesingle yarn bombing\textquotesingle{} in the village of Hurst, near Reading, England...}

\entryitemWithDescription{\hskip 0pt{}Battle for late Johnny Winter's music to play out in court}{https://apnews.com/article/d02ecbc4fde386298d5e6d342f4828e8}{FILE - Johnny Winter performs at the New Orleans Jazz \& Heritage Festival at Fair Grounds Race Course in New Orleans, May 3, 2014. Nearly nine years after Johnny Winter\textquotesingle s death, a battle for control of the legendary blues...}

\entryitemWithDescription{\hskip 0pt{}Roof collapse at house near Ohio State University injures 14}{https://apnews.com/article/75e70c82bbc08c5c59c44cde534122ba}{This image provided by WSYX shows people standing in front of a house where the roof collapsed in Columbus, Ohio, Saturday, April 29, 2023. Authorities say part of a house collapsed and 14 people were injured near The Ohio State...}

\entryitemWithDescription{\hskip 0pt{}AP Report Cards: Texans, Eagles get highest NFL draft grades}{https://apnews.com/article/6c5f5e93e17d4d5b304ef01655760cc2}{Houston Texans quarterback C.J. Stroud answers questions during an introductory news conference, Friday, April 28, 2023, in Houston. Stroud was selected in the first round by the Texans in the NFL football draft Thursday. (AP Photo/Kevin...}

\entryitemWithDescription{\hskip 0pt{}New Orleans restaurant shooting kills waiter, wounds tourist}{https://apnews.com/article/2bf62f055098a71e96ff42f4623b5d5d}{NEW ORLEANS (AP) --- A shooting outside a well-known New Orleans restaurant Friday killed an employee, and one bullet penetrated the restaurant and wounded a Chicago tourist visiting for the New Orleans Jazz and Heritage Festival. Interim...}

\entryitemWithDescription{\hskip 0pt{}Texas border city struggles with large arrival of migrants}{https://apnews.com/article/86bd7acbf3f13167db8d2197607fa940}{A group of people leave a welcome center for migrants in Brownsville, Texas, Friday, April 28, 2023. The city of Brownsville signed a disaster declaration after nearly 15,000 migrants crossed through the area, with many of them screened...}

\entryitemWithDescription{\hskip 0pt{}California man gets 4 1/2 years for role in US Capitol riot}{https://apnews.com/article/ba436979d4b21608f39aca61f5f8f6cd}{FILE - People loyal to President Donald Trump storm the U.S. Capitol on Jan. 6, 2021, in Washington. Federal authorities say a Southern California man who assaulted police with pepper spray during the storming of the U.S. Capitol was...}

\entryitemWithDescription{\hskip 0pt{}General Mills issues flour recall after salmonella discovery}{https://apnews.com/article/7a67fb9fd3238ed7d4a23b18730cfc2c}{MINNEAPOLIS, Minn. (AP) --- General Mills has issued a nationwide recall of its bleached and unbleached flour after discovering salmonella during a sampling of a 5-pound (2.3-kilogram) bag. The company is recalling 2-, 5- and 10-pound (0...}

\entryitemWithDescription{\hskip 0pt{}NYC partly shutters 4 parking garages after deadly collapse}{https://apnews.com/article/8b6c06aaf3382508642b255b18f47a8c}{FILE --- Cars are seen piled on top of each other at the scene of a partial collapse of a parking garage in the Financial District of New York, April 18, 2023, in New York. After the deadly collapse of a parking structure in lower...}