\entryitemWithDescription{\hskip 0pt{}Trump refers to Milwaukee as `horrible' just before the city hosts the Republican convention}{https://apnews.com/article/604fe33acb5606e9db1cbf3f966507e3}{MADISON, Wis. (AP) --- Former President Donald Trump used the word ``horrible'' in talking about Milwaukee --- the city where he will accept the Republican nomination next month --- during a closed-door meeting Thursday with GOP...}

\entryitemWithDescription{\hskip 0pt{}Sen. John Fetterman was at fault in car accident and seen going `high rate of speed,' police say}{https://apnews.com/article/d714084a1b17a23f233f2733c5694b5a}{HARRISBURG, Pa. (AP) --- Pennsylvania Sen. John Fetterman was seen driving at a ``high rate of speed'' on Sunday morning just before he rear-ended another car on Interstate 70 in Maryland, according to a state police report. The police...}

\entryitemWithDescription{\hskip 0pt{}A gray wolf was killed in southern Michigan. Experts remain stumped about how it got there.}{https://apnews.com/article/caadd0bc4c0eefb5faa334d0c1a5a960}{Wildlife experts have hit a dead end in their quest to determine how a gray wolf arrived in southern Michigan for the first time in more than 100 years. The wolf was killed in January by a hunter who told authorities that he had mistaken...}

\entryitemWithDescription{\hskip 0pt{}Large whale group spotted off New England includes orca eating a tuna, dozens of endangered species}{https://apnews.com/article/11a3e62c35dbb0c737f23ed34b74039e}{A large number of whales visiting the waters off New England included an uncommon sighting of an orca eating a tuna and an unusually large group of an endangered species of whale, scientists said. A research flight made 161 sightings of...}

\entryitemWithDescription{\hskip 0pt{}Puerto Rico restores power after a massive blackout as lawmakers call for a state of emergency}{https://apnews.com/article/029e3452bfe5910ce0a6f02d028c5cde}{BAYAMÓN, Puerto Rico (AP) --- A power company in Puerto Rico announced Thursday that it has restored electricity to most areas affected by a massive outage that hit the U.S. territory the previous day. The outage left over 340,000...}

\entryitemWithDescription{\hskip 0pt{}One Tech Tip: Use a roaming eSIM on your summer travels to avoid cellphone data fees}{https://apnews.com/article/eb192d2a7830ce901e4cab9389958e56}{LONDON (AP) --- For summer trips overseas, a smartphone is essential for most people. How else will you check Google Maps to find your Airbnb, post an Instagram video from the Eiffel Tower, or WhatsApp friends and family back home? Of...}

\entryitemWithDescription{\hskip 0pt{}Tom Brady enshrined into Patriots Hall of Fame during star-studded night}{https://apnews.com/article/d97884524e6d1a554f72e734dfaf399f}{FOXBOROUGH, Mass. (AP) --- Tom Brady brought the New England Patriots endless memories and six Super Bowl trophies during his two-decade run with the team. The Patriots made sure his induction into the franchise's Hall of Fame was a...}

\entryitemWithDescription{\hskip 0pt{}Joey Chestnut, Takeru Kobayashi to compete in Netflix hot dog eating competition}{https://apnews.com/article/2ca97d0a8a1a6ceb40ea681b5f0a57b5}{LOS ANGELES (AP) --- After organizers for Nathan's Famous Fourth of July hot dog-eating contest said Joey Chestnut wouldn't compete this year because of a deal with a rival brand, Netflix swiftly announced a new hot dog-eating competition...}

\entryitemWithDescription{\hskip 0pt{}Young bear spotted relaxing on a hammock in a Vermont yard}{https://apnews.com/article/e990b0047b1c5a1c2295422500b9fe98}{WAITSFIELD, Vt. (AP) --- Noah and Kristen Dweck have seen a number of black bears around their home in Vermont but this was a first: a bear relaxing on their hammock. Noah Dweck took iPhone video of two young bears in their yard in...}

\entryitemWithDescription{\hskip 0pt{}Florida's 2024 hurricane season arrives with a rainy deluge}{https://apnews.com/article/a37631902e119c0036d1fd51da2dba15}{The annual rainy season has arrived with a wallop in much of Florida, where a disorganized disturbance of tropical weather from the Gulf of Mexico has caused street flooding and triggered tornado watches but so far has not caused major...}

\entryitemWithDescription{\hskip 0pt{}Wreck of the last ship of famed Anglo-Irish explorer Shackleton found off the coast of Canada}{https://apnews.com/article/1b814ad4f88806980d687eeb7dce466b}{ST. JOHN'S, Newfoundland (AP) --- The wreck of the last ship belonging to Sir Ernest Shackleton, a famous Irish-born British explorer of Antarctica, has been found off the coast of Labrador in Canada, 62 years after it went missing. The...}

\entryitemWithDescription{\hskip 0pt{}Matty Healy's mom says The 1975 singer and model Gabbriette Bechtel are engaged}{https://apnews.com/article/bd658488094c931591a9eac884575849}{The 1975's Matty Healy and model Gabbriette Bechtel are engaged, accordingly to Healy's mother, the English actor Denise Welch. Welch, a regular panelist on the ITV talk show ``Loose Women,'' confirmed the news Wednesday on the U.K...}

\entryitemWithDescription{\hskip 0pt{}Denmark recalls 3 spicy instant noodle soup brands from South Korea used in online food challenges}{https://apnews.com/article/f622b2d901990a08d180eee3ce2260f2}{COPENHAGEN, Denmark (AP) --- Food authorities in Denmark have recalled three types of spicy instant noodle products imported from South Korea over possible risks for ``acute poisoning.'' Consumers are asked to discard them or return the...}