\entryitemWithDescription{\hskip 0pt{}Banksy London Zoo mural offers clue to why wild animals have been appearing all over city}{https://apnews.com/article/870717fa5e2328245758a59288f23c37}{LONDON (AP) --- Workers arriving at the London Zoo early Tuesday were surprised to discover an unexpected exhibit that suggested the animals were being set free. A mural by elusive street artist Banksy showed a gorilla holding up the...}

\entryitemWithDescription{\hskip 0pt{}Before lobster, Maine had a thriving sardine industry. A sunken ship reminds us of its storied past}{https://apnews.com/article/5c2bafbb60c003f61e91d5d034a59bb1}{PORTLAND, Maine (AP) --- An 83-foot (25-meter) motor boat that was one of the first refrigerated sardine carriers during the heyday of Maine's sardine industry is going to be scrapped after a recovery operation to retrieve the sunken...}

\entryitemWithDescription{\hskip 0pt{}Ford, Mazda warn owners to stop driving older vehicles with dangerous Takata air bag inflators}{https://apnews.com/article/3eb0b90b47c9d1417c15704db0b99f80}{DETROIT (AP) --- Ford and Mazda are warning the owners of more than 475,000 older vehicles in the U.S. not to drive them because they have dangerous Takata air bag inflators that have not been replaced. The warning issued Tuesday covers...}

\entryitemWithDescription{\hskip 0pt{}A burglary is reported at a Trump campaign office in Virginia}{https://apnews.com/article/073d9a821f1f2e58898126760ec5ff42}{ASHBURN, Va. (AP) --- A burglary was reported over the weekend at a Virginia campaign office for former President Donald Trump, and authorities are investigating whether anything was stolen. It happened Sunday at an office in Ashburn...}

\entryitemWithDescription{\hskip 0pt{}Starbucks replaces its CEO, names Chipotle chief to head the company}{https://apnews.com/article/0173c2b9189c808968613b1285c1c366}{Starbucks, struggling with weak demand and disgruntled investors, said Tuesday that CEO Laxman Narasimhan is stepping down after a little more than a year in the job. The Seattle coffee giant said Brian Niccol, the chairman and CEO of...}

\entryitemWithDescription{\hskip 0pt{}The Berlin Zoo is hoping for more German-born giant pandas as scans confirm a pregnancy}{https://apnews.com/article/a50290f10392389d5036c051a30bf725}{BERLIN (AP) --- The Berlin Zoo has much anticipated news: Meng Meng the panda is pregnant again, months after the first giant pandas born in Germany were sent to China. The zoo said Tuesday that ultrasound scans over the weekend showed...}

\entryitemWithDescription{\hskip 0pt{}Musk's interview with Trump marred by technical glitches}{https://apnews.com/article/51dfc560065aae825e6bb3f826090e4b}{Elon Musk's much-awaited interview with former President Donald Trump was marred by technical glitches on Monday, with people unable to join the audio conversation on X's Spaces platform. Eighteen minutes into an interview that was...}

\entryitemWithDescription{\hskip 0pt{}Jordan Chiles medal inquiry: USA Gymnastics says arbitration panel won't reconsider decision}{https://apnews.com/article/b982ecfff1e846c57b0e1cb524a84cad}{USA Gymnastics officials say an arbitration panel won't reconsider a decision asking gymnast Jordan Chiles to return the bronze medal she was awarded in the floor exercise at the Paris Olympics. USA Gymnastics says it will continue...}

\entryitemWithDescription{\hskip 0pt{}Arkansas officer fired after being caught on video beating inmate in back of patrol car}{https://apnews.com/article/94c962a1ba5f9b8b276ef00aee5c5424}{LITTLE ROCK, Ark. (AP) --- An Arkansas police officer has been fired after he was caught on video beating a handcuffed inmate in the back of his patrol car, and the police chief says he will refer the case to prosecutors. Jonesboro Police...}

\entryitemWithDescription{\hskip 0pt{}Jarren Duran suspended 2 games by Red Sox for shouting homophobic slur at fan who heckled him}{https://apnews.com/article/dbe97544ad2996f806bc764344fbbe93}{BOSTON (AP) --- The Boston Red Sox suspended Jarren Duran for two games on Monday without pay after he shouted a homophobic slur to a fan behind home plate who heckled him in a loss to the Houston Astros a day earlier. The exchange that...}

\entryitemWithDescription{\hskip 0pt{}An earthquake with a magnitude of 4.6 has struck the Los Angeles area, the USGS says}{https://apnews.com/article/81200455548c77cd95698536bdc5e919}{LOS ANGELES (AP) --- An earthquake with a magnitude of 4.6 has struck the Los Angeles area, the U.S. Geological Survey said Monday. People reported feeling it strongly across the Los Angeles area. A medical building shook and residents...}

\entryitemWithDescription{\hskip 0pt{}Haason Reddick has requested a trade from the Jets after being a camp holdout, AP source says}{https://apnews.com/article/e1d0b14ca7641fef3a92dc48e0a7b284}{FLORHAM PARK, N.J. (AP) --- Haason Reddick has requested a trade from the New York Jets after holding out from training camp while seeking a new contract, a person familiar with the situation told The Associated Press. The star edge...}

\entryitemWithDescription{\hskip 0pt{}Browns' plans for move to new dome stadium hits snag as county backs city's renovation proposal}{https://apnews.com/article/66055b5ad70ae6bf18e5057927dbba6d}{CLEVELAND (AP) --- The Browns' proposal to leave the lakefront and play in a new domed stadium in Cleveland's suburbs has hit a major snag. In a letter sent to team owners Dee and Jimmy Haslam, Cuyahoga County officials said Sunday they'...}