\entryitemWithDescription{\hskip 0pt{}New streaming app to 'Max' programming from HBO, Discovery}{https://apnews.com/article/9a662dfab76d312bc2af4d9cb13b9b98}{FILE - Sarah Snook, from left, Alan Ruck, Brian Cox, Jeremy Strong and Kieran Culkin attend the premiere of HBO\textquotesingle s "Succession" season four at Jazz at Lincoln Center on March 20, 2023, in New York. Warner Bros. Discovery...}

\entryitemWithDescription{\hskip 0pt{}Pet arrives home, dog-tired, after Alaskan sea-ice odyssey}{https://apnews.com/article/6f0fd32a87d17da49d2423eebefd680e}{In this photo provided by Mandy Iworrigan is Nanuq, in the middle with Brooklyn Faith, after the 1-year-old Australian shepherd was returned to Gambell, Alaska, on April 6, 2023, after it disappeared for a month and walked on the Bering...}

\entryitemWithDescription{\hskip 0pt{}An Escobar hippo killed in highway collision in Colombia}{https://apnews.com/article/7f3d2decaa8092eae7d3373847ae4c78}{FILE - A hippo swims in the Magdalena river in Puerto Triunfo, Colombia, Feb. 16, 2022. A hippopotamus descended from animals illegally brought to Colombia by the late drug kingpin Pablo Escobar has died in a collision with an SUV on a...}

\entryitemWithDescription{\hskip 0pt{}French investigative site claims Depardieu groped extras}{https://apnews.com/article/892968238e0daa4bc37d8f21637f6c5d}{FILE - Actor Gerard Depardieu attends the premiere of the movie "Tour de France" in Paris, France, Monday, Nov. 14, 2016. A French investigative news website claims that the actor Gérard Depardieu harassed, groped or sexually assaulted 13...}

\entryitemWithDescription{\hskip 0pt{}Michigan researchers find 1914 shipwrecks in Lake Superior}{https://apnews.com/article/2e0b4a2a8b5c2ebae589c964cadfe7c9}{In this image taken from video provided by the Great Lakes Shipwreck Historical Society, lettering identifying the wrecked ship as property of the Edward Hines Lumber Company is seen in Lake Superior in August 2022. (Great Lakes Shipwreck...}

\entryitemWithDescription{\hskip 0pt{}Judge admonishes Fox lawyers over evidence gap in libel case}{https://apnews.com/article/20e668b60238b93b857aa63d56525c65}{FILE - Rupert Murdoch introduces Secretary of State Mike Pompeo during the Herman Kahn Award Gala on Oct. 30, 2019, in New York. The judge presiding over a voting machine company's defamation lawsuit against Fox denied the company's...}

\entryitemWithDescription{\hskip 0pt{}Students' 1976 bicentennial mural on dam being replaced}{https://apnews.com/article/f9efa2efd818b561b81c8621c358fa90}{FILE - Seen is the Prado Dam with its bicentennial mural at a time when crews were working to close a breach in the dam, at left, due to heavy rains in Corona, Calif., on Jan. 14, 2005. A giant mural that students painted on a Southern...}

\entryitemWithDescription{\hskip 0pt{}Metallica returns with '72 Seasons'; band not slowing down}{https://apnews.com/article/ae3ae3b993d9de1d560f05fa6fe0abae}{FILE - James Hetfield, left, and Kirk Hammett of Metallica perform during the Global Citizen Festival on Saturday, Sept. 24, 2022, at Central Park in New York. Metallica\textquotesingle s latest album, "72 Seasons," releases Friday...}

\entryitemWithDescription{\hskip 0pt{}Hundreds forced from Indiana homes as plastics fire burns}{https://apnews.com/article/601a621343fff987747e99d7136d45b3}{Firefighters walk out of the site of an industrial fire in Richmond, Ind., Wednesday, April 12, 2023. Authorities urged people to evacuate if they live near the fire. The former factory site was used to store plastics and other materials...}

\entryitemWithDescription{\hskip 0pt{}Prince Harry will attend father's coronation, Meghan won't}{https://apnews.com/article/ed88499c6fdab56d0b502fce0186d62f}{FILE - Britain\textquotesingle s Prince Harry arrives in the gardens of Buckingham Palace in London, Jan 16, 2020. Buckingham Palace says Prince Harry will attend the Coronation service of his father, King Charles III, at Westminster...}

\entryitemWithDescription{\hskip 0pt{}Buffett says people shouldn't worry about Berkshire, banks}{https://apnews.com/article/2e6146a64b0d196b9ceea904c5af37df}{FILE - Warren Buffett, Chairman and CEO of Berkshire Hathaway, speaks during a game of bridge following the annual Berkshire Hathaway shareholders meeting on May 5, 2019, in Omaha, Neb. Buffett assured investors Wednesday, April 12, 2023...}

\entryitemWithDescription{\hskip 0pt{}3 Sherpa climbers missing after falling on Mount Everest}{https://apnews.com/article/747a3f146de07be22852c5d433b184f2}{KATHMANDU, Nepal (AP) --- Three Sherpa climbers were missing Wednesday after they fell into a deep crevasse on a treacherous section of Mount Everest just above the base camp, a Nepalese mountaineering official said. They fell into the...}

\entryitemWithDescription{\hskip 0pt{}Musk says owning Twitter 'painful' but needed to be done}{https://apnews.com/article/c0addadac3226b016e14b835e3745e62}{FILE - Elon Musk departs the Phillip Burton Federal Building and United States Court House in San Francisco on Jan. 24, 2023. Billionaire Elon Musk has told the BBC that running Twitter has been ``quite painful'' but that the social media...}