\entryitemWithDescription{\hskip 0pt{}Sacha Baron Cohen and Isla Fisher say they filed for divorce}{https://apnews.com/article/a3d891690b52684f8f9ac8e8227215da}{Sacha Baron Cohen and Isla Fisher say they filed for divorce last year after more than 20 years together. The English ``Borat'' star and the Australian ``Wedding Crashers'' actor who married in 2010 announced their split Friday in joint...}

\entryitemWithDescription{\hskip 0pt{}P\&G recalls 8.2 million bags of Tide, Gain and other laundry detergents over packaging defect}{https://apnews.com/article/58ee3ebe15ec343892287cee9968cd0b}{NEW YORK (AP) --- Procter \& Gamble is recalling more than 8 million bags of Tide, Gain, Ace and Ariel laundry detergent packets sold in the U.S. and Canada due to a defect in the products' child-resistant packaging. According to Friday...}

\entryitemWithDescription{\hskip 0pt{}What to know about the \$30 million cash heist in Los Angeles}{https://apnews.com/article/d34b769be34cbafcca14a897967d3bb2}{LOS ANGELES (AP) --- A brazen Los Angeles cash heist on Easter weekend in which thieves cracked a safe and got away with as much as \$30 million is believed to be one of the largest such heists in U.S. history. The heist has triggered...}

\entryitemWithDescription{\hskip 0pt{}Mikaela Shiffrin and Aleksander Aamodt Kilde announce their engagement}{https://apnews.com/article/ef9c73882f35a3a8bbe34fbd8e91ae53}{INNSBRUCK, Austria (AP) --- Skiing power couple Mikaela Shiffrin and Aleksander Aamodt Kilde have announced they're engaged to be married. Shiffrin, a two-time Olympic champion who has won a record 97 World Cup races, holds her ring up to...}

\entryitemWithDescription{\hskip 0pt{}2 Muslim women were forced to remove hijabs for mug shots. NYC will pay \$17.5M to settle their suit}{https://apnews.com/article/b8c74c66ae5de7c9218ff8f9191d44ba}{NEW YORK (AP) --- New York City has agreed to pay \$17.5 million to settle a lawsuit filed by two Muslim women who were forced to remove their head coverings to be photographed after they were arrested. The class-action lawsuit was filed...}

\entryitemWithDescription{\hskip 0pt{}Small plane clips 2 vehicles as it lands on North Carolina highway, but no injuries are reported}{https://apnews.com/article/cf9c55bc5011992a0a028f3e9346e4c4}{MONCURE, N.C. (AP) --- A small plane experiencing engine problems struck two vehicles as it landed on a highway near a North Carolina airport, but no injuries were reported, authorities said. The single-engine Lancair 360 with only the...}

\entryitemWithDescription{\hskip 0pt{}J\&J to pump another \$13B into its MedTech business with Shockwave deal}{https://apnews.com/article/fb308f70ee276b007fa759007913ee77}{Johnson \& Johnson is pumping more money into heart care with a roughly \$13-billion deal for Shockwave Medical, which specializes in technology that helps open clogged arteries. The health care giant said Friday that it will spend \$335...}

\entryitemWithDescription{\hskip 0pt{}A senior UK lawmaker fell victim to a sexting scam. His colleagues are being urged to go to police}{https://apnews.com/article/dd1673bdecf60301daa0648d680f3f9e}{LONDON (AP) --- British lawmakers who may have been targeted in a sexting scam were urged Friday to go to police, after a senior Conservative admitted disclosing the personal phone numbers of some colleagues to an unknown individual who...}

\entryitemWithDescription{\hskip 0pt{}Apple lays off more than 600 workers in California in its first major round of post-pandemic cuts}{https://apnews.com/article/9f10788b1d3552385ee8c7b20209ce17}{Apple is laying off more than 600 workers in California, marking the company's first big wave of post-pandemic job cuts amid a broader wave of tech industry consolidation. The iPhone maker notified 614 workers in multiple offices on March...}

\entryitemWithDescription{\hskip 0pt{}6 inmates who sued New York over its prison lockdown order will get to view solar eclipse after all}{https://apnews.com/article/44533719957e2999232597dcf327fd2d}{NEW YORK (AP) --- Six inmates who sued New York's corrections department over its decision to lock down prisons during next Monday's total solar eclipse will get to watch the celestial event after all. Lawyers for the six men incarcerated...}

\entryitemWithDescription{\hskip 0pt{}Thomas Gumbleton, Detroit Catholic bishop who opposed war and promoted social justice, dies at 94}{https://apnews.com/article/86eeb6953b7532249e6f0c0e48d688f3}{DETROIT (AP) --- Thomas Gumbleton, a Catholic bishop in Detroit who for decades was an international voice against war and racism and an advocate for labor and social justice, died Thursday. He was 94. Gumbleton's death was announced by...}

\entryitemWithDescription{\hskip 0pt{}Governor orders transit agency to drop bid to charge NYC Marathon \$750K for use of Verrazzano bridge}{https://apnews.com/article/33c9abe21e57228221af7c303ff29a11}{NEW YORK (AP) --- New York's governor on Thursday ordered the state's transit agency to drop efforts to impose a \$750,000 fee on the New York City Marathon for using the Verrazzano-Narrows Bridge. Democratic Gov. Kathy Hochul also...}

\entryitemWithDescription{\hskip 0pt{}Students walk out of schools across Alaska to protest the governor's veto of education package}{https://apnews.com/article/c158ccb8901d233674cbd2a8bfdd392d}{JUNEAU, Alaska (AP) --- Students in Alaska's capital walked out of school Thursday and marched through the halls of the statehouse to protest Republican Gov. Mike Dunleavy's latest education veto and the Legislature's failure to override...}