\entryitemWithDescription{\hskip 0pt{}3 caught in Florida Panhandle rip current die a day after couple drowns off state's Atlantic coast}{https://apnews.com/article/46e925504ad46cf653eb1bb09fc7496c}{PANAMA CITY BEACH, Fla. (AP) --- Three Alabama men who went for an evening swim shortly after arriving at a Florida Panhandle beach were caught in a rip current and died, authorities say. It was the latest in a rash of recent deaths in...}

\entryitemWithDescription{\hskip 0pt{}California boy, 4, who disappeared from campground found safe after 22 hours alone in wilderness}{https://apnews.com/article/b86780cd0c1367646d3c91bf30262eae}{FRESNO, Calif. (AP) --- A 4-year-old California boy who wandered away from a campground in the Sierra National Forest was found safe after spending 22 hours alone in the wilderness, authorities said. A search-and-rescue team of about 50...}

\entryitemWithDescription{\hskip 0pt{}Kylian Mbappé is getting used to his new mask ahead of France's game against Poland, teammate says}{https://apnews.com/article/0f69c6a0f691c7ce7c689b6560303fa0}{PADERBORN, Germany (AP) --- France captain Kylian Mbappé is getting used to wearing his new protective mask ahead of a possible return to play at Euro 2024 against Poland on Tuesday, his teammate Aurélien Tchouaméni said. Mbappé sat out...}

\entryitemWithDescription{\hskip 0pt{}`Inside Out 2' scores \$100M in its second weekend, setting records}{https://apnews.com/article/a60695cc07640226794b12c3a0017378}{NEW YORK (AP) --- Weekend number two was just as joyous for ``Inside Out 2.'' The Pixar sequel collected \$100 million in ticket sales in its second weekend, according to studio estimates Sunday, setting a new record for an animated movie...}

\entryitemWithDescription{\hskip 0pt{}Chicago's iconic `Bean' sculpture reopens to tourists after nearly a year of construction}{https://apnews.com/article/a312d27aa93f01f9f8df409354e40c88}{CHICAGO (AP) --- One of Chicago's most popular tourist attractions known as ``The Bean'' reopened to the public Sunday after nearly a year of renovations and construction. Construction started in August last year, and fencing around the...}

\entryitemWithDescription{\hskip 0pt{}Blue Jays' Orelvis Martínez gets 80-game drug suspension, 2 days after his major league debut}{https://apnews.com/article/7d0be9d018a1a973c0696c7b2bc6f56c}{NEW YORK (AP) --- Toronto Blue Jays infielder Orelvis Martínez was suspended for 80 games by Major League Baseball on Sunday following a positive test for the performance-enhancing drug Clomiphene, an announcement made two days after his...}

\entryitemWithDescription{\hskip 0pt{}Preppy, military and East-meets-West styles hit Paris Fashion Week shows}{https://apnews.com/article/d6e182d247f2e7a0770356ad5a8b82de}{PARIS (AP) --- Cultural fusions mixing Eastern and Western dress, as well as preppy and military styles hit Paris Fashion Weeks menswear shows on their final day. Here are some highlights of spring 2025 collections on Sunday: Sacai's...}

\entryitemWithDescription{\hskip 0pt{}A simple recipe for onigiri, or Japanese rice balls, with salted plums}{https://apnews.com/article/cba4010474c33d0382a84c828a6b3af0}{TOKYO (AP) --- Onigiri is a ball of rice with something inside, similar to how two slices of bread with something in between makes a sandwich. In the same way that just about every American has made and eaten a sandwich, so too have most...}

\entryitemWithDescription{\hskip 0pt{}A'ja Wilson and Caitlin Clark lead WNBA All-Star fan vote}{https://apnews.com/article/0b9b46d1403accb1d26511a769c3857a}{NEW YORK (AP) --- A'ja Wilson leads Caitlin Clark by just over a thousand votes in early fan voting for the WNBA All-Star Game, the league announced Friday. Clark's Indiana teammate Aliyah Boston is third, about 40,000 votes behind the...}

\entryitemWithDescription{\hskip 0pt{}38 dogs were close to drowning on a Mississippi lake. But some fishermen had quite a catch}{https://apnews.com/article/0fad270987a5750ebfecfc46fb62644c}{ATLANTA (AP) --- By the time fishermen spotted the first head bobbing above the water, the 38 dogs were exhausted and struggling to stay alive. The hound dogs had plunged into a large Mississippi lake while chasing a deer, a diversion...}

\entryitemWithDescription{\hskip 0pt{}Shiny monolith removed from mountains outside Las Vegas. How it got there still is a mystery}{https://apnews.com/article/ae6c044a719d9aee09916c59e886e04b}{LAS VEGAS (AP) --- A strange monolith found jutting out of the rocks in a remote mountain range near Las Vegas has been taken down by authorities. How it got there is still a mystery. ``It remains unknown how the item got to its location...}

\entryitemWithDescription{\hskip 0pt{}Retired Azzurri star Roberto Baggio robbed at home during Italy's loss to Spain}{https://apnews.com/article/3c3942887efd86af78b46c0bfb53d484}{ROME (AP) --- Retired Italy star Roberto Baggio was robbed at gunpoint at his home while watching the national team's game against Spain at the European Championship At least five armed robbers burst into Baggio's villa near the northern...}

\entryitemWithDescription{\hskip 0pt{}UK fans wonder if Taylor Swift will say 'So long, London' after Eras Tour}{https://apnews.com/article/6b25a44d14749d93d607064c77523151}{LONDON (AP) --- Taylor Swift fans enjoy parsing the singer-songwriter's lyrics for references to her romantic life and insights into her state of her mind. But the pop superstar's fans in the U.K. didn't have to listen closely to her...}